### 2017-01-09 reports/compoundPoisson/compoundPoisson.tex
compound Poisson progress report

\documentclass[a4paper]{proc}

\title{Parameter Estimation for the Compound Poisson Model}
\author{Sherman Ip \quad \today}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage{natbib}
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}

\DeclareMathOperator{\expfamily}{ExpFamily}
\DeclareMathOperator{\expectation}{\mathbb{E}}
\DeclareMathOperator{\variance}{\mathbb{V}ar}
\DeclareMathOperator{\cov}{\mathbb{C}ov}
\DeclareMathOperator{\corr}{\mathbb{C}orr}
\DeclareMathOperator{\bernoulli}{Bernoulli}
\DeclareMathOperator{\betaDist}{Beta}
\DeclareMathOperator{\dirichlet}{Dir}
\DeclareMathOperator{\bin}{Bin}
\DeclareMathOperator{\MN}{Multinomial}
\DeclareMathOperator{\prob}{\mathbb{P}}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\normal}{N}
\DeclareMathOperator{\gammaDist}{Gamma}
\DeclareMathOperator{\poisson}{Poisson}

\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\euler}{\mathrm{e}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\T}{^\textup{T}}
\newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
\newcommand{\BIC}{\textup{BIC}}

\newcommand{\vect}[1]{\mathbf{#1}}
\newcommand{\vectGreek}[1]{\boldsymbol{#1}}
\newcommand{\matr}[1]{\mathsf{#1}}

\begin{document}
\maketitle

\section{Introduction}
In the mini-project, a compound Poisson model was used to model the distribution of greyvalues in a pixel. The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to the energy spectrum. The greyvalue is then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.

Consider a pixel. Let $Y$ be the number of photons detected for that particular pixel. Let $U$ be the energy of a photon post-attenuation and is typically random, here it was assumed to be Normally distribued. Let $X$ be the greyvalue of that pixel. The model is hierarchical such that at the top layer
\begin{equation}
Y\sim\poisson\left(\nu\tau\right)
\end{equation}
\begin{equation}
U_i\sim\normal\left(\mu,\sigma^2\right) \quad \text{ for i.i.d. }i=1,2,3,\dotdotdot
\end{equation}
where $\nu$ is the rate of photon arrivals, $\tau$ is the time exposure, $\mu$ and $\sigma^2$ is the mean and variance of photon energy respectively. Then
\begin{equation}
X = \alpha\sum_{i=1}^Y U_i + e
\end{equation}
where $e\sim\normal(0,\beta^2)$, $\beta^2$ is the thermal noise variance and $\alpha$ is some constant and can be interpreted as the gain. It was shown that this model can be written down as a latent variable model such that 
\begin{equation}
Y\sim\poisson\left(\nu\tau\right)
\end{equation}
\begin{equation}
X|Y\sim\normal\left(\alpha\mu Y, \alpha^2\sigma^2 Y + \beta^2\right) \ .
\end{equation}

The model can be simplified by setting $\beta=0$. By doing so, the constant $\alpha$ becomes redundant as it can be simply absorbed by $\mu$ and $\sigma^2$. It was attempted to estimate the parameters $\nu$, $\mu$ and $\sigma^2$ for a given CT scan. An EM algorithm \cite{dempster1977maximum} was implemented but it suffered in the E step because the conditional expectation, that is $\expectation\left[Y|X\right]$ given the 3 parameters, was expressed as an infinite sum. Truncating the sum was not fesible because in some cases, a very large number of terms were needed to produce accurate results.

The main aims were to investigate the compound Poisson, approximations and methods for fitting it to data.

\section{Literature Review}
Compound Poisson was proposed to improve noise models in CT scans \cite{whiting2002signal}. Simple models have been used which assumed the greyvalues were Poisson distributed or Normally \cite{lu2002analytical} distributed. The compound Poisson improves on these models by considering the energy spectrum of x-ray quanta and integrating it into the x-ray detector \cite{whiting2006properties}. This has been useful in image reconstruction \cite{elbakri2003efficient}\cite{elbakri2002statistical}\cite{elbakri2001statistical}\cite{lasio2007statistical} and tested in experiments \cite{wang2008experimental}. The p.d.f.~of the greyvalues can be numerically obtained using the saddle point approximation for a given general energy spectrum \cite{elbakri2003efficient}.

A special case of the compound Poisson is the compound Poisson-Gamma model. The model is as follows:
\begin{equation}
Y\sim\poisson\left(\nu\tau\right)
\end{equation}
\begin{equation}
U\sim\gammaDist\left(\alpha,\lambda\right)
\end{equation}
\begin{equation}
X = \sum_{i=1}^Y U_i
\end{equation}
where $\alpha$ and $\lambda$ are the shape and rate parameters, $\nu$ is the photon rate and $\tau$ is the time exposure. Then it can be shown that
\begin{equation}
X|Y\sim\gammaDist\left(Y\alpha,\lambda\right) \ .
\end{equation}
This is special because the marginal $X$ is in the exponential family, more specifically in the Tweedie dispersion exponential family \cite{jorgensen1987exponential}.

It is very well known that the marginal $X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
\begin{equation}
M(\theta)=\expectation\left[\euler^{\theta X}\right] \ .
\end{equation}
Using the property of conditional expectations
\begin{equation*}
M(\theta)=\expectation\expectation\left[\euler^{\theta X}\right|Y]
\end{equation*}
and then the properties of the Gamma distribution
\begin{equation*}
M(\theta)=\expectation\left[\left(\frac{\lambda}{\lambda-\theta}\right)^{Y\alpha}\right] \ .
\end{equation*}
Finally using the m.g.f.~of the Poisson distribution
\begin{equation}
M(\theta)=\exp\left[\nu\tau\left(\left(\frac{\lambda}{\lambda-\theta}\right)^{\alpha}-1\right)\right] \ .
\end{equation}
Moments up to a number of orders then can be obtained. For example
\begin{equation}
\expectation\left[X\right]=\frac{\alpha\nu\tau}{\lambda}
\end{equation}
\begin{equation}
\variance\left[X\right]=\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}
\end{equation}
\begin{equation}
\expectation\left[(X-\mu)^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\nu\tau}{\lambda^3}
\end{equation}
where $\expectation\left[X\right]=\mu$.

For a given i.i.d.~random sample of compound Poisson-Gamma distributed data, the unknown parameters $\nu$, $\alpha$ and $\lambda$, can be estimated using method of moments. Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\mu\right)^j\right]$ for $j=2,3$. Then the estimators
\begin{equation}
\widehat{\nu}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\tau\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
\end{equation}
\begin{equation}
\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
\end{equation}
\begin{equation}
\widehat{\lambda}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
\end{equation}
are method of moments estimators of $\nu$, $\alpha$ and $\lambda$ respectively \cite{withers2011compound}. These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.

Estimation can also be done using the EM algorithm \cite{dempster1977maximum}, treating the random variable $Y$ to be latent. The problem with the EM algorithm is that the E step is not tractable. This problem can be tackled by truncating the infinite sum in a clever way so that the sum is over a number of high contributing terms to save computational cost \cite{dunn2005series}. Another way is to use MCMC in the E step \cite{booth1999maximizing}.

There exist approximate maximum log likelihood estimators. Under certain conditions, the random variable $X$ can be approximated using the Normal distribution and the likelihood can be maximised numerically. Another approximation is to use the saddle point approximation \cite{daniels1954saddlepoint} to approximate the p.d.f.~of $X$, thus an approximate likelihood can be obtained.

Lastly, because $X$ is in the dispersion exponential family, parameter estimation can be done through the GLM framework \cite{zhang2013likelihood}. The GLM framework and the saddlepoint approximation were used extensively for insurance claim data \cite{jorgensen1994fitting} \cite{jensen1991saddlepoint}.

\section{Probability Density Function}
The joint p.d.f.~$p_{X,Y}(x,y)$ has probability mass at $X=0$ and $Y=0$ with probability
\begin{equation}
\prob\left(X=0,Y=0\right)=\euler^{-\nu\tau} \ ,
\end{equation}
and continuous elsewhere
\begin{equation}
p_{X,Y}(x,y)=\frac{\lambda^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\lambda x}\euler^{-\nu\tau}\frac{(\nu\tau)^y}{y!}
\end{equation}
for $y=1,2,\dotdotdot$ and $x>0$. The marginal can be obtained by summing over all possible values of $y$. The marginal p.d.f.~has probability mass at $X=0$ with probability
\begin{equation}
\prob(X=0)=\euler^{-\nu\tau}
\end{equation}
and continuous elsewhere
\begin{equation}
p_{X}(x)=\sum_{y=1}^{\infty}\frac{\lambda^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\lambda x}\euler^{-\nu\tau}\frac{(\nu\tau)^y}{y!}
\end{equation}
for $x>0$. It is a mixture with one continuous component at $x>0$ and discrete mass at $x=0$. This makes the compound Poisson useful for modelling non-negative variables which can take values of 0. By inspection the marginal p.d.f.~cannot be written down in closed form.
\subsection{Normal Approximation}
The marginal p.d.f.~of $X$ can be approximated using the Normal distribution. Using the results of the mean and variance of $X$, the Normal approximation is
\begin{equation}
X\sim\normal\left(\frac{\alpha\nu\tau}{\lambda},\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}\right) \ .
\end{equation}
To assess when the Normal approximation is sensible to use can be done by investigating the m.g.f.~of $X$. The m.g.f.~can be written as
\begin{equation*}
M(\theta)=\exp\left[\nu\tau\left(\left(1-\frac{\theta}{\lambda}\right)^{-\alpha}-1\right)\right] \ .
\end{equation*}
Assuming $|\theta/\lambda|<1$ and using the binomial expansion
\begin{equation}
M(\theta)=\exp\left[\nu\tau\left(
\sum_{r=1}^{\infty}\frac{\theta^r}{r!\lambda^r}\prod_{t=1}^{r}(\alpha+t-1)
\right)\right] \ .
\end{equation}
This is similar to the m.g.f.~of the Normal distribution by considering the first 2 order terms
\begin{multline}
M(\theta)=\exp\left[\theta\frac{\alpha\nu\tau}{\lambda}+\frac{\theta^2}{2}\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}
\right.\\\left.
+\sum_{r=3}^\infty\nu\tau\frac{\theta^r}{r!\lambda^r}\prod_{t=1}^{r}(\alpha+t-1)
\right] \ .
\end{multline}
For the Normal approximation to be a good approximation, the third and higher order terms must be small. This can happen for large $\lambda$. In addition for large values of $\alpha$ 
\begin{equation}
\prod_{t=1}^{r}(\alpha+t-1)\approx\alpha^r \ .
\end{equation}
and this is smaller than the coefficient term $\prod_{t=1}^{r}(\alpha+t-1)$
\begin{equation}
\prod_{t=1}^{r}(\alpha+t-1) \geqslant \alpha^r \ .
\end{equation}
Thus large values of $\alpha$ slow down the relative growth of the $\prod_{t=1}^{r}(\alpha+t-1)$ term, perhaps justifying the Normal approximation.

A more general result can be obtained. This can be done by taking a Taylor expansion of the m.g.f.~of the gamma component in $M(\theta)$. That is let
\begin{equation}
M(\theta)=\exp\left[
\nu\tau\left(M_U(\theta)-1\right)
\right]
\end{equation}
where $M_U(\theta)$ is the m.g.f.~of $\gammaDist(\alpha,\lambda)$. Then taking the Taylor expansion
\begin{equation*}
M(\theta)=\exp\left[
\nu\tau\left(
\sum_{r=0}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}
-1
\right)
\right]
\end{equation*}
but because $M_U(0)=1$
\begin{equation}
M(\theta)=\exp\left[
\nu\tau
\sum_{r=1}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}
\right] \ .
\end{equation}
As before, this is similar to the m.g.f.~of the Normal distribution when considering the first 2 terms
\begin{multline}
M(\theta)=\exp\left[
\theta M_U'(0)\nu\tau+\frac{\theta^2}{2} M_U''(0)\nu\tau
\right.\\\left.+
\sum_{r=3}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}\nu\tau\right] \ .
\end{multline}
Thus for the Normal approximation to be good, the parameters $\alpha$ and $\lambda$ must be such that the third and higher moments of $\gammaDist(\alpha,\lambda)$ are much smaller than the first two moments.

\subsection{Saddle Point Approximation}
For a given m.g.f., that is
\begin{equation}
M(\theta)=\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x \ ,
\end{equation}
the saddle point approximation \cite{daniels1954saddlepoint} \cite{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddle point approximation is given as
\begin{equation}
p_X(x)\approx\left(2\pi K''(s)\right)^{-1/2}\exp\left[K(s)-sx\right]
\end{equation}
where $K(\theta) = \ln\left(M(\theta)\right)$, and $s=s(x)$ is the solution to the saddle point equation $K'(s)=x$.

For the compound Poisson-Gamma distribution, the saddle point approximation is given in Equation \eqref{eq:saddle_point_approx} and is valid only for $x>0$. The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary.

\begin{figure*}[htb]
\begin{multline}
p_X(x)\approx
\left(2\pi(\alpha+1)\right)^{-1/2}\left(\nu\tau\lambda^\alpha\alpha\right)^{1/(2(\alpha+1))}\euler^{-\nu\tau}
\\
\exp\left[
-\frac{\alpha+2}{2(\alpha+1)}\ln(x)-x\lambda+\left(\left(\frac{x\lambda}{\alpha}\right)^{\alpha}\nu\tau\right)^{1/(\alpha+1)}(\alpha+1)
\right]
\label{eq:saddle_point_approx}
\end{multline}
\end{figure*}

\subsection{Simulations}
Exact simulation of the compound Poisson distribution is easy, this is done by simulating the latent variable $Y$ and then simulating the observable given that latent variable, $X|Y$. An experiment was conducted to assess how good the density approximations are. This was done by simulating $10^4$ samples of a compound Poisson random variable, and then comparing the histogram of the samples with the density approximation. Three sets of parameters were chosen and the results are shown in Figure \ref{fig:histogram}.

For low $\nu\tau$, there is a chance of simulating zeros. The Normal approximation failed to capture the probability mass at zero because the Normal distribution was constrained to be symmetric. The saddlepoint approximation did capture probabilty mass at zero as shown by an increase in probability density towards zero. However for a distinct mixture looking compound Poisson, Figure \ref{fig:histogram} (d), the saddlepoint approxmation was not flexible enough to capture each individual peaks.

For the Normal looking compound Poisson, both approxmations performed well.
\begin{figure*}
\centerline{
	\centering
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_1.eps}
        \caption{Normal approximation: $\nu\tau=1$, $\alpha=1$, $\lambda=1$}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_1.eps}
        \caption{Saddlepoint approximation: $\nu\tau=1$, $\alpha=1$, $\lambda=1$}
    \end{subfigure}
}
\centerline{
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_2.eps}
        \caption{Normal approximation: $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_2.eps}
        \caption{Saddlepoint approximation: $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
    \end{subfigure}
}
\centerline{
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_3.eps}
        \caption{Normal approximation: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_3.eps}
        \caption{Saddlepoint approximation: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
    \end{subfigure}
}
\caption{A sample of $10^4$ compound Poisson random variables was simulated. The histogram of the samples was plotted along with the density approxmation.}
\label{fig:histogram}
\end{figure*}

\section{Parameter estimation}
The saddlepoint approxmation did capture the probabilty mass at zero, however the formula for the density approxmation does not support zero. As a result, the saddlepoint approxmation may not be suited to approximate the likelihood when there is a good chance of obtaining zeros in the data. A way around it is to adjust the data by adding a very small constant to all zeros in the data.

An experiment was conducted to optimise the saddle point likelihood approximation numerically using the quasi-Newton method. For a given set of compound Poisson parameters, this was done by simulating 100 i.i.d.~samples. Any zeros in the sample were converted to a small constant, the constant being 1/8th of the minimum of all non-zero data in the sample, this was done to make the approximated likelihood evaluable. The likelihood was then optimised using \texttt{MATLAB}'s \texttt{fminunc} function with the default settings. The initial value was set at the true value to see how much the optimiser diverges from the true value. This was repeated 1\,000 times to obtain an empirical sampling distribution.

2 sets of parameters, carried forward from the previous section were used: $\{\nu\tau=3,\alpha=400,\lambda=100\}$ and $\{\nu\tau=500,\alpha=80,\lambda=2\}$. Figure \ref{fig:sampling_dist} shows the empirical sampling distribution from the experiment. For these particular examples, the estimators appeared to be unbiased with nice behaving distributions and finite variance. However for the $\{\nu\tau=500,\alpha=80,\lambda=2\}$ case, the variance looks too small to be true. It was found that the estimator was extremely sensitive to the initial value and the optimiser may not moved much from the initial value, this seems to be the case here.

\begin{figure*}
\centerline{
	\centering
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_nu.eps}
        \caption{$\nu\tau$ estimates for $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_nu.eps}
        \caption{$\nu\tau$ estimates for  $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
    \end{subfigure}
}
\centerline{
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_alpha.eps}
        \caption{$\alpha$ estimates for  $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_alpha.eps}
        \caption{$\alpha$ estimates for $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
    \end{subfigure}
}
\centerline{
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_lambda.eps}
        \caption{$\lambda$ estimates for $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_lambda.eps}
        \caption{$\lambda$ estimates for $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
    \end{subfigure}
}
\caption{Sampling distribution of the maximum saddlepoint approximated likelihood estimators. Dotted line represent the true value.}
\label{fig:sampling_dist}
\end{figure*}

Figure \ref{fig:lnL} shows a plot of a typical log likelihood in the 3 parameter space. The log likelihood looks shallow and perhaps the optimiser in \texttt{MATLAB} may have struggled to improve estimations near the true value.

\begin{figure}
\centerline{\centering
\includegraphics[width=0.5\textwidth]{../figures/compoundPoisson/log_likelihood.eps}}
\caption{An example of the log likelihood of a sample of compound Poisson random variables with parameters: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
\label{fig:lnL}
\end{figure}

\section{Future work}
The \texttt{R} package \texttt{cplm} \cite{zhang2013likelihood} numerically estimate parameters for the compound Poisson in the GLM framework. However for large parameters, there were numerical problems and the estimators' performance were hit and miss. Future work will reply on this package and the saddlepoint approximation to estimate parameters for the compound Poisson. Numerical problems can come from ill-conditioned variables and variables need to be scaled. One useful property of the compound Poisson is that the parameter $\lambda$ can absorb any scaling by a constant. That is if one can express a compound Poisson random variable as
\begin{equation}
X\sim\text{CompoundPoisson}\left(\nu\tau,\alpha,\lambda\right)
\end{equation}
then for a positive constant $k$
\begin{equation}
kX\sim\text{CompoundPoisson}\left(\nu\tau,\alpha,\lambda/k\right) \ .
\end{equation}

\bibliographystyle{unsrt}
\bibliography{../bib}

\end{document}

### 2017-01-09 reports/compoundPoisson/compoundPoisson.tex
compound Poisson proof read

@@
 \title{Parameter Estimation for the Compound Poisson Model}
-\author{Sherman Ip \quad \today}
+\author{Sherman Ip \quad January 9, 2017}
 
@@
 The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to the energy spectrum.
-The greyvalue is then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.
+The greyvalue was then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.
 
@@
 
-For a given i.i.d.~random sample of compound Poisson-Gamma distributed data, the unknown parameters $\nu$, $\alpha$ and $\lambda$, can be estimated using method of moments.
+For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, the unknown parameters $\nu$, $\alpha$ and $\lambda$, can be estimated using method of moments.
 Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\mu\right)^j\right]$ for $j=2,3$.
@@
 However for large parameters, there were numerical problems and the estimators' performance were hit and miss.
-Future work will reply on this package and the saddlepoint approximation to estimate parameters for the compound Poisson.
+Future work will rely on this package and the saddlepoint approximation to estimate parameters for the compound Poisson.
 Numerical problems can come from ill-conditioned variables and variables need to be scaled.

### 2017-01-09 reports/compoundPoisson/compoundPoisson.tex
compoundPoisson report, spell check.

@@
 The Normal approximation failed to capture the probability mass at zero because the Normal distribution was constrained to be symmetric.
-The saddlepoint approximation did capture probabilty mass at zero as shown by an increase in probability density towards zero.
-However for a distinct mixture looking compound Poisson, Figure \ref{fig:histogram} (d), the saddlepoint approxmation was not flexible enough to capture each individual peaks.
+The saddlepoint approximation did capture probability mass at zero as shown by an increase in probability density towards zero.
+However for a distinct mixture looking compound Poisson, Figure \ref{fig:histogram} (d), the saddlepoint approximation was not flexible enough to capture each individual peaks.
 
-For the Normal looking compound Poisson, both approxmations performed well.
+For the Normal looking compound Poisson, both approximation performed well.
 \begin{figure*}
@@
 \section{Parameter estimation}
-The saddlepoint approxmation did capture the probabilty mass at zero, however the formula for the density approxmation does not support zero.
+The saddlepoint approximation did capture the probability mass at zero, however the formula for the density approximation does not support zero.
 As a result, the saddlepoint approxmation may not be suited to approximate the likelihood when there is a good chance of obtaining zeros in the data.

### 2017-03-06 reports/progress_1/progress_1.tex
Started on 18 month progress report.

--- 2017-01-09 reports/compoundPoisson/compoundPoisson.tex
@@
 
-\title{Parameter Estimation for the Compound Poisson Model}
-\author{Sherman Ip \quad \today}
+\title{18 month progress report}
+\author{Sherman Ip \quad Statistics \quad University of Warwick \quad March 31, 2017}
 
@@
 
+\begin{abstract}
+
+\end{abstract}
+
 \section{Introduction}
-In the mini-project, a compound Poisson model was used to model the distribution of greyvalues in a pixel.
-The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to the energy spectrum.
-The greyvalue is then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.
+3D printing, or additive layer manufacturing, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.
+Recently it has been commercialised and has served purposes in the medical field and engineering.
+The need for detecting defects from 3D printing is required in order to do quality control, especially if the 3D printed object is used for something critical for example body parts.
 
-Consider a pixel.
-Let $Y$ be the number of photons detected for that particular pixel.
-Let $U$ be the energy of a photon post-attenuation and is typically random, here it was assumed to be Normally distribued.
-Let $X$ be the greyvalue of that pixel.
-The model is hierarchical such that at the top layer
-\begin{equation}
-Y\sim\poisson\left(\nu\tau\right)
-\end{equation}
-\begin{equation}
-U_i\sim\normal\left(\mu,\sigma^2\right) \quad \text{ for i.i.d. }i=1,2,3,\dotdotdot
-\end{equation}
-where $\nu$ is the rate of photon arrivals, $\tau$ is the time exposure, $\mu$ and $\sigma^2$ is the mean and variance of photon energy respectively. Then
-\begin{equation}
-X = \alpha\sum_{i=1}^Y U_i + e
-\end{equation}
-where $e\sim\normal(0,\beta^2)$, $\beta^2$ is the thermal noise variance and $\alpha$ is some constant and can be interpreted as the gain.
-It was shown that this model can be written down as a latent variable model such that
-\begin{equation}
-Y\sim\poisson\left(\nu\tau\right)
-\end{equation}
-\begin{equation}
-X|Y\sim\normal\left(\alpha\mu Y, \alpha^2\sigma^2 Y + \beta^2\right) \ .
-\end{equation}
+X-ray computed tomography (CT) scans can be used to take images of a rotating 3D printed sample to obtain images at multiple angles.
+These x-ray images then can be combined to form a 3D projection and the detection of defects can start.
+However due to the random nature of x-ray photons in its production in an x-ray tube and attenuation, sources of error or noise is introduced.
+In order to do defect detection in a statistical manner, sources of error must be considered.
 
-The model can be simplified by setting $\beta=0$.
-By doing so, the constant $\alpha$ becomes redundant as it can be simply absorbed by $\mu$ and $\sigma^2$.
-It was attempted to estimate the parameters $\nu$, $\mu$ and $\sigma^2$ for a given CT scan.
-An EM algorithm \cite{dempster1977maximum} was implemented but it suffered in the E step because the conditional expectation, that is $\expectation\left[Y|X\right]$ given the 3 parameters, was expressed as an infinite sum.
-Truncating the sum was not fesible because in some cases, a very large number of terms were needed to produce accurate results.
+A mini-project on this topic was completed at 12 months of the PhD \cite{ip2016inside}.
+The main aim of that project was to conduct exploratory data analysis on a dataset of 100 images of an x-ray CT scan of a stationary 3D printed cuboid.
+Linear regressions were used to model the relationship between the variance and the mean greyvalue of each pixel.
+Separately latent variable models were fitted (or at least attempted) on the scans, such as PCA, factor analysis and the compound Poisson, to find sources of variance.
 
-The main aims were to investigate the compound Poisson, approximations and methods for fitting it to data.
-
-\section{Literature Review}
-Compound Poisson was proposed to improve noise models in CT scans \cite{whiting2002signal}.
-Simple models have been used which assumed the greyvalues were Poisson distributed or Normally \cite{lu2002analytical} distributed.
-The compound Poisson improves on these models by considering the energy spectrum of x-ray quanta and integrating it into the x-ray detector \cite{whiting2006properties}.
-This has been useful in image reconstruction \cite{elbakri2003efficient}\cite{elbakri2002statistical}\cite{elbakri2001statistical}\cite{lasio2007statistical} and tested in experiments \cite{wang2008experimental}.
-The p.d.f.~of the greyvalues can be numerically obtained using the saddle point approximation for a given general energy spectrum \cite{elbakri2003efficient}.
-
-A special case of the compound Poisson is the compound Poisson-Gamma model. The model is as follows:
-\begin{equation}
-Y\sim\poisson\left(\nu\tau\right)
-\end{equation}
-\begin{equation}
-U\sim\gammaDist\left(\alpha,\lambda\right)
-\end{equation}
-\begin{equation}
-X = \sum_{i=1}^Y U_i
-\end{equation}
-where $\alpha$ and $\lambda$ are the shape and rate parameters, $\nu$ is the photon rate and $\tau$ is the time exposure. Then it can be shown that
-\begin{equation}
-X|Y\sim\gammaDist\left(Y\alpha,\lambda\right) \ .
-\end{equation}
-This is special because the marginal $X$ is in the exponential family, more specifically in the Tweedie dispersion exponential family \cite{jorgensen1987exponential}.
-
-It is very well known that the marginal $X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
-\begin{equation}
-M(\theta)=\expectation\left[\euler^{\theta X}\right] \ .
-\end{equation}
-Using the property of conditional expectations
-\begin{equation*}
-M(\theta)=\expectation\expectation\left[\euler^{\theta X}\right|Y]
-\end{equation*}
-and then the properties of the Gamma distribution
-\begin{equation*}
-M(\theta)=\expectation\left[\left(\frac{\lambda}{\lambda-\theta}\right)^{Y\alpha}\right] \ .
-\end{equation*}
-Finally using the m.g.f.~of the Poisson distribution
-\begin{equation}
-M(\theta)=\exp\left[\nu\tau\left(\left(\frac{\lambda}{\lambda-\theta}\right)^{\alpha}-1\right)\right] \ .
-\end{equation}
-Moments up to a number of orders then can be obtained. For example
-\begin{equation}
-\expectation\left[X\right]=\frac{\alpha\nu\tau}{\lambda}
-\end{equation}
-\begin{equation}
-\variance\left[X\right]=\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}
-\end{equation}
-\begin{equation}
-\expectation\left[(X-\mu)^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\nu\tau}{\lambda^3}
-\end{equation}
-where $\expectation\left[X\right]=\mu$.
-
-For a given i.i.d.~random sample of compound Poisson-Gamma distributed data, the unknown parameters $\nu$, $\alpha$ and $\lambda$, can be estimated using method of moments.
-Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\mu\right)^j\right]$ for $j=2,3$.
-Then the estimators
-\begin{equation}
-\widehat{\nu}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\tau\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
-\end{equation}
-\begin{equation}
-\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
-\end{equation}
-\begin{equation}
-\widehat{\lambda}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
-\end{equation}
-are method of moments estimators of $\nu$, $\alpha$ and $\lambda$ respectively \cite{withers2011compound}.
-These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
-
-Estimation can also be done using the EM algorithm \cite{dempster1977maximum}, treating the random variable $Y$ to be latent.
-The problem with the EM algorithm is that the E step is not tractable.
-This problem can be tackled by truncating the infinite sum in a clever way so that the sum is over a number of high contributing terms to save computational cost \cite{dunn2005series}.
-Another way is to use MCMC in the E step \cite{booth1999maximizing}.
-
-There exist approximate maximum log likelihood estimators.
-Under certain conditions, the random variable $X$ can be approximated using the Normal distribution and the likelihood can be maximised numerically.
-Another approximation is to use the saddle point approximation \cite{daniels1954saddlepoint} to approximate the p.d.f.~of $X$, thus an approximate likelihood can be obtained.
-
-Lastly, because $X$ is in the dispersion exponential family, parameter estimation can be done through the GLM framework \cite{zhang2013likelihood}.
-The GLM framework and the saddlepoint approximation were used extensively for insurance claim data \cite{jorgensen1994fitting} \cite{jensen1991saddlepoint}.
-
-\section{Probability Density Function}
-The joint p.d.f.~$p_{X,Y}(x,y)$ has probability mass at $X=0$ and $Y=0$ with probability
-\begin{equation}
-\prob\left(X=0,Y=0\right)=\euler^{-\nu\tau} \ ,
-\end{equation}
-and continuous elsewhere
-\begin{equation}
-p_{X,Y}(x,y)=\frac{\lambda^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\lambda x}\euler^{-\nu\tau}\frac{(\nu\tau)^y}{y!}
-\end{equation}
-for $y=1,2,\dotdotdot$ and $x>0$. The marginal can be obtained by summing over all possible values of $y$. The marginal p.d.f.~has probability mass at $X=0$ with probability
-\begin{equation}
-\prob(X=0)=\euler^{-\nu\tau}
-\end{equation}
-and continuous elsewhere
-\begin{equation}
-p_{X}(x)=\sum_{y=1}^{\infty}\frac{\lambda^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\lambda x}\euler^{-\nu\tau}\frac{(\nu\tau)^y}{y!}
-\end{equation}
-for $x>0$.
-It is a mixture with one continuous component at $x>0$ and discrete mass at $x=0$.
-This makes the compound Poisson useful for modelling non-negative variables which can take values of 0.
-By inspection the marginal p.d.f.~cannot be written down in closed form.
-\subsection{Normal Approximation}
-The marginal p.d.f.~of $X$ can be approximated using the Normal distribution. Using the results of the mean and variance of $X$, the Normal approximation is
-\begin{equation}
-X\sim\normal\left(\frac{\alpha\nu\tau}{\lambda},\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}\right) \ .
-\end{equation}
-To assess when the Normal approximation is sensible to use can be done by investigating the m.g.f.~of $X$. The m.g.f.~can be written as
-\begin{equation*}
-M(\theta)=\exp\left[\nu\tau\left(\left(1-\frac{\theta}{\lambda}\right)^{-\alpha}-1\right)\right] \ .
-\end{equation*}
-Assuming $|\theta/\lambda|<1$ and using the binomial expansion
-\begin{equation}
-M(\theta)=\exp\left[\nu\tau\left(
-\sum_{r=1}^{\infty}\frac{\theta^r}{r!\lambda^r}\prod_{t=1}^{r}(\alpha+t-1)
-\right)\right] \ .
-\end{equation}
-This is similar to the m.g.f.~of the Normal distribution by considering the first 2 order terms
-\begin{multline}
-M(\theta)=\exp\left[\theta\frac{\alpha\nu\tau}{\lambda}+\frac{\theta^2}{2}\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}
-\right.\\\left.
-+\sum_{r=3}^\infty\nu\tau\frac{\theta^r}{r!\lambda^r}\prod_{t=1}^{r}(\alpha+t-1)
-\right] \ .
-\end{multline}
-For the Normal approximation to be a good approximation, the third and higher order terms must be small. This can happen for large $\lambda$. In addition for large values of $\alpha$ 
-\begin{equation}
-\prod_{t=1}^{r}(\alpha+t-1)\approx\alpha^r \ .
-\end{equation}
-and this is smaller than the coefficient term $\prod_{t=1}^{r}(\alpha+t-1)$
-\begin{equation}
-\prod_{t=1}^{r}(\alpha+t-1) \geqslant \alpha^r \ .
-\end{equation}
-Thus large values of $\alpha$ slow down the relative growth of the $\prod_{t=1}^{r}(\alpha+t-1)$ term, perhaps justifying the Normal approximation.
-
-A more general result can be obtained. This can be done by taking a Taylor expansion of the m.g.f.~of the gamma component in $M(\theta)$. That is let
-\begin{equation}
-M(\theta)=\exp\left[
-\nu\tau\left(M_U(\theta)-1\right)
-\right]
-\end{equation}
-where $M_U(\theta)$ is the m.g.f.~of $\gammaDist(\alpha,\lambda)$. Then taking the Taylor expansion
-\begin{equation*}
-M(\theta)=\exp\left[
-\nu\tau\left(
-\sum_{r=0}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}
--1
-\right)
-\right]
-\end{equation*}
-but because $M_U(0)=1$
-\begin{equation}
-M(\theta)=\exp\left[
-\nu\tau
-\sum_{r=1}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}
-\right] \ .
-\end{equation}
-As before, this is similar to the m.g.f.~of the Normal distribution when considering the first 2 terms
-\begin{multline}
-M(\theta)=\exp\left[
-\theta M_U'(0)\nu\tau+\frac{\theta^2}{2} M_U''(0)\nu\tau
-\right.\\\left.+
-\sum_{r=3}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}\nu\tau\right] \ .
-\end{multline}
-Thus for the Normal approximation to be good, the parameters $\alpha$ and $\lambda$ must be such that the third and higher moments of $\gammaDist(\alpha,\lambda)$ are much smaller than the first two moments.
-
-\subsection{Saddle Point Approximation}
-For a given m.g.f., that is
-\begin{equation}
-M(\theta)=\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x \ ,
-\end{equation}
-the saddle point approximation \cite{daniels1954saddlepoint} \cite{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddle point approximation is given as
-\begin{equation}
-p_X(x)\approx\left(2\pi K''(s)\right)^{-1/2}\exp\left[K(s)-sx\right]
-\end{equation}
-where $K(\theta) = \ln\left(M(\theta)\right)$, and $s=s(x)$ is the solution to the saddle point equation $K'(s)=x$.
-
-For the compound Poisson-Gamma distribution, the saddle point approximation is given in Equation \eqref{eq:saddle_point_approx} and is valid only for $x>0$.
-The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary.
-
-\begin{figure*}[htb]
-\begin{multline}
-p_X(x)\approx
-\left(2\pi(\alpha+1)\right)^{-1/2}\left(\nu\tau\lambda^\alpha\alpha\right)^{1/(2(\alpha+1))}\euler^{-\nu\tau}
-\\
-\exp\left[
--\frac{\alpha+2}{2(\alpha+1)}\ln(x)-x\lambda+\left(\left(\frac{x\lambda}{\alpha}\right)^{\alpha}\nu\tau\right)^{1/(\alpha+1)}(\alpha+1)
-\right]
-\label{eq:saddle_point_approx}
-\end{multline}
-\end{figure*}
-
-\subsection{Simulations}
-Exact simulation of the compound Poisson distribution is easy, this is done by simulating the latent variable $Y$ and then simulating the observable given that latent variable, $X|Y$.
-An experiment was conducted to assess how good the density approximations are.
-This was done by simulating $10^4$ samples of a compound Poisson random variable, and then comparing the histogram of the samples with the density approximation.
-Three sets of parameters were chosen and the results are shown in Figure \ref{fig:histogram}.
-
-For low $\nu\tau$, there is a chance of simulating zeros.
-The Normal approximation failed to capture the probability mass at zero because the Normal distribution was constrained to be symmetric.
-The saddlepoint approximation did capture probabilty mass at zero as shown by an increase in probability density towards zero.
-However for a distinct mixture looking compound Poisson, Figure \ref{fig:histogram} (d), the saddlepoint approxmation was not flexible enough to capture each individual peaks.
-
-For the Normal looking compound Poisson, both approxmations performed well.
-\begin{figure*}
-\centerline{
-	\centering
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_1.eps}
-        \caption{Normal approximation: $\nu\tau=1$, $\alpha=1$, $\lambda=1$}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_1.eps}
-        \caption{Saddlepoint approximation: $\nu\tau=1$, $\alpha=1$, $\lambda=1$}
-    \end{subfigure}
-}
-\centerline{
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_2.eps}
-        \caption{Normal approximation: $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_2.eps}
-        \caption{Saddlepoint approximation: $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
-    \end{subfigure}
-}
-\centerline{
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_3.eps}
-        \caption{Normal approximation: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_3.eps}
-        \caption{Saddlepoint approximation: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
-    \end{subfigure}
-}
-\caption{A sample of $10^4$ compound Poisson random variables was simulated. The histogram of the samples was plotted along with the density approxmation.}
-\label{fig:histogram}
-\end{figure*}
-
-\section{Parameter estimation}
-The saddlepoint approxmation did capture the probabilty mass at zero, however the formula for the density approxmation does not support zero.
-As a result, the saddlepoint approxmation may not be suited to approximate the likelihood when there is a good chance of obtaining zeros in the data.
-A way around it is to adjust the data by adding a very small constant to all zeros in the data.
-
-An experiment was conducted to optimise the saddle point likelihood approximation numerically using the quasi-Newton method.
-For a given set of compound Poisson parameters, this was done by simulating 100 i.i.d.~samples.
-Any zeros in the sample were converted to a small constant, the constant being 1/8th of the minimum of all non-zero data in the sample, this was done to make the approximated likelihood evaluable.
-The likelihood was then optimised using \texttt{MATLAB}'s \texttt{fminunc} function with the default settings.
-The initial value was set at the true value to see how much the optimiser diverges from the true value.
-This was repeated 1\,000 times to obtain an empirical sampling distribution.
-
-2 sets of parameters, carried forward from the previous section were used: $\{\nu\tau=3,\alpha=400,\lambda=100\}$ and $\{\nu\tau=500,\alpha=80,\lambda=2\}$.
-Figure \ref{fig:sampling_dist} shows the empirical sampling distribution from the experiment.
-For these particular examples, the estimators appeared to be unbiased with nice behaving distributions and finite variance.
-However for the $\{\nu\tau=500,\alpha=80,\lambda=2\}$ case, the variance looks too small to be true.
-It was found that the estimator was extremely sensitive to the initial value and the optimiser may not moved much from the initial value, this seems to be the case here.
-
-\begin{figure*}
-\centerline{
-	\centering
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_nu.eps}
-        \caption{$\nu\tau$ estimates for $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_nu.eps}
-        \caption{$\nu\tau$ estimates for  $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
-    \end{subfigure}
-}
-\centerline{
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_alpha.eps}
-        \caption{$\alpha$ estimates for  $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_alpha.eps}
-        \caption{$\alpha$ estimates for $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
-    \end{subfigure}
-}
-\centerline{
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_lambda.eps}
-        \caption{$\lambda$ estimates for $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_lambda.eps}
-        \caption{$\lambda$ estimates for $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
-    \end{subfigure}
-}
-\caption{Sampling distribution of the maximum saddlepoint approximated likelihood estimators. Dotted line represent the true value.}
-\label{fig:sampling_dist}
-\end{figure*}
-
-Figure \ref{fig:lnL} shows a plot of a typical log likelihood in the 3 parameter space.
-The log likelihood looks shallow and perhaps the optimiser in \texttt{MATLAB} may have struggled to improve estimations near the true value.
-
-\begin{figure}
-\centerline{\centering
-\includegraphics[width=0.5\textwidth]{../figures/compoundPoisson/log_likelihood.eps}}
-\caption{An example of the log likelihood of a sample of compound Poisson random variables with parameters: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
-\label{fig:lnL}
-\end{figure}
-
-\section{Future work}
-The \texttt{R} package \texttt{cplm} \cite{zhang2013likelihood} numerically estimate parameters for the compound Poisson in the GLM framework.
-However for large parameters, there were numerical problems and the estimators' performance were hit and miss.
-Future work will reply on this package and the saddlepoint approximation to estimate parameters for the compound Poisson.
-Numerical problems can come from ill-conditioned variables and variables need to be scaled.
-One useful property of the compound Poisson is that the parameter $\lambda$ can absorb any scaling by a constant.
-That is if one can express a compound Poisson random variable as
-\begin{equation}
-X\sim\text{CompoundPoisson}\left(\nu\tau,\alpha,\lambda\right)
-\end{equation}
-then for a positive constant $k$
-\begin{equation}
-kX\sim\text{CompoundPoisson}\left(\nu\tau,\alpha,\lambda/k\right) \ .
-\end{equation}
+After the mini-project, the main aims during the PhD was to extend the mini-project by developing a statistic to aid in defect detection while considering the randomness of photons.
+Another aim was to build a model for the noise.
 

### 2017-03-07 reports/progress_1/progress_1.tex
In progress report, added section about the data.

@@
 
-X-ray computed tomography (CT) scans can be used to take images of a rotating 3D printed sample to obtain images at multiple angles.
+X-ray computed tomography (CT) scans can be used to take images of a rotating 3D printed sample to obtain images of the sample at multiple angles.
 These x-ray images then can be combined to form a 3D projection and the detection of defects can start.
-However due to the random nature of x-ray photons in its production in an x-ray tube and attenuation, sources of error or noise is introduced.
+However due to the random nature of x-ray photons in its production in an x-ray tube and attenuation from the x-ray tube to the detector, sources of error or noise is introduced.
 In order to do defect detection in a statistical manner, sources of error must be considered.
@@
 
+This report will outline a pre-process method called shading correction and it was investigated how it affected the mean and variance relationship.
+The mean and variance relationship was modelled using GLM with different link functions.
+After finding a good model for the mean and variance, a statistics was developed to compare two images in the face of uncertainty.
+Lastly the compound Poisson was studied.
+
+\section{About the Data}
+Data was collected prior to the mini-project.
+20 black/grey/white (b/g/w) images were collected on 14/03/16 at around 1250.
+The b/g/w images are images obtained from the x-ray detector when exposed to x-rays at different settings.
+About 2 hours later at 1503, 100 images of a 3D printed cuboid (or sample) were taken.
+These images were obtained from the x-ray detector when exposed to x-rays with the sample between the x-ray source and detector.
+The detector used was the Perkin Elmer XRD 1621 digital X-ray detector, with settings shown in Table \ref{table:settings}.
+
+\begin{table*}
+	\centering
+	\begin{tabular}{c|c|c|c}
+		& Voltage (kV) & Power (W) & Exposure time (ms) \\
+		\hline
+		Black & 0.0 & 0.0 & 1000\\
+		Grey & 85 & 1.7 & 1000\\
+		White & 85 & 6.8 & 1000 \\
+		Sample & 100 & 33 & 500
+	\end{tabular}
+	\caption{Setting of the x-ray CT scan when collecting images from the x-ray detector. Error bars were not given and the number of significant figures shown are as given.}
+	\label{table:settings}
+\end{table*}
+
+The images were $(1\,996\times1\,996)$ pixels in size and in greyscale with 16 bits, in other words each pixel can have greyvalues which take integer values form 0 to $2^{16}-1$ inclusive.
+The greyvalues are in arbitrary units.
+The images are shown in Figure \ref{fig:image} and the histogram of greyvalues are shown in Figure \ref{fig:hist}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.45\textwidth]{../figures/data/140316_image.eps}
+	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
+	\label{fig:image}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.45\textwidth]{../figures/data/140316_histo.png}
+	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
+	\label{fig:hist}
+\end{figure}
+
+\section{Shading Correction}
+
+\section{Mean/Variance Relationship}
+
+\section{$Z$ Statistic}
+
+\section{Compound Poisson}
+
 \bibliographystyle{unsrt}

### 2017-03-09 reports/progress_1/progress_1.tex
In progress report, started on shading correction section.

@@
 The main aim of that project was to conduct exploratory data analysis on a dataset of 100 images of an x-ray CT scan of a stationary 3D printed cuboid.
-Linear regressions were used to model the relationship between the variance and the mean greyvalue of each pixel.
+Linear regressions were used to model the relationship between the variance and the mean grey value of each pixel.
 Separately latent variable models were fitted (or at least attempted) on the scans, such as PCA, factor analysis and the compound Poisson, to find sources of variance.
@@
 20 black/grey/white (b/g/w) images were collected on 14/03/16 at around 1250.
-The b/g/w images are images obtained from the x-ray detector when exposed to x-rays at different settings.
+The b/g/w images are images obtained from the x-ray detector when exposed to x-rays at different settings, they are useful for calibrating the detector thus b/g/w images can be called reference images.
 About 2 hours later at 1503, 100 images of a 3D printed cuboid (or sample) were taken.
@@
 		\hline
-		Black & 0.0 & 0.0 & 1000\\
+		Black & 0 & 0 & 1000\\
 		Grey & 85 & 1.7 & 1000\\
@@
 
-The images were $(1\,996\times1\,996)$ pixels in size and in greyscale with 16 bits, in other words each pixel can have greyvalues which take integer values form 0 to $2^{16}-1$ inclusive.
-The greyvalues are in arbitrary units.
-The images are shown in Figure \ref{fig:image} and the histogram of greyvalues are shown in Figure \ref{fig:hist}.
+The images were $(1\,996\times1\,996)$ pixels in size and are in greyscale with 16 bits, in other words each pixel can have grey values which take integer values from 0 to $2^{16}-1$ inclusive.
+The grey values are in arbitrary units.
+The images are shown in Figure \ref{fig:image} and the histogram of grey values are shown in Figure \ref{fig:hist}.
 
@@
 \section{Shading Correction}
+The x-ray detector is made up 32 panels, arranged in 2 rows and 16 columns.
+Unfortunately these panels do obviously show up in the b/g/w images which consequently create panel-wise effects in the image of the sample, as shown in Figure \ref{fig:image}.
+The effects can be described as introducing a gradient to the grey values within panels and perhaps between panels and globally.
+The aim of shading correction is to remove these effects to estimate the image of the scan if it were to have none of these effects.
+
+Let $N(x,y)$ be the grey value of the pixel at position $(x,y)$ in the obtained image.
+Similarly let $U(x,y)$ be they grey value of pixels of the shading-free image.
+The shading effects can be modelled using a linear relationship
+\begin{equation}
+N(x,y) = U(x,y)b(x,y) + a(x,y)
+\end{equation} 
+where $b(x,y)$ is the multiplicative effect and $a(x,y)$ is the additive effect \cite{young2000shading}.
+If it is possible to estimate the functions $b(x,y)$ and $a(x,y)$ using the estimators $\widehat{b}(x,y)$ and $\widehat{a}(x,y)$ respectively, then the shading-free image can be estimated using the estimator
+\begin{equation}
+\widehat{U}(x,y) = \frac{N(x,y)-\widehat{a}(x,y)}{\widehat{b}(x,y)} \times c_1 + c_2
+\end{equation}
+where $c_1$ and $c_2$ are some constants.
+One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the mean black and white (b/w) images.
+Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean black and white images respectively, then the estimators for $b(x,y)$ and $a(x,y)$ are
+\begin{equation}
+\widehat{b}(x,y) = \overline{W}(x,y) - \overline{B}(x,y)
+\end{equation}
+and
+\begin{equation}
+\widehat{a}(x,y) = \overline{B}(x,y)
+\end{equation}
+respectively.
+
+\subsection{Methods}
+A new shading correction will be proposed here which extends the shading correction method described in the previous section by considering the grey images.
+The objective of shading correction is to predict the shading free image given the scan image, this can be done using linear regression of the form
+\begin{equation}
+U(x,y) = N(x,y)\beta(x,y)+\alpha(x,y) \ .
+\end{equation}
+The shading free image is not truly known, but one should expect the b/g/w shading free images should be completely flat.
+By using the obtained b/g/w images to estimate the parameters of the linear regression, this becomes a regression problem.
+
+Let $R_\text{b}(x,y)$, $R_\text{g}(x,y)$ and $R_\text{w}(x,y)$ be the grey value of the pixel, at position $(x,y)$, of the sample mean b/g/w images respectively.
+Let these images have $h$ rows and $w$ columns.
+The shading free b/g/w images should be completely flat, in other words all the pixels should have the same grey value.
+A good guess what that grey value should be would be the sample mean of the grey values within the b/g/w images $\overline{R}_\text{b}$, $\overline{R}_\text{g}$ and $\overline{R}_\text{w}$ where
+\begin{equation}
+\overline{R}_j=\frac{\sum_{x=1}^w\sum_{y=1}^hR_j(x,y)}{n}
+\end{equation}
+for $j\in\{\text{b},\text{g},\text{w}\}$. By treating these within image sample mean grey values as the true shading free grey value, then the problem becomes a linear regression with 3 data points.
+
+Let the global sample mean be
+\begin{equation}
+\overline{R}=\frac{\overline{R}_\text{b} + \overline{R}_\text{g} + \overline{R}_\text{w}}{3}
+\end{equation}
+and the between image sample mean to be
+\begin{equation}
+\overline{R}_B(x,y)=\frac{R_\text{b}(x,y) + R_\text{g}(x,y) + R_\text{w}(x,y)}{3} \ ,
+\end{equation}
+then the estimators for $\beta(x,y)$ and $\alpha(x,y)$ are
+\begin{multline}
+\widehat{\beta}(x,y)=
+\\
+\frac{\sum_{j\in\{\text{b},\text{g},\text{w}\}}\left(R_j(x,y)-\overline{R}_B(x,y)\right)\left(\overline{R}_j-\overline{R}\right)}{\sum_{j\in\{\text{b},\text{g},\text{w}\}}\left(R_j(x,y)-\overline{R}_B(x,y)\right)^2}
+\end{multline}
+and
+\begin{equation}
+\widehat{\alpha}(x,y) = \overline{R}-\widehat{\beta}(x.y)\overline{R}_B(x,y) 
+\end{equation}
+respectively.
+
+Suppose now an image to be shading corrected is obtained $N(x,y)$. The shading free image $U(x,y)$ can be estimated by interpolating the linear regression
+\begin{equation}
+\widehat{U}(x,y) = \widehat{\beta}(x,y)N(x,y)+\widehat{\alpha}(x,y) \ .
+\end{equation}
+This can be extended to fewer or more than 3 reference images.
+The disadvantage of having more reference images is that it does cost time to take more scans.
+Shading correction which uses b/g/w images shall be referred to as b/g/w shading correction.
+Similarly shading correction which uses only the b/w images shall be referred to as b/w shading correction.
+
+Figure \ref{fig:shadingCorrection} shows an example of a scan before and after b/g/w shading correction.
+By inspection, the post shading correction background is smoother because the panel effects appeared to be gone, meeting the objective of shading correction.
+Figure \ref{fig:shadingCorrection_grad} shows the values of $\widehat{\beta}(x,y)$.
+By inspection there is some curvature in the $\widehat{\beta}$ image, with high gradients in the corners, in addition to panel-wise gradients.
+Problems occur if the reference images behave differently from expected.
+For example some pixels may be dead and do not vary at all, this resulted in infinite gradients highlighted by red circles in the figure.
+In order to combat this, any pixels with undefined grey values post shading correction were replaced with the sample median of its 8 nearest neighbours.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block.eps}
+		\caption{Shading uncorrected}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block_shadingCorrected.eps}
+		\caption{b/g/w shading correction}
+	\end{subfigure}
+	\caption{A x-ray CT scan image before and after b/g/w shading correction.}
+	\label{fig:shadingCorrection}
+\end{figure*}
+
+\begin{figure}
+	\includegraphics[width=0.45\textwidth]{../figures/shadingCorrection/gradient.png}
+	\caption{The gradient used in b/g/w shading correction. Red circles indicate infinite gradient, green circles indicate negative gradient.}
+	\label{fig:shadingCorrection_grad}
+\end{figure}
+
+\subsection{Experiments}
 

### 2017-03-10 reports/progress_1/progress_1.tex
In progress report, added polynomial fit in shading correction section.

@@
 
+To avoid dealing with dead pixels, a method was considered which smoothed the reference images prior to any shading correction parameter estimation.
+The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically.
+Second order panel-wise surface polynomials were fitted to the b/g/w images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}.
+The standardised residuals from the panel-wise fit are shown in Figure \ref{fig:polynomial_residual}.
+A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit.
+In the black and grey images, the residuals show a global ring which is very unusual for the black image because it is detecting no x-rays at all.
+The b/g/w residuals all show vertical stripes.
+The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_black.eps}
+		\caption{Black}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_grey.eps}
+		\caption{Grey}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_white.eps}
+		\caption{White}
+	\end{subfigure}
+	\caption{Second order panel-wise surface polynomials fit on the reference images.}
+	\label{fig:polynomial_shadingCorrection}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/residual_black.png}
+		\caption{Black}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/residual_grey.png}
+		\caption{Grey}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/residual_white.png}
+		\caption{White}
+	\end{subfigure}
+	\caption{Standardised residuals from the second order panel-wise surface polynomials fit on the reference images.}
+	\label{fig:polynomial_residual}
+\end{figure*}
+
 \subsection{Experiments}

### 2017-03-10 shadingCorrector/polynomial_shading_script.m

@@ -16,26 +16,41 @@ block_data = BlockData_140316('../data/140316');
 %set up shading correction for the data set
 block_data.addShadingCorrector(@ShadingCorrector_polynomial,true,[2,2,2]);
 
+reference_name = {'black','white','grey'};
+
 %for each reference image
 for i_index = 1:3
     %plot polynomial surface
-    figure;
+    fig = figure;
+    fig.Position(3:4) = [560,420];
     imagesc(block_data.shading_corrector.reference_image_array(:,:,i_index));
     colormap gray;
+    colorbar;
+    axis(gca,'off');
+    saveas(gca,strcat('reports/figures/shadingCorrection/polynomial_',reference_name{i_index},'.eps'));
     %plot residual
-    figure;
+    fig = figure;
+    fig.Position(3:4) = [560,420];
     ax = imagesc_truncate(block_data.shading_corrector.getZResidualImage(i_index));
     ax.CLim = [-2,2];
     colorbar;
+    axis(gca,'off');
+    saveas(gca,strcat('reports/figures/shadingCorrection/residual_',reference_name{i_index},'.png'));
 end
 
 %plot the shading corrected sample scan image
-figure;
+fig = figure;
+fig.Position(3:4) = [560,420];
 imagesc_truncate(block_data.loadSample(1));
 colorbar;
 colormap gray;
+axis(gca,'off');
+saveas(gca,'reports/figures/shadingCorrection/polynomial_shadingCorrection.eps');
 
 %plot the gradient in the shading correction
-figure;
+fig = figure;
+fig.Position(3:4) = [560,420];
 imagesc_truncate(block_data.shading_corrector.b_array);
 colorbar;
+saveas(gca,'reports/figures/shadingCorrection/polynomial_gradient.png');
+axis(gca,'off');

### 2017-03-15 reports/progress_1/progress_1.tex
In progress report, finished section on shading correction. Shading correction ANOVA is now an experiment.

@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
-	\includegraphics[width = 0.45\textwidth]{../figures/data/140316_image.eps}
+	\includegraphics[width = 0.9\textwidth]{../figures/data/140316_image.eps}
 	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
 	\label{fig:image}
-\end{figure}
+\end{figure*}
 
@@
 	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_shadingCorrection.eps}
+		\caption{b/g/w 2nd order polynomial shading correction}
+	\end{subfigure}
 	\caption{A x-ray CT scan image before and after b/g/w shading correction.}
@@
 
-\begin{figure}
-	\includegraphics[width=0.45\textwidth]{../figures/shadingCorrection/gradient.png}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{../figures/shadingCorrection/gradient.png}
+		\caption{b/g/w shading correction}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width=\textwidth]{../figures/shadingCorrection/polynomial_gradient.png}
+		\caption{b/g/w 2nd order polynomial shading correction}
+	\end{subfigure}
 	\caption{The gradient used in b/g/w shading correction. Red circles indicate infinite gradient, green circles indicate negative gradient.}
 	\label{fig:shadingCorrection_grad}
-\end{figure}
+\end{figure*}
 
@@
 The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects.
+Higher order polynomials can be considered but overfitting may be possible, as a result of higher order polynomials attempting to capture all the characteristics of the b/g/w images.
+
+Shading correction which uses the fitted polynomials as reference images will be referred to as b/g/w 2nd order polynomial shading correction.
+The gradient parameter for the b/g/w 2nd order polynomial shading correction is shown in Figure \ref{fig:shadingCorrection_grad}.
+It is smoother and robust because the gradients are of sensible values, for example no infinite values.
+The resulting shading correction is shown in Figure \ref{fig:shadingCorrection}.
+This method can be advantageous as the panel-wise 2nd order polynomial only captures gradients of each panel and  smooths out clusters of bad behaving pixels as shown in the residuals.
+As a result, the shading correction is smoother between pixels because the bad behaving pixels do not impact as much in the interpolation of the linear regression.
 
@@
 
+An experiment was conducted to assess the performance of shading correction.
+The methodology behind it is that shading correction applied on the reference images should remove shading effects and produce an image which is noisy but all the pixels should have the same mean grey value.
+
+The 20 b/g/w images were spilt into a training set and test set of equal size randomly.
+The training set was used to estimate the parameters for shading corrections.
+Afterwards, shading correction was applied to each image in the test set producing 10 shading corrected reference images of each grey scale.
+The within pixel variance and between pixel variance was recorded, exactly the same as ANOVA treating each pixel as a group.
+For each pixel to have the same mean grey value, the within and between pixel variance should be similar.
+The experiment was repeated 20 times by repeating the assignment of the training and test set.
+
+Figure \ref{fig:shadingCorr_bgw} shows a sample of reference images post shading correction.
+Without shading correction, the shading effects were clear.
+With b/w and b/g/w shading correction, the reference images appeared flatter.
+The flatness of the black and grey image depended if the grey images were used when training the shading correction.
+The b/g/w 2nd order polynomial shading correction retained some effects not captured by the panel wise polynomial fits.
+This can be tell because the shading corrected images were very similar to the residual plots in Figure \ref{fig:polynomial_residual}.
+
+Table \ref{table:bgw_anova} shows the within and between pixel variance of the grey values.
+The table shown that b/w and b/g/w shading correction does make an improvement because it brings the within and between pixel variances closer together.
+The performance of shading correction on the black and grey images appeared to depend if the grey images were used in training the shading correction.
+The b/g/w 2nd order polynomial shading correction does perform by bringing the within and between pixel variances closer together but not as much as b/w and b/g/w shading correction.
+
+In conclusion, b/w and b/g/w shading correction do perform well because there was evidence they are attempting to iron out all the pixel grey values to have the same mean.
+The b/g/w 2nd order polynomial shading correction does its job.
+However because the panel wise polynomial under fitted and did not capture all the shading effects, the shading correction also did not capture all the shading effects.
+
+The use of grey images in training the shading correction can be useful.
+It appeared that by considering the grey images, the shading correction performance on certain grey values was traded for other grey values.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/shadingCorrection_no_shad.png}
+		\caption{No shading correction}
+	\end{subfigure}
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/shadingCorrection_bw.png}
+		\caption{b/w shading correction}
+	\end{subfigure}
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/shadingCorrection_bgw.png}
+		\caption{b/g/w shading correction}
+	\end{subfigure}
+		\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/shadingCorrection_polynomial.png}
+		\caption{b/g/w 2nd order polynomial shading correction}
+	\end{subfigure}
+	\caption{Shading correction applied on reference images from a test set. A training set was used to train the shading correction.}
+	\label{fig:shadingCorr_bgw}
+\end{figure*}
+
+\begin{table*}
+	\centering
+	\begin{tabular}{c|c|c}
+		\input{../tables/bgwShadingANOVA_no_shad.tex_table}
+	\end{tabular}
+	\\
+	\vspace{.25cm}
+	a) No shading correction
+	\\\vspace{.5cm}
+	\begin{tabular}{c|c|c}
+		\input{../tables/bgwShadingANOVA_bw.tex_table}
+	\end{tabular}
+	\\
+	\vspace{.25cm}
+	b) b/w shading correction
+	\\\vspace{.5cm}
+	\begin{tabular}{c|c|c}
+		\input{../tables/bgwShadingANOVA_bgw.tex_table}
+	\end{tabular}
+	\\
+	\vspace{.25cm}
+	c) b/g/w shading correction
+	\\\vspace{.5cm}
+	\begin{tabular}{c|c|c}
+		\input{../tables/bgwShadingANOVA_polynomial.tex_table}
+	\end{tabular}
+	\\
+	\vspace{.25cm}
+	d) b/g/w 2nd order polynomial shading correction
+	\caption{Quartiles of the within pixel and between pixel variance after 20 repeats of the experiment.}
+	\label{table:bgw_anova}
+\end{table*}
+
 \section{Mean/Variance Relationship}

### 2017-03-15 meanVar/Experiment_GLM_meanVar_trainingTest.m

@@ -1,6 +1,22 @@
 classdef Experiment_GLM_meanVar_trainingTest < Experiment
-    %EXPERIMENT_GLM_MEANVAR_TRAININGTEST Summary of this class goes here
-    %   Detailed explanation goes here
+    %EXPERIMENT_GLM_MEANVAR_TRAININGTEST Assess the performance of GLM fit on mean var data
+    %   The images are spilt into 2 parts, training and test. GLM iss used
+    %   to model the variance and mean relationship, with variance as the
+    %   response. The response is gamma randomlly distributed with known
+    %   shape parameter.   
+    %
+    %   Only the top half of the images were used, this is to avoid the
+    %   form. In addition, the images were thresholded to only consider
+    %   pixels from the 3d printed sample.
+    %
+    %   The training set is used to train the glm, which is then used to
+    %   predict the variance of the test set. The training and mean
+    %   standarised residuals are plotted, that is the residual divided by
+    %   the std of gamma.
+    %
+    %   Different shading corrections, polynomial orders and link functions
+    %   were considered. The experiment was repeated by reassigning the
+    %   training and test set.
     
     %MEMBER VARIABLES
     properties
@@ -185,12 +201,7 @@ classdef Experiment_GLM_meanVar_trainingTest < Experiment
                         training_table(i_glm+1,2+i_shading) = 'NaN';
                     %else all training mse isn't nan, quote the quartile of the training mse
                     else
-                        [q2, up_error, down_error, E] = quoteQuartileError(training_mse_i,100);
-                        if E == '0'
-                            training_table(i_glm+1,2+i_shading) = strcat('$',q2,'\substack{+',up_error,'\\ -',down_error,'}$');
-                        else
-                            training_table(i_glm+1,2+i_shading) = strcat('$(',q2,'\substack{+',up_error,'\\ -',down_error,'})\times 10^{',E,'}$');
-                        end
+                        training_table(i_glm+1,2+i_shading) = quoteQuartileError(training_mse_i,100);
                     end
 
                     %get the test mse
@@ -222,7 +233,7 @@ classdef Experiment_GLM_meanVar_trainingTest < Experiment
     methods(Static)
         
         %GLOBAL: Call this to start experiment automatically
-        function GLOBAL()
+        function main()
             %repeat the experiment this many times
             n_repeat = 100;
             %set up the experiment

### 2017-03-15 shadingCorrector/Experiment_bgwShadingANOVA.m

@@ -1,0 +1,229 @@
+classdef Experiment_bgwShadingANOVA < Experiment
+    %EXPERIMENT_BGWSHADINGANOVA Experiment for using ANOVA to assess the
+    %performance of shading correction
+        %Use n_train b/g/w images to train the shading corrector, then uses the
+        %reminder of b/g/w images to do shading correction on. The variance
+        %between and within pixel is recorded. Repeated n_repeat times
+    
+    %MEMBER VARIABLES
+    properties
+        
+        %cell of arrays, one array for each shading corrector
+        %each array is 3 dimensional, containing variances
+            %dim 1: for each repeat (n_repeat length)
+            %dim 2: within pixel, between pixel (length 2)
+            %dim 3: b/g/w (length 2 or 3)
+        std_array;
+        
+        %cell of shading corrected b/g/w images
+            %dim 1: b/g/w
+            %dim 2: for each shading corrector
+        bgw_shading_array;
+        %dim 2 pointer for bgw_shading_array
+        shading_correction_pointer;
+        
+        %object containing the data
+        block_data;
+        
+        %the size of the training set
+        n_train;
+        
+        %random stream
+        rand_stream;
+        
+    end
+    
+    %METHODS
+    methods
+        
+        %CONSTRUCTOR
+        function this = Experiment_bgwShadingANOVA()
+            %superclass
+            this@Experiment('bgwShadingANOVA');
+            %assign member variables
+            this.n_train = 10;
+            this.block_data = BlockData_140316('../data/140316');
+            this.rand_stream = RandStream('mt19937ar','Seed',uint32(227482200));
+        end
+        
+        %DECLARE RESULT ARRAY
+        %PARAMETERS:
+            %n_repeat: number of times to repeat the experiment
+        function declareResultArray(this,n_repeat)
+            %assign member variables
+            this.std_array = cell(4,1);
+            this.bgw_shading_array = cell(3,4);
+            for i = 1:4
+                this.std_array{i} = zeros(n_repeat,2,3);
+            end
+            this.shading_correction_pointer = 1;
+        end
+        
+        %DO EXPERIMENT (one iteration)
+        function doExperiment(this)
+            %use its random stream
+            RandStream.setGlobalStream(this.rand_stream);
+            %for the 4 different types of shading correction, get the
+            %within and between pixel variance and save it to the member
+            %variable std_array
[…]

### 2017-03-16 reports/progress_1/progress_1.tex
In progress report, added references.

@@
 \section{Introduction}
-3D printing, or additive layer manufacturing, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.
-Recently it has been commercialised and has served purposes in the medical field and engineering.
+3D printing, or additive layer manufacturing \cite{kodama1981automatic} \cite{wong2012review}, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.
+Recently it has been commercialised and has served purposes in the medical field \cite{kang20163d} and engineering \cite{wong2012review}.
 The need for detecting defects from 3D printing is required in order to do quality control, especially if the 3D printed object is used for something critical for example body parts.
 
-X-ray computed tomography (CT) scans can be used to take images of a rotating 3D printed sample to obtain images of the sample at multiple angles.
+X-ray computed tomography (CT) \cite{hounsfield1980computed} \cite{michael2001x} \cite{cantatore2011introduction} scans can be used to take images of a rotating 3D printed sample to obtain images of the sample at multiple angles.
 These x-ray images then can be combined to form a 3D projection and the detection of defects can start.
@@
 \section{Shading Correction}
-The x-ray detector is made up 32 panels, arranged in 2 rows and 16 columns.
-Unfortunately these panels do obviously show up in the b/g/w images which consequently create panel-wise effects in the image of the sample, as shown in Figure \ref{fig:image}.
+The x-ray detector was made up 32 panels, arranged in 2 rows and 16 columns.
+Unfortunately these panels can be observed in the b/g/w images as a result of panel-wise effects in the image of the sample, as shown in Figure \ref{fig:image}.
 The effects can be described as introducing a gradient to the grey values within panels and perhaps between panels and globally.
@@
 \end{equation} 
-where $b(x,y)$ is the multiplicative effect and $a(x,y)$ is the additive effect \cite{young2000shading}.
+where $b(x,y)$ is the multiplicative effect and $a(x,y)$ is the additive effect \cite{munzenmayer2003enhancing}.
 If it is possible to estimate the functions $b(x,y)$ and $a(x,y)$ using the estimators $\widehat{b}(x,y)$ and $\widehat{a}(x,y)$ respectively, then the shading-free image can be estimated using the estimator
@@
 \end{equation}
-respectively.
+respectively \cite{young2000shading}.
 
@@
 
-To avoid dealing with dead pixels, a method was considered which smoothed the reference images prior to any shading correction parameter estimation.
+To avoid dealing with dead pixels \cite{brettschneider2014spatial}, a method was considered which smoothed the reference images prior to any shading correction parameter estimation.
 The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically.
@@
 
-In conclusion, b/w and b/g/w shading correction do perform well because there was evidence they are attempting to iron out all the pixel grey values to have the same mean.
-The b/g/w 2nd order polynomial shading correction does its job.
-However because the panel wise polynomial under fitted and did not capture all the shading effects, the shading correction also did not capture all the shading effects.
-
-The use of grey images in training the shading correction can be useful.
-It appeared that by considering the grey images, the shading correction performance on certain grey values was traded for other grey values.
-
 \begin{figure*}
@@
 
+In conclusion, b/w and b/g/w shading correction do perform well because there was evidence they are attempting to iron out all the pixel grey values to have the same mean.
+The b/g/w 2nd order polynomial shading correction does its job.
+However because the panel wise polynomial under fitted and did not capture all the shading effects, the shading correction also did not capture all the shading effects.
+
+The use of grey images in training the shading correction can be useful.
+It appeared that by considering the grey images, the shading correction performance on certain grey values was traded for other grey values.
+
+Additional methods for shading correction could be considered such as fitting a global polynomial in addition to the panel wise polynomials to the reference images.
+There exist methods which do not require reference images at all, such as entropy minimisation \cite{likar2000retrospective}, which could be studied further and may be useful here.
+
 \section{Mean/Variance Relationship}

### 2017-03-16 reports/progress_1/progress_1.tex
In progress report, started section on mean variance relationship.

@@
 \section{Mean/Variance Relationship}
+The variance can be used to quantify the uncertainty of a grey value in a pixel.
+The purpose of modelling the mean and variance relationship of the grey value of a pixel is to be able to predict the grey value variance of each pixel for a single scan.
+This then can be used for inference when comparing a scan with the CAM model.
+A basic linear regression was conducted in the mini-project \cite{ip2016inside}, here generalised linear models (GLM) \cite{nelder1972generalized} \cite{mccullagh1984generalized} was used to model the mean and variance relationship.
+
+The object of interest is the 3D printed sample.
+In the mini-project, it was found the background and the foam holding the 3D printed sample have different mean variance relationships \cite{ip2016inside}.
+Thus to model the mean variance relationship of the 3D printed sample, the 3D printed sample was segmented from the background and the foam.
+This was done by cropping the scans of the 3D printed sample in half, removing the bottom half containing the foam.
+Next a threshold was conducted using the following procedure:
+\begin{itemize}
+	\item For each of the 20 b/g/w images, apply a panel wise median filter of size $3\times3$. Pixels outside the panels were symmetrically extended.
+	\item Use these filtered reference images for shading correction.
+	\item Take the mean over all shading corrected scans.
+	\item Keep pixels with grey values less than $4.7\times 10^4$.
+\end{itemize}
+This method of segmentation was developed by informal experimentation.
+The resulting segmented image is shown in Figure \ref{fig:segment}.
+Other segmentation methods could be considered but further study of other methods may not be necessary here.
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.45 \textwidth]{../figures/meanVar/segment.eps}
+	\caption{Resulting segmentation of the 3D printed sample}
+	\label{fig:segment}
+\end{figure}
+
+The within pixel mean and variance grey value were estimated using the standard unbiased estimators.
+A few assumptions were made to justify the use of GLM to model the mean variance relationship.
+Firstly, it was assumed the standard error from estimating the mean was negligible.
+Secondly, it was assumed for a given pixel, the grey value from each scan were Normal i.i.d.
+Following from these assumptions, the sample variance is Gamma distributed with shape parameter $(n-1)/2$ where $n$ is the number of scans used to estimate the variance.
+Furthermore the standard error of the sample variance is proportional to $(n-1)^{-1/2}$, meaning the sample variance is more precise when more and more images were used to estimate the variance.
+This was experimentally shown in Figure \ref{fig:meanVar_sampleSize}, the spread of the sample variance decreased as $n$ increased.
+
+GLM can model the sample variance as the response variable being Gamma distributed, explained by the sample mean through a link function $g(\text{variance})$.
+Fitting of the model was done using iterative re-weighted least squares.
+The dispersion parameter need not to be estimated because the shape parameter is known.
+A linear fit using the identity link did show that the Gamma response captured the spread of the sample variance for different sample means, this is shown in Figure \ref{fig:meanVar_sampleSize}.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_25.eps}
+		\caption{$n=25$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_50.eps}
+		\caption{$n=50$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_75.eps}
+		\caption{$n=75$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_100.eps}
+		\caption{$n=100$}
+	\end{subfigure}
+	\caption{Mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample.
+The sample variance and sample mean were estimated using $n$ scans selected at random without replacement.
+A Gamma GLM was fitted with the identity link.
+The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
+	\label{fig:meanVar_sampleSize}
+\end{figure*}
+
+\subsection{Experiments}
 

### 2017-03-20 reports/progress_1/progress_1.tex
In progress report, draft finished on mean variance relationship.

@@
 
+The systematic component is defined as a linear combination of the sample mean features, for example $\beta_0+\beta_1\text{mean}^p$ where $\beta_0$ and $\beta_1$ are constants to be estimated and $p$ is the polynomial order.
+In GLM, the link function equates to the systematic function to form a relationship between the mean and variance.
+3 link functions were considered, identity, log and inverse, with the resulting mean and variance relationship shown in Table \ref{table:link_functions} and some fits in Figure \ref{fig:meanVar_link}.
+
+\begin{table}
+	\centering
+	\begin{tabular}{c|c}
+	Link function & Relationship \\
+	\hline
+	Identity & $\text{variance} = \beta_0+\beta_1\text{mean}^p$ \\
+	Log & $\text{variance} = \exp{\left(\beta_0+\beta_1\text{mean}^p\right)}$ \\
+	Inverse & $\text{variance} = \left(\beta_0+\beta_1\text{mean}^p\right)^{-1}$
+	\end{tabular}
+	\caption{Link functions and the resulting mean and variance relationship when using polynomial features.}
+	\label{table:link_functions}
+\end{table}
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_identity.eps}
+		\caption{Identity link, order 1}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_log.eps}
+		\caption{Log link, order -1}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_1.eps}
+		\caption{Inverse link, order -1}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_2.eps}
+		\caption{Inverse link, order -2}
+	\end{subfigure}
+	\caption{Shading uncorrected mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample.
+A Gamma GLM was fitted with different link functions and polynomial order.
+The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
+	\label{fig:meanVar_link}
+\end{figure*}
+
+Different shading corrections had an effect on the mean variance relationship, as shown in Figure \ref{fig:meanVar_shadingCorrection}.
+Due to some misbehaving pixels in the reference images, grey value outliers were possible such as negative values.
+Pixels with grey values less than $5.8\times 10^3$ or more than $6.6\times 10^4$ were considered outliers.
+Outliers were replaced by the median of its 8 nearest neighbours.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_no_shad.eps}
+		\caption{No shading correction}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bw.eps}
+		\caption{b/w shading correction}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bgw.eps}
+		\caption{b/g/w shading correction}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_polynomial.eps}
+		\caption{b/g/w 2nd order polynomial shading correction}
+	\end{subfigure}
+	\caption{Post shading correction mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample.
+A Gamma GLM was fitted with the identity link.
+The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
+	\label{fig:meanVar_shadingCorrection}
+\end{figure*}
+
 \subsection{Experiments}
+
+An experiment was conducted to assess the GLM fit on the mean and variance data for different link functions, polynomial orders and shading corrections.
+
+For a given link function, polynomial order and shading correction, the 100 images of the 3D printed sample were spilt into two equally sized sets: the training set and the test set.
+The within pixel sample mean and sample variance  grey value was estimated for both the training set and test set separately.
+The GLM was fitted onto the mean/variance data obtained from the training set.
+The fitted model was then used to predict the variance given the mean on the test set.
+The predicted variance given the mean then can be compared with the sample variance.
+
+Metrics such as the mean squared error can be used to assess how good the prediction is.
+However it should be noted that there is sampling error in the sample variance and the magnitude of the error varies for different means.
+In order to take the varying sampling error into account, the mean standardised squared error (MSSE) was used to assess the performance of the fitted GLM predicting the variance given the mean on the test set.
+The errors were standardised by dividing by the standard deviation of the GLM response.
+
+The experiment was repeated 100 times by reassigning the training and test set.
+
+The training and test MSSE are shown in Tables \ref{table:training} and \ref{table:test}.
+By using b/g/w shading correction, the test MSSE improved and suggests that b/g/w shading correction aids in variance prediction.
+b/w shading correction increased the MSSE by a magnitude of $\sim\times10^3$.
+A quick residual plot in Figure \ref{fig:glm_residual} showed that residuals were more centred at zero for b/g/w shading correction compared to b/w shading correction.
+
+The performance of the different link functions were very similar and no performance was gained by using higher order polynomials.
+
+\begin{table*}
+\centerline{
+\begin{tabular}{c|c|c|c|c}
+\input{../tables/GLM_meanVar_trainingTest_training.tex_table}
+\end{tabular}}
+\caption{Training mean squared standardised error from fitting GLM onto the mean/variance training set. Values stated are the quartiles from 100 repeats.}
+\label{table:training}
+\end{table*}
+
+\begin{table*}
+\centerline{
+\begin{tabular}{c|c|c|c|c}
+\input{../tables/GLM_meanVar_trainingTest_test.tex_table}
+\end{tabular}
+}
+\caption{Test mean squared standardised error from using GLM to predict variance given mean from the test set. Values stated are the quartiles from 100 repeats.}
+\label{table:test}
+\end{table*}
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/residual_no_shad.eps}
+		\caption{No shading correction}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bw.eps}
+		\caption{b/w shading correction}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bgw.eps}
+		\caption{b/g/w shading correction}
+	\end{subfigure}
+	\caption{Frequency density plot of the standardised residuals from predicting the variance given the mean of the test test using a training GLM with identity link function.}
+	\label{fig:glm_residual}
+\end{figure*}
+
+In conclusion it was found that b/g/w shading correction aid in variance prediction by making the mean variance data more linear.
+A simple identity link perform just as well as other link function which suggests a linear relationship between the variance and the mean.
 

### 2017-03-20 reports/progress_1/progress_1.tex
In progress report, added compound Poisson.

@@
 \section{Compound Poisson}
+In the mini-project, a compound Poisson model was used to model the distribution of greyvalues in a pixel.
+The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to the energy spectrum.
+The greyvalue was then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.
+
+Consider a pixel.
+Let $Y$ be the number of photons detected for that particular pixel.
+Let $U$ be the energy of a photon post-attenuation and is typically random, here it was assumed to be Normally distribued.
+Let $X$ be the greyvalue of that pixel.
+The model is hierarchical such that at the top layer
+\begin{equation}
+Y\sim\poisson\left(\nu\tau\right)
+\end{equation}
+\begin{equation}
+U_i\sim\normal\left(\mu,\sigma^2\right) \quad \text{ for i.i.d. }i=1,2,3,\dotdotdot
+\end{equation}
+where $\nu$ is the rate of photon arrivals, $\tau$ is the time exposure, $\mu$ and $\sigma^2$ is the mean and variance of photon energy respectively. Then
+\begin{equation}
+X = \alpha\sum_{i=1}^Y U_i + e
+\end{equation}
+where $e\sim\normal(0,\beta^2)$, $\beta^2$ is the thermal noise variance and $\alpha$ is some constant and can be interpreted as the gain.
+It was shown that this model can be written down as a latent variable model such that
+\begin{equation}
+Y\sim\poisson\left(\nu\tau\right)
+\end{equation}
+\begin{equation}
+X|Y\sim\normal\left(\alpha\mu Y, \alpha^2\sigma^2 Y + \beta^2\right) \ .
+\end{equation}
+
+The model can be simplified by setting $\beta=0$.
+By doing so, the constant $\alpha$ becomes redundant as it can be simply absorbed by $\mu$ and $\sigma^2$.
+It was attempted to estimate the parameters $\nu$, $\mu$ and $\sigma^2$ for a given CT scan.
+An EM algorithm \cite{dempster1977maximum} was implemented but it suffered in the E step because the conditional expectation, that is $\expectation\left[Y|X\right]$ given the 3 parameters, was expressed as an infinite sum.
+Truncating the sum was not fesible because in some cases, a very large number of terms were needed to produce accurate results.
+
+The main aims were to investigate the compound Poisson, approximations and methods for fitting it to data.
+
+\subsection{Literature Review}
+Compound Poisson was proposed to improve noise models in CT scans \cite{whiting2002signal}.
+Simple models have been used which assumed the greyvalues were Poisson distributed or Normally \cite{lu2002analytical} distributed.
+The compound Poisson improves on these models by considering the energy spectrum of x-ray quanta and integrating it into the x-ray detector \cite{whiting2006properties}.
+This has been useful in image reconstruction \cite{elbakri2003efficient}\cite{elbakri2002statistical}\cite{elbakri2001statistical}\cite{lasio2007statistical} and tested in experiments \cite{wang2008experimental}.
+The p.d.f.~of the greyvalues can be numerically obtained using the saddle point approximation for a given general energy spectrum \cite{elbakri2003efficient}.
+
+A special case of the compound Poisson is the compound Poisson-Gamma model. The model is as follows:
+\begin{equation}
+Y\sim\poisson\left(\nu\tau\right)
+\end{equation}
+\begin{equation}
+U\sim\gammaDist\left(\alpha,\lambda\right)
+\end{equation}
+\begin{equation}
+X = \sum_{i=1}^Y U_i
+\end{equation}
+where $\alpha$ and $\lambda$ are the shape and rate parameters, $\nu$ is the photon rate and $\tau$ is the time exposure. Then it can be shown that
+\begin{equation}
+X|Y\sim\gammaDist\left(Y\alpha,\lambda\right) \ .
+\end{equation}
+This is special because the marginal $X$ is in the exponential family, more specifically in the Tweedie dispersion exponential family \cite{jorgensen1987exponential}.
+
+It is very well known that the marginal $X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
+\begin{equation}
+M(\theta)=\expectation\left[\euler^{\theta X}\right] \ .
+\end{equation}
+Using the property of conditional expectations
+\begin{equation*}
+M(\theta)=\expectation\expectation\left[\euler^{\theta X}\right|Y]
+\end{equation*}
+and then the properties of the Gamma distribution
+\begin{equation*}
+M(\theta)=\expectation\left[\left(\frac{\lambda}{\lambda-\theta}\right)^{Y\alpha}\right] \ .
+\end{equation*}
+Finally using the m.g.f.~of the Poisson distribution
+\begin{equation}
+M(\theta)=\exp\left[\nu\tau\left(\left(\frac{\lambda}{\lambda-\theta}\right)^{\alpha}-1\right)\right] \ .
+\end{equation}
+Moments up to a number of orders then can be obtained. For example
+\begin{equation}
+\expectation\left[X\right]=\frac{\alpha\nu\tau}{\lambda}
+\end{equation}
+\begin{equation}
+\variance\left[X\right]=\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}
+\end{equation}
+\begin{equation}
+\expectation\left[(X-\mu)^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\nu\tau}{\lambda^3}
+\end{equation}
+where $\expectation\left[X\right]=\mu$.
+
+For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, the unknown parameters $\nu$, $\alpha$ and $\lambda$, can be estimated using method of moments.
+Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\mu\right)^j\right]$ for $j=2,3$.
+Then the estimators
+\begin{equation}
+\widehat{\nu}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\tau\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
+\end{equation}
+\begin{equation}
+\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
+\end{equation}
+\begin{equation}
+\widehat{\lambda}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
+\end{equation}
+are method of moments estimators of $\nu$, $\alpha$ and $\lambda$ respectively \cite{withers2011compound}.
+These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+
+Estimation can also be done using the EM algorithm \cite{dempster1977maximum}, treating the random variable $Y$ to be latent.
+The problem with the EM algorithm is that the E step is not tractable.
+This problem can be tackled by truncating the infinite sum in a clever way so that the sum is over a number of high contributing terms to save computational cost \cite{dunn2005series}.
+Another way is to use MCMC in the E step \cite{booth1999maximizing}.
+
+There exist approximate maximum log likelihood estimators.
+Under certain conditions, the random variable $X$ can be approximated using the Normal distribution and the likelihood can be maximised numerically.
+Another approximation is to use the saddle point approximation \cite{daniels1954saddlepoint} to approximate the p.d.f.~of $X$, thus an approximate likelihood can be obtained.
+
+Lastly, because $X$ is in the dispersion exponential family, parameter estimation can be done through the GLM framework \cite{zhang2013likelihood}.
+The GLM framework and the saddlepoint approximation were used extensively for insurance claim data \cite{jorgensen1994fitting} \cite{jensen1991saddlepoint}.
+
+\subsection{Probability Density Function}
+The joint p.d.f.~$p_{X,Y}(x,y)$ has probability mass at $X=0$ and $Y=0$ with probability
+\begin{equation}
+\prob\left(X=0,Y=0\right)=\euler^{-\nu\tau} \ ,
+\end{equation}
+and continuous elsewhere
+\begin{equation}
+p_{X,Y}(x,y)=\frac{\lambda^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\lambda x}\euler^{-\nu\tau}\frac{(\nu\tau)^y}{y!}
+\end{equation}
+for $y=1,2,\dotdotdot$ and $x>0$. The marginal can be obtained by summing over all possible values of $y$. The marginal p.d.f.~has probability mass at $X=0$ with probability
+\begin{equation}
+\prob(X=0)=\euler^{-\nu\tau}
+\end{equation}
+and continuous elsewhere
+\begin{equation}
+p_{X}(x)=\sum_{y=1}^{\infty}\frac{\lambda^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\lambda x}\euler^{-\nu\tau}\frac{(\nu\tau)^y}{y!}
+\end{equation}
+for $x>0$.
+It is a mixture with one continuous component at $x>0$ and discrete mass at $x=0$.
+This makes the compound Poisson useful for modelling non-negative variables which can take values of 0.
+By inspection the marginal p.d.f.~cannot be written down in closed form.
+\subsection{Normal Approximation}
+The marginal p.d.f.~of $X$ can be approximated using the Normal distribution. Using the results of the mean and variance of $X$, the Normal approximation is
+\begin{equation}
+X\sim\normal\left(\frac{\alpha\nu\tau}{\lambda},\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}\right) \ .
+\end{equation}
+To assess when the Normal approximation is sensible to use can be done by investigating the m.g.f.~of $X$. The m.g.f.~can be written as
+\begin{equation*}
+M(\theta)=\exp\left[\nu\tau\left(\left(1-\frac{\theta}{\lambda}\right)^{-\alpha}-1\right)\right] \ .
+\end{equation*}
+Assuming $|\theta/\lambda|<1$ and using the binomial expansion
+\begin{equation}
+M(\theta)=\exp\left[\nu\tau\left(
+\sum_{r=1}^{\infty}\frac{\theta^r}{r!\lambda^r}\prod_{t=1}^{r}(\alpha+t-1)
+\right)\right] \ .
+\end{equation}
+This is similar to the m.g.f.~of the Normal distribution by considering the first 2 order terms
+\begin{multline}
+M(\theta)=\exp\left[\theta\frac{\alpha\nu\tau}{\lambda}+\frac{\theta^2}{2}\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}
+\right.\\\left.
++\sum_{r=3}^\infty\nu\tau\frac{\theta^r}{r!\lambda^r}\prod_{t=1}^{r}(\alpha+t-1)
+\right] \ .
+\end{multline}
+For the Normal approximation to be a good approximation, the third and higher order terms must be small. This can happen for large $\lambda$. In addition for large values of $\alpha$ 
+\begin{equation}
+\prod_{t=1}^{r}(\alpha+t-1)\approx\alpha^r \ .
+\end{equation}
+and this is smaller than the coefficient term $\prod_{t=1}^{r}(\alpha+t-1)$
+\begin{equation}
+\prod_{t=1}^{r}(\alpha+t-1) \geqslant \alpha^r \ .
+\end{equation}
+Thus large values of $\alpha$ slow down the relative growth of the $\prod_{t=1}^{r}(\alpha+t-1)$ term, perhaps justifying the Normal approximation.
+
+A more general result can be obtained. This can be done by taking a Taylor expansion of the m.g.f.~of the gamma component in $M(\theta)$. That is let
+\begin{equation}
+M(\theta)=\exp\left[
+\nu\tau\left(M_U(\theta)-1\right)
+\right]
+\end{equation}
+where $M_U(\theta)$ is the m.g.f.~of $\gammaDist(\alpha,\lambda)$. Then taking the Taylor expansion
+\begin{equation*}
+M(\theta)=\exp\left[
+\nu\tau\left(
+\sum_{r=0}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}
+-1
+\right)
+\right]
+\end{equation*}
+but because $M_U(0)=1$
+\begin{equation}
+M(\theta)=\exp\left[
+\nu\tau
+\sum_{r=1}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}
+\right] \ .
+\end{equation}
+As before, this is similar to the m.g.f.~of the Normal distribution when considering the first 2 terms
+\begin{multline}
+M(\theta)=\exp\left[
+\theta M_U'(0)\nu\tau+\frac{\theta^2}{2} M_U''(0)\nu\tau
+\right.\\\left.+
+\sum_{r=3}^\infty M_U^{(r)}(0)\frac{\theta^r}{r!}\nu\tau\right] \ .
+\end{multline}
+Thus for the Normal approximation to be good, the parameters $\alpha$ and $\lambda$ must be such that the third and higher moments of $\gammaDist(\alpha,\lambda)$ are much smaller than the first two moments.
+
+\subsection{Saddle Point Approximation}
+For a given m.g.f., that is
+\begin{equation}
+M(\theta)=\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x \ ,
+\end{equation}
+the saddle point approximation \cite{daniels1954saddlepoint} \cite{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddle point approximation is given as
+\begin{equation}
+p_X(x)\approx\left(2\pi K''(s)\right)^{-1/2}\exp\left[K(s)-sx\right]
+\end{equation}
+where $K(\theta) = \ln\left(M(\theta)\right)$, and $s=s(x)$ is the solution to the saddle point equation $K'(s)=x$.
+
+For the compound Poisson-Gamma distribution, the saddle point approximation is given in Equation \eqref{eq:saddle_point_approx} and is valid only for $x>0$.
+The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary.
+
+\begin{figure*}[htb]
+\begin{multline}
+p_X(x)\approx
+\left(2\pi(\alpha+1)\right)^{-1/2}\left(\nu\tau\lambda^\alpha\alpha\right)^{1/(2(\alpha+1))}\euler^{-\nu\tau}
+\\
+\exp\left[
+-\frac{\alpha+2}{2(\alpha+1)}\ln(x)-x\lambda+\left(\left(\frac{x\lambda}{\alpha}\right)^{\alpha}\nu\tau\right)^{1/(\alpha+1)}(\alpha+1)
+\right]
+\label{eq:saddle_point_approx}
+\end{multline}
+\end{figure*}
+
+\subsection{Simulations}
+Exact simulation of the compound Poisson distribution is easy, this is done by simulating the latent variable $Y$ and then simulating the observable given that latent variable, $X|Y$.
+An experiment was conducted to assess how good the density approximations are.
+This was done by simulating $10^4$ samples of a compound Poisson random variable, and then comparing the histogram of the samples with the density approximation.
+Three sets of parameters were chosen and the results are shown in Figure \ref{fig:histogram}.
+
+For low $\nu\tau$, there is a chance of simulating zeros.
+The Normal approximation failed to capture the probability mass at zero because the Normal distribution was constrained to be symmetric.
+The saddlepoint approximation did capture probability mass at zero as shown by an increase in probability density towards zero.
+However for a distinct mixture looking compound Poisson, Figure \ref{fig:histogram} (d), the saddlepoint approximation was not flexible enough to capture each individual peaks.
+
+For the Normal looking compound Poisson, both approximation performed well.
+\begin{figure*}
+\centerline{
+	\centering
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_1.eps}
+        \caption{Normal approximation: $\nu\tau=1$, $\alpha=1$, $\lambda=1$}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_1.eps}
+        \caption{Saddlepoint approximation: $\nu\tau=1$, $\alpha=1$, $\lambda=1$}
+    \end{subfigure}
+}
+\centerline{
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_2.eps}
+        \caption{Normal approximation: $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_2.eps}
+        \caption{Saddlepoint approximation: $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
+    \end{subfigure}
+}
+\centerline{
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/normal_3.eps}
+        \caption{Normal approximation: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/saddle_3.eps}
+        \caption{Saddlepoint approximation: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
+    \end{subfigure}
+}
+\caption{A sample of $10^4$ compound Poisson random variables was simulated. The histogram of the samples was plotted along with the density approxmation.}
+\label{fig:histogram}
+\end{figure*}
+
+\subsection{Parameter estimation}
+The saddlepoint approximation did capture the probability mass at zero, however the formula for the density approximation does not support zero.
+As a result, the saddlepoint approxmation may not be suited to approximate the likelihood when there is a good chance of obtaining zeros in the data.
+A way around it is to adjust the data by adding a very small constant to all zeros in the data.
+
+An experiment was conducted to optimise the saddle point likelihood approximation numerically using the quasi-Newton method.
+For a given set of compound Poisson parameters, this was done by simulating 100 i.i.d.~samples.
+Any zeros in the sample were converted to a small constant, the constant being 1/8th of the minimum of all non-zero data in the sample, this was done to make the approximated likelihood evaluable.
+The likelihood was then optimised using \texttt{MATLAB}'s \texttt{fminunc} function with the default settings.
+The initial value was set at the true value to see how much the optimiser diverges from the true value.
+This was repeated 1\,000 times to obtain an empirical sampling distribution.
+
+2 sets of parameters, carried forward from the previous section were used: $\{\nu\tau=3,\alpha=400,\lambda=100\}$ and $\{\nu\tau=500,\alpha=80,\lambda=2\}$.
+Figure \ref{fig:sampling_dist} shows the empirical sampling distribution from the experiment.
+For these particular examples, the estimators appeared to be unbiased with nice behaving distributions and finite variance.
+However for the $\{\nu\tau=500,\alpha=80,\lambda=2\}$ case, the variance looks too small to be true.
+It was found that the estimator was extremely sensitive to the initial value and the optimiser may not moved much from the initial value, this seems to be the case here.
+
+\begin{figure*}
+\centerline{
+	\centering
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_nu.eps}
+        \caption{$\nu\tau$ estimates for $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_nu.eps}
+        \caption{$\nu\tau$ estimates for  $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
+    \end{subfigure}
+}
+\centerline{
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_alpha.eps}
+        \caption{$\alpha$ estimates for  $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_alpha.eps}
+        \caption{$\alpha$ estimates for $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
+    \end{subfigure}
+}
+\centerline{
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_1_lambda.eps}
+        \caption{$\lambda$ estimates for $\nu\tau=3$, $\alpha=400$, $\lambda=100$}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \includegraphics[width=1\textwidth]{../figures/compoundPoisson/sampling_dist_2_lambda.eps}
+        \caption{$\lambda$ estimates for $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
+    \end{subfigure}
+}
+\caption{Sampling distribution of the maximum saddlepoint approximated likelihood estimators. Dotted line represent the true value.}
+\label{fig:sampling_dist}
+\end{figure*}
+
+Figure \ref{fig:lnL} shows a plot of a typical log likelihood in the 3 parameter space.
+The log likelihood looks shallow and perhaps the optimiser in \texttt{MATLAB} may have struggled to improve estimations near the true value.
+
+\begin{figure}
+\centerline{\centering
+\includegraphics[width=0.5\textwidth]{../figures/compoundPoisson/log_likelihood.eps}}
+\caption{An example of the log likelihood of a sample of compound Poisson random variables with parameters: $\nu\tau=500$, $\alpha=80$, $\lambda=2$}
+\label{fig:lnL}
+\end{figure}
+
+\subsection{Future work}
+The \texttt{R} package \texttt{cplm} \cite{zhang2013likelihood} numerically estimate parameters for the compound Poisson in the GLM framework.
+However for large parameters, there were numerical problems and the estimators' performance were hit and miss.
+Future work will rely on this package and the saddlepoint approximation to estimate parameters for the compound Poisson.
+Numerical problems can come from ill-conditioned variables and variables need to be scaled.
+One useful property of the compound Poisson is that the parameter $\lambda$ can absorb any scaling by a constant.
+That is if one can express a compound Poisson random variable as
+\begin{equation}
+X\sim\text{CompoundPoisson}\left(\nu\tau,\alpha,\lambda\right)
+\end{equation}
+then for a positive constant $k$
+\begin{equation}
+kX\sim\text{CompoundPoisson}\left(\nu\tau,\alpha,\lambda/k\right) \ .
+\end{equation}
 

### 2017-03-21 reports/progress_1/progress_1.tex
In progress report, rush finish.

@@
 
-\section{$Z$ Statistic}
+\section{$Z$ Statistics}
+
+A statistic was developed which compares each pixel of a scan of a 3D printed sample with the true image, any outlying pixels then can be considered as a possible defect in the 3D printed sample.
+The statistic is based on the $Z$ statistic and is given as
+\begin{equation}
+Z(x,y) = \frac{\text{scan}(x,y) - \text{truth}(x,y)}{\sqrt{\widehat{\variance}[\text{scan}(x,y)]}}
+\end{equation}
+where $\widehat{\variance}[\text{scan}(x,y)]$ is the estimated grey value variance of a pixel at $(x,y)$ of the scan.
+The estimated variance can be obtained using a GLM model as discussed in the previous section.
+In addition, the scan image should be shaded corrected to remove as much shading effects as possible.
+Assuming the $Z$ statistics are standard Normal distributed, multiple hypothesis testing can be used to test each pixel to find significant or outlying pixels, such as the Bonferroni correction.
+
+\subsection{Experiments}
+An experiment was conducted to investigate the behaviour of the $Z$ statistics.
+b/g/w shading correction was applied prior to the experiment and any outlying pixels were interpolated as discussed in the previous section.
+The 100 images were spilt into 3 parts:
+\begin{itemize}
+	\item 50 images in the training set to train the mean variance relationship model using GLM with the identity link;
+	\item 25 images in the truth set, the mean over these images were used as the true image;
+	\item 25 images in the test set, each of these images will be compared to the true image.
+\end{itemize}
+Each image in the test set was compared to the true image by calculating the $Z$ statistic for each pixel. Thus for each pixel, a sample of 25 $Z$ statistics was obtained.
+
+A sample of $Z$ images are shown in Figure \ref{fig:p_values} and significant pixels are shown in Figure \ref{fig:critical_values}.
+The Bonferroni correction was used to correct for multiple testing.
+The $Z$ images showed that the $Z$ statistics within image varied scan to scan, suggesting images in the test set are not quite as similar as hoped for.
+Common significant pixels were picked up by the statistic, especially on the left edge.
+However fortunately only a few significant pixels were picked up from the 3D printed sample, this is important when making inference about the image.
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.45\textwidth]{../figures/meanVar/p_values.eps}
+	\caption{A sample of 6 images from the test set compared to the true image. The $Z$ statistics were transformed using the standard Normal c.d.f.}
+	\label{fig:p_values}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.45\textwidth]{../figures/meanVar/critical_values.eps}
+	\caption{Using the $Z$ statistics from Figure \ref{fig:p_values}, highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
+	\label{fig:critical_values}
+\end{figure}
+
+The $Z$ statistics were tested for Normality within pixel using the $\chi^2$ goodness of fit test.
+To make the test more powerful, 75 more $Z$ statistics were collected by reassigning the training, truth and test set and repeating the experiment 3 more times.
+Figure \ref{fig:chi_squared} show the $p$ values from the test were particularly low, especially on the bottom half of the image.
+In particular there is a vertical line of significant pixels as well.
+Normality may be a valid assumption but the bottom of the image where the foam is may break such an assumption.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_critical.eps}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_p_values.eps}
+	\end{subfigure}
+	\caption{$p$ values from the $\chi^2$ goodness of fit test within pixel.
+Highlighted in red are significant pixels at the $2\sigma$ significant level corrected for multiply testing using the Bonferroni correction.}
+	\label{fig:chi_squared}
+\end{figure*}
 

### 2017-03-23 reports/progress_1/progress_1.tex
In progress report, done a proof read.

@@
 \begin{abstract}
-
+X-ray CT can be used for defect detection and quality control of 3D printing.
+This report will outline statistical methods for comparing x-ray scans of a 3D printed sample with its computer model under the face of uncertainty.
+Shading correction methods and the mean and variance relationship were investigated.
+Lastly the compound Poisson was reviewed.
 \end{abstract}
@@
 \section{Introduction}
-3D printing, or additive layer manufacturing \cite{kodama1981automatic} \cite{wong2012review}, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.
+3D printing, or additive layer manufacturing \cite{kodama1981automatic}\cite{wong2012review}, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.
 Recently it has been commercialised and has served purposes in the medical field \cite{kang20163d} and engineering \cite{wong2012review}.
@@
 
-X-ray computed tomography (CT) \cite{hounsfield1980computed} \cite{michael2001x} \cite{cantatore2011introduction} scans can be used to take images of a rotating 3D printed sample to obtain images of the sample at multiple angles.
+X-ray computed tomography (CT) \cite{hounsfield1980computed}\cite{michael2001x}\cite{cantatore2011introduction} scans can be used to take images of a rotating 3D printed sample to obtain images of the sample at multiple angles.
 These x-ray images then can be combined to form a 3D projection and the detection of defects can start.
@@
 
-This report will outline a pre-process method called shading correction and it was investigated how it affected the mean and variance relationship.
-The mean and variance relationship was modelled using GLM with different link functions.
-After finding a good model for the mean and variance, a statistics was developed to compare two images in the face of uncertainty.
-Lastly the compound Poisson was studied.
+This report will outline a pre-process method called shading correction.
+The aim of shading correction is to remove shading effects before any statistical analysis is conducted.
+It was then investigated how different types of shading correction affected the mean and variance grey value of each pixel in a scan.
+Afterwards, the mean and variance relationship was modelled using a GLM with different link functions.
+After finding a good model for the mean and variance, a statistic was developed to compare a scan with a simulation in the face of uncertainty.
+Lastly the compound Poisson was studied with the hope it can aid in variance modelling and prediction.
 
@@
 20 black/grey/white (b/g/w) images were collected on 14/03/16 at around 1250.
-The b/g/w images are images obtained from the x-ray detector when exposed to x-rays at different settings, they are useful for calibrating the detector thus b/g/w images can be called reference images.
-About 2 hours later at 1503, 100 images of a 3D printed cuboid (or sample) were taken.
+The b/g/w images are images obtained from the x-ray detector when exposed to x-rays at different settings.
+They are useful for calibrating the detector, thus b/g/w images can be called reference images.
+About 2 hours later, 100 images of a 3D printed cuboid (or sample) were taken.
 These images were obtained from the x-ray detector when exposed to x-rays with the sample between the x-ray source and detector.
-The detector used was the Perkin Elmer XRD 1621 digital X-ray detector, with settings shown in Table \ref{table:settings}.
+The 3D printed was stationary and not rotating throughout the scans.
+The detector used was the Perkin Elmer XRD 1621 digital x-ray detector, with settings shown in Table \ref{table:settings}.
 
@@
 The x-ray detector was made up 32 panels, arranged in 2 rows and 16 columns.
-Unfortunately these panels can be observed in the b/g/w images as a result of panel-wise effects in the image of the sample, as shown in Figure \ref{fig:image}.
+Unfortunately these panels can be observed in the images which can be seen by the panel-wise effects, as shown in Figure \ref{fig:image}.
 The effects can be described as introducing a gradient to the grey values within panels and perhaps between panels and globally.
@@
 Let $N(x,y)$ be the grey value of the pixel at position $(x,y)$ in the obtained image.
-Similarly let $U(x,y)$ be they grey value of pixels of the shading-free image.
+Similarly let $U(x,y)$ be they grey value of pixels of the shading free image.
 The shading effects can be modelled using a linear relationship
@@
 \end{equation}
-where $c_1$ and $c_2$ are some constants.
-One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the mean black and white (b/w) images.
-Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean black and white images respectively, then the estimators for $b(x,y)$ and $a(x,y)$ are
+where $c_1$ and $c_2$ are user defined constants.
+One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the black and white (b/w) images.
+Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean between the 20 black and white images respectively.
+The estimators for $b(x,y)$ and $a(x,y)$ are
 \begin{equation}
@@
 The shading free image is not truly known, but one should expect the b/g/w shading free images should be completely flat.
-By using the obtained b/g/w images to estimate the parameters of the linear regression, this becomes a regression problem.
 
@@
 \begin{equation}
-\widehat{\alpha}(x,y) = \overline{R}-\widehat{\beta}(x.y)\overline{R}_B(x,y) 
+\widehat{\alpha}(x,y) = \overline{R}-\widehat{\beta}(x,y)\overline{R}_B(x,y) 
 \end{equation}
@@
 Figure \ref{fig:shadingCorrection_grad} shows the values of $\widehat{\beta}(x,y)$.
-By inspection there is some curvature in the $\widehat{\beta}$ image, with high gradients in the corners, in addition to panel-wise gradients.
+By inspection there is some curvature in the $\widehat{\beta}$ image, with high gradients in the corners.
 Problems occur if the reference images behave differently from expected.
-For example some pixels may be dead and do not vary at all, this resulted in infinite gradients highlighted by red circles in the figure.
+For example some pixels may be dead and do not vary at all, this resulted in infinite gradients, shown by red circles in the figure.
 In order to combat this, any pixels with undefined grey values post shading correction were replaced with the sample median of its 8 nearest neighbours.
@@
 A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit.
-In the black and grey images, the residuals show a global ring which is very unusual for the black image because it is detecting no x-rays at all.
-The b/g/w residuals all show vertical stripes.
+In the black and grey images, the residuals showe a global ring which was very unusual for the black image because it is detecting no x-rays at all.
+The b/g/w residuals all showed vertical stripes.
 The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects.
@@
 The resulting shading correction is shown in Figure \ref{fig:shadingCorrection}.
-This method can be advantageous as the panel-wise 2nd order polynomial only captures gradients of each panel and  smooths out clusters of bad behaving pixels as shown in the residuals.
+This method can be advantageous as the panel-wise 2nd order polynomial only captured panel effects parametrically and smoothed out clusters of bad behaving pixels as shown in the residuals.
 As a result, the shading correction is smoother between pixels because the bad behaving pixels do not impact as much in the interpolation of the linear regression.
@@
 
-An experiment was conducted to assess the performance of shading correction.
+An experiment was conducted to assess the performance of different types of shading correction.
 The methodology behind it is that shading correction applied on the reference images should remove shading effects and produce an image which is noisy but all the pixels should have the same mean grey value.
@@
 The 20 b/g/w images were spilt into a training set and test set of equal size randomly.
-The training set was used to estimate the parameters for shading corrections.
+The training set was used to estimate the parameters for shading correction.
 Afterwards, shading correction was applied to each image in the test set producing 10 shading corrected reference images of each grey scale.
-The within pixel variance and between pixel variance was recorded, exactly the same as ANOVA treating each pixel as a group.
+The post shading correction within pixel variance and between pixel variance was recorded, exactly the same procedure as ANOVA treating each pixel as a group.
 For each pixel to have the same mean grey value, the within and between pixel variance should be similar.
-The experiment was repeated 20 times by repeating the assignment of the training and test set.
+The experiment was repeated 20 times by changing randomly the assignment of the training and test set.
 
@@
 With b/w and b/g/w shading correction, the reference images appeared flatter.
-The flatness of the black and grey image depended if the grey images were used when training the shading correction.
+The flatness of the black and grey image depended on if the grey images were used when training the shading correction.
 The b/g/w 2nd order polynomial shading correction retained some effects not captured by the panel wise polynomial fits.
-This can be tell because the shading corrected images were very similar to the residual plots in Figure \ref{fig:polynomial_residual}.
+This was shown because the shading corrected images were very similar to the residual plots in Figure \ref{fig:polynomial_residual}.
 
@@
 	d) b/g/w 2nd order polynomial shading correction
-	\caption{Quartiles of the within pixel and between pixel variance after 20 repeats of the experiment.}
+	\caption{Within pixel and between pixel variance of the shading corrected reference images. Values stated are the quartiles from 20 repeats of the experiment.}
 	\label{table:bgw_anova}
@@
 It appeared that by considering the grey images, the shading correction performance on certain grey values was traded for other grey values.
-
 Additional methods for shading correction could be considered such as fitting a global polynomial in addition to the panel wise polynomials to the reference images.
@@
 
-\section{Mean/Variance Relationship}
+\section{Mean Variance Relationship}
 The variance can be used to quantify the uncertainty of a grey value in a pixel.
@@
 
-Different shading corrections had an effect on the mean variance relationship, as shown in Figure \ref{fig:meanVar_shadingCorrection}.
+Different shading corrections had small effects on the mean variance relationship, as shown in Figure \ref{fig:meanVar_shadingCorrection}.
 Due to some misbehaving pixels in the reference images, grey value outliers were possible such as negative values.
@@
 The within pixel sample mean and sample variance  grey value was estimated for both the training set and test set separately.
-The GLM was fitted onto the mean/variance data obtained from the training set.
+The GLM was fitted onto the mean variance data obtained from the training set.
 The fitted model was then used to predict the variance given the mean on the test set.
@@
 However it should be noted that there is sampling error in the sample variance and the magnitude of the error varies for different means.
-In order to take the varying sampling error into account, the mean standardised squared error (MSSE) was used to assess the performance of the fitted GLM predicting the variance given the mean on the test set.
+In order to take the varying sampling error into account, the mean standardised squared error (MSSE) was used to assess the performance of the fitted GLM predicting the variance given the mean.
 The errors were standardised by dividing by the standard deviation of the GLM response.
 
-The experiment was repeated 100 times by reassigning the training and test set.
-
-The training and test MSSE are shown in Tables \ref{table:training} and \ref{table:test}.
-By using b/g/w shading correction, the test MSSE improved and suggests that b/g/w shading correction aids in variance prediction.
+The experiment was repeated 100 times by reassigning the training and test set randomly.
+
+The training and test MSSE are shown in Table \ref{table:training}.
+NaN values were obtained when the iterative reweighted least squares failed to converge.
+By using b/g/w shading correction, the test MSSE improved which suggests that b/g/w shading correction aids in variance prediction.
 b/w shading correction increased the MSSE by a magnitude of $\sim\times10^3$.
 A quick residual plot in Figure \ref{fig:glm_residual} showed that residuals were more centred at zero for b/g/w shading correction compared to b/w shading correction.
+b/w shading correction struggled to correct the grey pixels correctly, creating bias in the model.
 
@@
 \begin{table*}
+\centering
 \centerline{
@@
 \end{tabular}}
-\caption{Training mean squared standardised error from fitting GLM onto the mean/variance training set. Values stated are the quartiles from 100 repeats.}
-\label{table:training}
-\end{table*}
-
-\begin{table*}
+\vspace{.25cm}
+a) Training error
+\\\vspace{.5cm}
 \centerline{
@@
 \input{../tables/GLM_meanVar_trainingTest_test.tex_table}
-\end{tabular}
-}
-\caption{Test mean squared standardised error from using GLM to predict variance given mean from the test set. Values stated are the quartiles from 100 repeats.}
-\label{table:test}
+\end{tabular}}
+\vspace{.25cm}
+b) Test error
+\\\vspace{.5cm}
+\caption{Mean squared standardised error using GLM with identity link to predict the variance given the mean. Values stated are the quartiles from 100 repeats.}
+\label{table:training}
 \end{table*}
@@
 
-\section{$Z$ Statistics}
-
-A statistic was developed which compares each pixel of a scan of a 3D printed sample with the true image, any outlying pixels then can be considered as a possible defect in the 3D printed sample.
+\section{Inference}
+
+A statistic was developed which compares each pixel of a scan of a 3D printed sample with the true image obtained from a computer model or simulation.
+Any outlying pixels then can be considered as a possible defect in the 3D printed sample.
 The statistic is based on the $Z$ statistic and is given as
 \begin{equation}
-Z(x,y) = \frac{\text{scan}(x,y) - \text{truth}(x,y)}{\sqrt{\widehat{\variance}[\text{scan}(x,y)]}}
-\end{equation}
+Z(x,y) = \frac{\text{scan}(x,y) - \text{model}(x,y)}{\sqrt{\widehat{\variance}[\text{scan}(x,y)]}}
+\end{equation}
+%$Z(x,y)=\frac{\text{scan}(x,y)-\text{model}(x,y)}{\sqrt{\widehat{\mathbb{V}\text{ar}}[\text{scan}(x,y)]}}$
 where $\widehat{\variance}[\text{scan}(x,y)]$ is the estimated grey value variance of a pixel at $(x,y)$ of the scan.
@@
 Common significant pixels were picked up by the statistic, especially on the left edge.
-However fortunately only a few significant pixels were picked up from the 3D printed sample, this is important when making inference about the image.
+Fortunately only a few significant pixels were picked up from the 3D printed sample.
 
@@
 The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to the energy spectrum.
-The greyvalue was then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.
+The grey value was then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.
 
@@
 Let $Y$ be the number of photons detected for that particular pixel.
-Let $U$ be the energy of a photon post-attenuation and is typically random, here it was assumed to be Normally distribued.
-Let $X$ be the greyvalue of that pixel.
+Let $U$ be the energy of a photon post-attenuation and is typically random, here it was assumed to be Normal distributed.
+Let $X$ be the grey value of that pixel.
 The model is hierarchical such that at the top layer
@@
 Compound Poisson was proposed to improve noise models in CT scans \cite{whiting2002signal}.
-Simple models have been used which assumed the greyvalues were Poisson distributed or Normally \cite{lu2002analytical} distributed.
+Simple models have been used which assumed the greyvalues were Poisson distributed or Normal \cite{lu2002analytical} distributed.
 The compound Poisson improves on these models by considering the energy spectrum of x-ray quanta and integrating it into the x-ray detector \cite{whiting2006properties}.
 This has been useful in image reconstruction \cite{elbakri2003efficient}\cite{elbakri2002statistical}\cite{elbakri2001statistical}\cite{lasio2007statistical} and tested in experiments \cite{wang2008experimental}.
-The p.d.f.~of the greyvalues can be numerically obtained using the saddle point approximation for a given general energy spectrum \cite{elbakri2003efficient}.
+The p.d.f.~of the grey values can be numerically obtained using the saddle point approximation for a given general energy spectrum \cite{elbakri2003efficient}.
 
@@
 \begin{equation}
-\prod_{t=1}^{r}(\alpha+t-1)\approx\alpha^r \ .
+\prod_{t=1}^{r}(\alpha+t-1)\approx\alpha^r
 \end{equation}

### 2017-03-24 reports/progress_1/progress_1.tex
In progress report, proof read.

@@
 These images were obtained from the x-ray detector when exposed to x-rays with the sample between the x-ray source and detector.
-The 3D printed was stationary and not rotating throughout the scans.
+The 3D printed sample was stationary and not rotating throughout the scans.
+The sample was held at the bottom by foam.
 The detector used was the Perkin Elmer XRD 1621 digital x-ray detector, with settings shown in Table \ref{table:settings}.
@@
 The grey values are in arbitrary units.
-The images are shown in Figure \ref{fig:image} and the histogram of grey values are shown in Figure \ref{fig:hist}.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width = 0.9\textwidth]{../figures/data/140316_image.eps}
+A sample of images are shown in Figure \ref{fig:image} and the histogram of grey values are shown in Figure \ref{fig:hist}.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width = \textwidth]{../figures/data/140316_image.png}
 	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
@@
 	\centering
-	\includegraphics[width = 0.45\textwidth]{../figures/data/140316_histo.png}
-	\caption{A black, grey, white and sample image obtained from the x-ray detector.}
+	\includegraphics[width = 0.45\textwidth]{../figures/data/140316_histo.eps}
+	\caption{Histogram of grey values from a black, grey, white and sample image obtained from the x-ray detector.}
 	\label{fig:hist}
@@
 One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the black and white (b/w) images.
-Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean between the 20 black and white images respectively.
+Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean over the 20 black and white images respectively.
 The estimators for $b(x,y)$ and $a(x,y)$ are
@@
 Let these images have $h$ rows and $w$ columns.
-The shading free b/g/w images should be completely flat, in other words all the pixels should have the same grey value.
-A good guess what that grey value should be would be the sample mean of the grey values within the b/g/w images $\overline{R}_\text{b}$, $\overline{R}_\text{g}$ and $\overline{R}_\text{w}$ where
+The shading free b/g/w images should be completely flat, in other words all the pixels within a reference image should have the same grey value.
+A good guess what that shading corrected grey value should be would be the sample mean of the shading uncorrected grey values within the b/g/w images $\overline{R}_\text{b}$, $\overline{R}_\text{g}$ and $\overline{R}_\text{w}$ where
 \begin{equation}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block.eps}
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block.png}
 		\caption{Shading uncorrected}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block_shadingCorrected.eps}
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/block_shadingCorrected.png}
 		\caption{b/g/w shading correction}
@@
 	\begin{subfigure}{0.45\textwidth}
-		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_shadingCorrection.eps}
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_shadingCorrection.png}
 		\caption{b/g/w 2nd order polynomial shading correction}
@@
 A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit.
-In the black and grey images, the residuals showe a global ring which was very unusual for the black image because it is detecting no x-rays at all.
+In the black and grey images, the residuals showed a global ring which was very unusual for the black image because it is detecting no x-rays at all.
 The b/g/w residuals all showed vertical stripes.
 The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects.
-Higher order polynomials can be considered but overfitting may be possible, as a result of higher order polynomials attempting to capture all the characteristics of the b/g/w images.
+Higher order polynomials can be considered but overfitting may be possible as may attempt to capture all the characteristics of the b/g/w images.
 
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_black.eps}
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_black.png}
 		\caption{Black}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_grey.eps}
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_grey.png}
 		\caption{Grey}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_white.eps}
+		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_white.png}
 		\caption{White}
@@
 The table shown that b/w and b/g/w shading correction does make an improvement because it brings the within and between pixel variances closer together.
-The performance of shading correction on the black and grey images appeared to depend if the grey images were used in training the shading correction.
+The performance of shading correction on the black and grey images appeared to depend on if the grey images were used in training the shading correction.
 The b/g/w 2nd order polynomial shading correction does perform by bringing the within and between pixel variances closer together but not as much as b/w and b/g/w shading correction.
@@
 
-In conclusion, b/w and b/g/w shading correction do perform well because there was evidence they are attempting to iron out all the pixel grey values to have the same mean.
+In conclusion, b/w and b/g/w shading correction did perform well because there was evidence they are attempting to iron out all the pixel grey values to have the same mean.
 The b/g/w 2nd order polynomial shading correction does its job.
@@
 
+In the mini-project, it was found the background and the foam holding the 3D printed sample have different mean variance relationships \cite{ip2016inside}.
 The object of interest is the 3D printed sample.
-In the mini-project, it was found the background and the foam holding the 3D printed sample have different mean variance relationships \cite{ip2016inside}.
 Thus to model the mean variance relationship of the 3D printed sample, the 3D printed sample was segmented from the background and the foam.
@@
 	\item Use these filtered reference images for shading correction.
-	\item Take the mean over all shading corrected scans.
+	\item Take the mean over all 100 shading corrected scans.
 	\item Keep pixels with grey values less than $4.7\times 10^4$.
@@
 	\centering
-	\includegraphics[width = 0.45 \textwidth]{../figures/meanVar/segment.eps}
+	\centerline{
+	\includegraphics[width = 0.5 \textwidth]{../figures/meanVar/segment.png}
+	}
 	\caption{Resulting segmentation of the 3D printed sample}
@@
 
-GLM can model the sample variance as the response variable being Gamma distributed, explained by the sample mean through a link function $g(\text{variance})$.
+GLM can model the sample variance as a Gamma distributed response variable, being explained by the sample mean through a link function $g(\text{variance})$.
 Fitting of the model was done using iterative re-weighted least squares.
-The dispersion parameter need not to be estimated because the shape parameter is known.
+The dispersion parameter need not to be estimated because the shape parameter $(n-1)/2$ is known.
 A linear fit using the identity link did show that the Gamma response captured the spread of the sample variance for different sample means, this is shown in Figure \ref{fig:meanVar_sampleSize}.
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_25.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_25.png}
 		\caption{$n=25$}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_50.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_50.png}
 		\caption{$n=50$}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_75.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_75.png}
 		\caption{$n=75$}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_100.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/sample_size_100.png}
 		\caption{$n=100$}
 	\end{subfigure}
-	\caption{Mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample.
+	\caption{Within pixel mean and variance grey value frequency density plot of each pixel in the segmented image of the 3D printed sample.
 The sample variance and sample mean were estimated using $n$ scans selected at random without replacement.
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_identity.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_identity.png}
 		\caption{Identity link, order 1}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_log.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_log.png}
 		\caption{Log link, order -1}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_1.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_1.png}
 		\caption{Inverse link, order -1}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_2.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/meanVar_canonical_2.png}
 		\caption{Inverse link, order -2}
 	\end{subfigure}
-	\caption{Shading uncorrected mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample.
-A Gamma GLM was fitted with different link functions and polynomial order.
+	\caption{Shading uncorrected within pixel mean and variance grey value frequency density plot of each pixel in the segmented image of the 3D printed sample.
+A Gamma GLM was fitted with different link functions and polynomial ordera.
 The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_no_shad.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_no_shad.png}
 		\caption{No shading correction}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bw.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bw.png}
 		\caption{b/w shading correction}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bgw.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_bgw.png}
 		\caption{b/g/w shading correction}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_polynomial.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/shadingCorrection_polynomial.png}
 		\caption{b/g/w 2nd order polynomial shading correction}
 	\end{subfigure}
-	\caption{Post shading correction mean and variance frequency density plot of each pixel's grey value in the segmented image of the 3D printed sample.
+	\caption{Post shading correction within pixel mean and variance grey value frequency density plot of each pixel in the segmented image of the 3D printed sample.
 A Gamma GLM was fitted with the identity link.
@@
 For a given link function, polynomial order and shading correction, the 100 images of the 3D printed sample were spilt into two equally sized sets: the training set and the test set.
-The within pixel sample mean and sample variance  grey value was estimated for both the training set and test set separately.
+The within pixel sample mean and sample variance grey value were estimated for both the training set and test set separately.
 The GLM was fitted onto the mean variance data obtained from the training set.
-The fitted model was then used to predict the variance given the mean on the test set.
+The fitted model was then used to predict the variance given the mean.
 The predicted variance given the mean then can be compared with the sample variance.
 
-Metrics such as the mean squared error can be used to assess how good the prediction is.
-However it should be noted that there is sampling error in the sample variance and the magnitude of the error varies for different means.
+There is sampling error in the sample variance and the magnitude of the error varies for different means.
 In order to take the varying sampling error into account, the mean standardised squared error (MSSE) was used to assess the performance of the fitted GLM predicting the variance given the mean.
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/residual_no_shad.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/residual_no_shad.png}
 		\caption{No shading correction}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bw.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bw.png}
 		\caption{b/w shading correction}
@@
 		\centering
-		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bgw.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/residual_bgw.png}
 		\caption{b/g/w shading correction}
 	\end{subfigure}
-	\caption{Frequency density plot of the standardised residuals from predicting the variance given the mean of the test test using a training GLM with identity link function.}
+	\caption{Frequency density plot of the standardised residuals from predicting the variance given the mean in test set using a training GLM with identity link function.}
 	\label{fig:glm_residual}
@@
 In conclusion it was found that b/g/w shading correction aid in variance prediction by making the mean variance data more linear.
-A simple identity link perform just as well as other link function which suggests a linear relationship between the variance and the mean.
+A simple identity link performed just as well as other link functions which suggests a linear relationship between the variance and the mean could be sufficient enough for the purpose of variance prediction.
 
@@
 
-A statistic was developed which compares each pixel of a scan of a 3D printed sample with the true image obtained from a computer model or simulation.
+A statistic was developed which compares each pixel of a single scan of a 3D printed sample with the true image obtained from a computer model or simulation.
 Any outlying pixels then can be considered as a possible defect in the 3D printed sample.
@@
 The estimated variance can be obtained using a GLM model as discussed in the previous section.
-In addition, the scan image should be shaded corrected to remove as much shading effects as possible.
+In addition, the scan image should be shading corrected to remove as much shading effects as possible.
 Assuming the $Z$ statistics are standard Normal distributed, multiple hypothesis testing can be used to test each pixel to find significant or outlying pixels, such as the Bonferroni correction.
@@
 \begin{itemize}
-	\item 50 images in the training set to train the mean variance relationship model using GLM with the identity link;
+	\item 50 images in the training set to train the mean variance relationship model using GLM, as described in the previous section, with the identity link;
 	\item 25 images in the truth set, the mean over these images were used as the true image;
@@
 
-A sample of $Z$ images are shown in Figure \ref{fig:p_values} and significant pixels are shown in Figure \ref{fig:critical_values}.
+A sample of $Z$ statistics are shown in Figure \ref{fig:p_values} and significant pixels are shown in Figure \ref{fig:critical_values}.
 The Bonferroni correction was used to correct for multiple testing.
-The $Z$ images showed that the $Z$ statistics within image varied scan to scan, suggesting images in the test set are not quite as similar as hoped for.
+The $Z$ statistics within image varied scan to scan, suggesting images in the test set were not quite as similar to each other as hoped for.
 Common significant pixels were picked up by the statistic, especially on the left edge.
-Fortunately only a few significant pixels were picked up from the 3D printed sample.
+Fortunately only a few significant pixels were picked up from the 3D printed sample, implying only a few false positives were detected.
 
@@
 	\centering
-	\includegraphics[width = 0.45\textwidth]{../figures/meanVar/p_values.eps}
-	\caption{A sample of 6 images from the test set compared to the true image. The $Z$ statistics were transformed using the standard Normal c.d.f.}
+	\centerline{
+	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/p_values.png}
+	}
+	\caption{A sample of $Z$ statistics obtained from comparing a scan from the test set to the true image. The $Z$ statistics were transformed using the standard Normal c.d.f.}
 	\label{fig:p_values}
@@
 	\centering
-	\includegraphics[width = 0.45\textwidth]{../figures/meanVar/critical_values.eps}
+	\centerline{
+	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/critical_values.png}
+	}
 	\caption{Using the $Z$ statistics from Figure \ref{fig:p_values}, highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
@@
 
-The $Z$ statistics were tested for Normality within pixel using the $\chi^2$ goodness of fit test.
-To make the test more powerful, 75 more $Z$ statistics were collected by reassigning the training, truth and test set and repeating the experiment 3 more times.
-Figure \ref{fig:chi_squared} show the $p$ values from the test were particularly low, especially on the bottom half of the image.
+The $Z$ statistics within pixel were tested for Normality  using the $\chi^2$ goodness of fit test.
+To make the test more powerful, 75 more $Z$ statistics were collected by reassigning randomly the training, truth and test set and repeating the experiment 3 more times.
+Figure \ref{fig:chi_squared} showed that the $p$ values from the $\chi^2$ test were particularly low, especially on the bottom half of the image.
 In particular there is a vertical line of significant pixels as well.
@@
 	\begin{subfigure}{0.45\textwidth}
-		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_critical.eps}
+		\includegraphics[width = \textwidth]{../figures/meanVar/chi_squared_critical.png}
 	\end{subfigure}
@@
 
+\subsection{Conclusion}
+The $Z$ statistics looked like a good candidate to make inference from a single scan of a 3D printed sample.
+There is further work to be done.
+Rather than using a subset of the data as the true image, simulations can be treated as the true image to investigate how well the $Z$ statistic perform in real life defect detection.
+Further multiple hypothesis testing should be investigated and inference can be extended to the 3D reconstructed data of the 3D printed sample.
+
 \section{Compound Poisson}
-In the mini-project, a compound Poisson model was used to model the distribution of greyvalues in a pixel.
-The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to the energy spectrum.
+In the mini-project, a compound Poisson model was used to model the distribution of greyvalues in a pixel \cite{ip2016inside}.
+The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to an energy spectrum.
 The grey value was then proportional to the sum of energies of each photon detected in some exposure time, with some Normal noise added.
@@
 
-The main aims were to investigate the compound Poisson, approximations and methods for fitting it to data.
+The main aims were to investigate the compound Poisson, approximations and methods for fitting it to data. The compound Possion then could be used in variance modelling or prediction in future work.
 
@@
 
-It is very well known that the marginal $X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
+It is very well known that the marginal p.d.f.~$X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
 \begin{equation}
@@
 By inspection the marginal p.d.f.~cannot be written down in closed form.
+
 \subsection{Normal Approximation}
@@
 \end{multline}
-For the Normal approximation to be a good approximation, the third and higher order terms must be small. This can happen for large $\lambda$. In addition for large values of $\alpha$ 
-\begin{equation}
-\prod_{t=1}^{r}(\alpha+t-1)\approx\alpha^r
-\end{equation}
-and this is smaller than the coefficient term $\prod_{t=1}^{r}(\alpha+t-1)$
-\begin{equation}
-\prod_{t=1}^{r}(\alpha+t-1) \geqslant \alpha^r \ .
-\end{equation}
-Thus large values of $\alpha$ slow down the relative growth of the $\prod_{t=1}^{r}(\alpha+t-1)$ term, perhaps justifying the Normal approximation.
-
-A more general result can be obtained. This can be done by taking a Taylor expansion of the m.g.f.~of the gamma component in $M(\theta)$. That is let
+For the Normal approximation to be a good approximation, the third and higher order terms must be small. This can happen for large $\lambda$.
+
+A more general result can be obtained. This can be done by taking a Taylor expansion of the m.g.f.~of the Gamma component in $M(\theta)$. That is let
 \begin{equation}
@@
 The saddlepoint approximation did capture probability mass at zero as shown by an increase in probability density towards zero.
-However for a distinct mixture looking compound Poisson, Figure \ref{fig:histogram} (d), the saddlepoint approximation was not flexible enough to capture each individual peaks.
+However for a distinct mixture looking compound Poisson, Figure \ref{fig:histogram} (d), the saddlepoint approximation was not flexible enough to capture each individual peak.
 
@@
 The initial value was set at the true value to see how much the optimiser diverges from the true value.
-This was repeated 1\,000 times to obtain an empirical sampling distribution.
+This was repeated 1\,000 times to obtain an empirical sampling distribution of the 3 estimators.
 
@@
 For these particular examples, the estimators appeared to be unbiased with nice behaving distributions and finite variance.
-However for the $\{\nu\tau=500,\alpha=80,\lambda=2\}$ case, the variance looks too small to be true.
-It was found that the estimator was extremely sensitive to the initial value and the optimiser may not moved much from the initial value, this seems to be the case here.
+However for the $\{\nu\tau=500,\alpha=80,\lambda=2\}$ case, the variance looked too small to be true.
+It was found that the estimator was extremely sensitive to the initial value and the optimiser may have not moved much from the initial value, this seems to be the case here.
 
@@
 Future work will rely on this package and the saddlepoint approximation to estimate parameters for the compound Poisson.
-Numerical problems can come from ill-conditioned variables and variables need to be scaled.
+Numerical problems can come from ill-conditioned variables and the data need to be scaled.
 One useful property of the compound Poisson is that the parameter $\lambda$ can absorb any scaling by a constant.

### 2017-03-24 meanVar/Experiment_GLM_meanVar_trainingTest.m

@@ -201,7 +201,7 @@ classdef Experiment_GLM_meanVar_trainingTest < Experiment
                         training_table(i_glm+1,2+i_shading) = 'NaN';
                     %else all training mse isn't nan, quote the quartile of the training mse
                     else
-                        training_table(i_glm+1,2+i_shading) = quoteQuartileError(training_mse_i,100);
+                        training_table(i_glm+1,2+i_shading) = quoteQuartileError(training_mse_i,1);
                     end
 
                     %get the test mse
@@ -211,12 +211,7 @@ classdef Experiment_GLM_meanVar_trainingTest < Experiment
                         test_table(i_glm+1,2+i_shading) = 'NaN';
                     %else all test mse isn't nan, quote the quartile of the test mse
                     else
-                        [q2, up_error, down_error, E] = quoteQuartileError(test_mse_i,100);
-                        if E == '0'
-                            test_table(i_glm+1,2+i_shading) = strcat('$',q2,'\substack{+',up_error,'\\ -',down_error,'}$');
-                        else
-                            test_table(i_glm+1,2+i_shading) = strcat('$(',q2,'\substack{+',up_error,'\\ -',down_error,'})\times 10^{',E,'}$');
-                        end
+                        test_table(i_glm+1,2+i_shading) = quoteQuartileError(test_mse_i,100);
                     end
                 end
 

### 2017-03-24 meanVar/residual_meanVar_script.m

@@ -162,5 +162,5 @@ for i_block = 1:numel(block_array)
     %set the background to white (of the figure)
     ax_array{i_block,2}.Color = 'white';
     %save figure
-    saveas(ax_array{i_block,2},strcat('reports/figures/meanVar/residual_',name_array{i_block},'.eps'),'epsc');
+    saveas(ax_array{i_block,2},strcat('reports/figures/meanVar/residual_',name_array{i_block},'.png'),'png');
 end

### 2017-03-24 meanVar/segmentation_script.m

@@ -30,7 +30,7 @@ ax = imagesc(slice);
 colormap gray;
 colorbar;
 axis(gca,'off');
-saveas(fig,'reports/figures/meanVar/segment.eps');
+saveas(fig,'reports/figures/meanVar/segment.png','png');
 
 %reshape the threshold indicator to be a vector
 threshold = reshape(threshold,[],1);

### 2017-03-24 meanVar/z_statistic_script.m

@@ -83,7 +83,7 @@ for i = 1:6
     colorbar;
     axis(gca,'off');
 end
-saveas(fig,'reports/figures/meanVar/p_values.eps','epsc');
+saveas(fig,'reports/figures/meanVar/p_values.png','png');
 
 %define the significance level
 sig_level = normcdf(-5) / block_data.area;
@@ -107,7 +107,7 @@ for i = 1:6
     %plot the significant pixels as a scatter plot
     scatter(x,y,'r');
 end
-saveas(fig,'reports/figures/meanVar/critical_values.eps','epsc');
+saveas(fig,'reports/figures/meanVar/critical_values.png','png');
 
 %---CHI SQUARED GOODNESS OF FIT TEST---%
 

### 2017-03-24 quoteQuartileError.m

@@ -92,11 +92,13 @@ function quote = quoteQuartileError(data, n_bootstrap)
     down_error = num2str(down_error);
     
     %fill in missing decimial places with zeros
-    while numel(up_error)<2+dec_places
-        up_error = [up_error,'0'];
-    end
-    while numel(down_error)<2+dec_places
-        down_error = [down_error,'0'];
+    if sig_fig ~= 1
+        while numel(up_error)<2+dec_places
+            up_error = [up_error,'0'];
+        end
+        while numel(down_error)<2+dec_places
+            down_error = [down_error,'0'];
+        end
     end
     
     %convert the exponent to string

### 2017-03-24 reports/progress_1/progress_1.tex
In progress report, subfigure Z statistics.

@@
 
-A sample of $Z$ statistics are shown in Figure \ref{fig:p_values} and significant pixels are shown in Figure \ref{fig:critical_values}.
+A sample of $Z$ statistics, along with significant pixels, are shown in Figure \ref{fig:p_values}.
 The Bonferroni correction was used to correct for multiple testing.
@@
 
-\begin{figure}
-	\centering
-	\centerline{
-	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/p_values.png}
-	}
-	\caption{A sample of $Z$ statistics obtained from comparing a scan from the test set to the true image. The $Z$ statistics were transformed using the standard Normal c.d.f.}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width = \textwidth]{../figures/meanVar/p_values.png}
+		\caption{$\Phi(Z)$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\includegraphics[width = \textwidth]{../figures/meanVar/critical_values.png}
+		\caption{Significant pixels}
+	\end{subfigure}
+	\caption{A sample of $Z$ statistics obtained from comparing a scan from the test set to the true image.
+In a) the $Z$ statistics were transformed using the standard Normal c.d.f.
+In b) highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
 	\label{fig:p_values}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\centerline{
-	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/critical_values.png}
-	}
-	\caption{Using the $Z$ statistics from Figure \ref{fig:p_values}, highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
-	\label{fig:critical_values}
-\end{figure}
+\end{figure*}
 

### 2017-03-24 meanVar/z_statistic_script.m

@@ -77,6 +77,7 @@ end
 
 %for 6 test image, plot the p value
 fig = figure;
+fig.Position(3:4) = [592, 675];
 for i = 1:6
     subplot(3,2,i);
     imagesc(p_array(:,:,i),[0,1]);
@@ -111,33 +112,33 @@ saveas(fig,'reports/figures/meanVar/critical_values.png','png');
 
 %---CHI SQUARED GOODNESS OF FIT TEST---%
 
-%p_image is an image containing the p values of each pixel from the chi
-%squared goodness of fit test
-p_image = zeros(block_data.height, block_data.width);
-%for each pixel in the image
-for i_width = 1:block_data.width
-    for i_height = 1:block_data.height
-        %get the z statistic from each test image
-        z_vector = reshape(z_array(i_height, i_width, :), [], 1);
-        %do the chi squared goodness of fit test, save the p value in p_image
-        p_image(i_height, i_width) = chi2gof_norm(z_vector, 5, false);
-    end
-end
-
-%plot the p values from the chi squared goodness of fit test
-figure;
-imagesc(p_image);
-colorbar;
-%get the critical value at the 2 sigma significance level
-p_critical = normcdf(-2) / block_data.area;
-%find significant pixels
-[y,x] = find(p_image < p_critical);
-hold on;
-%scatter plot significant pixels
-scatter(x,y,'r','filled');
-
-%plot histogram of p values
-figure;
-histogram(reshape(p_image, [], 1), 20, 'Normalization', 'countdensity');
-xlabel('p values');
-ylabel('Frequency density');
+% %p_image is an image containing the p values of each pixel from the chi
+% %squared goodness of fit test
+% p_image = zeros(block_data.height, block_data.width);
+% %for each pixel in the image
+% for i_width = 1:block_data.width
+%     for i_height = 1:block_data.height
+%         %get the z statistic from each test image
+%         z_vector = reshape(z_array(i_height, i_width, :), [], 1);
+%         %do the chi squared goodness of fit test, save the p value in p_image
+%         p_image(i_height, i_width) = chi2gof_norm(z_vector, 5, false);
+%     end
+% end
+% 
+% %plot the p values from the chi squared goodness of fit test
+% figure;
+% imagesc(p_image);
+% colorbar;
+% %get the critical value at the 2 sigma significance level
+% p_critical = normcdf(-2) / block_data.area;
+% %find significant pixels
[…]

### 2017-03-25 reports/progress_1/progress_1.tex
In progress report, complete.

@@
 \begin{equation}
-\overline{R}_j=\frac{\sum_{x=1}^w\sum_{y=1}^hR_j(x,y)}{n}
+\overline{R}_j=\frac{\sum_{x=1}^w\sum_{y=1}^hR_j(x,y)}{wh}
 \end{equation}
@@
 The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically.
-Second order panel-wise surface polynomials were fitted to the b/g/w images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}.
+Second order panel-wise surface polynomials were fitted to the $R_\text{b}(x,y)$, $R_\text{g}(x,y)$ and $R_\text{w}(x,y)$ images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}.
 The standardised residuals from the panel-wise fit are shown in Figure \ref{fig:polynomial_residual}.
@@
 The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects.
-Higher order polynomials can be considered but overfitting may be possible as may attempt to capture all the characteristics of the b/g/w images.
+Higher order polynomials can be considered but overfitting may be possible as it may attempt to capture all the characteristics of the b/g/w images.
 
@@
 	\caption{Shading uncorrected within pixel mean and variance grey value frequency density plot of each pixel in the segmented image of the 3D printed sample.
-A Gamma GLM was fitted with different link functions and polynomial ordera.
+A Gamma GLM was fitted with different link functions and polynomial orders.
 The solid and dotted lines are the mean response and the $\Phi(\pm 1)$ quantiles respectively.}
@@
 Pixels with grey values less than $5.8\times 10^3$ or more than $6.6\times 10^4$ were considered outliers.
-Outliers were replaced by the median of its 8 nearest neighbours.
+Outliers were replaced by the median of its 8 post shading correction nearest neighbours.
 
@@
 	\end{subfigure}
-	\caption{Frequency density plot of the standardised residuals from predicting the variance given the mean in test set using a training GLM with identity link function.}
+	\caption{Frequency density plot of the standardised residuals from predicting the variance given the mean using data in a test set. The model used is a GLM with identity link function.}
 	\label{fig:glm_residual}
@@
 \section{Compound Poisson}
-In the mini-project, a compound Poisson model was used to model the distribution of greyvalues in a pixel \cite{ip2016inside}.
+In the mini-project, a compound Poisson model was used to model the distribution of grey values in a pixel \cite{ip2016inside}.
 The model was built by assuming that photon arrivals are a Poisson process and that each photon has random energy, distributed according to an energy spectrum.
@@
 
-It is very well known that the marginal p.d.f.~$X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
+It is very well known that the marginal p.d.f.~of $X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
 \begin{equation}
@@
 
-For the Normal looking compound Poisson, both approximation performed well.
+For the Normal looking compound Poisson, both approximations performed well.
 \begin{figure*}

### 2017-08-15 reports/thesis/book.tex
Started on thesis draft.

\documentclass[12pt, a4paper]{memoir}
%\documentclass[12pt, a4paper, oldfontcommands]{memoir}
%\documentclass[12pt, a4paper]{report}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}

\let\footruleskip\undefined
\usepackage{fancyhdr}
\fancypagestyle{plain}{%
\fancyhf{}% clears all header and footer fields
\fancyhead[LE,RO]{\thepage}%
\renewcommand{\headrulewidth}{0pt}%
\renewcommand{\footrulewidth}{0pt}}

\DeclareMathOperator{\expfamily}{ExpFamily}
\DeclareMathOperator{\expectation}{\mathbb{E}}
\DeclareMathOperator{\variance}{\mathbb{V}ar}
\DeclareMathOperator{\cov}{\mathbb{C}ov}
\DeclareMathOperator{\corr}{\mathbb{C}orr}
\DeclareMathOperator{\bernoulli}{Bernoulli}
\DeclareMathOperator{\betaDist}{Beta}
\DeclareMathOperator{\dirichlet}{Dir}
\DeclareMathOperator{\bin}{Bin}
\DeclareMathOperator{\MN}{Multinomial}
\DeclareMathOperator{\prob}{\mathbb{P}}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\normal}{N}
\DeclareMathOperator{\gammaDist}{Gamma}
\DeclareMathOperator{\poisson}{Poisson}

\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\euler}{\mathrm{e}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\T}{^\textup{T}}
\newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
\newcommand{\BIC}{\textup{BIC}}

\newcommand{\vect}[1]{\mathbf{#1}}
\newcommand{\vectGreek}[1]{\boldsymbol{#1}}
\newcommand{\matr}[1]{\mathsf{#1}}

\begin{document}

\includepdf{title.pdf}

%\frontmatter
\section*{Abstract}
X-ray CT can be used for defect detection and quality control of 3D printing. This report will outline statistical methods for comparing x-ray scans of a 3D printed sample with its computer model under the face of uncertainty. Shading correction methods and the mean and variance relationship were investigated. Lastly the compound Poisson was reviewed.

\newpage

\section*{Acknowledgements}
\begin{itemize}
	\item Supervisors: Julia Brettschneider and Tom Nichols
	\item Inside Out Team: Wilfrid Kendall, Audrey Kueh, Jay Warnett and Clair Barnes
	\item EPSRC Funding: EP/L016710/1
\end{itemize}

\newpage
\tableofcontents*

%\mainmatter

\chapter{Introduction}

\chapter{Literature Review}

3D printing, formally additive manufacturing \citep{gibson2010additive} \citep{wong2012review}, has recently become state of the art technology which manufactures objects of complicated shapes with very high precision. It was developed in the 1980's \citep{kodama1981automatic} but recently it has been commercialised and is used in medical science \citep{kang20163d} and engineering \citep{wong2012review}. Because of such a wide range of applications, there has been a need for quality control and this can be done by scanning the 3D printed sample using x-ray computed tomography.

\section{X-ray Imaging}

\subsection{X-Ray Production}
Photons in CT scanning are produced in an X-ray tube. In an X-ray tube, a cathode, consisting of a heated filament, fires projectile electrons through an electric potential to a target which forms the anode \citep{michael2001x}, as shown in Figure \ref{fig:x_ray_tube}. Most of the kinetic energy of the projectile electrons is converted into heat however some is converted into electromagnetic radiation. This depends on how the projectile electrons interact with the atoms in the anode \citep{cantatore2011introduction}.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \emph{Source: G.~Michael (2001) \citep{michael2001x}}}
\label{fig:x_ray_tube}
\end{figure}

Bremsstrahlung radiation is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target. The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation. As a result, the photon energies in bremsstrahlung radiation is  a continuous spectrum and can range up to the maximum kinetic energy of the projectile electrons \citep{michael2001x}.

Characteristic radiation is due to projectile electrons colliding with electrons in the target atom and ionizing them. This produce vacancies in the electron shell and emits photons when the electrons in the target atom drops down back to the ground state. The energy of the emitted radiation is monoenergetic and depends on the binding energy of the target's atoms \citep{michael2001x}.

A typical energy spectrum of photons emitted from an X-ray tube is as shown in Figure \ref{fig:x_ray_spectrum}. The energy spectrum consist of both bremsstrahlung and characteristic radiation \citep{michael2001x}.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/x_ray_spectrum.png}
\caption{A typical energy spectrum of photons emitted from an X-ray tube. The continuous spectrum is the result of Bremmsstrahlung radiation. The peaks are the result of characteristic radiation. \emph{Source: G.~Michael (2001) \citep{michael2001x}}}
\label{fig:x_ray_spectrum}
\end{figure}

The voltage and current can be varied in the X-ray tube to produce different energy spectrums and rate of photon production. This can vary the results produced when collecting CT data \citep{cantatore2011introduction}. Another important factor is the focal spot size because smaller spot sizes produce sharper edges. Larger spot sizes produce unsharp results and this is know as the penumbra effect, as shown in Figure \ref{fig:x_ray_penumbra}. However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the X-ray tube.

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figures/x_ray_penumbra.png}
\caption{Larger focal spot sizes produces unsharp results. This is know as the penumbra effect. \emph{Source: F.~Welkenhuyzen et al.~(2009)\citep{welkenhuyzen2009industrial}}}
\label{fig:x_ray_penumbra}
\end{figure}

\subsection{Photon Interactions}
Photons emitted by the X-ray tube are projected onto the sample and interacts with it in a number of ways \citep{cantatore2011introduction}.

The sample can effectively absorb photons via the photoelectric effect or pair production \citep{cantatore2011introduction}. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}. In pair production, the photons convert into electron-position pairs by interacting with the Coulomb field of the sample's atomic nucleus \citep{hubbell2006electron}. In addition to getting absorbed, photons can be scattered by the sample. This happens when photons collide inelastically with and transfers its energy to the sample's electrons. This process is known as Compton scattering \citep{compton1923quantum}.

Suppose a mono-energetic X-ray pencil beam attenuating through an object with varying attenuation coefficient in position $\mu=\mu(x)$. The beam starts at $x=0$ and is detected at $x=L$, then the attenuation (decrease in X-ray intensity from $I_0$ to $I_1$) is given as \citep{cantatore2011introduction}
\begin{equation}
I_1 = I_0\exp\left[\int_0^L-\mu(x)\diff x\right].
\label{eq:beerLaw}
\end{equation}
By comparing the intensity before and after attenuation, the integral of the attenuation coefficient along the path of the X-ray can be calculated. Because of the discrete nature of pixels, the integral is usually replaced by a sum \citep{michael2001x}.

However it was shown that the attenuation coefficient does depend on the energy of the photons \citep{elbakri2002statistical}. Thus $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}. In general low energy photons are more likely to be absorbed than high energy photons, this increases the average energy of the attenuated photons and can be a source of error in CT scanning. This is referred to beam hardening and can cause inaccuracies in Equation \eqref{eq:beerLaw} \citep{michael2001x}. This can be reduced by placing a thin sheet of filter to absorb low energy photons \citep{welkenhuyzen2009industrial} or by correcting it in the data analysis stage \citep{michael2001x}.

\subsection{Detection and Reconstruction}
Most X-ray detectors are scintillator-photodiode detectors. The photons interact with the scintiallator material and produce visible light. The visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}. The detectors used in CT scanning are flat bed scanner which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.

\section{X-ray Computed Tomography}
Computed tomography (CT) scanning is a 3D imaging technique. It does this by reconstructing the geometry of the sample through a series of 2D X-ray images of the sample. The sample rotates after each image taken \citep{cantatore2011introduction}.

Figure \ref{fig:x_ray_ct} shows a diagram on how CT scanning works. A 2D image is taken by projecting X-ray photons onto the stationary sample. The photons are then scattered or absobred by the sample.  Some of these photons are then detected by an X-ray detector on the other side of the sample, which produces an image. After an image has been taken, the object rotates and another image is taken. Finally after a number of images, a 3D reconstruction of the object can be estimated \citep{cantatore2011introduction}.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/x_ray_ct.png}
\caption{X-ray computed tomography reconstructs the sample by projecting photons onto a rotating sample. The photons are then detected by the detector. \emph{Source: \url{http://www.phoenix-xray.com/}}}
\label{fig:x_ray_ct}
\end{figure}

CT scanning was invented by G. Hounsfield \citep{hounsfield1980computed} in the 1980's and it was mainly used for medical imaging. The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}. Recently CT has been used industrially for non-destructive testing in manufacturing \citep{cantatore2011introduction}. One possible application would be inspecting 3D printed samples \citep{villarraga2015assessing}. Other uses in science include the investigation of batteries \citep{o2017investigating} and materials \citep{wang2017x} \citep{zhang2016x}.

Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}. There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.

Studies have been done to use x-ray CT to do defection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}. This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}. Voids then can be classified as defects if the voids are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{amrhein2014characterization} \citep{gandossi2010probability}.

Full 3D x-ray CT scans can be slow and may not generalised well in production lines. However there is potential to bring in methods such as those used in airport luggage inspection to speed up to process \cite{warnett2016towards}.

There are many sources of error in CT scanning \citep{cantatore2011introduction} and this can cause problems when reconstructing the geometry of the sample. Sources of error include: dead pixels in the detector \citep{brettschneider2014spatial}, use of cone beams \citep{sun2016applications}, beam hardening and the orientation of the sample \citep{corcoran2016observations}.

The scale of the 2D images can be calibrated with the use of reference standards \citep{bartscher2007enhancement} \citep{lifton2013application}.

\section{Compound Poisson}

\chapter{Compound Poisson}
\chapter{Inference}

\bibliographystyle{apalike}
\bibliography{../bib}

\end{document}

### 2017-08-16 reports/thesis/book.tex
Added compound Poisson literature.

@@
 Full 3D x-ray CT scans can be slow and may not generalised well in production lines.
-However there is potential to bring in methods such as those used in airport luggage inspection to speed up to process \cite{warnett2016towards}.
+However there is potential to bring in methods such as those used in airport luggage inspection to speed up to process \citep{warnett2016towards}.
 
@@
 
+The grey values of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector.
+When the photons interact with the scintillator, they are converted into visible light.
+The visible light photons are then detected and converted into a grey value.
+How the detected visible light is converted is important in modelling the grey value.
+
+Should the grey value be proportional to the number of photons detected, the detector is known as a quantum counter and the grey value is a Poisson random variable, up to a constant \citep{whiting2006properties}.
+However if they grey value records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector.
+The grey value has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}.
+There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
+
+Many reconstruction algorithms have been proposed considering the compound Poisson nature of the detector \citep{elbakri2002statistical} \citep{elbakri2003statistical} \citep{lasio2007statistical} \citep{xie2008x} and beam hardening  \citep{elbakri2003efficient}.
+These will not be discussed here as they are beyond the scope of this thesis.
+
+Experiments have been done to verify the compound Poisson nature of the detector.
+This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers.
+It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent any may be electronic noise.
+The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.
+
+The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
+\begin{equation*}
+Y\sim\poisson(\lambda\tau)
+\end{equation*}
+and
+\begin{equation*}
+\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=1,2,3,\dotdotdot \ .
+\end{equation*}
+Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$. Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
+\begin{equation}
+X|Y = \sum_{i=1}^{Y}U_i+\kappa
+\label{eq:compoundPoisson_X|Y}
+\end{equation}
+where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained my marginalising the joint p.d.f.
+\begin{equation*}
+p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \ .
+\end{equation*}
+However it should be noted that $X=0$ if and only if $Y=0$. Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then
+\begin{equation}
+p_X(x) = 
+\begin{cases}
+\delta(x) \euler^{-\lambda} & \text{ if } x=0 \\ 
+\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ if } x>0 
+\end{cases}
+\end{equation}
+where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.
+
+The m.g.f.~of $X$ has a nicer form however. Let the m.g.f.~of $X$ be
+\begin{equation*}
+M_X(\theta)=\expectation\left[\euler^{X\theta}\right] \ .
+\end{equation*}
+This can be computed using the result for conditional expectations
+\begin{equation*}
+M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right] \ .
+\end{equation*}
+Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
+\begin{equation*}
+M_X(\theta)=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
+\end{equation*}
+\begin{equation*}
+M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right] \ .
+\end{equation*}
+But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.
+\begin{equation*}
+M_U(\theta)=\expectation\left[\euler^{U\theta}\right] \ ,
+\end{equation*}
+then
+\begin{equation*}
+M_X(\theta)=\expectation\left(
+\expectation\left[\euler^{\theta U_1}|Y\right]\cdot
+\expectation\left[\euler^{\theta U_2}|Y\right]\cdot
+\dotdotdot \cdot
+\expectation\left[\euler^{\theta U_Y}|Y\right]
+\right)
+\end{equation*}
+\begin{equation*}
+M_X(\theta)=\expectation\left[\left(M_U(\theta)\right)^Y\right]
+\end{equation*}
+\begin{equation*}
+M_X(\theta)=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right] \ .
+\end{equation*}
+It can be shown that the m.g.f.~of $Y$ is
+\begin{equation}
+M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]
+=\exp\left[
+\lambda\left(
+\euler^\theta-1
+\right)
+\right]
+\end{equation}
+then
+\begin{equation}
+M_X(\theta)
+=
+\exp\left[
+\lambda\left(
+M_U(\theta)-1
+\right)
+\right] \ .
+\end{equation}
+As long as the m.g.f.~of $U$ is known, then m.g.f.~of $X$ can be written in closed form.
+
+Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
+\begin{align*}
+M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
+M_X'(\theta)&=M_X(\theta)\lambda M_U'(\theta)
+\end{align*}
+then
+\begin{equation}
+\expectation\left[X\right]=\lambda\expectation\left[U\right] \ .
+\end{equation}
+Conducting the same procedure
+\begin{equation*}
+M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta) \ ,
+\end{equation*}
+the variance can be obtained
+\begin{align*}
+\variance\left[X\right]&=M_X''(0)-\left[M_X'(0)\right]^2 \\
+\variance\left[X\right]&=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2 \\
+\variance\left[X\right]&=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
+\end{align*}
+resulting in
+\begin{equation}
+\variance\left[X\right] = \lambda\expectation\left[U^2\right] \ .
+\end{equation}
+This can be extended for higher moments.
+
+Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of $X$.
+By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.
+
+A special case of the compound Poisson is the compound Poisson-Gamma model. The model is as follows:
+\begin{equation}
+Y\sim\poisson\left(\nu\tau\right)
+\end{equation}
+\begin{equation}
+U\sim\gammaDist\left(\alpha,\lambda\right)
+\end{equation}
+\begin{equation}
+X = \sum_{i=1}^Y U_i
+\end{equation}
+where $\alpha$ and $\lambda$ are the shape and rate parameters, $\nu$ is the photon rate and $\tau$ is the time exposure. Then it can be shown that
+\begin{equation}
+X|Y\sim\gammaDist\left(Y\alpha,\lambda\right) \ .
+\end{equation}
+This is special because the marginal $X$ is in the exponential family, more specifically in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}.
+
+It is very well known that the marginal p.d.f.~of $X$ is intractable. However the m.g.f.~can be written in closed form. The m.g.f.~is defined as
+\begin{equation}
+M(\theta)=\expectation\left[\euler^{\theta X}\right] \ .
+\end{equation}
+Using the property of conditional expectations
+\begin{equation*}
+M(\theta)=\expectation\expectation\left[\euler^{\theta X}\right|Y]
+\end{equation*}
+and then the properties of the Gamma distribution
+\begin{equation*}
+M(\theta)=\expectation\left[\left(\frac{\lambda}{\lambda-\theta}\right)^{Y\alpha}\right] \ .
+\end{equation*}
+Finally using the m.g.f.~of the Poisson distribution
+\begin{equation}
+M(\theta)=\exp\left[\nu\tau\left(\left(\frac{\lambda}{\lambda-\theta}\right)^{\alpha}-1\right)\right] \ .
+\end{equation}
+Moments up to a number of orders then can be obtained. For example
+\begin{equation}
+\expectation\left[X\right]=\frac{\alpha\nu\tau}{\lambda}
+\end{equation}
+\begin{equation}
+\variance\left[X\right]=\frac{\alpha(\alpha+1)\nu\tau}{\lambda^2}
+\end{equation}
+\begin{equation}
+\expectation\left[(X-\mu)^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\nu\tau}{\lambda^3}
+\end{equation}
+where $\expectation\left[X\right]=\mu$.
+
+For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, the unknown parameters $\nu$, $\alpha$ and $\lambda$, can be estimated using method of moments.
+Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\mu\right)^j\right]$ for $j=2,3$.
+Then the estimators
+\begin{equation}
+\widehat{\nu}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\tau\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
+\end{equation}
+\begin{equation}
+\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
+\end{equation}
+\begin{equation}
+\widehat{\lambda}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
+\end{equation}
+are method of moments estimators of $\nu$, $\alpha$ and $\lambda$ respectively \citep{withers2011compound}.
+These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+
+Estimation can also be done using the EM algorithm \citep{dempster1977maximum}, treating the random variable $Y$ to be latent.
+The problem with the EM algorithm is that the E step is not tractable.
+This problem can be tackled by truncating the infinite sum in a clever way so that the sum is over a number of high contributing terms to save computational cost \citep{dunn2005series}.
+Another way is to use MCMC in the E step \citep{booth1999maximizing}.
+
+There exist approximate maximum log likelihood estimators.
+Under certain conditions, the random variable $X$ can be approximated using the Normal distribution and the likelihood can be maximised numerically.
+Another approximation is to use the saddle point approximation \citep{daniels1954saddlepoint} to approximate the p.d.f.~of $X$, thus an approximate likelihood can be obtained.
+
+Lastly, because $X$ is in the dispersion exponential family, parameter estimation can be done through the GLM framework \citep{zhang2013likelihood}.
+The GLM framework and the saddlepoint approximation were used extensively for insurance claim data \citep{jorgensen1994fitting} \citep{jensen1991saddlepoint}.
+
 \chapter{Compound Poisson}

### 2017-08-17 reports/thesis/book.tex
Compound Poisson literature review.

--- 2017-08-15 reports/thesis/book.tex
@@
 \DeclareMathOperator{\poisson}{Poisson}
+\DeclareMathOperator{\CPoisson}{CP\Gamma}
 
@@
 
+The grey values of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector.
+When the photons interact with the scintillator, they are converted into visible light.
+The visible light photons are then detected and converted into a grey value.
+How the detected visible light is converted is important in modelling the grey value.
+
+Should the grey value be proportional to the number of photons detected, the detector is known as a quantum counter and the grey value is a Poisson random variable, up to a constant \citep{whiting2006properties}.
+However if the grey value records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector.
+The grey value has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}.
+There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
+
+Many reconstruction algorithms have been proposed considering the compound Poisson nature of the detector \citep{elbakri2002statistical} \citep{elbakri2003statistical} \citep{lasio2007statistical} \citep{xie2008x} and with beam hardening correction \citep{elbakri2003efficient}.
+These will not be discussed here as they are beyond the scope of this thesis.
+
+Experiments have been done to verify the compound Poisson nature of the detector.
+This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers.
+It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
+The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.
+
+The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
+\begin{equation*}
+Y\sim\poisson(\lambda)
+\end{equation*}
+and
+\begin{equation*}
+\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=1,2,3,\dotdotdot
+\end{equation*}
+where $\lambda>0$ is the Poisson rate parameter.
+Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$.
+Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
+\begin{equation}
+X|Y = \sum_{i=1}^{Y}U_i+\kappa
+\label{eq:compoundPoisson_X|Y}
+\end{equation}
+where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
+\begin{equation*}
+p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0\ .
+\end{equation*}
+However it should be noted that $X=0$ if and only if $Y=0$ with probability
+\begin{equation*}
+\prob(X=0)=\euler^{-\lambda} \ .
+\end{equation*}
+Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
+\begin{equation}
+p_X(x) = \delta(x) \euler^{-\lambda} + \sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for }x\geqslant 0
+\end{equation}
+where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.
+
+The m.g.f.~of $X$ has a nicer form however. Let the m.g.f.~of $X$ be
+\begin{equation*}
+M_X(\theta)=\expectation\left[\euler^{X\theta}\right] \ .
+\end{equation*}
+This can be computed using the result for conditional expectations
+\begin{equation*}
+M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right] \ .
+\end{equation*}
+Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
+\begin{equation*}
+M_X(\theta)=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
+\end{equation*}
+\begin{equation*}
+M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right] \ .
+\end{equation*}
+But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.
+\begin{equation*}
+M_U(\theta)=\expectation\left[\euler^{U\theta}\right] \ ,
+\end{equation*}
+then
+\begin{equation*}
+M_X(\theta)=\expectation\left(
+\expectation\left[\euler^{\theta U_1}|Y\right]\cdot
+\expectation\left[\euler^{\theta U_2}|Y\right]\cdot
+\dotdotdot \cdot
+\expectation\left[\euler^{\theta U_Y}|Y\right]
+\right)
+\end{equation*}
+\begin{equation*}
+M_X(\theta)=\expectation\left[\left(M_U(\theta)\right)^Y\right]
+\end{equation*}
+\begin{equation*}
+M_X(\theta)=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
+\end{equation*}
+\begin{equation*}
+M_X(\theta) = M_Y\left(\ln(M_U(\theta)\right)
+\end{equation*}
+where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
+\begin{equation}
+M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]
+=\exp\left[
+\lambda\left(
+\euler^\theta-1
+\right)
+\right]
+\end{equation}
+then
+\begin{equation}
+M_X(\theta)
+=
+\exp\left[
+\lambda\left(
+M_U(\theta)-1
+\right)
+\right] \ .
+\end{equation}
+As long as the m.g.f.~of $U$ is known, then m.g.f.~of $X$ can be written in closed form.
+
+Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
+\begin{align*}
+M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
+M_X'(\theta)&=M_X(\theta)\lambda M_U'(\theta)
+\end{align*}
+then
+\begin{equation}
+\expectation\left[X\right]=\lambda\expectation\left[U\right] \ .
+\end{equation}
+Conducting the same procedure
+\begin{equation*}
+M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta) \ ,
+\end{equation*}
+the variance can be obtained
+\begin{equation*}
+\variance\left[X\right]=M_X''(0)-\left[M_X'(0)\right]^2
+\end{equation*}
+\begin{equation*}
+\variance\left[X\right]=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
+\end{equation*}
+\begin{equation*}
+\variance\left[X\right]=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
+\end{equation*}
+resulting in
+\begin{equation}
+\variance\left[X\right] = \lambda\expectation\left[U^2\right] \ .
+\end{equation}
+This can be extended for higher moments.
+
+Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$.
+By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.
+
+If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
+\begin{equation}
+U\sim\gammaDist\left(\alpha,\beta\right)
+\end{equation}
+where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
+\begin{equation}
+X\sim\CPoisson(\lambda,\alpha,\beta) \ .
+\end{equation}
+The conditional distribution can be shown to be
+\begin{equation}
+X|Y\sim\gammaDist\left(Y\alpha,\lambda\right) \ .
+\end{equation}
+
+Using results derived earlier, the m.g.f.~of the of $X$ is
+\begin{equation}
+M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
+\end{equation}
+and moments can be obtained from it such as
+\begin{equation}
+\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
+\end{equation}
+\begin{equation}
+\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
+\label{eq:compoundPoisson_variance}
+\end{equation}
+and
+\begin{equation}
+\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3} \ .
+\end{equation}
+
+The p.d.f.~can be shown to be
+\begin{equation}
+p_X(x) = 
+\delta(x) \euler^{-\lambda}
++
+\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!}
+\quad\text{for }x\geqslant 0
+\label{eq:compoundPoisson_pdf}
+\end{equation}
+and it is well known the infinite sum cannot be written in closed form.
+There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddle point approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
+Of course direction simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated.
+The p.d.f.~then can be estimated using these simulated samples.
+
+For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, parameter estimation can be difficult.
+Maximum likelihood estimation is very complicated \citep{withers2011compound}.
+It can be made simpler by fixing $\alpha$ to be known \citep{withers2011compound} but this is not useful in this context.
+
+Because the moments of a compound Poisson-Gamma random variable can be obtained easily, method of moments estimators can be obtained.
+Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
+Then the estimators
+\begin{equation}
+\widehat{\lambda}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
+\end{equation}
+\begin{equation}
+\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
+\end{equation}
+\begin{equation}
+\widehat{\beta}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
+\end{equation}
+are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}.
+These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+
+However, parameter estimation can be made easier once it can be realised that the compound Poisson-Gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}.
+To show this, it is particular useful to reparametrize the compound Poisson-Gamma distribution using the following:
+\begin{equation}
+p=\frac{2+\alpha}{1+\alpha} \ ,
+\end{equation}
+\begin{equation}
+\mu=\frac{\lambda\alpha}{\beta} \ ,
+\end{equation}
+\begin{equation}
+\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}} \ .
+\end{equation}
+The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. It can be shown that $1<p<2$, $\mu>0$ and $\phi>0$.
+
+By rearranging the parameters to get
+\begin{equation}
+\lambda=\frac{\mu^{2-p}}{\phi(2-p)}
+\end{equation}
+\begin{equation}
+\alpha=\frac{2-p}{p-1}
+\end{equation}
+\begin{equation}
+\beta=\frac{1}{\phi(p-1)\mu^{p-1}}
+\end{equation}
+and substituting it into Equation \eqref{eq:compoundPoisson_pdf}, the p.m.f.~at zero can be shown to be
+\begin{equation}
+\prob(X=0) = \exp\left[
+-\frac{\mu^{2-p}}{\phi(2-p)}
+\right]
+\end{equation}
+and the p.d.f.~for $x>0$ is
+\begin{multline*}
+p_X(x) = \sum_{y=1}^{\infty}
+\left[\frac{1}{\phi(p-1)\mu^{p-1}}\right]^{y\alpha}
+\frac{1}{\Gamma(y\alpha)}
+x^{y\alpha-1}
+\exp\left[-\frac{x}{\phi(p-1)\mu^{p-1}}\right]
+\\
+\exp\left[-\frac{\mu^{2-p}}{\phi(2-p)}\right]
+\left[\frac{\mu^{2-p}}{\phi(2-p)}\right]^y
+\frac{1}{y!} \ .
+\end{multline*}
+Tidying up the equation
+\begin{multline*}
+p_X(x) = 
+\exp\left[\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)\right]\frac{1}{x}
+\\
+\sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)} \ .
+\end{multline*}
+To simplify further, it should be noted that
+\begin{align*}
+2-p-\alpha(p-1) &= 2-p - \frac{2-p}{p-1}(p-1)
+\\&=0
+\end{align*}
+so that
+\begin{equation}
+p_X(x) = 
+\exp\left[\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)\right]\frac{1}{x}
+\sum_{y=1}^{\infty}W_y(x,p,\phi)
+\end{equation}
+where
+\begin{equation}
+W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)} \ .
+\end{equation}
+
+Those familiar with generalised linear models \citep{nelder1972generalized} \citep{mccullagh1984generalized} will notice that for fixed $p$ or $\alpha$, the above is in the form of a distribution in the dispersive exponential family.
+Parameter estimation then can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
+These has applications in for example insurance claim data \citep{jorgensen1994fitting} \citep{smyth2002fitting}.
+
+Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
+One easy way is to to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
+
+One special property of the compound Poisson-Gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}. It has a special variance mean relationship
+\begin{equation}
+\variance[X] = \phi \mu^p
+\end{equation}
+where, as a reminder, $1<p<2$. This can be derived using Equation \eqref{eq:compoundPoisson_variance} or via the partition function $Z$. That is let
+\begin{equation}
+\theta = \frac{\mu^{1-p}}{1-p}
+\end{equation}
+and
+\begin{equation}
+\ln Z = \frac{1}{\phi(2-p)\theta^\alpha(1-p)^\alpha} \ ,
+\end{equation}
+then
+\begin{equation}
+\variance[X] = \phi^2 \frac{\partial^2\ln Z}{\partial\theta^2} \ .
+\end{equation}
+
 \chapter{Compound Poisson}

### 2017-08-18 reports/thesis/book.tex
Added compound Poisson normal approximation to thesis.

@@
 \usepackage{pdfpages}
+
+\setcounter{tocdepth}{2}
+\setcounter{secnumdepth}{2}
 
@@
 \DeclareMathOperator{\CPoisson}{CP\Gamma}
+\DeclareMathOperator{\normDist}{N}
 
@@
 Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
-One easy way is to to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
+One easy way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
 
@@
 \chapter{Compound Poisson}
+In this chapter, the compound Poisson-Gamma distribution is reviewed and studied.
+Firstly methods for evaluating the density of the compound Poisson-Gamma distribution are discussed.
+Approximations such as the Normal approximation or saddle point approximation \citep{daniels1954saddlepoint} can be used.
+These approximate densities can be written in closed form.
+Exact methods can be computationally challenging when dealing with the infinite sum but can be done when summing over important terms \citep{dunn2005series}.
+Next, a method for parameter estimation will be proposed here using the EM algorithm \citep{dempster1977maximum}.
+However in the end of the chapter, it will be shown that no unique maximum likelihood estimator exist when certain parameters of the compound Poisson-Gamma distribution gets too large.
+
+\section{Density Evaluation}
+Suppose $X\sim\CPoisson(\lambda,\alpha,\beta)$ and $\lambda,\alpha,\beta>0$ then the p.d.f.~of $X$ is
+\begin{equation}
+p_X(x) = 
+\delta(x) \euler^{-\lambda}
++
+\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y
+\quad\text{for }x\geqslant 0
+\end{equation}
+where
+\begin{equation}
+W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!} \ .
+\end{equation}
+The evaluation of this p.d.f.~is difficult because the sum of $W_y$ cannot be simplified. However the m.g.f.~of $X$ can be written down in closed form
+\begin{equation}
+M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right] \ .
+\end{equation}
+The m.g.f.~allows the study of limiting distributions of the compound Poisson-Gamma distribution.
+These limiting distributions then can be used to approximate the p.d.f.~of a compound Poisson-Gamma random variable.
+
+The saddle point approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation  of the m.g.f.~giving the p.d.f.
+However inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}.
+The saddle point approximation will be studied here.
+
+Lastly the infinite sum can be computationally summed in a clever way.
+This was done by summing only large terms in the sum and ignores small terms.
+By using Stirling's approximation, the largest term in the sum can be approximately found \citep{dunn2005series}.
+
+\subsection{Normal Approxmation}
+The m.g.f.~provides a starting point to what limiting distributions the compound Poisson-Gamma distribution converges to for large parameters.
+However the m.g.f.~of $X$ itself it not useful because when considering $\lambda\rightarrow\infty$ or $\alpha\rightarrow\infty$ then $M_X(\theta)\rightarrow\infty$.
+Also for $\beta\rightarrow\infty$, then $M_X(\theta)\rightarrow 1$ which is not useful either.
+
+The compound Poisson-Gamma random variable $X$ should be standardised to obtain useful limiting results from the m.g.f. Let
+\begin{equation}
+Z = \frac{X-\expectation[X]}{\sqrt{\variance[X]}} \ ,
+\end{equation}
+then using previous results
+\begin{equation*}
+Z = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}\left(
+X-\frac{\alpha\lambda}{\beta}
+\right)
+\end{equation*}
+\begin{equation}
+Z = bX+a
+\end{equation}
+where
+\begin{equation}
+b = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
+\end{equation}
+and
+\begin{equation}
+a = -\sqrt{\frac{\alpha\lambda}{\alpha+1}} \ .
+\end{equation}
+
+The m.g.f.~of $Z$ is then
+\begin{equation*}
+M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
+\end{equation*}
+\begin{equation*}
+M_Z(\theta)=\expectation\left[\euler^{(bX+a)\theta}\right]
+\end{equation*}
+\begin{equation*}
+M_Z(\theta)=\euler^{a\theta}M_X(b\theta) \ .
+\end{equation*}
+Substituting in the values
+\begin{equation*}
+M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
+\exp\left[
+\lambda\left(
+\left(
+\frac{\beta}{\beta-\frac{\beta\theta}{\sqrt{\alpha(\alpha+1)\lambda}}}
+\right)^\alpha-1
+\right)
+\right]
+\end{equation*}
+\begin{equation*}
+M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
+\exp\left[
+\lambda\left(
+\left(
+\frac{\sqrt{\alpha(\alpha+1)\lambda}}{\sqrt{\alpha(\alpha+1)\lambda}-\theta}
+\right)^\alpha
+-1\right)
+\right]
+\end{equation*}
+or in a different form
+\begin{equation}
+M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
+\exp\left[
+\lambda\left(
+\left(
+1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}
+\right)^{-\alpha}
+-1\right)
+\right] \ .
+\end{equation}
+
+The above form is useful so that the binomial expansion can be conducted, that is
+\begin{multline}
+\left(
+1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}
+\right)^{-\alpha}
+=
+1+
+\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
+\\
+\text{for }\frac{\|\theta\|}{\sqrt{\alpha(\alpha+1)\lambda}}<1 \ .
+\end{multline}
+Substituting in the binomial expansion
+\begin{equation*}
+M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
+\exp\left[
+\lambda
+\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
+\right] \ .
+\end{equation*}
+Writing in full the $r=1,2$ terms
+\begin{multline*}
+M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
+\exp\left[
+\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
++\frac{\theta^2}{2}
+\right.\\\left.
++\lambda\sum_{r=3}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
+\right]
+\end{multline*}
+and a term cancels out to get
+\begin{equation}
+M_Z(\theta)=
+\exp\left[
+	\frac{\theta^2}{2}
+	+\sum_{r=3}^\infty
+		\frac{\theta^r
+			\prod_{s=1}^r(\alpha+s-1)
+		}
+		{(\alpha(\alpha+1))^{r/2}r!}
+		\lambda^{1-r/2}
+\right] \ .
+\end{equation}
+
+For large $\lambda$
+\begin{equation}
+\lim_{\lambda\rightarrow\infty}M_Z(\theta)=\exp\left[\frac{\theta^2}{2}\right]
+\end{equation}
+which is the same as the m.g.f.~of a standard Normal variable, therefore
+\begin{equation}
+\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1) \ .
+\end{equation}
+This should make sense as for high $\lambda$, the Poisson random variable has a high expectation, increasing the number of Gamma random variables in a summation.
+Increasing the number of terms in a summation will triggle the central limit theorem.
+
+Next for high $\alpha$, it should be noted that
+\begin{equation*}
+\lim_{\alpha\rightarrow\infty}
+	\frac{
+		\prod_{s=1}^r(\alpha+s-1)
+	}
+	{(\alpha(\alpha+1))^{r/2}}
+=
+\frac{
+		\prod_{s=1}^r\alpha
+	}
+	{\alpha^{r}}
+\end{equation*}
+so that
+\begin{equation}
+\lim_{\alpha\rightarrow\infty}
+	\frac{
+		\prod_{s=1}^r(\alpha+s-1)
+	}
+	{(\alpha(\alpha+1))^{r/2}} = 1 \ .
+\end{equation}
+As a result
+\begin{equation}
+\lim_{\alpha\rightarrow\infty}
+M_Z(\theta)=
+\exp\left[
+	\frac{\theta^2}{2}
+	+\sum_{r=3}^\infty
+		\frac{\theta^r}
+		{r!}
+		\lambda^{1-r/2}
+\right] \ .
+\end{equation}
+However this shows that taking the limit $\alpha\rightarrow\infty$ is not enough to get a Normal limiting distribution.
+For a Normal limiting distribution, the limit must be accompanied with the limit $\lambda\rightarrow\infty$, that is
+\begin{equation}
+\lim_{\lambda\rightarrow\infty}\lim_{\alpha\rightarrow\infty}Z\sim\normal(0,1) \ .
+\end{equation}
+
+Finally it should be noted that $M_Z(\theta)$ is independent of $\beta$. Thus $\beta$ will have no effect on the convergence to a Normal limiting distribution.
+
+The limiting case where $\lambda\rightarrow 0$, $\alpha\rightarrow 0$ and $\beta\rightarrow 0$ will not be discussed here.
+
+\subsection{Normal Approximation - General Case}
+It was shown in certain situations, the compound Poisson-Gamma distribution can be approximated with the Normal distribution. This can be extended to the general compound Poisson.
+
+Let $Y\sim\poisson(\lambda)$ where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be some random variable for i.i.d.~$i=1,2,3,\dotdotdot$ with m.g.f.~$M_U(\theta)$. Let
+\begin{equation}
+X|Y = \sum_{i=1}^{Y}U_i \ .
+\end{equation}
+
+It can be shown that the m.g.f.~of $X$ is
+\begin{equation}
+M_X(\theta)=\exp\left[
+\lambda(M_U(\theta)-1)
+\right] \ .
+\end{equation}
+As in the compound Poisson-Gamma case, it is useful to standardise $X$ using
+\begin{equation*}
+Z = \frac{X-\lambda\expectation[U]}{\sqrt{\lambda\expectation[U^2]}}
+\end{equation*}
+\begin{equation}
+Z = \frac{X}{\sqrt{\lambda\expectation[U^2]}}
+-\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}} \ .
+\end{equation}
+The m.g.f.~of $Z$ is then
+\begin{equation*}
+M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
+\end{equation*}
+\begin{equation*}
+M_Z(\theta)=\exp\left[-\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}\right]
+\exp\left[
+\lambda\left(
+M_U\left(\frac{\theta}{\sqrt{\lambda\expectation[U^2]}}\right)-1
+\right)
+\right]
+\end{equation*}
+
+Taking the Taylor's series of $M_U(\theta)$
+\begin{equation}
+M_U(\theta) = 1 + \sum_{r=1}^\infty\frac{\theta^r}{r!}M_U^{(r)}(0)
+\quad\text{for }\lim_{r\rightarrow\infty}
+\left\|
+\frac{\theta}{r+1}\frac{M_U^{(r+1)}(0)}{M_U^{(r)}(0)}
+\right\|<1
+\end{equation}
+and substituting it into $M_Z(\theta)$
+\begin{equation*}
+M_Z(\theta)=\exp\left[-\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}\right]
+\exp\left[
+\lambda\sum_{r=1}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
+\right] \ .
+\end{equation*}
+Writing out in full the $r=1,2$ terms
+\begin{multline*}
+M_Z(\theta)=\exp\left[-\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}\right]
+\exp\left[
+\theta\frac{\sqrt{\lambda}M_U'(0)}{\sqrt{\expectation[U^2]}}
++
+\frac{\theta^2M_U''(0)}{2\expectation[U^2]}
+\right.\\+\left.
+\lambda\sum_{r=3}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
+\right] \ .
+\end{multline*}
+By using the fact that $\expectation[U^r]=M_U^{(r)}(0)$ for $r=0,1,2\dotdotdot$, a few terms cancel out to get
+\begin{equation}
+M_Z(\theta)=\exp\left[
+\frac{\theta^2}{2}
++
+\sum_{r=3}^\infty\frac{\theta^r \expectation[U^r]}{(\expectation[U^2])^{r/2}r!}\lambda^{1-r/2}
+\right] \ .
+\end{equation}
+
+For the limit $\lambda\rightarrow\infty$
+\begin{equation}
+\lim_{\lambda\rightarrow\infty}M_Z(\theta) = \exp\left[\frac{\theta^2}{2}\right]
+\end{equation}
+then it can be concluded that
+\begin{equation}
+\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1) \ .
+\end{equation}
+The convergence can be aided if the ratio $\dfrac{\expectation[U^r]}{(\expectation[U^2])^{r/2}}$ for $r=3,4,5,\dotdotdot$ are small.
+
 \chapter{Inference}

### 2017-08-19 reports/thesis/book.tex
Saddlepoint in thesis.

@@
 
-%\frontmatter
+\frontmatter
 \section*{Abstract}
@@
 
-%\mainmatter
+\mainmatter
 
@@
 and it is well known the infinite sum cannot be written in closed form.
-There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddle point approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
+There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
 Of course direction simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated.
@@
 Firstly methods for evaluating the density of the compound Poisson-Gamma distribution are discussed.
-Approximations such as the Normal approximation or saddle point approximation \citep{daniels1954saddlepoint} can be used.
+Approximations such as the Normal approximation or saddlepoint approximation \citep{daniels1954saddlepoint} can be used.
 These approximate densities can be written in closed form.
@@
 
-The saddle point approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation  of the m.g.f.~giving the p.d.f.
+The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation  of the m.g.f.~giving the p.d.f.
 However inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}.
-The saddle point approximation will be studied here.
+The saddlepoint approximation will be studied here.
 
@@
 
-Taking the Taylor's series of $M_U(\theta)$
+Taking the Maclaurin series of $M_U(\theta)$
 \begin{equation}
@@
 
+\subsection{Saddlepoint approximation}
+The m.g.f.~of a random variable $X$ is defined to be
+\begin{equation}
+M_X(\theta)=\expectation[\euler^{\theta X}]
+=
+\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x \ .
+\end{equation}
+For a given m.g.f., the saddlepoint approximation \cite{daniels1954saddlepoint} \cite{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
+\begin{equation}
+p_X(x)\approx\left(2\pi K_X''(s)\right)^{-1/2}\exp\left[K_X(s)-sx\right]
+\label{eq:saddlePoint:generalSaddlePoint}
+\end{equation}
+where $K_X(\theta) = \ln\left(M_X(\theta)\right)$, and $s=s(x)$ is the solution to the saddle point equation $K_X'(s)=x$.
+
+For the compound Poisson-Gamma distribution, the saddle point approximation is given as 
+\begin{multline}
+p_X(x)\approx
+\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+\euler^{-x\beta}
+\exp\left[x^{\frac{\alpha}{\alpha+1}}
+	\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
+\right]
+\\
+\text{for }x>0 \ .
+\label{eq:saddle_point_approx}
+\end{multline}
+The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary.
+Thus it may be more sensible to write the approximation up to a constant
+\begin{equation}
+p_X(x)\propto x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}\exp\left[x^{\frac{\alpha}{\alpha+1}}
+	\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
+\right] \ .
+\end{equation}
+
+For the remainder of this section, it will be shown how the saddlepoint approximation can be algebraically derived.
+First of all the cumulant generating function $K_X(\theta)$ can be obtained from the m.g.f.
+\begin{equation}
+K_X(\theta) = \lambda\left[
+\left(\frac{\beta}{\beta-\theta}\right)^\alpha-1
+\right] \ .
+\end{equation}
+Taking the derivative with respect to $\theta$
+\begin{equation}
+K_X'(\theta)=\frac{\lambda\alpha\beta^\alpha}{(\beta-\theta)^{\alpha+1}}
+\end{equation}
+and this is known as the saddlepoint equation. The quantity $s=s(x)$ is the solution to the equation $K_X'(s)=x$, that is
+\begin{equation*}
+\frac{\lambda\alpha\beta^\alpha}{(\beta-s)^{\alpha+1}} = x
+\end{equation*}
+with solution
+\begin{equation}
+s = \beta - \left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}} \ .
+\end{equation}
+
+The second derivative of the cumulant generating function is
+\begin{equation}
+K_X''(\theta)=\frac{\lambda\alpha(\alpha+1)\beta^\alpha}{(\beta-\theta)^{\alpha+2}} \ .
+\end{equation}
+Substituting this and $K_X(\theta)$ into Equation \eqref{eq:saddlePoint:generalSaddlePoint}
+\begin{equation*}
+p_X(x)\approx
+\frac{1}{\sqrt{2\pi}}\left[\frac{(\beta-s)^{\alpha+2}}{\lambda\alpha(\alpha+1)\beta^\alpha}\right]^{1/2}
+\exp\left[
+	\lambda\left(\left(\frac{\beta}{\beta-s}\right)^\alpha-1\right)-sx
+\right] \ .
+\end{equation*}
+Substituting in $s=s(x)$
+\begin{multline*}
+p_X(x)\approx
+\frac{1}{\sqrt{2\pi}}
+\left[
+\frac{\left(\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}\right)^{\alpha+2}}{\lambda\alpha(\alpha+1)\beta^\alpha}
+\right]^{1/2}
+\\
+\exp\left[
+	\lambda\left(
+		\left(
+			\frac{\beta}{\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}}
+		\right)^\alpha
+		-1
+	\right)
+	-x\left(
+		\beta-\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
+	\right)
+\right]
+\end{multline*}
+simplifying further
+\begin{multline*}
+p_X(x)\approx
+\frac{1}{\sqrt{2\pi}}
+\left[
+\frac{\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{\alpha+2}{\alpha+1}}}{\lambda\alpha(\alpha+1)\beta^\alpha}
+\right]^{1/2}
+\\
+\exp\left[
+	\lambda\left(
+		\beta^\alpha
+		\left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
+		-1
+	\right)
+	-x\beta
+	+(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{1-\frac{1}{\alpha+1}}
+\right]
+\end{multline*}
+\begin{multline*}
+p_X(x)\approx
+\frac{1}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+\left(\lambda\alpha\beta^\alpha\right)^{\left(\frac{\alpha+2}{\alpha+1}-1\right)/2}
+\\
+\exp\left[
+	\lambda\left(
+		\beta^\alpha
+		\left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
+		-1
+	\right)
+	-x\beta
+	+(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{\frac{\alpha}{\alpha+1}}
+\right]
+\end{multline*}
+\begin{multline*}
+p_X(x)\approx
+\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+\\
+\exp\left[
+	-\lambda
+	-x\beta
+	+x^{\frac{\alpha}{\alpha+1}}
+	\left(
+		\frac{\lambda\beta^\alpha}{\left(\lambda\alpha\beta^\alpha\right)^{\frac{\alpha}{\alpha+1}}}+\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
+	\right)
+\right]
+\end{multline*}
+\begin{multline*}
+p_X(x)\approx
+\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+\euler^{-x\beta}
+\\
+\exp\left[x^{\frac{\alpha}{\alpha+1}}
+	\left(
+		(\lambda\beta^\alpha)^{1-\frac{\alpha}{\alpha+1}}\alpha^{-\frac{\alpha}{\alpha+1}}
+		+\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
+	\right)
+\right]
+\end{multline*}
+\begin{multline*}
+p_X(x)\approx
+\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
+\\
+\exp\left[x^{\frac{\alpha}{\alpha+1}}
+	\left(
+		(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}\alpha^{-\frac{\alpha}{\alpha+1}}
+		+\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
+	\right)
+\right]
+\end{multline*}
+\begin{multline*}
+p_X(x)\approx
+\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
+\\
+\exp\left[x^{\frac{\alpha}{\alpha+1}}(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
+	\left(
+		\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
+	\right)
+\right] \ .
+\end{multline*}
+
+The expression $\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}$ can be simplified by putting the two terms over a common denominator
+\begin{align}
+\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}} & = \alpha^{\frac{1}{\alpha+1}}+\frac{1}{\alpha^{\frac{\alpha}{\alpha+1}}}
+\nonumber\\
+& = \frac{\alpha^{\frac{1}{\alpha+1}}\alpha^{\frac{\alpha}{\alpha+1}}+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
+\nonumber\\
+& = \frac{\alpha+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
+\end{align}
+so that
+\begin{equation*}
+p_X(x)\approx
+\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+\euler^{-x\beta}
+\exp\left[x^{\frac{\alpha}{\alpha+1}}
+	\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
+\right] \ .
+\end{equation*}
+
 \chapter{Inference}

### 2017-08-21 reports/thesis/book.tex
Added series evaluation to thesis.

@@
 \end{equation}
-For a given m.g.f., the saddlepoint approximation \cite{daniels1954saddlepoint} \cite{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
+For a given m.g.f., the saddlepoint approximation \citep{daniels1954saddlepoint} \citep{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
 \begin{equation}
@@
 \end{multline}
+It appears the approximation is not well defined for $x=0$.
+
 The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary.
@@
 
+\subsection{Series Evaluation}
+Evaluation of the p.d.f.~of the compound Poisson-Gamma distribution is difficult because of the infinite sum
+\begin{equation}
+p_X(x) = 
+\delta(x) \euler^{-\lambda}
++
+\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y
+\quad\text{for }x\geqslant 0
+\end{equation}
+where
+\begin{equation}
+W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!} \ .
+\end{equation}
+$W_y$ can be expressed in a different way using different parameters
+\begin{equation}
+W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+\end{equation}
+where
+\begin{equation}
+p=\frac{2+\alpha}{1+\alpha}
+\end{equation}
+and
+\begin{equation}
+\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}} \ .
+\end{equation}
+
+\cite{dunn2005series} approximated the sum by truncation
+\begin{equation}
+\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y
+\end{equation}
+where $y_\text{u}<y_{\text{max}}<y_\text{l}$ and $y_{\text{max}}$ is the value of $y$ which maximises $W_y$.
+\cite{dunn2005series} used Stirling's approximation to find $y_{\text{max}}$.
+This was done by treating $W_y$ as a continuous function of $y$ and is differentiable with respect to $y$.
+
+It is easier to differentiate $\ln(W_y)$ where
+\begin{multline*}
+\ln(W_y) = y\alpha\ln(x)-y(1+\alpha)\ln(\phi)-y\alpha\ln(p-1)\\-y\ln(2-p)-\ln(y!)-\ln\Gamma(y\alpha)
+\end{multline*}
+\begin{equation}
+\ln(W_y) =
+y\ln\left(
+	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
+\right)
+-\ln(y!)-\ln\Gamma(y\alpha) \ .
+\end{equation}
+Using Stirling's approximation
+\begin{equation}
+\ln(n!)\approx\ln\Gamma(n)\approx n\ln(n!)-n
+\end{equation}
+then
+\begin{equation}
+\ln(W_y) \approx
+y\ln\left(
+	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
+\right)
+-y\ln(y)+y-y\alpha\ln(y\alpha) + y\alpha \ .
+\end{equation}
+Taking the derivative with respect to $y$
+\begin{multline*}
+\frac{\partial \ln(W_y)}{\partial y} \approx
+\ln\left(
+	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
+\right)
+-\ln(y)-1+1
+\\-\alpha\ln(y\alpha)-\alpha+\alpha
+\end{multline*}
+\begin{equation}
+\frac{\partial \ln(W_y)}{\partial y} \approx
+\ln\left(
+	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
+\right)
+-\ln(y)
+-\alpha\ln(y\alpha) \ .
+\end{equation}
+
+Setting the derivative to zero
+\begin{equation*}
+0 \approx \ln\left(
+\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha}
+\right)
+\end{equation*}
+\begin{equation*}
+1 \approx 
+\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha}
+\end{equation*}
+\begin{equation*}
+y_{\text{max}}^{1+\alpha} \approx 
+\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)\alpha^\alpha}
+\end{equation*}
+\begin{equation*}
+y_{\text{max}} \approx 
+\frac{1}{\phi}
+\left(
+	\frac{x}{(p-1)\alpha}
+\right)^{\frac{\alpha}{1+\alpha}}
+(2-p)^{\frac{-1}{1+\alpha}} \ .
+\end{equation*}
+This can be simplified using the fact that 
+\begin{equation*}
+\alpha=\frac{2-p}{p-1} \ ,
+\end{equation*}
+\begin{equation*}
+\frac{1}{1+\alpha} = p-1
+\end{equation*}
+and
+\begin{equation*}
+\frac{\alpha}{1+\alpha} = 2-p
+\end{equation*}
+then
+\begin{equation*}
+y_{\text{max}} \approx 
+\frac{1}{\phi}
+\left(
+	\frac{x}{2-p}
+\right)^{2-p}
+(2-p)^{1-p}
+\end{equation*}
+and finally
+\begin{equation}
+y_{\text{max}} \approx \frac{x^{2-p}}{\phi(2-p)} \ .
+\end{equation}
+Because values of $y$ should be a positive integer, it would be appropriate to round the solution to $y_\text{max}$ accordingly
+\begin{equation}
+y_{\text{max}} = \text{max}\left[
+1,\text{round}\left(\frac{x^{2-p}}{\phi(2-p)}\right)
+\right] \ .
+\end{equation}
+
+To verify that $y_\text{max}$ is a maximum, the second derivative can be investigated
+\begin{equation}
+\frac{\partial^2\ln(W_y)}{\partial y^2}
+\approx
+-\frac{1}{y}(\alpha+1)
+\end{equation}
+to see that
+\begin{equation}
+\frac{\partial^2\ln(W_y)}{\partial y^2} < 0 \quad \text{for }y=1,2,3,\dotdotdot
+\end{equation}
+therefore $y_\text{max}$ is a maximum.
+
+Returning back to the truncation of the infinite sum
+\begin{equation}
+\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y \ ,
+\end{equation}
+$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant.
+To prevent overflow problems, it is advised to calculate each term in the summation in log scale and using the following equation
+\begin{equation}
+\ln\left[\sum_{y=y_\text{l}}^{y_\text{u}}W_y\right]
+= \ln\left(W_{y_\text{max}}\right)+\ln\sum_{y=y_\text{l}}^{y_\text{u}}\exp\left[
+\ln\left(W_y\right)-\ln\left(W_{y_\text{max}}\right)
+\right] \ .
+\end{equation}
+
 \chapter{Inference}

### 2017-08-24 reports/thesis/book.tex
In thesis, added compound Poisson simulation.

@@
 
-The limiting case where $\lambda\rightarrow 0$, $\alpha\rightarrow 0$ and $\beta\rightarrow 0$ will not be discussed here.
+The above results justify the use of the approximation
+\begin{equation}
+X\sim\normal\left(\frac{\lambda\alpha}{\beta},\frac{\lambda\alpha(\alpha+1)}{\beta^2}\right)
+\end{equation}
+for large $\lambda$. The limiting case where $\lambda\rightarrow 0$, $\alpha\rightarrow 0$ and $\beta\rightarrow 0$ will not be discussed here.
 
@@
 \end{equation}
-$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant.
-To prevent overflow problems, it is advised to calculate each term in the summation in log scale and using the following equation
+$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}.
+To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} and using the following equation
 \begin{equation}
@@
 
+\subsection{Simulation Studies}
+
+Simulations of a compound Poisson-Gamma random variable were conducted with the aim to compare how well these density evaluations methods perform.
+This was done by comparing the evaluated densities with the histogram of simulations and a Q-Q plot.
+The following compound Poisson-Gamma distributions were used in the simulations to capture the variety in the compound Poisson-Gamma family: $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(100,100,1)$.
+
+A few technical details will be stated here.
+The Normal approximation does not support probability mass at $x=0$, but instead has a support of $-\infty<x<\infty$.
+The Normal approximation with $-\infty<x<\infty$ support was used here.
+
+The saddlepoint approximation was computed up to a constant using
+\begin{equation}
+p_X(x) \propto \exp\left[
+-\frac{\alpha+2}{2(\alpha+1)}\ln(x)
+-x\beta
++\left(
+\frac{x\beta}{\alpha}
+\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1) - k
+\right]
+\end{equation}
+for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant to control over/underflow and it was chosen to be
+\begin{equation}
+k = \max_{i\in\text{simulation}}\left[
+-\frac{\alpha+2}{2(\alpha+1)}\ln(x_i)
+-x_i\beta
++\left(
+\frac{x_i\beta}{\alpha}
+\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
+\right] \ .
+\end{equation}
+The density was then was normalised by numerically integrating it using the trapezium rule using the 500 evaluated points.
+
+A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$, let
+\begin{equation}
+F_X(x) = \prob(X\leqslant x)
+\end{equation}
+\begin{equation}
+\widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}\left[
+\left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
+\right] \ ,
+\end{equation}
+then a Q-Q plot plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$.
+If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin.
+However there is no closed form for $F_X(x)$.
+When using the exact or saddlepoint method, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums.
+$\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
+For the saddlepoint approximation where $x=0$ cannot be evaluated, the lower limit of the numerical integral was chosen, arbitrary, to be
+\begin{equation}
+\frac{\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)}{\euler^{-\lambda}(1+\lambda)}\times 0.1 \ .
+\end{equation}
+
+For low $\lambda$ (Figures \ref{fig:cp_simulation_1} and \ref{fig:cp_simulation_3}) there is a chance of simulating zeros.
+The Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric.
+The saddlepoint approximation did capture probability mass at zero as shown by an increase in probability density towards zero.
+However in Figure \ref{fig:cp_simulation_3}, the compound Poisson-Gamma distribution looked like a mixture model and the saddlepoint approximation was not flexible enough to capture each individual peak.
+In addition, the Q-Q plots looked quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~at low densities.
+
+As $\lambda$ increased, all 3 density evaluation methods performed quite well.
+In Figure \ref{fig:cp_simulation_2}, the Normal approximation did not quite capture the skewness of the histogram.
+However in Figure \ref{fig:cp_simulation_4} for the Normal looking compound Poisson-Gamma random variable, all methods performed well.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist1.png}
+        \caption{Histogram - Exact method}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq1.png}
+        \caption{Q-Q plot - Exact method}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist1.png}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq1.png}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist1.png}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq1.png}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{Simulations of $\CPoisson(1,1,1)$ compared to different density evaluation methods}
+    \label{fig:cp_simulation_1}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist2.png}
+        \caption{Histogram - Exact method}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq2.png}
+        \caption{Q-Q plot - Exact method}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist2.png}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq2.png}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist2.png}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq2.png}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{Simulations of $\CPoisson(10,1,1)$ compared to different density evaluation methods}
+    \label{fig:cp_simulation_2}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist3.png}
+        \caption{Histogram - Exact method}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq3.png}
+        \caption{Q-Q plot - Exact method}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist3.png}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq3.png}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist3.png}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq3.png}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{Simulations of $\CPoisson(1,100,1)$ compared to different density evaluation methods}
+    \label{fig:cp_simulation_3}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist4.png}
+        \caption{Histogram - Exact method}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq4.png}
+        \caption{Q-Q plot - Exact method}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist4.png}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq4.png}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist4.png}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.7\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq4.png}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{Simulations of $\CPoisson(100,100,1)$ compared to different density evaluation methods}
+    \label{fig:cp_simulation_4}
+\end{figure}
+
 \chapter{Inference}

### 2017-08-25 reports/thesis/book.tex
Corrected simulation section in thesis.

@@
 
-The saddlepoint approximation was computed up to a constant using
+Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$. The saddlepoint approximation was computed up to a constant using
 \begin{equation}
@@
 \begin{equation}
-k = \max_{i\in\text{simulation}}\left[
+k = \max_{i\in\left\{1,2,3,\dotdotdot,n\right\}}\left[
 -\frac{\alpha+2}{2(\alpha+1)}\ln(x_i)
@@
 
-A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$, let
+A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Let
 \begin{equation}
@@
 $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
-For the saddlepoint approximation where $x=0$ cannot be evaluated, the lower limit of the numerical integral was chosen, arbitrary, to be
+For the saddlepoint approximation where $x=0$ cannot be evaluated and their exist a zero value in the sample, the lower limit of the numerical integral was chosen, arbitrary, to be
 \begin{equation}

### 2017-08-25 reports/thesis/book.tex
Started on EM in thesis.

@@
 
-\begin{document}
+\begin{document}\sloppy
 
@@
 \begin{equation}
-p_X(x) = \delta(x) \euler^{-\lambda} + \sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for }x\geqslant 0
+p_X(x) = 
+\begin{cases}
+\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
+\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
+\end{cases}
 \end{equation}
@@
 p_X(x) = 
-\delta(x) \euler^{-\lambda}
-+
-\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!}
-\quad\text{for }x\geqslant 0
+\begin{cases}
+\delta(x) \euler^{-\lambda} & \text{ for } x=x \\ 
+\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
+\end{cases}
 \label{eq:compoundPoisson_pdf}
@@
 p_X(x) = 
-\delta(x) \euler^{-\lambda}
-+
-\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y
-\quad\text{for }x\geqslant 0
+\begin{cases}
+\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
+\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y & \text{ for } x>0 
+\end{cases}
 \end{equation}
@@
 W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!} \ .
+\label{eq:compoundPoisson_w}
 \end{equation}
@@
 This should make sense as for high $\lambda$, the Poisson random variable has a high expectation, increasing the number of Gamma random variables in a summation.
-Increasing the number of terms in a summation will triggle the central limit theorem.
+Increasing the number of terms in a summation will trigger the central limit theorem.
 
@@
 
+\section{EM Algorithm}
+
+The EM algorithm \citep{dempster1977maximum} will be proposed here as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$.
+
+A popular method for parameter estimation is the maximum log likelihood method.
+Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively.
+The log likelihood is defined to be
+\begin{equation*}
+\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n\left[
+\mathbb{I}(x_i=0)\ln \prob(X=x_i)
++\mathbb{I}(x_i>0)\ln p_X(x_i)
+\right]
+\end{equation*}
+\begin{multline}
+\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n\left[
+-\mathbb{I}(x_i=0)\lambda
+\vphantom{\sum_i^i}\right.\\\left.
++\mathbb{I}(x_i>0)\left(
+	-\beta x_i-\lambda-\ln x -\ln\sum_{y=1}^\infty W_y
+\right)
+\right]
+\end{multline}
+where $W_y=W_y(\lambda,\alpha,\beta)$ was defined in Equation \eqref{eq:compoundPoisson_w}.
+$\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
+The gradient of the log likelihood can be evaluated \citep{dunn2005series} and optimisation can be done using gradient methods.
+
+The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable.
+Let $\left\{y_1,y_2,y_3,\dotdotdot, y_n\right\}$ be measurements of $Y$ and $\left\{x_1,x_2,x_3,\dotdotdot, x_n\right\}$ be measurements of $X|Y$.
+Define the joint log likelihood to be
+\begin{multline*}
+\ln L(\lambda,\alpha,\beta;X,Y)
+=
+\sum_{i=1}^n
+\left[
+	\mathbb{I}(y_i=0)
+	\ln
+	\prob(Y=0)
+	\right.\\\left.
+	+
+	\mathbb{I}(y_i>0)
+	\ln
+	\left[
+	p_{X|Y}(x_i|y_i)\prob(Y=y_i)
+	\right]
+\right]
+\end{multline*}
+so that
+\begin{multline}
+\ln L(\lambda,\alpha,\beta;X,Y)
+=
+\sum_{i=1}^n
+\left[
+	-\mathbb{I}(y_i=0)
+	\lambda
+	\right.\\\left.+
+	\mathbb{I}(y_i>0)
+	\left(
+	y_i\alpha\ln\beta-\ln\Gamma(y_i\alpha)+(y_i\alpha-1)\ln x_i - \beta x_i
+	\right.\right.\\\left.\left.	
+	- \lambda + y_i \ln \lambda - \ln(y!)
+	\right)
+\right] \ .
+\end{multline}
+The estimators are found by optimising the joint log likelihood.
+This is done iteratively by estimating the $Y$s given the $X$s and parameters (E step), followed by estimating the parameters given the $Y$s and $X$s (M step) until some convergence conditions are met.
+
+It will be shown that using some approximations, the E step and M step can be implemented.
+The Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} can also be found by using a few approximations.
+However simulations show that these estimators struggle for high $\lambda$ and it will be shown that this will be the case for all estimators.
+
+\subsection{E Step}
+
+\subsection{M Step}
+
+\subsection{Estimation Error}
+
+\subsection{Simulations}
+
+\subsection{Failure Cases}
+
 \chapter{Inference}

### 2017-08-28 reports/thesis/book.tex
In thesis, added E step.

@@
 W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!} \ .
+\label{eq:compoundPoisson_Wy}
 \end{equation}
@@
 \end{equation}
-where $y_\text{u}<y_{\text{max}}<y_\text{l}$ and $y_{\text{max}}$ is the value of $y$ which maximises $W_y$.
+where $y_\text{l}<y_{\text{max}}<y_\text{u}$ and $y_{\text{max}}$ is the value of $y$ which maximises $W_y$.
 \cite{dunn2005series} used Stirling's approximation to find $y_{\text{max}}$.
@@
 The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable.
-Let $\left\{y_1,y_2,y_3,\dotdotdot, y_n\right\}$ be measurements of $Y$ and $\left\{x_1,x_2,x_3,\dotdotdot, x_n\right\}$ be measurements of $X|Y$.
+Let $\left\{Y_1,Y_2,Y_3,\dotdotdot, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\dotdotdot, x_n\right\}$ be measurements of $X|Y$.
 Define the joint log likelihood to be
@@
 \left[
-	\mathbb{I}(y_i=0)
+	\mathbb{I}(Y_i=0)
 	\ln
@@
 	+
-	\mathbb{I}(y_i>0)
+	\mathbb{I}(Y_i>0)
 	\ln
 	\left[
-	p_{X|Y}(x_i|y_i)\prob(Y=y_i)
+	p_{X|Y}(x_i|Y_i)\prob(Y=Y_i)
 	\right]
@@
 \left[
-	-\mathbb{I}(y_i=0)
+	-\mathbb{I}(Y_i=0)
 	\lambda
 	\right.\\\left.+
-	\mathbb{I}(y_i>0)
+	\mathbb{I}(Y_i>0)
 	\left(
-	y_i\alpha\ln\beta-\ln\Gamma(y_i\alpha)+(y_i\alpha-1)\ln x_i - \beta x_i
+	Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
 	\right.\right.\\\left.\left.	
-	- \lambda + y_i \ln \lambda - \ln(y!)
+	- \lambda + Y_i \ln \lambda - \ln(Y!)
 	\right)
@@
 
+In the E step, the realizations of $Y$ are estimate using
+\begin{equation}
+y_i = \expectation\left[
+Y|X=x_i
+\right]
+\end{equation}
+for given parameters $\lambda$, $\alpha$ and $\beta$. The conditional expectation is calculated using
+\begin{equation}
+y_i = 
+\begin{cases}
+0 & \text{ for } x=0 \\ 
+\dfrac{\sum_{y=1}^\infty y \prob(Y=y|X=x_i)}{\sum_{y=1}^\infty \prob(Y=y|X=x_i)} & \text{ for } x>0
+\end{cases}
+\end{equation}
+where
+\begin{equation*}
+\prob(Y=y|X=x) = \frac{p_{X|Y}(x|y)\prob(Y=y)}{p_X(x)} \ .
+\end{equation*}
+Focussing on the $x>0$ case for now
+\begin{equation*}
+\prob(Y=y|X=x) = \frac{1}{p_X(x)}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\frac{\euler^{-\lambda}\lambda^y}{y!}
+\end{equation*}
+and
+\begin{equation}
+\prob(Y=y|X=x) = W_y \frac{\euler^{-\lambda-\beta x}}{x}
+\end{equation}
+where $W_y$ is defined in Equation \eqref{eq:compoundPoisson_Wy}.
+Then the conditional expectation is
+\begin{equation}
+y_i = \frac{\sum_{y=1}^\infty y W_y}{\sum_{y=1}^\infty W_y} \ .
+\end{equation}
+It was already established how the denominator can be evaluated \citep{dunn2005series}. A similar method for evaluating the numerator can be obtained by truncating the sum and summing large terms.
+
+Let
+\begin{equation}
+W_y^{(r)} = y^r W_y
+\end{equation}
+so that
+\begin{equation}
+y_i = \frac{\sum_{y=1}^\infty W^{(1)}_y}{\sum_{y=1}^\infty W_y} \ .
+\end{equation}
+The exponent $r=0,1,2,\dotdotdot$ will be useful in the M step where higher conditional moments are needed.
+The sum can be truncated
+\begin{equation}
+\sum_{y=1}^\infty W^{(r)}_y \approx \sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y
+\end{equation}
+where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. By expressing $\ln(W^{(r)}_y)$ as
+\begin{equation}
+\ln\left(W_y^{(r)}\right)=r\ln(y)+\ln(W_y)
+\end{equation}
+and then taking the derivative with respect to $y$
+\begin{equation}
+\frac{\partial \ln(W_y^{(r)})}{\partial y} = \frac{r}{y } + \frac{\partial \ln(W_y)}{\partial y} \ .
+\end{equation}
+Keep in mind that $y=1,2,3,\dotdotdot$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
+\begin{equation}
+\frac{\partial \ln(W_y^{(r)})}{\partial y} \approx \frac{\partial \ln(W_y)}{\partial y} \ .
+\end{equation}
+By using such an approximation, the method for evaluating the sum $\sum_{y=1}^\infty W^{(r)}_y$ is almost exactly the same as evaluating the sum $\sum_{y=1}^\infty W_y$, in particular $y_\text{max}$ are the same.
+For a given $r=0,1,2,\dotdotdot$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
+The limits will be different for different values of $r$.
+
 \subsection{M Step}

### 2017-08-30 reports/thesis/book.tex
In thesis, added M step.

@@
 \left[
-	\mathbb{I}(Y_i=0)
+	\mathbb{I}(x_i=0)
 	\ln
@@
 	+
-	\mathbb{I}(Y_i>0)
+	\mathbb{I}(x_i>0)
 	\ln
@@
 \left[
-	-\mathbb{I}(Y_i=0)
+	-\mathbb{I}(x_i=0)
 	\lambda
 	\right.\\\left.+
-	\mathbb{I}(Y_i>0)
+	\mathbb{I}(x_i>0)
 	\left(
@@
 	\right.\right.\\\left.\left.	
-	- \lambda + Y_i \ln \lambda - \ln(Y!)
+	- \lambda + Y_i \ln \lambda - \ln(Y_i!)
 	\right)
@@
 \begin{equation}
-y_i = \frac{\sum_{y=1}^\infty W^{(1)}_y}{\sum_{y=1}^\infty W_y} \ .
+y_i = \frac{\sum_{y=1}^\infty W^{(1)}_y}{\sum_{y=1}^\infty W_y}
+\end{equation}
+and
+\begin{equation}
+\variance[Y|X=x_i] = \frac{\sum_{y=1}^\infty W^{(2)}_y}{\sum_{y=1}^\infty W_y} - \left(y_i\right)^2 \ .
 \end{equation}
@@
 
+In the M step, the conditional expected joint log likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is then
+\begin{multline*}
+T(\lambda,\alpha,\beta)
+=
+\sum_{i=1}^n
+\expectation\left[
+	-\mathbb{I}(x_i=0)
+	\lambda
+	\right.\\\left.+
+	\mathbb{I}(x_i>0)
+	\left(
+	Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
+	\right.\right.\\\left.\left.	
+	- \lambda + Y_i \ln \lambda - \ln(Y_i!)
+	\right)
+|X_i=x_i\right]
+\end{multline*}
+\begin{multline*}
+T(\lambda,\alpha,\beta)
+=
+-n\lambda
+\\+
+	\sum_{i=1}^n
+	\mathbb{I}(x_i>0)
+	\left[
+	\expectation[Y_i|X_i=x_i]\alpha\ln\beta-\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]
+	\right.\\\left.
+	+\expectation[Y_i|X_i=x_i]\alpha\ln x_i - \beta x_i
+	+ \expectation[Y_i|X_i=x_i] \ln \lambda
+	\right] + c
+\end{multline*}
+where $c$ is some constant not dependent on $\lambda$, $\alpha$ or $\beta$.
+
+The conditional expectation $y_i = \expectation[Y_i|X_i=x_i]$ was calculated in the E step. The quantity $\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]$ can be calculated using the approximation
+\begin{equation}
+\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i] \approx
+\ln\Gamma(\alpha y_i) + \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
+\end{equation}
+where
+\begin{equation}
+\zeta_i = \variance[Y_i|X_i=x_i]
+\end{equation}
+calculated in the E step and $\psi$ is the digamma function. The objective function is then
+\begin{multline}
+T(\lambda,\alpha,\beta)
+=
+-n\lambda+
+	\sum_{i=1}^n
+	\mathbb{I}(x_i>0)
+	\left[
+	y_i\alpha\ln\beta-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
+	\right.\\\left.
+	+y_i\alpha\ln x_i - \beta x_i
+	+ y_i \ln \lambda
+	\vphantom{\frac{1}{1}}\right] + c \ .
+\end{multline}
+
+Taking the derivative with respect to $\lambda$
+\begin{equation}
+\frac{\partial T}{\partial\lambda} = -n + \frac{\sum_{i=1}^ny_i}{\lambda}
+\end{equation}
+and setting it to zero
+\begin{equation}
+\widehat{\lambda} = \frac{\sum_{i=1}^n y_i}{n}
+\end{equation}
+obtains a M step estimator, and a familiar one, for $\lambda$. Taking the second derivative with respect to $\lambda$
+\begin{equation}
+\frac{\partial^2 T}{\partial \lambda^2} = -\frac{\sum_{i=1}^ny_i}{\lambda^2} < 0
+\end{equation}
+verifies $\widehat{\lambda}$ maximises T. In addition
+\begin{equation}
+\frac{\partial^2 T}{\partial \alpha \partial \lambda } = 0
+\end{equation}
+and
+\begin{equation}
+\frac{\partial^2 T}{\partial \beta \partial \lambda } = 0 \ .
+\end{equation}
+
+Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second order can be obtained. For the first order these are:
+\begin{multline}
+\frac{\partial T}{\partial \alpha} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	y_i\ln\beta -\psi(\alpha y_i)y_i-\zeta_i\alpha\psi'(\alpha y_i)
+	\vphantom{\frac{1}{1}}\right.\\\left.
+	- \frac{1}{2}\zeta_i\alpha^2\psi''(\alpha y_i)y_i + y_i\ln x_i
+\right]
+\end{multline}
+and
+\begin{equation}
+\frac{\partial T}{\partial \beta} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+\frac{\alpha y_i}{\beta}-x_i
+\right] \ .
+\end{equation}
+The second orders are:
+\begin{equation}
+\frac{\partial^2 T}{\partial \alpha \partial \beta} =
+\sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right] \ ,
+\end{equation}
+\begin{equation}
+\frac{\partial^2 T}{\partial \beta^2} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[-\frac{\alpha y_i}{\beta^2}
+\right]
+\end{equation}
+and
+\begin{multline*}
+\frac{\partial^2 T}{\partial \alpha^2} =  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	-y_i^2\psi'(\alpha y_i) - \zeta_i\psi'(\alpha y_i) - \zeta_i\alpha y_i\psi''(\alpha y_i)
+	\vphantom{\frac{1}{2}}\right.\\\left.	
+	- \zeta_i\alpha\psi''(\alpha y_i)y_i
+	-\frac{1}{2}\zeta_i\alpha^2\psi'''(\alpha y_i)y_i^2
+\right]
+\end{multline*}
+simplifying to
+\begin{multline}
+\frac{\partial^2 T}{\partial \alpha^2} =  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
+	\vphantom{\frac{1}{2}}\right.\\\left.	
+	-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
+\right] \ .
+\end{multline}
+
+All the derivatives can be used in the Newton-Raphson iterative update, which is
+\begin{equation}
+\begin{pmatrix}
+\alpha \\ \beta
+\end{pmatrix}
+\leftarrow
+\begin{pmatrix}
+\alpha \\ \beta
+\end{pmatrix}
+\left[
+	\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T
+\right]^{-1}
+\left[\nabla_{\alpha,\beta} T\right]
+\end{equation}
+where
+\begin{equation}
+\nabla_{\alpha,\beta}=
+\begin{pmatrix}
+	{\partial}/{\partial \alpha}
+	\\
+	{\partial}/{\partial \beta}
+\end{pmatrix} \ .
+\end{equation}
+Since increasing $T$ is sufficient for the EM algorithm \citep{dempster1977maximum}, one step of the Newton-Raphson iterative update was chosen in the M step to avoid implementing a convergence condition.
+
 \subsection{Estimation Error}

### 2017-08-30 reports/thesis/book.tex
In thesis, added CR bound.

@@
 
+The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} from the Fisher's information matrix defined as
+\begin{equation}
+\matr{I} = -\expectation\left[
+\nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
+\right] \ .
+\end{equation}
+The calculation is similar to the derivatives of $T$, so using the same approximations and the that fact $\expectation[Y]=\lambda$, then
+\begin{equation}
+\matr{I}
+=
+\begin{pmatrix}
+\dfrac{n}{\lambda} & 0 & 0 \\
+0 & (\lambda^2+\lambda)\psi'(\alpha\lambda)+2\alpha\lambda^2\psi''(\alpha\lambda)+\frac{1}{2}\alpha^2\lambda^3\psi'''(\alpha\lambda) & -\dfrac{n\lambda}{\beta}\\
+0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
+\end{pmatrix} \ .
+\end{equation}
+The Cram\'er-Rao lower bound is then
+\begin{equation}
+\cov\left[
+\begin{pmatrix}
+\widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
+\end{pmatrix}
+\right]
+= \matr{I}^{-1} \ .
+\end{equation}
+
 \subsection{Simulations}

### 2017-09-01 reports/thesis/book.tex
Saved EM convergence figures.

@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist1.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq1.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist1.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq1.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist1.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq1.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist2.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq2.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist2.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq2.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist2.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq2.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist3.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq3.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist3.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq3.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist3.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq3.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist4.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq4.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist4.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq4.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist4.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.7\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq4.png}
@@
 
+\begin{figure}[p]
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lnL.eps}
+        \caption{Log likelihood}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lambda.eps}
+        \caption{$\lambda$}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_alpha.eps}
+        \caption{$\alpha$}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_beta.eps}
+        \caption{$\beta$}
+    \end{subfigure}
+    }
+    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
+The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+    \label{fig:compoundPoisson_convergence_1}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lnL.eps}
+        \caption{Log likelihood}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lambda.eps}
+        \caption{$\lambda$}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_alpha.eps}
+        \caption{$\alpha$}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_beta.eps}
+        \caption{$\beta$}
+    \end{subfigure}
+    }
+    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
+The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+    \label{fig:compoundPoisson_convergence_2}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lnL.eps}
+        \caption{Log likelihood}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lambda.eps}
+        \caption{$\lambda$}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_alpha.eps}
+        \caption{$\alpha$}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_beta.eps}
+        \caption{$\beta$}
+    \end{subfigure}
+    }
+    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
+The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+    \label{fig:compoundPoisson_convergence_3}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lnL.eps}
+        \caption{Log likelihood}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lambda.eps}
+        \caption{$\lambda$}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_alpha.eps}
+        \caption{$\alpha$}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_beta.eps}
+        \caption{$\beta$}
+    \end{subfigure}
+    }
+    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
+The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+    \label{fig:compoundPoisson_convergence_4}
+\end{figure}
+
 \subsection{Failure Cases}

### 2017-09-01 compoundPoisson/cpConvergence.m

@@ -8,7 +8,9 @@
     %beta: gamma rate parameter
     %n_repeat: number of times to repeat the experiment
     %n_step: number of EM steps
-function cpConvergence(n_simulation, lambda, alpha, beta, n_repeat, n_step)
+    %figure_location: directory location to save figures
+    %filename_suffix: file name of the saved figures
+function cpConvergence(n_simulation, lambda, alpha, beta, n_repeat, n_step, figure_location, filename_suffix)
 
     %declare array of lnL, lambda, alpha and beta for each step of EM and each repeat
         %dim 1: for each step of EM
@@ -57,45 +59,46 @@ function cpConvergence(n_simulation, lambda, alpha, beta, n_repeat, n_step)
         end
     end
     
-    
-    figure;
-    
     %plot the log likelihood
-    subplot(2,2,1);
+    fig = figure_latexSub;
     plot(0:n_step, lnL_array, 'b');
     xlabel('Number of EM steps');
     ylabel('lnL');
     xlim([0,n_step]);
+    saveas(fig,fullfile(figure_location,strcat(filename_suffix,'_lnL.eps')),'epsc');
     
     %plot lambda
-    subplot(2,2,2);
+    fig = figure_latexSub;
     plot(0:n_step, lambda_array, 'b');
     hold on;
-    plot([0,n_step], [lambda-std_array(1),lambda-std_array(1)], 'k-');
-    plot([0,n_step], [lambda+std_array(1),lambda+std_array(1)], 'k-');
+    plot([0,n_step], [lambda-std_array(1),lambda-std_array(1)], 'k--');
+    plot([0,n_step], [lambda+std_array(1),lambda+std_array(1)], 'k--');
     xlabel('Number of EM steps');
     ylabel('\lambda');
     xlim([0,n_step]);
+    saveas(fig,fullfile(figure_location,strcat(filename_suffix,'_lambda.eps')),'epsc');
     
     %plot alpha
-    subplot(2,2,3);
+    fig = figure_latexSub;
     plot(0:n_step, alpha_array, 'b');
     hold on;
-    plot([0,n_step], [alpha-std_array(2),alpha-std_array(2)], 'k-');
-    plot([0,n_step], [alpha+std_array(2),alpha+std_array(2)], 'k-');
+    plot([0,n_step], [alpha-std_array(2),alpha-std_array(2)], 'k--');
[…]

### 2017-09-01 compoundPoisson/script_cpExperiment.m

@@ -12,32 +12,27 @@ rng(uint32(353759542),'twister');
 
 n = 1000; %simulation sample size
 n_density = 3; %number of density evaluation methods
-n_parameter = 4; %number of parameter sets to be considered
 %directory for the figures to be saved
 figure_location = fullfile('reports','figures','compoundPoisson');
+
+%array of parameters to be investigated
+    %dim 1: for each set
+    %dim 2: lambda, alpha, beta
+parameter_array = [
+    1,1,1;
+    10,1,1;
+    1,100,1;
+    100,100,1
+];
+n_parameter = numel(parameter_array(:,1)); %number of parameter sets to be considered
 
 %for each parameter set
 for i_parameter = 1:n_parameter
     
-    %assign the parameters lambda, alpha, beta for a given i_parameter
-    switch i_parameter
-        case 1
-            lambda = 1;
-            alpha = 1;
-            beta = 1;
-        case 2
-            lambda = 10;
-            alpha = 1;
-            beta = 1;
-        case 3
-            lambda = 1;
-            alpha = 100;
-            beta = 1;
-        case 4
-            lambda = 100;
-            alpha = 100;
-            beta = 1;
-    end
+    %get parameters
+    lambda = parameter_array(i_parameter,1);
+    alpha = parameter_array(i_parameter,2);
+    beta = parameter_array(i_parameter,3);
     
     %simulated compound poisson
     X = CompoundPoisson.simulate(n,lambda,alpha,beta);
@@ -71,9 +66,14 @@ for i_parameter = 1:n_parameter
    end
 end
 
-% n = 100;
-% n_repeat = 10;
-% n_step = 5;
-% cpConvergence(n, 1, 1, 1, n_repeat, n_step);
-% cpConvergence(n, 1, 100, 1, n_repeat, n_step);
-% cpConvergence(n, 100, 100, 1, n_repeat, n_step);
+n_repeat = 10; %number of times to repeat the experiment
+n_step = 10; %number of EM steps
+%for each parameter set
+for i_parameter = 1:n_parameter
+    %get parameters
+    lambda = parameter_array(i_parameter,1);
+    alpha = parameter_array(i_parameter,2);
+    beta = parameter_array(i_parameter,3);
+    %plot the lnL, and parameters at each step of EM
+    cpConvergence(n, lambda, alpha, beta, n_repeat, n_step,figure_location,strcat('convergence_',num2str(i_parameter)));
+end

### 2017-09-01 reports/thesis/book.tex
In thesis, EM simulation.

@@
 
+An experiment was conducted to assess the performance on the EM algorithm.
+For a given set of parameters, 1\,000 samples of a $\CPoisson(\lambda,\alpha,\beta)$ random variable were simulated.
+The EM algorithm was initialised with its parameters at the true values to investigate the convergence in that vicinity.
+The log likelihood $\ln L(\lambda,\alpha,\beta;X)$ and the parameters were recorded at every EM step.
+The experiment was repeated 10 times using different simulated samples.
+
+The results for $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$ and $\CPoisson(100,100,1)$ are shown in Figures \ref{fig:compoundPoisson_convergence_1}, \ref{fig:compoundPoisson_convergence_2}, \ref{fig:compoundPoisson_convergence_3} and \ref{fig:compoundPoisson_convergence_4} respectively.
+Good performance can be seen for the $\lambda=1$ case with convergence of all 3 parameters within a step or two.
+The Cram\'er-Rao lower bound captured the spread of the estimates well.
+
+However for $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log likelihood.
+It appears the EM algorithm failed for $\lambda>10$ looking at these particular examples.
+
 \begin{figure}[p]

### 2017-09-12 reports/thesis/book.tex
In thesis, added failure in compound Poisson.

@@
 \sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right] \ ,
+\label{eq:compoundPoisson:d2tdadb}
 \end{equation}
@@
 \right]
+\label{eq:compoundPoisson:d2td2b}
 \end{equation}
@@
 \right] \ .
+\label{eq:compoundPoisson:d2td2a}
 \end{multline}
@@
 \end{equation}
-The calculation is similar to the derivatives of $T$, so using the same approximations and the that fact $\expectation[Y]=\lambda$, then
+The calculation is similar to the derivatives of $T$, so using the same approximations and the fact that $\expectation[Y]=\lambda$, then
 \begin{equation}
@@
 The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
     \label{fig:compoundPoisson_convergence_1}
@@
 The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
     \label{fig:compoundPoisson_convergence_2}
@@
 The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
     \label{fig:compoundPoisson_convergence_3}
@@
 The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation of the Cram\'er-Rao lower bound.}
+The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
     \label{fig:compoundPoisson_convergence_4}
@@
 
-\subsection{Failure Cases}
+\subsection{Failure Evaluation}
+It should be convincing that the EM algorithm failed when the compound-Poisson Gamma random variable starts behaving Normally.
+In particular in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ are stable while estimates of $\alpha$ and $\beta$ struggled to converge.
+This could be because as the compound-Poisson Gamma random variable approach being Normal, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate and there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$.
+
+One way to see this is to look at the Newton-Raphson step, in the M step, in particular the Hessian matrix $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ for high $\lambda$.
+The elements of the Hessian matrix can be found in Equations \eqref{eq:compoundPoisson:d2tdadb}, \eqref{eq:compoundPoisson:d2td2b} and \eqref{eq:compoundPoisson:d2td2a}.
+The $\dfrac{\partial^2T}{\partial\alpha^2}$ element is
+\begin{multline*}
+\frac{\partial^2 T}{\partial \alpha^2} =  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
+	\vphantom{\frac{1}{2}}\right.\\\left.	
+	-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
+\right] \ .
+\end{multline*}
+For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$. Firstly using Stirling's approximation
+\begin{equation}
+\ln\Gamma(n)\approx\ln(n!)\approx n\ln n-n
+\end{equation}
+then
+\begin{equation}
+\psi(n) = \frac{\partial\ln\Gamma(n)}{\partial n} \approx \ln n \ .
+\end{equation}
+Differentiating further
+\begin{align}
+\psi'(n) &\approx 1/n \\
+\psi''(n) & \approx -1/n^2 \\
+\psi'''(n) & \approx 2/n^3 \ .
+\end{align}
+Using the approximations, $\dfrac{\partial^2T}{\partial\alpha^2}$ can be approximated
+\begin{equation*}
+\frac{\partial^2 T}{\partial \alpha^2} \approx  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	-\frac{y_i^2+\zeta_i}{\alpha y_i} + 2\frac{\zeta_i\alpha y_i}{\alpha^2 y_i^2}
+	-\frac{1}{2}\frac{2\zeta_i\alpha^2y_i^2}{\alpha^3 y_i^3}
+\right]
+\end{equation*}
+to get
+\begin{equation}
+\frac{\partial^2 T}{\partial \alpha^2} \approx  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	-\frac{y_i}{\alpha}
+\right] \ .
+\end{equation}
+
+The Hessian matrix is then
+\begin{equation}
+\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T \approx
+\sum_{i=1}^n
+\mathbb{I}(x_i>0)
+\begin{pmatrix}
+-y_i/\alpha  & y_i/\beta \\
+y_i/\beta & -\alpha y_i/\beta^2
+\end{pmatrix}  \ . 
+\end{equation}
+The determinant of the Hessian matrix is then
+\begin{equation*}
+\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
+\approx
+\left(\sum_{i=1}^n-\frac{\alpha y_i}{\beta^2}\right)
+\left(\sum_{i=1}^n-\frac{y_i}{\alpha}\right) - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)^2
+\end{equation*}
+\begin{equation*}
+\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
+\approx
+\left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
+ - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)\left(\sum_{j=1}^n\frac{y_j}{\beta}\right)
+\end{equation*}
+\begin{equation*}
+\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
+\approx
+\left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
+ - \left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
+\end{equation*}
+to get
+\begin{equation}
+\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
+\approx
+0 \ .
+\end{equation}
+
+This results in a few things.
+Firstly $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ is singular thus its inverse cannot be evaluated, needed for the Newton-Raphson method.
+Secondly, the sufficient conditions to classify a stationary point as a maximum are that the diagonal elements of the Hessian matrix are negative and the determinate is positive.
+For high $\lambda$ and $\alpha$, the second condition is not met.
+
+Another argument which can be made is to restrict the parameter $\beta$ for a given mean to be
+\begin{equation}
+\beta = \frac{\lambda\alpha}{\widehat{\mu}}
+\label{eq:compoundPoisson:beta_restrict}
+\end{equation}
+where
+\begin{equation}
+\widehat{\mu} = \frac{1}{n}\sum_{i=1}^n x_i
+\end{equation}
+and investigate whenever a unique solution to $\dfrac{\partial T}{\partial \alpha} = 0$ can be found for high $\lambda$ and $\alpha$. The constrained objective function is
+\begin{multline*}
+T(\lambda,\alpha)
+=
+-n\lambda+
+	\sum_{i=1}^n
+	\mathbb{I}(x_i>0)
+	\left[
+	y_i\alpha\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
+	\right.\\\left.
+	+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
+	+ y_i \ln \lambda
+	\vphantom{\frac{1}{1}}\right] + c
+\end{multline*}
+which can be approximated to
+\begin{multline*}
+T(\lambda,\alpha)
+=
+-n\lambda+
+	\sum_{i=1}^n
+	\mathbb{I}(x_i>0)
+	\left[
+	y_i\alpha\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\alpha y_i\ln(\alpha y_i) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
+	\right.\\\left.
+	+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
+	+ y_i \ln \lambda
+	\vphantom{\frac{1}{1}}\right] + c
+\end{multline*}
+\begin{multline*}
+T(\lambda,\alpha)
+=
+-n\lambda+
+	\sum_{i=1}^n
+	\mathbb{I}(x_i>0)
+	\left[
+	y_i\alpha\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
+	\right.\\\left.
+	+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
+	+ y_i \ln \lambda
+	\vphantom{\frac{1}{1}}\right] + c \ .
+\end{multline*}
+Taking the derivative with respect to $\alpha$
+\begin{equation*}
+\frac{\partial T}{\partial \alpha}
+=
+	\sum_{i=1}^n
+	\mathbb{I}(x_i>0)
+	\left[
+	y_i\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right) +  y_i - \frac{1}{2}\frac{\zeta_i}{y_i}
+	+y_i\ln x_i - \frac{\lambda x_i}{\widehat{\mu}}
+	\vphantom{\frac{1}{1}}\right]
+\end{equation*}
+and this is not $\alpha$ dependent, thus there is no solution to $\alpha$.
 

### 2017-09-16 reports/thesis/book.tex
In thesis, typo corrected in Chapter 2, added notation for inference chapter.
Added references to CT.

@@
 
-CT scanning was invented by G.
-Hounsfield \citep{hounsfield1980computed} in the 1980's and it was mainly used for medical imaging.
+CT was solved theoretically by \cite{cormack1973reconstruction} and implemented  by \cite{hounsfield1973computerized} \citep{hounsfield1980computed}.
+It was mainly used for medical imaging.
 The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}.
@@
 \end{equation*}
-and
-\begin{equation*}
-\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=1,2,3,\dotdotdot
+that is
+\begin{equation*}
+\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\dotdotdot
 \end{equation*}
@@
 \begin{equation}
-X|Y\sim\gammaDist\left(Y\alpha,\lambda\right) \ .
+X|Y\sim\gammaDist\left(Y\alpha,\beta\right) \ .
 \end{equation}
@@
 \begin{equation}
-M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
+M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
 \end{equation}
@@
 \begin{cases}
-\delta(x) \euler^{-\lambda} & \text{ for } x=x \\ 
+\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
 \sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
@@
 There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
-Of course direction simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated.
+Of course direct simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated.
 The p.d.f.~then can be estimated using these simulated samples.
@@
 \chapter{Inference}
+%\begin{equation*}
+%i=1,2,3,\dotdotdot,n_{pixel}
+%\end{equation*}
+%\begin{equation*}
+%j=1,2,3,\dotdotdot,n_{repeat}
+%\end{equation*}
+%\begin{equation*}
+%x_i^{(j)} = \text{mean greyvalue of pixel }i\text{, }j\text{th repeat}
+%\end{equation*}
+%\begin{equation*}
+%y_i^{(j)} = \text{variance greyvalue of pixel }i\text{, }j\text{th repeat}
+%\end{equation*}
+%\begin{equation*}
+%\widehat{Y}^{(j)}(x) = \text{predicted variance greyvalue given }x
+%\end{equation*}
+%Trained $\widehat{Y}^{(j)}(x)$ using $(y_1^{(j)},x_1^{(j)}),(y_2^{(j)},x_2^{(j)}),(y_3^{(j)},x_3^{(j)}),\dotdotdot,(y_{n_{pixel}}^{(j)},x_{n_{pixel}}^{(j)})$.
+%\begin{equation*}
+%\widehat{\zeta}^{(j)}(x) = \text{predicted variance of the variance greyvalue given }x
+%\end{equation*}
+%
+%Below are the training statistics, but can be generalised to test statistics:
+%\begin{equation}
+%\text{MSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}\right]^2
+%\end{equation}
+%\begin{equation}
+%\text{MSSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\dfrac{\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}}{\sqrt{\widehat{\zeta}^{(j)}(x_i^{(j)})}}\right]^2
+%\end{equation}
+%\begin{equation}
+%\text{VAR}^{(j)} = \sum_{i=1}^{n_{pixel}}
+%\left[
+%\widehat{Y}^{(j)}(x_i^{(j)}) - \expectation(\widehat{Y}(x_i^{(j)}))
+%\right]^2
+%\end{equation}
+%\begin{equation}
+%\text{BIAS2}^{(j)} = \sum_{i=1}^{n_{pixel}}
+%\left[
+%\expectation(\widehat{Y}(x_i^{(j)}))
+%-
+%y_i^{(j)}
+%\right]^2
+%\end{equation}
+%where
+%\begin{equation}
+%\expectation(\widehat{Y}(x_i^{(j)})) \approx
+%\frac{1}{n_{repeat}}\sum_{j=1}^{n_{repeat}}
+%\widehat{Y}^{(j)}(x_i^{(j)})
+%\end{equation}
+%
+%\clearpage
+%\begin{equation}
+%Y(x) = y(x) + \epsilon(x)
+%\end{equation}
+%where
+%\begin{equation}
+%\expectation[\epsilon(x)] = 0, \quad \variance[\epsilon(x)] = \sigma^2(x) \ .
+%\end{equation}
+%The statistics for a given $x$ are:
+%\begin{equation}
+%\text{MSE}(x) = \expectation\left[
+%(Y(x)-\widehat{Y}(x))^2
+%\right]
+%\end{equation}
+%\begin{equation}
+%\text{VAR}(x) = \expectation\left[
+%(\widehat{Y}(x) - \expectation(\widehat{Y}(x))^2
+%\right]
+%\end{equation}
+%\begin{equation}
+%\text{BIAS2}(x) = \expectation\left[
+%(\expectation(\widehat{Y}(x) - y(x))^2
+%\right]
+%\end{equation}
+%\begin{equation}
+%\sigma^2(x) = \expectation\left[
+%(
+%Y(x) - \expectation(Y(x))
+%)^2
+%\right] \ .
+%\end{equation}
+%
+%$y(x)$ is unknown so the bias squared can be calculated using
+%\begin{equation}
+%\text{BIAS2}(X) = \text{MSE}(X) - \text{VAR}(X) - \sigma^2(x)
+%\end{equation}
+%
+%The expectations were estimated using bootstrapped samples of $Y(x)$ and $\widehat{Y}(x)$.
+%
+%\clearpage
+%
+%\begin{figure}
+%\centering
+%    \centerline{
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/training_MSSE.eps}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/test_MSSE.eps}
+%    \end{subfigure}
+%    }
+%    \caption{Mean squared standardised error}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%    \centerline{
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/training_MSE.eps}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/test_MSE.eps}
+%    \end{subfigure}
+%    }
+%    \caption{Mean squared error}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%    \centerline{
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/training_var.eps}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/test_var.eps}
+%    \end{subfigure}
+%    }
+%    \caption{Estimation variance}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%    \centerline{
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/training_bias2.eps}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/test_bias2.eps}
+%    \end{subfigure}
+%    }
+%    \caption{Bias squared}
+%\end{figure}
 

### 2017-09-17 reports/thesis/book.tex
In thesis, added more on detectors.

@@
 \includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
-\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \emph{Source: G.~Michael (2001) \citep{michael2001x}}}
+\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \citep{michael2001x}}
 \label{fig:x_ray_tube}
@@
 
-Bremsstrahlung radiation is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target.
+Bremsstrahlung is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target.
 The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation.
@@
 \caption{A typical energy spectrum of photons emitted from an X-ray tube.
-The continuous spectrum is the result of Bremmsstrahlung radiation.
+The continuous spectrum is the result of bremmsstrahlung.
 The peaks are the result of characteristic radiation.
-\emph{Source: G.~Michael (2001) \citep{michael2001x}}}
+\citep{michael2001x}}
 \label{fig:x_ray_spectrum}
@@
 
-\subsection{Detection and Reconstruction}
-Most X-ray detectors are scintillator-photodiode detectors.
-The photons interact with the scintiallator material and produce visible light.
-The visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}.
-The detectors used in CT scanning are flat bed scanner which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.
+\subsection{Detection}
+Most X-ray detectors are made up of a scintillator material \citep{greskovich1997ceramic} and photodiodes.
+Firstly the x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}.
+Lastly the visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}.
+Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected.
+The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.
+
+The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
+The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.
+The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image on a computer \citep{cierniak2011x}.
 
@@
 
-Studies have been done to use x-ray CT to do defection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}.
+Studies have been done to use x-ray CT to do defection detection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}.
 This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}.
@@
 
-The grey values of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector.
+The greyvalues of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector.
 When the photons interact with the scintillator, they are converted into visible light.
-The visible light photons are then detected and converted into a grey value.
-How the detected visible light is converted is important in modelling the grey value.
-
-Should the grey value be proportional to the number of photons detected, the detector is known as a quantum counter and the grey value is a Poisson random variable, up to a constant \citep{whiting2006properties}.
-However if the grey value records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector.
-The grey value has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}.
+The visible light photons are then detected and converted into a greyvalue.
+How the detected visible light is converted is important in modelling the greyvalue.
+
+Should the greyvalue be proportional to the number of photons detected, the detector is known as a quantum counter and the greyvalue is a Poisson random variable, up to a constant \citep{whiting2006properties}.
+However if the greyvalue records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector.
+The greyvalue has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}.
 There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.

### 2017-09-21 reports/thesis/book.tex
Produced VarBias2 graphs into thesis.

@@
 \chapter{Inference}
-%\begin{equation*}
-%i=1,2,3,\dotdotdot,n_{pixel}
-%\end{equation*}
-%\begin{equation*}
-%j=1,2,3,\dotdotdot,n_{repeat}
-%\end{equation*}
-%\begin{equation*}
-%x_i^{(j)} = \text{mean greyvalue of pixel }i\text{, }j\text{th repeat}
-%\end{equation*}
-%\begin{equation*}
-%y_i^{(j)} = \text{variance greyvalue of pixel }i\text{, }j\text{th repeat}
-%\end{equation*}
-%\begin{equation*}
-%\widehat{Y}^{(j)}(x) = \text{predicted variance greyvalue given }x
-%\end{equation*}
-%Trained $\widehat{Y}^{(j)}(x)$ using $(y_1^{(j)},x_1^{(j)}),(y_2^{(j)},x_2^{(j)}),(y_3^{(j)},x_3^{(j)}),\dotdotdot,(y_{n_{pixel}}^{(j)},x_{n_{pixel}}^{(j)})$.
-%\begin{equation*}
-%\widehat{\zeta}^{(j)}(x) = \text{predicted variance of the variance greyvalue given }x
-%\end{equation*}
-%
-%Below are the training statistics, but can be generalised to test statistics:
-%\begin{equation}
-%\text{MSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}\right]^2
-%\end{equation}
-%\begin{equation}
-%\text{MSSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\dfrac{\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}}{\sqrt{\widehat{\zeta}^{(j)}(x_i^{(j)})}}\right]^2
-%\end{equation}
-%\begin{equation}
-%\text{VAR}^{(j)} = \sum_{i=1}^{n_{pixel}}
-%\left[
-%\widehat{Y}^{(j)}(x_i^{(j)}) - \expectation(\widehat{Y}(x_i^{(j)}))
-%\right]^2
-%\end{equation}
-%\begin{equation}
-%\text{BIAS2}^{(j)} = \sum_{i=1}^{n_{pixel}}
-%\left[
-%\expectation(\widehat{Y}(x_i^{(j)}))
-%-
-%y_i^{(j)}
-%\right]^2
-%\end{equation}
-%where
-%\begin{equation}
-%\expectation(\widehat{Y}(x_i^{(j)})) \approx
-%\frac{1}{n_{repeat}}\sum_{j=1}^{n_{repeat}}
-%\widehat{Y}^{(j)}(x_i^{(j)})
-%\end{equation}
-%
-%\clearpage
-%\begin{equation}
-%Y(x) = y(x) + \epsilon(x)
-%\end{equation}
-%where
-%\begin{equation}
-%\expectation[\epsilon(x)] = 0, \quad \variance[\epsilon(x)] = \sigma^2(x) \ .
-%\end{equation}
-%The statistics for a given $x$ are:
-%\begin{equation}
-%\text{MSE}(x) = \expectation\left[
-%(Y(x)-\widehat{Y}(x))^2
-%\right]
-%\end{equation}
-%\begin{equation}
-%\text{VAR}(x) = \expectation\left[
-%(\widehat{Y}(x) - \expectation(\widehat{Y}(x))^2
-%\right]
-%\end{equation}
-%\begin{equation}
-%\text{BIAS2}(x) = \expectation\left[
-%(\expectation(\widehat{Y}(x) - y(x))^2
-%\right]
-%\end{equation}
-%\begin{equation}
-%\sigma^2(x) = \expectation\left[
-%(
-%Y(x) - \expectation(Y(x))
-%)^2
-%\right] \ .
-%\end{equation}
-%
-%$y(x)$ is unknown so the bias squared can be calculated using
-%\begin{equation}
-%\text{BIAS2}(X) = \text{MSE}(X) - \text{VAR}(X) - \sigma^2(x)
-%\end{equation}
-%
-%The expectations were estimated using bootstrapped samples of $Y(x)$ and $\widehat{Y}(x)$.
-%
-%\clearpage
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_MSSE.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_MSSE.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Mean squared standardised error}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_MSE.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_MSE.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Mean squared error}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_var.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_var.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Estimation variance}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_bias2.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_bias2.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Bias squared}
-%\end{figure}
+\begin{equation*}
+i=1,2,3,\dotdotdot,n_{pixel}
+\end{equation*}
+\begin{equation*}
+j=1,2,3,\dotdotdot,n_{fold}
+\end{equation*}
+\begin{equation*}
+x = \text{mean greyvalue of a pixel}
+\end{equation*}
+\begin{equation*}
+Y(x)= \text{variance greyvalue given }x
+\end{equation*}
+\begin{equation*}
+\widehat{Y}(x) = \text{predicted variance greyvalue given }x
+\end{equation*}
+
+Let
+\begin{equation}
+Y(x) = f(x) + \epsilon(x)
+\end{equation}
+where
+\begin{equation}
+\expectation[\epsilon(x)] = 0, \quad \variance[\epsilon(x)] = \sigma^2(x)
+\end{equation}
+and
+\begin{equation}
+f(x) = \expectation\left[Y(x)\right] \ .
+\end{equation}
+The statistics for a given $x$ are:
+\begin{equation}
+\text{RSS}(x) = \expectation\left[
+\left(\widehat{Y}(x) - Y(x)\right)^2
+\right]
+\end{equation}
+\begin{equation}
+\text{MSE}(x) = \expectation\left[
+\left(\widehat{Y}(x)-f(x)\right)^2
+\right]
+\end{equation}
+\begin{equation}
+\text{BIAS}(x) = 
+\expectation\left[\widehat{Y}(x)\right] - f(x)
+\end{equation}
+\begin{equation}
+\text{VAR}(x) = \expectation\left[
+\left(\widehat{Y}(x) - \expectation\left[\widehat{Y}(x)\right]\right)^2
+\right]
+\end{equation}
+\begin{equation}
+\sigma^2(x) = \expectation\left[
+\left(Y(x) - f(x)\right)^2
+\right] \ .
+\end{equation}
+
+Assuming $\expectation\left[\epsilon(x)\widehat{Y}(x)\right] = 0$, then
+\begin{equation}
+\text{MSE}(x) = \text{VAR}(x) + \text{BIAS}^2(x)
+\end{equation}
+and
+\begin{equation}
+\text{RSS}(x) = \text{MSE}(x) + \sigma^2(x)  .
+\end{equation}
+
+The images were spilt into a training set and a test set.
+The mean and variance of each pixel can be estimated for each set.
+This can be repeated multiple times by reassigning the training and test set.
+For the $j$th fold, $\widehat{Y}^{(j)}$ was trained using the training set.
+
+For a given model and a given $x$, the following was observed for each fold after training using the training set
+\begin{equation}
+\widehat{Y}^{(1)}(x),\widehat{Y}^{(2)}(x),\widehat{Y}^{(3)}(x),\dotdotdot,\widehat{Y}^{(n_{fold})}(x)
+\end{equation}
+and for each fold in the test set
+\begin{equation}
+Y^{(1)}(x),Y^{(2)}(x),Y^{(3)}(x),\dotdotdot,Y^{(n_{fold})}(x)
+\end{equation}
+then the following can be estimated
+\begin{equation}
+f(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}}Y^{(j)}(x)
+\end{equation}
+\begin{equation}
+\expectation\left[\widehat{Y}^{(j)}(x)\right] \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}}\widehat{Y}^{(j)}(x)
+\end{equation}
+and:
+\begin{equation}
+\text{RSS}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
+\left(\widehat{Y}^{(j)}(x) - Y^{(j)}(x)\right)^2
+\right]
+\end{equation}
+\begin{equation}
+\text{MSE}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
+\left(\widehat{Y}^{(j)}(x)-f(x)\right)^2
+\right]
+\end{equation}
+\begin{equation}
+\text{BIAS}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} 
+\left[\widehat{Y}^{(j)}(x)\right] - f(x)
+\end{equation}
+\begin{equation}
+\text{VAR}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
+\left(\widehat{Y}^{(j)}(x) - \expectation\left[\widehat{Y}^{(j)}(x)\right]\right)^2
+\right]
+\end{equation}
+\begin{equation}
+\sigma^2(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
+\left(Y^{(j)}(x) - f(x)\right)^2
+\right] \ .
+\end{equation}
+
+\clearpage
+
+\begin{figure}
+\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/noiseidentity_order_1.eps}
+        \caption{Identity, feature order 1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/noisecanonical_order_-1.eps}
+        \caption{Canonical, feature order -1}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/noisecanonical_order_-2.eps}
+        \caption{Canonical, feature order -2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/noiselog_order_-1.eps}
+        \caption{Log, feature order -1}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/noisecanonical_order_-2.eps}
+        \caption{Log, feature order -2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/noise1000_NN.eps}
+        \caption{1000-NN}
+    \end{subfigure}
+    }
+\end{figure}
+
+\begin{figure}
+\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/mseidentity_order_1.eps}
+        \caption{Identity, feature order 1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/msecanonical_order_-1.eps}
+        \caption{Canonical, feature order -1}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/msecanonical_order_-2.eps}
+        \caption{Canonical, feature order -2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/mselog_order_-1.eps}
+        \caption{Log, feature order -1}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/msecanonical_order_-2.eps}
+        \caption{Log, feature order -2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/mse1000_NN.eps}
+        \caption{1000-NN}
+    \end{subfigure}
+    }
+\end{figure}
+
+\begin{figure}
+\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/biasidentity_order_1.eps}
+        \caption{Identity, feature order 1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/biascanonical_order_-1.eps}
+        \caption{Canonical, feature order -1}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/biascanonical_order_-2.eps}
+        \caption{Canonical, feature order -2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/biaslog_order_-1.eps}
+        \caption{Log, feature order -1}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/biascanonical_order_-2.eps}
+        \caption{Log, feature order -2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/bias1000_NN.eps}
+        \caption{1000-NN}
+    \end{subfigure}
+    }
+\end{figure}
 

### 2018-02-22 reports/thesis/book.tex
Style thesis.
Updated make.m and added figures to thesis.

--- 2017-09-17 reports/thesis/book.tex
@@
 \begin{equation}
-I_1 = I_0\exp\left[\int_0^L-\mu(x)\diff x\right].
-\label{eq:beerLaw}
+	I_1 = I_0\exp\left[\int_0^L-\mu(x)\diff x\right].\label{eq:beerLaw}
 \end{equation}
@@
 \begin{equation*}
-p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0\ .
+	p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0
+	\ .
 \end{equation*}
@@
 \begin{equation*}
-M_X(\theta)=\expectation\left[\euler^{X\theta}\right] \ .
+	M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
+	\ .
 \end{equation*}
@@
 \begin{equation*}
-M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right] \ .
+	M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]
+	\ .
 \end{equation*}
@@
 \begin{equation*}
-M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right] \ .
+	M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
+	\ .
 \end{equation*}
@@
 \begin{equation*}
-M_U(\theta)=\expectation\left[\euler^{U\theta}\right] \ ,
+	M_U(\theta)=\expectation\left[\euler^{U\theta}\right]
+	\ ,
 \end{equation*}
@@
 \begin{equation}
-M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]
-=\exp\left[
-\lambda\left(
+	M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
+	\exp
+	\left[
+		\lambda
+		\left(
 		  \euler^\theta-1
@@
 \begin{equation}
-M_X(\theta)
-=
-\exp\left[
-\lambda\left(
+	M_X(\theta)=
+	\exp\left[
+		\lambda
+		\left(
 			M_U(\theta)-1
 		\right)
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-\expectation\left[X\right]=\lambda\expectation\left[U\right] \ .
+	\expectation\left[X\right]=\lambda\expectation\left[U\right]
+	\ .
 \end{equation}
@@
 \begin{equation*}
-M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta) \ ,
+	M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
+	\ ,
 \end{equation*}
@@
 \begin{equation}
-\variance\left[X\right] = \lambda\expectation\left[U^2\right] \ .
+	\variance\left[X\right] = \lambda\expectation\left[U^2\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-X\sim\CPoisson(\lambda,\alpha,\beta) \ .
+	X\sim\CPoisson(\lambda,\alpha,\beta)
+	\ .
 \end{equation}
@@
 \begin{equation}
-X|Y\sim\gammaDist\left(Y\alpha,\beta\right) \ .
+	X|Y\sim\gammaDist\left(Y\alpha,\beta\right)
+	\ .
 \end{equation}
@@
 \begin{equation}
-\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3} \ .
+	\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
+	\ .
 \end{equation}
@@
 \begin{equation}
-p=\frac{2+\alpha}{1+\alpha} \ ,
-\end{equation}
-\begin{equation}
-\mu=\frac{\lambda\alpha}{\beta} \ ,
-\end{equation}
-\begin{equation}
-\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}} \ .
+	p=\frac{2+\alpha}{1+\alpha}
+	\ ,
+\end{equation}
+\begin{equation}
+	\mu=\frac{\lambda\alpha}{\beta}
+	\ ,
+\end{equation}
+\begin{equation}
+	\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
+	\ .
 \end{equation}
@@
 \begin{equation}
-\beta=\frac{1}{\phi(p-1)\mu^{p-1}}
+	beta=\frac{1}{\phi(p-1)\mu^{p-1}}
 \end{equation}
@@
 \begin{equation}
-\prob(X=0) = \exp\left[
+	\prob(X=0) = \exp
+	\left[
 	    -\frac{\mu^{2-p}}{\phi(2-p)}
@@
 	p_X(x) = \sum_{y=1}^{\infty}
-\left[\frac{1}{\phi(p-1)\mu^{p-1}}\right]^{y\alpha}
+	\left[
+		\frac{1}{\phi(p-1)\mu^{p-1}}
+	\right]^{y\alpha}
 	\frac{1}{\Gamma(y\alpha)}
 	x^{y\alpha-1}
-\exp\left[-\frac{x}{\phi(p-1)\mu^{p-1}}\right]
-\\
-\exp\left[-\frac{\mu^{2-p}}{\phi(2-p)}\right]
-\left[\frac{\mu^{2-p}}{\phi(2-p)}\right]^y
-\frac{1}{y!} \ .
+	\exp\left[
+	    -\frac{x}{\phi(p-1)\mu^{p-1}}
+	\right]
+	\\
+	\exp\left[
+	    -\frac{\mu^{2-p}}{\phi(2-p)}
+	\right]
+	\left[
+		\frac{\mu^{2-p}}{\phi(2-p)}
+	\right]^y
+	\frac{1}{y!}
+	\ .
 \end{multline*}
@@
 	p_X(x) = 
-\exp\left[\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)\right]\frac{1}{x}
-\\
-\sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)} \ .
+	\exp\left[
+		\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)
+	\right]
+	\frac{1}{x}
+	\\
+	\sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+	\ .
 \end{multline*}
@@
 	p_X(x) = 
-\exp\left[\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)\right]\frac{1}{x}
+	\exp\left[
+		\frac{1}{\phi}
+		\left(
+			x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
+		\right)
+	\right]
+	\frac{1}{x}
 	\sum_{y=1}^{\infty}W_y(x,p,\phi)
@@
 \begin{equation}
-W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)} \ .
+	W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+	\ .
 \end{equation}
@@
 \end{equation}
+
+\chapter{Data Collection}
 
@@
 \begin{equation}
-W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!} \ .
+	W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
+	\ .
 	\label{eq:compoundPoisson_w}
@@
 \begin{equation}
-M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right] \ .
+	M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-Z = \frac{X-\expectation[X]}{\sqrt{\variance[X]}} \ ,
+	Z = \frac{X-\expectation[X]}{\sqrt{\variance[X]}}
+	\ ,
 \end{equation}
@@
 \begin{equation*}
-Z = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}\left(
+	Z = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
+	\left(
 		X-\frac{\alpha\lambda}{\beta}
@@
 \begin{equation}
-a = -\sqrt{\frac{\alpha\lambda}{\alpha+1}} \ .
+	a = -\sqrt{\frac{\alpha\lambda}{\alpha+1}}
+	\ .
 \end{equation}
@@
 \begin{equation*}
-M_Z(\theta)=\euler^{a\theta}M_X(b\theta) \ .
+	M_Z(\theta)=\euler^{a\theta}M_X(b\theta)
+	\ .
 \end{equation*}
@@
 \begin{equation*}
-M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
-\exp\left[
-\lambda\left(
+	M_Z(\theta)=
+	\exp\left(
+	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
+    \right)
+	\exp\left[
+		\lambda
+		\left(
 			\left(
 				\frac{\beta}{\beta-\frac{\beta\theta}{\sqrt{\alpha(\alpha+1)\lambda}}}
-\right)^\alpha-1
-\right)
-\right]
-\end{equation*}
-\begin{equation*}
-M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
-\exp\left[
-\lambda\left(
+			\right)^\alpha
+			-1
+		\right)
+	\right]
+\end{equation*}
+\begin{equation*}
+	M_Z(\theta)=
+	\exp\left(
+	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
+    \right)
+	\exp\left[
+		\lambda
+		\left(
 			\left(
@@
 			\right)^\alpha
--1\right)
+			-1
+		\right)
 	\right]
@@
 \begin{equation}
-M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
-\exp\left[
-\lambda\left(
+	M_Z(\theta)=
+	\exp\left(
+	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
+    \right)
+	\exp\left[
+		\lambda
+		\left(
 			\left(
@@
 			\right)^{-\alpha}
--1\right)
-\right] \ .
+			-1
+		\right)
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation*}
-M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
+	M_Z(\theta)=
+	\exp\left(
+	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
+    \right)
 	\exp\left[
@@
 		\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
-\right] \ .
+	\right]
+	\ .
 \end{equation*}
@@
 \begin{multline*}
-M_Z(\theta)=\exp\left(-\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}\right)
+	M_Z(\theta)=
+	\exp\left(
+	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
+    \right)
 	\exp\left[
@@
 		+\frac{\theta^2}{2}
-\right.\\\left.
+	\right.
+	\\
+	\left.
 		+\lambda\sum_{r=3}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
@@
 		+\sum_{r=3}^\infty
-		\frac{\theta^r
-			\prod_{s=1}^r(\alpha+s-1)
-		}
+		\frac
+			{\theta^r\prod_{s=1}^r(\alpha+s-1)}
 			{(\alpha(\alpha+1))^{r/2}r!}
 		\lambda^{1-r/2}
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 	}
-	{(\alpha(\alpha+1))^{r/2}}
+	{
+		\alpha(\alpha+1))^{r/2}
+	}
 	=
@@
 	}
-	{\alpha^{r}}
+	{
+		\alpha^{r}
+	}
 \end{equation*}
@@
 	}
-	{(\alpha(\alpha+1))^{r/2}} = 1 \ .
+	{
+		(\alpha(\alpha+1))^{r/2}
+	}
+	= 1
+	\ .
 \end{equation}
@@
 		+\sum_{r=3}^\infty
-		\frac{\theta^r}
-		{r!}
+		\frac{\theta^r}{r!}
 		\lambda^{1-r/2}
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-\lim_{\lambda\rightarrow\infty}\lim_{\alpha\rightarrow\infty}Z\sim\normal(0,1) \ .
+	\lim_{\lambda\rightarrow\infty}\lim_{\alpha\rightarrow\infty}Z\sim\normal(0,1)
+	\ .
 \end{equation}
@@
 \begin{equation}
-X|Y = \sum_{i=1}^{Y}U_i \ .
+	X|Y = \sum_{i=1}^{Y}U_i
+	\ .
 \end{equation}
@@
 \begin{equation}
-M_X(\theta)=\exp\left[
+	M_X(\theta)=
+	\exp\left[
 		\lambda(M_U(\theta)-1)
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 	Z = \frac{X}{\sqrt{\lambda\expectation[U^2]}}
--\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}} \ .
+	-\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
+	\ .
 \end{equation}
@@
 \begin{equation*}
-M_Z(\theta)=\exp\left[-\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}\right]
-\exp\left[
-\lambda\left(
-M_U\left(\frac{\theta}{\sqrt{\lambda\expectation[U^2]}}\right)-1
+	M_Z(\theta)=
+	\exp\left[
+	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
+	\right]
+	\exp\left[
+	\lambda
+	\left(
+		M_U
+		\left(
+			\frac{\theta}{\sqrt{\lambda\expectation[U^2]}}\right)-1
 		\right)
@@
 \begin{equation*}
-M_Z(\theta)=\exp\left[-\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}\right]
+	M_Z(\theta)=
+	\exp\left[
+	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
+    \right]
 	\exp\left[
 		\lambda\sum_{r=1}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
-\right] \ .
+	\right]
+	\ .
 \end{equation*}
@@
 \begin{multline*}
-M_Z(\theta)=\exp\left[-\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}\right]
+	M_Z(\theta)=\exp\left[
+	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
+	\right]
 	\exp\left[
@@
 		\frac{\theta^2M_U''(0)}{2\expectation[U^2]}
-\right.\\+\left.
+	\right.
+	\\+
+	\left.
 		\lambda\sum_{r=3}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
-\right] \ .
+	\right]
+	\ .
 \end{multline*}
@@
 \begin{equation}
-M_Z(\theta)=\exp\left[
+	M_Z(\theta)=
+	\exp\left[
 		\frac{\theta^2}{2}
@@
 		\sum_{r=3}^\infty\frac{\theta^r \expectation[U^r]}{(\expectation[U^2])^{r/2}r!}\lambda^{1-r/2}
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1) \ .
+	\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1)
+	\ .
 \end{equation}
@@
 	=
-\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x \ .
+	\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x
+	\ .
 \end{equation}
@@
 \begin{equation}
-p_X(x)\propto x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}\exp\left[x^{\frac{\alpha}{\alpha+1}}
-	\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
-\right] \ .
+	p_X(x)\propto x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
+	\exp\left[
+		x^{\frac{\alpha}{\alpha+1}}
+		\frac{
+			(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)
+		}
+		{
+			\alpha^{\frac{\alpha}{\alpha+1}}
+		}
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-K_X(\theta) = \lambda\left[
+	K_X(\theta) = \lambda
+	\left[
 		\left(\frac{\beta}{\beta-\theta}\right)^\alpha-1
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-s = \beta - \left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}} \ .
+	s = \beta - \left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
+	\ .
 \end{equation}
@@
 	p_X(x)\approx
-\frac{1}{\sqrt{2\pi}}\left[\frac{(\beta-s)^{\alpha+2}}{\lambda\alpha(\alpha+1)\beta^\alpha}\right]^{1/2}
+	\frac{1}{\sqrt{2\pi}}
+	\left[
+		\frac{
+			(\beta-s)^{\alpha+2}
+		}
+		{
+			\lambda\alpha(\alpha+1)\beta^\alpha
+		}
+	\right]^{1/2}
 	\exp\left[
 		\lambda\left(\left(\frac{\beta}{\beta-s}\right)^\alpha-1\right)-sx
-\right] \ .
+	\right]
+	\ .
 \end{equation*}
@@
 	\exp\left[
-	\lambda\left(
+		\lambda
+		\left(
 			\left(
@@
 	\left[
-\frac{\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{\alpha+2}{\alpha+1}}}{\lambda\alpha(\alpha+1)\beta^\alpha}
+		\frac{
+			\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{\alpha+2}{\alpha+1}}
+		}
+		{
+			\lambda\alpha(\alpha+1)\beta^\alpha
+		}
 	\right]^{1/2}
@@
 	\exp\left[
-	\lambda\left(
+		\lambda
+		\left(
 			\beta^\alpha
@@
 	p_X(x)\approx
-\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+	\frac{
+		\left(
+			\lambda\alpha\beta^\alpha
+		\right)^{\frac{1}{2(\alpha+1)}}
+	}
+	{
+		\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
+	}	
 	\\
@@
 		\left(
-		\frac{\lambda\beta^\alpha}{\left(\lambda\alpha\beta^\alpha\right)^{\frac{\alpha}{\alpha+1}}}+\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
+			\frac{
+				\lambda\beta^\alpha
+			}
+			{
+				\left(\lambda\alpha\beta^\alpha\right)^{\frac{\alpha}{\alpha+1}}
+			}
+			+
+			\left(
+				\lambda\alpha\beta^\alpha
+			\right)^{\frac{1}{\alpha+1}}
 		\right)
@@
 	p_X(x)\approx
-\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+	\frac{
+		\left(
+			\lambda\alpha\beta^\alpha
+		\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
+	}
+	{
+		\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
+	}
 	\euler^{-x\beta}
 	\\
-\exp\left[x^{\frac{\alpha}{\alpha+1}}
+	\exp\left[
+		x^{\frac{\alpha}{\alpha+1}}
 		\left(
 			(\lambda\beta^\alpha)^{1-\frac{\alpha}{\alpha+1}}\alpha^{-\frac{\alpha}{\alpha+1}}
-		+\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
+			+
+			\left(
+				\lambda\alpha\beta^\alpha
+			\right)^{\frac{1}{\alpha+1}}
 		\right)
@@
 	p_X(x)\approx
-\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
-\\
-\exp\left[x^{\frac{\alpha}{\alpha+1}}
-	\left(
-		(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}\alpha^{-\frac{\alpha}{\alpha+1}}
-		+\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
+	\frac{
+		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
+	}
+	{
+		\sqrt{2\pi(\alpha+1)}
+	}
+	x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
+	\\
+	\exp\left[
+		x^{\frac{\alpha}{\alpha+1}}
+		\left(
+			(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
+			\alpha^{-\frac{\alpha}{\alpha+1}}
+			+
+			\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
 		\right)
@@
 	p_X(x)\approx
-\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
-\\
-\exp\left[x^{\frac{\alpha}{\alpha+1}}(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
+	\frac{
+		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
+	}
+	{
+		\sqrt{2\pi(\alpha+1)}
+	}
+	x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
+	\\
+	\exp\left[
+		x^{\frac{\alpha}{\alpha+1}}(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
 		\left(
@@
 		\right)
-\right] \ .
+	\right]
+	\ .
 \end{multline*}
@@
 \begin{align}
-\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}} & = \alpha^{\frac{1}{\alpha+1}}+\frac{1}{\alpha^{\frac{\alpha}{\alpha+1}}}
+	\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
+	& = \alpha^{\frac{1}{\alpha+1}}+\frac{1}{\alpha^{\frac{\alpha}{\alpha+1}}}
 	\nonumber\\
@@
 p_X(x)\approx
-\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
+	\frac{
+		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
+	}
+	{
+		\sqrt{2\pi(\alpha+1)}
+	}
+	x^{-\frac{\alpha+2}{2(\alpha+1)}}
 	\euler^{-x\beta}
-\exp\left[x^{\frac{\alpha}{\alpha+1}}
+	\exp\left[
+		x^{\frac{\alpha}{\alpha+1}}
 		\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
-\right] \ .
+	\right]
+	\ .
 \end{equation*}
@@
 \begin{equation}
-W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!} \ .
+	W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
+	\ .
 	\label{eq:compoundPoisson_Wy}
@@
 	\ln(W_y) =
-y\ln\left(
+	y
+	\ln\left(
 		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
 	\right)
--\ln(y!)-\ln\Gamma(y\alpha) \ .
+	-\ln(y!)-\ln\Gamma(y\alpha)
+	\ .
 \end{equation}
@@
 	\right)
--y\ln(y)+y-y\alpha\ln(y\alpha) + y\alpha \ .
+	-y\ln(y)+y-y\alpha\ln(y\alpha) + y\alpha
+	\ .
 \end{equation}
@@
 	-\ln(y)-1+1
-\\-\alpha\ln(y\alpha)-\alpha+\alpha
+	\\
+	-\alpha\ln(y\alpha)-\alpha+\alpha
 \end{multline*}
@@
 	-\ln(y)
--\alpha\ln(y\alpha) \ .
+	-\alpha\ln(y\alpha)
+	\ .
 \end{equation}
@@
 	0 \approx \ln\left(
-\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha}
+		\frac{
+			x^\alpha
+		}
+		{
+			\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha
+		}
 	\right)
@@
 	\right)^{\frac{\alpha}{1+\alpha}}
-(2-p)^{\frac{-1}{1+\alpha}} \ .
+	(2-p)^{\frac{-1}{1+\alpha}}
+	\ .
 \end{equation*}
@@
 \begin{equation*}
-\alpha=\frac{2-p}{p-1} \ ,
+	\alpha=\frac{2-p}{p-1}
+	\ ,
 \end{equation*}
@@
 \begin{equation}
-y_{\text{max}} \approx \frac{x^{2-p}}{\phi(2-p)} \ .
+	y_{\text{max}} \approx \frac{x^{2-p}}{\phi(2-p)}
+	\ .
 \end{equation}
@@
 		1,\text{round}\left(\frac{x^{2-p}}{\phi(2-p)}\right)
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y \ ,
+	\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y
+	\ ,
 \end{equation}
@@
 \begin{equation}
-\ln\left[\sum_{y=y_\text{l}}^{y_\text{u}}W_y\right]
-= \ln\left(W_{y_\text{max}}\right)+\ln\sum_{y=y_\text{l}}^{y_\text{u}}\exp\left[
+	\ln\left[
+		\sum_{y=y_\text{l}}^{y_\text{u}}W_y
+	\right]
+	= 
+	\ln\left(
+		W_{y_\text{max}}
+	\right)
+	+\ln\sum_{y=y_\text{l}}^{y_\text{u}}
+	\exp\left[
 		\ln\left(W_y\right)-\ln\left(W_{y_\text{max}}\right)
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-p_X(x) \propto \exp\left[
--\frac{\alpha+2}{2(\alpha+1)}\ln(x)
+	p_X(x) \propto
+	\exp\left[
+		-\frac{\alpha+2}{2(\alpha+1)}
+		\ln(x)
 		-x\beta
@@
 \begin{equation}
-k = \max_{i\in\left\{1,2,3,\dotdotdot,n\right\}}\left[
--\frac{\alpha+2}{2(\alpha+1)}\ln(x_i)
+	k =
+	\max_{i\in\left\{1,2,3,\dotdotdot,n\right\}}
+	\left[
+		-\frac{\alpha+2}{2(\alpha+1)}
+		\ln(x_i)
 		-x_i\beta
@@
 		\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-\widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}\left[
+	\widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}
+	\left[
 		\left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
-\right] \ ,
+	\right]
+	\ ,
 \end{equation}
@@
 \begin{equation}
-\frac{\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)}{\euler^{-\lambda}(1+\lambda)}\times 0.1 \ .
+	\frac{
+		\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)
+	}
+	{
+		\euler^{-\lambda}(1+\lambda)
+	}
+	\times 0.1
+	\ .
 \end{equation}
@@
 \begin{equation*}
-\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n\left[
+	\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
+	\left[
 		\mathbb{I}(x_i=0)\ln \prob(X=x_i)
@@
 \begin{multline}
-\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n\left[
+	\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
+	\left[
 		-\mathbb{I}(x_i=0)\lambda
-\vphantom{\sum_i^i}\right.\\\left.
+		\vphantom{\sum_i^i}
+	\right.
+	\\
+	\left.
 		+\mathbb{I}(x_i>0)\left(
-	-\beta x_i-\lambda-\ln x -\ln\sum_{y=1}^\infty W_y
+		-1-\beta x_i-\lambda-\ln x -\ln\sum_{y=1}^\infty W_y
 		\right)
@@
 		\prob(Y=0)
-	\right.\\\left.
+	\right.
+	\\
+	\left.
 		+
@@
 \begin{multline}
-\ln L(\lambda,\alpha,\beta;X,Y)
-=
+	\ln L(\lambda,\alpha,\beta;X,Y)=
 	\sum_{i=1}^n
@@
 		\lambda
-	\right.\\\left.+
+	\right.
+	\\
+	\left.+
 		\mathbb{I}(x_i>0)
@@
 			Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
-	\right.\right.\\\left.\left.	
+		\right.
+	\right.
+	\\
+	\left.
+		\left.	
 			- \lambda + Y_i \ln \lambda - \ln(Y_i!)
 		\right)
-\right] \ .
+	\right]
+	\ .
 \end{multline}
@@
 \begin{equation}
-y_i = \expectation\left[
+	y_i =
+	\expectation\left[
 		Y|X=x_i
@@
 \begin{equation*}
-\prob(Y=y|X=x) = \frac{p_{X|Y}(x|y)\prob(Y=y)}{p_X(x)} \ .
+	\prob(Y=y|X=x) = \frac{p_{X|Y}(x|y)\prob(Y=y)}{p_X(x)}
+	\ .
 \end{equation*}
@@
 \begin{equation}
-y_i = \frac{\sum_{y=1}^\infty y W_y}{\sum_{y=1}^\infty W_y} \ .
+	y_i = \frac{\sum_{y=1}^\infty y W_y}{\sum_{y=1}^\infty W_y}
+	\ .
 \end{equation}
@@
 \begin{equation}
-\variance[Y|X=x_i] = \frac{\sum_{y=1}^\infty W^{(2)}_y}{\sum_{y=1}^\infty W_y} - \left(y_i\right)^2 \ .
+	\variance[Y|X=x_i] = \frac{\sum_{y=1}^\infty W^{(2)}_y}{\sum_{y=1}^\infty W_y} - \left(y_i\right)^2
+	\ .
 \end{equation}
@@
 \begin{equation}
-\frac{\partial \ln(W_y^{(r)})}{\partial y} = \frac{r}{y } + \frac{\partial \ln(W_y)}{\partial y} \ .
+	\frac{\partial \ln(W_y^{(r)})}{\partial y} = \frac{r}{y } + \frac{\partial \ln(W_y)}{\partial y}
+	\ .
 \end{equation}
@@
 \begin{equation}
-\frac{\partial \ln(W_y^{(r)})}{\partial y} \approx \frac{\partial \ln(W_y)}{\partial y} \ .
+	\frac{\partial \ln(W_y^{(r)})}{\partial y} \approx \frac{\partial \ln(W_y)}{\partial y}
+	\ .
 \end{equation}
@@
 \begin{multline*}
-T(\lambda,\alpha,\beta)
-=
+	T(\lambda,\alpha,\beta)=
 	\sum_{i=1}^n
@@
 			Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
-	\right.\right.\\\left.\left.	
+		\right.
+	\right.
+	\\
+	\left.
+		\left.	
 			- \lambda + Y_i \ln \lambda - \ln(Y_i!)
 		\right)
-|X_i=x_i\right]
+		|X_i=x_i
+	\right]
 \end{multline*}
 \begin{multline*}
-T(\lambda,\alpha,\beta)
-=
+	T(\lambda,\alpha,\beta)=
 	-n\lambda
-\\+
-	\sum_{i=1}^n
+	\\
+	+\sum_{i=1}^n
 	\mathbb{I}(x_i>0)
@@
 		\expectation[Y_i|X_i=x_i]\alpha\ln\beta-\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]
-	\right.\\\left.
+	\right.
+	\\
+	\left.
 		+\expectation[Y_i|X_i=x_i]\alpha\ln x_i - \beta x_i
@@
 \begin{multline}
-T(\lambda,\alpha,\beta)
-=
--n\lambda+
-	\sum_{i=1}^n
+	T(\lambda,\alpha,\beta)=
+	-n\lambda
+	+\sum_{i=1}^n
 	\mathbb{I}(x_i>0)
@@
 		y_i\alpha\ln\beta-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
-	\right.\\\left.
+	\right.
+	\\
+	\left.
 		+y_i\alpha\ln x_i - \beta x_i
 		+ y_i \ln \lambda
-	\vphantom{\frac{1}{1}}\right] + c \ .
+		\vphantom{\frac{1}{1}}
+	\right]
+	+ c
+	\ .
 \end{multline}
@@
 \begin{equation}
-\frac{\partial^2 T}{\partial \beta \partial \lambda } = 0 \ .
+	\frac{\partial^2 T}{\partial \beta \partial \lambda } = 0
+	\ .
 \end{equation}
@@
 \begin{multline}
-\frac{\partial T}{\partial \alpha} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	\frac{\partial T}{\partial \alpha} =
+	\sum_{i=1}^n\mathbb{I}(x_i>0)
+	\left[
 		y_i\ln\beta -\psi(\alpha y_i)y_i-\zeta_i\alpha\psi'(\alpha y_i)
-	\vphantom{\frac{1}{1}}\right.\\\left.
+		\vphantom{\frac{1}{1}}
+	\right.
+	\\
+	\left.
 		- \frac{1}{2}\zeta_i\alpha^2\psi''(\alpha y_i)y_i + y_i\ln x_i
@@
 	\frac{\alpha y_i}{\beta}-x_i
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 	\frac{\partial^2 T}{\partial \alpha \partial \beta} =
-\sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right] \ ,
+	\sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right]
+	\ ,
 	\label{eq:compoundPoisson:d2tdadb}
@@
 \begin{multline*}
-\frac{\partial^2 T}{\partial \alpha^2} =  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	\frac{\partial^2 T}{\partial \alpha^2} = 
+	\sum_{i=1}^n\mathbb{I}(x_i>0)
+	\left[
 		-y_i^2\psi'(\alpha y_i) - \zeta_i\psi'(\alpha y_i) - \zeta_i\alpha y_i\psi''(\alpha y_i)
@@
 \begin{multline}
-\frac{\partial^2 T}{\partial \alpha^2} =  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	\frac{\partial^2 T}{\partial \alpha^2} = 
+	\sum_{i=1}^n\mathbb{I}(x_i>0)
+	\left[
 		-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
-	\vphantom{\frac{1}{2}}\right.\\\left.	
+		\vphantom{\frac{1}{2}}
+	\right.
+	\\
+	\left.	
 		-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
@@
 	\right]^{-1}
-\left[\nabla_{\alpha,\beta} T\right]
+	\left[
+		\nabla_{\alpha,\beta} T
+	\right]
 \end{equation}
@@
 		{\partial}/{\partial \beta}
-\end{pmatrix} \ .
+	\end{pmatrix}
+	\ .
 \end{equation}
@@
 		\nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 \begin{equation}
-\matr{I}
-=
+	\matr{I}=
 	\begin{pmatrix}
@@
 		0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
-\end{pmatrix} \ .
+	\end{pmatrix}
+	\ .
 \end{equation}
@@
 	\right]
-= \matr{I}^{-1} \ .
+	=
+	\matr{I}^{-1}
+	\ .
 \end{equation}
@@
 \begin{multline*}
-\frac{\partial^2 T}{\partial \alpha^2} =  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	\frac{\partial^2 T}{\partial \alpha^2} = 
+	\sum_{i=1}^n\mathbb{I}(x_i>0)\left[
 		-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
-	\vphantom{\frac{1}{2}}\right.\\\left.	
+		\vphantom{\frac{1}{2}}
+	\right.
+	\\
+	\left.	
 		-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
-\right] \ .
+	\right]
+	\ .
 \end{multline*}
@@
 \begin{equation}
-\psi(n) = \frac{\partial\ln\Gamma(n)}{\partial n} \approx \ln n \ .
+	\psi(n) = \frac{\partial\ln\Gamma(n)}{\partial n} \approx \ln n
+	\ .
 \end{equation}
@@
 	\psi''(n) & \approx -1/n^2 \\
-\psi'''(n) & \approx 2/n^3 \ .
+	\psi'''(n) & \approx 2/n^3
+	\ .
 \end{align}
@@
 \begin{equation*}
-\frac{\partial^2 T}{\partial \alpha^2} \approx  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	\frac{\partial^2 T}{\partial \alpha^2} \approx 
+	\sum_{i=1}^n\mathbb{I}(x_i>0)
+	\left[
 		-\frac{y_i^2+\zeta_i}{\alpha y_i} + 2\frac{\zeta_i\alpha y_i}{\alpha^2 y_i^2}
@@
 \begin{equation}
-\frac{\partial^2 T}{\partial \alpha^2} \approx  \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
+	\frac{\partial^2 T}{\partial \alpha^2} \approx 
+	\sum_{i=1}^n\mathbb{I}(x_i>0)
+	\left[
 		-\frac{y_i}{\alpha}
-\right] \ .
+	\right]
+	\ .
 \end{equation}
@@
 		y_i/\beta & -\alpha y_i/\beta^2
-\end{pmatrix}  \ . 
+	\end{pmatrix}
+	\ . 
 \end{equation}
@@
 	\approx
-0 \ .
+	0
+	\ .
 \end{equation}
@@
 	\left[
-	y_i\alpha\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
-	\right.\\\left.
+	y_i\alpha
+	\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
+	\right.
+	\\
+	\left.
 		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
 		+ y_i \ln \lambda
-	\vphantom{\frac{1}{1}}\right] + c
+		\vphantom{\frac{1}{1}}
+	\right]
+	+ c
 \end{multline*}
@@
 \begin{multline*}
-T(\lambda,\alpha)
-=
+	T(\lambda,\alpha)=
 	-n\lambda+
@@
 		y_i\alpha\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\alpha y_i\ln(\alpha y_i) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
-	\right.\\\left.
+	\right.
+	\\
+	\left.
 		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
 		+ y_i \ln \lambda
-	\vphantom{\frac{1}{1}}\right] + c
+		\vphantom{\frac{1}{1}}
+	\right]
+	+ c
 \end{multline*}
 \begin{multline*}
-T(\lambda,\alpha)
-=
+	T(\lambda,\alpha)=
 	-n\lambda+
@@
 		y_i\alpha\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
-	\right.\\\left.
+	\right.
+	\\
+	\left.
 		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
 		+ y_i \ln \lambda
-	\vphantom{\frac{1}{1}}\right] + c \ .
+		\vphantom{\frac{1}{1}}
+	\right]
+	+ c
+	\ .
 \end{multline*}
@@
 \begin{equation*}
-\frac{\partial T}{\partial \alpha}
-=
+	\frac{\partial T}{\partial \alpha} =
 	\sum_{i=1}^n
@@
 	\left[
-	y_i\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right) +  y_i - \frac{1}{2}\frac{\zeta_i}{y_i}
+		y_i\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right)
+		+ y_i - \frac{1}{2}\frac{\zeta_i}{y_i}
 		+y_i\ln x_i - \frac{\lambda x_i}{\widehat{\mu}}
-	\vphantom{\frac{1}{1}}\right]
+		\vphantom{\frac{1}{1}}
+	\right]
 \end{equation*}
@@
 
+\chapter{Variance Prediction}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm6.eps}
+        \caption{$h=10^0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm8.eps}
+        \caption{$h=10^2$}
+    \end{subfigure}
+    }
+    \centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm9.eps}
+        \caption{$h=10^3$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm10.eps}
+        \caption{$h=10^4$}
+    \end{subfigure}
+    }
+    \caption{Epanechnikov kernel regression, with bandwidth $h$, fitted on the variance-mean data from \texttt{Mar16}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_25.eps}
+        \caption{$n=25$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_50.eps}
+        \caption{$n=50$}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_75.eps}
+        \caption{$n=75$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_100.eps}
+        \caption{$n=100$}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Mar16} using $n$ of the images.
+Fitted is a Gamma GLM with identity link.
+Error bars represent the $\Phi(\pm1)$ quantile.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad1_iGlm1.eps}
+        \caption{No shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad2_iGlm1.eps}
+        \caption{BW shading correction}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad3_iGlm1.eps}
+        \caption{Linear shading correction}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16 30deg} using different shading corrections.
+Fitted is a Gamma GLM with identity link.
+Error bars represent the $\Phi(\pm1)$ quantile.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm2.eps}
+        \caption{Inverse link, $x^{-1}$ feature}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm3.eps}
+        \caption{Inverse link, $x^{-2}$ feature}
+    \end{subfigure}
+    }
+    \centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm4.eps}
+        \caption{Log link, $x$ feature}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm5.eps}
+        \caption{Log link, $x^{-1}$ feature}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Mar16}.
+Fitted are Gamma GLM with different link functions and explanatory variables.
+Error bars represent the $\Phi(\pm1)$ quantile.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_training_MSE.eps}
+        \caption{Training error}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_test_MSE.eps}
+        \caption{Test error}
+    \end{subfigure}
+    }
+    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Mar16}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_training_MSE.eps}
+        \caption{Training error}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_test_MSE.eps}
+        \caption{Test error}
+    \end{subfigure}
+    }
+    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 30deg}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_training_MSE.eps}
+        \caption{Training error}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_test_MSE.eps}
+        \caption{Test error}
+    \end{subfigure}
+    }
+    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 120deg}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_training_MSE.eps}
+        \caption{Training error}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_test_MSE.eps}
+        \caption{Test error}
+    \end{subfigure}
+    }
+    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 30deg}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_training_MSE.eps}
+        \caption{Training error}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_test_MSE.eps}
+        \caption{Test error}
+    \end{subfigure}
+    }
+    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 120deg}.}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{../figures/meanVar/GlmDeviance_Mar16_scaled_deviance.eps}
+    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Mar16}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_30deg_scaled_deviance.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_120deg_scaled_deviance.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{July16}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_30deg_scaled_deviance.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_120deg_scaled_deviance.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Sep16}.}
+\end{figure}
+
 \chapter{Inference}
-%\begin{equation*}
-%i=1,2,3,\dotdotdot,n_{pixel}
-%\end{equation*}
-%\begin{equation*}
-%j=1,2,3,\dotdotdot,n_{repeat}
-%\end{equation*}
-%\begin{equation*}
-%x_i^{(j)} = \text{mean greyvalue of pixel }i\text{, }j\text{th repeat}
-%\end{equation*}
-%\begin{equation*}
-%y_i^{(j)} = \text{variance greyvalue of pixel }i\text{, }j\text{th repeat}
-%\end{equation*}
-%\begin{equation*}
-%\widehat{Y}^{(j)}(x) = \text{predicted variance greyvalue given }x
-%\end{equation*}
-%Trained $\widehat{Y}^{(j)}(x)$ using $(y_1^{(j)},x_1^{(j)}),(y_2^{(j)},x_2^{(j)}),(y_3^{(j)},x_3^{(j)}),\dotdotdot,(y_{n_{pixel}}^{(j)},x_{n_{pixel}}^{(j)})$.
-%\begin{equation*}
-%\widehat{\zeta}^{(j)}(x) = \text{predicted variance of the variance greyvalue given }x
-%\end{equation*}
-%
-%Below are the training statistics, but can be generalised to test statistics:
-%\begin{equation}
-%\text{MSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}\right]^2
-%\end{equation}
-%\begin{equation}
-%\text{MSSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\dfrac{\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}}{\sqrt{\widehat{\zeta}^{(j)}(x_i^{(j)})}}\right]^2
-%\end{equation}
-%\begin{equation}
-%\text{VAR}^{(j)} = \sum_{i=1}^{n_{pixel}}
-%\left[
-%\widehat{Y}^{(j)}(x_i^{(j)}) - \expectation(\widehat{Y}(x_i^{(j)}))
-%\right]^2
-%\end{equation}
-%\begin{equation}
-%\text{BIAS2}^{(j)} = \sum_{i=1}^{n_{pixel}}
-%\left[
-%\expectation(\widehat{Y}(x_i^{(j)}))
-%-
-%y_i^{(j)}
-%\right]^2
-%\end{equation}
-%where
-%\begin{equation}
-%\expectation(\widehat{Y}(x_i^{(j)})) \approx
-%\frac{1}{n_{repeat}}\sum_{j=1}^{n_{repeat}}
-%\widehat{Y}^{(j)}(x_i^{(j)})
-%\end{equation}
-%
-%\clearpage
-%\begin{equation}
-%Y(x) = y(x) + \epsilon(x)
-%\end{equation}
-%where
-%\begin{equation}
-%\expectation[\epsilon(x)] = 0, \quad \variance[\epsilon(x)] = \sigma^2(x) \ .
-%\end{equation}
-%The statistics for a given $x$ are:
-%\begin{equation}
-%\text{MSE}(x) = \expectation\left[
-%(Y(x)-\widehat{Y}(x))^2
-%\right]
-%\end{equation}
-%\begin{equation}
-%\text{VAR}(x) = \expectation\left[
-%(\widehat{Y}(x) - \expectation(\widehat{Y}(x))^2
-%\right]
-%\end{equation}
-%\begin{equation}
-%\text{BIAS2}(x) = \expectation\left[
-%(\expectation(\widehat{Y}(x) - y(x))^2
-%\right]
-%\end{equation}
-%\begin{equation}
-%\sigma^2(x) = \expectation\left[
-%(
-%Y(x) - \expectation(Y(x))
-%)^2
-%\right] \ .
-%\end{equation}
-%
-%$y(x)$ is unknown so the bias squared can be calculated using
-%\begin{equation}
-%\text{BIAS2}(X) = \text{MSE}(X) - \text{VAR}(X) - \sigma^2(x)
-%\end{equation}
-%
-%The expectations were estimated using bootstrapped samples of $Y(x)$ and $\widehat{Y}(x)$.
-%
-%\clearpage
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_MSSE.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_MSSE.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Mean squared standardised error}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_MSE.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_MSE.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Mean squared error}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_var.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_var.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Estimation variance}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/training_bias2.eps}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/test_bias2.eps}
-%    \end{subfigure}
-%    }
-%    \caption{Bias squared}
-%\end{figure}
 

### 2018-02-27 reports/thesis/book.tex
Started on meanVar in thesis.

@@
 
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm6.eps}
-        \caption{$h=10^0$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm8.eps}
-        \caption{$h=10^2$}
-    \end{subfigure}
-    }
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm9.eps}
-        \caption{$h=10^3$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm10.eps}
-        \caption{$h=10^4$}
-    \end{subfigure}
-    }
-    \caption{Epanechnikov kernel regression, with bandwidth $h$, fitted on the variance-mean data from \texttt{Mar16}.}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
-\end{figure}
+In the previous chapter, it was found that it is very hard to fit a compound Poisson random variable onto the grey values directly itself.
+It is not totally useless however.
+The compound Poisson model showed that the variance of the grey value has a linear relationship with the mean grey value.
+Given this, it would be possible to predict the variance of the grey value, given the grey value.
+This opens up new ways to predict the uncertainty of each individual pixel in an x-ray scan.
+
+In this chapter, different types of regressions were tested to see if they perform well in predicting grey value variance given the grey value.
+Two types of regressions were used.
+Generalised linear models \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized} (GLM) is a parametric regression which models the response variable as a random variable in the exponential family.
+In this project, a Gamma distributed random variable was chosen as the response variable.
+A non-parametric regression was also considered, here there kernel regression \citep{friedman2001elements} was used.
+
+Using the replicated x-ray images, the within individual pixel sample mean and sample variance were obtained.
+The sample variance-mean data were then used for the regressions to be fitted on.
+The deviance was investigated as a method of model selection.
+The regression was also used to test it's prediction performance on held out images.
+
+In the end, a GLM with a linear relationship between the variance and the mean was good enough.
+Its performance is similar to other complicated models and its simple form attracts those who follows Occam's razor, that the simpler models are usually better.
+The linear relationship is also justified by the compound Poisson model.
+
+\section{Variance-Mean Relationship}
+
+The sample variance-mean data were obtained from the replicated x-ray images, assuming each image are i.i.d.
+
+Let $x_{i,j}^{(r)}$ be the grey value of the pixel in the $i$th row and $j$th column in the $r$th image for $r=1,2,3,\dotdotdot,n$. The within individual pixel sample mean is
+\begin{equation}
+    \bar{x}_{i,j}=\frac{1}{n}\sum_{r=1}^n x_{i,j}^{(r)}
+\end{equation}
+and the within individual pixel sample variance is
+\begin{equation}
+    y_{i,j} =
+    \frac{1}{n-1}
+    \sum_{r=1}^n
+        \left(
+            x_{i,j}^{(r)} - \bar{x}_{i,j}
+        \right)^2
+    \ .
+\end{equation}
+
+Only the masked pixels will be considered here as this is the region of interest (ROI).
+The sample variance-mean data can be obtained by calculating the within individual pixel sample mean and variance for all ROI pixels and can be plotted as a histogram.
+For example, the sample variance-mean data for \texttt{Mar16} can be seen in Figure \ref{fig:meanvar_mar16_100}.
+
+\subsection{Generalised Linear Models}
+By making some assumptions, some useful and simple results can be obtained.
+Firstly, it was assumed the standard error from estimating the mean was negligible.
+Secondly, it was assumed for a given pixel, the grey value from each each were Normal i.i.d.
+Following from these assumptions, the sample variance is Gamma distributed with shape parameter $(n-1)/2$.
+Furthermore the standard error of the sample variance is proportional to $(n-1)^{-1/2}$, meaning the sample variance is more precise when more and more images were used to estimate the variance.
+This was experimentally shown in Figure \ref{fig:meanvar_mar16_differentn}, the spread of the sample variance decreased as $n$ increased.
 
@@
         \caption{$n=100$}
+        \label{fig:meanvar_mar16_100}
     \end{subfigure}
@@
 Error bars represent the $\Phi(\pm1)$ quantile.}
+    \label{fig:meanvar_mar16_differentn}
+\end{figure}
+
+A GLM \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized}, with Gamma distributed response, would then be an appropriate regression to be used.
+Let $Y$ be the grey value sample variance and $X$ be the grey value, then a GLM models $Y$ via the following
+\begin{equation}
+    Y|X \sim 
+    \gammaDist\left(
+        \frac{n-1}{2},
+        f(X)
+    \right)
+\end{equation}
+where $f(X)$ is some user specified function.
+Conventionally it is useful for the specified function to be a parameter of the conditional mean $Y|X$.
+This function is known as the link function and can be expressed as
+\begin{equation}
+g(\mu_X) = \eta(X)
+\end{equation}
+where $\mu_X=\expectation\left[Y|X\right]$ and $\eta(X)$ is a linear function of $X$, for example
+\begin{equation}
+\eta(X) = \beta_0 + \beta_1 X^p \ .
+\end{equation}
+For a specified link function and $p$, the GLM is fitted onto the data by estimating the parameters $\beta_0$ and $\beta_1$.
+
+In this project, the identity, inverse and log link functions were investigated for a selected few integer values of $p$.
+These link functions are shown in Table \ref{table:meanvar_linkfunctions}.
+They are fitted on the variance-mean data from \texttt{Mar16} as shown in Figure \ref{fig:meanvar_mar16}.
+
+\begin{table}
+    \centering
+    \begin{tabular}{c|c|c|c}
+    &\multicolumn{3}{c}{Link functions}\\
+    &Identity&Inverse&Log\\
+    \hline
+    $g(\mu)$&$\mu$&$1/\mu$&$\ln(\mu)$\\
+    \hline
+    $\expectation[Y|X=x]$&$\beta_0 + \beta_1 x^p$&$\left[\beta_0 + \beta_1 x^p\right]^{-1}$&$\exp\left[\beta_0 + \beta_1 x^p\right]$
+    \end{tabular}
+    \caption{Link functions}
+    \label{table:meanvar_linkfunctions}
+\end{table}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm2.eps}
+        \caption{Inverse link, $p=-1$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm3.eps}
+        \caption{Inverse link, $p=-2$}
+    \end{subfigure}
+    }
+    \centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm4.eps}
+        \caption{Log link, $p=1$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm5.eps}
+        \caption{Log link, $p=-1$}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the variance-mean data from \texttt{Mar16}.
+Fitted are Gamma GLM with different link functions polynomial features.
+Error bars represent the $\Phi(\pm1)$ quantile.}
+    \label{fig:meanvar_mar16}
+\end{figure}
+
+\subsection{Kernel Regression}
+
+Kernel regression \citep{friedman2001elements} is a type of non-parametric regression and its prediction is done using a weighted sum of the data rather then fitting a parametric model.
+Suppose a collection of variance-mean data were collected $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$, then the kernel regression is
+\begin{equation}
+    \widehat{y}(x)=
+    \dfrac{
+        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right) y_i
+    }
+    {
+        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right)
+    }
+\end{equation}
+where $k(x)$ is a specified kernel function and $\lambda$ is called the bandwidth. Popular choices for the kernel include the Gaussian kernel \citep{friedman2001elements}
+\begin{equation}
+    k(x)=\phi(x)
+\end{equation}
+and the Epanechnikov kernel \citep{friedman2001elements}
+\begin{equation}
+    k(x) = 
+    \begin{cases}
+        \frac{3}{4}\left(1-x^2\right)& \text{ for } -1<x<1 \\ 
+        0 & \text{ otherwise } 
+    \end{cases}
+    \ .
+\end{equation}
+
+An example of the kernel regression using the Epanechnikov kernel is shown in Figure \ref{fig:meanvar_epanechnikov}.
+It shows the kernel regression fitted onto the \texttt{Mar16} variance-mean data for different values of $\lambda$.
+The bandwidth controls how smooth the kernel regression is.
+Just by observation, $\lambda=1$ is too small because it is capturing the noise whereas $\lambda=10^4$ is too large as it did not captured the general shape of the variance-mean relationship.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm6.eps}
+        \caption{$\lambda=10^0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm8.eps}
+        \caption{$\lambda=10^2$}
+    \end{subfigure}
+    }
+    \centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm9.eps}
+        \caption{$\lambda=10^3$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm10.eps}
+        \caption{$\lambda=10^4$}
+    \end{subfigure}
+    }
+    \caption{Epanechnikov kernel regression, with bandwidth $\lambda$, fitted on the variance-mean data from \texttt{Mar16}.}
+    \label{fig:meanvar_epanechnikov}
+\end{figure}
+
+Choosing a good bandwidth can be done using cross validation methods \citep{friedman2001elements} but this can be computationally expensive thus time consuming.
+By eyeballing the figure and choosing a bandwidth which captures a smooth variance-mean relationship, a value of $\lambda=10^3$ was chosen.
+
+\section{Model Selection}
+
+In the previous section, several models for the variance-mean relationship have been described.
+This section will use model selection techniques to access the goodness of fit and prediction performance for each model.
+
+\subsection{Deviance}
+The deviance is one way to assess the goodness of fit of the regression on the variance-mean data. The deviance is defined to be
+\begin{equation}
+    D = 2\left(
+        \ln L_s - \ln L    
+    \right)
+\end{equation}
+where $L$ and $L_s$ are the likelihood and saturated likelihood respectively.
+
+Let $\alpha=(n-1)/2$ be the shape parameter.
+Suppose the variance-mean data consist of the following values $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$ and $\widehat{y}_i$ is the predicted $Y$ given $x_i$, then the log likelihood is
+\begin{equation}
+    \ln L = \sum_{i=1}^m \left[
+        \alpha\ln\alpha
+        -\alpha\ln \widehat{y_i}
+        -\ln\Gamma(\alpha)
+        +(\alpha-1)\ln y_i
+        -\frac{\alpha y_i}{\widehat{y}_i}
+    \right]
+    \ .
+\end{equation}
+The log saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ so that
+\begin{equation}
+    \ln L_s = \sum_{i=1}^m \left[
+        \alpha\ln\alpha
+        -\alpha\ln{y_i}
+        -\ln\Gamma(\alpha)
+        +(\alpha-1)\ln y_i
+        -\alpha
+    \right]
+    \ .
+\end{equation}
+Following from this, the deviance is then
+\begin{equation}
+    D = 2\alpha
+    \sum_{i=1}^m\left[
+        \dfrac{
+            y_i-\widehat{y}_i
+        }
+        {
+            \widehat{y}_i
+        }
+        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
+    \right]
+    \ .
+\end{equation}
+The scaled deviance can be obtained by removing the factor of $\alpha$ to get
+\begin{equation}
+    D^* = 2
+    \sum_{i=1}^m\left[
+        \dfrac{
+            y_i-\widehat{y}_i
+        }
+        {
+            \widehat{y}_i
+        }
+        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
+    \right]
+    \ .
+\end{equation}
+It is given that $D\sim\chi_{m-2}^2$ which implies that $\expectation\left[D\right]=m-2$.
+Because the GLMs considered here all have 2 parameters with known $\alpha$, the best model is the model with the lowest scaled deviance.
+
+The analysis on the deviance was conducted by fitting GLMs with different link functions and polynomial orders $p$ onto the variance-mean data using all $n=100$ images from \texttt{Mar16}.
+The deviance was then calculated.
+This procedure was done using multiple bootstrap samples \citep{efron1992bootstrap} of the $m$ images to get a sample of scaled deviance.
+
+The resulting 100 bootstrapped scaled deviance are shown in Figure \ref{fig:meanvar_deviance_mar16}.
+The scaled deviance does not vary much from model to model and suggests that the goodness of fit are all very similar.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{../figures/meanVar/GlmDeviance_Mar16_scaled_deviance.eps}
+    \caption{Scaled deviance when fitting Gamma GLM on the variance-mean data from \texttt{Mar16}.}
+    \label{fig:meanvar_deviance_mar16}
+\end{figure}
+
+In this particular example, $m\approx 2\times 10^6$ and $n=100$. Then one would expect the scaled deviance to have values
+\begin{align*}
+    \expectation\left[D^*\right]&=\frac{1}{\alpha}\expectation\left[D\right]
+    \\
+    &=\frac{2}{n-1}\times (m-2)
+    \\
+    &\approx \frac{2}{100}\times 2\times 10^6
+    \\
+    &\approx 4 \times 10^4
+\end{align*}
+which is similar in magnitude obtained from the bootstrap samples.
+
+\subsection{Cross Validation}
+
+\subsection{Shading Correction}
+
+\section{Conclusion}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
 \end{figure}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm2.eps}
-        \caption{Inverse link, $x^{-1}$ feature}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm3.eps}
-        \caption{Inverse link, $x^{-2}$ feature}
-    \end{subfigure}
-    }
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm4.eps}
-        \caption{Log link, $x$ feature}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm5.eps}
-        \caption{Log link, $x^{-1}$ feature}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Mar16}.
-Fitted are Gamma GLM with different link functions and explanatory variables.
-Error bars represent the $\Phi(\pm1)$ quantile.}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_training_MSE.eps}
@@
 	\centering
-    \includegraphics[width=0.49\textwidth]{../figures/meanVar/GlmDeviance_Mar16_scaled_deviance.eps}
-    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Mar16}.}
-\end{figure}
-
-\begin{figure}
-	\centering
     \centerline{

### 2018-02-28 reports/thesis/book.tex
MeanVar chapter in thesis rushed.

@@
 The resulting 100 bootstrapped scaled deviance are shown in Figure \ref{fig:meanvar_deviance_mar16}.
+The kernel regression was also included.
 The scaled deviance does not vary much from model to model and suggests that the goodness of fit are all very similar.
@@
 
-In this particular example, $m\approx 2\times 10^6$ and $n=100$. Then one would expect the scaled deviance to have values
+In this particular example, $m\approx 1.3\times 10^6$ and $n=100$. Then one would expect the scaled deviance to have values
 \begin{align*}
@@
     \\
-    &\approx \frac{2}{100}\times 2\times 10^6
-    \\
-    &\approx 4 \times 10^4
+    &\approx \frac{2}{100-1}\times (1.3\times 10^6-2)
+    \\
+    &\approx 2.6 \times 10^4
 \end{align*}
-which is similar in magnitude obtained from the bootstrap samples.
+which is similar in magnitude but lower compared to the scaled deviances obtained from the bootstrap samples.
+This suggests the shape parameter $\alpha=(n-1)/2$ is too big and perhaps should be smaller.
+The estimation of the shape parameter here is however not too important as it is not used to further calculations.
 
@@
 
-\subsection{Shading Correction}
-
-\section{Conclusion}
+Another way to do model selection is cross validation \cite{friedman2001elements}.
+In the \texttt{Mar16} dataset, the 100 images were spilt into 2 equally sized sets called the training set and the test set.
+This produced 2 variance-mean data, one from each set.
+The regression was fitted onto the training set and the training set only.
+
+Prediction using the fitted regression can be accessed.
+This was done by calculating the mean squared error of the prediction of the training set, known as the training error, or the test set, known as the test error.
+
+20 samples of training and test errors were obtained by repeating the analysis using another random allocation of the training and test set.
+The results are shown in Figure \ref{fig:meanvar_mar16mse}.
+Each of the regressions considered all have similar prediction ability with the exception of GLM with log link and $p=1$ which performed significantly worse.
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_training_MSE.eps}
+        \caption{Training error}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_test_MSE.eps}
+        \caption{Test error}
+    \end{subfigure}
+    }
+    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Mar16}.}
+    \label{fig:meanvar_mar16mse}
 \end{figure}
 
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
-\end{figure}
+\subsection{Shading Correction}
+
+%\begin{figure}
+%	\centering
+%    \centerline{
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
+%        \caption{30 deg}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
+%        \caption{120 deg}
+%    \end{subfigure}
+%    }
+%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%    \centerline{
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
+%        \caption{30 deg}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
+%        \caption{120 deg}
+%    \end{subfigure}
+%    }
+%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
+%\end{figure}
+
+It was investigated how shading correction affects the variance-mean relationship.
+Figure \ref{fig:meanvar_shadingcorrection_july16_30deg} shows the sample variance-mean for the \texttt{July16 30deg} data with different types of shading correction applied.
+At a quick glance, it appeared the shading correction did not do much to the sample variance-mean data.
+However a closer look at low means showed that shading correction had a particular effect and formed a tighter cluster in the bottom-left of the variance-mean histogram.
+This implied that shading correction made more dark pixels have similar grey values.
 
@@
 Error bars represent the $\Phi(\pm1)$ quantile.}
+    \label{fig:meanvar_shadingcorrection_july16_30deg}
 \end{figure}
+
+In this section, the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} were considered.
+These are the only datasets with black, grey and white images which are used in shading correction.
+
+A regression was fitted using all images in each dataset to get the sample variance-mean data.
+The scaled deviance was calculated and repeated using bootstrapped samples of the images to get 100 samples of the scaled deviance.
+These are shown in Figures \ref{fig:meanvar_deviance_july16} and \ref{fig:meanvar_deviance_sep16} for the datasets \texttt{July16} and \texttt{Sep16} respectively.
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Mar16}.}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_30deg_scaled_deviance.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_120deg_scaled_deviance.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{July16}.}
+    \label{fig:meanvar_deviance_july16}
 \end{figure}
@@
     \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_30deg_scaled_deviance.eps}
+        \caption{30 deg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_120deg_scaled_deviance.eps}
+        \caption{120 deg}
+    \end{subfigure}
+    }
+    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Sep16}.}
+    \label{fig:meanvar_deviance_sep16}
+\end{figure}
+
+The scaled deviance did not vary much from model to model and shading correction to another.
+However there was one notable exception in \texttt{July16 120deg} where it appeared the scaled deviance preferred the log link with $p=-2$.
+Figure \ref{fig:meanvar_july16_glm} shows how the curvature of the log link captured the sample variance-mean data.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm1.eps}
+        \caption{Identity link, $p=1$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm3.eps}
+        \caption{Log link, $p=-2$}
+    \end{subfigure}
+    }
+    \caption{Log frequency density graph of the sample variance-mean data from the \texttt{July16 120deg} dataset.}
+    \label{fig:meanvar_july16_glm}
+\end{figure}
+
+Worryingly there appeared to be a significant change in the scaled deviance at different angles in the \texttt{July 16} dataset. This is unexplained.
+
+Another analysis was done by holding out half of the images and assigned it as the test set.
+The remaining images were assigned to be the training set and was used to train different types of regressions.
+The training and test MSE are shown in Figures \ref{fig:meanvar_mse_july16_30deg}, \ref{fig:meanvar_mse_july16_120deg}, \ref{fig:meanvar_mse_sep16_30deg} \& \ref{fig:meanvar_mse_sep16_120deg} for the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} respectively.
+
+What is remarkable is how much shading correction improved the training and test MSE, in particular in the \texttt{Sep16} dataset.
+
+\begin{figure}
+\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_training_MSE.eps}
@@
     \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 30deg}.}
+    \label{fig:meanvar_mse_july16_30deg}
 \end{figure}
@@
     \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 120deg}.}
+    \label{fig:meanvar_mse_july16_120deg}
 \end{figure}
@@
     \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 30deg}.}
+    \label{fig:meanvar_mse_sep16_30deg}
 \end{figure}
@@
     \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 120deg}.}
+    \label{fig:meanvar_mse_sep16_120deg}
 \end{figure}
 
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_30deg_scaled_deviance.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_120deg_scaled_deviance.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{July16}.}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_30deg_scaled_deviance.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_120deg_scaled_deviance.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Sep16}.}
-\end{figure}
+\section{Conclusion}
+Experimentally it was found that a Gamma GLM with identity link and $p=1$ performed just as well with other GLM with different link functions and non-parametric regressions.
+A Gamma GLM with identity link and $p=1$ is essentially a simple linear regression.
+The simple linear regression is attractive as the linear relationship between the variance and mean is backed up by the compound Poisson model of x-ray photon behaviour.
+The simple linear regression is also a good candidate for the variance-mean model to those who prefer simpler models and follows Occam’s razor.
+
+It was also found that shading correction aid in variance prediction. This highlights the important of shading correction and should be applied to images whenever possible.
 

### 2018-03-16 reports/thesis/book.tex
Started on inference section.

@@
 
+The aim of this project is to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist}.
+\texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample.
+Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.
+
+Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect.
+However in the previous chapters, it was found that x-ray photons behave randomly and large differences in the comparison can be due to chance.
+Thus the comparisons should be done under the face of uncertainty.
+
+A pixel by pixel inference was proposed to do defect detection. A statistic $z_{i,j}$ for the $(i,j)$ positioned pixel can be calculated for all pixels. This statistic is
+\begin{equation}
+    z_{i,j} = 
+    \dfrac{
+        \text{scan}_{i,j} - \text{aRTist}_{i,j}
+    }
+    {
+        \sqrt{\widehat{\variance}\left[\text{scan}_{i,j}\right]}
+    }
+\end{equation}
+where $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is the estimated grey value variance of pixel $(i,j)$ in the scan.
+Under mild assumptions, it was shown in the previous chapters that the grey values in the scan are Normal.
+Thus by treating the simulated image from \texttt{aRTist} as known, then
+\begin{equation}
+z_{i,j}\sim \normal(0,1) \ .
+\end{equation}
+This means the randomness of the $z_{i,j}$ statistics can be quantified.
+
+The estimation of the grey value variance given the grey value, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ will be explained here.
+The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample.
+These replicated x-ray scans provide variance-mean data which then can be used to train the variance model, such as a Gamma distributed GLM.
+The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
+
+This method can be applied to the dataset \texttt{Sep16 120deg}. The 20 x-ray images were spilt into 3. 10 images were used to train the variance-mean model,
+
 \bibliographystyle{apalike}

### 2018-03-19 reports/thesis/book.tex
Added intro to inference chapter.

@@
 
-The estimation of the grey value variance given the grey value, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ will be explained here.
+The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ will be explained here.
 The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample.
@@
 The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
-
-This method can be applied to the dataset \texttt{Sep16 120deg}. The 20 x-ray images were spilt into 3. 10 images were used to train the variance-mean model,
+The variance was then predicted using the grey value in the \texttt{aRTist} simulation.
+
+This method for inference can be applied to the dataset \texttt{Sep16 120deg}.
+The 20 x-ray images were spilt into 2.
+19 images were used to train the variance-mean model.
+One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_scan_aRTist}.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/scan.eps}
+        \caption{X-ray image}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/aRTist.eps}
+        \caption{\texttt{aRTist} simulation}
+    \end{subfigure}
+    }
+    \caption{An x-ray scan of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset. This can be compared directly to the \texttt{aRTist} simulation for defects.}
+    \label{fig:inference_scan_aRTist}
+\end{figure}
+
+For each pixel, a $z_{i,j}$ statistic was calculated.
+A $z_{i,j}$ statistic too large in magnitude can be considered to be evidence of a positive result.
+Another way to represent the $z_{i,j}$ statistic is the $p$-value which is given as
+\begin{equation}
+    p_{i,j} = 2(1-\Phi(\|z_{i,j}\|))
+\end{equation}
+which can takes values $0\leqslant p_{i,j} \leqslant 1$.
+A $p$-value too small is considered to be evidence of a positive result.
+The result $z$ statistics and $p$-values are shown in Figure \ref{fig:logp_z}.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/logp.eps}
+        \caption{$-\log p\text{-values}$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/z_image.eps}
+        \caption{$z$ statistics}
+    \end{subfigure}
+    }
+    \caption{The resulting z statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
+    \label{fig:logp_z}
+\end{figure}
+
+The resulting $z$ statistics and $p$-values are concerning.
+This is because the $p$-values are not very smooth on the surfaces of the sample.
+It should be expected that small $p$-values are in areas of the defects.
+Significant pixels were chosen for $\|z\|>\input{../figures/inference/z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level.
+The significant pixels are shown in Figure \ref{fig:sig_pixels}.
+
+This proposed method for defect detection failed because too many false positives were detected.
+These false positives appear to have some structure, for example clustering in the corners or on surfaces.
+In addition, false negatives were detected because not all of the defects were detected.
+
+Model misspecification appears to be the main source of error.
+The $z$ statistics can be inspected using a histogram, as shown in Figure \ref{fig:z_histo}.
+The histogram of the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect.
+However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{../figures/inference/sig_pixels.eps}
+    \caption{Signficiant pixels highlighted at the $z_\alpha = 2$ significance level.}
+    \label{fig:sig_pixels}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{../figures/inference/z_histo.eps}
+    \caption{Histogram of the $z$ statistics}
+    \label{fig:z_histo}
+\end{figure}
+
+This chapter will cover hypothesis testing, for a single test and then for multiple tests.
+The empirical null will then be reviewed which then can be extended to an image filter, called the empirical null filter.
+This filter will adjust each $z$ statistic according to its neighbours, ironing out false positive results.
+Simulations and actual results will be shown at the end of the chapter.
 

### 2018-03-19 reports/thesis/book.tex
Added hypothesis testing section.

@@
 
+\section{Hypothesis Testing}
+
+Hypothesis testing dates back to \cite{pearson1900on}, \cite{neyman1933on} and \cite{fisher1970statistical}. It is so fundamental in science that it is now taught in schools.
+
+The focus on this section is on the single hypothesis test.
+Here the random variable $Z\sim\normal(\mu,1)$ will be studied here as this is of interest in this project.
+It also appears in other tests such as the difference in sample means.
+
+In the context of this project, an example of hypothesis testing will be given here. Here, it was assumed that $Z\sim\normal(0,1)$. A null hypothesis can be written down to describe this
+\begin{equation}
+    H_0:\mu=0 \ .
+\end{equation}
+It specifies the assumptions made on the random variable $Z$. Any data behaving as assumed is treated as a negative result.
+
+A positive result is obtained when unlikely data is obtained and this happens if $Z$ deviates too much from 0. This can be described as testing $H_0$ against an alternative hypothesis $H_1$ where
+\begin{equation}
+    H_1:\mu\neq0 \ .
+\end{equation}
+How much $Z$ deviates from 0 to be considered a positive is up to the user but typically $\|Z\|>z_\alpha$ where $z_\alpha =2$ is considered significant.
+
+A way to quantify the threshold for a positive result is to use something called the size of the test, otherwise known as the significance level, denoted as $\alpha$.
+This is the probability of a false positive result, which can be denoted as
+\begin{equation}
+    \prob(\|Z\|>z_\alpha|H_0) = \alpha \ .
+\end{equation}
+Using the fact the Normal distribution is symmetric then
+\begin{equation}
+    2(1 - \Phi(z_\alpha)) = \alpha \ .
+    \label{eq:inference_single_alpha}
+\end{equation}
+The choice of $z_\alpha=2$ will set the size of the test to be $\alpha\approx 4.55\%$. This sort of choice of threshold and size is sensible.
+
+The $p$-value is a way to represent an observation of the data $Z=z$. Similar to the size, the $p$-value is
+\begin{equation}
+    p=2(1-\Phi(\|z\|)) \ .
+\end{equation}
+As a result, the $p$-value can be compared directly to the size of the test. That is there is a positive result if $p<\alpha$, otherwise it is a negative result.
+
+The power of the test is defined as the probability of a true positive result. For unknown $\mu$, it is useful to investigate the power for a range of $\mu$.
+
+\section{Multiple Hypothesis Testing}
+
+\section{Empirical Null}
+
+\section{Empirical Null Filter}
+
+\section{Results}
+
 \bibliographystyle{apalike}

### 2018-03-20 reports/thesis/book.tex
Moved chapters to tex files.

--- 2018-03-16 reports/thesis/book.tex
@@
 \chapter{Literature Review}
-
-3D printing, formally additive manufacturing \citep{gibson2010additive} \citep{wong2012review}, has recently become state of the art technology which manufactures objects of complicated shapes with very high precision.
-It was developed in the 1980's \citep{kodama1981automatic} but recently it has been commercialised and is used in medical science \citep{kang20163d} and engineering \citep{wong2012review}.
-Because of such a wide range of applications, there has been a need for quality control and this can be done by scanning the 3D printed sample using x-ray computed tomography.
-
-\section{X-ray Imaging}
-
-\subsection{X-Ray Production}
-Photons in CT scanning are produced in an X-ray tube.
-In an X-ray tube, a cathode, consisting of a heated filament, fires projectile electrons through an electric potential to a target which forms the anode \citep{michael2001x}, as shown in Figure \ref{fig:x_ray_tube}.
-Most of the kinetic energy of the projectile electrons is converted into heat however some is converted into electromagnetic radiation.
-This depends on how the projectile electrons interact with the atoms in the anode \citep{cantatore2011introduction}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
-	\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \citep{michael2001x}}
-	\label{fig:x_ray_tube}
-\end{figure}
-
-Bremsstrahlung is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target.
-The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation.
-As a result, the photon energies in bremsstrahlung radiation is  a continuous spectrum and can range up to the maximum kinetic energy of the projectile electrons \citep{michael2001x}.
-
-Characteristic radiation is due to projectile electrons colliding with electrons in the target atom and ionizing them.
-This produce vacancies in the electron shell and emits photons when the electrons in the target atom drops down back to the ground state.
-The energy of the emitted radiation is monoenergetic and depends on the binding energy of the target's atoms \citep{michael2001x}.
-
-A typical energy spectrum of photons emitted from an X-ray tube is as shown in Figure \ref{fig:x_ray_spectrum}.
-The energy spectrum consist of both bremsstrahlung and characteristic radiation \citep{michael2001x}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{figures/x_ray_spectrum.png}
-	\caption{A typical energy spectrum of photons emitted from an X-ray tube.
-The continuous spectrum is the result of bremmsstrahlung.
-The peaks are the result of characteristic radiation.
-\citep{michael2001x}}
-	\label{fig:x_ray_spectrum}
-\end{figure}
-
-The voltage and current can be varied in the X-ray tube to produce different energy spectrums and rate of photon production.
-This can vary the results produced when collecting CT data \citep{cantatore2011introduction}.
-Another important factor is the focal spot size because smaller spot sizes produce sharper edges.
-Larger spot sizes produce unsharp results and this is know as the penumbra effect, as shown in Figure \ref{fig:x_ray_penumbra}.
-However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the X-ray tube.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=1\textwidth]{figures/x_ray_penumbra.png}
-	\caption{Larger focal spot sizes produces unsharp results. This is know as the penumbra effect. \emph{Source: F.~Welkenhuyzen et al.~(2009)\citep{welkenhuyzen2009industrial}}}
-	\label{fig:x_ray_penumbra}
-\end{figure}
-
-\subsection{Photon Interactions}
-Photons emitted by the X-ray tube are projected onto the sample and interacts with it in a number of ways \citep{cantatore2011introduction}.
-
-The sample can effectively absorb photons via the photoelectric effect or pair production \citep{cantatore2011introduction}.
-In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}.
-In pair production, the photons convert into electron-position pairs by interacting with the Coulomb field of the sample's atomic nucleus \citep{hubbell2006electron}.
-In addition to getting absorbed, photons can be scattered by the sample.
-This happens when photons collide inelastically with and transfers its energy to the sample's electrons.
-This process is known as Compton scattering \citep{compton1923quantum}.
-
-Suppose a mono-energetic X-ray pencil beam attenuating through an object with varying attenuation coefficient in position $\mu=\mu(x)$.
-The beam starts at $x=0$ and is detected at $x=L$, then the attenuation (decrease in X-ray intensity from $I_0$ to $I_1$) is given as \citep{cantatore2011introduction}
-\begin{equation}
-	I_1 = I_0\exp\left[\int_0^L-\mu(x)\diff x\right].\label{eq:beerLaw}
-\end{equation}
-By comparing the intensity before and after attenuation, the integral of the attenuation coefficient along the path of the X-ray can be calculated.
-Because of the discrete nature of pixels, the integral is usually replaced by a sum \citep{michael2001x}.
-
-However it was shown that the attenuation coefficient does depend on the energy of the photons \citep{elbakri2002statistical}.
-Thus $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}.
-In general low energy photons are more likely to be absorbed than high energy photons, this increases the average energy of the attenuated photons and can be a source of error in CT scanning.
-This is referred to beam hardening and can cause inaccuracies in Equation \eqref{eq:beerLaw} \citep{michael2001x}.
-This can be reduced by placing a thin sheet of filter to absorb low energy photons \citep{welkenhuyzen2009industrial} or by correcting it in the data analysis stage \citep{michael2001x}.
-
-\subsection{Detection}
-Most X-ray detectors are made up of a scintillator material \citep{greskovich1997ceramic} and photodiodes.
-Firstly the x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}.
-Lastly the visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}.
-Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected.
-The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.
-
-The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
-The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.
-The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image on a computer \citep{cierniak2011x}.
-
-\section{X-ray Computed Tomography}
-Computed tomography (CT) scanning is a 3D imaging technique.
-It does this by reconstructing the geometry of the sample through a series of 2D X-ray images of the sample.
-The sample rotates after each image taken \citep{cantatore2011introduction}.
-
-Figure \ref{fig:x_ray_ct} shows a diagram on how CT scanning works.
-A 2D image is taken by projecting X-ray photons onto the stationary sample.
-The photons are then scattered or absobred by the sample.
-Some of these photons are then detected by an X-ray detector on the other side of the sample, which produces an image.
-After an image has been taken, the object rotates and another image is taken.
-Finally after a number of images, a 3D reconstruction of the object can be estimated \citep{cantatore2011introduction}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\textwidth]{figures/x_ray_ct.png}
-	\caption{X-ray computed tomography reconstructs the sample by projecting photons onto a rotating sample.
-The photons are then detected by the detector.
-\emph{Source: \url{http://www.phoenix-xray.com/}}}
-	\label{fig:x_ray_ct}
-\end{figure}
-
-CT was solved theoretically by \cite{cormack1973reconstruction} and implemented by \cite{hounsfield1973computerized} \citep{hounsfield1980computed}.
-It was mainly used for medical imaging.
-The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}.
-Recently CT has been used industrially for non-destructive testing in manufacturing \citep{cantatore2011introduction}.
-One possible application would be inspecting 3D printed samples \citep{villarraga2015assessing}.
-Other uses in science include the investigation of batteries \citep{o2017investigating} and materials \citep{wang2017x} \citep{zhang2016x}.
-
-Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
-There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.
-
-Studies have been done to use x-ray CT to do defection detection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}.
-This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}.
-Voids then can be classified as defects if the voids are larger than some volume threshold.
-This threshold controls the probability of the detection of defects \citep{amrhein2014characterization} \citep{gandossi2010probability}.
-
-Full 3D x-ray CT scans can be slow and may not generalised well in production lines.
-However there is potential to bring in methods such as those used in airport luggage inspection to speed up to process \citep{warnett2016towards}.
-
-There are many sources of error in CT scanning \citep{cantatore2011introduction} and this can cause problems when reconstructing the geometry of the sample.
-Sources of error include: dead pixels in the detector \citep{brettschneider2014spatial}, use of cone beams \citep{sun2016applications}, beam hardening and the orientation of the sample \citep{corcoran2016observations}.
-
-The scale of the 2D images can be calibrated with the use of reference standards \citep{bartscher2007enhancement} \citep{lifton2013application}.
-
-\section{Compound Poisson}
-
-The greyvalues of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector.
-When the photons interact with the scintillator, they are converted into visible light.
-The visible light photons are then detected and converted into a greyvalue.
-How the detected visible light is converted is important in modelling the greyvalue.
-
-Should the greyvalue be proportional to the number of photons detected, the detector is known as a quantum counter and the greyvalue is a Poisson random variable, up to a constant \citep{whiting2006properties}.
-However if the greyvalue records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector.
-The greyvalue has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}.
-There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
-
-Many reconstruction algorithms have been proposed considering the compound Poisson nature of the detector \citep{elbakri2002statistical} \citep{elbakri2003statistical} \citep{lasio2007statistical} \citep{xie2008x} and with beam hardening correction \citep{elbakri2003efficient}.
-These will not be discussed here as they are beyond the scope of this thesis.
-
-Experiments have been done to verify the compound Poisson nature of the detector.
-This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers.
-It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
-The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.
-
-The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
-\begin{equation*}
-	Y\sim\poisson(\lambda)
-\end{equation*}
-that is
-\begin{equation*}
-	\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\dotdotdot
-\end{equation*}
-where $\lambda>0$ is the Poisson rate parameter.
-Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$.
-Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
-\begin{equation}
-	X|Y = \sum_{i=1}^{Y}U_i+\kappa
-	\label{eq:compoundPoisson_X|Y}
-\end{equation}
-where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
-\begin{equation*}
-	p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0
-	\ .
-\end{equation*}
-However it should be noted that $X=0$ if and only if $Y=0$ with probability
-\begin{equation*}
-	\prob(X=0)=\euler^{-\lambda} \ .
-\end{equation*}
-Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
-\begin{equation}
-	p_X(x) = 
-	\begin{cases}
-		\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
-		\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
-	\end{cases}
-\end{equation}
-where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.
-
-The m.g.f.~of $X$ has a nicer form however. Let the m.g.f.~of $X$ be
-\begin{equation*}
-	M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
-	\ .
-\end{equation*}
-This can be computed using the result for conditional expectations
-\begin{equation*}
-	M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]
-	\ .
-\end{equation*}
-Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
-\begin{equation*}
-	M_X(\theta)=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
-\end{equation*}
-\begin{equation*}
-	M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
-	\ .
-\end{equation*}
-But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.
-\begin{equation*}
-	M_U(\theta)=\expectation\left[\euler^{U\theta}\right]
-	\ ,
-\end{equation*}
-then
-\begin{equation*}
-	M_X(\theta)=\expectation\left(
-		\expectation\left[\euler^{\theta U_1}|Y\right]\cdot
-		\expectation\left[\euler^{\theta U_2}|Y\right]\cdot
-		\dotdotdot \cdot
-		\expectation\left[\euler^{\theta U_Y}|Y\right]
-	\right)
-\end{equation*}
-\begin{equation*}
-	M_X(\theta)=\expectation\left[\left(M_U(\theta)\right)^Y\right]
-\end{equation*}
-\begin{equation*}
-	M_X(\theta)=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
-\end{equation*}
-\begin{equation*}
-	M_X(\theta) = M_Y\left(\ln(M_U(\theta)\right)
-\end{equation*}
-where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
-\begin{equation}
-	M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
-	\exp
-	\left[
-		\lambda
-		\left(
-		  \euler^\theta-1
-		\right)
-	\right]
-\end{equation}
-then
-\begin{equation}
-	M_X(\theta)=
-	\exp\left[
-		\lambda
-		\left(
-			M_U(\theta)-1
-		\right)
-	\right]
-	\ .
-\end{equation}
-As long as the m.g.f.~of $U$ is known, then m.g.f.~of $X$ can be written in closed form.
-
-Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
-\begin{align*}
-	M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
-	M_X'(\theta)&=M_X(\theta)\lambda M_U'(\theta)
-\end{align*}
-then
-\begin{equation}
-	\expectation\left[X\right]=\lambda\expectation\left[U\right]
-	\ .
-\end{equation}
-Conducting the same procedure
-\begin{equation*}
-	M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
-	\ ,
-\end{equation*}
-the variance can be obtained
-\begin{equation*}
-	\variance\left[X\right]=M_X''(0)-\left[M_X'(0)\right]^2
-\end{equation*}
-\begin{equation*}
-	\variance\left[X\right]=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
-\end{equation*}
-\begin{equation*}
-	\variance\left[X\right]=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
-\end{equation*}
-resulting in
-\begin{equation}
-	\variance\left[X\right] = \lambda\expectation\left[U^2\right]
-	\ .
-\end{equation}
-This can be extended for higher moments.
-
-Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$.
-By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.
-
-If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
-\begin{equation}
-	U\sim\gammaDist\left(\alpha,\beta\right)
-\end{equation}
-where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
-\begin{equation}
-	X\sim\CPoisson(\lambda,\alpha,\beta)
-	\ .
-\end{equation}
-The conditional distribution can be shown to be
-\begin{equation}
-	X|Y\sim\gammaDist\left(Y\alpha,\beta\right)
-	\ .
-\end{equation}
-
-Using results derived earlier, the m.g.f.~of the of $X$ is
-\begin{equation}
-	M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
-\end{equation}
-and moments can be obtained from it such as
-\begin{equation}
-	\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
-\end{equation}
-\begin{equation}
-	\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
-	\label{eq:compoundPoisson_variance}
-\end{equation}
-and
-\begin{equation}
-	\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
-	\ .
-\end{equation}
-
-The p.d.f.~can be shown to be
-\begin{equation}
-	p_X(x) = 
-	\begin{cases}
-		\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
-		\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
-	\end{cases}
-	\label{eq:compoundPoisson_pdf}
-\end{equation}
-and it is well known the infinite sum cannot be written in closed form.
-There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
-Of course direct simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated.
-The p.d.f.~then can be estimated using these simulated samples.
-
-For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, parameter estimation can be difficult.
-Maximum likelihood estimation is very complicated \citep{withers2011compound}.
-It can be made simpler by fixing $\alpha$ to be known \citep{withers2011compound} but this is not useful in this context.
-
-Because the moments of a compound Poisson-Gamma random variable can be obtained easily, method of moments estimators can be obtained.
-Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
-Then the estimators
-\begin{equation}
-	\widehat{\lambda}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
-\end{equation}
-\begin{equation}
-	\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
-\end{equation}
-\begin{equation}
-	\widehat{\beta}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
-\end{equation}
-are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}.
-These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
-
-However, parameter estimation can be made easier once it can be realised that the compound Poisson-Gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}.
-To show this, it is particular useful to reparametrize the compound Poisson-Gamma distribution using the following:
-\begin{equation}
-	p=\frac{2+\alpha}{1+\alpha}
-	\ ,
-\end{equation}
-\begin{equation}
-	\mu=\frac{\lambda\alpha}{\beta}
-	\ ,
-\end{equation}
-\begin{equation}
-	\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
-	\ .
-\end{equation}
-The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. It can be shown that $1<p<2$, $\mu>0$ and $\phi>0$.
-
-By rearranging the parameters to get
-\begin{equation}
-	\lambda=\frac{\mu^{2-p}}{\phi(2-p)}
-\end{equation}
-\begin{equation}
-	\alpha=\frac{2-p}{p-1}
-\end{equation}
-\begin{equation}
-	beta=\frac{1}{\phi(p-1)\mu^{p-1}}
-\end{equation}
-and substituting it into Equation \eqref{eq:compoundPoisson_pdf}, the p.m.f.~at zero can be shown to be
-\begin{equation}
-	\prob(X=0) = \exp
-	\left[
-	    -\frac{\mu^{2-p}}{\phi(2-p)}
-	\right]
-\end{equation}
-and the p.d.f.~for $x>0$ is
-\begin{multline*}
-	p_X(x) = \sum_{y=1}^{\infty}
-	\left[
-		\frac{1}{\phi(p-1)\mu^{p-1}}
-	\right]^{y\alpha}
-	\frac{1}{\Gamma(y\alpha)}
-	x^{y\alpha-1}
-	\exp\left[
-	    -\frac{x}{\phi(p-1)\mu^{p-1}}
-	\right]
-	\\
-	\exp\left[
-	    -\frac{\mu^{2-p}}{\phi(2-p)}
-	\right]
-	\left[
-		\frac{\mu^{2-p}}{\phi(2-p)}
-	\right]^y
-	\frac{1}{y!}
-	\ .
-\end{multline*}
-Tidying up the equation
-\begin{multline*}
-	p_X(x) = 
-	\exp\left[
-		\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)
-	\right]
-	\frac{1}{x}
-	\\
-	\sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-	\ .
-\end{multline*}
-To simplify further, it should be noted that
-\begin{align*}
-	2-p-\alpha(p-1) &= 2-p - \frac{2-p}{p-1}(p-1)
-	\\&=0
-\end{align*}
-so that
-\begin{equation}
-	p_X(x) = 
-	\exp\left[
-		\frac{1}{\phi}
-		\left(
-			x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
-		\right)
-	\right]
-	\frac{1}{x}
-	\sum_{y=1}^{\infty}W_y(x,p,\phi)
-\end{equation}
-where
-\begin{equation}
-	W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-	\ .
-\end{equation}
-
-Those familiar with generalised linear models \citep{nelder1972generalized} \citep{mccullagh1984generalized} will notice that for fixed $p$ or $\alpha$, the above is in the form of a distribution in the dispersive exponential family.
-Parameter estimation then can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
-These has applications in for example insurance claim data \citep{jorgensen1994fitting} \citep{smyth2002fitting}.
-
-Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
-One easy way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
-
-One special property of the compound Poisson-Gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}. It has a special variance mean relationship
-\begin{equation}
-	\variance[X] = \phi \mu^p
-\end{equation}
-where, as a reminder, $1<p<2$. This can be derived using Equation \eqref{eq:compoundPoisson_variance} or via the partition function $Z$. That is let
-\begin{equation}
-	\theta = \frac{\mu^{1-p}}{1-p}
-\end{equation}
-and
-\begin{equation}
-	\ln Z = \frac{1}{\phi(2-p)\theta^\alpha(1-p)^\alpha} \ ,
-\end{equation}
-then
-\begin{equation}
-	\variance[X] = \phi^2 \frac{\partial^2\ln Z}{\partial\theta^2} \ .
-\end{equation}
+\input{chapters/1_literatureReview.tex}
 
@@
 \chapter{Compound Poisson}
-In this chapter, the compound Poisson-Gamma distribution is reviewed and studied.
-Firstly methods for evaluating the density of the compound Poisson-Gamma distribution are discussed.
-Approximations such as the Normal approximation or saddlepoint approximation \citep{daniels1954saddlepoint} can be used.
-These approximate densities can be written in closed form.
-Exact methods can be computationally challenging when dealing with the infinite sum but can be done when summing over important terms \citep{dunn2005series}.
-Next, a method for parameter estimation will be proposed here using the EM algorithm \citep{dempster1977maximum}.
-However in the end of the chapter, it will be shown that no unique maximum likelihood estimator exist when certain parameters of the compound Poisson-Gamma distribution gets too large.
-
-\section{Density Evaluation}
-Suppose $X\sim\CPoisson(\lambda,\alpha,\beta)$ and $\lambda,\alpha,\beta>0$ then the p.d.f.~of $X$ is
-\begin{equation}
-	p_X(x) = 
-	\begin{cases}
-		\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
-		\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y & \text{ for } x>0 
-	\end{cases}
-\end{equation}
-where
-\begin{equation}
-	W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
-	\ .
-	\label{eq:compoundPoisson_w}
-\end{equation}
-The evaluation of this p.d.f.~is difficult because the sum of $W_y$ cannot be simplified. However the m.g.f.~of $X$ can be written down in closed form
-\begin{equation}
-	M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
-	\ .
-\end{equation}
-The m.g.f.~allows the study of limiting distributions of the compound Poisson-Gamma distribution.
-These limiting distributions then can be used to approximate the p.d.f.~of a compound Poisson-Gamma random variable.
-
-The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation  of the m.g.f.~giving the p.d.f.
-However inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}.
-The saddlepoint approximation will be studied here.
-
-Lastly the infinite sum can be computationally summed in a clever way.
-This was done by summing only large terms in the sum and ignores small terms.
-By using Stirling's approximation, the largest term in the sum can be approximately found \citep{dunn2005series}.
-
-\subsection{Normal Approxmation}
-The m.g.f.~provides a starting point to what limiting distributions the compound Poisson-Gamma distribution converges to for large parameters.
-However the m.g.f.~of $X$ itself it not useful because when considering $\lambda\rightarrow\infty$ or $\alpha\rightarrow\infty$ then $M_X(\theta)\rightarrow\infty$.
-Also for $\beta\rightarrow\infty$, then $M_X(\theta)\rightarrow 1$ which is not useful either.
-
-The compound Poisson-Gamma random variable $X$ should be standardised to obtain useful limiting results from the m.g.f. Let
-\begin{equation}
-	Z = \frac{X-\expectation[X]}{\sqrt{\variance[X]}}
-	\ ,
-\end{equation}
-then using previous results
-\begin{equation*}
-	Z = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
-	\left(
-		X-\frac{\alpha\lambda}{\beta}
-	\right)
-\end{equation*}
-\begin{equation}
-	Z = bX+a
-\end{equation}
-where
-\begin{equation}
-	b = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
-\end{equation}
-and
-\begin{equation}
-	a = -\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-	\ .
-\end{equation}
-
-The m.g.f.~of $Z$ is then
-\begin{equation*}
-	M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=\expectation\left[\euler^{(bX+a)\theta}\right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=\euler^{a\theta}M_X(b\theta)
-	\ .
-\end{equation*}
-Substituting in the values
-\begin{equation*}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\lambda
-		\left(
-			\left(
-				\frac{\beta}{\beta-\frac{\beta\theta}{\sqrt{\alpha(\alpha+1)\lambda}}}
-			\right)^\alpha
-			-1
-		\right)
-	\right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\lambda
-		\left(
-			\left(
-				\frac{\sqrt{\alpha(\alpha+1)\lambda}}{\sqrt{\alpha(\alpha+1)\lambda}-\theta}
-			\right)^\alpha
-			-1
-		\right)
-	\right]
-\end{equation*}
-or in a different form
-\begin{equation}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\lambda
-		\left(
-			\left(
-				1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}	
-			\right)^{-\alpha}
-			-1
-		\right)
-	\right]
-	\ .
-\end{equation}
-
-The above form is useful so that the binomial expansion can be conducted, that is
-\begin{multline}
-	\left(
-		1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}
-	\right)^{-\alpha}
-	=
-	1+
-	\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
-	\\
-	\text{for }\frac{\|\theta\|}{\sqrt{\alpha(\alpha+1)\lambda}}<1 \ .
-\end{multline}
-Substituting in the binomial expansion
-\begin{equation*}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\lambda
-		\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
-	\right]
-	\ .
-\end{equation*}
-Writing in full the $r=1,2$ terms
-\begin{multline*}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-		+\frac{\theta^2}{2}
-	\right.
-	\\
-	\left.
-		+\lambda\sum_{r=3}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
-	\right]
-\end{multline*}
-and a term cancels out to get
-\begin{equation}
-	M_Z(\theta)=
-	\exp\left[
-		\frac{\theta^2}{2}
-		+\sum_{r=3}^\infty
-		\frac
-			{\theta^r\prod_{s=1}^r(\alpha+s-1)}
-			{(\alpha(\alpha+1))^{r/2}r!}
-		\lambda^{1-r/2}
-	\right]
-	\ .
-\end{equation}
-
-For large $\lambda$
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}M_Z(\theta)=\exp\left[\frac{\theta^2}{2}\right]
-\end{equation}
-which is the same as the m.g.f.~of a standard Normal variable, therefore
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1) \ .
-\end{equation}
-This should make sense as for high $\lambda$, the Poisson random variable has a high expectation, increasing the number of Gamma random variables in a summation.
-Increasing the number of terms in a summation will trigger the central limit theorem.
-
-Next for high $\alpha$, it should be noted that
-\begin{equation*}
-	\lim_{\alpha\rightarrow\infty}
-	\frac{
-		\prod_{s=1}^r(\alpha+s-1)
-	}
-	{
-		\alpha(\alpha+1))^{r/2}
-	}
-	=
-	\frac{
-		\prod_{s=1}^r\alpha
-	}
-	{
-		\alpha^{r}
-	}
-\end{equation*}
-so that
-\begin{equation}
-	\lim_{\alpha\rightarrow\infty}
-	\frac{
-		\prod_{s=1}^r(\alpha+s-1)
-	}
-	{
-		(\alpha(\alpha+1))^{r/2}
-	}
-	= 1
-	\ .
-\end{equation}
-As a result
-\begin{equation}
-	\lim_{\alpha\rightarrow\infty}
-	M_Z(\theta)=
-	\exp\left[
-		\frac{\theta^2}{2}
-		+\sum_{r=3}^\infty
-		\frac{\theta^r}{r!}
-		\lambda^{1-r/2}
-	\right]
-	\ .
-\end{equation}
-However this shows that taking the limit $\alpha\rightarrow\infty$ is not enough to get a Normal limiting distribution.
-For a Normal limiting distribution, the limit must be accompanied with the limit $\lambda\rightarrow\infty$, that is
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}\lim_{\alpha\rightarrow\infty}Z\sim\normal(0,1)
-	\ .
-\end{equation}
-
-Finally it should be noted that $M_Z(\theta)$ is independent of $\beta$. Thus $\beta$ will have no effect on the convergence to a Normal limiting distribution.
-
-The above results justify the use of the approximation
-\begin{equation}
-	X\sim\normal\left(\frac{\lambda\alpha}{\beta},\frac{\lambda\alpha(\alpha+1)}{\beta^2}\right)
-\end{equation}
-for large $\lambda$. The limiting case where $\lambda\rightarrow 0$, $\alpha\rightarrow 0$ and $\beta\rightarrow 0$ will not be discussed here.
-
-\subsection{Normal Approximation - General Case}
-It was shown in certain situations, the compound Poisson-Gamma distribution can be approximated with the Normal distribution. This can be extended to the general compound Poisson.
-
-Let $Y\sim\poisson(\lambda)$ where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be some random variable for i.i.d.~$i=1,2,3,\dotdotdot$ with m.g.f.~$M_U(\theta)$. Let
-\begin{equation}
-	X|Y = \sum_{i=1}^{Y}U_i
-	\ .
-\end{equation}
-
-It can be shown that the m.g.f.~of $X$ is
-\begin{equation}
-	M_X(\theta)=
-	\exp\left[
-		\lambda(M_U(\theta)-1)
-	\right]
-	\ .
-\end{equation}
-As in the compound Poisson-Gamma case, it is useful to standardise $X$ using
-\begin{equation*}
-	Z = \frac{X-\lambda\expectation[U]}{\sqrt{\lambda\expectation[U^2]}}
-\end{equation*}
-\begin{equation}
-	Z = \frac{X}{\sqrt{\lambda\expectation[U^2]}}
-	-\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-	\ .
-\end{equation}
-The m.g.f.~of $Z$ is then
-\begin{equation*}
-	M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=
-	\exp\left[
-	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-	\right]
-	\exp\left[
-	\lambda
-	\left(
-		M_U
-		\left(
-			\frac{\theta}{\sqrt{\lambda\expectation[U^2]}}\right)-1
-		\right)
-	\right]
-\end{equation*}
-
-Taking the Maclaurin series of $M_U(\theta)$
-\begin{equation}
-	M_U(\theta) = 1 + \sum_{r=1}^\infty\frac{\theta^r}{r!}M_U^{(r)}(0)
-	\quad\text{for }\lim_{r\rightarrow\infty}
-	\left\|
-		\frac{\theta}{r+1}\frac{M_U^{(r+1)}(0)}{M_U^{(r)}(0)}
-	\right\|<1
-\end{equation}
-and substituting it into $M_Z(\theta)$
-\begin{equation*}
-	M_Z(\theta)=
-	\exp\left[
-	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-    \right]
-	\exp\left[
-		\lambda\sum_{r=1}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
-	\right]
-	\ .
-\end{equation*}
-Writing out in full the $r=1,2$ terms
-\begin{multline*}
-	M_Z(\theta)=\exp\left[
-	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-	\right]
-	\exp\left[
-		\theta\frac{\sqrt{\lambda}M_U'(0)}{\sqrt{\expectation[U^2]}}
-		+
-		\frac{\theta^2M_U''(0)}{2\expectation[U^2]}
-	\right.
-	\\+
-	\left.
-		\lambda\sum_{r=3}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
-	\right]
-	\ .
-\end{multline*}
-By using the fact that $\expectation[U^r]=M_U^{(r)}(0)$ for $r=0,1,2\dotdotdot$, a few terms cancel out to get
-\begin{equation}
-	M_Z(\theta)=
-	\exp\left[
-		\frac{\theta^2}{2}
-		+
-		\sum_{r=3}^\infty\frac{\theta^r \expectation[U^r]}{(\expectation[U^2])^{r/2}r!}\lambda^{1-r/2}
-	\right]
-	\ .
-\end{equation}
-
-For the limit $\lambda\rightarrow\infty$
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}M_Z(\theta) = \exp\left[\frac{\theta^2}{2}\right]
-\end{equation}
-then it can be concluded that
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1)
-	\ .
-\end{equation}
-The convergence can be aided if the ratio $\dfrac{\expectation[U^r]}{(\expectation[U^2])^{r/2}}$ for $r=3,4,5,\dotdotdot$ are small.
-
-\subsection{Saddlepoint approximation}
-The m.g.f.~of a random variable $X$ is defined to be
-\begin{equation}
-	M_X(\theta)=\expectation[\euler^{\theta X}]
-	=
-	\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x
-	\ .
-\end{equation}
-For a given m.g.f., the saddlepoint approximation \citep{daniels1954saddlepoint} \citep{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
-\begin{equation}
-	p_X(x)\approx\left(2\pi K_X''(s)\right)^{-1/2}\exp\left[K_X(s)-sx\right]
-	\label{eq:saddlePoint:generalSaddlePoint}
-\end{equation}
-where $K_X(\theta) = \ln\left(M_X(\theta)\right)$, and $s=s(x)$ is the solution to the saddle point equation $K_X'(s)=x$.
-
-For the compound Poisson-Gamma distribution, the saddle point approximation is given as 
-\begin{multline}
-	p_X(x)\approx
-	\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
-	\euler^{-x\beta}
-	\exp\left[x^{\frac{\alpha}{\alpha+1}}
-		\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
-	\right]
-	\\
-	\text{for }x>0 \ .
-	\label{eq:saddle_point_approx}
-\end{multline}
-It appears the approximation is not well defined for $x=0$.
-
-The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary.
-Thus it may be more sensible to write the approximation up to a constant
-\begin{equation}
-	p_X(x)\propto x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
-	\exp\left[
-		x^{\frac{\alpha}{\alpha+1}}
-		\frac{
-			(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)
-		}
-		{
-			\alpha^{\frac{\alpha}{\alpha+1}}
-		}
-	\right]
-	\ .
-\end{equation}
-
-For the remainder of this section, it will be shown how the saddlepoint approximation can be algebraically derived.
-First of all the cumulant generating function $K_X(\theta)$ can be obtained from the m.g.f.
-\begin{equation}
-	K_X(\theta) = \lambda
-	\left[
-		\left(\frac{\beta}{\beta-\theta}\right)^\alpha-1
-	\right]
-	\ .
-\end{equation}
-Taking the derivative with respect to $\theta$
-\begin{equation}
-	K_X'(\theta)=\frac{\lambda\alpha\beta^\alpha}{(\beta-\theta)^{\alpha+1}}
-\end{equation}
-and this is known as the saddlepoint equation. The quantity $s=s(x)$ is the solution to the equation $K_X'(s)=x$, that is
-\begin{equation*}
-	\frac{\lambda\alpha\beta^\alpha}{(\beta-s)^{\alpha+1}} = x
-\end{equation*}
-with solution
-\begin{equation}
-	s = \beta - \left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
-	\ .
-\end{equation}
-
-The second derivative of the cumulant generating function is
-\begin{equation}
-	K_X''(\theta)=\frac{\lambda\alpha(\alpha+1)\beta^\alpha}{(\beta-\theta)^{\alpha+2}} \ .
-\end{equation}
-Substituting this and $K_X(\theta)$ into Equation \eqref{eq:saddlePoint:generalSaddlePoint}
-\begin{equation*}
-	p_X(x)\approx
-	\frac{1}{\sqrt{2\pi}}
-	\left[
-		\frac{
-			(\beta-s)^{\alpha+2}
-		}
-		{
-			\lambda\alpha(\alpha+1)\beta^\alpha
-		}
-	\right]^{1/2}
-	\exp\left[
-		\lambda\left(\left(\frac{\beta}{\beta-s}\right)^\alpha-1\right)-sx
-	\right]
-	\ .
-\end{equation*}
-Substituting in $s=s(x)$
-\begin{multline*}
-	p_X(x)\approx
-	\frac{1}{\sqrt{2\pi}}
-	\left[
-		\frac{\left(\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}\right)^{\alpha+2}}{\lambda\alpha(\alpha+1)\beta^\alpha}
-	\right]^{1/2}
-	\\
-	\exp\left[
-		\lambda
-		\left(
-			\left(
-				\frac{\beta}{\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}}
-			\right)^\alpha
-			-1
-		\right)
-		-x\left(
-			\beta-\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
-		\right)
-	\right]
-\end{multline*}
-simplifying further
-\begin{multline*}
-	p_X(x)\approx
-	\frac{1}{\sqrt{2\pi}}
-	\left[
-		\frac{
-			\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{\alpha+2}{\alpha+1}}
-		}
-		{
-			\lambda\alpha(\alpha+1)\beta^\alpha
-		}
-	\right]^{1/2}
-	\\
-	\exp\left[
-		\lambda
-		\left(
-			\beta^\alpha
-			\left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
-			-1
-		\right)
-		-x\beta
-		+(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{1-\frac{1}{\alpha+1}}
-	\right]
-\end{multline*}
-\begin{multline*}
-	p_X(x)\approx
-	\frac{1}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
-	\left(\lambda\alpha\beta^\alpha\right)^{\left(\frac{\alpha+2}{\alpha+1}-1\right)/2}
-	\\
-	\exp\left[
-		\lambda\left(
-			\beta^\alpha
-			\left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
-			-1
-		\right)
-		-x\beta
-		+(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{\frac{\alpha}{\alpha+1}}
-	\right]
-\end{multline*}
-\begin{multline*}
-	p_X(x)\approx
-	\frac{
-		\left(
-			\lambda\alpha\beta^\alpha
-		\right)^{\frac{1}{2(\alpha+1)}}
-	}
-	{
-		\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
-	}	
-	\\
-	\exp\left[
-		-\lambda
-		-x\beta
-		+x^{\frac{\alpha}{\alpha+1}}
-		\left(
-			\frac{
-				\lambda\beta^\alpha
-			}
-			{
-				\left(\lambda\alpha\beta^\alpha\right)^{\frac{\alpha}{\alpha+1}}
-			}
-			+
-			\left(
-				\lambda\alpha\beta^\alpha
-			\right)^{\frac{1}{\alpha+1}}
-		\right)
-	\right]
-\end{multline*}
-\begin{multline*}
-	p_X(x)\approx
-	\frac{
-		\left(
-			\lambda\alpha\beta^\alpha
-		\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-	}
-	{
-		\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
-	}
-	\euler^{-x\beta}
-	\\
-	\exp\left[
-		x^{\frac{\alpha}{\alpha+1}}
-		\left(
-			(\lambda\beta^\alpha)^{1-\frac{\alpha}{\alpha+1}}\alpha^{-\frac{\alpha}{\alpha+1}}
-			+
-			\left(
-				\lambda\alpha\beta^\alpha
-			\right)^{\frac{1}{\alpha+1}}
-		\right)
-	\right]
-\end{multline*}
-\begin{multline*}
-	p_X(x)\approx
-	\frac{
-		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-	}
-	{
-		\sqrt{2\pi(\alpha+1)}
-	}
-	x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
-	\\
-	\exp\left[
-		x^{\frac{\alpha}{\alpha+1}}
-		\left(
-			(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
-			\alpha^{-\frac{\alpha}{\alpha+1}}
-			+
-			\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
-		\right)
-	\right]
-\end{multline*}
-\begin{multline*}
-	p_X(x)\approx
-	\frac{
-		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-	}
-	{
-		\sqrt{2\pi(\alpha+1)}
-	}
-	x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
-	\\
-	\exp\left[
-		x^{\frac{\alpha}{\alpha+1}}(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
-		\left(
-			\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
-		\right)
-	\right]
-	\ .
-\end{multline*}
-
-The expression $\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}$ can be simplified by putting the two terms over a common denominator
-\begin{align}
-	\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
-	& = \alpha^{\frac{1}{\alpha+1}}+\frac{1}{\alpha^{\frac{\alpha}{\alpha+1}}}
-	\nonumber\\
-	& = \frac{\alpha^{\frac{1}{\alpha+1}}\alpha^{\frac{\alpha}{\alpha+1}}+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
-	\nonumber\\
-	& = \frac{\alpha+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
-\end{align}
-so that
-\begin{equation*}
-p_X(x)\approx
-	\frac{
-		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-	}
-	{
-		\sqrt{2\pi(\alpha+1)}
-	}
-	x^{-\frac{\alpha+2}{2(\alpha+1)}}
-	\euler^{-x\beta}
-	\exp\left[
-		x^{\frac{\alpha}{\alpha+1}}
-		\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
-	\right]
-	\ .
-\end{equation*}
-
-\subsection{Series Evaluation}
-Evaluation of the p.d.f.~of the compound Poisson-Gamma distribution is difficult because of the infinite sum
-\begin{equation}
-p_X(x) = 
-	\delta(x) \euler^{-\lambda}
-	+
-	\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y
-	\quad\text{for }x\geqslant 0
-\end{equation}
-where
-\begin{equation}
-	W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
-	\ .
-	\label{eq:compoundPoisson_Wy}
-\end{equation}
-$W_y$ can be expressed in a different way using different parameters
-\begin{equation}
-	W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-\end{equation}
-where
-\begin{equation}
-	p=\frac{2+\alpha}{1+\alpha}
-\end{equation}
-and
-\begin{equation}
-	\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}} \ .
-\end{equation}
-
-\cite{dunn2005series} approximated the sum by truncation
-\begin{equation}
-	\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y
-\end{equation}
-where $y_\text{l}<y_{\text{max}}<y_\text{u}$ and $y_{\text{max}}$ is the value of $y$ which maximises $W_y$.
-\cite{dunn2005series} used Stirling's approximation to find $y_{\text{max}}$.
-This was done by treating $W_y$ as a continuous function of $y$ and is differentiable with respect to $y$.
-
-It is easier to differentiate $\ln(W_y)$ where
-\begin{multline*}
-	\ln(W_y) = y\alpha\ln(x)-y(1+\alpha)\ln(\phi)-y\alpha\ln(p-1)\\-y\ln(2-p)-\ln(y!)-\ln\Gamma(y\alpha)
-\end{multline*}
-\begin{equation}
-	\ln(W_y) =
-	y
-	\ln\left(
-		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-	\right)
-	-\ln(y!)-\ln\Gamma(y\alpha)
-	\ .
-\end{equation}
-Using Stirling's approximation
-\begin{equation}
-	\ln(n!)\approx\ln\Gamma(n)\approx n\ln(n!)-n
-\end{equation}
-then
-\begin{equation}
-	\ln(W_y) \approx
-	y\ln\left(
-		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-	\right)
-	-y\ln(y)+y-y\alpha\ln(y\alpha) + y\alpha
-	\ .
-\end{equation}
-Taking the derivative with respect to $y$
-\begin{multline*}
-	\frac{\partial \ln(W_y)}{\partial y} \approx
-	\ln\left(
-		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-	\right)
-	-\ln(y)-1+1
-	\\
-	-\alpha\ln(y\alpha)-\alpha+\alpha
-\end{multline*}
-\begin{equation}
-	\frac{\partial \ln(W_y)}{\partial y} \approx
-	\ln\left(
-		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-	\right)
-	-\ln(y)
-	-\alpha\ln(y\alpha)
-	\ .
-\end{equation}
-
-Setting the derivative to zero
-\begin{equation*}
-	0 \approx \ln\left(
-		\frac{
-			x^\alpha
-		}
-		{
-			\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha
-		}
-	\right)
-\end{equation*}
-\begin{equation*}
-	1 \approx 
-	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha}
-\end{equation*}
-\begin{equation*}
-	y_{\text{max}}^{1+\alpha} \approx 
-	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)\alpha^\alpha}
-\end{equation*}
-\begin{equation*}
-	y_{\text{max}} \approx 
-	\frac{1}{\phi}
-	\left(
-		\frac{x}{(p-1)\alpha}
-	\right)^{\frac{\alpha}{1+\alpha}}
-	(2-p)^{\frac{-1}{1+\alpha}}
-	\ .
-\end{equation*}
-This can be simplified using the fact that 
-\begin{equation*}
-	\alpha=\frac{2-p}{p-1}
-	\ ,
-\end{equation*}
-\begin{equation*}
-	\frac{1}{1+\alpha} = p-1
-\end{equation*}
-and
-\begin{equation*}
-	\frac{\alpha}{1+\alpha} = 2-p
-\end{equation*}
-then
-\begin{equation*}
-	y_{\text{max}} \approx 
-	\frac{1}{\phi}
-	\left(
-		\frac{x}{2-p}
-	\right)^{2-p}
-	(2-p)^{1-p}
-\end{equation*}
-and finally
-\begin{equation}
-	y_{\text{max}} \approx \frac{x^{2-p}}{\phi(2-p)}
-	\ .
-\end{equation}
-Because values of $y$ should be a positive integer, it would be appropriate to round the solution to $y_\text{max}$ accordingly
-\begin{equation}
-	y_{\text{max}} = \text{max}\left[
-		1,\text{round}\left(\frac{x^{2-p}}{\phi(2-p)}\right)
-	\right]
-	\ .
-\end{equation}
-
-To verify that $y_\text{max}$ is a maximum, the second derivative can be investigated
-\begin{equation}
-	\frac{\partial^2\ln(W_y)}{\partial y^2}
-	\approx
-	-\frac{1}{y}(\alpha+1)
-\end{equation}
-to see that
-\begin{equation}
-	\frac{\partial^2\ln(W_y)}{\partial y^2} < 0 \quad \text{for }y=1,2,3,\dotdotdot
-\end{equation}
-therefore $y_\text{max}$ is a maximum.
-
-Returning back to the truncation of the infinite sum
-\begin{equation}
-	\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y
-	\ ,
-\end{equation}
-$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}.
-To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} and using the following equation
-\begin{equation}
-	\ln\left[
-		\sum_{y=y_\text{l}}^{y_\text{u}}W_y
-	\right]
-	= 
-	\ln\left(
-		W_{y_\text{max}}
-	\right)
-	+\ln\sum_{y=y_\text{l}}^{y_\text{u}}
-	\exp\left[
-		\ln\left(W_y\right)-\ln\left(W_{y_\text{max}}\right)
-	\right]
-	\ .
-\end{equation}
-
-\subsection{Simulation Studies}
-
-Simulations of a compound Poisson-Gamma random variable were conducted with the aim to compare how well these density evaluations methods perform.
-This was done by comparing the evaluated densities with the histogram of simulations and a Q-Q plot.
-The following compound Poisson-Gamma distributions were used in the simulations to capture the variety in the compound Poisson-Gamma family: $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(100,100,1)$.
-
-A few technical details will be stated here.
-The Normal approximation does not support probability mass at $x=0$, but instead has a support of $-\infty<x<\infty$.
-The Normal approximation with $-\infty<x<\infty$ support was used here.
-
-Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$. The saddlepoint approximation was computed up to a constant using
-\begin{equation}
-	p_X(x) \propto
-	\exp\left[
-		-\frac{\alpha+2}{2(\alpha+1)}
-		\ln(x)
-		-x\beta
-		+\left(
-		\frac{x\beta}{\alpha}
-		\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1) - k
-	\right]
-\end{equation}
-for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant to control over/underflow and it was chosen to be
-\begin{equation}
-	k =
-	\max_{i\in\left\{1,2,3,\dotdotdot,n\right\}}
-	\left[
-		-\frac{\alpha+2}{2(\alpha+1)}
-		\ln(x_i)
-		-x_i\beta
-		+\left(
-			\frac{x_i\beta}{\alpha}
-		\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
-	\right]
-	\ .
-\end{equation}
-The density was then was normalised by numerically integrating it using the trapezium rule using the 500 evaluated points.
-
-A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Let
-\begin{equation}
-	F_X(x) = \prob(X\leqslant x)
-\end{equation}
-\begin{equation}
-	\widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}
-	\left[
-		\left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
-	\right]
-	\ ,
-\end{equation}
-then a Q-Q plot plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$.
-If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin.
-However there is no closed form for $F_X(x)$.
-When using the exact or saddlepoint method, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums.
-$\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
-For the saddlepoint approximation where $x=0$ cannot be evaluated and their exist a zero value in the sample, the lower limit of the numerical integral was chosen, arbitrary, to be
-\begin{equation}
-	\frac{
-		\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)
-	}
-	{
-		\euler^{-\lambda}(1+\lambda)
-	}
-	\times 0.1
-	\ .
-\end{equation}
-
-For low $\lambda$ (Figures \ref{fig:cp_simulation_1} and \ref{fig:cp_simulation_3}) there is a chance of simulating zeros.
-The Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric.
-The saddlepoint approximation did capture probability mass at zero as shown by an increase in probability density towards zero.
-However in Figure \ref{fig:cp_simulation_3}, the compound Poisson-Gamma distribution looked like a mixture model and the saddlepoint approximation was not flexible enough to capture each individual peak.
-In addition, the Q-Q plots looked quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~at low densities.
-
-As $\lambda$ increased, all 3 density evaluation methods performed quite well.
-In Figure \ref{fig:cp_simulation_2}, the Normal approximation did not quite capture the skewness of the histogram.
-However in Figure \ref{fig:cp_simulation_4} for the Normal looking compound Poisson-Gamma random variable, all methods performed well.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist1.png}
-        \caption{Histogram - Exact method}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq1.png}
-        \caption{Q-Q plot - Exact method}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist1.png}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq1.png}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist1.png}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq1.png}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{Simulations of $\CPoisson(1,1,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_1}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist2.png}
-        \caption{Histogram - Exact method}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq2.png}
-        \caption{Q-Q plot - Exact method}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist2.png}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq2.png}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist2.png}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq2.png}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{Simulations of $\CPoisson(10,1,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_2}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist3.png}
-        \caption{Histogram - Exact method}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq3.png}
-        \caption{Q-Q plot - Exact method}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist3.png}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq3.png}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist3.png}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq3.png}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{Simulations of $\CPoisson(1,100,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_3}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist4.png}
-        \caption{Histogram - Exact method}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq4.png}
-        \caption{Q-Q plot - Exact method}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist4.png}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq4.png}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist4.png}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq4.png}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{Simulations of $\CPoisson(100,100,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_4}
-\end{figure}
-
-\section{EM Algorithm}
-
-The EM algorithm \citep{dempster1977maximum} will be proposed here as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$.
-
-A popular method for parameter estimation is the maximum log likelihood method.
-Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively.
-The log likelihood is defined to be
-\begin{equation*}
-	\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
-	\left[
-		\mathbb{I}(x_i=0)\ln \prob(X=x_i)
-		+\mathbb{I}(x_i>0)\ln p_X(x_i)
-	\right]
-\end{equation*}
-\begin{multline}
-	\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
-	\left[
-		-\mathbb{I}(x_i=0)\lambda
-		\vphantom{\sum_i^i}
-	\right.
-	\\
-	\left.
-		+\mathbb{I}(x_i>0)\left(
-		-1-\beta x_i-\lambda-\ln x -\ln\sum_{y=1}^\infty W_y
-		\right)
-	\right]
-\end{multline}
-where $W_y=W_y(\lambda,\alpha,\beta)$ was defined in Equation \eqref{eq:compoundPoisson_w}.
-$\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
-The gradient of the log likelihood can be evaluated \citep{dunn2005series} and optimisation can be done using gradient methods.
-
-The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable.
-Let $\left\{Y_1,Y_2,Y_3,\dotdotdot, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\dotdotdot, x_n\right\}$ be measurements of $X|Y$.
-Define the joint log likelihood to be
-\begin{multline*}
-	\ln L(\lambda,\alpha,\beta;X,Y)
-	=
-	\sum_{i=1}^n
-	\left[
-		\mathbb{I}(x_i=0)
-		\ln
-		\prob(Y=0)
-	\right.
-	\\
-	\left.
-		+
-		\mathbb{I}(x_i>0)
-		\ln
-		\left[
-			p_{X|Y}(x_i|Y_i)\prob(Y=Y_i)
-		\right]
-	\right]
-\end{multline*}
-so that
-\begin{multline}
-	\ln L(\lambda,\alpha,\beta;X,Y)=
-	\sum_{i=1}^n
-	\left[
-		-\mathbb{I}(x_i=0)
-		\lambda
-	\right.
-	\\
-	\left.+
-		\mathbb{I}(x_i>0)
-		\left(
-			Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
-		\right.
-	\right.
-	\\
-	\left.
-		\left.	
-			- \lambda + Y_i \ln \lambda - \ln(Y_i!)
-		\right)
-	\right]
-	\ .
-\end{multline}
-The estimators are found by optimising the joint log likelihood.
-This is done iteratively by estimating the $Y$s given the $X$s and parameters (E step), followed by estimating the parameters given the $Y$s and $X$s (M step) until some convergence conditions are met.
-
-It will be shown that using some approximations, the E step and M step can be implemented.
-The Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} can also be found by using a few approximations.
-However simulations show that these estimators struggle for high $\lambda$ and it will be shown that this will be the case for all estimators.
-
-\subsection{E Step}
-
-In the E step, the realizations of $Y$ are estimate using
-\begin{equation}
-	y_i =
-	\expectation\left[
-		Y|X=x_i
-	\right]
-\end{equation}
-for given parameters $\lambda$, $\alpha$ and $\beta$. The conditional expectation is calculated using
-\begin{equation}
-	y_i = 
-	\begin{cases}
-		0 & \text{ for } x=0 \\ 
-		\dfrac{\sum_{y=1}^\infty y \prob(Y=y|X=x_i)}{\sum_{y=1}^\infty \prob(Y=y|X=x_i)} & \text{ for } x>0
-	\end{cases}
-\end{equation}
-where
-\begin{equation*}
-	\prob(Y=y|X=x) = \frac{p_{X|Y}(x|y)\prob(Y=y)}{p_X(x)}
-	\ .
-\end{equation*}
-Focussing on the $x>0$ case for now
-\begin{equation*}
-	\prob(Y=y|X=x) = \frac{1}{p_X(x)}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\frac{\euler^{-\lambda}\lambda^y}{y!}
-\end{equation*}
-and
-\begin{equation}
-	\prob(Y=y|X=x) = W_y \frac{\euler^{-\lambda-\beta x}}{x}
-\end{equation}
-where $W_y$ is defined in Equation \eqref{eq:compoundPoisson_Wy}.
-Then the conditional expectation is
-\begin{equation}
-	y_i = \frac{\sum_{y=1}^\infty y W_y}{\sum_{y=1}^\infty W_y}
-	\ .
-\end{equation}
-It was already established how the denominator can be evaluated \citep{dunn2005series}. A similar method for evaluating the numerator can be obtained by truncating the sum and summing large terms.
-
-Let
-\begin{equation}
-	W_y^{(r)} = y^r W_y
-\end{equation}
-so that
-\begin{equation}
-	y_i = \frac{\sum_{y=1}^\infty W^{(1)}_y}{\sum_{y=1}^\infty W_y}
-\end{equation}
-and
-\begin{equation}
-	\variance[Y|X=x_i] = \frac{\sum_{y=1}^\infty W^{(2)}_y}{\sum_{y=1}^\infty W_y} - \left(y_i\right)^2
-	\ .
-\end{equation}
-The exponent $r=0,1,2,\dotdotdot$ will be useful in the M step where higher conditional moments are needed.
-The sum can be truncated
-\begin{equation}
-	\sum_{y=1}^\infty W^{(r)}_y \approx \sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y
-\end{equation}
-where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. By expressing $\ln(W^{(r)}_y)$ as
-\begin{equation}
-	\ln\left(W_y^{(r)}\right)=r\ln(y)+\ln(W_y)
-\end{equation}
-and then taking the derivative with respect to $y$
-\begin{equation}
-	\frac{\partial \ln(W_y^{(r)})}{\partial y} = \frac{r}{y } + \frac{\partial \ln(W_y)}{\partial y}
-	\ .
-\end{equation}
-Keep in mind that $y=1,2,3,\dotdotdot$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
-\begin{equation}
-	\frac{\partial \ln(W_y^{(r)})}{\partial y} \approx \frac{\partial \ln(W_y)}{\partial y}
-	\ .
-\end{equation}
-By using such an approximation, the method for evaluating the sum $\sum_{y=1}^\infty W^{(r)}_y$ is almost exactly the same as evaluating the sum $\sum_{y=1}^\infty W_y$, in particular $y_\text{max}$ are the same.
-For a given $r=0,1,2,\dotdotdot$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
-The limits will be different for different values of $r$.
-
-\subsection{M Step}
-
-In the M step, the conditional expected joint log likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is then
-\begin{multline*}
-	T(\lambda,\alpha,\beta)=
-	\sum_{i=1}^n
-	\expectation\left[
-		-\mathbb{I}(x_i=0)
-		\lambda
-	\right.
-	\\
-	\left.+
-		\mathbb{I}(x_i>0)
-		\left(
-			Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
-		\right.
-	\right.
-	\\
-	\left.
-		\left.	
-			- \lambda + Y_i \ln \lambda - \ln(Y_i!)
-		\right)
-		|X_i=x_i
-	\right]
-\end{multline*}
-\begin{multline*}
-	T(\lambda,\alpha,\beta)=
-	-n\lambda
-	\\
-	+\sum_{i=1}^n
-	\mathbb{I}(x_i>0)
-	\left[
-		\expectation[Y_i|X_i=x_i]\alpha\ln\beta-\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]
-	\right.
-	\\
-	\left.
-		+\expectation[Y_i|X_i=x_i]\alpha\ln x_i - \beta x_i
-		+ \expectation[Y_i|X_i=x_i] \ln \lambda
-	\right] + c
-\end{multline*}
-where $c$ is some constant not dependent on $\lambda$, $\alpha$ or $\beta$.
-
-The conditional expectation $y_i = \expectation[Y_i|X_i=x_i]$ was calculated in the E step. The quantity $\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]$ can be calculated using the approximation
-\begin{equation}
-	\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i] \approx
-	\ln\Gamma(\alpha y_i) + \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
-\end{equation}
-where
-\begin{equation}
-	\zeta_i = \variance[Y_i|X_i=x_i]
-\end{equation}
-calculated in the E step and $\psi$ is the digamma function. The objective function is then
-\begin{multline}
-	T(\lambda,\alpha,\beta)=
-	-n\lambda
-	+\sum_{i=1}^n
-	\mathbb{I}(x_i>0)
-	\left[
-		y_i\alpha\ln\beta-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
-	\right.
-	\\
-	\left.
-		+y_i\alpha\ln x_i - \beta x_i
-		+ y_i \ln \lambda
-		\vphantom{\frac{1}{1}}
-	\right]
-	+ c
-	\ .
-\end{multline}
-
-Taking the derivative with respect to $\lambda$
-\begin{equation}
-	\frac{\partial T}{\partial\lambda} = -n + \frac{\sum_{i=1}^ny_i}{\lambda}
-\end{equation}
-and setting it to zero
-\begin{equation}
-	\widehat{\lambda} = \frac{\sum_{i=1}^n y_i}{n}
-\end{equation}
-obtains a M step estimator, and a familiar one, for $\lambda$. Taking the second derivative with respect to $\lambda$
-\begin{equation}
-	\frac{\partial^2 T}{\partial \lambda^2} = -\frac{\sum_{i=1}^ny_i}{\lambda^2} < 0
-\end{equation}
-verifies $\widehat{\lambda}$ maximises T. In addition
-\begin{equation}
-	\frac{\partial^2 T}{\partial \alpha \partial \lambda } = 0
-\end{equation}
-and
-\begin{equation}
-	\frac{\partial^2 T}{\partial \beta \partial \lambda } = 0
-	\ .
-\end{equation}
-
-Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second order can be obtained. For the first order these are:
-\begin{multline}
-	\frac{\partial T}{\partial \alpha} =
-	\sum_{i=1}^n\mathbb{I}(x_i>0)
-	\left[
-		y_i\ln\beta -\psi(\alpha y_i)y_i-\zeta_i\alpha\psi'(\alpha y_i)
-		\vphantom{\frac{1}{1}}
-	\right.
-	\\
-	\left.
-		- \frac{1}{2}\zeta_i\alpha^2\psi''(\alpha y_i)y_i + y_i\ln x_i
-	\right]
-\end{multline}
-and
-\begin{equation}
-	\frac{\partial T}{\partial \beta} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
-	\frac{\alpha y_i}{\beta}-x_i
-	\right]
-	\ .
-\end{equation}
-The second orders are:
-\begin{equation}
-	\frac{\partial^2 T}{\partial \alpha \partial \beta} =
-	\sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right]
-	\ ,
-	\label{eq:compoundPoisson:d2tdadb}
-\end{equation}
-\begin{equation}
-	\frac{\partial^2 T}{\partial \beta^2} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[-\frac{\alpha y_i}{\beta^2}
-	\right]
-	\label{eq:compoundPoisson:d2td2b}
-\end{equation}
-and
-\begin{multline*}
-	\frac{\partial^2 T}{\partial \alpha^2} = 
-	\sum_{i=1}^n\mathbb{I}(x_i>0)
-	\left[
-		-y_i^2\psi'(\alpha y_i) - \zeta_i\psi'(\alpha y_i) - \zeta_i\alpha y_i\psi''(\alpha y_i)
-		\vphantom{\frac{1}{2}}\right.\\\left.	
-		- \zeta_i\alpha\psi''(\alpha y_i)y_i
-		-\frac{1}{2}\zeta_i\alpha^2\psi'''(\alpha y_i)y_i^2
-	\right]
-\end{multline*}
-simplifying to
-\begin{multline}
-	\frac{\partial^2 T}{\partial \alpha^2} = 
-	\sum_{i=1}^n\mathbb{I}(x_i>0)
-	\left[
-		-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
-		\vphantom{\frac{1}{2}}
-	\right.
-	\\
-	\left.	
-		-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
-	\right] \ .
-	\label{eq:compoundPoisson:d2td2a}
-\end{multline}
-
-All the derivatives can be used in the Newton-Raphson iterative update, which is
-\begin{equation}
-	\begin{pmatrix}
-		\alpha \\ \beta
-	\end{pmatrix}
-	\leftarrow
-	\begin{pmatrix}
-		\alpha \\ \beta
-	\end{pmatrix}
-	\left[
-		\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T
-	\right]^{-1}
-	\left[
-		\nabla_{\alpha,\beta} T
-	\right]
-\end{equation}
-where
-\begin{equation}
-	\nabla_{\alpha,\beta}=
-	\begin{pmatrix}
-		{\partial}/{\partial \alpha}
-		\\
-		{\partial}/{\partial \beta}
-	\end{pmatrix}
-	\ .
-\end{equation}
-Since increasing $T$ is sufficient for the EM algorithm \citep{dempster1977maximum}, one step of the Newton-Raphson iterative update was chosen in the M step to avoid implementing a convergence condition.
-
-\subsection{Estimation Error}
-
-The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} from the Fisher's information matrix defined as
-\begin{equation}
-	\matr{I} = -\expectation\left[
-		\nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
-	\right]
-	\ .
-\end{equation}
-The calculation is similar to the derivatives of $T$, so using the same approximations and the fact that $\expectation[Y]=\lambda$, then
-\begin{equation}
-	\matr{I}=
-	\begin{pmatrix}
-		\dfrac{n}{\lambda} & 0 & 0 \\
-		0 & (\lambda^2+\lambda)\psi'(\alpha\lambda)+2\alpha\lambda^2\psi''(\alpha\lambda)+\frac{1}{2}\alpha^2\lambda^3\psi'''(\alpha\lambda) & -\dfrac{n\lambda}{\beta}\\
-		0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
-	\end{pmatrix}
-	\ .
-\end{equation}
-The Cram\'er-Rao lower bound is then
-\begin{equation}
-	\cov\left[
-		\begin{pmatrix}
-			\widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
-		\end{pmatrix}
-	\right]
-	=
-	\matr{I}^{-1}
-	\ .
-\end{equation}
-
-\subsection{Simulations}
-
-An experiment was conducted to assess the performance on the EM algorithm.
-For a given set of parameters, 1\,000 samples of a $\CPoisson(\lambda,\alpha,\beta)$ random variable were simulated.
-The EM algorithm was initialised with its parameters at the true values to investigate the convergence in that vicinity.
-The log likelihood $\ln L(\lambda,\alpha,\beta;X)$ and the parameters were recorded at every EM step.
-The experiment was repeated 10 times using different simulated samples.
-
-The results for $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$ and $\CPoisson(100,100,1)$ are shown in Figures \ref{fig:compoundPoisson_convergence_1}, \ref{fig:compoundPoisson_convergence_2}, \ref{fig:compoundPoisson_convergence_3} and \ref{fig:compoundPoisson_convergence_4} respectively.
-Good performance can be seen for the $\lambda=1$ case with convergence of all 3 parameters within a step or two.
-The Cram\'er-Rao lower bound captured the spread of the estimates well.
-
-However for $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log likelihood.
-It appears the EM algorithm failed for $\lambda>10$ looking at these particular examples.
-
-\begin{figure}[p]
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lnL.eps}
-        \caption{Log likelihood}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lambda.eps}
-        \caption{$\lambda$}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_alpha.eps}
-        \caption{$\alpha$}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_beta.eps}
-        \caption{$\beta$}
-    \end{subfigure}
-    }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
-    \label{fig:compoundPoisson_convergence_1}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lnL.eps}
-        \caption{Log likelihood}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lambda.eps}
-        \caption{$\lambda$}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_alpha.eps}
-        \caption{$\alpha$}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_beta.eps}
-        \caption{$\beta$}
-    \end{subfigure}
-    }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
-    \label{fig:compoundPoisson_convergence_2}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lnL.eps}
-        \caption{Log likelihood}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lambda.eps}
-        \caption{$\lambda$}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_alpha.eps}
-        \caption{$\alpha$}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_beta.eps}
-        \caption{$\beta$}
-    \end{subfigure}
-    }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
-    \label{fig:compoundPoisson_convergence_3}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lnL.eps}
-        \caption{Log likelihood}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lambda.eps}
-        \caption{$\lambda$}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_alpha.eps}
-        \caption{$\alpha$}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_beta.eps}
-        \caption{$\beta$}
-    \end{subfigure}
-    }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
-    \label{fig:compoundPoisson_convergence_4}
-\end{figure}
-
-\subsection{Failure Evaluation}
-It should be convincing that the EM algorithm failed when the compound-Poisson Gamma random variable starts behaving Normally.
-In particular in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ are stable while estimates of $\alpha$ and $\beta$ struggled to converge.
-This could be because as the compound-Poisson Gamma random variable approach being Normal, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate and there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$.
-
-One way to see this is to look at the Newton-Raphson step, in the M step, in particular the Hessian matrix $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ for high $\lambda$.
-The elements of the Hessian matrix can be found in Equations \eqref{eq:compoundPoisson:d2tdadb}, \eqref{eq:compoundPoisson:d2td2b} and \eqref{eq:compoundPoisson:d2td2a}.
-The $\dfrac{\partial^2T}{\partial\alpha^2}$ element is
-\begin{multline*}
-	\frac{\partial^2 T}{\partial \alpha^2} = 
-	\sum_{i=1}^n\mathbb{I}(x_i>0)\left[
-		-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
-		\vphantom{\frac{1}{2}}
-	\right.
-	\\
-	\left.	
-		-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
-	\right]
-	\ .
-\end{multline*}
-For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$. Firstly using Stirling's approximation
-\begin{equation}
-	\ln\Gamma(n)\approx\ln(n!)\approx n\ln n-n
-\end{equation}
-then
-\begin{equation}
-	\psi(n) = \frac{\partial\ln\Gamma(n)}{\partial n} \approx \ln n
-	\ .
-\end{equation}
-Differentiating further
-\begin{align}
-	\psi'(n) &\approx 1/n \\
-	\psi''(n) & \approx -1/n^2 \\
-	\psi'''(n) & \approx 2/n^3
-	\ .
-\end{align}
-Using the approximations, $\dfrac{\partial^2T}{\partial\alpha^2}$ can be approximated
-\begin{equation*}
-	\frac{\partial^2 T}{\partial \alpha^2} \approx 
-	\sum_{i=1}^n\mathbb{I}(x_i>0)
-	\left[
-		-\frac{y_i^2+\zeta_i}{\alpha y_i} + 2\frac{\zeta_i\alpha y_i}{\alpha^2 y_i^2}
-		-\frac{1}{2}\frac{2\zeta_i\alpha^2y_i^2}{\alpha^3 y_i^3}
-	\right]
-\end{equation*}
-to get
-\begin{equation}
-	\frac{\partial^2 T}{\partial \alpha^2} \approx 
-	\sum_{i=1}^n\mathbb{I}(x_i>0)
-	\left[
-		-\frac{y_i}{\alpha}
-	\right]
-	\ .
-\end{equation}
-
-The Hessian matrix is then
-\begin{equation}
-	\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T \approx
-	\sum_{i=1}^n
-	\mathbb{I}(x_i>0)
-	\begin{pmatrix}
-		-y_i/\alpha  & y_i/\beta \\
-		y_i/\beta & -\alpha y_i/\beta^2
-	\end{pmatrix}
-	\ . 
-\end{equation}
-The determinant of the Hessian matrix is then
-\begin{equation*}
-	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
-	\approx
-	\left(\sum_{i=1}^n-\frac{\alpha y_i}{\beta^2}\right)
-	\left(\sum_{i=1}^n-\frac{y_i}{\alpha}\right) - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)^2
-\end{equation*}
-\begin{equation*}
-	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
-	\approx
-	\left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
-	 - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)\left(\sum_{j=1}^n\frac{y_j}{\beta}\right)
-\end{equation*}
-\begin{equation*}
-	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
-	\approx
-	\left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
-	 - \left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
-\end{equation*}
-to get
-\begin{equation}
-	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
-	\approx
-	0
-	\ .
-\end{equation}
-
-This results in a few things.
-Firstly $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ is singular thus its inverse cannot be evaluated, needed for the Newton-Raphson method.
-Secondly, the sufficient conditions to classify a stationary point as a maximum are that the diagonal elements of the Hessian matrix are negative and the determinate is positive.
-For high $\lambda$ and $\alpha$, the second condition is not met.
-
-Another argument which can be made is to restrict the parameter $\beta$ for a given mean to be
-\begin{equation}
-	\beta = \frac{\lambda\alpha}{\widehat{\mu}}
-	\label{eq:compoundPoisson:beta_restrict}
-\end{equation}
-where
-\begin{equation}
-	\widehat{\mu} = \frac{1}{n}\sum_{i=1}^n x_i
-\end{equation}
-and investigate whenever a unique solution to $\dfrac{\partial T}{\partial \alpha} = 0$ can be found for high $\lambda$ and $\alpha$. The constrained objective function is
-\begin{multline*}
-	T(\lambda,\alpha)
-	=
-	-n\lambda+
-	\sum_{i=1}^n
-	\mathbb{I}(x_i>0)
-	\left[
-	y_i\alpha
-	\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
-	\right.
-	\\
-	\left.
-		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
-		+ y_i \ln \lambda
-		\vphantom{\frac{1}{1}}
-	\right]
-	+ c
-\end{multline*}
-which can be approximated to
-\begin{multline*}
-	T(\lambda,\alpha)=
-	-n\lambda+
-	\sum_{i=1}^n
-	\mathbb{I}(x_i>0)
-	\left[
-		y_i\alpha\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\alpha y_i\ln(\alpha y_i) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
-	\right.
-	\\
-	\left.
-		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
-		+ y_i \ln \lambda
-		\vphantom{\frac{1}{1}}
-	\right]
-	+ c
-\end{multline*}
-\begin{multline*}
-	T(\lambda,\alpha)=
-	-n\lambda+
-	\sum_{i=1}^n
-	\mathbb{I}(x_i>0)
-	\left[
-		y_i\alpha\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
-	\right.
-	\\
-	\left.
-		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
-		+ y_i \ln \lambda
-		\vphantom{\frac{1}{1}}
-	\right]
-	+ c
-	\ .
-\end{multline*}
-Taking the derivative with respect to $\alpha$
-\begin{equation*}
-	\frac{\partial T}{\partial \alpha} =
-	\sum_{i=1}^n
-	\mathbb{I}(x_i>0)
-	\left[
-		y_i\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right)
-		+ y_i - \frac{1}{2}\frac{\zeta_i}{y_i}
-		+y_i\ln x_i - \frac{\lambda x_i}{\widehat{\mu}}
-		\vphantom{\frac{1}{1}}
-	\right]
-\end{equation*}
-and this is not $\alpha$ dependent, thus there is no solution to $\alpha$.
+\input{chapters/3_compoundPoisson.tex}
 
 \chapter{Variance Prediction}
-
-In the previous chapter, it was found that it is very hard to fit a compound Poisson random variable onto the grey values directly itself.
-It is not totally useless however.
-The compound Poisson model showed that the variance of the grey value has a linear relationship with the mean grey value.
-Given this, it would be possible to predict the variance of the grey value, given the grey value.
-This opens up new ways to predict the uncertainty of each individual pixel in an x-ray scan.
-
-In this chapter, different types of regressions were tested to see if they perform well in predicting grey value variance given the grey value.
-Two types of regressions were used.
-Generalised linear models \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized} (GLM) is a parametric regression which models the response variable as a random variable in the exponential family.
-In this project, a Gamma distributed random variable was chosen as the response variable.
-A non-parametric regression was also considered, here there kernel regression \citep{friedman2001elements} was used.
-
-Using the replicated x-ray images, the within individual pixel sample mean and sample variance were obtained.
-The sample variance-mean data were then used for the regressions to be fitted on.
-The deviance was investigated as a method of model selection.
-The regression was also used to test it's prediction performance on held out images.
-
-In the end, a GLM with a linear relationship between the variance and the mean was good enough.
-Its performance is similar to other complicated models and its simple form attracts those who follows Occam's razor, that the simpler models are usually better.
-The linear relationship is also justified by the compound Poisson model.
-
-\section{Variance-Mean Relationship}
-
-The sample variance-mean data were obtained from the replicated x-ray images, assuming each image are i.i.d.
-
-Let $x_{i,j}^{(r)}$ be the grey value of the pixel in the $i$th row and $j$th column in the $r$th image for $r=1,2,3,\dotdotdot,n$. The within individual pixel sample mean is
-\begin{equation}
-    \bar{x}_{i,j}=\frac{1}{n}\sum_{r=1}^n x_{i,j}^{(r)}
-\end{equation}
-and the within individual pixel sample variance is
-\begin{equation}
-    y_{i,j} =
-    \frac{1}{n-1}
-    \sum_{r=1}^n
-        \left(
-            x_{i,j}^{(r)} - \bar{x}_{i,j}
-        \right)^2
-    \ .
-\end{equation}
-
-Only the masked pixels will be considered here as this is the region of interest (ROI).
-The sample variance-mean data can be obtained by calculating the within individual pixel sample mean and variance for all ROI pixels and can be plotted as a histogram.
-For example, the sample variance-mean data for \texttt{Mar16} can be seen in Figure \ref{fig:meanvar_mar16_100}.
-
-\subsection{Generalised Linear Models}
-By making some assumptions, some useful and simple results can be obtained.
-Firstly, it was assumed the standard error from estimating the mean was negligible.
-Secondly, it was assumed for a given pixel, the grey value from each each were Normal i.i.d.
-Following from these assumptions, the sample variance is Gamma distributed with shape parameter $(n-1)/2$.
-Furthermore the standard error of the sample variance is proportional to $(n-1)^{-1/2}$, meaning the sample variance is more precise when more and more images were used to estimate the variance.
-This was experimentally shown in Figure \ref{fig:meanvar_mar16_differentn}, the spread of the sample variance decreased as $n$ increased.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_25.eps}
-        \caption{$n=25$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_50.eps}
-        \caption{$n=50$}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_75.eps}
-        \caption{$n=75$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_100.eps}
-        \caption{$n=100$}
-        \label{fig:meanvar_mar16_100}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Mar16} using $n$ of the images.
-Fitted is a Gamma GLM with identity link.
-Error bars represent the $\Phi(\pm1)$ quantile.}
-    \label{fig:meanvar_mar16_differentn}
-\end{figure}
-
-A GLM \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized}, with Gamma distributed response, would then be an appropriate regression to be used.
-Let $Y$ be the grey value sample variance and $X$ be the grey value, then a GLM models $Y$ via the following
-\begin{equation}
-    Y|X \sim 
-    \gammaDist\left(
-        \frac{n-1}{2},
-        f(X)
-    \right)
-\end{equation}
-where $f(X)$ is some user specified function.
-Conventionally it is useful for the specified function to be a parameter of the conditional mean $Y|X$.
-This function is known as the link function and can be expressed as
-\begin{equation}
-g(\mu_X) = \eta(X)
-\end{equation}
-where $\mu_X=\expectation\left[Y|X\right]$ and $\eta(X)$ is a linear function of $X$, for example
-\begin{equation}
-\eta(X) = \beta_0 + \beta_1 X^p \ .
-\end{equation}
-For a specified link function and $p$, the GLM is fitted onto the data by estimating the parameters $\beta_0$ and $\beta_1$.
-
-In this project, the identity, inverse and log link functions were investigated for a selected few integer values of $p$.
-These link functions are shown in Table \ref{table:meanvar_linkfunctions}.
-They are fitted on the variance-mean data from \texttt{Mar16} as shown in Figure \ref{fig:meanvar_mar16}.
-
-\begin{table}
-    \centering
-    \begin{tabular}{c|c|c|c}
-    &\multicolumn{3}{c}{Link functions}\\
-    &Identity&Inverse&Log\\
-    \hline
-    $g(\mu)$&$\mu$&$1/\mu$&$\ln(\mu)$\\
-    \hline
-    $\expectation[Y|X=x]$&$\beta_0 + \beta_1 x^p$&$\left[\beta_0 + \beta_1 x^p\right]^{-1}$&$\exp\left[\beta_0 + \beta_1 x^p\right]$
-    \end{tabular}
-    \caption{Link functions}
-    \label{table:meanvar_linkfunctions}
-\end{table}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm2.eps}
-        \caption{Inverse link, $p=-1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm3.eps}
-        \caption{Inverse link, $p=-2$}
-    \end{subfigure}
-    }
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm4.eps}
-        \caption{Log link, $p=1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm5.eps}
-        \caption{Log link, $p=-1$}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the variance-mean data from \texttt{Mar16}.
-Fitted are Gamma GLM with different link functions polynomial features.
-Error bars represent the $\Phi(\pm1)$ quantile.}
-    \label{fig:meanvar_mar16}
-\end{figure}
-
-\subsection{Kernel Regression}
-
-Kernel regression \citep{friedman2001elements} is a type of non-parametric regression and its prediction is done using a weighted sum of the data rather then fitting a parametric model.
-Suppose a collection of variance-mean data were collected $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$, then the kernel regression is
-\begin{equation}
-    \widehat{y}(x)=
-    \dfrac{
-        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right) y_i
-    }
-    {
-        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right)
-    }
-\end{equation}
-where $k(x)$ is a specified kernel function and $\lambda$ is called the bandwidth. Popular choices for the kernel include the Gaussian kernel \citep{friedman2001elements}
-\begin{equation}
-    k(x)=\phi(x)
-\end{equation}
-and the Epanechnikov kernel \citep{friedman2001elements}
-\begin{equation}
-    k(x) = 
-    \begin{cases}
-        \frac{3}{4}\left(1-x^2\right)& \text{ for } -1<x<1 \\ 
-        0 & \text{ otherwise } 
-    \end{cases}
-    \ .
-\end{equation}
-
-An example of the kernel regression using the Epanechnikov kernel is shown in Figure \ref{fig:meanvar_epanechnikov}.
-It shows the kernel regression fitted onto the \texttt{Mar16} variance-mean data for different values of $\lambda$.
-The bandwidth controls how smooth the kernel regression is.
-Just by observation, $\lambda=1$ is too small because it is capturing the noise whereas $\lambda=10^4$ is too large as it did not captured the general shape of the variance-mean relationship.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm6.eps}
-        \caption{$\lambda=10^0$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm8.eps}
-        \caption{$\lambda=10^2$}
-    \end{subfigure}
-    }
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm9.eps}
-        \caption{$\lambda=10^3$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm10.eps}
-        \caption{$\lambda=10^4$}
-    \end{subfigure}
-    }
-    \caption{Epanechnikov kernel regression, with bandwidth $\lambda$, fitted on the variance-mean data from \texttt{Mar16}.}
-    \label{fig:meanvar_epanechnikov}
-\end{figure}
-
-Choosing a good bandwidth can be done using cross validation methods \citep{friedman2001elements} but this can be computationally expensive thus time consuming.
-By eyeballing the figure and choosing a bandwidth which captures a smooth variance-mean relationship, a value of $\lambda=10^3$ was chosen.
-
-\section{Model Selection}
-
-In the previous section, several models for the variance-mean relationship have been described.
-This section will use model selection techniques to access the goodness of fit and prediction performance for each model.
-
-\subsection{Deviance}
-The deviance is one way to assess the goodness of fit of the regression on the variance-mean data. The deviance is defined to be
-\begin{equation}
-    D = 2\left(
-        \ln L_s - \ln L    
-    \right)
-\end{equation}
-where $L$ and $L_s$ are the likelihood and saturated likelihood respectively.
-
-Let $\alpha=(n-1)/2$ be the shape parameter.
-Suppose the variance-mean data consist of the following values $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$ and $\widehat{y}_i$ is the predicted $Y$ given $x_i$, then the log likelihood is
-\begin{equation}
-    \ln L = \sum_{i=1}^m \left[
-        \alpha\ln\alpha
-        -\alpha\ln \widehat{y_i}
-        -\ln\Gamma(\alpha)
-        +(\alpha-1)\ln y_i
-        -\frac{\alpha y_i}{\widehat{y}_i}
-    \right]
-    \ .
-\end{equation}
-The log saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ so that
-\begin{equation}
-    \ln L_s = \sum_{i=1}^m \left[
-        \alpha\ln\alpha
-        -\alpha\ln{y_i}
-        -\ln\Gamma(\alpha)
-        +(\alpha-1)\ln y_i
-        -\alpha
-    \right]
-    \ .
-\end{equation}
-Following from this, the deviance is then
-\begin{equation}
-    D = 2\alpha
-    \sum_{i=1}^m\left[
-        \dfrac{
-            y_i-\widehat{y}_i
-        }
-        {
-            \widehat{y}_i
-        }
-        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
-    \right]
-    \ .
-\end{equation}
-The scaled deviance can be obtained by removing the factor of $\alpha$ to get
-\begin{equation}
-    D^* = 2
-    \sum_{i=1}^m\left[
-        \dfrac{
-            y_i-\widehat{y}_i
-        }
-        {
-            \widehat{y}_i
-        }
-        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
-    \right]
-    \ .
-\end{equation}
-It is given that $D\sim\chi_{m-2}^2$ which implies that $\expectation\left[D\right]=m-2$.
-Because the GLMs considered here all have 2 parameters with known $\alpha$, the best model is the model with the lowest scaled deviance.
-
-The analysis on the deviance was conducted by fitting GLMs with different link functions and polynomial orders $p$ onto the variance-mean data using all $n=100$ images from \texttt{Mar16}.
-The deviance was then calculated.
-This procedure was done using multiple bootstrap samples \citep{efron1992bootstrap} of the $m$ images to get a sample of scaled deviance.
-
-The resulting 100 bootstrapped scaled deviance are shown in Figure \ref{fig:meanvar_deviance_mar16}.
-The kernel regression was also included.
-The scaled deviance does not vary much from model to model and suggests that the goodness of fit are all very similar.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.49\textwidth]{../figures/meanVar/GlmDeviance_Mar16_scaled_deviance.eps}
-    \caption{Scaled deviance when fitting Gamma GLM on the variance-mean data from \texttt{Mar16}.}
-    \label{fig:meanvar_deviance_mar16}
-\end{figure}
-
-In this particular example, $m\approx 1.3\times 10^6$ and $n=100$. Then one would expect the scaled deviance to have values
-\begin{align*}
-    \expectation\left[D^*\right]&=\frac{1}{\alpha}\expectation\left[D\right]
-    \\
-    &=\frac{2}{n-1}\times (m-2)
-    \\
-    &\approx \frac{2}{100-1}\times (1.3\times 10^6-2)
-    \\
-    &\approx 2.6 \times 10^4
-\end{align*}
-which is similar in magnitude but lower compared to the scaled deviances obtained from the bootstrap samples.
-This suggests the shape parameter $\alpha=(n-1)/2$ is too big and perhaps should be smaller.
-The estimation of the shape parameter here is however not too important as it is not used to further calculations.
-
-\subsection{Cross Validation}
-
-Another way to do model selection is cross validation \cite{friedman2001elements}.
-In the \texttt{Mar16} dataset, the 100 images were spilt into 2 equally sized sets called the training set and the test set.
-This produced 2 variance-mean data, one from each set.
-The regression was fitted onto the training set and the training set only.
-
-Prediction using the fitted regression can be accessed.
-This was done by calculating the mean squared error of the prediction of the training set, known as the training error, or the test set, known as the test error.
-
-20 samples of training and test errors were obtained by repeating the analysis using another random allocation of the training and test set.
-The results are shown in Figure \ref{fig:meanvar_mar16mse}.
-Each of the regressions considered all have similar prediction ability with the exception of GLM with log link and $p=1$ which performed significantly worse.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Mar16}.}
-    \label{fig:meanvar_mar16mse}
-\end{figure}
-
-\subsection{Shading Correction}
-
-%\begin{figure}
-%	\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
-%        \caption{30 deg}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
-%        \caption{120 deg}
-%    \end{subfigure}
-%    }
-%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
-%        \caption{30 deg}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
-%        \caption{120 deg}
-%    \end{subfigure}
-%    }
-%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
-%\end{figure}
-
-It was investigated how shading correction affects the variance-mean relationship.
-Figure \ref{fig:meanvar_shadingcorrection_july16_30deg} shows the sample variance-mean for the \texttt{July16 30deg} data with different types of shading correction applied.
-At a quick glance, it appeared the shading correction did not do much to the sample variance-mean data.
-However a closer look at low means showed that shading correction had a particular effect and formed a tighter cluster in the bottom-left of the variance-mean histogram.
-This implied that shading correction made more dark pixels have similar grey values.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad1_iGlm1.eps}
-        \caption{No shading correction}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad2_iGlm1.eps}
-        \caption{BW shading correction}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad3_iGlm1.eps}
-        \caption{Linear shading correction}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16 30deg} using different shading corrections.
-Fitted is a Gamma GLM with identity link.
-Error bars represent the $\Phi(\pm1)$ quantile.}
-    \label{fig:meanvar_shadingcorrection_july16_30deg}
-\end{figure}
-
-In this section, the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} were considered.
-These are the only datasets with black, grey and white images which are used in shading correction.
-
-A regression was fitted using all images in each dataset to get the sample variance-mean data.
-The scaled deviance was calculated and repeated using bootstrapped samples of the images to get 100 samples of the scaled deviance.
-These are shown in Figures \ref{fig:meanvar_deviance_july16} and \ref{fig:meanvar_deviance_sep16} for the datasets \texttt{July16} and \texttt{Sep16} respectively.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_30deg_scaled_deviance.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_120deg_scaled_deviance.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{July16}.}
-    \label{fig:meanvar_deviance_july16}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_30deg_scaled_deviance.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_120deg_scaled_deviance.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Sep16}.}
-    \label{fig:meanvar_deviance_sep16}
-\end{figure}
-
-The scaled deviance did not vary much from model to model and shading correction to another.
-However there was one notable exception in \texttt{July16 120deg} where it appeared the scaled deviance preferred the log link with $p=-2$.
-Figure \ref{fig:meanvar_july16_glm} shows how the curvature of the log link captured the sample variance-mean data.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm1.eps}
-        \caption{Identity link, $p=1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm3.eps}
-        \caption{Log link, $p=-2$}
-    \end{subfigure}
-    }
-    \caption{Log frequency density graph of the sample variance-mean data from the \texttt{July16 120deg} dataset.}
-    \label{fig:meanvar_july16_glm}
-\end{figure}
-
-Worryingly there appeared to be a significant change in the scaled deviance at different angles in the \texttt{July 16} dataset. This is unexplained.
-
-Another analysis was done by holding out half of the images and assigned it as the test set.
-The remaining images were assigned to be the training set and was used to train different types of regressions.
-The training and test MSE are shown in Figures \ref{fig:meanvar_mse_july16_30deg}, \ref{fig:meanvar_mse_july16_120deg}, \ref{fig:meanvar_mse_sep16_30deg} \& \ref{fig:meanvar_mse_sep16_120deg} for the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} respectively.
-
-What is remarkable is how much shading correction improved the training and test MSE, in particular in the \texttt{Sep16} dataset.
-
-\begin{figure}
-\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 30deg}.}
-    \label{fig:meanvar_mse_july16_30deg}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 120deg}.}
-    \label{fig:meanvar_mse_july16_120deg}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 30deg}.}
-    \label{fig:meanvar_mse_sep16_30deg}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 120deg}.}
-    \label{fig:meanvar_mse_sep16_120deg}
-\end{figure}
-
-\section{Conclusion}
-Experimentally it was found that a Gamma GLM with identity link and $p=1$ performed just as well with other GLM with different link functions and non-parametric regressions.
-A Gamma GLM with identity link and $p=1$ is essentially a simple linear regression.
-The simple linear regression is attractive as the linear relationship between the variance and mean is backed up by the compound Poisson model of x-ray photon behaviour.
-The simple linear regression is also a good candidate for the variance-mean model to those who prefer simpler models and follows Occam’s razor.
-
-It was also found that shading correction aid in variance prediction. This highlights the important of shading correction and should be applied to images whenever possible.
+\input{chapters/4_variancePrediction.tex}
 
 \chapter{Inference}
-
-The aim of this project is to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist}.
-\texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample.
-Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.
-
-Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect.
-However in the previous chapters, it was found that x-ray photons behave randomly and large differences in the comparison can be due to chance.
-Thus the comparisons should be done under the face of uncertainty.
-
-A pixel by pixel inference was proposed to do defect detection. A statistic $z_{i,j}$ for the $(i,j)$ positioned pixel can be calculated for all pixels. This statistic is
-\begin{equation}
-    z_{i,j} = 
-    \dfrac{
-        \text{scan}_{i,j} - \text{aRTist}_{i,j}
-    }
-    {
-        \sqrt{\widehat{\variance}\left[\text{scan}_{i,j}\right]}
-    }
-\end{equation}
-where $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is the estimated grey value variance of pixel $(i,j)$ in the scan.
-Under mild assumptions, it was shown in the previous chapters that the grey values in the scan are Normal.
-Thus by treating the simulated image from \texttt{aRTist} as known, then
-\begin{equation}
-z_{i,j}\sim \normal(0,1) \ .
-\end{equation}
-This means the randomness of the $z_{i,j}$ statistics can be quantified.
-
-The estimation of the grey value variance given the grey value, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ will be explained here.
-The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample.
-These replicated x-ray scans provide variance-mean data which then can be used to train the variance model, such as a Gamma distributed GLM.
-The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
-
-This method can be applied to the dataset \texttt{Sep16 120deg}. The 20 x-ray images were spilt into 3. 10 images were used to train the variance-mean model,
+\input{chapters/5_inference.tex}
 

### 2018-03-20 reports/thesis/chapters/1_literatureReview.tex
Moved chapters to tex files.

3D printing, formally additive manufacturing \citep{gibson2010additive} \citep{wong2012review}, has recently become state of the art technology which manufactures objects of complicated shapes with very high precision. It was developed in the 1980's \citep{kodama1981automatic} but recently it has been commercialised and is used in medical science \citep{kang20163d} and engineering \citep{wong2012review}. Because of such a wide range of applications, there has been a need for quality control and this can be done by scanning the 3D printed sample using x-ray computed tomography.

\section{X-ray Imaging}

\subsection{X-Ray Production}
Photons in CT scanning are produced in an X-ray tube. In an X-ray tube, a cathode, consisting of a heated filament, fires projectile electrons through an electric potential to a target which forms the anode \citep{michael2001x}, as shown in Figure \ref{fig:x_ray_tube}. Most of the kinetic energy of the projectile electrons is converted into heat however some is converted into electromagnetic radiation. This depends on how the projectile electrons interact with the atoms in the anode \citep{cantatore2011introduction}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
	\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \citep{michael2001x}}
	\label{fig:x_ray_tube}
\end{figure}

Bremsstrahlung is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target. The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation. As a result, the photon energies in bremsstrahlung radiation is  a continuous spectrum and can range up to the maximum kinetic energy of the projectile electrons \citep{michael2001x}.

Characteristic radiation is due to projectile electrons colliding with electrons in the target atom and ionizing them. This produce vacancies in the electron shell and emits photons when the electrons in the target atom drops down back to the ground state. The energy of the emitted radiation is monoenergetic and depends on the binding energy of the target's atoms \citep{michael2001x}.

A typical energy spectrum of photons emitted from an X-ray tube is as shown in Figure \ref{fig:x_ray_spectrum}. The energy spectrum consist of both bremsstrahlung and characteristic radiation \citep{michael2001x}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{figures/x_ray_spectrum.png}
	\caption{A typical energy spectrum of photons emitted from an X-ray tube. The continuous spectrum is the result of bremmsstrahlung. The peaks are the result of characteristic radiation. \citep{michael2001x}}
	\label{fig:x_ray_spectrum}
\end{figure}

The voltage and current can be varied in the X-ray tube to produce different energy spectrums and rate of photon production. This can vary the results produced when collecting CT data \citep{cantatore2011introduction}. Another important factor is the focal spot size because smaller spot sizes produce sharper edges. Larger spot sizes produce unsharp results and this is know as the penumbra effect, as shown in Figure \ref{fig:x_ray_penumbra}. However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the X-ray tube.

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{figures/x_ray_penumbra.png}
	\caption{Larger focal spot sizes produces unsharp results. This is know as the penumbra effect. \emph{Source: F.~Welkenhuyzen et al.~(2009)\citep{welkenhuyzen2009industrial}}}
	\label{fig:x_ray_penumbra}
\end{figure}

\subsection{Photon Interactions}
Photons emitted by the X-ray tube are projected onto the sample and interacts with it in a number of ways \citep{cantatore2011introduction}.

The sample can effectively absorb photons via the photoelectric effect or pair production \citep{cantatore2011introduction}. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}. In pair production, the photons convert into electron-position pairs by interacting with the Coulomb field of the sample's atomic nucleus \citep{hubbell2006electron}. In addition to getting absorbed, photons can be scattered by the sample. This happens when photons collide inelastically with and transfers its energy to the sample's electrons. This process is known as Compton scattering \citep{compton1923quantum}.

Suppose a mono-energetic X-ray pencil beam attenuating through an object with varying attenuation coefficient in position $\mu=\mu(x)$. The beam starts at $x=0$ and is detected at $x=L$, then the attenuation (decrease in X-ray intensity from $I_0$ to $I_1$) is given as \citep{cantatore2011introduction}
\begin{equation}
	I_1 = I_0\exp\left[\int_0^L-\mu(x)\diff x\right].\label{eq:beerLaw}
\end{equation}
By comparing the intensity before and after attenuation, the integral of the attenuation coefficient along the path of the X-ray can be calculated. Because of the discrete nature of pixels, the integral is usually replaced by a sum \citep{michael2001x}.

However it was shown that the attenuation coefficient does depend on the energy of the photons \citep{elbakri2002statistical}. Thus $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}. In general low energy photons are more likely to be absorbed than high energy photons, this increases the average energy of the attenuated photons and can be a source of error in CT scanning. This is referred to beam hardening and can cause inaccuracies in Equation \eqref{eq:beerLaw} \citep{michael2001x}. This can be reduced by placing a thin sheet of filter to absorb low energy photons \citep{welkenhuyzen2009industrial} or by correcting it in the data analysis stage \citep{michael2001x}.

\subsection{Detection}
Most X-ray detectors are made up of a scintillator material \citep{greskovich1997ceramic} and photodiodes. Firstly the x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}. Lastly the visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}. Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.

The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}. The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}. The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image on a computer \citep{cierniak2011x}.

\section{X-ray Computed Tomography}
Computed tomography (CT) scanning is a 3D imaging technique. It does this by reconstructing the geometry of the sample through a series of 2D X-ray images of the sample. The sample rotates after each image taken \citep{cantatore2011introduction}.

Figure \ref{fig:x_ray_ct} shows a diagram on how CT scanning works. A 2D image is taken by projecting X-ray photons onto the stationary sample. The photons are then scattered or absobred by the sample.  Some of these photons are then detected by an X-ray detector on the other side of the sample, which produces an image. After an image has been taken, the object rotates and another image is taken. Finally after a number of images, a 3D reconstruction of the object can be estimated \citep{cantatore2011introduction}.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{figures/x_ray_ct.png}
	\caption{X-ray computed tomography reconstructs the sample by projecting photons onto a rotating sample. The photons are then detected by the detector. \emph{Source: \url{http://www.phoenix-xray.com/}}}
	\label{fig:x_ray_ct}
\end{figure}

CT was solved theoretically by \cite{cormack1973reconstruction} and implemented by \cite{hounsfield1973computerized} \citep{hounsfield1980computed}. It was mainly used for medical imaging. The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}. Recently CT has been used industrially for non-destructive testing in manufacturing \citep{cantatore2011introduction}. One possible application would be inspecting 3D printed samples \citep{villarraga2015assessing}. Other uses in science include the investigation of batteries \citep{o2017investigating} and materials \citep{wang2017x} \citep{zhang2016x}.

Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}. There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.

Studies have been done to use x-ray CT to do defection detection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}. This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}. Voids then can be classified as defects if the voids are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{amrhein2014characterization} \citep{gandossi2010probability}.

Full 3D x-ray CT scans can be slow and may not generalised well in production lines. However there is potential to bring in methods such as those used in airport luggage inspection to speed up to process \citep{warnett2016towards}.

There are many sources of error in CT scanning \citep{cantatore2011introduction} and this can cause problems when reconstructing the geometry of the sample. Sources of error include: dead pixels in the detector \citep{brettschneider2014spatial}, use of cone beams \citep{sun2016applications}, beam hardening and the orientation of the sample \citep{corcoran2016observations}.

The scale of the 2D images can be calibrated with the use of reference standards \citep{bartscher2007enhancement} \citep{lifton2013application}.

\section{Compound Poisson}

The greyvalues of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector. When the photons interact with the scintillator, they are converted into visible light. The visible light photons are then detected and converted into a greyvalue. How the detected visible light is converted is important in modelling the greyvalue.

Should the greyvalue be proportional to the number of photons detected, the detector is known as a quantum counter and the greyvalue is a Poisson random variable, up to a constant \citep{whiting2006properties}. However if the greyvalue records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector. The greyvalue has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}. There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.

Many reconstruction algorithms have been proposed considering the compound Poisson nature of the detector \citep{elbakri2002statistical} \citep{elbakri2003statistical} \citep{lasio2007statistical} \citep{xie2008x} and with beam hardening correction \citep{elbakri2003efficient}. These will not be discussed here as they are beyond the scope of this thesis.

Experiments have been done to verify the compound Poisson nature of the detector. This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers. It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise. The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.

The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
\begin{equation*}
	Y\sim\poisson(\lambda)
\end{equation*}
that is
\begin{equation*}
	\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\dotdotdot
\end{equation*}
where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$. Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
\begin{equation}
	X|Y = \sum_{i=1}^{Y}U_i+\kappa
	\label{eq:compoundPoisson_X|Y}
\end{equation}
where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
\begin{equation*}
	p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0
	\ .
\end{equation*}
However it should be noted that $X=0$ if and only if $Y=0$ with probability
\begin{equation*}
	\prob(X=0)=\euler^{-\lambda} \ .
\end{equation*}
Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
\begin{equation}
	p_X(x) = 
	\begin{cases}
		\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
		\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
	\end{cases}
\end{equation}
where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.

The m.g.f.~of $X$ has a nicer form however. Let the m.g.f.~of $X$ be
\begin{equation*}
	M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
	\ .
\end{equation*}
This can be computed using the result for conditional expectations
\begin{equation*}
	M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]
	\ .
\end{equation*}
Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
\begin{equation*}
	M_X(\theta)=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
\end{equation*}
\begin{equation*}
	M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
	\ .
\end{equation*}
But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.
\begin{equation*}
	M_U(\theta)=\expectation\left[\euler^{U\theta}\right]
	\ ,
\end{equation*}
then
\begin{equation*}
	M_X(\theta)=\expectation\left(
		\expectation\left[\euler^{\theta U_1}|Y\right]\cdot
		\expectation\left[\euler^{\theta U_2}|Y\right]\cdot
		\dotdotdot \cdot
		\expectation\left[\euler^{\theta U_Y}|Y\right]
	\right)
\end{equation*}
\begin{equation*}
	M_X(\theta)=\expectation\left[\left(M_U(\theta)\right)^Y\right]
\end{equation*}
\begin{equation*}
	M_X(\theta)=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
\end{equation*}
\begin{equation*}
	M_X(\theta) = M_Y\left(\ln(M_U(\theta)\right)
\end{equation*}
where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
\begin{equation}
	M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
	\exp
	\left[
		\lambda
		\left(
		  \euler^\theta-1
		\right)
	\right]
\end{equation}
then
\begin{equation}
	M_X(\theta)=
	\exp\left[
		\lambda
		\left(
			M_U(\theta)-1
		\right)
	\right]
	\ .
\end{equation}
As long as the m.g.f.~of $U$ is known, then m.g.f.~of $X$ can be written in closed form.

Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
\begin{align*}
	M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
	M_X'(\theta)&=M_X(\theta)\lambda M_U'(\theta)
\end{align*}
then
\begin{equation}
	\expectation\left[X\right]=\lambda\expectation\left[U\right]
	\ .
\end{equation}
Conducting the same procedure
\begin{equation*}
	M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
	\ ,
\end{equation*}
the variance can be obtained
\begin{equation*}
	\variance\left[X\right]=M_X''(0)-\left[M_X'(0)\right]^2
\end{equation*}
\begin{equation*}
	\variance\left[X\right]=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
\end{equation*}
\begin{equation*}
	\variance\left[X\right]=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
\end{equation*}
resulting in
\begin{equation}
	\variance\left[X\right] = \lambda\expectation\left[U^2\right]
	\ .
\end{equation}
This can be extended for higher moments.

Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$. By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.

If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
\begin{equation}
	U\sim\gammaDist\left(\alpha,\beta\right)
\end{equation}
where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
\begin{equation}
	X\sim\CPoisson(\lambda,\alpha,\beta)
	\ .
\end{equation}
The conditional distribution can be shown to be
\begin{equation}
	X|Y\sim\gammaDist\left(Y\alpha,\beta\right)
	\ .
\end{equation}

Using results derived earlier, the m.g.f.~of the of $X$ is
\begin{equation}
	M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
\end{equation}
and moments can be obtained from it such as
\begin{equation}
	\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
\end{equation}
\begin{equation}
	\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
	\label{eq:compoundPoisson_variance}
\end{equation}
and
\begin{equation}
	\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
	\ .
\end{equation}

The p.d.f.~can be shown to be
\begin{equation}
	p_X(x) = 
	\begin{cases}
		\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
		\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
	\end{cases}
	\label{eq:compoundPoisson_pdf}
\end{equation}
and it is well known the infinite sum cannot be written in closed form. There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}. Of course direct simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated. The p.d.f.~then can be estimated using these simulated samples.

For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, parameter estimation can be difficult. Maximum likelihood estimation is very complicated \citep{withers2011compound}. It can be made simpler by fixing $\alpha$ to be known \citep{withers2011compound} but this is not useful in this context.

Because the moments of a compound Poisson-Gamma random variable can be obtained easily, method of moments estimators can be obtained. Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$. Then the estimators
\begin{equation}
	\widehat{\lambda}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
\end{equation}
\begin{equation}
	\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
\end{equation}
\begin{equation}
	\widehat{\beta}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
\end{equation}
are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}. These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.

However, parameter estimation can be made easier once it can be realised that the compound Poisson-Gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}. To show this, it is particular useful to reparametrize the compound Poisson-Gamma distribution using the following:
\begin{equation}
	p=\frac{2+\alpha}{1+\alpha}
	\ ,
\end{equation}
\begin{equation}
	\mu=\frac{\lambda\alpha}{\beta}
	\ ,
\end{equation}
\begin{equation}
	\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
	\ .
\end{equation}
The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. It can be shown that $1<p<2$, $\mu>0$ and $\phi>0$.

By rearranging the parameters to get
\begin{equation}
	\lambda=\frac{\mu^{2-p}}{\phi(2-p)}
\end{equation}
\begin{equation}
	\alpha=\frac{2-p}{p-1}
\end{equation}
\begin{equation}
	beta=\frac{1}{\phi(p-1)\mu^{p-1}}
\end{equation}
and substituting it into Equation \eqref{eq:compoundPoisson_pdf}, the p.m.f.~at zero can be shown to be
\begin{equation}
	\prob(X=0) = \exp
	\left[
	    -\frac{\mu^{2-p}}{\phi(2-p)}
	\right]
\end{equation}
and the p.d.f.~for $x>0$ is
\begin{multline*}
	p_X(x) = \sum_{y=1}^{\infty}
	\left[
		\frac{1}{\phi(p-1)\mu^{p-1}}
	\right]^{y\alpha}
	\frac{1}{\Gamma(y\alpha)}
	x^{y\alpha-1}
	\exp\left[
	    -\frac{x}{\phi(p-1)\mu^{p-1}}
	\right]
	\\
	\exp\left[
	    -\frac{\mu^{2-p}}{\phi(2-p)}
	\right]
	\left[
		\frac{\mu^{2-p}}{\phi(2-p)}
	\right]^y
	\frac{1}{y!}
	\ .
\end{multline*}
Tidying up the equation
\begin{multline*}
	p_X(x) = 
	\exp\left[
		\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)
	\right]
	\frac{1}{x}
	\\
	\sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
	\ .
\end{multline*}
To simplify further, it should be noted that
\begin{align*}
	2-p-\alpha(p-1) &= 2-p - \frac{2-p}{p-1}(p-1)
	\\&=0
\end{align*}
so that
\begin{equation}
	p_X(x) = 
	\exp\left[
		\frac{1}{\phi}
		\left(
			x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
		\right)
	\right]
	\frac{1}{x}
	\sum_{y=1}^{\infty}W_y(x,p,\phi)
\end{equation}
where
\begin{equation}
	W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
	\ .
\end{equation}

Those familiar with generalised linear models \citep{nelder1972generalized} \citep{mccullagh1984generalized} will notice that for fixed $p$ or $\alpha$, the above is in the form of a distribution in the dispersive exponential family. Parameter estimation then can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}. These has applications in for example insurance claim data \citep{jorgensen1994fitting} \citep{smyth2002fitting}.

Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}. One easy way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.

One special property of the compound Poisson-Gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}. It has a special variance mean relationship
\begin{equation}
	\variance[X] = \phi \mu^p
\end{equation}
where, as a reminder, $1<p<2$. This can be derived using Equation \eqref{eq:compoundPoisson_variance} or via the partition function $Z$. That is let
\begin{equation}
	\theta = \frac{\mu^{1-p}}{1-p}
\end{equation}
and
\begin{equation}
	\ln Z = \frac{1}{\phi(2-p)\theta^\alpha(1-p)^\alpha} \ ,
\end{equation}
then
\begin{equation}
	\variance[X] = \phi^2 \frac{\partial^2\ln Z}{\partial\theta^2} \ .
\end{equation}

### 2018-03-20 reports/thesis/chapters/3_compoundPoisson.tex
Moved chapters to tex files.

In this chapter, the compound Poisson-Gamma distribution is reviewed and studied. Firstly methods for evaluating the density of the compound Poisson-Gamma distribution are discussed. Approximations such as the Normal approximation or saddlepoint approximation \citep{daniels1954saddlepoint} can be used. These approximate densities can be written in closed form. Exact methods can be computationally challenging when dealing with the infinite sum but can be done when summing over important terms \citep{dunn2005series}. Next, a method for parameter estimation will be proposed here using the EM algorithm \citep{dempster1977maximum}. However in the end of the chapter, it will be shown that no unique maximum likelihood estimator exist when certain parameters of the compound Poisson-Gamma distribution gets too large.

\section{Density Evaluation}
Suppose $X\sim\CPoisson(\lambda,\alpha,\beta)$ and $\lambda,\alpha,\beta>0$ then the p.d.f.~of $X$ is
\begin{equation}
	p_X(x) = 
	\begin{cases}
		\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
		\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y & \text{ for } x>0 
	\end{cases}
\end{equation}
where
\begin{equation}
	W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
	\ .
	\label{eq:compoundPoisson_w}
\end{equation}
The evaluation of this p.d.f.~is difficult because the sum of $W_y$ cannot be simplified. However the m.g.f.~of $X$ can be written down in closed form
\begin{equation}
	M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
	\ .
\end{equation}
The m.g.f.~allows the study of limiting distributions of the compound Poisson-Gamma distribution. These limiting distributions then can be used to approximate the p.d.f.~of a compound Poisson-Gamma random variable.

The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation  of the m.g.f.~giving the p.d.f. However inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}. The saddlepoint approximation will be studied here.

Lastly the infinite sum can be computationally summed in a clever way. This was done by summing only large terms in the sum and ignores small terms. By using Stirling's approximation, the largest term in the sum can be approximately found \citep{dunn2005series}.

\subsection{Normal Approxmation}
The m.g.f.~provides a starting point to what limiting distributions the compound Poisson-Gamma distribution converges to for large parameters. However the m.g.f.~of $X$ itself it not useful because when considering $\lambda\rightarrow\infty$ or $\alpha\rightarrow\infty$ then $M_X(\theta)\rightarrow\infty$. Also for $\beta\rightarrow\infty$, then $M_X(\theta)\rightarrow 1$ which is not useful either.

The compound Poisson-Gamma random variable $X$ should be standardised to obtain useful limiting results from the m.g.f. Let
\begin{equation}
	Z = \frac{X-\expectation[X]}{\sqrt{\variance[X]}}
	\ ,
\end{equation}
then using previous results
\begin{equation*}
	Z = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
	\left(
		X-\frac{\alpha\lambda}{\beta}
	\right)
\end{equation*}
\begin{equation}
	Z = bX+a
\end{equation}
where
\begin{equation}
	b = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
\end{equation}
and
\begin{equation}
	a = -\sqrt{\frac{\alpha\lambda}{\alpha+1}}
	\ .
\end{equation}

The m.g.f.~of $Z$ is then
\begin{equation*}
	M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
\end{equation*}
\begin{equation*}
	M_Z(\theta)=\expectation\left[\euler^{(bX+a)\theta}\right]
\end{equation*}
\begin{equation*}
	M_Z(\theta)=\euler^{a\theta}M_X(b\theta)
	\ .
\end{equation*}
Substituting in the values
\begin{equation*}
	M_Z(\theta)=
	\exp\left(
	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
    \right)
	\exp\left[
		\lambda
		\left(
			\left(
				\frac{\beta}{\beta-\frac{\beta\theta}{\sqrt{\alpha(\alpha+1)\lambda}}}
			\right)^\alpha
			-1
		\right)
	\right]
\end{equation*}
\begin{equation*}
	M_Z(\theta)=
	\exp\left(
	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
    \right)
	\exp\left[
		\lambda
		\left(
			\left(
				\frac{\sqrt{\alpha(\alpha+1)\lambda}}{\sqrt{\alpha(\alpha+1)\lambda}-\theta}
			\right)^\alpha
			-1
		\right)
	\right]
\end{equation*}
or in a different form
\begin{equation}
	M_Z(\theta)=
	\exp\left(
	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
    \right)
	\exp\left[
		\lambda
		\left(
			\left(
				1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}	
			\right)^{-\alpha}
			-1
		\right)
	\right]
	\ .
\end{equation}

The above form is useful so that the binomial expansion can be conducted, that is
\begin{multline}
	\left(
		1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}
	\right)^{-\alpha}
	=
	1+
	\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
	\\
	\text{for }\frac{\|\theta\|}{\sqrt{\alpha(\alpha+1)\lambda}}<1 \ .
\end{multline}
Substituting in the binomial expansion
\begin{equation*}
	M_Z(\theta)=
	\exp\left(
	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
    \right)
	\exp\left[
		\lambda
		\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
	\right]
	\ .
\end{equation*}
Writing in full the $r=1,2$ terms
\begin{multline*}
	M_Z(\theta)=
	\exp\left(
	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
    \right)
	\exp\left[
		\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
		+\frac{\theta^2}{2}
	\right.
	\\
	\left.
		+\lambda\sum_{r=3}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
	\right]
\end{multline*}
and a term cancels out to get
\begin{equation}
	M_Z(\theta)=
	\exp\left[
		\frac{\theta^2}{2}
		+\sum_{r=3}^\infty
		\frac
			{\theta^r\prod_{s=1}^r(\alpha+s-1)}
			{(\alpha(\alpha+1))^{r/2}r!}
		\lambda^{1-r/2}
	\right]
	\ .
\end{equation}

For large $\lambda$
\begin{equation}
	\lim_{\lambda\rightarrow\infty}M_Z(\theta)=\exp\left[\frac{\theta^2}{2}\right]
\end{equation}
which is the same as the m.g.f.~of a standard Normal variable, therefore
\begin{equation}
	\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1) \ .
\end{equation}
This should make sense as for high $\lambda$, the Poisson random variable has a high expectation, increasing the number of Gamma random variables in a summation. Increasing the number of terms in a summation will trigger the central limit theorem.

Next for high $\alpha$, it should be noted that
\begin{equation*}
	\lim_{\alpha\rightarrow\infty}
	\frac{
		\prod_{s=1}^r(\alpha+s-1)
	}
	{
		\alpha(\alpha+1))^{r/2}
	}
	=
	\frac{
		\prod_{s=1}^r\alpha
	}
	{
		\alpha^{r}
	}
\end{equation*}
so that
\begin{equation}
	\lim_{\alpha\rightarrow\infty}
	\frac{
		\prod_{s=1}^r(\alpha+s-1)
	}
	{
		(\alpha(\alpha+1))^{r/2}
	}
	= 1
	\ .
\end{equation}
As a result
\begin{equation}
	\lim_{\alpha\rightarrow\infty}
	M_Z(\theta)=
	\exp\left[
		\frac{\theta^2}{2}
		+\sum_{r=3}^\infty
		\frac{\theta^r}{r!}
		\lambda^{1-r/2}
	\right]
	\ .
\end{equation}
However this shows that taking the limit $\alpha\rightarrow\infty$ is not enough to get a Normal limiting distribution. For a Normal limiting distribution, the limit must be accompanied with the limit $\lambda\rightarrow\infty$, that is
\begin{equation}
	\lim_{\lambda\rightarrow\infty}\lim_{\alpha\rightarrow\infty}Z\sim\normal(0,1)
	\ .
\end{equation}

Finally it should be noted that $M_Z(\theta)$ is independent of $\beta$. Thus $\beta$ will have no effect on the convergence to a Normal limiting distribution.

The above results justify the use of the approximation
\begin{equation}
	X\sim\normal\left(\frac{\lambda\alpha}{\beta},\frac{\lambda\alpha(\alpha+1)}{\beta^2}\right)
\end{equation}
for large $\lambda$. The limiting case where $\lambda\rightarrow 0$, $\alpha\rightarrow 0$ and $\beta\rightarrow 0$ will not be discussed here.

\subsection{Normal Approximation - General Case}
It was shown in certain situations, the compound Poisson-Gamma distribution can be approximated with the Normal distribution. This can be extended to the general compound Poisson.

Let $Y\sim\poisson(\lambda)$ where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be some random variable for i.i.d.~$i=1,2,3,\dotdotdot$ with m.g.f.~$M_U(\theta)$. Let
\begin{equation}
	X|Y = \sum_{i=1}^{Y}U_i
	\ .
\end{equation}

It can be shown that the m.g.f.~of $X$ is
\begin{equation}
	M_X(\theta)=
	\exp\left[
		\lambda(M_U(\theta)-1)
	\right]
	\ .
\end{equation}
As in the compound Poisson-Gamma case, it is useful to standardise $X$ using
\begin{equation*}
	Z = \frac{X-\lambda\expectation[U]}{\sqrt{\lambda\expectation[U^2]}}
\end{equation*}
\begin{equation}
	Z = \frac{X}{\sqrt{\lambda\expectation[U^2]}}
	-\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
	\ .
\end{equation}
The m.g.f.~of $Z$ is then
\begin{equation*}
	M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
\end{equation*}
\begin{equation*}
	M_Z(\theta)=
	\exp\left[
	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
	\right]
	\exp\left[
	\lambda
	\left(
		M_U
		\left(
			\frac{\theta}{\sqrt{\lambda\expectation[U^2]}}\right)-1
		\right)
	\right]
\end{equation*}

Taking the Maclaurin series of $M_U(\theta)$
\begin{equation}
	M_U(\theta) = 1 + \sum_{r=1}^\infty\frac{\theta^r}{r!}M_U^{(r)}(0)
	\quad\text{for }\lim_{r\rightarrow\infty}
	\left\|
		\frac{\theta}{r+1}\frac{M_U^{(r+1)}(0)}{M_U^{(r)}(0)}
	\right\|<1
\end{equation}
and substituting it into $M_Z(\theta)$
\begin{equation*}
	M_Z(\theta)=
	\exp\left[
	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
    \right]
	\exp\left[
		\lambda\sum_{r=1}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
	\right]
	\ .
\end{equation*}
Writing out in full the $r=1,2$ terms
\begin{multline*}
	M_Z(\theta)=\exp\left[
	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
	\right]
	\exp\left[
		\theta\frac{\sqrt{\lambda}M_U'(0)}{\sqrt{\expectation[U^2]}}
		+
		\frac{\theta^2M_U''(0)}{2\expectation[U^2]}
	\right.
	\\+
	\left.
		\lambda\sum_{r=3}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
	\right]
	\ .
\end{multline*}
By using the fact that $\expectation[U^r]=M_U^{(r)}(0)$ for $r=0,1,2\dotdotdot$, a few terms cancel out to get
\begin{equation}
	M_Z(\theta)=
	\exp\left[
		\frac{\theta^2}{2}
		+
		\sum_{r=3}^\infty\frac{\theta^r \expectation[U^r]}{(\expectation[U^2])^{r/2}r!}\lambda^{1-r/2}
	\right]
	\ .
\end{equation}

For the limit $\lambda\rightarrow\infty$
\begin{equation}
	\lim_{\lambda\rightarrow\infty}M_Z(\theta) = \exp\left[\frac{\theta^2}{2}\right]
\end{equation}
then it can be concluded that
\begin{equation}
	\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1)
	\ .
\end{equation}
The convergence can be aided if the ratio $\dfrac{\expectation[U^r]}{(\expectation[U^2])^{r/2}}$ for $r=3,4,5,\dotdotdot$ are small.

\subsection{Saddlepoint approximation}
The m.g.f.~of a random variable $X$ is defined to be
\begin{equation}
	M_X(\theta)=\expectation[\euler^{\theta X}]
	=
	\int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x
	\ .
\end{equation}
For a given m.g.f., the saddlepoint approximation \citep{daniels1954saddlepoint} \citep{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
\begin{equation}
	p_X(x)\approx\left(2\pi K_X''(s)\right)^{-1/2}\exp\left[K_X(s)-sx\right]
	\label{eq:saddlePoint:generalSaddlePoint}
\end{equation}
where $K_X(\theta) = \ln\left(M_X(\theta)\right)$, and $s=s(x)$ is the solution to the saddle point equation $K_X'(s)=x$.

For the compound Poisson-Gamma distribution, the saddle point approximation is given as 
\begin{multline}
	p_X(x)\approx
	\frac{\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
	\euler^{-x\beta}
	\exp\left[x^{\frac{\alpha}{\alpha+1}}
		\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
	\right]
	\\
	\text{for }x>0 \ .
	\label{eq:saddle_point_approx}
\end{multline}
It appears the approximation is not well defined for $x=0$.

The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary. Thus it may be more sensible to write the approximation up to a constant
\begin{equation}
	p_X(x)\propto x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
	\exp\left[
		x^{\frac{\alpha}{\alpha+1}}
		\frac{
			(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)
		}
		{
			\alpha^{\frac{\alpha}{\alpha+1}}
		}
	\right]
	\ .
\end{equation}

For the remainder of this section, it will be shown how the saddlepoint approximation can be algebraically derived. First of all the cumulant generating function $K_X(\theta)$ can be obtained from the m.g.f.
\begin{equation}
	K_X(\theta) = \lambda
	\left[
		\left(\frac{\beta}{\beta-\theta}\right)^\alpha-1
	\right]
	\ .
\end{equation}
Taking the derivative with respect to $\theta$
\begin{equation}
	K_X'(\theta)=\frac{\lambda\alpha\beta^\alpha}{(\beta-\theta)^{\alpha+1}}
\end{equation}
and this is known as the saddlepoint equation. The quantity $s=s(x)$ is the solution to the equation $K_X'(s)=x$, that is
\begin{equation*}
	\frac{\lambda\alpha\beta^\alpha}{(\beta-s)^{\alpha+1}} = x
\end{equation*}
with solution
\begin{equation}
	s = \beta - \left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
	\ .
\end{equation}

The second derivative of the cumulant generating function is
\begin{equation}
	K_X''(\theta)=\frac{\lambda\alpha(\alpha+1)\beta^\alpha}{(\beta-\theta)^{\alpha+2}} \ .
\end{equation}
Substituting this and $K_X(\theta)$ into Equation \eqref{eq:saddlePoint:generalSaddlePoint}
\begin{equation*}
	p_X(x)\approx
	\frac{1}{\sqrt{2\pi}}
	\left[
		\frac{
			(\beta-s)^{\alpha+2}
		}
		{
			\lambda\alpha(\alpha+1)\beta^\alpha
		}
	\right]^{1/2}
	\exp\left[
		\lambda\left(\left(\frac{\beta}{\beta-s}\right)^\alpha-1\right)-sx
	\right]
	\ .
\end{equation*}
Substituting in $s=s(x)$
\begin{multline*}
	p_X(x)\approx
	\frac{1}{\sqrt{2\pi}}
	\left[
		\frac{\left(\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}\right)^{\alpha+2}}{\lambda\alpha(\alpha+1)\beta^\alpha}
	\right]^{1/2}
	\\
	\exp\left[
		\lambda
		\left(
			\left(
				\frac{\beta}{\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}}
			\right)^\alpha
			-1
		\right)
		-x\left(
			\beta-\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
		\right)
	\right]
\end{multline*}
simplifying further
\begin{multline*}
	p_X(x)\approx
	\frac{1}{\sqrt{2\pi}}
	\left[
		\frac{
			\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{\alpha+2}{\alpha+1}}
		}
		{
			\lambda\alpha(\alpha+1)\beta^\alpha
		}
	\right]^{1/2}
	\\
	\exp\left[
		\lambda
		\left(
			\beta^\alpha
			\left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
			-1
		\right)
		-x\beta
		+(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{1-\frac{1}{\alpha+1}}
	\right]
\end{multline*}
\begin{multline*}
	p_X(x)\approx
	\frac{1}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
	\left(\lambda\alpha\beta^\alpha\right)^{\left(\frac{\alpha+2}{\alpha+1}-1\right)/2}
	\\
	\exp\left[
		\lambda\left(
			\beta^\alpha
			\left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
			-1
		\right)
		-x\beta
		+(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{\frac{\alpha}{\alpha+1}}
	\right]
\end{multline*}
\begin{multline*}
	p_X(x)\approx
	\frac{
		\left(
			\lambda\alpha\beta^\alpha
		\right)^{\frac{1}{2(\alpha+1)}}
	}
	{
		\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
	}	
	\\
	\exp\left[
		-\lambda
		-x\beta
		+x^{\frac{\alpha}{\alpha+1}}
		\left(
			\frac{
				\lambda\beta^\alpha
			}
			{
				\left(\lambda\alpha\beta^\alpha\right)^{\frac{\alpha}{\alpha+1}}
			}
			+
			\left(
				\lambda\alpha\beta^\alpha
			\right)^{\frac{1}{\alpha+1}}
		\right)
	\right]
\end{multline*}
\begin{multline*}
	p_X(x)\approx
	\frac{
		\left(
			\lambda\alpha\beta^\alpha
		\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
	}
	{
		\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
	}
	\euler^{-x\beta}
	\\
	\exp\left[
		x^{\frac{\alpha}{\alpha+1}}
		\left(
			(\lambda\beta^\alpha)^{1-\frac{\alpha}{\alpha+1}}\alpha^{-\frac{\alpha}{\alpha+1}}
			+
			\left(
				\lambda\alpha\beta^\alpha
			\right)^{\frac{1}{\alpha+1}}
		\right)
	\right]
\end{multline*}
\begin{multline*}
	p_X(x)\approx
	\frac{
		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
	}
	{
		\sqrt{2\pi(\alpha+1)}
	}
	x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
	\\
	\exp\left[
		x^{\frac{\alpha}{\alpha+1}}
		\left(
			(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
			\alpha^{-\frac{\alpha}{\alpha+1}}
			+
			\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
		\right)
	\right]
\end{multline*}
\begin{multline*}
	p_X(x)\approx
	\frac{
		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
	}
	{
		\sqrt{2\pi(\alpha+1)}
	}
	x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
	\\
	\exp\left[
		x^{\frac{\alpha}{\alpha+1}}(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
		\left(
			\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
		\right)
	\right]
	\ .
\end{multline*}

The expression $\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}$ can be simplified by putting the two terms over a common denominator
\begin{align}
	\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
	& = \alpha^{\frac{1}{\alpha+1}}+\frac{1}{\alpha^{\frac{\alpha}{\alpha+1}}}
	\nonumber\\
	& = \frac{\alpha^{\frac{1}{\alpha+1}}\alpha^{\frac{\alpha}{\alpha+1}}+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
	\nonumber\\
	& = \frac{\alpha+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
\end{align}
so that
\begin{equation*}
p_X(x)\approx
	\frac{
		\left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
	}
	{
		\sqrt{2\pi(\alpha+1)}
	}
	x^{-\frac{\alpha+2}{2(\alpha+1)}}
	\euler^{-x\beta}
	\exp\left[
		x^{\frac{\alpha}{\alpha+1}}
		\frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
	\right]
	\ .
\end{equation*}

\subsection{Series Evaluation}
Evaluation of the p.d.f.~of the compound Poisson-Gamma distribution is difficult because of the infinite sum
\begin{equation}
p_X(x) = 
	\delta(x) \euler^{-\lambda}
	+
	\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y
	\quad\text{for }x\geqslant 0
\end{equation}
where
\begin{equation}
	W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
	\ .
	\label{eq:compoundPoisson_Wy}
\end{equation}
$W_y$ can be expressed in a different way using different parameters
\begin{equation}
	W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
\end{equation}
where
\begin{equation}
	p=\frac{2+\alpha}{1+\alpha}
\end{equation}
and
\begin{equation}
	\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}} \ .
\end{equation}

\cite{dunn2005series} approximated the sum by truncation
\begin{equation}
	\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y
\end{equation}
where $y_\text{l}<y_{\text{max}}<y_\text{u}$ and $y_{\text{max}}$ is the value of $y$ which maximises $W_y$. \cite{dunn2005series} used Stirling's approximation to find $y_{\text{max}}$. This was done by treating $W_y$ as a continuous function of $y$ and is differentiable with respect to $y$.

It is easier to differentiate $\ln(W_y)$ where
\begin{multline*}
	\ln(W_y) = y\alpha\ln(x)-y(1+\alpha)\ln(\phi)-y\alpha\ln(p-1)\\-y\ln(2-p)-\ln(y!)-\ln\Gamma(y\alpha)
\end{multline*}
\begin{equation}
	\ln(W_y) =
	y
	\ln\left(
		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
	\right)
	-\ln(y!)-\ln\Gamma(y\alpha)
	\ .
\end{equation}
Using Stirling's approximation
\begin{equation}
	\ln(n!)\approx\ln\Gamma(n)\approx n\ln(n!)-n
\end{equation}
then
\begin{equation}
	\ln(W_y) \approx
	y\ln\left(
		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
	\right)
	-y\ln(y)+y-y\alpha\ln(y\alpha) + y\alpha
	\ .
\end{equation}
Taking the derivative with respect to $y$
\begin{multline*}
	\frac{\partial \ln(W_y)}{\partial y} \approx
	\ln\left(
		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
	\right)
	-\ln(y)-1+1
	\\
	-\alpha\ln(y\alpha)-\alpha+\alpha
\end{multline*}
\begin{equation}
	\frac{\partial \ln(W_y)}{\partial y} \approx
	\ln\left(
		\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
	\right)
	-\ln(y)
	-\alpha\ln(y\alpha)
	\ .
\end{equation}

Setting the derivative to zero
\begin{equation*}
	0 \approx \ln\left(
		\frac{
			x^\alpha
		}
		{
			\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha
		}
	\right)
\end{equation*}
\begin{equation*}
	1 \approx 
	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha}
\end{equation*}
\begin{equation*}
	y_{\text{max}}^{1+\alpha} \approx 
	\frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)\alpha^\alpha}
\end{equation*}
\begin{equation*}
	y_{\text{max}} \approx 
	\frac{1}{\phi}
	\left(
		\frac{x}{(p-1)\alpha}
	\right)^{\frac{\alpha}{1+\alpha}}
	(2-p)^{\frac{-1}{1+\alpha}}
	\ .
\end{equation*}
This can be simplified using the fact that 
\begin{equation*}
	\alpha=\frac{2-p}{p-1}
	\ ,
\end{equation*}
\begin{equation*}
	\frac{1}{1+\alpha} = p-1
\end{equation*}
and
\begin{equation*}
	\frac{\alpha}{1+\alpha} = 2-p
\end{equation*}
then
\begin{equation*}
	y_{\text{max}} \approx 
	\frac{1}{\phi}
	\left(
		\frac{x}{2-p}
	\right)^{2-p}
	(2-p)^{1-p}
\end{equation*}
and finally
\begin{equation}
	y_{\text{max}} \approx \frac{x^{2-p}}{\phi(2-p)}
	\ .
\end{equation}
Because values of $y$ should be a positive integer, it would be appropriate to round the solution to $y_\text{max}$ accordingly
\begin{equation}
	y_{\text{max}} = \text{max}\left[
		1,\text{round}\left(\frac{x^{2-p}}{\phi(2-p)}\right)
	\right]
	\ .
\end{equation}

To verify that $y_\text{max}$ is a maximum, the second derivative can be investigated
\begin{equation}
	\frac{\partial^2\ln(W_y)}{\partial y^2}
	\approx
	-\frac{1}{y}(\alpha+1)
\end{equation}
to see that
\begin{equation}
	\frac{\partial^2\ln(W_y)}{\partial y^2} < 0 \quad \text{for }y=1,2,3,\dotdotdot
\end{equation}
therefore $y_\text{max}$ is a maximum.

Returning back to the truncation of the infinite sum
\begin{equation}
	\sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y
	\ ,
\end{equation}
$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}. To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} and using the following equation
\begin{equation}
	\ln\left[
		\sum_{y=y_\text{l}}^{y_\text{u}}W_y
	\right]
	= 
	\ln\left(
		W_{y_\text{max}}
	\right)
	+\ln\sum_{y=y_\text{l}}^{y_\text{u}}
	\exp\left[
		\ln\left(W_y\right)-\ln\left(W_{y_\text{max}}\right)
	\right]
	\ .
\end{equation}

\subsection{Simulation Studies}

Simulations of a compound Poisson-Gamma random variable were conducted with the aim to compare how well these density evaluations methods perform. This was done by comparing the evaluated densities with the histogram of simulations and a Q-Q plot. The following compound Poisson-Gamma distributions were used in the simulations to capture the variety in the compound Poisson-Gamma family: $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(100,100,1)$.

A few technical details will be stated here. The Normal approximation does not support probability mass at $x=0$, but instead has a support of $-\infty<x<\infty$. The Normal approximation with $-\infty<x<\infty$ support was used here.

Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$. The saddlepoint approximation was computed up to a constant using
\begin{equation}
	p_X(x) \propto
	\exp\left[
		-\frac{\alpha+2}{2(\alpha+1)}
		\ln(x)
		-x\beta
		+\left(
		\frac{x\beta}{\alpha}
		\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1) - k
	\right]
\end{equation}
for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant to control over/underflow and it was chosen to be
\begin{equation}
	k =
	\max_{i\in\left\{1,2,3,\dotdotdot,n\right\}}
	\left[
		-\frac{\alpha+2}{2(\alpha+1)}
		\ln(x_i)
		-x_i\beta
		+\left(
			\frac{x_i\beta}{\alpha}
		\right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
	\right]
	\ .
\end{equation}
The density was then was normalised by numerically integrating it using the trapezium rule using the 500 evaluated points.

A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Let
\begin{equation}
	F_X(x) = \prob(X\leqslant x)
\end{equation}
\begin{equation}
	\widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}
	\left[
		\left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
	\right]
	\ ,
\end{equation}
then a Q-Q plot plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$. If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin. However there is no closed form for $F_X(x)$. When using the exact or saddlepoint method, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums. $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation. For the saddlepoint approximation where $x=0$ cannot be evaluated and their exist a zero value in the sample, the lower limit of the numerical integral was chosen, arbitrary, to be
\begin{equation}
	\frac{
		\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)
	}
	{
		\euler^{-\lambda}(1+\lambda)
	}
	\times 0.1
	\ .
\end{equation}

For low $\lambda$ (Figures \ref{fig:cp_simulation_1} and \ref{fig:cp_simulation_3}) there is a chance of simulating zeros. The Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric. The saddlepoint approximation did capture probability mass at zero as shown by an increase in probability density towards zero. However in Figure \ref{fig:cp_simulation_3}, the compound Poisson-Gamma distribution looked like a mixture model and the saddlepoint approximation was not flexible enough to capture each individual peak. In addition, the Q-Q plots looked quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~at low densities.

As $\lambda$ increased, all 3 density evaluation methods performed quite well. In Figure \ref{fig:cp_simulation_2}, the Normal approximation did not quite capture the skewness of the histogram. However in Figure \ref{fig:cp_simulation_4} for the Normal looking compound Poisson-Gamma random variable, all methods performed well.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist1.png}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq1.png}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist1.png}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq1.png}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist1.png}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq1.png}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{Simulations of $\CPoisson(1,1,1)$ compared to different density evaluation methods}
    \label{fig:cp_simulation_1}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist2.png}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq2.png}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist2.png}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq2.png}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist2.png}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq2.png}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{Simulations of $\CPoisson(10,1,1)$ compared to different density evaluation methods}
    \label{fig:cp_simulation_2}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist3.png}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq3.png}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist3.png}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq3.png}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist3.png}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq3.png}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{Simulations of $\CPoisson(1,100,1)$ compared to different density evaluation methods}
    \label{fig:cp_simulation_3}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist4.png}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq4.png}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist4.png}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq4.png}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist4.png}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq4.png}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{Simulations of $\CPoisson(100,100,1)$ compared to different density evaluation methods}
    \label{fig:cp_simulation_4}
\end{figure}

\section{EM Algorithm}

The EM algorithm \citep{dempster1977maximum} will be proposed here as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$.

A popular method for parameter estimation is the maximum log likelihood method. Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log likelihood is defined to be
\begin{equation*}
	\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
	\left[
		\mathbb{I}(x_i=0)\ln \prob(X=x_i)
		+\mathbb{I}(x_i>0)\ln p_X(x_i)
	\right]
\end{equation*}
\begin{multline}
	\ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
	\left[
		-\mathbb{I}(x_i=0)\lambda
		\vphantom{\sum_i^i}
	\right.
	\\
	\left.
		+\mathbb{I}(x_i>0)\left(
		-1-\beta x_i-\lambda-\ln x -\ln\sum_{y=1}^\infty W_y
		\right)
	\right]
\end{multline}
where $W_y=W_y(\lambda,\alpha,\beta)$ was defined in Equation \eqref{eq:compoundPoisson_w}. $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood. The gradient of the log likelihood can be evaluated \citep{dunn2005series} and optimisation can be done using gradient methods.

The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable. Let $\left\{Y_1,Y_2,Y_3,\dotdotdot, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\dotdotdot, x_n\right\}$ be measurements of $X|Y$. Define the joint log likelihood to be
\begin{multline*}
	\ln L(\lambda,\alpha,\beta;X,Y)
	=
	\sum_{i=1}^n
	\left[
		\mathbb{I}(x_i=0)
		\ln
		\prob(Y=0)
	\right.
	\\
	\left.
		+
		\mathbb{I}(x_i>0)
		\ln
		\left[
			p_{X|Y}(x_i|Y_i)\prob(Y=Y_i)
		\right]
	\right]
\end{multline*}
so that
\begin{multline}
	\ln L(\lambda,\alpha,\beta;X,Y)=
	\sum_{i=1}^n
	\left[
		-\mathbb{I}(x_i=0)
		\lambda
	\right.
	\\
	\left.+
		\mathbb{I}(x_i>0)
		\left(
			Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
		\right.
	\right.
	\\
	\left.
		\left.	
			- \lambda + Y_i \ln \lambda - \ln(Y_i!)
		\right)
	\right]
	\ .
\end{multline}
The estimators are found by optimising the joint log likelihood. This is done iteratively by estimating the $Y$s given the $X$s and parameters (E step), followed by estimating the parameters given the $Y$s and $X$s (M step) until some convergence conditions are met.

It will be shown that using some approximations, the E step and M step can be implemented. The Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} can also be found by using a few approximations. However simulations show that these estimators struggle for high $\lambda$ and it will be shown that this will be the case for all estimators.

\subsection{E Step}

In the E step, the realizations of $Y$ are estimate using
\begin{equation}
	y_i =
	\expectation\left[
		Y|X=x_i
	\right]
\end{equation}
for given parameters $\lambda$, $\alpha$ and $\beta$. The conditional expectation is calculated using
\begin{equation}
	y_i = 
	\begin{cases}
		0 & \text{ for } x=0 \\ 
		\dfrac{\sum_{y=1}^\infty y \prob(Y=y|X=x_i)}{\sum_{y=1}^\infty \prob(Y=y|X=x_i)} & \text{ for } x>0
	\end{cases}
\end{equation}
where
\begin{equation*}
	\prob(Y=y|X=x) = \frac{p_{X|Y}(x|y)\prob(Y=y)}{p_X(x)}
	\ .
\end{equation*}
Focussing on the $x>0$ case for now
\begin{equation*}
	\prob(Y=y|X=x) = \frac{1}{p_X(x)}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\frac{\euler^{-\lambda}\lambda^y}{y!}
\end{equation*}
and
\begin{equation}
	\prob(Y=y|X=x) = W_y \frac{\euler^{-\lambda-\beta x}}{x}
\end{equation}
where $W_y$ is defined in Equation \eqref{eq:compoundPoisson_Wy}.
Then the conditional expectation is
\begin{equation}
	y_i = \frac{\sum_{y=1}^\infty y W_y}{\sum_{y=1}^\infty W_y}
	\ .
\end{equation}
It was already established how the denominator can be evaluated \citep{dunn2005series}. A similar method for evaluating the numerator can be obtained by truncating the sum and summing large terms.

Let
\begin{equation}
	W_y^{(r)} = y^r W_y
\end{equation}
so that
\begin{equation}
	y_i = \frac{\sum_{y=1}^\infty W^{(1)}_y}{\sum_{y=1}^\infty W_y}
\end{equation}
and
\begin{equation}
	\variance[Y|X=x_i] = \frac{\sum_{y=1}^\infty W^{(2)}_y}{\sum_{y=1}^\infty W_y} - \left(y_i\right)^2
	\ .
\end{equation}
The exponent $r=0,1,2,\dotdotdot$ will be useful in the M step where higher conditional moments are needed.
The sum can be truncated
\begin{equation}
	\sum_{y=1}^\infty W^{(r)}_y \approx \sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y
\end{equation}
where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. By expressing $\ln(W^{(r)}_y)$ as
\begin{equation}
	\ln\left(W_y^{(r)}\right)=r\ln(y)+\ln(W_y)
\end{equation}
and then taking the derivative with respect to $y$
\begin{equation}
	\frac{\partial \ln(W_y^{(r)})}{\partial y} = \frac{r}{y } + \frac{\partial \ln(W_y)}{\partial y}
	\ .
\end{equation}
Keep in mind that $y=1,2,3,\dotdotdot$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
\begin{equation}
	\frac{\partial \ln(W_y^{(r)})}{\partial y} \approx \frac{\partial \ln(W_y)}{\partial y}
	\ .
\end{equation}
By using such an approximation, the method for evaluating the sum $\sum_{y=1}^\infty W^{(r)}_y$ is almost exactly the same as evaluating the sum $\sum_{y=1}^\infty W_y$, in particular $y_\text{max}$ are the same. For a given $r=0,1,2,\dotdotdot$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant. The limits will be different for different values of $r$.

\subsection{M Step}

In the M step, the conditional expected joint log likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is then
\begin{multline*}
	T(\lambda,\alpha,\beta)=
	\sum_{i=1}^n
	\expectation\left[
		-\mathbb{I}(x_i=0)
		\lambda
	\right.
	\\
	\left.+
		\mathbb{I}(x_i>0)
		\left(
			Y_i\alpha\ln\beta-\ln\Gamma(Y_i\alpha)+(Y_i\alpha-1)\ln x_i - \beta x_i
		\right.
	\right.
	\\
	\left.
		\left.	
			- \lambda + Y_i \ln \lambda - \ln(Y_i!)
		\right)
		|X_i=x_i
	\right]
\end{multline*}
\begin{multline*}
	T(\lambda,\alpha,\beta)=
	-n\lambda
	\\
	+\sum_{i=1}^n
	\mathbb{I}(x_i>0)
	\left[
		\expectation[Y_i|X_i=x_i]\alpha\ln\beta-\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]
	\right.
	\\
	\left.
		+\expectation[Y_i|X_i=x_i]\alpha\ln x_i - \beta x_i
		+ \expectation[Y_i|X_i=x_i] \ln \lambda
	\right] + c
\end{multline*}
where $c$ is some constant not dependent on $\lambda$, $\alpha$ or $\beta$.

The conditional expectation $y_i = \expectation[Y_i|X_i=x_i]$ was calculated in the E step. The quantity $\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]$ can be calculated using the approximation
\begin{equation}
	\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i] \approx
	\ln\Gamma(\alpha y_i) + \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
\end{equation}
where
\begin{equation}
	\zeta_i = \variance[Y_i|X_i=x_i]
\end{equation}
calculated in the E step and $\psi$ is the digamma function. The objective function is then
\begin{multline}
	T(\lambda,\alpha,\beta)=
	-n\lambda
	+\sum_{i=1}^n
	\mathbb{I}(x_i>0)
	\left[
		y_i\alpha\ln\beta-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
	\right.
	\\
	\left.
		+y_i\alpha\ln x_i - \beta x_i
		+ y_i \ln \lambda
		\vphantom{\frac{1}{1}}
	\right]
	+ c
	\ .
\end{multline}

Taking the derivative with respect to $\lambda$
\begin{equation}
	\frac{\partial T}{\partial\lambda} = -n + \frac{\sum_{i=1}^ny_i}{\lambda}
\end{equation}
and setting it to zero
\begin{equation}
	\widehat{\lambda} = \frac{\sum_{i=1}^n y_i}{n}
\end{equation}
obtains a M step estimator, and a familiar one, for $\lambda$. Taking the second derivative with respect to $\lambda$
\begin{equation}
	\frac{\partial^2 T}{\partial \lambda^2} = -\frac{\sum_{i=1}^ny_i}{\lambda^2} < 0
\end{equation}
verifies $\widehat{\lambda}$ maximises T. In addition
\begin{equation}
	\frac{\partial^2 T}{\partial \alpha \partial \lambda } = 0
\end{equation}
and
\begin{equation}
	\frac{\partial^2 T}{\partial \beta \partial \lambda } = 0
	\ .
\end{equation}

Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second order can be obtained. For the first order these are:
\begin{multline}
	\frac{\partial T}{\partial \alpha} =
	\sum_{i=1}^n\mathbb{I}(x_i>0)
	\left[
		y_i\ln\beta -\psi(\alpha y_i)y_i-\zeta_i\alpha\psi'(\alpha y_i)
		\vphantom{\frac{1}{1}}
	\right.
	\\
	\left.
		- \frac{1}{2}\zeta_i\alpha^2\psi''(\alpha y_i)y_i + y_i\ln x_i
	\right]
\end{multline}
and
\begin{equation}
	\frac{\partial T}{\partial \beta} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
	\frac{\alpha y_i}{\beta}-x_i
	\right]
	\ .
\end{equation}
The second orders are:
\begin{equation}
	\frac{\partial^2 T}{\partial \alpha \partial \beta} =
	\sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right]
	\ ,
	\label{eq:compoundPoisson:d2tdadb}
\end{equation}
\begin{equation}
	\frac{\partial^2 T}{\partial \beta^2} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[-\frac{\alpha y_i}{\beta^2}
	\right]
	\label{eq:compoundPoisson:d2td2b}
\end{equation}
and
\begin{multline*}
	\frac{\partial^2 T}{\partial \alpha^2} = 
	\sum_{i=1}^n\mathbb{I}(x_i>0)
	\left[
		-y_i^2\psi'(\alpha y_i) - \zeta_i\psi'(\alpha y_i) - \zeta_i\alpha y_i\psi''(\alpha y_i)
		\vphantom{\frac{1}{2}}\right.\\\left.	
		- \zeta_i\alpha\psi''(\alpha y_i)y_i
		-\frac{1}{2}\zeta_i\alpha^2\psi'''(\alpha y_i)y_i^2
	\right]
\end{multline*}
simplifying to
\begin{multline}
	\frac{\partial^2 T}{\partial \alpha^2} = 
	\sum_{i=1}^n\mathbb{I}(x_i>0)
	\left[
		-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
		\vphantom{\frac{1}{2}}
	\right.
	\\
	\left.	
		-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
	\right] \ .
	\label{eq:compoundPoisson:d2td2a}
\end{multline}

All the derivatives can be used in the Newton-Raphson iterative update, which is
\begin{equation}
	\begin{pmatrix}
		\alpha \\ \beta
	\end{pmatrix}
	\leftarrow
	\begin{pmatrix}
		\alpha \\ \beta
	\end{pmatrix}
	\left[
		\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T
	\right]^{-1}
	\left[
		\nabla_{\alpha,\beta} T
	\right]
\end{equation}
where
\begin{equation}
	\nabla_{\alpha,\beta}=
	\begin{pmatrix}
		{\partial}/{\partial \alpha}
		\\
		{\partial}/{\partial \beta}
	\end{pmatrix}
	\ .
\end{equation}
Since increasing $T$ is sufficient for the EM algorithm \citep{dempster1977maximum}, one step of the Newton-Raphson iterative update was chosen in the M step to avoid implementing a convergence condition.

\subsection{Estimation Error}

The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} from the Fisher's information matrix defined as
\begin{equation}
	\matr{I} = -\expectation\left[
		\nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
	\right]
	\ .
\end{equation}
The calculation is similar to the derivatives of $T$, so using the same approximations and the fact that $\expectation[Y]=\lambda$, then
\begin{equation}
	\matr{I}=
	\begin{pmatrix}
		\dfrac{n}{\lambda} & 0 & 0 \\
		0 & (\lambda^2+\lambda)\psi'(\alpha\lambda)+2\alpha\lambda^2\psi''(\alpha\lambda)+\frac{1}{2}\alpha^2\lambda^3\psi'''(\alpha\lambda) & -\dfrac{n\lambda}{\beta}\\
		0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
	\end{pmatrix}
	\ .
\end{equation}
The Cram\'er-Rao lower bound is then
\begin{equation}
	\cov\left[
		\begin{pmatrix}
			\widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
		\end{pmatrix}
	\right]
	=
	\matr{I}^{-1}
	\ .
\end{equation}

\subsection{Simulations}

An experiment was conducted to assess the performance on the EM algorithm. For a given set of parameters, 1\,000 samples of a $\CPoisson(\lambda,\alpha,\beta)$ random variable were simulated. The EM algorithm was initialised with its parameters at the true values to investigate the convergence in that vicinity. The log likelihood $\ln L(\lambda,\alpha,\beta;X)$ and the parameters were recorded at every EM step. The experiment was repeated 10 times using different simulated samples.

The results for $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$ and $\CPoisson(100,100,1)$ are shown in Figures \ref{fig:compoundPoisson_convergence_1}, \ref{fig:compoundPoisson_convergence_2}, \ref{fig:compoundPoisson_convergence_3} and \ref{fig:compoundPoisson_convergence_4} respectively. Good performance can be seen for the $\lambda=1$ case with convergence of all 3 parameters within a step or two. The Cram\'er-Rao lower bound captured the spread of the estimates well.

However for $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log likelihood. It appears the EM algorithm failed for $\lambda>10$ looking at these particular examples.

\begin{figure}[p]
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_1}
\end{figure}

\begin{figure}[p]
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_2}
\end{figure}

\begin{figure}[p]
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_3}
\end{figure}

\begin{figure}[p]
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lnL.eps}
        \caption{Log likelihood}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lambda.eps}
        \caption{$\lambda$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_alpha.eps}
        \caption{$\alpha$}
    \end{subfigure}
        \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_beta.eps}
        \caption{$\beta$}
    \end{subfigure}
    }
    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times. The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment. The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
    \label{fig:compoundPoisson_convergence_4}
\end{figure}

\subsection{Failure Evaluation}
It should be convincing that the EM algorithm failed when the compound-Poisson Gamma random variable starts behaving Normally. In particular in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ are stable while estimates of $\alpha$ and $\beta$ struggled to converge. This could be because as the compound-Poisson Gamma random variable approach being Normal, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate and there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$.

One way to see this is to look at the Newton-Raphson step, in the M step, in particular the Hessian matrix $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ for high $\lambda$. The elements of the Hessian matrix can be found in Equations \eqref{eq:compoundPoisson:d2tdadb}, \eqref{eq:compoundPoisson:d2td2b} and \eqref{eq:compoundPoisson:d2td2a}. The $\dfrac{\partial^2T}{\partial\alpha^2}$ element is 
\begin{multline*}
	\frac{\partial^2 T}{\partial \alpha^2} = 
	\sum_{i=1}^n\mathbb{I}(x_i>0)\left[
		-(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
		\vphantom{\frac{1}{2}}
	\right.
	\\
	\left.	
		-\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
	\right]
	\ .
\end{multline*}
For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$. Firstly using Stirling's approximation
\begin{equation}
	\ln\Gamma(n)\approx\ln(n!)\approx n\ln n-n
\end{equation}
then
\begin{equation}
	\psi(n) = \frac{\partial\ln\Gamma(n)}{\partial n} \approx \ln n
	\ .
\end{equation}
Differentiating further
\begin{align}
	\psi'(n) &\approx 1/n \\
	\psi''(n) & \approx -1/n^2 \\
	\psi'''(n) & \approx 2/n^3
	\ .
\end{align}
Using the approximations, $\dfrac{\partial^2T}{\partial\alpha^2}$ can be approximated
\begin{equation*}
	\frac{\partial^2 T}{\partial \alpha^2} \approx 
	\sum_{i=1}^n\mathbb{I}(x_i>0)
	\left[
		-\frac{y_i^2+\zeta_i}{\alpha y_i} + 2\frac{\zeta_i\alpha y_i}{\alpha^2 y_i^2}
		-\frac{1}{2}\frac{2\zeta_i\alpha^2y_i^2}{\alpha^3 y_i^3}
	\right]
\end{equation*}
to get
\begin{equation}
	\frac{\partial^2 T}{\partial \alpha^2} \approx 
	\sum_{i=1}^n\mathbb{I}(x_i>0)
	\left[
		-\frac{y_i}{\alpha}
	\right]
	\ .
\end{equation}

The Hessian matrix is then
\begin{equation}
	\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T \approx
	\sum_{i=1}^n
	\mathbb{I}(x_i>0)
	\begin{pmatrix}
		-y_i/\alpha  & y_i/\beta \\
		y_i/\beta & -\alpha y_i/\beta^2
	\end{pmatrix}
	\ . 
\end{equation}
The determinant of the Hessian matrix is then
\begin{equation*}
	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
	\approx
	\left(\sum_{i=1}^n-\frac{\alpha y_i}{\beta^2}\right)
	\left(\sum_{i=1}^n-\frac{y_i}{\alpha}\right) - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)^2
\end{equation*}
\begin{equation*}
	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
	\approx
	\left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
	 - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)\left(\sum_{j=1}^n\frac{y_j}{\beta}\right)
\end{equation*}
\begin{equation*}
	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
	\approx
	\left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
	 - \left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
\end{equation*}
to get
\begin{equation}
	\|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
	\approx
	0
	\ .
\end{equation}

This results in a few things. Firstly $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ is singular thus its inverse cannot be evaluated, needed for the Newton-Raphson method. Secondly, the sufficient conditions to classify a stationary point as a maximum are that the diagonal elements of the Hessian matrix are negative and the determinate is positive. For high $\lambda$ and $\alpha$, the second condition is not met.

Another argument which can be made is to restrict the parameter $\beta$ for a given mean to be
\begin{equation}
	\beta = \frac{\lambda\alpha}{\widehat{\mu}}
	\label{eq:compoundPoisson:beta_restrict}
\end{equation}
where
\begin{equation}
	\widehat{\mu} = \frac{1}{n}\sum_{i=1}^n x_i
\end{equation}
and investigate whenever a unique solution to $\dfrac{\partial T}{\partial \alpha} = 0$ can be found for high $\lambda$ and $\alpha$. The constrained objective function is
\begin{multline*}
	T(\lambda,\alpha)
	=
	-n\lambda+
	\sum_{i=1}^n
	\mathbb{I}(x_i>0)
	\left[
	y_i\alpha
	\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\ln\Gamma(\alpha y_i) - \frac{1}{2}\zeta_i\alpha^2\psi'(y_i\alpha)
	\right.
	\\
	\left.
		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
		+ y_i \ln \lambda
		\vphantom{\frac{1}{1}}
	\right]
	+ c
\end{multline*}
which can be approximated to
\begin{multline*}
	T(\lambda,\alpha)=
	-n\lambda+
	\sum_{i=1}^n
	\mathbb{I}(x_i>0)
	\left[
		y_i\alpha\ln\left(\frac{\lambda\alpha}{\widehat{\mu}}\right)-\alpha y_i\ln(\alpha y_i) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
	\right.
	\\
	\left.
		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
		+ y_i \ln \lambda
		\vphantom{\frac{1}{1}}
	\right]
	+ c
\end{multline*}
\begin{multline*}
	T(\lambda,\alpha)=
	-n\lambda+
	\sum_{i=1}^n
	\mathbb{I}(x_i>0)
	\left[
		y_i\alpha\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right) + \alpha y_i - \frac{1}{2}\frac{\zeta_i\alpha}{y_i}
	\right.
	\\
	\left.
		+y_i\alpha\ln x_i - \frac{\lambda\alpha x_i}{\widehat{\mu}}
		+ y_i \ln \lambda
		\vphantom{\frac{1}{1}}
	\right]
	+ c
	\ .
\end{multline*}
Taking the derivative with respect to $\alpha$
\begin{equation*}
	\frac{\partial T}{\partial \alpha} =
	\sum_{i=1}^n
	\mathbb{I}(x_i>0)
	\left[
		y_i\ln\left(\frac{\lambda}{y_i\widehat{\mu}}\right)
		+ y_i - \frac{1}{2}\frac{\zeta_i}{y_i}
		+y_i\ln x_i - \frac{\lambda x_i}{\widehat{\mu}}
		\vphantom{\frac{1}{1}}
	\right]
\end{equation*}
and this is not $\alpha$ dependent, thus there is no solution to $\alpha$.

### 2018-03-20 reports/thesis/chapters/4_variancePrediction.tex
Moved chapters to tex files.

In the previous chapter, it was found that it is very hard to fit a compound Poisson random variable onto the grey values directly itself. It is not totally useless however. The compound Poisson model showed that the variance of the grey value has a linear relationship with the mean grey value. Given this, it would be possible to predict the variance of the grey value, given the grey value. This opens up new ways to predict the uncertainty of each individual pixel in an x-ray scan.

In this chapter, different types of regressions were tested to see if they perform well in predicting grey value variance given the grey value. Two types of regressions were used. Generalised linear models \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized} (GLM) is a parametric regression which models the response variable as a random variable in the exponential family. In this project, a Gamma distributed random variable was chosen as the response variable. A non-parametric regression was also considered, here there kernel regression \citep{friedman2001elements} was used.

Using the replicated x-ray images, the within individual pixel sample mean and sample variance were obtained. The sample variance-mean data were then used for the regressions to be fitted on. The deviance was investigated as a method of model selection. The regression was also used to test it's prediction performance on held out images.

In the end, a GLM with a linear relationship between the variance and the mean was good enough. Its performance is similar to other complicated models and its simple form attracts those who follows Occam's razor, that the simpler models are usually better. The linear relationship is also justified by the compound Poisson model.

\section{Variance-Mean Relationship}

The sample variance-mean data were obtained from the replicated x-ray images, assuming each image are i.i.d.

Let $x_{i,j}^{(r)}$ be the grey value of the pixel in the $i$th row and $j$th column in the $r$th image for $r=1,2,3,\dotdotdot,n$. The within individual pixel sample mean is
\begin{equation}
    \bar{x}_{i,j}=\frac{1}{n}\sum_{r=1}^n x_{i,j}^{(r)}
\end{equation}
and the within individual pixel sample variance is
\begin{equation}
    y_{i,j} =
    \frac{1}{n-1}
    \sum_{r=1}^n
        \left(
            x_{i,j}^{(r)} - \bar{x}_{i,j}
        \right)^2
    \ .
\end{equation}

Only the masked pixels will be considered here as this is the region of interest (ROI). The sample variance-mean data can be obtained by calculating the within individual pixel sample mean and variance for all ROI pixels and can be plotted as a histogram. For example, the sample variance-mean data for \texttt{Mar16} can be seen in Figure \ref{fig:meanvar_mar16_100}.

\subsection{Generalised Linear Models}
By making some assumptions, some useful and simple results can be obtained. Firstly, it was assumed the standard error from estimating the mean was negligible. Secondly, it was assumed for a given pixel, the grey value from each each were Normal i.i.d. Following from these assumptions, the sample variance is Gamma distributed with shape parameter $(n-1)/2$. Furthermore the standard error of the sample variance is proportional to $(n-1)^{-1/2}$, meaning the sample variance is more precise when more and more images were used to estimate the variance. This was experimentally shown in Figure \ref{fig:meanvar_mar16_differentn}, the spread of the sample variance decreased as $n$ increased.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_25.eps}
        \caption{$n=25$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_50.eps}
        \caption{$n=50$}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_75.eps}
        \caption{$n=75$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_100.eps}
        \caption{$n=100$}
        \label{fig:meanvar_mar16_100}
    \end{subfigure}
    }
    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Mar16} using $n$ of the images. Fitted is a Gamma GLM with identity link. Error bars represent the $\Phi(\pm1)$ quantile.}
    \label{fig:meanvar_mar16_differentn}
\end{figure}

A GLM \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized}, with Gamma distributed response, would then be an appropriate regression to be used. Let $Y$ be the grey value sample variance and $X$ be the grey value, then a GLM models $Y$ via the following
\begin{equation}
    Y|X \sim 
    \gammaDist\left(
        \frac{n-1}{2},
        f(X)
    \right)
\end{equation}
where $f(X)$ is some user specified function. Conventionally it is useful for the specified function to be a parameter of the conditional mean $Y|X$. This function is known as the link function and can be expressed as
\begin{equation}
g(\mu_X) = \eta(X)
\end{equation}
where $\mu_X=\expectation\left[Y|X\right]$ and $\eta(X)$ is a linear function of $X$, for example
\begin{equation}
\eta(X) = \beta_0 + \beta_1 X^p \ .
\end{equation}
For a specified link function and $p$, the GLM is fitted onto the data by estimating the parameters $\beta_0$ and $\beta_1$.

In this project, the identity, inverse and log link functions were investigated for a selected few integer values of $p$. These link functions are shown in Table \ref{table:meanvar_linkfunctions}. They are fitted on the variance-mean data from \texttt{Mar16} as shown in Figure \ref{fig:meanvar_mar16}.

\begin{table}
    \centering
    \begin{tabular}{c|c|c|c}
    &\multicolumn{3}{c}{Link functions}\\
    &Identity&Inverse&Log\\
    \hline
    $g(\mu)$&$\mu$&$1/\mu$&$\ln(\mu)$\\
    \hline
    $\expectation[Y|X=x]$&$\beta_0 + \beta_1 x^p$&$\left[\beta_0 + \beta_1 x^p\right]^{-1}$&$\exp\left[\beta_0 + \beta_1 x^p\right]$
    \end{tabular}
    \caption{Link functions}
    \label{table:meanvar_linkfunctions}
\end{table}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm2.eps}
        \caption{Inverse link, $p=-1$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm3.eps}
        \caption{Inverse link, $p=-2$}
    \end{subfigure}
    }
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm4.eps}
        \caption{Log link, $p=1$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm5.eps}
        \caption{Log link, $p=-1$}
    \end{subfigure}
    }
    \caption{Log frequency density of the variance-mean data from \texttt{Mar16}. Fitted are Gamma GLM with different link functions polynomial features. Error bars represent the $\Phi(\pm1)$ quantile.}
    \label{fig:meanvar_mar16}
\end{figure}

\subsection{Kernel Regression}

Kernel regression \citep{friedman2001elements} is a type of non-parametric regression and its prediction is done using a weighted sum of the data rather then fitting a parametric model. Suppose a collection of variance-mean data were collected $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$, then the kernel regression is
\begin{equation}
    \widehat{y}(x)=
    \dfrac{
        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right) y_i
    }
    {
        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right)
    }
\end{equation}
where $k(x)$ is a specified kernel function and $\lambda$ is called the bandwidth. Popular choices for the kernel include the Gaussian kernel \citep{friedman2001elements}
\begin{equation}
    k(x)=\phi(x)
\end{equation}
and the Epanechnikov kernel \citep{friedman2001elements}
\begin{equation}
    k(x) = 
    \begin{cases}
        \frac{3}{4}\left(1-x^2\right)& \text{ for } -1<x<1 \\ 
        0 & \text{ otherwise } 
    \end{cases}
    \ .
\end{equation}

An example of the kernel regression using the Epanechnikov kernel is shown in Figure \ref{fig:meanvar_epanechnikov}. It shows the kernel regression fitted onto the \texttt{Mar16} variance-mean data for different values of $\lambda$. The bandwidth controls how smooth the kernel regression is. Just by observation, $\lambda=1$ is too small because it is capturing the noise whereas $\lambda=10^4$ is too large as it did not captured the general shape of the variance-mean relationship.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm6.eps}
        \caption{$\lambda=10^0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm8.eps}
        \caption{$\lambda=10^2$}
    \end{subfigure}
    }
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm9.eps}
        \caption{$\lambda=10^3$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm10.eps}
        \caption{$\lambda=10^4$}
    \end{subfigure}
    }
    \caption{Epanechnikov kernel regression, with bandwidth $\lambda$, fitted on the variance-mean data from \texttt{Mar16}.}
    \label{fig:meanvar_epanechnikov}
\end{figure}

Choosing a good bandwidth can be done using cross validation methods \citep{friedman2001elements} but this can be computationally expensive thus time consuming. By eyeballing the figure and choosing a bandwidth which captures a smooth variance-mean relationship, a value of $\lambda=10^3$ was chosen.

\section{Model Selection}

In the previous section, several models for the variance-mean relationship have been described. This section will use model selection techniques to access the goodness of fit and prediction performance for each model.

\subsection{Deviance}
The deviance is one way to assess the goodness of fit of the regression on the variance-mean data. The deviance is defined to be
\begin{equation}
    D = 2\left(
        \ln L_s - \ln L    
    \right)
\end{equation}
where $L$ and $L_s$ are the likelihood and saturated likelihood respectively.

Let $\alpha=(n-1)/2$ be the shape parameter. Suppose the variance-mean data consist of the following values $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$ and $\widehat{y}_i$ is the predicted $Y$ given $x_i$, then the log likelihood is
\begin{equation}
    \ln L = \sum_{i=1}^m \left[
        \alpha\ln\alpha
        -\alpha\ln \widehat{y_i}
        -\ln\Gamma(\alpha)
        +(\alpha-1)\ln y_i
        -\frac{\alpha y_i}{\widehat{y}_i}
    \right]
    \ .
\end{equation}
The log saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ so that
\begin{equation}
    \ln L_s = \sum_{i=1}^m \left[
        \alpha\ln\alpha
        -\alpha\ln{y_i}
        -\ln\Gamma(\alpha)
        +(\alpha-1)\ln y_i
        -\alpha
    \right]
    \ .
\end{equation}
Following from this, the deviance is then
\begin{equation}
    D = 2\alpha
    \sum_{i=1}^m\left[
        \dfrac{
            y_i-\widehat{y}_i
        }
        {
            \widehat{y}_i
        }
        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
    \right]
    \ .
\end{equation}
The scaled deviance can be obtained by removing the factor of $\alpha$ to get
\begin{equation}
    D^* = 2
    \sum_{i=1}^m\left[
        \dfrac{
            y_i-\widehat{y}_i
        }
        {
            \widehat{y}_i
        }
        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
    \right]
    \ .
\end{equation}
It is given that $D\sim\chi_{m-2}^2$ which implies that $\expectation\left[D\right]=m-2$. Because the GLMs considered here all have 2 parameters with known $\alpha$, the best model is the model with the lowest scaled deviance.

The analysis on the deviance was conducted by fitting GLMs with different link functions and polynomial orders $p$ onto the variance-mean data using all $n=100$ images from \texttt{Mar16}. The deviance was then calculated. This procedure was done using multiple bootstrap samples \citep{efron1992bootstrap} of the $m$ images to get a sample of scaled deviance.

The resulting 100 bootstrapped scaled deviance are shown in Figure \ref{fig:meanvar_deviance_mar16}. The kernel regression was also included. The scaled deviance does not vary much from model to model and suggests that the goodness of fit are all very similar.

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{../figures/meanVar/GlmDeviance_Mar16_scaled_deviance.eps}
    \caption{Scaled deviance when fitting Gamma GLM on the variance-mean data from \texttt{Mar16}.}
    \label{fig:meanvar_deviance_mar16}
\end{figure}

In this particular example, $m\approx 1.3\times 10^6$ and $n=100$. Then one would expect the scaled deviance to have values
\begin{align*}
    \expectation\left[D^*\right]&=\frac{1}{\alpha}\expectation\left[D\right]
    \\
    &=\frac{2}{n-1}\times (m-2)
    \\
    &\approx \frac{2}{100-1}\times (1.3\times 10^6-2)
    \\
    &\approx 2.6 \times 10^4
\end{align*}
which is similar in magnitude but lower compared to the scaled deviances obtained from the bootstrap samples. This suggests the shape parameter $\alpha=(n-1)/2$ is too big and perhaps should be smaller. The estimation of the shape parameter here is however not too important as it is not used to further calculations.

\subsection{Cross Validation}

Another way to do model selection is cross validation \cite{friedman2001elements}. In the \texttt{Mar16} dataset, the 100 images were spilt into 2 equally sized sets called the training set and the test set. This produced 2 variance-mean data, one from each set. The regression was fitted onto the training set and the training set only.

Prediction using the fitted regression can be accessed. This was done by calculating the mean squared error of the prediction of the training set, known as the training error, or the test set, known as the test error.

20 samples of training and test errors were obtained by repeating the analysis using another random allocation of the training and test set. The results are shown in Figure \ref{fig:meanvar_mar16mse}. Each of the regressions considered all have similar prediction ability with the exception of GLM with log link and $p=1$ which performed significantly worse.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_training_MSE.eps}
        \caption{Training error}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_test_MSE.eps}
        \caption{Test error}
    \end{subfigure}
    }
    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Mar16}.}
    \label{fig:meanvar_mar16mse}
\end{figure}

\subsection{Shading Correction}

%\begin{figure}
%	\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
%        \caption{30 deg}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
%        \caption{120 deg}
%    \end{subfigure}
%    }
%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
%\end{figure}
%
%\begin{figure}
%	\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
%        \caption{30 deg}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
%        \caption{120 deg}
%    \end{subfigure}
%    }
%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
%\end{figure}

It was investigated how shading correction affects the variance-mean relationship. Figure \ref{fig:meanvar_shadingcorrection_july16_30deg} shows the sample variance-mean for the \texttt{July16 30deg} data with different types of shading correction applied. At a quick glance, it appeared the shading correction did not do much to the sample variance-mean data. However a closer look at low means showed that shading correction had a particular effect and formed a tighter cluster in the bottom-left of the variance-mean histogram. This implied that shading correction made more dark pixels have similar grey values.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad1_iGlm1.eps}
        \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad2_iGlm1.eps}
        \caption{BW shading correction}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad3_iGlm1.eps}
        \caption{Linear shading correction}
    \end{subfigure}
    }
    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16 30deg} using different shading corrections. Fitted is a Gamma GLM with identity link. Error bars represent the $\Phi(\pm1)$ quantile.}
    \label{fig:meanvar_shadingcorrection_july16_30deg}
\end{figure}

In this section, the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} were considered. These are the only datasets with black, grey and white images which are used in shading correction.

A regression was fitted using all images in each dataset to get the sample variance-mean data. The scaled deviance was calculated and repeated using bootstrapped samples of the images to get 100 samples of the scaled deviance. These are shown in Figures \ref{fig:meanvar_deviance_july16} and \ref{fig:meanvar_deviance_sep16} for the datasets \texttt{July16} and \texttt{Sep16} respectively.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_30deg_scaled_deviance.eps}
        \caption{30 deg}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_120deg_scaled_deviance.eps}
        \caption{120 deg}
    \end{subfigure}
    }
    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{July16}.}
    \label{fig:meanvar_deviance_july16}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_30deg_scaled_deviance.eps}
        \caption{30 deg}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_120deg_scaled_deviance.eps}
        \caption{120 deg}
    \end{subfigure}
    }
    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Sep16}.}
    \label{fig:meanvar_deviance_sep16}
\end{figure}

The scaled deviance did not vary much from model to model and shading correction to another. However there was one notable exception in \texttt{July16 120deg} where it appeared the scaled deviance preferred the log link with $p=-2$. Figure \ref{fig:meanvar_july16_glm} shows how the curvature of the log link captured the sample variance-mean data.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm1.eps}
        \caption{Identity link, $p=1$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm3.eps}
        \caption{Log link, $p=-2$}
    \end{subfigure}
    }
    \caption{Log frequency density graph of the sample variance-mean data from the \texttt{July16 120deg} dataset.}
    \label{fig:meanvar_july16_glm}
\end{figure}

Worryingly there appeared to be a significant change in the scaled deviance at different angles in the \texttt{July 16} dataset. This is unexplained.

Another analysis was done by holding out half of the images and assigned it as the test set. The remaining images were assigned to be the training set and was used to train different types of regressions. The training and test MSE are shown in Figures \ref{fig:meanvar_mse_july16_30deg}, \ref{fig:meanvar_mse_july16_120deg}, \ref{fig:meanvar_mse_sep16_30deg} \& \ref{fig:meanvar_mse_sep16_120deg} for the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} respectively.

What is remarkable is how much shading correction improved the training and test MSE, in particular in the \texttt{Sep16} dataset.

\begin{figure}
\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_training_MSE.eps}
        \caption{Training error}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_test_MSE.eps}
        \caption{Test error}
    \end{subfigure}
    }
    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 30deg}.}
    \label{fig:meanvar_mse_july16_30deg}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_training_MSE.eps}
        \caption{Training error}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_test_MSE.eps}
        \caption{Test error}
    \end{subfigure}
    }
    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 120deg}.}
    \label{fig:meanvar_mse_july16_120deg}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_training_MSE.eps}
        \caption{Training error}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_test_MSE.eps}
        \caption{Test error}
    \end{subfigure}
    }
    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 30deg}.}
    \label{fig:meanvar_mse_sep16_30deg}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_training_MSE.eps}
        \caption{Training error}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_test_MSE.eps}
        \caption{Test error}
    \end{subfigure}
    }
    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 120deg}.}
    \label{fig:meanvar_mse_sep16_120deg}
\end{figure}

\section{Conclusion}
Experimentally it was found that a Gamma GLM with identity link and $p=1$ performed just as well with other GLM with different link functions and non-parametric regressions. A Gamma GLM with identity link and $p=1$ is essentially a simple linear regression. The simple linear regression is attractive as the linear relationship between the variance and mean is backed up by the compound Poisson model of x-ray photon behaviour. The simple linear regression is also a good candidate for the variance-mean model to those who prefer simpler models and follows Occam’s razor.

It was also found that shading correction aid in variance prediction. This highlights the important of shading correction and should be applied to images whenever possible.

### 2018-03-20 reports/thesis/chapters/5_inference.tex
Moved chapters to tex files.

The aim of this project is to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist}. \texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.

Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and large differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A statistic $z_{i,j}$ for the $(i,j)$ positioned pixel can be calculated for all pixels. This statistic is
\begin{equation}
    z_{i,j} = 
    \dfrac{
        \text{scan}_{i,j} - \text{aRTist}_{i,j}
    }
    {
        \sqrt{\widehat{\variance}\left[\text{scan}_{i,j}\right]}
    }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is the estimated grey value variance of pixel $(i,j)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan are Normal. Thus by treating the simulated image from \texttt{aRTist} as known, then
\begin{equation}
z_{i,j}\sim \normal(0,1) \ .
\end{equation}
This means the randomness of the $z_{i,j}$ statistics can be quantified.

The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ will be explained here. The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample. These replicated x-ray scans provide variance-mean data which then can be used to train the variance model, such as a Gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation.

This method for inference can be applied to the dataset \texttt{Sep16 120deg}. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_scan_aRTist}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/scan.eps}
        \caption{X-ray image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/aRTist.eps}
        \caption{\texttt{aRTist} simulation}
    \end{subfigure}
    }
    \caption{An x-ray scan of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset. This can be compared directly to the \texttt{aRTist} simulation for defects.}
    \label{fig:inference_scan_aRTist}
\end{figure}

For each pixel, a $z_{i,j}$ statistic was calculated. A $z_{i,j}$ statistic too large in magnitude can be considered to be evidence of a positive result. Another way to represent the $z_{i,j}$ statistic is the $p$-value which is given as
\begin{equation}
    p_{i,j} = 2(1-\Phi(\|z_{i,j}\|))
\end{equation}
which can takes values $0\leqslant p_{i,j} \leqslant 1$. A $p$-value too small is considered to be evidence of a positive result. The result $z$ statistics and $p$-values are shown in Figure \ref{fig:logp_z}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/logp.eps}
        \caption{$-\log p\text{-values}$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/z_image.eps}
        \caption{$z$ statistics}
    \end{subfigure}
    }
    \caption{The resulting z statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
    \label{fig:logp_z}
\end{figure}

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Significant pixels were chosen for $\|z\|>\input{../figures/inference/z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:sig_pixels}.

This proposed method for defect detection failed because too many false positives were detected. These false positives appear to have some structure, for example clustering in the corners or on surfaces. In addition, false negatives were detected because not all of the defects were detected.

Model misspecification appears to be the main source of error. The $z$ statistics can be inspected using a histogram, as shown in Figure \ref{fig:z_histo}. The histogram of the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/sig_pixels.eps}
    \caption{Signficiant pixels highlighted at the $z_\alpha = 2$ significance level.}
    \label{fig:sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/z_histo.eps}
    \caption{Histogram of the $z$ statistics}
    \label{fig:z_histo}
\end{figure}

This chapter will cover hypothesis testing, for a single test and then for multiple tests. The empirical null will then be reviewed which then can be extended to an image filter, called the empirical null filter. This filter will adjust each $z$ statistic according to its neighbours, ironing out false positive results. Simulations and actual results will be shown at the end of the chapter.

\section{Hypothesis Testing}

Hypothesis testing dates back to \cite{pearson1900on}, \cite{neyman1933on} and \cite{fisher1970statistical}. It is so fundamental in science that it is now taught in schools.

The focus on this section is on the single hypothesis test. Here the random variable $Z\sim\normal(\mu,1)$ will be studied here as this is of interest in this project. It also appears in other tests such as the difference in sample means.

In the context of this project, an example of hypothesis testing will be given here. Here, it was assumed that $Z\sim\normal(0,1)$. A null hypothesis can be written down to describe this
\begin{equation}
    H_0:\mu=0 \ .
\end{equation}
It specifies the assumptions made on the random variable $Z$. Any data behaving as assumed is treated as a negative result.

A positive result is obtained when unlikely data is obtained and this happens if $Z$ deviates too much from 0. This can be described as testing $H_0$ against an alternative hypothesis $H_1$ where
\begin{equation}
    H_1:\mu\neq0 \ .
\end{equation}
How much $Z$ deviates from 0 to be considered a positive is up to the user but typically $\|Z\|>z_\alpha$ where $z_\alpha =2$ is considered significant.

A way to quantify the threshold for a positive result is to use something called the size of the test, otherwise known as the significance level, denoted as $\alpha$. This is the probability of a false positive result, which can be denoted as
\begin{equation}
    \prob(\|Z\|>z_\alpha|H_0) = \alpha \ .
\end{equation}
Using the fact the Normal distribution is symmetric then
\begin{equation}
    2(1 - \Phi(z_\alpha)) = \alpha \ .
    \label{eq:inference_single_alpha}
\end{equation}
The choice of $z_\alpha=2$ will set the size of the test to be $\alpha\approx 4.55\%$. This sort of choice of threshold and size is sensible.

The $p$-value is a way to represent an observation of the data $Z=z$. Similar to the size, the $p$-value is
\begin{equation}
    p=2(1-\Phi(\|z\|)) \ .
\end{equation}
As a result, the $p$-value can be compared directly to the size of the test. That is there is a positive result if $p<\alpha$, otherwise it is a negative result.

The power of the test is defined as the probability of a true positive result. For unknown $\mu$, it is useful to investigate the power for a range of $\mu$.

\section{Multiple Hypothesis Testing}

\section{Empirical Null}

\section{Empirical Null Filter}

\section{Results}

### 2018-03-20 reports/thesis/chapters/5_inference.tex
Added multiple hypothesis test section.

@@
 
+In this section, the single hypothesis test will be extended and the multiple hypothesis testing \citep{shaffer1995multiple} shall be reviewed.
+
+Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$ where $Z_i\sim\normal(\mu,1)$ for $i=1,2,\dotdotdot,n$ and i.i.d.
+One can test each of these statistics for the following hypotheses $H_0:\mu=0$ and $H_1:\mu\neq 0$.
+Using the method from the single hypothesis test at the $z_\alpha=2$ level, any statistic where $\|Z_i\|>2$ for $i=1,2,\dotdotdot,n$ would be considered a positive result.
+
+Bringing in methods from single hypothesis testing to the multiple version has drawbacks.
+Assuming that the null hypothesis is true for all $Z_i$ for $i=1,2,\dotdotdot,n$, then by definition $\alpha\approx 4.55\%$ of the data will be tested positive, and falsely positive.
+Still under the same assumption, the probability of at least one positive result, known as the family-wise error rate (FWER) \citep{shaffer1995multiple}, is
+\begin{align}
+    \text{FWER}&=1-\prob(\text{no positive results}|H_0) \nonumber\\
+    \text{FWER}&=1-\left[(1-\alpha)^n\right] \label{eq:inference_fwer}\ .
+\end{align}
+To put into context, for $\alpha\approx 4.55\%$ and $n=20$ then remarkably $\text{FWER}\approx60.6\%$. This method for multiple hypothesis testing will have too many false positive results.
+
+The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family wise error rate.
+This is done by adjusting the size of the test to be $\alpha/n$.
+By using the adjusted size, Equation \eqref{eq:inference_fwer} becomes
+\begin{equation}
+    \text{FWER}=1-\left[(1-\alpha/n)^n\right]\ .
+\end{equation}
+Using the approximation $(1-\alpha/n)^n\approx = 1-\alpha$ then
+\begin{equation}
+    \text{FWER}\approx \alpha \ .
+\end{equation}
+This shows that the Bonferroni correction controls the family-wise error rate.
+However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negative results.
+This is because the correction traded too many false positives for false negatives.
+
+The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate.
+The FDR is the proportion of false positives out of all positive results.
+
+In practice the BH procedure adjusts the size of the test between the Bonferroni correction and the uncorrected test.
+The BH procedure also adapts to the data, meaning the procedure chooses different sizes for different data.
+
+The procedure is as follows.
+Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$.
+They will need to be converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$.
+The adjusted size $\alpha_{\text{BH}}$ is
+\begin{equation}
+    \alpha_{\text{BH}} = \frac{\alpha k}{n}
+\end{equation}
+where
+\begin{equation}
+    k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
+    \ .
+\end{equation}
+This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as positive results.
+For completeness, if $p_{(1)}>\alpha/n$, then $k=1$ and the Bonferroni correction is recovered.
+The procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$, then the $p$-values are uniformly distributed \citep{simes1986improved}.
+
+It can be shown that the BH procedure controls the FDR such that
+\begin{equation}
+    \expectation[\text{FDR}]\leqslant\pi_0\alpha\leqslant\alpha
+\end{equation}
+where $\pi_0$ is the proportion of true nulls out of $n$ tests \citep{benjamini1995controlling}, this is usually unknown in practice.
+
 \section{Empirical Null}

### 2018-03-21 reports/thesis/chapters/5_inference.tex
Added a script for error rates in multiple hypothesis testing.

@@
 \begin{align}
+    \text{FWER}&=1-\prob(\text{no false positives}) \nonumber\\
     \text{FWER}&=1-\prob(\text{no positive results}|H_0) \nonumber\\
@@
 
-The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family wise error rate.
+While the uncorrected method for multiple hypothesis testing has it flaws, it does control the per comparison error rate (PCER) \citep{benjamini1995controlling}.
+PCER is the proportion of false positives out of all tests.
+There are corrections for multiple hypothesis testing which controls different things.
+Conventionally they are expressed in terms of the number of errors made in testing, these are defined in Table \ref{table:inference_randomvariables}.
+Using the notation, formally PCER is defined as
+\begin{equation}
+    \text{PCER}=
+    \dfrac{
+        1
+    }
+    {
+        n
+    }
+    \expectation[V]
+    \ .
+\end{equation}
+It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
+\begin{equation}
+    \text{PCER}\leqslant\alpha \ .
+\end{equation}
+
+\begin{table}
+    \centering
+    \begin{tabular}{c|c|c|c}
+        &Negative&Positive&Total\\\hline
+        True null & $U$ & $V$ & $n_0$\\
+        Non-true null & $T$ & $S$ & $n-n_0$\\\hline
+        &$n-R$&$R$&$n$
+    \end{tabular}
+    \caption{Random variable definitions for the different types of error made in multiple hypothesis testing}
+    \label{table:inference_randomvariables}
+\end{table}
+
+The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the FWER.
 This is done by adjusting the size of the test to be $\alpha/n$.
@@
 \end{equation}
-This shows that the Bonferroni correction controls the family-wise error rate.
+This shows that the Bonferroni correction controls the family-wise error rate such that
+\begin{equation}
+    \text{FWER} \leqslant \alpha \ .
+\end{equation}
 However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negative results.
@@
 The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate.
-The FDR is the proportion of false positives out of all positive results.
+The FDR is the proportion of false positives out of all positive results, that is
+\begin{equation}
+    \expectation[\text{FDR}] = \expectation\left[
+        \dfrac{V}{R}
+    \right]
+    \ .
+\end{equation}
 
@@
 For completeness, if $p_{(1)}>\alpha/n$, then $k=1$ and the Bonferroni correction is recovered.
-The procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$, then the $p$-values are uniformly distributed \citep{simes1986improved}.
+The procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
+However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.
 
@@
 \begin{equation}
-    \expectation[\text{FDR}]\leqslant\pi_0\alpha\leqslant\alpha
+    \text{FDR}\leqslant\pi_0\alpha\leqslant\alpha
 \end{equation}
-where $\pi_0$ is the proportion of true nulls out of $n$ tests \citep{benjamini1995controlling}, this is usually unknown in practice.
+where $\pi_0=n_0/n$ \citep{benjamini1995controlling}, this is usually unknown in practice.
+
+In summary, the uncorrected, Bonferroni and BH correction controls for different error rates according to the threshold $\alpha$, summarised in Table \ref{table:inference_corrections}.
+
+\begin{table}
+    \centering
+    \begin{tabular}{c|c}
+        Correction&Controls for\\\hline
+        No correction&$\text{PCER}\leqslant\alpha$\\
+        Bonferroni&$\text{FWER}\leqslant\alpha$\\
+        BH&$\text{FDR}\leqslant\alpha$
+    \end{tabular}
+    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
+    \label{table:inference_corrections}
+\end{table}
+
+\begin{table}
+    \input{../tables/inference_error_rate1.tex_table}
+    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level.
+1\,000 test statistics were simulated, all standard Normal.
+Error bars represent the standard errors after 1\,000 repeats of the experiment.}
+\end{table}
+
+\begin{table}
+    \input{../tables/inference_error_rate2.tex_table}
+    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level.
+1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$.
+Error bars represent the standard errors after 1\,000 repeats of the experiment.}
+\end{table}
 

### 2018-03-21 LatexTable.m

@@ -1,0 +1,232 @@
+%CLASS: LATEXTABLE For outputting  a table of x +/- err type data into a latex table
+classdef LatexTable < handle
+    
+    %MEMBER VARIABLES
+    properties (SetAccess = protected)
+        mean_array; %matrix of mean values to be printed on a table
+        error_array; %matrix of error values to be printed on a table
+        n_row; %number of rows in the table (not including labels)
+        n_col; %number of columns in the table (not including labels)
+        row_label; %cell array of strings, labelling each row
+        col_label; %cell array of strings, labelling each column
+        n_sig; %number of significant figures used for the errors
+        n_dec_for_no_error; %number of decimial places for values with no errors
+    end
+    
+    %METHODS
+    methods (Access = public)
+        
+        %CONSTRUCTOR
+        %PARAMETERS:
+            %mean_array: matrix of mean values to be printed on a table
+            %error_array: matrix of error values to be printed on a table
+            %row_label: cell array of strings, labelling each row
+            %col_label: cell array of strings, labelling each column
+        function this = LatexTable(mean_array, error_array, row_label, col_label)
+            %assign member variables
+            this.mean_array = mean_array;
+            this.error_array = error_array;
+            this.row_label = row_label;
+            this.col_label = col_label;
+            [n_row,n_col] = size(mean_array);
+            this.n_row = n_row;
+            this.n_col = n_col;
+            %assign default values for the member variables
+            this.n_sig = 1;
+            this.n_dec_for_no_error = 3;
+        end
+        
+        %METHOD: SET N DECIMIAL
+        %Set the number of significant figures used for the errors
+        %PARAMETERS:
+            %n_sig
+        function setNSig(this, n_sig)
+            this.n_sig = n_sig;
+        end
+        
+        %METHOD: SET N DECIMAL FOR NO ERROR
+        %Set the number of decimial places for values with no errors
+        %PARAMETERS:
+            %n_decimal
+        function setNDecimalForNoError(this, n_decimal)
+            this.n_dec_for_no_error = n_decimal;
+        end
+        
+        %METHOD: PRINT
+        %Output the table of values into a latex table to a specified file
+        %PARAMETERS:
+            %file_name: the file to print the latex table to
+        function print(this, file_name)
+            
+            %declare a string cell array, each cell represent a latex table cell
+            string_array = cell(this.n_row+1, this.n_col+1);
+            %top left corner is blank
+            string_array{1} = '';
+            %for each row
[…]

### 2018-03-21 printStringArrayToLatexTable.m

@@ -1,48 +1,0 @@
-%FUNCTION PRINT STRAING ARRAY TO LATEX TABLE
-%Print the string array into latex format to a file
-%PARAMETERS:
-    %string_array: 2 dimensional array of strings
-    %file_name: the file to print the latex table onto
-function printStringArrayToLatexTable(string_array, file_name)
-
-    %get the size of the string array
-    [n_row, n_column] = size(string_array);
-    
-    %start the latex code with a blank
-    latex_code = '';
-    
-    %for each row
-    for i_row = 1:n_row
-        
-        %for each column
-        for i_column = 1:n_column
-            
-            %append the string in the array to the latex table
-            latex_code = [latex_code, char(string_array(i_row,i_column))];
-            
-            %if this is not the last column, append '&'
-            if i_column ~= n_column
-                latex_code = strcat(latex_code, '&');
-            end
-            
-        end
-        
-        %if this is not the last row
-        if i_row ~= n_row
-            %append double back slash
-            latex_code = [latex_code, '\\ '];
-        end
-        
-        %if this is the first row, append \hline
-        if i_row == 1
-            latex_code = [latex_code, '\hline '];
-        end
-    end
-
-    %print the latex code to the file
-    file = fopen(fullfile(cd,file_name),'w');
-    fprintf(file,'%s', latex_code);
-    fclose(file);
-
-end
-

### 2018-03-21 quoteStdError.m

@@ -1,108 +1,0 @@
-%QUOTE STD ERROR
-%Returns the mean and std error bar in the form of error bars and the order of
-%magnitude, the number of significant figures is justified by using the
-%order of magnitude of the bootstrap error of the error
-%PARAMETERS:
-    %data: vector of data
-    %n_bootstrap: number of boostrap samples to use, if 1 use 1 sig fig, if
-    %2 use 2 sig fig for the error
-%RETURN:
-    %quote: string
-function quote = quoteStdError(data, n_bootstrap)
-
-    %get the number of data
-    n = numel(data);
-
-    %work out the mean
-    q = mean(data);
-    %get the std
-    err = std(data);
-    
-    %set the number of significant figures to be used for the error
-    if n_bootstrap == 1
-        error_sig_fig = 1;
-    elseif n_bootstrap == 2
-        error_sig_fig = 2;
-    %else, use bootstrap samples to see how much the error varies
-    else
-        %declare array of bootstrap samples of the error
-        error_bootstrap = zeros(n_bootstrap,1);
-        %for n_boostrap times
-        for i_bootstrap = 1:n_bootstrap
-            %get the bootstrap sample of the data
-            bootstrap_index = randi([1,n],n,1);
-            data_bootstrap = data(bootstrap_index);
-            %estimate the error of the bootstrap sample
-            error_bootstrap(i_bootstrap) = std(data_bootstrap);
-        end
-
-        %get the order of magnitude of the ratio between the error and the bootstrap variance
-        error_mag_order = orderMagnitude(std(error_bootstrap)/err);
-
-        %error_sig_fig is an integer, if it is equal to 0 or more
-        if error_mag_order >= 0
-            error_sig_fig = 1;
-        %else the number of significant figures is 2 or -error_mag_order+1
-        else
-            error_sig_fig = 2;
-            %error_sig_fig = -error_mag_order+1;
-        end
-    end
-
-    %E is the exponent of q2
-    E = floor(log10(abs(q)));
-    
-    %get the mantissa of the errors and q2
-    err = err * 10^-E;
-    q = q * 10^-E;
-    
-    %get the number of decimial places of the least significant figure of the error
-        %-floor(log10(err)) gets the exponent of the errors
-        %error_sig_fig - 1 increases the number of decimial places according to the number of significant figures of the error
-    dec_places = -floor(log10(err)) + error_sig_fig - 1;
[…]

### 2018-03-22 reports/thesis/chapters/5_inference.tex
Adjusted multiple hypothesis section.

@@
 
-In this section, the single hypothesis test will be extended and the multiple hypothesis testing \citep{shaffer1995multiple} shall be reviewed.
+In this section, the single hypothesis test will be extended and the multiple hypothesis testing \citep{shaffer1995multiple, dudoit2003multiple} shall be reviewed.
 
@@
 \end{equation}
+It is defined that $\text{FDR}=0$ when $R=0$.
 
@@
 This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as positive results.
-For completeness, if $p_{(1)}>\alpha/n$, then $k=1$ and the Bonferroni correction is recovered.
-The procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
+For the case where $p_{(1)}>\alpha/n$, then $k=1$ shall be chosen so that the Bonferroni correction is used instead.
+The BH procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
 However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.
@@
 \begin{table}
+    \centering
     \input{../tables/inference_error_rate1.tex_table}
@@
 \begin{table}
+    \centering
     \input{../tables/inference_error_rate2.tex_table}

### 2018-03-23 reports/thesis/chapters/5_inference.tex
Added example to multiple test.

@@
 
+\subsection{Examples}
+
+A few numerical examples will be shown here to explore the properties of the 3 different types of method to do multiple hypothesis testing.
+Two scenarios will be shown here.
+In the first case.
+1\,000 $\normal(0,1)$ test statistics are simulated, all test statistics are all null.
+In the second case, 800 null $\normal(0,1)$ and 200 alternative $\normal(2,1)$ test statistics were simulated.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/inference/nullhisto.eps}
+	\caption{A histogram of simulated of 1\,000 null test statistics.
+Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
+	\label{fig:inference_nullhisto}
+\end{figure}
+
+A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_nullhisto}.
+The critical boundaries are also shown.
+In the uncorrected case, the critical region is $\|Z\|>2$.
+Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08$.
+By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so.
+The Bonferroni correction performs well because it tested all the test statistics as negative correctly.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/inference/nullpvalues.eps}
+	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
+	\label{fig:inference_nullpvalues}
+\end{figure}
+
+The ordered $p$-values are shown in Figure \ref{fig:inference_nullpvalues}.
+The $p$-values form a straight line as a result of being uniformly distributed.
+The critical line is $0.0455\times\text{order}/1\,000$.
+This corresponds to the BH procedure and $p$-values below where the 2 curves intersect are considered positive results.
+In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure.
+As a result, the Bonferroni and BH procedure tested all test statistics to be negative correctly.
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.7\textwidth]{../figures/inference/althisto.eps}
+	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics.
+Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
+	\label{fig:inference_althisto}
+\end{figure}
+
+In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated.
+The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_althisto}.
+The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario.
+However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../figures/inference/alt_z_critical.txt}$.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/altpvalues.eps}
+        \caption{All $p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/altpvalues_zoom.eps}
+        \caption{Zoomed in}
+    \end{subfigure}
+    }
+    \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
+	\label{fig:altpvalues}
+\end{figure}
+
+The ordered $p$-values are shown in Figure \ref{fig:altpvalues}.
+This time there are $p$-values below the critical line according to the BH procedure, testing $\input{../figures/inference/alt_n_positive_bh.txt}$ test statistics as positive.
+The uncorrected test tested $\input{../figures/inference/alt_n_positive_uncorrected.txt}$ test statistics as positive.
+
+This example shows a number of things.
+The BH procedure adapts to the data to control for the FDR.
+The uncorrected method did produce more positive results but at a cost of more false positives.
+It may seem unimpressive that the BH procedure only tested $\input{../figures/inference/alt_n_positive_bh.txt}$ positive results, but this is to control the FDR or the number of false positives out of all positive results.
+
+Unfortunately not all 200 non-null test statistics were tested as positive, statisticians would describe it as not powerful.
+This is however unavoidable as a number of null and non-null test statistics will be similar in value.
+The aim of hypothesis testing is not to classify positive and negative results correctly, but rather highlight a number of test statistics which are worth investigating.
+
 \begin{table}

### 2018-03-23 scripts/multi_test_script.m

@@ -77,6 +77,14 @@ z_bh = z_bh(end);
 file_id = fopen(fullfile('reports','figures','inference','alt_z_critical.txt'),'w');
 fprintf(file_id,'%.2f',z_bh);
 fclose(file_id);
+%save the number of positive results for uncorrected
+file_id = fopen(fullfile('reports','figures','inference','alt_n_positive_uncorrected.txt'),'w');
+fprintf(file_id,'%.0f',sum(abs(X)>=z_uncorrected));
+fclose(file_id);
+%save the number of positive results for BH
+file_id = fopen(fullfile('reports','figures','inference','alt_n_positive_bh.txt'),'w');
+fprintf(file_id,'%.0f',sum(abs(X)>=z_bh));
+fclose(file_id);
 
 %plot histogram of test statistics
 fig = LatexFigure.main();

### 2018-03-26 reports/thesis/chapters/5_inference.tex
Completed multiple hypothesis section.

@@
 Assuming that the null hypothesis is true for all $Z_i$ for $i=1,2,\dotdotdot,n$, then by definition $\alpha\approx 4.55\%$ of the data will be tested positive, and falsely positive.
-Still under the same assumption, the probability of at least one positive result, known as the family-wise error rate (FWER) \citep{shaffer1995multiple}, is
+Still under the same assumption, the probability of at least one false positive result, known as the family-wise error rate (FWER) \citep{shaffer1995multiple}, is
 \begin{align}
@@
 \begin{equation}
-    \expectation[\text{FDR}] = \expectation\left[
+    \text{FDR} = \expectation\left[
         \dfrac{V}{R}
@@
 \end{equation}
-It is defined that $\text{FDR}=0$ when $R=0$.
+It is defined that $V/R=0$ when $R=0$.
 
@@
 
-In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated.
-The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_althisto}.
-The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario.
-However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../figures/inference/alt_z_critical.txt}$.
-
 \begin{figure}
@@
 
+In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated.
+The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_althisto}.
+The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario.
+However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../figures/inference/alt_z_critical.txt}$.
+
 The ordered $p$-values are shown in Figure \ref{fig:altpvalues}.
-This time there are $p$-values below the critical line according to the BH procedure, testing $\input{../figures/inference/alt_n_positive_bh.txt}$ test statistics as positive.
+There are $p$-values below the critical line according to the BH procedure, testing $\input{../figures/inference/alt_n_positive_bh.txt}$ test statistics as positive.
 The uncorrected test tested $\input{../figures/inference/alt_n_positive_uncorrected.txt}$ test statistics as positive.
@@
 
+The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null.
+Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ test statistics were tested positive.
+From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed, following the notation in Table \ref{table:inference_randomvariables}.
+The error rates can be estimated
+\begin{equation}
+	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
+\end{equation}
+\begin{equation}
+	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
+\end{equation}
+\begin{equation}
+	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
+	\ .
+\end{equation}
+The estimates of PCER and FDR is esentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the variance of the Beta distribution is used to quantify the error
+\begin{equation}
+	\text{standard error of }\widehat{\text{FWER}} = 
+	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
+\end{equation}
+where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$.
+
 \begin{table}
@@
 Error bars represent the standard errors after 1\,000 repeats of the experiment.}
+    \label{table:inference_error_rate1}
 \end{table}
@@
 Error bars represent the standard errors after 1\,000 repeats of the experiment.}
+     \label{table:inference_error_rate1}
 \end{table}
+
+Error rates estimations for the two scenarios are shown in Tables \ref{table:inference_error_rate1} and \ref{table:inference_error_rate1} for $N=1\,000$.
+These estimations show that the 3 different types of multiple hypothesis controls for different rates.
+The uncorrected, Bonferroni and BH controls the PCER, FWER and FDR to be equal or below $\alpha\approx 0.455$ respectively, equality is met when all the test statistics are all truly null.
 

### 2018-03-26 reports/thesis/chapters/5_inference.tex
Stared on empirical null section.

@@
 
+By treating each pixel as a hypothesis test, methods for multiple hypothesis can be deployed.
+At the start of the chapter, a scan from the \texttt{Sep16 120deg} dataset was compared to the \texttt{aRTist} simulation, obtaining a $z$ image.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/sub_z_image.eps}
+        \caption{$z$ image with section highlighted}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo.eps}
+        \caption{Histogram of section}
+    \end{subfigure}
+    }
+    \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown.}
+    \label{fig:inference_sub_z}
+\end{figure}
+
+A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_sub_z}.
+One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}$.
+However a quick look at the histogram will show that almost half of the pixels will be tested as positive.
+It is questionable whenever such number of positive results is sensible, in particular in an area where defects are not expected.
+
+The histogram showed that the majority of the $z$ statistics are centred around 2 and has a bell shaped curve, a characteristic of the Normal distribution.
+If the data shows that the majority is centred elsewhere then expected, is it right to then to test the majority of the data as positive?
+This is an example of model misspecification because it was assumed that the $z$ statistics are distributed as $\normal(0,1)$ when in reality they are distributed as $\normal(\mu_0,\sigma_0^2)$.
+
+The empirical null \citep{efron2004large} adjusts the assumptions made on the $z$ statistics according to the majority of the data and treating it as the norm, relaxing the assumptions needed.
+It requires the following assumptions: the majority of the data are truly null, non-null test statistics are rare and the null test statistics are Normal distributed.
+
+The method will be described here.
+Suppose the following test statistics were obtained $z_1,z_2,\dotdotdot,z_n$.
+First the histogram needs to be smoothed.
+\cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} will be used here because it has simpler mathematical properties.
+The kernel density estimate is
+\begin{equation}
+	\widehat{p}(z)=
+	\frac{1}{nh}
+	\sum_{i=1}^n\phi\left(
+		\dfrac{z_i-z}{h}
+	\right)
+\end{equation}
+where $h$ is the bandwidth. The bandwidth was chosen such that
+\begin{equation}
+	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
+\end{equation}
+where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.
+The parameters of the empirical null are estimated using the kernel density estimate.
+The resulting estimated density is shown in Figure \ref{fig:inference_sub_density_estimate}.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo_nocritical.eps}
+        \caption{Histogram}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/sub_z_parzen.eps}
+        \caption{Kernel density estimate}
+    \end{subfigure}
+    }
+    \caption{The density of the test statistics can be estimated using a histogram or a kernel density estimate.}
+    \label{fig:inference_sub_density_estimate}
+\end{figure}
+
+ Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$.
+is to be found.
+This is then used as the mean of the empirical null.
+The calculation of $\widehat{\mu}_0$ can be numerically using the Newton-Raphson method.
+Using the mode, the standard deviation of the empirical null is estimated using
+ \begin{equation}
+ 	\widehat{\sigma}_0 = \left[
+ 		\left.
+ 			-\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
+ 		\right|_{z=\widehat{\mu}_0}
+ 	\right]^{-1/2}
+ \end{equation}
+
+\subsection{Statistical Details}
+
+\subsection{Mode Finding}
+
+\subsection{Bandwidth Selection}
+
+\subsection{Results}
+
 \section{Empirical Null Filter}

### 2018-03-28 reports/thesis/chapters/5_inference.tex
Added emprirical null introduction.

@@
 In the uncorrected case, the critical region is $\|Z\|>2$.
-Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08$.
+Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08...$.
 By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so.
@@
 The $p$-values form a straight line as a result of being uniformly distributed.
-The critical line is $0.0455\times\text{order}/1\,000$.
+The critical line is $0.0455...\times\text{order}/1\,000$.
 This corresponds to the BH procedure and $p$-values below where the 2 curves intersect are considered positive results.
@@
 A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_sub_z}.
-One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}$.
+One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}...$.
 However a quick look at the histogram will show that almost half of the pixels will be tested as positive.
@@
     }
-    \caption{The density of the test statistics can be estimated using a histogram or a kernel density estimate.}
+    \caption{The density of the test statistics can be estimated using a histogram or a kernel density estimate.
+The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
     \label{fig:inference_sub_density_estimate}
@@
 
- Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$.
-is to be found.
-This is then used as the mean of the empirical null.
-The calculation of $\widehat{\mu}_0$ can be numerically using the Newton-Raphson method.
-Using the mode, the standard deviation of the empirical null is estimated using
+Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is to be found.
+This is then used as the mean of the empirical null \citep{efron2004large}.
+The calculation of $\widehat{\mu}_0$ can be numerically found using the Newton-Raphson method.
+Using the mode, the standard deviation of the empirical null is estimated using \citep{efron2004large}
 \begin{equation}
@@
 	\right]^{-1/2}
+	\ .
 \end{equation}
+In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../figures/inference/sub_null_sigma.txt}...$.
+It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.
 
-\subsection{Statistical Details}
+The empirical null is used to correct the test statistics $z_1,z_2,\dotdotdot,z_n$ to $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ by standardising the test statistics
+\begin{equation}
+	\zeta_i = \dfrac{
+		z_i - \widehat{\mu}_0
+	}
+	{
+		\widehat{\sigma}_0
+	}
+	\ .
+\end{equation}
+The corrected test statistics $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ are then used in any multiple hypothesis testing procedures.
+Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../figures/inference/sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../figures/inference/sub_null_critical1.txt}...$ and $\input{../figures/inference/sub_null_critical2.txt}...\leqslant Z$.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo_null.eps}
+        \caption{Histogram of $z$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/sub_z_p_values.eps}
+        \caption{Ordered $p$ values}
+    \end{subfigure}
+    }
+    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
+    \label{fig:inference_sub_z_critical_regions}
+\end{figure}
+
+These new critical regions are shown in Figure \ref{fig:inference_sub_z_critical_regions}.
+No positive results were found and the $p$-values are sensible as they look uniformly distributed.
+This demonstrated that the empirical null adjusts the parameters of the null distribution to fit the data in order to make sensible inference.
+
+In this section, a more mathematical approach to the empirical null will be taken to examine why and when this method works.
+Next computational concepts will be discussed such as on how the mode of the kernel density estimator is found and what makes a good bandwidth in the kernel density estimator.
+
+\subsection{Statistical Justification}
 
@@
 
-\subsection{Results}
-
 \section{Empirical Null Filter}
-
-\section{Results}

### 2018-03-29 reports/thesis/chapters/5_inference.tex
Completed introduction to empirical null.

@@
 \begin{equation}
-	\widehat{p}(z)=
+	\widehat{p}_Z(z)=
 	\frac{1}{nh}
@@
 
-\subsection{Statistical Justification}
+\subsection{More on the Empirical Null}
+
+\cite{efron2004large} invented the empirical null to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
+These problems are similar to the one observed at the start of this chapter.
+The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false,schwartzman2009empirical}.
+
+For formality, the null and alternative hypotheses shall be described here. Assume that the $z$ statistics under the null hypothesis are such that
+\begin{equation}
+	Z_i|H_0\sim\normal(\mu,\widehat{\sigma}_0^2)
+\end{equation}
+for $i=1,2,\dotdotdot,n$ and i.i.d. The hypotheses are then
+\begin{equation}
+	H_0:\mu = \widehat{\mu}_0
+\end{equation}
+and
+\begin{equation}
+	H_1:\mu\neq\widehat{\mu}_0
+	\ .
+\end{equation}
+Essentially null $z$ statistics are assumed to be Normal distributed, with parameters using the empirical null. Statistics which deviates too much from $\widehat{\mu}_0$ are considered to be positive.
+
+The distribution of the $z$ statistics can be described using a mixture model. Let the random variable $Z$ have the probability density function
+\begin{equation}
+	p_Z(z) =
+	\pi_0 p_{Z|H_0}(z) + \pi_1 p_{Z|H_1}(z)
+\end{equation}
+where $0\leqslant\pi_0\leqslant 1$ and  $\pi_1 = 1-\pi_0$. In addition, the null distribution is
+\begin{equation}
+	p_{Z|H_0}(z) = 
+	\dfrac{1}{\sqrt{2\pi}\widehat{\sigma}_0}
+	\exp\left[
+		-\dfrac{1}{2}
+		\left(
+			\dfrac{z-\widehat{\mu}_0}{\widehat{\sigma}_0}
+		\right)^2
+	\right]
+\end{equation}
+as it was assumed to be Normal. The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified.
+
+The empirical null parameters can be obtained from the following.
+Assume that $\pi_0$ is large, say bigger than 0.9 \citep{efron2004large}, and at and around the mode the probability density function is dominated by the null distribution.
+This implies that
+\begin{equation}
+	p_{Z}(z) \approx \pi_0 p_{Z|H_0}(z)
+\end{equation}
+for values of $z$ around the mode.
+Finding the maximum for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution.
+This justifies the use of the mode for the empirical null mean \citep{efron2004large}
+\begin{equation}
+	\widehat{\mu}_0 = \argmax\widehat{p}_Z(z) \ .
+\end{equation} 
+The empirical null standard deviation can be obtained by noting that
+\begin{equation}
+	p_{Z}(z) = 
+	\dfrac{\pi_0}{\sqrt{2\pi}\widehat{\sigma}_0}
+	\exp\left[
+		-\dfrac{1}{2}
+		\left(
+			\dfrac{z-\widehat{\mu}_0}{\widehat{\sigma}_0}
+		\right)^2
+	\right] \ .
+\end{equation}
+Taking the log of both sides
+\begin{equation}
+	\ln p_{Z}(z) = 
+	\ln\left[
+		\dfrac{\pi_0}{\sqrt{2\pi}\widehat{\sigma}_0}
+	\right]
+	-\dfrac{1}{2}
+	\left(
+		\dfrac{z-\widehat{\mu}_0}{\widehat{\sigma}_0}
+	\right)^2
+	\ .
+\end{equation}
+Taking derivatives of the log density
+\begin{equation}
+	\dfrac{\partial}{\partial z} \ln p_{Z}(z) =
+	-\left(
+		\dfrac{
+			z-\widehat{\mu}_0
+		}
+		{
+			\widehat{\sigma}_0^2
+		}
+	\right)
+\end{equation}
+\begin{equation}
+	\dfrac{\partial^2}{\partial^2 z} \ln p_{Z}(z) =
+	-\dfrac{
+		1
+	}
+	{
+		\widehat{\sigma}_0^2
+	}
+\end{equation}
+which motivates the estimator \citep{efron2004large}
+\begin{equation}
+	\widehat{\sigma}_0 = \left[
+		\left.
+			-\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
+		\right|_{z=\widehat{\mu}_0}
+	\right]^{-1/2}
+	\ .
+\end{equation}
+The evaluation of $z=\widehat{\mu}_0$ is used as in that region, one would hope that null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.
+
+This method does not need estimations of $\pi_0$ which makes it quite useful.
+The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}.
+Because of the assumptions made on the empirical null, the easiest method is
+\begin{equation}
+	\widehat{\pi}_0 = \dfrac{\widehat{p}_Z(z)}{p_{Z|H_0}(\widehat{\mu}_0)}
+	\ .
+\end{equation}
+\cite{efron2004large} also motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.
 

### 2018-03-30 reports/thesis/chapters/5_inference.tex
Started on mode finding.

@@
 	\right)
+	\label{eq:inference_kernel_density_estimate}
 \end{equation}
@@
 
+The mode can be found by solving for $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$.
+This cannot be solved in closed form easily and should be done numerically.
+The  Newton-Raphson method can be used to solve $\hat{p}_Z'(z) = 0$ for $z$.
+Instead the log space will be used, solving
+\begin{equation}
+	\dfrac{
+		\partial
+	}
+	{
+		\partial z
+	}
+	\ln\widehat{p}_Z(z)
+	= 0
+\end{equation}
+for $z$. This will at least find stationary points.
+
+The Newton-Raphson method is an iterative algorithm and requires an initial value $z^{(0)}$. The iterative step is
+\begin{equation}
+	z^{(r+1)} =
+	z^{(r)}
+	-\dfrac{
+		\left.
+			\dfrac{
+				\partial
+			}
+			{
+				\partial z
+			}
+			\ln\widehat{p}_Z(z)
+		\right|_{z = z^{(r)}}
+	}
+	{
+		\left.
+			\dfrac{
+				\partial^2
+			}
+			{
+				\partial z^2
+			}
+			\ln\widehat{p}_Z(z)
+		\right|_{z = z^{(r)}}
+	} 
+\end{equation}
+for $r=0,1,2,3,\dotdotdot$ until some convergence condition is met. The derivatives for the log density can be obtained via the following. Recall that the kernel density estimate is
+\begin{equation}
+	\widehat{p}_Z(z)=
+	\frac{1}{nh}
+	\sum_{i=1}^n\phi\left(
+		\dfrac{z_i-z}{h}
+	\right)
+	\tag{\ref{eq:inference_kernel_density_estimate}}
+\end{equation}
+so that the log density is
+\begin{equation}
+	\ln\widehat{p}_Z(z)=
+	\ln\left(
+		\dfrac{1}{nh}
+	\right)
+	+
+	\ln\left[
+		\sum_{i=1}^n
+		\phi\left(
+			\dfrac{
+				z_i - z
+			}
+			{
+				h
+			}
+		\right)
+	\right]
+	\ .
+\end{equation}
+Taking the first derivative
+\begin{equation}
+	\dfrac{
+		\partial
+	}
+	{
+		\partial z
+	}
+	\ln\widehat{p}_Z(z)
+	=
+	\dfrac{
+		1
+	}
+	{
+		\sum_{i=1}^n
+		\phi\left(
+			\dfrac{
+				z_i - z
+			}
+			{
+				h
+			}
+		\right)
+	}
+	\times
+	\sum_{i=1}^n
+	\phi'\left(
+		\dfrac{
+			z_i - z
+		}
+		{
+			h
+		}
+	\right)
+	\left(
+		-\dfrac{
+			1
+		}
+		{
+			h
+		}
+	\right)
+	\ .
+\end{equation}
+Using the fact that $\phi(z)=(2\pi)^{-1/2}\exp(-z^2/2)$, then $\phi'(z)=-z\phi(z)$. This can be used to simplify the equation to be
+\begin{equation}
+	\dfrac{
+		\partial
+	}
+	{
+		\partial z
+	}
+	\ln\widehat{p}_Z(z)
+	=
+	\dfrac{
+		\sum_{i=1}^n
+		\phi\left(
+			\dfrac{
+				z_i - z
+			}
+			{
+				h
+			}
+		\right)
+		\left(
+			\dfrac{
+				z_i - z
+			}
+			{
+				h
+			}
+		\right)
+	}
+	{
+		h
+		\sum_{i=1}^n
+		\phi\left(
+			\dfrac{
+				z_i - z
+			}
+			{
+				h
+			}
+		\right)
+	}
+	\ .
+\end{equation}
+
+Taking the derivative again
+\begin{multline}
+	\dfrac{
+		\partial^2
+	}
+	{
+		\partial z^2
+	}
+	\ln\widehat{p}_Z(z)
+	=
+	\left[
+		h\sum_{i=1}^n
+		\phi\left(
+			\dfrac{
+				z_i-z
+			}
+			{
+				h
+			}
+		\right)
+	\right]^{-2}
+	\times
+	\left\{
+		h\left[
+			\sum_{i=1}^n
+			\phi\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+		\right]
+	\right.
+	\\
+	\left.
+		\times
+		\sum_{i=1}^n\left[
+			\phi'\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+			\left(
+				-\dfrac{
+					1
+				}
+				{
+					h
+				}
+			\right)
+			\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+			+\phi\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+			\left(
+				-\dfrac{
+					1
+				}
+				{
+					h
+				}
+			\right)
+		\right]
+	\right.
+	\\
+	\left.
+		-
+		\left[
+			\sum_{i=1}^n
+			\phi\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+			\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+		\right]
+		\left[
+			h\sum_{i=1}^n
+			\phi'\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+			\left(
+				-\dfrac{
+					1
+				}
+				{
+					h
+				}
+			\right)
+		\right]
+	\right\}
+	\ .
+\end{multline}
+Using the fact that $\phi'(z)=-z\phi(z)$, then it can be simplified to
+\begin{multline}
+	\dfrac{
+		\partial^2
+	}
+	{
+		\partial z^2
+	}
+	\ln\widehat{p}_Z(z)
+	=
+	\left[
+		h\sum_{i=1}^n
+		\phi\left(
+			\dfrac{
+				z_i-z
+			}
+			{
+				h
+			}
+		\right)
+	\right]^{-2}
+	\times
+	\left\{
+		\left[
+			\sum_{i=1}^n
+			\phi\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+		\right]
+	\right.
+	\\
+	\left.
+		\times
+		\left[
+			\sum_{i=1}^n
+			\phi\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+			\left(
+				\left(
+					\dfrac{
+						z_i-z
+					}
+					{
+						h
+					}
+				\right)^2
+				-1
+			\right)
+		\right]
+		-
+		\left[
+			\sum_{i=1}^n
+			\phi\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+		\right.
+	\right.
+	\\
+	\left.
+		\left.
+			\left(
+				\dfrac{
+					z_i-z
+				}
+				{
+					h
+				}
+			\right)
+		\right]^2
+	\right\}
+	\ .
+\end{multline}
+
 \subsection{Bandwidth Selection}

### 2018-04-03 reports/thesis/chapters/5_inference.tex
Added convergence conditions.

@@
 \end{equation}
-
 Taking the derivative again
@@
 
+It was chosen that convergence is met when either 10 update steps were taken or when
+\begin{equation}
+	\left\|
+		\dfrac{
+			\partial
+		}
+		{
+			\partial z
+		}
+	\ln\widehat{p}_Z(z)
+	\right\|
+	<10^{-5}
+\end{equation}
+at the current step. This was chosen arbitrary to speed up the algorithm without losing too much accuracy. At the end of the algorithm, for a successful convergence it was required, in addition, that
+\begin{equation}
+	\left.
+		\dfrac{
+			\partial^2
+		}
+		{
+			\partial z^2
+		}
+		\ln\widehat{p}_Z(z)
+	\right|_{z=\widehat{\mu}_0}
+	< 0 \ .
+\end{equation}
+Following a successful convergence, the estimator $\widehat{\sigma}_0$ can be calculated straight away.
+
+The algorithm does depend on the initial value so using different initial values is recommended.
+It was chosen here to use the quartiles of the data as the initial values and then select the best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of the different initial values.
+Should the algorithm still fail, a random data point is selected to be the initial value until a successful convergence is achieved.
+The Newton-Raphson method can fail if it converges to a stationary point other than a global maximum, for example a local maxima or a point of inflection.
+
 \subsection{Bandwidth Selection}

### 2018-04-03 reports/thesis/chapters/5_inference.tex
Started on bandwidth selection.

@@
 	\ .
+	\label{eq:inference_zeta}
 \end{equation}
@@
 
+The choice of the bandwidth $h$ is important for the kernel density estimator.
+It controls how smooth the kernel density estimator is, with higher values of $h$ producing smoother curves \citep{friedman2001elements}.
+Cross validation methods do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
+Another option are rules of thumb \citep{silverman1986density, sheather2004density} and are typically of the form
+\begin{equation}
+	h = bn^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right)
+\end{equation}
+where $b=0.9$ \citep{silverman1986density}.
+This rule of thumb was developed with consideration of bimodal Normal distributions \citep{silverman1986density}.
+Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{sheather2004density}.
+
+In the context of the empirical null, the kernel density estimator is only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$.
+Thus a good bandwidth is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate.
+However exact properties of these estimators based on the kernel density estimators can be rather complicated.
+Empirical properties shall be studied here.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull1.eps}
+        \caption{$\mu_0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull2.eps}
+        \caption{$\sigma_0$}
+    \end{subfigure}
+    }
+    \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
+    \label{fig:inference_ZNull1}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull3.eps}
+        \caption{3D plot}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull4.png}
+        \caption{Heatmap}
+    \end{subfigure}
+    }
+    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
+    \label{fig:inference_ZNull2}
+\end{figure}
+
+An experiment was conducted to investigate the behaviour of the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, on a dataset of simulated all null $\normal(0,1)$.
+Various values of $h$ and $n$ were investigated.
+In reality non-null test statistics may appear in the dataset but they should not be too common and interfere with the density estimate too much.
+For a given $h$ and $n$, 50 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation.
+The median squared error for each of the estimators were plotted as shown in Figure \ref{fig:inference_ZNull1}.
+
+$\widehat{\mu}_0$ has low median squared error for large bandwidths, in particular for low $n$.
+This is because smoother curves prevents any false bimodal features appearing, making it easier to find the mode.
+
+A smooth valley can be seen for the median squared error for $\widehat{\sigma}_0$.
+It appears for a given $n$, there exist a bandwidth which minimise the median squared error.
+However the rules of thumb does not optimise for $\widehat{\sigma}_0$ and undershoots it.
+This can be particularly seen in Figure \ref{fig:inference_ZNull2} where the median values of $\widehat{\sigma}_0$ are plotted.
+In this simulation, the true value is $\sigma_0=1$ and all rules of thumb produced biased estimates, in particular underestimates it.
+
+Overestimates and underestimates are both dangerous, but it depends on the importance of false positives and false negatives.
+This is because $\widehat{\sigma}_0$ is used to rescale the test statistics accordingly.
+Recall that the corrected test statistics are
+\begin{equation}
+	\zeta_i = \dfrac{
+		z_i - \widehat{\mu}_0
+	}
+	{
+		\widehat{\sigma}_0
+	}
+	\ .
+	\tag{\ref{eq:inference_zeta}}
+\end{equation}
+Low values of $\widehat{\sigma}_0$ will produce high values in magnitude of $\zeta_i$, potentially testing more of these test statistics as positive.
+High values of $\widehat{\sigma}_0$ does the opposite.
+Large number of positive results can led to more false positive results and vice versa.
+
 \section{Empirical Null Filter}

### 2018-04-04 reports/thesis/chapters/5_inference.tex
Finished bandwidth selection.

@@
 	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
+	\label{eq:inference_ourruleofthumb}
 \end{equation}
@@
 
+The optimal bandwidth for a given $n$ was found numerically.
+Such a relationship can be seen clearly seen in Figure \ref{fig:inference_ZNull_mse_plot} which plots the log mean squared error against the bandwidth for various $n$.
+A local quadratic regression \citep{friedman2001elements} was fitted and this was used to find the bandwidth which minimises the log squared error for a given $n$.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot1.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot5.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot9.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot12.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot16.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot20.eps}
+    \end{subfigure}
+    }
+    \caption{A local quadratic regression was fitted on the log mean squared error for estimating $\sigma_0$ against the bandwidth.
+The estimator $\widehat{\sigma}_0$ uses the kernel density estimator fitted onto $n$ simulated standard Normal data.
+Boxplots were used to represent the variation of the error from 50 repeats.}
+    \label{fig:inference_ZNull_mse_plot}
+\end{figure}
+
+A relationship between the optimal bandwidth and $n$ was attempted to be found. It was assumed such a relationship has the linear from
+\begin{equation}
+	h_{\text{optimal}} = b n^{-1/5} + a
+\end{equation}
+where $b$ and $a$ are parameters to be fitted.
+Figure \ref{fig:inference_ZNull_mserule_of_thumb} show the fitting of an identity link Gamma GLM in order to estimate $b$ and $a$.
+The estimated parameters are shown in Table \ref{table:inference_ZNull_mse_glm_estimate}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/inference/ZNull_mserule_of_thumb.eps}
+	\caption{An identity link Gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$.
+The boxplot show the bootstrap error in finding the optimal bandwidth, which is only there for illustration purposes.}
+	\label{fig:inference_ZNull_mserule_of_thumb}
+\end{figure}
+
+\begin{table}
+	\centering
+	\input{../tables/ZNull_mse_glm_estimate.txt}
+	\caption{Estimated and standard error gradient and intercept from the linear relationship in Figure \ref{fig:inference_ZNull_mserule_of_thumb}.}
+	\label{table:inference_ZNull_mse_glm_estimate}
+\end{table}
+
+The results show that the rules of thumb can be improved if a small bias is added to it.
+This is because an intercept was found when fitting a linear relationship between the optimal bandwidth and $n^{-1/5}$.
+Adding this bias should improve the performance of the estimator $\widehat{\sigma}_0$.
+The gradient is similar to the rules of thumb in the literature \citep{sheather2004density}.
+
+Those familiar with local quadratic regressions would know that a kernel and a smoothness parameter need to be specified \citep{friedman2001elements}.
+In these plots a Gaussian kernel was used with smoothness parameter $\input{../tables/ZNull_bandwidth.txt}$.
+The smoothness parameter $\input{../tables/ZNull_bandwidth.txt}$ was chosen from a quick inspection of the curves.
+The units of the smoothness parameter is not too important here.
+But one should note that the smoothness parameter would affect the solution to the optimal bandwidth.
+
+To take into the sensitivity to the smoothness parameter, the whole analysis was repeated using various smoothness parameters.
+The gradient and intercept for various smoothness parameters are shown in Figure \ref{fig:inference_ZNull_msesensitive}.
+It can seen that the intercept is fairly stable, including the gradient at smoothness parameter around $\input{../tables/ZNull_bandwidth.txt}$.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/inference/ZNull_msesensitive.eps}
+	\caption{Finding the relationship between the optimal bandwidth and $n^{-1/5}$ was repeated for various smoothness parameters in the local quadratic regression.
+Error bars represent the standard error.}
+	\label{fig:inference_ZNull_msesensitive}
+\end{figure}
+
+In conclusion, a small bias added to the rule of thumb will improve the performance of the estimator $\widehat{\sigma}_0$.
+\cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggest the use of $b=0.9$ rather than $b=1.06$.
+Following from this, it was chosen that the intercept shall be added to Silverman's rule of thumb for the use in the empirical null
+\begin{equation}
+	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
+	\ .
+	\tag{\ref{eq:inference_ourruleofthumb}}
+\end{equation}
+
 \section{Empirical Null Filter}

### 2018-04-05 reports/thesis/chapters/5_inference.tex
Added plotPValues method, added alternative example.

@@
 \end{equation}
-where $\pi_0=n_0/n$ \citep{benjamini1995controlling}, this is usually unknown in practice.
+where $\pi_0=n_0/n$ \citep{benjamini1995controlling}, which is usually unknown in practice.
 
@@
 
-A few numerical examples will be shown here to explore the properties of the 3 different types of method to do multiple hypothesis testing.
+A few numerical examples will be shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing.
 Two scenarios will be shown here.
-In the first case.
-1\,000 $\normal(0,1)$ test statistics are simulated, all test statistics are all null.
-In the second case, 800 null $\normal(0,1)$ and 200 alternative $\normal(2,1)$ test statistics were simulated.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/inference/nullhisto.eps}
+In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics are all null.
+In the second case, 800 null $\normal(0,1)$ and 200 alternative $\normal(2,1)$ independent test statistics were simulated.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/inference/nullhisto.eps}
 	\caption{A histogram of simulated of 1\,000 null test statistics.
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/inference/nullpvalues.eps}
+	\includegraphics[width=0.8\textwidth]{../figures/inference/nullpvalues.eps}
 	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
@@
 	\centering
-	\includegraphics[width = 0.7\textwidth]{../figures/inference/althisto.eps}
+	\includegraphics[width = 0.8\textwidth]{../figures/inference/althisto.eps}
 	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics.
@@
 	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/altpvalues.eps}
-        \caption{All $p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/altpvalues_zoom.eps}
-        \caption{Zoomed in}
-    \end{subfigure}
-    }
+	\includegraphics[width=0.8\textwidth]{../figures/inference/altpvalues.eps}
     \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
@@
 The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null.
-Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ test statistics were tested positive.
-From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed, following the notation in Table \ref{table:inference_randomvariables}.
+Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ number of test statistics were observed to be tested positive.
+From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed.
+In other words, they are realisations of the random variables defined in Table \ref{table:inference_randomvariables}.
 The error rates can be estimated
@@
 However a quick look at the histogram will show that almost half of the pixels will be tested as positive.
-It is questionable whenever such number of positive results is sensible, in particular in an area where defects are not expected.
+It is questionable whether such number of positive results is sensible, in particular in an area where defects are not expected.
 
@@
 
-\cite{efron2004large} invented the empirical null to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
+\cite{efron2004large} was motivated to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
 These problems are similar to the one observed at the start of this chapter.
@@
 Cross validation methods do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
-Another option are rules of thumb \citep{silverman1986density, sheather2004density} and are typically of the form
-\begin{equation}
-	h = bn^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right)
+Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are typically of the form
+\begin{equation}
+	h = bn^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right)
 \end{equation}
@@
 \begin{equation}
-	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
+	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right) + 0.16
 	\ .
@@
 
+\subsection{Further Discussion}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_image.eps}
+        \caption{$z$ image}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_image_2.eps}
+        \caption{Sample from left}
+    \end{subfigure}
+    }
+    \caption{$z$ image from comparing a scan with \texttt{aRTist}. A sub-sample containing a defect is shown. Highlighted in red are significant pixels.}
+    \label{fig:inference_alt_empirical_z_image}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_histo_null.eps}
+        \caption{Histogram}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_parzen.eps}
+        \caption{Kernel density estimate}
+    \end{subfigure}
+    }
+    \caption{Histogram and kernel density estimate of the $z$ statistics, taken from the sub-sample.}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/inference/alt_empirical_z_p_values.eps}
+	\caption{Ordered $p$ values corrected for the empirical null.}
+\end{figure}
+
 \section{Empirical Null Filter}

### 2018-04-05 inference/ZTester.m

@@ -401,6 +401,29 @@ classdef ZTester < handle
             plot(z_plot,(1-this.p0)*this.n_test*this.estimateH1Density(z_plot));
         end
         
+        %METHOD: PLOT P VALUES
+        %Plot the p values in order with the BH critical region
+        function plotPValues(this)
+            %get array of x axis values : integers representing the order
+            order_index = 1:this.n_test;
+            %scatter plot the ordered p values
+            scatter(1:this.n_test, sort(reshape(this.p_image,[],1)),'.');
+            xlabel('order');
+            ylabel('p value');
+            hold on;
+            %plot the BH critical line
+            ax = gca;
+            ax_area = area(order_index,this.size/this.n_test*order_index);
+            %set properties of curves
+            ax_area.FaceAlpha = 0.2;
+            ax_area.LineStyle = '--';
+            ax_area.EdgeColor = ax.ColorOrder(2,:);
+            ax_area.FaceColor = ax.ColorOrder(2,:);
+            ax = gca;
+            ax.XScale = 'log';
+            ax.YScale = 'log';
+        end
+        
     end
     
 end

### 2018-04-06 reports/thesis/chapters/5_inference.tex
Empirical null complete.

@@
 
+A further example will be given here.
+A $200\times200$ sub-sample, containing a defect, was taken as shown in Figure \ref{fig:inference_alt_empirical_z_image}.
+The histogram of the test statistics are shown in Figure \ref{fig:inference_alt_empirical_z_histogram}.
+It can be seen that the null distribution is not centred at zero, however the empirical null takes that into account.
+The estimation of the empirical null parameters are robust as it only depends on the density estimate at the mode only, it should not be affected by non-null test statistics.
+
 \begin{figure}
@@
     \caption{Histogram and kernel density estimate of the $z$ statistics, taken from the sub-sample.}
-\end{figure}
+    \label{fig:inference_alt_empirical_z_histogram}
+\end{figure}
+
+The BH procedure can be conducted, corrected for the empirical null.
+The $p$-values are shown in \ref{fig:inference_alt_empirical_z_p_values}, a number of them are significant.
+The significant pixels are shown in red in Figure \ref{fig:inference_alt_empirical_z_image}.
+The majority of the significant pixels are cluster together and highlighting the defect.
+Not all of the defect was tested positive, but a good number of them are.
+This should be enough to raise suspicion in that particular area.
 
@@
 	\caption{Ordered $p$ values corrected for the empirical null.}
-\end{figure}
+	\label{fig:inference_alt_empirical_z_p_values}
+\end{figure}
+
+Only a few pixels were falsely tested as positive, however they are typically isolated single pixels.
+Isolated positive pixels should be discarded as they are more than likely to be tested positive by random chance.
+The technician should of improved the resolution of the x-ray apparatus if one is looking for defects, a or two pixel in size, for the given resolution.
+
+Clusters of significant pixels should raise suspicions.
+One could create a binary image, assigning a Boolean value whether that pixel is tested positive or not.
+A binary image filter, such as erode followed by a dilate, can be used to remove isolate significant pixels and emphasise the cluster of significant pixels.
+
+The empirical null is a good tool for defect detection under model misspecification.
+One possible implementation is to spilt the $z$ image into a grid and conduct inference in each section separately.
+There are problems with this though.
+The first problem is that how the grid is overlaid can be arbitrary, for example the grid can be translated to produce different sections.
+Secondly one could ask how the results from each section are combined \citep{efron2008simultaneous}?
+The empirical null filter is another implementation for the empirical null which only requires a window size to be specified.
 

### 2018-04-06 reports/thesis/chapters/5_inference.tex
Added qq plot in inference chapter.

@@
     \includegraphics[width=0.7\textwidth]{../figures/inference/sig_pixels.eps}
-    \caption{Signficiant pixels highlighted at the $z_\alpha = 2$ significance level.}
+    \caption{Significant pixels highlighted at the $z_\alpha = 2$ significance level.}
     \label{fig:sig_pixels}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{../figures/inference/z_histo.eps}
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    	\includegraphics[width=\textwidth]{../figures/inference/z_histo.eps}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+    	\includegraphics[width=\textwidth]{../figures/inference/z_qq.eps}
+    \end{subfigure}
+	}
     \caption{Histogram of the $z$ statistics}
@@
 \section{Empirical Null Filter}
+
+The empirical null filter is an extension to the empirical null. In this setting, the parameters of the empirical null varies spatially. Let $Z_{x,y}$ be the test statistic at position $(x,y)$, then
+\begin{equation}
+	Z_{x,y}\sim\normal\left(
+		\mu_{0,x,y},\sigma_{0,x,y}^2
+	\right)
+\end{equation}
+where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the empirical null mean and standard deviation at position $(x,y)$ respectively. The empirical null filter aims to estimate these parameters.
+
+The method is the following.
+A window size needs to be specified, say $201\times201$.
+The window is placed over and centred at pixel $(x,y)$ capturing the pixels $z_{i,j}$ for $x-100\leqslant i \leqslant x+100$ and $y-100\leqslant j \leqslant y+100$.
+The estimators $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ are the empirical null mean and standard deviation estimators, respectively, using the pixels captured in that window.
+This is then repeated for all $x$ and $y$.
+The $z$ statistics are then corrected using
+\begin{equation}
+	\zeta_{x,y} = 
+	\dfrac{
+		z_{x,y}-\widehat{\mu}_{0,x,y}
+	}
+	{
+		\widehat{\sigma}_{0,x,y}
+	}
+\end{equation}
+and only the corrected test statistics are used in the BH procedure.
+
+There are ways to speed up the implementation of the empirical null filter by sacrificing accuracy.
+For example, instead of estimating the empirical null parameters for every pixel, a number of them can be estimated and then the remaining values can be interpolated.
+However it was found that interpolating $\widehat{\sigma}_{0,x,y}$ can yield highly varying results.
+To avoid this problem, it can be assumed that $\sigma_{0,x,y}=\sigma_0$ for all $x$ and $y$.
+Then the estimator $\widehat{\sigma}_0$ is the empirical null standard deviation estimator using all location corrected $z$ test statistics.

### 2018-04-06 inference/EmpericalConvolution.m

@@ -141,7 +141,7 @@ classdef EmpericalConvolution < handle
         %This is worked out using the emperical null of all mean corrected z statistics
         function setVarUniformNull(this)
             z_tester_all = ZTester((this.z_image - this.mean_null));
-            z_tester_all.estimateNull(1000);
+            z_tester_all.estimateNull();
             this.var_uniform_null = z_tester_all.var_null;
         end
         

### 2018-04-06 reports/thesis/chapters/5_inference.tex
Made script for inference example, changed labelling in inference chapter.

@@
 Model misspecification appears to be the main source of error.
-The $z$ statistics can be inspected using a histogram, as shown in Figure \ref{fig:z_histo}.
-The histogram of the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect.
+The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:z_histo}.
+It can be seen that the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect.
 However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.
@@
     	\includegraphics[width=\textwidth]{../figures/inference/z_histo.eps}
+    	\caption{Histogram}
     \end{subfigure}
@@
     	\includegraphics[width=\textwidth]{../figures/inference/z_qq.eps}
-    \end{subfigure}
-	}
-    \caption{Histogram of the $z$ statistics}
+    	\caption{QQ plot}
+    \end{subfigure}
+	}
+    \caption{Distribution of the  $z$ statistics with the BH procedure critical region}
     \label{fig:z_histo}

### 2018-04-06 scripts/empirical_null_script.m

@@ -7,54 +7,7 @@ clc;
 close all;
 clearvars;
 
-%set random seed
-rand_stream = RandStream('mt19937ar','Seed',uint32(3538096789));
-
-%load data and add shading correction
-block_data = AbsBlock_Sep16_120deg();
-block_data.addDefaultShadingCorrector();
-
-%get random permutation for each image
-index = rand_stream.randperm(block_data.n_sample);
-n_test = 1;
-n_train = block_data.n_sample - n_test;
-training_index = index(1:n_train);
-test_index = index((n_train+1):(n_train+n_test));
-
-%get a phanton image and aRTist image
-aRTist = block_data.getShadingCorrectedARTistImage(ShadingCorrector(),1:block_data.reference_white);
-
-%get the segmentation image
-segmentation = block_data.getSegmentation();
-%get the number of segmented images
-n_pixel = sum(sum(segmentation));
-
-%get the training images
-training_stack = block_data.loadImageStack(training_index);
-%segment the image
-training_stack = reshape(training_stack,block_data.area,n_train);
-training_stack = training_stack(reshape(segmentation,[],1),:);
-%get the segmented mean and variance greyvalue
-training_mean = mean(training_stack,2);
-training_var = var(training_stack,[],2);
-
-%train glm using the training set mean and variance
-model = GlmGamma(1,IdentityLink());
-model.setShapeParameter((n_train-1)/2);
-model.train(training_mean,training_var);
-
-%predict variance given aRTist
-var_predict = reshape(model.predict(reshape(aRTist,[],1)),block_data.height, block_data.width);
-
-%get the test images
-test = block_data.loadImageStack(test_index);
-
-%get the z statistic
-z_image = (test - aRTist)./sqrt(var_predict);
-%set non segmented pixels to be nan
-z_image(~segmentation) = nan;
-%find the number of non-nan pixels
-m = sum(sum(~isnan(z_image)));
+set_up_inference_example;
 
 %define the coordinates of the subsample
 row_subsample = 1100:1299; %array of row indicies

### 2018-04-06 scripts/set_up_inference_example.m

@@ -1,0 +1,48 @@
+%set random seed
+rand_stream = RandStream('mt19937ar','Seed',uint32(3538096789));
+
+%load data and add shading correction
+block_data = AbsBlock_Sep16_120deg();
+block_data.addDefaultShadingCorrector();
+
+%get random permutation for each image
+index = rand_stream.randperm(block_data.n_sample);
+n_test = 1;
+n_train = block_data.n_sample - n_test;
+training_index = index(1:n_train);
+test_index = index((n_train+1):(n_train+n_test));
+
+%get a phanton image and aRTist image
+aRTist = block_data.getShadingCorrectedARTistImage(ShadingCorrector(),1:block_data.reference_white);
+
+%get the segmentation image
+segmentation = block_data.getSegmentation();
+%get the number of segmented images
+n_pixel = sum(sum(segmentation));
+
+%get the training images
+training_stack = block_data.loadImageStack(training_index);
+%segment the image
+training_stack = reshape(training_stack,block_data.area,n_train);
+training_stack = training_stack(reshape(segmentation,[],1),:);
+%get the segmented mean and variance greyvalue
+training_mean = mean(training_stack,2);
+training_var = var(training_stack,[],2);
+
+%train glm using the training set mean and variance
+model = GlmGamma(1,IdentityLink());
+model.setShapeParameter((n_train-1)/2);
+model.train(training_mean,training_var);
+
+%predict variance given aRTist
+var_predict = reshape(model.predict(reshape(aRTist,[],1)),block_data.height, block_data.width);
+
+%get the test images
+test = block_data.loadImageStack(test_index);
+
+%get the z statistic
+z_image = (test - aRTist)./sqrt(var_predict);
+%set non segmented pixels to be nan
+z_image(~segmentation) = nan;
+%find the number of non-nan pixels
+m = sum(sum(~isnan(z_image)));

### 2018-04-06 reports/thesis/chapters/5_inference.tex
Organised the inference script, made script and section on empirical null filter, removed and changed some of ZTester methods.

@@
 Then the estimator $\widehat{\sigma}_0$ is the empirical null standard deviation estimator using all location corrected $z$ test statistics.
+
+The empirical null filter was used on the example at the start of the chapter.
+It was used on a grid of $20\times 20$ points, the remaining values were interpolated.
+It was also assumed the empirical null standard deviation was constant, the methodology discussed in the previous paragraph.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/filter_z_image.eps}
+        \caption{$z$ image}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/filter_p_image.eps}
+        \caption{$\log p$-value image}
+    \end{subfigure}
+    }
+    \caption{The $z$ image and $p$-value image after using the empirical null filter.}
+    \label{fig:inference_filter_z_p_image}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/filter_histogram.eps}
+        \caption{Histogram of $z$ statistics}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/filter_p.eps}
+        \caption{Ordered $p$ values}
+    \end{subfigure}
+    }
+    \caption{Histogram of $z$ statistics and the corresponding ordered $p$-values}
+    \label{fig:inference_filter_z_ordered_p}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_sig_image.eps}
+	\caption{Using the empirical null filter, significant pixels were highlighted in red.} 
+	\label{fig:inference_filter_sig_image}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_mean_null.eps}
+	\caption{The estimated empirical null mean} 
+	\label{fig:inference_filter_mean_null}
+\end{figure}

### 2018-04-06 scripts/filter_script.m

@@ -1,0 +1,39 @@
+clc;
+clearvars;
+close all;
+
+set_up_inference_example;
+
+convolution = EmpericalConvolution(z_image,20, 20, [200,200]);
+convolution.estimateNull();
+convolution.setMask(segmentation);
+convolution.doTest();
+
+fig = LatexFigure.sub();
+convolution.z_tester.plotHistCritical();
+saveas(fig,fullfile('reports','figures','inference','filter_histogram.eps'),'epsc');
+
+fig = LatexFigure.sub();
+convolution.z_tester.plotPValues();
+saveas(fig,fullfile('reports','figures','inference','filter_p.eps'),'epsc');
+
+fig = LatexFigure.sub();
+image_plot = ImagescSignificant(convolution.getZNull());
+image_plot.plot();
+saveas(fig,fullfile('reports','figures','inference','filter_z_image.eps'),'epsc');
+
+fig = LatexFigure.sub();
+image_plot = ImagescSignificant(-log10(convolution.p_image));
+image_plot.plot();
+saveas(fig,fullfile('reports','figures','inference','filter_p_image.eps'),'epsc');
+
+fig = LatexFigure.main();
+image_plot = ImagescSignificant(test);
+image_plot.addSigPixels(convolution.sig_image);
+image_plot.plot();
+saveas(fig,fullfile('reports','figures','inference','filter_sig_image.eps'),'epsc');
+
+fig = LatexFigure.main();
+image_plot = ImagescSignificant(convolution.mean_null);
+image_plot.plot();
+saveas(fig,fullfile('reports','figures','inference','filter_mean_null.eps'),'epsc');

### 2018-04-08 reports/thesis/chapters/5_inference.tex
Modified value and figures output locations.

@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/inference/nullhisto.eps}
+	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullhisto.eps}
 	\caption{A histogram of simulated of 1\,000 null test statistics.
 Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
-	\label{fig:inference_nullhisto}
-\end{figure}
-
-A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_nullhisto}.
+	\label{fig:inference_multi_test_nullhisto}
+\end{figure}
+
+A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto}.
 The critical boundaries are also shown.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/inference/nullpvalues.eps}
+	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
 	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
-	\label{fig:inference_nullpvalues}
-\end{figure}
-
-The ordered $p$-values are shown in Figure \ref{fig:inference_nullpvalues}.
+	\label{fig:inference_multi_test_nullpvalues}
+\end{figure}
+
+The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullpvalues}.
 The $p$-values form a straight line as a result of being uniformly distributed.
@@
 	\centering
-	\includegraphics[width = 0.8\textwidth]{../figures/inference/althisto.eps}
+	\includegraphics[width = 0.8\textwidth]{../figures/inference/multi_test_althisto.eps}
 	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics.
 Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
-	\label{fig:inference_althisto}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/inference/altpvalues.eps}
+	\label{fig:inference_multi_test_althisto}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_altpvalues.eps}
     \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
-	\label{fig:altpvalues}
+	\label{fig:inference_multi_test_altpvalues}
 \end{figure}
@@
 In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated.
-The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_althisto}.
+The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto}.
 The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario.
-However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../figures/inference/alt_z_critical.txt}$.
-
-The ordered $p$-values are shown in Figure \ref{fig:altpvalues}.
-There are $p$-values below the critical line according to the BH procedure, testing $\input{../figures/inference/alt_n_positive_bh.txt}$ test statistics as positive.
-The uncorrected test tested $\input{../figures/inference/alt_n_positive_uncorrected.txt}$ test statistics as positive.
+However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}$.
+
+The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_altpvalues}.
+There are $p$-values below the critical line according to the BH procedure, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive.
+The uncorrected test tested $\input{../tables/multi_test_alt_n_positive_uncorrected.txt}$ test statistics as positive.
 
@@
 The uncorrected method did produce more positive results but at a cost of more false positives.
-It may seem unimpressive that the BH procedure only tested $\input{../figures/inference/alt_n_positive_bh.txt}$ positive results, but this is to control the FDR or the number of false positives out of all positive results.
+It may seem unimpressive that the BH procedure only tested $\input{../tables/multi_test_alt_n_positive_bh.txt}$ positive results, but this is to control the FDR or the number of false positives out of all positive results.
 
@@
     \centering
-    \input{../tables/inference_error_rate1.tex_table}
+    \input{../tables/inference_error_rate1.txt}
     \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level.
@@
     \centering
-    \input{../tables/inference_error_rate2.tex_table}
+    \input{../tables/inference_error_rate2.txt}
     \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level.
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/sub_z_image.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_image.eps}
         \caption{$z$ image with section highlighted}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo.eps}
         \caption{Histogram of section}
@@
     \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown.}
-    \label{fig:inference_sub_z}
-\end{figure}
-
-A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_sub_z}.
-One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}...$.
+    \label{fig:inference_empirical_null_sub_z}
+\end{figure}
+
+A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_empirical_null_sub_z}.
+One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../tables/empirical_null_sub_boundary.txt}...$.
 However a quick look at the histogram will show that almost half of the pixels will be tested as positive.
@@
 The parameters of the empirical null are estimated using the kernel density estimate.
-The resulting estimated density is shown in Figure \ref{fig:inference_sub_density_estimate}.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo_nocritical.eps}
+The resulting estimated density is shown in Figure \ref{fig:inference_empirical_null_sub_density_estimate}.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_nocritical.eps}
         \caption{Histogram}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/sub_z_parzen.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_parzen.eps}
         \caption{Kernel density estimate}
@@
 The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
-    \label{fig:inference_sub_density_estimate}
+    \label{fig:inference_empirical_null_sub_density_estimate}
 \end{figure}
@@
 \end{equation}
-In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../figures/inference/sub_null_sigma.txt}...$.
+In this particular example, it was found that $\widehat{\mu}_0=\input{../tables/empirical_null_sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../tables/empirical_null_sub_null_sigma.txt}...$.
 It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.
@@
 The corrected test statistics $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ are then used in any multiple hypothesis testing procedures.
-Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../figures/inference/sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../figures/inference/sub_null_critical1.txt}...$ and $\input{../figures/inference/sub_null_critical2.txt}...\leqslant Z$.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo_null.eps}
+Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../tables/empirical_null_sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../tables/empirical_null_sub_null_critical1.txt}...$ and $\input{../tables/empirical_null_sub_null_critical2.txt}...\leqslant Z$.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_null.eps}
         \caption{Histogram of $z$}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/sub_z_p_values.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_p_values.eps}
         \caption{Ordered $p$ values}
@@
     \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
-    \label{fig:inference_sub_z_critical_regions}
-\end{figure}
-
-These new critical regions are shown in Figure \ref{fig:inference_sub_z_critical_regions}.
+    \label{fig:inference_empirical_null_sub_z_critical_regions}
+\end{figure}
+
+These new critical regions are shown in Figure \ref{fig:inference_empirical_null_sub_z_critical_regions}.
 No positive results were found and the $p$-values are sensible as they look uniformly distributed.
@@
 
+The $z$ and $p$-value image, as shown in Figure \ref{fig:inference_filter_z_p_image}, now look more
+
 \begin{figure}

### 2018-04-08 inference/scripts/alt_empirical_script.m

@@ -1,7 +1,6 @@
 %EMPIRICAL NULL SCRIPT
-%Takes a sample from a z image
-%Plots a histogram of the z statistics before any empirical null correction
-%Does the empirical null correction and print results
+%Takes a sample from a z image, containing a defect
+%Plots a histogram of the z statistics with the BH critical region, corrected for the empirical null
 
 clc;
 close all;
@@ -53,7 +52,7 @@ legend('z histogram','critical','Location','northeast');
 saveas(fig,fullfile('reports','figures','inference','alt_empirical_z_histo_null.eps'),'epsc');
 
 %FIGURE
-%Plot the frequency density estimate along with the empirical null mean and std
+%Plot the frequency density estimate along with the empirical null mean and std, and critical boundary
 fig = LatexFigure.sub();
 z_tester.plotDensityEstimate(x_plot);
 hold on;
@@ -78,6 +77,8 @@ fig = LatexFigure.main();
 z_tester.plotPValues();
 saveas(fig,fullfile('reports','figures','inference','alt_empirical_z_p_values.eps'),'epsc');
 
+%FIGURE
+%plot the z image with highlighted significant pixels
 fig = LatexFigure.main();
 image_plot = ImagescSignificant(z_image(row_subsample, col_subsample));
 image_plot.addSigPixels(z_tester.sig_image);

### 2018-04-08 inference/scripts/multi_test_script.m

@@ -11,6 +11,7 @@ close all;
 clearvars;
 
 %%%%%CASE 1%%%%%
+%1000 N(0,1)
 
 %declare rng
 rand_stream = RandStream('mt19937ar','Seed',uint32(3499211588));
@@ -42,15 +43,16 @@ bonferroni_test.plotCritical();
 xlabel('z');
 ylabel('frequency density');
 legend(ax.Children([5,4,2]),'z histogram','uncorrected critical','bonferroni critical');
-saveas(fig,fullfile('reports','figures','inference','nullhisto.eps'),'epsc');
+saveas(fig,fullfile('reports','figures','inference','multi_test_nullhisto.eps'),'epsc');
 
 %plot the ordered p values
 fig = LatexFigure.main();
 z_tester.plotPValues();
 legend('p values','critical','Location','northwest');
-saveas(fig,fullfile('reports','figures','inference','nullpvalues.eps'),'epsc');
+saveas(fig,fullfile('reports','figures','inference','multi_test_nullpvalues.eps'),'epsc');
 
 %%%%%CASE 2%%%%%
+%800 N(0,1) and 200 N(0,1)
 
 %number of test statistics to be simulated
 n = 1000;
@@ -73,15 +75,15 @@ uncorrected_test.setCriticalColour([0,0.4470,0.7410]);
 z_bh = z_tester.getZCritical();
 z_bh = z_bh(end);
 %save the boundary
-file_id = fopen(fullfile('reports','figures','inference','alt_z_critical.txt'),'w');
+file_id = fopen(fullfile('reports','tables','multi_test_alt_z_critical.txt'),'w');
 fprintf(file_id,'%.2f',z_bh);
 fclose(file_id);
 %save the number of positive results for uncorrected
-file_id = fopen(fullfile('reports','figures','inference','alt_n_positive_uncorrected.txt'),'w');
+file_id = fopen(fullfile('reports','tables','multi_test_alt_n_positive_uncorrected.txt'),'w');
 fprintf(file_id,'%.0f',sum(uncorrected_test.sig_image));
 fclose(file_id);
 %save the number of positive results for BH
-file_id = fopen(fullfile('reports','figures','inference','alt_n_positive_bh.txt'),'w');
+file_id = fopen(fullfile('reports','tables','multi_test_alt_n_positive_bh.txt'),'w');
 fprintf(file_id,'%.0f',sum(z_tester.sig_image));
 fclose(file_id);
 
@@ -98,10 +100,10 @@ z_tester.plotCritical();
[…]

### 2018-04-08 reports/thesis/chapters/5_inference.tex
Further modified value and figures output locations.

@@
 19 images were used to train the variance-mean model.
-One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_scan_aRTist}.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/scan.eps}
+One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_initial_artist_scan_aRTist}.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_scan.eps}
         \caption{X-ray image}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/aRTist.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_aRTist.eps}
         \caption{\texttt{aRTist} simulation}
@@
     \caption{An x-ray scan of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset. This can be compared directly to the \texttt{aRTist} simulation for defects.}
-    \label{fig:inference_scan_aRTist}
+    \label{fig:inference_initial_artist_scan_aRTist}
 \end{figure}
@@
 A $p$-value too small is considered to be evidence of a positive result.
-The result $z$ statistics and $p$-values are shown in Figure \ref{fig:logp_z}.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/logp.eps}
+The result $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_logp.eps}
         \caption{$-\log p\text{-values}$}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/z_image.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_image.eps}
         \caption{$z$ statistics}
@@
     \caption{The resulting z statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
-    \label{fig:logp_z}
+    \label{fig:inference_initial_artist_logp_z}
 \end{figure}
@@
 It should be expected that small $p$-values are in areas of the defects.
-Significant pixels were chosen for $\|z\|>\input{../figures/inference/z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level.
-The significant pixels are shown in Figure \ref{fig:sig_pixels}.
+Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level.
+The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.
 
@@
 Model misspecification appears to be the main source of error.
-The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:z_histo}.
+The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}.
 It can be seen that the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect.
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{../figures/inference/sig_pixels.eps}
+    \includegraphics[width=0.7\textwidth]{../figures/inference/initial_artist_sig_pixels.eps}
     \caption{Significant pixels highlighted at the $z_\alpha = 2$ significance level.}
-    \label{fig:sig_pixels}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/z_histo.eps}
+    \label{fig:inference_initial_artist_sig_pixels}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_histo.eps}
     	\caption{Histogram}
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/z_qq.eps}
+    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_qq.eps}
     	\caption{QQ plot}
@@
     \caption{Distribution of the  $z$ statistics with the BH procedure critical region}
-    \label{fig:z_histo}
+    \label{fig:inference_initial_artist_z_histo}
 \end{figure}

### 2018-04-10 reports/thesis/chapters/5_inference.tex
Modified ZNull figures.
Started on empirical null filter experiments.

@@
     }
-    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
+    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of simulated $\normal(0,1)$ data.
+On the right, lines represent the rule of thumb for various values of $b$.
+On the left shows the true value of $\sigma_0=1$ as a plane, the empirical truth is where that plan intersects the surface.}
     \label{fig:inference_ZNull2}
@@
 
-The $z$ and $p$-value image, as shown in Figure \ref{fig:inference_filter_z_p_image}, now look more
+The $z$ and $p$-value image, as shown in Figure \ref{fig:inference_filter_z_p_image}, now look more spatially uniform.
+The defects and some of the edges and corners are highlighted with their small $p$-values.
+In particular, Figure \ref{fig:inference_filter_z_ordered_p} shows that the test statistics look more Normal but with heavier tails.
+The heavier tails are contributed to non-null test statistics.
+Significant pixels are shown in Figure \ref{fig:inference_filter_sig_image}.
+It is encouraging to see less false positives and more defects being picked up.
+Because the BH procedure controls the FDR, some false positives are inevitable.
 
@@
 \end{figure}
+
+In summary, the empirical null filter irons out each pixel in the $z$ image using the local mode.
+Figure \ref{fig:inference_filter_mean_null} shows the $\widehat{\mu}_{0,x,y}$ image, which varies a lot but smoothly.
+This demonstrated that by corrected the test statistics accordingly, sensible inference was achieved.
+
+In the remaining of the chapter, properties of the empirical null filter are investigated.
+
+\subsection{All Null Simulation}
+
+An experiment was conducted to investigate how well the empirical null filter performs with no defects. The dataset \texttt{July 30deg} was used in this experiment.
+
+The images in the dataset were spilt into two halves randomly.
+The mean over the first half of the images was taken and this was used as the ground truth, acting like an \texttt{aRTist} simulation.
+A smooth function was added to the ground truth to contaminate it and cause some systematic error.
+The idea was that the empirical null filter did inference without being effected too much by the smooth function.
+
+In the second half, all but one of the images were used in the training of the variance-mean model.
+The remaining image, the test image, was then used to compare with the simulated ground truth, producing a $z$ image.
+The $z$ image was then inferred using the empirical null filter and then the BH procedure.
+
+The smooth functions investigated were a plane and a sinusoid.
+The harshness of the smooth functions were controlled using the gradient for the plane, and the amplitude for the sinusoid.
+The smooth functions are for the plane
+\begin{equation}
+	\delta\left[
+		(x-x_0)+(y-y_0)
+	\right]
+\end{equation}
+and the sinusoid
+\begin{equation}
+	A\sin\left[
+		\dfrac{
+			2\pi
+		}
+		{
+			750
+		}
+		\left(
+			(y-y_0)-(x-x_0)
+		\right)
+	\right]
+\end{equation}
+where $\delta$ is the gradient, $A$ is the amplitude and $(x_0,y_0)$ is the centre of the image.
+
+Because no defects were implemented in this experiment, any positive results are false.
+The false positive rates were investigated for different harshness of the smooth functions.
+The experiment was repeated 20 times by randomly reallocating the images used for the ground truth, variance-mean training and testing.
+
+Figures \ref{fig:inference_NoDefect_Plane_sigma} and \ref{fig:inference_NoDefect_Sinusoid_sigma} shows the false positive rate for the plane and sinusoid contamination respectively.
+It can be seen that false positives can happen and in particular when the smooth function is quite harsh and varies a lot spatially.
+This showed that the empirical null filter was not completely perfect and false positives can happen.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane2sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane3sigma.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane4sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane5sigma.eps}
+    \end{subfigure}
+    }
+    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane. Various $z_\alpha$ levels and gradients are shown.}
+    \label{fig:inference_NoDefect_Plane_sigma}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid2sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid3sigma.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid4sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid5sigma.eps}
+    \end{subfigure}
+    }
+    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid. Various $z_\alpha$ levels and gradients are shown.}
+    \label{fig:inference_NoDefect_Sinusoid_sigma}
+\end{figure}
+
+The spatial properties of the false positives did depend on the smooth function.
+Figures \ref{fig:inference_NoDefect_Plane_p_sig} and \ref{fig:inference_NoDefect_Sinusoid_p_sig} shows the location of the positive results for the plane and sinusoid contamination respectively.
+The $p$-values are also shown.
+These false positives are concerning as they are clustered together, giving false indication of a defect.
+
+In practice, the amount of contamination won't be as harsh as the one demonstrated here.
+As long as the smooth function is slowly varying spatially, the empirical null filter will correct the test statistics accordingly.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_pvalues.eps}
+        \caption{$\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_sig.eps}
+        \caption{$z$ image with red significant pixels}
+    \end{subfigure}
+    }
+    \caption{The $p$-values and significant pixels when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
+    \label{fig:inference_NoDefect_Plane_p_sig}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_pvalues.eps}
+        \caption{$\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_sig.eps}
+        \caption{$z$ image with red significant pixels}
+    \end{subfigure}
+    }
+    \caption{The $p$-values and significant pixels when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $10^4$.}
+    \label{fig:inference_NoDefect_Sinusoid_p_sig}
+\end{figure}
+
+Figure \ref{fig:inference_NoDefect_nullmean} shows the estimated empirical null mean.
+It is remarkable that the empirical null mean recovers the smooth functions but artefacts from interpolation can be seen for the sinusoid contamination.
+The grid like structure in Figure \ref{fig:inference_NoDefect_Sinusoid_nullmean} shows that the estimated empirical null mean was not very smooth and more points should of been used to reduce the amount of interpolation, increasing the accuracy of the estimation.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_nullmean.eps}
+        \caption{Plane, $\delta = 7.0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_nullmean.eps}
+        \caption{Sinusoid, $A=10^4$}
+        \label{fig:inference_NoDefect_Sinusoid_nullmean}
+    \end{subfigure}
+    }
+    \caption{Empirical null mean when using the empirical null filter on an $z$ image where the ground truth was contaminated by a smooth function.}
+    \label{fig:inference_NoDefect_nullmean}
+\end{figure}
+
+These examples showed that the empirical null filter corrected the test statistics accordingly.
+However in extreme cases, the empirical null filter can fail producing clusters of low $p$-values giving an illusion of a defect.
+In practice, extreme cases should not happen.
+Referring back to the real life example in Figure \ref{fig:inference_filter_mean_null}, the empirical null mean only varied around $0\pm3$ which is a small variation compared to Figure \ref{fig:inference_NoDefect_nullmean}.
+
+\subsection{Defected Simulation}

### 2018-04-10 make.m

@@ -79,18 +79,24 @@ this.printResults();
 
 this = Experiment_ZNull();
 this.run();
+this.printResults();
 
 this = Experiment_ZNull_mse();
 this.run();
+this.printResults();
 
 this = Experiment_NoDefect_Plane();
 this.run();
+this.printResults();
 
 this = Experiment_NoDefect_Sinusoid();
 this.run();
+this.printResults();
 
 this = Experiment_SimulateRoc_Squares();
 this.run();
+this.printResults();
 
 this = Experiment_SimulateRoc_Line();
 this.run();
+this.printResults();

### 2018-04-13 reports/thesis/chapters/5_inference.tex
Adjusted a few bib entries.

@@
 It should be expected that small $p$-values are in areas of the defects.
-Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level.
+Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level.
 The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.
@@
 These problems are similar to the one observed at the start of this chapter.
-The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false,schwartzman2009empirical}.
+The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
 
@@
 The majority of the significant pixels are cluster together and highlighting the defect.
-Not all of the defect was tested positive, but a good number of them are.
+Not all of the defects were tested positive, but a good number of them are.
 This should be enough to raise suspicion in that particular area.
@@
         \includegraphics[width=\textwidth]{../figures/inference/filter_p_image.eps}
-        \caption{$\log p$-value image}
+        \caption{$-\log p$-values}
     \end{subfigure}
@@
     }
-    \caption{The $p$-values and significant pixels when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
+    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
     \label{fig:inference_NoDefect_Plane_p_sig}
@@
     }
-    \caption{The $p$-values and significant pixels when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $10^4$.}
+    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $10^4$.}
     \label{fig:inference_NoDefect_Sinusoid_p_sig}
@@
 These examples showed that the empirical null filter corrected the test statistics accordingly.
-However in extreme cases, the empirical null filter can fail producing clusters of low $p$-values giving an illusion of a defect.
+However in extreme cases, the empirical null filter can fail and producing clusters of low $p$-values giving an illusion of a defect.
 In practice, extreme cases should not happen.
@@
 \subsection{Defected Simulation}
+
+receiver operating characteristic \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use}

### 2018-04-16 reports/thesis/chapters/5_inference.tex
Added SimulateRoc experiment to thesis.

@@
 
-receiver operating characteristic \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use}
+An experiment was conducted to see if the empirical null filter detect defects under contamination.
+Just like the previous experiment, the dataset \texttt{July 30deg} was used.
+The images in the dataset were spilt, the mean of the first half acted as the ground truth, the rest were used to train the variance-mean model, one held out for testing.
+A plane with gradient $\delta=3$ was added to the ground truth to contaminate it.
+The contamination from the plane is quite mild following from the previous experiment.
+
+Furthermore, defects were added to the ground truth by increasing selected pixels' grey-values. Shapes such as squares and lines were used to simulate voids and cracks.
+
+The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} were investigated.
+The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds.
+Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity instead.
+
+The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
+Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed throughly in \citep{cook2007use}.
+The area under the ROC curve was recorded for different intensity values of the defect.
+
+Figures \ref{fig:inference_SimulateRoc_Line_p_sig} and \ref{fig:inference_SimulateRoc_Squares_p_sig} shows the results of using the empirical null filter for inference.
+In this example an array of squares and a single vertical line were used to defect the ground truth by adding 298 to the grey value, a particular small number.
+The defects were picked up which is remarkable.
+The structure of the false positives is quite similar to Figure \ref{fig:inference_NoDefect_Plane_p_sig}, indicating that the plane was still quite harsh and responsible for the false positives.
+
+The empirical null filter can fail if it treats a defect as the null.
+This can be mildly seen in Figure \ref{fig:inference_SimulateRoc_Squares_p_sig}, the top rows of square defects were not detected but the area outside the defect were tested as positive.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_pvalues.eps}
+        \caption{$-\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_sig.eps}
+        \caption{Image with significant pixels}
+    \end{subfigure}
+    }
+    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by a single vertical line with value 298.}
+    \label{fig:inference_SimulateRoc_Line_p_sig}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_pvalues.eps}
+        \caption{$-\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_sig.eps}
+        \caption{Image with significant pixels}
+    \end{subfigure}
+    }
+    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by an array of squares with value 298.}
+    \label{fig:inference_SimulateRoc_Squares_p_sig}
+\end{figure}
+
+The ROC curves for different defect intensities are shown in Figures \ref{fig:inference_SimulateRoc_Lines_roc} and \ref{fig:inference_SimulateRoc_Squares_roc}.
+The dotted diagonal line show the ROC curve if the test classify each pixel randomly.
+Perfect classification happens on the top left when the true positive rate is one and the false positive rate is zero.
+A sample of ROC curves were obtained by reallocating the images to the ground truth, variance-mean training and testing, this was done 5 times.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_1.eps}
+        \caption{Defect intensity = 100}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_7.eps}
+        \caption{Defect intensity = 207}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_14.eps}
+        \caption{Defect intensity = 483}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_20.eps}
+        \caption{Defect intensity = 1000}
+    \end{subfigure}
+    }
+    \caption{ROC curves when using the empirical null filter on a simulated comparison.
+The ground truth was contaminated by a plane and defected by an single vertical line.
+Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
+This was done 5 times.}
+    \label{fig:inference_SimulateRoc_Lines_roc}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_1.eps}
+        \caption{Defect intensity = 100}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_7.eps}
+        \caption{Defect intensity = 207}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_14.eps}
+        \caption{Defect intensity = 483}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_20.eps}
+        \caption{Defect intensity = 1000}
+    \end{subfigure}
+    }
+    \caption{ROC curves when using the empirical null filter on a simulated comparison.
+The ground truth was contaminated by a plane and defected by an array of squares.
+Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
+This was done 5 times.}
+    \label{fig:inference_SimulateRoc_Squares_roc}
+\end{figure}
+
+Figure \ref{fig:inference_SimulateRoc_roc_area} shows the area under the ROC curves for the single vertical line and array of squares defect.
+The areas were calculated using the trapezium rule.
+The results are promising with near perfect performance with defect intensities at least 600.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_area.eps}
+        \caption{Line}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_area.eps}
+        \caption{Squares}
+    \end{subfigure}
+    }
+    \caption{The area under the ROC curves for different defects and defect intensities.
+The ground truth was contaminated by a plane and defected.
+The experiment was repeated 5 times by reallocating images to the ground truth, variance-mean training and testing.
+The box plot represent those 5 repeats.}
+    \label{fig:inference_SimulateRoc_roc_area}
+\end{figure}
+
+The experiments shows that the empirical null filter can correct the null distribution locally, giving better inference.
+In extreme cases, for example if the defect intensity is very small or the amount of contamination is rather large, the empirical null filter can fail.
+Harsh contamination can produce false positives because spatially rapidly changing grey values could be detected as a defect.
+The worst case would be that this would make defects appear to be the null, giving completely the opposite inference.
+
+These extreme cases should not happen.
+As seen in the real life example at the start of the section, false positives are rare but they do have some spatial structure.
+If the defect intensity is too small to be detected, the contrast of the x-ray imaging apparatus should be adjusted to cater for it.

### 2018-04-18 reports/thesis/chapters/5_inference.tex
Adjusted harshness in NoDefect_Sinusoid, proof read inference chapter.

@@
-The aim of this project is to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist}.
-\texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample.
+The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+\texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}.
 Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.
@@
 Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect.
-However in the previous chapters, it was found that x-ray photons behave randomly and large differences in the comparison can be due to chance.
+However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance.
 Thus the comparisons should be done under the face of uncertainty.
 
-A pixel by pixel inference was proposed to do defect detection. A statistic $z_{i,j}$ for the $(i,j)$ positioned pixel can be calculated for all pixels. This statistic is
-\begin{equation}
-    z_{i,j} = 
-    \dfrac{
-        \text{scan}_{i,j} - \text{aRTist}_{i,j}
-    }
-    {
-        \sqrt{\widehat{\variance}\left[\text{scan}_{i,j}\right]}
-    }
-\end{equation}
-where $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is the estimated grey value variance of pixel $(i,j)$ in the scan.
-Under mild assumptions, it was shown in the previous chapters that the grey values in the scan are Normal.
-Thus by treating the simulated image from \texttt{aRTist} as known, then
-\begin{equation}
-z_{i,j}\sim \normal(0,1) \ .
-\end{equation}
-This means the randomness of the $z_{i,j}$ statistics can be quantified.
-
-The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ will be explained here.
+A pixel by pixel inference was proposed to do defect detection. A statistic $z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
+\begin{equation}
+    Z_{x,y} = 
+    \dfrac{
+        \text{scan}_{x,y} - \text{aRTist}_{x,y}
+    }
+    {
+        \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
+    }
+\end{equation}
+where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.
+Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal.
+Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $z_{i,j}$ statistics can be quantified
+\begin{equation}
+Z_{i,j}\sim \normal(0,1) \ .
+\end{equation}
+As with usual statistical convention, upper case $Z$ denote a random variable. Whereas lower case $z$ denote a realisation or an observation of that random variable.
+
+The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is be explained here.
 The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample.
-These replicated x-ray scans provide variance-mean data which then can be used to train the variance model, such as a Gamma distributed GLM.
+These replicated x-ray scans provide variance-mean data which was used to train the variance model, such as a Gamma distributed GLM.
 The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
@@
 
-This method for inference can be applied to the dataset \texttt{Sep16 120deg}.
+This method for inference was applied to the dataset \texttt{Sep16 120deg}.
+Here a cuboid with voids were purposefully manufactured to see if they can be detected.
 The 20 x-ray images were spilt into 2.
@@
 One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_initial_artist_scan_aRTist}.
+In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.
 
@@
 
-For each pixel, a $z_{i,j}$ statistic was calculated.
-A $z_{i,j}$ statistic too large in magnitude can be considered to be evidence of a positive result.
-Another way to represent the $z_{i,j}$ statistic is the $p$-value which is given as
-\begin{equation}
-    p_{i,j} = 2(1-\Phi(\|z_{i,j}\|))
+For each pixel, a $z$ statistic was calculated.
+A $z$ statistic too large in magnitude can be considered to be evidence of a positive result.
+Another way to represent the $z$ statistic is the $p$-value which is given as
+\begin{equation}
+    p_{x,y} = 2(1-\Phi(\|z_{x,y}\|))
 \end{equation}
 which can takes values $0\leqslant p_{i,j} \leqslant 1$.
-A $p$-value too small is considered to be evidence of a positive result.
-The result $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.
+A $p$-value too small is considered to be evidence of a defect.
+The resulting $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.
 
@@
     }
-    \caption{The resulting z statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
+    \caption{The resulting $z$ statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
     \label{fig:inference_initial_artist_logp_z}
@@
 It should be expected that small $p$-values are in areas of the defects.
-Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level.
+Pixels are significant, or considered to be evidence of a defect, when for $\|z_{x,y}\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level.
 The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.
@@
 
-Model misspecification appears to be the main source of error.
-The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}.
-It can be seen that the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect.
+Model misspecification appeared to be the main source of error.
+The $z$ statistics was inspected using a histogram and a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}.
+It can be seen that the $z$ statistics does not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect.
 However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.
@@
     \includegraphics[width=0.7\textwidth]{../figures/inference/initial_artist_sig_pixels.eps}
-    \caption{Significant pixels highlighted at the $z_\alpha = 2$ significance level.}
+    \caption{Significant pixels highlighted using the BH procedure at the $z_\alpha = 2$ significance level.}
     \label{fig:inference_initial_artist_sig_pixels}
@@
 	}
-    \caption{Distribution of the  $z$ statistics with the BH procedure critical region}
+    \caption{Distribution of the  $z$ statistics with the BH procedure critical region at the $z_\alpha=2$ level.}
     \label{fig:inference_initial_artist_z_histo}
@@
 
-This chapter will cover hypothesis testing, for a single test and then for multiple tests.
-The empirical null will then be reviewed which then can be extended to an image filter, called the empirical null filter.
-This filter will adjust each $z$ statistic according to its neighbours, ironing out false positive results.
-Simulations and actual results will be shown at the end of the chapter.
+This chapter covers hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test.
+The empirical null is reviewed and then extended to an image filter, called the empirical null filter.
+This filter adjust each $z$ statistic according to its neighbours, ironing out false positive results.
+Simulations and actual results was shown at the end of the chapter.
 
@@
 
-Hypothesis testing dates back to \cite{pearson1900on}, \cite{neyman1933on} and \cite{fisher1970statistical}. It is so fundamental in science that it is now taught in schools.
+Hypothesis testing dates back to \cite{pearson1900on}, \cite{neyman1933on} and \cite{fisher1970statistical}. It is one of the most fundamental methods in science.
 
 The focus on this section is on the single hypothesis test.
-Here the random variable $Z\sim\normal(\mu,1)$ will be studied here as this is of interest in this project.
+A Normal random variable is studied as this is of interest in this project.
 It also appears in other tests such as the difference in sample means.
 
-In the context of this project, an example of hypothesis testing will be given here. Here, it was assumed that $Z\sim\normal(0,1)$. A null hypothesis can be written down to describe this
+In the context of this project, an example of hypothesis testing is given here.
+Here, it was assumed that the test statistic $Z\sim\normal(0,1)$.
+A null hypothesis is written down to describe this.
+This is done by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis
 \begin{equation}
@@
 \end{equation}
-It specifies the assumptions made on the random variable $Z$. Any data behaving as assumed is treated as a negative result.
-
-A positive result is obtained when unlikely data is obtained and this happens if $Z$ deviates too much from 0. This can be described as testing $H_0$ against an alternative hypothesis $H_1$ where
+This specifies the assumptions made on the random variable $Z$, here the mean is zero. Any data behaving as assumed is treated as a negative result or not significant.
+
+A positive, or significant, result is obtained when unlikely data is obtained and this happens if $Z$ deviates too much from 0.
+This can be described as testing $H_0$ against an alternative hypothesis $H_1$ where
 \begin{equation}
@@
 \end{equation}
-How much $Z$ deviates from 0 to be considered a positive is up to the user but typically $\|Z\|>z_\alpha$ where $z_\alpha =2$ is considered significant.
+How much $Z$ deviates from 0 to be considered a positive is up to the user but typically $\|Z\|>z_\alpha$ where $z_\alpha =2$ is a typical choice for the threshold.
 
@@
 \end{equation}
-The choice of $z_\alpha=2$ will set the size of the test to be $\alpha\approx 4.55\%$. This sort of choice of threshold and size is sensible.
+The choice of $z_\alpha=2$ set the size of the test to be $\alpha\approx 4.55\%$. The $z_\alpha=2$ level is used throughout this project.
 
@@
 
-In this section, the single hypothesis test will be extended and the multiple hypothesis testing \citep{shaffer1995multiple, dudoit2003multiple} shall be reviewed.
+In this section, the single hypothesis test is extended and the multiple hypothesis testing \citep{shaffer1995multiple, dudoit2003multiple} is reviewed.
 
 Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$ where $Z_i\sim\normal(\mu,1)$ for $i=1,2,\dotdotdot,n$ and i.i.d.
-One can test each of these statistics for the following hypotheses $H_0:\mu=0$ and $H_1:\mu\neq 0$.
-Using the method from the single hypothesis test at the $z_\alpha=2$ level, any statistic where $\|Z_i\|>2$ for $i=1,2,\dotdotdot,n$ would be considered a positive result.
+Suppose each individual statistic were used to test the following hypotheses $H_0:\mu=0$ and $H_1:\mu\neq 0$.
+Using the method from the single hypothesis test at the $z_\alpha=2$ level, any statistic where $\|Z_i\|>2$ for $i=1,2,\dotdotdot,n$ would be considered significant.
 
@@
 There are corrections for multiple hypothesis testing which controls different things.
-Conventionally they are expressed in terms of the number of errors made in testing, these are defined in Table \ref{table:inference_randomvariables}.
+Conventionally they are expressed in terms of the number true/false positives/negatives, these are defined in Table \ref{table:inference_randomvariables}.
 Using the notation, formally PCER is defined as
@@
     \end{tabular}
-    \caption{Random variable definitions for the different types of error made in multiple hypothesis testing}
+    \caption{Random variable definitions for true/false positives/negatives made in multiple hypothesis testing}
     \label{table:inference_randomvariables}
@@
 \end{equation}
-However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negative results.
+However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives.
 This is because the correction traded too many false positives for false negatives.
 
-The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate.
+The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the PCER or FWER.
 The FDR is the proportion of false positives out of all positive results, that is
@@
 Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$.
-They will need to be converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$.
-The adjusted size $\alpha_{\text{BH}}$ is
+They are converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$.
+Suppose a size $\alpha$ is provided beforehand.
+The size is then adjusted to
 \begin{equation}
@@
 \end{equation}
-This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as positive results.
-For the case where $p_{(1)}>\alpha/n$, then $k=1$ shall be chosen so that the Bonferroni correction is used instead.
+This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as significant.
+For the case where $p_{(1)}>\alpha/n$, then $k=1$ was chosen so that the Bonferroni correction is used instead.
 The BH procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
@@
 
-A few numerical examples will be shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing.
-Two scenarios will be shown here.
-In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics are all null.
-In the second case, 800 null $\normal(0,1)$ and 200 alternative $\normal(2,1)$ independent test statistics were simulated.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullhisto.eps}
-	\caption{A histogram of simulated of 1\,000 null test statistics.
-Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
-	\label{fig:inference_multi_test_nullhisto}
-\end{figure}
-
-A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto}.
+A few numerical examples is shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing.
+Two scenarios is shown here.
+In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics were null.
+In the second case, 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ independent test statistics were simulated.
+
+A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}.
 The critical boundaries are also shown.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
-	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
-	\label{fig:inference_multi_test_nullpvalues}
-\end{figure}
-
-The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullpvalues}.
+The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}.
 The $p$-values form a straight line as a result of being uniformly distributed.
-The critical line is $0.0455...\times\text{order}/1\,000$.
-This corresponds to the BH procedure and $p$-values below where the 2 curves intersect are considered positive results.
+The critical line is $0.0455...\times\text{order}/1\,000$ using the BH procedure.
 In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure.
@@
     \centering
-	\includegraphics[width = 0.8\textwidth]{../figures/inference/multi_test_althisto.eps}
-	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics.
-Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
-	\label{fig:inference_multi_test_althisto}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_altpvalues.eps}
-    \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
-	\label{fig:inference_multi_test_altpvalues}
+    \begin{subfigure}[b]{0.8\textwidth}
+    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullhisto.eps}
+    	\caption{Histogram}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.8\textwidth}
+    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
+    	\caption{Ordered $p$-values}
+    \end{subfigure}
+    \caption{1\,000 null test statistics were simulated.
+a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.
+b) Any values below the critical line are declared significant using the BH procedure.}
+    \label{fig:inference_multi_test_nullhisto_pvalues}
 \end{figure}
@@
 In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated.
-The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto}.
+The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}.
 The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario.
-However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}$.
-
-The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_altpvalues}.
-There are $p$-values below the critical line according to the BH procedure, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive.
+However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}...$.
+
+The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}.
+There are $p$-values below the critical line according to the BH procedure.
+$p$-values below where the curves intersect are considered significant, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive.
 The uncorrected test tested $\input{../tables/multi_test_alt_n_positive_uncorrected.txt}$ test statistics as positive.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.8\textwidth}
+    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_althisto.eps}
+    	\caption{Histogram}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.8\textwidth}
+    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_altpvalues.eps}
+    	\caption{Ordered $p$-values}
+    \end{subfigure}
+    \caption{800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics were simulated.
+a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.
+b) Any values below the critical line are declared significant using the BH procedure.}
+    \label{fig:inference_multi_test_althisto_pvalues}
+\end{figure}
 
@@
 This is however unavoidable as a number of null and non-null test statistics will be similar in value.
-The aim of hypothesis testing is not to classify positive and negative results correctly, but rather highlight a number of test statistics which are worth investigating.
+The aim of hypothesis testing is not to classify positive and negative results correctly, but rather highlight a number of test statistics which are worth investigation.
 
@@
 \end{equation}
-The estimates of PCER and FDR is esentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the variance of the Beta distribution is used to quantify the error
+The estimates of PCER and FDR is essentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the standard error was chosen to be
 \begin{equation}
@@
 where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$.
+Without going into too much detail, this comes from setting a prior $\text{FWER}\sim\betaDist(0,0)$ and assuming that $\mathbb{I}(V\neq0)\sim\bernoulli(\text{FWER})$.
+The posterior distribution is $\text{FWER}|V_1,V_2,\dotdotdot V_N\sim\betaDist(a,b)$ and the variance was used for the standard error.
 
@@
     \centering
+    \begin{subtable}{\textwidth}
+    	\centering
     	\input{../tables/inference_error_rate1.txt}
+    	\caption{1\,000 $\normal(0,1)$}
+    \end{subtable}
+    \begin{subtable}{\textwidth}
+    	\centering
+    	\input{../tables/inference_error_rate2.txt}
+    	\caption{800 $\normal(0,1)$ and 200 $\normal(2,1)$}
+    \end{subtable}
     \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level.
-1\,000 test statistics were simulated, all standard Normal.
+1\,000 test statistics were simulated, in a) all test statistics are null and b) some are non-null.
 Error bars represent the standard errors after 1\,000 repeats of the experiment.}
-    \label{table:inference_error_rate1}
+    \label{table:inference_error_rate}
 \end{table}
 
-\begin{table}
-    \centering
-    \input{../tables/inference_error_rate2.txt}
-    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level.
-1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$.
-Error bars represent the standard errors after 1\,000 repeats of the experiment.}
-     \label{table:inference_error_rate1}
-\end{table}
-
-Error rates estimations for the two scenarios are shown in Tables \ref{table:inference_error_rate1} and \ref{table:inference_error_rate1} for $N=1\,000$.
-These estimations show that the 3 different types of multiple hypothesis controls for different rates.
+Error rates estimations for the two scenarios are shown in Table \ref{table:inference_error_rate} for $N=1\,000$.
+These estimations show that the 3 different types of multiple hypothesis controls for different error rates.
 The uncorrected, Bonferroni and BH controls the PCER, FWER and FDR to be equal or below $\alpha\approx 0.455$ respectively, equality is met when all the test statistics are all truly null.
@@
     }
-    \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown.}
+    \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown. The critical region was obtained using the BH procedure.}
     \label{fig:inference_empirical_null_sub_z}
@@
 A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_empirical_null_sub_z}.
-One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../tables/empirical_null_sub_boundary.txt}...$.
-However a quick look at the histogram will show that almost half of the pixels will be tested as positive.
-It is questionable whether such number of positive results is sensible, in particular in an area where defects are not expected.
+The BH procedure was used at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../tables/empirical_null_sub_boundary.txt}...$.
+However a quick look at the histogram showed that almost half of the pixels were significant.
+It is questionable whether such number of positive results is sensible, in particular in an area where defects were not expected.
 
 The histogram showed that the majority of the $z$ statistics are centred around 2 and has a bell shaped curve, a characteristic of the Normal distribution.
-If the data shows that the majority is centred elsewhere then expected, is it right to then to test the majority of the data as positive?
+If the data showed that the majority is centred elsewhere then expected, is it right to then to test the majority of the data as positive?
 This is an example of model misspecification because it was assumed that the $z$ statistics are distributed as $\normal(0,1)$ when in reality they are distributed as $\normal(\mu_0,\sigma_0^2)$.
@@
 
-The method will be described here.
+The method is described here.
 Suppose the following test statistics were obtained $z_1,z_2,\dotdotdot,z_n$.
-First the histogram needs to be smoothed.
-\cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} will be used here because it has simpler mathematical properties.
-The kernel density estimate is
+First the histogram is smoothed.
+\cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} was used here because it has simpler mathematical properties.
+The kernel density estimate \citep{parzen1962on} is
 \begin{equation}
@@
     }
-    \caption{The density of the test statistics can be estimated using a histogram or a kernel density estimate.
+    \caption{The density of the test statistics was estimated using a histogram or a kernel density estimate.
 The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
@@
 
-Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is to be found.
-This is then used as the mean of the empirical null \citep{efron2004large}.
-The calculation of $\widehat{\mu}_0$ can be numerically found using the Newton-Raphson method.
-Using the mode, the standard deviation of the empirical null is estimated using \citep{efron2004large}
+Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is found.
+This is used as the mean of the empirical null \citep{efron2004large}.
+The calculation of $\widehat{\mu}_0$ was numerically found using the Newton-Raphson method.
+Using the mode, the standard deviation of the empirical null was estimated using \citep{efron2004large}
+\begin{equation}
+	\widehat{\sigma}_0 = \left[
+		\left.
+			-\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_Z(z)
+		\right|_{z=\widehat{\mu}_0}
+	\right]^{-1/2}
+	\ .
+\end{equation}
+In this particular example, it was found that $\widehat{\mu}_0=\input{../tables/empirical_null_sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../tables/empirical_null_sub_null_sigma.txt}...$.
+It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.
+
+The empirical null was used to correct the test statistics $z_1,z_2,\dotdotdot,z_n$ to $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ by standardising the test statistics
+\begin{equation}
+	\zeta_i = \dfrac{
+		z_i - \widehat{\mu}_0
+	}
+	{
+		\widehat{\sigma}_0
+	}
+	\ .
+	\label{eq:inference_zeta}
+\end{equation}
+The corrected test statistics $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ were used in any multiple hypothesis testing procedures.
+Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../tables/empirical_null_sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../tables/empirical_null_sub_null_critical1.txt}...$ and $\input{../tables/empirical_null_sub_null_critical2.txt}...\leqslant Z$.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_null.eps}
+        \caption{Histogram of $z$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_p_values.eps}
+        \caption{Ordered $p$ values}
+    \end{subfigure}
+    }
+    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
+    \label{fig:inference_empirical_null_sub_z_critical_regions}
+\end{figure}
+
+These new critical regions are shown in Figure \ref{fig:inference_empirical_null_sub_z_critical_regions}.
+No positive results were found and the $p$-values are sensible as they look uniformly distributed.
+This demonstrated that the empirical null adjust the parameters of the null distribution to fit the majority of the data in order to make sensible inference.
+
+In this section, a more mathematical approach to the empirical null is taken to examine why and when this method works.
+Next computational concepts is discussed such as on how the mode of the kernel density estimator is found and what makes a good bandwidth in the kernel density estimator.
+This section is finished with a further discussion.
+
+\subsection{More on the Empirical Null}
+
+\cite{efron2004large} was motivated to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
+These problems are similar to the one observed at the start of this chapter.
+The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
+
+For formality, the null and alternative hypotheses is described here. Assume that the $z$ statistics under the null hypothesis are such that
+\begin{equation}
+	Z_i|H_0\sim\normal(\mu,\sigma_0^2)
+\end{equation}
+for $i=1,2,\dotdotdot,n$ and i.i.d. The hypotheses are then
+\begin{equation}
+	H_0:\mu = \mu_0
+\end{equation}
+and
+\begin{equation}
+	H_1:\mu\neq\mu_0
+\end{equation}
+where $\mu_0$ and $\sigma_0$ are the empirical null mean and standard deviation respectively.
+Essentially null $z$ statistics are assumed to be Normal distributed, with parameters using the empirical null.
+Statistics which deviates too much from $\mu_0$ are considered to be positive.
+
+The distribution of the $z$ statistics can be described using a mixture model. Let the random variable $Z$ have the probability density function
+\begin{equation}
+	p_Z(z) =
+	\pi_0 p_{Z|H_0}(z) + \pi_1 p_{Z|H_1}(z)
+\end{equation}
+where $0\leqslant\pi_0\leqslant 1$ and  $\pi_1 = 1-\pi_0$. In addition, the null distribution is
+\begin{equation}
+	p_{Z|H_0}(z) = 
+	\dfrac{1}{\sqrt{2\pi}\widehat{\sigma}_0}
+	\exp\left[
+		-\dfrac{1}{2}
+		\left(
+			\dfrac{z-{\mu}_0}{{\sigma}_0}
+		\right)^2
+	\right]
+\end{equation}
+as it was assumed to be Normal. The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified.
+
+The empirical null parameters are to be estimated.
+Assuming that $\pi_0$ is large, say bigger than 0.9 \citep{efron2004large}, and at and around the mode the probability density function is dominated by the null distribution.
+This implies that
+\begin{equation}
+	p_{Z}(z) \approx \pi_0 p_{Z|H_0}(z)
+\end{equation}
+for values of $z$ around the mode.
+Finding the maximum for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution.
+This justifies the use of the mode for the empirical null mean \citep{efron2004large}
+\begin{equation}
+	\widehat{\mu}_0 = \argmax\widehat{p}_Z(z) \ .
+\end{equation} 
+The empirical null standard deviation was obtained from the log density. For values of $z$ at and around the mode
+\begin{equation}
+	\ln p_{Z}(z) = 
+	\ln\left[
+		\dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
+	\right]
+	-\dfrac{1}{2}
+	\left(
+		\dfrac{z-{\mu}_0}{{\sigma}_0}
+	\right)^2
+	\ .
+\end{equation}
+Taking derivatives
+\begin{equation}
+	\dfrac{\partial}{\partial z} \ln p_{Z}(z) =
+	-\left(
+		\dfrac{
+			z-{\mu}_0
+		}
+		{
+			{\sigma}_0^2
+		}
+	\right)
+\end{equation}
+\begin{equation}
+	\dfrac{\partial^2}{\partial^2 z} \ln p_{Z}(z) =
+	-\dfrac{
+		1
+	}
+	{
+		{\sigma}_0^2
+	}
+\end{equation}
+which motivates the estimator \citep{efron2004large}
 \begin{equation}
@@
 \end{equation}
-In this particular example, it was found that $\widehat{\mu}_0=\input{../tables/empirical_null_sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../tables/empirical_null_sub_null_sigma.txt}...$.
-It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.
-
-The empirical null is used to correct the test statistics $z_1,z_2,\dotdotdot,z_n$ to $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ by standardising the test statistics
-\begin{equation}
-	\zeta_i = \dfrac{
-		z_i - \widehat{\mu}_0
-	}
-	{
-		\widehat{\sigma}_0
-	}
-	\ .
-	\label{eq:inference_zeta}
-\end{equation}
-The corrected test statistics $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ are then used in any multiple hypothesis testing procedures.
-Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../tables/empirical_null_sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../tables/empirical_null_sub_null_critical1.txt}...$ and $\input{../tables/empirical_null_sub_null_critical2.txt}...\leqslant Z$.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_null.eps}
-        \caption{Histogram of $z$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_p_values.eps}
-        \caption{Ordered $p$ values}
-    \end{subfigure}
-    }
-    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
-    \label{fig:inference_empirical_null_sub_z_critical_regions}
-\end{figure}
-
-These new critical regions are shown in Figure \ref{fig:inference_empirical_null_sub_z_critical_regions}.
-No positive results were found and the $p$-values are sensible as they look uniformly distributed.
-This demonstrated that the empirical null adjusts the parameters of the null distribution to fit the data in order to make sensible inference.
-
-In this section, a more mathematical approach to the empirical null will be taken to examine why and when this method works.
-Next computational concepts will be discussed such as on how the mode of the kernel density estimator is found and what makes a good bandwidth in the kernel density estimator.
-
-\subsection{More on the Empirical Null}
-
-\cite{efron2004large} was motivated to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
-These problems are similar to the one observed at the start of this chapter.
-The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
-
-For formality, the null and alternative hypotheses shall be described here. Assume that the $z$ statistics under the null hypothesis are such that
-\begin{equation}
-	Z_i|H_0\sim\normal(\mu,\widehat{\sigma}_0^2)
-\end{equation}
-for $i=1,2,\dotdotdot,n$ and i.i.d. The hypotheses are then
-\begin{equation}
-	H_0:\mu = \widehat{\mu}_0
-\end{equation}
-and
-\begin{equation}
-	H_1:\mu\neq\widehat{\mu}_0
-	\ .
-\end{equation}
-Essentially null $z$ statistics are assumed to be Normal distributed, with parameters using the empirical null. Statistics which deviates too much from $\widehat{\mu}_0$ are considered to be positive.
-
-The distribution of the $z$ statistics can be described using a mixture model. Let the random variable $Z$ have the probability density function
-\begin{equation}
-	p_Z(z) =
-	\pi_0 p_{Z|H_0}(z) + \pi_1 p_{Z|H_1}(z)
-\end{equation}
-where $0\leqslant\pi_0\leqslant 1$ and  $\pi_1 = 1-\pi_0$. In addition, the null distribution is
-\begin{equation}
-	p_{Z|H_0}(z) = 
-	\dfrac{1}{\sqrt{2\pi}\widehat{\sigma}_0}
-	\exp\left[
-		-\dfrac{1}{2}
-		\left(
-			\dfrac{z-\widehat{\mu}_0}{\widehat{\sigma}_0}
-		\right)^2
-	\right]
-\end{equation}
-as it was assumed to be Normal. The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified.
-
-The empirical null parameters can be obtained from the following.
-Assume that $\pi_0$ is large, say bigger than 0.9 \citep{efron2004large}, and at and around the mode the probability density function is dominated by the null distribution.
-This implies that
-\begin{equation}
-	p_{Z}(z) \approx \pi_0 p_{Z|H_0}(z)
-\end{equation}
-for values of $z$ around the mode.
-Finding the maximum for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution.
-This justifies the use of the mode for the empirical null mean \citep{efron2004large}
-\begin{equation}
-	\widehat{\mu}_0 = \argmax\widehat{p}_Z(z) \ .
-\end{equation} 
-The empirical null standard deviation can be obtained by noting that
-\begin{equation}
-	p_{Z}(z) = 
-	\dfrac{\pi_0}{\sqrt{2\pi}\widehat{\sigma}_0}
-	\exp\left[
-		-\dfrac{1}{2}
-		\left(
-			\dfrac{z-\widehat{\mu}_0}{\widehat{\sigma}_0}
-		\right)^2
-	\right] \ .
-\end{equation}
-Taking the log of both sides
-\begin{equation}
-	\ln p_{Z}(z) = 
-	\ln\left[
-		\dfrac{\pi_0}{\sqrt{2\pi}\widehat{\sigma}_0}
-	\right]
-	-\dfrac{1}{2}
-	\left(
-		\dfrac{z-\widehat{\mu}_0}{\widehat{\sigma}_0}
-	\right)^2
-	\ .
-\end{equation}
-Taking derivatives of the log density
-\begin{equation}
-	\dfrac{\partial}{\partial z} \ln p_{Z}(z) =
-	-\left(
-		\dfrac{
-			z-\widehat{\mu}_0
-		}
-		{
-			\widehat{\sigma}_0^2
-		}
-	\right)
-\end{equation}
-\begin{equation}
-	\dfrac{\partial^2}{\partial^2 z} \ln p_{Z}(z) =
-	-\dfrac{
-		1
-	}
-	{
-		\widehat{\sigma}_0^2
-	}
-\end{equation}
-which motivates the estimator \citep{efron2004large}
-\begin{equation}
-	\widehat{\sigma}_0 = \left[
-		\left.
-			-\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
-		\right|_{z=\widehat{\mu}_0}
-	\right]^{-1/2}
-	\ .
-\end{equation}
 The evaluation of $z=\widehat{\mu}_0$ is used as in that region, one would hope that null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.
@@
 The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}.
-Because of the assumptions made on the empirical null, the easiest method is
-\begin{equation}
-	\widehat{\pi}_0 = \dfrac{\widehat{p}_Z(z)}{p_{Z|H_0}(\widehat{\mu}_0)}
-	\ .
-\end{equation}
-\cite{efron2004large} also motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.
+\cite{efron2004large} motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.
 
@@
 
-The mode can be found by solving for $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$.
+The mode was found by solving for $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$.
 This cannot be solved in closed form easily and should be done numerically.
 The  Newton-Raphson method can be used to solve $\hat{p}_Z'(z) = 0$ for $z$.
-Instead the log space will be used, solving
+Instead the log space was used, solving
 \begin{equation}
@@
 \end{equation}
-for $z$. This will at least find stationary points.
+for $z$. This at least find stationary points.
 
@@
 \end{equation}
-for $r=0,1,2,3,\dotdotdot$ until some convergence condition is met. The derivatives for the log density can be obtained via the following. Recall that the kernel density estimate is
+for $r=0,1,2,3,\dotdotdot$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is
 \begin{equation}
@@
 \end{equation}
-Using the fact that $\phi(z)=(2\pi)^{-1/2}\exp(-z^2/2)$, then $\phi'(z)=-z\phi(z)$. This can be used to simplify the equation to be
+Using the fact that $\phi(z)=(2\pi)^{-1/2}\exp(-z^2/2)$, then $\phi'(z)=-z\phi(z)$. This is used to simplify the equation to be
 \begin{equation}
@@
 \end{multline}
-Using the fact that $\phi'(z)=-z\phi(z)$, then it can be simplified to
+Using the fact that $\phi'(z)=-z\phi(z)$, then it is simplified to
 \begin{multline}
@@
 
-It was chosen that convergence is met when either 10 update steps were taken or when
+It was chosen that convergence was met when either 10 update steps were taken or when
 \begin{equation}
@@
 \end{equation}
-Following a successful convergence, the estimator $\widehat{\sigma}_0$ can be calculated straight away.
+Following a successful convergence, the estimator $\widehat{\sigma}_0$ was calculated straight away.
 
 The algorithm does depend on the initial value so using different initial values is recommended.
-It was chosen here to use the quartiles of the data as the initial values and then select the best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of the different initial values.
+It was chosen here to use the quartiles of the data as the initial values and then select the best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of all the different initial values.
 Should the algorithm still fail, a random data point is selected to be the initial value until a successful convergence is achieved.
-The Newton-Raphson method can fail if it converges to a stationary point other than a global maximum, for example a local maxima or a point of inflection.
+The Newton-Raphson method can fail if it converges to a stationary point other than a global maximum, for example a local maximum or a point of inflection.
 
@@
 However exact properties of these estimators based on the kernel density estimators can be rather complicated.
-Empirical properties shall be studied here.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull1.eps}
-        \caption{$\mu_0$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull2.eps}
-        \caption{$\sigma_0$}
-    \end{subfigure}
-    }
-    \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
-    \label{fig:inference_ZNull1}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull3.eps}
-        \caption{3D plot}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull4.png}
-        \caption{Heatmap}
-    \end{subfigure}
-    }
-    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of simulated $\normal(0,1)$ data.
-On the right, lines represent the rule of thumb for various values of $b$.
-On the left shows the true value of $\sigma_0=1$ as a plane, the empirical truth is where that plan intersects the surface.}
-    \label{fig:inference_ZNull2}
-\end{figure}
-
-An experiment was conducted to investigate the behaviour of the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, on a dataset of simulated all null $\normal(0,1)$.
+Empirical properties is studied here.
+
+An experiment was conducted to investigate the behaviour of the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, on a dataset of $n$ simulated all null $\normal(0,1)$.
 Various values of $h$ and $n$ were investigated.
@@
 For a given $h$ and $n$, 50 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation.
-The median squared error for each of the estimators were plotted as shown in Figure \ref{fig:inference_ZNull1}.
-
-$\widehat{\mu}_0$ has low median squared error for large bandwidths, in particular for low $n$.
-This is because smoother curves prevents any false bimodal features appearing, making it easier to find the mode.
+The median squared error, over the 50 repeats, for each of the estimators were plotted as shown in Figure \ref{fig:inference_ZNull1}.
+
+$\widehat{\mu}_0$ has low median squared error for large bandwidths.
+For low $n$, large bandwidths are particularly important because smoother curves prevents any false bimodal features appearing, making it easier to find the mode.
 
@@
 
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull1.eps}
+        \caption{$\mu_0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull2.eps}
+        \caption{$\sigma_0$}
+    \end{subfigure}
+    }
+    \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
+    \label{fig:inference_ZNull1}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull3.eps}
+        \caption{3D plot}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/ZNull4.png}
+        \caption{Heatmap}
+    \end{subfigure}
+    }
+    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of $n$ simulated $\normal(0,1)$ data.
+On the right, lines represent the rule of thumb for various values of $b$.
+On the left shows the true value of $\sigma_0=1$ as a plane, the empirical truth is where that plan intersects the surface.}
+    \label{fig:inference_ZNull2}
+\end{figure}
+
 Overestimates and underestimates are both dangerous, but it depends on the importance of false positives and false negatives.
-This is because $\widehat{\sigma}_0$ is used to rescale the test statistics accordingly.
+This is because $\widehat{\sigma}_0$ was used to rescale the test statistics accordingly.
 Recall that the corrected test statistics are
@@
 \end{equation}
-Low values of $\widehat{\sigma}_0$ will produce high values in magnitude of $\zeta_i$, potentially testing more of these test statistics as positive.
+Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $\zeta_i$, potentially testing more of these test statistics as significant.
 High values of $\widehat{\sigma}_0$ does the opposite.
@@
 The optimal bandwidth for a given $n$ was found numerically.
-Such a relationship can be seen clearly seen in Figure \ref{fig:inference_ZNull_mse_plot} which plots the log mean squared error against the bandwidth for various $n$.
+Such a relationship can be seen in Figure \ref{fig:inference_ZNull_mse_plot} which plots the log squared error against the bandwidth for various $n$.
 A local quadratic regression \citep{friedman2001elements} was fitted and this was used to find the bandwidth which minimises the log squared error for a given $n$.
@@
 
-The results show that the rules of thumb can be improved if a small bias is added to it.
+The results showed that the rules of thumb can be improved if a small bias is added to it.
 This is because an intercept was found when fitting a linear relationship between the optimal bandwidth and $n^{-1/5}$.
@@
 
-In conclusion, a small bias added to the rule of thumb will improve the performance of the estimator $\widehat{\sigma}_0$.
+In conclusion, a small bias added to the rule of thumb improved the performance of the estimator $\widehat{\sigma}_0$.
 \cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggest the use of $b=0.9$ rather than $b=1.06$.
-Following from this, it was chosen that the intercept shall be added to Silverman's rule of thumb for the use in the empirical null
+Following from this, it was chosen that the intercept was added to Silverman's rule of thumb for the use in the empirical null
 \begin{equation}
@@
 
-A further example will be given here.
+A further example is given here.
 A $200\times200$ sub-sample, containing a defect, was taken as shown in Figure \ref{fig:inference_alt_empirical_z_image}.
-The histogram of the test statistics are shown in Figure \ref{fig:inference_alt_empirical_z_histogram}.
+The histogram of the test statistics, along with the empirical null, is shown in Figure \ref{fig:inference_alt_empirical_z_histogram}.
 It can be seen that the null distribution is not centred at zero, however the empirical null takes that into account.
@@
         \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_histo_null.eps}
-        \caption{Histogram}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_parzen.eps}
-        \caption{Kernel density estimate}
-    \end{subfigure}
-    }
-    \caption{Histogram and kernel density estimate of the $z$ statistics, taken from the sub-sample.}
+        \caption{Histogram and empirical null}
         \label{fig:inference_alt_empirical_z_histogram}
-\end{figure}
-
-The BH procedure can be conducted, corrected for the empirical null.
-The $p$-values are shown in \ref{fig:inference_alt_empirical_z_p_values}, a number of them are significant.
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_p_values.eps}
+        \caption{Ordered $p$-values}
+        \label{fig:inference_alt_empirical_z_p_values}
+    \end{subfigure}
+    }
+    \caption{Histogram and $p$-values, corrected using the empirical null, of the test statistics taken from the sub-sample.}
+\end{figure}
+
+The BH procedure was conducted, corrected for the empirical null.
+The $p$-values are shown in Figure \ref{fig:inference_alt_empirical_z_p_values}.
+$\input{../tables/alt_empirical_n_sig.txt}$ pixels were significant.
 The significant pixels are shown in red in Figure \ref{fig:inference_alt_empirical_z_image}.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/inference/alt_empirical_z_p_values.eps}
-	\caption{Ordered $p$ values corrected for the empirical null.}
-	\label{fig:inference_alt_empirical_z_p_values}
-\end{figure}
-
 Only a few pixels were falsely tested as positive, however they are typically isolated single pixels.
@@
 The empirical null is a good tool for defect detection under model misspecification.
-One possible implementation is to spilt the $z$ image into a grid and conduct inference in each section separately.
+The empirical null could be used to solve the problem encountered at the start of the chapter.
+Recall that false positives were a problem due to model misspecification because the test statistics were not standard Normal distributed, as seen in Figure \ref{fig:inference_initial_artist_z_histo}.
+However the problem is that looking at the test statistics spatially in Figure \ref{fig:inference_initial_artist_logp_z}, the empirical null varied spatially.
+This is because it looked like the value of the test statistics depended on which surface it is on for example.
+
+One possible solution is to spilt the $z$ image into a grid and conduct inference in each section separately.
 There are problems with this though.
 The first problem is that how the grid is overlaid can be arbitrary, for example the grid can be translated to produce different sections.
-Secondly one could ask how the results from each section are combined \citep{efron2008simultaneous}?
-The empirical null filter is another implementation for the empirical null which only requires a window size to be specified.
+Secondly it is not clear how to combine the results from each section \citep{efron2008simultaneous}.
 
@@
 
-The empirical null filter is an extension to the empirical null. In this setting, the parameters of the empirical null varies spatially. Let $Z_{x,y}$ be the test statistic at position $(x,y)$, then
-\begin{equation}
-	Z_{x,y}\sim\normal\left(
-		\mu_{0,x,y},\sigma_{0,x,y}^2
-	\right)
-\end{equation}
-where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the empirical null mean and standard deviation at position $(x,y)$ respectively. The empirical null filter aims to estimate these parameters.
+The empirical null filter is an extension to the empirical null. In this setting, the parameters of the empirical null varies spatially. Let $Z_{x,y}$ be the test statistic at position $(x,y)$ and
+\begin{equation}
+	Z_{x,y}|H_0\sim\normal\left(
+		\mu_{x,y},\sigma_{0,x,y}^2
+	\right)
+	\ .
+\end{equation}
+Let the hypotheses
+\begin{equation}
+	H_0:\mu_{x,y}=\mu_{0,x,y}
+\end{equation}
+and
+\begin{equation}
+	H_1:\mu_{x,y}\neq\mu_{0,x,y}
+\end{equation}
+be tested for each pixel individually where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the empirical null mean and standard deviation at position $(x,y)$ respectively.
+The empirical null filter aims to estimate these parameters.
 
@@
 In particular, Figure \ref{fig:inference_filter_z_ordered_p} shows that the test statistics look more Normal but with heavier tails.
-The heavier tails are contributed to non-null test statistics.
+The heavier tails are contributed by non-null test statistics.
 Significant pixels are shown in Figure \ref{fig:inference_filter_sig_image}.
-It is encouraging to see less false positives and more defects being picked up.
+It was encouraging to see less false positives and more defects being picked up.
 Because the BH procedure controls the FDR, some false positives are inevitable.
@@
     }
-    \caption{Histogram of $z$ statistics and the corresponding ordered $p$-values}
+    \caption{Histogram of $z$ statistics and the corresponding ordered $p$-values when using the empirical null filter.}
     \label{fig:inference_filter_z_ordered_p}
@@
 Figure \ref{fig:inference_filter_mean_null} shows the $\widehat{\mu}_{0,x,y}$ image, which varies a lot but smoothly.
-This demonstrated that by corrected the test statistics accordingly, sensible inference was achieved.
-
-In the remaining of the chapter, properties of the empirical null filter are investigated.
+This demonstrated that by correcting the test statistics accordingly, sensible inference was achieved.
+
+In the remaining of the chapter, properties of the empirical null filter were investigated.
 
@@
 A smooth function was added to the ground truth to contaminate it and cause some systematic error.
-The idea was that the empirical null filter did inference without being effected too much by the smooth function.
+The idea was that the empirical null filter should do inference without being affected too much by the smooth function.
 
@@
 Figures \ref{fig:inference_NoDefect_Plane_sigma} and \ref{fig:inference_NoDefect_Sinusoid_sigma} shows the false positive rate for the plane and sinusoid contamination respectively.
-It can be seen that false positives can happen and in particular when the smooth function is quite harsh and varies a lot spatially.
+For sensible varying functions, the empirical null filter did a good job of not being detecting the contamination as significant.
+In extreme cases it can be seen that false positives can happen and in particular when the smooth function is quite harsh and varies a lot spatially.
 This showed that the empirical null filter was not completely perfect and false positives can happen.
@@
     }
-    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $10^4$.}
+    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $3\times10^3$.}
     \label{fig:inference_NoDefect_Sinusoid_p_sig}
@@
 
-Furthermore, defects were added to the ground truth by increasing selected pixels' grey-values. Shapes such as squares and lines were used to simulate voids and cracks.
+Furthermore, defects were added to the ground truth by increasing selected pixels' grey values. Shapes such as squares and lines were used to simulate voids and cracks.
 
@@
 The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds.
-Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity instead.
+Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity.
 
 The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
-Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed throughly in \citep{cook2007use}.
+Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed throughly in \cite{cook2007use}.
 The area under the ROC curve was recorded for different intensity values of the defect.
@@
 Figures \ref{fig:inference_SimulateRoc_Line_p_sig} and \ref{fig:inference_SimulateRoc_Squares_p_sig} shows the results of using the empirical null filter for inference.
-In this example an array of squares and a single vertical line were used to defect the ground truth by adding 298 to the grey value, a particular small number.
+In this example an array of squares and a single vertical line were used to defect the ground truth by adding 298 to the grey value, a particularly small number.
 The defects were picked up which is remarkable.
-The structure of the false positives is quite similar to Figure \ref{fig:inference_NoDefect_Plane_p_sig}, indicating that the plane was still quite harsh and responsible for the false positives.
+The structure of the false positives is quite similar to Figure \ref{fig:inference_NoDefect_Plane_p_sig}, indicating that the plane was still mildly harsh and responsible for the false positives.
 
@@
 The dotted diagonal line show the ROC curve if the test classify each pixel randomly.
-Perfect classification happens on the top left when the true positive rate is one and the false positive rate is zero.
+Perfect classification happens on the top left of the graph when the true positive rate is one and the false positive rate is zero.
 A sample of ROC curves were obtained by reallocating the images to the ground truth, variance-mean training and testing, this was done 5 times.

### 2018-04-18 inference/NoDefect/Experiment_NoDefect_Sinusoid.m

@@ -28,7 +28,7 @@ classdef Experiment_NoDefect_Sinusoid < Experiment_NoDefect
         %OVERRIDE: SETUP
         function setup(this)
             %call superclass version of setup
-            this.setup@Experiment_NoDefect(RandStream('mt19937ar','Seed',uint32(707037501)), linspace(0,1E4,10));
+            this.setup@Experiment_NoDefect(RandStream('mt19937ar','Seed',uint32(707037501)), linspace(0,3E3,10));
         end
         
         %IMPLEMENTED: GET DEFECT SIMULATOR

### 2018-04-18 inference/scripts/alt_empirical_script.m

@@ -42,38 +42,32 @@ z_bh_empirical = z_tester.getZCritical();
 %Plot the histogram of z statistics
 %Also plot the empirical null BH critical boundary
 fig = LatexFigure.sub();
-z_tester.plotHistogram();
-hold on;
-z_tester.plotCritical();
-ylabel('frequency density');
-xlabel('z');
-hold on;
-legend('z histogram','critical','Location','northeast');
+z_tester.plotHistCritical();
 saveas(fig,fullfile('reports','figures','inference','alt_empirical_z_histo_null.eps'),'epsc');
 
-%FIGURE
-%Plot the frequency density estimate along with the empirical null mean and std, and critical boundary
-fig = LatexFigure.sub();
-z_tester.plotDensityEstimate(x_plot);
-hold on;
-z_tester.plotCritical();
-plot([mu_0,mu_0],[0,numel(z_sample)*density_estimate.getDensityEstimate(mu_0)],'k--'); %plot mode
-%get the value of the density estimate at mu +/- sigma
-f_at_sigma_1 = mean(density_estimate.getDensityEstimate([mu_0-sigma_0,mu_0+sigma_0]));
-%plot line and arrows to represent 2 std
-plot([mu_0-sigma_0,mu_0+sigma_0],numel(z_sample)*[f_at_sigma_1,f_at_sigma_1],'k--');
-scatter(mu_0-sigma_0,numel(z_sample)*f_at_sigma_1,'k<','filled');
-scatter(mu_0+sigma_0,numel(z_sample)*f_at_sigma_1,'k>','filled');
-ylabel('frequency density');
-xlabel('z');
-hold on;
-legend('density estimate','critical','Location','northeast');
-saveas(fig,fullfile('reports','figures','inference','alt_empirical_z_parzen.eps'),'epsc');
+% %FIGURE
+% %Plot the frequency density estimate along with the empirical null mean and std, and critical boundary
+% fig = LatexFigure.sub();
+% z_tester.plotDensityEstimate(x_plot);
+% hold on;
+% z_tester.plotCritical();
+% plot([mu_0,mu_0],[0,numel(z_sample)*density_estimate.getDensityEstimate(mu_0)],'k--'); %plot mode
+% %get the value of the density estimate at mu +/- sigma
+% f_at_sigma_1 = mean(density_estimate.getDensityEstimate([mu_0-sigma_0,mu_0+sigma_0]));
[…]

### 2018-12-05 reports/thesis/book.tex
Added multiple hypothesis test section.
Adjusted harshness in NoDefect_Sinusoid, proof read inference chapter.
Started on empirical null filter subsection

@@
 \usepackage{pdfpages}
+\usepackage{MnSymbol} %udots
 
@@
 \DeclareMathOperator{\CPoisson}{CP\Gamma}
-\DeclareMathOperator{\normDist}{N}
+\DeclareMathOperator*{\argmax}{argmax}
 
@@
 \section*{Abstract}
-X-ray CT can be used for defect detection and quality control of 3D printing.
-This report will outline statistical methods for comparing x-ray scans of a 3D printed sample with its computer model under the face of uncertainty.
-Shading correction methods and the mean and variance relationship were investigated.
-Lastly the compound Poisson was reviewed.
+X-ray computed tomography (CT) can be used for defect detection in 3D printing.
+The object is scanned at multiple angles to reconstruct the object in 3D space.
+The process can be time consuming.
+The aim of this project was to investigate if it is possible to conduct defect detection in projection space from a single scan to speed up the defect detection procedure.
+To do this, a 3D printed sample was manufactured with voids to see if they can be detected.
+
+X-ray photons behave randomly.
+Hence to do defect detection pixel by pixel, uncertainty must be taken into account.
+A compound Poisson model was used to model the grey valyes in a pixel.
+It assumed that photon arrivals are a Poisson process with Gamma distributed energy.
+This resulted in a linear relationship between the mean and variance of the grey value, which was used for variance prediction and to quantify the uncertainty.
+
+Software, called \texttt{aRTist}, was used to simulate the scan and it was compared with the x-ray acquisition under the face of uncertainty.
+However the software, and the information provided to it, was not perfect which led to model misspecification and incorrect inference.
+The empirical null filter was proposed.
+It adjust each pixel statistic so that inference was done by comparing each pixel with the majority of its local pixels.
 

### 2018-12-05 reports/thesis/chapters/5_inference.tex
Started on empirical null filter subsection

@@
 
-The empirical null filter is an extension to the empirical null. In this setting, the parameters of the empirical null varies spatially. Let $Z_{x,y}$ be the test statistic at position $(x,y)$ and
+The empirical null filter extends the empirical null to images.
+In this setting, the parameters of the null distribution varies spatially, slowly and smoothly in 2D space.
+Let $Z_{x,y}$ be the test statistic of the pixel at position $(x,y)$ for $x=1,2,\dotdotdot,W$ and $y=1,2,\dotdotdot,H$.
+Let each pixel have a test statistic distributed under the null such that
 \begin{equation}
@@
 \end{equation}
-Let the hypotheses
+Let the hypothesis
 \begin{equation}
@@
 \end{equation}
+\begin{equation}
+	H_1:\mu_{x,y}\neq\mu_{0,x,y}
+\end{equation}
+be tested for each pixel individually where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively.
+Suppose $Z_{x,y}=z_{x,y}$ were observed for all $x$ and $y$.
+The empirical null filter aims to estimate the parameters $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ for all $x$ and $y$.
+This is so that inference can be done under the empirical null distribution.
+
+The empirical null filter uses the empirical null on neighbouring pixels to estimate the null distribution parameters.
+For example to estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel of radius $r$ is centred at $(x,y)$.
+All the pixels captured in the circular kernel are then used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
+\begin{equation}
+	\widehat{\mu}_{0,x,y}
+	=
+	\widehat{\mu}_{0,x,y}
+		\left(
+			\text{all }z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
+		\right)
+\end{equation}
 and
 \begin{equation}
-	H_1:\mu_{x,y}\neq\mu_{0,x,y}
-\end{equation}
-be tested for each pixel individually where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the empirical null mean and standard deviation at position $(x,y)$ respectively.
-The empirical null filter aims to estimate these parameters.
-
-The method is the following.
-A window size needs to be specified, say $201\times201$.
-The window is placed over and centred at pixel $(x,y)$ capturing the pixels $z_{i,j}$ for $x-100\leqslant i \leqslant x+100$ and $y-100\leqslant j \leqslant y+100$.
-The estimators $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ are the empirical null mean and standard deviation estimators, respectively, using the pixels captured in that window.
-This is then repeated for all $x$ and $y$.
-The $z$ statistics are then corrected using
+	\widehat{\sigma}_{0,x,y}
+	=
+	\widehat{\sigma}_{0,x,y}
+		\left(
+			\text{all }z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
+		\right)
+	\ .
+\end{equation}
+Using these estimates, the test statistics are then corrected using
 \begin{equation}
@@
 \end{equation}
-and only the corrected test statistics are used in the BH procedure.
+and only the corrected test statistics are used in hypothesis testing.
+
+The critical parameter of choice is the kernel radius $r$.
+A $r$ too small will treat defects as the null and will not detect them.
+A $r$ too big can also cause problems as well.
+The empirical null filter does assume the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal.
+If $r$ is too big, the kernel will capture far away test statistics with a very different null distribution.
+If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution.
+Furthermore, if $r\rightarrow \infty$, then this is just using the empirical null on all pixels which is, as discussed before, not sensible.
+
+$r$ does control the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$. If the size of the defects are known, then $r$ should be selected such that
+\begin{equation}
+\dfrac{
+	\text{area of defect}
+}
+{
+	\pi r^2
+}
+\approx
+5\% \text{ to } 10 \%
+\end{equation}
+so that $\pi_0$ is of a sensible value.
+In practice, the defects are unknown so various kernel radiuses should be tried out.
+But in general, the kernel radius should be much larger than the size of the defect.
+
+The empirical null filter was implemented in an open source software called \texttt{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \texttt{GitHub} \citep{imagej2018rank}.
+This class implemented filters, such as the mean filter and median filter, using a circular kernel and multiple threads, making this a suitable framework for the empirical null filter.
+Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \texttt{Fiji} \citep{schindelin2012fiji}, a distribution of \texttt{ImageJ}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../figures/inference/fiji/gui.png}
+    \caption{Graphical user interface of the empirical null filter in \texttt{Fiji}.
+The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate.
+By products such as the empirical null parameters can be shown after the filtering as well.}
+    \label{fig:inference_fijiGui}
+\end{figure}
+
+As a test, the empirical null filter with $r=5$ was used on a \texttt{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
+It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it does verify the filter works on arbitrary images.
+The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all ${x,y}$ could be of interest.
+In particular the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}.
+Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters.
+The empirical null mean creates an impasto look which is similar to the result in \cite{griffin2000mean}.
+Spread filters such as the standard deviation filter can be used to detect edges.
+Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation.
+The resulting images are similar but it was notable that the edges in the empirical null standard deviation are sharper.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
+        \caption{Before filtering}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridgeFilter.png}
+        \caption{After filtering}
+    \end{subfigure}
+    }
+    \caption{Empirical null filter with $r=5$ on the sample image \texttt{bridge.gif}.}
+    \label{fig:inference_fijiBridgeFilter}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
+        \caption{No filter}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/mean.png}
+        \caption{Mean filter}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/median.png}
+        \caption{Median filter}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullMean.png}
+        \caption{Empirical null mean}
+    \end{subfigure}
+    }
+    \caption{Various average filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}}
+    \label{fig:inference_fijiMean}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/std.png}
+        \caption{Standard deviation filter}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullStd.png}
+        \caption{Empirical null standard deviation}
+    \end{subfigure}
+    }
+    \caption{Various spread filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
+    \label{fig:inference_fijiStd}
+\end{figure}
+
+\subsection{Design and Implementation}
+
+When using the the empirical null filter in \texttt{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
+Here the user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $\zeta_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
+The menu also has options for by product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, and quartile filters.
+Advanced options are available to the user.
+The number of initial values set the number of valid solutions required in the Newton-Raphson method on finding the mode of the density estimate.
+The user can also set the maximum number of steps and tolerance for the Newton-Raphson method.
+The bandwidth parameters for the kernel density estimate can also be adjusted here.
+
+Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design has already been done.
+\texttt{RankFilters} contain implementations of filters such as the mean filter and median filter.
+The implementation makes use of multiple threads, each thread filters a row in parallel.
+This is done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache.
+Then for each column, the thread does its calculations using the cache then replaces the pixel value of the image to be filtered.
+Once the row has been filtered, the thread then moves onto the next unfiltered row.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+	    \begin{tabular}{lllllll}
+	       $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
+	       $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
+	       $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\ \cline{4-6}
+	       $\cdots$ & $z_{1,1}$ & \multicolumn{1}{l|}{$z_{1,1}$} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
+	       $\cdots$ & $z_{2,1}$ & \multicolumn{1}{l|}{$z_{2,1}$}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
+	       $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
+		\end{tabular}
+		\caption{Nearest pixel padding}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+	    \begin{tabular}{lllllll}
+	       $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
+	       $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\
+	       $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\ \cline{4-6}
+	       $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
+	       $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
+	       $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
+		\end{tabular}
+		\caption{\texttt{NaN} padding}
+	\end{subfigure}
+	\caption{When a kernel contain pixels outside the region of interest as shown by the solid line, the missing pixels can either be interpolated using the nearest pixel or completely ignored by filling in the missing pixels with \texttt{NaN}.}
+	\label{fig:inference_padding}
+\end{figure}
+
+\subsection{All Null Simulation}
+
+An experiment was conducted to investigate how well the empirical null filter performs with no defects. The dataset \texttt{July 30deg} was used in this experiment.
+
+The images in the dataset were spilt into two halves randomly.
+The mean over the first half of the images was taken and this was used as the ground truth, acting like an \texttt{aRTist} simulation.
+A smooth function was added to the ground truth to contaminate it and cause some systematic error.
+The idea was that the empirical null filter should do inference without being affected too much by the smooth function.
+
+In the second half, all but one of the images were used in the training of the variance-mean model.
+The remaining image, the test image, was then used to compare with the simulated ground truth, producing a $z$ image.
+The $z$ image was then inferred using the empirical null filter and then the BH procedure.
+
+The smooth functions investigated were a plane and a sinusoid.
+The harshness of the smooth functions were controlled using the gradient for the plane, and the amplitude for the sinusoid.
+The smooth functions are for the plane
+\begin{equation}
+	\delta\left[
+		(x-x_0)+(y-y_0)
+	\right]
+\end{equation}
+and the sinusoid
+\begin{equation}
+	A\sin\left[
+		\dfrac{
+			2\pi
+		}
+		{
+			750
+		}
+		\left(
+			(y-y_0)-(x-x_0)
+		\right)
+	\right]
+\end{equation}
+where $\delta$ is the gradient, $A$ is the amplitude and $(x_0,y_0)$ is the centre of the image.
+
+Because no defects were implemented in this experiment, any positive results are false.
+The false positive rates were investigated for different harshness of the smooth functions.
+The experiment was repeated 20 times by randomly reallocating the images used for the ground truth, variance-mean training and testing.
+
+Figures \ref{fig:inference_NoDefect_Plane_sigma} and \ref{fig:inference_NoDefect_Sinusoid_sigma} shows the false positive rate for the plane and sinusoid contamination respectively.
+For sensible varying functions, the empirical null filter did a good job of not being detecting the contamination as significant.
+In extreme cases it can be seen that false positives can happen and in particular when the smooth function is quite harsh and varies a lot spatially.
+This showed that the empirical null filter was not completely perfect and false positives can happen.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane2sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane3sigma.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane4sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane5sigma.eps}
+    \end{subfigure}
+    }
+    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane. Various $z_\alpha$ levels and gradients are shown.}
+    \label{fig:inference_NoDefect_Plane_sigma}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid2sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid3sigma.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid4sigma.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid5sigma.eps}
+    \end{subfigure}
+    }
+    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid. Various $z_\alpha$ levels and gradients are shown.}
+    \label{fig:inference_NoDefect_Sinusoid_sigma}
+\end{figure}
+
+The spatial properties of the false positives did depend on the smooth function.
+Figures \ref{fig:inference_NoDefect_Plane_p_sig} and \ref{fig:inference_NoDefect_Sinusoid_p_sig} shows the location of the positive results for the plane and sinusoid contamination respectively.
+The $p$-values are also shown.
+These false positives are concerning as they are clustered together, giving false indication of a defect.
+
+In practice, the amount of contamination won't be as harsh as the one demonstrated here.
+As long as the smooth function is slowly varying spatially, the empirical null filter will correct the test statistics accordingly.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_pvalues.eps}
+        \caption{$\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_sig.eps}
+        \caption{$z$ image with red significant pixels}
+    \end{subfigure}
+    }
+    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
+    \label{fig:inference_NoDefect_Plane_p_sig}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_pvalues.eps}
+        \caption{$\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_sig.eps}
+        \caption{$z$ image with red significant pixels}
+    \end{subfigure}
+    }
+    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $3\times10^3$.}
+    \label{fig:inference_NoDefect_Sinusoid_p_sig}
+\end{figure}
+
+Figure \ref{fig:inference_NoDefect_nullmean} shows the estimated empirical null mean.
+It is remarkable that the empirical null mean recovers the smooth functions but artefacts from interpolation can be seen for the sinusoid contamination.
+The grid like structure in Figure \ref{fig:inference_NoDefect_Sinusoid_nullmean} shows that the estimated empirical null mean was not very smooth and more points should of been used to reduce the amount of interpolation, increasing the accuracy of the estimation.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_nullmean.eps}
+        \caption{Plane, $\delta = 7.0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_nullmean.eps}
+        \caption{Sinusoid, $A=10^4$}
+        \label{fig:inference_NoDefect_Sinusoid_nullmean}
+    \end{subfigure}
+    }
+    \caption{Empirical null mean when using the empirical null filter on an $z$ image where the ground truth was contaminated by a smooth function.}
+    \label{fig:inference_NoDefect_nullmean}
+\end{figure}
+
+These examples showed that the empirical null filter corrected the test statistics accordingly.
+However in extreme cases, the empirical null filter can fail and producing clusters of low $p$-values giving an illusion of a defect.
+In practice, extreme cases should not happen.
+Referring back to the real life example in Figure \ref{fig:inference_filter_mean_null}, the empirical null mean only varied around $0\pm3$ which is a small variation compared to Figure \ref{fig:inference_NoDefect_nullmean}.
+
+\subsection{Defected Simulation}
+
+An experiment was conducted to see if the empirical null filter detect defects under contamination.
+Just like the previous experiment, the dataset \texttt{July 30deg} was used.
+The images in the dataset were spilt, the mean of the first half acted as the ground truth, the rest were used to train the variance-mean model, one held out for testing.
+A plane with gradient $\delta=3$ was added to the ground truth to contaminate it.
+The contamination from the plane is quite mild following from the previous experiment.
+
+Furthermore, defects were added to the ground truth by increasing selected pixels' grey values. Shapes such as squares and lines were used to simulate voids and cracks.
+
+The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} were investigated.
+The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds.
+Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity.
+
+The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
+Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed throughly in \cite{cook2007use}.
+The area under the ROC curve was recorded for different intensity values of the defect.
+
+Figures \ref{fig:inference_SimulateRoc_Line_p_sig} and \ref{fig:inference_SimulateRoc_Squares_p_sig} shows the results of using the empirical null filter for inference.
+In this example an array of squares and a single vertical line were used to defect the ground truth by adding 298 to the grey value, a particularly small number.
+The defects were picked up which is remarkable.
+The structure of the false positives is quite similar to Figure \ref{fig:inference_NoDefect_Plane_p_sig}, indicating that the plane was still mildly harsh and responsible for the false positives.
+
+The empirical null filter can fail if it treats a defect as the null.
+This can be mildly seen in Figure \ref{fig:inference_SimulateRoc_Squares_p_sig}, the top rows of square defects were not detected but the area outside the defect were tested as positive.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_pvalues.eps}
+        \caption{$-\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_sig.eps}
+        \caption{Image with significant pixels}
+    \end{subfigure}
+    }
+    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by a single vertical line with value 298.}
+    \label{fig:inference_SimulateRoc_Line_p_sig}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_pvalues.eps}
+        \caption{$-\log p$-values}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_sig.eps}
+        \caption{Image with significant pixels}
+    \end{subfigure}
+    }
+    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by an array of squares with value 298.}
+    \label{fig:inference_SimulateRoc_Squares_p_sig}
+\end{figure}
+
+The ROC curves for different defect intensities are shown in Figures \ref{fig:inference_SimulateRoc_Lines_roc} and \ref{fig:inference_SimulateRoc_Squares_roc}.
+The dotted diagonal line show the ROC curve if the test classify each pixel randomly.
+Perfect classification happens on the top left of the graph when the true positive rate is one and the false positive rate is zero.
+A sample of ROC curves were obtained by reallocating the images to the ground truth, variance-mean training and testing, this was done 5 times.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_1.eps}
+        \caption{Defect intensity = 100}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_7.eps}
+        \caption{Defect intensity = 207}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_14.eps}
+        \caption{Defect intensity = 483}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_20.eps}
+        \caption{Defect intensity = 1000}
+    \end{subfigure}
+    }
+    \caption{ROC curves when using the empirical null filter on a simulated comparison.
+The ground truth was contaminated by a plane and defected by an single vertical line.
+Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
+This was done 5 times.}
+    \label{fig:inference_SimulateRoc_Lines_roc}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_1.eps}
+        \caption{Defect intensity = 100}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_7.eps}
+        \caption{Defect intensity = 207}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_14.eps}
+        \caption{Defect intensity = 483}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_20.eps}
+        \caption{Defect intensity = 1000}
+    \end{subfigure}
+    }
+    \caption{ROC curves when using the empirical null filter on a simulated comparison.
+The ground truth was contaminated by a plane and defected by an array of squares.
+Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
+This was done 5 times.}
+    \label{fig:inference_SimulateRoc_Squares_roc}
+\end{figure}
+
+Figure \ref{fig:inference_SimulateRoc_roc_area} shows the area under the ROC curves for the single vertical line and array of squares defect.
+The areas were calculated using the trapezium rule.
+The results are promising with near perfect performance with defect intensities at least 600.
+
+\begin{figure}
+	\centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_area.eps}
+        \caption{Line}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_area.eps}
+        \caption{Squares}
+    \end{subfigure}
+    }
+    \caption{The area under the ROC curves for different defects and defect intensities.
+The ground truth was contaminated by a plane and defected.
+The experiment was repeated 5 times by reallocating images to the ground truth, variance-mean training and testing.
+The box plot represent those 5 repeats.}
+    \label{fig:inference_SimulateRoc_roc_area}
+\end{figure}
+
+The experiments shows that the empirical null filter can correct the null distribution locally, giving better inference.
+In extreme cases, for example if the defect intensity is very small or the amount of contamination is rather large, the empirical null filter can fail.
+Harsh contamination can produce false positives because spatially rapidly changing grey values could be detected as a defect.
+The worst case would be that this would make defects appear to be the null, giving completely the opposite inference.
+
+These extreme cases should not happen.
+As seen in the real life example at the start of the section, false positives are rare but they do have some spatial structure.
+If the defect intensity is too small to be detected, the contrast of the x-ray imaging apparatus should be adjusted to cater for it.
+
+\subsection{Real Data}
 
@@
 In the remaining of the chapter, properties of the empirical null filter were investigated.
-
-\subsection{All Null Simulation}
-
-An experiment was conducted to investigate how well the empirical null filter performs with no defects. The dataset \texttt{July 30deg} was used in this experiment.
-
-The images in the dataset were spilt into two halves randomly.
-The mean over the first half of the images was taken and this was used as the ground truth, acting like an \texttt{aRTist} simulation.
-A smooth function was added to the ground truth to contaminate it and cause some systematic error.
-The idea was that the empirical null filter should do inference without being affected too much by the smooth function.
-
-In the second half, all but one of the images were used in the training of the variance-mean model.
-The remaining image, the test image, was then used to compare with the simulated ground truth, producing a $z$ image.
-The $z$ image was then inferred using the empirical null filter and then the BH procedure.
-
-The smooth functions investigated were a plane and a sinusoid.
-The harshness of the smooth functions were controlled using the gradient for the plane, and the amplitude for the sinusoid.
-The smooth functions are for the plane
-\begin{equation}
-	\delta\left[
-		(x-x_0)+(y-y_0)
-	\right]
-\end{equation}
-and the sinusoid
-\begin{equation}
-	A\sin\left[
-		\dfrac{
-			2\pi
-		}
-		{
-			750
-		}
-		\left(
-			(y-y_0)-(x-x_0)
-		\right)
-	\right]
-\end{equation}
-where $\delta$ is the gradient, $A$ is the amplitude and $(x_0,y_0)$ is the centre of the image.
-
-Because no defects were implemented in this experiment, any positive results are false.
-The false positive rates were investigated for different harshness of the smooth functions.
-The experiment was repeated 20 times by randomly reallocating the images used for the ground truth, variance-mean training and testing.
-
-Figures \ref{fig:inference_NoDefect_Plane_sigma} and \ref{fig:inference_NoDefect_Sinusoid_sigma} shows the false positive rate for the plane and sinusoid contamination respectively.
-For sensible varying functions, the empirical null filter did a good job of not being detecting the contamination as significant.
-In extreme cases it can be seen that false positives can happen and in particular when the smooth function is quite harsh and varies a lot spatially.
-This showed that the empirical null filter was not completely perfect and false positives can happen.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane2sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane3sigma.eps}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane4sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane5sigma.eps}
-    \end{subfigure}
-    }
-    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane. Various $z_\alpha$ levels and gradients are shown.}
-    \label{fig:inference_NoDefect_Plane_sigma}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid2sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid3sigma.eps}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid4sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid5sigma.eps}
-    \end{subfigure}
-    }
-    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid. Various $z_\alpha$ levels and gradients are shown.}
-    \label{fig:inference_NoDefect_Sinusoid_sigma}
-\end{figure}
-
-The spatial properties of the false positives did depend on the smooth function.
-Figures \ref{fig:inference_NoDefect_Plane_p_sig} and \ref{fig:inference_NoDefect_Sinusoid_p_sig} shows the location of the positive results for the plane and sinusoid contamination respectively.
-The $p$-values are also shown.
-These false positives are concerning as they are clustered together, giving false indication of a defect.
-
-In practice, the amount of contamination won't be as harsh as the one demonstrated here.
-As long as the smooth function is slowly varying spatially, the empirical null filter will correct the test statistics accordingly.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_pvalues.eps}
-        \caption{$\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_sig.eps}
-        \caption{$z$ image with red significant pixels}
-    \end{subfigure}
-    }
-    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
-    \label{fig:inference_NoDefect_Plane_p_sig}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_pvalues.eps}
-        \caption{$\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_sig.eps}
-        \caption{$z$ image with red significant pixels}
-    \end{subfigure}
-    }
-    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $3\times10^3$.}
-    \label{fig:inference_NoDefect_Sinusoid_p_sig}
-\end{figure}
-
-Figure \ref{fig:inference_NoDefect_nullmean} shows the estimated empirical null mean.
-It is remarkable that the empirical null mean recovers the smooth functions but artefacts from interpolation can be seen for the sinusoid contamination.
-The grid like structure in Figure \ref{fig:inference_NoDefect_Sinusoid_nullmean} shows that the estimated empirical null mean was not very smooth and more points should of been used to reduce the amount of interpolation, increasing the accuracy of the estimation.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_nullmean.eps}
-        \caption{Plane, $\delta = 7.0$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_nullmean.eps}
-        \caption{Sinusoid, $A=10^4$}
-        \label{fig:inference_NoDefect_Sinusoid_nullmean}
-    \end{subfigure}
-    }
-    \caption{Empirical null mean when using the empirical null filter on an $z$ image where the ground truth was contaminated by a smooth function.}
-    \label{fig:inference_NoDefect_nullmean}
-\end{figure}
-
-These examples showed that the empirical null filter corrected the test statistics accordingly.
-However in extreme cases, the empirical null filter can fail and producing clusters of low $p$-values giving an illusion of a defect.
-In practice, extreme cases should not happen.
-Referring back to the real life example in Figure \ref{fig:inference_filter_mean_null}, the empirical null mean only varied around $0\pm3$ which is a small variation compared to Figure \ref{fig:inference_NoDefect_nullmean}.
-
-\subsection{Defected Simulation}
-
-An experiment was conducted to see if the empirical null filter detect defects under contamination.
-Just like the previous experiment, the dataset \texttt{July 30deg} was used.
-The images in the dataset were spilt, the mean of the first half acted as the ground truth, the rest were used to train the variance-mean model, one held out for testing.
-A plane with gradient $\delta=3$ was added to the ground truth to contaminate it.
-The contamination from the plane is quite mild following from the previous experiment.
-
-Furthermore, defects were added to the ground truth by increasing selected pixels' grey values. Shapes such as squares and lines were used to simulate voids and cracks.
-
-The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} were investigated.
-The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds.
-Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity.
-
-The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
-Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed throughly in \cite{cook2007use}.
-The area under the ROC curve was recorded for different intensity values of the defect.
-
-Figures \ref{fig:inference_SimulateRoc_Line_p_sig} and \ref{fig:inference_SimulateRoc_Squares_p_sig} shows the results of using the empirical null filter for inference.
-In this example an array of squares and a single vertical line were used to defect the ground truth by adding 298 to the grey value, a particularly small number.
-The defects were picked up which is remarkable.
-The structure of the false positives is quite similar to Figure \ref{fig:inference_NoDefect_Plane_p_sig}, indicating that the plane was still mildly harsh and responsible for the false positives.
-
-The empirical null filter can fail if it treats a defect as the null.
-This can be mildly seen in Figure \ref{fig:inference_SimulateRoc_Squares_p_sig}, the top rows of square defects were not detected but the area outside the defect were tested as positive.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_pvalues.eps}
-        \caption{$-\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_sig.eps}
-        \caption{Image with significant pixels}
-    \end{subfigure}
-    }
-    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by a single vertical line with value 298.}
-    \label{fig:inference_SimulateRoc_Line_p_sig}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_pvalues.eps}
-        \caption{$-\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_sig.eps}
-        \caption{Image with significant pixels}
-    \end{subfigure}
-    }
-    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by an array of squares with value 298.}
-    \label{fig:inference_SimulateRoc_Squares_p_sig}
-\end{figure}
-
-The ROC curves for different defect intensities are shown in Figures \ref{fig:inference_SimulateRoc_Lines_roc} and \ref{fig:inference_SimulateRoc_Squares_roc}.
-The dotted diagonal line show the ROC curve if the test classify each pixel randomly.
-Perfect classification happens on the top left of the graph when the true positive rate is one and the false positive rate is zero.
-A sample of ROC curves were obtained by reallocating the images to the ground truth, variance-mean training and testing, this was done 5 times.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_1.eps}
-        \caption{Defect intensity = 100}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_7.eps}
-        \caption{Defect intensity = 207}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_14.eps}
-        \caption{Defect intensity = 483}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_20.eps}
-        \caption{Defect intensity = 1000}
-    \end{subfigure}
-    }
-    \caption{ROC curves when using the empirical null filter on a simulated comparison.
-The ground truth was contaminated by a plane and defected by an single vertical line.
-Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
-This was done 5 times.}
-    \label{fig:inference_SimulateRoc_Lines_roc}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_1.eps}
-        \caption{Defect intensity = 100}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_7.eps}
-        \caption{Defect intensity = 207}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_14.eps}
-        \caption{Defect intensity = 483}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_20.eps}
-        \caption{Defect intensity = 1000}
-    \end{subfigure}
-    }
-    \caption{ROC curves when using the empirical null filter on a simulated comparison.
-The ground truth was contaminated by a plane and defected by an array of squares.
-Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
-This was done 5 times.}
-    \label{fig:inference_SimulateRoc_Squares_roc}
-\end{figure}
-
-Figure \ref{fig:inference_SimulateRoc_roc_area} shows the area under the ROC curves for the single vertical line and array of squares defect.
-The areas were calculated using the trapezium rule.
-The results are promising with near perfect performance with defect intensities at least 600.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_area.eps}
-        \caption{Line}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_area.eps}
-        \caption{Squares}
-    \end{subfigure}
-    }
-    \caption{The area under the ROC curves for different defects and defect intensities.
-The ground truth was contaminated by a plane and defected.
-The experiment was repeated 5 times by reallocating images to the ground truth, variance-mean training and testing.
-The box plot represent those 5 repeats.}
-    \label{fig:inference_SimulateRoc_roc_area}
-\end{figure}
-
-The experiments shows that the empirical null filter can correct the null distribution locally, giving better inference.
-In extreme cases, for example if the defect intensity is very small or the amount of contamination is rather large, the empirical null filter can fail.
-Harsh contamination can produce false positives because spatially rapidly changing grey values could be detected as a defect.
-The worst case would be that this would make defects appear to be the null, giving completely the opposite inference.
-
-These extreme cases should not happen.
-As seen in the real life example at the start of the section, false positives are rare but they do have some spatial structure.
-If the defect intensity is too small to be detected, the contrast of the x-ray imaging apparatus should be adjusted to cater for it.

### 2018-12-09 reports/thesis/chapters/5_inference.tex
Wrote design and implementation of the empirical null filter

@@
 Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters.
-The empirical null mean creates an impasto look which is similar to the result in \cite{griffin2000mean}.
+The empirical null mean creates an impasto look and preserve edges which is similar to the result in \cite{griffin2000mean}.
 Spread filters such as the standard deviation filter can be used to detect edges.
 Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation.
-The resulting images are similar but it was notable that the edges in the empirical null standard deviation are sharper.
+The resulting images are similar but it was notable that the edges in the empirical null standard deviation are sharper, suggesting that the empirical null standard deviation is a more robust measure of spread compared to the standard deviation.
 
@@
 Advanced options are available to the user.
-The number of initial values set the number of valid solutions required in the Newton-Raphson method on finding the mode of the density estimate.
+The number of initial values set the number of valid solutions to be found in the Newton-Raphson method on finding the mode of the density estimate, the solution with the gradient closest to zero is then used in further calculations.
 The user can also set the maximum number of steps and tolerance for the Newton-Raphson method.
@@
 This is done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache.
-Then for each column, the thread does its calculations using the cache then replaces the pixel value of the image to be filtered.
+Then for each column, the thread does calculations using the cache then replaces the pixel value of the image to be filtered.
 Once the row has been filtered, the thread then moves onto the next unfiltered row.
+Rows in the cache not needed are overwritten with more recent rows.
+
+When the kernel captures pixels outside the boundary of the image or region of interest (ROI), \texttt{RankFilters} uses nearest pixel padding which fills in pixels outside the ROI with values to the nearest pixels.
+Figure \ref{fig:inference_padding_nearest} shows an example of nearest pixel padding on the top left corner of a rectangle ROI.
+This is not suitable for the empirical null filter as this will cause bias in a lot of calculations, especially the density fitting.
+The empirical null filter uses \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}.
+This indicate that these pixels are outside the ROI and are ignored.
+The number of non-\texttt{NaN} captured by the kernel is kept track for calculations such as the bandwidth for the kernel density estimate.
 
@@
 		\caption{Nearest pixel padding}
+		\label{fig:inference_padding_nearest}
 	\end{subfigure}
@@
 		\caption{\texttt{NaN} padding}
-	\end{subfigure}
-	\caption{When a kernel contain pixels outside the region of interest as shown by the solid line, the missing pixels can either be interpolated using the nearest pixel or completely ignored by filling in the missing pixels with \texttt{NaN}.}
+		\label{fig:inference_padding_nan}
+	\end{subfigure}
+	\caption{When a kernel contain pixels outside the region of interest as shown by the solid line, the missing pixels can either be extrapolated using the nearest pixel or completely ignored by filling in the missing pixels with \texttt{NaN}.}
 	\label{fig:inference_padding}
 \end{figure}
+
+Line filtering is done from left to right.
+At the start on the far left, an initial value of the median of all the pixels in the kernel is used.
+In addition, various initial values are randomly tried out until a requested number of valid solutions are found, the solution with the gradient closest to zero is used.
+For the following pixel to the right, the empirical null mean of the neighbouring left pixel is used as a initial point.
+This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
+
+Trying out more initial values is an advantage because it eliminates the chances of obtaining a sub-optimal solution such as a local maxima.
+However this is traded for computational cost.
+Additional initial values were generated by sampling from the Normal distribution centred on the first initial value and with standard deviation the same as the standard deviation using all pixels in the kernel.
 

### 2018-12-09 reports/thesis/chapters/5_inference.tex
Started writing on noContamination experiment
tex: made command /addNumber which inputs a text file protected and without space at the end
.eps figures are saved in allNullGaussian
.txt files are saved in allNullGaussian
new figures in allNullGaussian

@@
 
+\subsection{Uncontaminated Experiment}
+The empirical null filter was demonstrated on a $\addNumber{../figures/inference/noContamination/imageSize.txt}\times \addNumber{../figures/inference/noContamination/imageSize.txt}$ image where each pixel has $\normal(0,1)$ test statistics.
+The test statistics after filtering should preserve its original distribution, or at least close to it.
+An experiment was conducted to investigate the empirical properties when filtering such as an image.
+
+An example of the Gaussian image before and after filtering, with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt} is shown in Figure \ref{fig:inference_noContamination_images}.
+A quick glance shows little difference, in particular the QQ plot in Figure \ref{fig:inference_noContamination_qq} shows that the post filter test statistics looked reasonably Normal.
+Because the empirical null mean and empirical null standard deviation are non-Normal random variables, the post filtered test statistics will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
+
+In this experiment, the sample mean and sample variance of the pre/post filtered test statistics were investigated.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.49\textwidth]{../figures/inference/noContamination/qq.eps}
+	\caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
+	\label{fig:inference_noContamination_qq}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/unfiltered.eps}
+		\caption{Unfiltered}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/filtered.eps}
+		\caption{Filtered}
+	\end{subfigure}
+	\caption{A $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
+	\label{fig:inference_noContamination_images}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/nullmean.eps}
+		\caption{Empirical null mean}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/nullstd.eps}
+		\caption{Empirical null std}
+	\end{subfigure}
+	\caption{The empirical null parameters when filtering a $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt}.}
+	\label{fig:inference_noContamination_nullimages}
+\end{figure}
+
+\subsection{Contaminated Experiment}
+
+\subsection{Contaminated Defect Experiment}
+
 \subsection{All Null Simulation}

### 2018-12-10 reports/thesis/chapters/5_inference.tex
Writing up allnull experiments
Wrote subsection No Contamination Experiment, Contamination Experiment
Experiment_AllNull export numbers and figures

--- 2018-12-09 reports/thesis/chapters/5_inference.tex
@@
 
+\subsection{Uncontaminated Experiment}
+The empirical null filter was demonstrated on an image where each pixel has i.i.d.~$\normal(0,1)$ test statistics.
+The test statistics after filtering should preserve its original distribution, or at least close to it.
+An experiment was conducted to investigate the empirical properties when filtering such as an image.
+
+An example of a  $\addNumber{../figures/inference/noContamination/imageSize.txt}\times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering, with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt} is shown in Figure \ref{fig:inference_noContamination_images}.
+A quick glance shows little difference, in particular the QQ plot in Figure \ref{fig:inference_noContamination_qq} shows that the post filter test statistics looked reasonably Normal.
+Because the empirical null mean and empirical null standard deviation are non-Normal random variables, the post filtered test statistics will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.49\textwidth]{../figures/inference/noContamination/allNullGaussianqq.eps}
+	\caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
+	\label{fig:inference_noContamination_qq}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussianunfiltered.eps}
+		\caption{Unfiltered}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussianfiltered.eps}
+		\caption{Filtered}
+	\end{subfigure}
+	}
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussiannullmean.eps}
+		\caption{Empirical null mean}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussiannullstd.eps}
+		\caption{Empirical null std}
+	\end{subfigure}
+	}
+	\caption{A $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.
+Also shown are the empirical null mean and empirical null std.}
+	\label{fig:inference_noContamination_images}
+\end{figure}
+
+In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$ was simulated.
+The sample mean and sample variance of the post filtered test statistics were recorded.
+This was repeated \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} times by simulating another Gaussian image.
+Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradius1.txt}$ to $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradiusend.txt}$ were investigated.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianmean.eps}
+		\caption{Post filter sample mean}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianvariance.eps}
+		\caption{Post filter sample variance}
+	\end{subfigure}
+	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$.
+The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} repeats of the experiment.
+The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
+	\label{fig:inference_allnullgaussian}
+\end{figure}
+
+The results are shown in Figure \ref{fig:inference_allnullgaussian}.
+
+\afterpage{\clearpage}
+\subsection{Contaminated Experiment}
+Consider a $\addNumber{../figures/inference/contamination/imageSize.txt}\times \addNumber{../figures/inference/contamination/imageSize.txt}$ Gaussian image with some contamination.
+For example let the pixels be $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where the null mean is a linear function
+\begin{equation}
+\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)
+\end{equation}
+where $(x_0,y_0)$ is the centre of the image and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
+There are no defects or non-null pixels defined here, therefore any positive detections are false.
+
+Figure \ref{fig:inference_contamination_images} shows an example of a contaminated image before and after filtering.
+When doing a hypothesis test, the contamination caused systematic error such that there are false positives on the two corners of the unfiltered image.
+The empirical null filter can recover the original image by extracting the systematic errors such as the plane, as shown by the empirical null mean, and the increase of variance, as shown by the empirical null std.
+
+The QQ plot of the filtered test statistics, as shown in Figure \ref{fig:inference_contamination_qq}, shows that there may be a variance mismatch.
+A mismatch in the variance will increase or decrease the sensitivity of the test, a larger variance would make more test statistics more likely to be tested as positive.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.49\textwidth]{../figures/inference/contamination/allNullPlaneqq.eps}
+	\caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ contaminated Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
+	\label{fig:inference_contamination_qq}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlaneunfiltered.eps}
+				\caption{Unfiltered}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanefiltered.eps}
+				\caption{Filtered}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanenullmean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanenullstd.eps}
+				\caption{Empirical null std}
+			\end{subfigure}
+		}
+	\caption{A $\addNumber{../figures/inference/contamination/imageSize.txt} \times \addNumber{../figures/inference/contamination/imageSize.txt}$ contaminated Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/contamination/radius.txt}.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
+Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+Also shown are the empirical null mean and empirical null std.}
+	\label{fig:inference_contamination_images}
+\end{figure}
+
+An experiment was conducted to investigate the sample mean and sample variance of the filtered contaminated image.
+Ideally the sample mean and sample variance should be 0 and 1 respectively.
+Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradius1.txt}$ to $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} times.
+
+The results are shown in Figure \ref{fig:inference_allnullplane}.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanemean.eps}
+		\caption{Post filter sample mean}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanevariance.eps}
+		\caption{Post filter sample variance}
+	\end{subfigure}
+	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
+The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} repeats of the experiment.
+The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
+	\label{fig:inference_allnullplane}
+\end{figure}
+
+\subsection{Contaminated Defect Experiment}
+
 \subsection{All Null Simulation}

### 2018-12-12 reports/thesis/chapters/5_inference.tex
Completed un/contaminated writing

@@
 \subsection{Uncontaminated Experiment}
+
 The empirical null filter was demonstrated on an image where each pixel has i.i.d.~$\normal(0,1)$ test statistics.
@@
 
-An example of a  $\addNumber{../figures/inference/noContamination/imageSize.txt}\times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering, with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt} is shown in Figure \ref{fig:inference_noContamination_images}.
+An example of a  $\addNumber{../figures/inference/noContamination/imageSize.txt}\times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering, with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt}, is shown in Figure \ref{fig:inference_noContamination_images}.
 A quick glance shows little difference, in particular the QQ plot in Figure \ref{fig:inference_noContamination_qq} shows that the post filter test statistics looked reasonably Normal.
-Because the empirical null mean and empirical null standard deviation are non-Normal random variables, the post filtered test statistics will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
-
-\begin{figure}[ht]
+Because the empirical null mean and empirical null standard deviation are random variables with some distribution, the post filtered test statistics will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
+
+\begin{figure}[htp]
 	\centering
@@
 
-\begin{figure}[p]
+\begin{figure}[pht]
 	\centering
@@
 
-\begin{figure}
+\begin{figure}[htp]
 	\centering
@@
 The results are shown in Figure \ref{fig:inference_allnullgaussian}.
-
-\afterpage{\clearpage}
+The post filter sample test statistic means do agree with zero as expected.
+There is some bias with the post filter sample test statistics variances, it was found that this was sensitive to the bandwidth parameters for the kernel density estimate.
+The large sampling error can come from a number of sources.
+The empirical null parameters are random variables, thus correction using these can increase the variance.
+Also pixel to pixel correlation can be introduced as the empirical null parameters are functions of neighbouring pixels, this can contribute to the sample error.
+
+It should be noted that the slight decrease of the post filter test statistic will decrease the sensitivity of the hypothesis test ever so slightly.
+
+%\afterpage{\clearpage}
 \subsection{Contaminated Experiment}
+
 Consider a $\addNumber{../figures/inference/contamination/imageSize.txt}\times \addNumber{../figures/inference/contamination/imageSize.txt}$ Gaussian image with some contamination.
@@
 The QQ plot of the filtered test statistics, as shown in Figure \ref{fig:inference_contamination_qq}, shows that there may be a variance mismatch.
-A mismatch in the variance will increase or decrease the sensitivity of the test, a larger variance would make more test statistics more likely to be tested as positive.
-
-\begin{figure}[ht]
+A mismatch in the variance will increase or decrease the sensitivity of the test, a larger variance would increase the sensitivity.
+
+\begin{figure}[htp]
 	\centering
@@
 The results are shown in Figure \ref{fig:inference_allnullplane}.
-
-\begin{figure}
+The filter correctly centred the test statistics at zero.
+However there was some variance mismatch and this depended on the kernel radius.
+A kernel radius of about 80 scaled the test statistics correctly.
+This suggest there may be an optimal kernel radius for a null distribution.
+In addition, the sensitivity may not be exactly preserved after filtering.
+
+\begin{figure}[htp]
 	\centering

### 2018-12-12 reports/thesis/chapters/5_inference.tex
Started on simulated defect write up
Wrote about contaminated defected experiment
Line defect is 5 pixels thick in PlaneMultLine
Change alt mean to 3
Save figures for scripts in defectsimulation

@@
 
-\subsection{All Null Simulation}
-
-An experiment was conducted to investigate how well the empirical null filter performs with no defects. The dataset \texttt{July 30deg} was used in this experiment.
-
-The images in the dataset were spilt into two halves randomly.
-The mean over the first half of the images was taken and this was used as the ground truth, acting like an \texttt{aRTist} simulation.
-A smooth function was added to the ground truth to contaminate it and cause some systematic error.
-The idea was that the empirical null filter should do inference without being affected too much by the smooth function.
-
-In the second half, all but one of the images were used in the training of the variance-mean model.
-The remaining image, the test image, was then used to compare with the simulated ground truth, producing a $z$ image.
-The $z$ image was then inferred using the empirical null filter and then the BH procedure.
-
-The smooth functions investigated were a plane and a sinusoid.
-The harshness of the smooth functions were controlled using the gradient for the plane, and the amplitude for the sinusoid.
-The smooth functions are for the plane
-\begin{equation}
-	\delta\left[
-		(x-x_0)+(y-y_0)
-	\right]
-\end{equation}
-and the sinusoid
-\begin{equation}
-	A\sin\left[
-		\dfrac{
-			2\pi
-		}
-		{
-			750
-		}
-		\left(
-			(y-y_0)-(x-x_0)
-		\right)
-	\right]
-\end{equation}
-where $\delta$ is the gradient, $A$ is the amplitude and $(x_0,y_0)$ is the centre of the image.
-
-Because no defects were implemented in this experiment, any positive results are false.
-The false positive rates were investigated for different harshness of the smooth functions.
-The experiment was repeated 20 times by randomly reallocating the images used for the ground truth, variance-mean training and testing.
-
-Figures \ref{fig:inference_NoDefect_Plane_sigma} and \ref{fig:inference_NoDefect_Sinusoid_sigma} shows the false positive rate for the plane and sinusoid contamination respectively.
-For sensible varying functions, the empirical null filter did a good job of not being detecting the contamination as significant.
-In extreme cases it can be seen that false positives can happen and in particular when the smooth function is quite harsh and varies a lot spatially.
-This showed that the empirical null filter was not completely perfect and false positives can happen.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane2sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane3sigma.eps}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane4sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane5sigma.eps}
-    \end{subfigure}
-    }
-    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane. Various $z_\alpha$ levels and gradients are shown.}
-    \label{fig:inference_NoDefect_Plane_sigma}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid2sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid3sigma.eps}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid4sigma.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid5sigma.eps}
-    \end{subfigure}
-    }
-    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid. Various $z_\alpha$ levels and gradients are shown.}
-    \label{fig:inference_NoDefect_Sinusoid_sigma}
-\end{figure}
-
-The spatial properties of the false positives did depend on the smooth function.
-Figures \ref{fig:inference_NoDefect_Plane_p_sig} and \ref{fig:inference_NoDefect_Sinusoid_p_sig} shows the location of the positive results for the plane and sinusoid contamination respectively.
-The $p$-values are also shown.
-These false positives are concerning as they are clustered together, giving false indication of a defect.
-
-In practice, the amount of contamination won't be as harsh as the one demonstrated here.
-As long as the smooth function is slowly varying spatially, the empirical null filter will correct the test statistics accordingly.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_pvalues.eps}
-        \caption{$\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_sig.eps}
-        \caption{$z$ image with red significant pixels}
-    \end{subfigure}
-    }
-    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
-    \label{fig:inference_NoDefect_Plane_p_sig}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_pvalues.eps}
-        \caption{$\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_sig.eps}
-        \caption{$z$ image with red significant pixels}
-    \end{subfigure}
-    }
-    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $3\times10^3$.}
-    \label{fig:inference_NoDefect_Sinusoid_p_sig}
-\end{figure}
-
-Figure \ref{fig:inference_NoDefect_nullmean} shows the estimated empirical null mean.
-It is remarkable that the empirical null mean recovers the smooth functions but artefacts from interpolation can be seen for the sinusoid contamination.
-The grid like structure in Figure \ref{fig:inference_NoDefect_Sinusoid_nullmean} shows that the estimated empirical null mean was not very smooth and more points should of been used to reduce the amount of interpolation, increasing the accuracy of the estimation.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_nullmean.eps}
-        \caption{Plane, $\delta = 7.0$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_nullmean.eps}
-        \caption{Sinusoid, $A=10^4$}
-        \label{fig:inference_NoDefect_Sinusoid_nullmean}
-    \end{subfigure}
-    }
-    \caption{Empirical null mean when using the empirical null filter on an $z$ image where the ground truth was contaminated by a smooth function.}
-    \label{fig:inference_NoDefect_nullmean}
-\end{figure}
-
-These examples showed that the empirical null filter corrected the test statistics accordingly.
-However in extreme cases, the empirical null filter can fail and producing clusters of low $p$-values giving an illusion of a defect.
-In practice, extreme cases should not happen.
-Referring back to the real life example in Figure \ref{fig:inference_filter_mean_null}, the empirical null mean only varied around $0\pm3$ which is a small variation compared to Figure \ref{fig:inference_NoDefect_nullmean}.
-
-\subsection{Defected Simulation}
-
-An experiment was conducted to see if the empirical null filter detect defects under contamination.
-Just like the previous experiment, the dataset \texttt{July 30deg} was used.
-The images in the dataset were spilt, the mean of the first half acted as the ground truth, the rest were used to train the variance-mean model, one held out for testing.
-A plane with gradient $\delta=3$ was added to the ground truth to contaminate it.
-The contamination from the plane is quite mild following from the previous experiment.
-
-Furthermore, defects were added to the ground truth by increasing selected pixels' grey values. Shapes such as squares and lines were used to simulate voids and cracks.
-
-The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} were investigated.
-The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds.
-Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity.
-
-The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
-Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed throughly in \cite{cook2007use}.
-The area under the ROC curve was recorded for different intensity values of the defect.
-
-Figures \ref{fig:inference_SimulateRoc_Line_p_sig} and \ref{fig:inference_SimulateRoc_Squares_p_sig} shows the results of using the empirical null filter for inference.
-In this example an array of squares and a single vertical line were used to defect the ground truth by adding 298 to the grey value, a particularly small number.
-The defects were picked up which is remarkable.
-The structure of the false positives is quite similar to Figure \ref{fig:inference_NoDefect_Plane_p_sig}, indicating that the plane was still mildly harsh and responsible for the false positives.
-
-The empirical null filter can fail if it treats a defect as the null.
-This can be mildly seen in Figure \ref{fig:inference_SimulateRoc_Squares_p_sig}, the top rows of square defects were not detected but the area outside the defect were tested as positive.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_pvalues.eps}
-        \caption{$-\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_sig.eps}
-        \caption{Image with significant pixels}
-    \end{subfigure}
-    }
-    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by a single vertical line with value 298.}
-    \label{fig:inference_SimulateRoc_Line_p_sig}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_pvalues.eps}
-        \caption{$-\log p$-values}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_sig.eps}
-        \caption{Image with significant pixels}
-    \end{subfigure}
-    }
-    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by an array of squares with value 298.}
-    \label{fig:inference_SimulateRoc_Squares_p_sig}
-\end{figure}
-
-The ROC curves for different defect intensities are shown in Figures \ref{fig:inference_SimulateRoc_Lines_roc} and \ref{fig:inference_SimulateRoc_Squares_roc}.
-The dotted diagonal line show the ROC curve if the test classify each pixel randomly.
-Perfect classification happens on the top left of the graph when the true positive rate is one and the false positive rate is zero.
-A sample of ROC curves were obtained by reallocating the images to the ground truth, variance-mean training and testing, this was done 5 times.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_1.eps}
-        \caption{Defect intensity = 100}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_7.eps}
-        \caption{Defect intensity = 207}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_14.eps}
-        \caption{Defect intensity = 483}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_20.eps}
-        \caption{Defect intensity = 1000}
-    \end{subfigure}
-    }
-    \caption{ROC curves when using the empirical null filter on a simulated comparison.
-The ground truth was contaminated by a plane and defected by an single vertical line.
-Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
-This was done 5 times.}
-    \label{fig:inference_SimulateRoc_Lines_roc}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_1.eps}
-        \caption{Defect intensity = 100}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_7.eps}
-        \caption{Defect intensity = 207}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_14.eps}
-        \caption{Defect intensity = 483}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_20.eps}
-        \caption{Defect intensity = 1000}
-    \end{subfigure}
-    }
-    \caption{ROC curves when using the empirical null filter on a simulated comparison.
-The ground truth was contaminated by a plane and defected by an array of squares.
-Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing.
-This was done 5 times.}
-    \label{fig:inference_SimulateRoc_Squares_roc}
-\end{figure}
-
-Figure \ref{fig:inference_SimulateRoc_roc_area} shows the area under the ROC curves for the single vertical line and array of squares defect.
-The areas were calculated using the trapezium rule.
-The results are promising with near perfect performance with defect intensities at least 600.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_area.eps}
-        \caption{Line}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_area.eps}
-        \caption{Squares}
-    \end{subfigure}
-    }
-    \caption{The area under the ROC curves for different defects and defect intensities.
-The ground truth was contaminated by a plane and defected.
-The experiment was repeated 5 times by reallocating images to the ground truth, variance-mean training and testing.
-The box plot represent those 5 repeats.}
-    \label{fig:inference_SimulateRoc_roc_area}
-\end{figure}
-
-The experiments shows that the empirical null filter can correct the null distribution locally, giving better inference.
-In extreme cases, for example if the defect intensity is very small or the amount of contamination is rather large, the empirical null filter can fail.
-Harsh contamination can produce false positives because spatially rapidly changing grey values could be detected as a defect.
-The worst case would be that this would make defects appear to be the null, giving completely the opposite inference.
-
-These extreme cases should not happen.
-As seen in the real life example at the start of the section, false positives are rare but they do have some spatial structure.
-If the defect intensity is too small to be detected, the contrast of the x-ray imaging apparatus should be adjusted to cater for it.
-
-\subsection{Real Data}
-
-There are ways to speed up the implementation of the empirical null filter by sacrificing accuracy.
-For example, instead of estimating the empirical null parameters for every pixel, a number of them can be estimated and then the remaining values can be interpolated.
-However it was found that interpolating $\widehat{\sigma}_{0,x,y}$ can yield highly varying results.
-To avoid this problem, it can be assumed that $\sigma_{0,x,y}=\sigma_0$ for all $x$ and $y$.
-Then the estimator $\widehat{\sigma}_0$ is the empirical null standard deviation estimator using all location corrected $z$ test statistics.
-
-The empirical null filter was used on the example at the start of the chapter.
-It was used on a grid of $20\times 20$ points, the remaining values were interpolated.
-It was also assumed the empirical null standard deviation was constant, the methodology discussed in the previous paragraph.
-
-The $z$ and $p$-value image, as shown in Figure \ref{fig:inference_filter_z_p_image}, now look more spatially uniform.
-The defects and some of the edges and corners are highlighted with their small $p$-values.
-In particular, Figure \ref{fig:inference_filter_z_ordered_p} shows that the test statistics look more Normal but with heavier tails.
-The heavier tails are contributed by non-null test statistics.
-Significant pixels are shown in Figure \ref{fig:inference_filter_sig_image}.
-It was encouraging to see less false positives and more defects being picked up.
-Because the BH procedure controls the FDR, some false positives are inevitable.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/filter_z_image.eps}
-        \caption{$z$ image}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/filter_p_image.eps}
-        \caption{$-\log p$-values}
-    \end{subfigure}
-    }
-    \caption{The $z$ image and $p$-value image after using the empirical null filter.}
-    \label{fig:inference_filter_z_p_image}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/filter_histogram.eps}
-        \caption{Histogram of $z$ statistics}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/filter_p.eps}
-        \caption{Ordered $p$ values}
-    \end{subfigure}
-    }
-    \caption{Histogram of $z$ statistics and the corresponding ordered $p$-values when using the empirical null filter.}
-    \label{fig:inference_filter_z_ordered_p}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_sig_image.eps}
-	\caption{Using the empirical null filter, significant pixels were highlighted in red.} 
-	\label{fig:inference_filter_sig_image}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_mean_null.eps}
-	\caption{The estimated empirical null mean} 
-	\label{fig:inference_filter_mean_null}
-\end{figure}
-
-In summary, the empirical null filter irons out each pixel in the $z$ image using the local mode.
-Figure \ref{fig:inference_filter_mean_null} shows the $\widehat{\mu}_{0,x,y}$ image, which varies a lot but smoothly.
-This demonstrated that by correcting the test statistics accordingly, sensible inference was achieved.
-
-In the remaining of the chapter, properties of the empirical null filter were investigated.
+The study will now turn to contaminated defected images.
+Let $Z_{x,y}$ be the test statistics of pixel $(x,y)$ and under the null, it is distributed such that $Z_{x,y}|H_0\sim\normal(0,1)$.
+Defects refer to statistics which do not follow the null distribution, but instead an alternative distribution.
+For example it can be $Z_{x,y}|H_1\sim\normal(\mu_{1,x,y},1)$ and this example was used in this experiment.
+Contamination is a linear transform of the test statistics $Z_{x,y}$ such that
+\begin{equation}
+	C_{x,y} = Z_{x,y}\sigma_{0,x,y} + \mu_{0,x,y} \ .
+\end{equation}
+The empirical null filter recovers $Z_{x,y}$ from $C_{x,y}$. The values of the filtered test statistics are denoted as $\zeta_{x,y}$.
+
+Various simulated defects were investigated. Dust defect with intensity $\pi_1$ assign all test statistics to be distributed such that
+\begin{equation}
+	p_{Z_{x,y}}(z)=(1-\pi_1)p_{Z_{x,y}|H_0}(z) + \pi_1 p_{Z_{x,y}|H_1}(z) \ .
+\end{equation}
+In other words, test statistics has the alternative distribution with probability $\pi_1$, and has the null distribution otherwise.
+This was chosen because the proportion of null statistics captured by a kernel should be independent of the radius of the kernel.
+
+A line defect assign columns of pixels to have the alternative distribution, a kernel would only capture a section of defect.
+Similarly different shapes are used such as a square defect.
+With a square defect, a kernel can capture the entire defect.
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imagePreContaminated.eps}
+				\caption{Uncontaminated}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageContaminated.eps}
+				\caption{Contaminated}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageFiltered.eps}
+				\caption{Filtered}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_nullStd.eps}
+				\caption{Empirical null std}
+			\end{subfigure}
+		}
+	\caption{A $256 \times 256$ dust defect Gaussian image with/without contamination and after filtering with kernel radius 20.
+Defected pixels have the distribution $\normal(3,1)$.
+The dust defect has intensity $\pi_1 = 0.1$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imagePreContaminated.eps}
+				\caption{Uncontaminated}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageContaminated.eps}
+				\caption{Contaminated}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageFiltered.eps}
+				\caption{Filtered}
+			\end{subfigure}
+		}
+	\caption{A $256 \times 256$ line defect Gaussian image with/without contamination and after filtering with kernel radius 20.
+Defected pixels have the distribution $\normal(3,1)$.
+The line is 5 pixels thick.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imagePreContaminated.eps}
+				\caption{Uncontaminated}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageContaminated.eps}
+				\caption{Contaminated}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageFiltered.eps}
+				\caption{Filtered}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_nullMean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+		}
+	\caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 20.
+Defected pixels have the distribution $\normal(3,1)$.
+The square is $30\times 30$ pixels in size.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imagePreContaminated.eps}
+				\caption{Uncontaminated}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageContaminated.eps}
+				\caption{Contaminated}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageFiltered.eps}
+				\caption{Filtered}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullMean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+		}
+	\caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 40.
+Defected pixels have the distribution $\normal(3,1)$.
+The square is $30\times 30$ pixels in size.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_roc.eps}
+				\caption{Dust defect $\pi_1=0.1$, $r=20$}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_roc.eps}
+				\caption{5 pixels thick line defect, $r=20$}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_roc.eps}
+				\caption{$30\times 30$ square defect, $r=20$}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_roc.eps}
+				\caption{$30\times 30$ square defect, $r=40$}
+			\end{subfigure}
+		}
+	\caption{ROC}
+\end{figure}

### 2018-12-12 inference/DefectSimulator/PlaneMultLine.m

@@ -8,6 +8,8 @@ classdef PlaneMultLine < PlaneMult
     %parameters of the alt distribution
     altMean;
     altStd;
+    %how thick the defect line is
+    lineThickness = 5;
   end
   
   methods (Access = public)
@@ -34,8 +36,8 @@ classdef PlaneMultLine < PlaneMult
       %imagePreBias: defected Gaussian image without the smooth function added
     function [image, isAltImage, imagePreBias] = getDefectedImage(this, size)
       [image, isAltImage] = this.getDefectedImage@DefectSimulator(size);
-      [image, isAltImage] = this.addLineDefect(image, isAltImage, round(size(2)/2), 1, ...
-          this.altMean, this.altStd);
+      [image, isAltImage] = this.addLineDefect(image, isAltImage, round(size(2)/2), ...
+          this.lineThickness, this.altMean, this.altStd);
       imagePreBias = image;
       image = this.multiply(image, this.multiplier);
       image = this.addPlane(image, this.grad);

### 2018-12-15 reports/thesis/chapters/5_inference.tex
Wrote up about contaminated defected images

@@
 A kernel radius of about 80 scaled the test statistics correctly.
-This suggest there may be an optimal kernel radius for a null distribution.
-In addition, the sensitivity may not be exactly preserved after filtering.
+This suggest there may be an optimal kernel radius for this particular null distribution.
+Another caveat is that the sensitivity may not be exactly preserved after filtering.
 
@@
 
-Various simulated defects were investigated. Dust defect with intensity $\pi_1$ assign all test statistics to be distributed such that
+Various simulated defects were investigated. Salt defect (named after salt and pepper noise) with density $\pi_1$ assign all test statistics to be distributed such that
 \begin{equation}
@@
 \end{equation}
-In other words, test statistics has the alternative distribution with probability $\pi_1$, and has the null distribution otherwise.
+In other words, test statistics will have the alternative distribution with probability $\pi_1$, and have the null distribution otherwise.
 This was chosen because the proportion of null statistics captured by a kernel should be independent of the radius of the kernel.
@@
 A line defect assign columns of pixels to have the alternative distribution, a kernel would only capture a section of defect.
-Similarly different shapes are used such as a square defect.
+Similarly different shapes were used such as a square defect.
 With a square defect, a kernel can capture the entire defect.
+
+An example of a salt defected image is shown in Figure \ref{fig:inference_saltDefect}, the figure also includes the image contaminated and filtered after contamination.
+The contamination caused some systematic errors, such as increasing the sensitivity such that are there more positive pixels in particular in two of the corners of the image.
+The empirical null filter recovers the defected image from the contaminated image so that appropriate inference can be done.
+However some statistical power is lost in the filtered image.
+This is because in areas of high empirical null std, the sensitivity decreased thus there is less detection power.
+This cannot be avoided as areas of high empirical null std is due to the sampling error.
+Using different kernel radiuses will change the sampling error of the empirical null std but it cannot be eliminated.
+Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_lineDefect}.
+
+The square defected images, including the contaminated ones, are shown in Figures \ref{fig:inference_squareDefect} and \ref{fig:inference_square2Defect}.
+Figure \ref{fig:inference_squareDefect} filtered the contaminated image using a kernel radius of $r=20$, while Figure \ref{fig:inference_square2Defect} used a kernel radius of $r=40$.
+With $r=20$, the kernel is smaller than the square defect, therefore the defect was treated as the null and this shows in the empirical null mean.
+This resulted in difficulty detecting the defect.
+With $r=40$, the kernel is much bigger than the defect and treated the defect as non-null.
+The empirical null filter recovers the gradient in the empirical null which was then used for inference.
 
@@
 Defected pixels have the distribution $\normal(3,1)$.
-The dust defect has intensity $\pi_1 = 0.1$.
+The salt defect has density $\pi_1 = 0.1$.
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
+	\label{fig:inference_saltDefect}
 \end{figure}
@@
 				\caption{Filtered}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_nullStd.eps}
+				\caption{Empirical null std}
 			\end{subfigure}
@@
 Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
+	\label{fig:inference_lineDefect}
 \end{figure}
@@
 Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
+	\label{fig:inference_squareDefect}
 \end{figure}
@@
 Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
-\end{figure}
-
-\begin{figure}[p]
+	\label{fig:inference_square2Defect}
+\end{figure}
+
+The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} are shown in Figure \ref{fig:inference_defectSimulationRoc} for the various defects.
+The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds.
+Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity.
+The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
+Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed thoroughly in \cite{cook2007use}.
+The area under the ROC curve was recorded for different intensity values of the defect.
+
+\begin{figure}[htp]
 	\centering
@@
 				\caption{$30\times 30$ square defect, $r=20$}
+				\label{fig:inference_defectSimulationRoc_square20}
 			\end{subfigure}
@@
 		}
-	\caption{ROC}
-\end{figure}
+	\caption{ROC curves for various defected $256\times 256$ Gaussian images.
+The difference curves show the results for the non-contaminated image, contaminated image, and filtered contaminated image.
+Defected pixels have the distribution $\normal(3,1)$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
+	\label{fig:inference_defectSimulationRoc}
+\end{figure}
+
+In terms of the area under the ROC curves, the empirical null filter improves the performance over using the unfiltered contaminated image.
+Not as good as the uncontaminated image but it is an improvement.
+For kernel radiuses too small, such as Figure \ref{fig:inference_defectSimulationRoc_square20}, the empirical null filter deteriorates the performance dramatically and it would be better off using the contaminated image.

### 2018-12-15 inference/defectsimulation/defectLine.m

@@ -26,4 +26,5 @@ altStd = 1;
 
 defectSimulator = PlaneMultLine(randStream, trueNullMeanGrad, trueNullStd, altMean, altStd);
 defectExample = DefectExample();
+defectExample.setPlotDefectNullStd(true);
 defectExample.plotExample(defectSimulator, imageSize, radius, directory, prefix);

### 2018-12-19 reports/thesis/chapters/5_inference.tex
Completed defectsimulation section
Wrote contaminated defected experiment section
PlaneMultLine makes line thickness a parameter
Corrected plotting in Experiment_DefectSimulationDust

@@
 In terms of the area under the ROC curves, the empirical null filter improves the performance over using the unfiltered contaminated image.
-Not as good as the uncontaminated image but it is an improvement.
+The performance before contamination cannot be recovered but it is an improvement.
 For kernel radiuses too small, such as Figure \ref{fig:inference_defectSimulationRoc_square20}, the empirical null filter deteriorates the performance dramatically and it would be better off using the contaminated image.
+
+The ROC is useful because it considers all thresholds or sensitivities used in the hypothesis testing.
+However in the previous experiment, it was found there was some variance mismatch before and after filtering with regards to the test statistics.
+As a result, for a given threshold, such as controlling the FDR, the sensitivity may change ever so slightly after filtering.
+
+An experiment was conducted to investigate the sensitivity before and after filtering.
+A $256\times 256$ Gaussian image with dust defect of density $\pi_1=0.1$ was investigated.
+A kernel radius of $r=20$ was used.
+The type 1 error, type 2 error and the FDR were investigated before contamination, after contamination and after filtering for various alternative distribution.
+The alternative distribution used is $Z_{x,y}|H_1\sim\normal(\mu_1,1)$ where $\mu_1$ is the alternative mean and was varied for this experiment.
+
+\begin{figure}[htp]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_roc.eps}
+				\caption{ROC area}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_type1.eps}
+				\caption{Type 1 error}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_type2.eps}
+				\caption{Type 2 error}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_fdr.eps}
+				\caption{FDR}
+				\label{fig:inference_DefectSimulationDust_fdr}
+			\end{subfigure}
+		}
+	\caption{ROC area and various errors obtained when conducting hypothesis test on the uncontaminated image, contaminated image and the filtered contaminated image of a $256 \times 256$ salt defect, Gaussian image.
+The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_radius.txt}.
+Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
+The salt defect has density $\pi_1 = 0.1$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The FDR was controlled at the $2\sigma$ level.
+The box plot summarise the \addNumber{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_nRepeat.txt} repeats of the experiment.
+Some contamination plots may have been omitted due to being off the scale.}
+	\label{fig:inference_DefectSimulationDust}
+\end{figure}
+
+The results are shown in Figure \ref{fig:inference_DefectSimulationDust}.
+The ROC areas were quantified here and shows that, in terms of the ROC area, using the filter improved the performance of the test from the contamination.
+Figure \ref{fig:inference_DefectSimulationDust_fdr} illustrate that in the uncontaminated image, the FDR is controlled below 5\%.
+However after contamination and then filtering, the FDR was not well controlled at this threshold.
+Ideally the error rates before contamination and after filtering should be similar so that sensitivity is preserved after filtering.
+This should highlight that while performance can be recovered from contamination in terms of the ROC area, the FDR threshold may not be preserved.
+
+There is also the question of what kernel size to choose for a given defect.
+Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $\pi_1=0.1$ to satisfy some assumptions made for the empirical null.
+Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of kernel which is a defect to 10\%.
+In other words for a kernel with radius $r$
+\begin{equation}
+0.1 > \dfrac{\text{maximum area of defect captured by the kernel}}{\text{area of kernel}} \ .
+\end{equation}
+For a $d \times d$ square defect this is
+\begin{equation}
+r > d \sqrt{\dfrac{10}{\pi}} \ .
+\end{equation}
+In the example of $d=30$, this is about $r>54$. For the line defect with thickness $d$, it can be involved because the maximum area of the line defect captured by the kernel is
+\begin{equation}
+2r^2
+\left[
+	\dfrac{d}{2r}\sqrt{1-\left(\dfrac{d}{2r}\right)^2}
+	+\text{arcsin}\left(\dfrac{d}{2r}\right)
+\right] \ .
+\end{equation}
+For $d=5$, the radius is about $r>32$.
+These are rules of thumb because the kernel won't be perfectly circular when used on a grid of pixels.
+It should be pointed out that the implementation can accept non-integer radiuses if desired.
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_roc.eps}
+				\caption{ROC area}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_type1.eps}
+				\caption{Type 1 error}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_type2.eps}
+				\caption{Type 2 error}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_fdr.eps}
+				\caption{FDR}
+			\end{subfigure}
+		}
+	\caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses.
+The dotted lines show the 95\% percentile when the hypothesis test was done on the uncontaminated image.
+Defected pixels have the distribution $\normal(\addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_altMean.txt},1)$.
+The line defect is 5 pixels thick.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The FDR was controlled at the $2\sigma$ level.
+The box plot summarise the \addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_nRepeat.txt} repeats of the experiment.}
+	\label{fig:inference_Experiment_DefectRadiusLine}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_roc.eps}
+				\caption{ROC area}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_type1.eps}
+				\caption{Type 1 error}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_type2.eps}
+				\caption{Type 2 error}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_fdr.eps}
+				\caption{FDR}
+			\end{subfigure}
+		}
+	\caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
+The dotted lines show the 95\% percentile when the hypothesis test was done on the uncontaminated image.
+Defected pixels have the distribution $\normal(\addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_altMean.txt},1)$.
+The square defect is $30\times 30$ pixels in size.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The FDR was controlled at the $2\sigma$ level.
+The box plot summarise the \addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_nRepeat.txt} repeats of the experiment.}
+	\label{fig:inference_Experiment_DefectRadiusSquare}
+\end{figure}
+
+An experiment was conducted where the contaminated defected image were filtered for various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
+Hypothesis testing was done on the uncontaminated and filtered contaminated image.
+The area under the ROC curve and various errors were recorded.
+Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.
+
+The results show that the ROC area increased with kernel radius.
+This does highlight that a kernel with a good radius can performance almost as though there was no contamination.
+For large kernel radius, the FDR becomes similar to the FDR obtained from the uncontaminated image.
+Thus it appears a large kernel radius helped preserve FDR control after filtering in these examples.
+However a large kernel radius does come at a computational cost.
+Choosing a kernel radius is a matter of trading computational cost with precise FDR control.

### 2018-12-19 inference/defectsimulation/Experiment_DefectRadiusLine.m

@@ -1,5 +1,9 @@
 classdef Experiment_DefectRadiusLine < Experiment_DefectRadius
   
+  properties (SetAccess = private)
+    lineThickness = 5;
+  end
+  
   methods (Access = public)
     
     function this = Experiment_DefectRadiusLine()
@@ -16,7 +20,7 @@ classdef Experiment_DefectRadiusLine < Experiment_DefectRadius
     
     function defectSimulator = getDefectSimulator(this)
       defectSimulator = PlaneMultLine(this.randStream, this.gradContamination, ...
-          this.multContamination, this.altMean, this.altStd);
+          this.multContamination, this.altMean, this.altStd, this.lineThickness);
     end
     
   end

### 2018-12-19 inference/defectsimulation/Experiment_DefectSimulationDust.m

@@ -20,8 +20,9 @@ classdef Experiment_DefectSimulationDust < Experiment
     radius = 20; %radius of the empirical null filter kernel
     randStream = RandStream('mt19937ar','Seed',uint32(153380491)); %rng
     nIntial = 3; %number of initial points used for the empirical null filter
+    nRoc = 1000; %number of points used for the roc curve
     
-    altMeanArray = 1:5; %array of alt distribution means to investigate
+    altMeanArray = linspace(1,5,9); %array of alt distribution means to investigate
     altStd = 1; %std of the alt distribution
     gradContamination = [0.01, 0.01]; %gradient of the contamination
     multContamination = 2; %multiplier of the contamination
@@ -30,7 +31,7 @@ classdef Experiment_DefectSimulationDust < Experiment
     %records results
       %dim 1: for each repeat
       %dim 2: for each alt mean
-      %dim 3: size 2, pre/post contamination
+      %dim 3: size 2, pre-contamination, contaminated, filtered contaminated
     type1ErrorArray;
     type2ErrorArray;
     fdrArray;
@@ -47,14 +48,26 @@ classdef Experiment_DefectSimulationDust < Experiment
     
     %METHOD: PRINT RESULTS
     %Plots type 1, type 2, area of ROC vs alternative mean
-    %Plots pre/post contamination results on the same graph
+    %Plots pre/post contamination and filtered results on the same graph
     function printResults(this)
       
+      directory = fullfile('reports','figures','inference','defectsimulation');
+      
+      %print radius
+      fildId = fopen(fullfile(directory,strcat(this.experiment_name,'_radius.txt')),'w');
+      fprintf(fildId,'%d',this.radius);
+      fclose(fildId);
+      
+      %print nRepeat
+      fildId = fopen(fullfile(directory,strcat(this.experiment_name,'_nRepeat.txt')),'w');
+      fprintf(fildId,'%d',this.nRepeat);
+      fclose(fildId);
+      
       %Plots pre/post contamination results on the same graph, so offset them
-      offset = 0.05;
+      offset = 0.06;
       
       %plot roc area vs alt mean
-      figure;
+      fig = LatexFigure.sub();
       ax = gca;
[…]

### 2018-12-19 inference/defectsimulation/defectLine.m

@@ -20,11 +20,13 @@ imageSize = 256;
 radius = 20; %kernel radius
 trueNullStd = 2; %multiplier in the contimation
 trueNullMeanGrad = [0.01, 0.01]; %gradient of contimation
+lineThickness = 5;
 %distribution parameters of the alt distribution
 altMean = 3;
 altStd = 1;
 
-defectSimulator = PlaneMultLine(randStream, trueNullMeanGrad, trueNullStd, altMean, altStd);
+defectSimulator = PlaneMultLine(randStream, trueNullMeanGrad, trueNullStd, altMean, altStd, ...
+    lineThickness);
 defectExample = DefectExample();
 defectExample.setPlotDefectNullStd(true);
 defectExample.plotExample(defectSimulator, imageSize, radius, directory, prefix);

### 2018-12-21 reports/thesis/chapters/5_inference.tex
Added real data in inference chapter

@@
 Choosing a kernel radius is a matter of trading computational cost with precise FDR control.
+
+\subsection{Real Data}
+
+\begin{figure}[htp]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_z.eps}
+				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_z.eps}
+				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2.txt}$}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_z.eps}
+				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3.txt}$}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_z.eps}
+				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4.txt}$}
+			\end{subfigure}
+		}
+	\caption{Filtered $z$ image from the \texttt{Sep16 120deg} dataset. Various kernel radiuses were used.}
+	\label{fig:inference_sep16120deg_zfiltered}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_sig.eps}
+				\caption{Image with sig.~pixels}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_logp.eps}
+				\caption{$-\log p$}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_nullMean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_nullStd.eps}
+				\caption{Empirical null std}
+			\end{subfigure}
+		}
+	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$.
+a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and std.}
+	\label{fig:inference_sep16120deg_inference_radius1}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_sig.eps}
+				\caption{Image with sig.~pixels}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_logp.eps}
+				\caption{$-\log p$}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_nullMean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_nullStd.eps}
+				\caption{Empirical null std}
+			\end{subfigure}
+		}
+	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2.txt}$.
+a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and std.}
+	\label{fig:inference_sep16120deg_inference_radius2}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_sig.eps}
+				\caption{Image with sig.~pixels}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_logp.eps}
+				\caption{$-\log p$}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_nullMean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_nullStd.eps}
+				\caption{Empirical null std}
+			\end{subfigure}
+		}
+	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3.txt}$.
+a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and std.}
+	\label{fig:inference_sep16120deg_inference_radius3}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_sig.eps}
+				\caption{Image with sig.~pixels}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_logp.eps}
+				\caption{$-\log p$}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_nullMean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_nullStd.eps}
+				\caption{Empirical null std}
+			\end{subfigure}
+		}
+	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4.txt}$.
+a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and std.}
+	\label{fig:inference_sep16120deg_inference_radius4}
+\end{figure}
+
+The empirical null filter was applied to the \texttt{Sep16 120deg} image as shown at the start of the chapter.
+Figure \ref{fig:inference_sep16120deg_zfiltered} shows the filtered $z$ images for various kernel radiuses.
+For $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image is smooth and treated everything as the null.
+When a large enough radius was used, the defects are highlighted by the higher $z$ statistics and everything else remain unchanged.
+Figures \ref{fig:inference_sep16120deg_inference_radius1} to \ref{fig:inference_sep16120deg_inference_radius4} shows the resulting inference along with the empirical null parameters.
+The figures shows that for large enough kernel radius, the filter irons out the false positives observed at the start of this chapter.
+All of the defects were successfully highlighted by the hypothesis test.
+
+False positives were detected on the bottom right of the 3D printed sample.
+This is the result of the null distribution being bimodal where each face has a different distribution.
+Figure \ref{fig:inference_cornerSelect} illustrates this.
+The geometry of the faces and the kernel is such it results in one of the faces to be treated as non-null and then tested positive, falsely so.
+
+\begin{figure}[htp]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/cornerSelect.png}
+				\caption{$z$ image with kernel of radius $r=120$}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/cornerSelectHisto.png}
+				\caption{Histogram of $z$ in the kernel}
+			\end{subfigure}
+		}
+	\caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the $z$ statistics captured by the kernel shows a bimodal distribution.}
+	\label{fig:inference_cornerSelect}
+\end{figure}
+
+The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}.
+It was segmented using the edges of the projection of the 3D printed object.
+The empirical null filter was then used on each segment independently, ignoring pixels outside the segment the filter is working on.
+The resulting filtered segments were stitched together to form the resulting filtered image.
+By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.
+It can be seen that the empirical null mean does change face to face, resulting in a clear boundary set by the edges.
+Most of false positives around the corners and edges have been eliminated.
+
+\begin{figure}[htp]
+	\centering
+	\includegraphics[width=0.49\textwidth]{../figures/inference/defectdetect/segment.JPG}
+	\caption{The $z$ was segmented further into 7 segments.}
+	\label{fig:inference_segmentFurther}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_sig.eps}
+				\caption{Image with sig.~pixels}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_logp.eps}
+				\caption{$-\log p$}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_nullMean.eps}
+				\caption{Empirical null mean}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_nullStd.eps}
+				\caption{Empirical null std}
+			\end{subfigure}
+		}
+	\caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4.txt}$.
+a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+The $z$ statistics from all segments were combined in the BH procedure.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and std.}
+	\label{fig:inference_subroisep16120deg_inference_radius4}
+\end{figure}

### 2018-12-21 inference/defectDetect/ExperimentSubRoiDefectDetect.m

@@ -14,9 +14,11 @@ classdef (Abstract) ExperimentSubRoiDefectDetect < ExperimentDefectDetect
     
     %OVERRIDE: PRINT RESULTS
     %Include the significant pixels when doing hypothesis testing on each segment separately
-    function printResults(this)
+    %PARAMETERS:
+      %nullStdCLim: cLim for the null std plot, empty to use default min and max null std for cLim
+    function printResults(this, cLim)
       
-      this.printResults@ExperimentDefectDetect();
+      this.printResults@ExperimentDefectDetect(cLim);
       
       %for each radius
       for iRadius = 1:numel(this.radiusArray)
@@ -37,11 +39,13 @@ classdef (Abstract) ExperimentSubRoiDefectDetect < ExperimentDefectDetect
         end
         
         %plot the test image with the significant pixels from each segment
-        figure;
+        fig = LatexFigure.sub();
         sigPlot = ImagescSignificant(this.scan.loadImageStack(this.testIndex));
         sigPlot.addSigPixels(sigImage);
         sigPlot.setDilateSize(2);
         sigPlot.plot();
+        saveas(fig,fullfile(directory, strcat(this.experiment_name,'_radius',num2str(iRadius), ...
+            '_sigSeparate.eps')),'epsc');
         
       end
 

### 2019-02-05 reports/thesis/chapters/5_inference.tex
Figure export for NullIid, deleted Mixture2

@@
 \end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullMean.eps}
+				\caption{Empirical null}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullMean.eps}
+				\caption{MAD mode null}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullMean.eps}
+				\caption{Mean variance null}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullMean.eps}
+				\caption{Median IQR null}
+			\end{subfigure}
+		}
+	\caption{Different types of central tendency estimators were used on $\pi r^2$ $\normal(0,1)$ random variables.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample mean.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullStd.eps}
+				\caption{Empirical null}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullStd.eps}
+				\caption{MAD mode null}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullStd.eps}
+				\caption{Mean variance null}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullStd.eps}
+				\caption{Median IQR null}
+			\end{subfigure}
+		}
+	\caption{Different types of statistical dispersion estimators were used on $\pi r^2$ $\normal(0,1)$ random variables.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample variance.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zMean.eps}
+				\caption{Empirical null}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zMean.eps}
+				\caption{MAD mode null}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zMean.eps}
+				\caption{Mean variance null}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zMean.eps}
+				\caption{Median IQR null}
+			\end{subfigure}
+		}
+	\caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators.
+Shown are the mean of the normalised random variables.
+The dotted lines show the 95\% confidence interval for the sample mean.
+The box plots represent 100 repeats of the simulation.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zStd.eps}
+				\caption{Empirical null}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zStd.eps}
+				\caption{MAD mode null}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zStd.eps}
+				\caption{Mean variance null}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zStd.eps}
+				\caption{Median IQR null}
+			\end{subfigure}
+		}
+	\caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators.
+Shown are the standard deviation of the normalised random variables.
+The dotted lines show the 95\% confidence interval for the sample variance.
+The box plots represent 100 repeats of the simulation.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zKurtosis.eps}
+				\caption{Empirical null}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zKurtosis.eps}
+				\caption{MAD mode null}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zKurtosis.eps}
+				\caption{Mean variance null}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zKurtosis.eps}
+				\caption{Median IQR null}
+			\end{subfigure}
+		}
+	\caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators.
+Shown are the sample kurtosis of the normalised random variables.
+The dotted lines show the 95\% confidence interval for the sample kurtosis.
+The box plots represent 100 repeats of the simulation.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullMean.eps}
+				\caption{Empirical null}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullMean.eps}
+				\caption{MAD mode null}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullMean.eps}
+				\caption{Mean variance null}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullMean.eps}
+				\caption{Median IQR null}
+			\end{subfigure}
+		}
+	\caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables.
+The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample mean.}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\centerline{
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullStd.eps}
+				\caption{Empirical null}
+			\end{subfigure}
+			\begin{subfigure}[b]{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullStd.eps}
+				\caption{MAD mode null}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullStd.eps}
+				\caption{Mean variance null}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullStd.eps}
+				\caption{Median IQR null}
+			\end{subfigure}
+		}
+	\caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables.
+The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample variance.}
+\end{figure}

### 2019-02-05 inference/NullIid/NullIidMixture2.m

@@ -1,19 +1,0 @@
-classdef (Abstract) NullIidMixture2 < NullIid
-  
-  methods (Access = protected)
-    
-    function setup(this, seed)
-      this.setup@NullIid(seed);
-    end
-    
-    function z = getSample(this, n)
-      isNull = this.randStream.rand(n,1) < 0.9;
-      z = zeros(n,1);
-      z(isNull) = this.randStream.randn(sum(isNull),1);
-      z(~isNull) = this.randStream.randn(sum(~isNull),1) + (this.randStream.randi([0,1])*2-1)*3;
-    end
-    
-  end
-  
-end
-

### 2019-02-05 inference/NullIid/NullIidMixture2MadMode.m

@@ -1,20 +1,0 @@
-classdef NullIidMixture2MadMode < NullIidMixture2
-
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@NullIidMixture2(uint32(2373797645));
-    end
-    
-    function [nullMean, nullStd] = getNull(this, z)
-      empiricalNull = MadModeNull(z, 0, ...
-          this.randStream.randi([intmin('int32'),intmax('int32')],'int32'));
-      empiricalNull.estimateNull();
-      nullMean = empiricalNull.getNullMean();
-      nullStd = empiricalNull.getNullStd();
-    end
-    
-  end
-  
-end
-

### 2019-02-06 reports/thesis/chapters/5_inference.tex
Renamed allnull experiment

@@
 
-In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$ was simulated.
+In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$ was simulated.
 The sample mean and sample variance of the post filtered test statistics were recorded.
-This was repeated \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} times by simulating another Gaussian image.
-Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradius1.txt}$ to $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradiusend.txt}$ were investigated.
+This was repeated \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} times by simulating another Gaussian image.
+Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radius1.txt}$ to $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radiusend.txt}$ were investigated.
 
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianmean.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_mean.eps}
 		\caption{Post filter sample mean}
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianvariance.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_variance.eps}
 		\caption{Post filter sample variance}
 	\end{subfigure}
-	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} repeats of the experiment.
+	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$.
+The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} repeats of the experiment.
 The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
@@
 Ideally the sample mean and sample variance should be 0 and 1 respectively.
-Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradius1.txt}$ to $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} times.
+Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/AllNullPlane_radius1.txt}$ to $r=\addNumber{../figures/inference/allnull/AllNullPlane_radiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} times.
 
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanemean.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_mean.eps}
 		\caption{Post filter sample mean}
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanevariance.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_variance.eps}
 		\caption{Post filter sample variance}
 	\end{subfigure}
-	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$.
+	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$.
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} repeats of the experiment.
+The box plots summarise the \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} repeats of the experiment.
 The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}

### 2019-02-06 inference/allnull/allNullPlane.m

@@ -37,7 +37,7 @@ fclose(file_id);
 %contaminate the image
 defectSimulator = PlaneMult(randStream, trueNullMeanGrad, trueNullStd);
 image = defectSimulator.getDefectedImage([imageSize, imageSize]);
-filter = EmpiricalNullFilter(radius); %filter it
+filter = MadModeNullFilter(radius); %filter it
 filter.setNInitial(3);
 filter.filter(image);
 

### 2019-03-07 reports/thesis/chapters/5_inference.tex
Modified inference chapter, added figures

@@
 
-\section{Hypothesis Testing}
+\section{Literature Review}
 
@@
 The power of the test is defined as the probability of a true positive result. For unknown $\mu$, it is useful to investigate the power for a range of $\mu$.
-
-\section{Multiple Hypothesis Testing}
 
@@
 
-\subsection{Examples}
-
-A few numerical examples is shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing.
-Two scenarios is shown here.
-In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics were null.
-In the second case, 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ independent test statistics were simulated.
-
-A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}.
-The critical boundaries are also shown.
-In the uncorrected case, the critical region is $\|Z\|>2$.
-Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08...$.
-By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so.
-The Bonferroni correction performs well because it tested all the test statistics as negative correctly.
-
-The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}.
-The $p$-values form a straight line as a result of being uniformly distributed.
-The critical line is $0.0455...\times\text{order}/1\,000$ using the BH procedure.
-In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure.
-As a result, the Bonferroni and BH procedure tested all test statistics to be negative correctly.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.8\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullhisto.eps}
-    	\caption{Histogram}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.8\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
-    	\caption{Ordered $p$-values}
-    \end{subfigure}
-    \caption{1\,000 null test statistics were simulated.
-a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.
-b) Any values below the critical line are declared significant using the BH procedure.}
-    \label{fig:inference_multi_test_nullhisto_pvalues}
-\end{figure}
-
-In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated.
-The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}.
-The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario.
-However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}...$.
-
-The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}.
-There are $p$-values below the critical line according to the BH procedure.
-$p$-values below where the curves intersect are considered significant, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive.
-The uncorrected test tested $\input{../tables/multi_test_alt_n_positive_uncorrected.txt}$ test statistics as positive.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.8\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_althisto.eps}
-    	\caption{Histogram}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.8\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_altpvalues.eps}
-    	\caption{Ordered $p$-values}
-    \end{subfigure}
-    \caption{800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics were simulated.
-a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.
-b) Any values below the critical line are declared significant using the BH procedure.}
-    \label{fig:inference_multi_test_althisto_pvalues}
-\end{figure}
-
-This example shows a number of things.
-The BH procedure adapts to the data to control for the FDR.
-The uncorrected method did produce more positive results but at a cost of more false positives.
-It may seem unimpressive that the BH procedure only tested $\input{../tables/multi_test_alt_n_positive_bh.txt}$ positive results, but this is to control the FDR or the number of false positives out of all positive results.
-
-Unfortunately not all 200 non-null test statistics were tested as positive, statisticians would describe it as not powerful.
-This is however unavoidable as a number of null and non-null test statistics will be similar in value.
-The aim of hypothesis testing is not to classify positive and negative results correctly, but rather highlight a number of test statistics which are worth investigation.
-
-The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null.
-Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ number of test statistics were observed to be tested positive.
-From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed.
-In other words, they are realisations of the random variables defined in Table \ref{table:inference_randomvariables}.
-The error rates can be estimated
-\begin{equation}
-	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
-\end{equation}
-\begin{equation}
-	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
-\end{equation}
-\begin{equation}
-	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
-	\ .
-\end{equation}
-The estimates of PCER and FDR is essentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the standard error was chosen to be
-\begin{equation}
-	\text{standard error of }\widehat{\text{FWER}} = 
-	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
-\end{equation}
-where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$.
-Without going into too much detail, this comes from setting a prior $\text{FWER}\sim\betaDist(0,0)$ and assuming that $\mathbb{I}(V\neq0)\sim\bernoulli(\text{FWER})$.
-The posterior distribution is $\text{FWER}|V_1,V_2,\dotdotdot V_N\sim\betaDist(a,b)$ and the variance was used for the standard error.
-
-\begin{table}
-    \centering
-    \begin{subtable}{\textwidth}
-    	\centering
-    	\input{../tables/inference_error_rate1.txt}
-    	\caption{1\,000 $\normal(0,1)$}
-    \end{subtable}
-    \begin{subtable}{\textwidth}
-    	\centering
-    	\input{../tables/inference_error_rate2.txt}
-    	\caption{800 $\normal(0,1)$ and 200 $\normal(2,1)$}
-    \end{subtable}
-    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level.
-1\,000 test statistics were simulated, in a) all test statistics are null and b) some are non-null.
-Error bars represent the standard errors after 1\,000 repeats of the experiment.}
-    \label{table:inference_error_rate}
-\end{table}
-
-Error rates estimations for the two scenarios are shown in Table \ref{table:inference_error_rate} for $N=1\,000$.
-These estimations show that the 3 different types of multiple hypothesis controls for different error rates.
-The uncorrected, Bonferroni and BH controls the PCER, FWER and FDR to be equal or below $\alpha\approx 0.455$ respectively, equality is met when all the test statistics are all truly null.
-
-\section{Empirical Null}
-
 By treating each pixel as a hypothesis test, methods for multiple hypothesis can be deployed.
@@
 
-\subsection{More on the Empirical Null}
+\section{Empirical Null}
 
@@
 	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull1.eps}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
         \caption{$\mu_0$}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
         \caption{$\sigma_0$}
     \end{subfigure}
-    }
     \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
@@
 	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull3.eps}
-        \caption{3D plot}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull4.png}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error3.eps}
         \caption{Heatmap}
     \end{subfigure}
-    }
     \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of $n$ simulated $\normal(0,1)$ data.
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot1.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot5.eps}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot9.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot12.eps}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot16.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot20.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot1.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot51.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot100.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot150.eps}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot199.eps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot249.eps}
     \end{subfigure}
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/inference/ZNull_mserule_of_thumb.eps}
+	\includegraphics[width=0.7\textwidth]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
 	\caption{An identity link Gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$.
@@
 	\centering
-	\input{../tables/ZNull_mse_glm_estimate.txt}
+	\input{../figures/inference/BandwidthSelection2_bandwidthEstimate.txt}
 	\caption{Estimated and standard error gradient and intercept from the linear relationship in Figure \ref{fig:inference_ZNull_mserule_of_thumb}.}
@@
 
-Those familiar with local quadratic regressions would know that a kernel and a smoothness parameter need to be specified \citep{friedman2001elements}.
-In these plots a Gaussian kernel was used with smoothness parameter $\input{../tables/ZNull_bandwidth.txt}$.
-The smoothness parameter $\input{../tables/ZNull_bandwidth.txt}$ was chosen from a quick inspection of the curves.
-The units of the smoothness parameter is not too important here.
-But one should note that the smoothness parameter would affect the solution to the optimal bandwidth.
-
-To take into the sensitivity to the smoothness parameter, the whole analysis was repeated using various smoothness parameters.
-The gradient and intercept for various smoothness parameters are shown in Figure \ref{fig:inference_ZNull_msesensitive}.
-It can seen that the intercept is fairly stable, including the gradient at smoothness parameter around $\input{../tables/ZNull_bandwidth.txt}$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/inference/ZNull_msesensitive.eps}
-	\caption{Finding the relationship between the optimal bandwidth and $n^{-1/5}$ was repeated for various smoothness parameters in the local quadratic regression.
-Error bars represent the standard error.}
-	\label{fig:inference_ZNull_msesensitive}
-\end{figure}
-
 In conclusion, a small bias added to the rule of thumb improved the performance of the estimator $\widehat{\sigma}_0$.
@@
 
-\subsection{Further Discussion}
+\section{Empirical Null Filter}
 
@@
 Secondly it is not clear how to combine the results from each section \citep{efron2008simultaneous}.
-
-\section{Empirical Null Filter}
 
@@
 
-In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$ was simulated.
+In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$ was simulated.
 The sample mean and sample variance of the post filtered test statistics were recorded.
-This was repeated \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} times by simulating another Gaussian image.
-Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radius1.txt}$ to $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radiusend.txt}$ were investigated.
+This was repeated \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} times by simulating another Gaussian image.
+Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_radius1.txt}$ to $r = \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_radiusend.txt}$ were investigated.
 
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_mean.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_mean.eps}
 		\caption{Post filter sample mean}
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_variance.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_variance.eps}
 		\caption{Post filter sample variance}
 	\end{subfigure}
-	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} repeats of the experiment.
+	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
+The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
 The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
@@
 Ideally the sample mean and sample variance should be 0 and 1 respectively.
-Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/AllNullPlane_radius1.txt}$ to $r=\addNumber{../figures/inference/allnull/AllNullPlane_radiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} times.
+Different radiuses were investigated from ???
+to ???
+and repeated ???
+times.
 
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_mean.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
 		\caption{Post filter sample mean}
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_variance.eps}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
 		\caption{Post filter sample variance}
 	\end{subfigure}
-	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$.
+	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} repeats of the experiment.
+The box plots summarise the \addNumber{../figures/inference/allnull/AllNullPlaneEmpirical_nrepeat.txt} repeats of the experiment.
 The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
@@
 			\begin{subfigure}{0.49\textwidth}
-				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullMean.eps}
-				\caption{Empirical null mean}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullStd.eps}
+				\caption{Empirical null std}
 			\end{subfigure}
@@
 			\begin{subfigure}{0.49\textwidth}
-				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_roc.eps}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_roc.eps}
 				\caption{ROC area}
@@
 			\begin{subfigure}{0.49\textwidth}
-				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_type1.eps}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type1.eps}
 				\caption{Type 1 error}
@@
 			\begin{subfigure}{0.49\textwidth}
-				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_type2.eps}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type2.eps}
 				\caption{Type 2 error}
@@
 			\begin{subfigure}{0.49\textwidth}
-				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_fdr.eps}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_fdr.eps}
+				\caption{FDR}
+			\end{subfigure}
+		}
+	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered image of a $256 \times 256$ salt defected Gaussian image.
+a) shows the ROC area when testing the image before and after filtering.
+In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering.
+The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}.
+Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
+The salt defect has density $\pi_1 = 0.1$.
+The FDR was controlled at the 5\% level.
+The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_roc.eps}
+				\caption{ROC area}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type1.eps}
+				\caption{Type 1 error}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type2.eps}
+				\caption{Type 2 error}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_fdr.eps}
+				\caption{FDR}
+			\end{subfigure}
+		}
+	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered image of a $256 \times 256$ salt defected Gaussian image.
+a) shows the ROC area when testing the image before and after filtering.
+In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering.
+The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}.
+Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
+The salt defect has density $\pi_1 = 0.1$.
+The FDR was controlled at the 5\% level.
+The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_roc.eps}
+				\caption{ROC area}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_type1.eps}
+				\caption{Type 1 error}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_type2.eps}
+				\caption{Type 2 error}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_fdr.eps}
 				\caption{FDR}
@@
 		}
-	\caption{ROC area and various errors obtained when conducting hypothesis test on the uncontaminated image, contaminated image and the filtered contaminated image of a $256 \times 256$ salt defect, Gaussian image.
-The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_radius.txt}.
+	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
+a) shows the ROC area when testing the image before/after contamination and after filtering.
+In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
+The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}.
 Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
@@
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The FDR was controlled at the $2\sigma$ level.
-The box plot summarise the \addNumber{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_nRepeat.txt} repeats of the experiment.
-Some contamination plots may have been omitted due to being off the scale.}
+The FDR was controlled at the 5\% level.
+The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
 	\label{fig:inference_DefectSimulationDust}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_roc.eps}
+				\caption{ROC area}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_type1.eps}
+				\caption{Type 1 error}
+			\end{subfigure}
+		}
+		\centerline{
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_type2.eps}
+				\caption{Type 2 error}
+			\end{subfigure}
+			\begin{subfigure}{0.49\textwidth}
+				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_fdr.eps}
+				\caption{FDR}
+				\label{fig:inference_DefectSimulationDust_fdr}
+			\end{subfigure}
+		}
+	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
+a) shows the ROC area when testing the image before/after contamination and after filtering.
+In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
+The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}.
+Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
+The salt defect has density $\pi_1 = 0.1$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The FDR was controlled at the 5\% level.
+The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
 \end{figure}
@@
 
-\subsection{Real Data}
+\section{Results}
 
@@
 \end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_mean.eps}
+		\caption{Empirical Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_mean.eps}
+		\caption{MAD Mode Null}
+	\end{subfigure}
+	}
+	\centerline{
+		\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_mean.eps}
+		\caption{Median IQR Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_mean.eps}
+		\caption{Mean Var Null}
+	\end{subfigure}
+	}
+	\caption{The sample mean of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
+The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
+The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_variance.eps}
+		\caption{Empirical Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_variance.eps}
+		\caption{MAD Mode Null}
+	\end{subfigure}
+	}
+	\centerline{
+		\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_variance.eps}
+		\caption{Median IQR Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_variance.eps}
+		\caption{Mean Var Null}
+	\end{subfigure}
+	}
+	\caption{The sample std of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
+The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
+The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_kurtosis.eps}
+		\caption{Empirical Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_kurtosis.eps}
+		\caption{MAD Mode Null}
+	\end{subfigure}
+	}
+	\centerline{
+		\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_kurtosis.eps}
+		\caption{Median IQR Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_kurtosis.eps}
+		\caption{Mean Var Null}
+	\end{subfigure}
+	}
+	\caption{The sample kurtosis of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
+The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
+The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
+		\caption{Empirical Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_mean.eps}
+		\caption{MAD Mode Null}
+	\end{subfigure}
+	}
+	\centerline{
+		\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_mean.eps}
+		\caption{Median IQR Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_mean.eps}
+		\caption{Mean Var Null}
+	\end{subfigure}
+	}
+	\caption{The sample mean test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
+The box plots summarise the 100 repeats of the experiment.
+The dotted lines show the critical region at the 5\% level using standard tests for the sample mean and sample variance, assuming independence.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
+		\caption{Empirical Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_variance.eps}
+		\caption{MAD Mode Null}
+	\end{subfigure}
+	}
+	\centerline{
+		\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_variance.eps}
+		\caption{Median IQR Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_variance.eps}
+		\caption{Mean Var Null}
+	\end{subfigure}
+	}
+	\caption{The sample standard deviation test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
+The box plots summarise the 100 repeats of the experiment.
+The dotted lines show the critical region at the 5\% level using standard tests for the sample mean and sample variance, assuming independence.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\centerline{
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_kurtosis.eps}
+		\caption{Empirical Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_kurtosis.eps}
+		\caption{MAD Mode Null}
+	\end{subfigure}
+	}
+	\centerline{
+		\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_kurtosis.eps}
+		\caption{Median IQR Null}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_kurtosis.eps}
+		\caption{Mean Var Null}
+	\end{subfigure}
+	}
+	\caption{The sample kurtosis test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
+The box plots summarise the 100 repeats of the experiment.
+The dotted lines show the critical region at the 5\% level using standard tests for the sample mean and sample variance, assuming independence.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValuePreContaminated.eps}
+		\caption{Before contamination}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValueFiltered.eps}
+		\caption{After filtering}
+	\end{subfigure}
+	\caption{$p$ values when doing hypothesis testing on a $256 \times 256$ dust defect Gaussian image.
+In b), the image was contaminated and then filtered using the \emph{empirical} null filter kernel radius 20.
+Defected pixels have the distribution $\normal(1,1)$.
+The salt defect has density $\pi_1 = 0.1$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The critical region was chosen to control the FDR at 5\%.}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValuePreContaminated2.eps}
+		\caption{Before contamination}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValueFiltered2.eps}
+		\caption{After filtering}
+	\end{subfigure}
+	\caption{$p$ values when doing hypothesis testing on a $256 \times 256$ dust defect Gaussian image.
+In b), the image was contaminated and then filtered using the \emph{MAD mode} null filter kernel radius 20.
+Defected pixels have the distribution $\normal(1,1)$.
+The salt defect has density $\pi_1 = 0.1$.
+The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The critical region was chosen to control the FDR at 5\%.}
+\end{figure}
+
+\section{Conclusion}

### 2019-03-11 reports/thesis/chapters/5_inference.tex
Start on inference chapter

@@
 The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-\texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}.
+\texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}.
 Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.
@@
 
-A pixel by pixel inference was proposed to do defect detection. A statistic $z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
+A pixel by pixel inference was proposed to do defect detection. A statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
 \begin{equation}
@@
     \dfrac{
-        \text{scan}_{x,y} - \text{aRTist}_{x,y}
+        \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
     }
@@
 Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal.
-Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $z_{i,j}$ statistics can be quantified
-\begin{equation}
-Z_{i,j}\sim \normal(0,1) \ .
+Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $Z_{i,j}$ statistics can be approximately quantified
+\begin{equation}
+Z_{x,y}\sim \normal(0,1) \ .
 \end{equation}
@@
 
-The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is be explained here.
-The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample.
-These replicated x-ray scans provide variance-mean data which was used to train the variance model, such as a Gamma distributed GLM.
+The variance model, $\widehat{\variance}\left[\text{scan}_{i,j}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample.
+These replicated x-ray images were manually segmented.
+This provided variance-mean data and was used to train the variance model, such as a Gamma distributed GLM.
 The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
-The variance was then predicted using the grey value in the \texttt{aRTist} simulation.
+The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.
 
 This method for inference was applied to the dataset \texttt{Sep16 120deg}.
-Here a cuboid with voids were purposefully manufactured to see if they can be detected.
+Here a cuboid with voids were purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}.
 The 20 x-ray images were spilt into 2.
 19 images were used to train the variance-mean model.
-One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_initial_artist_scan_aRTist}.
+One image, called the test image, was used to compare with \texttt{aRTist}.
 In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.
+The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist}.
 
@@
   \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_scan.eps}
+  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
+  \caption{CAD of a 3D cuboid with voids}
+  \label{fig:inference_testObject}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
       \caption{X-ray image}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_aRTist.eps}
+      \label{fig:inference_inferenceIntro_inference_scan}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
       \caption{\texttt{aRTist} simulation}
-    \end{subfigure}
-    }
-    \caption{An x-ray scan of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset. This can be compared directly to the \texttt{aRTist} simulation for defects.}
-    \label{fig:inference_initial_artist_scan_aRTist}
+      \label{fig:inference_inferenceIntro_inference_artist}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
+      \caption{$-\log p\text{-values}$}
+      \label{fig:inference_inferenceIntro_inference_pvalue}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
+      \caption{Positive pixels}
+      \label{fig:inference_inferenceIntro_inference_positivePixels}
+    \end{subfigure}
+  }
+  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids.
+The $p$-values obtained were used for hypothesis testing using the \cite{benjamini1995controlling} procedure, controlling the FDR at the 5\% level.
+Pixels detected as positive are shown in red in d).}
+  \label{fig:inference_inferenceIntro_inference}
 \end{figure}
@@
 For each pixel, a $z$ statistic was calculated.
-A $z$ statistic too large in magnitude can be considered to be evidence of a positive result.
-Another way to represent the $z$ statistic is the $p$-value which is given as
+A $z$ statistic too large in magnitude will classify that pixel as a positive result.
+In the hypothesis testing framework \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent $z$ statistic in a different way
 \begin{equation}
@@
 \end{equation}
-which can takes values $0\leqslant p_{i,j} \leqslant 1$.
-A $p$-value too small is considered to be evidence of a defect.
-The resulting $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_logp.eps}
-        \caption{$-\log p\text{-values}$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_image.eps}
-        \caption{$z$ statistics}
-    \end{subfigure}
-    }
-    \caption{The resulting $z$ statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
-    \label{fig:inference_initial_artist_logp_z}
-\end{figure}
-
-The resulting $z$ statistics and $p$-values are concerning.
+which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.
+
+The resulting $p$-values are concerning.
 This is because the $p$-values are not very smooth on the surfaces of the sample.
 It should be expected that small $p$-values are in areas of the defects.
-Pixels are significant, or considered to be evidence of a defect, when for $\|z_{x,y}\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level.
-The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.
+Pixels are tested positive, or considered to be evidence of a defect, when $\|z_{x,y}\|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$.
+This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure.
+The positive pixels are shown in Figure \ref{fig:inference_inferenceIntro_inference_positivePixels}.
 
@@
 Model misspecification appeared to be the main source of error.
-The $z$ statistics was inspected using a histogram and a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}.
-It can be seen that the $z$ statistics does not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect.
-However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.
+The $z$ statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}.
+It can be seen that the majority of the $z$ statistics does not look Normal.
+Also the majority of the $p$-values does not look uniformly distributed.
+This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.
 
@@
   \centering
-    \includegraphics[width=0.7\textwidth]{../figures/inference/initial_artist_sig_pixels.eps}
-    \caption{Significant pixels highlighted using the BH procedure at the $z_\alpha = 2$ significance level.}
-    \label{fig:inference_initial_artist_sig_pixels}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_histo.eps}
-    	\caption{Histogram}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.49\textwidth}
-    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_qq.eps}
-    	\caption{QQ plot}
-    \end{subfigure}
-	}
-    \caption{Distribution of the  $z$ statistics with the BH procedure critical region at the $z_\alpha=2$ level.}
-    \label{fig:inference_initial_artist_z_histo}
-\end{figure}
-
-This chapter covers hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test.
-The empirical null is reviewed and then extended to an image filter, called the empirical null filter.
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
+    \caption{Histogram of $z$}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
+    \caption{$p$-values}
+  \end{subfigure}
+}
+  \caption{a) The histogram of the $z$ statistics is compared with the standard Normal distribution.
+The standard Normal distribution is known as the null distribution in this scenario.
+b) The $p$-values are ordered and plotted.
+The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure.}
+  \label{fig:inference_inferenceIntro_histogram}
+\end{figure}
+
+This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test.
+Assumptions used on the hypothesis testing can be relaxed using the empirical null \citep{efron2004large}, which is reviewed here.
+The empirical null is then extended to an image filter, called the empirical null filter.
 This filter adjust each $z$ statistic according to its neighbours, ironing out false positive results.
-Simulations and actual results was shown at the end of the chapter.
+Simulations and results are shown towards the end of the chapter.
 
@@
 
+\subsection{Approximate Properties of $\widehat{\sigma}_0$}
+
 \subsection{Bandwidth Selection}
@@
 This rule of thumb was developed with consideration of bimodal Normal distributions \citep{silverman1986density}.
-Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{sheather2004density}.
-
-In the context of the empirical null, the kernel density estimator is only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$.
-Thus a good bandwidth is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate.
+Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{silverman1986density, sheather2004density}.
+
+The kernel density estimator is only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$.
+Thus a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate.
 However exact properties of these estimators based on the kernel density estimators can be rather complicated.
-Empirical properties is studied here.
+Empirical properties were studied here.
 
@@
 Various values of $h$ and $n$ were investigated.
-In reality non-null test statistics may appear in the dataset but they should not be too common and interfere with the density estimate too much.
-For a given $h$ and $n$, 50 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation.
-The median squared error, over the 50 repeats, for each of the estimators were plotted as shown in Figure \ref{fig:inference_ZNull1}.
+For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation.
+The median squared error was obtained by taking the median over all squared errors from the 100 estimates.
+Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors.
 
@@
 However the rules of thumb does not optimise for $\widehat{\sigma}_0$ and undershoots it.
-This can be particularly seen in Figure \ref{fig:inference_ZNull2} where the median values of $\widehat{\sigma}_0$ are plotted.
-In this simulation, the true value is $\sigma_0=1$ and all rules of thumb produced biased estimates, in particular underestimates it.
+Figure \ref{fig:inference_BandwidthSelection_error3} shows the median of the estimates of $\sigma_0$.
+The true value in this simulation is $\sigma_0=1$ which is represented as a horizontal plane.
+Bandwidths too small underestimate $\sigma_0$, bandwidths too big over estimates $\sigma_0$.
 
@@
   \end{subfigure}
-    \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
-    \label{fig:inference_ZNull1}
+  \caption{Median squared error of the estimators of the empirical null parameters from 100 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
+  \label{fig:inference_BandwidthSelection_error}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of $n$ simulated $\normal(0,1)$ data.
-On the right, lines represent the rule of thumb for various values of $b$.
-On the left shows the true value of $\sigma_0=1$ as a plane, the empirical truth is where that plan intersects the surface.}
-    \label{fig:inference_ZNull2}
-\end{figure}
-
-Overestimates and underestimates are both dangerous, but it depends on the importance of false positives and false negatives.
+    \caption{Median value of $\widehat{\sigma}_0$ from 100 repeats of $n$ simulated $\normal(0,1)$ data. The true value is $\sigma_0=1$ which is represented by a horizontal plane.}
+    \label{fig:inference_BandwidthSelection_error3}
+\end{figure}
+
+Overestimates and underestimates are both dangerous and it can affect the false positive and false negative rate.
 This is because $\widehat{\sigma}_0$ was used to rescale the test statistics accordingly.
@@
 \begin{equation}
-	\zeta_i = \dfrac{
+  t_i = \dfrac{
     z_i - \widehat{\mu}_0
@@
 \end{equation}
-Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $\zeta_i$, potentially testing more of these test statistics as significant.
+Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $t_i$, potentially testing more of these test statistics as positive.
 High values of $\widehat{\sigma}_0$ does the opposite.
-Large number of positive results can led to more false positive results and vice versa.
+Large number of positives can led to more false positives and vice versa.
 
 The optimal bandwidth for a given $n$ was found numerically.
-Such a relationship can be seen in Figure \ref{fig:inference_ZNull_mse_plot} which plots the log squared error against the bandwidth for various $n$.
-A local quadratic regression \citep{friedman2001elements} was fitted and this was used to find the bandwidth which minimises the log squared error for a given $n$.
+Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $n$.
+A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimises the log squared error for a given $n$.
 
@@
     }
-    \caption{A local quadratic regression was fitted on the log mean squared error for estimating $\sigma_0$ against the bandwidth.
+    \caption{A smoothing spline was fitted on the log squared error for estimating $\sigma_0$ against the bandwidth.
 The estimator $\widehat{\sigma}_0$ uses the kernel density estimator fitted onto $n$ simulated standard Normal data.
-Boxplots were used to represent the variation of the error from 50 repeats.}
-    \label{fig:inference_ZNull_mse_plot}
+Boxplots represent the variation of the error from 100 repeats.
+The red dashed line shows the bandwidth which minimise the fitted spline.}
+    \label{fig:inference_BandwidthSelection2_plot}
 \end{figure}
@@
 where $b$ and $a$ are parameters to be fitted.
-Figure \ref{fig:inference_ZNull_mserule_of_thumb} show the fitting of an identity link Gamma GLM in order to estimate $b$ and $a$.
-The estimated parameters are shown in Table \ref{table:inference_ZNull_mse_glm_estimate}.
+Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} show the fitting of an identity link gamma GLM in order to estimate $b$ and $a$.
+The estimated parameters are shown in Table \ref{table:inference_BandwidthSelection2_ruleOfThumb}.
 
@@
   \includegraphics[width=0.7\textwidth]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
-	\caption{An identity link Gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$.
-The boxplot show the bootstrap error in finding the optimal bandwidth, which is only there for illustration purposes.}
-	\label{fig:inference_ZNull_mserule_of_thumb}
+  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 95\% prediction interval.}
+  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
 \end{figure}
@@
   \input{../figures/inference/BandwidthSelection2_bandwidthEstimate.txt}
-	\caption{Estimated and standard error gradient and intercept from the linear relationship in Figure \ref{fig:inference_ZNull_mserule_of_thumb}.}
-	\label{table:inference_ZNull_mse_glm_estimate}
+  \caption{Estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
+  \label{table:inference_BandwidthSelection2_ruleOfThumb}
 \end{table}

### 2019-03-13 reports/thesis/chapters/5_inference.tex
Write inference chapter literature review

@@
 Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal.
-Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $Z_{i,j}$ statistics can be approximately quantified
+Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $Z_{x,y}$ statistics, assuming there are no defects, can be approximately quantified
 \begin{equation}
@@
 \begin{equation}
-    p_{x,y} = 2(1-\Phi(\|z_{x,y}\|))
+  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
 \end{equation}
@@
 It should be expected that small $p$-values are in areas of the defects.
-Pixels are tested positive, or considered to be evidence of a defect, when $\|z_{x,y}\|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$.
+Pixels are tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$.
 This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure.
@@
 
-Hypothesis testing dates back to \cite{pearson1900on}, \cite{neyman1933on} and \cite{fisher1970statistical}. It is one of the most fundamental methods in science.
-
-The focus on this section is on the single hypothesis test.
-A Normal random variable is studied as this is of interest in this project.
-It also appears in other tests such as the difference in sample means.
-
-In the context of this project, an example of hypothesis testing is given here.
-Here, it was assumed that the test statistic $Z\sim\normal(0,1)$.
-A null hypothesis is written down to describe this.
-This is done by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis
-\begin{equation}
-    H_0:\mu=0 \ .
-\end{equation}
-This specifies the assumptions made on the random variable $Z$, here the mean is zero. Any data behaving as assumed is treated as a negative result or not significant.
-
-A positive, or significant, result is obtained when unlikely data is obtained and this happens if $Z$ deviates too much from 0.
-This can be described as testing $H_0$ against an alternative hypothesis $H_1$ where
-\begin{equation}
-    H_1:\mu\neq0 \ .
-\end{equation}
-How much $Z$ deviates from 0 to be considered a positive is up to the user but typically $\|Z\|>z_\alpha$ where $z_\alpha =2$ is a typical choice for the threshold.
-
-A way to quantify the threshold for a positive result is to use something called the size of the test, otherwise known as the significance level, denoted as $\alpha$.
-This is the probability of a false positive result, which can be denoted as
-\begin{equation}
-    \prob(\|Z\|>z_\alpha|H_0) = \alpha \ .
-\end{equation}
-Using the fact the Normal distribution is symmetric then
-\begin{equation}
-    2(1 - \Phi(z_\alpha)) = \alpha \ .
-    \label{eq:inference_single_alpha}
-\end{equation}
-The choice of $z_\alpha=2$ set the size of the test to be $\alpha\approx 4.55\%$. The $z_\alpha=2$ level is used throughout this project.
-
-The $p$-value is a way to represent an observation of the data $Z=z$. Similar to the size, the $p$-value is
-\begin{equation}
-    p=2(1-\Phi(\|z\|)) \ .
-\end{equation}
-As a result, the $p$-value can be compared directly to the size of the test. That is there is a positive result if $p<\alpha$, otherwise it is a negative result.
-
-The power of the test is defined as the probability of a true positive result. For unknown $\mu$, it is useful to investigate the power for a range of $\mu$.
-
-In this section, the single hypothesis test is extended and the multiple hypothesis testing \citep{shaffer1995multiple, dudoit2003multiple} is reviewed.
-
-Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$ where $Z_i\sim\normal(\mu,1)$ for $i=1,2,\dotdotdot,n$ and i.i.d.
-Suppose each individual statistic were used to test the following hypotheses $H_0:\mu=0$ and $H_1:\mu\neq 0$.
-Using the method from the single hypothesis test at the $z_\alpha=2$ level, any statistic where $\|Z_i\|>2$ for $i=1,2,\dotdotdot,n$ would be considered significant.
-
-Bringing in methods from single hypothesis testing to the multiple version has drawbacks.
-Assuming that the null hypothesis is true for all $Z_i$ for $i=1,2,\dotdotdot,n$, then by definition $\alpha\approx 4.55\%$ of the data will be tested positive, and falsely positive.
-Still under the same assumption, the probability of at least one false positive result, known as the family-wise error rate (FWER) \citep{shaffer1995multiple}, is
-\begin{align}
-    \text{FWER}&=1-\prob(\text{no false positives}) \nonumber\\
-    \text{FWER}&=1-\prob(\text{no positive results}|H_0) \nonumber\\
-    \text{FWER}&=1-\left[(1-\alpha)^n\right] \label{eq:inference_fwer}\ .
-\end{align}
-To put into context, for $\alpha\approx 4.55\%$ and $n=20$ then remarkably $\text{FWER}\approx60.6\%$. This method for multiple hypothesis testing will have too many false positive results.
-
-While the uncorrected method for multiple hypothesis testing has it flaws, it does control the per comparison error rate (PCER) \citep{benjamini1995controlling}.
+Consider a $z$ statistic from a pixel.
+If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$.
+This can be described in another way by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$.
+A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$.
+A statistic which does not have the null distribution is known as non-null.
+
+In hypothesis testing \cite{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example.
+A positive result is declared when $p<\alpha$, else it is a negative result.
+Correct and incorrect testing of the statistics can occur.
+For example testing a null statistic as positive is known as a false positive.
+It can be shown that $\alpha$ controls the false positive rate.
+$\alpha=5.0\%$ is a typical choice.
+Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.
+
+Multiple hypothesis testing occurs when there are more than one hypothesis to test.
+For example $n$ pixels can be tested where the $z$ statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$.
+The null hypothesis is $H_{0,i}:\mu_i=0$ and is tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$.
+Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.
+
+The uncorrected test classify any $p_i<\alpha$ as positive.
+This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increase \citep{shaffer1995multiple}.
+This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}.
 PCER is the proportion of false positives out of all tests.
-There are corrections for multiple hypothesis testing which controls different things.
-Conventionally they are expressed in terms of the number true/false positives/negatives, these are defined in Table \ref{table:inference_randomvariables}.
-Using the notation, formally PCER is defined as
+The number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}.
+Using the notation, PCER is defined as
 \begin{equation}
   \text{PCER}=
-    \dfrac{
-        1
-    }
-    {
-        n
-    }
+  \dfrac{1}{n}
   \expectation[V]
@@
     &Negative&Positive&Total\\\hline
-        True null & $U$ & $V$ & $n_0$\\
-        Non-true null & $T$ & $S$ & $n-n_0$\\\hline
+    Null & $U$ & $V$ & $n_0$\\
+    Non-null & $T$ & $S$ & $n-n_0$\\\hline
     &$n-R$&$R$&$n$
@@
 
-The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the FWER.
+The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
+\begin{equation}
+  \text{FWER} = 1-\prob(V=0) \ .
+  \label{eq:inference_fwer}
+\end{equation}
 This is done by adjusting the size of the test to be $\alpha/n$.
-By using the adjusted size, Equation \eqref{eq:inference_fwer} becomes
-\begin{equation}
-    \text{FWER}=1-\left[(1-\alpha/n)^n\right]\ .
-\end{equation}
-Using the approximation $(1-\alpha/n)^n\approx = 1-\alpha$ then
-\begin{equation}
-    \text{FWER}\approx \alpha \ .
-\end{equation}
+By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$.
+Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$.
 This shows that the Bonferroni correction controls the family-wise error rate such that
@@
 \begin{equation}
-    \text{FDR} = \expectation\left[
-        \dfrac{V}{R}
-    \right]
+  \text{FDR} = \expectation\left[\dfrac{V}{R}\right]
   \ .
@@
 
-In practice the BH procedure adjusts the size of the test between the Bonferroni correction and the uncorrected test.
-The BH procedure also adapts to the data, meaning the procedure chooses different sizes for different data.
-
-The procedure is as follows.
-Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$.
-They are converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$.
+The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test.
+It adapts to the data and choose different sizes for different data.
+The procedure is as follows, the $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$.
 Suppose a size $\alpha$ is provided beforehand.
@@
 \end{equation}
-This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as significant.
-For the case where $p_{(1)}>\alpha/n$, then $k=1$ was chosen so that the Bonferroni correction is used instead.
-The BH procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
+This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive.
+For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
+The BH procedure comes from the fact that if all the statistics are null and independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
 However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.
-
 It can be shown that the BH procedure controls the FDR such that
 \begin{equation}
-    \text{FDR}\leqslant\pi_0\alpha\leqslant\alpha
-\end{equation}
-where $\pi_0=n_0/n$ \citep{benjamini1995controlling}, which is usually unknown in practice.
+  \text{FDR}\leqslant\alpha
+\end{equation}
+\citep{benjamini1995controlling}.
 
@@
 
-By treating each pixel as a hypothesis test, methods for multiple hypothesis can be deployed.
-At the start of the chapter, a scan from the \texttt{Sep16 120deg} dataset was compared to the \texttt{aRTist} simulation, obtaining a $z$ image.
-
 \begin{figure}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_image.eps}
+      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
       \caption{$z$ image with section highlighted}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo.eps}
+      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
       \caption{Histogram of section}
@@
     \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown. The critical region was obtained using the BH procedure.}
-    \label{fig:inference_empirical_null_sub_z}
-\end{figure}
-
-A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_empirical_null_sub_z}.
-The BH procedure was used at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../tables/empirical_null_sub_boundary.txt}...$.
-However a quick look at the histogram showed that almost half of the pixels were significant.
+    \label{fig:inference_inferenceSubsample1_histogram}
+\end{figure}
+
+Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+The distribution of the $z$ statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$.
+Almost half of the pixels were were tested positive.
 It is questionable whether such number of positive results is sensible, in particular in an area where defects were not expected.
 
-The histogram showed that the majority of the $z$ statistics are centred around 2 and has a bell shaped curve, a characteristic of the Normal distribution.
-If the data showed that the majority is centred elsewhere then expected, is it right to then to test the majority of the data as positive?
-This is an example of model misspecification because it was assumed that the $z$ statistics are distributed as $\normal(0,1)$ when in reality they are distributed as $\normal(\mu_0,\sigma_0^2)$.
-
-The empirical null \citep{efron2004large} adjusts the assumptions made on the $z$ statistics according to the majority of the data and treating it as the norm, relaxing the assumptions needed.
-It requires the following assumptions: the majority of the data are truly null, non-null test statistics are rare and the null test statistics are Normal distributed.
-
-The method is described here.
-Suppose the following test statistics were obtained $z_1,z_2,\dotdotdot,z_n$.
-First the histogram is smoothed.
-\cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} was used here because it has simpler mathematical properties.
-The kernel density estimate \citep{parzen1962on} is
-\begin{equation}
-  \widehat{p}_Z(z)=
-  \frac{1}{nh}
-  \sum_{i=1}^n\phi\left(
-    \dfrac{z_i-z}{h}
-  \right)
-  \label{eq:inference_kernel_density_estimate}
-\end{equation}
-where $h$ is the bandwidth. The bandwidth was chosen such that
-\begin{equation}
-  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
-  \label{eq:inference_ourruleofthumb}
-\end{equation}
-where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.
-The parameters of the empirical null are estimated using the kernel density estimate.
-The resulting estimated density is shown in Figure \ref{fig:inference_empirical_null_sub_density_estimate}.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_nocritical.eps}
-        \caption{Histogram}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_parzen.eps}
-        \caption{Kernel density estimate}
-    \end{subfigure}
-    }
-    \caption{The density of the test statistics was estimated using a histogram or a kernel density estimate.
-The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
-    \label{fig:inference_empirical_null_sub_density_estimate}
-\end{figure}
-
-Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is found.
-This is used as the mean of the empirical null \citep{efron2004large}.
-The calculation of $\widehat{\mu}_0$ was numerically found using the Newton-Raphson method.
-Using the mode, the standard deviation of the empirical null was estimated using \citep{efron2004large}
-\begin{equation}
-  \widehat{\sigma}_0 = \left[
-    \left.
-      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_Z(z)
-    \right|_{z=\widehat{\mu}_0}
-  \right]^{-1/2}
-  \ .
-\end{equation}
-In this particular example, it was found that $\widehat{\mu}_0=\input{../tables/empirical_null_sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../tables/empirical_null_sub_null_sigma.txt}...$.
-It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.
-
-The empirical null was used to correct the test statistics $z_1,z_2,\dotdotdot,z_n$ to $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ by standardising the test statistics
-\begin{equation}
-  \zeta_i = \dfrac{
-    z_i - \widehat{\mu}_0
-  }
-  {
-    \widehat{\sigma}_0
-  }
-  \ .
-  \label{eq:inference_zeta}
-\end{equation}
-The corrected test statistics $\zeta_1,\zeta_2,\dotdotdot,\zeta_n$ were used in any multiple hypothesis testing procedures.
-Using the BH procedure, the critical region was found to be $\|\zeta\|\geqslant\input{../tables/empirical_null_sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../tables/empirical_null_sub_null_critical1.txt}...$ and $\input{../tables/empirical_null_sub_null_critical2.txt}...\leqslant Z$.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_null.eps}
-        \caption{Histogram of $z$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_p_values.eps}
-        \caption{Ordered $p$ values}
-    \end{subfigure}
-    }
-    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
-    \label{fig:inference_empirical_null_sub_z_critical_regions}
-\end{figure}
-
-These new critical regions are shown in Figure \ref{fig:inference_empirical_null_sub_z_critical_regions}.
-No positive results were found and the $p$-values are sensible as they look uniformly distributed.
-This demonstrated that the empirical null adjust the parameters of the null distribution to fit the majority of the data in order to make sensible inference.
-
-In this section, a more mathematical approach to the empirical null is taken to examine why and when this method works.
-Next computational concepts is discussed such as on how the mode of the kernel density estimator is found and what makes a good bandwidth in the kernel density estimator.
-This section is finished with a further discussion.
-
-\section{Empirical Null}
-
-\cite{efron2004large} was motivated to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
-These problems are similar to the one observed at the start of this chapter.
-The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
-
-For formality, the null and alternative hypotheses is described here. Assume that the $z$ statistics under the null hypothesis are such that
-\begin{equation}
-  Z_i|H_0\sim\normal(\mu,\sigma_0^2)
-\end{equation}
-for $i=1,2,\dotdotdot,n$ and i.i.d. The hypotheses are then
-\begin{equation}
-  H_0:\mu = \mu_0
-\end{equation}
-and
-\begin{equation}
-  H_1:\mu\neq\mu_0
-\end{equation}
-where $\mu_0$ and $\sigma_0$ are the empirical null mean and standard deviation respectively.
-Essentially null $z$ statistics are assumed to be Normal distributed, with parameters using the empirical null.
-Statistics which deviates too much from $\mu_0$ are considered to be positive.
-
-The distribution of the $z$ statistics can be described using a mixture model. Let the random variable $Z$ have the probability density function
+This problem commonly occur in large scale multiple hypothesis testing \citep{efron2004large} such as in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
+It appears that the null distribution was misspecified as $Z_i|H_{0,i}\sim\normal(0,1)$ when in reality they are distributed as $Z_i|H_{0,i}\sim\normal(\mu_0,\sigma_0^2)$, where $\mu_0$ and $\sigma_0$ are the null mean and null standard deviation respectively.
+
+In practice $\mu_0$ and $\sigma_0$ are unknown.
+The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate.
+Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively.
+The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\cdots,n$.
+
+In \citep{efron2004large}, a few assumptions were made in order to obtain the estimators $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Let the test statistic $Z$ have the p.d.f.
 \begin{equation}
@@
 \end{equation}
-as it was assumed to be Normal. The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified.
-
-The empirical null parameters are to be estimated.
-Assuming that $\pi_0$ is large, say bigger than 0.9 \citep{efron2004large}, and at and around the mode the probability density function is dominated by the null distribution.
+as it was assumed to be Normal.
+The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified.
+Assume that the majority of the data are null and non-null test statistics are rare, say $\pi_0>0.9$ \citep{efron2004large}.
+Then around the mode, the probability density function would be dominated by the null distribution.
 This implies that
@@
 \begin{equation}
-  \widehat{\mu}_0 = \argmax\widehat{p}_Z(z) \ .
-\end{equation} 
-The empirical null standard deviation was obtained from the log density. For values of $z$ at and around the mode
+  \widehat{\mu}_0 = \argmax\widehat{p}_Z(z)
+\end{equation}
+where $\widehat{p}_Z(z)$ is the density estimation of $p_Z(z)$, for example it could be a smoothing spline fitted onto the histogram \citep{efron2004large}.
+
+The null standard deviation was estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
 \begin{equation}
@@
 \end{equation}
-The evaluation of $z=\widehat{\mu}_0$ is used as in that region, one would hope that null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.
+The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.
 
@@
 \cite{efron2004large} motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.
+
+The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
+There exist various methods for the empicial null.
+\citep{schwartzman2008empirical} uses Poisson regression on the histogram counts in regions where the null statistics dominate.
+The empirical characteristic function was used in \citep{jin2007estimating}.
+
+\section{Empirical Null}
+
+The method is described here.
+Suppose the following test statistics were obtained $z_1,z_2,\cdots,z_n$.
+First the histogram is smoothed.
+\cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} was used here because it has simpler mathematical properties.
+The kernel density estimate \citep{parzen1962on} is
+\begin{equation}
+  \widehat{p}_Z(z)=
+  \frac{1}{nh}
+  \sum_{i=1}^n\phi\left(
+    \dfrac{z_i-z}{h}
+  \right)
+  \label{eq:inference_kernel_density_estimate}
+\end{equation}
+where $h$ is the bandwidth. The bandwidth was chosen such that
+\begin{equation}
+  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
+  \label{eq:inference_ourruleofthumb}
+\end{equation}
+where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.
+The parameters of the empirical null are estimated using the kernel density estimate.
+The resulting estimated density is shown in Figure \ref{fig:inference_empirical_null_sub_density_estimate}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
+  \caption{The density of the test statistics was estimated using a histogram or a kernel density estimate.
+The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
+  \label{fig:inference_empirical_null_sub_density_estimate}
+\end{figure}
+
+Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is found.
+This is used as the mean of the empirical null \citep{efron2004large}.
+The calculation of $\widehat{\mu}_0$ was numerically found using the Newton-Raphson method.
+Using the mode, the standard deviation of the empirical null was estimated using \citep{efron2004large}
+\begin{equation}
+  \widehat{\sigma}_0 = \left[
+    \left.
+      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_Z(z)
+    \right|_{z=\widehat{\mu}_0}
+  \right]^{-1/2}
+  \ .
+\end{equation}
+In this particular example, it was found that $\widehat{\mu}_0=\input{../tables/empirical_null_sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../tables/empirical_null_sub_null_sigma.txt}...$.
+It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.
+
+The empirical null was used to correct the test statistics $z_1,z_2,\cdots,z_n$ to $\zeta_1,\zeta_2,\cdots,\zeta_n$ by standardising the test statistics
+\begin{equation}
+  \zeta_i = \dfrac{
+    z_i - \widehat{\mu}_0
+  }
+  {
+    \widehat{\sigma}_0
+  }
+  \ .
+  \label{eq:inference_zeta}
+\end{equation}
+The corrected test statistics $\zeta_1,\zeta_2,\cdots,\zeta_n$ were used in any multiple hypothesis testing procedures.
+Using the BH procedure, the critical region was found to be $|\zeta|\geqslant\input{../tables/empirical_null_sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../tables/empirical_null_sub_null_critical1.txt}...$ and $\input{../tables/empirical_null_sub_null_critical2.txt}...\leqslant Z$.
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_null.eps}
+        \caption{Histogram of $z$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_p_values.eps}
+        \caption{Ordered $p$ values}
+    \end{subfigure}
+    }
+    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
+    \label{fig:inference_empirical_null_sub_z_critical_regions}
+\end{figure}
+
+These new critical regions are shown in Figure \ref{fig:inference_empirical_null_sub_z_critical_regions}.
+No positive results were found and the $p$-values are sensible as they look uniformly distributed.
+This demonstrated that the empirical null adjust the parameters of the null distribution to fit the majority of the data in order to make sensible inference.
+
+In this section, a more mathematical approach to the empirical null is taken to examine why and when this method works.
+Next computational concepts is discussed such as on how the mode of the kernel density estimator is found and what makes a good bandwidth in the kernel density estimator.
+This section is finished with a further discussion.
 
@@
 \end{equation}
-for $r=0,1,2,3,\dotdotdot$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is
+for $r=0,1,2,3,\cdots$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is
 \begin{equation}
@@
 \begin{equation}
-  \left\|
+  \left|
     \dfrac{
@@
   \ln\widehat{p}_Z(z)
-  \right\|
+  \right|
   <10^{-5}
@@
 In this setting, the parameters of the null distribution varies spatially, slowly and smoothly in 2D space.
-Let $Z_{x,y}$ be the test statistic of the pixel at position $(x,y)$ for $x=1,2,\dotdotdot,W$ and $y=1,2,\dotdotdot,H$.
+Let $Z_{x,y}$ be the test statistic of the pixel at position $(x,y)$ for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$.
 Let each pixel have a test statistic distributed under the null such that

### 2019-03-14 reports/thesis/chapters/5_inference.tex
Writing empirical null section, null std represented by plotting empirical null distribution

@@
 It can be shown that $\alpha$ controls the false positive rate.
-$\alpha=5.0\%$ is a typical choice.
+$\alpha=5.0\%$ is a typical choice and was used throughout this thesis.
 Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.
@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
-      \caption{$z$ image with section highlighted}
+      \caption{$z$ statistics}
     \end{subfigure}
@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
-      \caption{Histogram of section}
-    \end{subfigure}
-    }
-    \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown. The critical region was obtained using the BH procedure.}
+      \caption{Histogram of $z$ in sub-image}
+    \end{subfigure}
+    }
+    \caption{The resulting $z$ image is shown in a).
+A $200\times 200$ sub-image was taken shown by the dashed lines.
+A histogram of the $z$ statistics in the sub-image is shown in b).
+The critical region was obtained by using the BH procedure at the 5\% FDR level.}
     \label{fig:inference_inferenceSubsample1_histogram}
@@
 
-The method is described here.
-Suppose the following test statistics were obtained $z_1,z_2,\cdots,z_n$.
-First the histogram is smoothed.
-\cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} was used here because it has simpler mathematical properties.
+Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
 The kernel density estimate \citep{parzen1962on} is
@@
 where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.
-The parameters of the empirical null are estimated using the kernel density estimate.
-The resulting estimated density is shown in Figure \ref{fig:inference_empirical_null_sub_density_estimate}.
 
@@
   \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
-  \caption{The density of the test statistics was estimated using a histogram or a kernel density estimate.
-The dotted lines in the kernel density estimate shows the empirical null mean and standard deviation estimation.}
-  \label{fig:inference_empirical_null_sub_density_estimate}
-\end{figure}
-
-Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$, is found.
-This is used as the mean of the empirical null \citep{efron2004large}.
-The calculation of $\widehat{\mu}_0$ was numerically found using the Newton-Raphson method.
-Using the mode, the standard deviation of the empirical null was estimated using \citep{efron2004large}
-\begin{equation}
-  \widehat{\sigma}_0 = \left[
-    \left.
-      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_Z(z)
-    \right|_{z=\widehat{\mu}_0}
-  \right]^{-1/2}
-  \ .
-\end{equation}
-In this particular example, it was found that $\widehat{\mu}_0=\input{../tables/empirical_null_sub_null_mu.txt}...$ and $\widehat{\sigma}_0=\input{../tables/empirical_null_sub_null_sigma.txt}...$.
-It was found that both of these estimators have negligible bootstrap \citep{efron1992bootstrap} variance or error.
-
-The empirical null was used to correct the test statistics $z_1,z_2,\cdots,z_n$ to $\zeta_1,\zeta_2,\cdots,\zeta_n$ by standardising the test statistics
-\begin{equation}
-  \zeta_i = \dfrac{
-    z_i - \widehat{\mu}_0
+  \caption{The density of the $z$ statistics was estimated using a kernel density estimate. The dot dash lines shows the empirical null distribution.}
+  \label{fig:inference_inferenceSubsample1_densityEstimate}
+\end{figure}
+
+The null parameters were estimated.
+The null mean was estimated by numerically finding the mode of the density estimate.
+The null standard deviation was estimated using the curvature of the density estimate at the mode.
+This resulted in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
+In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.
+
+The use of the kernel density estimate has its advantages.
+The only tuning parameter is the bandwidth $h$ and the density estimate is simple enough to do calculus on it.
+Speed may be an issue as an evaluation of the density estimate requires the sum over the $n$ $z$ statistics.
+
+The $z$ statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
+\begin{equation}
+  T_i = \dfrac{
+    Z_i - \widehat{\mu}_0
   }
@@
   }
-  \ .
-  \label{eq:inference_zeta}
-\end{equation}
-The corrected test statistics $\zeta_1,\zeta_2,\cdots,\zeta_n$ were used in any multiple hypothesis testing procedures.
-Using the BH procedure, the critical region was found to be $|\zeta|\geqslant\input{../tables/empirical_null_sub_null_critical_zeta.txt}...$ or in terms of the original units $Z \leqslant \input{../tables/empirical_null_sub_null_critical1.txt}...$ and $\input{../tables/empirical_null_sub_null_critical2.txt}...\leqslant Z$.
+  \label{eq:inference_empiricalNullNormalise}
+\end{equation}
+for $i=1,2,\cdots,n$. The normalised $p$-values were obtained by using
+\begin{equation}
+  p_i = 2(1-\Phi(|t_i|))
+\end{equation}
+and then were used in the BH procedure.
+The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$.
+In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places.
+The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_histo_null.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullHistogram.eps}
         \caption{Histogram of $z$}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/empirical_null_sub_z_p_values.eps}
-        \caption{Ordered $p$ values}
-    \end{subfigure}
-    }
-    \caption{The critical regions were adjusted using the empirical null. The empirical null were also used to adjust the $z$ statistics, producing sensible $p$-values}
-    \label{fig:inference_empirical_null_sub_z_critical_regions}
-\end{figure}
-
-These new critical regions are shown in Figure \ref{fig:inference_empirical_null_sub_z_critical_regions}.
-No positive results were found and the $p$-values are sensible as they look uniformly distributed.
-This demonstrated that the empirical null adjust the parameters of the null distribution to fit the majority of the data in order to make sensible inference.
-
-In this section, a more mathematical approach to the empirical null is taken to examine why and when this method works.
-Next computational concepts is discussed such as on how the mode of the kernel density estimator is found and what makes a good bandwidth in the kernel density estimator.
-This section is finished with a further discussion.
+        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullPValues.eps}
+        \caption{$p$ values}
+    \end{subfigure}
+    }
+    \caption{The critical regions and $p$-values were adjusted using the empirical null.}
+    \label{fig:inference_inferenceSubsample1_nullResults}
+\end{figure}
+
+No positive results were found and the $p$-values were sensible as they looked uniformly distributed.
+This demonstrated that the empirical null adjusted the parameters of the null distribution to fit the majority of the data in order to make sensible inference.
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_zImage.eps}
+        \caption{$z$ statistics}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_subimagePositive.eps}
+        \caption{$z$ from the sub-image}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullHistogram.eps}
+        \caption{Histogram of $z$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullPValues.eps}
+        \caption{$p$ values}
+    \end{subfigure}
+    }
+    \caption{A $200\times 200$ sub-image containing a defect is shown in a).
+The empirical null was used to test pixels, positive pixels are shown in red in b).
+The histogram of the $z$ statistics are shown in c) along with the critical region.
+The normalised $p$-values are shown in d).
+The critical regions were adjusted using the empirical null and obtained using the BH procedure, controlling the FDR at 5\%.}
+    \label{fig:inference_inferenceSubsample2}
+\end{figure}
+
+Another example is shown in Figure \ref{fig:inference_inferenceSubsample2} where a $200\times 200$ sub-image containing a defect was used.
+It can be seen that the null distribution was not centred at zero, however the empirical null took it into account.
+The estimation of the empirical null parameters were robust as it only depended on the density estimate at the mode only, it should not be affected by non-null test statistics.
+
+The BH procedure was conducted using the normalised $p$-values.
+$\inputNumber{../figures/inference/inferenceSubsample2_nPositive.txt}$ pixels were tested positive.
+The majority of the positive pixels were found to be clustered together, which highlighted the defect.
+Not all of the defects were tested positive, but a good number of them are.
+This should be enough to raise suspicion in that particular area.
+Only a few pixels were falsely tested as positive, however they are typically isolated single pixels.
+Isolated positive pixels should be discarded as they are more than likely to be tested positive by random chance.
+
+This section describes the empirical null implementation in detail, in particular the numerical and computational aspects.
+The empirical properties of the sampling distribution of the null parameter estimators were studied.
 
@@
 \section{Conclusion}
+
+Clusters of significant pixels should raise suspicions.
+One could create a binary image, assigning a Boolean value whether that pixel is tested positive or not.
+A binary image filter, such as erode followed by a dilate, can be used to remove isolate significant pixels and emphasise the cluster of significant pixels.

### 2019-03-14 reports/thesis/chapters/5_inference.tex
Write up empirical null

@@
 Taking the first derivative
-\begin{equation}
+\begin{equation*}
   \dfrac{
@@
   \ .
-\end{equation}
+\end{equation*}
 Using the fact that $\phi(z)=(2\pi)^{-1/2}\exp(-z^2/2)$, then $\phi'(z)=-z\phi(z)$. This is used to simplify the equation to be
@@
 Taking the derivative again
-\begin{multline}
+\begin{multline*}
   \dfrac{
@@
   \ .
-\end{multline}
+\end{multline*}
 Using the fact that $\phi'(z)=-z\phi(z)$, then it is simplified to
@@
 \begin{equation}
-  \left|
+  \log\left|
+    \left.
     \dfrac{
@@
   \ln\widehat{p}_Z(z)
+  \right|_{z=\widehat{\mu}_0}
   \right|
-  <10^{-5}
+  <-5
 \end{equation}
@@
 
-The algorithm does depend on the initial value so using different initial values is recommended.
-It was chosen here to use the quartiles of the data as the initial values and then select the best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of all the different initial values.
-Should the algorithm still fail, a random data point is selected to be the initial value until a successful convergence is achieved.
+The algorithm does depend on the initial value so using different initial values were used.
+Further initial values were generated by sampling from $\normal(z^{(0)}, s_z^2)$.
+This was done multiple times until 3 valid solutions were obtained.
+The best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of all the different initial values was used as the final answer.
 The Newton-Raphson method can fail if it converges to a stationary point other than a global maximum, for example a local maximum or a point of inflection.
 
-\subsection{Approximate Properties of $\widehat{\sigma}_0$}
-
 \subsection{Bandwidth Selection}
 
-The choice of the bandwidth $h$ is important for the kernel density estimator.
-It controls how smooth the kernel density estimator is, with higher values of $h$ producing smoother curves \citep{friedman2001elements}.
-Cross validation methods do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
+The bandwidth $h$ controls how smooth the kernel density estimator is, higher values producing smoother curves \citep{friedman2001elements}.
+Cross validation methods to select $h$ do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
 Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are typically of the form
@@
 
-The kernel density estimator is only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$.
+The kernel density estimator was only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$.
 Thus a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate.
-However exact properties of these estimators based on the kernel density estimators can be rather complicated.
-Empirical properties were studied here.
-
-An experiment was conducted to investigate the behaviour of the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, on a dataset of $n$ simulated all null $\normal(0,1)$.
-Various values of $h$ and $n$ were investigated.
-For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation.
+Exact properties of these estimators based on the kernel density estimators can be rather complicated.
+For example numerous approximations were needed to show that $\widehat{\sigma}_0$ is an unbiased estimator of $\sigma_0$ to the first order, where higher order terms are functions of $\widehat{\mu}_0 - \mu_0$ and $h$.
+This is shown in Appendix ?.
+
+An experiment was conducted to investigate how the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, varied with $h$ and $n$.
+This was done on a simulated dataset of $n$ standard Normal random variables.
+For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation of the datasets.
 The median squared error was obtained by taking the median over all squared errors from the 100 estimates.
@@
 This is because $\widehat{\sigma}_0$ was used to rescale the test statistics accordingly.
-Recall that the corrected test statistics are
-\begin{equation}
-  t_i = \dfrac{
-    z_i - \widehat{\mu}_0
-  }
-  {
-    \widehat{\sigma}_0
-  }
-  \ .
-  \tag{\ref{eq:inference_zeta}}
-\end{equation}
+Recall that the normalised test statistics are $t_i = \dfrac{z_i - \widehat{\mu}_0}{\widehat{\sigma}_0}$.
 Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $t_i$, potentially testing more of these test statistics as positive.
@@
 A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimises the log squared error for a given $n$.
+\texttt{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures.
+The optimisation was done using \texttt{MATLAB}'s gradient free \texttt{fminsearch} function, using $h=0.9n^{-1/5}$ as the initial value.
 
@@
 where $b$ and $a$ are parameters to be fitted.
-Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} show the fitting of an identity link gamma GLM in order to estimate $b$ and $a$.
+This was chosen to establish a simple relationship with the rules of thumb.
+Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} show the fitting of an identity link Gamma GLM in order to estimate $b$ and $a$.
 The estimated parameters are shown in Table \ref{table:inference_BandwidthSelection2_ruleOfThumb}.
@@
 
-The results showed that the rules of thumb can be improved if a small bias is added to it.
+The rules of thumb can be improved if a small bias is added to it.
 This is because an intercept was found when fitting a linear relationship between the optimal bandwidth and $n^{-1/5}$.
@@
 
+The GLM fit in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} appeared to underfit, which suggest there may be a more complicated relationship between the optimal bandwidth and $n$.
+The method used in fitting the smoothing spline could contribute to the underfitting.
+For example if the smoothing spline was not smooth enough so that local minima appear, it would add variance to the location of the optimal bandwidth.
+A basic linear relationship was chosen to avoid overfitting and keep the rule of thumb simple.
+
 In conclusion, a small bias added to the rule of thumb improved the performance of the estimator $\widehat{\sigma}_0$.
@@
 \section{Empirical Null Filter}
-
-A further example is given here.
-A $200\times200$ sub-sample, containing a defect, was taken as shown in Figure \ref{fig:inference_alt_empirical_z_image}.
-The histogram of the test statistics, along with the empirical null, is shown in Figure \ref{fig:inference_alt_empirical_z_histogram}.
-It can be seen that the null distribution is not centred at zero, however the empirical null takes that into account.
-The estimation of the empirical null parameters are robust as it only depends on the density estimate at the mode only, it should not be affected by non-null test statistics.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_image.eps}
-        \caption{$z$ image}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_image_2.eps}
-        \caption{Sample from left}
-    \end{subfigure}
-    }
-    \caption{$z$ image from comparing a scan with \texttt{aRTist}. A sub-sample containing a defect is shown. Highlighted in red are significant pixels.}
-    \label{fig:inference_alt_empirical_z_image}
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_histo_null.eps}
-        \caption{Histogram and empirical null}
-        \label{fig:inference_alt_empirical_z_histogram}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_p_values.eps}
-        \caption{Ordered $p$-values}
-        \label{fig:inference_alt_empirical_z_p_values}
-    \end{subfigure}
-    }
-    \caption{Histogram and $p$-values, corrected using the empirical null, of the test statistics taken from the sub-sample.}
-\end{figure}
-
-The BH procedure was conducted, corrected for the empirical null.
-The $p$-values are shown in Figure \ref{fig:inference_alt_empirical_z_p_values}.
-$\input{../tables/alt_empirical_n_sig.txt}$ pixels were significant.
-The significant pixels are shown in red in Figure \ref{fig:inference_alt_empirical_z_image}.
-The majority of the significant pixels are cluster together and highlighting the defect.
-Not all of the defects were tested positive, but a good number of them are.
-This should be enough to raise suspicion in that particular area.
-
-Only a few pixels were falsely tested as positive, however they are typically isolated single pixels.
-Isolated positive pixels should be discarded as they are more than likely to be tested positive by random chance.
-The technician should of improved the resolution of the x-ray apparatus if one is looking for defects, a or two pixel in size, for the given resolution.
-
-Clusters of significant pixels should raise suspicions.
-One could create a binary image, assigning a Boolean value whether that pixel is tested positive or not.
-A binary image filter, such as erode followed by a dilate, can be used to remove isolate significant pixels and emphasise the cluster of significant pixels.
 

### 2019-03-18 reports/thesis/chapters/5_inference.tex
Appendix for inference

@@
 \begin{equation}
-  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
+  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right) + 0.16
   \label{eq:inference_ourruleofthumb}
@@
 \end{equation}
-for $r=0,1,2,3,\cdots$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is
-\begin{equation}
-  \widehat{p}_Z(z)=
+for $r=0,1,2,3,\cdots$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is $\widehat{p}_Z(z)=
   \frac{1}{nh}
   \sum_{i=1}^n\phi\left(
-    \dfrac{z_i-z}{h}
-  \right)
-  \tag{\ref{eq:inference_kernel_density_estimate}}
-\end{equation}
+    \frac{z_i-z}{h}
+  \right) $
 so that the log density is
@@
 Exact properties of these estimators based on the kernel density estimators can be rather complicated.
-For example numerous approximations were needed to show that $\widehat{\sigma}_0$ is an unbiased estimator of $\sigma_0$ to the first order, where higher order terms are functions of $\widehat{\mu}_0 - \mu_0$ and $h$.
-This is shown in Appendix ?.
+For example numerous approximations were needed to show that $\widehat{\sigma}_0^2$ is an unbiased estimator of $\sigma_0^2$ to the first order, where higher order terms are functions of $(\widehat{\mu}_0 - \mu_0)^2$ and $h$.
+This is shown in Appendix \ref{chapter:appendix_expectationNullStdEstimator}.
 

### 2019-03-21 reports/thesis/chapters/5_inference.tex
Corrected setBandwidth in EmpiricalNull.m, added to inference chapter

@@
 
-The variance model, $\widehat{\variance}\left[\text{scan}_{i,j}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample.
+The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample.
 These replicated x-ray images were manually segmented.
@@
 A $z$ statistic too large in magnitude will classify that pixel as a positive result.
-In the hypothesis testing framework \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent $z$ statistic in a different way
+In two-tailed hypothesis testing framework \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent $z$ statistic in a different way
 \begin{equation}
@@
     \caption{$p$-values}
+    \label{fig:inference_inferenceIntro_pvalue}
   \end{subfigure}
@@
 This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test.
-Assumptions used on the hypothesis testing can be relaxed using the empirical null \citep{efron2004large}, which is reviewed here.
+Assumptions used on the hypothesis testing can be relaxed by using the empirical null \citep{efron2004large}, which is reviewed here.
 The empirical null is then extended to an image filter, called the empirical null filter.
@@
 
-In hypothesis testing \cite{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example.
+In two-tailed hypothesis testing \cite{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example.
 A positive result is declared when $p<\alpha$, else it is a negative result.
@@
 For example $n$ pixels can be tested where the $z$ statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$.
-The null hypothesis is $H_{0,i}:\mu_i=0$ and is tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$.
+The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$.
 Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.
@@
 It adapts to the data and choose different sizes for different data.
-The procedure is as follows, the $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$.
+The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$.
 Suppose a size $\alpha$ is provided beforehand.
@@
 For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
+For example in Figure \ref{fig:inference_inferenceIntro_pvalue} the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.
+
 The BH procedure comes from the fact that if all the statistics are null and independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
@@
 The distribution of the $z$ statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$.
-Almost half of the pixels were were tested positive.
-It is questionable whether such number of positive results is sensible, in particular in an area where defects were not expected.
+Almost half of the pixels were tested positive.
+It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.
 
@@
 
-In \citep{efron2004large}, a few assumptions were made in order to obtain the estimators $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Let the test statistic $Z$ have the p.d.f.
+In \cite{efron2004large}, a few assumptions were made in order to obtain the estimators $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Let the test statistic $Z$ have the p.d.f.
 \begin{equation}
@@
   p_{Z|H_0}(z) = 
-  \dfrac{1}{\sqrt{2\pi}\widehat{\sigma}_0}
+  \dfrac{1}{\sqrt{2\pi}\sigma_0}
   \exp\left[
@@
     \left(
-      \dfrac{z-{\mu}_0}{{\sigma}_0}
+      \dfrac{z-{\mu}_0}{\sigma_0}
     \right)^2
@@
 for values of $z$ around the mode.
-Finding the maximum for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution.
-This justifies the use of the mode for the empirical null mean \citep{efron2004large}
+Finding the mode for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution.
+This justify the use of the mode for the empirical null mean \citep{efron2004large}
 \begin{equation}
@@
 \begin{equation}
-  \dfrac{\partial^2}{\partial^2 z} \ln p_{Z}(z) =
+  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) =
   -\dfrac{
@@
 There exist various methods for the empicial null.
-\citep{schwartzman2008empirical} uses Poisson regression on the histogram counts in regions where the null statistics dominate.
-The empirical characteristic function was used in \citep{jin2007estimating}.
+\cite{schwartzman2008empirical} uses Poisson regression on the histogram counts in regions where the null statistics dominate.
+The empirical characteristic function was used in \cite{jin2007estimating}.
 
@@
   \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
-  \caption{The density of the $z$ statistics was estimated using a kernel density estimate. The dot dash lines shows the empirical null distribution.}
+  \caption{The density of the $z$ statistics was estimated using a kernel density estimate.
+The dot dash lines shows the empirical null distribution multiplied by some constant, this is to insulate the two densities have the same curvature at the mode.}
   \label{fig:inference_inferenceSubsample1_densityEstimate}
@@
 
-The mode was found by solving for $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$.
-This cannot be solved in closed form easily and should be done numerically.
+The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$.
+This cannot be solved in closed form easily and was done numerically.
 The  Newton-Raphson method can be used to solve $\hat{p}_Z'(z) = 0$ for $z$.
@@
 
-It was chosen that convergence was met when either 10 update steps were taken or when
-\begin{equation}
-  \log\left|
+A convergence criteria was met when either 10 update steps were taken or when
+\begin{equation}
+  \log\left[\left|
     \left.
@@
   \right|_{z=\widehat{\mu}_0}
-  \right|
+  \right|\right]
   <-5
@@
 
-\subsection{Bandwidth Selection}
+\subsection{Bandwidth Tuning}
 
@@
 \begin{equation}
-  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right) + 0.16
+  h = \left(0.9n^{-1/5}+ 0.16\right) \times\text{min}\left(s_z,\text{IQR}_z/1.34\right) 
   \ .
@@
 
+\afterpage{\clearpage}
+\subsection{Sampling Distribution Experiments}
+
+Various estimators of central tendency and dispersion were compared with the empirical null estimates of the null mean and null standard deviation.
+The empirical sampling distribution of these estimators were observed to look for properties such as bias, variance and robustness.
+The central tendency looked at were the median and mean.
+The dispersions looked at were the median absolute deviation (MAD) around the mode $\times 1.4826$, interquartile range (IQR) $\div 1.349$ and the standard deviation.
+The normalisation constants were used so that the MAD and IQR can be compared directly to the standard deviation.
+
+A dataset of $n = \pi r^2$ standard Normal random variables were simulated to obtain estimates of central tendency and dispersion.
+This was repeated 100 times to obtain a sampling distribution.
+The results are shown in Figures \ref{fig:inference_NullIidMean} and \ref{fig:inference_NullIidStd}.
+The null mean and standard deviation estimations both suffer from high variance, much higher than typical robust estimators such as the median and IQR.
+
+The estimation of the null standard deviation has some positive bias and it was found that this bias is quite sensitive to the bandwidth.
+Further fine tuning on the bandwidth would be required for the empirical null standard deviation to be unbiased.
+For example it appeared there is consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
+The source of bias could come from the fact that the bandwidth was tuned to minimise the mean squared error rather than the squared bias.
+
+To test for robustness, a dataset of $n = \pi r^2$ mixture of Gaussian random variables were simulated with the following distribution: $\normal(0,1)$ with probability $90\%$, $\normal(3,1)$ with probability $10\%$.
+The $\normal(3,1)$ component acts as non-null statistics and robust estimators should be unaffected by it.
+The results are shown in Figures \ref{fig:inference_NullIidMixtureMean} and \ref{fig:inference_NullIidMixtureStd}.
+The empirical null estimators are robust to the non-null component but still suffers from high variance.
+The rest of the estimators were affected by the non-null statistics, making them unsuitable to estimate parameters of the null component.
+
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullMean.eps}
+        \caption{Empirical null mean}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullMean.eps}
+        \caption{Median}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullMean.eps}
+        \caption{Mean}
+      \end{subfigure}
+    }
+  \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample mean.}
+  \label{fig:inference_NullIidMean}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullStd.eps}
+        \caption{Empirical null std.}
+      \end{subfigure}
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullStd.eps}
+        \caption{MAD mode}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullStd.eps}
+        \caption{IQR}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullStd.eps}
+        \caption{Standard deviation}
+      \end{subfigure}
+    }
+  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample variance.}
+  \label{fig:inference_NullIidStd}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullMean.eps}
+        \caption{Empirical null mean}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullMean.eps}
+        \caption{Median}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullMean.eps}
+        \caption{Mean}
+      \end{subfigure}
+    }
+  \caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables.
+The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample mean.}
+  \label{fig:inference_NullIidMixtureMean}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullStd.eps}
+        \caption{Empirical null std.}
+      \end{subfigure}
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullStd.eps}
+        \caption{MAD mode}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullStd.eps}
+        \caption{IQR}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullStd.eps}
+        \caption{Standard deviation}
+      \end{subfigure}
+    }
+  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables.
+The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
+Shown are the sampling distributions from 100 repeats.
+The dotted lines show the 95\% confidence interval for the sample variance.}
+  \label{fig:inference_NullIidMixtureStd}
+\end{figure}
+
+\afterpage{\clearpage}
 \section{Empirical Null Filter}
 
-The empirical null is a good tool for defect detection under model misspecification.
-The empirical null could be used to solve the problem encountered at the start of the chapter.
-Recall that false positives were a problem due to model misspecification because the test statistics were not standard Normal distributed, as seen in Figure \ref{fig:inference_initial_artist_z_histo}.
-However the problem is that looking at the test statistics spatially in Figure \ref{fig:inference_initial_artist_logp_z}, the empirical null varied spatially.
-This is because it looked like the value of the test statistics depended on which surface it is on for example.
-
-One possible solution is to spilt the $z$ image into a grid and conduct inference in each section separately.
+Returning back to the example at the start of the chapter, the empirical null could be used on the histogram shown in Figure \ref{fig:inference_inferenceIntro_histogram}.
+The resulting empirical null distribution is shown in Figure \ref{fig:inference_inferenceSubsampleAll}.
+The empirical null distribution has a very large standard deviation and would test all pixels as negative, this is incorrect.
+
+\begin{figure}[hpt]
+  \centering
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
+    \caption{$z$ statistics}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
+    \caption{Empirical null fitted onto histogram}
+  \end{subfigure}
+  \caption{The resulting $z$ statistics are shown in a).
+The density estimate of the statistics is shown in b).
+The empirical null distribution multiplied by some constant is also plotted in b); this is to illustrate the curvature is the same as the density estimate at the mode.}
+  \label{fig:inference_inferenceSubsampleAll}
+\end{figure}
+
+The problem is that the empirical distribution of the $z$ statistics did not look Normal.
+It appeared that the $z$ statistics varied spatially, suggesting the empirical null varied spatially as well.
+One possible reason is because it looked like the value of the $z$ statistics depended on which surface it was on for example.
+
+One possible extension to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
 There are problems with this though.
 The first problem is that how the grid is overlaid can be arbitrary, for example the grid can be translated to produce different sections.
-Secondly it is not clear how to combine the results from each section \citep{efron2008simultaneous}.
+Secondly it is not clear how to combine the results from each section together \citep{efron2008simultaneous}.
 
 The empirical null filter extends the empirical null to images.
-In this setting, the parameters of the null distribution varies spatially, slowly and smoothly in 2D space.
-Let $Z_{x,y}$ be the test statistic of the pixel at position $(x,y)$ for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$.
-Let each pixel have a test statistic distributed under the null such that
-\begin{equation}
-  Z_{x,y}|H_0\sim\normal\left(
-    \mu_{x,y},\sigma_{0,x,y}^2
-  \right)
-  \ .
-\end{equation}
-Let the hypothesis
-\begin{equation}
-  H_0:\mu_{x,y}=\mu_{0,x,y}
-\end{equation}
-\begin{equation}
-  H_1:\mu_{x,y}\neq\mu_{0,x,y}
-\end{equation}
-be tested for each pixel individually where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively.
-Suppose $Z_{x,y}=z_{x,y}$ were observed for all $x$ and $y$.
+The parameters of the null distribution varies spatially, slowly and smoothly in 2D space.
+Let the test statistic of the pixel at position $(x,y)$ be
+\begin{equation}
+Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{x,y}^2)
+\end{equation}
+for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Define the null hypotheses to be
+\begin{equation}
+  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
+\end{equation}
+which are tested against
+\begin{equation}
+  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
+\end{equation}
  The empirical null filter aims to estimate the parameters $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ for all $x$ and $y$.
-This is so that inference can be done under the empirical null distribution.
 
 The empirical null filter uses the empirical null on neighbouring pixels to estimate the null distribution parameters.
-For example to estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel of radius $r$ is centred at $(x,y)$.
-All the pixels captured in the circular kernel are then used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
+To estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel of radius $r$ was centred at $(x,y)$.
+All the pixels captured by the circular kernel were then used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
 \begin{equation}
@@
     \left(
-      \text{all }z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
+      \text{all }Z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
     \right)
@@
 \end{equation}
-Using these estimates, the test statistics are then corrected using
-\begin{equation}
-  \zeta_{x,y} = 
-  \dfrac{
-    z_{x,y}-\widehat{\mu}_{0,x,y}
+Using these estimates, the test statistics were normalised using
+\begin{equation}
+  T_{x,y} = 
+  \dfrac{
+    Z_{x,y}-\widehat{\mu}_{0,x,y}
   }
@@
 \end{equation}
-and only the corrected test statistics are used in hypothesis testing.
-
-The critical parameter of choice is the kernel radius $r$.
+and only the normalised test statistics were used in hypothesis testing.
+
+The parameter of choice is the kernel radius $r$.
 A $r$ too small will treat defects as the null and will not detect them.
 A $r$ too big can also cause problems as well.
-The empirical null filter does assume the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal.
+The empirical null filter assumes that the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal.
 If $r$ is too big, the kernel will capture far away test statistics with a very different null distribution.
 If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution.
-Furthermore, if $r\rightarrow \infty$, then this is just using the empirical null on all pixels which is, as discussed before, not sensible.
+Furthermore, if $r\rightarrow \infty$, then this is just using the empirical null on all pixels.
 
@@
 }
-\approx
+<
 5\% \text{ to } 10 \%
@@
 
+There exist similar filters, for example the local normalization filter \citep{sage2003teaching, sage2018local} uses a Gaussian filter to obtain $\widehat{\mu}_{0,x,y}$.
+$\widehat{\sigma}_{0,x,y}^2$ was obtained by applying another Gaussian filter on the $\left(z_{x,y}-\widehat{\mu}_{0,x,y}\right)^2$ image.
+The purpose of this filter was to normalise images with uneven illumination.
+The disadvantage of using the local normalization filter for estimating the null parameters is that it uses a Gaussian filter.
+This is a type weighted mean which won't be robust to non-null statistics.
+In addition, the two Gaussian filters can have different radiuses, it is not clear how to set them.
+
+\subsection{Design and Implementation}
+
 The empirical null filter was implemented in an open source software called \texttt{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \texttt{GitHub} \citep{imagej2018rank}.
-This class implemented filters, such as the mean filter and median filter, using a circular kernel and multiple threads, making this a suitable framework for the empirical null filter.
+This class implemented filters, such as the mean filter and median filter, using a circular kernel, making this a suitable framework for the empirical null filter.
 Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \texttt{Fiji} \citep{schindelin2012fiji}, a distribution of \texttt{ImageJ}.
@@
 The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate.
-By products such as the empirical null parameters can be shown after the filtering as well.}
+By-products such as the empirical null parameters can be shown after the filtering as well.}
     \label{fig:inference_fijiGui}
@@
 As a test, the empirical null filter with $r=5$ was used on a \texttt{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
-It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it does verify the filter works on arbitrary images.
+It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it does verify the filter works on arbitrary images with some computational considerations.
 The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all ${x,y}$ could be of interest.
@@
 
-\subsection{Design and Implementation}
-
 When using the the empirical null filter in \texttt{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
-Here the user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $\zeta_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
-The menu also has options for by product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, and quartile filters.
+Here the user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
+The menu also has options for by-product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, and quartile filters.
 Advanced options are available to the user.
@@
 At the start on the far left, an initial value of the median of all the pixels in the kernel is used.
-In addition, various initial values are randomly tried out until a requested number of valid solutions are found, the solution with the gradient closest to zero is used.
+In addition, various initial values were randomly tried out until a requested number of valid solutions are found, the solution with the greatest value of $p_Z(\widehat{\mu}_0)$ was used.
 For the following pixel to the right, the empirical null mean of the neighbouring left pixel is used as a initial point.
@@
 Additional initial values were generated by sampling from the Normal distribution centred on the first initial value and with standard deviation the same as the standard deviation using all pixels in the kernel.
+
+When filtering arbitrary images such as \texttt{bridge.gif}, a few computational considerations were needed.
+\texttt{bridge.gif} is an 8-bit image so values are represented as integers.
+This open up opportunities for the inter-quartile range and the standard deviation to be zero, this caused problems as this set the bandwidth to be zero.
+When the standard deviation is zero, it was set to $0.289$ which corresponds to the standard deviation of a Uniform random variable.
+When the inter-quartile range is zero, the inter-quartile range was set to the standard deviation $\times 1.34$.
+
+When the number of initial values is too few, poor solutions to $\widehat{\mu}_0$ are uncommon which then propagate to the pixel to the right and used as its initial value.
+Poor initial values could cause the Newton-Raphson method to never converge.
+If the Newton-Raphson method failed to converge too many times, the median is used as the new initial value.
+Should it fail too, the program gives up and puts a $\texttt{NaN}$ in that pixel.
 
@@
 
-%\afterpage{\clearpage}
+\afterpage{\clearpage}
 \subsection{Contaminated Experiment}
@@
 
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullMean.eps}
-        \caption{Empirical null}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullMean.eps}
-        \caption{MAD mode null}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullMean.eps}
-        \caption{Mean variance null}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullMean.eps}
-        \caption{Median IQR null}
-      \end{subfigure}
-    }
-  \caption{Different types of central tendency estimators were used on $\pi r^2$ $\normal(0,1)$ random variables.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullStd.eps}
-        \caption{Empirical null}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullStd.eps}
-        \caption{MAD mode null}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullStd.eps}
-        \caption{Mean variance null}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullStd.eps}
-        \caption{Median IQR null}
-      \end{subfigure}
-    }
-  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ $\normal(0,1)$ random variables.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zMean.eps}
-        \caption{Empirical null}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zMean.eps}
-        \caption{MAD mode null}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zMean.eps}
-        \caption{Mean variance null}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zMean.eps}
-        \caption{Median IQR null}
-      \end{subfigure}
-    }
-  \caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators.
-Shown are the mean of the normalised random variables.
-The dotted lines show the 95\% confidence interval for the sample mean.
-The box plots represent 100 repeats of the simulation.}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zStd.eps}
-        \caption{Empirical null}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zStd.eps}
-        \caption{MAD mode null}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zStd.eps}
-        \caption{Mean variance null}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zStd.eps}
-        \caption{Median IQR null}
-      \end{subfigure}
-    }
-  \caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators.
-Shown are the standard deviation of the normalised random variables.
-The dotted lines show the 95\% confidence interval for the sample variance.
-The box plots represent 100 repeats of the simulation.}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zKurtosis.eps}
-        \caption{Empirical null}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zKurtosis.eps}
-        \caption{MAD mode null}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zKurtosis.eps}
-        \caption{Mean variance null}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zKurtosis.eps}
-        \caption{Median IQR null}
-      \end{subfigure}
-    }
-  \caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators.
-Shown are the sample kurtosis of the normalised random variables.
-The dotted lines show the 95\% confidence interval for the sample kurtosis.
-The box plots represent 100 repeats of the simulation.}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullMean.eps}
-        \caption{Empirical null}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullMean.eps}
-        \caption{MAD mode null}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullMean.eps}
-        \caption{Mean variance null}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullMean.eps}
-        \caption{Median IQR null}
-      \end{subfigure}
-    }
-  \caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables.
-The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullStd.eps}
-        \caption{Empirical null}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullStd.eps}
-        \caption{MAD mode null}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullStd.eps}
-        \caption{Mean variance null}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullStd.eps}
-        \caption{Median IQR null}
-      \end{subfigure}
-    }
-  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables.
-The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
-\end{figure}
-
 \begin{figure}[htp]

### 2019-03-21 inference/nulliid/nullIid.m

@@ -1,31 +1,39 @@
 this = NullIidEmpirical();
 this.run();
 this.printResults();
+close all;
 
 this = NullIidMeanVar();
 this.run();
 this.printResults();
+close all;
 
 this = NullIidMedianIqr();
 this.run();
 this.printResults();
+close all;
 
 this = NullIidMadMode();
 this.run();
 this.printResults();
+close all;
 
 this = NullIidMixtureEmpirical();
 this.run();
 this.printResults();
+close all;
 
 this = NullIidMixtureMeanVar();
 this.run();
 this.printResults();
+close all;
 
 this = NullIidMixtureMedianIqr();
 this.run();
 this.printResults();
+close all;
 
 this = NullIidMixtureMadMode();
 this.run();
 this.printResults();
+close all;

### 2019-03-21 inference/scripts/inferenceSubsample.m

@@ -13,8 +13,10 @@ clc;
 clearvars;
 close all;
 
+subsampleExample(1:2000, 1:2000, 'inferenceSubsampleAll'); %whole image
 subsampleExample(1100:1299, 400:599, 'inferenceSubsample1'); %subimage with no defect
 subsampleExample(500:699, 500:699, 'inferenceSubsample2'); %subimage with defect
+
 
 %PARAMETERS:
   %rowSubsample: vector of indicies of rows which indiciate the position of the subimage
@@ -39,6 +41,7 @@ function subsampleExample(rowSubsample, colSubsample, name)
       %null correction
   zSampleImage = zImage(rowSubsample, colSubsample);
   zSampleVector = reshape(zSampleImage,[],1);
+  zSampleVector(isnan(zSampleVector)) = [];
   zTester = ZTester(zSampleImage);
   zTester.doTest();
   zCritical = zTester.getZCritical();
@@ -57,8 +60,9 @@ function subsampleExample(rowSubsample, colSubsample, name)
   saveas(fig, fullfile('reports','figures','inference',strcat(name,'_histogram.eps')),'epsc');
 
   %estimate the empirical null and do the test
-  zTester.estimateNull(0, int32(1351727940));
+  zTester.estimateNull(0, int32(-854868324));
   zTester.doTest();
+  
   zCritical = zTester.getZCritical(); %get the critical boundary
   mu0 = zTester.nullMean; %get the empirical null mean
   sigma0 = zTester.nullStd; %get the empirical null std
@@ -78,9 +82,10 @@ function subsampleExample(rowSubsample, colSubsample, name)
   nullPdfPlot = numel(zSampleVector) * parzen.getDensityEstimate(mu0) * sqrt(2*pi) * sigma0 * ...
       normpdf(xPlot, mu0, sigma0) ;
   plot(xPlot,  nullPdfPlot, 'r-.');
-  legend('density estimate', 'empirical null');
+  legend('density estimate', 'empirical null', 'Location', 'best');
   ylabel('frequency density');
   xlabel('z stat');
+  xlim([min(zSampleVector), max(zSampleVector)]);
   saveas(fig,fullfile('reports','figures','inference',strcat(name,'_densityEstimate.eps')),'epsc');
 
   %SAVE VALUE

### 2019-03-22 reports/thesis/chapters/5_inference.tex
Modified allnull and defectsimulation
ZTester, plot uniform distribution line in p value plot
allNullScript contain scripts
Rename DefectRadius classes
Added to inference chapter

@@
 
-\subsection{Uncontaminated Experiment}
-
-The empirical null filter was demonstrated on an image where each pixel has i.i.d.~$\normal(0,1)$ test statistics.
+\subsection{All-null Experiment}
+
+An experiment was conducted to demonstrate the effects of the empirical null filter on a simulated $256\times 256$ Gaussian image, where all the pixels have value distributed as standard Normal.
+The purpose is to simulate test statistics which are null and ideally no positive results should be detected.
 The test statistics after filtering should preserve its original distribution, or at least close to it.
-An experiment was conducted to investigate the empirical properties when filtering such as an image.
-
-An example of a  $\addNumber{../figures/inference/noContamination/imageSize.txt}\times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering, with a kernel radius of \addNumber{../figures/inference/noContamination/radius.txt}, is shown in Figure \ref{fig:inference_noContamination_images}.
-A quick glance shows little difference, in particular the QQ plot in Figure \ref{fig:inference_noContamination_qq} shows that the post filter test statistics looked reasonably Normal.
-Because the empirical null mean and empirical null standard deviation are random variables with some distribution, the post filtered test statistics will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
+The statistical moments before and after filtering should be the same and were investigated.
+Because the empirical null mean and empirical null standard deviation are random variables with some distribution, the filtered pixels will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
+
+\emph{Contamination} is defined as some smooth and slowly varying function added and/or multiplied to an image.
+When contaminating a Gaussian image, it may cause errors in hypothesis testing if the null distribution was incorrectly specified as standard Normal.
+In this experiment, the contamination was a gradient such that the pixel at position $(x,y)$ have a value distributed as $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_{0,x,y}^2)$ where
+\begin{equation}
+  \mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0) \ ,
+\end{equation}
+$(x_0,y_0)$ is the centre of the image and $\sigma_{0,x,y}=2$ for all $(x,y)$.
+
+A caveat is that some bias to the null variance estimation would be introduced because of the contamination.
+This is because sources of variance captured by the kernel are from $\sigma_{0,x,y}$ and also from the variability of $\mu_{0,x,y}$.
+This can be shown.
+Let $Z_{x,y}$ be the value of the pixels captured by the circular kernel for integer values of $(x,y)$ such that $x^2+y^2\leqslant r$.
+Suppose that $Z_{x,y}\sim\normal(ax+by,c^2\sigma^2)$.
+The calculations of the expectation and variance of $Z_{x,y}$ can be approximated by treating $x$ and $y$ as uniformly distributed within a circle centred at the origin with radius $r$.
+The expectation is $\expectation[Z_{X,Y}] = \expectation\expectation[Z_{X,Y}|X,Y]=0$.
+The variance is given as $\variance[Z_{X,Y}] = \expectation\variance[Z_{X,Y}|X,Y] + \variance\expectation[Z_{X,Y}|X,Y]$.
+From the distribution of $Z_{X,Y}$, $\expectation\variance[Z_{X,Y}|X,Y] = c^2\sigma^2$ and $\variance\expectation[Z_{X,Y}|X,Y]=\variance[aX+bY]$.
+This is worked out to be
+\begin{align}
+\variance[aX+bY] &= \dfrac{1}{\pi r^2}\int_{\rho=0}^{\rho=r}\int_{\theta=0}^{\theta=2\pi}
+\rho^3(a\cos\theta + b\sin\theta)^2 \diff \theta \diff \rho
+\nonumber\\
+& = \dfrac{1}{4}(a^2+b^2)r^2
+\end{align}
+thus
+\begin{equation}
+\variance[Z_{X,Y}] = \dfrac{1}{4}(a^2+b^2)r^2 + c^2\sigma^2 \ .
+\end{equation}
+This shows that when estimating the null variance on a contaminated Gaussian image, there may be a $(a^2+b^2)r^2/4$ bias.
+If the contamination is slowly varying, that is $a$ and $b$ are small, then the bias should be small.
+
+\begin{figure}[p]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_beforeFilter.eps}
+    \caption{Unfiltered}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_afterFilter.eps}
+    \caption{Filtered}
+    \label{fig:inference_allNullGaussianScript_afterFilter}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullMean.eps}
+    \caption{Empirical null mean}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullStd.eps}
+    \caption{Empirical null std}
+  \end{subfigure}
+  }
+  \caption{A $256\times 256$ Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null std.}
+  \label{fig:inference_allNullGaussianScript}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_beforeFilter.eps}
+    \caption{Unfiltered}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_afterFilter.eps}
+    \caption{Filtered}
+    \label{fig:inference_allNullPlaneScript_afterFilter}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullMean.eps}
+    \caption{Empirical null mean}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullStd.eps}
+    \caption{Empirical null std}
+  \end{subfigure}
+  }
+  \caption{A $256\times 256$ contaminated Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null std.}
+  \label{fig:inference_allNullPlaneScript}
+\end{figure}
 
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/noContamination/allNullGaussianqq.eps}
-  \caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
-  \label{fig:inference_noContamination_qq}
-\end{figure}
-
-\begin{figure}[pht]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussianunfiltered.eps}
-    \caption{Unfiltered}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussianfiltered.eps}
-    \caption{Filtered}
-  \end{subfigure}
-  }
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussiannullmean.eps}
-    \caption{Empirical null mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/noContamination/allNullGaussiannullstd.eps}
-    \caption{Empirical null std}
-  \end{subfigure}
-  }
-  \caption{A $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.
-Also shown are the empirical null mean and empirical null std.}
-  \label{fig:inference_noContamination_images}
-\end{figure}
-
-In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$ was simulated.
-The sample mean and sample variance of the post filtered test statistics were recorded.
-This was repeated \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} times by simulating another Gaussian image.
-Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_radius1.txt}$ to $r = \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_radiusend.txt}$ were investigated.
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_pValue.eps}
+    \caption{No contamination}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_pValue.eps}
+    \caption{With contamination}
+  \end{subfigure}
+  \caption{$p$-values of values from a filtered $256\times 256$ Gaussian image with kernel radius 20.
+In b), the Gaussian image was contaminated before filtering.
+The $p$-values were obtained from the images in Figures \ref{fig:inference_allNullGaussianScript_afterFilter} and \ref{fig:inference_allNullPlaneScript_afterFilter}.
+The dotted lines shows the $p$-values if they were uniformly distributed.}
+  \label{fig:inference_allNull_pValues}
+\end{figure}
+
+An example of a Gaussian image with/without contamination before/after filtering are shown in Figures \ref{fig:inference_allNullGaussianScript} and \ref{fig:inference_allNullPlaneScript}.
+In the contaminated example.
+the filter managed to estimate the null mean, picking up the gradient.
+This enabled the normalised image to look flat to remove the contamination.
+The $p$-values after filtering are shown in Figure \ref{fig:inference_allNull_pValues}.
+A quick inspection suggest that the filtered pixels looked reasonably Normal for this particular example.
+
+For a given kernel radius $r$, 100 different Gaussian images were filtered to investigate the within image mean, standard deviation and kurtosis of the filtered statistics.
+Various other filters were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter.
+They use different estimators to estimate the null parameters as their name suggest, Table \ref{table:inference_nullFilters} clarifies them.
+
+\begin{table}[ht]
+  \centering
+  \begin{tabular}{c|c|c}
+    Filters&Null mean&Null Standard deviation\\\hline
+    MAD mode null&Mode&MAD around the mode $\times1.4826$\\
+    Median IQR null&Median&IQR $\div1.349$\\
+    Mean variance null&Mean&Standard deviation
+  \end{tabular}
+  \caption{Various filters using different estimators to estimate the null parameters are described here.}
+  \label{table:inference_nullFilters}
+\end{table}
 
@@
   \centering
+  \centerline{
   \begin{subfigure}[b]{0.49\textwidth}
     \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_mean.eps}
-    \caption{Post filter sample mean}
-  \end{subfigure}
+    \caption{Empirical Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_mean.eps}
+    \caption{MAD Mode Null}
+  \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_mean.eps}
+    \caption{Median IQR Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_mean.eps}
+    \caption{Mean Var Null}
+  \end{subfigure}
+  }
+  \caption{The within image sample \emph{mean} of the test statistics in a filtered Gaussian image of size $256\times256$.
+The box plots summarise the 100 repeats of the experiment.
+The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \label{fig:inference_AllNullGaussian_mean}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \centerline{
   \begin{subfigure}[b]{0.49\textwidth}
     \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_variance.eps}
-    \caption{Post filter sample variance}
-  \end{subfigure}
-  \caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
-The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
-  \label{fig:inference_allnullgaussian}
-\end{figure}
-
-The results are shown in Figure \ref{fig:inference_allnullgaussian}.
-The post filter sample test statistic means do agree with zero as expected.
-There is some bias with the post filter sample test statistics variances, it was found that this was sensitive to the bandwidth parameters for the kernel density estimate.
-The large sampling error can come from a number of sources.
-The empirical null parameters are random variables, thus correction using these can increase the variance.
-Also pixel to pixel correlation can be introduced as the empirical null parameters are functions of neighbouring pixels, this can contribute to the sample error.
-
-It should be noted that the slight decrease of the post filter test statistic will decrease the sensitivity of the hypothesis test ever so slightly.
+    \caption{Empirical Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_variance.eps}
+    \caption{MAD Mode Null}
+  \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_variance.eps}
+    \caption{Median IQR Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_variance.eps}
+    \caption{Mean Var Null}
+  \end{subfigure}
+  }
+  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered Gaussian image of size $256\times256$.
+The box plots summarise the 100 repeats of the experiment.
+The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \label{fig:inference_AllNullGaussian_var}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_kurtosis.eps}
+    \caption{Empirical Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_kurtosis.eps}
+    \caption{MAD Mode Null}
+  \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_kurtosis.eps}
+    \caption{Median IQR Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_kurtosis.eps}
+    \caption{Mean Var Null}
+  \end{subfigure}
+  }
+  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered Gaussian image of size $256\times256$.
+The box plots summarise the 100 repeats of the experiment.
+The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \label{fig:inference_AllNullGaussian_kurtosis}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
+    \caption{Empirical Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_mean.eps}
+    \caption{MAD Mode Null}
+  \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_mean.eps}
+    \caption{Median IQR Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_mean.eps}
+    \caption{Mean Var Null}
+  \end{subfigure}
+  }
+  \caption{The within image sample \emph{mean} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
+The box plots summarise the 100 repeats of the experiment.
+The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \label{fig:inference_AllNullPlane_mean}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
+    \caption{Empirical Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_variance.eps}
+    \caption{MAD Mode Null}
+  \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_variance.eps}
+    \caption{Median IQR Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_variance.eps}
+    \caption{Mean Var Null}
+  \end{subfigure}
+  }
+  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
+The box plots summarise the 100 repeats of the experiment.
+The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \label{fig:inference_AllNullPlane_var}
+\end{figure}
+
+\begin{figure}[htp]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_kurtosis.eps}
+    \caption{Empirical Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_kurtosis.eps}
+    \caption{MAD Mode Null}
+  \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_kurtosis.eps}
+    \caption{Median IQR Null}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_kurtosis.eps}
+    \caption{Mean Var Null}
+  \end{subfigure}
+  }
+  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
+The box plots summarise the 100 repeats of the experiment.
+The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \label{fig:inference_AllNullPlane_kurtosis}
+\end{figure}
+
+The results for the filtered images are shown in Figures \ref{fig:inference_AllNullGaussian_mean}, \ref{fig:inference_AllNullGaussian_var} and \ref{fig:inference_AllNullGaussian_kurtosis}.
+For the filtered \emph{contaminated} images, they are in Figures \ref{fig:inference_AllNullPlane_mean}, \ref{fig:inference_AllNullPlane_var} and \ref{fig:inference_AllNullPlane_kurtosis}.
+The filtered test statistic means did agree with zero as expected, showing that the filters centred the statistics when normalising.
+When using the empirical null filter, there was some negative bias with the standard deviation of the filtered test statistics.
+The negative bias comes from the positive bias when estimating the null standard deviation.
+
+When filtering the contaminated image, all estimators suffered from negative bias in the standard deviation of the filtered statistics, in particular when the kernel radius increases.
+This is shown in Figure \ref{fig:inference_AllNullPlane_var}.
+As discussed before, the kernel captures the variation due to the contamination and this adds intrinsic bias to the null variance.
+As a result, this adds bias when estimating the null variance.
+
+The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} shows that the empirical null filter can cause the filtered statistics to have heavy tails, in particular for small kernel radiuses.
+This could cause problems in hypothesis testing because heavy tails could be misinterpreted as contribution from non-null statistics.
+The source of the kurtosis inflation is from the estimation of the null standard deviation.
+This can be seen by comparing the empirical null filter with the MAD mode null filter because the only difference between the two filters is in the estimation of the null standard deviation.
 
@@
 \subsection{Contaminated Experiment}
-
-Consider a $\addNumber{../figures/inference/contamination/imageSize.txt}\times \addNumber{../figures/inference/contamination/imageSize.txt}$ Gaussian image with some contamination.
-For example let the pixels be $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where the null mean is a linear function
-\begin{equation}
-\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)
-\end{equation}
-where $(x_0,y_0)$ is the centre of the image and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-There are no defects or non-null pixels defined here, therefore any positive detections are false.
 
@@
 A mismatch in the variance will increase or decrease the sensitivity of the test, a larger variance would increase the sensitivity.
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/contamination/allNullPlaneqq.eps}
-  \caption{QQ plot of the test statistics of a filtered $\addNumber{../figures/inference/noContamination/imageSize.txt} \times \addNumber{../figures/inference/noContamination/imageSize.txt}$ contaminated Gaussian image after filtering with kernel radius \addNumber{../figures/inference/noContamination/radius.txt}.}
-  \label{fig:inference_contamination_qq}
-\end{figure}
-
-\begin{figure}[pht]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlaneunfiltered.eps}
-        \caption{Unfiltered}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanefiltered.eps}
-        \caption{Filtered}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanenullmean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/contamination/allNullPlanenullstd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{A $\addNumber{../figures/inference/contamination/imageSize.txt} \times \addNumber{../figures/inference/contamination/imageSize.txt}$ contaminated Gaussian image before and after filtering with kernel radius \addNumber{../figures/inference/contamination/radius.txt}.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
-Also shown are the empirical null mean and empirical null std.}
-  \label{fig:inference_contamination_images}
-\end{figure}
 
@@
 Another caveat is that the sensitivity may not be exactly preserved after filtering.
-
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
-    \caption{Post filter sample mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
-    \caption{Post filter sample variance}
-  \end{subfigure}
-  \caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/AllNullPlaneEmpirical_nrepeat.txt} repeats of the experiment.
-The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
-  \label{fig:inference_allnullplane}
-\end{figure}
 
@@
 In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering.
-The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}.
-Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
+The filter used a kernel radius Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
 The salt defect has density $\pi_1 = 0.1$.
@@
 In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering.
-The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}.
-Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
+The filter used a kernel radius  Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
 The salt defect has density $\pi_1 = 0.1$.
@@
 In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
-The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}.
+The filter used a kernel radius .
 Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
@@
   \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_mean.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_mean.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_mean.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_mean.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The sample mean of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
-The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_variance.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_variance.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_variance.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_variance.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The sample std of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
-The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_kurtosis.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_kurtosis.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_kurtosis.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_kurtosis.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The sample kurtosis of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment.
-The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_mean.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_mean.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_mean.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The sample mean test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-The box plots summarise the 100 repeats of the experiment.
-The dotted lines show the critical region at the 5\% level using standard tests for the sample mean and sample variance, assuming independence.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_variance.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_variance.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_variance.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The sample standard deviation test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-The box plots summarise the 100 repeats of the experiment.
-The dotted lines show the critical region at the 5\% level using standard tests for the sample mean and sample variance, assuming independence.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_kurtosis.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_kurtosis.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_kurtosis.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_kurtosis.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The sample kurtosis test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$.
-The box plots summarise the 100 repeats of the experiment.
-The dotted lines show the critical region at the 5\% level using standard tests for the sample mean and sample variance, assuming independence.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
   \begin{subfigure}[b]{0.49\textwidth}

### 2019-03-22 inference/allnull/allNullGaussian.m

@@ -1,66 +1,0 @@
-%SCRIPT: ALL NULL GAUSSIAN
-%Filters a Gaussian image
-%Shows the image before and after filtering
-%Shows the empirical null mean and std image
-%Plots the qq plot of the post filter greyvalues
-
-clc;
-clearvars;
-close all;
-
-directory = fullfile('reports','figures','inference','noContamination');
-randStream = RandStream('mt19937ar','Seed',uint32(3499211588)); %instantise a rng
-
-imageSize = 256; %size of the image
-radius = 20; %radius of kernel
-
-%save the imageSize and radius
-file_id = fopen(fullfile(directory,'imageSize.txt'),'w');
-fprintf(file_id,'%d',imageSize);
-fclose(file_id);
-file_id = fopen(fullfile(directory,'radius.txt'),'w');
-fprintf(file_id,'%d',radius);
-fclose(file_id);
-
-image = randStream.randn(imageSize,imageSize); %create gaussian image
-filter = EmpiricalNullFilter(radius); %filter it
-filter.setNInitial(3);
-filter.filter(image);
-
-%get the empirical null and the filtered image
-imageFiltered = filter.getFilteredImage();
-nullMean = filter.getNullMean();
-nullStd = filter.getNullStd();
-
-%plot the image before filtering
-fig = LatexFigure.sub();
-imagePlot = ImagescSignificant(image);
-imagePlot.setCLim([-3,3]);
-imagePlot.plot();
-saveas(fig,fullfile(directory, 'allNullGaussianunfiltered.eps'),'epsc');
-
-%plot the image after filtering
-fig = LatexFigure.sub();
-imagePlot = ImagescSignificant(imageFiltered);
-imagePlot.setCLim([-3,3]);
-imagePlot.plot();
-saveas(fig,fullfile(directory, 'allNullGaussianfiltered.eps'),'epsc');
-
-%qq plot of the image after filtering
-fig = LatexFigure.sub();
-qqplot(reshape(imageFiltered,[],1));
-title('');
-ylabel('quantiles of filtered pixels');
-xlabel('standard normal quantiles');
-saveas(fig,fullfile(directory, 'allNullGaussianqq.eps'),'epsc');
-
-%empirical null plot
-fig = LatexFigure.sub();
-imagePlot = ImagescSignificant(nullMean);
-imagePlot.plot();
[…]

### 2019-03-22 inference/allnull/allNullScript.m

@@ -1,0 +1,81 @@
+%ALL NULL GAUSSIAN SCRIPT
+%Filters a image
+%Shows the image before and after filtering
+%Shows the empirical null mean and std image
+%Plots the p values of the post filter greyvalues
+
+clc;
+clearvars;
+close all;
+
+imageSize = 256;
+
+%=====ALL NULL GAUSSIAN=====%
+randStream = RandStream('mt19937ar','Seed',uint32(3499211588)); %instantise a rng
+image = randStream.randn(imageSize,imageSize); %create gaussian image
+allNullExample(image, 'allNullGaussianScript');
+
+%=====ALL NULL PLANE=====%
+%contaminate the image
+randStream = RandStream('mt19937ar','Seed',uint32(581365657)); %instantise a rng
+trueNullStd = 2;
+trueNullMeanGrad = [0.01, 0.01];
+defectSimulator = PlaneMult(randStream, trueNullMeanGrad, trueNullStd);
+image = defectSimulator.getDefectedImage([imageSize, imageSize]);
+allNullExample(image, 'allNullPlaneScript');
+
+%FUNCTION: ALL NULL EXAMPLE
+%PARAMETERS:
+  %image: to be filtered
+  %name: prefix of the file saved containing the figures
+function allNullExample(image, name)
+  
+  directory = fullfile('reports','figures','inference');
+  
+  radius = 20;
+  filter = EmpiricalNullFilter(radius); %filter it
+  filter.filter(image);
+  
+  %get the empirical null and the filtered image
+  imageFiltered = filter.getFilteredImage();
+  nullMean = filter.getNullMean();
+  nullStd = filter.getNullStd();
+  clim = [min(min(imageFiltered)), max(max(imageFiltered))];
+  stdClim = [0, clim(2)];
+  
+  %plot the image before filtering
+  fig = LatexFigure.sub();
+  imagePlot = ImagescSignificant(image);
+  imagePlot.setCLim(clim);
+  imagePlot.plot();
+  saveas(fig,fullfile(directory, strcat(name,'_beforeFilter.eps')),'epsc');
+  
+  %plot the image after filtering
+  fig = LatexFigure.sub();
+  imagePlot = ImagescSignificant(imageFiltered);
+  imagePlot.setCLim(clim);
+  imagePlot.plot();
[…]

### 2019-03-22 inference/defectsimulation/DefectRadius.m

@@ -5,7 +5,7 @@
     %recover the image from contamination. These 2 images are then used to do a hypothesis test to
     %find the defects. The type 1 error, type 2 error, fdr and area of roc are recorded. The
     %experiment is repeated by producing another image.
-classdef Experiment_DefectRadius < Experiment
+classdef DefectRadius < Experiment
 
   properties (SetAccess = protected)
     
@@ -34,8 +34,8 @@ classdef Experiment_DefectRadius < Experiment
   methods (Access = public)
     
     %CONSTRUCTOR
-    function this = Experiment_DefectRadius(experimentName)
-      this@Experiment(experimentName);
+    function this = DefectRadius()
+      this@Experiment();
     end
     
     %METHOD: PRINT RESULTS
@@ -149,7 +149,7 @@ classdef Experiment_DefectRadius < Experiment
         for iRepeat = 1:this.nRepeat
           
           %get the defected image pre/post contamination
-          [imagePostCont, isAltImage, imagePreCont] = ...
+          [imagePostCont, isNonNullImage, imagePreCont] = ...
               defectSimulator.getDefectedImage([this.imageSize, this.imageSize]);
 
           %filter it
@@ -168,34 +168,34 @@ classdef Experiment_DefectRadius < Experiment
           zTesterPostCont.doTest();
 
           %get the roc area
-          [~, ~, this.rocAreaArray(iRepeat, iRadius, 1)] = roc(imagePreCont, isAltImage, 100);
-          [~, ~, this.rocAreaArray(iRepeat, iRadius, 2)] = roc(imageFiltered, isAltImage, 100);
+          [~, ~, this.rocAreaArray(iRepeat, iRadius, 1)] = roc(imagePreCont, isNonNullImage, 100);
+          [~, ~, this.rocAreaArray(iRepeat, iRadius, 2)] = roc(imageFiltered, isNonNullImage, 100);
           
           %get the error rates fdrArray
           
           this.type1ErrorArray(iRepeat, iRadius, 1) = ...
-              sum(zTesterPreCont.sig_image(~isAltImage)) / sum(sum(~isAltImage));
+              sum(zTesterPreCont.positiveImage(~isNonNullImage)) / sum(sum(~isNonNullImage));
           this.type1ErrorArray(iRepeat, iRadius, 2) = ...
-              sum(zTesterPostCont.sig_image(~isAltImage)) / sum(sum(~isAltImage));
[…]

### 2019-03-22 inference/defectsimulation/DefectRadiusSquare.m

@@ -1,4 +1,4 @@
-classdef Experiment_DefectRadiusSquare < Experiment_DefectRadius
+classdef DefectRadiusSquare < DefectRadius
   
   properties (SetAccess = private)
     defectSize = 30;
@@ -6,8 +6,8 @@ classdef Experiment_DefectRadiusSquare < Experiment_DefectRadius
   
   methods (Access = public)
     
-    function this = Experiment_DefectRadiusSquare()
-      this@Experiment_DefectRadius('Experiment_DefectRadiusSquare');
+    function this = DefectRadiusSquare()
+      this@DefectRadius();
     end
     
   end
@@ -15,7 +15,7 @@ classdef Experiment_DefectRadiusSquare < Experiment_DefectRadius
   methods (Access = protected)
     
     function setup(this)
-      this.setup@Experiment_DefectRadius(uint32(3826400333));
+      this.setup@DefectRadius(uint32(3826400333));
     end
     
     function defectSimulator = getDefectSimulator(this)

### 2019-03-23 reports/thesis/chapters/5_inference.tex
Put defectExample script together

@@
 \afterpage{\clearpage}
-\subsection{Contaminated Experiment}
+\subsection{Detecting Defects Experiment}
 
@@
 Another caveat is that the sensitivity may not be exactly preserved after filtering.
-
-\subsection{Contaminated Defect Experiment}
 
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imagePreContaminated.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageFiltered.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_nullStd.eps}
         \caption{Empirical null std}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imagePreContaminated.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageFiltered.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_nullStd.eps}
         \caption{Empirical null std}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imagePreContaminated.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageFiltered.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imagePreContaminated.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageFiltered.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullStd.eps}
-        \caption{Empirical null std}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_nullMean.eps}
+        \caption{Empirical null mean}
       \end{subfigure}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_roc.eps}
         \caption{Dust defect $\pi_1=0.1$, $r=20$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_roc.eps}
         \caption{5 pixels thick line defect, $r=20$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_roc.eps}
         \caption{$30\times 30$ square defect, $r=20$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_roc.eps}
         \caption{$30\times 30$ square defect, $r=40$}

### 2019-03-23 inference/defectsimulation/defectLine.m

@@ -1,32 +1,0 @@
-%SCRIPT: DEFECT LINE
-%Plot Gaussian image with line defect with plane contimation
-%Plot empirical null mean
-%Plot empirical null std
-%Plot roc curve before and after contimation
-%For the z_alpha=2 level, print:
-  %type 1 error
-  %type 2 error
-  %area under ROC
-
-clc;
-clearvars;
-close all;
-
-directory = fullfile('reports','figures','inference','defectsimulation');
-prefix = 'defectLine';
-randStream = RandStream('mt19937ar','Seed',uint32(2816384857)); %instantise a rng
-
-imageSize = 256;
-radius = 20; %kernel radius
-trueNullStd = 2; %multiplier in the contimation
-trueNullMeanGrad = [0.01, 0.01]; %gradient of contimation
-lineThickness = 5;
-%distribution parameters of the alt distribution
-altMean = 3;
-altStd = 1;
-
-defectSimulator = PlaneMultLine(randStream, trueNullMeanGrad, trueNullStd, altMean, altStd, ...
-    lineThickness);
-defectExample = DefectExample(randStream);
-defectExample.setPlotDefectNullStd(true);
-defectExample.plotExample(defectSimulator, imageSize, radius, directory, prefix);

### 2019-03-23 inference/defectsimulation/defectSquare.m

@@ -1,36 +1,0 @@
-%SCRIPT: DEFECT SQUARE
-%Using non-sensible kernel size
-%Plot Gaussian image with square defect with plane contimation
-%Plot empirical null mean
-%Plot empirical null std
-%Plot roc curve before and after contimation
-%For the z_alpha=2 level, print:
-  %type 1 error
-  %type 2 error
-  %area under ROC
-
-clc;
-clearvars;
-close all;
-
-directory = fullfile('reports','figures','inference','defectsimulation');
-prefix = 'defectSquare';
-randStream = RandStream('mt19937ar','Seed',uint32(4120988592)); %instantise a rng
-
-imageSize = 256;
-radius = 20; %kernel radius
-trueNullStd = 2; %multiplier in the contimation
-trueNullMeanGrad = [0.01, 0.01]; %gradient of contimation
-defectSize = 30; %size of the square defect
-%distribution parameters of the alt distribution
-altMean = 3;
-altStd = 1;
-
-defectSimulator = PlaneMultSquare(randStream, trueNullMeanGrad, trueNullStd, defectSize, ...
-    altMean, altStd);
-%for a large altMean, the empirical null filter requires more initial values to jump to the other
-%mode
-defectExample = DefectExample(randStream);
-defectExample.setNInitial(10);
-defectExample.setCLimNullMean([-2.5, 5]);
-defectExample.plotExample(defectSimulator, imageSize, radius, directory, prefix);

### 2019-03-23 reports/thesis/chapters/5_inference.tex
Relocate inference figures

@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullMean.eps}
         \caption{Median}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullMean.eps}
         \caption{Mean}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
         \caption{Empirical null std.}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMadMode_nullStd.eps}
         \caption{MAD mode}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullStd.eps}
         \caption{IQR}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullStd.eps}
         \caption{Standard deviation}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullMean.eps}
         \caption{Median}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullMean.eps}
         \caption{Mean}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
         \caption{Empirical null std.}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMadMode_nullStd.eps}
         \caption{MAD mode}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullStd.eps}
         \caption{IQR}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullStd.eps}
         \caption{Standard deviation}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_mean.eps}
     \caption{Empirical Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_mean.eps}
     \caption{MAD Mode Null}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_mean.eps}
     \caption{Median IQR Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_mean.eps}
     \caption{Mean Var Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_variance.eps}
     \caption{Empirical Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_variance.eps}
     \caption{MAD Mode Null}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_variance.eps}
     \caption{Median IQR Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_variance.eps}
     \caption{Mean Var Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_kurtosis.eps}
     \caption{Empirical Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_kurtosis.eps}
     \caption{MAD Mode Null}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_kurtosis.eps}
     \caption{Median IQR Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_kurtosis.eps}
     \caption{Mean Var Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_mean.eps}
     \caption{Empirical Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_mean.eps}
     \caption{MAD Mode Null}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_mean.eps}
     \caption{Median IQR Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_mean.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_mean.eps}
     \caption{Mean Var Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_variance.eps}
     \caption{Empirical Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_variance.eps}
     \caption{MAD Mode Null}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_variance.eps}
     \caption{Median IQR Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_variance.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_variance.eps}
     \caption{Mean Var Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_kurtosis.eps}
     \caption{Empirical Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_kurtosis.eps}
     \caption{MAD Mode Null}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_kurtosis.eps}
     \caption{Median IQR Null}
@@
   \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_kurtosis.eps}
+    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_kurtosis.eps}
     \caption{Mean Var Null}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_roc.eps}
         \caption{ROC area}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type1.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_type1.eps}
         \caption{Type 1 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_type2.eps}
         \caption{Type 2 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_fdr.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_fdr.eps}
         \caption{FDR}
@@
 The FDR was controlled at the 5\% level.
-The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
+The box plot summarise the 100 repeats of the experiment.}
 \end{figure}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_roc.eps}
         \caption{ROC area}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type1.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_type1.eps}
         \caption{Type 1 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_type2.eps}
         \caption{Type 2 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_fdr.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_fdr.eps}
         \caption{FDR}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
         \caption{ROC area}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_type1.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
         \caption{Type 1 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_type2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
         \caption{Type 2 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_fdr.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
         \caption{FDR}
@@
 The FDR was controlled at the 5\% level.
-The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
+The box plot summarise the 100 repeats of the experiment.}
   \label{fig:inference_DefectSimulationDust}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_roc.eps}
         \caption{ROC area}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_type1.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_type1.eps}
         \caption{Type 1 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_type2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_type2.eps}
         \caption{Type 2 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_fdr.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_fdr.eps}
         \caption{FDR}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_roc.eps}
         \caption{ROC area}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_type1.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type1.eps}
         \caption{Type 1 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_type2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type2.eps}
         \caption{Type 2 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_fdr.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_fdr.eps}
         \caption{FDR}
@@
 The dotted lines show the 95\% percentile when the hypothesis test was done on the uncontaminated image.
-Defected pixels have the distribution $\normal(\addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_altMean.txt},1)$.
+Defected pixels have the distribution $\normal(3,1)$.
 The line defect is 5 pixels thick.
@@
 The FDR was controlled at the $2\sigma$ level.
-The box plot summarise the \addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusLine_nRepeat.txt} repeats of the experiment.}
+The box plot summarise the 100 repeats of the experiment.}
   \label{fig:inference_Experiment_DefectRadiusLine}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
         \caption{ROC area}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_type1.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
         \caption{Type 1 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_type2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
         \caption{Type 2 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_fdr.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
         \caption{FDR}
@@
 The dotted lines show the 95\% percentile when the hypothesis test was done on the uncontaminated image.
-Defected pixels have the distribution $\normal(\addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_altMean.txt},1)$.
+Defected pixels have the distribution $\normal(3,1)$.
 The square defect is $30\times 30$ pixels in size.
@@
 The FDR was controlled at the $2\sigma$ level.
-The box plot summarise the \addNumber{../figures/inference/defectsimulation/Experiment_DefectRadiusSquare_nRepeat.txt} repeats of the experiment.}
+The box plot summarise the 100 repeats of the experiment.}
   \label{fig:inference_Experiment_DefectRadiusSquare}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_z.eps}
-        \caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_z.eps}
-        \caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2.txt}$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_z.eps}
-        \caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_z.eps}
-        \caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4.txt}$}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$}
       \end{subfigure}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_sig.eps}
         \caption{Image with sig.~pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$.
 a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_sig.eps}
         \caption{Image with sig.~pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$.
 a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_sig.eps}
         \caption{Image with sig.~pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$.
 a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_sig.eps}
         \caption{Image with sig.~pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$.
 a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
@@
 Figure \ref{fig:inference_sep16120deg_zfiltered} shows the filtered $z$ images for various kernel radiuses.
-For $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image is smooth and treated everything as the null.
+For $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image is smooth and treated everything as the null.
 When a large enough radius was used, the defects are highlighted by the higher $z$ statistics and everything else remain unchanged.
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/cornerSelect.png}
+        \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.png}
         \caption{$z$ image with kernel of radius $r=120$}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/cornerSelectHisto.png}
+        \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHisto.png}
         \caption{Histogram of $z$ in the kernel}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/defectdetect/segment.JPG}
+  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
   \caption{The $z$ was segmented further into 7 segments.}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
         \caption{Image with sig.~pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4.txt}$.
+  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$.
 a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
@@
 
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValuePreContaminated.eps}
-    \caption{Before contamination}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValueFiltered.eps}
-    \caption{After filtering}
-  \end{subfigure}
-  \caption{$p$ values when doing hypothesis testing on a $256 \times 256$ dust defect Gaussian image.
-In b), the image was contaminated and then filtered using the \emph{empirical} null filter kernel radius 20.
-Defected pixels have the distribution $\normal(1,1)$.
-The salt defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The critical region was chosen to control the FDR at 5\%.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValuePreContaminated2.eps}
-    \caption{Before contamination}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_pValueFiltered2.eps}
-    \caption{After filtering}
-  \end{subfigure}
-  \caption{$p$ values when doing hypothesis testing on a $256 \times 256$ dust defect Gaussian image.
-In b), the image was contaminated and then filtered using the \emph{MAD mode} null filter kernel radius 20.
-Defected pixels have the distribution $\normal(1,1)$.
-The salt defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The critical region was chosen to control the FDR at 5\%.}
-\end{figure}
-
 \section{Conclusion}

### 2019-03-23 inference/allnull/AllNull.m

@@ -60,7 +60,7 @@ classdef AllNull < Experiment
     function printResults(this)
       
       %where to save the figures
-      directory = fullfile('reports','figures','inference','allnull');
+      directory = fullfile('reports','figures','inference');
       
       %save properties of this experiment to txt
       

### 2019-03-23 inference/defectDetect/defectdetect.m

@@ -1,5 +1,9 @@
 this = DefectDetectSep16120deg();
 this.run();
+this.printResults();
+close all;
 
 this = DefectDetectSubRoiSep16120deg();
 this.run();
+this.printResults();
+close all;

### 2019-03-23 inference/defectsimulation/DefectRadius.m

@@ -43,18 +43,7 @@ classdef DefectRadius < Experiment
     %Plots pre/post contamination results on the same graph
     function printResults(this)
       
-      directory = fullfile('reports','figures','inference','defectsimulation');
-      
-      %print alt mean
-      fildId = fopen(fullfile(directory,strcat(this.experiment_name,'_altMean.txt')),'w');
-      fprintf(fildId,'%d',this.altMean);
-      fclose(fildId);
-      
-      %print nRepeat
-      fildId = fopen(fullfile(directory,strcat(this.experiment_name,'_nRepeat.txt')),'w');
-      fprintf(fildId,'%d',this.nRepeat);
-      fclose(fildId);
-      
+      directory = fullfile('reports','figures','inference');
       offset = 1;
       
       %plot roc area vs alt mean
@@ -67,8 +56,8 @@ classdef DefectRadius < Experiment
       ax.XLim(1) = this.radiusArray(1) - offset;
       ax.XLim(2) = this.radiusArray(end) + offset;
       oracleInterval = quantile(reshape(this.rocAreaArray(:,:,1),[],1), [0.025, 0.975]);
-      plot(ax.XLim, [oracleInterval(1), oracleInterval(1)], 'k--', 'LineWidth', 2);
-      plot(ax.XLim, [oracleInterval(2), oracleInterval(2)], 'k--', 'LineWidth', 2);
+      plot(ax.XLim, [oracleInterval(1), oracleInterval(1)], 'k--');
+      plot(ax.XLim, [oracleInterval(2), oracleInterval(2)], 'k--');
       xlabel('kernel radius');
       ylabel('roc area');
       saveas(fig,fullfile(directory, strcat(this.experiment_name,'_roc.eps')),'epsc');
@@ -83,8 +72,8 @@ classdef DefectRadius < Experiment
       ax.XLim(1) = this.radiusArray(1) - offset;
       ax.XLim(2) = this.radiusArray(end) + offset;
       oracleInterval = quantile(reshape(this.type1ErrorArray(:,:,1),[],1), [0.025, 0.975]);
-      plot(ax.XLim, [oracleInterval(1), oracleInterval(1)], 'k--', 'LineWidth', 2);
-      plot(ax.XLim, [oracleInterval(2), oracleInterval(2)], 'k--', 'LineWidth', 2);
+      plot(ax.XLim, [oracleInterval(1), oracleInterval(1)], 'k--');
[…]

### 2019-03-23 reports/thesis/chapters/5_inference.tex
Inference chapter
Done defectsimulation section
Done defectdetect section

@@
 
-Figure \ref{fig:inference_contamination_images} shows an example of a contaminated image before and after filtering.
-When doing a hypothesis test, the contamination caused systematic error such that there are false positives on the two corners of the unfiltered image.
-The empirical null filter can recover the original image by extracting the systematic errors such as the plane, as shown by the empirical null mean, and the increase of variance, as shown by the empirical null std.
-
-The QQ plot of the filtered test statistics, as shown in Figure \ref{fig:inference_contamination_qq}, shows that there may be a variance mismatch.
-A mismatch in the variance will increase or decrease the sensitivity of the test, a larger variance would increase the sensitivity.
-
-An experiment was conducted to investigate the sample mean and sample variance of the filtered contaminated image.
-Ideally the sample mean and sample variance should be 0 and 1 respectively.
-Different radiuses were investigated from ???
-to ???
-and repeated ???
-times.
-
-The results are shown in Figure \ref{fig:inference_allnullplane}.
-The filter correctly centred the test statistics at zero.
-However there was some variance mismatch and this depended on the kernel radius.
-A kernel radius of about 80 scaled the test statistics correctly.
-This suggest there may be an optimal kernel radius for this particular null distribution.
-Another caveat is that the sensitivity may not be exactly preserved after filtering.
-
-The study will now turn to contaminated defected images.
-Let $Z_{x,y}$ be the test statistics of pixel $(x,y)$ and under the null, it is distributed such that $Z_{x,y}|H_0\sim\normal(0,1)$.
-Defects refer to statistics which do not follow the null distribution, but instead an alternative distribution.
-For example it can be $Z_{x,y}|H_1\sim\normal(\mu_{1,x,y},1)$ and this example was used in this experiment.
-Contamination is a linear transform of the test statistics $Z_{x,y}$ such that
-\begin{equation}
-  C_{x,y} = Z_{x,y}\sigma_{0,x,y} + \mu_{0,x,y} \ .
-\end{equation}
-The empirical null filter recovers $Z_{x,y}$ from $C_{x,y}$. The values of the filtered test statistics are denoted as $\zeta_{x,y}$.
-
-Various simulated defects were investigated. Salt defect (named after salt and pepper noise) with density $\pi_1$ assign all test statistics to be distributed such that
-\begin{equation}
-  p_{Z_{x,y}}(z)=(1-\pi_1)p_{Z_{x,y}|H_0}(z) + \pi_1 p_{Z_{x,y}|H_1}(z) \ .
-\end{equation}
-In other words, test statistics will have the alternative distribution with probability $\pi_1$, and have the null distribution otherwise.
-This was chosen because the proportion of null statistics captured by a kernel should be independent of the radius of the kernel.
-
-A line defect assign columns of pixels to have the alternative distribution, a kernel would only capture a section of defect.
-Similarly different shapes were used such as a square defect.
-With a square defect, a kernel can capture the entire defect.
-
-An example of a salt defected image is shown in Figure \ref{fig:inference_saltDefect}, the figure also includes the image contaminated and filtered after contamination.
-The contamination caused some systematic errors, such as increasing the sensitivity such that are there more positive pixels in particular in two of the corners of the image.
-The empirical null filter recovers the defected image from the contaminated image so that appropriate inference can be done.
-However some statistical power is lost in the filtered image.
-This is because in areas of high empirical null std, the sensitivity decreased thus there is less detection power.
-This cannot be avoided as areas of high empirical null std is due to the sampling error.
-Using different kernel radiuses will change the sampling error of the empirical null std but it cannot be eliminated.
-Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_lineDefect}.
-
-The square defected images, including the contaminated ones, are shown in Figures \ref{fig:inference_squareDefect} and \ref{fig:inference_square2Defect}.
-Figure \ref{fig:inference_squareDefect} filtered the contaminated image using a kernel radius of $r=20$, while Figure \ref{fig:inference_square2Defect} used a kernel radius of $r=40$.
-With $r=20$, the kernel is smaller than the square defect, therefore the defect was treated as the null and this shows in the empirical null mean.
-This resulted in difficulty detecting the defect.
-With $r=40$, the kernel is much bigger than the defect and treated the defect as non-null.
-The empirical null filter recovers the gradient in the empirical null which was then used for inference.
+In this experiment, the empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination.
+A \emph{defect} is a pixel which has a value not distributed under null distribution, but instead an alternative distribution.
+For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
+
+To recap, \emph{contamination} is the result of a linear transform of the test statistics $Z_{x,y}$.
+For example in this experiment, the image was multiplied by 2 and a gradient was added to it.
+Suppose the image does contain defects, then an example of a resulting distribution is
+\begin{align}
+  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
+  \\
+  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
+\end{align}
+where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects.
+
+The empirical null filter aims to estimate the null distribution parameters from $Z_{x,y}$ in order to normalise it to form $T_{x,y}$.
+By normalising it, $T_{x,y}|H_{0,x,y}$ should be approximately standard Normal and hypothesis testing can be used to detect defects.
+
+Various defects were investigated.
+Speckle defect with density $\pi_1$ assign all test statistics to be non-null with probability $\pi_1$, and are null otherwise.
+This was chosen because the proportion of null statistics captured by the kernel should be the same all for all kernel radiuses.
+A line defect assign columns of pixels to be non-null, a kernel would only capture a section of defect.
+Different shapes were used such as a square defect.
+With a square defect, a kernel can capture the entire defect if its radius is large enough.
 
@@
     }
-  \caption{A $256 \times 256$ dust defect Gaussian image with/without contamination and after filtering with kernel radius 20.
+  \caption{A $256 \times 256$ Gaussian image with \emph{speckle} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius 20 in c).
 Defected pixels have the distribution $\normal(3,1)$.
-The salt defect has density $\pi_1 = 0.1$.
+The speckle defect has density $\pi_1 = 0.1$.
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
-  \label{fig:inference_saltDefect}
+Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+  \label{fig:inference_defectDustExample}
 \end{figure}
@@
     }
-  \caption{A $256 \times 256$ line defect Gaussian image with/without contamination and after filtering with kernel radius 20.
+  \caption{A $256 \times 256$ Gaussian image with a \emph{line} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius 20 in c).
 Defected pixels have the distribution $\normal(3,1)$.
-The line is 5 pixels thick.
+The line defect is 5 pixels thick.
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
-  \label{fig:inference_lineDefect}
+Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+  \label{fig:inference_defectLineExample}
 \end{figure}
@@
     }
-  \caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 20.
+  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius \emph{20} in c).
 Defected pixels have the distribution $\normal(3,1)$.
-The square is $30\times 30$ pixels in size.
+The square defect is $30\times 30$ pixels in size.
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
-  \label{fig:inference_squareDefect}
+Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+  \label{fig:inference_defectSquareExample}
 \end{figure}
@@
     }
-  \caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 40.
+  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius \emph{40} in c).
 Defected pixels have the distribution $\normal(3,1)$.
-The square is $30\times 30$ pixels in size.
+The square defect is $30\times 30$ pixels in size.
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
-  \label{fig:inference_square2Defect}
-\end{figure}
-
-The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} are shown in Figure \ref{fig:inference_defectSimulationRoc} for the various defects.
-The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds.
-Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity.
+Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+  \label{fig:inference_defectSquare2Example}
+\end{figure}
+
+An example of a speckle defected image is shown in Figure \ref{fig:inference_defectDustExample}, the figure also shows the image contaminated and then filtered.
+The contamination caused some systematic errors in hypothesis testing, such as an increase of positive pixels and in particular in two of the corners of the image.
+The empirical null filter recovers the image from the contaminated image so that appropriate inference can be done.
+However some statistical power was lost in the filtered image.
+This is because in areas of high empirical null standard deviation, the normalised statistics become too small which then decreased the detection power.
+This cannot be avoided as areas of high empirical null standard deviation is due to the sampling error.
+Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_defectLineExample}.
+
+The square defected images, including the contaminated ones, are shown in Figures \ref{fig:inference_defectSquareExample} and \ref{fig:inference_defectSquare2Example}.
+Figure \ref{fig:inference_defectSquareExample} filtered the contaminated image using a kernel radius of $r=20$, while Figure \ref{fig:inference_defectSquare2Example} used a kernel radius of $r=40$.
+With $r=20$, the kernel is smaller than the square defect, therefore the defect was treated as the null and this evident in the empirical null mean.
+This resulted in difficulty detecting the defect.
+With $r=40$, the kernel is bigger than the defect and treated the defect as non-null.
+The empirical null filter recovers the gradient in the empirical null which was then used for normalisation.
+
+The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} are shown in Figure \ref{fig:inference_defectSimulationRoc} for the various defects and filters.
+The ROC curve is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
 The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
 Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed thoroughly in \cite{cook2007use}.
-The area under the ROC curve was recorded for different intensity values of the defect.
 
@@
   \caption{ROC curves for various defected $256\times 256$ Gaussian images.
-The difference curves show the results for the non-contaminated image, contaminated image, and filtered contaminated image.
+The upper/lower dashed line show the resulting ROC curve when testing on an image without/with contamination respectively.
+The different curves are the resulting ROC curves after filtering a contaminated image.
 Defected pixels have the distribution $\normal(3,1)$.
@@
 
-The ROC is useful because it considers all thresholds or sensitivities used in the hypothesis testing.
+The ROC considers all thresholds or specificities used in the hypothesis testing.
 However in the previous experiment, it was found there was some variance mismatch before and after filtering with regards to the test statistics.
-As a result, for a given threshold, such as controlling the FDR, the sensitivity may change ever so slightly after filtering.
-
-An experiment was conducted to investigate the sensitivity before and after filtering.
-A $256\times 256$ Gaussian image with dust defect of density $\pi_1=0.1$ was investigated.
-A kernel radius of $r=20$ was used.
-The type 1 error, type 2 error and the FDR were investigated before contamination, after contamination and after filtering for various alternative distribution.
-The alternative distribution used is $Z_{x,y}|H_1\sim\normal(\mu_1,1)$ where $\mu_1$ is the alternative mean and was varied for this experiment.
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_type1.eps}
-        \caption{Type 1 error}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_type2.eps}
-        \caption{Type 2 error}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_fdr.eps}
-        \caption{FDR}
-      \end{subfigure}
-    }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered image of a $256 \times 256$ salt defected Gaussian image.
-a) shows the ROC area when testing the image before and after filtering.
-In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering.
-The filter used a kernel radius Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
-The salt defect has density $\pi_1 = 0.1$.
-The FDR was controlled at the 5\% level.
-The box plot summarise the 100 repeats of the experiment.}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_type1.eps}
-        \caption{Type 1 error}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_type2.eps}
-        \caption{Type 2 error}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_fdr.eps}
-        \caption{FDR}
-      \end{subfigure}
-    }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered image of a $256 \times 256$ salt defected Gaussian image.
-a) shows the ROC area when testing the image before and after filtering.
-In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering.
-The filter used a kernel radius  Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
-The salt defect has density $\pi_1 = 0.1$.
-The FDR was controlled at the 5\% level.
-The box plot summarise the 100 repeats of the experiment.}
-\end{figure}
+As a result, for a given threshold, such as controlling the FDR, the specificity may change ever so slightly after filtering.
+
+An experiment was conducted to investigate the specificity of the test before and after filtering.
+A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated.
+Before the experiment, various baselines were obtained.
+An image with a defect was simulated and then tested to obtain the ROC area, type 1 error, type 2 error and the FDR.
+The image was than contaminated and tested to obtain the 4 measurements again.
+This was repeated 300 times to obtain the empirical distribution of the ROC area, type 1 error, type 2 error and FDR when testing on a un/contaminated image with defects.
+The ROC area, type 1 error, type 2 error and FDR were measured when testing on a filtered contaminated image with defects, a kernel radius of $r=20$ was used and was repeated 100 times.
 
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
+        \label{fig:inference_DefectSimulationDust_type1}
         \caption{Type 1 error}
@@
 a) shows the ROC area when testing the image before/after contamination and after filtering.
-In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
-The filter used a kernel radius .
+In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
+The filter used a kernel radius of 20.
 Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
@@
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The FDR was controlled at the 5\% level.
+The test was done at the 5\% FDR level.
 The box plot summarise the 100 repeats of the experiment.}
@@
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_type1.eps}
-        \caption{Type 1 error}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_type2.eps}
-        \caption{Type 2 error}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_fdr.eps}
-        \caption{FDR}
-        \label{fig:inference_DefectSimulationDust_fdr}
-      \end{subfigure}
-    }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
-a) shows the ROC area when testing the image before/after contamination and after filtering.
-In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
-The filter used a kernel radius .
-Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
-The salt defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The FDR was controlled at the 5\% level.
-The box plot summarise the 100 repeats of the experiment.}
-\end{figure}
-
 The results are shown in Figure \ref{fig:inference_DefectSimulationDust}.
-The ROC areas were quantified here and shows that, in terms of the ROC area, using the filter improved the performance of the test from the contamination.
-Figure \ref{fig:inference_DefectSimulationDust_fdr} illustrate that in the uncontaminated image, the FDR is controlled below 5\%.
-However after contamination and then filtering, the FDR was not well controlled at this threshold.
-Ideally the error rates before contamination and after filtering should be similar so that sensitivity is preserved after filtering.
-This should highlight that while performance can be recovered from contamination in terms of the ROC area, the FDR threshold may not be preserved.
-
-There is also the question of what kernel size to choose for a given defect.
+The ROC areas were quantified here and shows that using the filter improved the performance of the test from the contamination.
+The type 1 error, or specificity, did decreased after filtering.
+However the results illustrated that the FDR is controlled quite well at around 5\% after filtering.
+This means that in this particular example, the FDR control is consistent after contamination and filtering.
+
+There is the question of what kernel size to choose for a given defect.
 Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $\pi_1=0.1$ to satisfy some assumptions made for the empirical null.
@@
 \end{equation}
-In the example of $d=30$, this is about $r>54$. For the line defect with thickness $d$, it can be involved because the maximum area of the line defect captured by the kernel is
-\begin{equation}
-2r^2
-\left[
-  \dfrac{d}{2r}\sqrt{1-\left(\dfrac{d}{2r}\right)^2}
-  +\text{arcsin}\left(\dfrac{d}{2r}\right)
-\right] \ .
-\end{equation}
-For $d=5$, the radius is about $r>32$.
-These are rules of thumb because the kernel won't be perfectly circular when used on a grid of pixels.
+In the example of $d=30$, this is about $r>54$.
+For the line defect with thickness $d$, the radius is about $r>32$.
+These are rules of thumb because the kernel is not perfectly circular when used on a grid of pixels.
 It should be pointed out that the implementation can accept non-integer radiuses if desired.
@@
   \caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses.
-The dotted lines show the 95\% percentile when the hypothesis test was done on the uncontaminated image.
+The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
 Defected pixels have the distribution $\normal(3,1)$.
@@
 The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The FDR was controlled at the $2\sigma$ level.
+The test was done at the 5\% FDR level.
 The box plot summarise the 100 repeats of the experiment.}
@@
   \caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
-The dotted lines show the 95\% percentile when the hypothesis test was done on the uncontaminated image.
+he dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
 Defected pixels have the distribution $\normal(3,1)$.
@@
 An experiment was conducted where the contaminated defected image were filtered for various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
-Hypothesis testing was done on the uncontaminated and filtered contaminated image.
-The area under the ROC curve and various errors were recorded.
+Hypothesis testing was done on the uncontaminated and filtered contaminated image and the area under the ROC curve and various errors were recorded, this was repeated 100 times.
+The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
 Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.
@@
 This does highlight that a kernel with a good radius can performance almost as though there was no contamination.
-For large kernel radius, the FDR becomes similar to the FDR obtained from the uncontaminated image.
-Thus it appears a large kernel radius helped preserve FDR control after filtering in these examples.
+It also appears that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
+
+For large enough kernel radius, the FDR is controlled at around, perhaps a bit below, 5\%.
+It appears a large kernel radius helped preserve FDR control after filtering in these examples.
 However a large kernel radius does come at a computational cost.
@@
 
+\afterpage{\clearpage}
 \section{Results}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_sig.eps}
-        \caption{Image with sig.~pixels}
+        \caption{Image with positive pixels}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_sig.eps}
-        \caption{Image with sig.~pixels}
+        \caption{Image with positive pixels}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_sig.eps}
-        \caption{Image with sig.~pixels}
+        \caption{Image with positive pixels}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_sig.eps}
-        \caption{Image with sig.~pixels}
+        \caption{Image with positive pixels}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
-        \caption{Image with sig.~pixels}
+        \caption{Image with positive pixels}
       \end{subfigure}

### 2019-03-24 reports/thesis/chapters/5_inference.tex
Inference chapter
Edited inference chapter
Edited clim in defectExample
Edited xlim in DefectRadius

@@
 
-Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect.
+Disagreement between the scan and \texttt{aRTist} can be found by subtracting one image from the other, any values too big in magnitude can be considered as a defect.
 However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance.
@@
 
-A pixel by pixel inference was proposed to do defect detection. A statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
+A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic is
 \begin{equation}
@@
 Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal.
-Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $Z_{x,y}$ statistics, assuming there are no defects, can be approximately quantified
+Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
 \begin{equation}
@@
 \end{equation}
-As with usual statistical convention, upper case $Z$ denote a random variable. Whereas lower case $z$ denote a realisation or an observation of that random variable.
+As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.
 
@@
 These replicated x-ray images were manually segmented.
-This provided variance-mean data and was used to train the variance model, such as a Gamma distributed GLM.
+This provided variance-mean data and was used to train the variance model, such as a gamma distributed GLM.
 The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
@@
 This method for inference was applied to the dataset \texttt{Sep16 120deg}.
-Here a cuboid with voids were purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}.
+A cuboid (4 cm $\times$ 4 cm $\times$ 6 cm) with voids was purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}.
+The voids were of various diameters 2.4 mm, 1.2 mm, 0.6 mm and 0.3 mm.
+6 voids for each diameter were designed in the CAD.
+Voids with diameters 2.4 mm and 0.6 mm were regularly arranged, otherwise they were arranged irregularly.
+The precision of the manufacturing was in the order of $\pm0.1\text{ mm}$.
+
+\begin{figure}[htp]
+  \centering
+  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
+  \caption{CAD of a 3D cuboid with voids; the scale shown is approximate.}
+  \label{fig:inference_testObject}
+\end{figure}
+
 The 20 x-ray images were spilt into 2.
@@
 In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.
-The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
-  \caption{CAD of a 3D cuboid with voids}
-  \label{fig:inference_testObject}
-\end{figure}
+The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
 
@@
   \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids.
-The $p$-values obtained were used for hypothesis testing using the \cite{benjamini1995controlling} procedure, controlling the FDR at the 5\% level.
+The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level.
 Pixels detected as positive are shown in red in d).}
@@
 
-For each pixel, a $z$ statistic was calculated.
-A $z$ statistic too large in magnitude will classify that pixel as a positive result.
-In two-tailed hypothesis testing framework \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent $z$ statistic in a different way
+For each pixel, a test statistic was calculated.
+A test statistic too large in magnitude will classify that pixel as a positive result.
+In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
 \begin{equation}
@@
 Model misspecification appeared to be the main source of error.
-The $z$ statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}.
-It can be seen that the majority of the $z$ statistics does not look Normal.
+The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}.
+It can be seen that the majority of the test statistics does not look Normal.
 Also the majority of the $p$-values does not look uniformly distributed.
@@
 
-\begin{figure}
+\begin{figure}[htp]
   \centering
@@
     \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
-    \caption{Histogram of $z$}
+    \caption{Histogram}
   \end{subfigure}
@@
 }
-  \caption{a) The histogram of the $z$ statistics is compared with the standard Normal distribution.
+  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution.
 The standard Normal distribution is known as the null distribution in this scenario.
 b) The $p$-values are ordered and plotted.
-The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure.}
+The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure.
+The dotted line shows the result if the $p$-values were uniformly distributed.}
   \label{fig:inference_inferenceIntro_histogram}
@@
 The empirical null is then extended to an image filter, called the empirical null filter.
-This filter adjust each $z$ statistic according to its neighbours, ironing out false positive results.
+This filter adjust each test statistic according to its neighbours, ironing out false positive results.
 Simulations and results are shown towards the end of the chapter.
@@
 
-Consider a $z$ statistic from a pixel.
+Consider a test statistic from a pixel.
 If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$.
@@
 
-In two-tailed hypothesis testing \cite{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example.
+In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example.
 A positive result is declared when $p<\alpha$, else it is a negative result.
@@
 
-Multiple hypothesis testing occurs when there are more than one hypothesis to test.
-For example $n$ pixels can be tested where the $z$ statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$.
+Multiple hypothesis testing occurs when there are more than one hypotheses to test.
+For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$.
 The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$.
@@
 The uncorrected test classify any $p_i<\alpha$ as positive.
-This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increase \citep{shaffer1995multiple}.
+This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}.
 This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}.
@@
 
-\begin{table}
+\begin{table}[htp]
   \centering
@@
   \end{tabular}
-  \caption{Random variable definitions for true/false positives/negatives made in multiple hypothesis testing}
+  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
   \label{table:inference_randomvariables}
@@
 \begin{equation}
-  \text{FWER} = 1-\prob(V=0) \ .
+  \text{FWER} = \prob(V\geqslant1) \ .
   \label{eq:inference_fwer}
@@
 This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive.
-For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
-For example in Figure \ref{fig:inference_inferenceIntro_pvalue} the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.
+For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
+For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.
 
@@
 
-\begin{table}
+\begin{table}[htp]
     \centering
@@
 
-\begin{figure}
+Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+The distribution of the test statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$.
+Almost half of the pixels were tested positive.
+It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.
+
+\begin{figure}[htp]
   \centering
@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
-      \caption{$z$ statistics}
+      \caption{Test statistics}
     \end{subfigure}
@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
-      \caption{Histogram of $z$ in sub-image}
+      \caption{Histogram of test in sub-image}
     \end{subfigure}
@@
 A $200\times 200$ sub-image was taken shown by the dashed lines.
-A histogram of the $z$ statistics in the sub-image is shown in b).
+A histogram of the test statistics in the sub-image is shown in b).
 The critical region was obtained by using the BH procedure at the 5\% FDR level.}
@@
 \end{figure}
-
-Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}.
-The distribution of the $z$ statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$.
-Almost half of the pixels were tested positive.
-It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.
 
@@
 
-The null standard deviation was estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
+The null standard deviation is estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
 \begin{equation}
@@
 
-This method does not need estimations of $\pi_0$ which makes it quite useful.
+This method does not need estimations of $\pi_0$ which makes it quite convenient.
 The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}.
@@
 \begin{equation}
-  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right) + 0.16
+  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_z,\text{IQR}_z/1.34\right)
   \label{eq:inference_ourruleofthumb}
 \end{equation}
-where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.
-
-\begin{figure}
+where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range.
+
+\begin{figure}[htp]
   \centering
   \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
-  \caption{The density of the $z$ statistics was estimated using a kernel density estimate.
-The dot dash lines shows the empirical null distribution multiplied by some constant, this is to insulate the two densities have the same curvature at the mode.}
+  \caption{The density of the test statistics was estimated using a kernel density estimate.
+The dot dash lines show the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
   \label{fig:inference_inferenceSubsample1_densityEstimate}
@@
 The only tuning parameter is the bandwidth $h$ and the density estimate is simple enough to do calculus on it.
-Speed may be an issue as an evaluation of the density estimate requires the sum over the $n$ $z$ statistics.
-
-The $z$ statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
+Speed may be an issue as an evaluation of the density estimate requires the sum over the $n$ test statistics.
+
+The test statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
 \begin{equation}
@@
     }
-    \caption{The critical regions and $p$-values were adjusted using the empirical null.}
+    \caption{The critical regions and $p$-values were adjusted using the empirical null in the sub-image example.}
     \label{fig:inference_inferenceSubsample1_nullResults}
@@
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_zImage.eps}
-        \caption{$z$ statistics}
+        \caption{test statistics}
     \end{subfigure}
@@
 The empirical null was used to test pixels, positive pixels are shown in red in b).
-The histogram of the $z$ statistics are shown in c) along with the critical region.
+The histogram of the test statistics are shown in c) along with the critical region.
 The normalised $p$-values are shown in d).
-The critical regions were adjusted using the empirical null and obtained using the BH procedure, controlling the FDR at 5\%.}
+The critical regions were adjusted using the empirical null and obtained using the BH procedure at the 5\% FDR level.}
     \label{fig:inference_inferenceSubsample2}
@@
 This was done on a simulated dataset of $n$ standard Normal random variables.
-For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation of the datasets.
+For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation of the dataset.
 The median squared error was obtained by taking the median over all squared errors from the 100 estimates.
@@
 $\widehat{\mu}_0$ has low median squared error for large bandwidths.
-For low $n$, large bandwidths are particularly important because smoother curves prevents any false bimodal features appearing, making it easier to find the mode.
+For low $n$, large bandwidths are particularly useful because smoother curves prevent any false bimodal features appearing, making it easier to find the mode.
 
 A smooth valley can be seen for the median squared error for $\widehat{\sigma}_0$.
-It appears for a given $n$, there exist a bandwidth which minimise the median squared error.
-However the rules of thumb does not optimise for $\widehat{\sigma}_0$ and undershoots it.
+It appeared for a given $n$, there exist a bandwidth which minimise the median squared error.
+However the rules of thumb did not optimise for $\widehat{\sigma}_0$ and undershot it.
 Figure \ref{fig:inference_BandwidthSelection_error3} shows the median of the estimates of $\sigma_0$.
 The true value in this simulation is $\sigma_0=1$ which is represented as a horizontal plane.
-Bandwidths too small underestimate $\sigma_0$, bandwidths too big over estimates $\sigma_0$.
-
-\begin{figure}
+Bandwidths too small underestimated $\sigma_0$, bandwidths too big overestimated $\sigma_0$.
+
+\begin{figure}[htp]
   \centering
@@
   \end{subfigure}
-  \caption{Median squared error of the estimators of the empirical null parameters from 100 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
+  \caption{Median squared error of the estimators of the empirical null parameters from 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
   \label{fig:inference_BandwidthSelection_error}
@@
     \end{subfigure}
-    \caption{Median value of $\widehat{\sigma}_0$ from 100 repeats of $n$ simulated $\normal(0,1)$ data. The true value is $\sigma_0=1$ which is represented by a horizontal plane.}
+    \caption{Median value of $\widehat{\sigma}_0$ from 100 repeats of $n$ simulated standard Normal data. The true value is $\sigma_0=1$ which is represented by a horizontal plane.}
     \label{fig:inference_BandwidthSelection_error3}
@@
 Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $n$.
-A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimises the log squared error for a given $n$.
+A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimised the log squared error for a given $n$.
 \texttt{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures.
@@
     }
+    \medskip
     \centerline{
@@
     \caption{A smoothing spline was fitted on the log squared error for estimating $\sigma_0$ against the bandwidth.
-The estimator $\widehat{\sigma}_0$ uses the kernel density estimator fitted onto $n$ simulated standard Normal data.
 Boxplots represent the variation of the error from 100 repeats.
-The red dashed line shows the bandwidth which minimise the fitted spline.}
+The red dashed line shows the bandwidth which minimised the fitted spline.}
     \label{fig:inference_BandwidthSelection2_plot}
@@
 This was chosen to establish a simple relationship with the rules of thumb.
-Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} show the fitting of an identity link Gamma GLM in order to estimate $b$ and $a$.
+Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} show the fitting of an identity link gamma GLM in order to estimate $b$ and $a$.
 The estimated parameters are shown in Table \ref{table:inference_BandwidthSelection2_ruleOfThumb}.
 
-\begin{figure}
+\begin{figure}[htp]
   \centering
@@
 The method used in fitting the smoothing spline could contribute to the underfitting.
-For example if the smoothing spline was not smooth enough so that local minima appear, it would add variance to the location of the optimal bandwidth.
+For example if the smoothing spline was not smooth enough so that local minima appeared, it would add variance to the location of the optimal bandwidth.
 A basic linear relationship was chosen to avoid overfitting and keep the rule of thumb simple.
@@
 In conclusion, a small bias added to the rule of thumb improved the performance of the estimator $\widehat{\sigma}_0$.
-\cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggest the use of $b=0.9$ rather than $b=1.06$.
-Following from this, it was chosen that the intercept was added to Silverman's rule of thumb for the use in the empirical null
-\begin{equation}
-  h = \left(0.9n^{-1/5}+ 0.16\right) \times\text{min}\left(s_z,\text{IQR}_z/1.34\right) 
-  \ .
-  \tag{\ref{eq:inference_ourruleofthumb}}
-\end{equation}
+\cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggested the use of $b=0.9$.
+Following from this, it was chosen that the intercept was added to Silverman's rule of thumb for the use in the empirical null $h = \left(0.9n^{-1/5}+ 0.16\right) \times\text{min}\left(s_z,\text{IQR}_z/1.34\right)$.
 
@@
 The results are shown in Figures \ref{fig:inference_NullIidMean} and \ref{fig:inference_NullIidStd}.
-The null mean and standard deviation estimations both suffer from high variance, much higher than typical robust estimators such as the median and IQR.
-
-The estimation of the null standard deviation has some positive bias and it was found that this bias is quite sensitive to the bandwidth.
+The empirical null mean and empirical null standard deviation estimations both suffered from high variance, much higher than typical robust estimators such as the median and IQR.
+
+The empirical null standard deviation had some positive bias and it was found that this bias was quite sensitive to the bandwidth.
 Further fine tuning on the bandwidth would be required for the empirical null standard deviation to be unbiased.
-For example it appeared there is consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
+For example it appeared there was consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
 The source of bias could come from the fact that the bandwidth was tuned to minimise the mean squared error rather than the squared bias.
@@
 The resulting empirical null distribution is shown in Figure \ref{fig:inference_inferenceSubsampleAll}.
-The empirical null distribution has a very large standard deviation and would test all pixels as negative, this is incorrect.
-
-\begin{figure}[hpt]
+The empirical null distribution had a very large standard deviation and would test all pixels as negative, this is incorrect.
+
+\begin{figure}[htp]
   \centering
@@
     \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
-    \caption{$z$ statistics}
+    \caption{Test statistics}
   \end{subfigure}
@@
   \end{subfigure}
-  \caption{The resulting $z$ statistics are shown in a).
+  \caption{The resulting test statistics are shown in a).
 The density estimate of the statistics is shown in b).
@@
 
-The problem is that the empirical distribution of the $z$ statistics did not look Normal.
-It appeared that the $z$ statistics varied spatially, suggesting the empirical null varied spatially as well.
-One possible reason is because it looked like the value of the $z$ statistics depended on which surface it was on for example.
+The problem was that the empirical distribution of the test statistics did not look Normal.
+It appeared that the test statistics varied spatially, suggesting the empirical null varied spatially as well.
+One possible reason is because it looked like the value of the test statistics depended on which surface it was on for example.
 
@@
 
-The empirical null filter uses the empirical null on neighbouring pixels to estimate the null distribution parameters.
+The empirical null filter uses the empirical null on neighbouring pixels to estimate the null parameters.
 To estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel of radius $r$ was centred at $(x,y)$.
-All the pixels captured by the circular kernel were then used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
-\begin{equation}
+All the pixels captured by the circular kernel were used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
+\begin{align}
   \widehat{\mu}_{0,x,y}
-  =
+  &=
   \widehat{\mu}_{0,x,y}
@@
     \right)
-\end{equation}
-and
-\begin{equation}
+\\
   \widehat{\sigma}_{0,x,y}
-  =
+  &=
   \widehat{\sigma}_{0,x,y}
@@
   \ .
-\end{equation}
+\end{align}
 Using these estimates, the test statistics were normalised using
@@
 
-$r$ does control the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$. If the size of the defects are known, then $r$ should be selected such that
-\begin{equation}
-\dfrac{
-  \text{area of defect}
-}
-{
-  \pi r^2
-}
-<
-5\% \text{ to } 10 \%
-\end{equation}
-so that $\pi_0$ is of a sensible value.
+$r$ control the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$.
+$r$ should be selected so that $\pi_0$ is of a sensible value, for example $>90\%$.
 In practice, the defects are unknown so various kernel radiuses should be tried out.
-But in general, the kernel radius should be much larger than the size of the defect.
+In general, the kernel radius should be much larger than the size of the defect.
 
@@
 As a test, the empirical null filter with $r=5$ was used on a \texttt{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
-It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it does verify the filter works on arbitrary images with some computational considerations.
+It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it did verify that the filter worked on arbitrary images with some computational considerations.
 The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all ${x,y}$ could be of interest.
@@
 Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters.
-The empirical null mean creates an impasto look and preserve edges which is similar to the result in \cite{griffin2000mean}.
+The empirical null mean created an impasto effect and preserved edges which is similar to the result in \cite{griffin2000mean}.
 Spread filters such as the standard deviation filter can be used to detect edges.
 Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation.
-The resulting images are similar but it was notable that the edges in the empirical null standard deviation are sharper, suggesting that the empirical null standard deviation is a more robust measure of spread compared to the standard deviation.
-
-\begin{figure}
+The resulting images were similar but it was notable that the edges in the empirical null standard deviation were sharper, suggesting that the empirical null standard deviation is a more robust measure of spread compared to the standard deviation.
+
+\begin{figure}[htp]
   \centering
@@
 Advanced options are available to the user.
-The number of initial values set the number of valid solutions to be found in the Newton-Raphson method on finding the mode of the density estimate, the solution with the gradient closest to zero is then used in further calculations.
+The number of initial values set the number of valid solutions to be found in the Newton-Raphson method on finding the mode of the density estimate.
 The user can also set the maximum number of steps and tolerance for the Newton-Raphson method.
@@
 
-Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design has already been done.
+Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design had already been done.
 \texttt{RankFilters} contain implementations of filters such as the mean filter and median filter.
-The implementation makes use of multiple threads, each thread filters a row in parallel.
-This is done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache.
-Then for each column, the thread does calculations using the cache then replaces the pixel value of the image to be filtered.
+The implementation uses multiple threads, each thread filters a row in parallel.
+This was done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache.
+Then for each column, the thread does calculations using the cache then replaces the pixel value of the image to be filtered with the resulting calculation.
 Once the row has been filtered, the thread then moves onto the next unfiltered row.
@@
 Figure \ref{fig:inference_padding_nearest} shows an example of nearest pixel padding on the top left corner of a rectangle ROI.
-This is not suitable for the empirical null filter as this will cause bias in a lot of calculations, especially the density fitting.
-The empirical null filter uses \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}.
+This is not suitable for the empirical null filter as this will cause bias in the density estimation.
+The empirical null filter used \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}.
 This indicate that these pixels are outside the ROI and are ignored.
-The number of non-\texttt{NaN} captured by the kernel is kept track for calculations such as the bandwidth for the kernel density estimate.
-
-\begin{figure}
+The number of non-\texttt{NaN} captured by the kernel was kept track for calculations such as the bandwidth.
+
+\begin{figure}[htp]
   \centering
@@
 
-Line filtering is done from left to right.
-At the start on the far left, an initial value of the median of all the pixels in the kernel is used.
-In addition, various initial values were randomly tried out until a requested number of valid solutions are found, the solution with the greatest value of $p_Z(\widehat{\mu}_0)$ was used.
-For the following pixel to the right, the empirical null mean of the neighbouring left pixel is used as a initial point.
+Line filtering was done from left to right.
+At the start on the far left, an initial value of the median of all the pixels in the kernel was used.
+In addition, various initial values were randomly tried out until a requested number of valid solutions were found.
+For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as a initial point.
 This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
 
-Trying out more initial values is an advantage because it eliminates the chances of obtaining a sub-optimal solution such as a local maxima.
-However this is traded for computational cost.
-Additional initial values were generated by sampling from the Normal distribution centred on the first initial value and with standard deviation the same as the standard deviation using all pixels in the kernel.
-
 When filtering arbitrary images such as \texttt{bridge.gif}, a few computational considerations were needed.
-\texttt{bridge.gif} is an 8-bit image so values are represented as integers.
-This open up opportunities for the inter-quartile range and the standard deviation to be zero, this caused problems as this set the bandwidth to be zero.
-When the standard deviation is zero, it was set to $0.289$ which corresponds to the standard deviation of a Uniform random variable.
+\texttt{bridge.gif} is an 8-bit image so values were represented as integers.
+This opened up opportunities for the inter-quartile range and the standard deviation to be zero, this caused problems as this set the bandwidth to be zero.
+When the standard deviation is zero, it was set to $0.289$ which corresponds to the standard deviation of a uniform random variable.
 When the inter-quartile range is zero, the inter-quartile range was set to the standard deviation $\times 1.34$.
@@
 This can be shown.
-Let $Z_{x,y}$ be the value of the pixels captured by the circular kernel for integer values of $(x,y)$ such that $x^2+y^2\leqslant r$.
+Let $Z_{x,y}$ be the value of the pixels captured by the circular kernel for integer values of $(x,y)$ such that $x^2+y^2\leqslant r^2$.
 Suppose that $Z_{x,y}\sim\normal(ax+by,c^2\sigma^2)$.
@@
   }
-  \caption{A $256\times 256$ Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null std.}
+  \caption{A $256\times 256$ Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
   \label{fig:inference_allNullGaussianScript}
@@
   }
-  \caption{A $256\times 256$ contaminated Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null std.}
+  \caption{A $256\times 256$ contaminated Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
   \label{fig:inference_allNullPlaneScript}
@@
   \end{subfigure}
-  \caption{$p$-values of values from a filtered $256\times 256$ Gaussian image with kernel radius 20.
+  \caption{$p$-values from a filtered $256\times 256$ Gaussian image with kernel radius 20.
 In b), the Gaussian image was contaminated before filtering.
@@
 An example of a Gaussian image with/without contamination before/after filtering are shown in Figures \ref{fig:inference_allNullGaussianScript} and \ref{fig:inference_allNullPlaneScript}.
-In the contaminated example.
-the filter managed to estimate the null mean, picking up the gradient.
+In the contaminated example, the filter managed to estimate the null mean, picking up the gradient.
 This enabled the normalised image to look flat to remove the contamination.
@@
 
-\begin{figure}[htp]
+\begin{figure}
   \centering
@@
 
-When filtering the contaminated image, all estimators suffered from negative bias in the standard deviation of the filtered statistics, in particular when the kernel radius increases.
+When filtering the contaminated image, all estimators suffered from negative bias in the standard deviation of the filtered statistics, in particular when the kernel radius increased.
 This is shown in Figure \ref{fig:inference_AllNullPlane_var}.
-As discussed before, the kernel captures the variation due to the contamination and this adds intrinsic bias to the null variance.
-As a result, this adds bias when estimating the null variance.
-
-The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} shows that the empirical null filter can cause the filtered statistics to have heavy tails, in particular for small kernel radiuses.
+As discussed before, the kernel captured the variation due to the contamination and this added intrinsic bias to the null variance.
+As a result, this added bias when estimating the null variance.
+
+The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} showed that the empirical null filter caused the filtered statistics to have heavy tails, in particular for small kernel radiuses.
 This could cause problems in hypothesis testing because heavy tails could be misinterpreted as contribution from non-null statistics.
@@
 In this experiment, the empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination.
-A \emph{defect} is a pixel which has a value not distributed under null distribution, but instead an alternative distribution.
+A \emph{defect} is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
 For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
@@
 The speckle defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
@@
 The line defect is 5 pixels thick.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
@@
 The square defect is $30\times 30$ pixels in size.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
@@
 The contamination caused some systematic errors in hypothesis testing, such as an increase of positive pixels and in particular in two of the corners of the image.
-The empirical null filter recovers the image from the contaminated image so that appropriate inference can be done.
+The empirical null filter recovered the image from the contaminated image so that appropriate inference was done.
 However some statistical power was lost in the filtered image.
-This is because in areas of high empirical null standard deviation, the normalised statistics become too small which then decreased the detection power.
-This cannot be avoided as areas of high empirical null standard deviation is due to the sampling error.
+This is because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
+This cannot be avoided as areas of high empirical null standard deviation was due to the sampling error.
 Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_defectLineExample}.
@@
 With $r=40$, the kernel is bigger than the defect and treated the defect as non-null.
-The empirical null filter recovers the gradient in the empirical null which was then used for normalisation.
+The empirical null filter recovered the gradient in the empirical null which was then used for normalisation.
 
@@
 Defected pixels have the distribution $\normal(3,1)$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
   \label{fig:inference_defectSimulationRoc}
@@
 
-In terms of the area under the ROC curves, the empirical null filter improves the performance over using the unfiltered contaminated image.
-The performance before contamination cannot be recovered but it is an improvement.
-For kernel radiuses too small, such as Figure \ref{fig:inference_defectSimulationRoc_square20}, the empirical null filter deteriorates the performance dramatically and it would be better off using the contaminated image.
+In terms of the area under the ROC curves, the empirical null filter improved the performance over using the unfiltered contaminated image.
+The performance before contamination cannot be recovered but it was an improvement.
+For kernel radiuses too small, such as Figure \ref{fig:inference_defectSimulationRoc_square20}, the empirical null filter deteriorated the performance and it would be better off using the contaminated image.
 
@@
 However in the previous experiment, it was found there was some variance mismatch before and after filtering with regards to the test statistics.
-As a result, for a given threshold, such as controlling the FDR, the specificity may change ever so slightly after filtering.
+As a result, for a given threshold such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
 
@@
 The salt defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
@@
 The results are shown in Figure \ref{fig:inference_DefectSimulationDust}.
-The ROC areas were quantified here and shows that using the filter improved the performance of the test from the contamination.
+The ROC areas quantified showed that using the filter improved the performance of the test from the contamination.
 The type 1 error, or specificity, did decreased after filtering.
 However the results illustrated that the FDR is controlled quite well at around 5\% after filtering.
-This means that in this particular example, the FDR control is consistent after contamination and filtering.
+This meant that in this particular example, the FDR control is consistent after contamination and filtering.
 
@@
 \end{equation}
-For a $d \times d$ square defect this is
-\begin{equation}
-r > d \sqrt{\dfrac{10}{\pi}} \ .
-\end{equation}
+For a $d \times d$ square defect this is $r > d \sqrt{10/\pi}$.
 In the example of $d=30$, this is about $r>54$.
-For the line defect with thickness $d$, the radius is about $r>32$.
+For the line defect with thickness $5$, the radius is about $r>32$.
 These are rules of thumb because the kernel is not perfectly circular when used on a grid of pixels.
@@
 The line defect is 5 pixels thick.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
@@
   \caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
-he dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
+The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
 Defected pixels have the distribution $\normal(3,1)$.
 The square defect is $30\times 30$ pixels in size.
-The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
@@
 
-The results show that the ROC area increased with kernel radius.
-This does highlight that a kernel with a good radius can performance almost as though there was no contamination.
-It also appears that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
-
-For large enough kernel radius, the FDR is controlled at around, perhaps a bit below, 5\%.
-It appears a large kernel radius helped preserve FDR control after filtering in these examples.
-However a large kernel radius does come at a computational cost.
+The results showed that the ROC area increased with kernel radius.
+This highlighted that a kernel with a good radius can performance almost as though there was no contamination.
+It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
+
+For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%.
+It appeared a large kernel radius helped preserve FDR control after filtering in these examples.
+However a large kernel radius did come at a computational cost.
 Choosing a kernel radius is a matter of trading computational cost with precise FDR control.
@@
   \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$.
-a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and std.}
+c) and d) Empirical null mean and deviation.}
   \label{fig:inference_sep16120deg_inference_radius1}
@@
   \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$.
-a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and std.}
+c) and d) Empirical null mean and deviation.}
   \label{fig:inference_sep16120deg_inference_radius2}
@@
   \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$.
-a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and std.}
+c) and d) Empirical null mean and deviation.}
   \label{fig:inference_sep16120deg_inference_radius3}
@@
   \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$.
-a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and std.}
+c) and d) Empirical null mean and deviation.}
   \label{fig:inference_sep16120deg_inference_radius4}
@@
 Figure \ref{fig:inference_sep16120deg_zfiltered} shows the filtered $z$ images for various kernel radiuses.
-For $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image is smooth and treated everything as the null.
-When a large enough radius was used, the defects are highlighted by the higher $z$ statistics and everything else remain unchanged.
+For $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image was smooth and treated everything as the null.
+When a large enough radius was used, the defects were highlighted by the higher test statistics and everything else remain unchanged.
 Figures \ref{fig:inference_sep16120deg_inference_radius1} to \ref{fig:inference_sep16120deg_inference_radius4} shows the resulting inference along with the empirical null parameters.
-The figures shows that for large enough kernel radius, the filter irons out the false positives observed at the start of this chapter.
+The figures shows that for large enough kernel radius, the filter ironed out the false positives observed at the start of the chapter.
 All of the defects were successfully highlighted by the hypothesis test.
@@
 False positives were detected on the bottom right of the 3D printed sample.
-This is the result of the null distribution being bimodal where each face has a different distribution.
+This was the result of the null distribution being bimodal where each face had a different distribution.
 Figure \ref{fig:inference_cornerSelect} illustrates this.
-The geometry of the faces and the kernel is such it results in one of the faces to be treated as non-null and then tested positive, falsely so.
+The geometry of the faces and the kernel was such that it resulted in one of the faces to be treated as non-null and then tested positive, falsely so.
 
@@
     }
-  \caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the $z$ statistics captured by the kernel shows a bimodal distribution.}
+  \caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the test statistics captured by the kernel shows a bimodal distribution.}
   \label{fig:inference_cornerSelect}
@@
 It was segmented using the edges of the projection of the 3D printed object.
-The empirical null filter was then used on each segment independently, ignoring pixels outside the segment the filter is working on.
+The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
 The resulting filtered segments were stitched together to form the resulting filtered image.
@@
   \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
-  \caption{The $z$ was segmented further into 7 segments.}
+  \caption{The $z$ image was segmented further into 7 segments.}
   \label{fig:inference_segmentFurther}
@@
   \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$.
-a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.
-The $z$ statistics from all segments were combined in the BH procedure.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
+The test statistics from all segments were combined in the BH procedure.
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and std.}
+c) and d) Empirical null mean and standard deviation.}
   \label{fig:inference_subroisep16120deg_inference_radius4}
@@
 A binary image filter, such as erode followed by a dilate, can be used to remove isolate significant pixels and emphasise the cluster of significant pixels.
+
+Robust statistics \citep{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}

### 2019-03-24 inference/defectsimulation/DefectRadius.m

@@ -44,7 +44,7 @@ classdef DefectRadius < Experiment
     function printResults(this)
       
       directory = fullfile('reports','figures','inference');
-      offset = 1;
+      rightOffset = 10;
       
       %plot roc area vs alt mean
       fig = LatexFigure.sub();
@@ -53,11 +53,10 @@ classdef DefectRadius < Experiment
       boxplot.setPosition(this.radiusArray);
       boxplot.plot();
       hold on;
-      ax.XLim(1) = this.radiusArray(1) - offset;
-      ax.XLim(2) = this.radiusArray(end) + offset;
       oracleInterval = quantile(reshape(this.rocAreaArray(:,:,1),[],1), [0.025, 0.975]);
       plot(ax.XLim, [oracleInterval(1), oracleInterval(1)], 'k--');
       plot(ax.XLim, [oracleInterval(2), oracleInterval(2)], 'k--');
+      ax.XLim(2) = ax.XLim(2) + rightOffset;
       xlabel('kernel radius');
       ylabel('roc area');
       saveas(fig,fullfile(directory, strcat(this.experiment_name,'_roc.eps')),'epsc');
@@ -69,11 +68,10 @@ classdef DefectRadius < Experiment
       boxplot.setPosition(this.radiusArray);
       boxplot.plot();
       hold on;
-      ax.XLim(1) = this.radiusArray(1) - offset;
-      ax.XLim(2) = this.radiusArray(end) + offset;
       oracleInterval = quantile(reshape(this.type1ErrorArray(:,:,1),[],1), [0.025, 0.975]);
       plot(ax.XLim, [oracleInterval(1), oracleInterval(1)], 'k--');
       plot(ax.XLim, [oracleInterval(2), oracleInterval(2)], 'k--');
+      ax.XLim(2) = ax.XLim(2) + rightOffset;
       xlabel('kernel radius');
       ylabel('type 1 error');
       saveas(fig,fullfile(directory, strcat(this.experiment_name,'_type1.eps')),'epsc');
@@ -85,11 +83,10 @@ classdef DefectRadius < Experiment
       boxplot.setPosition(this.radiusArray);
       boxplot.plot();
       hold on;
-      ax.XLim(1) = this.radiusArray(1) - offset;
-      ax.XLim(2) = this.radiusArray(end) + offset;
[…]

### 2019-03-25 reports/thesis/chapters/5_inference.tex
Inference chapter complete

@@
 \end{equation}
-and only the normalised test statistics were used in hypothesis testing.
+and only the normalised test statistics were used in hypothesis testing. It should be noted that because the kernels can overlap, correlation between $T_{x,y}$ for different $(x,y)$ is introduced.
 
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+Highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectDustExample}
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+Highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectLineExample}
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+Highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectSquareExample}
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive when controlling at the 5\% FDR level.}
+Highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectSquare2Example}
@@
 This meant that in this particular example, the FDR control is consistent after contamination and filtering.
+At situations with low detection power, the FDR can fluctuate between 0 and 1 and can take only so many values.
+For example if 3 positive pixels were detected, then the FDR can only take values of multiples of $1/3$ between and including 0 and 1.
 
@@
 
+It appeared there exist a kernel radius which minimised the type 2 error. So a large kernel radius is required for FDR control but too large can lose statistical power.
+
 \afterpage{\clearpage}
@@
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.png}
-        \caption{$z$ image with kernel of radius $r=120$}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHisto.png}
-        \caption{Histogram of $z$ in the kernel}
-      \end{subfigure}
-    }
-  \caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the test statistics captured by the kernel shows a bimodal distribution.}
-  \label{fig:inference_cornerSelect}
-\end{figure}
-
 The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}.
@@
 By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.
-It can be seen that the empirical null mean does change face to face, resulting in a clear boundary set by the edges.
+It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
 Most of false positives around the corners and edges have been eliminated.
+
+\begin{figure}[htp]
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.png}
+      \caption{$z$ image with kernel of radius $r=120$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHisto.png}
+      \caption{Histogram of $z$ in the kernel}
+    \end{subfigure}
+  }
+  \caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the test statistics captured by the kernel shows a bimodal distribution.}
+  \label{fig:inference_cornerSelect}
+\end{figure}
 
@@
 
-Clusters of significant pixels should raise suspicions.
-One could create a binary image, assigning a Boolean value whether that pixel is tested positive or not.
-A binary image filter, such as erode followed by a dilate, can be used to remove isolate significant pixels and emphasise the cluster of significant pixels.
-
-Robust statistics \citep{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}
+The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference.
+In the experiments, it was found that the FDR level is preserved after filtering.
+In experiments it was found that the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}.
+
+False positives do occur but this is unavoidable because tests were done at the 5\% FDR level.
+Typically in the experiments, false positives were isolated single pixels and probably occurred due to random chance.
+Clusters of positive pixels should raise suspicion.
+One could create a binary image, assigning a Boolean value whether that pixel was tested positive or not.
+A binary image filter, such as erode followed by a dilate, can be used to remove isolated positive pixels to emphasise the cluster of positive pixels.
+
+For good results, the faces of the 3D printed cuboid were segmented.
+This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly.
+Manual segmentation was easy to do because a cuboid has 6 faces.
+However, segmentation of faces cannot be generalised well to 3D printed samples with complicated geometry and curved surfaces.
+
+The main issue was how slow the filter was.
+Figure \ref{fig:inference_timing} shows the timings of the empirical null filter and the mean variance filter.
+For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.
+
+\begin{figure}[htp]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
+        \caption{Empirical null filter}
+      \end{subfigure}
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
+        \caption{Mean variance null filter}
+      \end{subfigure}
+    }
+  \caption{Timings when filtering a $256\times 256$ image. Note the y-axis change scale.}
+  \label{fig:inference_timing}
+\end{figure}
+
+There are a few strategies to accelerate the filter.
+The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \texttt{CUDA} and \texttt{C++} is fruitless if there may exist a faster method.
+Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation.
+The problem is that the assumption of a slow varying null parameter is required much more because of the use of interpolation, this may cause bigger problems due to the face to face transition observed in the experiments.
+It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbour pixels due to the interpolation.
+
+Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics.
+Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
+The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.
+However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
+
+The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
+Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
+On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.

### 2019-04-09 reports/paper1/paper.tex
Initial paper commit

--- 2019-03-25 reports/thesis/chapters/5_inference.tex
@@
-The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+\documentclass[twocolumn]{article}
+
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage{amsbsy}
+\usepackage{graphicx}
+\usepackage[outdir=./]{epstopdf}
+\usepackage[round]{natbib} 
+\usepackage{url}
+\usepackage{subcaption}
+\usepackage{hyperref}
+\usepackage{hyphenat}
+\usepackage{pdfpages}
+\usepackage{MnSymbol} %udots
+\usepackage{afterpage} %\afterpage{\clearpage}
+\usepackage{siunitx} %for measurements
+
+\setcounter{tocdepth}{2}
+\setcounter{secnumdepth}{2}
+
+\let\footruleskip\undefined
+\usepackage{fancyhdr}
+\pagestyle{plain}
+
+\DeclareMathOperator{\variance}{\mathbb{V}ar}
+\DeclareMathOperator{\normal}{N}
+\DeclareMathOperator*{\argmax}{argmax}
+
+\newcommand{\addNumber}[1]{\protect\input{#1}\unskip}
+\newcommand{\inputNumber}[1]{\protect\input{#1}\unskip}
+
+\title{Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays}
+\date{2019}
+\author{
+  Sherman Lo \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams \and Jason Warnett
+}
+
+\begin{document}\sloppy
+
+\maketitle
+
+\begin{abstract}
+X-ray computed tomography (CT) can be used for defect detection in additive manufacturing.
+The object is scanned at multiple angles to reconstruct the object in 3D space.
+The process can be time consuming.
+The aim is to investigate if it is possible to conduct defect detection from a single scan to speed up the quality control procedure.
+An experiment was conducted, a 3D printed sample was manufactured with voids to see if they can be detected.
+
+Software, \texttt{aRTist}, was used to simulate the scan and it was compared with the x-ray acquisition under the face of uncertainty.
+Each pixel was treated as a hypothesis test.
+The software, and the information provided to it, was not perfect which led to model misspecification and incorrect inference.
+The empirical null filter was proposed.
+It locally normalise each test statistic using robust estimators of the mean and deviation.
+This reduces the number of false positives.
+Sensible inference was achieved in the simulation and experiment.
+\end{abstract}
+
+\section{Introduction}
+
+Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}.
+The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
+The disadvantage of x-ray CT is that it involves calculations on acquisition of hundreds of angles of the sample.
+
+Speeding up the quality control process on the production line could be done by doing inspection on a few number of x-ray images \citep{warnett2016towards}.
+These x-ray images are compared with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
 \texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}.
-Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.
+Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods.
 
-Disagreement between the scan and \texttt{aRTist} can be found by subtracting one image from the other, any values too big in magnitude can be considered as a defect.
-However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance.
-Thus the comparisons should be done under the face of uncertainty.
+A method was proposed to compare the x-ray image with \texttt{aRTist} by treating the simulation of \texttt{aRTist} as the ground truth.
+This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
+Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
+This was necessary because the simulation of \texttt{aRTist} do not match up perfectly with the x-ray image, producing incorrect inference.
+The empirical null filter is demonstrated on simulated and real data.
 
-A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic is
+\section{Method}
+
+\subsection{Apparatus and Procedures}
+
+A ABS plastic cuboid (\SI{4}{\centi\metre} $\times$ \SI{4}{\centi\metre} $\times$ \SI{6}{\centi\metre}) with voids was purposefully manufactured to see if they can be detected.
+The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus} 3D printer.
+The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
+6 voids for each diameter were designed in the CAD.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly.
+The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.
+
+\begin{figure}[htp]
+  \centering
+  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
+  \caption{CAD of a 3D cuboid with voids; the scale shown is approximate.}
+  \label{fig:inference_testObject}
+\end{figure}
+
+The x-ray source used a tungsten filament with a copper filter.
+The current and voltage was set to \SI{250}{\micro\ampere} and \SI{80}{\kilo\volt} respectively.
+The exposure time was \SI{500}{\milli\second}.
+The x-ray detector is a \emph{Perkin Elmer XRD 1621 AN/CN} digital x-ray detector, producing a $2000\times 2000$ 16-bit image.
+Shading correction \citep{young2000shading, munzenmayer2003enhancing}, using a black image at \SI{0}{\kilo\volt} and a white image at \SI{80}{\kilo\volt}, were used to remove panel effects from the x-ray detector.
+
+The 3D printed sample was scanned 20 times.
+The 20 x-ray images were spilt into 2.
+19 random images were held out.
+The remaining image was used to compare with \texttt{aRTist}.
+In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.
+
+\subsection{Statistical Methodology}
+
+Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \texttt{aRTist}.
+A disagreement too big will classify that pixel as a positive result.
+A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels.
+This test statistic, together makes a $z$ image, is
 \begin{equation}
@@
 where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.
-Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal.
-Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
+
+The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}.
+The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample.
+These replicated x-ray images were manually segmented.
+This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model.
+The model used was a gamma distributed GLM \citep{nelder1972generalized, mccullagh1984generalized} with an identity link.
+The variance was predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable when working out the test statistics.
+
+It was assumed that the grey values were Normal, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
 \begin{equation}
-Z_{x,y}\sim \normal(0,1) \ .
+Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
 \end{equation}
-As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.
-
-The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample.
-These replicated x-ray images were manually segmented.
-This provided variance-mean data and was used to train the variance model, such as a gamma distributed GLM.
-The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
-The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.
-
-This method for inference was applied to the dataset \texttt{Sep16 120deg}.
-A cuboid (4 cm $\times$ 4 cm $\times$ 6 cm) with voids was purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}.
-The voids were of various diameters 2.4 mm, 1.2 mm, 0.6 mm and 0.3 mm.
-6 voids for each diameter were designed in the CAD.
-Voids with diameters 2.4 mm and 0.6 mm were regularly arranged, otherwise they were arranged irregularly.
-The precision of the manufacturing was in the order of $\pm0.1\text{ mm}$.
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
-  \caption{CAD of a 3D cuboid with voids; the scale shown is approximate.}
-  \label{fig:inference_testObject}
-\end{figure}
-
-The 20 x-ray images were spilt into 2.
-19 images were used to train the variance-mean model.
-One image, called the test image, was used to compare with \texttt{aRTist}.
-In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.
-The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
-
-\begin{figure}
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
-      \caption{X-ray image}
-      \label{fig:inference_inferenceIntro_inference_scan}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
-      \caption{\texttt{aRTist} simulation}
-      \label{fig:inference_inferenceIntro_inference_artist}
-    \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
-      \caption{$-\log p\text{-values}$}
-      \label{fig:inference_inferenceIntro_inference_pvalue}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
-      \caption{Positive pixels}
-      \label{fig:inference_inferenceIntro_inference_positivePixels}
-    \end{subfigure}
-  }
-  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids.
-The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level.
-Pixels detected as positive are shown in red in d).}
-  \label{fig:inference_inferenceIntro_inference}
-\end{figure}
-
-For each pixel, a test statistic was calculated.
-A test statistic too large in magnitude will classify that pixel as a positive result.
-In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
-\begin{equation}
-  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
-\end{equation}
-which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.
-
-The resulting $p$-values are concerning.
-This is because the $p$-values are not very smooth on the surfaces of the sample.
-It should be expected that small $p$-values are in areas of the defects.
-Pixels are tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$.
-This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure.
-The positive pixels are shown in Figure \ref{fig:inference_inferenceIntro_inference_positivePixels}.
-
-This proposed method for defect detection failed because too many false positives were detected.
-These false positives appear to have some structure, for example clustering in the corners or on surfaces.
-In addition, false negatives were detected because not all of the defects were detected.
-
-Model misspecification appeared to be the main source of error.
-The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}.
-It can be seen that the majority of the test statistics does not look Normal.
-Also the majority of the $p$-values does not look uniformly distributed.
-This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
-    \caption{Histogram}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
-    \caption{$p$-values}
-    \label{fig:inference_inferenceIntro_pvalue}
-  \end{subfigure}
-}
-  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution.
-The standard Normal distribution is known as the null distribution in this scenario.
-b) The $p$-values are ordered and plotted.
-The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure.
-The dotted line shows the result if the $p$-values were uniformly distributed.}
-  \label{fig:inference_inferenceIntro_histogram}
-\end{figure}
-
-This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test.
-Assumptions used on the hypothesis testing can be relaxed by using the empirical null \citep{efron2004large}, which is reviewed here.
-The empirical null is then extended to an image filter, called the empirical null filter.
-This filter adjust each test statistic according to its neighbours, ironing out false positive results.
-Simulations and results are shown towards the end of the chapter.
-
-\section{Literature Review}
-
-Consider a test statistic from a pixel.
-If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$.
-This can be described in another way by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$.
-A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$.
-A statistic which does not have the null distribution is known as non-null.
-
-In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example.
-A positive result is declared when $p<\alpha$, else it is a negative result.
-Correct and incorrect testing of the statistics can occur.
-For example testing a null statistic as positive is known as a false positive.
-It can be shown that $\alpha$ controls the false positive rate.
-$\alpha=5.0\%$ is a typical choice and was used throughout this thesis.
-Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.
-
-Multiple hypothesis testing occurs when there are more than one hypotheses to test.
-For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$.
-The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$.
-Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.
-
-The uncorrected test classify any $p_i<\alpha$ as positive.
-This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}.
-This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}.
-PCER is the proportion of false positives out of all tests.
-The number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}.
-Using the notation, PCER is defined as
-\begin{equation}
-  \text{PCER}=
-  \dfrac{1}{n}
-  \expectation[V]
-  \ .
-\end{equation}
-It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
-\begin{equation}
-  \text{PCER}\leqslant\alpha \ .
-\end{equation}
-
-\begin{table}[htp]
-  \centering
-  \begin{tabular}{c|c|c|c}
-    &Negative&Positive&Total\\\hline
-    Null & $U$ & $V$ & $n_0$\\
-    Non-null & $T$ & $S$ & $n-n_0$\\\hline
-    &$n-R$&$R$&$n$
-  \end{tabular}
-  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
-  \label{table:inference_randomvariables}
-\end{table}
-
-The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
-\begin{equation}
-  \text{FWER} = \prob(V\geqslant1) \ .
-  \label{eq:inference_fwer}
-\end{equation}
-This is done by adjusting the size of the test to be $\alpha/n$.
-By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$.
-Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$.
-This shows that the Bonferroni correction controls the family-wise error rate such that
-\begin{equation}
-  \text{FWER} \leqslant \alpha \ .
-\end{equation}
-However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives.
-This is because the correction traded too many false positives for false negatives.
-
-The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the PCER or FWER.
-The FDR is the proportion of false positives out of all positive results, that is
-\begin{equation}
-  \text{FDR} = \expectation\left[\dfrac{V}{R}\right]
-  \ .
-\end{equation}
-It is defined that $V/R=0$ when $R=0$.
-
-The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test.
-It adapts to the data and choose different sizes for different data.
-The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$.
-Suppose a size $\alpha$ is provided beforehand.
-The size is then adjusted to
-\begin{equation}
-  \alpha_{\text{BH}} = \frac{\alpha k}{n}
-\end{equation}
-where
-\begin{equation}
-  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
-  \ .
-\end{equation}
-This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive.
-For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
-For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.
-
-The BH procedure comes from the fact that if all the statistics are null and independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
-However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.
-It can be shown that the BH procedure controls the FDR such that
-\begin{equation}
-  \text{FDR}\leqslant\alpha
-\end{equation}
-\citep{benjamini1995controlling}.
-
-In summary, the uncorrected, Bonferroni and BH correction controls for different error rates according to the threshold $\alpha$, summarised in Table \ref{table:inference_corrections}.
-
-\begin{table}[htp]
-    \centering
-    \begin{tabular}{c|c}
-        Correction&Controls for\\\hline
-        No correction&$\text{PCER}\leqslant\alpha$\\
-        Bonferroni&$\text{FWER}\leqslant\alpha$\\
-        BH&$\text{FDR}\leqslant\alpha$
-    \end{tabular}
-    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
-    \label{table:inference_corrections}
-\end{table}
-
-Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}.
-The distribution of the test statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$.
-Almost half of the pixels were tested positive.
-It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
-      \caption{Test statistics}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
-      \caption{Histogram of test in sub-image}
-    \end{subfigure}
-    }
-    \caption{The resulting $z$ image is shown in a).
-A $200\times 200$ sub-image was taken shown by the dashed lines.
-A histogram of the test statistics in the sub-image is shown in b).
-The critical region was obtained by using the BH procedure at the 5\% FDR level.}
-    \label{fig:inference_inferenceSubsample1_histogram}
-\end{figure}
-
-This problem commonly occur in large scale multiple hypothesis testing \citep{efron2004large} such as in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
-It appears that the null distribution was misspecified as $Z_i|H_{0,i}\sim\normal(0,1)$ when in reality they are distributed as $Z_i|H_{0,i}\sim\normal(\mu_0,\sigma_0^2)$, where $\mu_0$ and $\sigma_0$ are the null mean and null standard deviation respectively.
-
-In practice $\mu_0$ and $\sigma_0$ are unknown.
-The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate.
-Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively.
-The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\cdots,n$.
-
-In \cite{efron2004large}, a few assumptions were made in order to obtain the estimators $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Let the test statistic $Z$ have the p.d.f.
-\begin{equation}
-  p_Z(z) =
-  \pi_0 p_{Z|H_0}(z) + \pi_1 p_{Z|H_1}(z)
-\end{equation}
-where $0\leqslant\pi_0\leqslant 1$ and  $\pi_1 = 1-\pi_0$. In addition, the null distribution is
-\begin{equation}
-  p_{Z|H_0}(z) = 
-  \dfrac{1}{\sqrt{2\pi}\sigma_0}
-  \exp\left[
-    -\dfrac{1}{2}
-    \left(
-      \dfrac{z-{\mu}_0}{\sigma_0}
-    \right)^2
-  \right]
-\end{equation}
-as it was assumed to be Normal.
-The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified.
-Assume that the majority of the data are null and non-null test statistics are rare, say $\pi_0>0.9$ \citep{efron2004large}.
-Then around the mode, the probability density function would be dominated by the null distribution.
-This implies that
-\begin{equation}
-  p_{Z}(z) \approx \pi_0 p_{Z|H_0}(z)
-\end{equation}
-for values of $z$ around the mode.
-Finding the mode for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution.
-This justify the use of the mode for the empirical null mean \citep{efron2004large}
-\begin{equation}
-  \widehat{\mu}_0 = \argmax\widehat{p}_Z(z)
-\end{equation}
-where $\widehat{p}_Z(z)$ is the density estimation of $p_Z(z)$, for example it could be a smoothing spline fitted onto the histogram \citep{efron2004large}.
-
-The null standard deviation is estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
-\begin{equation}
-  \ln p_{Z}(z) = 
-  \ln\left[
-    \dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
-  \right]
-  -\dfrac{1}{2}
-  \left(
-    \dfrac{z-{\mu}_0}{{\sigma}_0}
-  \right)^2
-  \ .
-\end{equation}
-Taking derivatives
-\begin{equation}
-  \dfrac{\partial}{\partial z} \ln p_{Z}(z) =
-  -\left(
-    \dfrac{
-      z-{\mu}_0
-    }
-    {
-      {\sigma}_0^2
-    }
-  \right)
-\end{equation}
-\begin{equation}
-  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) =
-  -\dfrac{
-    1
-  }
-  {
-    {\sigma}_0^2
-  }
-\end{equation}
-which motivates the estimator \citep{efron2004large}
-\begin{equation}
-  \widehat{\sigma}_0 = \left[
-    \left.
-      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
-    \right|_{z=\widehat{\mu}_0}
-  \right]^{-1/2}
-  \ .
-\end{equation}
-The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.
-
-This method does not need estimations of $\pi_0$ which makes it quite convenient.
-The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}.
-\cite{efron2004large} motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.
-
-The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
-There exist various methods for the empicial null.
-\cite{schwartzman2008empirical} uses Poisson regression on the histogram counts in regions where the null statistics dominate.
-The empirical characteristic function was used in \cite{jin2007estimating}.
-
-\section{Empirical Null}
-
-Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
-The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
-The kernel density estimate \citep{parzen1962on} is
-\begin{equation}
-  \widehat{p}_Z(z)=
-  \frac{1}{nh}
-  \sum_{i=1}^n\phi\left(
-    \dfrac{z_i-z}{h}
-  \right)
-  \label{eq:inference_kernel_density_estimate}
-\end{equation}
-where $h$ is the bandwidth. The bandwidth was chosen such that
-\begin{equation}
-  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_z,\text{IQR}_z/1.34\right)
-  \label{eq:inference_ourruleofthumb}
-\end{equation}
-where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range.
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
-  \caption{The density of the test statistics was estimated using a kernel density estimate.
-The dot dash lines show the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
-  \label{fig:inference_inferenceSubsample1_densityEstimate}
-\end{figure}
-
-The null parameters were estimated.
-The null mean was estimated by numerically finding the mode of the density estimate.
-The null standard deviation was estimated using the curvature of the density estimate at the mode.
-This resulted in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
-In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.
-
-The use of the kernel density estimate has its advantages.
-The only tuning parameter is the bandwidth $h$ and the density estimate is simple enough to do calculus on it.
-Speed may be an issue as an evaluation of the density estimate requires the sum over the $n$ test statistics.
-
-The test statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
-\begin{equation}
-  T_i = \dfrac{
-    Z_i - \widehat{\mu}_0
-  }
-  {
-    \widehat{\sigma}_0
-  }
-  \label{eq:inference_empiricalNullNormalise}
-\end{equation}
-for $i=1,2,\cdots,n$. The normalised $p$-values were obtained by using
-\begin{equation}
-  p_i = 2(1-\Phi(|t_i|))
-\end{equation}
-and then were used in the BH procedure.
-The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$.
-In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places.
-The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullHistogram.eps}
-        \caption{Histogram of $z$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullPValues.eps}
-        \caption{$p$ values}
-    \end{subfigure}
-    }
-    \caption{The critical regions and $p$-values were adjusted using the empirical null in the sub-image example.}
-    \label{fig:inference_inferenceSubsample1_nullResults}
-\end{figure}
-
-No positive results were found and the $p$-values were sensible as they looked uniformly distributed.
-This demonstrated that the empirical null adjusted the parameters of the null distribution to fit the majority of the data in order to make sensible inference.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_zImage.eps}
-        \caption{test statistics}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_subimagePositive.eps}
-        \caption{$z$ from the sub-image}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullHistogram.eps}
-        \caption{Histogram of $z$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullPValues.eps}
-        \caption{$p$ values}
-    \end{subfigure}
-    }
-    \caption{A $200\times 200$ sub-image containing a defect is shown in a).
-The empirical null was used to test pixels, positive pixels are shown in red in b).
-The histogram of the test statistics are shown in c) along with the critical region.
-The normalised $p$-values are shown in d).
-The critical regions were adjusted using the empirical null and obtained using the BH procedure at the 5\% FDR level.}
-    \label{fig:inference_inferenceSubsample2}
-\end{figure}
-
-Another example is shown in Figure \ref{fig:inference_inferenceSubsample2} where a $200\times 200$ sub-image containing a defect was used.
-It can be seen that the null distribution was not centred at zero, however the empirical null took it into account.
-The estimation of the empirical null parameters were robust as it only depended on the density estimate at the mode only, it should not be affected by non-null test statistics.
-
-The BH procedure was conducted using the normalised $p$-values.
-$\inputNumber{../figures/inference/inferenceSubsample2_nPositive.txt}$ pixels were tested positive.
-The majority of the positive pixels were found to be clustered together, which highlighted the defect.
-Not all of the defects were tested positive, but a good number of them are.
-This should be enough to raise suspicion in that particular area.
-Only a few pixels were falsely tested as positive, however they are typically isolated single pixels.
-Isolated positive pixels should be discarded as they are more than likely to be tested positive by random chance.
-
-This section describes the empirical null implementation in detail, in particular the numerical and computational aspects.
-The empirical properties of the sampling distribution of the null parameter estimators were studied.
-
-\subsection{Mode Finding}
-
-The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$.
-This cannot be solved in closed form easily and was done numerically.
-The  Newton-Raphson method can be used to solve $\hat{p}_Z'(z) = 0$ for $z$.
-Instead the log space was used, solving
-\begin{equation}
-  \dfrac{
-    \partial
-  }
-  {
-    \partial z
-  }
-  \ln\widehat{p}_Z(z)
-  = 0
-\end{equation}
-for $z$. This at least find stationary points.
-
-The Newton-Raphson method is an iterative algorithm and requires an initial value $z^{(0)}$. The iterative step is
-\begin{equation}
-  z^{(r+1)} =
-  z^{(r)}
-  -\dfrac{
-    \left.
-      \dfrac{
-        \partial
-      }
-      {
-        \partial z
-      }
-      \ln\widehat{p}_Z(z)
-    \right|_{z = z^{(r)}}
-  }
-  {
-    \left.
-      \dfrac{
-        \partial^2
-      }
-      {
-        \partial z^2
-      }
-      \ln\widehat{p}_Z(z)
-    \right|_{z = z^{(r)}}
-  } 
-\end{equation}
-for $r=0,1,2,3,\cdots$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is $\widehat{p}_Z(z)=
-  \frac{1}{nh}
-  \sum_{i=1}^n\phi\left(
-    \frac{z_i-z}{h}
-  \right) $
-so that the log density is
-\begin{equation}
-  \ln\widehat{p}_Z(z)=
-  \ln\left(
-    \dfrac{1}{nh}
-  \right)
-  +
-  \ln\left[
-    \sum_{i=1}^n
-    \phi\left(
-      \dfrac{
-        z_i - z
-      }
-      {
-        h
-      }
-    \right)
-  \right]
-  \ .
-\end{equation}
-Taking the first derivative
-\begin{equation*}
-  \dfrac{
-    \partial
-  }
-  {
-    \partial z
-  }
-  \ln\widehat{p}_Z(z)
-  =
-  \dfrac{
-    1
-  }
-  {
-    \sum_{i=1}^n
-    \phi\left(
-      \dfrac{
-        z_i - z
-      }
-      {
-        h
-      }
-    \right)
-  }
-  \times
-  \sum_{i=1}^n
-  \phi'\left(
-    \dfrac{
-      z_i - z
-    }
-    {
-      h
-    }
-  \right)
-  \left(
-    -\dfrac{
-      1
-    }
-    {
-      h
-    }
-  \right)
-  \ .
-\end{equation*}
-Using the fact that $\phi(z)=(2\pi)^{-1/2}\exp(-z^2/2)$, then $\phi'(z)=-z\phi(z)$. This is used to simplify the equation to be
-\begin{equation}
-  \dfrac{
-    \partial
-  }
-  {
-    \partial z
-  }
-  \ln\widehat{p}_Z(z)
-  =
-  \dfrac{
-    \sum_{i=1}^n
-    \phi\left(
-      \dfrac{
-        z_i - z
-      }
-      {
-        h
-      }
-    \right)
-    \left(
-      \dfrac{
-        z_i - z
-      }
-      {
-        h
-      }
-    \right)
-  }
-  {
-    h
-    \sum_{i=1}^n
-    \phi\left(
-      \dfrac{
-        z_i - z
-      }
-      {
-        h
-      }
-    \right)
-  }
-  \ .
-\end{equation}
-Taking the derivative again
-\begin{multline*}
-  \dfrac{
-    \partial^2
-  }
-  {
-    \partial z^2
-  }
-  \ln\widehat{p}_Z(z)
-  =
-  \left[
-    h\sum_{i=1}^n
-    \phi\left(
-      \dfrac{
-        z_i-z
-      }
-      {
-        h
-      }
-    \right)
-  \right]^{-2}
-  \times
-  \left\{
-    h\left[
-      \sum_{i=1}^n
-      \phi\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-    \right]
-  \right.
-  \\
-  \left.
-    \times
-    \sum_{i=1}^n\left[
-      \phi'\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-      \left(
-        -\dfrac{
-          1
-        }
-        {
-          h
-        }
-      \right)
-      \left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-      +\phi\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-      \left(
-        -\dfrac{
-          1
-        }
-        {
-          h
-        }
-      \right)
-    \right]
-  \right.
-  \\
-  \left.
-    -
-    \left[
-      \sum_{i=1}^n
-      \phi\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-      \left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-    \right]
-    \left[
-      h\sum_{i=1}^n
-      \phi'\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-      \left(
-        -\dfrac{
-          1
-        }
-        {
-          h
-        }
-      \right)
-    \right]
-  \right\}
-  \ .
-\end{multline*}
-Using the fact that $\phi'(z)=-z\phi(z)$, then it is simplified to
-\begin{multline}
-  \dfrac{
-    \partial^2
-  }
-  {
-    \partial z^2
-  }
-  \ln\widehat{p}_Z(z)
-  =
-  \left[
-    h\sum_{i=1}^n
-    \phi\left(
-      \dfrac{
-        z_i-z
-      }
-      {
-        h
-      }
-    \right)
-  \right]^{-2}
-  \times
-  \left\{
-    \left[
-      \sum_{i=1}^n
-      \phi\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-    \right]
-  \right.
-  \\
-  \left.
-    \times
-    \left[
-      \sum_{i=1}^n
-      \phi\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-      \left(
-        \left(
-          \dfrac{
-            z_i-z
-          }
-          {
-            h
-          }
-        \right)^2
-        -1
-      \right)
-    \right]
-    -
-    \left[
-      \sum_{i=1}^n
-      \phi\left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-    \right.
-  \right.
-  \\
-  \left.
-    \left.
-      \left(
-        \dfrac{
-          z_i-z
-        }
-        {
-          h
-        }
-      \right)
-    \right]^2
-  \right\}
-  \ .
-\end{multline}
-
-A convergence criteria was met when either 10 update steps were taken or when
-\begin{equation}
-  \log\left[\left|
-    \left.
-    \dfrac{
-      \partial
-    }
-    {
-      \partial z
-    }
-  \ln\widehat{p}_Z(z)
-  \right|_{z=\widehat{\mu}_0}
-  \right|\right]
-  <-5
-\end{equation}
-at the current step. This was chosen arbitrary to speed up the algorithm without losing too much accuracy. At the end of the algorithm, for a successful convergence it was required, in addition, that
-\begin{equation}
-  \left.
-    \dfrac{
-      \partial^2
-    }
-    {
-      \partial z^2
-    }
-    \ln\widehat{p}_Z(z)
-  \right|_{z=\widehat{\mu}_0}
-  < 0 \ .
-\end{equation}
-Following a successful convergence, the estimator $\widehat{\sigma}_0$ was calculated straight away.
-
-The algorithm does depend on the initial value so using different initial values were used.
-Further initial values were generated by sampling from $\normal(z^{(0)}, s_z^2)$.
-This was done multiple times until 3 valid solutions were obtained.
-The best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of all the different initial values was used as the final answer.
-The Newton-Raphson method can fail if it converges to a stationary point other than a global maximum, for example a local maximum or a point of inflection.
-
-\subsection{Bandwidth Tuning}
-
-The bandwidth $h$ controls how smooth the kernel density estimator is, higher values producing smoother curves \citep{friedman2001elements}.
-Cross validation methods to select $h$ do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
-Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are typically of the form
-\begin{equation}
-  h = bn^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right)
-\end{equation}
-where $b=0.9$ \citep{silverman1986density}.
-This rule of thumb was developed with consideration of bimodal Normal distributions \citep{silverman1986density}.
-Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{silverman1986density, sheather2004density}.
-
-The kernel density estimator was only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$.
-Thus a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate.
-Exact properties of these estimators based on the kernel density estimators can be rather complicated.
-For example numerous approximations were needed to show that $\widehat{\sigma}_0^2$ is an unbiased estimator of $\sigma_0^2$ to the first order, where higher order terms are functions of $(\widehat{\mu}_0 - \mu_0)^2$ and $h$.
-This is shown in Appendix \ref{chapter:appendix_expectationNullStdEstimator}.
-
-An experiment was conducted to investigate how the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, varied with $h$ and $n$.
-This was done on a simulated dataset of $n$ standard Normal random variables.
-For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation of the dataset.
-The median squared error was obtained by taking the median over all squared errors from the 100 estimates.
-Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors.
-
-$\widehat{\mu}_0$ has low median squared error for large bandwidths.
-For low $n$, large bandwidths are particularly useful because smoother curves prevent any false bimodal features appearing, making it easier to find the mode.
-
-A smooth valley can be seen for the median squared error for $\widehat{\sigma}_0$.
-It appeared for a given $n$, there exist a bandwidth which minimise the median squared error.
-However the rules of thumb did not optimise for $\widehat{\sigma}_0$ and undershot it.
-Figure \ref{fig:inference_BandwidthSelection_error3} shows the median of the estimates of $\sigma_0$.
-The true value in this simulation is $\sigma_0=1$ which is represented as a horizontal plane.
-Bandwidths too small underestimated $\sigma_0$, bandwidths too big overestimated $\sigma_0$.
-
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
-      \caption{$\mu_0$}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
-      \caption{$\sigma_0$}
-  \end{subfigure}
-  \caption{Median squared error of the estimators of the empirical null parameters from 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
-  \label{fig:inference_BandwidthSelection_error}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error3.eps}
-        \caption{Heatmap}
-    \end{subfigure}
-    \caption{Median value of $\widehat{\sigma}_0$ from 100 repeats of $n$ simulated standard Normal data. The true value is $\sigma_0=1$ which is represented by a horizontal plane.}
-    \label{fig:inference_BandwidthSelection_error3}
-\end{figure}
-
-Overestimates and underestimates are both dangerous and it can affect the false positive and false negative rate.
-This is because $\widehat{\sigma}_0$ was used to rescale the test statistics accordingly.
-Recall that the normalised test statistics are $t_i = \dfrac{z_i - \widehat{\mu}_0}{\widehat{\sigma}_0}$.
-Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $t_i$, potentially testing more of these test statistics as positive.
-High values of $\widehat{\sigma}_0$ does the opposite.
-Large number of positives can led to more false positives and vice versa.
-
-The optimal bandwidth for a given $n$ was found numerically.
-Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $n$.
-A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimised the log squared error for a given $n$.
-\texttt{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures.
-The optimisation was done using \texttt{MATLAB}'s gradient free \texttt{fminsearch} function, using $h=0.9n^{-1/5}$ as the initial value.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot1.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot51.eps}
-    \end{subfigure}
-    }
-    \medskip
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot100.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot150.eps}
-    \end{subfigure}
-    }
-    \medskip
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot199.eps}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot249.eps}
-    \end{subfigure}
-    }
-    \caption{A smoothing spline was fitted on the log squared error for estimating $\sigma_0$ against the bandwidth.
-Boxplots represent the variation of the error from 100 repeats.
-The red dashed line shows the bandwidth which minimised the fitted spline.}
-    \label{fig:inference_BandwidthSelection2_plot}
-\end{figure}
-
-A relationship between the optimal bandwidth and $n$ was attempted to be found. It was assumed such a relationship has the linear from
-\begin{equation}
-  h_{\text{optimal}} = b n^{-1/5} + a
-\end{equation}
-where $b$ and $a$ are parameters to be fitted.
-This was chosen to establish a simple relationship with the rules of thumb.
-Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} show the fitting of an identity link gamma GLM in order to estimate $b$ and $a$.
-The estimated parameters are shown in Table \ref{table:inference_BandwidthSelection2_ruleOfThumb}.
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.7\textwidth]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
-  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 95\% prediction interval.}
-  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
-\end{figure}
-
-\begin{table}[htp]
-  \centering
-  \input{../figures/inference/BandwidthSelection2_bandwidthEstimate.txt}
-  \caption{Estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
-  \label{table:inference_BandwidthSelection2_ruleOfThumb}
-\end{table}
-
-The rules of thumb can be improved if a small bias is added to it.
-This is because an intercept was found when fitting a linear relationship between the optimal bandwidth and $n^{-1/5}$.
-Adding this bias should improve the performance of the estimator $\widehat{\sigma}_0$.
-The gradient is similar to the rules of thumb in the literature \citep{sheather2004density}.
-
-The GLM fit in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} appeared to underfit, which suggest there may be a more complicated relationship between the optimal bandwidth and $n$.
-The method used in fitting the smoothing spline could contribute to the underfitting.
-For example if the smoothing spline was not smooth enough so that local minima appeared, it would add variance to the location of the optimal bandwidth.
-A basic linear relationship was chosen to avoid overfitting and keep the rule of thumb simple.
-
-In conclusion, a small bias added to the rule of thumb improved the performance of the estimator $\widehat{\sigma}_0$.
-\cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggested the use of $b=0.9$.
-Following from this, it was chosen that the intercept was added to Silverman's rule of thumb for the use in the empirical null $h = \left(0.9n^{-1/5}+ 0.16\right) \times\text{min}\left(s_z,\text{IQR}_z/1.34\right)$.
-
-\afterpage{\clearpage}
-\subsection{Sampling Distribution Experiments}
-
-Various estimators of central tendency and dispersion were compared with the empirical null estimates of the null mean and null standard deviation.
-The empirical sampling distribution of these estimators were observed to look for properties such as bias, variance and robustness.
-The central tendency looked at were the median and mean.
-The dispersions looked at were the median absolute deviation (MAD) around the mode $\times 1.4826$, interquartile range (IQR) $\div 1.349$ and the standard deviation.
-The normalisation constants were used so that the MAD and IQR can be compared directly to the standard deviation.
-
-A dataset of $n = \pi r^2$ standard Normal random variables were simulated to obtain estimates of central tendency and dispersion.
-This was repeated 100 times to obtain a sampling distribution.
-The results are shown in Figures \ref{fig:inference_NullIidMean} and \ref{fig:inference_NullIidStd}.
-The empirical null mean and empirical null standard deviation estimations both suffered from high variance, much higher than typical robust estimators such as the median and IQR.
-
-The empirical null standard deviation had some positive bias and it was found that this bias was quite sensitive to the bandwidth.
-Further fine tuning on the bandwidth would be required for the empirical null standard deviation to be unbiased.
-For example it appeared there was consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
-The source of bias could come from the fact that the bandwidth was tuned to minimise the mean squared error rather than the squared bias.
-
-To test for robustness, a dataset of $n = \pi r^2$ mixture of Gaussian random variables were simulated with the following distribution: $\normal(0,1)$ with probability $90\%$, $\normal(3,1)$ with probability $10\%$.
-The $\normal(3,1)$ component acts as non-null statistics and robust estimators should be unaffected by it.
-The results are shown in Figures \ref{fig:inference_NullIidMixtureMean} and \ref{fig:inference_NullIidMixtureStd}.
-The empirical null estimators are robust to the non-null component but still suffers from high variance.
-The rest of the estimators were affected by the non-null statistics, making them unsuitable to estimate parameters of the null component.
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullMean.eps}
-        \caption{Median}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullMean.eps}
-        \caption{Mean}
-      \end{subfigure}
-    }
-  \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
-  \label{fig:inference_NullIidMean}
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
-        \caption{Empirical null std.}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMadMode_nullStd.eps}
-        \caption{MAD mode}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullStd.eps}
-        \caption{IQR}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullStd.eps}
-        \caption{Standard deviation}
-      \end{subfigure}
-    }
-  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
-  \label{fig:inference_NullIidStd}
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullMean.eps}
-        \caption{Median}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullMean.eps}
-        \caption{Mean}
-      \end{subfigure}
-    }
-  \caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables.
-The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
-  \label{fig:inference_NullIidMixtureMean}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
-        \caption{Empirical null std.}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMadMode_nullStd.eps}
-        \caption{MAD mode}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullStd.eps}
-        \caption{IQR}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullStd.eps}
-        \caption{Standard deviation}
-      \end{subfigure}
-    }
-  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables.
-The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
-  \label{fig:inference_NullIidMixtureStd}
-\end{figure}
-
-\afterpage{\clearpage}
-\section{Empirical Null Filter}
-
-Returning back to the example at the start of the chapter, the empirical null could be used on the histogram shown in Figure \ref{fig:inference_inferenceIntro_histogram}.
-The resulting empirical null distribution is shown in Figure \ref{fig:inference_inferenceSubsampleAll}.
-The empirical null distribution had a very large standard deviation and would test all pixels as negative, this is incorrect.
-
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
-    \caption{Test statistics}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
-    \caption{Empirical null fitted onto histogram}
-  \end{subfigure}
-  \caption{The resulting test statistics are shown in a).
-The density estimate of the statistics is shown in b).
-The empirical null distribution multiplied by some constant is also plotted in b); this is to illustrate the curvature is the same as the density estimate at the mode.}
-  \label{fig:inference_inferenceSubsampleAll}
-\end{figure}
-
-The problem was that the empirical distribution of the test statistics did not look Normal.
-It appeared that the test statistics varied spatially, suggesting the empirical null varied spatially as well.
-One possible reason is because it looked like the value of the test statistics depended on which surface it was on for example.
-
-One possible extension to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
-There are problems with this though.
-The first problem is that how the grid is overlaid can be arbitrary, for example the grid can be translated to produce different sections.
-Secondly it is not clear how to combine the results from each section together \citep{efron2008simultaneous}.
-
-The empirical null filter extends the empirical null to images.
-The parameters of the null distribution varies spatially, slowly and smoothly in 2D space.
-Let the test statistic of the pixel at position $(x,y)$ be
-\begin{equation}
-Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{x,y}^2)
-\end{equation}
-for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Define the null hypotheses to be
+for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$.
+$\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively.
+Their estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ also respectively.
+Define the null hypotheses to be
 \begin{equation}
@@
 \end{equation}
- The empirical null filter aims to estimate the parameters $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ for all $x$ and $y$.
+The empirical null filter aims to obtain the estimators $\widehat{\mu}
+_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large}.
 
-The empirical null filter uses the empirical null on neighbouring pixels to estimate the null parameters.
-To estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel of radius $r$ was centred at $(x,y)$.
-All the pixels captured by the circular kernel were used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
-\begin{align}
-  \widehat{\mu}_{0,x,y}
-  &=
-  \widehat{\mu}_{0,x,y}
-    \left(
-      \text{all }Z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
+To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$.
+All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{parzen1962on, friedman2001elements}
+\begin{equation}
+\widehat{p}_{Z_{x,y}}(z) = 
+\frac{1}{nh}
+  \sum_{i,j\in K_{x,y}}\phi\left(
+    \dfrac{z_{i,j}-z}{h}
   \right)
-\\
-  \widehat{\sigma}_{0,x,y}
-  &=
-  \widehat{\sigma}_{0,x,y}
-    \left(
-      \text{all }Z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
-    \right)
-  \ .
-\end{align}
-Using these estimates, the test statistics were normalised using
+\end{equation}
+where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth.
+The bandwidth was chosen such that
+\begin{equation}
+  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
+  \label{eq:inference_ourruleofthumb}
+\end{equation}
+where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of pixels in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}.
+The estimates were obtained by solving
+\begin{equation}
+\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
+\end{equation}
+using the Newton-Raphson method and
+\begin{equation}
+  \widehat{\sigma}_{0,x,y} = \left[
+    \left.
+      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
+    \right|_{z=\widehat{\mu}_{0,x,y}}
+  \right]^{-1/2}
+\end{equation}
+\citep{efron2004large}. The test statistics were normalised using
 \begin{equation}
@@
     \widehat{\sigma}_{0,x,y}
-  }
+  } \ .
 \end{equation}
-and only the normalised test statistics were used in hypothesis testing. It should be noted that because the kernels can overlap, correlation between $T_{x,y}$ for different $(x,y)$ is introduced.
+All the normalised test statistics were converted to $p$-values
+\begin{equation}
+  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
+\end{equation}
+and was used in the \cite{benjamini1995controlling} (BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.
 
-The parameter of choice is the kernel radius $r$.
-A $r$ too small will treat defects as the null and will not detect them.
-A $r$ too big can also cause problems as well.
-The empirical null filter assumes that the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal.
-If $r$ is too big, the kernel will capture far away test statistics with a very different null distribution.
-If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution.
-Furthermore, if $r\rightarrow \infty$, then this is just using the empirical null on all pixels.
+\subsection{Software Development}
 
-$r$ control the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$.
-$r$ should be selected so that $\pi_0$ is of a sensible value, for example $>90\%$.
-In practice, the defects are unknown so various kernel radiuses should be tried out.
-In general, the kernel radius should be much larger than the size of the defect.
+The empirical null filter was implemented using \texttt{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}.
 
-There exist similar filters, for example the local normalization filter \citep{sage2003teaching, sage2018local} uses a Gaussian filter to obtain $\widehat{\mu}_{0,x,y}$.
-$\widehat{\sigma}_{0,x,y}^2$ was obtained by applying another Gaussian filter on the $\left(z_{x,y}-\widehat{\mu}_{0,x,y}\right)^2$ image.
-The purpose of this filter was to normalise images with uneven illumination.
-The disadvantage of using the local normalization filter for estimating the null parameters is that it uses a Gaussian filter.
-This is a type weighted mean which won't be robust to non-null statistics.
-In addition, the two Gaussian filters can have different radiuses, it is not clear how to set them.
+\section{Simulation}
 
-\subsection{Design and Implementation}
+The empirical null filter was tested to see if it can detect simulated defects from a $256\times 256$ contaminated image.
+A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
+For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
+A $30\times 30$ square defect was simulated.
+A kernel can capture the entire defect if its radius is large enough.
 
-The empirical null filter was implemented in an open source software called \texttt{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \texttt{GitHub} \citep{imagej2018rank}.
-This class implemented filters, such as the mean filter and median filter, using a circular kernel, making this a suitable framework for the empirical null filter.
-Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \texttt{Fiji} \citep{schindelin2012fiji}, a distribution of \texttt{ImageJ}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{../figures/inference/fiji/gui.png}
-    \caption{Graphical user interface of the empirical null filter in \texttt{Fiji}.
-The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate.
-By-products such as the empirical null parameters can be shown after the filtering as well.}
-    \label{fig:inference_fijiGui}
-\end{figure}
-
-As a test, the empirical null filter with $r=5$ was used on a \texttt{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
-It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it did verify that the filter worked on arbitrary images with some computational considerations.
-The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all ${x,y}$ could be of interest.
-In particular the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}.
-Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters.
-The empirical null mean created an impasto effect and preserved edges which is similar to the result in \cite{griffin2000mean}.
-Spread filters such as the standard deviation filter can be used to detect edges.
-Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation.
-The resulting images were similar but it was notable that the edges in the empirical null standard deviation were sharper, suggesting that the empirical null standard deviation is a more robust measure of spread compared to the standard deviation.
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
-        \caption{Before filtering}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridgeFilter.png}
-        \caption{After filtering}
-    \end{subfigure}
-    }
-    \caption{Empirical null filter with $r=5$ on the sample image \texttt{bridge.gif}.}
-    \label{fig:inference_fijiBridgeFilter}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
-        \caption{No filter}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/mean.png}
-        \caption{Mean filter}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/median.png}
-        \caption{Median filter}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullMean.png}
-        \caption{Empirical null mean}
-    \end{subfigure}
-    }
-    \caption{Various average filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}}
-    \label{fig:inference_fijiMean}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/std.png}
-        \caption{Standard deviation filter}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullStd.png}
-        \caption{Empirical null standard deviation}
-    \end{subfigure}
-    }
-    \caption{Various spread filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
-    \label{fig:inference_fijiStd}
-\end{figure}
-
-When using the the empirical null filter in \texttt{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
-Here the user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
-The menu also has options for by-product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, and quartile filters.
-Advanced options are available to the user.
-The number of initial values set the number of valid solutions to be found in the Newton-Raphson method on finding the mode of the density estimate.
-The user can also set the maximum number of steps and tolerance for the Newton-Raphson method.
-The bandwidth parameters for the kernel density estimate can also be adjusted here.
-
-Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design had already been done.
-\texttt{RankFilters} contain implementations of filters such as the mean filter and median filter.
-The implementation uses multiple threads, each thread filters a row in parallel.
-This was done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache.
-Then for each column, the thread does calculations using the cache then replaces the pixel value of the image to be filtered with the resulting calculation.
-Once the row has been filtered, the thread then moves onto the next unfiltered row.
-Rows in the cache not needed are overwritten with more recent rows.
-
-When the kernel captures pixels outside the boundary of the image or region of interest (ROI), \texttt{RankFilters} uses nearest pixel padding which fills in pixels outside the ROI with values to the nearest pixels.
-Figure \ref{fig:inference_padding_nearest} shows an example of nearest pixel padding on the top left corner of a rectangle ROI.
-This is not suitable for the empirical null filter as this will cause bias in the density estimation.
-The empirical null filter used \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}.
-This indicate that these pixels are outside the ROI and are ignored.
-The number of non-\texttt{NaN} captured by the kernel was kept track for calculations such as the bandwidth.
-
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
-      \begin{tabular}{lllllll}
-         $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
-         $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
-         $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\ \cline{4-6}
-         $\cdots$ & $z_{1,1}$ & \multicolumn{1}{l|}{$z_{1,1}$} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
-         $\cdots$ & $z_{2,1}$ & \multicolumn{1}{l|}{$z_{2,1}$}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
-         $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
-    \end{tabular}
-    \caption{Nearest pixel padding}
-    \label{fig:inference_padding_nearest}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-      \begin{tabular}{lllllll}
-         $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
-         $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\
-         $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\ \cline{4-6}
-         $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
-         $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
-         $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
-    \end{tabular}
-    \caption{\texttt{NaN} padding}
-    \label{fig:inference_padding_nan}
-  \end{subfigure}
-  \caption{When a kernel contain pixels outside the region of interest as shown by the solid line, the missing pixels can either be extrapolated using the nearest pixel or completely ignored by filling in the missing pixels with \texttt{NaN}.}
-  \label{fig:inference_padding}
-\end{figure}
-
-Line filtering was done from left to right.
-At the start on the far left, an initial value of the median of all the pixels in the kernel was used.
-In addition, various initial values were randomly tried out until a requested number of valid solutions were found.
-For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as a initial point.
-This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
-
-When filtering arbitrary images such as \texttt{bridge.gif}, a few computational considerations were needed.
-\texttt{bridge.gif} is an 8-bit image so values were represented as integers.
-This opened up opportunities for the inter-quartile range and the standard deviation to be zero, this caused problems as this set the bandwidth to be zero.
-When the standard deviation is zero, it was set to $0.289$ which corresponds to the standard deviation of a uniform random variable.
-When the inter-quartile range is zero, the inter-quartile range was set to the standard deviation $\times 1.34$.
-
-When the number of initial values is too few, poor solutions to $\widehat{\mu}_0$ are uncommon which then propagate to the pixel to the right and used as its initial value.
-Poor initial values could cause the Newton-Raphson method to never converge.
-If the Newton-Raphson method failed to converge too many times, the median is used as the new initial value.
-Should it fail too, the program gives up and puts a $\texttt{NaN}$ in that pixel.
-
-\subsection{All-null Experiment}
-
-An experiment was conducted to demonstrate the effects of the empirical null filter on a simulated $256\times 256$ Gaussian image, where all the pixels have value distributed as standard Normal.
-The purpose is to simulate test statistics which are null and ideally no positive results should be detected.
-The test statistics after filtering should preserve its original distribution, or at least close to it.
-The statistical moments before and after filtering should be the same and were investigated.
-Because the empirical null mean and empirical null standard deviation are random variables with some distribution, the filtered pixels will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
-
-\emph{Contamination} is defined as some smooth and slowly varying function added and/or multiplied to an image.
-When contaminating a Gaussian image, it may cause errors in hypothesis testing if the null distribution was incorrectly specified as standard Normal.
-In this experiment, the contamination was a gradient such that the pixel at position $(x,y)$ have a value distributed as $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_{0,x,y}^2)$ where
-\begin{equation}
-  \mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0) \ ,
-\end{equation}
-$(x_0,y_0)$ is the centre of the image and $\sigma_{0,x,y}=2$ for all $(x,y)$.
-
-A caveat is that some bias to the null variance estimation would be introduced because of the contamination.
-This is because sources of variance captured by the kernel are from $\sigma_{0,x,y}$ and also from the variability of $\mu_{0,x,y}$.
-This can be shown.
-Let $Z_{x,y}$ be the value of the pixels captured by the circular kernel for integer values of $(x,y)$ such that $x^2+y^2\leqslant r^2$.
-Suppose that $Z_{x,y}\sim\normal(ax+by,c^2\sigma^2)$.
-The calculations of the expectation and variance of $Z_{x,y}$ can be approximated by treating $x$ and $y$ as uniformly distributed within a circle centred at the origin with radius $r$.
-The expectation is $\expectation[Z_{X,Y}] = \expectation\expectation[Z_{X,Y}|X,Y]=0$.
-The variance is given as $\variance[Z_{X,Y}] = \expectation\variance[Z_{X,Y}|X,Y] + \variance\expectation[Z_{X,Y}|X,Y]$.
-From the distribution of $Z_{X,Y}$, $\expectation\variance[Z_{X,Y}|X,Y] = c^2\sigma^2$ and $\variance\expectation[Z_{X,Y}|X,Y]=\variance[aX+bY]$.
-This is worked out to be
-\begin{align}
-\variance[aX+bY] &= \dfrac{1}{\pi r^2}\int_{\rho=0}^{\rho=r}\int_{\theta=0}^{\theta=2\pi}
-\rho^3(a\cos\theta + b\sin\theta)^2 \diff \theta \diff \rho
-\nonumber\\
-& = \dfrac{1}{4}(a^2+b^2)r^2
-\end{align}
-thus
-\begin{equation}
-\variance[Z_{X,Y}] = \dfrac{1}{4}(a^2+b^2)r^2 + c^2\sigma^2 \ .
-\end{equation}
-This shows that when estimating the null variance on a contaminated Gaussian image, there may be a $(a^2+b^2)r^2/4$ bias.
-If the contamination is slowly varying, that is $a$ and $b$ are small, then the bias should be small.
-
-\begin{figure}[p]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_beforeFilter.eps}
-    \caption{Unfiltered}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_afterFilter.eps}
-    \caption{Filtered}
-    \label{fig:inference_allNullGaussianScript_afterFilter}
-  \end{subfigure}
-  }
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullMean.eps}
-    \caption{Empirical null mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullStd.eps}
-    \caption{Empirical null std}
-  \end{subfigure}
-  }
-  \caption{A $256\times 256$ Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
-  \label{fig:inference_allNullGaussianScript}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_beforeFilter.eps}
-    \caption{Unfiltered}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_afterFilter.eps}
-    \caption{Filtered}
-    \label{fig:inference_allNullPlaneScript_afterFilter}
-  \end{subfigure}
-  }
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullMean.eps}
-    \caption{Empirical null mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullStd.eps}
-    \caption{Empirical null std}
-  \end{subfigure}
-  }
-  \caption{A $256\times 256$ contaminated Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
-  \label{fig:inference_allNullPlaneScript}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_pValue.eps}
-    \caption{No contamination}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_pValue.eps}
-    \caption{With contamination}
-  \end{subfigure}
-  \caption{$p$-values from a filtered $256\times 256$ Gaussian image with kernel radius 20.
-In b), the Gaussian image was contaminated before filtering.
-The $p$-values were obtained from the images in Figures \ref{fig:inference_allNullGaussianScript_afterFilter} and \ref{fig:inference_allNullPlaneScript_afterFilter}.
-The dotted lines shows the $p$-values if they were uniformly distributed.}
-  \label{fig:inference_allNull_pValues}
-\end{figure}
-
-An example of a Gaussian image with/without contamination before/after filtering are shown in Figures \ref{fig:inference_allNullGaussianScript} and \ref{fig:inference_allNullPlaneScript}.
-In the contaminated example, the filter managed to estimate the null mean, picking up the gradient.
-This enabled the normalised image to look flat to remove the contamination.
-The $p$-values after filtering are shown in Figure \ref{fig:inference_allNull_pValues}.
-A quick inspection suggest that the filtered pixels looked reasonably Normal for this particular example.
-
-For a given kernel radius $r$, 100 different Gaussian images were filtered to investigate the within image mean, standard deviation and kurtosis of the filtered statistics.
-Various other filters were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter.
-They use different estimators to estimate the null parameters as their name suggest, Table \ref{table:inference_nullFilters} clarifies them.
-
-\begin{table}[ht]
-  \centering
-  \begin{tabular}{c|c|c}
-    Filters&Null mean&Null Standard deviation\\\hline
-    MAD mode null&Mode&MAD around the mode $\times1.4826$\\
-    Median IQR null&Median&IQR $\div1.349$\\
-    Mean variance null&Mean&Standard deviation
-  \end{tabular}
-  \caption{Various filters using different estimators to estimate the null parameters are described here.}
-  \label{table:inference_nullFilters}
-\end{table}
-
-\begin{figure}
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_mean.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_mean.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_mean.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_mean.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The within image sample \emph{mean} of the test statistics in a filtered Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
-  \label{fig:inference_AllNullGaussian_mean}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_variance.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_variance.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_variance.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_variance.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
-  \label{fig:inference_AllNullGaussian_var}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_kurtosis.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_kurtosis.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_kurtosis.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_kurtosis.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
-  \label{fig:inference_AllNullGaussian_kurtosis}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_mean.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_mean.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_mean.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_mean.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The within image sample \emph{mean} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
-  \label{fig:inference_AllNullPlane_mean}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_variance.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_variance.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_variance.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_variance.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
-  \label{fig:inference_AllNullPlane_var}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_kurtosis.eps}
-    \caption{Empirical Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_kurtosis.eps}
-    \caption{MAD Mode Null}
-  \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_kurtosis.eps}
-    \caption{Median IQR Null}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_kurtosis.eps}
-    \caption{Mean Var Null}
-  \end{subfigure}
-  }
-  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
-  \label{fig:inference_AllNullPlane_kurtosis}
-\end{figure}
-
-The results for the filtered images are shown in Figures \ref{fig:inference_AllNullGaussian_mean}, \ref{fig:inference_AllNullGaussian_var} and \ref{fig:inference_AllNullGaussian_kurtosis}.
-For the filtered \emph{contaminated} images, they are in Figures \ref{fig:inference_AllNullPlane_mean}, \ref{fig:inference_AllNullPlane_var} and \ref{fig:inference_AllNullPlane_kurtosis}.
-The filtered test statistic means did agree with zero as expected, showing that the filters centred the statistics when normalising.
-When using the empirical null filter, there was some negative bias with the standard deviation of the filtered test statistics.
-The negative bias comes from the positive bias when estimating the null standard deviation.
-
-When filtering the contaminated image, all estimators suffered from negative bias in the standard deviation of the filtered statistics, in particular when the kernel radius increased.
-This is shown in Figure \ref{fig:inference_AllNullPlane_var}.
-As discussed before, the kernel captured the variation due to the contamination and this added intrinsic bias to the null variance.
-As a result, this added bias when estimating the null variance.
-
-The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} showed that the empirical null filter caused the filtered statistics to have heavy tails, in particular for small kernel radiuses.
-This could cause problems in hypothesis testing because heavy tails could be misinterpreted as contribution from non-null statistics.
-The source of the kurtosis inflation is from the estimation of the null standard deviation.
-This can be seen by comparing the empirical null filter with the MAD mode null filter because the only difference between the two filters is in the estimation of the null standard deviation.
-
-\afterpage{\clearpage}
-\subsection{Detecting Defects Experiment}
-
-In this experiment, the empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination.
-A \emph{defect} is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
-For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
-
-To recap, \emph{contamination} is the result of a linear transform of the test statistics $Z_{x,y}$.
-For example in this experiment, the image was multiplied by 2 and a gradient was added to it.
+Contamination is the result of a linear transform of the test statistics $Z_{x,y}$.
+For example.
+in this experiment, the image was multiplied by 2 and a gradient was added to it.
 Suppose the image does contain defects, then an example of a resulting distribution is
@@
 \end{align}
-where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects.
+where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
+This was used in this experiment to simulate a contaminated image with defects.
+The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.
 
-The empirical null filter aims to estimate the null distribution parameters from $Z_{x,y}$ in order to normalise it to form $T_{x,y}$.
-By normalising it, $T_{x,y}|H_{0,x,y}$ should be approximately standard Normal and hypothesis testing can be used to detect defects.
-
-Various defects were investigated.
-Speckle defect with density $\pi_1$ assign all test statistics to be non-null with probability $\pi_1$, and are null otherwise.
-This was chosen because the proportion of null statistics captured by the kernel should be the same all for all kernel radiuses.
-A line defect assign columns of pixels to be non-null, a kernel would only capture a section of defect.
-Different shapes were used such as a square defect.
-With a square defect, a kernel can capture the entire defect if its radius is large enough.
-
-\begin{figure}[p]
+\begin{figure}
   \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imagePreContaminated.eps}
-        \caption{Uncontaminated}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageContaminated.eps}
-        \caption{Contaminated}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageFiltered.eps}
-        \caption{Filtered}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{A $256 \times 256$ Gaussian image with \emph{speckle} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius 20 in c).
-Defected pixels have the distribution $\normal(3,1)$.
-The speckle defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
-  \label{fig:inference_defectDustExample}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imagePreContaminated.eps}
-        \caption{Uncontaminated}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageContaminated.eps}
-        \caption{Contaminated}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageFiltered.eps}
-        \caption{Filtered}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{A $256 \times 256$ Gaussian image with a \emph{line} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius 20 in c).
-Defected pixels have the distribution $\normal(3,1)$.
-The line defect is 5 pixels thick.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
-  \label{fig:inference_defectLineExample}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imagePreContaminated.eps}
-        \caption{Uncontaminated}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageContaminated.eps}
-        \caption{Contaminated}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageFiltered.eps}
-        \caption{Filtered}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-    }
-  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius \emph{20} in c).
-Defected pixels have the distribution $\normal(3,1)$.
-The square defect is $30\times 30$ pixels in size.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
-  \label{fig:inference_defectSquareExample}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imagePreContaminated.eps}
-        \caption{Uncontaminated}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
-        \caption{Contaminated}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageFiltered.eps}
-        \caption{Filtered}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-    }
-  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius \emph{40} in c).
-Defected pixels have the distribution $\normal(3,1)$.
-The square defect is $30\times 30$ pixels in size.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
+  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
+  \caption{A $256\times 256$ contaminated Gaussian image with a $30 \times 30$ square defect.
+The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
   \label{fig:inference_defectSquare2Example}
@@
 
-An example of a speckle defected image is shown in Figure \ref{fig:inference_defectDustExample}, the figure also shows the image contaminated and then filtered.
-The contamination caused some systematic errors in hypothesis testing, such as an increase of positive pixels and in particular in two of the corners of the image.
-The empirical null filter recovered the image from the contaminated image so that appropriate inference was done.
-However some statistical power was lost in the filtered image.
-This is because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
-This cannot be avoided as areas of high empirical null standard deviation was due to the sampling error.
-Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_defectLineExample}.
+The contamination is a nuisance because the test statistics have larger variance and larger values at the two corners. This cause an inflation in false positives which leads to incorrect inference.
 
-The square defected images, including the contaminated ones, are shown in Figures \ref{fig:inference_defectSquareExample} and \ref{fig:inference_defectSquare2Example}.
-Figure \ref{fig:inference_defectSquareExample} filtered the contaminated image using a kernel radius of $r=20$, while Figure \ref{fig:inference_defectSquare2Example} used a kernel radius of $r=40$.
-With $r=20$, the kernel is smaller than the square defect, therefore the defect was treated as the null and this evident in the empirical null mean.
-This resulted in difficulty detecting the defect.
-With $r=40$, the kernel is bigger than the defect and treated the defect as non-null.
-The empirical null filter recovered the gradient in the empirical null which was then used for normalisation.
+Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null.
+In this simulate example, it is about $r>54$.
+A kernel too small would treat the defects as null, making them difficult to detect.
 
-The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} are shown in Figure \ref{fig:inference_defectSimulationRoc} for the various defects and filters.
-The ROC curve is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
+The receiver operating characteristic (ROC) curve \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} was studied in this experiment.
+The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
 The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
@@
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_roc.eps}
-        \caption{Dust defect $\pi_1=0.1$, $r=20$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_roc.eps}
-        \caption{5 pixels thick line defect, $r=20$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_roc.eps}
-        \caption{$30\times 30$ square defect, $r=20$}
-        \label{fig:inference_defectSimulationRoc_square20}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_roc.eps}
-        \caption{$30\times 30$ square defect, $r=40$}
-      \end{subfigure}
-    }
-  \caption{ROC curves for various defected $256\times 256$ Gaussian images.
-The upper/lower dashed line show the resulting ROC curve when testing on an image without/with contamination respectively.
-The different curves are the resulting ROC curves after filtering a contaminated image.
-Defected pixels have the distribution $\normal(3,1)$.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
-  \label{fig:inference_defectSimulationRoc}
-\end{figure}
+An experiment was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$.
+Hypothesis testing was done on the uncontaminated and filtered contaminated image.
+The area under the ROC curve and various errors were recorded.
+This was repeated 100 times by simulating another contaminated image with a defect.
+To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
+The results are shown in Figure \ref{fig:inference_Experiment_DefectRadiusSquare}.
 
-In terms of the area under the ROC curves, the empirical null filter improved the performance over using the unfiltered contaminated image.
-The performance before contamination cannot be recovered but it was an improvement.
-For kernel radiuses too small, such as Figure \ref{fig:inference_defectSimulationRoc_square20}, the empirical null filter deteriorated the performance and it would be better off using the contaminated image.
-
-The ROC considers all thresholds or specificities used in the hypothesis testing.
-However in the previous experiment, it was found there was some variance mismatch before and after filtering with regards to the test statistics.
-As a result, for a given threshold such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
-
-An experiment was conducted to investigate the specificity of the test before and after filtering.
-A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated.
-Before the experiment, various baselines were obtained.
-An image with a defect was simulated and then tested to obtain the ROC area, type 1 error, type 2 error and the FDR.
-The image was than contaminated and tested to obtain the 4 measurements again.
-This was repeated 300 times to obtain the empirical distribution of the ROC area, type 1 error, type 2 error and FDR when testing on a un/contaminated image with defects.
-The ROC area, type 1 error, type 2 error and FDR were measured when testing on a filtered contaminated image with defects, a kernel radius of $r=20$ was used and was repeated 100 times.
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
-        \label{fig:inference_DefectSimulationDust_type1}
-        \caption{Type 1 error}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
-        \caption{Type 2 error}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
-        \caption{FDR}
-        \label{fig:inference_DefectSimulationDust_fdr}
-      \end{subfigure}
-    }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
-a) shows the ROC area when testing the image before/after contamination and after filtering.
-In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
-The filter used a kernel radius of 20.
-Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
-The salt defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The test was done at the 5\% FDR level.
-The box plot summarise the 100 repeats of the experiment.}
-  \label{fig:inference_DefectSimulationDust}
-\end{figure}
-
-The results are shown in Figure \ref{fig:inference_DefectSimulationDust}.
-The ROC areas quantified showed that using the filter improved the performance of the test from the contamination.
-The type 1 error, or specificity, did decreased after filtering.
-However the results illustrated that the FDR is controlled quite well at around 5\% after filtering.
-This meant that in this particular example, the FDR control is consistent after contamination and filtering.
-At situations with low detection power, the FDR can fluctuate between 0 and 1 and can take only so many values.
-For example if 3 positive pixels were detected, then the FDR can only take values of multiples of $1/3$ between and including 0 and 1.
-
-There is the question of what kernel size to choose for a given defect.
-Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $\pi_1=0.1$ to satisfy some assumptions made for the empirical null.
-Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of kernel which is a defect to 10\%.
-In other words for a kernel with radius $r$
-\begin{equation}
-0.1 > \dfrac{\text{maximum area of defect captured by the kernel}}{\text{area of kernel}} \ .
-\end{equation}
-For a $d \times d$ square defect this is $r > d \sqrt{10/\pi}$.
-In the example of $d=30$, this is about $r>54$.
-For the line defect with thickness $5$, the radius is about $r>32$.
-These are rules of thumb because the kernel is not perfectly circular when used on a grid of pixels.
-It should be pointed out that the implementation can accept non-integer radiuses if desired.
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type1.eps}
-        \caption{Type 1 error}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type2.eps}
-        \caption{Type 2 error}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_fdr.eps}
-        \caption{FDR}
-      \end{subfigure}
-    }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
-Defected pixels have the distribution $\normal(3,1)$.
-The line defect is 5 pixels thick.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The test was done at the 5\% FDR level.
-The box plot summarise the 100 repeats of the experiment.}
-  \label{fig:inference_Experiment_DefectRadiusLine}
-\end{figure}
-
-\begin{figure}[p]
+\begin{figure*}[p]
   \centering
@@
     }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
-Defected pixels have the distribution $\normal(3,1)$.
-The square defect is $30\times 30$ pixels in size.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $256 \times 256$ filtered contaminated Gaussian image with a $30\times 30$ square defect.
+Various kernel radiuses were investigated.
+The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect.
+The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
 The test was done at the 5\% FDR level.
@@
   \label{fig:inference_Experiment_DefectRadiusSquare}
-\end{figure}
-
-An experiment was conducted where the contaminated defected image were filtered for various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
-Hypothesis testing was done on the uncontaminated and filtered contaminated image and the area under the ROC curve and various errors were recorded, this was repeated 100 times.
-The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
-Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.
+\end{figure*}
 
 The results showed that the ROC area increased with kernel radius.
-This highlighted that a kernel with a good radius can performance almost as though there was no contamination.
+This highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination.
 It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
 
+Preserving FDR is important because it keeps the FDR consistent before and after filtering.
 For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%.
 It appeared a large kernel radius helped preserve FDR control after filtering in these examples.
-However a large kernel radius did come at a computational cost.
-Choosing a kernel radius is a matter of trading computational cost with precise FDR control.
 
-It appeared there exist a kernel radius which minimised the type 2 error. So a large kernel radius is required for FDR control but too large can lose statistical power.
+It appeared there is a kernel radius which minimised the type 2 error. A large kernel radius is required for FDR control but too large can lose statistical power.
 
-\afterpage{\clearpage}
 \section{Results}
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$}
-      \end{subfigure}
-    }
-  \caption{Filtered $z$ image from the \texttt{Sep16 120deg} dataset. Various kernel radiuses were used.}
-  \label{fig:inference_sep16120deg_zfiltered}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_sig.eps}
-        \caption{Image with positive pixels}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius1}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_sig.eps}
-        \caption{Image with positive pixels}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius2}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_sig.eps}
-        \caption{Image with positive pixels}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius3}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_sig.eps}
-        \caption{Image with positive pixels}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius4}
-\end{figure}
-
-The empirical null filter was applied to the \texttt{Sep16 120deg} image as shown at the start of the chapter.
-Figure \ref{fig:inference_sep16120deg_zfiltered} shows the filtered $z$ images for various kernel radiuses.
-For $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image was smooth and treated everything as the null.
-When a large enough radius was used, the defects were highlighted by the higher test statistics and everything else remain unchanged.
-Figures \ref{fig:inference_sep16120deg_inference_radius1} to \ref{fig:inference_sep16120deg_inference_radius4} shows the resulting inference along with the empirical null parameters.
-The figures shows that for large enough kernel radius, the filter ironed out the false positives observed at the start of the chapter.
-All of the defects were successfully highlighted by the hypothesis test.
-
-False positives were detected on the bottom right of the 3D printed sample.
-This was the result of the null distribution being bimodal where each face had a different distribution.
-Figure \ref{fig:inference_cornerSelect} illustrates this.
-The geometry of the faces and the kernel was such that it resulted in one of the faces to be treated as non-null and then tested positive, falsely so.
-
-The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}.
+The empirical null was used on the real data.
+The x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
 It was segmented using the edges of the projection of the 3D printed object.
@@
 The resulting filtered segments were stitched together to form the resulting filtered image.
-By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.
+The resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.
+
+The larger defects were successfully highlighted by the hypothesis test.
 It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
-Most of false positives around the corners and edges have been eliminated.
+This probably suggest that the contamination or inaccuracy from \texttt{aRTist} was face dependent.
 
-\begin{figure}[htp]
+\begin{figure}
   \centering
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.png}
-      \caption{$z$ image with kernel of radius $r=120$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHisto.png}
-      \caption{Histogram of $z$ in the kernel}
-    \end{subfigure}
-  }
-  \caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the test statistics captured by the kernel shows a bimodal distribution.}
-  \label{fig:inference_cornerSelect}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
-  \caption{The $z$ image was segmented further into 7 segments.}
+  \includegraphics[width=0.45\textwidth]{../figures/inference/segment.JPG}
+  \caption{The x-ray image was segmented further into 7 segments or ROI.}
   \label{fig:inference_segmentFurther}
@@
 
-\begin{figure}[p]
+\begin{figure*}
   \centering
@@
   \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-The test statistics from all segments were combined in the BH procedure.
+a) X-ray image with highlighted red positive pixels at the 5\% FDR level.
 b) $p$-values on the log scale.
@@
   \label{fig:inference_subroisep16120deg_inference_radius4}
-\end{figure}
+\end{figure*}
 
@@
 In the experiments, it was found that the FDR level is preserved after filtering.
-In experiments it was found that the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}.
 
@@
 
-\begin{figure}[htp]
+\begin{figure*}
   \centering
@@
   \label{fig:inference_timing}
-\end{figure}
+\end{figure*}
 
@@
 
-The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
+The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel.
 Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
 On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.
+
+\section{Acknowledgements}
+This work is funded by EPSRC grant numbers EP/K031066/1 and EP/L016710/1.
+
+\bibliographystyle{apalike}
+\bibliography{../bib}
+
+\end{document}

### 2019-04-09 reports/paper1/paper.tex
Paper revision

@@
-\documentclass[twocolumn]{article}
+\documentclass{proc}
 
@@
 
-\subsection{Apparatus and Procedures}
+\subsection{Apparatus and Data Collection}
 
@@
 The empirical null filter was implemented using \texttt{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}.
+It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads.
+Each thread filters a row in parallel.
+
+Line filtering was done from left to right.
+At the start on the far left, an initial value of the median of all the pixels in the kernel was used.
+For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as a initial point.
+This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
+
+When filtering a pixel, the Newton-Raphson method was used to solve for $\widehat{\mu}_{0,x,y}=z$
+\begin{equation}
+  \dfrac{\partial}{\partial z}\ln\widehat{p}_{Z_{x,y}}(z) = 0
+\end{equation}
+by using the iterative procedure
+\begin{equation}
+  z^{(r+1)} =
+  z^{(r)}
+  -\dfrac{
+    \left.
+      \dfrac{
+        \partial
+      }
+      {
+        \partial z
+      }
+      \ln\widehat{p}_{Z_{x,y}}(z)
+    \right|_{z = z^{(r)}}
+  }
+  {
+    \left.
+      \dfrac{
+        \partial^2
+      }
+      {
+        \partial z^2
+      }
+      \ln\widehat{p}_{Z_{x,y}}(z)
+    \right|_{z = z^{(r)}}
+  } 
+\end{equation}
+where $z^{(0)}$ is the initial value. A convergence criteria was met when either 10 update steps were taken or when
+\begin{equation}
+  \log\left[\left|
+    \left.
+    \dfrac{
+      \partial
+    }
+    {
+      \partial z
+    }
+  \ln\widehat{p}_{x,y}(z)
+  \right|_{z=z^{(r)}}
+  \right|\right]
+  <-5
+\end{equation}
+at the current step. This was chosen arbitrary to speed up the algorithm without losing too much accuracy. The solution is valid if
+\begin{equation}
+  \left.
+    \dfrac{
+      \partial^2
+    }
+    {
+      \partial z^2
+    }
+    \ln\widehat{p}_{Z_{x,y}}(z)
+  \right|_{z=\widehat{\mu}_{0,x,y}}
+  < 0 \ .
+\end{equation}
+Further initial values were generated by sampling from $\normal(z^{(0)}, s_{x,y}^2)$.
+This was done multiple times until 3 valid solutions were obtained.
+The best solution, the one with the largest $\ln\widehat{p}_{Z_{x,y}}\left(\widehat{\mu}_{0,x,y}\right)$, out of all the different initial values was used as the final answer.
 
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
-        \caption{Image with positive pixels}
+        \caption{X-ray image with positive pixels}
       \end{subfigure}

### 2019-04-09 reports/paper1/paper.tex
Revision

@@
 This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model.
-The model used was a gamma distributed GLM \citep{nelder1972generalized, mccullagh1984generalized} with an identity link.
+The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link.
 The variance was predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable when working out the test statistics.
@@
 The empirical null filter aims to obtain the estimators $\widehat{\mu}
-_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large}.
+_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$.
+This is based on the empirical null \citep{efron2004large} where hypothesis testing is done by comparing a test statistic with the empirical distribution of the majority of the test statistics rather than a specified null distribution.
 
@@
 \end{equation}
-where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of pixels in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}.
+where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}.
 The estimates were obtained by solving
@@
 Line filtering was done from left to right.
-At the start on the far left, an initial value of the median of all the pixels in the kernel was used.
-For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as a initial point.
+At the start on the far left, an initial value of the median of all the test statistics in the kernel was used.
+For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial point.
 This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
@@
 Contamination is the result of a linear transform of the test statistics $Z_{x,y}$.
-For example.
-in this experiment, the image was multiplied by 2 and a gradient was added to it.
+For example in this experiment, the image was multiplied by 2 and a gradient was added to it.
 Suppose the image does contain defects, then an example of a resulting distribution is
@@
 
-The contamination is a nuisance because the test statistics have larger variance and larger values at the two corners. This cause an inflation in false positives which leads to incorrect inference.
+The contamination is a nuisance because the test statistics will have larger variance and larger values at the two corners.
+This will cause an inflation in false positives which will lead to incorrect inference.
 
 Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null.
-In this simulate example, it is about $r>54$.
+In this simulated example, it is about $r>54$.
 A kernel too small would treat the defects as null, making them difficult to detect.
@@
 
-Preserving FDR is important because it keeps the FDR consistent before and after filtering.
+Keeping the FDR consistent before and after filtering is desirable so that the FDR is kept controlled at a specified level after filtering.
 For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%.

### 2019-04-09 reports/paper1/paper.tex
Revision

@@
 
-Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}.
+Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography \citep{thompson2016x}.
 The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
@@
     }
-  \caption{Timings when filtering a $256\times 256$ image. Note the y-axis change scale.}
+  \caption{Timings when filtering a $256\times 256$ image.
+The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
+Note the y-axis change scale.}
   \label{fig:inference_timing}

### 2019-04-28 reports/paper1/paper.tex
Revision

--- 2019-04-09 reports/paper1/paper.tex
@@
 \begin{abstract}
-X-ray computed tomography (CT) can be used for defect detection in additive manufacturing.
+X-ray computed tomography can be used for defect detection in additive manufacturing.
 The object is scanned at multiple angles to reconstruct the object in 3D space.
-The process can be time consuming.
-The aim is to investigate if it is possible to conduct defect detection from a single scan to speed up the quality control procedure.
-An experiment was conducted, a 3D printed sample was manufactured with voids to see if they can be detected.
-
-Software, \texttt{aRTist}, was used to simulate the scan and it was compared with the x-ray acquisition under the face of uncertainty.
-Each pixel was treated as a hypothesis test.
-The software, and the information provided to it, was not perfect which led to model misspecification and incorrect inference.
-The empirical null filter was proposed.
-It locally normalise each test statistic using robust estimators of the mean and deviation.
-This reduces the number of false positives.
-Sensible inference was achieved in the simulation and experiment.
+To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single scan.
+A 3D printed sample was manufactured with voids to see if they can be detected.
+The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test.
+The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
 \end{abstract}
@@
 The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
-The disadvantage of x-ray CT is that it involves calculations on acquisition of hundreds of angles of the sample.
+The disadvantage of x-ray CT is that it involves calculations on the acquisition of hundreds of angles of the sample.
 
-Speeding up the quality control process on the production line could be done by doing inspection on a few number of x-ray images \citep{warnett2016towards}.
+Speeding up the quality control process on the production line could be done by doing an inspection on a few numbers of x-ray images \citep{warnett2016towards}.
 These x-ray images are compared with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
@@
 This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
-Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
+However beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
 This was necessary because the simulation of \texttt{aRTist} do not match up perfectly with the x-ray image, producing incorrect inference.
-The empirical null filter is demonstrated on simulated and real data.
 
-\section{Method}
+An x-ray image of a 3D printed sample was obtained and compared with the \texttt{aRTist} simulation in an experiment.
+The procedure is shown in the methods section along with the description of the empirical null filter.
+In addition, the software development and simulation studies of the filter was discussed.
+The results from the simulation and the experiment are shown in the results section.
+The conclusion section summarises the study along with a discussion on further work.
+
+\section{Methods}
 
@@
 
-\begin{figure}[htp]
+\begin{figure}
   \centering
-  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
-  \caption{CAD of a 3D cuboid with voids; the scale shown is approximate.}
+  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
+  \caption{CAD of a 3D cuboid with voids.
+The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
+6 voids for each diameter were designed in the CAD.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly.
+The scale shown is approximate.}
   \label{fig:inference_testObject}
@@
 
-The 3D printed sample was scanned 20 times.
+The 3D printed sample was scanned 20 times at a fixed angle.
 The 20 x-ray images were spilt into 2.
@@
 
-\section{Simulation}
+\subsection{Simulation}
 
@@
 where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
-This was used in this experiment to simulate a contaminated image with defects.
+This was used in this study to simulate a contaminated image with defects.
 The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.
@@
 
-An experiment was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$.
-Hypothesis testing was done on the uncontaminated and filtered contaminated image.
+A simulation study was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$.
+Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image.
 The area under the ROC curve and various errors were recorded.
-This was repeated 100 times by simulating another contaminated image with a defect.
+This was repeated 100 times by simulating another image.
 To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
-The results are shown in Figure \ref{fig:inference_Experiment_DefectRadiusSquare}.
 
@@
 
-The results showed that the ROC area increased with kernel radius.
-This highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination.
+\section{Results}
+
+The result from the simulation is shown Figure \ref{fig:inference_Experiment_DefectRadiusSquare}.
+The ROC area increased with kernel radius which highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination.
 It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
@@
 
-\section{Results}
-
-The empirical null was used on the real data.
-The x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
+In the experiment with the 3D printed sample, the x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
 It was segmented using the edges of the projection of the 3D printed object.
@@
 
+The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel.
+Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
+On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.
+
 Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics.
@@
 However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
-
-The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel.
-Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
-On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.
 

### 2019-04-30 reports/thesis/chapters/1_literatureReview.tex
Start literture review

@@
-3D printing, formally additive manufacturing \citep{gibson2010additive} \citep{wong2012review}, has recently become state of the art technology which manufactures objects of complicated shapes with very high precision.
-It was developed in the 1980's \citep{kodama1981automatic} but recently it has been commercialised and is used in medical science \citep{kang20163d} and engineering \citep{wong2012review}.
-Because of such a wide range of applications, there has been a need for quality control and this can be done by scanning the 3D printed sample using x-ray computed tomography.
+One of the first methods of additive manufacturing (AM) is stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} which involves the curing of a photosensitive resin using an ultraviolet laser.
+The technology has evolved and AM is capable of manufacturing objects with complicated internal and external geometries.
+However, there is a need for product inspection and in particular assessing the quality of the internal structures.
+
+Imaging using x-rays \citep{rontgen1896on} have been used in the medical field.
+In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patent has an x-ray image taken at multiple angles.
+These x-ray images are used to reconstruct what was taken in 3D in order to make a diagnostic.
+
+X-ray computed tomography (XCT) can be used as a non-destructive test for additive manufactured objects, this is the main theme of this thesis.
+Various reviews on additive manufacturing exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}.
+For XCT used in manufacturing, there are \cite{cantatore2011introduction, kruth2011computed, sun2012overview}.
+\cite{thompson2016x} reviewed the applications of XCT on AM.
+
+In this chapter, AM is reviewed followed by XCT. The latest research for the use of XCT on AM is reviewed at the end of the chapter.
+
+\section{Additive Manufacturing}
+
+Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer.
+Typically this is a slow and expensive method compared to destructive methods such as drilling and cutting for example.
+However, this is not the full picture.
+The set up cost for AM is low, in particular destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}.
+This is why AM used to be called rapid prototyping \citep{kruth1991material}, it was suitable to manufacture bespoke items.
+
+Various different AM technologies were invented during the advancement of AM.
+Because of this, there are various applications of AM, for example in medical and biomedical sciences \citep{kang20163d, kourra2018computed}, engineering \citep{cooper2015design}, food engineering \citep{godoi20163d} and art \citep{ornes2013mathematics, grossman2019bathsheba}.
+
+\subsection{Additive Manufacturing Technologies}
+
+The different AM technologies can be classified based on the apparatus, for example liquid based or power based, and/or on the method of manufacturing, for example point by point or layer by layer \citep{kruth1991material}.
+The liquid based AM technologies presented here are stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} and fused deposition modelling \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
+The following power based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}.
+
+Stereolithography is a liquid based AM technology.
+It consist of a container containing a liquid photo-hardening monomer or polymer as well as a piston and platform which holds and moves the manufactured product up and down.
+A laser with a specific wavelength, typically \SIrange{300}{400}{\nano\metre} \citep{kodama1981automatic}, is emitted onto a point of the surface of the liquid and solidifies.
+The laser is controlled by a computer to solidified specific parts of the liquid surface.
+The platform is lowered and the cycle repeats, manufacturing the object layer by layer.
+Laser absorption happens a few tenths of a millimetre which corresponds to the thickness of each layer \citep{kruth1991material, pham1998comparison}.
+
+Fused deposition modelling is another liquid based AM technology.
+A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer.
+The material is usually plastic in a form of a thin filament.
+It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}.
+The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer.
+The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.
+In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.0001 inches (\SI{0.003}{\milli\metre}).
+
+3D printing is a powder based AM technology.
+A jetting head deposit a binding agent in droplets onto a bed of powder of ceramic, metal or polymer.
+The binding agent is cured via evaporation or heating which glues the powder particles together.
+The bed can move in all 3 dimensions and the object is manufactured layer by layer.
+The binding agent must have low viscosity so it can be deposited, it may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}.
+The thickness of each layer is determined by the size of the droplets of the binding agent, which can be as small as \SI{15}{\micro\metre} in diameter \citep{sachs1990three}.
+\cite{sachs1990three} reported a tolerance of 0.001 inches (\SI{0.03}{\milli\metre}).
+
+Selective laser sintering, electron beam melting and laser engineered net shaping are powder based AM technology.
+Selective laser sintering is similar to 3D printing but instead a laser is used to sinter or fuse the powder particles together.
+This is done in a chamber heated just below the melting point of the material \citep{wong2012review}.
+Various materials such as metal and plastics can be used \citep{wong2012review}.
+Electron beam melting is similar but instead an electron beam is used instead of a laser and this is done in a high vacuum chamber to avoid oxidation \citep{wong2012review}.
+In laser engineered net shaping, a powder bed is not used; instead the powder is deposited on the desired location and then melted using a laser.
+This is a popular method to manufacture metal objects \citep{gibson2010additive}.
+
+There are many more AM technologies but they can be found in numerous review literatures.
+A comparison of the mentioned AM technologies available at the time were done by \cite{pham1998comparison, kim2008benchmark}.
+Factors such as material cost, mechanical properties and the resolution of the manufacturing were considered.
+There are also safety aspects to assess, for example powder in powder based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}.
+This makes fused deposition modelling a popular choice and can be used in an office environment \citep{ngo2018additive}.
+
+The strength of the manufactured object vary from geometry to geometry but also from direction to direction.
+Because the manufactured object was made layer by layer, the strength varies if the load was applied in the building direction (vertical) or the scanning direction (horizontal) \citep{kim2008benchmark}.
+Experimental results shown that fused deposition modelling has superior strength in the scanning direction but weak in the building direction \citep{kim2008benchmark}.
+
+The strongest manufactured methods were found to be powder based methods and stereolithography, however they are slow and material costs are high \citep{kim2008benchmark}.
+Fused deposition modelling has low costs and high speeds but suffers from weak mechanical properties \citep{ngo2018additive}.
+
+The materials available for each AM technology varies.
+The materials used in stereolithography is limited because of the use of liquids with photo-hardening properties \citep{ngo2018additive}.
+Fused deposition modelling is limited to plastics \citep{ngo2018additive}.
+Selective laser sintering and laser engineered net shaping can manufacture objects using metals such as aluminium alloys, steel, titanium and titanium alloys \citep{herzog2016additive}.
+
+\subsection{Pre/Post Processing}
+
+The blueprint of the object to be manufactured is called a computer-aided design (CAD).
+For it to be processed by an AM apparatus, the CAD is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of series of triangles.
+STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}.
+Some accuracy is lost here as the surface of the CAD is represented approximately by triangles \citep{gibson2010additive}.
+The STL file is then sliced into layers \citep{jamieson1995direct, vatani2009enhanced} so that the AM apparatus knows what to build for each layer.
+
+When the AM object is manufactured, post processing techniques can be done at this stage.
+For example sanding may be done to smooth the surfaces \citep{gibson2010additive}.
+The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+This will be reviewed in the second half of this chapter.
+
+As with any apparatus, regular maintenance is required \citep{bell2014maintaining}.
+
+\subsection{Online Inspection and Defects}
+
+The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}.
+The idea is that problems in the manufacturing is found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
+
+There are various discontinuities in AM, in particular in the manufacturing of metal parts \citep{everton2016review}.
+For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}; they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}.
+Layers may not fuse together and form elongated pores, this can be fixed by increasing the energy of the beam but too high will cause evaporation of the AM part \citep{mumtaz2008high}.
+They can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review}.
+Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles on the surface of the AM part \citep{li2012balling, gu2009balling}.
+The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}.
+Low oxygen content in the environment \citep{niu1999instability} and higher energy beams \citep{gu2009balling} can reduce the balling effect.
+Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.
+
+Various methods are used for in-situ process monitoring.
+Most commonly a high speed camera is installed capturing the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}.
+Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}.
+Other methods include measuring the surface using a laser \citep{cerniglia2015inspection} and using an infrared camera to measure the temperature of the melt pool \citep{rodriguez2012integration}.
 

### 2019-05-01 reports/thesis/chapters/1_literatureReview.tex
Write XCT

@@
 Imaging using x-rays \citep{rontgen1896on} have been used in the medical field.
-In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patent has an x-ray image taken at multiple angles.
+In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patient has an x-ray image taken at multiple angles.
 These x-ray images are used to reconstruct what was taken in 3D in order to make a diagnostic.
@@
 
-\section{X-ray Imaging}
+\section{X-ray Computed Tomography}
+
+XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement.
+Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}.
+Reverse engineering is possible when XCT is combined with AM, for example it was use for improving existing hollow engine valves \citep{cooper2015design}.
+However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}.
+This is because is a lot of inconsistent in the setup of XCT apparatuses and on controlling the sources of error.
+
+\subsection{Concepts from the Medical Field}
+
+The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a bed.
+An x-ray source and x-ray detector pair rotate and/or translate around and/or along the patient to get readings of the x-rays after attenuating the patient using different paths.
+X-ray beams are pencil beams in the early versions of XCT.
+To reduce scanning times, cone shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}.
+These multiple x-ray readings or images can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}.
+
+The patient cannot be exposed to too much radiation, therefore the x-rays used are of low power.
+This can cause noisy readings from the detector.
+The sources of noise are from the behaviour of the x-rays and from the electronics in the detector \citep{yang2010noise}.
+In this realm of low signal to noise ratio, the noise has a compound Poisson element to it \citep{whiting2002signal, whiting2006properties}.
+Many reconstruction algorithms have been proposed to take the compound Poisson noise into consideration \citep{elbakri2002statistical, elbakri2003efficient, elbakri2003statistical, lasio2007statistical, xie2008x}.
+They are very complicated will not be discussed here because they are beyond the scope of this thesis.
+
+\subsection{Acquisition Process}
+
+Higher power x-rays can be used in XCT for the purpose of manufacturing and metrology because there is no consequence of the manufactured object being scanned absorbing the radiation.
+The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
+X-ray images are taken while the object rotates.
+Typically the x-ray is a cone beam \citep{kruth2011computed}.
+
+The acquisition process consist of the production of x-rays, x-ray attenuating the object, the detection of x-rays and the reconstruction process.
+
+X-rays \citep{rontgen1896on} are produced in an x-ray tube.
+It consist of a vacuum tube containing a cathode and an anode.
+Electrons are fired from the cathode to the anode due to an electric potential.
+The cathode is usually tungsten and the anode contains a small amount of tungsten, molybdenum or copper \citep{sun2012overview}.
+
+The electrons can interact with the anode in a number of ways.
+The electrons can be deflected or decelerated due to the electric field from the nucleus of the target material, the energy lost by the electrons is emitted as bremsstrahlung radiation.
+The energy of the bremsstrahlung radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}.
+Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it.
+This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state.
+This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target.
+
+The efficiency of an x-ray tube is poor, 99\% of the electron energy is converted to heat, the rest on x-rays \citep{kruth2011computed}.
+
+Photons are emitted from the x-ray tube as a Poisson process.
+The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode.
+The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies.
+
+The object being scanned are being exposed x-ray photons in XCT.
+X-ray photons undergo attenuation when interacting with the object in a number of ways.
+The object can absorb the photons via the photoelectric effect.
+In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}.
+Photons can be scattered by the sample by colliding inelastically with and transfers its energy to the an electron.
+This process is known as Compton scattering \citep{compton1923quantum}.
+The photoelectric effect and Compton scattering make a number of photons undetectable.
+However if some of the photons avoid these processes, they are detected and their energy is left unaffected.
+
+Beer's law simplifies these quantum mechanistic process.
+Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis.
+Let $\mu=\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation.
+A differential equation can be setup such that
+\begin{equation}
+\dfrac{\diff I}{\diff x} = -I\mu(x)
+\end{equation}
+which can be solved
+\begin{equation}
+I = I_0\exp\left[\int_{\text{path of photon}}-\mu(x)\diff x\right] \ .
+\label{eq:beerLaw}
+\end{equation}
+However the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}.
+Therefore $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}.
+In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the attenuated photons.
+This is called beam hardening.
+
+After attenuation, the x-ray photons are detected by the x-ray detector.
+Most X-ray detectors are made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes.
+The x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}.
+The visible light is detected by photodiodes and covert it into electrical signal \citep{michael2001x}.
+The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{whiting2006properties, kruth2011computed}.
+
+Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected.
+The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.
+
+The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
+The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.
+The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}.
+
+%DEAD PIXELS, PANELS
+
+Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
+There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.
+
+Reconstruction \citep{radon1986on} There exist various reconstruction algorithms \citep{smith1990cone}
+
+\subsection{Metrology}
+
+\subsection{Latest Research}
 
@@
 There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
-
-Many reconstruction algorithms have been proposed considering the compound Poisson nature of the detector \citep{elbakri2002statistical} \citep{elbakri2003statistical} \citep{lasio2007statistical} \citep{xie2008x} and with beam hardening correction \citep{elbakri2003efficient}.
-These will not be discussed here as they are beyond the scope of this thesis.
 

### 2019-05-02 reports/thesis/chapters/1_literatureReview.tex
Literature review complete

@@
 Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}.
-Reverse engineering is possible when XCT is combined with AM, for example it was use for improving existing hollow engine valves \citep{cooper2015design}.
+Reverse engineering is possible when XCT is combined with AM, for example it was used for improving existing hollow engine valves \citep{cooper2015design}.
 However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}.
-This is because is a lot of inconsistent in the setup of XCT apparatuses and on controlling the sources of error.
+This is because there is a lot of inconsistent in the setup of XCT apparatuses and on controlling the sources of error.
 
@@
 
-The acquisition process consist of the production of x-rays, x-ray attenuating the object, the detection of x-rays and the reconstruction process.
+The acquisition process consist of the production of x-rays, x-rays attenuating the object, the detection of x-rays and the reconstruction process.
 
@@
 The electrons can interact with the anode in a number of ways.
-The electrons can be deflected or decelerated due to the electric field from the nucleus of the target material, the energy lost by the electrons is emitted as bremsstrahlung radiation.
+The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material, the energy lost by the electrons is emitted as bremsstrahlung radiation.
 The energy of the bremsstrahlung radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}.
@@
 
-The efficiency of an x-ray tube is poor, 99\% of the electron energy is converted to heat, the rest on x-rays \citep{kruth2011computed}.
+The efficiency of an x-ray tube is poor, 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.
 
-Photons are emitted from the x-ray tube as a Poisson process.
+Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process.
 The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode.
@@
 
-The object being scanned are being exposed x-ray photons in XCT.
+The object being scanned are exposed to x-ray photons in XCT.
 X-ray photons undergo attenuation when interacting with the object in a number of ways.
@@
 Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis.
-Let $\mu=\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation.
-A differential equation can be setup such that
+Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation.
+A differential equation can be set up to model the decay of photons as it attenuate through the object such that
 \begin{equation}
@@
 \begin{equation}
-I = I_0\exp\left[\int_{\text{path of photon}}-\mu(x)\diff x\right] \ .
+I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(u)\diff u\right] \ .
 \label{eq:beerLaw}
 \end{equation}
-However the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}.
-Therefore $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}.
-In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the attenuated photons.
+However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}.
+Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law.
+In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the detected photons.
 This is called beam hardening.
@@
 After attenuation, the x-ray photons are detected by the x-ray detector.
-Most X-ray detectors are made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes.
+The detectors used in XCT are typically flat bed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes.
 The x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}.
-The visible light is detected by photodiodes and covert it into electrical signal \citep{michael2001x}.
+The visible light is detected by photodiodes and coverts it into an electrical signal \citep{michael2001x}.
 The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{whiting2006properties, kruth2011computed}.
+The electrical signals are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}.
 
@@
 The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.
+The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
 
-The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
-The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.
-The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}.
+Once multiple x-ray images of the object have been acquired at multiple angles, the reconstruction process can start.
+The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray images.
+It should be reminded that the x-ray images are based on the line integral of the attenuation coefficient along the path of photons.
+This problem was formed by \cite{radon1986on} as the `determination of functions from their integral values along certain manifolds'.
 
-%DEAD PIXELS, PANELS
+There exist many reconstruction algorithms in XCT \citep{smith1990cone} such as the filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
+Once the reconstruction has been done, the shape or surface can be extracted by use of thresholding \citep{kruth2011computed}.
+There exist many software for the reconstruction stage of XCT \citep{reinhart2008industrial, sun2012overview}.
 
-Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
-There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.
+\subsection{Metrology in Practice}
 
-Reconstruction \citep{radon1986on} There exist various reconstruction algorithms \citep{smith1990cone}
+XCT can be used to measure the length of the object, making it useful for measuring AM objects internally and externally.
+\emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.
 
-\subsection{Metrology}
+As with a lot of measurement apparatus, calibration is required.
+In XCT, the scale of each voxel in the reconstruction can be obtained by using XCT on an object with pre-determined lengths, these are known as reference standards \citep{bartscher2007enhancement} but can have similar names.
+Reference standards can vary in geometry such as a sphere on a cylinder \citep{lifton2013application}, two spheres on a cylinder \citep{sun2016reference}, a cube with cut outs \citep{kiekens2011test}, a plate with various features \citep{moylan2014additive, mohring2015testpart}, a hollow cylinder, a step-cylinder and a ball-bar \citep{bartscher2007enhancement}.
+They can be manufactured using AM \citep{mohring2015testpart} but this can become a chicken and egg problem, determining the measurements of an AM object using an AM object.
+
+There are many variables in XCT and a lot of them have to be controlled.
+For example XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.
+
+The set up of XCT has a number of variables.
+The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray image.
+The exposure time is also a factor.
+These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}.
+The magnification can be adjusted by adjusting the distances between the x-ray tube, the object and the x-ray detector.
+Increasing the magnification increases the image resolution but can cause blurred images \citep{kruth2011computed}.
+Another important factor is the focal spot size because larger spot sizes produce blurry results, this is know as the penumbra effect \citep{kueh2016modelling}.
+However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.
+There is also the question on how to orient the object on the turntable \citep{corcoran2016observations}.
+All of these variables can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however there may be inconsistencies.
+For example even though the target material of the anode and power is specified, the energy spectrum can still vary \citep{stumbo2004direct}.
+
+Problems can occur in the detector.
+For examples pixels in the acquired x-ray can be defected or dead \citep{brettschneider2014spatial} and panels can appear \citep{yang2009evaluation}.
+Spatially correlated noise can be observed as well \citep{sun2016characterisation}.
+
+Errors due to beam hardening can occur.
+Low energy photons are more likely to be absorbed or scattered, this causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior.
+This can cause flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed} as well as artefacts \citep{sun2016applications}.
+Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper.
+This reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}.
+Beam hardening can also be considered in the reconstruction stage \citep{sun2016applications}.
+
+The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm as it caters for cone beams.
+However it assumes a circular trajectory from the source which can produce artefacts \citep{sun2016applications}.
 
@@
 
-\subsection{X-Ray Production}
-Photons in CT scanning are produced in an X-ray tube.
-In an X-ray tube, a cathode, consisting of a heated filament, fires projectile electrons through an electric potential to a target which forms the anode \citep{michael2001x}, as shown in Figure \ref{fig:x_ray_tube}.
-Most of the kinetic energy of the projectile electrons is converted into heat however some is converted into electromagnetic radiation.
-This depends on how the projectile electrons interact with the atoms in the anode \citep{cantatore2011introduction}.
+The most common use of XCT in AM is the investigation of pores in the manufactured object \citep{thompson2016x}.
+Pores can be classified as defects if the pores are larger than some volume threshold.
+This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
-	\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \citep{michael2001x}}
-	\label{fig:x_ray_tube}
-\end{figure}
+The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}.
+However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
+The strength of XCT comes from the fact that the location of the pores can be visualised and compared to the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}.
+\cite{leuders2015fatigue} pointed out that the location of the pores is an important factor.
+In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
 
-Bremsstrahlung is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target.
-The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation.
-As a result, the photon energies in bremsstrahlung radiation is  a continuous spectrum and can range up to the maximum kinetic energy of the projectile electrons \citep{michael2001x}.
+One of the disadvantages of XCT is that it is a slow process.
+Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar.
+The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}.
+\cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction.
+This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs.
+X-ray images at fewer angles can be taken but they can be obtained in one acquisition, speeding up the process.
 
-Characteristic radiation is due to projectile electrons colliding with electrons in the target atom and ionizing them.
-This produce vacancies in the electron shell and emits photons when the electrons in the target atom drops down back to the ground state.
-The energy of the emitted radiation is monoenergetic and depends on the binding energy of the target's atoms \citep{michael2001x}.
-
-A typical energy spectrum of photons emitted from an X-ray tube is as shown in Figure \ref{fig:x_ray_spectrum}.
-The energy spectrum consist of both bremsstrahlung and characteristic radiation \citep{michael2001x}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{figures/x_ray_spectrum.png}
-	\caption{A typical energy spectrum of photons emitted from an X-ray tube.
-The continuous spectrum is the result of bremmsstrahlung.
-The peaks are the result of characteristic radiation.
-\citep{michael2001x}}
-	\label{fig:x_ray_spectrum}
-\end{figure}
-
-The voltage and current can be varied in the X-ray tube to produce different energy spectrums and rate of photon production.
-This can vary the results produced when collecting CT data \citep{cantatore2011introduction}.
-Another important factor is the focal spot size because smaller spot sizes produce sharper edges.
-Larger spot sizes produce unsharp results and this is know as the penumbra effect, as shown in Figure \ref{fig:x_ray_penumbra}.
-However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the X-ray tube.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=1\textwidth]{figures/x_ray_penumbra.png}
-	\caption{Larger focal spot sizes produces unsharp results. This is know as the penumbra effect. \emph{Source: F.~Welkenhuyzen et al.~(2009)\citep{welkenhuyzen2009industrial}}}
-	\label{fig:x_ray_penumbra}
-\end{figure}
-
-\subsection{Photon Interactions}
-Photons emitted by the X-ray tube are projected onto the sample and interacts with it in a number of ways \citep{cantatore2011introduction}.
-
-The sample can effectively absorb photons via the photoelectric effect or pair production \citep{cantatore2011introduction}.
-In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}.
-In pair production, the photons convert into electron-position pairs by interacting with the Coulomb field of the sample's atomic nucleus \citep{hubbell2006electron}.
-In addition to getting absorbed, photons can be scattered by the sample.
-This happens when photons collide inelastically with and transfers its energy to the sample's electrons.
-This process is known as Compton scattering \citep{compton1923quantum}.
-
-Suppose a mono-energetic X-ray pencil beam attenuating through an object with varying attenuation coefficient in position $\mu=\mu(x)$.
-The beam starts at $x=0$ and is detected at $x=L$, then the attenuation (decrease in X-ray intensity from $I_0$ to $I_1$) is given as \citep{cantatore2011introduction}
-\begin{equation}
-	I_1 = I_0\exp\left[\int_0^L-\mu(x)\diff x\right].\label{eq:beerLaw}
-\end{equation}
-By comparing the intensity before and after attenuation, the integral of the attenuation coefficient along the path of the X-ray can be calculated.
-Because of the discrete nature of pixels, the integral is usually replaced by a sum \citep{michael2001x}.
-
-However it was shown that the attenuation coefficient does depend on the energy of the photons \citep{elbakri2002statistical}.
-Thus $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}.
-In general low energy photons are more likely to be absorbed than high energy photons, this increases the average energy of the attenuated photons and can be a source of error in CT scanning.
-This is referred to beam hardening and can cause inaccuracies in Equation \eqref{eq:beerLaw} \citep{michael2001x}.
-This can be reduced by placing a thin sheet of filter to absorb low energy photons \citep{welkenhuyzen2009industrial} or by correcting it in the data analysis stage \citep{michael2001x}.
-
-\subsection{Detection}
-Most X-ray detectors are made up of a scintillator material \citep{greskovich1997ceramic} and photodiodes.
-Firstly the x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}.
-Lastly the visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}.
-Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected.
-The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.
-
-The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
-The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.
-The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image on a computer \citep{cierniak2011x}.
-
-\section{X-ray Computed Tomography}
-Computed tomography (CT) scanning is a 3D imaging technique.
-It does this by reconstructing the geometry of the sample through a series of 2D X-ray images of the sample.
-The sample rotates after each image taken \citep{cantatore2011introduction}.
-
-Figure \ref{fig:x_ray_ct} shows a diagram on how CT scanning works.
-A 2D image is taken by projecting X-ray photons onto the stationary sample.
-The photons are then scattered or absobred by the sample.
-Some of these photons are then detected by an X-ray detector on the other side of the sample, which produces an image.
-After an image has been taken, the object rotates and another image is taken.
-Finally after a number of images, a 3D reconstruction of the object can be estimated \citep{cantatore2011introduction}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\textwidth]{figures/x_ray_ct.png}
-	\caption{X-ray computed tomography reconstructs the sample by projecting photons onto a rotating sample.
-The photons are then detected by the detector.
-\emph{Source: \url{http://www.phoenix-xray.com/}}}
-	\label{fig:x_ray_ct}
-\end{figure}
-
-CT was solved theoretically by \cite{cormack1973reconstruction} and implemented by \cite{hounsfield1973computerized} \citep{hounsfield1980computed}.
-It was mainly used for medical imaging.
-The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}.
-Recently CT has been used industrially for non-destructive testing in manufacturing \citep{cantatore2011introduction}.
-One possible application would be inspecting 3D printed samples \citep{villarraga2015assessing}.
-Other uses in science include the investigation of batteries \citep{o2017investigating} and materials \citep{wang2017x} \citep{zhang2016x}.
-
-Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
-There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.
-
-Studies have been done to use x-ray CT to do defection detection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}.
-This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}.
-Voids then can be classified as defects if the voids are larger than some volume threshold.
-This threshold controls the probability of the detection of defects \citep{amrhein2014characterization} \citep{gandossi2010probability}.
-
-Full 3D x-ray CT scans can be slow and may not generalised well in production lines.
-However there is potential to bring in methods such as those used in airport luggage inspection to speed up to process \citep{warnett2016towards}.
-
-There are many sources of error in CT scanning \citep{cantatore2011introduction} and this can cause problems when reconstructing the geometry of the sample.
-Sources of error include: dead pixels in the detector \citep{brettschneider2014spatial}, use of cone beams \citep{sun2016applications}, beam hardening and the orientation of the sample \citep{corcoran2016observations}.
-
-The scale of the 2D images can be calibrated with the use of reference standards \citep{bartscher2007enhancement} \citep{lifton2013application}.
-
-\section{Compound Poisson}
-
-The greyvalues of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector.
-When the photons interact with the scintillator, they are converted into visible light.
-The visible light photons are then detected and converted into a greyvalue.
-How the detected visible light is converted is important in modelling the greyvalue.
-
-Should the greyvalue be proportional to the number of photons detected, the detector is known as a quantum counter and the greyvalue is a Poisson random variable, up to a constant \citep{whiting2006properties}.
-However if the greyvalue records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector.
-The greyvalue has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}.
-There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
-
-Experiments have been done to verify the compound Poisson nature of the detector.
-This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers.
-It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
-The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.
-
-The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
-\begin{equation*}
-	Y\sim\poisson(\lambda)
-\end{equation*}
-that is
-\begin{equation*}
-	\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\dotdotdot
-\end{equation*}
-where $\lambda>0$ is the Poisson rate parameter.
-Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$.
-Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
-\begin{equation}
-	X|Y = \sum_{i=1}^{Y}U_i+\kappa
-	\label{eq:compoundPoisson_X|Y}
-\end{equation}
-where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
-\begin{equation*}
-	p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0
-	\ .
-\end{equation*}
-However it should be noted that $X=0$ if and only if $Y=0$ with probability
-\begin{equation*}
-	\prob(X=0)=\euler^{-\lambda} \ .
-\end{equation*}
-Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
-\begin{equation}
-	p_X(x) = 
-	\begin{cases}
-		\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
-		\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
-	\end{cases}
-\end{equation}
-where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.
-
-The m.g.f.~of $X$ has a nicer form however. Let the m.g.f.~of $X$ be
-\begin{equation*}
-	M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
-	\ .
-\end{equation*}
-This can be computed using the result for conditional expectations
-\begin{equation*}
-	M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]
-	\ .
-\end{equation*}
-Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
-\begin{equation*}
-	M_X(\theta)=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
-\end{equation*}
-\begin{equation*}
-	M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
-	\ .
-\end{equation*}
-But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.
-\begin{equation*}
-	M_U(\theta)=\expectation\left[\euler^{U\theta}\right]
-	\ ,
-\end{equation*}
-then
-\begin{equation*}
-	M_X(\theta)=\expectation\left(
-		\expectation\left[\euler^{\theta U_1}|Y\right]\cdot
-		\expectation\left[\euler^{\theta U_2}|Y\right]\cdot
-		\dotdotdot \cdot
-		\expectation\left[\euler^{\theta U_Y}|Y\right]
-	\right)
-\end{equation*}
-\begin{equation*}
-	M_X(\theta)=\expectation\left[\left(M_U(\theta)\right)^Y\right]
-\end{equation*}
-\begin{equation*}
-	M_X(\theta)=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
-\end{equation*}
-\begin{equation*}
-	M_X(\theta) = M_Y\left(\ln(M_U(\theta)\right)
-\end{equation*}
-where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
-\begin{equation}
-	M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
-	\exp
-	\left[
-		\lambda
-		\left(
-		  \euler^\theta-1
-		\right)
-	\right]
-\end{equation}
-then
-\begin{equation}
-	M_X(\theta)=
-	\exp\left[
-		\lambda
-		\left(
-			M_U(\theta)-1
-		\right)
-	\right]
-	\ .
-\end{equation}
-As long as the m.g.f.~of $U$ is known, then m.g.f.~of $X$ can be written in closed form.
-
-Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
-\begin{align*}
-	M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
-	M_X'(\theta)&=M_X(\theta)\lambda M_U'(\theta)
-\end{align*}
-then
-\begin{equation}
-	\expectation\left[X\right]=\lambda\expectation\left[U\right]
-	\ .
-\end{equation}
-Conducting the same procedure
-\begin{equation*}
-	M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
-	\ ,
-\end{equation*}
-the variance can be obtained
-\begin{equation*}
-	\variance\left[X\right]=M_X''(0)-\left[M_X'(0)\right]^2
-\end{equation*}
-\begin{equation*}
-	\variance\left[X\right]=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
-\end{equation*}
-\begin{equation*}
-	\variance\left[X\right]=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
-\end{equation*}
-resulting in
-\begin{equation}
-	\variance\left[X\right] = \lambda\expectation\left[U^2\right]
-	\ .
-\end{equation}
-This can be extended for higher moments.
-
-Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$.
-By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.
-
-If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
-\begin{equation}
-	U\sim\gammaDist\left(\alpha,\beta\right)
-\end{equation}
-where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
-\begin{equation}
-	X\sim\CPoisson(\lambda,\alpha,\beta)
-	\ .
-\end{equation}
-The conditional distribution can be shown to be
-\begin{equation}
-	X|Y\sim\gammaDist\left(Y\alpha,\beta\right)
-	\ .
-\end{equation}
-
-Using results derived earlier, the m.g.f.~of the of $X$ is
-\begin{equation}
-	M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
-\end{equation}
-and moments can be obtained from it such as
-\begin{equation}
-	\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
-\end{equation}
-\begin{equation}
-	\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
-	\label{eq:compoundPoisson_variance}
-\end{equation}
-and
-\begin{equation}
-	\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
-	\ .
-\end{equation}
-
-The p.d.f.~can be shown to be
-\begin{equation}
-	p_X(x) = 
-	\begin{cases}
-		\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
-		\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
-	\end{cases}
-	\label{eq:compoundPoisson_pdf}
-\end{equation}
-and it is well known the infinite sum cannot be written in closed form.
-There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
-Of course direct simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated.
-The p.d.f.~then can be estimated using these simulated samples.
-
-For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, parameter estimation can be difficult.
-Maximum likelihood estimation is very complicated \citep{withers2011compound}.
-It can be made simpler by fixing $\alpha$ to be known \citep{withers2011compound} but this is not useful in this context.
-
-Because the moments of a compound Poisson-Gamma random variable can be obtained easily, method of moments estimators can be obtained.
-Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
-Then the estimators
-\begin{equation}
-	\widehat{\lambda}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
-\end{equation}
-\begin{equation}
-	\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
-\end{equation}
-\begin{equation}
-	\widehat{\beta}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
-\end{equation}
-are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}.
-These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
-
-However, parameter estimation can be made easier once it can be realised that the compound Poisson-Gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}.
-To show this, it is particular useful to reparametrize the compound Poisson-Gamma distribution using the following:
-\begin{equation}
-	p=\frac{2+\alpha}{1+\alpha}
-	\ ,
-\end{equation}
-\begin{equation}
-	\mu=\frac{\lambda\alpha}{\beta}
-	\ ,
-\end{equation}
-\begin{equation}
-	\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
-	\ .
-\end{equation}
-The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. It can be shown that $1<p<2$, $\mu>0$ and $\phi>0$.
-
-By rearranging the parameters to get
-\begin{equation}
-	\lambda=\frac{\mu^{2-p}}{\phi(2-p)}
-\end{equation}
-\begin{equation}
-	\alpha=\frac{2-p}{p-1}
-\end{equation}
-\begin{equation}
-	beta=\frac{1}{\phi(p-1)\mu^{p-1}}
-\end{equation}
-and substituting it into Equation \eqref{eq:compoundPoisson_pdf}, the p.m.f.~at zero can be shown to be
-\begin{equation}
-	\prob(X=0) = \exp
-	\left[
-	    -\frac{\mu^{2-p}}{\phi(2-p)}
-	\right]
-\end{equation}
-and the p.d.f.~for $x>0$ is
-\begin{multline*}
-	p_X(x) = \sum_{y=1}^{\infty}
-	\left[
-		\frac{1}{\phi(p-1)\mu^{p-1}}
-	\right]^{y\alpha}
-	\frac{1}{\Gamma(y\alpha)}
-	x^{y\alpha-1}
-	\exp\left[
-	    -\frac{x}{\phi(p-1)\mu^{p-1}}
-	\right]
-	\\
-	\exp\left[
-	    -\frac{\mu^{2-p}}{\phi(2-p)}
-	\right]
-	\left[
-		\frac{\mu^{2-p}}{\phi(2-p)}
-	\right]^y
-	\frac{1}{y!}
-	\ .
-\end{multline*}
-Tidying up the equation
-\begin{multline*}
-	p_X(x) = 
-	\exp\left[
-		\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)
-	\right]
-	\frac{1}{x}
-	\\
-	\sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-	\ .
-\end{multline*}
-To simplify further, it should be noted that
-\begin{align*}
-	2-p-\alpha(p-1) &= 2-p - \frac{2-p}{p-1}(p-1)
-	\\&=0
-\end{align*}
-so that
-\begin{equation}
-	p_X(x) = 
-	\exp\left[
-		\frac{1}{\phi}
-		\left(
-			x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
-		\right)
-	\right]
-	\frac{1}{x}
-	\sum_{y=1}^{\infty}W_y(x,p,\phi)
-\end{equation}
-where
-\begin{equation}
-	W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-	\ .
-\end{equation}
-
-Those familiar with generalised linear models \citep{nelder1972generalized} \citep{mccullagh1984generalized} will notice that for fixed $p$ or $\alpha$, the above is in the form of a distribution in the dispersive exponential family.
-Parameter estimation then can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
-These has applications in for example insurance claim data \citep{jorgensen1994fitting} \citep{smyth2002fitting}.
-
-Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
-One easy way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
-
-One special property of the compound Poisson-Gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}. It has a special variance mean relationship
-\begin{equation}
-	\variance[X] = \phi \mu^p
-\end{equation}
-where, as a reminder, $1<p<2$. This can be derived using Equation \eqref{eq:compoundPoisson_variance} or via the partition function $Z$. That is let
-\begin{equation}
-	\theta = \frac{\mu^{1-p}}{1-p}
-\end{equation}
-and
-\begin{equation}
-	\ln Z = \frac{1}{\phi(2-p)\theta^\alpha(1-p)^\alpha} \ ,
-\end{equation}
-then
-\begin{equation}
-	\variance[X] = \phi^2 \frac{\partial^2\ln Z}{\partial\theta^2} \ .
-\end{equation}
+Instead of reconstructing the object, the analysis can be done on the x-ray images itself, or projection space, by comparing it to a simulation such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+\cite{brierley2018optimized} developed an algorithm to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition.
+It is however very complicated as it is optimising over a very large dimensional space.
+\cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulations with each other, one with defects and the other without.
+It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.

### 2019-05-06 reports/thesis/chapters/1_literatureReview.tex
Literature review complete

@@
 One of the first methods of additive manufacturing (AM) is stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} which involves the curing of a photosensitive resin using an ultraviolet laser.
-The technology has evolved and AM is capable of manufacturing objects with complicated internal and external geometries.
+The technology has evolved and AM is capable of manufacturing objects with complicated internal and external geometries, some examples are shown in Figure \ref{fig:literature_3dprint}.
 However, there is a need for product inspection and in particular assessing the quality of the internal structures.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_3dprint.png}
+  \caption{Examples of additive manufactured parts: a) lattice structure, b) toy, c) chain, d) model of a facial implant, e) spanner, f) ratchet mechanism, g) toy, h) series of rotatable gears, i) lattice structure.
+Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
+  \label{fig:literature_3dprint}
+\end{figure}
 
@@
 The following power based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}.
+Illustrations of these technologies are shown in Figure \ref{fig:literature_technologies}.
+
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.59\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_stl.png}
+      \caption{Stereolithography}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.39\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_fdm.png}
+      \caption{Fused deposition modelling}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_3dp.png}
+      \caption{3D printing}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.7\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_technologies_laser.png}
+      \caption{Selective laser sintering}
+    \end{subfigure}
+  }
+  \caption{Diagrams of various AM technologies. Reprinted from \cite{wang20173d} with permission from Elsevier.}
+  \label{fig:literature_technologies}
+\end{figure}
 
@@
 A laser with a specific wavelength, typically \SIrange{300}{400}{\nano\metre} \citep{kodama1981automatic}, is emitted onto a point of the surface of the liquid and solidifies.
-The laser is controlled by a computer to solidified specific parts of the liquid surface.
+The laser is controlled by a computer to solidify specific parts of the liquid surface.
 The platform is lowered and the cycle repeats, manufacturing the object layer by layer.
@@
 The binding agent is cured via evaporation or heating which glues the powder particles together.
-The bed can move in all 3 dimensions and the object is manufactured layer by layer.
+The jetting head can move in the $x-y$ plane and the object is manufactured layer by layer by moving the platform in the $z$ direction and renewing the powder using a roller.
 The binding agent must have low viscosity so it can be deposited, it may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}.
@@
 This is done in a chamber heated just below the melting point of the material \citep{wong2012review}.
-Various materials such as metal and plastics can be used \citep{wong2012review}.
+Various materials such as metals and plastics can be used \citep{wong2012review}.
 Electron beam melting is similar but instead an electron beam is used instead of a laser and this is done in a high vacuum chamber to avoid oxidation \citep{wong2012review}.
-In laser engineered net shaping, a powder bed is not used; instead the powder is deposited on the desired location and then melted using a laser.
+In laser engineered net shaping, a powder bed is not used; the powder is deposited on the desired location and then melted using a laser, as shown in Figure \ref{fig:literature_lens}.
 This is a popular method to manufacture metal objects \citep{gibson2010additive}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_lens.png}
+  \caption{Laser engineered net shaping. Reprinted from \citep{wong2012review} under the CC BY 3.0 license.}
+  \label{fig:literature_lens}
+\end{figure}
 
@@
 The strength of the manufactured object vary from geometry to geometry but also from direction to direction.
-Because the manufactured object was made layer by layer, the strength varies if the load was applied in the building direction (vertical) or the scanning direction (horizontal) \citep{kim2008benchmark}.
+Because the manufactured object are made layer by layer, the strength varies if the load was applied in the building direction (vertical) or the scanning direction (horizontal) \citep{kim2008benchmark}.
 Experimental results shown that fused deposition modelling has superior strength in the scanning direction but weak in the building direction \citep{kim2008benchmark}.
@@
 The blueprint of the object to be manufactured is called a computer-aided design (CAD).
-For it to be processed by an AM apparatus, the CAD is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of series of triangles.
+For it to be processed by an AM apparatus, the CAD is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of a series of triangles, an example is shown in Figure \ref{fig:literature_stl}.
 STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
+  \caption{An example of a CAD (left) converted to a STL file (right). Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
+  \label{fig:literature_stl}
+\end{figure}
+
 When the AM object is manufactured, post processing techniques can be done at this stage.
@@
 The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
-This will be reviewed in the second half of this chapter.
 
@@
 The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}.
-The idea is that problems in the manufacturing is found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
+The idea is that problems in the manufacturing are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
 
 There are various discontinuities in AM, in particular in the manufacturing of metal parts \citep{everton2016review}.
-For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}; they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}.
+For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}, they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}.
 Layers may not fuse together and form elongated pores, this can be fixed by increasing the energy of the beam but too high will cause evaporation of the AM part \citep{mumtaz2008high}.
 They can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review}.
-Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles on the surface of the AM part \citep{li2012balling, gu2009balling}.
+They are observable using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}.
+Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}.
 The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}.
 Low oxygen content in the environment \citep{niu1999instability} and higher energy beams \citep{gu2009balling} can reduce the balling effect.
+Some examples are shown in Figure \ref{fig:literature_balling} using an electron scanning microscope.
 Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.99\textwidth]{../figures/literatureReview/literature_pores.png}
+  \caption{A scanning electron microscope image of a) pores and b) elongated pores from an electron beam melting manufactured object. Reprinted from \cite{tammas2015xct} under the CC BY 4.0 license.}
+  \label{fig:literature_pores}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_balling.png}
+  \caption{A scanning electron microscope image of balling on a selective laser melting manufactured object. Reprinted from \cite{li2012balling} with permission from Springer Nature.}
+  \label{fig:literature_balling}
+\end{figure}
 
@@
 The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a bed.
-An x-ray source and x-ray detector pair rotate and/or translate around and/or along the patient to get readings of the x-rays after attenuating the patient using different paths.
-X-ray beams are pencil beams in the early versions of XCT.
-To reduce scanning times, cone shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}.
+An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating the patient using different paths.
+X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}.
+To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}.
 These multiple x-ray readings or images can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}.
+This is illustrated in Figure \ref{fig:literature_medicalct}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.99\textwidth]{../figures/literatureReview/literature_medicalct.png}
+  \caption{In medical XCT, a fan shaped x-ray beam is emitted and attenuate through the patient and detected by a detector.
+The x-ray source and detector rotate around and translate along the patient.
+By collecting readings at different angles, the image of the patient can be reconstructed.
+Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
+  \label{fig:literature_medicalct}
+\end{figure}
 
@@
 Many reconstruction algorithms have been proposed to take the compound Poisson noise into consideration \citep{elbakri2002statistical, elbakri2003efficient, elbakri2003statistical, lasio2007statistical, xie2008x}.
-They are very complicated will not be discussed here because they are beyond the scope of this thesis.
 
@@
 Typically the x-ray is a cone beam \citep{kruth2011computed}.
+This is illustrated in Figure \ref{fig:literature_xct}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.75\textwidth]{../figures/literatureReview/literature_xct.png}
+  \caption{The setup of XCT used in metrology. Reprinted from \cite{warnett2016towards} under the CC BY 3.0 license.}
+  \label{fig:literature_xct}
+\end{figure}
 
@@
 
-X-rays \citep{rontgen1896on} are produced in an x-ray tube.
+X-rays \citep{rontgen1896on} are produced in an x-ray tube, a diagram shown in Figure \ref{fig:literature_tube}.
 It consist of a vacuum tube containing a cathode and an anode.
@@
 The cathode is usually tungsten and the anode contains a small amount of tungsten, molybdenum or copper \citep{sun2012overview}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{../figures/literatureReview/literature_tube.png}
+  \caption{An x-ray tube. Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
+  \label{fig:literature_tube}
+\end{figure}
 
@@
 This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state.
-This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target.
+This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.
 
@@
 The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode.
-The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies.
+The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies \citep{sun2012overview}.
+An example is shown in Figure \ref{fig:literature_spectrum}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{../figures/literatureReview/literature_spectrum.png}
+  \caption{An example of the distribution of energies a photon can have emitted from an x-ray tube.
+Bremsstrahlung and characteristic radiation contribute to the continuous and discrete components of the distribution.
+Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
+  \label{fig:literature_spectrum}
+\end{figure}
 
 The object being scanned are exposed to x-ray photons in XCT.
-X-ray photons undergo attenuation when interacting with the object in a number of ways.
+X-ray photons undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}.
 The object can absorb the photons via the photoelectric effect.
-In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}.
-Photons can be scattered by the sample by colliding inelastically with and transfers its energy to the an electron.
+In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}.
+Photons can be scattered by the object by colliding inelastically with and transfers its energy to the an electron.
 This process is known as Compton scattering \citep{compton1923quantum}.
@@
 Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law.
-In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the detected photons.
+In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the detected photons \citep{sun2012overview}.
 This is called beam hardening.
@@
 The x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}.
-The visible light is detected by photodiodes and coverts it into an electrical signal \citep{michael2001x}.
+The visible light is detected by photodiodes and coverts it into an electrical signal.
 The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{whiting2006properties, kruth2011computed}.
@@
 In XCT, the scale of each voxel in the reconstruction can be obtained by using XCT on an object with pre-determined lengths, these are known as reference standards \citep{bartscher2007enhancement} but can have similar names.
-Reference standards can vary in geometry such as a sphere on a cylinder \citep{lifton2013application}, two spheres on a cylinder \citep{sun2016reference}, a cube with cut outs \citep{kiekens2011test}, a plate with various features \citep{moylan2014additive, mohring2015testpart}, a hollow cylinder, a step-cylinder and a ball-bar \citep{bartscher2007enhancement}.
-They can be manufactured using AM \citep{mohring2015testpart} but this can become a chicken and egg problem, determining the measurements of an AM object using an AM object.
+Reference standards can vary in geometry such as a sphere on a cylinder \citep{lifton2013application}, two spheres on a cylinder \citep{sun2016reference}, a cube with cut outs \citep{kiekens2011test}, a hollow cylinder, a step-cylinder and a ball-bar \citep{bartscher2007enhancement}; the latter three are shown in Figure \ref{fig:literature_referenceStandards}.
+
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test1.png}
+      \caption{Hollow cylinder}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test2.png}
+      \caption{Step-cylinder}
+    \end{subfigure}
+  }
+  \begin{subfigure}[b]{0.6\textwidth}
+    \includegraphics[width=\textwidth]{../figures/literatureReview/literature_test3.png}
+    \caption{Ball-bar}
+  \end{subfigure}
+  \caption{Various reference standards: a) aluminium hollow cylinder, outer diameters \SI{30}{\milli\metre} and \SI{20}{\milli\metre}, b) aluminium step-cylinder with diameter \SI{300}{\milli\metre}, c) ceramic balls of diameter \SI{30}{\milli\metre} on a carbon fibre rod, the balls are separated by \SI{100}{\milli\metre}.
+Reprinted from \citep{bartscher2007enhancement} with permission from Elsevier.}
+  \label{fig:literature_referenceStandards}
+\end{figure}
 
@@
 The magnification can be adjusted by adjusting the distances between the x-ray tube, the object and the x-ray detector.
-Increasing the magnification increases the image resolution but can cause blurred images \citep{kruth2011computed}.
-Another important factor is the focal spot size because larger spot sizes produce blurry results, this is know as the penumbra effect \citep{kueh2016modelling}.
-However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.
-There is also the question on how to orient the object on the turntable \citep{corcoran2016observations}.
-All of these variables can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however there may be inconsistencies.
+Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}.
+Blurry results from larger spot sizes, this is know as the penumbra effect \citep{kueh2016modelling}.
+However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_magnification.png}
+  \caption{The magnification can be adjusted by adjusting the distances between the x-ray source, the object and the x-ray detector.
+Because of a finite x-ray spot size, blurry effects are produced using a magnification too large.
+Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
+  \label{fig:literature_magnification}
+\end{figure}
+
+There is also the question on how to orient the object on the turntable \citep{corcoran2016observations} as well as how many angles to use \citep{kruth2011computed}.
+More angles produce a more accurate reconstruction but requires more acquisition time.
+Figure \ref{fig:literature_angles} shows an example of a reconstruction using various number of angles.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
+  \caption{A reconstruction when scanning three aligned balls using a different number of angles. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
+  \label{fig:literature_angles}
+\end{figure}
+
+All of the parameters of XCT discussed can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however there may be inconsistencies.
 For example even though the target material of the anode and power is specified, the energy spectrum can still vary \citep{stumbo2004direct}.
@@
 Problems can occur in the detector.
-For examples pixels in the acquired x-ray can be defected or dead \citep{brettschneider2014spatial} and panels can appear \citep{yang2009evaluation}.
+For examples pixels in the acquired x-ray can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can appear \citep{yang2009evaluation}.
 Spatially correlated noise can be observed as well \citep{sun2016characterisation}.
@@
 This can cause flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed} as well as artefacts \citep{sun2016applications}.
-Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper.
-This reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}.
-Beam hardening can also be considered in the reconstruction stage \citep{sun2016applications}.
+Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate, called a filter, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper.
+Figure \ref{fig:literature_hardening} shows an example of a reconstruction with and without a filter, without the filter the outer perimeter appears less dense than it should be.
+A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}.
+Early reconstruction algorithms assumed no beam hardening but it can be corrected using modern methods \citep{sun2016applications}.
+
+\begin{figure}
+  \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_hardening_noFilter.png}
+      \caption{No filter}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.4\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_hardening_filter.png}
+      \caption{Al/Cu filter}
+    \end{subfigure}
+  \caption{A reconstruction of a hollow cylinder, outer diameter \SI{6.0}{\milli\metre} and inner diameter \SI{0.6}{\milli\metre}.
+In a), no filter was used.
+In b) a filter was placed in front of the x-ray tube.
+Reprinted from \citep{kruth2011computed} with permission from Elsevier}
+  \label{fig:literature_hardening}
+\end{figure}
 
 The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm as it caters for cone beams.
-However it assumes a circular trajectory from the source which can produce artefacts \citep{sun2016applications}.
+However it assumes a circular trajectory from the source which can cause artefacts if assumptions are not met \citep{sun2016applications}.
 
@@
 However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
-The strength of XCT comes from the fact that the location of the pores can be visualised and compared to the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+The strength of XCT comes from the fact that the location of the pores can be visualised, for example in Figure \ref{fig:literature_pores3D}, and compared to the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
 Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}.
 \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor.
-In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.
+
+\begin{figure}
+  \centering
+      \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_pores3D1.png}
+      \caption{Reconstruction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_pores3D2.png}
+      \caption{Sample from the reconstruction}
+    \end{subfigure}
+    \caption{The reconstruction can show pores in the manufactured object.
+b) shows the reconstructed samples from the blue cubes in a).
+Reprinted from \cite{tammas2015xct} under the CC BY 4.0 license.}
+    \label{fig:literature_pores3D}
+\end{figure}
+
+\begin{figure}
+  \centering
+      \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_warnett1.png}
+      \caption{External}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_warnett2.png}
+      \caption{Internal}
+    \end{subfigure}
+    \caption{The reconstruction was aligned and compared to the CAD.
+The surface heat map shows the surface deviation (or `variance' in the literature) externally (a) and internally (b).
+Reprinted from \cite{warnett2016towards} under the CC BY 3.0 license.}
+    \label{fig:literature_warnett}
+\end{figure}
 
@@
 Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar.
-The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}.
+The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}.
 \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction.
-This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs.
+This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}.
 X-ray images at fewer angles can be taken but they can be obtained in one acquisition, speeding up the process.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_conveyor.png}
+  \caption{XCT can be done on a conveyor belt surrounded by x-ray source and detector pairs. Reprinted from \cite{warnett2016towards} under the CC BY 3.0 license.}
+  \label{fig:literature_conveyor}
+\end{figure}
 

### 2019-05-25 reports/thesis/chapters/2_dataCollection.tex

Figure \ref{fig:data_AbsNoFilter} shows the data. Shading correction is done via the following. It requires calibration images, they are projections of nothing at different powers. For each calibration image, calculate the within image mean. For each pixel, do a linear regression of the within image mean versus the grey value for different powers: bw shading correction uses only the black and max power calibration images, linear shading correction uses all calibration images. The regression maps the uncorrected grey value ($x$) to the shading corrected grey value ($y$) for this particular pixel.

An example is shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap}. In Figure \ref{fig:data_shadingCorrectionExample_gainMap} a), 3 random pixels were used to demonstrate the regression. The gradient of the regression for all pixels are shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap} b).

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
      \caption{Projection of sample at \SI{44}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
      \caption{Simulation of sample at \SI{44}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
      \caption{Projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
      \caption{Projection at \SI{44}{\watt}}
    \end{subfigure}
  }
  \caption{Projections obtained; note the colour scale may vary.}
  \label{fig:data_AbsNoFilter}
\end{figure}

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
      \caption{Example gain curves}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_bw.eps}
      \caption{Normalised gain map}
    \end{subfigure}
  }
  \caption{Normalised gain map from bw shading correction is shown in b). They were obtained by using the gradient in the example shown in a) for 3 random pixels.}
  \label{fig:data_shadingCorrectionExample_gainMap}
\end{figure}

The gain is actually the sensitivity so it should be a plot of the grey value versus the power, this is shown in Figure \ref{fig:data_shadingCorrectionExample_gain}. However this is similar to the linear regression done for shading correction.

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_bw.eps}
      \caption{bw shading correction}
    \end{subfigure}
  }
  \caption{Gain curve before and after shading correction. The box plot summarise all $2000\times2000$ pixels in a projection.}
  \label{fig:data_shadingCorrectionExample_gain}
\end{figure}

In the black image, I've noticed the vertical read-out structure can be seen. This can be done by plotting the grey value down a column as shown in Figure \ref{fig:data_oddEven}. In particular, the grey value jumps up and down at every pixel, this is seen by plotting the same profile curve but for every odd and even $y$. Shading correction corrects this because the black image has information on the odd/even structure which is then fed into the shading correction.

An autocorrelation plot could be plotted, but it's easier to do a Fourier transform, this is shown in Figure \ref{fig:data_fft}.

No read-out structure can be seen horizontally, see Figure \ref{fig:data_oddEvenX}. Panel structure can be seen however.

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_null.eps}
      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_null.eps}
      \caption{No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_bw.eps}
      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_bw.eps}
      \caption{bw shading correction}
    \end{subfigure}
  }
  \caption{Left shows the profile plot of a black image at $(879,y)$ before and after shading correction. Right shows two curves for odd and even $y$.}
  \label{fig:data_oddEven}
\end{figure}

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_bw.eps}
      \caption{bw shading correction}
    \end{subfigure}
  }
  \caption{Fourier transform on the black image before and after shading correction. The colour scale is in arbitrary units and range between 0 to 255.}
  \label{fig:data_fft}
\end{figure}

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_nullX.eps}
      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_nullX.eps}
      \caption{No shading correction}
    \end{subfigure}
  }
  \caption{Left shows the profile plot of a black image at $(y,879)$ before and after shading correction. Right shows two curves for odd and even $y$.}
  \label{fig:data_oddEvenX}
\end{figure}

### 2019-05-25 reports/thesis/chapters/3_compoundPoisson.tex

@@
+\section{Compound Poisson}
+
+The greyvalues of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector.
+When the photons interact with the scintillator, they are converted into visible light.
+The visible light photons are then detected and converted into a greyvalue.
+How the detected visible light is converted is important in modelling the greyvalue.
+
+Should the greyvalue be proportional to the number of photons detected, the detector is known as a quantum counter and the greyvalue is a Poisson random variable, up to a constant \citep{whiting2006properties}.
+However if the greyvalue records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector.
+The greyvalue has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}.
+There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
+
+Experiments have been done to verify the compound Poisson nature of the detector.
+This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers.
+It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
+The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.
+
+The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
+\begin{equation*}
+	Y\sim\poisson(\lambda)
+\end{equation*}
+that is
+\begin{equation*}
+	\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\dotdotdot
+\end{equation*}
+where $\lambda>0$ is the Poisson rate parameter.
+Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$.
+Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
+\begin{equation}
+	X|Y = \sum_{i=1}^{Y}U_i+\kappa
+	\label{eq:compoundPoisson_X|Y}
+\end{equation}
+where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
+\begin{equation*}
+	p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0
+	\ .
+\end{equation*}
+However it should be noted that $X=0$ if and only if $Y=0$ with probability
+\begin{equation*}
+	\prob(X=0)=\euler^{-\lambda} \ .
+\end{equation*}
+Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
+\begin{equation}
+	p_X(x) = 
+	\begin{cases}
+		\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
+		\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
+	\end{cases}
+\end{equation}
+where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.
+
+The m.g.f.~of $X$ has a nicer form however. Let the m.g.f.~of $X$ be
+\begin{equation*}
+	M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
+	\ .
+\end{equation*}
+This can be computed using the result for conditional expectations
+\begin{equation*}
+	M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]
+	\ .
+\end{equation*}
+Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
+\begin{equation*}
+	M_X(\theta)=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
+\end{equation*}
+\begin{equation*}
+	M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
+	\ .
+\end{equation*}
+But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.
+\begin{equation*}
+	M_U(\theta)=\expectation\left[\euler^{U\theta}\right]
+	\ ,
+\end{equation*}
+then
+\begin{equation*}
+	M_X(\theta)=\expectation\left(
+		\expectation\left[\euler^{\theta U_1}|Y\right]\cdot
+		\expectation\left[\euler^{\theta U_2}|Y\right]\cdot
+		\dotdotdot \cdot
+		\expectation\left[\euler^{\theta U_Y}|Y\right]
+	\right)
+\end{equation*}
+\begin{equation*}
+	M_X(\theta)=\expectation\left[\left(M_U(\theta)\right)^Y\right]
+\end{equation*}
+\begin{equation*}
+	M_X(\theta)=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
+\end{equation*}
+\begin{equation*}
+	M_X(\theta) = M_Y\left(\ln(M_U(\theta)\right)
+\end{equation*}
+where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
+\begin{equation}
+	M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
+	\exp
+	\left[
+		\lambda
+		\left(
+		  \euler^\theta-1
+		\right)
+	\right]
+\end{equation}
+then
+\begin{equation}
+	M_X(\theta)=
+	\exp\left[
+		\lambda
+		\left(
+			M_U(\theta)-1
+		\right)
+	\right]
+	\ .
+\end{equation}
+As long as the m.g.f.~of $U$ is known, then m.g.f.~of $X$ can be written in closed form.
+
+Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
+\begin{align*}
+	M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
+	M_X'(\theta)&=M_X(\theta)\lambda M_U'(\theta)
+\end{align*}
+then
+\begin{equation}
+	\expectation\left[X\right]=\lambda\expectation\left[U\right]
+	\ .
+\end{equation}
+Conducting the same procedure
+\begin{equation*}
+	M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
+	\ ,
+\end{equation*}
+the variance can be obtained
+\begin{equation*}
+	\variance\left[X\right]=M_X''(0)-\left[M_X'(0)\right]^2
+\end{equation*}
+\begin{equation*}
+	\variance\left[X\right]=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
+\end{equation*}
+\begin{equation*}
+	\variance\left[X\right]=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
+\end{equation*}
+resulting in
+\begin{equation}
+	\variance\left[X\right] = \lambda\expectation\left[U^2\right]
+	\ .
+\end{equation}
+This can be extended for higher moments.
+
+Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$.
+By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.
+
+If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
+\begin{equation}
+	U\sim\gammaDist\left(\alpha,\beta\right)
+\end{equation}
+where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
+\begin{equation}
+	X\sim\CPoisson(\lambda,\alpha,\beta)
+	\ .
+\end{equation}
+The conditional distribution can be shown to be
+\begin{equation}
+	X|Y\sim\gammaDist\left(Y\alpha,\beta\right)
+	\ .
+\end{equation}
+
+Using results derived earlier, the m.g.f.~of the of $X$ is
+\begin{equation}
+	M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
+\end{equation}
+and moments can be obtained from it such as
+\begin{equation}
+	\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
+\end{equation}
+\begin{equation}
+	\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
+	\label{eq:compoundPoisson_variance}
+\end{equation}
+and
+\begin{equation}
+	\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
+	\ .
+\end{equation}
+
+The p.d.f.~can be shown to be
+\begin{equation}
+	p_X(x) = 
+	\begin{cases}
+		\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
+		\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
+	\end{cases}
+	\label{eq:compoundPoisson_pdf}
+\end{equation}
+and it is well known the infinite sum cannot be written in closed form.
+There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
+Of course direct simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated.
+The p.d.f.~then can be estimated using these simulated samples.
+
+For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, parameter estimation can be difficult.
+Maximum likelihood estimation is very complicated \citep{withers2011compound}.
+It can be made simpler by fixing $\alpha$ to be known \citep{withers2011compound} but this is not useful in this context.
+
+Because the moments of a compound Poisson-Gamma random variable can be obtained easily, method of moments estimators can be obtained.
+Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
+Then the estimators
+\begin{equation}
+	\widehat{\lambda}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
+\end{equation}
+\begin{equation}
+	\widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
+\end{equation}
+\begin{equation}
+	\widehat{\beta}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
+\end{equation}
+are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}.
+These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+
+However, parameter estimation can be made easier once it can be realised that the compound Poisson-Gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}.
+To show this, it is particular useful to reparametrize the compound Poisson-Gamma distribution using the following:
+\begin{equation}
+	p=\frac{2+\alpha}{1+\alpha}
+	\ ,
+\end{equation}
+\begin{equation}
+	\mu=\frac{\lambda\alpha}{\beta}
+	\ ,
+\end{equation}
+\begin{equation}
+	\phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
+	\ .
+\end{equation}
+The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. It can be shown that $1<p<2$, $\mu>0$ and $\phi>0$.
+
+By rearranging the parameters to get
+\begin{equation}
+	\lambda=\frac{\mu^{2-p}}{\phi(2-p)}
+\end{equation}
+\begin{equation}
+	\alpha=\frac{2-p}{p-1}
+\end{equation}
+\begin{equation}
+	beta=\frac{1}{\phi(p-1)\mu^{p-1}}
+\end{equation}
+and substituting it into Equation \eqref{eq:compoundPoisson_pdf}, the p.m.f.~at zero can be shown to be
+\begin{equation}
+	\prob(X=0) = \exp
+	\left[
+	    -\frac{\mu^{2-p}}{\phi(2-p)}
+	\right]
+\end{equation}
+and the p.d.f.~for $x>0$ is
+\begin{multline*}
+	p_X(x) = \sum_{y=1}^{\infty}
+	\left[
+		\frac{1}{\phi(p-1)\mu^{p-1}}
+	\right]^{y\alpha}
+	\frac{1}{\Gamma(y\alpha)}
+	x^{y\alpha-1}
+	\exp\left[
+	    -\frac{x}{\phi(p-1)\mu^{p-1}}
+	\right]
+	\\
+	\exp\left[
+	    -\frac{\mu^{2-p}}{\phi(2-p)}
+	\right]
+	\left[
+		\frac{\mu^{2-p}}{\phi(2-p)}
+	\right]^y
+	\frac{1}{y!}
+	\ .
+\end{multline*}
+Tidying up the equation
+\begin{multline*}
+	p_X(x) = 
+	\exp\left[
+		\frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)
+	\right]
+	\frac{1}{x}
+	\\
+	\sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+	\ .
+\end{multline*}
+To simplify further, it should be noted that
+\begin{align*}
+	2-p-\alpha(p-1) &= 2-p - \frac{2-p}{p-1}(p-1)
+	\\&=0
+\end{align*}
+so that
+\begin{equation}
+	p_X(x) = 
+	\exp\left[
+		\frac{1}{\phi}
+		\left(
+			x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
+		\right)
+	\right]
+	\frac{1}{x}
+	\sum_{y=1}^{\infty}W_y(x,p,\phi)
+\end{equation}
+where
+\begin{equation}
+	W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+	\ .
+\end{equation}
+
+Those familiar with generalised linear models \citep{nelder1972generalized} \citep{mccullagh1984generalized} will notice that for fixed $p$ or $\alpha$, the above is in the form of a distribution in the dispersive exponential family.
+Parameter estimation then can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
+These has applications in for example insurance claim data \citep{jorgensen1994fitting} \citep{smyth2002fitting}.
+
+Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
+One easy way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
+
+One special property of the compound Poisson-Gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}. It has a special variance mean relationship
+\begin{equation}
+	\variance[X] = \phi \mu^p
+\end{equation}
+where, as a reminder, $1<p<2$. This can be derived using Equation \eqref{eq:compoundPoisson_variance} or via the partition function $Z$. That is let
+\begin{equation}
+	\theta = \frac{\mu^{1-p}}{1-p}
+\end{equation}
+and
+\begin{equation}
+	\ln Z = \frac{1}{\phi(2-p)\theta^\alpha(1-p)^\alpha} \ ,
+\end{equation}
+then
+\begin{equation}
+	\variance[X] = \phi^2 \frac{\partial^2\ln Z}{\partial\theta^2} \ .
+\end{equation}
+
 In this chapter, the compound Poisson-Gamma distribution is reviewed and studied.

### 2019-05-25 reports/thesis/chapters/5_inference.tex

@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius2.txt}$}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius3.txt}$}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_z.eps}
+        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$}
       \end{subfigure}
@@
   \caption{Filtered $z$ image from the \texttt{Sep16 120deg} dataset. Various kernel radiuses were used.}
-  \label{fig:inference_sep16120deg_zfiltered}
+  \label{fig:inference_AbsFilterDeg120_zfiltered}
 \end{figure}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius1}
+  \label{fig:inference_AbsFilterDeg120_inference_radius1}
 \end{figure}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius2.txt}$.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius2}
+  \label{fig:inference_AbsFilterDeg120_inference_radius2}
 \end{figure}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius3.txt}$.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius3}
+  \label{fig:inference_AbsFilterDeg120_inference_radius3}
 \end{figure}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$.
+  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_sep16120deg_inference_radius4}
+  \label{fig:inference_AbsFilterDeg120_inference_radius4}
 \end{figure}
@@
 The empirical null filter was applied to the \texttt{Sep16 120deg} image as shown at the start of the chapter.
-Figure \ref{fig:inference_sep16120deg_zfiltered} shows the filtered $z$ images for various kernel radiuses.
-For $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image was smooth and treated everything as the null.
+Figure \ref{fig:inference_AbsFilterDeg120_zfiltered} shows the filtered $z$ images for various kernel radiuses.
+For $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$, the resulting $z$ image was smooth and treated everything as the null.
 When a large enough radius was used, the defects were highlighted by the higher test statistics and everything else remain unchanged.
-Figures \ref{fig:inference_sep16120deg_inference_radius1} to \ref{fig:inference_sep16120deg_inference_radius4} shows the resulting inference along with the empirical null parameters.
+Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} to \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference along with the empirical null parameters.
 The figures shows that for large enough kernel radius, the filter ironed out the false positives observed at the start of the chapter.
@@
 The resulting filtered segments were stitched together to form the resulting filtered image.
-By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.
+By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
 It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$.
+  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 c) and d) Empirical null mean and standard deviation.}
-  \label{fig:inference_subroisep16120deg_inference_radius4}
+  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
 \end{figure}

### 2019-05-25 reports/paper1/paper.tex
Update figure

@@
 The resulting filtered segments were stitched together to form the resulting filtered image.
-The resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.
+The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
 
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
         \caption{X-ray image with positive pixels}
@@
 c) and d) Empirical null mean and standard deviation.}
-  \label{fig:inference_subroisep16120deg_inference_radius4}
+  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
 \end{figure*}

### 2019-05-25 reports/paper1/paper.tex
Revise paper

@@
 \usepackage{siunitx} %for measurements
+\usepackage{soul}%highlight changes
 
@@
 
-\title{Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays}
+\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
 \date{2019}
@@
 X-ray computed tomography can be used for defect detection in additive manufacturing.
-The object is scanned at multiple angles to reconstruct the object in 3D space.
-To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single scan.
-A 3D printed sample was manufactured with voids to see if they can be detected.
+\hl{Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
+To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.} A 3D printed sample was manufactured with voids to see if they can be detected.
 The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test.
@@
 The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
-The disadvantage of x-ray CT is that it involves calculations on the acquisition of hundreds of angles of the sample.
+The disadvantage of x-ray CT is that it involves the \hl{acquisition and reconstruction of thousands} of projections of the sample.
+Speeding up the quality control process on the production line could be done by doing an inspection on a \hl{fewer number of projections by sacrificing accuracy} \citep{warnett2016towards, brierley2018optimized}.
 
-Speeding up the quality control process on the production line could be done by doing an inspection on a few numbers of x-ray images \citep{warnett2016towards}.
-These x-ray images are compared with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-\texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}.
-Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods.
+A method was proposed to compare a \hl{single projection with a simulation of that projection and treating it as the ground truth.} This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
+Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
+This was necessary because the simulation of the projection did not match up perfectly, producing incorrect inference.
 
-A method was proposed to compare the x-ray image with \texttt{aRTist} by treating the simulation of \texttt{aRTist} as the ground truth.
-This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
-However beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
-This was necessary because the simulation of \texttt{aRTist} do not match up perfectly with the x-ray image, producing incorrect inference.
-
-An x-ray image of a 3D printed sample was obtained and compared with the \texttt{aRTist} simulation in an experiment.
+An x-ray \hl{projection} of a 3D printed sample was obtained and compared with the simulation in an experiment.
 The procedure is shown in the methods section along with the description of the empirical null filter.
@@
 
-A ABS plastic cuboid (\SI{4}{\centi\metre} $\times$ \SI{4}{\centi\metre} $\times$ \SI{6}{\centi\metre}) with voids was purposefully manufactured to see if they can be detected.
-The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus} 3D printer.
-The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
+An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected.
+The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer.
+The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
 6 voids for each diameter were designed in the CAD.
@@
   \caption{CAD of a 3D cuboid with voids.
-The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
+The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
 6 voids for each diameter were designed in the CAD.
@@
 
-The x-ray source used a tungsten filament with a copper filter.
-The current and voltage was set to \SI{250}{\micro\ampere} and \SI{80}{\kilo\volt} respectively.
-The exposure time was \SI{500}{\milli\second}.
-The x-ray detector is a \emph{Perkin Elmer XRD 1621 AN/CN} digital x-ray detector, producing a $2000\times 2000$ 16-bit image.
-Shading correction \citep{young2000shading, munzenmayer2003enhancing}, using a black image at \SI{0}{\kilo\volt} and a white image at \SI{80}{\kilo\volt}, were used to remove panel effects from the x-ray detector.
+X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}.
+The \SI{225}{\kilo\volt} source was used with a $2000\times2000$ pixel \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}.
+This object was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}.
+A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible.
+20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}.
+A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.
 
 The 3D printed sample was scanned 20 times at a fixed angle.
-The 20 x-ray images were spilt into 2.
-19 random images were held out.
-The remaining image was used to compare with \texttt{aRTist}.
-In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.
+The 20 x-ray projections were spilt into 2.
+19 random projections were held out.
+The remaining projection was used to compare with the simulation using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+In the \emph{aRTist} simulation, the software did a simulation as if the voids were not there.
+Numerical methods were used to align the simulated x-ray image to the obtained x-ray projection.
 
@@
 
-Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \texttt{aRTist}.
+Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \emph{aRTist}.
 A disagreement too big will classify that pixel as a positive result.
@@
   \dfrac{
-    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
+    \text{scan}_{x,y} - \emph{aRTist}_{x,y}
   }
@@
 The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link.
-The variance was predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable when working out the test statistics.
+The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable when working out the test statistics.
 
@@
 
-The empirical null filter was implemented using \texttt{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}.
+The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}.
 It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads.
@@
 It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
-This probably suggest that the contamination or inaccuracy from \texttt{aRTist} was face dependent.
+This probably suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.
 
@@
 The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
-Note the y-axis change scale.}
+Note that the $y$-axis changes scale.
+The box plot summarise 100 repeated measurements of the timings.}
   \label{fig:inference_timing}
@@
 There are a few strategies to accelerate the filter.
-The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \texttt{CUDA} and \texttt{C++} is fruitless if there may exist a faster method.
+The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method.
 Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation.
@@
 \section{Acknowledgements}
-This work is funded by EPSRC grant numbers EP/K031066/1 and EP/L016710/1.
+This work is funded by EPSRC grant numbers EP/K031066/1 (Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing) and EP/L016710/1 (EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme).
 

### 2019-05-25 reports/paper1/paper.tex
Revise paper

@@
 \usepackage{siunitx} %for measurements
-\usepackage{soul}%highlight changes
 
@@
 X-ray computed tomography can be used for defect detection in additive manufacturing.
-\hl{Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
-To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.} A 3D printed sample was manufactured with voids to see if they can be detected.
+Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
+To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.
+A 3D printed sample was manufactured with voids to see if they can be detected.
 The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test.
 The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
+Voids with diameters in the order of millimetres were detectable.
 \end{abstract}
@@
 
-Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}.
-The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
-The disadvantage of x-ray CT is that it involves the \hl{acquisition and reconstruction of thousands} of projections of the sample.
-Speeding up the quality control process on the production line could be done by doing an inspection on a \hl{fewer number of projections by sacrificing accuracy} \citep{warnett2016towards, brierley2018optimized}.
+Quality control in additive manufacturing can be done using x-ray computed tomography (CT) \citep{thompson2016x}.
+The CT is compared with the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
+The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample.
+Speeding up the quality control process on the production line could be done by doing an inspection using a fewer number of projections by sacrificing accuracy \citep{warnett2016towards, brierley2018optimized}.
 
-A method was proposed to compare a \hl{single projection with a simulation of that projection and treating it as the ground truth.} This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
+A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth.
+This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
 Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
-This was necessary because the simulation of the projection did not match up perfectly, producing incorrect inference.
+This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
 
-An x-ray \hl{projection} of a 3D printed sample was obtained and compared with the simulation in an experiment.
+An x-ray projection of a 3D printed sample was obtained and compared with the simulation in an experiment.
 The procedure is shown in the methods section along with the description of the empirical null filter.
@@
 The \SI{225}{\kilo\volt} source was used with a $2000\times2000$ pixel \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}.
-This object was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}.
+The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}.
 A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible.
@@
 
-The 3D printed sample was scanned 20 times at a fixed angle.
-The 20 x-ray projections were spilt into 2.
+The projection of the 3D printed sample was obtained and repeated 20 times at a fixed angle.
+The 20 projections were spilt into 2.
 19 random projections were held out.
@@
 In the \emph{aRTist} simulation, the software did a simulation as if the voids were not there.
-Numerical methods were used to align the simulated x-ray image to the obtained x-ray projection.
+Numerical methods were used to align the simulated projection to the obtained projection.
 
@@
 
-Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \emph{aRTist}.
+Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the \emph{aRTist} projection.
 A disagreement too big will classify that pixel as a positive result.
@@
   \dfrac{
-    \text{scan}_{x,y} - \emph{aRTist}_{x,y}
+    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
   }
   {
-    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
+    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
   }
 \end{equation}
-where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.
+where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.
 
-The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}.
-The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample.
-These replicated x-ray images were manually segmented.
+The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}.
+The fitting of the model was done using the held out replicated projections of the sample.
+These replicated projections were manually segmented.
 This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model.
 The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link.
-The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable when working out the test statistics.
+The variance was predicted using the grey value in the \emph{aRTist} projection as the predictor variable when working out the test statistics.
 
@@
 
-The empirical null filter was tested to see if it can detect simulated defects from a $256\times 256$ contaminated image.
+The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{px}\times \SI{256}{px}$ contaminated image.
 A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
 For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
-A $30\times 30$ square defect was simulated.
+A $\SI{30}{px}\times \SI{30}{px}$ square defect was simulated.
 A kernel can capture the entire defect if its radius is large enough.
@@
   \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
-  \caption{A $256\times 256$ contaminated Gaussian image with a $30 \times 30$ square defect.
+  \caption{A $\SI{256}{px}\times \SI{256}{px}$ contaminated Gaussian image with a $\SI{30}{px} \times \SI{30}{px}$ square defect.
 The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
@@
 Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null.
-In this simulated example, it is about $r>54$.
+In this simulated example, it is about $r>\SI{54}{px}$.
 A kernel too small would treat the defects as null, making them difficult to detect.
@@
     }
-  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $256 \times 256$ filtered contaminated Gaussian image with a $30\times 30$ square defect.
+  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{px} \times \SI{256}{px}$ filtered contaminated Gaussian image with a $\SI{30}{px}\times \SI{30}{px}$ square defect.
 Various kernel radiuses were investigated.
@@
 The test was done at the 5\% FDR level.
-The box plot summarise the 100 repeats of the experiment.}
+The box plot summarise the 100 repeated measurements of the experiment.}
   \label{fig:inference_Experiment_DefectRadiusSquare}
@@
 
-In the experiment with the 3D printed sample, the x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
-It was segmented using the edges of the projection of the 3D printed object.
+In the experiment with the 3D printed sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
+It was segmented using the edges of the projection of the 3D printed sample.
 The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
@@
   \includegraphics[width=0.45\textwidth]{../figures/inference/segment.JPG}
-  \caption{The x-ray image was segmented further into 7 segments or ROI.}
+  \caption{The x-ray projection was segmented further into 7 segments or ROI.}
   \label{fig:inference_segmentFurther}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
-        \caption{X-ray image with positive pixels}
+        \caption{X-ray projection with positive pixels}
       \end{subfigure}
@@
     }
-  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$.
-a) X-ray image with highlighted red positive pixels at the 5\% FDR level.
+  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{px}$.
+a) X-ray projection with highlighted red positive pixels at the 5\% FDR level.
 b) $p$-values on the log scale.
@@
 
-The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference.
+The empirical null filter caters for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable.
+This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference.
 In the experiments, it was found that the FDR level is preserved after filtering.
@@
     }
-  \caption{Timings when filtering a $256\times 256$ image.
+  \caption{Timings when filtering a $\SI{256}{px}\times \SI{256}{px}$ image.
 The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image.

### 2019-05-25 reports/paper1/paper.tex
Revise paper

@@
 A 3D printed sample was manufactured with voids to see if they can be detected.
-The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test.
+The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test.
 The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
@@
 
-The projection of the 3D printed sample was obtained and repeated 20 times at a fixed angle.
+The projection of the sample was obtained and repeated 20 times at a fixed angle.
 The 20 projections were spilt into 2.
 19 random projections were held out.
-The remaining projection was used to compare with the simulation using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-In the \emph{aRTist} simulation, the software did a simulation as if the voids were not there.
+The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+\emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
+CAD of the sample \citep{bellon2011simulation, deresch2012simulating}.
+\emph{aRTist} was used to obtained a simulation projection as if the voids were not there.
 Numerical methods were used to align the simulated projection to the obtained projection.
+A shading correction was applied to the simulated projection using a flat black image and a simulated white image.
 
@@
 
-Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the \emph{aRTist} projection.
+Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the simulated projection.
 A disagreement too big will classify that pixel as a positive result.
@@
 The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link.
-The variance was predicted using the grey value in the \emph{aRTist} projection as the predictor variable when working out the test statistics.
+The variance was predicted using the grey value in the simulated projection as the predictor variable when working out the test statistics.
 
@@
 In the experiment with the 3D printed sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
-It was segmented using the edges of the projection of the 3D printed sample.
+It was segmented using the edges of the projection of the sample.
 The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
@@
 
-The empirical null filter caters for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable.
+The empirical null filter catered for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable.
 This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference.
@@
 Note that the $y$-axis changes scale.
-The box plot summarise 100 repeated measurements of the timings.}
+The box plot summarise the 100 repeated measurements of the timings.}
   \label{fig:inference_timing}

### 2019-05-26 reports/paper1/paper.tex
Grammar check

@@
 Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
-To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.
+To avoid this time-consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.
 A 3D printed sample was manufactured with voids to see if they can be detected.
@@
 Quality control in additive manufacturing can be done using x-ray computed tomography (CT) \citep{thompson2016x}.
-The CT is compared with the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
+The CT is compared with the computer-aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
 The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample.
@@
 This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
-Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
+Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
 This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
@@
 The procedure is shown in the methods section along with the description of the empirical null filter.
-In addition, the software development and simulation studies of the filter was discussed.
+In addition, the software development and simulation studies of the filter were discussed.
 The results from the simulation and the experiment are shown in the results section.
@@
 6 voids for each diameter were designed in the CAD.
-Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly.
 The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.
@@
   \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
-  \caption{CAD of a 3D cuboid with voids.
+  \caption{The CAD of a 3D cuboid with voids.
 The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
 6 voids for each diameter were designed in the CAD.
-Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly.
 The scale shown is approximate.}
@@
 The projection of the sample was obtained and repeated 20 times at a fixed angle.
-The 20 projections were spilt into 2.
+The 20 projections were split into 2.
 19 random projections were held out.
@@
 CAD of the sample \citep{bellon2011simulation, deresch2012simulating}.
-\emph{aRTist} was used to obtained a simulation projection as if the voids were not there.
+\emph{aRTist} was used to obtain a simulation projection as if the voids were not there.
 Numerical methods were used to align the simulated projection to the obtained projection.

### 2019-06-03 reports/thesis/chapters/2_dataCollection.tex
Writing data collection chapter

@@
+An experiment was conducted where a test sample was additively manufactured with purposely designed voids.
+The objective is to see if the voids can be detected using a single projection.
+This was done by comparing a projection of the test sample with the simulation of that projection as if the voids were not there.
+The simulated projections were produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+It can simulate projections of the test sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the CAD of the test sample \citep{bellon2011simulation, deresch2012simulating}.
+
+\cite{brierley2018optimized} did something similar by comparing a projection of the test sample, with no voids, with a simulation of that projection with voids added in the CAD.
+The experiment presented here is the other side of the coin, putting voids in the physical test sample rather than in the simulated projection.
+This makes the experiment more realistic by attempting to detect real voids.
+Being able to detect voids in projection space suggest quality control can be done in projection space, rather than reconstruction space, to speed up the quality control procedure.
+
+This chapter describes the apparatus used to manufacture the test sample and obtaining the projections.
+There is also a discussion, at the end of the chapter, on shading correction which was used to remove detector panel and x-ray spot effects from the projections.
+
+Many figures presented here were given by engineers in relation to the experiment or by the manufacturer. Figures with no error bars were rounded to an appropriate number of significant figures.
+
+\section{Apparatus}
+
+The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids, the CAD shown in Figure \ref{fig:inference_testObject}.
+The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
+6 voids for each diameter were designed in the CAD.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
+  \caption{CAD of the test object; the scale shown is approximate.}
+  \label{fig:inference_testObject}
+\end{figure}
+
+The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test object made of plastic (acrylonitrile butadiene styrene or ABS).
+The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.
+Another test object was manufactured made from titanium (Ti-6Al-4V)
+
+X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector.
+The target material in the x-ray source is tungsten.
+The sensor in the detector is made up of 2 rows and 16 columns of panels.
+The sensor has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ with produced a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
+Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$.
+The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects.
+The gain and offset were adjusted by the engineers to produce a projection with good contrast, each pixel then has a grey value in units of analogue to digital units (\SI{}{\adu}).
+
+Greyscale projections were taken in addition to the projection of the test object.
+These are projections with nothing to scan at different powers used in the x-ray tube.
+The power was varied by fixing the potential difference and varying the current.
+The greyscale projections were used for calibration such as shading correction.
+
+Replicate projections of the test object and greyscale projections were obtained by repeating the scan. These replicated projections were used to study the noise observed in the projections.
+
+Filters used to tackle beam hardening were used such as \SI{0.350}{\milli\metre} of copper and \SI{2.000}{\milli\metre} of tin.
+
+\section{Datasets}
+
+3 datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}.
+Projections of the ABS test object were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test object was used in \texttt{TiFilter}.
+2 angular projections were taken for all datasets as well as greyscale projections.
+To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.
+
+The properties of each dataset is shown in Table \ref{table:data_dataset}.
+Properties include the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections.
+A sample of the obtained, simulated and greyscale projections for the datasets \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter} are shown in Figures \ref{fig:data_AbsNoFilter}, \ref{fig:data_AbsFilter} and \ref{fig:data_TiFilter} respectively.
+
+\begin{sidewaystable}
+\centering
+\begin{tabular}{l|lll}
+                                                       & \multicolumn{3}{c}{Dataset name}                                                \\
+                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             & \texttt{TiFilter}        \\ \hline
+potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             & 190                      \\
+power (\SI{}{\watt})                                   & 36                   & 20                             & 19.95                    \\
+filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper & \SI{3}{\milli\metre} tin \\
+time exposure (\SI{}{\milli\second})                   & 708                  & 500                            & 1415                     \\
+distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            & 86                       \\
+distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            & 875                      \\
+number of replications                                 & 100                  & 20                             & 20                       \\ \hline
+powers used for greyscale projections (\SI{}{\watt})   & 0                    & 0                              & 0                        \\
+\multicolumn{1}{c|}{\vdots}                            & 10.08                & 4.96                           & 10.07                    \\
+\multicolumn{1}{c|}{\vdots}                            & 18.08                & 10                             & 19.95                    \\
+\multicolumn{1}{c|}{\vdots}                            & 28                   & 15.04                          &                          \\
+\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             &                          \\
+number of replications                                 & 20                   & 20                             & 20                      
+\end{tabular}
+\caption{Properties of the 3 datasets obtained for the experiment.}
+\label{table:data_dataset}
+\end{sidewaystable}
+
+\begin{figure}[p]
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
+      \caption{Projection of sample at \SI{36}{\watt}}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
+      \caption{Simulation of sample at \SI{36}{\watt}}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
+      \caption{Projection at \SI{0}{\watt}}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
+      \caption{Projection at \SI{36}{\watt}}
+    \end{subfigure}
+  }
+  \caption{\texttt{AbsNoFilter} projections obtained; note the colour scale may vary.}
+  \label{fig:data_AbsNoFilter}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30.eps}
+      \caption{Projection of sample at \SI{20}{\watt}}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30_sim.eps}
+      \caption{Simulation of sample at \SI{20}{\watt}}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration1.eps}
+      \caption{Projection at \SI{0}{\watt}}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration5.eps}
+      \caption{Projection at \SI{20}{\watt}}
+    \end{subfigure}
+  }
+  \caption{\texttt{AbsFilter} projections obtained; note the colour scale may vary.}
+  \label{fig:data_AbsFilter}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30.eps}
+      \caption{Projection of sample at \SI{20}{\watt}}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30_sim.eps}
+      \caption{Simulation of sample at \SI{20}{\watt}}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration1.eps}
+      \caption{Projection at \SI{0}{\watt}}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration3.eps}
+      \caption{Projection at \SI{20}{\watt}}
+    \end{subfigure}
+  }
+  \caption{\texttt{TiFilter} Projections obtained; note the colour scale may vary.}
+  \label{fig:data_TiFilter}
+\end{figure}
+
+The projections do indeed show the test sample, however, with panel and spot effects.
+The structure of the 32 panels are predominate in the black image in particular, this was observed by \cite{yang2009evaluation} as well.
+This is concerning because systematic errors could be caused as a result of the panel effects in the black image when presented only with background radiation.
+The x-ray spot can be observed, in particular in the white image, and is the result of using a cone beam.
+\cite{kueh2016modelling} studied the x-ray spot by fitting a mixture of a Gaussian spot and an uniform spot onto the x-ray spot.
+
+\section{Shading Correction}
+
+Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity of the projections such as panel and spot effects.
+Shading correction is typically done using the greyscale projections and how the pixels respond to different powers.
+For example the black and white images can be used to correct the projection using
+\begin{equation}
+U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times B+A
+\end{equation}
+where $N_{x,y}$ is the obtained projection, $U_{x,y}$ is the shading corrected projection and $A$ and $B$ are some user defined constants \citep{young2000shading, munzenmayer2003enhancing}.
+This can be extended to include more greyscale projections by using the fact that the grey value respond linearly to the power of the x-ray source \citep{seibert1998flat}.
+More generally, shading correction can be expressed as
+\begin{equation}
+U_{x,y} = N_{x,y} \beta_{x,y} + \alpha_{x,y}
+\end{equation}
+where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}.
+However there is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ depends on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.
+
+Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to some parametric function \citep{likar2000retrospective}.
+There is also a method which uses a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.
+
+In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user defined constants.
+The shading correction was then experimented to investigate its performance when shading correcting greyvalue projections.
+
+\subsection{Proposed Shading Correction}
+
+Let $N_{x,y}(P)$ be the grey value of pixel $(x,y)$ after being exposed to x-rays of power $P$ for some fixed exposure time.
+The power can be varied at the x-ray source when obtaining the greyscale projections or via attenuation assuming no beam hardening.
+Let $U_{x,y}(P)$ be the shading-free pixel at $(x,y)$.
+Assume that
+\begin{equation}
+U_{x,y}(P) = N_{x,y}(P)\beta_{x,y}+\alpha_{x,y}
+\end{equation}
+where $\beta_{x,y}$ and $\alpha_{x,y}$ is some constant which varies spatially. Suppose when
+
+\subsection{ANOVA}
+
 Figure \ref{fig:data_AbsNoFilter} shows the data.
@@
 The gradient of the regression for all pixels are shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap} b).
-
-\begin{figure}
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
-      \caption{Projection of sample at \SI{44}{\watt}}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
-      \caption{Simulation of sample at \SI{44}{\watt}}
-    \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
-      \caption{Projection at \SI{0}{\watt}}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
-      \caption{Projection at \SI{44}{\watt}}
-    \end{subfigure}
-  }
-  \caption{Projections obtained; note the colour scale may vary.}
-  \label{fig:data_AbsNoFilter}
-\end{figure}
 

### 2019-06-05 reports/thesis/chapters/2_dataCollection.tex

@@
 
-\cite{brierley2018optimized} did something similar by comparing a projection of the test sample, with no voids, with a simulation of that projection with voids added in the CAD.
+\cite{brierley2018optimized} did something similar by comparing a projection of the test sample, with no voids, with a simulation of that projection with voids added.
 The experiment presented here is the other side of the coin, putting voids in the physical test sample rather than in the simulated projection.
 This makes the experiment more realistic by attempting to detect real voids.
-Being able to detect voids in projection space suggest quality control can be done in projection space, rather than reconstruction space, to speed up the quality control procedure.
+Being able to detect voids suggest quality control can be done in projection space, rather than reconstruction space, to speed up the quality control procedure.
 
@@
 The sensor in the detector is made up of 2 rows and 16 columns of panels.
-The sensor has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ with produced a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
+The sensor has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produced a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
 Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$.
@@
 Greyscale projections were taken in addition to the projection of the test object.
-These are projections with nothing to scan at different powers used in the x-ray tube.
+These are projections with nothing between the source and the detector with the x-ray tube at different powers.
 The power was varied by fixing the potential difference and varying the current.
 The greyscale projections were used for calibration such as shading correction.
+The greyscale projection with the x-ray turned off is called the black image.
+The greyscale projection with the x-ray set up the same when obtaining the test object projection is called the white image.
 
-Replicate projections of the test object and greyscale projections were obtained by repeating the scan. These replicated projections were used to study the noise observed in the projections.
+Replicate test object projections and greyscale projections were obtained by repeating the acquisition. These replicated projections were used to study the noise observed in the projections.
 
 Filters used to tackle beam hardening were used such as \SI{0.350}{\milli\metre} of copper and \SI{2.000}{\milli\metre} of tin.
+
+\emph{aRTist} was used to simulate the test object projection and all greyscale projections except for the black image.
+The black image was simulated by producing an uniform image with grey value the mean over the obtained black image.
+The engineers used numerical methods to align the simulated projection with the obtained projection.
 
@@
 Projections of the ABS test object were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test object was used in \texttt{TiFilter}.
-2 angular projections were taken for all datasets as well as greyscale projections.
+2 angular projections were taken for all datasets.
+Greyscale projections were obtained as well.
 To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.
@@
 Shading correction is typically done using the greyscale projections and how the pixels respond to different powers.
-For example the black and white images can be used to correct the projection using
+For example the black and white image, or images when averaging over replications, can be used to correct the projection using
 \begin{equation}
 U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times B+A
+\label{eq:data_shadingCorrectionOld}
 \end{equation}
@@
 \begin{equation}
-U_{x,y} = N_{x,y} \beta_{x,y} + \alpha_{x,y}
+U_{x,y} = \beta_{x,y} N_{x,y} + \alpha_{x,y}
 \end{equation}
 where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}.
-However there is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ depends on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.
+However there is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ actually depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.
 
@@
 
-Let $N_{x,y}(P)$ be the grey value of pixel $(x,y)$ after being exposed to x-rays of power $P$ for some fixed exposure time.
-The power can be varied at the x-ray source when obtaining the greyscale projections or via attenuation assuming no beam hardening.
-Let $U_{x,y}(P)$ be the shading-free pixel at $(x,y)$.
-Assume that
+Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube of power $P$ for some fixed time exposure $t$.
+$S_{x,y}(P)$ may be averaged over replications.
+Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube of power $P_\text{proj}$ for some fixed time exposure $t$.
+Therefore the black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.
+
+The shading free image $U_{x,y}$ is not truly known, but it should expected that the shading corrected greyscale projection should be flat with some noise, in other words $\expectation\left[S_{x,y}(P)\right]=\mu_{S}(P)$ and $\variance\left[S_{x,y}(P)\right]=\sigma_{S}^2(P)$ for all $x=1,2,\cdots,L$ and $y=1,2,\cdots,H$.
+Suppose $\mu_{S}(P)$ was estimated using the within projection mean
 \begin{equation}
-U_{x,y}(P) = N_{x,y}(P)\beta_{x,y}+\alpha_{x,y}
+\overline{S}(P) = \dfrac{1}{\text{WH}}
+\sum_{x=1}^W\sum_{y=1}^H S_{x,y}(P) \ .
 \end{equation}
-where $\beta_{x,y}$ and $\alpha_{x,y}$ is some constant which varies spatially. Suppose when
+Consider a pixel at $(x,y)$, shading correction was done by fitting a linear regression on
+\begin{equation}
+\overline{S}(P) = \beta_{x,y} S_{x,y}(P) + \alpha_{x,y} \quad(+\varepsilon)
+\end{equation}
+for $P\in \mathfrak{P}$ where $\mathfrak{P} = \left\{0,P_1,P_2,\cdots, P_\text{proj}\right\}$ are the powers used for the greyscale projections.
+$\varepsilon$ is a random variable and an error term, it is included only for formality purposes.
+Let $b_{x,y}$ and $a_{x,y}$ be the estimated parameters of $\beta_{x,y}$ and $\alpha_{x,y}$ from the linear regression respectively.
+Given a projection $N_{x,y}$, the shading corrected projection $U_{x,y}$ is
+\begin{equation}
+U_{x,y} = b_{x,y} N_{x,y} + a_{x,y}
+\end{equation}
+or in the form of Equation \eqref{eq:data_shadingCorrectionOld}
+\begin{multline}
+U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times \left[b_{x,y}(\text{white}_{x,y}-\text{black}_{x,y})\right]\\+\left[b_{x,y} \text{black}_{x,y} + a_{x,y}\right] \ .
+\end{multline}
+In full, the equations for $b_{x,y}$ and $a_{x,y}$ are given as
+\begin{equation}
+b_{x,y} = \dfrac{
+  \sum_{P\in\mathfrak{P}}(S_{x,y}(P) - \overline{S}_{x,y})(\overline{S}(P) - \overline{S})
+}{
+  \sum_{P\in\mathfrak{P}}(S_{x,y}(P) - \overline{S}_{x,y})^2
+}
+\end{equation}
+and
+\begin{equation}
+a_{x,y} = \overline{S} - b_{x,y}\overline{S}_{x,y}
+\end{equation}
+where $\overline{S}_{x,y}$ is the between projection mean
+\begin{equation}
+\overline{S}_{x,y} = \dfrac{1}{|\mathfrak{P}|}\sum_{P\in\mathfrak{P}}S_{x,y}(P)
+\end{equation}
+and $\overline{S}$ is the global mean
+\begin{equation}
+\overline{S} = \dfrac{1}{|\mathfrak{P}|}\sum_{P\in\mathfrak{P}}\overline{S}(P) \ .
+\end{equation}
+This type of shading correction shall be referred to as linear shading correction. Expressing shading correction in this way has the advantage that there are no user defined constants.
+
+An example of the linear regression is shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap} where 3 random pixels were chosen for illustration.
+By plotting the within projection mean versus the grey value for a particular pixel, a linear relationship can be observed.
+The gradient varied for different pixels which correspond to different sensitivities.
+The resulting shading correction for the \texttt{AbsNoFilter} projection is shown in Figure \ref{fig:data_shadingCorrectionExample_image}.
+It can be observed that the shading correction remove panel and spot effects from the background and test object.
+
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
+      \caption{Linear regression}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_linear.eps}
+      \caption{$b_{x,y}$}
+    \end{subfigure}
+  }
+  \caption{For each pixel, a linear regression was fitted on the within projection mean versus the grey value for each greyscale projection.
+3 random pixels were used to illustrate this in a).
+b) shows the fitted gradient for all pixels.}
+  \label{fig:data_shadingCorrectionExample_gainMap}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_null.eps}
+      \caption{No shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_bw.eps}
+      \caption{Linear shading correction}
+    \end{subfigure}
+  }
+  \caption{Projection of \texttt{AbsNoFilter} with and without shading correction}
+  \label{fig:data_shadingCorrectionExample_image}
+\end{figure}
+
+A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as BW shading correction.
 
@@
 The gradient of the regression for all pixels are shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap} b).
-
-\begin{figure}
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
-      \caption{Example gain curves}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_bw.eps}
-      \caption{Normalised gain map}
-    \end{subfigure}
-  }
-  \caption{Normalised gain map from bw shading correction is shown in b). They were obtained by using the gradient in the example shown in a) for 3 random pixels.}
-  \label{fig:data_shadingCorrectionExample_gainMap}
-\end{figure}
 

### 2019-06-05 reports/thesis/chapters/5_inference.tex

@@
-The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-\texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}.
-Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.
-
 Disagreement between the scan and \texttt{aRTist} can be found by subtracting one image from the other, any values too big in magnitude can be considered as a defect.
@@
 The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.
-
-This method for inference was applied to the dataset \texttt{Sep16 120deg}.
-A cuboid (4 cm $\times$ 4 cm $\times$ 6 cm) with voids was purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}.
-The voids were of various diameters 2.4 mm, 1.2 mm, 0.6 mm and 0.3 mm.
-6 voids for each diameter were designed in the CAD.
-Voids with diameters 2.4 mm and 0.6 mm were regularly arranged, otherwise they were arranged irregularly.
-The precision of the manufacturing was in the order of $\pm0.1\text{ mm}$.
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
-  \caption{CAD of a 3D cuboid with voids; the scale shown is approximate.}
-  \label{fig:inference_testObject}
-\end{figure}
 

### 2019-06-05 reports/paper1/paper.tex
Intro rewritten

@@
 \author{
-  Sherman Lo \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams \and Jason Warnett
+  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams
 }
@@
 
-Quality control in additive manufacturing can be done using x-ray computed tomography (CT) \citep{thompson2016x}.
-The CT is compared with the computer-aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}.
+Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries.
+One example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
+A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer.
+The material is usually plastic in a form of a thin filament.
+It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}.
+The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer.
+The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.
+
+However, there is a need for product inspection and in particular assessing the quality of the internal structures.
+For example, voids can form between layers which can hinder the mechanical properties of the product \citep{wang20173d, ngo2018additive}.
+In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}.
+Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}.
+
+Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT).
+The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
+X-ray projections are taken while the object rotates.
+Typically the x-ray is a cone beam \citep{kruth2011computed}.
+The x-ray projections are then used to reconstruct the object in 3D \citep{brooks1976principles, feldkamp1984practical, smith1990cone}.
+
+XCT is commonly used for the investigation of pores in the manufactured object \citep{thompson2016x}.
+Pores can be classified as defects if the pores are larger than some volume threshold.
+This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.
+The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}.
+However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
+
+The strength of XCT comes from the fact that the location of the pores can be visualised.
+Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}.
+\cite{leuders2015fatigue} pointed out that the location of the pores is an important factor.
+In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \linebreak\citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+
 The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample.
-Speeding up the quality control process on the production line could be done by doing an inspection using a fewer number of projections by sacrificing accuracy \citep{warnett2016towards, brierley2018optimized}.
+Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar.
+The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}.
 
-A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth.
-This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
-Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
-This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
+Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+\cite{brierley2018optimized} demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without.
+It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.
 
-An x-ray projection of a 3D printed sample was obtained and compared with the simulation in an experiment.
-The procedure is shown in the methods section along with the description of the empirical null filter.
-In addition, the software development and simulation studies of the filter were discussed.
+It was investigated whenever defects can be detected from a single x-ray projection.
+This was done by obtaining an x-ray projection of a 3D printed sample, with purposely designed voids, and comparing it with the simulation.
+The apparatus and procedures are shown in the methods section.
+In addition, software development and simulation studies were discussed.
 The results from the simulation and the experiment are shown in the results section.
@@
 
-Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the simulated projection.
+A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth.
+This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
 A disagreement too big will classify that pixel as a positive result.
-A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels.
-This test statistic, together makes a $z$ image, is
+Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
+This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
+
+A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
 \begin{equation}
@@
 
-The empirical null filter catered for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable.
+Voids in the order of millimetres were detectable which shows potential in defect detection in projection space.
+This can be extended to multiple projections and perhaps in real time on a conveyor belt.
+
+The empirical null filter catered for inaccuracies made by \emph{aRTist}.
 This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference.

### 2019-06-07 reports/thesis/chapters/2_dataCollection.tex
chapter 2 writing

@@
 \begin{equation}
-U_{x,y} = b_{x,y} N_{x,y} + a_{x,y}
+U_{x,y} = b_{x,y} N_{x,y} + a_{x,y} \ .
 \end{equation}
-or in the form of Equation \eqref{eq:data_shadingCorrectionOld}
-\begin{multline}
-U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times \left[b_{x,y}(\text{white}_{x,y}-\text{black}_{x,y})\right]\\+\left[b_{x,y} \text{black}_{x,y} + a_{x,y}\right] \ .
-\end{multline}
 In full, the equations for $b_{x,y}$ and $a_{x,y}$ are given as
@@
 The resulting shading correction for the \texttt{AbsNoFilter} projection is shown in Figure \ref{fig:data_shadingCorrectionExample_image}.
-It can be observed that the shading correction remove panel and spot effects from the background and test object.
+It can be observed that the shading correction removed the panel and spot effects from the background and test object.
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_bw.eps}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_linear.eps}
       \caption{Linear shading correction}
@@
 A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as BW shading correction.
+
+\subsection{Exploratory Analysis}
+
+Shading correction on a greyscale projection should result in a image which is flat with some noise.
+To avoid overfitting, one greyscale projection from each power were held out and used to fit the parameters of the shading correction.
+Shading correction was then used on unused greyscale projections in this exploratory analysis.
+
+Figure \ref{fig:data_shadingCorrectionExample_greyvaluePower} shows the grey values in each greyscale projections before and after shading correction.
+The sensitivity, which corresponds to the gradient in units of \SI{}{\adu\per\watt}, became more consistent between pixels with shading correction.
+This should mean that pixels will respond similarly to each other.
+
+\begin{figure}
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_null.eps}
+      \caption{No shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_linear.eps}
+      \caption{Linear shading correction}
+    \end{subfigure}
+  }
+  \caption{Grey values in the \texttt{AbsNoFilter} greyscale projections before and after shading correction. The box plot summarise all $2000\times2000$ pixels in a projection.}
+  \label{fig:data_shadingCorrectionExample_greyvaluePower}
+\end{figure}
+
+The \texttt{AbsNoFilter} black image before and after shading correction is shown in Figure \ref{fig:data_shadingCorrectionExample_black}.
+The flatness of the image can be shown using a profile plot, this is a plot of the grey values along a column or row, an example shown in Figure \ref{fig:data_oddEven}.
+The figure shows that the shading uncorrected black image is not flat but a remarkable structure can be observed by plotting only the odd rows and even rows separately.
+Such a plot shows that the grey values depend on neighbouring pixels, where the majority of pixels on even rows have grey values larger than pixels above and below it.
+Perhaps this is caused by the read-out structure in the detector.
+
+The BW shading corrected black image looks very uniform but there is some structure in the linear shading correction.
+By giving linear shading correction various greyscale projections, it tried to generalise to a range of powers and thus may struggle at shading correcting the black and white images.
+
+\begin{figure}
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_bw.eps}
+      \caption{BW shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
+      \caption{Linear shading correction}
+    \end{subfigure}
+  }
+  \caption{The \texttt{AbsNoFilter} black image after shading correction.}
+  \label{fig:data_shadingCorrectionExample_black}
+\end{figure}
+
+\begin{figure}
+  \centerline{
+    \begin{subfigure}[b]{\textwidth}
+      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_null.eps}
+      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_null.eps}
+      \caption{No shading correction}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{\textwidth}
+      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_bw.eps}
+      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_bw.eps}
+      \caption{BW shading correction}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{\textwidth}
+      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_linear.eps}
+      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_linear.eps}
+      \caption{linear shading correction}
+    \end{subfigure}
+  }
+  \caption{Left shows the profile plot of a \texttt{AbsNoFilter} black image at $(879,y)$. Right shows two curves for odd and even $y$.}
+  \label{fig:data_oddEven}
+\end{figure}
+
+% \begin{figure}
+%   \centering
+%   \centerline{
+%     \begin{subfigure}[b]{0.49\textwidth}
+%       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_null.eps}
+%       \caption{No shading correction}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.49\textwidth}
+%       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_bw.eps}
+%       \caption{BW shading correction}
+%     \end{subfigure}
+%   }
+%   \begin{subfigure}[b]{0.49\textwidth}
+%     \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_linear.eps}
+%     \caption{Linear shading correction}
+%   \end{subfigure}
+%   \caption{Fourier transform on the black image before and after shading correction. The colour scale is in arbitrary units and range between 0 to 255.}
+%   \label{fig:data_fft}
+% \end{figure}
 
@@
 
-\begin{figure}
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_null.eps}
-      \caption{No shading correction}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_bw.eps}
-      \caption{bw shading correction}
-    \end{subfigure}
-  }
-  \caption{Gain curve before and after shading correction. The box plot summarise all $2000\times2000$ pixels in a projection.}
-  \label{fig:data_shadingCorrectionExample_gain}
-\end{figure}
-
 In the black image, I've noticed the vertical read-out structure can be seen.
@@
 No read-out structure can be seen horizontally, see Figure \ref{fig:data_oddEvenX}. Panel structure can be seen however.
-
-\begin{figure}
-  \centerline{
-    \begin{subfigure}[b]{\textwidth}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_null.eps}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_null.eps}
-      \caption{No shading correction}
-    \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{\textwidth}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_bw.eps}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_bw.eps}
-      \caption{bw shading correction}
-    \end{subfigure}
-  }
-  \caption{Left shows the profile plot of a black image at $(879,y)$ before and after shading correction. Right shows two curves for odd and even $y$.}
-  \label{fig:data_oddEven}
-\end{figure}
-
-\begin{figure}
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_null.eps}
-      \caption{No shading correction}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_bw.eps}
-      \caption{bw shading correction}
-    \end{subfigure}
-  }
-  \caption{Fourier transform on the black image before and after shading correction. The colour scale is in arbitrary units and range between 0 to 255.}
-  \label{fig:data_fft}
-\end{figure}
-
-\begin{figure}
-  \centerline{
-    \begin{subfigure}[b]{\textwidth}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_nullX.eps}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_nullX.eps}
-      \caption{No shading correction}
-    \end{subfigure}
-  }
-  \caption{Left shows the profile plot of a black image at $(y,879)$ before and after shading correction. Right shows two curves for odd and even $y$.}
-  \label{fig:data_oddEvenX}
-\end{figure}

### 2019-06-07 reports/paper1/paper.tex
Revise paper

@@
 \author{
-  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams
+  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Mark Williams \and Thomas Nichols \and Julia Brettschneider 
 }
+
+\DeclareSIUnit\pixel{px}
+\DeclareSIUnit\adu{ADU}
 
@@
 \begin{abstract}
-X-ray computed tomography can be used for defect detection in additive manufacturing.
+X-ray computed tomography can be used for defect detection in additive manufacturing (AM).
 Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
 To avoid this time-consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.
-A 3D printed sample was manufactured with voids to see if they can be detected.
+An AM sample was manufactured with voids to see if they can be detected.
 The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test.
@@
 
-Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries.
+Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries \citep{wong2012review, ngo2018additive}.
 One example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
@@
 
-Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT).
+Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT) \citep{kruth2011computed, sun2012overview}.
 The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
 X-ray projections are taken while the object rotates.
-Typically the x-ray is a cone beam \citep{kruth2011computed}.
+Typically the x-ray is a cone beam.
 The x-ray projections are then used to reconstruct the object in 3D \citep{brooks1976principles, feldkamp1984practical, smith1990cone}.
 
-XCT is commonly used for the investigation of pores in the manufactured object \citep{thompson2016x}.
+In AM, XCT is commonly used for the investigation of pores \citep{thompson2016x}.
 Pores can be classified as defects if the pores are larger than some volume threshold.
@@
 \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor.
-In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \linebreak\citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
 
@@
 It was investigated whenever defects can be detected from a single x-ray projection.
-This was done by obtaining an x-ray projection of a 3D printed sample, with purposely designed voids, and comparing it with the simulation.
+This was done by obtaining an x-ray projection of an AM sample, with purposely designed voids, and comparing it with the simulation.
 The apparatus and procedures are shown in the methods section.
@@
   \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
-  \caption{The CAD of a 3D cuboid with voids.
+  \caption{The CAD of a cuboid with voids.
 The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
@@
 X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}.
-The \SI{225}{\kilo\volt} source was used with a $2000\times2000$ pixel \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}.
+The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}.
 The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}.
@@
 
-The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{px}\times \SI{256}{px}$ contaminated image.
+The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated image.
 A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
 For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
-A $\SI{30}{px}\times \SI{30}{px}$ square defect was simulated.
+A $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect was simulated.
 A kernel can capture the entire defect if its radius is large enough.
@@
   \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
-  \caption{A $\SI{256}{px}\times \SI{256}{px}$ contaminated Gaussian image with a $\SI{30}{px} \times \SI{30}{px}$ square defect.
+  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect.
 The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
@@
 Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null.
-In this simulated example, it is about $r>\SI{54}{px}$.
+In this simulated example, it is about $r>\SI{54}{\pixel}$.
 A kernel too small would treat the defects as null, making them difficult to detect.
@@
     }
-  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{px} \times \SI{256}{px}$ filtered contaminated Gaussian image with a $\SI{30}{px}\times \SI{30}{px}$ square defect.
+  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect.
 Various kernel radiuses were investigated.
@@
 
-In the experiment with the 3D printed sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
+In the experiment with the AM sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
 It was segmented using the edges of the projection of the sample.
@@
     }
-  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{px}$.
+  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$.
 a) X-ray projection with highlighted red positive pixels at the 5\% FDR level.
@@
 
-For good results, the faces of the 3D printed cuboid were segmented.
+For good results, the faces of the AM cuboid were segmented.
 This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly.
 Manual segmentation was easy to do because a cuboid has 6 faces.
-However, segmentation of faces cannot be generalised well to 3D printed samples with complicated geometry and curved surfaces.
+However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.
 
@@
     }
-  \caption{Timings when filtering a $\SI{256}{px}\times \SI{256}{px}$ image.
+  \caption{Timings when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image.
 The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
@@
 Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
-The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.
+The EM algorithm \citep{dempster1977maximum, bishop2006pattern} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.
 However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.

### 2019-06-17 reports/paper1/paper.tex
Revise paper

@@
-\documentclass{proc}
+\documentclass{article}
 
@@
 \usepackage[outdir=./]{epstopdf}
-\usepackage[round]{natbib} 
+\usepackage[square,semicolon]{natbib} 
 \usepackage{url}
@@
 \usepackage{siunitx} %for measurements
+\usepackage[figurename=Fig.]{caption}
+\usepackage[numbib]{tocbibind} %number references and figure title
+\usepackage{authblk}
 
@@
 
+%to number list of figures
+\renewcommand{\listoffigures}{\begingroup
+\tocsection
+\tocfile{\listfigurename}{lof}
+\endgroup}
+
 \title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
-\date{2019}
-\author{
-  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Mark Williams \and Thomas Nichols \and Julia Brettschneider 
-}
+\author[1, *]{S.E.~Lo}
+\author[2]{J.W.~Warnett}
+\author[2]{G.J.~Gibbons}
+\author[2]{M.A.~Williams}
+\author[3]{T.E.~Nichols}
+\author[1]{J.A.~Brettschneider}
+\affil[1]{Department of Statistics, University of Warwick, Coventry, CV4 7AL, UK}
+\affil[2]{Warwick Manufacturing Group, University of Warwick, Coventry, CV4 7AL, UK}
+\affil[3]{Big Data Institute, Old Road Campus, University of Oxford, Oxford, OX3 7LF, UK}
+\affil[*]{Corresponding author: s.ip@warwick.ac.uk, +442476574812}
 
@@
 
+\begin{titlepage}
 \maketitle
@@
 \begin{abstract}
-X-ray computed tomography can be used for defect detection in additive manufacturing (AM).
+\noindent
+\textbf{BACKGROUND}: X-ray computed tomography can be used for defect detection in additive manufacturing (AM).
 Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
-To avoid this time-consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection.
-An AM sample was manufactured with voids to see if they can be detected.
+\newline
+\textbf{OBJECTIVE}: It was investigated whenever it is possible to detect defects based on a single angular projection.
+The motivation behind it is that defect detection in projection space should be faster than in reconstruction space.
+\newline
+\textbf{METHODS}: An AM sample was manufactured with voids to see if they can be detected.
 The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test.
-The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
-Voids with diameters in the order of millimetres were detectable.
+The simulation was not perfect which led to misleading results.
+The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
+\newline
+\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable.
+Simulation studies have shown that statistical properties such as the false discovery rate were preserved when using the filter.
+\newline
+\textbf{CONCLUSIONS}: Defect detection in projection space is possible.
+This can be extended to multiple independent projections in real time on a conveyor belt.
+The main bottle neck is the multiple evaluation of functions required for robust estimation in the empirical null filter.
+Speed up could be possible by implementing the filter on a GPU or exploring further robust estimators.
+\newline
+\newline
+\emph{Keywords:} Hypothesis testing, local normalisation, image filtering, projection space, additive manufacturing, voids, defects, quality control
 \end{abstract}
+
+\end{titlepage}
 
@@
 
-Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries \citep{wong2012review, ngo2018additive}.
-One example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
+Additive manufacturing (AM) is an emerging technology that overcomes many traditional methods such as computer numerical control (CNC).
+In AM, the product is manufactured layer by layer to product complicated internal and external geometries \citep{ngo2018additive, wong2012review}.
+One common example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
 A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer.
@@
 The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.
+Powder based AM such as selective laser sintering \citep{3d2019our, deckard1989method, dtm1990the} can manufacture metal products.
 
-However, there is a need for product inspection and in particular assessing the quality of the internal structures.
-For example, voids can form between layers which can hinder the mechanical properties of the product \citep{wang20173d, ngo2018additive}.
-In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}.
-Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}.
+There is a need for product inspection, in particular quality assessment of the internal structures.
+The properties of materials produced by AM are not yet fully understood.
+For example, voids can form between layers which can impact the mechanical properties of the product \citep{ngo2018additive, wang20173d}.
+In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{tammas2015xct, thijs2010study}.
+Low wetting ability of the melt pool can cause balling, a phenomenon where spherical or ellipsoidal deposits on the surface of the AM part.
+They are formed by sintered powder with insufficient contact on the existing layer \citep{gu2009balling, li2012balling}.
 
-Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT) \citep{kruth2011computed, sun2012overview}.
+Non-destructive testing, such as x-ray computed tomography (XCT), can be used to assess the quality of the product \citep{kruth2011computed, sun2012overview}.
 The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
-X-ray projections are taken while the object rotates.
+X-ray projections are taken at a series of angles.
 Typically the x-ray is a cone beam.
@@
 Pores can be classified as defects if the pores are larger than some volume threshold.
-This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.
+This threshold controls the probability of the detection of defects \citep{amrhein2014characterization, gandossi2010probability}.
 The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}.
-However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
+More accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
 
-The strength of XCT comes from the fact that the location of the pores can be visualised.
-Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}.
-\cite{leuders2015fatigue} pointed out that the location of the pores is an important factor.
-In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+An advantage of XCT is that the location of the pores can be visualised.
+Studies have shown a link between porosity and stress concentration \citep{carlton2016damage, leuders2015fatigue, siddique2015computed}.
+The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}.
+In addition to pores, surface deviation can be measured by aligning the reconstruction with the computer-aided design (CAD) model and measuring any discrepancies \citep{kim2016inspection, lee2015compliance, villarraga2015assessing}.
 
-The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample.
-Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar.
-The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}.
+A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample.
+XCT is not a instantaneous process so progress bars are usually featured in marketing for XCT such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}.
+Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.
 
-Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-\cite{brierley2018optimized} demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without.
-It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.
+Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection.
+It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}.
+The simulated projections are made in software called \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}.
+It is however inevitable that information is lost from the jump from reconstruction space to projection space, for example a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.
 
-It was investigated whenever defects can be detected from a single x-ray projection.
-This was done by obtaining an x-ray projection of an AM sample, with purposely designed voids, and comparing it with the simulation.
+This paper investigates whether defects can be detected from a single x-ray projection.
+To validate our method, we designed an AM test cuboid with purposely designed voids.
+An x-ray projection was obtained and compared with the simulation from \emph{aRTist} in order to detect these voids.
+The simulation was not perfect which led to misleading results.
+The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
 The apparatus and procedures are shown in the methods section.
-In addition, software development and simulation studies were discussed.
+In addition, computational implementation and simulation studies of the empirical null filter are discussed.
 The results from the simulation and the experiment are shown in the results section.
@@
 
-An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected.
-The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer.
-The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
-6 voids for each diameter were designed in the CAD.
-Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly.
-The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
-  \caption{The CAD of a cuboid with voids.
-The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
-6 voids for each diameter were designed in the CAD.
-Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly.
-The scale shown is approximate.}
-  \label{fig:inference_testObject}
-\end{figure}
+An ABS plastic test cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected.
+The CAD model of the test cuboid is shown in Fig.~\ref{fig:inference_testObject}.
+It was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer.
+Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly.
+The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.
 
@@
 The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}.
-A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible.
+A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible.
 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}.
-A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.
+A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.
 
 The projection of the sample was obtained and repeated 20 times at a fixed angle.
-The 20 projections were split into 2.
-19 random projections were held out.
-The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+19 randomly selected projections were held out.
+The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}.
 \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
@@
 Numerical methods were used to align the simulated projection to the obtained projection.
-A shading correction was applied to the simulated projection using a flat black image and a simulated white image.
+The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated white image.
 
@@
 A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth.
-This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test.
+This was done by using two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate (FDR) \citep{benjamini2010discovering, benjamini1995controlling}, treating each pixel as an individual test.
 A disagreement too big will classify that pixel as a positive result.
-Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
+Beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
 This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
@@
 This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model.
-The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link.
+The model used was a gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} with an identity link.
 The variance was predicted using the grey value in the simulated projection as the predictor variable when working out the test statistics.
@@
 To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$.
-All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{parzen1962on, friedman2001elements}
+All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{friedman2001elements, parzen1962on}
 \begin{equation}
@@
 \end{equation}
-where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}.
+where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to Silverman's rule of thumb \citep{sheather2004density, silverman1986density}.
 The estimates were obtained by solving
@@
 \end{equation}
-and was used in the \cite{benjamini1995controlling} (BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.
+and was used in the  Benjamini-Hochberg \citep{benjamini1995controlling}(BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.
 
-\subsection{Software Development}
+\subsection{Computational Implementation}
 
-The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}.
+The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, perez2013image, schindelin2012fiji, schneider2012nih} by modifying the existing class \texttt{RankFilters}.
 It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads.
@@
 This was used in this study to simulate a contaminated image with defects.
-The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.
+The contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.
+
+The contamination is a nuisance because the test statistics will have larger variance and larger values at the two corners.
+This will cause an inflation in false positives which will lead to incorrect inference.
+
+It was suggested that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null \citep{efron2004large, schwartzman2008empirical}.
+In this simulated example, it is about $r>\SI{54}{\pixel}$.
+A kernel too small would treat the defects as null, making them difficult to detect.
+
+The receiver operating characteristic (ROC) curve \citep{cook2007use, friedman2001elements, green1966signal, hanley1982meaning, metz1978basic} was studied in this experiment.
+The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
+The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
+Interpretations of the area do exist \citep{hanley1982meaning, metz1978basic} and discussed thoroughly \citep{cook2007use}.
+
+A simulation study was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$.
+Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image.
+The area under the ROC curve and various errors were recorded.
+This was repeated 100 times by simulating another image.
+To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
+
+\section{Results}
+
+The result from the simulation is shown Fig.~\ref{fig:inference_Experiment_DefectRadiusSquare}.
+The ROC area increased with kernel radius which highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination.
+It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
+
+Keeping the FDR consistent before and after filtering is desirable so that the FDR is kept controlled at a specified level after filtering.
+For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%.
+It appeared a large kernel radius helped preserve FDR control after filtering in these examples.
+
+It appeared there is a kernel radius which minimised the type 2 error. A large kernel radius is required for FDR control but too large can lose statistical power.
+
+In the experiment with the AM sample, the x-ray projection was manually segmented further as shown in Fig.~\ref{fig:inference_segmentFurther}.
+It was segmented using the edges of the projection of the sample.
+The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
+The resulting filtered segments were stitched together to form the resulting filtered image.
+The resulting inference is shown in Fig.~\ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
+
+The larger defects were successfully highlighted by the hypothesis test.
+It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
+This probably suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.
+
+\section{Conclusion}
+
+Voids in the order of millimetres were detectable which shows potential in defect detection in projection space.
+This can be extended to multiple projections and perhaps in real time on a conveyor belt.
+
+The empirical null filter catered for inaccuracies made by \emph{aRTist}.
+This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference.
+In the experiments, it was found that the FDR level is preserved after filtering.
+
+False positives do occur but this is unavoidable because tests were done at the 5\% FDR level.
+Typically in the experiments, false positives were isolated single pixels and probably occurred due to random chance.
+Clusters of positive pixels should raise suspicion.
+One could create a binary image, assigning a Boolean value whether that pixel was tested positive or not.
+A binary image filter, such as erode followed by a dilate, can be used to remove isolated positive pixels to emphasise the cluster of positive pixels.
+
+For good results, the faces of the AM cuboid were segmented.
+This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly.
+Manual segmentation was easy to do because a cuboid has 6 faces.
+However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.
+
+The main issue was how slow the filter was.
+Fig.~\ref{fig:inference_timing} shows the timings of the empirical null filter and the mean variance filter.
+For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.
+
+There are a few strategies to accelerate the filter.
+The empirical null filter may be accelerated using GPUs \citep{eklund2013medical, hwu2011gpu, yang2008parallel}, however efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method.
+Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation.
+The problem is that the assumption of a slow varying null parameter is required much more because of the use of interpolation, this may cause bigger problems due to the face to face transition observed in the experiments.
+It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbour pixels due to the interpolation.
+
+The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel.
+Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
+On the other hand, there are methods which uses the histogram count and it was found that the estimation of the null parameters was insensitive to the histogram binning \citep{schwartzman2008empirical}.
+
+Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics.
+Potential faster methods than the empirical null could exist in literature \citep{hampel1986robust, huber2009robust, jewson2018principles, maronna2006robust, rousseeuw1987robust}.
+The EM algorithm \citep{bishop2006pattern, dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.
+However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
+
+\section{Acknowledgements}
+This work is funded by EPSRC grant numbers EP/K031066/1 (Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing) and EP/L016710/1 (EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme).
+
+\settocbibname{References}
+\bibliographystyle{acm}
+\bibliography{../bib}
+
+\setlofname{Figure Captions}
+\listoffigures
+
+\section{Figures}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
+  \caption{The CAD model of the test cuboid with voids.
+Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly.
+The scale shown is approximate.}
+  \label{fig:inference_testObject}
+\end{figure}
 
@@
 
-The contamination is a nuisance because the test statistics will have larger variance and larger values at the two corners.
-This will cause an inflation in false positives which will lead to incorrect inference.
-
-Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null.
-In this simulated example, it is about $r>\SI{54}{\pixel}$.
-A kernel too small would treat the defects as null, making them difficult to detect.
-
-The receiver operating characteristic (ROC) curve \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} was studied in this experiment.
-The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
-The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
-Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed thoroughly in \cite{cook2007use}.
-
-A simulation study was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$.
-Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image.
-The area under the ROC curve and various errors were recorded.
-This was repeated 100 times by simulating another image.
-To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
-
-\begin{figure*}[p]
+\begin{figure}
   \centering
@@
   \label{fig:inference_Experiment_DefectRadiusSquare}
-\end{figure*}
-
-\section{Results}
-
-The result from the simulation is shown Figure \ref{fig:inference_Experiment_DefectRadiusSquare}.
-The ROC area increased with kernel radius which highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination.
-It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
-
-Keeping the FDR consistent before and after filtering is desirable so that the FDR is kept controlled at a specified level after filtering.
-For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%.
-It appeared a large kernel radius helped preserve FDR control after filtering in these examples.
-
-It appeared there is a kernel radius which minimised the type 2 error. A large kernel radius is required for FDR control but too large can lose statistical power.
-
-In the experiment with the AM sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}.
-It was segmented using the edges of the projection of the sample.
-The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
-The resulting filtered segments were stitched together to form the resulting filtered image.
-The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
-
-The larger defects were successfully highlighted by the hypothesis test.
-It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
-This probably suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
@@
   \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
-\end{figure*}
+\end{figure}
 
-\section{Conclusion}
-
-Voids in the order of millimetres were detectable which shows potential in defect detection in projection space.
-This can be extended to multiple projections and perhaps in real time on a conveyor belt.
-
-The empirical null filter catered for inaccuracies made by \emph{aRTist}.
-This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference.
-In the experiments, it was found that the FDR level is preserved after filtering.
-
-False positives do occur but this is unavoidable because tests were done at the 5\% FDR level.
-Typically in the experiments, false positives were isolated single pixels and probably occurred due to random chance.
-Clusters of positive pixels should raise suspicion.
-One could create a binary image, assigning a Boolean value whether that pixel was tested positive or not.
-A binary image filter, such as erode followed by a dilate, can be used to remove isolated positive pixels to emphasise the cluster of positive pixels.
-
-For good results, the faces of the AM cuboid were segmented.
-This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly.
-Manual segmentation was easy to do because a cuboid has 6 faces.
-However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.
-
-The main issue was how slow the filter was.
-Figure \ref{fig:inference_timing} shows the timings of the empirical null filter and the mean variance filter.
-For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.
-
-\begin{figure*}
+\begin{figure}
   \centering
@@
   \label{fig:inference_timing}
-\end{figure*}
-
-There are a few strategies to accelerate the filter.
-The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method.
-Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation.
-The problem is that the assumption of a slow varying null parameter is required much more because of the use of interpolation, this may cause bigger problems due to the face to face transition observed in the experiments.
-It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbour pixels due to the interpolation.
-
-The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel.
-Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
-On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.
-
-Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics.
-Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
-The EM algorithm \citep{dempster1977maximum, bishop2006pattern} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.
-However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
-
-\section{Acknowledgements}
-This work is funded by EPSRC grant numbers EP/K031066/1 (Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing) and EP/L016710/1 (EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme).
-
-\bibliographystyle{apalike}
-\bibliography{../bib}
+\end{figure}
 

### 2019-06-20 reports/paper1/paper.tex
Paper revise

@@
 \usepackage[outdir=./]{epstopdf}
-\usepackage[square,semicolon]{natbib} 
+\usepackage[square,comma]{natbib} 
 \usepackage{url}
@@
 
-\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
-\author[1, *]{S.E.~Lo}
+\title{Inspection of additive manufacturing from a single x-ray projection using local empirical null hypotheses}
+\date{2019}
+\author[1]{S.E.~Lo}
 \author[2]{J.W.~Warnett}
@@
 \author[3]{T.E.~Nichols}
-\author[1]{J.A.~Brettschneider}
+\author[1,*]{J.A.~Brettschneider}
 \affil[1]{Department of Statistics, University of Warwick, Coventry, CV4 7AL, UK}
@@
 \affil[3]{Big Data Institute, Old Road Campus, University of Oxford, Oxford, OX3 7LF, UK}
-\affil[*]{Corresponding author: s.ip@warwick.ac.uk, +442476574812}
+\affil[*]{Corresponding author: julia.brettschneider@warwick.ac.uk, +442476574812}
 
@@
 \newline
-\textbf{OBJECTIVE}: It was investigated whenever it is possible to detect defects based on a single angular projection.
-The motivation behind it is that defect detection in projection space should be faster than in reconstruction space.
+\textbf{OBJECTIVE}: It was investigated whether it is possible to detect defects based on a single angular projection, avoiding the time-consuming reconstruction process.
 \newline
@@
 The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test.
-The simulation was not perfect which led to misleading results.
-The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
+To overcome imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
 \newline
-\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable.
-Simulation studies have shown that statistical properties such as the false discovery rate were preserved when using the filter.
+\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable. Simulation studies have shown that statistical properties such as the false discovery rate were preserved.
 \newline
 \textbf{CONCLUSIONS}: Defect detection in projection space is possible.
-This can be extended to multiple independent projections in real time on a conveyor belt.
+This work is a contribution towards real-time quality control in AM.
 The main bottle neck is the multiple evaluation of functions required for robust estimation in the empirical null filter.
-Speed up could be possible by implementing the filter on a GPU or exploring further robust estimators.
+Speeding up could be possible by implementing the filter on a GPU or exploring further robust estimators.
 \newline
 \newline
-\emph{Keywords:} Hypothesis testing, local normalisation, image filtering, projection space, additive manufacturing, voids, defects, quality control
+\emph{Keywords:} Additive manufacturing, projection space, hypothesis testing, empirical null, local normalisation, image filtering, voids, defects, quality control
 \end{abstract}
@@
 This paper investigates whether defects can be detected from a single x-ray projection.
-To validate our method, we designed an AM test cuboid with purposely designed voids.
+To validate our method, we designed an AM test sample with purposely designed voids.
 An x-ray projection was obtained and compared with the simulation from \emph{aRTist} in order to detect these voids.
@@
 \subsection{Apparatus and Data Collection}
+\label{subsection:appratus}
 
-An ABS plastic test cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected.
-The CAD model of the test cuboid is shown in Fig.~\ref{fig:inference_testObject}.
+An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected.
+The CAD model of the test sample is shown in Fig.~\ref{fig:inference_testObject}.
 It was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer.
@@
 
-\subsection{Statistical Methodology}
+\subsection{The Empirical Null Filter}
 
-A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth.
-This was done by using two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate (FDR) \citep{benjamini2010discovering, benjamini1995controlling}, treating each pixel as an individual test.
-A disagreement too big will classify that pixel as a positive result.
-Beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics.
-This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
+We propose a statistical method to compare a single projection with a simulation of that projection to look for any significant differences which may indicate a defect.
+It is built on two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate (FDR) \citep{benjamini2010discovering, benjamini1995controlling}, conducting individual test for each pixel.
+A disagreement too big, relative to the anticipated variance of the projection, will classify that pixel as a positive result.
+Beforehand, the empirical null \citep{efron2004large} is used to locally normalisation \citep{sage2018local, sage2003teaching} the test statistics.
+This is necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
 
-A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
+Fig.~\ref{fig:flowchart} shows a flowchart which summarises the process of the experiment.
+The CAD model was used as a blueprint for the manufacture of the test sample.
+Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty.
+The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values.
+A threshold was used for the $p$-values to classify pixels as positive for defects or not.
+
+For each position $(x,y)$, we calculate a test statistic
 \begin{equation}
@@
 where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.
+We used a variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ with linear relationship between the variance and the grey value \citep{yang2010noise}.
+We used was a gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} with an identity link.
+The fitting of the model was done using the held out replicated projections of the sample (see Section \ref{subsection:appratus}).
+These replicated projections were manually segmented so that only pixels which represent the test sample were used.
+This provided variance-mean data, where each pixel is a data point, which was used to fit the variance model.
+The variance was predicted using the grey value in the simulated projection as the predictor variable.
 
-The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}.
-The fitting of the model was done using the held out replicated projections of the sample.
-These replicated projections were manually segmented.
-This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model.
-The model used was a gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} with an identity link.
-The variance was predicted using the grey value in the simulated projection as the predictor variable when working out the test statistics.
-
-It was assumed that the grey values were Normal, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
+It was assumed that the grey values were Normally distributed, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
 \begin{equation}
@@
 for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$.
-$\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively.
-Their estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ also respectively.
-Define the null hypotheses to be
+$\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively with estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ respectively.
+Define the null hypotheses
 \begin{equation}
@@
 \end{equation}
-which are tested against
+and the alternative hypotheses
 \begin{equation}
@@
 
-To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$.
+To obtain the estimates, a circular kernel $C_r(x,y)$ with radius $r$ was centred at $(x,y)$.
 All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{friedman2001elements, parzen1962on}
@@
 \end{equation}
-where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth.
+where $K_{x,y} = C_r(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth.
 The bandwidth was chosen such that
@@
 \begin{equation}
-\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
+\widehat\mu_{0,x,y} = \argmax\widehat{p}_{Z_{x,y}}(z)
 \end{equation}
@@
     \widehat{\sigma}_{0,x,y}
-  } \ .
+  }
 \end{equation}
-All the normalised test statistics were converted to $p$-values
+and converted to $p$-values
 \begin{equation}
-  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
+  p_{x,y} = 2(1-\Phi(|t_{x,y}|)) \ .
 \end{equation}
-and was used in the  Benjamini-Hochberg \citep{benjamini1995controlling}(BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.
+
+Pixels are classified as positive for defects if its $p$-value is less than some threshold $\alpha$.
+The Benjamini-Hochberg \citep{benjamini1995controlling}(BH) procedure was used to select the threshold such that the FDR is less than 5\%.
+This was done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$, where $N$ is the area of the ROI, and using the threshold
+\begin{equation}
+  \alpha = \frac{0.05 k}{N}
+\end{equation}
+where
+\begin{equation}
+  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{N}\alpha
+  \ .
+\end{equation}
 
@@
 The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, perez2013image, schindelin2012fiji, schneider2012nih} by modifying the existing class \texttt{RankFilters}.
-It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads.
+The class contains implementations of filters, such as the mean filter and the median filter, using a circular kernel and multiple threads.
 Each thread filters a row in parallel.
@@
 This was done multiple times until 3 valid solutions were obtained.
-The best solution, the one with the largest $\ln\widehat{p}_{Z_{x,y}}\left(\widehat{\mu}_{0,x,y}\right)$, out of all the different initial values was used as the final answer.
+The best solution, the one with the largest $\ln\widehat{p}_{Z_{x,y}}\left(\widehat{\mu}_{0,x,y}\right)$ out of all the different initial values, was used as the final answer.
 
-\subsection{Simulation}
+\subsection{Simulation of Defect Detection}
 
-The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated image.
-A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
+We tested if the empirical null filter can detect simulated defects from a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated image.
+Statistically speaking, a defect is a pixel which has a value not distributed under the null distribution, but instead a alternative distribution.
 For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
@@
 
-Contamination is the result of a linear transform of the test statistics $Z_{x,y}$.
-For example in this experiment, the image was multiplied by 2 and a gradient was added to it.
-Suppose the image does contain defects, then an example of a resulting distribution is
+Contamination was simulated by a linear transform of the test statistics $Z_{x,y}$.
+For example in this experiment, the image was multiplied by 2 and a gradient was added.
+The null and alternative distributions are
 \begin{align}
@@
   \\
-  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
+  Z_{x,y}|H_{1,x,y}&\sim\normal(\mu_{0,x,y}+2\mu_1,2^2)
 \end{align}
-where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
-This was used in this study to simulate a contaminated image with defects.
-The contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.
+respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
+A simulated contaminated defected image was made by sampling $Z_{x,y}|H_{0,x,y}$ in areas with no defects and $Z_{x,y}|H_{1,x,y}$ with defects.
+An example of contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.
 
-The contamination is a nuisance because the test statistics will have larger variance and larger values at the two corners.
-This will cause an inflation in false positives which will lead to incorrect inference.
+The contamination will cause the test statistics to have larger variance and larger values at the two corners where $\mu_{0,x,y}$ is large. This will cause an inflation in false positives.
 
@@
 
-The receiver operating characteristic (ROC) curve \citep{cook2007use, friedman2001elements, green1966signal, hanley1982meaning, metz1978basic} was studied in this experiment.
-The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
+The receiver operating characteristic (ROC) curve \citep{cook2007use, friedman2001elements, green1966signal, hanley1982meaning, metz1978basic} is a parametric plot, displaying the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
 The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
@@
 
-A simulation study was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$.
+A simulation study was conducted where a simulated contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$.
 Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image.
@@
 
-For good results, the faces of the AM cuboid were segmented.
+For good results, the faces of the AM sample were segmented.
 This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly.
@@
 \listoffigures
-
+\clearpage
 \section{Figures}
 
-\begin{figure}
+\begin{figure}[h]
   \centering
-  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
-  \caption{The CAD model of the test cuboid with voids.
+  \includegraphics[width=0.49\textwidth]{../figures/inference/TestObject.png}
+  \caption{The CAD model of the test sample with voids.
 Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model.
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
+  \includegraphics[width=0.7\textwidth]{../figures/flowchart.eps}
+  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection.}
+  \label{fig:flowchart}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
   \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect.
-The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
+The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
   \label{fig:inference_defectSquare2Example}
@@
 The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect.
-The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
+The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
 The test was done at the 5\% FDR level.
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{../figures/inference/segment.JPG}
+  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
   \caption{The x-ray projection was segmented further into 7 segments or ROI.}

### 2019-06-22 reports/paper1/paper.tex
Paper revise

@@
 \DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator{\expectation}{\mathbb{E}}
 
@@
 
-\title{Inspection of additive manufacturing from a single x-ray projection using local empirical null hypotheses}
+\title{Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter}
 \date{2019}
@@
 \subsection{The Empirical Null Filter}
+\label{subsection:empiricalnullfilter}
 
 We propose a statistical method to compare a single projection with a simulation of that projection to look for any significant differences which may indicate a defect.
-It is built on two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate (FDR) \citep{benjamini2010discovering, benjamini1995controlling}, conducting individual test for each pixel.
+It is built on two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate \citep{benjamini2010discovering, benjamini1995controlling}, conducting individual test for each pixel.
 A disagreement too big, relative to the anticipated variance of the projection, will classify that pixel as a positive result.
@@
 
-Fig.~\ref{fig:flowchart} shows a flowchart which summarises the process of the experiment.
+Fig.~\ref{fig:flowchart} shows a flowchart which summarises the process of the experiment and defect detection.
 The CAD model was used as a blueprint for the manufacture of the test sample.
 Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty.
+The uncertainty was modelled using the replicated projections.
 The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values.
@@
 
-For each position $(x,y)$, we calculate a test statistic
+For each position $(x,y)$, a test statistic was calculated
 \begin{equation}
@@
 where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.
-We used a variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ with linear relationship between the variance and the grey value \citep{yang2010noise}.
-We used was a gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} with an identity link.
+The variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}.
+A gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} was used with an identity link.
 The fitting of the model was done using the held out replicated projections of the sample (see Section \ref{subsection:appratus}).
@@
 \end{equation}
-where $K_{x,y} = C_r(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth.
+where $K_{x,y} = C_r(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the standard Normal density function and $h$ is the bandwidth.
 The bandwidth was chosen such that
@@
 Pixels are classified as positive for defects if its $p$-value is less than some threshold $\alpha$.
-The Benjamini-Hochberg \citep{benjamini1995controlling}(BH) procedure was used to select the threshold such that the FDR is less than 5\%.
-This was done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$, where $N$ is the area of the ROI, and using the threshold
+The Benjamini-Hochberg (BH) \citep{benjamini1995controlling} procedure was used to select the threshold such that the false discovery rate (FDR) is less than 5\%.
+The FDR is defined as
+\begin{equation}
+\text{FDR}=\expectation\left[\dfrac{\text{number of false positives}}{\text{number of positives}}\right]
+\end{equation}
+where the ratio is defined to be zero when the number of positives is zero.
+It indicates the average proportion of positives which are false.
+The BH procedure is done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$, where $N$ is the area of the ROI, and using the threshold
 \begin{equation}
@@
 \subsection{Computational Implementation}
+\label{subsection:computational}
 
@@
 
+To satisfy the condition that the empirical null mean is slowly and smoothly varying, the x-ray projection of the test sample was manually segmented further as shown in Fig.~\ref{fig:inference_segmentFurther}.
+It was segmented using the edges of the projection of the sample.
+The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter was working on.
+The resulting filtered segments were stitched together to form the resulting filtered image prior to any hypothesis testing.
+
 \subsection{Simulation of Defect Detection}
+\label{subsection:simulation}
 
@@
 Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image.
-The area under the ROC curve and various errors were recorded.
-This was repeated 100 times by simulating another image.
-To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
+The area under the ROC curve (AUC) and statistical errors were recorded.
+This was repeated 100 times by simulating another image and repeating the measurement.
+To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.
 
@@
 
-The result from the simulation is shown Fig.~\ref{fig:inference_Experiment_DefectRadiusSquare}.
-The ROC area increased with kernel radius which highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination.
-It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
+In the simulation study, defection detection was conducted on a uncontaminated defected image and a filtered contaminated defected image so that the statistical properties were compared.
+The results from the simulation is shown Fig.~\ref{fig:inference_Experiment_DefectRadiusSquare}.
 
-Keeping the FDR consistent before and after filtering is desirable so that the FDR is kept controlled at a specified level after filtering.
-For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%.
-It appeared a large kernel radius helped preserve FDR control after filtering in these examples.
+The area under the ROC curve (AUC) increased with kernel radius which highlighted that a filtered image with a suitable radius kernel can perform almost as well as though there was no contamination.
+The rule of thumb (see Section \ref{subsection:simulation}) suggest a kernel radius of $r>\SI{54}{\pixel}$ which achieved optimal AUC thus justifies the use of the rule of thumb.
 
-It appeared there is a kernel radius which minimised the type 2 error. A large kernel radius is required for FDR control but too large can lose statistical power.
+It was observed that there is a kernel radius which minimised the type 2 error.
+A large kernel radius helped preserve false discovery rate (FDR) control after filtering in these examples but a kernel radius too large can lose statistical power.
+Keeping the FDR consistent before and after filtering is desirable so it is controlled at a specified level after filtering.
+For large enough kernel radius, the FDR was controlled at fluctuates around 5\%.
 
-In the experiment with the AM sample, the x-ray projection was manually segmented further as shown in Fig.~\ref{fig:inference_segmentFurther}.
-It was segmented using the edges of the projection of the sample.
-The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
-The resulting filtered segments were stitched together to form the resulting filtered image.
-The resulting inference is shown in Fig.~\ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
+The running times of the filtering are shown in Fig.~\ref{fig:inference_timing}.
+The running times are compared with the mean variance filter which normalise the statistics using the sample mean and sample standard deviation.
+Compared to the mean variance filter, the empirical null filter was slow and much slower for larger kernel radiuses.
 
+The resulting inference from the test sample is shown in Fig.~\ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
 The larger defects were successfully highlighted by the hypothesis test.
-It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
-This probably suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.
+The empirical null mean changed face to face, resulting in a clear boundary set by the edges.
+This suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.
 
@@
 
-The main issue was how slow the filter was.
-Fig.~\ref{fig:inference_timing} shows the timings of the empirical null filter and the mean variance filter.
 For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.
-
 There are a few strategies to accelerate the filter.
@@
 However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
+
+\section{Appendix}
+Code which reproduces this paper can be found on the \emph{GitHub} page.
 
@@
 
+\clearpage
+
 \begin{figure}
@@
 
+\clearpage
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
+  \caption{The x-ray projection was segmented further into 7 segments or ROI.}
+  \label{fig:inference_segmentFurther}
+\end{figure}
+
+\clearpage
+
 \begin{figure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
-        \caption{ROC area}
+        \caption{AUC}
       \end{subfigure}
@@
     }
-  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect.
-Various kernel radiuses were investigated.
+  \caption{Area under the ROC curve (AUC) and statistical errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect for Various kernel radiuses.
 The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect.
 The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.
-The test was done at the 5\% FDR level.
-The box plot summarise the 100 repeated measurements of the experiment.}
+The test was conducted at the 5\% FDR level.
+The box plots summarise the 100 repeated measurements of the simulation.}
   \label{fig:inference_Experiment_DefectRadiusSquare}
@@
 
+\clearpage
+
 \begin{figure}
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
-  \caption{The x-ray projection was segmented further into 7 segments or ROI.}
-  \label{fig:inference_segmentFurther}
+    \centerline{
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
+        \caption{Empirical null filter}
+      \end{subfigure}
+      \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
+        \caption{Mean variance null filter}
+      \end{subfigure}
+    }
+  \caption{Running times when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image.
+The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
+Note that the $y$-axis changes scale.
+The box plots summarise the 100 repeated measurements of the running times.}
+  \label{fig:inference_timing}
 \end{figure}
+
+\clearpage
 
@@
 
-\begin{figure}
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
-        \caption{Empirical null filter}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
-        \caption{Mean variance null filter}
-      \end{subfigure}
-    }
-  \caption{Timings when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image.
-The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
-Note that the $y$-axis changes scale.
-The box plot summarise the 100 repeated measurements of the timings.}
-  \label{fig:inference_timing}
-\end{figure}
-
 \end{document}

### 2019-06-25 reports/paper1/paper.tex

@@
 \usepackage[outdir=./]{epstopdf}
-\usepackage[square,comma]{natbib} 
+\usepackage[square,numbers,comma]{natbib} 
 \usepackage{url}
@@
 The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test.
-To overcome imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
+To overcome the imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
 \newline
@@
 This work is a contribution towards real-time quality control in AM.
-The main bottle neck is the multiple evaluation of functions required for robust estimation in the empirical null filter.
+The main bottleneck is the multiple evaluations of functions required for robust estimation in the empirical null filter.
 Speeding up could be possible by implementing the filter on a GPU or exploring further robust estimators.
@@
 \newline
-\emph{Keywords:} Additive manufacturing, projection space, hypothesis testing, empirical null, local normalisation, image filtering, voids, defects, quality control
+\emph{Keywords:} Additive manufacturing, 3D printing, projection space, hypothesis testing, empirical null, local normalisation, image filtering, voids, defects, quality control
 \end{abstract}
@@
 
-Additive manufacturing (AM) is an emerging technology that overcomes many traditional methods such as computer numerical control (CNC).
-In AM, the product is manufactured layer by layer to product complicated internal and external geometries \citep{ngo2018additive, wong2012review}.
+Additive manufacturing (AM) is an emerging technology that overcomes many traditional methods such as computer numerical control machining (CNC).
+In AM, the product is manufactured layer by layer to produce complicated internal and external geometries \citep{ngo2018additive, wong2012review}.
 One common example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
 A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer.
-The material is usually plastic in a form of a thin filament.
+The material is usually plastic in the form of a thin filament.
 It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}.
@@
 The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.
-Powder based AM such as selective laser sintering \citep{3d2019our, deckard1989method, dtm1990the} can manufacture metal products.
+Powder-based AM such as selective laser sintering \citep{3d2019our, deckard1989method, dtm1990the} can manufacture metal products.
 
-There is a need for product inspection, in particular quality assessment of the internal structures.
+There is a need for product inspection, in particular, quality assessment of the internal structures.
 The properties of materials produced by AM are not yet fully understood.
 For example, voids can form between layers which can impact the mechanical properties of the product \citep{ngo2018additive, wang20173d}.
-In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{tammas2015xct, thijs2010study}.
-Low wetting ability of the melt pool can cause balling, a phenomenon where spherical or ellipsoidal deposits on the surface of the AM part.
+In power-based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{tammas2015xct, thijs2010study}.
+Low wetting ability of the melt pool can cause balling, a phenomenon where spherical or ellipsoidal particles form on the surface of the AM part.
 They are formed by sintered powder with insufficient contact on the existing layer \citep{gu2009balling, li2012balling}.
@@
 The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}.
-In addition to pores, surface deviation can be measured by aligning the reconstruction with the computer-aided design (CAD) model and measuring any discrepancies \citep{kim2016inspection, lee2015compliance, villarraga2015assessing}.
+In addition to pores, the surface deviation can be measured by aligning the reconstruction with the computer-aided design (CAD) model and measuring any discrepancies \citep{kim2016inspection, lee2015compliance, villarraga2015assessing}.
 
 A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample.
-XCT is not a instantaneous process so progress bars are usually featured in marketing for XCT such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}.
+XCT is not an instantaneous process so progress bars are usually featured XCT marketing such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}.
 Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.
@@
 The simulated projections are made in software called \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}.
-It is however inevitable that information is lost from the jump from reconstruction space to projection space, for example a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.
+It is however inevitable that information is lost from the jump from reconstruction space to projection space, for example, a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.
 
@@
 To validate our method, we designed an AM test sample with purposely designed voids.
-An x-ray projection was obtained and compared with the simulation from \emph{aRTist} in order to detect these voids.
+An x-ray projection was obtained and compared with the simulated projection from \emph{aRTist} in order to detect these voids.
 The simulation was not perfect which led to misleading results.
@@
 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}.
-A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.
+A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using 20 black (\SI{0}{\kilo\volt}) and 20 white images (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.
 
-The projection of the sample was obtained and repeated 20 times at a fixed angle.
-19 randomly selected projections were held out.
+19 randomly selected projections, of the test sample, were held out.
 The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}.
@@
 We propose a statistical method to compare a single projection with a simulation of that projection to look for any significant differences which may indicate a defect.
-It is built on two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate \citep{benjamini2010discovering, benjamini1995controlling}, conducting individual test for each pixel.
+It is built on two-tailed multiple hypotheses testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate \citep{benjamini2010discovering, benjamini1995controlling}, conducting an individual test for each pixel.
 A disagreement too big, relative to the anticipated variance of the projection, will classify that pixel as a positive result.
-Beforehand, the empirical null \citep{efron2004large} is used to locally normalisation \citep{sage2018local, sage2003teaching} the test statistics.
+Beforehand, the empirical null \citep{efron2004large} is used to locally normalise \citep{sage2018local, sage2003teaching} the test statistics.
 This is necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.
@@
 for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$.
-$\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively with estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ respectively.
+$\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$.
+Their estimates, $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ respectively, are called the empirical null mean and empirical null standard deviation.
 Define the null hypotheses
@@
 A simulated contaminated defected image was made by sampling $Z_{x,y}|H_{0,x,y}$ in areas with no defects and $Z_{x,y}|H_{1,x,y}$ with defects.
-An example of contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.
+An example of a contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.
 
-The contamination will cause the test statistics to have larger variance and larger values at the two corners where $\mu_{0,x,y}$ is large. This will cause an inflation in false positives.
+The contamination will cause the test statistics to have larger variance and larger values at the two corners where $\mu_{0,x,y}$ is large. This will cause inflation in false positives.
 
-It was suggested that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null \citep{efron2004large, schwartzman2008empirical}.
+It was suggested that, as a rule of thumb, the proportion of non-null statistics captured by the kernel should not be larger than $0.1$ to satisfy some assumptions made for the empirical null \citep{efron2004large, schwartzman2008empirical}.
 In this simulated example, it is about $r>\SI{54}{\pixel}$.
@@
 This was repeated 100 times by simulating another image and repeating the measurement.
-To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.
+To form a baseline to compare with, the results of the uncontaminated defected image were all pooled together to obtain the empirical distribution of the AUC and statistical errors without contamination.
 
@@
 
-In the simulation study, defection detection was conducted on a uncontaminated defected image and a filtered contaminated defected image so that the statistical properties were compared.
+In the simulation study, defect detection was conducted on a filtered contaminated defected image to investigate the statistical properties of the method.
+The aim of the filter was to remove the contamination so that sensible inference was achieved.
 The results from the simulation is shown Fig.~\ref{fig:inference_Experiment_DefectRadiusSquare}.
@@
 Keeping the FDR consistent before and after filtering is desirable so it is controlled at a specified level after filtering.
-For large enough kernel radius, the FDR was controlled at fluctuates around 5\%.
+For large enough kernel radius, the FDR was controlled at and fluctuates around 5\%.
 
 The running times of the filtering are shown in Fig.~\ref{fig:inference_timing}.
-The running times are compared with the mean variance filter which normalise the statistics using the sample mean and sample standard deviation.
-Compared to the mean variance filter, the empirical null filter was slow and much slower for larger kernel radiuses.
+The running times are compared with the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation.
+Compared to the mean-variance filter, the empirical null filter was slow and much slower for larger kernel radiuses.
 
@@
 The empirical null mean changed face to face, resulting in a clear boundary set by the edges.
-This suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.
+This suggests that the contamination or inaccuracy from \emph{aRTist} was face dependent.
 
@@
 
-Voids in the order of millimetres were detectable which shows potential in defect detection in projection space.
-This can be extended to multiple projections and perhaps in real time on a conveyor belt.
+Voids in the order of millimetres were detectable which shows potential in defect detection in projection space. This
+work is a contribution towards real-time quality control in AM.
 
 The empirical null filter catered for inaccuracies made by \emph{aRTist}.
-This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference.
+This demonstrated that the filter can adjust the null hypotheses according to the data to make a sensible inference.
 In the experiments, it was found that the FDR level is preserved after filtering.
@@
 The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel.
-Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
-On the other hand, there are methods which uses the histogram count and it was found that the estimation of the null parameters was insensitive to the histogram binning \citep{schwartzman2008empirical}.
+Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however, that would require tuning the histogram bins as well as the tuning parameters for the spline.
+On the other hand, there are methods which use the histogram count and it was found that the estimation of the null parameters was insensitive to the histogram binning \citep{schwartzman2008empirical}.
 
@@
 The EM algorithm \citep{bishop2006pattern, dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.
-However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
+However, the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
 
@@
         \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
-        \caption{Mean variance null filter}
+        \caption{Mean-variance null filter}
       \end{subfigure}
@@
   \caption{Running times when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image.
-The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
+The mean-variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
 Note that the $y$-axis changes scale.

### 2019-07-01 reports/paper1/paper.tex
Revise paper, add getTime for AllNull

@@
 This paper investigates whether defects can be detected from a single x-ray projection.
-To validate our method, we designed an AM test sample with purposely designed voids.
-An x-ray projection was obtained and compared with the simulated projection from \emph{aRTist} in order to detect these voids.
-The simulation was not perfect which led to misleading results.
-The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
-The apparatus and procedures are shown in the methods section.
-In addition, computational implementation and simulation studies of the empirical null filter are discussed.
+To validate our method, we designed an AM test sample with purposely designed voids to see if they can be detected.
+The methods section is split into four parts.
+In Section \ref{subsection:appratus}, a CAD model of the test sample was designed and manufactured using AM.
+Replicate x-ray projections were obtained of the test sample as well as a simulated projection, without the voids, using \emph{aRTist}.
+Section \ref{subsection:empiricalnullfilter} explains how the obtained and simulated projections were compared to detect these voids under the face of uncertainty.
+The uncertainty was modelled using the replicated projections.
+To overcome the imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
+The implementation of the empirical null filter is discussed in Section \ref{subsection:computational} and tested on small simulated projections in Section \ref{subsection:simulation}.
 The results from the simulation and the experiment are shown in the results section.
@@
 Pixels are classified as positive for defects if its $p$-value is less than some threshold $\alpha$.
-The Benjamini-Hochberg (BH) \citep{benjamini1995controlling} procedure was used to select the threshold such that the false discovery rate (FDR) is less than 5\%.
-The FDR is defined as
+It controls the per comparison error rate (PCER) \citep{benjamini1995controlling} which is the average proportion of false positives out of all tests or
+\begin{equation}
+\text{PCER}=\dfrac{1}{N}\expectation\left[\text{number of false positives}\right]
+\end{equation}
+where $N$ is the number of pixels to test.
+A typical choice is $\alpha=0.05$ \citep{wasserstein2019moving}.
+This method of thresholding is flawed because of the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}.
+For example, suppose none of the pixels represents a defect, then on average, 5\% of these pixels are tested positive and falsely so.
+This is troublesome and costly because false positives suggest a defect in areas where there are not any defects.
+
+The false discovery rate (FDR) is the average proportion of positives which are false or
 \begin{equation}
@@
 where the ratio is defined to be zero when the number of positives is zero.
-It indicates the average proportion of positives which are false.
-The BH procedure is done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$, where $N$ is the area of the ROI, and using the threshold
+The Benjamini-Hochberg (BH) \citep{benjamini1995controlling} procedure was used to select the threshold such that the FDR is less than 5\%.
+This allows control for false positives relative to the number of positives.
+The BH procedure is done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$ and then using the threshold
 \begin{equation}
@@
 
-The running times of the filtering are shown in Fig.~\ref{fig:inference_timing}.
-The running times are compared with the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation.
-Compared to the mean-variance filter, the empirical null filter was slow and much slower for larger kernel radiuses.
+The running times for the empirical null filter with radius \SI{50}{\pixel} were measured to be \SI[separate-uncertainty = true]{26.72(35)}{\second}.
+This was compared to simpler filters such as the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation.
+Running times of \SI[separate-uncertainty = true]{0.0100(12)}{\second} were achieved using the mean-variance filter.
+With both of these filters, running time increased with kernel radius.
 
@@
 
-Voids in the order of millimetres were detectable which shows potential in defect detection in projection space. This
-work is a contribution towards real-time quality control in AM.
+Voids in the order of millimetres were detectable which shows potential in defect detection in projection space. This work is a contribution towards real-time quality control in AM.
 
@@
 
-For good results, the faces of the AM sample were segmented.
+For good results, the faces of the test sample were segmented.
 This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly.
 Manual segmentation was easy to do because a cuboid has 6 faces.
-However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.
+However, segmentation of faces cannot be generalised well to AM products with complicated geometry and curved surfaces.
 
@@
 \section{Appendix}
-Code which reproduces this paper can be found on the \emph{GitHub} page.
+Code which reproduces this paper can be found on the \emph{GitHub} page \url{https://github.com/shermanip/oxwasp_insideout}.
 
@@
 This work is funded by EPSRC grant numbers EP/K031066/1 (Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing) and EP/L016710/1 (EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme).
+We would like to thank Wilfred S.~Kendall for his role as principal investigator.
 
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
-        \caption{Empirical null filter}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
-        \caption{Mean-variance null filter}
-      \end{subfigure}
-    }
-  \caption{Running times when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image.
-The mean-variance null filter uses the sample mean and sample standard deviation to locally normalise the image.
-Note that the $y$-axis changes scale.
-The box plots summarise the 100 repeated measurements of the running times.}
-  \label{fig:inference_timing}
-\end{figure}
-
-\clearpage
-
-\begin{figure}
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}

### 2019-07-01 reports/paper1/paper.tex
Revise paper

@@
 
+In the experiment with the test sample, the angle was chosen to distinguish the designed voids.
+For general AM products, finding a suitable singular projection angle can be difficult.
+This problem can be tackled by conducting defect detection on a small number of different angular projections independently to pick up defects hidden behind another.
+
 For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.

### 2019-07-09 reports/thesis/chapters/4_variancePrediction.tex
printResults for GlmSelect

@@
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsNoFilterLinear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsNoFilterLinear_reciprocalcriterion.txt}
+\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectAicAbsFilterLinear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varMean/GlmSelectBicAbsFilterLinear_reciprocalcriterion.txt}
+\end{tabular}
+\end{sidewaystable}
+
 In the previous chapter, it was found that it is very hard to fit a compound Poisson random variable onto the grey values directly itself.

### 2019-07-15 reports/thesis/chapters/4_variancePrediction.tex
varmean experiments print results
Fix syntax error in GlmSelectAic
Figures saved in reports/figures/varmean
VarMeanCv plots training and test deviance

--- 2018-03-20 reports/thesis/chapters/4_variancePrediction.tex
@@
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalcriterion.txt}
+\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalcriterion.txt}
+\end{tabular}
+\end{sidewaystable}
+
 In the previous chapter, it was found that it is very hard to fit a compound Poisson random variable onto the grey values directly itself.

### 2019-07-15 varmean/devianceGraph.m

@@ -1,0 +1,13 @@
+clearvars;
+close all;
+
+xPlot = linspace(-1,1,100);
+ratio = 10.^(xPlot);
+yPlot = 2*(ratio - 1 - log(ratio));
+
+figure;
+plot(ratio, yPlot);
+ax = gca;
+ax.XScale = 'log';
+xlabel('$y/\widehat{y}$','Interpreter','latex');
+ylabel('deviance');

### 2019-07-15 varmean/glmselect/GlmSelect.m

@@ -97,17 +97,17 @@ classdef GlmSelect < Experiment
         %quote polynomial with the most votes
         [maxCount,maxKey] = max(polynomialCount);
         
-        file = fopen(fullfile('reports','figures','varMean',strcat(class(this), ...
+        file = fopen(fullfile('reports','figures','varmean',strcat(class(this), ...
             '_',this.linkArray{iLink},'order.txt')),'wt');
         fprintf(file, polynomialKey{maxKey});
         fclose(file);
         
-        file = fopen(fullfile('reports','figures','varMean',strcat(class(this), ...
+        file = fopen(fullfile('reports','figures','varmean',strcat(class(this), ...
             '_',this.linkArray{iLink},'vote.txt')),'wt');
         fprintf(file, num2str(maxCount));
         fclose(file);
         
-        file = fopen(fullfile('reports','figures','varMean',strcat(class(this), ...
+        file = fopen(fullfile('reports','figures','varmean',strcat(class(this), ...
             '_',this.linkArray{iLink},'criterion.txt')),'wt');
         fprintf(file, devianceQuote);
         fclose(file);

### 2019-07-15 varmean/glmselect/GlmSelectAic.m

@@ -11,6 +11,7 @@ classdef GlmSelectAic < GlmSelect
     
     function aic = getCriterion(this, glm)
       aic = 2*glm.NumCoefficients - 2*this.getLogLikelihood(glm);
+    end
     
   end
   

### 2019-07-15 varmean/varmeancv/varmeancv.m

@@ -11,35 +11,71 @@ for i = 1:numel(experiments)
   experiments{i}.run();
 end
 
-experiments = {...
-  VarMeanCvAbsNoFilterNull();
-  VarMeanCvAbsNoFilterBw();
-  VarMeanCvAbsNoFilterLinear();
-};
+%print results
+for iData = 1:2
+  
+  %get array of the same data but with different shading corrections
+  switch iData
+    case 1
+      experiments = {...
+        VarMeanCvAbsNoFilterNull();
+        VarMeanCvAbsNoFilterBw();
+        VarMeanCvAbsNoFilterLinear();
+      };
+    case 2
+      experiments = {...
+        VarMeanCvAbsFilterNull();
+        VarMeanCvAbsFilterBw();
+        VarMeanCvAbsFilterLinear();
+      };
+  end
+  
+  %use just an experiment to get properties of the experiment
+  this = experiments{1};
+  
+  %get list of shading correction
+  shadingCorrectionNameArray = cell(size(experiments));
+  for iShadingCorrection = 1:numel(shadingCorrectionNameArray)
+    shadingCorrector = experiments{iShadingCorrection}.scan.shadingCorrector;
+    if (isempty(shadingCorrector))
+      shadingCorrectionNameArray{iShadingCorrection} = 'null';
+    else
+      shadingCorrectionNameArray{iShadingCorrection} = shadingCorrector.getName();
+    end
+  end
+  
+  %plot the training and test deviance
+  for iStat = 1:2
+    isTrainingDeviance = iStat == 1;
+    if (isTrainingDeviance)
+      statName = 'training deviance';
+    else
+      statName = 'test deviance';
+    end
+    
+    %plot the test deviance for each shading correction
+    fig = LatexFigure.sub();
+    legendArray = line(0,0);
+    for iShadingCorrection = 1:numel(experiments)
+      boxplots = experiments{iShadingCorrection}. ...
+          printResults(-0.1 + ((iShadingCorrection-1)*0.1), isTrainingDeviance);
+      legendArray(iShadingCorrection) = boxplots.getLegendAx();
+    end
 
-fig = figure;
-legendArray = line(0,0);
-for i = 1:numel(experiments)
-  boxplots = experiments{i}.printResults(-0.1 + ((i-1)*0.1),true);
-  legendArray(i) = boxplots.getLegendAx();
-end
-this = experiments{1};
-%retick the x axis
[…]

### 2019-07-16 reports/thesis/chapters/2_dataCollection.tex
ANOVA write up

@@
 
-A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as BW shading correction.
+A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.
 
@@
 
-The BW shading corrected black image looks very uniform but there is some structure in the linear shading correction.
+The BW shading corrected black and white image looks very uniform but there is some structure in the linear shading correction.
 By giving linear shading correction various greyscale projections, it tried to generalise to a range of powers and thus may struggle at shading correcting the black and white images.
@@
   \label{fig:data_shadingCorrectionExample_black}
+\end{figure}
+
+\begin{figure}
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
+      \caption{BW shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_linear.eps}
+      \caption{Linear shading correction}
+    \end{subfigure}
+  }
+  \caption{The \texttt{AbsNoFilter} white image after shading correction.}
+  \label{fig:data_shadingCorrectionExample_white}
 \end{figure}
@@
 
-% \begin{figure}
-%   \centering
-%   \centerline{
-%     \begin{subfigure}[b]{0.49\textwidth}
-%       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_null.eps}
-%       \caption{No shading correction}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.49\textwidth}
-%       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_bw.eps}
-%       \caption{BW shading correction}
-%     \end{subfigure}
-%   }
-%   \begin{subfigure}[b]{0.49\textwidth}
-%     \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_linear.eps}
-%     \caption{Linear shading correction}
-%   \end{subfigure}
-%   \caption{Fourier transform on the black image before and after shading correction. The colour scale is in arbitrary units and range between 0 to 255.}
-%   \label{fig:data_fft}
-% \end{figure}
-
 \subsection{ANOVA}
 
-Figure \ref{fig:data_AbsNoFilter} shows the data.
-Shading correction is done via the following.
-It requires calibration images, they are projections of nothing at different powers.
-For each calibration image, calculate the within image mean.
-For each pixel, do a linear regression of the within image mean versus the grey value for different powers: bw shading correction uses only the black and max power calibration images, linear shading correction uses all calibration images.
-The regression maps the uncorrected grey value ($x$) to the shading corrected grey value ($y$) for this particular pixel.
+An experiment was conducted to quantify the performance of the different types of shading correction.
+Applying shading correction on the greyscale image should remove effects from the panels and the spot, leaving a flat noisy image with no spatial structure.
+The variance within a pixel and across replications should be similar to between pixels within a replication if the shading correction flatten the greyscale images.
 
-An example is shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap}.
-In Figure \ref{fig:data_shadingCorrectionExample_gainMap} a), 3 random pixels were used to demonstrate the regression.
-The gradient of the regression for all pixels are shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap} b).
+In the \texttt{AbsNoFilter} dataset, there are 20 replicated greyscale images for each power.
+One randomly selected replication from each power was assigned to the training set and used to calibrate the shading correction.
+The remaining images was assigned to the test set and the shading correction was applied to each image.
 
-The gain is actually the sensitivity so it should be a plot of the grey value versus the power, this is shown in Figure \ref{fig:data_shadingCorrectionExample_gain}.
-However this is similar to the linear regression done for shading correction.
+For each power, the within and between pixel variance was calculated.
+Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\cdots,n$ replicates.
+The within and between pixel variance are
+\begin{equation}
+s_\mathrm{w}^2(P)=\dfrac{1}{WH(n-1)}
+  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{n}
+  \left(
+    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
+  \right)^2
+\end{equation}
+and
+\begin{equation}
+s_\mathrm{b}^2(P)=\dfrac{1}{WH-1}
+  \sum_{x=1}^{W}\sum_{y=1}^{H}
+  \left(
+    \overline{U}_{x,y}(P) - \overline{U}(P)
+  \right)^2
+\end{equation}
+respectively where
+\begin{equation}
+  \overline{U}_{x,y}(P) = \dfrac{1}{n}\sum_{j=1}^{n}U_{x,y}^{(j)}(P)
+\end{equation}
+and
+\begin{equation}
+  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
+  \ .
+\end{equation}
+In this specific experiment, $W=2000$, $H=2000$ and $n=19$. The $F$ statistic is
+\begin{equation}
+F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
+\end{equation}
+and should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.
 
-In the black image, I've noticed the vertical read-out structure can be seen.
-This can be done by plotting the grey value down a column as shown in Figure \ref{fig:data_oddEven}.
-In particular, the grey value jumps up and down at every pixel, this is seen by plotting the same profile curve but for every odd and even $y$.
-Shading correction corrects this because the black image has information on the odd/even structure which is then fed into the shading correction.
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
+      \caption{No shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
+      \caption{BW shading correction}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
+      \caption{Linear shading Correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
+      \caption{$F$ statistic}
+    \end{subfigure}
+  }
+  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale images.
+The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power.
+The box plots represent the 100 repeats.
+The experiment was repeated by reselecting the greyscale image used for training the shading correction.}
+  \label{fig:data_anova}
+\end{figure}
 
-An autocorrelation plot could be plotted, but it's easier to do a Fourier transform, this is shown in Figure \ref{fig:data_fft}.
+The results are shown in Figure \ref{fig:data_anova} and shows that with shading correction, the within and between pixel variance become more similar.
+A difference between BW and linear shading correction is that for the black image, the $F$ statistic is better for BW compared to linear shading correction.
+For the rest of the powers, linear shading correction outperforms BW shading correction.
+This shows that linear shading correction generalise to powers between the black and white image.
+Since beam extinction is avoided, black grey values in the obtained projection should not be possible.
+As a result, the linear shading correction is recommended for its good performance for various powers.
 
-No read-out structure can be seen horizontally, see Figure \ref{fig:data_oddEvenX}. Panel structure can be seen however.
+Using the $F$ test from ANOVA was found to be too strict in this experiment.
+Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1,WH(n-1)}$.
+In this experiment, the 5\% critical value is 1.001 to 3 decimal places.
+This may be due to the grey values of the greyscale images not satisfying the assumptions for the $F$ test, for example they may not be i.i.d.

### 2019-07-17 reports/thesis/chapters/4_variancePrediction.tex
GlmSelect write up

--- 2018-03-20 reports/thesis/chapters/4_variancePrediction.tex
@@
 
-\section{Variance-Mean Relationship}
+\subsection{Generalised Linear Models}
 
-The sample variance-mean data were obtained from the replicated x-ray images, assuming each image are i.i.d.
-
-Let $x_{i,j}^{(r)}$ be the grey value of the pixel in the $i$th row and $j$th column in the $r$th image for $r=1,2,3,\dotdotdot,n$. The within individual pixel sample mean is
+The sample variance-mean data were obtained from the replicated projections.
+Let $x_{x,y}^{(r)}$ be the grey value of the pixel at $(x.y)$ from the $r$th replicate projection for $r=1,2,3,\dotdotdot,n$.
+The pixel sample mean is
 \begin{equation}
-    \bar{x}_{i,j}=\frac{1}{n}\sum_{r=1}^n x_{i,j}^{(r)}
+    \overline{x}_{x,y}=\frac{1}{n}\sum_{r=1}^n x_{x,y}^{(r)}
 \end{equation}
-and the within individual pixel sample variance is
+and the pixel sample variance is
 \begin{equation}
-    y_{i,j} =
+    y_{x,y} =
     \frac{1}{n-1}
@@
         \left(
-            x_{i,j}^{(r)} - \bar{x}_{i,j}
+            x_{x,y}^{(r)} - \overline{x}_{x,y}
         \right)^2
@@
 \end{equation}
+Only pixels in the region of interest (ROI) were considered here, that is pixels which represent the test sample.
 
-Only the masked pixels will be considered here as this is the region of interest (ROI).
-The sample variance-mean data can be obtained by calculating the within individual pixel sample mean and variance for all ROI pixels and can be plotted as a histogram.
-For example, the sample variance-mean data for \texttt{Mar16} can be seen in Figure \ref{fig:meanvar_mar16_100}.
+The aim is to model and predict the pixel variance given the pixel grey value by fitting a model onto the sample variance-mean data.
+No spatial information is used, thus the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\cdots,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
+Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$.
+It was assumed the standard error from estimating the mean was negligible so that the uncertainty is captured by the random variable $Y$.
+It was assumed that for a given pixel, the grey values are Normally distributed and i.i.d.
+Let $\sigma^2(x)$ be the variance given a grey value $x$, then it can be shown that
+\begin{equation}
+\dfrac{(n-1)Y(x)}{\sigma^2(x)}\sim\chi^2_{n-1}
+\end{equation}
+which results in
+\begin{equation}
+Y(x)\sim\gammaDist\left(\alpha,\dfrac{\alpha}{\sigma^2(x)}\right)
+\end{equation}
+where $\alpha=(n-1)/2$ is the shape parameter. The expectation and variance are
+\begin{equation}
+\expectation\left[Y(x)\right]=\sigma^2(x)
+\end{equation}
+and
+\begin{equation}
+\variance\left[Y(x)\right]=\dfrac{\sigma^2(x)}{\alpha}
+\end{equation}
+respectively.
 
-\subsection{Generalised Linear Models}
-By making some assumptions, some useful and simple results can be obtained.
-Firstly, it was assumed the standard error from estimating the mean was negligible.
-Secondly, it was assumed for a given pixel, the grey value from each each were Normal i.i.d.
-Following from these assumptions, the sample variance is Gamma distributed with shape parameter $(n-1)/2$.
-Furthermore the standard error of the sample variance is proportional to $(n-1)^{-1/2}$, meaning the sample variance is more precise when more and more images were used to estimate the variance.
-This was experimentally shown in Figure \ref{fig:meanvar_mar16_differentn}, the spread of the sample variance decreased as $n$ increased.
+This framework allows the use of generalised linear models (GLM) \citep{nelder1972generalized,nelder1972generalized_2, mccullagh1984generalized}.
+In the gamma distribution case, GLM can be used to model
+\begin{equation}
+Y(x)\sim\gammaDist\left(\alpha,\dfrac{\alpha}{g^{-1}(\eta(x))}\right)
+\end{equation}
+where $g(\sigma^2)$ is the link function and $\eta(x)$ is a linear function called the systematic component. It should be noted that
+\begin{equation}
+  \expectation\left[Y(x)\right]=g^{-1}(\eta(x))
+\end{equation}
+which shows how the link function and systematic component work together. Examples of link functions are the identity link
+\begin{equation}
+g(\sigma^2)=g^{-1}(\sigma^2)=\sigma^2
+\end{equation}
+and, for the gamma distribution case, the canonical link
+\begin{equation}
+g(\sigma^2)=g^{-1}(\sigma^2)=1/\sigma^2 \ .
+\end{equation}
+An example of a systematic component are polynomials $\eta(x)=\beta_0+\sum_{j=1}^{p-1}\beta_j x^j$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \beta_0+\sum_{j=1}^{p-1}\beta_j x^j$.
+Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \cdots, \beta_{p-1}$ given data for the model to fit onto.
+
+Once the parameters have been estimated, prediction of the variance given a grey value $x$ is done using the expectation $\widehat{y}(x) = \expectation\left[Y(x)\right] = g^{-1}(\eta(x))$.
+
+\section{Model Selection}
+
+This section describes how forward stepwise selection \citep{friedman2001elements} was used to select which polynomials to use in the systematic component.
+
+In summary, forward stepwise selection fits a basic model to the data initially.
+A term is added to make the model more complicated at each step to improve the fit onto the data.
+This is continued until the model cannot be improved subject to overfitting.
+The Akaike information criterion (AIC) \citep{friedman2001elements} and the Bayesian information criterion (BIC) \citep{friedman2001elements} are criteria which can be used to assess the fit of the model at each step without overfitting to the data too much.
+
+The AIC and BIC are given as
+\begin{equation}
+\AIC = 2p-2\ln L
+\end{equation}
+and
+\begin{equation}
+\BIC = p\ln m - 2\ln L
+\end{equation}
+respectively where $p$ is the number of terms in the systematic component, $m$ is the size of the data set and $\ln L$ is the log likelihood of the GLM.
+The model with the lowest AIC or BIC is preferred.
+GLM aims to maximise the log likelihood but the additional terms in the criteria penalise models with too many terms.
+The log likelihood is given as
+\begin{equation}
+  \ln L = \sum_{i=1}^m \left[
+    \alpha\ln\alpha
+    -\ln\Gamma(\alpha)
+    -\alpha\ln \widehat{y}_i
+    +(\alpha-1)\ln y_i
+    -\frac{\alpha y_i}{\widehat{y}_i}
+  \right]
+  \ .
+\end{equation}
+where $\widehat{y}_i=\expectation\left[Y(x_i)\right]$. It should be reminded that $\alpha=(n-1)/2$ was assumed to be known and does not need to be estimated.
+
+The procedure is as follows.
+A criterion and a link function is chosen beforehand.
+In the initial step, a GLM with systematic component $\eta(x)=\beta_0$ is fitted and the criterion is recorded.
+In the next step, a polynomial term with one order higher is added to the systematic component $\eta(x)=\beta_0+\beta_1 x$, fitted and the criterion recorded.
+In addition, a polynomial term with one order lower is added $\beta(x)=\beta_{-1}x^{-1}+\beta_0$ and fitted separately with the criterion recorded.
+The model which decreases the criterion the most is accepted.
+Adding higher and lower order polynomials to the systematic component is repeated, for example after accepting $\eta(x)=\beta_0+\beta_1 x$, the following systematic components $\eta(x)=\beta_0+\beta_1 x+\beta_2x^2$ and $\eta(x)=\beta_{-1}x^{-1}+\beta_0+\beta_1 x$ are fitted and assessed.
+This is repeated until the criterion cannot be decreased and the procedure is left with the final model.
+
+Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilterDeg120} and \texttt{AbsFilterDeg120}.
+The procedure was repeated 100 times by using a random permutation with replacement of the replicated projections to work out a different sample variance-mean data which introduces some variation to the data.
+The procedure was also repeated using various shading corrections to investigate the effects of shading correction on the variance-mean relationship.
+
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalcriterion.txt}
+\end{tabular}
+\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilterDeg120}.
+The columns of the table represent different shading corrections used on the projections.
+Forward stepwise selection was repeated 100 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+The row labelled order shows the most common selected polynomial orders.
+The error bars are the standard deviation from the 100 repeats.}
+\label{table:meanVar_glmselect_absnofilter}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalcriterion.txt}
+\end{tabular}
+\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilterDeg120}.
+The columns of the table represent different shading corrections used on the projections.
+Forward stepwise selection was repeated 100 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+The row labelled order shows the most common selected polynomial orders.
+The error bars are the standard deviation from the 100 repeats.}
+\label{table:meanVar_glmselect_absfilter}
+\end{sidewaystable}
+
+The results are shown in Tables \ref{table:meanVar_glmselect_absnofilter} and \ref{table:meanVar_glmselect_absfilter}.
+The models selected all have only two terms and are quite simple.
+Different shading correction or different criteria had no effect on the selected model.
+The method is quite robust to the variation introduced to the dataset when repeating the experiment because all 100 repeats consistently selected the same model.
+
+There was some variation to the selected models between datasets.
+For example when using the identity link, \texttt{AbsNoFilterDeg120} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilterDeg120} prefers $\eta(x)=\beta_{-1}x^{-1}\beta_0$.
+Using the canonical link, both datasets selected $\eta(x)=\beta_{-1}x^{-1}\beta_0$ which correspond to $\widehat{y}(x)=\left(\beta_{-1}x^{-1}+\beta_0\right)^{-1}$.
+Figures \ref{fig:meanVar_varMeanExample_AbsNoFilterDeg120} and \ref{fig:meanVar_varMeanExample_AbsFilterDeg120} shows the GLM fits.
+There is a leverage towards the low grey values because there are more low grey values in the dataset.
+As a result, the GLM does not capture the curvature towards the high grey values.
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_25.eps}
-        \caption{$n=25$}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
+        \caption{$\widehat{y}(x)=\beta_0+\beta_1 x$}
     \end{subfigure}
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_50.eps}
-        \caption{$n=50$}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
+        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$}
     \end{subfigure}
     }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_75.eps}
-        \caption{$n=75$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/sample_size_100.eps}
-        \caption{$n=100$}
-        \label{fig:meanvar_mar16_100}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Mar16} using $n$ of the images.
-Fitted is a Gamma GLM with identity link.
-Error bars represent the $\Phi(\pm1)$ quantile.}
-    \label{fig:meanvar_mar16_differentn}
+    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter}.
+The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
+    \label{fig:meanVar_varMeanExample_AbsNoFilterDeg120}
 \end{figure}
-
-A GLM \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized}, with Gamma distributed response, would then be an appropriate regression to be used.
-Let $Y$ be the grey value sample variance and $X$ be the grey value, then a GLM models $Y$ via the following
-\begin{equation}
-    Y|X \sim 
-    \gammaDist\left(
-        \frac{n-1}{2},
-        f(X)
-    \right)
-\end{equation}
-where $f(X)$ is some user specified function.
-Conventionally it is useful for the specified function to be a parameter of the conditional mean $Y|X$.
-This function is known as the link function and can be expressed as
-\begin{equation}
-g(\mu_X) = \eta(X)
-\end{equation}
-where $\mu_X=\expectation\left[Y|X\right]$ and $\eta(X)$ is a linear function of $X$, for example
-\begin{equation}
-\eta(X) = \beta_0 + \beta_1 X^p \ .
-\end{equation}
-For a specified link function and $p$, the GLM is fitted onto the data by estimating the parameters $\beta_0$ and $\beta_1$.
-
-In this project, the identity, inverse and log link functions were investigated for a selected few integer values of $p$.
-These link functions are shown in Table \ref{table:meanvar_linkfunctions}.
-They are fitted on the variance-mean data from \texttt{Mar16} as shown in Figure \ref{fig:meanvar_mar16}.
-
-\begin{table}
-    \centering
-    \begin{tabular}{c|c|c|c}
-    &\multicolumn{3}{c}{Link functions}\\
-    &Identity&Inverse&Log\\
-    \hline
-    $g(\mu)$&$\mu$&$1/\mu$&$\ln(\mu)$\\
-    \hline
-    $\expectation[Y|X=x]$&$\beta_0 + \beta_1 x^p$&$\left[\beta_0 + \beta_1 x^p\right]^{-1}$&$\exp\left[\beta_0 + \beta_1 x^p\right]$
-    \end{tabular}
-    \caption{Link functions}
-    \label{table:meanvar_linkfunctions}
-\end{table}
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm2.eps}
-        \caption{Inverse link, $p=-1$}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
+        \caption{$\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$}
     \end{subfigure}
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm3.eps}
-        \caption{Inverse link, $p=-2$}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
+        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$}
     \end{subfigure}
     }
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm4.eps}
-        \caption{Log link, $p=1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm5.eps}
-        \caption{Log link, $p=-1$}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the variance-mean data from \texttt{Mar16}.
-Fitted are Gamma GLM with different link functions polynomial features.
-Error bars represent the $\Phi(\pm1)$ quantile.}
-    \label{fig:meanvar_mar16}
+    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter}.
+The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
+    \label{fig:meanVar_varMeanExample_AbsFilterDeg120}
 \end{figure}
-
-\subsection{Kernel Regression}
-
-Kernel regression \citep{friedman2001elements} is a type of non-parametric regression and its prediction is done using a weighted sum of the data rather then fitting a parametric model.
-Suppose a collection of variance-mean data were collected $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$, then the kernel regression is
-\begin{equation}
-    \widehat{y}(x)=
-    \dfrac{
-        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right) y_i
-    }
-    {
-        \sum_{i=1}^m k\left(\dfrac{x-x_i}{\lambda}\right)
-    }
-\end{equation}
-where $k(x)$ is a specified kernel function and $\lambda$ is called the bandwidth. Popular choices for the kernel include the Gaussian kernel \citep{friedman2001elements}
-\begin{equation}
-    k(x)=\phi(x)
-\end{equation}
-and the Epanechnikov kernel \citep{friedman2001elements}
-\begin{equation}
-    k(x) = 
-    \begin{cases}
-        \frac{3}{4}\left(1-x^2\right)& \text{ for } -1<x<1 \\ 
-        0 & \text{ otherwise } 
-    \end{cases}
-    \ .
-\end{equation}
-
-An example of the kernel regression using the Epanechnikov kernel is shown in Figure \ref{fig:meanvar_epanechnikov}.
-It shows the kernel regression fitted onto the \texttt{Mar16} variance-mean data for different values of $\lambda$.
-The bandwidth controls how smooth the kernel regression is.
-Just by observation, $\lambda=1$ is too small because it is capturing the noise whereas $\lambda=10^4$ is too large as it did not captured the general shape of the variance-mean relationship.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm6.eps}
-        \caption{$\lambda=10^0$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm8.eps}
-        \caption{$\lambda=10^2$}
-    \end{subfigure}
-    }
-    \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm9.eps}
-        \caption{$\lambda=10^3$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_Mar16_iShad1_iGlm10.eps}
-        \caption{$\lambda=10^4$}
-    \end{subfigure}
-    }
-    \caption{Epanechnikov kernel regression, with bandwidth $\lambda$, fitted on the variance-mean data from \texttt{Mar16}.}
-    \label{fig:meanvar_epanechnikov}
-\end{figure}
-
-Choosing a good bandwidth can be done using cross validation methods \citep{friedman2001elements} but this can be computationally expensive thus time consuming.
-By eyeballing the figure and choosing a bandwidth which captures a smooth variance-mean relationship, a value of $\lambda=10^3$ was chosen.
-
-\section{Model Selection}
-
-In the previous section, several models for the variance-mean relationship have been described.
-This section will use model selection techniques to access the goodness of fit and prediction performance for each model.
 
@@
 Suppose the variance-mean data consist of the following values $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$ and $\widehat{y}_i$ is the predicted $Y$ given $x_i$, then the log likelihood is
-\begin{equation}
-    \ln L = \sum_{i=1}^m \left[
-        \alpha\ln\alpha
-        -\alpha\ln \widehat{y_i}
-        -\ln\Gamma(\alpha)
-        +(\alpha-1)\ln y_i
-        -\frac{\alpha y_i}{\widehat{y}_i}
-    \right]
-    \ .
-\end{equation}
+
 The log saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ so that

### 2019-07-19 reports/thesis/chapters/4_variancePrediction.tex
Write up varmean

@@
-In the previous chapter, it was found that it is very hard to fit a compound Poisson random variable onto the grey values directly itself.
-It is not totally useless however.
-The compound Poisson model showed that the variance of the grey value has a linear relationship with the mean grey value.
-Given this, it would be possible to predict the variance of the grey value, given the grey value.
-This opens up new ways to predict the uncertainty of each individual pixel in an x-ray scan.
+In the previous chapter, it was found that it was hard to fit a compound Poisson random variable onto the grey values directly itself.
+Results did show that the variance of the grey value has a linear relationship with the mean grey value.
+As a result, it would be possible to predict the variance of the grey value, given the grey value.
+This opens up new ways to predict the uncertainty of each individual pixel in an x-ray projection.
 
-In this chapter, different types of regressions were tested to see if they perform well in predicting grey value variance given the grey value.
-Two types of regressions were used.
-Generalised linear models \citep{nelder1972generalized} \citep{nelder1972generalized_2} \citep{mccullagh1984generalized} (GLM) is a parametric regression which models the response variable as a random variable in the exponential family.
-In this project, a Gamma distributed random variable was chosen as the response variable.
-A non-parametric regression was also considered, here there kernel regression \citep{friedman2001elements} was used.
+In this chapter, generalised linear models \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} with different link functions and polynomial explanatory variables were selected using forward step-wise selection.
+These selected models were compared using cross validation to find the best model.
 
-Using the replicated x-ray images, the within individual pixel sample mean and sample variance were obtained.
-The sample variance-mean data were then used for the regressions to be fitted on.
-The deviance was investigated as a method of model selection.
-The regression was also used to test it's prediction performance on held out images.
-
-In the end, a GLM with a linear relationship between the variance and the mean was good enough.
-Its performance is similar to other complicated models and its simple form attracts those who follows Occam's razor, that the simpler models are usually better.
-The linear relationship is also justified by the compound Poisson model.
-
-\subsection{Generalised Linear Models}
+\section{Generalised Linear Models}
 
 The sample variance-mean data were obtained from the replicated projections.
-Let $x_{x,y}^{(r)}$ be the grey value of the pixel at $(x.y)$ from the $r$th replicate projection for $r=1,2,3,\dotdotdot,n$.
+Let $x_{x,y}^{(r)}$ be the grey value of the pixel at $(x,y)$ from the $r$th replicate projection for $r=1,2,3,\dotdotdot,n$.
 The pixel sample mean is
@@
 It was assumed the standard error from estimating the mean was negligible so that the uncertainty is captured by the random variable $Y$.
-It was assumed that for a given pixel, the grey values are Normally distributed and i.i.d.
+It was assumed that for a given pixel, the grey values are Normal and i.i.d.
 Let $\sigma^2(x)$ be the variance given a grey value $x$, then it can be shown that
@@
 \end{equation}
-where $g(\sigma^2)$ is the link function and $\eta(x)$ is a linear function called the systematic component. It should be noted that
+where $g(y)$ is the link function and $\eta(x)$ is a linear function called the systematic component. It should be noted that
 \begin{equation}
@@
 \begin{equation}
-g(\sigma^2)=g^{-1}(\sigma^2)=\sigma^2
+g(y)=g^{-1}(y)=y
 \end{equation}
@@
 \begin{equation}
-g(\sigma^2)=g^{-1}(\sigma^2)=1/\sigma^2 \ .
+g(y)=g^{-1}(y)=1/y \ .
 \end{equation}
@@
 \end{equation}
-respectively where $p$ is the number of terms in the systematic component, $m$ is the size of the data set and $\ln L$ is the log likelihood of the GLM.
+respectively where $p$ is the number of terms in the systematic component and $\ln L$ is the log likelihood of the GLM.
 The model with the lowest AIC or BIC is preferred.
@@
 \end{equation}
-where $\widehat{y}_i=\expectation\left[Y(x_i)\right]$. It should be reminded that $\alpha=(n-1)/2$ was assumed to be known and does not need to be estimated.
+where $\widehat{y}_i=\widehat{y}(x_i)$. It should be reminded that $\alpha=(n-1)/2$ was assumed to be known and does not need to be estimated.
 
@@
 Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilterDeg120} and \texttt{AbsFilterDeg120}.
-The procedure was repeated 100 times by using a random permutation with replacement of the replicated projections to work out a different sample variance-mean data which introduces some variation to the data.
+The procedure was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data.
 The procedure was also repeated using various shading corrections to investigate the effects of shading correction on the variance-mean relationship.
@@
 There was some variation to the selected models between datasets.
-For example when using the identity link, \texttt{AbsNoFilterDeg120} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilterDeg120} prefers $\eta(x)=\beta_{-1}x^{-1}\beta_0$.
-Using the canonical link, both datasets selected $\eta(x)=\beta_{-1}x^{-1}\beta_0$ which correspond to $\widehat{y}(x)=\left(\beta_{-1}x^{-1}+\beta_0\right)^{-1}$.
+For example when using the identity link, \texttt{AbsNoFilterDeg120} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilterDeg120} prefers $\eta(x)=\beta_{-1}x^{-1}+\beta_0$.
+Using the canonical link, both datasets selected $\eta(x)=\beta_{-1}x^{-1}+\beta_0$ which correspond to $\widehat{y}(x)=\left(\beta_{-1}x^{-1}+\beta_0\right)^{-1}$.
 Figures \ref{fig:meanVar_varMeanExample_AbsNoFilterDeg120} and \ref{fig:meanVar_varMeanExample_AbsFilterDeg120} shows the GLM fits.
@@
     }
-    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter}.
+    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilterDeg120} with linear shading correction.
 The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
@@
     }
-    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter}.
+    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilterDeg120} with linear shading correction.
 The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
@@
 
-\subsection{Deviance}
-The deviance is one way to assess the goodness of fit of the regression on the variance-mean data. The deviance is defined to be
+\section{Cross Validation}
+
+Instead of assessing the model fit using the AIC and BIC, the performance on predicting the variance given a grey value can be assessed using cross validation \citep{friedman2001elements}.
+Cross validation assess the model to make predictions on data it has not seen before.
+This is done by randomly splitting the $m$ data points into two disjoint sets, the training set and the test set.
+It was chosen that the training and test set are of the same size.
+The model is fitted onto the training set.
+Afterwards, the fitted model predict the variances given the grey values in the test set which are compared to the actual variances.
+
+The mean scaled deviance was used to assess the performance of variance prediction. The deviance is defined to be
 \begin{equation}
   D = 2\left(
-        \ln L_s - \ln L    
+    \ln L_\mathrm{s} - \ln L    
   \right)
 \end{equation}
-where $L$ and $L_s$ are the likelihood and saturated likelihood respectively.
-
-Let $\alpha=(n-1)/2$ be the shape parameter.
-Suppose the variance-mean data consist of the following values $\{(y_1,x_1),(y_2,x_2),\dotdotdot,(y_m,x_m)\}$ and $\widehat{y}_i$ is the predicted $Y$ given $x_i$, then the log likelihood is
-
-The log saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ so that
+where $L$ and $L_\mathrm{s}$ are the likelihood and saturated likelihood respectively.  The saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ in the likelihood so that
 \begin{equation}
-    \ln L_s = \sum_{i=1}^m \left[
+  \ln L_\mathrm{s} = \sum_{i=1}^m \left[
     \alpha\ln\alpha
+    -\ln\Gamma(\alpha)
     -\alpha\ln{y_i}
-        -\ln\Gamma(\alpha)
     +(\alpha-1)\ln y_i
@@
 \end{equation}
-Following from this, the deviance is then
+Following from this, the deviance is
 \begin{equation}
@@
 \end{equation}
-The scaled deviance can be obtained by removing the factor of $\alpha$ to get
+The mean scaled deviance is obtained by removing the factor of $\alpha$ and dividing by $m$ to get
 \begin{equation}
-    D^* = 2
+    D_\mathrm{s} = \dfrac{2}{m}
     \sum_{i=1}^m\left[
@@
 \end{equation}
-It is given that $D\sim\chi_{m-2}^2$ which implies that $\expectation\left[D\right]=m-2$.
-Because the GLMs considered here all have 2 parameters with known $\alpha$, the best model is the model with the lowest scaled deviance.
-
-The analysis on the deviance was conducted by fitting GLMs with different link functions and polynomial orders $p$ onto the variance-mean data using all $n=100$ images from \texttt{Mar16}.
-The deviance was then calculated.
-This procedure was done using multiple bootstrap samples \citep{efron1992bootstrap} of the $m$ images to get a sample of scaled deviance.
-
-The resulting 100 bootstrapped scaled deviance are shown in Figure \ref{fig:meanvar_deviance_mar16}.
-The kernel regression was also included.
-The scaled deviance does not vary much from model to model and suggests that the goodness of fit are all very similar.
 
@@
   \centering
-    \includegraphics[width=0.49\textwidth]{../figures/meanVar/GlmDeviance_Mar16_scaled_deviance.eps}
-    \caption{Scaled deviance when fitting Gamma GLM on the variance-mean data from \texttt{Mar16}.}
-    \label{fig:meanvar_deviance_mar16}
+  \includegraphics[width=0.49\textwidth]{../figures/varmean/devianceGraph.eps}
+  \caption{Scaled deviance loss function}
+  \label{fig:meanVar_deviance}
 \end{figure}
 
-In this particular example, $m\approx 1.3\times 10^6$ and $n=100$. Then one would expect the scaled deviance to have values
-\begin{align*}
-    \expectation\left[D^*\right]&=\frac{1}{\alpha}\expectation\left[D\right]
-    \\
-    &=\frac{2}{n-1}\times (m-2)
-    \\
-    &\approx \frac{2}{100-1}\times (1.3\times 10^6-2)
-    \\
-    &\approx 2.6 \times 10^4
-\end{align*}
-which is similar in magnitude but lower compared to the scaled deviances obtained from the bootstrap samples.
-This suggests the shape parameter $\alpha=(n-1)/2$ is too big and perhaps should be smaller.
-The estimation of the shape parameter here is however not too important as it is not used to further calculations.
+The mean scaled deviance is a loss function which increases as $y_i/\widehat{y}_i$ deviates from one, this is shown in Figure \ref{fig:meanVar_deviance} and it should be noted the $x$-axis is in log scale.
+Another way to show this is by letting $r_i = y_i/\widehat{y}_i$ and $d_i = 2\left[r-1-\ln r\right]$ be an element from the sum in the deviance.
+For $r_i\approx 1$, $\ln(r)\approx(r-1)-(r-1)^2/2$ which implies $d_i\approx (r-1)^2$ with minimum at one.
+For $r_i$ deviate greatly from one, the loss function is asymmetric.
+For example a ratio of $r_i=10^1$ has a greater penalty than $r_i=10^{-1}$.
+This means in extreme cases, overestimates are penalised less than underestimates relative to $y_i$.
 
-\subsection{Cross Validation}
+Assuming the model is correct, it is given that $D\sim\chi_{m-p}^2$ which implies that for large $m$,
+\begin{equation}
+\expectation\left[D_\mathrm{s}\right] = \dfrac{1}{\alpha}
+\end{equation}
+and
+\begin{equation}
+\variance\left[D_\mathrm{s}\right] = \dfrac{2}{\alpha^2 m} \ .
+\end{equation}
+Because $\alpha=(n-1)/2$, this shows that the number of replicated projections used to obtain the sample variance-mean data has an influence on the mean scaled deviance.
+This result can be used to estimate $\alpha$ if it is unknown.
 
-Another way to do model selection is cross validation \cite{friedman2001elements}.
-In the \texttt{Mar16} dataset, the 100 images were spilt into 2 equally sized sets called the training set and the test set.
-This produced 2 variance-mean data, one from each set.
-The regression was fitted onto the training set and the training set only.
-
-Prediction using the fitted regression can be accessed.
-This was done by calculating the mean squared error of the prediction of the training set, known as the training error, or the test set, known as the test error.
-
-20 samples of training and test errors were obtained by repeating the analysis using another random allocation of the training and test set.
-The results are shown in Figure \ref{fig:meanvar_mar16mse}.
-Each of the regressions considered all have similar prediction ability with the exception of GLM with log link and $p=1$ which performed significantly worse.
+Cross validation was performed on the datasets \texttt{AbsNoFilterDeg120} and \texttt{AbsFilterDeg120} with various different shading corrections.
+The models selected from forward step-wise selection in the previous section were assessed.
+They are $\widehat{y}(x)=\beta_0+\beta_1 x$ and $\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ using the identity link and $\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ using the canonical link.
+The analysis was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data.
 
@@
   \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_training_MSE.eps}
-        \caption{Training error}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanCv_AbsNoFilterDeg120_testmeanscaleddeviance.eps}
+      \caption{\texttt{AbsNoFilterDeg120}}
   \end{subfigure}
   \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Mar16_test_MSE.eps}
-        \caption{Test error}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanCv_AbsFilterDeg120_testmeanscaleddeviance.eps}
+      \caption{\texttt{AbsFilterDeg120}}
   \end{subfigure}
   }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Mar16}.}
-    \label{fig:meanvar_mar16mse}
+  \caption{Test mean scaled deviance from predicting variances in a test set using a GLM fitted onto a training set.
+The box plot represent the 100 repeats of the analysis by by using a random permutation with replacement of the replicated projections to work out a different sample variance-mean data.}
+  \label{fig:meanVar_varMeanCv}
 \end{figure}
 
-\subsection{Shading Correction}
+The results from the cross validation is shown in Figure \ref{fig:meanVar_varMeanCv}.
+The performance of the three candidate models were very similar.
+One exception is the model $\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ fitted onto the \texttt{AbsNoFilterDeg120} dataset, the mean scaled deviance was significantly larger and this is expected from a model not favoured in the forward step-wise selection in the previous section.
 
-%\begin{figure}
-%	\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_30deg.eps}
-%        \caption{30 deg}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_July16_120deg.eps}
-%        \caption{120 deg}
-%    \end{subfigure}
-%    }
-%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16}. The error bars represent the variance-mean quartiles from the reference images.}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%    \centerline{
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_30deg.eps}
-%        \caption{30 deg}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{../figures/meanVar/meanVarAbsBlock_Sep16_120deg.eps}
-%        \caption{120 deg}
-%    \end{subfigure}
-%    }
-%    \caption{Log frequency density of the within pixel variance-mean data from \texttt{Sep16}. The error bars represent the variance-mean quartiles from the reference images.}
-%\end{figure}
+Shading correction, again, did not had an effect in the analysis.
 
-It was investigated how shading correction affects the variance-mean relationship.
-Figure \ref{fig:meanvar_shadingcorrection_july16_30deg} shows the sample variance-mean for the \texttt{July16 30deg} data with different types of shading correction applied.
-At a quick glance, it appeared the shading correction did not do much to the sample variance-mean data.
-However a closer look at low means showed that shading correction had a particular effect and formed a tighter cluster in the bottom-left of the variance-mean histogram.
-This implied that shading correction made more dark pixels have similar grey values.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad1_iGlm1.eps}
-        \caption{No shading correction}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad2_iGlm1.eps}
-        \caption{BW shading correction}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_30deg_iShad3_iGlm1.eps}
-        \caption{Linear shading correction}
-    \end{subfigure}
-    }
-    \caption{Log frequency density of the within pixel variance-mean data from \texttt{July16 30deg} using different shading corrections.
-Fitted is a Gamma GLM with identity link.
-Error bars represent the $\Phi(\pm1)$ quantile.}
-    \label{fig:meanvar_shadingcorrection_july16_30deg}
-\end{figure}
-
-In this section, the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} were considered.
-These are the only datasets with black, grey and white images which are used in shading correction.
-
-A regression was fitted using all images in each dataset to get the sample variance-mean data.
-The scaled deviance was calculated and repeated using bootstrapped samples of the images to get 100 samples of the scaled deviance.
-These are shown in Figures \ref{fig:meanvar_deviance_july16} and \ref{fig:meanvar_deviance_sep16} for the datasets \texttt{July16} and \texttt{Sep16} respectively.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_30deg_scaled_deviance.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_July16_120deg_scaled_deviance.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{July16}.}
-    \label{fig:meanvar_deviance_july16}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_30deg_scaled_deviance.eps}
-        \caption{30 deg}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmDeviance_Sep16_120deg_scaled_deviance.eps}
-        \caption{120 deg}
-    \end{subfigure}
-    }
-    \caption{Scaled deviance when fitting Gamma GLM on the within pixel variance-mean data from \texttt{Sep16}.}
-    \label{fig:meanvar_deviance_sep16}
-\end{figure}
-
-The scaled deviance did not vary much from model to model and shading correction to another.
-However there was one notable exception in \texttt{July16 120deg} where it appeared the scaled deviance preferred the log link with $p=-2$.
-Figure \ref{fig:meanvar_july16_glm} shows how the curvature of the log link captured the sample variance-mean data.
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm1.eps}
-        \caption{Identity link, $p=1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/MeanVarFit_July16_120deg_iShad1_iGlm3.eps}
-        \caption{Log link, $p=-2$}
-    \end{subfigure}
-    }
-    \caption{Log frequency density graph of the sample variance-mean data from the \texttt{July16 120deg} dataset.}
-    \label{fig:meanvar_july16_glm}
-\end{figure}
-
-Worryingly there appeared to be a significant change in the scaled deviance at different angles in the \texttt{July 16} dataset. This is unexplained.
-
-Another analysis was done by holding out half of the images and assigned it as the test set.
-The remaining images were assigned to be the training set and was used to train different types of regressions.
-The training and test MSE are shown in Figures \ref{fig:meanvar_mse_july16_30deg}, \ref{fig:meanvar_mse_july16_120deg}, \ref{fig:meanvar_mse_sep16_30deg} \& \ref{fig:meanvar_mse_sep16_120deg} for the datasets \texttt{July16 30deg}, \texttt{July16 120deg}, \texttt{Sep16 30deg} and \texttt{Sep16 120deg} respectively.
-
-What is remarkable is how much shading correction improved the training and test MSE, in particular in the \texttt{Sep16} dataset.
-
-\begin{figure}
-\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_30deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 30deg}.}
-    \label{fig:meanvar_mse_july16_30deg}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_July16_120deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{July16 120deg}.}
-    \label{fig:meanvar_mse_july16_120deg}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_30deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 30deg}.}
-    \label{fig:meanvar_mse_sep16_30deg}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_training_MSE.eps}
-        \caption{Training error}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/meanVar/GlmMse_Sep16_120deg_test_MSE.eps}
-        \caption{Test error}
-    \end{subfigure}
-    }
-    \caption{Mean squared error in variance prediction using different regressions on the variance-mean data from \texttt{Sep16 120deg}.}
-    \label{fig:meanvar_mse_sep16_120deg}
-\end{figure}
+From these results, it is recommended that the relationship $\widehat{y}(x)=\beta_0+\beta_1 x$ should be used for its simple form, similar performance to other candidate models and connections to the compound Poisson.
 
 \section{Conclusion}
-Experimentally it was found that a Gamma GLM with identity link and $p=1$ performed just as well with other GLM with different link functions and non-parametric regressions.
-A Gamma GLM with identity link and $p=1$ is essentially a simple linear regression.
-The simple linear regression is attractive as the linear relationship between the variance and mean is backed up by the compound Poisson model of x-ray photon behaviour.
-The simple linear regression is also a good candidate for the variance-mean model to those who prefer simpler models and follows Occam’s razor.
 
-It was also found that shading correction aid in variance prediction. This highlights the important of shading correction and should be applied to images whenever possible.
+It was found that a gamma GLM with relationship $\widehat{y}(x)=\beta_0+\beta_1 x$ using the identity link was a good model.
+The simple linear relationship is attractive because it is justified by the compound Poisson model of x-ray photon behaviour.
+This model is also preferred by those who follows Occam’s razor.
+
+Non-parametric and machine learning methods may be used in the prediction of variance for more flexible models.
+These models are flexible, however, they are slow and are unnecessary in a low dimensional problem with a large number of data points.

### 2019-07-19 varmean/devianceGraph.m

@@ -1,3 +1,9 @@
+%SCRIPT: DEVIANCE GRAPH
+%Plot the mean scaled deviance (gamma) vs ratio of value/prediction
+%
+%y-axis: linear scale
+%x-axis: log scale
+
 clearvars;
 close all;
 
@@ -5,9 +11,10 @@ xPlot = linspace(-1,1,100);
 ratio = 10.^(xPlot);
 yPlot = 2*(ratio - 1 - log(ratio));
 
-figure;
+fig = LatexFigure.sub();
 plot(ratio, yPlot);
 ax = gca;
 ax.XScale = 'log';
 xlabel('$y/\widehat{y}$','Interpreter','latex');
-ylabel('scaled deviance');
+ylabel('mean scaled deviance');
+saveas(fig, fullfile('reports','figures','varmean', strcat(mfilename,'.eps')), 'epsc');

### 2019-07-24 reports/thesis/chapters/3_compoundPoisson.tex
start on compound Poisson chapter

--- 2018-03-20 reports/thesis/chapters/3_compoundPoisson.tex
@@
-In this chapter, the compound Poisson-Gamma distribution is reviewed and studied.
-Firstly methods for evaluating the density of the compound Poisson-Gamma distribution are discussed.
-Approximations such as the Normal approximation or saddlepoint approximation \citep{daniels1954saddlepoint} can be used.
-These approximate densities can be written in closed form.
-Exact methods can be computationally challenging when dealing with the infinite sum but can be done when summing over important terms \citep{dunn2005series}.
-Next, a method for parameter estimation will be proposed here using the EM algorithm \citep{dempster1977maximum}.
-However in the end of the chapter, it will be shown that no unique maximum likelihood estimator exist when certain parameters of the compound Poisson-Gamma distribution gets too large.
-
-\section{Density Evaluation}
-Suppose $X\sim\CPoisson(\lambda,\alpha,\beta)$ and $\lambda,\alpha,\beta>0$ then the p.d.f.~of $X$ is
+The grey value of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the test sample and the scintillator in the detector.
+By modelling using a random variable, the uncertainty can be quantified and considered when conducting inference about any detected defects.
+
+The compound Poisson distribution is studied here because of the compound Poission-like behaviour from the detection of photons.
+It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.)
+\begin{equation}
+  \prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\cdots
+\end{equation}
+where $\lambda>0$ is the Poisson rate parameter.
+Let $U_i$ be some independent and identically distributed (i.i.d.) latent random variables with probability density function (p.d.f.) $p_U(u)$ for $i=1,2,3,\dotdotdot$.
+Let $X$ be a compound Poisson random variable where
+\begin{equation}
+  X|Y = \sum_{i=1}^{Y}U_i \ .
+  \label{eq:compoundPoisson_X|Y}
+\end{equation}
+The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
+\begin{equation}
+  p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0
+  \ .
+\end{equation}
+It should be noted that $X=0$ if and only if $Y=0$ with probability $\prob(X=0)=\euler^{-\lambda}$. Then $X$ has probability mass at $X=0$ and probability density at $X>0$ which results in the p.d.f.
 \begin{equation}
@@
     \delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
-		\euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y & \text{ for } x>0 
+    \sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
   \end{cases}
 \end{equation}
+where $\delta(x)$ is the Dirac delta function.
+
+This chapter starts with a literature review on the compound Poisson distribution, how it is derived from the behaviour of photons, how its likelihood is evaluated and methods for fitting onto data.
+A model was proposed for the pixel's grey values and the expectation-maximization (EM) algorithm was implemented to fit the model onto data.
+It was found that for high photon rate, there were identifiability issues.
+The chapter is concluded on a discussion on why the EM algorithm failed.
+
+\section{Literature Review}
+
+\subsection{Compound Poisson in x-ray detection}
+
+In an x-ray tube, photons are emitted as a Poisson process and each photon has some random energy due to bremsstrahlung and characteristic radiation.
+This shares similarities to the compound Poisson.
+Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$.
+Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\cdots$.
+$U_i$ has p.d.f.~$p_U(u)$.
+The random variables discussed here covers all the latent variables in the compound Poisson.
+
+Photons emitted from the x-ray tube undergo attenuation when propagating through the test sample.
+Assuming no beam hardening, some photons are either absorbed or scattered, making them undetectable.
+Scattered photons may be detected but it is very rare.
+Attenuated photon energy remains unaffected so attenuation decreases the parameter $\lambda$ and the amount it decreases by depends on the attenuation coefficient of the material and the amount of material the x-ray attenuates.
+The parameters of the random variable $U_i$ remains unchanged because the energy of each photon remains the same after attenuation, assuming no beam hardening.
+
+When the photons interact with the scintillator in the detector, they are converted into visible light.
+The visible light photons are then detected and converted into a a grey value.
+A quantum counter set the digital signal to be linear with to the number of photons detected \citep{whiting2006properties}.
+Let $X$ be the grey value observed, then
+\begin{equation}
+X = bY + \epsilon
+\end{equation}
+where $\epsilon\sim\normal(a,\kappa)$, $b$ and $a$ are some constant and $\kappa$ is the variance of electronic noise. In a quantum counter, the mean and variance of the grey value are
+\begin{equation}
+\expectation\left[X\right] = b\lambda + a
+\end{equation}
+and
+\begin{equation}
+\variance\left[X\right] = b^2\lambda + \kappa
+\end{equation}
+respectively. By eliminating $\lambda$
+\begin{equation}
+\variance\left[X\right] = b\expectation\left[X\right]+\kappa-ab \ ,
+\end{equation}
+a linear relationship between the variance and expectation of the grey value is obtained.
+
+An energy integrating detector records the grey value which is linear to the energy detected \citep{whiting2006properties}. The grey value $X$ is
+\begin{equation}
+X|Y = \sum_{i=1}^Y U_i + \epsilon \ .
+\end{equation}
+This is the compound Poisson with Normal noise added to it.
+The scale factor $b$ is not included as this can be absorbed into $U$.
+Using the result that $\expectation\left[X\right]=\expectation\expectation\left[X|Y\right]$ and $\variance\left[X\right] = \variance\expectation\left[X|Y\right] + \expectation\variance\left[X|Y\right]$, the mean and variance of the grey value are
+\begin{equation}
+\expectation\left[X\right] = \lambda\expectation\left[U\right]+a
+\end{equation}
+and
+\begin{equation}
+\variance\left[X\right] = \lambda \expectation\left[U^2\right]+\kappa
+\end{equation}
+respectively. Eliminating $\lambda$ obtains
+\begin{equation}
+\variance\left[X\right] = \dfrac{\expectation\left[U^2\right]}{\expectation\left[U\right]} \expectation\left[X\right] + \kappa - a\dfrac{\expectation\left[U^2\right]}{\expectation\left[U\right]} \ .
+\end{equation}
+By assuming no beam hardening, $\expectation\left[U\right]$ and $\expectation\left[U^2\right]$ remains constant, thus there is a linear relationship between the variance and expectation of the grey value.
+There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
+
+Experiments have been done to verify the compound Poisson nature of the detector.
+This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers.
+It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
+The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.
+
+\subsection{Moment generating function}
+
+Returning back to the compound Poisson with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$. Let the moment generating function (m.g.f.) of $X$ be
+\begin{equation}
+  M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
+  \ .
+\end{equation}
+This can be computed using the result for conditional expectations $M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]$.
+Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
+\begin{align}
+  M_X(\theta)&=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
+  \\
+  &=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
+  \ .
+\end{align}
+But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.~$M_U(\theta)=\expectation\left[\euler^{U\theta}\right]$, then
+\begin{align}
+  M_X(\theta)&=\expectation\left(
+    \expectation\left[\euler^{\theta U_1}|Y\right]\cdot
+    \expectation\left[\euler^{\theta U_2}|Y\right]\cdot
+    \dotdotdot \cdot
+    \expectation\left[\euler^{\theta U_Y}|Y\right]
+  \right)
+  \\
+  &=\expectation\left[\left(M_U(\theta)\right)^Y\right]
+  \\
+  &=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
+  \\
+  & = M_Y\left(\ln(M_U(\theta)\right)
+\end{align}
+where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
+$
+  M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
+  \exp
+  \left[
+    \lambda
+    \left(
+      \euler^\theta-1
+    \right)
+  \right]
+$
+then
+\begin{equation}
+  M_X(\theta)=
+  \exp\left[
+    \lambda
+    \left(
+      M_U(\theta)-1
+    \right)
+  \right]
+  \ .
+\end{equation}
+
+Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
+\begin{align}
+  M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
+  &=M_X(\theta)\lambda M_U'(\theta)
+\end{align}
+then
+\begin{equation}
+  \expectation\left[X\right]=\lambda\expectation\left[U\right]
+  \ .
+\end{equation}
+Conducting the same procedure
+\begin{equation}
+  M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
+  \ ,
+\end{equation}
+the variance can be obtained
+\begin{align}
+  \variance\left[X\right]&=M_X''(0)-\left[M_X'(0)\right]^2
+  \\
+  &=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
+  \\
+  &=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
+\end{align}
+resulting in
+\begin{equation}
+  \variance\left[X\right] = \lambda\expectation\left[U^2\right]
+  \ .
+\end{equation}
+This can be extended for higher moments.
+
+Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$.
+By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.
+
+\subsection{Generalised linear model}
+
+A special case of the compound Poisson is when $U\sim\gammaDist\left(\alpha,\beta\right)$ where $\alpha>0$ is the gamma shape parameter and $\beta>0$ is the gamma rate parameter.
+The special case is used for example in \cite{xu2009electronic}.
+This is known as the compound Poisson-gamma distribution and denoted as $X\sim\CPoisson(\lambda,\alpha,\beta)$ and has p.d.f.
+\begin{equation}
+  p_X(x) = 
+  \begin{cases}
+    \delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
+    \sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
+  \end{cases}
+  \ .
+  \label{eq:compoundPoisson_pdf}
+\end{equation}
+The conditional distribution can be shown to be $X|Y\sim\gammaDist\left(Y\alpha,\beta\right)$.
+
+It can be shown that the compound Poisson-gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}.
+To show this, it is useful to reparametrize the compound Poisson-gamma distribution using the following:
+\begin{equation}
+  p=\frac{2+\alpha}{1+\alpha}
+  \ ,
+\end{equation}
+\begin{equation}
+  \mu=\frac{\lambda\alpha}{\beta}
+  \ ,
+\end{equation}
+\begin{equation}
+  \phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
+  \ .
+\end{equation}
+The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. It can be shown that $1<p<2$, $\mu>0$ and $\phi>0$.
+
+By rearranging the parameters to get
+\begin{equation}
+  \lambda=\frac{\mu^{2-p}}{\phi(2-p)}
+\end{equation}
+\begin{equation}
+  \alpha=\frac{2-p}{p-1}
+\end{equation}
+\begin{equation}
+  \beta=\frac{1}{\phi(p-1)\mu^{p-1}}
+\end{equation}
+and substituting it into Equation \eqref{eq:compoundPoisson_pdf}, the p.m.f.~at zero can be shown to be
+\begin{equation}
+  \prob(X=0) = \exp
+  \left[
+      -\frac{\mu^{2-p}}{\phi(2-p)}
+  \right]
+\end{equation}
+and the p.d.f.~for $x>0$ is
+\begin{multline}
+  p_X(x) = \sum_{y=1}^{\infty}
+  \left[
+    \frac{1}{\phi(p-1)\mu^{p-1}}
+  \right]^{y\alpha}
+  \frac{1}{\Gamma(y\alpha)}
+  x^{y\alpha-1}
+  \exp\left[
+      -\frac{x}{\phi(p-1)\mu^{p-1}}
+  \right]
+  \\
+  \exp\left[
+      -\frac{\mu^{2-p}}{\phi(2-p)}
+  \right]
+  \left[
+    \frac{\mu^{2-p}}{\phi(2-p)}
+  \right]^y
+  \frac{1}{y!}
+  \ .
+\end{multline}
+Tidying up the equation
+\begin{multline}
+  p_X(x) = 
+  \exp\left[
+    \frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)
+  \right]
+  \frac{1}{x}
+  \\
+  \sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+  \ .
+\end{multline}
+To simplify further, it should be noted that $2-p-\alpha(p-1) = 2-p - \frac{2-p}{p-1}(p-1) =0$ so that
+\begin{equation}
+  p_X(x) = 
+  \exp\left[
+    \frac{1}{\phi}
+    \left(
+      x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
+    \right)
+  \right]
+  \frac{1}{x}
+  \sum_{y=1}^{\infty}W_y(x,p,\phi)
+\end{equation}
 where
 \begin{equation}
-	W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
-	\ .
-	\label{eq:compoundPoisson_w}
-\end{equation}
-The evaluation of this p.d.f.~is difficult because the sum of $W_y$ cannot be simplified. However the m.g.f.~of $X$ can be written down in closed form
+  W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+  \ .
+\end{equation}
+This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ or $\alpha$ because the above is in the form of a distribution in the dispersive exponential family.
+Parameter estimation then can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
+These has applications in for example insurance claim data \citep{jorgensen1994fitting, smyth2002fitting}.
+
+Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
+One easy way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
+
+One special property of the compound Poisson-gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}. It has a special variance mean relationship
+\begin{equation}
+  \variance[X] = \phi \mu^p
+\end{equation}
+where, as a reminder, $1<p<2$. This can be derived using the partition function $Z$. Let
+\begin{equation}
+  \theta = \frac{\mu^{1-p}}{1-p}
+\end{equation}
+and
+\begin{equation}
+  \ln Z = \frac{1}{\phi(2-p)\theta^\alpha(1-p)^\alpha} \ ,
+\end{equation}
+then
+\begin{equation}
+  \variance[X] = \phi^2 \frac{\partial^2\ln Z}{\partial\theta^2} \ .
+\end{equation}
+
+\subsection{Method of moments}
+
+The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma random variable. The m.g.f.~of the of $X$ is
+\begin{equation}
+  M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
+\end{equation}
+and moments can be obtained from it such as
+\begin{equation}
+  \expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
+\end{equation}
+\begin{equation}
+  \variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
+  \label{eq:compoundPoisson_variance}
+\end{equation}
+and
+\begin{equation}
+  \expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
+  \ .
+\end{equation}
+
+Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$. Then the estimators
+\begin{equation}
+  \widehat{\lambda}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
+\end{equation}
+\begin{equation}
+  \widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
+\end{equation}
+\begin{equation}
+  \widehat{\beta}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
+\end{equation}
+are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}.
+These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+
+\subsection{Normal approximation}
+
+The evaluation of the density of a compound Poisson-gamma distribution is useful so that the likelihood can be obtained.
+The likelihood then can be used to find, for example, maximum likelihood estimators.
+A problem occurs when dealing with the infinite sum in the p.d.f.~because it cannot be simplified.
+There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
+Monte Carlo methods can be used to evaluate the p.d.f.~by simulating compound Poisson-gamma random variables.
+
+The m.g.f.~of $X$ is
 \begin{equation}
@@
 \end{equation}
-The m.g.f.~allows the study of limiting distributions of the compound Poisson-Gamma distribution.
+It provides a starting point to what limiting distributions the compound Poisson-gamma distribution converges to for large parameters.
 These limiting distributions then can be used to approximate the p.d.f.~of a compound Poisson-Gamma random variable.
-
-The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation  of the m.g.f.~giving the p.d.f.
-However inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}.
-The saddlepoint approximation will be studied here.
-
-Lastly the infinite sum can be computationally summed in a clever way.
-This was done by summing only large terms in the sum and ignores small terms.
-By using Stirling's approximation, the largest term in the sum can be approximately found \citep{dunn2005series}.
-
-\subsection{Normal Approxmation}
-The m.g.f.~provides a starting point to what limiting distributions the compound Poisson-Gamma distribution converges to for large parameters.
-However the m.g.f.~of $X$ itself it not useful because when considering $\lambda\rightarrow\infty$ or $\alpha\rightarrow\infty$ then $M_X(\theta)\rightarrow\infty$.
+The m.g.f.~of $X$ itself it not useful because when considering $\lambda\rightarrow\infty$ or $\alpha\rightarrow\infty$ then $M_X(\theta)\rightarrow\infty$.
 Also for $\beta\rightarrow\infty$, then $M_X(\theta)\rightarrow 1$ which is not useful either.
 
-The compound Poisson-Gamma random variable $X$ should be standardised to obtain useful limiting results from the m.g.f. Let
+The compound Poisson-gamma random variable $X$ can be standardised to obtain useful limiting results from the m.g.f. Let
 \begin{equation}
@@
 then using previous results
-\begin{equation*}
-	Z = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
-	\left(
-		X-\frac{\alpha\lambda}{\beta}
-	\right)
-\end{equation*}
 \begin{equation}
@@
 The m.g.f.~of $Z$ is then
-\begin{equation*}
-	M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=\expectation\left[\euler^{(bX+a)\theta}\right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=\euler^{a\theta}M_X(b\theta)
-	\ .
-\end{equation*}
+\begin{align}
+  M_Z(\theta)&=\expectation\left[\euler^{Z\theta}\right]
+  \\
+  &=\expectation\left[\euler^{(bX+a)\theta}\right]
+  \\
+  &=\euler^{a\theta}M_X(b\theta)
+  \ .
+\end{align}
 Substituting in the values
-\begin{equation*}
-	M_Z(\theta)=
+\begin{align}
+  M_Z(\theta)&=
   \exp\left(
@@
   \right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=
+  \\
+  &=
   \exp\left(
@@
   \right]
-\end{equation*}
+\end{align}
 or in a different form
@@
 Substituting in the binomial expansion
-\begin{equation*}
+\begin{equation}
 	M_Z(\theta)=
@@
 	\ .
-\end{equation*}
+\end{equation}
 Writing in full the $r=1,2$ terms
-\begin{multline*}
+\begin{multline}
 	M_Z(\theta)=
@@
 	\right]
-\end{multline*}
+\end{multline}
 and a term cancels out to get
@@
 \end{equation}
-This should make sense as for high $\lambda$, the Poisson random variable has a high expectation, increasing the number of Gamma random variables in a summation.
+This should make sense as for high $\lambda$, the Poisson random variable has a high expectation, increasing the number of gamma random variables in a summation.
 Increasing the number of terms in a summation will trigger the central limit theorem.
@@
 Next for high $\alpha$, it should be noted that
-\begin{equation*}
+\begin{equation}
   \lim_{\alpha\rightarrow\infty}
@@
   }
-\end{equation*}
+\end{equation}
 so that
@@
 
-\subsection{Normal Approximation - General Case}
-It was shown in certain situations, the compound Poisson-Gamma distribution can be approximated with the Normal distribution. This can be extended to the general compound Poisson.
-
-Let $Y\sim\poisson(\lambda)$ where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be some random variable for i.i.d.~$i=1,2,3,\dotdotdot$ with m.g.f.~$M_U(\theta)$. Let
-\begin{equation}
-	X|Y = \sum_{i=1}^{Y}U_i
-	\ .
-\end{equation}
-
-It can be shown that the m.g.f.~of $X$ is
-\begin{equation}
-	M_X(\theta)=
-	\exp\left[
-		\lambda(M_U(\theta)-1)
-	\right]
-	\ .
-\end{equation}
-As in the compound Poisson-Gamma case, it is useful to standardise $X$ using
-\begin{equation*}
-	Z = \frac{X-\lambda\expectation[U]}{\sqrt{\lambda\expectation[U^2]}}
-\end{equation*}
-\begin{equation}
-	Z = \frac{X}{\sqrt{\lambda\expectation[U^2]}}
-	-\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-	\ .
-\end{equation}
-The m.g.f.~of $Z$ is then
-\begin{equation*}
-	M_Z(\theta)=\expectation\left[\euler^{Z\theta}\right]
-\end{equation*}
-\begin{equation*}
-	M_Z(\theta)=
-	\exp\left[
-	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-	\right]
-	\exp\left[
-	\lambda
-	\left(
-		M_U
-		\left(
-			\frac{\theta}{\sqrt{\lambda\expectation[U^2]}}\right)-1
-		\right)
-	\right]
-\end{equation*}
-
-Taking the Maclaurin series of $M_U(\theta)$
-\begin{equation}
-	M_U(\theta) = 1 + \sum_{r=1}^\infty\frac{\theta^r}{r!}M_U^{(r)}(0)
-	\quad\text{for }\lim_{r\rightarrow\infty}
-	\left\|
-		\frac{\theta}{r+1}\frac{M_U^{(r+1)}(0)}{M_U^{(r)}(0)}
-	\right\|<1
-\end{equation}
-and substituting it into $M_Z(\theta)$
-\begin{equation*}
-	M_Z(\theta)=
-	\exp\left[
-	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-    \right]
-	\exp\left[
-		\lambda\sum_{r=1}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
-	\right]
-	\ .
-\end{equation*}
-Writing out in full the $r=1,2$ terms
-\begin{multline*}
-	M_Z(\theta)=\exp\left[
-	    -\theta\frac{\sqrt{\lambda}\expectation[U]}{\sqrt{\expectation[U^2]}}
-	\right]
-	\exp\left[
-		\theta\frac{\sqrt{\lambda}M_U'(0)}{\sqrt{\expectation[U^2]}}
-		+
-		\frac{\theta^2M_U''(0)}{2\expectation[U^2]}
-	\right.
-	\\+
-	\left.
-		\lambda\sum_{r=3}^\infty\frac{\theta^r}{(\lambda\expectation[U^2])^{r/2}r!}M_U^{(r)}(0)
-	\right]
-	\ .
-\end{multline*}
-By using the fact that $\expectation[U^r]=M_U^{(r)}(0)$ for $r=0,1,2\dotdotdot$, a few terms cancel out to get
-\begin{equation}
-	M_Z(\theta)=
-	\exp\left[
-		\frac{\theta^2}{2}
-		+
-		\sum_{r=3}^\infty\frac{\theta^r \expectation[U^r]}{(\expectation[U^2])^{r/2}r!}\lambda^{1-r/2}
-	\right]
-	\ .
-\end{equation}
-
-For the limit $\lambda\rightarrow\infty$
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}M_Z(\theta) = \exp\left[\frac{\theta^2}{2}\right]
-\end{equation}
-then it can be concluded that
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1)
-	\ .
-\end{equation}
-The convergence can be aided if the ratio $\dfrac{\expectation[U^r]}{(\expectation[U^2])^{r/2}}$ for $r=3,4,5,\dotdotdot$ are small.
-
 \subsection{Saddlepoint approximation}
+
+The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation of the m.g.f.~giving the p.d.f.
+Inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}.
+The saddlepoint approximation will be studied here.
+
 The m.g.f.~of a random variable $X$ is defined to be
@@
 \end{equation}
-For a given m.g.f., the saddlepoint approximation \citep{daniels1954saddlepoint} \citep{butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
+For a given m.g.f., the saddlepoint approximation \citep{daniels1954saddlepoint, butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
 \begin{equation}
@@
 
-For the compound Poisson-Gamma distribution, the saddle point approximation is given as 
+For the compound Poisson-gamma distribution, the saddle point approximation is given as 
 \begin{multline}
@@
 \end{multline}
-It appears the approximation is not well defined for $x=0$.
+The approximation is not well defined for $x=0$.
 
@@
 \subsection{Series Evaluation}
-Evaluation of the p.d.f.~of the compound Poisson-Gamma distribution is difficult because of the infinite sum
+
+The infinite sum can be computationally summed in a clever way.
+This was done by summing only large terms in the sum and ignores small terms.
+By using Stirling's approximation, the largest term in the sum can be approximately found \citep{dunn2005series}.
+The p.d.f.~of the compound Poisson-gamma distribution is difficult because of the infinite sum
 \begin{equation}
@@
 \end{equation}
-Using Stirling's approximation
-\begin{equation}
-	\ln(n!)\approx\ln\Gamma(n)\approx n\ln(n!)-n
-\end{equation}
-then
+Using Stirling's approximation $\ln(n!)\approx\ln\Gamma(n)\approx n\ln(n!)-n$, then
 \begin{equation}
@@
 
-\subsection{Simulation Studies}
+\section{Simulation studies on density evaluation}
 
@@
 \end{figure}
+
+\section{Proposed models}
 
@@
 
-\subsection{Failure Evaluation}
+\section{Failure Evaluation}
 It should be convincing that the EM algorithm failed when the compound-Poisson Gamma random variable starts behaving Normally.

### 2019-07-26 reports/thesis/chapters/3_compoundPoisson.tex
Compound Poisson complete re-write
Histogram class
Re-wrote comparing histogram for compound Poisson, script is in cpHistogram
Change order of text for the compound Poisson chapter
In book.tex, use command for figure size

@@
 
-\subsection{Compound Poisson in x-ray detection}
+\subsection{Compound Poisson in X-ray Detection}
 
@@
 
-\subsection{Moment generating function}
+\subsection{Moment Generating Function}
 
@@
 
-\subsection{Generalised linear model}
+\subsection{Generalised Linear Model}
 
@@
 
-\subsection{Method of moments}
+\subsection{Method of Moments}
 
@@
 
-\subsection{Normal approximation}
+\subsection{Normal Approximation}
 
@@
 
-\subsection{Saddlepoint approximation}
+\subsection{Saddlepoint Approximation}
 
@@
 
-\subsection{Series Evaluation}
+\subsection{Exact Method using Series Evaluation}
 
@@
 
-\section{Simulation studies on density evaluation}
-
-Simulations of a compound Poisson-Gamma random variable were conducted with the aim to compare how well these density evaluations methods perform.
+\section{Simulation Studies on Density Evaluation}
+
+Simulations of a compound Poisson-gamma random variable were conducted with the aim to compare how well these density evaluations methods perform.
 This was done by comparing the evaluated densities with the histogram of simulations and a Q-Q plot.
-The following compound Poisson-Gamma distributions were used in the simulations to capture the variety in the compound Poisson-Gamma family: $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(100,100,1)$.
-
-A few technical details will be stated here.
-The Normal approximation does not support probability mass at $x=0$, but instead has a support of $-\infty<x<\infty$.
-The Normal approximation with $-\infty<x<\infty$ support was used here.
-
-Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$. The saddlepoint approximation was computed up to a constant using
+The following compound Poisson-gamma distributions were used in the simulations to capture the variety in the compound Poisson-gamma family: $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(100,100,1)$.
+
+A few technical problems with the histogram because the compound Poisson has probability mass at zero and probability density for positive numbers.
+To correctly represent the empirical distribution of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers.
+However, the Normal approximation and the saddlepoint approximation does not have support at zero.
+Therefore to compare these approximate densities to the empirical distribution fairly, a histogram containing both zero and positive samples was used when appropriate.
+
+The evaluation of the p.d.f.~using the saddlepoint approximate required a bit of caution to avoid over/underflow problems.
+Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$.
+The saddlepoint approximation was computed up to a constant using
 \begin{equation}
@@
 \end{equation}
-for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant to control over/underflow and it was chosen to be
+for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ was chosen to be
 \begin{equation}
@@
 
-A Q-Q plot is a plot which compares the empirical with the theoretical c.d.f. Let
+A Q-Q plot is a plot which compares the empirical c.d.f.~with the theoretical c.d.f. Let
 \begin{equation}
@@
 \end{equation}
+and
 \begin{equation}
@@
 \end{equation}
-then a Q-Q plot plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$.
+then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$.
 If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin.
-However there is no closed form for $F_X(x)$.
-When using the exact or saddlepoint method, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums.
+For the exact method and the saddlepoint approximate, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums.
 $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
-For the saddlepoint approximation where $x=0$ cannot be evaluated and their exist a zero value in the sample, the lower limit of the numerical integral was chosen, arbitrary, to be
-\begin{equation}
-	\frac{
-		\euler^{-\lambda}\lambda\cdot\text{min}\left(\text{non-zero samples}\right)
-	}
-	{
-		\euler^{-\lambda}(1+\lambda)
-	}
-	\times 0.1
-	\ .
-\end{equation}
-
-For low $\lambda$ (Figures \ref{fig:cp_simulation_1} and \ref{fig:cp_simulation_3}) there is a chance of simulating zeros.
-The Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric.
-The saddlepoint approximation did capture probability mass at zero as shown by an increase in probability density towards zero.
-However in Figure \ref{fig:cp_simulation_3}, the compound Poisson-Gamma distribution looked like a mixture model and the saddlepoint approximation was not flexible enough to capture each individual peak.
-In addition, the Q-Q plots looked quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~at low densities.
-
-As $\lambda$ increased, all 3 density evaluation methods performed quite well.
-In Figure \ref{fig:cp_simulation_2}, the Normal approximation did not quite capture the skewness of the histogram.
-However in Figure \ref{fig:cp_simulation_4} for the Normal looking compound Poisson-Gamma random variable, all methods performed well.
+Because the Normal and saddlepoint approximation does not support zero, the Q-Q plot was omitted for these approximations for large $\lambda$.
+
+When plotting the probability of obtaining a zero or the p.d.f.~for positive values, confidence intervals were plotted as well.
+Consider a bin in a histogram, the confidence intervals were obtained by assuming that the frequency in a bin $\sim\poisson(\text{p.d.f.~evaluated at the bin}\times 1\,000 \times \text{bin width})$.
+
+For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}, \ref{fig:compoundPoisson_histogram_1_100_1}, \ref{fig:compoundPoisson_histogram_approx_1_1_1} and \ref{fig:compoundPoisson_histogram_approx_1_100_1}) there is a chance of simulating zeros.
+For $\lambda = 1$, the Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values.
+The saddlepoint approximation did capture the probability mass at zero as shown by an increase in probability density towards zero.
+For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough them.
+In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation or inversion of the c.d.f.
+
+As $\lambda$ increased, in Figures \ref{fig:compoundPoisson_histogram_10_1_1} and \ref{fig:compoundPoisson_histogram_100_1_1}, all 3 density evaluation methods performed quite well.
+For $\CPoisson(10,1,1)$ in Figure \ref{fig:compoundPoisson_histogram_10_1_1}, the Normal approximation did not quite capture the skewness.
+In Figure \ref{fig:compoundPoisson_histogram_100_1_1}, $\lambda$ was high enough where the compound-Poisson distribution starts to converge to a Normal distribution.
+All methods performed well in this realm.
 
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist1.png}
-        \caption{Histogram - Exact method}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq1.png}
-        \caption{Q-Q plot - Exact method}
-    \end{subfigure}
-    }
+    \begin{subfigure}[b]{\mainSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
+        \caption{Left: Expected and observed frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
+    \end{subfigure}
+    }
+    \vspace{2em}
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist1.png}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq1.png}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist1.png}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq1.png}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{Simulations of $\CPoisson(1,1,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_1}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha1beta1.eps}
+        \caption{Q-Q plot}
+    \end{subfigure}
+    }
+    \caption{1\,000 simulations of a $\CPoisson(1,1,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
+In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
+    \label{fig:compoundPoisson_histogram_1_1_1}
 \end{figure}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist2.png}
-        \caption{Histogram - Exact method}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq2.png}
-        \caption{Q-Q plot - Exact method}
-    \end{subfigure}
-    }
+    \begin{subfigure}[b]{\mainSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
+        \caption{Left: Expected and observed frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
+    \end{subfigure}
+    }
+    \vspace{2em}
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist2.png}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq2.png}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist2.png}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq2.png}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{Simulations of $\CPoisson(10,1,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_2}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha100beta1.eps}
+        \caption{Q-Q plot}
+    \end{subfigure}
+    }
+    \caption{1\,000 simulations of a $\CPoisson(1,100,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
+In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
+    \label{fig:compoundPoisson_histogram_1_100_1}
 \end{figure}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist3.png}
-        \caption{Histogram - Exact method}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq3.png}
-        \caption{Q-Q plot - Exact method}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist3.png}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq3.png}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist3.png}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq3.png}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{Simulations of $\CPoisson(1,100,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_3}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
+        \caption{Normal approximation}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
+        \caption{Saddlepoint approximation}
+    \end{subfigure}
+    }
+    \caption{1\,000 simulations of a $\CPoisson(1,1,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
+In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_approx_1_1_1}
 \end{figure}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_hist4.png}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
+        \caption{Normal approximation}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
+        \caption{Saddlepoint approximation}
+    \end{subfigure}
+    }
+    \caption{1\,000 simulations of a $\CPoisson(1,100,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
+In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_approx_1_100_1}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda10alpha1beta1.eps}
         \caption{Histogram - Exact method}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_qq4.png}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda10alpha1beta1.eps}
         \caption{Q-Q plot - Exact method}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_hist4.png}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda10alpha1beta1.eps}
         \caption{Histogram - Normal approx.}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_norm_qq4.png}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda10alpha1beta1.eps}
         \caption{Q-Q plot - Normal approx.}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_hist4.png}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda10alpha1beta1.eps}
         \caption{Histogram - Saddlepoint approx.}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/cp_saddle_qq4.png}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda10alpha1beta1.eps}
         \caption{Q-Q plot - Saddlepoint approx.}
@@
     }
-    \caption{Simulations of $\CPoisson(100,100,1)$ compared to different density evaluation methods}
-    \label{fig:cp_simulation_4}
+    \caption{1\,000 simulations of a $\CPoisson(10,1,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.
+On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_10_1_1}
 \end{figure}
 
-\section{Proposed models}
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda100alpha100beta1.eps}
+        \caption{Histogram - Exact method}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda100alpha100beta1.eps}
+        \caption{Q-Q plot - Exact method}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda100alpha100beta1.eps}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda100alpha100beta1.eps}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda100alpha100beta1.eps}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda100alpha100beta1.eps}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{1\,000 simulations of a $\CPoisson(100,100,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.
+On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_100_1_1}
+\end{figure}
+
+\section{Proposed Model}
+
+The compound Poisson-gamma distribution can be used to model the grey values of each pixel in a projection.
+Suppose a projection has $m$ pixels and $n$ replicate projections were obtained.
+Let $X_{i,j}$ and $Y_{i,j}$ be the grey value and photon count, respectively, of the $i$th pixel in the $j$th replicate projection.
+
+By assuming no beam hardening, the distribution of the photon does not change with attenuation.
+As a result all pixels will detect photons with identical energy distributions thus $\alpha$ and $\beta$ are the same for all pixels.
+Attenuation does affect the photon count, the more material a photon has to attenuate, the lower the number of detectable photons.
+The amount of attenuation depends on the specific path from the source to a pixel in a detector, so $\lambda_i$ varies from pixel to pixel.
+Electronic Normal noise $\epsilon_{i,j}\sim\normal(a,\kappa)$ may be added as well.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{../figures/compoundpoisson/graphicalModel.eps}
+  \caption{Graphical model of the grey value $X_{i,j}$ for each of the $m$ pixels in the $n$ replicate projections.
+$Y_{i,j}\sim\poisson(\lambda_i)$ is the photon count.
+The grey value has a compound Poisson gamma element $X_{i,j}|Y_{i,j}\sim\gammaDist(Y_{i,j}\alpha,\beta)$ and can be extended by adding electronic noise $\epsilon_{i,j}\sim\normal(a,\kappa)$.}
+  \label{fig:compoundPoisson_graphicalModel}
+\end{figure}
+
+The graphical model in Figure \ref{fig:compoundPoisson_graphicalModel} illustrates how all of these variables link together.
+$a$ and $\kappa$ are unknown parameters but can be estimated beforehand using replicate black images.
+The energy of each photon $U\sim\gammaDist(\alpha,\beta)$ was omitted because the conditional distribution $X|Y\sim\gammaDist(Y\alpha,\beta)$ encapsulates each detected photon energy already.
+
+The model may be simplified by omitting the electronic noise, this can be done by setting $a=0$ and $\kappa=0$.
+The number of pixels can be set to $m=1$ as well.
+The model is well set up for the EM algorithm \citep{dempster1977maximum}.
+If each $Y_{i,j}$ is known, then $\lambda_i$, $\alpha$ and $\beta$ can be estimated using maximum likelihood.
+$Y_{i,j}$ could be estimated if $\lambda_i$, $\alpha$ and $\beta$ are known.
+This problem can be tackled using the EM algorithm.
 

### 2019-07-26 Histogram.m

@@ -1,0 +1,30 @@
+classdef Histogram < handle
+  
+  properties (SetAccess = protected)
+    n; %count for each bin
+    edges; %the border of each bin
+    binWidth; %the width of each bin
+    freqDensity; %freq density of each bin, count / binwidth
+  end
+  
+  methods (Access = public)
+    
+    %CONSTRUCTOR
+    function this = Histogram(X, edges)
+      if nargin == 1
+        [this.n, this.edges] = histcounts(X);
+      elseif nargin == 2
+        [this.n, this.edges] = histcounts(X, edges);
+      end
+      this.binWidth = this.edges(2:end) - this.edges(1:(end-1));
+      this.freqDensity = [0, this.n./this.binWidth, 0];
+    end
+    
+    %METHOD: PLOT
+    function plot(this)
+      stairs([this.edges(1),this.edges], this.freqDensity);
+    end
+    
+  end
+  
+end

### 2019-07-26 compoundpoisson/CompoundPoisson.m

@@ -1,501 +1,504 @@
 classdef CompoundPoisson < handle
-
-    %MEMBER VARIABLES
-    properties
-        lambda; %poisson parameter
-        alpha; %gamma shape parameter
-        beta; %gamma rate parameter
-        phi; %dispersion parameter
-        p; %power index
-        mu; %mean
-        sigma; %standard deviation
-        X; %array of observed compound poisson variables
-        Y; %array of latent poisson variables
-        Y_var; %array of latent poisson variances
-        n; %number of data points
-        n_compound_poisson_term; %maximum number of terms to be calculated in the compound poisson sum
-        
-        
-        compound_poisson_sum_threshold; %negative number
-        %if ln(compound poisson term / biggest compound poisson term) > compound_poisson_sum_threshold
-        %then that term is considered for the compound poisson sum
-        
-        can_support_zero_mass; %boolean, ture if can support probability mass at 0
-        
-        name; %name of this object (for figure saving purposes);
+  
+  %MEMBER VARIABLES
+  properties (SetAccess = protected)
+    lambda; %poisson parameter
+    alpha; %gamma shape parameter
+    beta; %gamma rate parameter
+    phi; %dispersion parameter
+    p; %power index
+    mu; %mean
+    sigma; %standard deviation
+    X; %array of observed compound poisson variables
+    Y; %array of latent poisson variables
+    YVar; %array of latent poisson variances
+    n; %number of data points
+    %maximum number of terms to be calculated in the compound poisson sum
+    nCompoundPoissonTerm = 1E7;
+    
+    compoundPoissonSumThreshold = -37; %negative number
+    %if ln(compound poisson term / biggest compound poisson term) > compoundPoissonSumThreshold
+    %then that term is considered for the compound poisson sum
+    
+    isSupportZeroMass = true; %boolean, ture if can support probability mass at 0
+  end
+  
+  %METHODS
+  methods
+    
+    %CONSTRUCTOR
+    function this = CompoundPoisson()
     end
-
-    %METHODS
-    methods
-        
-        %CONSTRUCTOR
-        %PARAMETERS
-            %X: vector of data
-        function this = CompoundPoisson()
-            %assign member variables
-            this.n_compound_poisson_term = 1E7;
-            this.compound_poisson_sum_threshold = -37;
-            this.can_support_zero_mass = true;
-            this.name = 'cp';
[…]

### 2019-07-26 compoundpoisson/CompoundPoisson_saddle.m

@@ -1,63 +1,0 @@
-%COMPOUND POISSON SADDLEPOINT APPROXIMATION
-%SEE SUPER CLASS COMPOUND POISSON
-    %overrides pdf methods to use saddlepoint approximation
-classdef CompoundPoisson_saddle < CompoundPoisson
-    
-    properties
-    end
-    
-    methods
-        
-        %CONSTRUCTOR
-        function this = CompoundPoisson_saddle()
-            %call superclass
-            this@CompoundPoisson();
-            this.can_support_zero_mass = false;
-            this.name = 'cp_saddle';
-        end
-        
-        %OVERRIDE: GET DENSITY
-        %For a range of the domain and given parameters, return the
-        %saddlepoint density. The normalisation constant was worked out
-        %using the trapezium rule, with n_point - 1 strips
-        %PARAMETERS:
-            %x: row vector, equally spaced out compound poisson random variables
-        %RETURN:
-            %f: row vector of size n_points containing the saddle density for each point
-            %x: row vector of size n_points, linspace(x_min,x_max,n_point)
-        function pdf = getPdf(this,x)
-            %work out the log terms
-            log_terms = sum([-(this.alpha+2)/(2*(this.alpha+1))*log(x);
-                -x*this.beta;
-                (x*this.beta/this.alpha).^(this.alpha/(this.alpha+1))*(this.lambda)^(1/(this.alpha+1))*(this.alpha+1)
-                ]);
-            
-            %k is some constant to control over and under flow
-            k = max(log_terms);
-            %k = this.lambda;
-            
-            %work out the saddle density
-            pdf = exp(log_terms - k);
-
-            %work out the height of the trapziums
-            h = (max(x)-min(x))/(numel(x)-1);
-            %integrate the function
-            area = 0.5*h*(pdf(1)+pdf(end)+2*sum(pdf(2:(end-1))));
-            
-            %normalise the saddle density
-            pdf = pdf/area;
-        end
-        
-        %OVERRIDE: GET LOG DENSITY
-        %PARAMETER:
-            %x: scalar, compound poisson variable
-        %RETURN:
-            %ln_pdf: log density
-        function ln_pdf = getlnpdf(this,x)
-            ln_pdf = log(this.getPdf(x));
-        end
-        
-    end
-    
-end
-

### 2019-07-28 reports/thesis/chapters/3_compoundPoisson.tex
Revise compound Poisson chapter

@@
 The compound Poisson distribution is studied here because of the compound Poission-like behaviour from the detection of photons.
-It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.)
-\begin{equation}
-  \prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\cdots
-\end{equation}
-where $\lambda>0$ is the Poisson rate parameter.
-Let $U_i$ be some independent and identically distributed (i.i.d.) latent random variables with probability density function (p.d.f.) $p_U(u)$ for $i=1,2,3,\dotdotdot$.
+It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.) $\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!}$ for $y=0,1,2,\cdots$, where $\lambda>0$ is the Poisson rate parameter.
+Let $U_i$ be some independent and identically distributed (i.i.d.) latent random variables with probability density function (p.d.f.) $p_U(u)$ for $i=1,2,3,\cdots$.
 Let $X$ be a compound Poisson random variable where
@@
 \end{equation}
-It should be noted that $X=0$ if and only if $Y=0$ with probability $\prob(X=0)=\euler^{-\lambda}$. Then $X$ has probability mass at $X=0$ and probability density at $X>0$ which results in the p.d.f.
+It should be noted that $X=0$ if and only if $Y=0$ with probability $\prob(X=0)=\euler^{-\lambda}$.
+Then $X$ has probability mass at zero and probability density for positive numbers which results in the p.d.f.
 \begin{equation}
@@
 When the photons interact with the scintillator in the detector, they are converted into visible light.
-The visible light photons are then detected and converted into a a grey value.
+The visible light photons are then detected and converted into a digital signal.
 A quantum counter set the digital signal to be linear with to the number of photons detected \citep{whiting2006properties}.
@@
 
-An energy integrating detector records the grey value which is linear to the energy detected \citep{whiting2006properties}. The grey value $X$ is
+An energy integrating detector records the grey value as linear to the energy detected \citep{whiting2006properties}. The grey value $X$ is
 \begin{equation}
@@
 Experiments have been done to verify the compound Poisson nature of the detector.
-This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers.
+This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation, yang2010noise} at different voltages and powers.
 It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
@@
 
-Returning back to the compound Poisson with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$. Let the moment generating function (m.g.f.) of $X$ be
-\begin{equation}
-  M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
-  \ .
-\end{equation}
-This can be computed using the result for conditional expectations $M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]$.
-Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
-\begin{align}
-  M_X(\theta)&=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
-  \\
-  &=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
-  \ .
-\end{align}
-But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.~$M_U(\theta)=\expectation\left[\euler^{U\theta}\right]$, then
-\begin{align}
-  M_X(\theta)&=\expectation\left(
-    \expectation\left[\euler^{\theta U_1}|Y\right]\cdot
-    \expectation\left[\euler^{\theta U_2}|Y\right]\cdot
-    \dotdotdot \cdot
-    \expectation\left[\euler^{\theta U_Y}|Y\right]
-  \right)
-  \\
-  &=\expectation\left[\left(M_U(\theta)\right)^Y\right]
-  \\
-  &=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
-  \\
-  & = M_Y\left(\ln(M_U(\theta)\right)
-\end{align}
-where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
-$
-  M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
-  \exp
-  \left[
-    \lambda
-    \left(
-      \euler^\theta-1
-    \right)
-  \right]
-$
-then
+Returning back to the compound Poisson with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$.
+Let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
+It can be shown that the m.g.f.~is
 \begin{equation}
@@
     \right)
-  \right]
-  \ .
-\end{equation}
-
-Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
+  \right] \ .
+\end{equation}
+The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.
+Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero.
+In other words, $\expectation[X^r]=M_X^{(r)}(\theta)$.
+Then it can be shown that
 \begin{align}
-  M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
-  &=M_X(\theta)\lambda M_U'(\theta)
+  \expectation\left[X\right]&=\lambda\expectation\left[U\right]
+  \\
+  \variance\left[X\right] &= \lambda\expectation\left[U^2\right]
 \end{align}
-then
-\begin{equation}
-  \expectation\left[X\right]=\lambda\expectation\left[U\right]
-  \ .
-\end{equation}
-Conducting the same procedure
-\begin{equation}
-  M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
-  \ ,
-\end{equation}
-the variance can be obtained
-\begin{align}
-  \variance\left[X\right]&=M_X''(0)-\left[M_X'(0)\right]^2
-  \\
-  &=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
-  \\
-  &=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
-\end{align}
-resulting in
-\begin{equation}
-  \variance\left[X\right] = \lambda\expectation\left[U^2\right]
-  \ .
-\end{equation}
-This can be extended for higher moments.
-
-Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$.
-By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.
-
-\subsection{Generalised Linear Model}
+which agrees with the results in the previous section. The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.
+
+\subsection{Compound Poisson-Gamma}
 
 A special case of the compound Poisson is when $U\sim\gammaDist\left(\alpha,\beta\right)$ where $\alpha>0$ is the gamma shape parameter and $\beta>0$ is the gamma rate parameter.
-The special case is used for example in \cite{xu2009electronic}.
-This is known as the compound Poisson-gamma distribution and denoted as $X\sim\CPoisson(\lambda,\alpha,\beta)$ and has p.d.f.
+This was used for example in \cite{xu2009electronic}.
+This is known as the compound Poisson-gamma distribution.
+This is denoted by $X\sim\CPoisson(\lambda,\alpha,\beta)$ and has p.d.f.
 \begin{equation}
@@
 \end{equation}
-The conditional distribution can be shown to be $X|Y\sim\gammaDist\left(Y\alpha,\beta\right)$.
+Recall that $X|Y=\sum_{i=1}^YU_i$ which involves a sum of gamma random variables. It can be shown that
+\begin{equation}
+  X|Y\sim\gammaDist\left(Y\alpha,\beta\right).
+\end{equation}
+
+The m.g.f.~of $U$ is $M_U(\theta) = \left(\dfrac{\beta}{\beta-\alpha}\right)^\alpha$. Then the m.g.f.~of $X$ is
+\begin{equation}
+  M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
+\end{equation}
+and moments can be obtained from it such as
+\begin{equation}
+  \expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
+\end{equation}
+\begin{equation}
+  \variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
+  \label{eq:compoundPoisson_variance}
+\end{equation}
+and
+\begin{equation}
+  \expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
+  \ .
+\end{equation}
+
+\subsection{Generalised Linear Model}
 
 It can be shown that the compound Poisson-gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}.
-To show this, it is useful to reparametrize the compound Poisson-gamma distribution using the following:
+To show this, it is useful to parametrise the compound Poisson-gamma distribution using the following:
 \begin{equation}
@@
 \end{equation}
-The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. It can be shown that $1<p<2$, $\mu>0$ and $\phi>0$.
-
-By rearranging the parameters to get
-\begin{equation}
-  \lambda=\frac{\mu^{2-p}}{\phi(2-p)}
-\end{equation}
-\begin{equation}
-  \alpha=\frac{2-p}{p-1}
-\end{equation}
-\begin{equation}
-  \beta=\frac{1}{\phi(p-1)\mu^{p-1}}
-\end{equation}
-and substituting it into Equation \eqref{eq:compoundPoisson_pdf}, the p.m.f.~at zero can be shown to be
+The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively.
+The parameters take the values of $1<p<2$, $\mu>0$ and $\phi>0$.
+After parametrising, it can be shown that the p.m.f.~at zero is
 \begin{equation}
@@
 and the p.d.f.~for $x>0$ is
-\begin{multline}
-  p_X(x) = \sum_{y=1}^{\infty}
-  \left[
-    \frac{1}{\phi(p-1)\mu^{p-1}}
-  \right]^{y\alpha}
-  \frac{1}{\Gamma(y\alpha)}
-  x^{y\alpha-1}
-  \exp\left[
-      -\frac{x}{\phi(p-1)\mu^{p-1}}
-  \right]
-  \\
-  \exp\left[
-      -\frac{\mu^{2-p}}{\phi(2-p)}
-  \right]
-  \left[
-    \frac{\mu^{2-p}}{\phi(2-p)}
-  \right]^y
-  \frac{1}{y!}
-  \ .
-\end{multline}
-Tidying up the equation
-\begin{multline}
-  p_X(x) = 
-  \exp\left[
-    \frac{1}{\phi}\left(x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}\right)
-  \right]
-  \frac{1}{x}
-  \\
-  \sum_{y=1}^{\infty}\frac{x^{y\alpha}\mu^{y[2-p-\alpha(p-1)]}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-  \ .
-\end{multline}
-To simplify further, it should be noted that $2-p-\alpha(p-1) = 2-p - \frac{2-p}{p-1}(p-1) =0$ so that
 \begin{equation}
@@
 \begin{equation}
-  W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-  \ .
-\end{equation}
+  W_y = W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
+  \ .
+\end{equation}
+The derivation is shown in Appendix \ref{chapter:appendix_tweedie}.
 This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ or $\alpha$ because the above is in the form of a distribution in the dispersive exponential family.
-Parameter estimation then can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
-These has applications in for example insurance claim data \citep{jorgensen1994fitting, smyth2002fitting}.
-
+This has applications in, for example, insurance claim data \citep{jorgensen1994fitting, smyth2002fitting}.
+
+Parameter estimation for fixed $p$ can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
 Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
-One easy way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
-
-One special property of the compound Poisson-gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}. It has a special variance mean relationship
+One way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
+
+One special property of the compound Poisson-gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}.
+It can be shown that it has a special variance mean relationship
 \begin{equation}
@@
 \end{equation}
-where, as a reminder, $1<p<2$. This can be derived using the partition function $Z$. Let
-\begin{equation}
-  \theta = \frac{\mu^{1-p}}{1-p}
-\end{equation}
-and
-\begin{equation}
-  \ln Z = \frac{1}{\phi(2-p)\theta^\alpha(1-p)^\alpha} \ ,
-\end{equation}
-then
-\begin{equation}
-  \variance[X] = \phi^2 \frac{\partial^2\ln Z}{\partial\theta^2} \ .
-\end{equation}
+where $1<p<2$.
+This is derived in Appendix \ref{chapter:appendix_tweedie}.
+It should be noted that this relationship is for fixed $p$.
+This is different from the linear variance mean relationship found at the start of the chapter which was for fixed $\alpha$ from assuming no beam hardening.
 
@@
 
-The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma random variable. The m.g.f.~of the of $X$ is
-\begin{equation}
-  M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
-\end{equation}
-and moments can be obtained from it such as
-\begin{equation}
-  \expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
-\end{equation}
-\begin{equation}
-  \variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
-  \label{eq:compoundPoisson_variance}
-\end{equation}
-and
-\begin{equation}
-  \expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
-  \ .
-\end{equation}
-
-Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$. Then the estimators
+The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma random variable.
+Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
+Then the estimators
 \begin{equation}
@@
 
-The m.g.f.~of $X$ is
-\begin{equation}
-M(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
-\ .
-\end{equation}
-It provides a starting point to what limiting distributions the compound Poisson-gamma distribution converges to for large parameters.
-These limiting distributions then can be used to approximate the p.d.f.~of a compound Poisson-Gamma random variable.
-The m.g.f.~of $X$ itself it not useful because when considering $\lambda\rightarrow\infty$ or $\alpha\rightarrow\infty$ then $M_X(\theta)\rightarrow\infty$.
-Also for $\beta\rightarrow\infty$, then $M_X(\theta)\rightarrow 1$ which is not useful either.
-
-The compound Poisson-gamma random variable $X$ can be standardised to obtain useful limiting results from the m.g.f. Let
-\begin{equation}
-  Z = \frac{X-\expectation[X]}{\sqrt{\variance[X]}}
-  \ ,
-\end{equation}
-then using previous results
-\begin{equation}
-  Z = bX+a
-\end{equation}
-where
-\begin{equation}
-  b = \frac{\beta}{\sqrt{\alpha(\alpha+1)\lambda}}
-\end{equation}
-and
-\begin{equation}
-  a = -\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-  \ .
-\end{equation}
-
-The m.g.f.~of $Z$ is then
-\begin{align}
-  M_Z(\theta)&=\expectation\left[\euler^{Z\theta}\right]
-  \\
-  &=\expectation\left[\euler^{(bX+a)\theta}\right]
-  \\
-  &=\euler^{a\theta}M_X(b\theta)
-  \ .
-\end{align}
-Substituting in the values
-\begin{align}
-  M_Z(\theta)&=
-  \exp\left(
-      -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-  \exp\left[
-    \lambda
-    \left(
-      \left(
-        \frac{\beta}{\beta-\frac{\beta\theta}{\sqrt{\alpha(\alpha+1)\lambda}}}
-      \right)^\alpha
-      -1
-    \right)
-  \right]
-  \\
-  &=
-  \exp\left(
-      -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-  \exp\left[
-    \lambda
-    \left(
-      \left(
-        \frac{\sqrt{\alpha(\alpha+1)\lambda}}{\sqrt{\alpha(\alpha+1)\lambda}-\theta}
-      \right)^\alpha
-      -1
-    \right)
-  \right]
-\end{align}
-or in a different form
-\begin{equation}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\lambda
-		\left(
-			\left(
-				1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}	
-			\right)^{-\alpha}
-			-1
-		\right)
-	\right]
-	\ .
-\end{equation}
-
-The above form is useful so that the binomial expansion can be conducted, that is
-\begin{multline}
-	\left(
-		1-\frac{\theta}{\sqrt{\alpha(\alpha+1)\lambda}}
-	\right)^{-\alpha}
-	=
-	1+
-	\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
-	\\
-	\text{for }\frac{\|\theta\|}{\sqrt{\alpha(\alpha+1)\lambda}}<1 \ .
-\end{multline}
-Substituting in the binomial expansion
-\begin{equation}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\lambda
-		\sum_{r=1}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
-	\right]
-	\ .
-\end{equation}
-Writing in full the $r=1,2$ terms
-\begin{multline}
-	M_Z(\theta)=
-	\exp\left(
-	    -\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-    \right)
-	\exp\left[
-		\theta\sqrt{\frac{\alpha\lambda}{\alpha+1}}
-		+\frac{\theta^2}{2}
-	\right.
-	\\
-	\left.
-		+\lambda\sum_{r=3}^\infty \frac{\theta^r\prod_{s=1}^r(\alpha+s-1)}{(\alpha(\alpha+1)\lambda)^{r/2}r!}
-	\right]
-\end{multline}
-and a term cancels out to get
-\begin{equation}
-	M_Z(\theta)=
-	\exp\left[
-		\frac{\theta^2}{2}
-		+\sum_{r=3}^\infty
-		\frac
-			{\theta^r\prod_{s=1}^r(\alpha+s-1)}
-			{(\alpha(\alpha+1))^{r/2}r!}
-		\lambda^{1-r/2}
-	\right]
-	\ .
-\end{equation}
-
-For large $\lambda$
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}M_Z(\theta)=\exp\left[\frac{\theta^2}{2}\right]
-\end{equation}
-which is the same as the m.g.f.~of a standard Normal variable, therefore
-\begin{equation}
-	\lim_{\lambda\rightarrow\infty}Z\sim\normal(0,1) \ .
-\end{equation}
-This should make sense as for high $\lambda$, the Poisson random variable has a high expectation, increasing the number of gamma random variables in a summation.
-Increasing the number of terms in a summation will trigger the central limit theorem.
-
-Next for high $\alpha$, it should be noted that
-\begin{equation}
-  \lim_{\alpha\rightarrow\infty}
-  \frac{
-    \prod_{s=1}^r(\alpha+s-1)
-  }
-  {
-    \alpha(\alpha+1))^{r/2}
-  }
-  =
-  \frac{
-    \prod_{s=1}^r\alpha
-  }
-  {
-    \alpha^{r}
-  }
-\end{equation}
-so that
-\begin{equation}
-  \lim_{\alpha\rightarrow\infty}
-  \frac{
-    \prod_{s=1}^r(\alpha+s-1)
-  }
-  {
-    (\alpha(\alpha+1))^{r/2}
-  }
-  = 1
-  \ .
-\end{equation}
-As a result
-\begin{equation}
-  \lim_{\alpha\rightarrow\infty}
-  M_Z(\theta)=
-  \exp\left[
-    \frac{\theta^2}{2}
-    +\sum_{r=3}^\infty
-    \frac{\theta^r}{r!}
-    \lambda^{1-r/2}
-  \right]
-  \ .
-\end{equation}
-However this shows that taking the limit $\alpha\rightarrow\infty$ is not enough to get a Normal limiting distribution.
-For a Normal limiting distribution, the limit must be accompanied with the limit $\lambda\rightarrow\infty$, that is
-\begin{equation}
-  \lim_{\lambda\rightarrow\infty}\lim_{\alpha\rightarrow\infty}Z\sim\normal(0,1)
-  \ .
-\end{equation}
-
-Finally it should be noted that $M_Z(\theta)$ is independent of $\beta$. Thus $\beta$ will have no effect on the convergence to a Normal limiting distribution.
-
-The above results justify the use of the approximation
-\begin{equation}
-	X\sim\normal\left(\frac{\lambda\alpha}{\beta},\frac{\lambda\alpha(\alpha+1)}{\beta^2}\right)
-\end{equation}
-for large $\lambda$. The limiting case where $\lambda\rightarrow 0$, $\alpha\rightarrow 0$ and $\beta\rightarrow 0$ will not be discussed here.
+The m.g.f.~provides a starting point to what limiting distributions the compound Poisson-gamma distribution converges to for large parameters.
+These limiting distributions can be used to approximate the p.d.f.~of the compound Poisson-gamma distribution.
+
+It can be shown for large $\lambda$, the Normal approximation is
+\begin{equation}
+  X\sim\normal\left(\frac{\lambda\alpha}{\beta},\frac{\lambda\alpha(\alpha+1)}{\beta^2}\right) \ .
+\end{equation}
+The solution is shown in Appendix \ref{chapter:appendix_normalApproximation}.
 
@@
 
-The m.g.f.~of a random variable $X$ is defined to be
-\begin{equation}
-  M_X(\theta)=\expectation[\euler^{\theta X}]
-  =
-  \int_{-\infty}^{\infty}\euler^{x\theta} p_X(x) \diff x
-  \ .
-\end{equation}
-For a given m.g.f., the saddlepoint approximation \citep{daniels1954saddlepoint, butler2007saddlepoint} finds an approximate $p_X(x)$. The saddlepoint approximation is given as
+For a given m.g.f.~$M_X(\theta)$, the saddlepoint approximation \citep{daniels1954saddlepoint, butler2007saddlepoint} finds an approximate p.d.f.~$p_X(x)$. The saddlepoint approximation is given as
 \begin{equation}
@@
   \\
-  \text{for }x>0 \ .
+  \text{for }x>0
   \label{eq:saddle_point_approx}
 \end{multline}
-The approximation is not well defined for $x=0$.
+with the derivation shown in Appendix \ref{chapter:appendix_saddlepoint}. The approximation is not well defined for $x=0$.
 
@@
 
-For the remainder of this section, it will be shown how the saddlepoint approximation can be algebraically derived.
-First of all the cumulant generating function $K_X(\theta)$ can be obtained from the m.g.f.
-\begin{equation}
-  K_X(\theta) = \lambda
-  \left[
-    \left(\frac{\beta}{\beta-\theta}\right)^\alpha-1
-  \right]
-  \ .
-\end{equation}
-Taking the derivative with respect to $\theta$
-\begin{equation}
-  K_X'(\theta)=\frac{\lambda\alpha\beta^\alpha}{(\beta-\theta)^{\alpha+1}}
-\end{equation}
-and this is known as the saddlepoint equation. The quantity $s=s(x)$ is the solution to the equation $K_X'(s)=x$, that is
-\begin{equation*}
-  \frac{\lambda\alpha\beta^\alpha}{(\beta-s)^{\alpha+1}} = x
-\end{equation*}
-with solution
-\begin{equation}
-  s = \beta - \left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
-  \ .
-\end{equation}
-
-The second derivative of the cumulant generating function is
-\begin{equation}
-  K_X''(\theta)=\frac{\lambda\alpha(\alpha+1)\beta^\alpha}{(\beta-\theta)^{\alpha+2}} \ .
-\end{equation}
-Substituting this and $K_X(\theta)$ into Equation \eqref{eq:saddlePoint:generalSaddlePoint}
-\begin{equation*}
-  p_X(x)\approx
-  \frac{1}{\sqrt{2\pi}}
-  \left[
-    \frac{
-      (\beta-s)^{\alpha+2}
-    }
-    {
-      \lambda\alpha(\alpha+1)\beta^\alpha
-    }
-  \right]^{1/2}
-  \exp\left[
-    \lambda\left(\left(\frac{\beta}{\beta-s}\right)^\alpha-1\right)-sx
-  \right]
-  \ .
-\end{equation*}
-Substituting in $s=s(x)$
-\begin{multline*}
-  p_X(x)\approx
-  \frac{1}{\sqrt{2\pi}}
-  \left[
-    \frac{\left(\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}\right)^{\alpha+2}}{\lambda\alpha(\alpha+1)\beta^\alpha}
-  \right]^{1/2}
-  \\
-  \exp\left[
-    \lambda
-    \left(
-      \left(
-        \frac{\beta}{\beta-\beta+\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}}
-      \right)^\alpha
-      -1
-    \right)
-    -x\left(
-      \beta-\left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{1}{\alpha+1}}
-    \right)
-  \right]
-\end{multline*}
-simplifying further
-\begin{multline*}
-  p_X(x)\approx
-  \frac{1}{\sqrt{2\pi}}
-  \left[
-    \frac{
-      \left(\frac{\lambda\alpha\beta^\alpha}{x}\right)^{\frac{\alpha+2}{\alpha+1}}
-    }
-    {
-      \lambda\alpha(\alpha+1)\beta^\alpha
-    }
-  \right]^{1/2}
-  \\
-  \exp\left[
-    \lambda
-    \left(
-      \beta^\alpha
-      \left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
-      -1
-    \right)
-    -x\beta
-    +(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{1-\frac{1}{\alpha+1}}
-  \right]
-\end{multline*}
-\begin{multline*}
-  p_X(x)\approx
-  \frac{1}{\sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}}
-  \left(\lambda\alpha\beta^\alpha\right)^{\left(\frac{\alpha+2}{\alpha+1}-1\right)/2}
-  \\
-  \exp\left[
-    \lambda\left(
-      \beta^\alpha
-      \left(\frac{x}{\lambda\alpha\beta^\alpha}\right)^{\frac{\alpha}{\alpha+1}}
-      -1
-    \right)
-    -x\beta
-    +(\lambda\alpha\beta^\alpha)^{\frac{1}{\alpha+1}}x^{\frac{\alpha}{\alpha+1}}
-  \right]
-\end{multline*}
-\begin{multline*}
-  p_X(x)\approx
-  \frac{
-    \left(
-      \lambda\alpha\beta^\alpha
-    \right)^{\frac{1}{2(\alpha+1)}}
-  }
-  {
-    \sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
-  } 
-  \\
-  \exp\left[
-    -\lambda
-    -x\beta
-    +x^{\frac{\alpha}{\alpha+1}}
-    \left(
-      \frac{
-        \lambda\beta^\alpha
-      }
-      {
-        \left(\lambda\alpha\beta^\alpha\right)^{\frac{\alpha}{\alpha+1}}
-      }
-      +
-      \left(
-        \lambda\alpha\beta^\alpha
-      \right)^{\frac{1}{\alpha+1}}
-    \right)
-  \right]
-\end{multline*}
-\begin{multline*}
-  p_X(x)\approx
-  \frac{
-    \left(
-      \lambda\alpha\beta^\alpha
-    \right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-  }
-  {
-    \sqrt{2\pi(\alpha+1)}}x^{-\frac{\alpha+2}{2(\alpha+1)}
-  }
-  \euler^{-x\beta}
-  \\
-  \exp\left[
-    x^{\frac{\alpha}{\alpha+1}}
-    \left(
-      (\lambda\beta^\alpha)^{1-\frac{\alpha}{\alpha+1}}\alpha^{-\frac{\alpha}{\alpha+1}}
-      +
-      \left(
-        \lambda\alpha\beta^\alpha
-      \right)^{\frac{1}{\alpha+1}}
-    \right)
-  \right]
-\end{multline*}
-\begin{multline*}
-  p_X(x)\approx
-  \frac{
-    \left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-  }
-  {
-    \sqrt{2\pi(\alpha+1)}
-  }
-  x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
-  \\
-  \exp\left[
-    x^{\frac{\alpha}{\alpha+1}}
-    \left(
-      (\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
-      \alpha^{-\frac{\alpha}{\alpha+1}}
-      +
-      \left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{\alpha+1}}
-    \right)
-  \right]
-\end{multline*}
-\begin{multline*}
-  p_X(x)\approx
-  \frac{
-    \left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-  }
-  {
-    \sqrt{2\pi(\alpha+1)}
-  }
-  x^{-\frac{\alpha+2}{2(\alpha+1)}}\euler^{-x\beta}
-  \\
-  \exp\left[
-    x^{\frac{\alpha}{\alpha+1}}(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}
-    \left(
-      \alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
-    \right)
-  \right]
-  \ .
-\end{multline*}
-
-The expression $\alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}$ can be simplified by putting the two terms over a common denominator
-\begin{align}
-  \alpha^{-\frac{\alpha}{\alpha+1}}+\alpha^{\frac{1}{\alpha+1}}
-  & = \alpha^{\frac{1}{\alpha+1}}+\frac{1}{\alpha^{\frac{\alpha}{\alpha+1}}}
-  \nonumber\\
-  & = \frac{\alpha^{\frac{1}{\alpha+1}}\alpha^{\frac{\alpha}{\alpha+1}}+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
-  \nonumber\\
-  & = \frac{\alpha+1}{\alpha^{\frac{\alpha}{\alpha+1}}}
-\end{align}
-so that
-\begin{equation*}
-p_X(x)\approx
-  \frac{
-    \left(\lambda\alpha\beta^\alpha\right)^{\frac{1}{2(\alpha+1)}}\euler^{-\lambda}
-  }
-  {
-    \sqrt{2\pi(\alpha+1)}
-  }
-  x^{-\frac{\alpha+2}{2(\alpha+1)}}
-  \euler^{-x\beta}
-  \exp\left[
-    x^{\frac{\alpha}{\alpha+1}}
-    \frac{(\lambda\beta^\alpha)^{\frac{1}{\alpha+1}}(\alpha+1)}{\alpha^{\frac{\alpha}{\alpha+1}}}
-  \right]
-  \ .
-\end{equation*}
-
-\subsection{Exact Method using Series Evaluation}
-
-The infinite sum can be computationally summed in a clever way.
-This was done by summing only large terms in the sum and ignores small terms.
-By using Stirling's approximation, the largest term in the sum can be approximately found \citep{dunn2005series}.
-The p.d.f.~of the compound Poisson-gamma distribution is difficult because of the infinite sum
-\begin{equation}
-p_X(x) = 
-  \delta(x) \euler^{-\lambda}
-  +
-  \euler^{-\beta x-\lambda}\frac{1}{x}\sum_{y=1}^{\infty}W_y
-  \quad\text{for }x\geqslant 0
-\end{equation}
-where
-\begin{equation}
-  W_y = \frac{\beta^{y\alpha}\lambda^yx^{y\alpha}}{\Gamma(y\alpha)y!}
-  \ .
-  \label{eq:compoundPoisson_Wy}
-\end{equation}
-$W_y$ can be expressed in a different way using different parameters
-\begin{equation}
-  W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
-\end{equation}
-where
-\begin{equation}
-  p=\frac{2+\alpha}{1+\alpha}
-\end{equation}
-and
-\begin{equation}
-  \phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}} \ .
-\end{equation}
-
+\subsection{Series Evaluation}
+
+The infinite sum, $\sum_{y=1}^\infty W_y$, can be computationally summed in a clever way in order to evaluate the p.d.f.
+This was done by summing only large terms in the sum and ignore small terms \citep{dunn2005series}.
 \cite{dunn2005series} approximated the sum by truncation
@@
 \end{equation}
-where $y_\text{l}<y_{\text{max}}<y_\text{u}$ and $y_{\text{max}}$ is the value of $y$ which maximises $W_y$.
-\cite{dunn2005series} used Stirling's approximation to find $y_{\text{max}}$.
-This was done by treating $W_y$ as a continuous function of $y$ and is differentiable with respect to $y$.
-
-It is easier to differentiate $\ln(W_y)$ where
-\begin{multline*}
-  \ln(W_y) = y\alpha\ln(x)-y(1+\alpha)\ln(\phi)-y\alpha\ln(p-1)\\-y\ln(2-p)-\ln(y!)-\ln\Gamma(y\alpha)
-\end{multline*}
-\begin{equation}
-  \ln(W_y) =
-  y
-  \ln\left(
-    \frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-  \right)
-  -\ln(y!)-\ln\Gamma(y\alpha)
-  \ .
-\end{equation}
-Using Stirling's approximation $\ln(n!)\approx\ln\Gamma(n)\approx n\ln(n!)-n$, then
-\begin{equation}
-  \ln(W_y) \approx
-  y\ln\left(
-    \frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-  \right)
-  -y\ln(y)+y-y\alpha\ln(y\alpha) + y\alpha
-  \ .
-\end{equation}
-Taking the derivative with respect to $y$
-\begin{multline*}
-  \frac{\partial \ln(W_y)}{\partial y} \approx
-  \ln\left(
-    \frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-  \right)
-  -\ln(y)-1+1
-  \\
-  -\alpha\ln(y\alpha)-\alpha+\alpha
-\end{multline*}
-\begin{equation}
-  \frac{\partial \ln(W_y)}{\partial y} \approx
-  \ln\left(
-    \frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)}
-  \right)
-  -\ln(y)
-  -\alpha\ln(y\alpha)
-  \ .
-\end{equation}
-
-Setting the derivative to zero
-\begin{equation*}
-  0 \approx \ln\left(
-    \frac{
-      x^\alpha
-    }
-    {
-      \phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha
-    }
-  \right)
-\end{equation*}
-\begin{equation*}
-  1 \approx 
-  \frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)y_{\text{max}}^{1+\alpha}\alpha^\alpha}
-\end{equation*}
-\begin{equation*}
-  y_{\text{max}}^{1+\alpha} \approx 
-  \frac{x^\alpha}{\phi^{1+\alpha}(p-1)^\alpha(2-p)\alpha^\alpha}
-\end{equation*}
-\begin{equation*}
-  y_{\text{max}} \approx 
-  \frac{1}{\phi}
-  \left(
-    \frac{x}{(p-1)\alpha}
-  \right)^{\frac{\alpha}{1+\alpha}}
-  (2-p)^{\frac{-1}{1+\alpha}}
-  \ .
-\end{equation*}
-This can be simplified using the fact that 
-\begin{equation*}
-  \alpha=\frac{2-p}{p-1}
-  \ ,
-\end{equation*}
-\begin{equation*}
-  \frac{1}{1+\alpha} = p-1
-\end{equation*}
-and
-\begin{equation*}
-  \frac{\alpha}{1+\alpha} = 2-p
-\end{equation*}
-then
-\begin{equation*}
-  y_{\text{max}} \approx 
-  \frac{1}{\phi}
-  \left(
-    \frac{x}{2-p}
-  \right)^{2-p}
-  (2-p)^{1-p}
-\end{equation*}
-and finally
+where $y_\text{l}<y_{\text{max}}<y_\text{u}$ and $y_{\text{max}}$ is the value of $y$ which maximises $W_y$. \cite{dunn2005series} used Stirling's approximation to find that
 \begin{equation}
   y_{\text{max}} \approx \frac{x^{2-p}}{\phi(2-p)}
-  \ .
-\end{equation}
+\end{equation}
+by treating $W_y$ as a continuous and differentiable function of $y$.
+The derivation is shown in \ref{chapter:appendix_compoundPoissonSeries}.
 Because values of $y$ should be a positive integer, it would be appropriate to round the solution to $y_\text{max}$ accordingly
@@
 
-To verify that $y_\text{max}$ is a maximum, the second derivative can be investigated
-\begin{equation}
-  \frac{\partial^2\ln(W_y)}{\partial y^2}
-  \approx
-  -\frac{1}{y}(\alpha+1)
-\end{equation}
-to see that
-\begin{equation}
-  \frac{\partial^2\ln(W_y)}{\partial y^2} < 0 \quad \text{for }y=1,2,3,\dotdotdot
-\end{equation}
-therefore $y_\text{max}$ is a maximum.
-
-Returning back to the truncation of the infinite sum
-\begin{equation}
-  \sum_{y=1}^\infty W_y \approx \sum_{y=y_\text{l}}^{y_\text{u}}W_y
-  \ ,
-\end{equation}
 $y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}.
-To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} and using the following equation
+To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} by using the following equation
 \begin{equation}
@@
 This was done by comparing the evaluated densities with the histogram of simulations and a Q-Q plot.
-The following compound Poisson-gamma distributions were used in the simulations to capture the variety in the compound Poisson-gamma family: $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(100,100,1)$.
-
-A few technical problems with the histogram because the compound Poisson has probability mass at zero and probability density for positive numbers.
+The following compound Poisson-gamma distributions were used in the simulations to capture the variety in the compound Poisson-gamma family: $\CPoisson(1,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(10,1,1)$, $\CPoisson(100,100,1)$.
+Varying $\beta$ is not interesting here as this only scales the random variable.
+
+There were a few technical problems with the histogram because the compound Poisson has probability mass at zero and probability density for positive numbers.
 To correctly represent the empirical distribution of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers.
 However, the Normal approximation and the saddlepoint approximation does not have support at zero.
-Therefore to compare these approximate densities to the empirical distribution fairly, a histogram containing both zero and positive samples was used when appropriate.
+Therefore, to compare these approximate densities to the empirical distribution fairly, a histogram containing both zero and positive samples was used when appropriate.
 
 The evaluation of the p.d.f.~using the saddlepoint approximate required a bit of caution to avoid over/underflow problems.
-Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$.
+Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\cdots,x_n\right\}$.
 The saddlepoint approximation was computed up to a constant using
@@
 \end{equation}
-for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ was chosen to be
+for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant was chosen to be
 \begin{equation}
   k =
-  \max_{i\in\left\{1,2,3,\dotdotdot,n\right\}}
+  \max_{i\in\left\{1,2,3,\cdots,n\right\}}
   \left[
@@
 
-A Q-Q plot is a plot which compares the empirical c.d.f.~with the theoretical c.d.f. Let
+A Q-Q plot is a plot which compares the empirical quantiles with the theoretical quantiles. Let
 \begin{equation}
@@
 \end{equation}
-then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotdotdot,\frac{n-0.5}{n}$.
+then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\cdots,\frac{n-0.5}{n}$.
 If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin.
@@
 $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
-Because the Normal and saddlepoint approximation does not support zero, the Q-Q plot was omitted for these approximations for large $\lambda$.
+Because the Normal and saddlepoint approximation does not support zero, the Q-Q plot was omitted for these approximations for small $\lambda$.
 
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
-        \caption{Left: Expected and observed frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
+        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
-        \caption{Left: Expected and observed frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
+        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
     \end{subfigure}
@@
 
-By assuming no beam hardening, the distribution of the photon does not change with attenuation.
+By assuming no beam hardening, the distribution of the photon energy does not change with attenuation.
 As a result all pixels will detect photons with identical energy distributions thus $\alpha$ and $\beta$ are the same for all pixels.
@@
 The graphical model in Figure \ref{fig:compoundPoisson_graphicalModel} illustrates how all of these variables link together.
-$a$ and $\kappa$ are unknown parameters but can be estimated beforehand using replicate black images.
-The energy of each photon $U\sim\gammaDist(\alpha,\beta)$ was omitted because the conditional distribution $X|Y\sim\gammaDist(Y\alpha,\beta)$ encapsulates each detected photon energy already.
+$a$ and $\kappa$ are unknown parameters but can be estimated beforehand from replicate black images.
+The energy of each photon $U\sim\gammaDist(\alpha,\beta)$ was omitted in the graphical model because the conditional distribution $X|Y\sim\gammaDist(Y\alpha,\beta)$ encapsulates each detected photon energy already.
 
@@
 The number of pixels can be set to $m=1$ as well.
-The model is well set up for the EM algorithm \citep{dempster1977maximum}.
-If each $Y_{i,j}$ is known, then $\lambda_i$, $\alpha$ and $\beta$ can be estimated using maximum likelihood.
-$Y_{i,j}$ could be estimated if $\lambda_i$, $\alpha$ and $\beta$ are known.
-This problem can be tackled using the EM algorithm.
+Parameter estimation can be done using gradient methods because the likelihood of the compound Poisson can be evaluated \citep{dunn2005series}.
+However, the EM algorithm is faster and the model is well set up for it.\citep{dempster1977maximum}.
 
@@
 
-The EM algorithm \citep{dempster1977maximum} will be proposed here as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotdotdot,x_n\right\}$.
-
-A popular method for parameter estimation is the maximum log likelihood method.
-Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively.
-The log likelihood is defined to be
+The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\cdots,x_n\right\}$.
+
+Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log likelihood is defined to be
 \begin{equation*}
@@
     \right)
-	\right]
+  \right] \ .
 \end{multline}
-where $W_y=W_y(\lambda,\alpha,\beta)$ was defined in Equation \eqref{eq:compoundPoisson_w}.
 $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
-The gradient of the log likelihood can be evaluated \citep{dunn2005series} and optimisation can be done using gradient methods.
 
 The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable.
-Let $\left\{Y_1,Y_2,Y_3,\dotdotdot, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\dotdotdot, x_n\right\}$ be measurements of $X|Y$.
+Let $\left\{Y_1,Y_2,Y_3,\cdots, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\cdots, x_n\right\}$ be measurements of $X|Y$.
 Define the joint log likelihood to be
@@
 It will be shown that using some approximations, the E step and M step can be implemented.
-The Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} can also be found by using a few approximations.
+The Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} can also be found by using a few approximations.
 However simulations show that these estimators struggle for high $\lambda$ and it will be shown that this will be the case for all estimators.
@@
 \begin{equation}
-	\prob(Y=y|X=x) = W_y \frac{\euler^{-\lambda-\beta x}}{x}
-\end{equation}
-where $W_y$ is defined in Equation \eqref{eq:compoundPoisson_Wy}.
+  \prob(Y=y|X=x) = W_y \frac{\euler^{-\lambda-\beta x}}{x p_X(x)} \ .
+\end{equation}
 Then the conditional expectation is
@@
 \end{equation}
-It was already established how the denominator can be evaluated \citep{dunn2005series}. A similar method for evaluating the numerator can be obtained by truncating the sum and summing large terms.
+As discussed before, the sum in the denominator can be evaluated using the method by \cite{dunn2005series}.
+A similar method for evaluating the numerator can be obtained by truncating the sum and summing large terms.
 
@@
 \begin{equation}
-	W_y^{(r)} = y^r W_y
+  W_y^{(r)} = y^r W_y \quad \text{for }r=1,2,3,\cdots
 \end{equation}
@@
 \begin{equation}
-	y_i = \frac{\sum_{y=1}^\infty W^{(1)}_y}{\sum_{y=1}^\infty W_y}
-\end{equation}
-and
-\begin{equation}
-	\variance[Y|X=x_i] = \frac{\sum_{y=1}^\infty W^{(2)}_y}{\sum_{y=1}^\infty W_y} - \left(y_i\right)^2
-	\ .
-\end{equation}
-The exponent $r=0,1,2,\dotdotdot$ will be useful in the M step where higher conditional moments are needed.
-The sum can be truncated
+  y_i = \frac{\sum_{y=1}^\infty W^{(1)}_y}{\sum_{y=1}^\infty W_y} \ .
+\end{equation}
+Similarly
+\begin{equation}
+  \zeta_i = \variance[Y|X=x_i] = \frac{\sum_{y=1}^\infty W^{(2)}_y}{\sum_{y=1}^\infty W_y} - \left(y_i\right)^2
+  \ .
+\end{equation}
+The expectation terms, $y_i$ and $\zeta_i$, are evaluated in the M step so that they can be used in the E step. The evaluation can be done by truncating the sum
 \begin{equation}
@@
 \end{equation}
-Keep in mind that $y=1,2,3,\dotdotdot$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
+Keep in mind that $y=1,2,3,\cdots$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
 \begin{equation}
@@
 \end{equation}
-By using such an approximation, the method for evaluating the sum $\sum_{y=1}^\infty W^{(r)}_y$ is almost exactly the same as evaluating the sum $\sum_{y=1}^\infty W_y$, in particular $y_\text{max}$ are the same.
-For a given $r=0,1,2,\dotdotdot$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
+Therefore the maximum of $W_y^{(r)}$ is located at $y_\text{max}$ for all $r=0,1,2,\cdots$.
+The same method of evaluating $W_y$ can be used to evaluate $W_y^{(r)}$.
+For a given $r=0,1,2,\cdots$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
 The limits will be different for different values of $r$.
@@
 \end{multline*}
-\begin{multline*}
+\begin{multline}
   T(\lambda,\alpha,\beta)=
@@
   \right] + c
-\end{multline*}
+\end{multline}
 where $c$ is some constant not dependent on $\lambda$, $\alpha$ or $\beta$.
 
-The conditional expectation $y_i = \expectation[Y_i|X_i=x_i]$ was calculated in the E step. The quantity $\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]$ can be calculated using the approximation
+The conditional expectation $y_i = \expectation[Y_i|X_i=x_i]$ and $\zeta_i = \variance[Y_i|X_i=x_i]$ were calculated beforehand in the E step.
+The quantity $\expectation[\ln\Gamma(Y_i\alpha)|X_i=x_i]$ can be calculated using the approximation
 \begin{equation}
@@
 \end{equation}
-where
-\begin{equation}
-	\zeta_i = \variance[Y_i|X_i=x_i]
-\end{equation}
-calculated in the E step and $\psi$ is the digamma function. The objective function is then
+where $\psi(n)$ is the digamma function. The objective function is then
 \begin{multline}
@@
 
-All the derivatives can be used in the Newton-Raphson iterative update, which is
+All the derivatives can be used in the Newton-Raphson iterative update to update the estimators $\widehat{\alpha}$ and $\widehat{\beta}$. The update is
 \begin{equation}
   \begin{pmatrix}
-		\alpha \\ \beta
+    \widehat{\alpha} \\ \widehat{\beta}
   \end{pmatrix}
@@
   \begin{pmatrix}
-		\alpha \\ \beta
+    \widehat{\alpha} \\ \widehat{\beta}
   \end{pmatrix}
-	\left[
-		\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T
+  -
+  \left[
+    \nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T \left. T \right |_{\alpha = \widehat{\alpha}, \beta=\widehat{\beta}}
   \right]^{-1}
   \left[
-		\nabla_{\alpha,\beta} T
+    \nabla_{\alpha,\beta} \left. T \right |_{\alpha = \widehat{\alpha}, \beta=\widehat{\beta}}
   \right]
@@
 
-The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information} \citep{cramer1946mathematical} from the Fisher's information matrix defined as
+The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} from the Fisher's information matrix defined as
 \begin{equation}
@@
   \right]
-	\ .
-\end{equation}
-The calculation is similar to the derivatives of $T$, so using the same approximations and the fact that $\expectation[Y]=\lambda$, then
+\end{equation}
+where
+\begin{equation}
+  \nabla_{\lambda, \alpha,\beta}=
+  \begin{pmatrix}
+    {\partial}/{\partial \lambda}
+    \\
+    {\partial}/{\partial \alpha}
+    \\
+    {\partial}/{\partial \beta}
+  \end{pmatrix}
+  \ .
+\end{equation}
+The calculation is similar to the derivatives of $T$ using the same approximations.
+Using the fact that $\expectation[Y]=\lambda$ and another approximation $\expectation\left[\psi^{(r)}(\alpha Y)\right]\approx\psi^{(r)}(\alpha \lambda)$, then
 \begin{equation}
@@
 \section{Failure Evaluation}
-It should be convincing that the EM algorithm failed when the compound-Poisson Gamma random variable starts behaving Normally.
+
+It should be convincing that the EM algorithm failed when the compound Poisson-gamma random variable starts behaving Normally.
 In particular in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ are stable while estimates of $\alpha$ and $\beta$ struggled to converge.
-This could be because as the compound-Poisson Gamma random variable approach being Normal, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate and there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$.
-
-One way to see this is to look at the Newton-Raphson step, in the M step, in particular the Hessian matrix $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ for high $\lambda$.
+This could be because as the compound Poisson-gamma random variable approach being Normal, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate and there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$.
+
+\subsection{Determinant of the Hessian}
+
+One investigation is to look at the Newton-Raphson step in the M step, in particular the Hessian matrix $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ for high $\lambda$.
 The elements of the Hessian matrix can be found in Equations \eqref{eq:compoundPoisson:d2tdadb}, \eqref{eq:compoundPoisson:d2td2b} and \eqref{eq:compoundPoisson:d2td2a}.
-The $\dfrac{\partial^2T}{\partial\alpha^2}$ element is
+Recall that
 \begin{multline*}
@@
 \end{multline*}
-For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$. Firstly using Stirling's approximation
+For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$. Firstly, using Stirling's approximation
 \begin{equation}
@@
 \end{align}
-Using the approximations, $\dfrac{\partial^2T}{\partial\alpha^2}$ can be approximated
+$\dfrac{\partial^2T}{\partial\alpha^2}$ can be approximated
 \begin{equation*}
@@
 
-The Hessian matrix is then
+The Hessian matrix is, omitting the $\mathbb{I}(x_i>0)$ term,
 \begin{equation}
@@
   \sum_{i=1}^n
-	\mathbb{I}(x_i>0)
   \begin{pmatrix}
@@
 The determinant of the Hessian matrix is then
-\begin{equation*}
+\begin{align*}
   \|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
-	\approx
+  &\approx
   \left(\sum_{i=1}^n-\frac{\alpha y_i}{\beta^2}\right)
   \left(\sum_{i=1}^n-\frac{y_i}{\alpha}\right) - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)^2
-\end{equation*}
-\begin{equation*}
+  \\
   \|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
-	\approx
+  &\approx
   \left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
    - \left(\sum_{i=1}^n\frac{y_i}{\beta}\right)\left(\sum_{j=1}^n\frac{y_j}{\beta}\right)
-\end{equation*}
-\begin{equation*}
+  \\
   \|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
-	\approx
+  &\approx
   \left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
    - \left(\sum_{i=1}^n\sum_{j=1}^n\frac{y_iy_j}{\beta^2}\right)
-\end{equation*}
+\end{align*}
 to get
@@
 
-Another argument which can be made is to restrict the parameter $\beta$ for a given mean to be
+\subsection{Constrained Objective}
+
+The parameter $\beta$ can be constrained for a given mean to be
 \begin{equation}
@@
 \end{equation}
-and investigate whenever a unique solution to $\dfrac{\partial T}{\partial \alpha} = 0$ can be found for high $\lambda$ and $\alpha$. The constrained objective function is
-\begin{multline*}
+and it was investigated whenever a unique solution to $\dfrac{\partial T}{\partial \alpha} = 0$ can be found for high $\lambda$ and $\alpha$. The constrained objective function is
+\begin{multline}
   T(\lambda,\alpha)
@@
   + c
-\end{multline*}
+\end{multline}
 which can be approximated to
@@
 \end{multline*}
-\begin{multline*}
+\begin{multline}
   T(\lambda,\alpha)=
@@
   \ .
-\end{multline*}
+\end{multline}
 Taking the derivative with respect to $\alpha$
-\begin{equation*}
+\begin{equation}
   \frac{\partial T}{\partial \alpha} =
@@
   \right]
-\end{equation*}
+\end{equation}
 and this is not $\alpha$ dependent, thus there is no solution to $\alpha$.

### 2019-07-29 reports/thesis/chapters/3_compoundPoisson.tex
Compound Poisson chapter

@@
     \delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
-    \sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
+    \displaystyle\sum_{y=1}^{\infty}\dfrac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
   \end{cases}
@@
 The derivation is shown in Appendix \ref{chapter:appendix_tweedie}.
-This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ or $\alpha$ because the above is in the form of a distribution in the dispersive exponential family.
+This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ and $\phi$ because the above is in the form of a distribution in the dispersive exponential family.
 This has applications in, for example, insurance claim data \citep{jorgensen1994fitting, smyth2002fitting}.
@@
 This is derived in Appendix \ref{chapter:appendix_tweedie}.
-It should be noted that this relationship is for fixed $p$.
-This is different from the linear variance mean relationship found at the start of the chapter which was for fixed $\alpha$ from assuming no beam hardening.
+It should be noted that this relationship is for fixed $p$ and $\phi$.
+This is different from the linear variance mean relationship found at the start of the chapter which was for fixed $\alpha$ and $\beta$ from assuming no beam hardening.
 

### 2019-07-29 reports/thesis/chapters/3_compoundPoisson.tex
compound poisson scripts completed

@@
 
-The results for $\CPoisson(1,1,1)$, $\CPoisson(10,1,1)$, $\CPoisson(1,100,1)$ and $\CPoisson(100,100,1)$ are shown in Figures \ref{fig:compoundPoisson_convergence_1}, \ref{fig:compoundPoisson_convergence_2}, \ref{fig:compoundPoisson_convergence_3} and \ref{fig:compoundPoisson_convergence_4} respectively.
-Good performance can be seen for the $\lambda=1$ case with convergence of all 3 parameters within a step or two.
+The results for $\CPoisson(1,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(10,1,1)$ and $\CPoisson(100,100,1)$ are shown in Figures \ref{fig:compoundPoisson_convergence_1}, \ref{fig:compoundPoisson_convergence_2}, \ref{fig:compoundPoisson_convergence_3} and \ref{fig:compoundPoisson_convergence_4} respectively.
+Good performance was observed in the $\lambda=1$ case with convergence of all 3 parameters within a step or two.
 The Cram\'er-Rao lower bound captured the spread of the estimates well.
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lnL.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lnL.eps}
         \caption{Log likelihood}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_lambda.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_alpha.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_alpha.eps}
         \caption{$\alpha$}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_1_beta.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_beta.eps}
         \caption{$\beta$}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lnL.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lnL.eps}
         \caption{Log likelihood}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_lambda.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_alpha.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_alpha.eps}
         \caption{$\alpha$}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_2_beta.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_beta.eps}
         \caption{$\beta$}
@@
     }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
+    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
 The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lnL.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lnL.eps}
         \caption{Log likelihood}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_lambda.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_alpha.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_alpha.eps}
         \caption{$\alpha$}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_3_beta.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_beta.eps}
         \caption{$\beta$}
@@
     }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
+    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
 The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lnL.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lnL.eps}
         \caption{Log likelihood}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_lambda.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_alpha.eps}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_alpha.eps}
         \caption{$\alpha$}
     \end{subfigure}
-        \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/compoundPoisson/convergence_4_beta.eps}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_beta.eps}
         \caption{$\beta$}
@@
 and this is not $\alpha$ dependent, thus there is no solution to $\alpha$.
+
+\subsection{Log Likelihood Plot}
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpLogLikelihoodPlot_CompoundPoissonlambda1alpha1beta1.eps}
+        \caption{$\CPoisson(1,1,1)$}
+    \end{subfigure}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpLogLikelihoodPlot_CompoundPoissonlambda1alpha100beta1.eps}
+        \caption{$\CPoisson(1,100,1)$}
+    \end{subfigure}
+    }
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpLogLikelihoodPlot_CompoundPoissonlambda10alpha1beta1.eps}
+        \caption{$\CPoisson(10,1,1)$}
+    \end{subfigure}
+        \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpLogLikelihoodPlot_CompoundPoissonlambda100alpha100beta1.eps}
+        \caption{$\CPoisson(100,100,1)$}
+    \end{subfigure}
+    }
+    \caption{Log likelihood from a simulation of 100 compound Poisson-gamma random variables. $\lambda$ is fixed at the true value.}
+    \label{fig:compoundPoisson_loglikelihoodplot}
+\end{figure}
+
+The log likelihood, using a simulation of 100 compound Poisson-gamma random variables, are shown in Figure \ref{fig:compoundPoisson_loglikelihoodplot}.
+These plots are concerning because the likelihood appeared not to be convex and there is no unique maxima, surprising in $\lambda=1$ case as well.
+
+It was observed there is a saddle point in the log likelihood for the $\CPoisson(1,100,1)$ case. This is when the log likelihood increases and decreases. This suggest a possibility of a local maxima.
+
+These plots suggest there is no unique maximum likelihood estimator and the EM algorithm would be very sensitive to the starting position, including for small $\lambda$.
+
+\section{Conclusion}
+The compound Poisson-gamma distribution was studied but it was found there were identifiability issues when fitting the model onto simulated data, in particular for high $\lambda$.
+
+XCT is in the realm of high $\lambda$ and this can be shown using back of the envelope calculations.
+Using the properties in the \texttt{AbsNoFilter} dataset, the power and potential difference of the x-ray tube are $P=\SI{36}{\watt}$ and $V=\SI{80}{\kilo\volt}$ respectively.
+The time exposure is $\tau=\SI{708}{\milli\second}$.
+Assume an efficiency of \SI{0.01}{{photon}\,{electron}^{-1}} and the charge per electron is $e=\SI{1.602e-19}{\coulomb\,{electron}^{-1}}$.
+Assume the photons projected onto the array of $2\,000^2\,\si{\pixel}$.
+The number of photons detected per pixel is
+\begin{align*}
+\lambda &\approx \dfrac{\text{efficiency} P \tau}{\text{number of pixels} V e}
+\\
+&\sim 10^7\,\si{{photon}\,\pixel^{-1}}
+\ .
+\end{align*}
+Fitting the compound Poisson model onto XCT data would not be possible with such a high value of $\lambda$.
+
+All is not lost though, it was found there was a linear relationship between the variance and mean of the grey value in a pixel.
+This suggest the uncertainty can be predicted by using such a relationship.
+The next chapter investigates this.

### 2019-07-29 compoundpoisson/CompoundPoisson.m

@@ -69,6 +69,12 @@ classdef CompoundPoisson < handle
       this.sigma = sqrt(this.phi * this.mu^this.p);
     end
     
+    %METHODS: SET N
+    %Set the number of data, this is required to evaluate the Fisher's information matrix
+    function setN(this, n)
+      this.n = n;
+    end
+    
     %METHOD: GET DENSITY
     %PARAMETER:
       %x: vector of compound Poisson variables
@@ -119,6 +125,7 @@ classdef CompoundPoisson < handle
     
     %METHOD: GET FISHER'S INFORMATION MATRIX
     %Returns the Fisher's information matrix (using the joint log likelihood)
+    %NOTE: this.n needs to be set, call the method setN to do this
     function I = getFisherInformation(this)
       
       %declare 3 x 3 matrix

### 2019-07-29 compoundpoisson/cpQQDensity.m

@@ -1,117 +1,0 @@
-%FUNCTION: COMPOUND POISSON QQ PLOT FOR DENSITIES
-%Plots histograms of simulations and pdf (exact or approximate)
-%Plots qq plot, simulated quantiles (p) vs theoretical quantiles (p) for an array of p
-%PARAMETERS:
-    %compound_poisson: CompoundPoisson object, contains simulated data
-    %histo_file: directory to save histogram figure
-    %qq_file: directory to save the qq figure
-function cpQQDensity(compound_poisson, histo_file, qq_file)
-
-    %number of points when plotting densities
-    n_linspace = 500;
-    %number of trapeziums to be used
-    n_trapezium = 10000;
-
-    %% SET UP
-
-    %get data from compound poisson object
-    X = compound_poisson.X;
-    
-    %get the index of data points with the value 0
-    n = compound_poisson.n;
-    zero_index = (X==0);
-    %get the number of zeros
-    n_0 = sum(zero_index);
-    %get non-zero data
-    X_no_0 = X(~zero_index);
-
-    %get an array of xs, equally spaced out across the range of the observed simulated data
-    x_array = linspace(min(X),max(X),n_linspace);
-    %if the minimum of the data is 0, remove it
-    if x_array(1)==0
-        x_array(1) = [];
-    end
-    
-    %get the pdf and mass at 0
-    pdf_range = compound_poisson.getPdf(x_array);
-    if compound_poisson.isSupportZeroMass
-        p_0 = compound_poisson.getPdf(0);
-    end
-
-    %% DENSITY
-    
-    fig = LatexFigure.sub();
-    
-    %plot the histogram (frequency density axis on the left)
-    %do not include zeros if support zero mass
-    if compound_poisson.isSupportZeroMass
-        if (n_0~=0)
-            yyaxis left;
-        end
-        h = histogram(X_no_0,'Normalization','CountDensity');
-    else
-        h = histogram(X,'Normalization','CountDensity');
-    end
-    hold on;
-    %plot the pdf
-    plot(x_array,pdf_range*(n),'r-');
-    ylabel('freq. density');
-    
-    %if this density can support zero mass and there are zeros
-    if compound_poisson.isSupportZeroMass && (n_0~=0)
-        %plot the zero frequency for both the simulation and the pmf (frequency axis on the right)
-        yyaxis right;
[…]

### 2019-07-29 reports/thesis/chapters/3_compoundPoisson.tex
Add citations to compound Poisson

@@
 
-The compound Poisson distribution is studied here because of the compound Poission-like behaviour from the detection of photons.
+The compound Poisson distribution is studied here because of the compound Poission-like behaviour from the detection of photons \citep{whiting2002signal, elbakri2003efficient, whiting2006properties}.
 It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.) $\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!}$ for $y=0,1,2,\cdots$, where $\lambda>0$ is the Poisson rate parameter.
@@
 Assuming no beam hardening, some photons are either absorbed or scattered, making them undetectable.
-Scattered photons may be detected but it is very rare.
+Scattered photons may be detected but it is very rare \citep{cantatore2011introduction}.
 Attenuated photon energy remains unaffected so attenuation decreases the parameter $\lambda$ and the amount it decreases by depends on the attenuation coefficient of the material and the amount of material the x-ray attenuates.
@@
 \end{equation}
-a linear relationship between the variance and expectation of the grey value is obtained.
+a linear relationship between the variance and expectation of the grey value \citep{ma2012varaince} is obtained.
 
@@
 \end{equation}
-By assuming no beam hardening, $\expectation\left[U\right]$ and $\expectation\left[U^2\right]$ remains constant, thus there is a linear relationship between the variance and expectation of the grey value.
+By assuming no beam hardening, $\expectation\left[U\right]$ and $\expectation\left[U^2\right]$ remains constant, thus there is a linear relationship between the variance and expectation of the grey value \citep{yang2009evaluation}.
 There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
@@
     \right)
-  \right] \ .
-\end{equation}
+  \right]
+\end{equation}
+\citep{gatto2010saddlepoint}.
 The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.
@@
 
-It can be shown for large $\lambda$, the Normal approximation is
+It can be shown for large $\lambda$, the Normal approximation \citep{shevtsova2014on} is
 \begin{equation}
@@
 
-For the compound Poisson-gamma distribution, the saddle point approximation is given as 
+For the compound Poisson-gamma distribution, the saddle point approximation \citep{jensen1991saddlepoint} is given as 
 \begin{multline}
@@
 The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\cdots,x_n\right\}$.
+The use of the EM algorithm here for the compound Poisson is similar to \cite{elbakri2003statistical, xu2009electronic}.
 

### 2019-07-30 reports/thesis/chapters/1_literatureReview.tex
Revise lit review

@@
 
-X-ray computed tomography (XCT) can be used as a non-destructive test for additive manufactured objects, this is the main theme of this thesis.
-Various reviews on additive manufacturing exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}.
+X-ray computed tomography (XCT) can be used as a non-destructive test for AM products, this is the main theme of this thesis.
+Various reviews on AM exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}.
 For XCT used in manufacturing, there are \cite{cantatore2011introduction, kruth2011computed, sun2012overview}.
@@
 Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer.
-Typically this is a slow and expensive method compared to destructive methods such as drilling and cutting for example.
+Typically this is a slow and expensive method compared to destructive methods such as computer numerical control (CNC) machining for example.
 However, this is not the full picture.
@@
 The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.
-In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.0001 inches (\SI{0.003}{\milli\metre}).
+In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).
 
@@
 
-The blueprint of the object to be manufactured is called a computer-aided design (CAD).
-For it to be processed by an AM apparatus, the CAD is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of a series of triangles, an example is shown in Figure \ref{fig:literature_stl}.
+The blueprint of the object to be manufactured is called a computer-aided design (CAD) model.
+For it to be processed by an AM apparatus, the CAD model is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of a series of triangles, an example is shown in Figure \ref{fig:literature_stl}.
 STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}.
-Some accuracy is lost here as the surface of the CAD is represented approximately by triangles \citep{gibson2010additive}.
+Some accuracy is lost here as the surface of the CAD model is represented approximately by triangles \citep{gibson2010additive}.
 The STL file is then sliced into layers \citep{jamieson1995direct, vatani2009enhanced} so that the AM apparatus knows what to build for each layer.
@@
   \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
-  \caption{An example of a CAD (left) converted to a STL file (right). Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
+  \caption{An example of a CAD model (left) converted to a STL file (right). Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
   \label{fig:literature_stl}
@@
 For example sanding may be done to smooth the surfaces \citep{gibson2010additive}.
-The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
 
@@
 
-\subsection{Online Inspection and Defects}
+\subsection{Defects and Quality Control}
 
-The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}.
-The idea is that problems in the manufacturing are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
-
-There are various discontinuities in AM, in particular in the manufacturing of metal parts \citep{everton2016review}.
+There are various discontinuities in AM.
+In FDM, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}.
+Internal voids can be formed due to insufficient material flow \citep{weeren1995quality}.
+Other factors which can cause defects include misalignment of the platform or nozzle, depletion of material and lack of adhesion due to low temperatures \citep{gunaydin2018common}.
+There are also problems in the manufacturing of metal parts \citep{everton2016review}.
 For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}, they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}.
@@
 
+The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}.
+The idea is that problems in the manufacturing are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
 Various methods are used for in-situ process monitoring.
@@
 The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a bed.
-An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating the patient using different paths.
+An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient using different paths.
 X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}.
 To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}.
-These multiple x-ray readings or images can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}.
+These multiple x-ray readings can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}.
 This is illustrated in Figure \ref{fig:literature_medicalct}.
@@
 
-Higher power x-rays can be used in XCT for the purpose of manufacturing and metrology because there is no consequence of the manufactured object being scanned absorbing the radiation.
+High power x-rays can be used in XCT for the purpose of manufacturing and metrology because there is no consequence of the manufactured object absorbing the radiation.
 The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
-X-ray images are taken while the object rotates.
+X-ray projections are taken while the object rotates.
 Typically the x-ray is a cone beam \citep{kruth2011computed}.
@@
 The electrons can interact with the anode in a number of ways.
-The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material, the energy lost by the electrons is emitted as bremsstrahlung radiation.
-The energy of the bremsstrahlung radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}.
+The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material.
+The energy lost by the electrons is emitted as bremsstrahlung radiation.
+It depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}.
 Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it.
@@
 
-Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process.
+Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process \citep{cierniak2011x}.
 The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode.
@@
 
-The object being scanned are exposed to x-ray photons in XCT.
-X-ray photons undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}.
+The scanned object are exposed to x-ray photons which undergoes attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}.
 The object can absorb the photons via the photoelectric effect.
 In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}.
-Photons can be scattered by the object by colliding inelastically with and transfers its energy to the an electron.
+Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron.
 This process is known as Compton scattering \citep{compton1923quantum}.
@@
 The detectors used in XCT are typically flat bed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes.
-The x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}.
-The visible light is detected by photodiodes and coverts it into an electrical signal.
-The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{whiting2006properties, kruth2011computed}.
+The x-ray photons interact with the scintiallator material and produce visible light pluses \citep{rossner1993conversion}.
+These pulses are detected by photodiodes and converted into an electrical signal \citep{nikl2006scintillation, ren2018tutorial}.
+The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{nikl2006scintillation, whiting2006properties, kruth2011computed, ren2018tutorial}.
 The electrical signals are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}.
+This image is known as a projection.
 
-Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected.
-The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.
+Not all of the visible light pulses are detected by the photodiodes, thus not all the x-ray photons are detected.
+The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}.
 The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
 
-Once multiple x-ray images of the object have been acquired at multiple angles, the reconstruction process can start.
-The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray images.
-It should be reminded that the x-ray images are based on the line integral of the attenuation coefficient along the path of photons.
+Once multiple projections of the object have been acquired at multiple angles, the reconstruction process can start.
+The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray projections.
+This is done using the fact that the projections are based on the line integral of the attenuation coefficient along the path of photons.
 This problem was formed by \cite{radon1986on} as the `determination of functions from their integral values along certain manifolds'.
@@
 XCT can be used to measure the length of the object, making it useful for measuring AM objects internally and externally.
-\emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.
+\emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.
 
@@
 The set up of XCT has a number of variables.
-The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray image.
+The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray projection.
 The exposure time is also a factor.
@@
 Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}.
-Blurry results from larger spot sizes, this is know as the penumbra effect \citep{kueh2016modelling}.
+Larger spot sizes cause more blurry results, this is known as the penumbra effect \citep{kueh2016modelling}.
 However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.
@@
   \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
-  \caption{A reconstruction when scanning three aligned balls using a different number of angles. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
+  \caption{A reconstruction when scanning three aligned balls using a different number angular projections. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
   \label{fig:literature_angles}
@@
 Problems can occur in the detector.
-For examples pixels in the acquired x-ray can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can appear \citep{yang2009evaluation}.
-Spatially correlated noise can be observed as well \citep{sun2016characterisation}.
+For examples pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
+Spatially correlated noise within a projection can be observed \citep{sun2016characterisation} as well as correlation between acquisitions, this is known as image lag \citep{yang2009evaluation}.
+Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.
 
@@
 This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.
+The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}.
+Accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
 
-The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}.
-However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
-The strength of XCT comes from the fact that the location of the pores can be visualised, for example in Figure \ref{fig:literature_pores3D}, and compared to the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+An advantage of XCT is that the location of the pores can be visualised, for example in Figure \ref{fig:literature_pores3D}, and compared to the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
 Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}.
-\cite{leuders2015fatigue} pointed out that the location of the pores is an important factor.
-In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.
+The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}.
+In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD model and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.
 
@@
     \end{subfigure}
-    \caption{The reconstruction was aligned and compared to the CAD.
+    \caption{The reconstruction was aligned and compared to the CAD model.
 The surface heat map shows the surface deviation (or `variance' in the literature) externally (a) and internally (b).
@@
 One of the disadvantages of XCT is that it is a slow process.
-Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar.
+XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control.
 The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}.
@@
 This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}.
-X-ray images at fewer angles can be taken but they can be obtained in one acquisition, speeding up the process.
+Fewer angular projections were taken but they can be obtained in one go, speeding up the process.
 
@@
 
-Instead of reconstructing the object, the analysis can be done on the x-ray images itself, or projection space, by comparing it to a simulation such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+Instead of reconstructing the object, the analysis can be done on the projections itself, or in projection space, by comparing it to a simulated projection produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
 \cite{brierley2018optimized} developed an algorithm to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition.
 It is however very complicated as it is optimising over a very large dimensional space.
-\cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulations with each other, one with defects and the other without.
-It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.
+\cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without.
+Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.
+
+It is however inevitable that accuracy is lost from the jump from reconstruction space to projection space, for example, a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.

### 2019-08-01 reports/thesis/chapters/2_dataCollection.tex
Data collection chapter
Wrote chapter
Added ShadingCorrectionAnovaAbsFilter

@@
+The objective of this thesis is to investigate if voids can be detected using a single projection.
 An experiment was conducted where a test sample was additively manufactured with purposely designed voids.
-The objective is to see if the voids can be detected using a single projection.
 This was done by comparing a projection of the test sample with the simulation of that projection as if the voids were not there.
@@
 This chapter describes the apparatus used to manufacture the test sample and obtaining the projections.
-There is also a discussion, at the end of the chapter, on shading correction which was used to remove detector panel and x-ray spot effects from the projections.
+There is also a discussion, at the end of the chapter, on shading correction which was used to remove panel and x-ray spot effects from the projections.
 
@@
   \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
-  \caption{CAD of the test object; the scale shown is approximate.}
+  \caption{CAD model of the test sample; the scale shown is approximate.}
   \label{fig:inference_testObject}
@@
 X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector.
-The target material in the x-ray source is tungsten.
-The sensor in the detector is made up of 2 rows and 16 columns of panels.
-The sensor has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produced a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
+The target material in the x-ray tube is tungsten.
+The detector is made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produce a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
 Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$.
 The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects.
-The gain and offset were adjusted by the engineers to produce a projection with good contrast, each pixel then has a grey value in units of analogue to digital units (\SI{}{\adu}).
+The gain and offset were adjusted by the engineers to produce a projection with good contrast and with negligible penumbra effect.
+Each pixel has a grey value in units of analogue to digital units (\SI{}{\adu}).
 
@@
 The greyscale projection with the x-ray turned off is called the black image.
-The greyscale projection with the x-ray set up the same when obtaining the test object projection is called the white image.
+The greyscale projection with the x-ray set up the same when obtaining the test sample projection is called the white image.
 
-Replicate test object projections and greyscale projections were obtained by repeating the acquisition. These replicated projections were used to study the noise observed in the projections.
+Replicate test sample projections and greyscale projections were obtained by repeating the acquisition. These replicated projections were used to study the noise observed in the projections.
 
-Filters used to tackle beam hardening were used such as \SI{0.350}{\milli\metre} of copper and \SI{2.000}{\milli\metre} of tin.
+Filters were used, such as \SI{0.350}{\milli\metre} of copper and \SI{2.000}{\milli\metre} of tin, to tackle beam hardening.
 
@@
 
-3 datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}.
-Projections of the ABS test object were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test object was used in \texttt{TiFilter}.
-2 angular projections were taken for all datasets.
-Greyscale projections were obtained as well.
-To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.
+Three datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}.
+They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections.
+Projections of the ABS test sample were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test sample was used in \texttt{TiFilter}.
+To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter} and \texttt{TiFilter}.
 
-The properties of each dataset is shown in Table \ref{table:data_dataset}.
+The properties of each dataset are shown in Table \ref{table:data_dataset}.
 Properties include the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections.
@@
 potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             & 190                      \\
-power (\SI{}{\watt})                                   & 36                   & 20                             & 19.95                    \\
+power (\SI{}{\watt})                                   & 36                   & 20                             & 20                       \\
 filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper & \SI{3}{\milli\metre} tin \\
@@
 distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            & 875                      \\
-number of replications                                 & 100                  & 20                             & 20                       \\ \hline
-powers used for greyscale projections (\SI{}{\watt})   & 0                    & 0                              & 0                        \\
-\multicolumn{1}{c|}{\vdots}                            & 10.08                & 4.96                           & 10.07                    \\
-\multicolumn{1}{c|}{\vdots}                            & 18.08                & 10                             & 19.95                    \\
-\multicolumn{1}{c|}{\vdots}                            & 28                   & 15.04                          &                          \\
+number of replications for each angle                  & 100                  & 20                             & 20                       \\ \hline
+powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            & 0.0                      \\
+\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            & 10                       \\
+\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             & 20                       \\
+\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             &                          \\
 \multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             &                          \\
-number of replications                                 & 20                   & 20                             & 20                      
+number of replications for each power                  & 20                   & 20                             & 20                    
 \end{tabular}
-\caption{Properties of the 3 datasets obtained for the experiment.}
+\caption{Properties of the three datasets obtained for the experiment.}
 \label{table:data_dataset}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
-      \caption{Projection of sample at \SI{36}{\watt}}
+      \caption{Obtained projection at \SI{36}{\watt}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
-      \caption{Simulation of sample at \SI{36}{\watt}}
+      \caption{Simulated projection at \SI{36}{\watt}}
     \end{subfigure}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
-      \caption{Projection at \SI{0}{\watt}}
+      \caption{Greyscale projection at \SI{0}{\watt}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
-      \caption{Projection at \SI{36}{\watt}}
+      \caption{Greyscale projection at \SI{36}{\watt}}
     \end{subfigure}
   }
-  \caption{\texttt{AbsNoFilter} projections obtained; note the colour scale may vary.}
+  \caption{\texttt{AbsNoFilter} projections at \ang{30}; note the colour scale may vary.}
   \label{fig:data_AbsNoFilter}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30.eps}
-      \caption{Projection of sample at \SI{20}{\watt}}
+      \caption{Obtained projection at \SI{20}{\watt}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30_sim.eps}
-      \caption{Simulation of sample at \SI{20}{\watt}}
+      \caption{Simulated projection at \SI{20}{\watt}}
     \end{subfigure}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration1.eps}
-      \caption{Projection at \SI{0}{\watt}}
+      \caption{Greyscale projection at \SI{0}{\watt}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration5.eps}
-      \caption{Projection at \SI{20}{\watt}}
+      \caption{Greyscale projection at \SI{20}{\watt}}
     \end{subfigure}
   }
-  \caption{\texttt{AbsFilter} projections obtained; note the colour scale may vary.}
+  \caption{\texttt{AbsFilter} projections at \ang{30}; note the colour scale may vary.}
   \label{fig:data_AbsFilter}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30.eps}
-      \caption{Projection of sample at \SI{20}{\watt}}
+      \caption{Obtained projection at \SI{20}{\watt}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30_sim.eps}
-      \caption{Simulation of sample at \SI{20}{\watt}}
+      \caption{Simulated projection at \SI{20}{\watt}}
     \end{subfigure}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration1.eps}
-      \caption{Projection at \SI{0}{\watt}}
+      \caption{Greyscale projection at \SI{0}{\watt}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration3.eps}
-      \caption{Projection at \SI{20}{\watt}}
+      \caption{Greyscale projection at \SI{20}{\watt}}
     \end{subfigure}
   }
-  \caption{\texttt{TiFilter} Projections obtained; note the colour scale may vary.}
+  \caption{\texttt{TiFilter} projections at \ang{30}; note the colour scale may vary.}
   \label{fig:data_TiFilter}
@@
 This is concerning because systematic errors could be caused as a result of the panel effects in the black image when presented only with background radiation.
-The x-ray spot can be observed, in particular in the white image, and is the result of using a cone beam.
+The x-ray spot can be observed, in particular in the white image, and this is the result of using a cone beam.
 \cite{kueh2016modelling} studied the x-ray spot by fitting a mixture of a Gaussian spot and an uniform spot onto the x-ray spot.
+
+\afterpage{\clearpage}
 
@@
 
-Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity of the projections such as panel and spot effects.
-Shading correction is typically done using the greyscale projections and how the pixels respond to different powers.
-For example the black and white image, or images when averaging over replications, can be used to correct the projection using
+Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity of the projections as a result from panel and spot effects.
+Shading correction is typically done by using the greyscale projections and looking at how the grey values respond to different powers for different pixels.
+For example the black and white image can be used to correct the projections using
 \begin{equation}
@@
 where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}.
-However there is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ actually depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.
-
-Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to some parametric function \citep{likar2000retrospective}.
-There is also a method which uses a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.
+There is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ may depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.
+Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to some parametric function \citep{likar2000retrospective} and using a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.
 
 In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user defined constants.
-The shading correction was then experimented to investigate its performance when shading correcting greyvalue projections.
+The shading correction was then experimented to investigate its performance when shading correcting greyscale projections.
 
@@
 
-Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube of power $P$ for some fixed time exposure $t$.
+Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$.
 $S_{x,y}(P)$ may be averaged over replications.
-Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube of power $P_\text{proj}$ for some fixed time exposure $t$.
-Therefore the black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.
+Let $x=1,2,3,\cdots, W$ and $y=1,2,3,\cdots,H$.
+Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$.
+The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.
 
-The shading free image $U_{x,y}$ is not truly known, but it should expected that the shading corrected greyscale projection should be flat with some noise, in other words $\expectation\left[S_{x,y}(P)\right]=\mu_{S}(P)$ and $\variance\left[S_{x,y}(P)\right]=\sigma_{S}^2(P)$ for all $x=1,2,\cdots,L$ and $y=1,2,\cdots,H$.
+The shading free image is not truly known, but it should expected that the shading corrected greyscale projection should be flat with some noise.
+In other words, all pixels in a shading corrected greyscale projection should have grey values with the same expectation $\mu_{S}(P)$ and same variance $\sigma_{S}^2(P)$.
 Suppose $\mu_{S}(P)$ was estimated using the within projection mean
@@
 \end{equation}
-for $P\in \mathfrak{P}$ where $\mathfrak{P} = \left\{0,P_1,P_2,\cdots, P_\text{proj}\right\}$ are the powers used for the greyscale projections.
+for $P\in \mathbb{P}$ where $\mathbb{P} = \left\{0,P_1,P_2,\cdots, P_\text{proj}\right\}$ are the powers used for the greyscale projections.
 $\varepsilon$ is a random variable and an error term, it is included only for formality purposes.
@@
 b_{x,y} = \dfrac{
-  \sum_{P\in\mathfrak{P}}(S_{x,y}(P) - \overline{S}_{x,y})(\overline{S}(P) - \overline{S})
+  \sum_{P\in\mathbb{P}}(S_{x,y}(P) - \overline{S}_{x,y})(\overline{S}(P) - \overline{S})
 }{
-  \sum_{P\in\mathfrak{P}}(S_{x,y}(P) - \overline{S}_{x,y})^2
+  \sum_{P\in\mathbb{P}}(S_{x,y}(P) - \overline{S}_{x,y})^2
 }
@@
 \begin{equation}
-\overline{S}_{x,y} = \dfrac{1}{|\mathfrak{P}|}\sum_{P\in\mathfrak{P}}S_{x,y}(P)
+\overline{S}_{x,y} = \dfrac{1}{|\mathbb{P}|}\sum_{P\in\mathbb{P}}S_{x,y}(P)
 \end{equation}
@@
 \begin{equation}
-\overline{S} = \dfrac{1}{|\mathfrak{P}|}\sum_{P\in\mathfrak{P}}\overline{S}(P) \ .
+\overline{S} = \dfrac{1}{|\mathbb{P}|}\sum_{P\in\mathbb{P}}\overline{S}(P) \ .
 \end{equation}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_interpolation.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_gradient_linear.eps}
@@
   \caption{For each pixel, a linear regression was fitted on the within projection mean versus the grey value for each greyscale projection.
+The \texttt{AbsNoFilter} dataset was used.
 3 random pixels were used to illustrate this in a).
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_null.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_linear.eps}
@@
   }
-  \caption{Projection of \texttt{AbsNoFilter} with and without shading correction}
+  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction}
   \label{fig:data_shadingCorrectionExample_image}
@@
 
-A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.
+A variation of the shading correction which uses only the black and white image such that $\mathbb{P}=\left\{0,P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.
 
@@
 
-Shading correction on a greyscale projection should result in a image which is flat with some noise.
+It was investigated if shading correction on a greyscale projection result in an image which is flat with some noise.
 To avoid overfitting, one greyscale projection from each power were held out and used to fit the parameters of the shading correction.
@@
 The sensitivity, which corresponds to the gradient in units of \SI{}{\adu\per\watt}, became more consistent between pixels with shading correction.
-This should mean that pixels will respond similarly to each other.
+This should mean that pixels will respond similarly to each other for varying power.
 
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_null.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_linear.eps}
@@
   }
-  \caption{Grey values in the \texttt{AbsNoFilter} greyscale projections before and after shading correction. The box plot summarise all $2000\times2000$ pixels in a projection.}
+  \caption{Grey values in the greyscale projections before and after shading correction using the \texttt{AbsNoFilter} dataset. The box plot summarise all $2\,000\times2\,000$ pixels in a projection.}
   \label{fig:data_shadingCorrectionExample_greyvaluePower}
@@
 
-The \texttt{AbsNoFilter} black image before and after shading correction is shown in Figure \ref{fig:data_shadingCorrectionExample_black}.
+The \texttt{AbsNoFilter} black and white images before and after shading correction are shown in Figure \ref{fig:data_shadingCorrectionExample_greyscale}.
 The flatness of the image can be shown using a profile plot, this is a plot of the grey values along a column or row, an example shown in Figure \ref{fig:data_oddEven}.
@@
 
-The BW shading corrected black and white image looks very uniform but there is some structure in the linear shading correction.
-By giving linear shading correction various greyscale projections, it tried to generalise to a range of powers and thus may struggle at shading correcting the black and white images.
+The BW shading corrected black and white image appeared uniform but there is some structure in the linear shading correction.
+By giving linear shading correction various greyscale projections, it tried to generalise to a range of powers, thus may struggle at shading correcting the black and white images.
 
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_bw.eps}
-      \caption{BW shading correction}
+      \caption{Black - BW shading correction}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
-      \caption{Linear shading correction}
+      \caption{Black - Linear shading correction}
     \end{subfigure}
   }
-  \caption{The \texttt{AbsNoFilter} black image after shading correction.}
-  \label{fig:data_shadingCorrectionExample_black}
-\end{figure}
-
-\begin{figure}
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
-      \caption{BW shading correction}
+      \caption{White - BW shading correction}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_linear.eps}
-      \caption{Linear shading correction}
+      \caption{White - Linear shading correction}
     \end{subfigure}
   }
-  \caption{The \texttt{AbsNoFilter} white image after shading correction.}
-  \label{fig:data_shadingCorrectionExample_white}
+  \caption{The black and white images after shading correction from the \texttt{AbsNoFilter} dataset.}
+  \label{fig:data_shadingCorrectionExample_greyscale}
 \end{figure}
@@
     \begin{subfigure}[b]{\textwidth}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_null.eps}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_null.eps}
+      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_null.eps}
+      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_null.eps}
       \caption{No shading correction}
@@
     \begin{subfigure}[b]{\textwidth}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_bw.eps}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_bw.eps}
+      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_bw.eps}
+      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_bw.eps}
       \caption{BW shading correction}
@@
     \begin{subfigure}[b]{\textwidth}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot1_linear.eps}
-      \includegraphics[width=0.49\textwidth]{../figures/data/oddEvenPlot2_linear.eps}
+      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_linear.eps}
+      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_linear.eps}
       \caption{linear shading correction}
@@
   }
-  \caption{Left shows the profile plot of a \texttt{AbsNoFilter} black image at $(879,y)$. Right shows two curves for odd and even $y$.}
+  \caption{Left shows the profile plot of a \texttt{AbsNoFilter} black image at $(879,y)$ using various shading corrections. Right shows two curves for odd and even $y$.}
   \label{fig:data_oddEven}
@@
 
-In the \texttt{AbsNoFilter} dataset, there are 20 replicated greyscale images for each power.
+In each dataset, there are 20 replicated greyscale images for each power.
 One randomly selected replication from each power was assigned to the training set and used to calibrate the shading correction.
@@
 \begin{equation}
-s_\mathrm{b}^2(P)=\dfrac{1}{WH-1}
+s_\mathrm{b}^2(P)=\dfrac{n}{WH-1}
   \sum_{x=1}^{W}\sum_{y=1}^{H}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
@@
   }
-  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale images.
+  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections.
 The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power.
+The experiment was repeated by reselecting the greyscale projections used for training the shading correction.
 The box plots represent the 100 repeats.
-The experiment was repeated by reselecting the greyscale image used for training the shading correction.}
-  \label{fig:data_anova}
+The \texttt{AbsNoFilter} dataset was used here.}
+  \label{fig:data_anovaAbsNoFilter}
 \end{figure}
 
-The results are shown in Figure \ref{fig:data_anova} and shows that with shading correction, the within and between pixel variance become more similar.
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_null.eps}
+      \caption{No shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_bw.eps}
+      \caption{BW shading correction}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
+      \caption{Linear shading Correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_FStatistic.eps}
+      \caption{$F$ statistic}
+    \end{subfigure}
+  }
+  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections.
+The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power.
+The experiment was repeated by reselecting the greyscale projections used for training the shading correction.
+The box plots represent the 100 repeats.
+The \texttt{AbsFilter} dataset was used here.}
+  \label{fig:data_anovaAbsFilter}
+\end{figure}
+
+The results are shown in Figures \ref{fig:data_anovaAbsNoFilter} and \ref{fig:data_anovaAbsFilter} for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively.
+With shading correction, the within and between pixel variance became more similar.
 A difference between BW and linear shading correction is that for the black image, the $F$ statistic is better for BW compared to linear shading correction.
@@
 Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1,WH(n-1)}$.
-In this experiment, the 5\% critical value is 1.001 to 3 decimal places.
-This may be due to the grey values of the greyscale images not satisfying the assumptions for the $F$ test, for example they may not be i.i.d.
+In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for the purpose of this analysis.
+This may be due to the grey values of the greyscale projections not satisfying the assumptions for the $F$ test, for example they may not be i.i.d.
+
+\subsection{Conclusion}
+
+Shading correction is important because it removes any panel and spot effects from projections which may cause systematic errors in any statistical analysis.
+Shading correcting the greyscale projections visually produced a flat image but there were some spatial variation which was picked up by the between pixel variances in ANOVA.
+
+Linear shading correction performed well, in terms of ANOVA, on all greyscale projections except for the black image.
+This is because linear shading correction trains on greyscale projections of various powers and generalises to these powers.
+Linear shading correction is used throughout this thesis.
+
+The variance of the greyscale projections were studied in this chapter.
+This is fairly straightforward because the greyscale projections are flat images.
+The noise of a projection of a test sample is studied in the next chapter and this is done by modelling the grey value of each pixel as a compound Poisson random variable.

### 2019-08-01 reports/thesis/chapters/3_compoundPoisson.tex
Made CpEmAlgorithm an Experiment

@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lnL.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lnL.eps}
         \caption{Log likelihood}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lambda.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_alpha.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_alpha.eps}
         \caption{$\alpha$}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_beta.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_beta.eps}
         \caption{$\beta$}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lnL.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lnL.eps}
         \caption{Log likelihood}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lambda.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_alpha.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_alpha.eps}
         \caption{$\alpha$}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_beta.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_beta.eps}
         \caption{$\beta$}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lnL.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lnL.eps}
         \caption{Log likelihood}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lambda.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_alpha.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_alpha.eps}
         \caption{$\alpha$}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_beta.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_beta.eps}
         \caption{$\beta$}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lnL.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lnL.eps}
         \caption{Log likelihood}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lambda.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lambda.eps}
         \caption{$\lambda$}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_alpha.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_alpha.eps}
         \caption{$\alpha$}
@@
         \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_beta.eps}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_beta.eps}
         \caption{$\beta$}
@@
 \end{figure}
+
+\afterpage{\clearpage}
 

### 2019-08-01 compoundpoisson/cpEmAlgorithm.m

@@ -1,162 +1,0 @@
-%SCRIPT: COMPOUND POISSON EM ALGORITHM
-%Fit the compound Poisson onto simulated data using the EM algorithm
-%Plots, at each step of EM, the:
-  %log likelihood (marginal, not joint)
-  %lambda estimate
-  %alpha estimate
-  %beta estimate
-
-close all;
-clearvars;
-
-%random seed
-rng(uint32(2225638568),'twister');
-
-n = 1000; %simulation sample size
-
-%array of different ways to evaluate compound Poisson density
-modelArray = cell(3,1);
-modelArray{1} = CompoundPoisson();
-modelArray{2} = CompoundPoissonNorm();
-modelArray{3} = CompoundPoissonSaddle();
-nModel = numel(modelArray);
-
-%directory for the figures to be saved
-figureLocation = fullfile('reports','figures','compoundpoisson');
-
-%array of parameters to be investigated
-  %dim 1: for each set
-  %dim 2: lambda, alpha, beta
-parameterArray = [
-  1,1,1;
-  10,1,1;
-  1,100,1;
-  100,100,1
-  ];
-%array to plot zero count for each of the parameters
-isPlotZeroArray = [true, false, true, false];
-nParameter = numel(parameterArray(:,1)); %number of parameters sets to be considered
-
-nRepeat = 10; %number of times to repeat the experiment
-nStep = 10; %number of EM steps
-%for each parameter set
-for iParameter = 1:nParameter
-  %get parameters
-  lambda = parameterArray(iParameter,1);
-  alpha = parameterArray(iParameter,2);
-  beta = parameterArray(iParameter,3);
-  %plot the lnL, and parameters at each step of EM
-  emAlgorithm(n, lambda, alpha, beta, nRepeat, nStep, figureLocation);
-end
-
-%NESTED FUNCTION: EM ALGORITHM
-%Plots the log likelihood and parameters at each step of EM
-%The starting points for the EM algorithm is at the true value
-%PARAMETERS:
-  %nSimulation: number of data points in the simulation
-  %lambda: poisson parameter
-  %alpha: gamma shape parameter
-  %beta: gamma rate parameter
-  %nRepeat: number of times to repeat the experiment
-  %nStep: number of EM steps
[…]

### 2019-08-01 reports/thesis/chapters/2_dataCollection.tex
data collection chpater contains black white images

@@
   }
-  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction}
+  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction.}
   \label{fig:data_shadingCorrectionExample_image}
@@
     \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_null.eps}
+      \caption{Black - No shading correction}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_null.eps}
+      \caption{White - No shading correction}
+    \end{subfigure}
+  }
+  \centerline{
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_bw.eps}
@@
     \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
-      \caption{Black - Linear shading correction}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
+      \caption{White - BW shading correction}
     \end{subfigure}
@@
     \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
-      \caption{White - BW shading correction}
+      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
+      \caption{Black - Linear shading correction}
     \end{subfigure}
@@
   }
-  \caption{The black and white images after shading correction from the \texttt{AbsNoFilter} dataset.}
+  \caption{The black and white images before and after shading correction from the \texttt{AbsNoFilter} dataset.}
   \label{fig:data_shadingCorrectionExample_greyscale}
@@
 
-\begin{figure}
+\begin{figure}[p]
   \centering

### 2019-08-01 reports/thesis/chapters/3_compoundPoisson.tex
CompoundPoisson chapter
Added 3rd order moment
Use multlined in align

@@
   \variance\left[X\right] &= \lambda\expectation\left[U^2\right]
+  \\
+  \expectation\left[(X-\expectation[X])^3\right] &=\lambda\expectation\left[U^3\right]
 \end{align}
-which agrees with the results in the previous section. The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.
+which agrees with the expectation and variance results in the previous section. The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.
 
@@
 
-The m.g.f.~of $U$ is $M_U(\theta) = \left(\dfrac{\beta}{\beta-\alpha}\right)^\alpha$. Then the m.g.f.~of $X$ is
+The m.g.f.~of $U$ is $M_U(\theta) = \left(\dfrac{\beta}{\beta-\theta}\right)^\alpha$. Then the m.g.f.~of $X$ is
 \begin{equation}
@@
 Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log likelihood is defined to be
-\begin{equation*}
-  \ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
+\begin{align}
+  \ln L(\lambda,\alpha,\beta;X) &= \sum_{i=1}^n
   \left[
@@
   \right]
-\end{equation*}
-\begin{multline}
-  \ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
+  \nonumber \\
+  &\!\begin{multlined}[b]
+  =
+    \sum_{i=1}^n
     \left[
@@
     \right.
-  \\
+    {}\\
     \left.
@@
     \right] \ .
-\end{multline}
+  \end{multlined}
+\end{align}
+
 $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
@@
 In the M step, the conditional expected joint log likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is then
-\begin{multline*}
-  T(\lambda,\alpha,\beta)=
+\begin{align}
+  T(\lambda,\alpha,\beta)&=
+  \begin{multlined}[t]
     \sum_{i=1}^n
@@
     \right]
-\end{multline*}
-\begin{multline}
-  T(\lambda,\alpha,\beta)=
+  \end{multlined}
+  \nonumber\\
+  &\!\begin{multlined}[b]=
     -n\lambda
@@
     \right] + c
-\end{multline}
+  \end{multlined}
+\end{align}
 where $c$ is some constant not dependent on $\lambda$, $\alpha$ or $\beta$.
@@
   \\
-  \|\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T\|
   &\approx
@@
 which can be approximated to
-\begin{multline*}
-  T(\lambda,\alpha)=
+\begin{align}
+  T(\lambda,\alpha)&=
+  \begin{multlined}[t]
     -n\lambda+
@@
     + c
-\end{multline*}
-\begin{multline}
-  T(\lambda,\alpha)=
+  \end{multlined}
+  \nonumber\\
+  &\!\begin{multlined}[b]=
     -n\lambda+
@@
     \ .
-\end{multline}
+  \end{multlined}
+\end{align}
 Taking the derivative with respect to $\alpha$
@@
 
-The log likelihood, using a simulation of 100 compound Poisson-gamma random variables, are shown in Figure \ref{fig:compoundPoisson_loglikelihoodplot}.
-These plots are concerning because the likelihood appeared not to be convex and there is no unique maxima, surprising in $\lambda=1$ case as well.
+The log likelihood, using a simulation of 100 compound Poisson-gamma random variables, are plotted for fixed $\lambda$ in Figure \ref{fig:compoundPoisson_loglikelihoodplot}.
+These plots are concerning because the likelihood appeared not to be convex and there is no unique maxima for all $\lambda$ investigated.
 
@@
 
-These plots suggest there is no unique maximum likelihood estimator and the EM algorithm would be very sensitive to the starting position, including for small $\lambda$.
+As a results, there is no unique maximum likelihood estimator and the EM algorithm would be very sensitive to the starting position, including for small $\lambda$.
 
@@
 The time exposure is $\tau=\SI{708}{\milli\second}$.
-Assume an efficiency of \SI{0.01}{{photon}\,{electron}^{-1}} and the charge per electron is $e=\SI{1.602e-19}{\coulomb\,{electron}^{-1}}$.
+Assume an efficiency of \SI{0.01}{{photon.}{electron}^{-1}} and the charge per electron is $e=\SI{1.602e-19}{\coulomb\,{electron}^{-1}}$.
 Assume the photons projected onto the array of $2\,000^2\,\si{\pixel}$.
@@
 \begin{align*}
-\lambda &\approx \dfrac{\text{efficiency} P \tau}{\text{number of pixels} V e}
+\lambda &\approx \dfrac{\text{efficiency} \times P \tau}{\text{number of pixels} \times V e}
 \\

### 2019-08-02 reports/thesis/book.tex
Started writing on noContamination experiment
tex: made command /addNumber which inputs a text file protected and without space at the end
.eps figures are saved in allNullGaussian
.txt files are saved in allNullGaussian
new figures in allNullGaussian
Writing up allnull experiments
Wrote subsection No Contamination Experiment, Contamination Experiment
Experiment_AllNull export numbers and figures
inputNumber command in latex
Appendix for inference
Start literture review
Start chapter 2
printResults for GlmSelect
GlmSelect write up
Compound Poisson complete re-write
Histogram class
Re-wrote com

@@
 \usepackage{MnSymbol} %udots
+\usepackage{afterpage} %\afterpage{\clearpage}
+\usepackage{siunitx} %for measurements
+\usepackage{rotating}
+\usepackage{multirow} %for multirow tables
+\usepackage{mathtools} %multlined
+\usepackage{longtable}
 
@@
 \newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
-\newcommand{\BIC}{\textup{BIC}}
+\newcommand{\BIC}{\mathrm{BIC}}
+\newcommand{\AIC}{\mathrm{AIC}}
+
+\newcommand{\subSize}{0.49\textwidth}
+\newcommand{\mainSize}{0.8\textwidth}
 
@@
 
+\newcommand{\addNumber}[1]{\protect\input{#1}\unskip}
+\newcommand{\inputNumber}[1]{\protect\input{#1}\unskip}
+
+\DeclareSIUnit\pixel{px}
+\DeclareSIUnit\adu{ADU}
+
 \begin{document}\sloppy
 
-\includepdf{title.pdf}
+\begin{titlingpage}
+\centering
+{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications in Additive Manufacturing \par}
+\vspace{1cm}
+{\Large Sherman E.~Lo\par}
+{\Large Doctor of Philosophy in Statistics\par}
+\vfill
+{\Large University of Warwick\par}
+{\Large Department of Statistics\par}
+{\Large September 2019\par}
+\end{titlingpage}
 
 \frontmatter
-\section*{Abstract}
+
+\newpage
+\tableofcontents*
+\newpage
+\listoffigures
+\newpage
+\listoftables
+
+\chapter{Acknowledgements}
+I would like to thank my supervisors Julia Brettschneider and Tom Nichols.
+I would also like to thank my calibrators, as part of the Inside-Out group, in Warwick Statistics, Clair Barnes, Wilfred Kendall and Audrey Kueh, and the Warwick Manufacturing Group, Greg Gibbons, Jay Warnett and Mark Williams.
+
+This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1).
+I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar Martens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.
+
+\chapter{Declaration}
+This thesis is the author's own work and has not been published at the time of submitting.
+
+This thesis is a result of collaborative research with Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing funded by EPSRC (EP/K031066/1).
+Greg Gibbons and Jay Warnett, from the Warwick Manufacturing Group, were responsible for the fabrication, x-ray computed tomography acquisition and simulation of test samples used in this thesis.
+In this thesis, they are referred to as engineers.
+
+This thesis has not been submitted for a degree at another university.
+
+\chapter{Abstract}
 X-ray computed tomography (CT) can be used for defect detection in 3D printing.
@@
 
-\section*{Acknowledgements}
-\begin{itemize}
-	\item Supervisors: Julia Brettschneider and Tom Nichols
-	\item Inside Out Team: Wilfrid Kendall, Audrey Kueh, Jay Warnett and Clair Barnes
-	\item EPSRC Funding: EP/L016710/1
-\end{itemize}
-
-\newpage
-\tableofcontents*
-
 \mainmatter
@@
 \chapter{Data Collection}
+\input{chapters/2_dataCollection.tex}
 
@@
 
+\begin{appendices}
+\input{chapters/appendix.tex}
+\end{appendices}
+
 \end{document}

### 2019-08-05 reports/thesis/book.tex
Update delcaration

@@
 \usepackage{siunitx} %for measurements
-\usepackage{rotating}
+\usepackage[figuresright]{rotating}
 \usepackage{multirow} %for multirow tables
@@
 \usepackage{longtable}
+\usepackage{bibentry}
 
@@
 \chapter{Declaration}
-This thesis is the author's own work and has not been published at the time of submitting.
+This thesis is submitted to the University of Warwick in support of my application for the degree of Doctor of Philosophy.
+It has been composed by myself and has not been submitted in any previous application for any degree.
 
-This thesis is a result of collaborative research with Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing funded by EPSRC (EP/K031066/1).
-Greg Gibbons and Jay Warnett, from the Warwick Manufacturing Group, were responsible for the fabrication, x-ray computed tomography acquisition and simulation of test samples used in this thesis.
-In this thesis, they are referred to as engineers.
+The work presented (including data generated and data analysis) was carried out by the author except in the cases outlined below:
+\begin{itemize}
+  \item The fabrication, x-ray computed tomography acquisition and simulation of test samples were done by Greg Gibbons and Jay Warnett, from the Warwick Manufacturing Group, as part of Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing funded by EPSRC (EP/K031066/1).
+\end{itemize}
 
-This thesis has not been submitted for a degree at another university.
+Parts of this thesis have been published by the author:
+\begin{itemize}
+  \item\nobibliography*\bibentry{lo2019detection}
+\end{itemize}
 

### 2019-08-05 reports/thesis/chapters/4_variancePrediction.tex
Update varmean
Grouped shading corrections together in GlmSelect and VarMeanCv
Residual analysis
Write variancePrediction chapter

@@
 
-Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilterDeg120} and \texttt{AbsFilterDeg120}.
-The procedure was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data.
+Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter}.
+The procedure was repeated 10 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data.
 The procedure was also repeated using various shading corrections to investigate the effects of shading correction on the variance-mean relationship.
@@
 \multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
-\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityorder.txt}     \\
-                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identityvote.txt}      \\
-                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_identitycriterion.txt} \\ \hline
-\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityorder.txt}     \\
-                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identityvote.txt}      \\
-                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_identitycriterion.txt} \\
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_identitycriterion.txt} \\
 \\
 \multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
-\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalorder.txt}     \\
-                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalvote.txt}      \\
-                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterLinear_reciprocalcriterion.txt} \\ \hline
-\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalorder.txt}     \\
-                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalvote.txt}      \\
-                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterLinear_reciprocalcriterion.txt}
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg30linear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg30linear_reciprocalcriterion.txt}
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilterDeg120}.
+\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{30}.
 The columns of the table represent different shading corrections used on the projections.
-Forward stepwise selection was repeated 100 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
 The row labelled order shows the most common selected polynomial orders.
-The error bars are the standard deviation from the 100 repeats.}
-\label{table:meanVar_glmselect_absnofilter}
+The error bars are the standard deviation from the 10 repeats.}
+\label{table:meanVar_glmselect_absnofilterdeg30}
 \end{sidewaystable}
@@
 \multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
-\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityorder.txt}     \\
-                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identityvote.txt}      \\
-                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_identitycriterion.txt} \\ \hline
-\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityorder.txt}     \\
-                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identityvote.txt}      \\
-                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_identitycriterion.txt} \\
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_identitycriterion.txt} \\
 \\
 \multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
-\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalorder.txt}     \\
-                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalvote.txt}      \\
-                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterLinear_reciprocalcriterion.txt} \\ \hline
-\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalorder.txt}     \\
-                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalvote.txt}      \\
-                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterNull_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterBw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterLinear_reciprocalcriterion.txt}
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsNoFilterDeg120linear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsNoFilterDeg120linear_reciprocalcriterion.txt}
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilterDeg120}.
+\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{120}.
 The columns of the table represent different shading corrections used on the projections.
-Forward stepwise selection was repeated 100 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
 The row labelled order shows the most common selected polynomial orders.
-The error bars are the standard deviation from the 100 repeats.}
-\label{table:meanVar_glmselect_absfilter}
+The error bars are the standard deviation from the 10 repeats.}
+\label{table:meanVar_glmselect_absnofilterdeg120}
 \end{sidewaystable}
 
-The results are shown in Tables \ref{table:meanVar_glmselect_absnofilter} and \ref{table:meanVar_glmselect_absfilter}.
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg30linear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg30linear_reciprocalcriterion.txt}
+\end{tabular}
+\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}.
+The columns of the table represent different shading corrections used on the projections.
+Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+The row labelled order shows the most common selected polynomial orders.
+The error bars are the standard deviation from the 10 repeats.}
+\label{table:meanVar_glmselect_absfilterdeg30}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+\centering
+\begin{tabular}{cc|ccc}
+\multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_identitycriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_identityorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_identityorder.txt}     \\
+                     & votes     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_identityvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_identityvote.txt}       & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_identityvote.txt}      \\
+                     & criterion & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_identitycriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_identitycriterion.txt} \\
+\\
+\multicolumn{2}{c|}{Canonical Link}& null & bw & linear \\ \hline
+\multirow{3}{*}{AIC} & order      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectAicAbsFilterDeg120linear_reciprocalcriterion.txt} \\ \hline
+\multirow{3}{*}{BIC} & order      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_reciprocalorder.txt}     & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_reciprocalorder.txt}     \\
+                     & votes      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_reciprocalvote.txt}      & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_reciprocalvote.txt}      \\
+                     & criterion  & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120null_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120bw_reciprocalcriterion.txt} & \inputNumber{../figures/varmean/GlmSelectBicAbsFilterDeg120linear_reciprocalcriterion.txt}
+\end{tabular}
+\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}.
+The columns of the table represent different shading corrections used on the projections.
+Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+The row labelled order shows the most common selected polynomial orders.
+The error bars are the standard deviation from the 10 repeats.}
+\label{table:meanVar_glmselect_absfilterdeg120}
+\end{sidewaystable}
+
+The results are shown in Tables \ref{table:meanVar_glmselect_absnofilterdeg30} and \ref{table:meanVar_glmselect_absnofilterdeg120} for \texttt{AbsNoFilter} and Tables \ref{table:meanVar_glmselect_absfilterdeg30} and \ref{table:meanVar_glmselect_absfilterdeg120} for for \texttt{AbsFilter}.
 The models selected all have only two terms and are quite simple.
 Different shading correction or different criteria had no effect on the selected model.
-The method is quite robust to the variation introduced to the dataset when repeating the experiment because all 100 repeats consistently selected the same model.
+The method is quite robust to the variation introduced to the dataset when repeating the experiment because all 10 repeats consistently selected the same model.
 
 There was some variation to the selected models between datasets.
-For example when using the identity link, \texttt{AbsNoFilterDeg120} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilterDeg120} prefers $\eta(x)=\beta_{-1}x^{-1}+\beta_0$.
+For example when using the identity link, \texttt{AbsNoFilter} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilter} prefers $\eta(x)=\beta_{-1}x^{-1}+\beta_0$.
 Using the canonical link, both datasets selected $\eta(x)=\beta_{-1}x^{-1}+\beta_0$ which correspond to $\widehat{y}(x)=\left(\beta_{-1}x^{-1}+\beta_0\right)^{-1}$.
-Figures \ref{fig:meanVar_varMeanExample_AbsNoFilterDeg120} and \ref{fig:meanVar_varMeanExample_AbsFilterDeg120} shows the GLM fits.
-There is a leverage towards the low grey values because there are more low grey values in the dataset.
-As a result, the GLM does not capture the curvature towards the high grey values.
+
+Figures \ref{fig:meanVar_varMeanExample_AbsNoFilter} and \ref{fig:meanVar_varMeanExample_AbsFilter} shows the GLM fits for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively.
+The prediction intervals were obtained using the distribution $\widehat{Y}(x)\sim\gammaDist\left(\alpha, \dfrac{\alpha}{g^{-1}\left(\widehat{\eta}(x)\right)}\right)$ where $\widehat{\eta}(x)$ is the fitted systematic component.
+The fits all looked reasonable except for \texttt{AbsNoFilter} at \ang{120} where the fit did not capture the inflection.
+The forward stepwise selection may not pick this up because there are a lot of low grey values, causing a leverage towards these low grey values and the inflection does not stand out to the method.
 
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
-        \caption{$\widehat{y}(x)=\beta_0+\beta_1 x$}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_identity000010.eps}
+        \caption{$\widehat{y}(x)=\beta_0+\beta_1 x$ at \ang{30}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
-        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_reciprocal000100.eps}
+        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{30}}
     \end{subfigure}
     }
-    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilterDeg120} with linear shading correction.
-The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
-    \label{fig:meanVar_varMeanExample_AbsNoFilterDeg120}
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
+        \caption{$\widehat{y}(x)=\beta_0+\beta_1 x$ at \ang{120}}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
+        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{120}}
+    \end{subfigure}
+    }
+    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction.
+The red solid line shows the GLM fit along with $\Phi(\pm 1)$ prediction interval as dashed lines.}
+    \label{fig:meanVar_varMeanExample_AbsNoFilter}
 \end{figure}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
-        \caption{$\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_identity000100.eps}
+        \caption{$\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
-        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_reciprocal000100.eps}
+        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
     \end{subfigure}
     }
-    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilterDeg120} with linear shading correction.
-The red solid line shows the GLM fit along with $\Phi(\pm 1)$ quantile error bars as dashed lines.}
-    \label{fig:meanVar_varMeanExample_AbsFilterDeg120}
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
+        \caption{$\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
+        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
+    \end{subfigure}
+    }
+    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction.
+The red solid line shows the GLM fit along with $\Phi(\pm 1)$ prediction interval as dashed lines.}
+    \label{fig:meanVar_varMeanExample_AbsFilter}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/varmean/devianceGraph.eps}
+  \includegraphics[width=\subSize]{../figures/varmean/devianceGraph.eps}
   \caption{Scaled deviance loss function}
@@
   \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/varmean/varMeanCv_AbsNoFilterDeg120_testmeanscaleddeviance.eps}
-      \caption{\texttt{AbsNoFilterDeg120}}
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/VarMeanCvAbsNoFilterDeg30_testmeanscaleddeviance.eps}
+      \caption{\texttt{AbsNoFilter} at \ang{30}}
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/varmean/varMeanCv_AbsFilterDeg120_testmeanscaleddeviance.eps}
-      \caption{\texttt{AbsFilterDeg120}}
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/VarMeanCvAbsNoFilterDeg120_testmeanscaleddeviance.eps}
+      \caption{\texttt{AbsFilter} at \ang{120}}
+  \end{subfigure}
+  }
+    \centerline{
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/VarMeanCvAbsFilterDeg30_testmeanscaleddeviance.eps}
+      \caption{\texttt{AbsFilter} at \ang{30}}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/VarMeanCvAbsFilterDeg120_testmeanscaleddeviance.eps}
+      \caption{\texttt{AbsFilter} at \ang{120}}
   \end{subfigure}
@@
 
+\section{Residual Analysis}
+
+A residual analysis was conducted to look for anything overlooked.
+The model $\widehat{y}(x)=\beta_0+\beta_1 x$ was looked at here.
+A residual plot plots $r_i=y_i-\widehat{y}(x_i)$ for all $x_i$ in the dataset.
+This was done using a 2D histogram.
+Due to the gamma GLM, higher grey values typically have bigger residuals in magnitude, a predicted residual interval is included in the histogram to aid judging the residuals.
+This interval was obtained by obtaining the prediction interval and subtracting it from the fit.
+
+\begin{figure}
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg30_vsgreyvalue.eps}
+      \caption{\texttt{AbsNoFilter} at \ang{30}}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg120_vsgreyvalue.eps}
+      \caption{\texttt{AbsFilter} at \ang{120}}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg30_vsgreyvalue.eps}
+      \caption{\texttt{AbsFilter} at \ang{30}}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg120_vsgreyvalue.eps}
+      \caption{\texttt{AbsFilter} at \ang{120}}
+  \end{subfigure}
+  }
+  \caption{Log frequency density histogram of the residuals given the mean grey value.
+The residuals are from fitting a gamma GLM of the form $\widehat{y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
+The dashed red line shows the $\Phi(\pm 1)$ predicted residual interval.}
+  \label{fig:meanVar_residualGreyvalue}
+\end{figure}
+
+The residual plots are shown in Figure \ref{fig:meanVar_residualGreyvalue}.
+The residuals are all sensible and increase in size with grey value which is captured by the predicted residual interval.
+The inflection in \texttt{AbsNoFilter} at \ang{120}, as discussed previously, can be seen more clearly here.
+
+\begin{figure}
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg30_spatial.eps}
+      \caption{\texttt{AbsNoFilter} at \ang{30}}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg120_spatial.eps}
+      \caption{\texttt{AbsNoFilter} at \ang{120}}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg30_spatial.eps}
+      \caption{\texttt{AbsFilter} at \ang{30}}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg120_spatial.eps}
+      \caption{\texttt{AbsFilter} at \ang{120}}
+  \end{subfigure}
+  }
+  \caption{Absolute value residuals from fitting a gamma GLM of the form $\widehat{y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
+Highlighted in a red box is an inflection.}
+  \label{fig:meanVar_spatialResidual}
+\end{figure}
+
+Because no spatial information was used in modelling the variance, the residuals were plotted on top of the projections to look for any spatial structure, this is shown in Figure \ref{fig:meanVar_spatialResidual}.
+Because of the geometry of the test sample, lower grey values, thus smaller residuals, are found in the middle of the projection.
+Similarly higher grey values, thus bigger residuals, are found on the edges of the test sample.
+Considering that, the residuals do not show any striking spatial structure.
+Again, the inflection in \texttt{AbsNoFilter} at \ang{120} can be seen more clearly here.
+
 \section{Conclusion}
 
-It was found that a gamma GLM with relationship $\widehat{y}(x)=\beta_0+\beta_1 x$ using the identity link was a good model.
-The simple linear relationship is attractive because it is justified by the compound Poisson model of x-ray photon behaviour.
-This model is also preferred by those who follows Occam’s razor.
+Various parametric models were investigated.
+A gamma GLM with identity and canonical link functions were looked at with different explanatory polynomials.
+In terms of cross-validation, most of the models looked at have similar prediction performance when predicting the variance given a grey value.
+Thus the relationship $\widehat{y}(x)=\beta_0+\beta_1 x$ using the identity link is attractive for its simplicity and links with the compound Poisson model.
+
+It was found shading correction had little effect on the variance-mean relationship.
+
+As discussed in the compound Poisson chapter, a linear relationship can be derived by assuming no beam hardening.
+Then it should be expected that a linear relationship is observed in the dataset \texttt{AbsFilter}.
+In the forward stepwise selection, \texttt{AbsNoFilter} consistently selected the linear model, given the identity link function.
+\texttt{AbsFilter} did not select the linear model but in terms of cross-validation prediction performance, the linear model was just as good as the other models.
+
+It was unusual to see an infection in the sample variance-mean data in \texttt{AbsNoFilter} at \ang{120} which was not captured by the GLM.
+A good explanation was not found but perhaps the absence of an x-ray filter may have contributed to this.
 

### 2019-08-05 Experiment.m

@@ -22,6 +22,8 @@ classdef Experiment < handle
     directory = fullfile('results'); %where the resuls are saved
     experimentName; %string, name of the experiment and the file name for storing it in a .mat file
     isComplete; %boolean, true if the experiment is completed
+    nIteration; %total of iterations in the experiment
+    iIteration; %number of iterations done so far
   end
   properties (SetAccess = protected, GetAccess = protected)
     nArrow; %number of arrows to be displayed in the progress bar
@@ -88,6 +90,22 @@ classdef Experiment < handle
   
   %PROTECTED METHODS
   methods (Access = public)
+    
+    %METHOD: SET N ITERATION
+    %Set the number of iterations so that the method madeProgress can called
+    %PARAMETERS:
+      %nIteration: number of iterations in the experiment
+    function setNIteration(this, nIteration)
+      this.nIteration = nIteration;
+      this.iIteration = 0;
+    end
+    
+    %METHOD: MADE PROGRESS
+    %Update the number of iterations made in this experiment and print the progress bar
+    function madeProgress(this)
+      this.iIteration = this.iIteration+1;
+      this.printProgress(this.iIteration / this.nIteration);
+    end
     
     %METHOD: PRINT PROGRESS
     %Displays a progress bar (with resoloution of 20)

### 2019-08-05 varmean/glmselect/GlmSelectAicAbsFilterDeg30.m

@@ -1,0 +1,15 @@
+classdef GlmSelectAicAbsFilterDeg30 < GlmSelectAic
+  
+  properties
+  end
+  
+  methods (Access = protected)
+    
+    function setup(this)
+      this.setup@GlmSelectAic('AbsFilterDeg30', uint32(1939773748));
+    end
+    
+  end
+  
+end
+

### 2019-08-05 varmean/glmselect/GlmSelectAicAbsFilterNull.m

@@ -1,15 +1,0 @@
-classdef GlmSelectAicAbsFilterNull < GlmSelectAic
-  
-  properties
-  end
-  
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@GlmSelectAic(AbsFilterDeg120(), uint32(3361338167));
-    end
-    
-  end
-  
-end
-

### 2019-08-05 varmean/glmselect/GlmSelectAicAbsNoFilterDeg30.m

@@ -1,0 +1,15 @@
+classdef GlmSelectAicAbsNoFilterDeg30 < GlmSelectAic
+  
+  properties
+  end
+  
+  methods (Access = protected)
+    
+    function setup(this)
+      this.setup@GlmSelectAic('AbsNoFilterDeg30', uint32(2276554737));
+    end
+    
+  end
+  
+end
+

### 2019-08-05 varmean/glmselect/GlmSelectAicAbsNoFilterLinear.m

@@ -1,15 +1,0 @@
-classdef GlmSelectAicAbsNoFilterLinear < GlmSelectAic
-  
-  properties
-  end
-  
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@GlmSelectAic(AbsNoFilterDeg120(), uint32(2133083960));
-      this.scan.addShadingCorrectorLinear();
-    end
-    
-  end
-  
-end

### 2019-08-05 varmean/glmselect/GlmSelectBicAbsFilterBw.m

@@ -1,15 +1,0 @@
-classdef GlmSelectBicAbsFilterBw < GlmSelectBic
-  
-  properties
-  end
-  
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@GlmSelectBic(AbsFilterDeg120(), uint32(524295056));
-      this.scan.addShadingCorrectorBw();
-    end
-    
-  end
-  
-end

### 2019-08-05 varmean/glmselect/GlmSelectBicAbsNoFilterNull.m

@@ -1,15 +1,0 @@
-classdef GlmSelectBicAbsNoFilterNull < GlmSelectBic
-  
-  properties
-  end
-  
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@GlmSelectBic(AbsNoFilterDeg120(), uint32(50307422));
-    end
-    
-  end
-  
-end
-

### 2019-08-05 varmean/varMeanExample.m

@@ -5,6 +5,8 @@
 clearvars;
 close all;
 
+plotExample(AbsNoFilterDeg30, {[0,0,0;0,1,0], [0,0,0;1,0,0]}, {'identity', 'reciprocal'});
+plotExample(AbsFilterDeg30, {[0,0,0;1,0,0], [0,0,0;1,0,0]}, {'identity', 'reciprocal'});
 plotExample(AbsNoFilterDeg120, {[0,0,0;0,1,0], [0,0,0;1,0,0]}, {'identity', 'reciprocal'});
 plotExample(AbsFilterDeg120, {[0,0,0;1,0,0], [0,0,0;1,0,0]}, {'identity', 'reciprocal'});
 

### 2019-08-05 varmean/varMeanResidual.m

@@ -1,0 +1,83 @@
+%SCRIPT: VAR MEAN RESIDUAL
+%Plot the residual vs greyvalue and residual on the projections
+
+close all;
+clearvars;
+
+directory = fullfile('reports','figures','varmean');
+
+%list of datasets
+scanArray = cell(1,1);
+scanArray{1} = AbsNoFilterDeg30();
+scanArray{2} = AbsNoFilterDeg120();
+scanArray{3} = AbsFilterDeg30();
+scanArray{4} = AbsFilterDeg120();
+for iScan = 1:numel(scanArray)
+  scanArray{iScan}.addShadingCorrectorLinear();
+end
+link = 'identity';
+termMatrix = [0,0;1,0];
+
+%for each data
+for iScan = 1:numel(scanArray)
+  
+  scan = scanArray{iScan};
+  %get the grey values
+  greyValueArray = getGreyValue(scan);
+  %get var-mean data
+  xOriginal = mean(greyValueArray,2);
+  X = xOriginal;
+  y = var(greyValueArray,[],2); %get the variance of the greyvalues
+  
+  %normalise the data
+  xCentre = mean(X,1);
+  xScale = std(X,[],1);
+  X = (X-xCentre)./xScale; %noramlise
+  yStd = std(y);
+  y = y/yStd; %noramlise
+  
+  %fit model
+  model = fitglm(X, y, termMatrix, 'Distribution', 'gamma', 'Link', link);
+  residual = (y - table2array(model.Fitted(:,1))) * yStd;
+  
+  %get shape parameter
+  alpha = (scan.nSample - 1) / 2;
+
+  %get confidence intervals for the residuals
+  xPlot = linspace(min(xOriginal), max(xOriginal), 1000)';
+  XPlot = (xPlot-xCentre)./xScale;
+  yPlot = model.predict(XPlot) * yStd;
+  upError = gaminv(normcdf(1), alpha, yPlot/alpha) - yPlot;
+  downError = gaminv(normcdf(-1), alpha, yPlot/alpha) - yPlot;
+
+  %plot the heat map of the residual vs grey value
+  hist3Heatmap = Hist3Heatmap();
+  fig = LatexFigure.sub();
+  hist3Heatmap.plot(xOriginal, residual);
+  hold on;
+  plot(xPlot, upError, 'r--');
+  plot(xPlot, downError, 'r--');
+  xlabel('mean grey value (ADU)');
+  ylabel('residual (ADU²)');
[…]

### 2019-08-05 varmean/varmeancv/VarMeanCv.m

@@ -10,6 +10,7 @@
   %y = a + bx using identity link
   %y = a + b/x using identity link
   %y = 1/(a+b/x) using reciprocal link
+%Different shading corrections were investigated: null, bw, linear
 classdef VarMeanCv < Experiment
   
   properties (SetAccess = public)
@@ -19,12 +20,15 @@ classdef VarMeanCv < Experiment
     %see https://uk.mathworks.com/matlabcentral/answers/159732-2014b-axis-label-errors-when-printing-to-postscript
     %see https://uk.mathworks.com/matlabcentral/answers/290136-unwanted-whitespace-gap-in-figure-text-before-symbols-and-subscripts-in-matlab-2015a-for-pdf-and-e
     modelArray = {'y=a+bx','y=a+b/x','y=(a+b/x)⁻¹'};
-    scan; %contains the projections to work on, apply shading correction if needed
+    scanArray; %array of projections with different shading corrections to work on
     nRepeat = 100; %number of times to repeat the experiment
+    
+    nShadingCorrection = 3;
     
     %array of training and test deviance
       %dim 1: for each repeat
       %dim 2: for each model
+      %dim 3: for each shading correction
     devianceTrainingArray;
     devianceTestArray;
     
@@ -34,20 +38,69 @@ classdef VarMeanCv < Experiment
   
   methods (Access = public)
     
+    %CONSTRUCTOR
     function this = VarMeanCv()
       this@Experiment();
     end
     
     %IMPLEMENTED: PRINT RESULTS
+    %Plots the training and test deviance for the different shading corrections and models
+    function printResults(this)
+      %get list of shading correction
+      shadingCorrectionNameArray = cell(this.nShadingCorrection,1);
+      for iShadingCorrection = 1:this.nShadingCorrection
+        shadingCorrectionNameArray{iShadingCorrection} = ...
+            this.scanArray{iShadingCorrection}.getShadingCorrectionStatus();
+      end
+
+      %plot the training and test deviance
+      for iStat = 1:2
+        isTrainingDeviance = iStat == 1;
+        if (isTrainingDeviance)
+          statName = 'training mean scaled deviance';
+        else
+          statName = 'test mean scaled deviance';
+        end
+
+        %plot the test deviance for each shading correction
+        fig = LatexFigure.sub();
+        legendArray = line(0,0);
+        for iShadingCorrection = 1:this.nShadingCorrection
[…]

### 2019-08-05 varmean/varmeancv/VarMeanCvAbsNoFilterDeg30.m

@@ -1,0 +1,11 @@
+classdef VarMeanCvAbsNoFilterDeg30 < VarMeanCv
+  
+  methods (Access = protected)
+    
+    function setup(this)
+      this.setup@VarMeanCv('AbsNoFilterDeg30', uint32(4034685242));
+    end
+    
+  end
+  
+end

### 2019-08-05 varmean/varmeancv/VarMeanCvAbsNoFilterLinear.m

@@ -1,12 +1,0 @@
-classdef VarMeanCvAbsNoFilterLinear < VarMeanCv
-  
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@VarMeanCv(AbsNoFilterDeg120(), uint32(889800029));
-      this.scan.addShadingCorrectorLinear();
-    end
-    
-  end
-  
-end

### 2019-08-05 varmean/varmeancv/varMeanCv.m

@@ -1,81 +1,11 @@
 experiments = {...
-  VarMeanCvAbsNoFilterNull();
-  VarMeanCvAbsNoFilterBw();
-  VarMeanCvAbsNoFilterLinear();
-  VarMeanCvAbsFilterNull();
-  VarMeanCvAbsFilterBw();
-  VarMeanCvAbsFilterLinear();
+  VarMeanCvAbsNoFilterDeg30();
+  VarMeanCvAbsNoFilterDeg120();
+  VarMeanCvAbsFilterDeg30();
+  VarMeanCvAbsFilterDeg120();
 };
 
 for i = 1:numel(experiments)
   experiments{i}.run();
-end
-
-%print results
-for iData = 1:2
-  
-  %get array of the same data but with different shading corrections
-  switch iData
-    case 1
-      experiments = {...
-        VarMeanCvAbsNoFilterNull();
-        VarMeanCvAbsNoFilterBw();
-        VarMeanCvAbsNoFilterLinear();
-      };
-    case 2
-      experiments = {...
-        VarMeanCvAbsFilterNull();
-        VarMeanCvAbsFilterBw();
-        VarMeanCvAbsFilterLinear();
-      };
-  end
-  
-  %use just an experiment to get properties of the experiment
-  this = experiments{1};
-  
-  %get list of shading correction
-  shadingCorrectionNameArray = cell(size(experiments));
-  for iShadingCorrection = 1:numel(shadingCorrectionNameArray)
-    shadingCorrector = experiments{iShadingCorrection}.scan.shadingCorrector;
-    if (isempty(shadingCorrector))
-      shadingCorrectionNameArray{iShadingCorrection} = 'null';
-    else
-      shadingCorrectionNameArray{iShadingCorrection} = shadingCorrector.getName();
-    end
-  end
-  
-  %plot the training and test deviance
-  for iStat = 1:2
-    isTrainingDeviance = iStat == 1;
-    if (isTrainingDeviance)
-      statName = 'training mean scaled deviance';
-    else
-      statName = 'test mean scaled deviance';
-    end
-    
-    %plot the test deviance for each shading correction
-    fig = LatexFigure.sub();
-    legendArray = line(0,0);
-    for iShadingCorrection = 1:numel(experiments)
-      boxplots = experiments{iShadingCorrection}. ...
-          printResults(-0.1 + ((iShadingCorrection-1)*0.1), isTrainingDeviance);
[…]

### 2019-08-05 reports/thesis/chapters/3_compoundPoisson.tex
compound poisson

@@
 \end{equation}
-It should be noted that $X=0$ if and only if $Y=0$ with probability $\prob(X=0)=\euler^{-\lambda}$.
-Then $X$ has probability mass at zero and probability density for positive numbers which results in the p.d.f.
+It should be noted that $X=0$ if and only if $Y=0$ and this happens with probability $\prob(Y=0)=\euler^{-\lambda}$.
+This implies that $X$ has probability mass at zero and probability density for positive numbers which results in the p.d.f.
 \begin{equation}
@@
 
-This chapter starts with a literature review on the compound Poisson distribution, how it is derived from the behaviour of photons, how its likelihood is evaluated and methods for fitting onto data.
+This chapter starts with a literature review on the compound Poisson distribution, how it is derived from the behaviour of photons, how its likelihood is evaluated and methods for fitting it onto data.
 A model was proposed for the pixel's grey values and the expectation-maximization (EM) algorithm was implemented to fit the model onto data.
@@
 \end{equation}
-where $\epsilon\sim\normal(a,\kappa)$, $b$ and $a$ are some constant and $\kappa$ is the variance of electronic noise. In a quantum counter, the mean and variance of the grey value are
+where $\epsilon\sim\normal(a,\kappa)$, $b$ and $a$ are some constant and $\kappa$ is the variance of electronic noise. The mean and variance of the grey value are
 \begin{equation}
@@
 This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation, yang2010noise} at different voltages and powers.
-It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
-The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.
+It was found there were two components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
+The electronic noise can be modelled using a Normal distribution \citep{xu2009electronic}.
 
@@
 The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.
-Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero.
-In other words, $\expectation[X^r]=M_X^{(r)}(\theta)$.
+Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting $\theta$ to zero.
+In other words, $\expectation[X^r]=M_X^{(r)}(0)$.
 Then it can be shown that
@@
 
-The m.g.f.~of $U$ is $M_U(\theta) = \left(\dfrac{\beta}{\beta-\theta}\right)^\alpha$. Then the m.g.f.~of $X$ is
+The m.g.f.~of $U$ is $M_U(\theta) = \left(\dfrac{\beta}{\beta-\theta}\right)^\alpha$, then the m.g.f.~of $X$ is
 \begin{equation}
@@
 by treating $W_y$ as a continuous and differentiable function of $y$.
-The derivation is shown in \ref{chapter:appendix_compoundPoissonSeries}.
+The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonSeries}.
 Because values of $y$ should be a positive integer, it would be appropriate to round the solution to $y_\text{max}$ accordingly
@@
 \end{equation}
-for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant was chosen to be
+for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant which was chosen to be
 \begin{equation}
@@
 $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
-Because the Normal and saddlepoint approximation does not support zero, the Q-Q plot was omitted for these approximations for small $\lambda$.
+Because the Normal and saddlepoint approximation does not support zero, the Q-Q plot was omitted for small $\lambda$.
 
@@
 
-For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}, \ref{fig:compoundPoisson_histogram_1_100_1}, \ref{fig:compoundPoisson_histogram_approx_1_1_1} and \ref{fig:compoundPoisson_histogram_approx_1_100_1}) there is a chance of simulating zeros.
+For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}, \ref{fig:compoundPoisson_histogram_1_100_1} and \ref{fig:compoundPoisson_histogram_approx}) there is a chance of simulating zeros.
 For $\lambda = 1$, the Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values.
 The saddlepoint approximation did capture the probability mass at zero as shown by an increase in probability density towards zero.
-For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough them.
+For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough to capture them.
 In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation or inversion of the c.d.f.
@@
     }
-    \caption{1\,000 simulations of a $\CPoisson(1,1,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
+    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
 In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
@@
     }
-    \caption{1\,000 simulations of a $\CPoisson(1,100,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
+    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
 In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
-        \caption{Normal approximation}
+        \caption{$\CPoisson(1,1,1)$ Normal approx.}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
-        \caption{Saddlepoint approximation}
-    \end{subfigure}
-    }
-    \caption{1\,000 simulations of a $\CPoisson(1,1,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
-In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
-    \label{fig:compoundPoisson_histogram_approx_1_1_1}
+        \caption{$\CPoisson(1,1,1)$ saddlepoint approx.}
+    \end{subfigure}
+    }
+    \vspace{1em}
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
+        \caption{$\CPoisson(1,100,1)$ Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
+        \caption{$\CPoisson(1,100,1)$ saddlepoint approx.}
+        \label{fig:compoundPoisson_histogram_approx_1_100_1}
+    \end{subfigure}
+    }
+    \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
+The dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_approx}
 \end{figure}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
-        \caption{Normal approximation}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
-        \caption{Saddlepoint approximation}
-    \end{subfigure}
-    }
-    \caption{1\,000 simulations of a $\CPoisson(1,100,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
-In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
-    \label{fig:compoundPoisson_histogram_approx_1_100_1}
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda10alpha1beta1.eps}
@@
     }
-    \caption{1\,000 simulations of a $\CPoisson(10,1,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.
+    \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
 On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
@@
     }
-    \caption{1\,000 simulations of a $\CPoisson(100,100,1)$ random variable were simulated and its empirical distribution is compared to the p.d.f.
+    \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
 On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
@@
 Parameter estimation can be done using gradient methods because the likelihood of the compound Poisson can be evaluated \citep{dunn2005series}.
-However, the EM algorithm is faster and the model is well set up for it.\citep{dempster1977maximum}.
+However, the EM algorithm is faster and the model is well set up for it.
 
@@
 \end{align}
-
 $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
@@
 The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable.
-Let $\left\{Y_1,Y_2,Y_3,\cdots, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\cdots, x_n\right\}$ be measurements of $X|Y$.
+Let $\left\{Y_1,Y_2,Y_3,\cdots, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\cdots, x_n\right\}$ be the respective measurements of $X|Y$.
 Define the joint log likelihood to be
@@
 The Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} can also be found by using a few approximations.
-However simulations show that these estimators struggle for high $\lambda$ and it will be shown that this will be the case for all estimators.
+However, simulations showed that these estimators struggle for high $\lambda$.
 
@@
 
-In the M step, the conditional expected joint log likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is then
+In the M step, the conditional expected joint log likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is
 \begin{align}
@@
 The results for $\CPoisson(1,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(10,1,1)$ and $\CPoisson(100,100,1)$ are shown in Figures \ref{fig:compoundPoisson_convergence_1}, \ref{fig:compoundPoisson_convergence_2}, \ref{fig:compoundPoisson_convergence_3} and \ref{fig:compoundPoisson_convergence_4} respectively.
-Good performance was observed in the $\lambda=1$ case with convergence of all 3 parameters within a step or two.
+Good performance was observed in the $\lambda=1$ case with convergence of all three parameters within a step or two.
 The Cram\'er-Rao lower bound captured the spread of the estimates well.
 
-However for $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log likelihood.
+For $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log likelihood.
 It appears the EM algorithm failed for $\lambda>10$ looking at these particular examples.
@@
 In particular in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ are stable while estimates of $\alpha$ and $\beta$ struggled to converge.
-This could be because as the compound Poisson-gamma random variable approach being Normal, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate and there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$.
+This could be because as the compound Poisson-gamma distribution approach the Normal distribution, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate because there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$ using the three parameters $(\lambda,\alpha,\beta)$.
 
@@
 \end{multline*}
-For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$. Firstly, using Stirling's approximation
-\begin{equation}
-  \ln\Gamma(n)\approx\ln(n!)\approx n\ln n-n
-\end{equation}
-then
+For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$.
+Firstly, using Stirling's approximation $\ln\Gamma(n)\approx\ln(n!)\approx n\ln n-n$ then
 \begin{equation}
@@
 \end{equation}
-The determinant of the Hessian matrix is then
+The determinant of the Hessian matrix is
 \begin{align*}
@@
 \end{align*}
-to get
+to obtain
 \begin{equation}
@@
 This results in a few things.
-Firstly $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ is singular thus its inverse cannot be evaluated, needed for the Newton-Raphson method.
+Firstly, $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ is singular thus its inverse cannot be evaluated which is needed for the Newton-Raphson method.
 Secondly, the sufficient conditions to classify a stationary point as a maximum are that the diagonal elements of the Hessian matrix are negative and the determinate is positive.
@@
 
-It was observed there is a saddle point in the log likelihood for the $\CPoisson(1,100,1)$ case. This is when the log likelihood increases and decreases. This suggest a possibility of a local maxima.
+It was observed there is a saddle point in the log likelihood for the $\CPoisson(1,100,1)$ case.
+This is when the log likelihood increased and decreased when varying $\alpha$ and $\beta$.
+This suggest a possibility of a local maxima.
 
@@
 
-All is not lost though, it was found there was a linear relationship between the variance and mean of the grey value in a pixel.
+All is not lost though, it was found there is a linear relationship between the variance and mean of the grey value in a pixel.
 This suggest the uncertainty can be predicted by using such a relationship.

### 2019-08-05 reports/thesis/book.tex
Front cover
compound poisson
Corrections in 3 and 4

@@
 \newcommand{\T}{^\textup{T}}
-\newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
+\newcommand{\dotdotdot}{\cdots}
 \newcommand{\BIC}{\mathrm{BIC}}
@@
 \centering
-{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications in Additive Manufacturing \par}
+{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications to Additive Manufacturing \par}
 \vspace{1cm}
@@
 {\Large Doctor of Philosophy in Statistics\par}
+\vfill
+\includegraphics[width = 0.75\textwidth]{../figures/frontCover.jpg}
 \vfill
@@
 This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1).
-I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar Martens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.
+I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar M\"{a}rtens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.
 

### 2019-08-05 reports/thesis/chapters/3_compoundPoisson.tex
Corrections in 3 and 4

@@
     \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
-In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
+In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
     \label{fig:compoundPoisson_histogram_1_1_1}
@@
     \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
-In a), the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency or frequency density.}
+In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
     \label{fig:compoundPoisson_histogram_1_100_1}
@@
     \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
-The dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+The dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
     \label{fig:compoundPoisson_histogram_approx}
@@
     \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
-On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
     \label{fig:compoundPoisson_histogram_10_1_1}
@@
     \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
-On the left, the dotted red line shows the $\Phi(\pm1)$ quantile of the expected frequency density.}
+On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
     \label{fig:compoundPoisson_histogram_100_1_1}

### 2019-08-05 reports/thesis/chapters/4_variancePrediction.tex
Corrections in 3 and 4

@@
-In the previous chapter, it was found that it was hard to fit a compound Poisson random variable onto the grey values directly itself.
+In the previous chapter, it was found that it was hard to fit a compound Poisson distribution onto the grey values.
 Results did show that the variance of the grey value has a linear relationship with the mean grey value.
@@
 
-In this chapter, generalised linear models \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} with different link functions and polynomial explanatory variables were selected using forward step-wise selection.
-These selected models were compared using cross validation to find the best model.
+In this chapter, generalised linear models \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} with different link functions and polynomial features were selected using forward step-wise selection.
+These selected models were compared using cross validation to find the best model and verified using residual analysis.
 
@@
 The sample variance-mean data were obtained from the replicated projections.
-Let $x_{x,y}^{(r)}$ be the grey value of the pixel at $(x,y)$ from the $r$th replicate projection for $r=1,2,3,\dotdotdot,n$.
+Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotdotdot,n$.
 The pixel sample mean is
 \begin{equation}
-    \overline{x}_{x,y}=\frac{1}{n}\sum_{r=1}^n x_{x,y}^{(r)}
+    \overline{x}_{i,j}=\frac{1}{n}\sum_{r=1}^n x_{i,j}^{(r)}
 \end{equation}
@@
 \begin{equation}
-    y_{x,y} =
+    y_{i,j} =
     \frac{1}{n-1}
@@
         \left(
-            x_{x,y}^{(r)} - \overline{x}_{x,y}
+            x_{i,j}^{(r)} - \overline{x}_{i,j}
         \right)^2
@@
 \end{equation}
-Only pixels in the region of interest (ROI) were considered here, that is pixels which represent the test sample.
+Only pixels in the region of interest (ROI) were considered here, that is pixels which represent the test sample. The ROI was created by manually segmenting the test sample from the projection.
 
-The aim is to model and predict the pixel variance given the pixel grey value by fitting a model onto the sample variance-mean data.
-No spatial information is used, thus the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\cdots,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
+The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by fitting a model onto the sample variance-mean data.
+No spatial information was used, thus the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\cdots,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
 Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$.
@@
 \end{equation}
-An example of a systematic component are polynomials $\eta(x)=\beta_0+\sum_{j=1}^{p-1}\beta_j x^j$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \beta_0+\sum_{j=1}^{p-1}\beta_j x^j$.
+There is also the log link $g(y)=\ln y$ but $y$ must be a unitless quantity, for example Poisson counts, for it to be comparable.
+Because $y$ is in units of $\SI{}{\adu^2}$, the log link is not used in this analysis.
+
+An example of a systematic component are polynomial features $\eta(x)=\beta_0+\sum_{j=1}^{p-1}\beta_j x^j$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \beta_0+\sum_{j=1}^{p-1}\beta_j x^j$.
 Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \cdots, \beta_{p-1}$ given data for the model to fit onto.
 
-Once the parameters have been estimated, prediction of the variance given a grey value $x$ is done using the expectation $\widehat{y}(x) = \expectation\left[Y(x)\right] = g^{-1}(\eta(x))$.
+Once the parameters have been estimated, prediction of the variance given a grey value $x$ is done by using $\widehat{y}(x) = g^{-1}(\widehat{\eta}(x))$ where $\widehat{\eta}(x)$ is the systematic component using the estimated parameters.
 
@@
 
-This section describes how forward stepwise selection \citep{friedman2001elements} was used to select which polynomials to use in the systematic component.
+This section describes how forward stepwise selection \citep{friedman2001elements} was used to select which polynomial features to use in the systematic component.
 
 In summary, forward stepwise selection fits a basic model to the data initially.
-A term is added to make the model more complicated at each step to improve the fit onto the data.
+A feature is added to make the model more complicated at each step to improve the fit onto the data.
 This is continued until the model cannot be improved subject to overfitting.
@@
 \end{equation}
-respectively where $p$ is the number of terms in the systematic component and $\ln L$ is the log likelihood of the GLM.
+respectively where $p$ is the number of features in the systematic component and $\ln L$ is the log likelihood of the GLM.
 The model with the lowest AIC or BIC is preferred.
@@
 In the initial step, a GLM with systematic component $\eta(x)=\beta_0$ is fitted and the criterion is recorded.
-In the next step, a polynomial term with one order higher is added to the systematic component $\eta(x)=\beta_0+\beta_1 x$, fitted and the criterion recorded.
-In addition, a polynomial term with one order lower is added $\beta(x)=\beta_{-1}x^{-1}+\beta_0$ and fitted separately with the criterion recorded.
+In the next step, a polynomial feature with one order higher is added to the systematic component $\eta(x)=\beta_0+\beta_1 x$, fitted and the criterion recorded.
+In addition, a polynomial feature with one order lower is added $\beta(x)=\beta_{-1}x^{-1}+\beta_0$ and fitted separately with the criterion recorded.
 The model which decreases the criterion the most is accepted.
 Adding higher and lower order polynomials to the systematic component is repeated, for example after accepting $\eta(x)=\beta_0+\beta_1 x$, the following systematic components $\eta(x)=\beta_0+\beta_1 x+\beta_2x^2$ and $\eta(x)=\beta_{-1}x^{-1}+\beta_0+\beta_1 x$ are fitted and assessed.
+The fitted parameters $\beta_0$ and $\beta_1$ may change when adding more terms.
 This is repeated until the criterion cannot be decreased and the procedure is left with the final model.
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{30}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{30}.
 The columns of the table represent different shading corrections used on the projections.
 Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
-The row labelled order shows the most common selected polynomial orders.
+`Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
 The error bars are the standard deviation from the 10 repeats.}
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{120}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{120}.
 The columns of the table represent different shading corrections used on the projections.
 Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
-The row labelled order shows the most common selected polynomial orders.
+`Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
 The error bars are the standard deviation from the 10 repeats.}
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}.
 The columns of the table represent different shading corrections used on the projections.
 Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
-The row labelled order shows the most common selected polynomial orders.
+`Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
 The error bars are the standard deviation from the 10 repeats.}
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial orders when fitting a GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{120}.
 The columns of the table represent different shading corrections used on the projections.
 Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
-The row labelled order shows the most common selected polynomial orders.
+`Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
 The error bars are the standard deviation from the 10 repeats.}
@@
 
-The results are shown in Tables \ref{table:meanVar_glmselect_absnofilterdeg30} and \ref{table:meanVar_glmselect_absnofilterdeg120} for \texttt{AbsNoFilter} and Tables \ref{table:meanVar_glmselect_absfilterdeg30} and \ref{table:meanVar_glmselect_absfilterdeg120} for for \texttt{AbsFilter}.
-The models selected all have only two terms and are quite simple.
+The results are shown in Tables \ref{table:meanVar_glmselect_absnofilterdeg30} and \ref{table:meanVar_glmselect_absnofilterdeg120} for \texttt{AbsNoFilter} and Tables \ref{table:meanVar_glmselect_absfilterdeg30} and \ref{table:meanVar_glmselect_absfilterdeg120} for \texttt{AbsFilter}.
+The models selected are quite simple and all have two features.
 Different shading correction or different criteria had no effect on the selected model.
@@
 Figures \ref{fig:meanVar_varMeanExample_AbsNoFilter} and \ref{fig:meanVar_varMeanExample_AbsFilter} shows the GLM fits for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively.
-The prediction intervals were obtained using the distribution $\widehat{Y}(x)\sim\gammaDist\left(\alpha, \dfrac{\alpha}{g^{-1}\left(\widehat{\eta}(x)\right)}\right)$ where $\widehat{\eta}(x)$ is the fitted systematic component.
+The prediction intervals were obtained using the distribution $\widehat{Y}(x)\sim\gammaDist\left(\alpha, \dfrac{\alpha}{g^{-1}\left(\widehat{\eta}(x)\right)}\right)$.
 The fits all looked reasonable except for \texttt{AbsNoFilter} at \ang{120} where the fit did not capture the inflection.
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_identity000010.eps}
-        \caption{$\widehat{y}(x)=\beta_0+\beta_1 x$ at \ang{30}}
+        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{30}}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_reciprocal000100.eps}
-        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{30}}
+        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{30}}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
-        \caption{$\widehat{y}(x)=\beta_0+\beta_1 x$ at \ang{120}}
+        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{120}}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
-        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{120}}
+        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{120}}
     \end{subfigure}
@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction.
-The red solid line shows the GLM fit along with $\Phi(\pm 1)$ prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the $\Phi(+1)-\Phi(-1)$ prediction interval as dashed lines.}
     \label{fig:meanVar_varMeanExample_AbsNoFilter}
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_identity000100.eps}
-        \caption{$\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
+        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_reciprocal000100.eps}
-        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
+        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{30}}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
-        \caption{$\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
+        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{120}}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
-        \caption{$\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
+        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
     \end{subfigure}
@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction.
-The red solid line shows the GLM fit along with $\Phi(\pm 1)$ prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the $\Phi(+1)-\Phi(-1)$ prediction interval as dashed lines.}
     \label{fig:meanVar_varMeanExample_AbsFilter}
@@
 
-Cross validation was performed on the datasets \texttt{AbsNoFilterDeg120} and \texttt{AbsFilterDeg120} with various different shading corrections.
+Cross validation was performed on the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} with various shading corrections.
 The models selected from forward step-wise selection in the previous section were assessed.
-They are $\widehat{y}(x)=\beta_0+\beta_1 x$ and $\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ using the identity link and $\widehat{y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ using the canonical link.
+They are ${y}(x)=\beta_0+\beta_1 x$ and ${y}(x)=\beta_{-1}x^{-1}+\beta_0$ using the identity link and ${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ using the canonical link.
 The analysis was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data.
@@
       \includegraphics[width=\textwidth]{../figures/varmean/VarMeanCvAbsNoFilterDeg120_testmeanscaleddeviance.eps}
-      \caption{\texttt{AbsFilter} at \ang{120}}
+      \caption{\texttt{AbsNoFilter} at \ang{120}}
   \end{subfigure}
@@
 The performance of the three candidate models were very similar.
-One exception is the model $\widehat{y}(x)=\beta_{-1}x^{-1}+\beta_0$ fitted onto the \texttt{AbsNoFilterDeg120} dataset, the mean scaled deviance was significantly larger and this is expected from a model not favoured in the forward step-wise selection in the previous section.
+One exception is the model ${y}(x)=\beta_{-1}x^{-1}+\beta_0$ fitted onto the \texttt{AbsNoFilter} dataset, the mean scaled deviance was significantly larger and this is expected from a model not favoured in the forward step-wise selection in the previous section.
 
-Shading correction, again, did not had an effect in the analysis.
+Shading correction did not had a significant effect in the analysis.
 
-From these results, it is recommended that the relationship $\widehat{y}(x)=\beta_0+\beta_1 x$ should be used for its simple form, similar performance to other candidate models and connections to the compound Poisson.
+From these results, it is recommended that the relationship ${y}(x)=\beta_0+\beta_1 x$ should be used for its simple form, similar performance to other candidate models and connections to the compound Poisson.
 
@@
 A residual analysis was conducted to look for anything overlooked.
-The model $\widehat{y}(x)=\beta_0+\beta_1 x$ was looked at here.
-A residual plot plots $r_i=y_i-\widehat{y}(x_i)$ for all $x_i$ in the dataset.
+The model ${y}(x)=\beta_0+\beta_1 x$ was analysed A residual plot plots $r_i=y_i-\widehat{y}(x_i)$ for all $x_i$ in the dataset.
 This was done using a 2D histogram.
@@
   \caption{Log frequency density histogram of the residuals given the mean grey value.
-The residuals are from fitting a gamma GLM of the form $\widehat{y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
-The dashed red line shows the $\Phi(\pm 1)$ predicted residual interval.}
+The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
+The dashed red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the predicted residual.}
   \label{fig:meanVar_residualGreyvalue}
@@
   }
-  \caption{Absolute value residuals from fitting a gamma GLM of the form $\widehat{y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
-Highlighted in a red box is an inflection.}
+  \caption{Absolute value residuals from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
+Highlighted in a red box is an example of an inflection.}
   \label{fig:meanVar_spatialResidual}
@@
 Because of the geometry of the test sample, lower grey values, thus smaller residuals, are found in the middle of the projection.
-Similarly higher grey values, thus bigger residuals, are found on the edges of the test sample.
+Similarly, higher grey values, thus bigger residuals, are found on the edges of the test sample.
 Considering that, the residuals do not show any striking spatial structure.
@@
 Various parametric models were investigated.
-A gamma GLM with identity and canonical link functions were looked at with different explanatory polynomials.
+A gamma GLM with identity and canonical link functions were looked at with different polynomial features.
 In terms of cross-validation, most of the models looked at have similar prediction performance when predicting the variance given a grey value.
@@
 
-Non-parametric and machine learning methods may be used in the prediction of variance for more flexible models.
-These models are flexible, however, they are slow and are unnecessary in a low dimensional problem with a large number of data points.
+More flexible models such as non-parametric and machine learning methods may be used, however, they are slow and are unnecessary in a low dimensional problem with a large number of data points.

### 2019-08-06 reports/thesis/chapters/3_compoundPoisson.tex
Added method of moments

@@
 \subsection{Compound Poisson-Gamma}
-
+\label{chapter:compoundPoisson_compoundPoissonGamma}
 A special case of the compound Poisson is when $U\sim\gammaDist\left(\alpha,\beta\right)$ where $\alpha>0$ is the gamma shape parameter and $\beta>0$ is the gamma rate parameter.
@@
 The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma random variable.
-Suppose $\widehat{\mu}$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
+Suppose $\widehat{\mu}_1$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
 Then the estimators
 \begin{equation}
-  \widehat{\lambda}=\frac{\widehat{\mu}^2\widehat{\mu}_2}{\left(2\widehat{\mu}_2^2-\widehat{\mu}_3\widehat{\mu}\right)}
-\end{equation}
-\begin{equation}
-  \widehat{\alpha}=\frac{\widehat{\mu}_3\widehat{\mu}-2\widehat{\mu}_2^2}{\widehat{\mu}_2^2-\widehat{\mu}\widehat{\mu}_3}
-\end{equation}
-\begin{equation}
-  \widehat{\beta}=\frac{\widehat{\mu}\widehat{\mu}_2}{\widehat{\mu}\widehat{\mu}_3-\widehat{\mu}_2^2}
+  \widehat{\lambda}=\frac{\widehat{\mu}_1^2\widehat{\mu}_2}{2\widehat{\mu}_2^2-\widehat{\mu}_1\widehat{\mu}_3}
+\end{equation}
+\begin{equation}
+  \widehat{\alpha}=\frac{2\widehat{\mu}_2^2-\widehat{\mu}_1\widehat{\mu}_3}{\widehat{\mu}_1\widehat{\mu}_3-\widehat{\mu}_2^2}
+\end{equation}
+\begin{equation}
+  \widehat{\beta}=\frac{\widehat{\mu}_1\widehat{\mu}_2}{\widehat{\mu}_1\widehat{\mu}_3-\widehat{\mu}_2^2}
 \end{equation}

### 2019-08-06 reports/thesis/chapters/3_compoundPoisson.tex
Added method of moments

@@
 \end{equation}
-are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}.
-These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}, this is shown in Appendix \ref{chapter:appendix_methodofmoments} These estimators suffer because estimation is not done through the suf.ficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
 

### 2019-08-06 reports/thesis/chapters/3_compoundPoisson.tex
Added method of moments

--- 2019-08-06 reports/thesis/chapters/3_compoundPoisson.tex
@@
 \end{equation}
-are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}.
-These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}, this is shown in Appendix \ref{chapter:appendix_methodofmoments} These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
 

### 2019-08-08 reports/thesis/chapters/3_compoundPoisson.tex
inference chapter
subroi for more projections
use of dotsc
plot sub roi section

@@
 The compound Poisson distribution is studied here because of the compound Poission-like behaviour from the detection of photons \citep{whiting2002signal, elbakri2003efficient, whiting2006properties}.
-It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.) $\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!}$ for $y=0,1,2,\cdots$, where $\lambda>0$ is the Poisson rate parameter.
-Let $U_i$ be some independent and identically distributed (i.i.d.) latent random variables with probability density function (p.d.f.) $p_U(u)$ for $i=1,2,3,\cdots$.
+It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.) $\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!}$ for $y=0,1,2,\dotsc$, where $\lambda>0$ is the Poisson rate parameter.
+Let $U_i$ be some independent and identically distributed (i.i.d.) latent random variables with probability density function (p.d.f.) $p_U(u)$ for $i=1,2,3,\dotsc$.
 Let $X$ be a compound Poisson random variable where
@@
 Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$.
-Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\cdots$.
+Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\dotsc$.
 $U_i$ has p.d.f.~$p_U(u)$.
@@
 The evaluation of the p.d.f.~using the saddlepoint approximate required a bit of caution to avoid over/underflow problems.
-Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\cdots,x_n\right\}$.
+Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
 The saddlepoint approximation was computed up to a constant using
@@
   k =
-  \max_{i\in\left\{1,2,3,\cdots,n\right\}}
+  \max_{i\in\left\{1,2,3,\dotsc,n\right\}}
   \left[
@@
 \end{equation}
-then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\cdots,\frac{n-0.5}{n}$.
+then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotsc,\frac{n-0.5}{n}$.
 If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin.
@@
 
-The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\cdots,x_n\right\}$.
+The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
 The use of the EM algorithm here for the compound Poisson is similar to \cite{elbakri2003statistical, xu2009electronic}.
@@
 The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable.
-Let $\left\{Y_1,Y_2,Y_3,\cdots, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\cdots, x_n\right\}$ be the respective measurements of $X|Y$.
+Let $\left\{Y_1,Y_2,Y_3,\dotsc, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\dotsc, x_n\right\}$ be the respective measurements of $X|Y$.
 Define the joint log likelihood to be
@@
 \begin{equation}
-  W_y^{(r)} = y^r W_y \quad \text{for }r=1,2,3,\cdots
+  W_y^{(r)} = y^r W_y \quad \text{for }r=1,2,3,\dotsc
 \end{equation}
@@
 \end{equation}
-Keep in mind that $y=1,2,3,\cdots$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
+Keep in mind that $y=1,2,3,\dotsc$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
 \begin{equation}
@@
 \end{equation}
-Therefore the maximum of $W_y^{(r)}$ is located at $y_\text{max}$ for all $r=0,1,2,\cdots$.
+Therefore the maximum of $W_y^{(r)}$ is located at $y_\text{max}$ for all $r=0,1,2,\dotsc$.
 The same method of evaluating $W_y$ can be used to evaluate $W_y^{(r)}$.
-For a given $r=0,1,2,\cdots$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
+For a given $r=0,1,2,\dotsc$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
 The limits will be different for different values of $r$.

### 2019-08-08 reports/thesis/chapters/4_variancePrediction.tex
inference chapter
subroi for more projections
use of dotsc
plot sub roi section

@@
 The sample variance-mean data were obtained from the replicated projections.
-Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotdotdot,n$.
+Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotsc,n$.
 The pixel sample mean is
@@
 The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by fitting a model onto the sample variance-mean data.
-No spatial information was used, thus the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\cdots,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
+No spatial information was used, thus the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
 Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$.
@@
 An example of a systematic component are polynomial features $\eta(x)=\beta_0+\sum_{j=1}^{p-1}\beta_j x^j$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \beta_0+\sum_{j=1}^{p-1}\beta_j x^j$.
-Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \cdots, \beta_{p-1}$ given data for the model to fit onto.
+Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \dotsc, \beta_{p-1}$ given data for the model to fit onto.
 
@@
 More flexible models such as non-parametric and machine learning methods may be used, however, they are slow and are unnecessary in a low dimensional problem with a large number of data points.
+
+With the ability to predict the variance given a grey value of a pixel, the uncertainty can be quantified.
+In the next chapter, the projection is compared to a simulated projection under the face of that uncertainty.

### 2019-08-08 reports/thesis/chapters/5_inference.tex
inference chapter
subroi for more projections
use of dotsc
plot sub roi section

@@
-Disagreement between the scan and \texttt{aRTist} can be found by subtracting one image from the other, any values too big in magnitude can be considered as a defect.
+Disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other, any values too big in magnitude can be considered as a defect.
 However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance.
@@
 
-A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic is
+A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ was calculated for all pixels at $(x,y)$. This test statistic is
 \begin{equation}
@@
   \dfrac{
-    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
-  }
-  {
-    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
-  }
-\end{equation}
-where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.
-Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal.
-Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
+    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
+  }
+  {
+    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
+  }
+\end{equation}
+where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.
+For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution.
+Thus by treating the simulated projection from \emph{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
 \begin{equation}
@@
 
-The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample.
-These replicated x-ray images were manually segmented.
-This provided variance-mean data and was used to train the variance model, such as a gamma distributed GLM.
-The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model.
-The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.
-
-The 20 x-ray images were spilt into 2.
-19 images were used to train the variance-mean model.
-One image, called the test image, was used to compare with \texttt{aRTist}.
-In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.
-The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
-
-\begin{figure}
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+To illustrate this method of inference, the projections from the dataset \texttt{AbsFilter} at \ang{120} was used.
+To recap, replicate projections of a test sample with purposefully manufactured voids were obtained.
+\emph{aRTist} was used to create a simulation of that projection but as if the voids were not there.
+Thus the method should pick these voids up.
+
+A projection and the \emph{aRTist} projection is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
+The 20 replicate projections were spilt into two.
+19 randomly selected projections were used for the variance-mean model to fit onto.
+A gamma GLM with a basic linear relationship was used.
+The remaining projection was compared with the \emph{aRTist} projection, the variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.
+
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
@@
   }
-  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids.
+  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect the purposefully manufactured voids.
 The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level.
@@
 For each pixel, a test statistic was calculated.
-A test statistic too large in magnitude will classify that pixel as a positive result.
+A test statistic too large in magnitude, relative to the anticipated variance, will classify that pixel as a positive result.
 In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
@@
 The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}.
-It can be seen that the majority of the test statistics does not look Normal.
-Also the majority of the $p$-values does not look uniformly distributed.
+It can be seen that the majority of the test statistics does come from a Normal distribution.
+Also, the majority of the $p$-values are not look uniformly distributed.
 This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.
 
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
@@
 It can be shown that $\alpha$ controls the false positive rate.
-$\alpha=5.0\%$ is a typical choice and was used throughout this thesis.
+$\alpha=5.0\%$ is a typical choice and is used throughout this thesis.
 Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.
@@
 Multiple hypothesis testing occurs when there are more than one hypotheses to test.
-For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$.
-The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$.
-Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.
+For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$.
+The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,n$.
+Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_n$.
 
@@
 
-\begin{table}[htp]
+\begin{table}
   \centering
@@
 \end{equation}
-However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives.
+However, in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives.
 This is because the correction traded too many false positives for false negatives.
@@
 It adapts to the data and choose different sizes for different data.
-The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$.
+The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(n)}$.
 Suppose a size $\alpha$ is provided beforehand.
-The size is then adjusted to
+The size is adjusted to
 \begin{equation}
@@
 \end{equation}
-This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive.
+This test the statistics with $p$-values $p_{(1)},p_{(2)},\dotsc,p_{(k)}$ as positive.
 For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
@@
 
-\begin{table}[htp]
+\begin{table}
     \centering
@@
 Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}.
-The distribution of the test statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$.
-Almost half of the pixels were tested positive.
+The distribution of the test statistics appeared Normal but not centred at zero.
+So by using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$, almost half of the pixels were tested positive.
 It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
@@
 Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively.
-The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\cdots,n$.
+The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\dotsc,n$.
 
@@
 Taking derivatives
-\begin{equation}
-  \dfrac{\partial}{\partial z} \ln p_{Z}(z) =
+\begin{align}
+  \dfrac{\partial}{\partial z} \ln p_{Z}(z) &=
   -\left(
@@
   \right)
-\end{equation}
-\begin{equation}
-  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) =
+  \nonumber\\
+  &=
   -\dfrac{
@@
   }
-\end{equation}
+\end{align}
 which motivates the estimator \citep{efron2004large}
@@
   \ .
+  \label{eq:inference_nullStdEstimator}
 \end{equation}
@@
 There exist various methods for the empicial null.
-\cite{schwartzman2008empirical} uses Poisson regression on the histogram counts in regions where the null statistics dominate.
+\cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate.
 The empirical characteristic function was used in \cite{jin2007estimating}.
@@
 
-Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+Returning back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
 The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
@@
 \end{equation}
-where $h$ is the bandwidth. The bandwidth was chosen such that
+where $h$ is the bandwidth and $phi(x)$ is the standard Normal density. The bandwidth was chosen such that
 \begin{equation}
@@
 \end{equation}
-where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range.
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
+where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range. This bandwidth is justified later on in this section.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\subSize]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
   \caption{The density of the test statistics was estimated using a kernel density estimate.
@@
 
-The null parameters were estimated.
 The null mean was estimated by numerically finding the mode of the density estimate.
-The null standard deviation was estimated using the curvature of the density estimate at the mode.
-This resulted in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
+The null standard deviation was estimated using Equation \eqref{eq:inference_nullStdEstimator}.
+This results in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
 In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.
@@
 
-The test statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
+The test statistics were normalised to $T_1,T_2,\dotsc,T_n$ by using
 \begin{equation}
@@
 \end{equation}
-for $i=1,2,\cdots,n$. The normalised $p$-values were obtained by using
+for $i=1,2,\dotsc,n$. The normalised $p$-values were obtained by using
 \begin{equation}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullHistogram.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullPValues.eps}
-        \caption{$p$ values}
-    \end{subfigure}
-    }
-    \caption{The critical regions and $p$-values were adjusted using the empirical null in the sub-image example.}
+        \caption{$p$-values}
+    \end{subfigure}
+    }
+    \caption{Histogram of the test statistics from the sub-image in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+Also shown are the critical regions and $p$-values which were adjusted using the empirical null.}
     \label{fig:inference_inferenceSubsample1_nullResults}
@@
 
-No positive results were found and the $p$-values were sensible as they looked uniformly distributed.
-This demonstrated that the empirical null adjusted the parameters of the null distribution to fit the majority of the data in order to make sensible inference.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+No positive results were found and the $p$-values were sensible as they resemble the uniformly distribution.
+This demonstrated that the empirical null adjusted the parameters of the null distribution to fit onto the majority of the data in order to make sensible inference.
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_zImage.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_subimagePositive.eps}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullHistogram.eps}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullPValues.eps}
@@
 It can be seen that the null distribution was not centred at zero, however the empirical null took it into account.
-The estimation of the empirical null parameters were robust as it only depended on the density estimate at the mode only, it should not be affected by non-null test statistics.
+The estimation of the empirical null parameters were robust as it depends on the density estimate at the mode only, it should not be affected by non-null test statistics.
 
@@
 
-The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$.
-This cannot be solved in closed form easily and was done numerically.
-The  Newton-Raphson method can be used to solve $\hat{p}_Z'(z) = 0$ for $z$.
-Instead the log space was used, solving
+The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$ numerically. The Newton-Raphson method was used to solve
 \begin{equation}
@@
 \end{equation}
-for $z$. This at least find stationary points.
-
-The Newton-Raphson method is an iterative algorithm and requires an initial value $z^{(0)}$. The iterative step is
+for $z$ which finds stationary points. The method is an iterative algorithm and requires an initial value $z^{(0)}$. The iterative step is
 \begin{equation}
@@
 \end{equation}
-for $r=0,1,2,3,\cdots$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is $\widehat{p}_Z(z)=
+for $r=0,1,2,3,\dotsc$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is $\widehat{p}_Z(z)=
   \frac{1}{nh}
@@
 Further initial values were generated by sampling from $\normal(z^{(0)}, s_z^2)$.
-This was done multiple times until 3 valid solutions were obtained.
+This was done multiple times until three valid solutions were obtained.
 The best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of all the different initial values was used as the final answer.
@@
 It appeared for a given $n$, there exist a bandwidth which minimise the median squared error.
-However the rules of thumb did not optimise for $\widehat{\sigma}_0$ and undershot it.
+The rules of thumb did not optimise for $\widehat{\sigma}_0$ and undershot it.
 Figure \ref{fig:inference_BandwidthSelection_error3} shows the median of the estimates of $\sigma_0$.
@@
 
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
       \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
@@
 
-\begin{figure}[htp]
-  \centering
-    \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error3.eps}
@@
 A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimised the log squared error for a given $n$.
-\texttt{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures.
-The optimisation was done using \texttt{MATLAB}'s gradient free \texttt{fminsearch} function, using $h=0.9n^{-1/5}$ as the initial value.
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+\emph{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures.
+The optimisation was done using \emph{MATLAB}'s gradient free \texttt{fminsearch} function, using $h=0.9n^{-1/5}$ as the initial value.
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot1.eps}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot51.eps}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot100.eps}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot150.eps}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot199.eps}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot249.eps}
@@
     }
-    \caption{A smoothing spline was fitted on the log squared error for estimating $\sigma_0$ against the bandwidth.
-Boxplots represent the variation of the error from 100 repeats.
+    \caption{A smoothing spline was fitted on the log squared error for estimating $\sigma_0$ on $n$ simulated standard Normal random variables.
+The bandwidth was varied.
+The experiment was repeated by simulating the standard Normal random variables again.
+The boxplots represent the variation of the error from the 100 repeats.
 The red dashed line shows the bandwidth which minimised the fitted spline.}
@@
 The method used in fitting the smoothing spline could contribute to the underfitting.
-For example if the smoothing spline was not smooth enough so that local minima appeared, it would add variance to the location of the optimal bandwidth.
+For example if the smoothing spline was not smooth enough so that multiple local minimums appeared, it would add variance to the location of the optimal bandwidth if the optimisation algorithm converges to a local minimum.
 A basic linear relationship was chosen to avoid overfitting and keep the rule of thumb simple.
@@
     \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullMean.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullMean.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullMean.eps}
@@
     \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
@@
       \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMadMode_nullStd.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullStd.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullStd.eps}
@@
     \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullMean.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullMean.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullMean.eps}
@@
     \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
@@
       \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMadMode_nullStd.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullStd.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullStd.eps}
@@
 
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
@@
 
-The problem was that the empirical distribution of the test statistics did not look Normal.
+The problem was that the empirical distribution of all of the test statistics looked like it did not came from a Normal distribution.
 It appeared that the test statistics varied spatially, suggesting the empirical null varied spatially as well.
-One possible reason is because it looked like the value of the test statistics depended on which surface it was on for example.
-
-One possible extension to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
+To account for the spatially variability of the null parameters, one possible extension is to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
 There are problems with this though.
 The first problem is that how the grid is overlaid can be arbitrary, for example the grid can be translated to produce different sections.
-Secondly it is not clear how to combine the results from each section together \citep{efron2008simultaneous}.
+Secondly, it is not clear how to combine the results from each section together \citep{efron2008simultaneous}.
 
@@
 \end{equation}
-for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Define the null hypotheses to be
+for $x=1,2,\dotsc,W$ and $y=1,2,\dotsc,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Define the null hypotheses to be
 \begin{equation}
@@
 The empirical null filter uses the empirical null on neighbouring pixels to estimate the null parameters.
-To estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel of radius $r$ was centred at $(x,y)$.
-All the pixels captured by the circular kernel were used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
-\begin{align}
-  \widehat{\mu}_{0,x,y}
-  &=
-  \widehat{\mu}_{0,x,y}
-    \left(
-      \text{all }Z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
-    \right)
-\\
-  \widehat{\sigma}_{0,x,y}
-  &=
-  \widehat{\sigma}_{0,x,y}
-    \left(
-      \text{all }Z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
-    \right)
-  \ .
-\end{align}
-Using these estimates, the test statistics were normalised using
+To estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel $C_r(x,y)$ of radius $r$ was centred at $(x,y)$.
+All the pixels captured by the circular kernel and the ROI were used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
+\begin{equation}
+  \widehat{\mu}_{0,x,y} = \argmax\widehat{p}_{Z_{x,y}}(z)
+\end{equation}
+\begin{equation}
+  \widehat{\sigma}_{0,x,y} = \left[
+    \left.
+      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
+    \right|_{z=\widehat{\mu}_{0,x,y}}
+  \right]^{-1/2}
+\end{equation}
+where the density estimate is
+\begin{equation}
+\widehat{p}_{Z_{x,y}}(z) = 
+\frac{1}{nh}
+  \sum_{i,j\in K_{x,y}}\phi\left(
+    \dfrac{z_{i,j}-z}{h}
+  \right)
+\end{equation}
+and $K_{x,y} = C_r(x,y) \cap \text{ROI}$. Using these estimates, the test statistics were normalised using
 \begin{equation}
@@
 The disadvantage of using the local normalization filter for estimating the null parameters is that it uses a Gaussian filter.
-This is a type weighted mean which won't be robust to non-null statistics.
+This is a type weighted mean which is not robust to non-null statistics.
 In addition, the two Gaussian filters can have different radiuses, it is not clear how to set them.
@@
 
-The empirical null filter was implemented in an open source software called \texttt{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \texttt{GitHub} \citep{imagej2018rank}.
+The empirical null filter was implemented in an open source software called \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \emph{GitHub} \citep{imagej2018rank}.
 This class implemented filters, such as the mean filter and median filter, using a circular kernel, making this a suitable framework for the empirical null filter.
-Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \texttt{Fiji} \citep{schindelin2012fiji}, a distribution of \texttt{ImageJ}.
+Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \emph{Fiji} \citep{schindelin2012fiji}, a distribution of \emph{ImageJ}.
 
@@
     \includegraphics[width=\textwidth]{../figures/inference/fiji/gui.png}
-    \caption{Graphical user interface of the empirical null filter in \texttt{Fiji}.
+    \caption{Graphical user interface of the empirical null filter in \emph{Fiji}.
 The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate.
@@
 
-As a test, the empirical null filter with $r=5$ was used on a \texttt{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
+As a test, the empirical null filter with $r=5$ was used on a \emph{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
 It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it did verify that the filter worked on arbitrary images with some computational considerations.
@@
 The empirical null mean created an impasto effect and preserved edges which is similar to the result in \cite{griffin2000mean}.
-Spread filters such as the standard deviation filter can be used to detect edges.
+Dispersion filters such as the standard deviation filter can be used to detect edges.
 Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation.
-The resulting images were similar but it was notable that the edges in the empirical null standard deviation were sharper, suggesting that the empirical null standard deviation is a more robust measure of spread compared to the standard deviation.
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+The resulting images were similar but it was notable that the edges in the empirical null standard deviation were sharper, suggesting that the empirical null standard deviation is a more robust measure of dispersion compared to the standard deviation.
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/bridgeFilter.png}
@@
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/mean.png}
@@
     \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/median.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/nullMean.png}
@@
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/std.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/fiji/nullStd.png}
@@
 
-When using the the empirical null filter in \texttt{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
+When using the the empirical null filter in \emph{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
 Here the user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
@@
 
-When the kernel captures pixels outside the boundary of the image or region of interest (ROI), \texttt{RankFilters} uses nearest pixel padding which fills in pixels outside the ROI with values to the nearest pixels.
+When the kernel captures pixels outside the boundary of the image or ROI, \texttt{RankFilters} uses nearest pixel padding which fills in pixels outside the ROI with values to the nearest pixels.
 Figure \ref{fig:inference_padding_nearest} shows an example of nearest pixel padding on the top left corner of a rectangle ROI.
@@
 
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{\subSize}
       \begin{tabular}{lllllll}
          $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
-         $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
-         $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\ \cline{4-6}
-         $\cdots$ & $z_{1,1}$ & \multicolumn{1}{l|}{$z_{1,1}$} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
-         $\cdots$ & $z_{2,1}$ & \multicolumn{1}{l|}{$z_{2,1}$}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
+         $\dotsc$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\dotsc$ \\
+         $\dotsc$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\dotsc$ \\ \cline{4-6}
+         $\dotsc$ & $z_{1,1}$ & \multicolumn{1}{l|}{$z_{1,1}$} & $z_{1,1}$ & $z_{1,2}$ & $\dotsc$ \\
+         $\dotsc$ & $z_{2,1}$ & \multicolumn{1}{l|}{$z_{2,1}$}  & $z_{2,1}$ & $z_{2,2}$ & $\dotsc$ \\
          $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
       \begin{tabular}{lllllll}
          $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
-         $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\
-         $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\ \cline{4-6}
-         $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
-         $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
+         $\dotsc$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\dotsc$ \\
+         $\dotsc$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\dotsc$ \\ \cline{4-6}
+         $\dotsc$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}} & $z_{1,1}$ & $z_{1,2}$ & $\dotsc$ \\
+         $\dotsc$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}}  & $z_{2,1}$ & $z_{2,2}$ & $\dotsc$ \\
          $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
@@
 The statistical moments before and after filtering should be the same and were investigated.
-Because the empirical null mean and empirical null standard deviation are random variables with some distribution, the filtered pixels will never be Normal and any Normality tests would be too strict for the purpose of this experiment.
+Because the empirical null mean and empirical null standard deviation are random variables with some distribution, the filtered pixels will never be Normal and any normality tests would be too strict for the purpose of this experiment.
 
 \emph{Contamination} is defined as some smooth and slowly varying function added and/or multiplied to an image.
-When contaminating a Gaussian image, it may cause errors in hypothesis testing if the null distribution was incorrectly specified as standard Normal.
+Contaminating a Gaussian image may cause errors in hypothesis testing if the null distribution was incorrectly specified as standard Normal.
 In this experiment, the contamination was a gradient such that the pixel at position $(x,y)$ have a value distributed as $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_{0,x,y}^2)$ where
@@
 
-\begin{figure}[p]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_beforeFilter.eps}
-    \caption{Unfiltered}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_afterFilter.eps}
-    \caption{Filtered}
-    \label{fig:inference_allNullGaussianScript_afterFilter}
-  \end{subfigure}
-  }
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullMean.eps}
-    \caption{Empirical null mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullStd.eps}
-    \caption{Empirical null std}
-  \end{subfigure}
-  }
-  \caption{A $256\times 256$ Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
-  \label{fig:inference_allNullGaussianScript}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_beforeFilter.eps}
-    \caption{Unfiltered}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_afterFilter.eps}
-    \caption{Filtered}
-    \label{fig:inference_allNullPlaneScript_afterFilter}
-  \end{subfigure}
-  }
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullMean.eps}
-    \caption{Empirical null mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullStd.eps}
-    \caption{Empirical null std}
-  \end{subfigure}
-  }
-  \caption{A $256\times 256$ contaminated Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
-  \label{fig:inference_allNullPlaneScript}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_pValue.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_pValue.eps}
@@
 
+\begin{figure}[p]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_beforeFilter.eps}
+    \caption{Unfiltered}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_afterFilter.eps}
+    \caption{Filtered}
+    \label{fig:inference_allNullGaussianScript_afterFilter}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullMean.eps}
+    \caption{Empirical null mean}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullStd.eps}
+    \caption{Empirical null std}
+  \end{subfigure}
+  }
+  \caption{A $256\times 256$ Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
+  \label{fig:inference_allNullGaussianScript}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_beforeFilter.eps}
+    \caption{Unfiltered}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_afterFilter.eps}
+    \caption{Filtered}
+    \label{fig:inference_allNullPlaneScript_afterFilter}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullMean.eps}
+    \caption{Empirical null mean}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullStd.eps}
+    \caption{Empirical null std}
+  \end{subfigure}
+  }
+  \caption{A $256\times 256$ contaminated Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
+  \label{fig:inference_allNullPlaneScript}
+\end{figure}
+
 An example of a Gaussian image with/without contamination before/after filtering are shown in Figures \ref{fig:inference_allNullGaussianScript} and \ref{fig:inference_allNullPlaneScript}.
 In the contaminated example, the filter managed to estimate the null mean, picking up the gradient.
-This enabled the normalised image to look flat to remove the contamination.
+This enabled the filtered image to look flat and removed the contamination.
 The $p$-values after filtering are shown in Figure \ref{fig:inference_allNull_pValues}.
-A quick inspection suggest that the filtered pixels looked reasonably Normal for this particular example.
+A quick inspection suggest that the filtered pixels appeared reasonably Normal for this particular example.
 
@@
 
-\begin{table}[ht]
+\begin{table}
   \centering
@@
   \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_mean.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_mean.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_mean.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_mean.eps}
@@
   \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_variance.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_variance.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_variance.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_variance.eps}
@@
   \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_kurtosis.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_kurtosis.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_kurtosis.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_kurtosis.eps}
@@
   \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_mean.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_mean.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_mean.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_mean.eps}
@@
 
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_variance.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_variance.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_variance.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_variance.eps}
@@
 
-\begin{figure}[htp]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{0.49\textwidth}
+\begin{figure}
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_kurtosis.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_kurtosis.eps}
@@
   \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_kurtosis.eps}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.49\textwidth}
+  \begin{subfigure}[b]{\subSize}
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_kurtosis.eps}
@@
 \afterpage{\clearpage}
-\subsection{Detecting Defects Experiment}
+\subsection{Detection of Simulated Defects}
 
@@
 A line defect assign columns of pixels to be non-null, a kernel would only capture a section of defect.
-Different shapes were used such as a square defect.
-With a square defect, a kernel can capture the entire defect if its radius is large enough.
+A square defect was also investigated and a kernel can only capture the entire defect if its radius is large enough.
 
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imagePreContaminated.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageContaminated.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageFiltered.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_nullStd.eps}
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
+In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectDustExample}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imagePreContaminated.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageContaminated.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageFiltered.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_nullStd.eps}
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
+In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectLineExample}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imagePreContaminated.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageContaminated.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageFiltered.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_nullMean.eps}
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
+In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectSquareExample}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imagePreContaminated.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageFiltered.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_nullMean.eps}
@@
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-Highlighted in red are pixels tested as positive at the 5\% FDR level.}
+In a) and c),
+  highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectSquare2Example}
@@
 An example of a speckle defected image is shown in Figure \ref{fig:inference_defectDustExample}, the figure also shows the image contaminated and then filtered.
-The contamination caused some systematic errors in hypothesis testing, such as an increase of positive pixels and in particular in two of the corners of the image.
-The empirical null filter recovered the image from the contaminated image so that appropriate inference was done.
-However some statistical power was lost in the filtered image.
-This is because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
+Without filtering, the top-left and bottom-right of the contaminated image have large, in magnitude, test statistics.
+In these areas, a lot of pixels would be detected as falsely positive.
+By using the empirical null filter, the resulting filtered image reassemble the uncontaminated image and appropriate inference can be done on the filtered image.
+However, some statistical power was lost when conducting inference on the filtered image because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
 This cannot be avoided as areas of high empirical null standard deviation was due to the sampling error.
@@
 Figure \ref{fig:inference_defectSquareExample} filtered the contaminated image using a kernel radius of $r=20$, while Figure \ref{fig:inference_defectSquare2Example} used a kernel radius of $r=40$.
-With $r=20$, the kernel is smaller than the square defect, therefore the defect was treated as the null and this evident in the empirical null mean.
+With $r=20$, the kernel is smaller than the square defect, therefore the defect was treated as the null.
+This is evident because the empirical null mean captured the defect.
 This resulted in difficulty detecting the defect.
 With $r=40$, the kernel is bigger than the defect and treated the defect as non-null.
-The empirical null filter recovered the gradient in the empirical null which was then used for normalisation.
+In this scenario, the empirical null filter recovered the gradient in the empirical null which was then used for normalisation.
 
@@
 The ROC curve is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds.
-The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
+The area under the ROC curve (AUC) is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}.
 Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed thoroughly in \cite{cook2007use}.
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
+\begin{figure}
+  \centering
+    \centerline{
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_roc.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_roc.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_roc.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_roc.eps}
@@
 
-In terms of the area under the ROC curves, the empirical null filter improved the performance over using the unfiltered contaminated image.
+In terms of AUC, the empirical null filter improved the performance over using the unfiltered contaminated image.
 The performance before contamination cannot be recovered but it was an improvement.
@@
 
-The ROC considers all thresholds or specificities used in the hypothesis testing.
-However in the previous experiment, it was found there was some variance mismatch before and after filtering with regards to the test statistics.
+\subsection{Speckle Defect Experiment}
+
+The ROC curves considers all thresholds or specificities used in the hypothesis testing.
+In the previous experiment, it was found there was some variance mismatch before and after filtering with regards to the test statistics.
 As a result, for a given threshold such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
@@
 The image was than contaminated and tested to obtain the 4 measurements again.
-This was repeated 300 times to obtain the empirical distribution of the ROC area, type 1 error, type 2 error and FDR when testing on a un/contaminated image with defects.
+This was repeated 300 times to obtain the empirical distribution of the AUC, type 1 error, type 2 error and FDR when testing on a un/contaminated image with defects.
 The ROC area, type 1 error, type 2 error and FDR were measured when testing on a filtered contaminated image with defects, a kernel radius of $r=20$ was used and was repeated 100 times.
 
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
+\begin{figure}
+  \centering
+    \centerline{
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+        \caption{AUC}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
@@
     }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
-a) shows the ROC area when testing the image before/after contamination and after filtering.
+  \caption{AUC and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
+a) shows the AUC when testing the image before/after contamination and after filtering.
 In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
@@
 The results are shown in Figure \ref{fig:inference_DefectSimulationDust}.
-The ROC areas quantified showed that using the filter improved the performance of the test from the contamination.
+The AUC quantified showed that using the filter improved the performance of the test from the contamination.
 The type 1 error, or specificity, did decreased after filtering.
@@
 
+\subsection{Optimal Kernel Radius Experiment}
+
 There is the question of what kernel size to choose for a given defect.
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+        \caption{AUC}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type1.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type2.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_fdr.eps}
@@
     }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses.
+  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses.
 The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
-        \caption{ROC area}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+        \caption{AUC}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
@@
     }
-  \caption{ROC area and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
+  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
 The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
@@
 An experiment was conducted where the contaminated defected image were filtered for various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
-Hypothesis testing was done on the uncontaminated and filtered contaminated image and the area under the ROC curve and various errors were recorded, this was repeated 100 times.
-The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.
+Hypothesis testing was done on the uncontaminated and filtered contaminated image and the AUC and various errors were recorded, this was repeated 100 times.
+The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.
 Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.
 
-The results showed that the ROC area increased with kernel radius.
+The results showed that the AUC increased with kernel radius.
 This highlighted that a kernel with a good radius can performance almost as though there was no contamination.
-It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
+It also appeared that the optimal AUC was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
 
@@
 \section{Results}
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius2.txt}$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius3.txt}$}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_z.eps}
-        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$}
-      \end{subfigure}
-    }
-  \caption{Filtered $z$ image from the \texttt{Sep16 120deg} dataset. Various kernel radiuses were used.}
-  \label{fig:inference_AbsFilterDeg120_zfiltered}
-\end{figure}
+The empirical null filter has been developed and tested thoroughly on simulated images.
+In this section, the filter is applied to the projections in the \texttt{AbsFilter} and \texttt{TiFilter} datasets.
+
+\subsection{ABS Test Sample}
 
@@
     \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
@@
       \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$.
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
     \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_sig.eps}
-        \caption{Image with positive pixels}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius2.txt}$.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_AbsFilterDeg120_inference_radius2}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_sig.eps}
-        \caption{Image with positive pixels}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius3.txt}$.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
-  \label{fig:inference_AbsFilterDeg120_inference_radius3}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
@@
       \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
+      \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
@@
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
@@
     }
-  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$.
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 
-The empirical null filter was applied to the \texttt{Sep16 120deg} image as shown at the start of the chapter.
-Figure \ref{fig:inference_AbsFilterDeg120_zfiltered} shows the filtered $z$ images for various kernel radiuses.
-For $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$, the resulting $z$ image was smooth and treated everything as the null.
-When a large enough radius was used, the defects were highlighted by the higher test statistics and everything else remain unchanged.
-Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} to \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference along with the empirical null parameters.
-The figures shows that for large enough kernel radius, the filter ironed out the false positives observed at the start of the chapter.
-All of the defects were successfully highlighted by the hypothesis test.
-
-False positives were detected on the bottom right of the 3D printed sample.
+The empirical null filter was applied to the \texttt{AbsFilter} projection at \ang{120}.
+Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} and \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference when using a kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ and $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ respectively.
+With a small radius, the empirical null treated the voids as the null which is shown by the empirical null mean capturing the features of the voids.
+When a large enough radius was used, the larger voids were highlighted by the hypothesis test and the empirical null mean became smoother.
+This is evident that this method ironed out the false positives observed at the start of the chapter.
+
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.eps}
+      \caption{$z$ image with section highlighted}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHist.eps}
+      \caption{Histogram of $z$ in the kernel}
+    \end{subfigure}
+  }
+  \caption{A section of the bottom right of a unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
+  \label{fig:inference_cornerSelect}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\subSize]{../figures/inference/segment.eps}
+  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
+  \label{fig:inference_segmentFurther}
+\end{figure}
+
+False positives were detected on the bottom right of the test sample.
 This was the result of the null distribution being bimodal where each face had a different distribution.
 Figure \ref{fig:inference_cornerSelect} illustrates this.
-The geometry of the faces and the kernel was such that it resulted in one of the faces to be treated as non-null and then tested positive, falsely so.
+The geometry of the faces and the kernel used was such that it resulted in one of the faces to be treated as non-null and then tested positive, falsely so.
+
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
+        \caption{Image with positive pixels}
+      \end{subfigure}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
+        \caption{$-\log p$}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
+        \caption{Empirical null mean}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
+        \caption{Empirical null std}
+      \end{subfigure}
+    }
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$ was used.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
+The test statistics from all segments were combined in the BH procedure.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and standard deviation.}
+  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
+        \caption{Image with positive pixels}
+      \end{subfigure}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}
+        \caption{$-\log p$}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
+        \caption{Empirical null mean}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
+        \caption{Empirical null std}
+      \end{subfigure}
+    }
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}$ was used.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
+The test statistics from all segments were combined in the BH procedure.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and standard deviation.}
+  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
+\end{figure}
 
 The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}.
-It was segmented using the edges of the projection of the 3D printed object.
+It was segmented using the edges of the $z$ image.
 The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
@@
 
-\begin{figure}[htp]
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.png}
-      \caption{$z$ image with kernel of radius $r=120$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHisto.png}
-      \caption{Histogram of $z$ in the kernel}
-    \end{subfigure}
-  }
-  \caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the test statistics captured by the kernel shows a bimodal distribution.}
-  \label{fig:inference_cornerSelect}
-\end{figure}
-
-\begin{figure}[htp]
-  \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
-  \caption{The $z$ image was segmented further into 7 segments.}
-  \label{fig:inference_segmentFurther}
+The same procedure was done on the projection at \ang{30}, as shown in Figure \ref{fig:inference_subroiAbsFilterDeg30_inference_radius1}, with similar results.
+
+\subsection{Titanium Test Sample}
+
+The whole procedure was repeated on the titanium test sample in the dataset \texttt{TiFilter}.
+The resulting $z$ statistics are shown in Figure \ref{fig:inference_subroiTiFilter_unfiteredZ} and shows, as in the \texttt{AbsFilter} case, a boundary on the edges of the test sample.
+The faces of the test sample were manually segmented and the empirical null filter was used on each segment separately and stitched together to form the final stages of the analysis.
+
+\begin{figure}
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_unfilteredZ.eps}
+        \caption{\ang{30}}
+      \end{subfigure}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_unfilteredZ.eps}
+        \caption{\ang{120}}
+      \end{subfigure}
+    }
+  \caption{Unfiltered $z$ images from the dataset \texttt{TiFilter}}
+  \label{fig:inference_subroiTiFilter_unfiteredZ}
 \end{figure}
@@
     \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
         \caption{Image with positive pixels}
       \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}
         \caption{$-\log p$}
@@
     \centerline{
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
         \caption{Empirical null mean}
       \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
         \caption{Empirical null std}
@@
     }
-  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$.
+  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 c) and d) Empirical null mean and standard deviation.}
-  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
-\end{figure}
+  \label{fig:inference_subroiTiFilterDeg30_inference}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
+        \caption{Image with positive pixels}
+      \end{subfigure}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}
+        \caption{$-\log p$}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
+        \caption{Empirical null mean}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
+        \caption{Empirical null std}
+      \end{subfigure}
+    }
+  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}$ was used.
+a) Highlighted in red are positive pixels at the 5\% FDR level.
+The test statistics from all segments were combined in the BH procedure.
+b) $p$-values on the log scale.
+c) and d) Empirical null mean and standard deviation.}
+  \label{fig:inference_subroiTiFilterDeg120_inference}
+\end{figure}
+
+The resulting inference are shown in Figures \ref{fig:inference_subroiTiFilterDeg30_inference} and \ref{fig:inference_subroiTiFilterDeg120_inference}.
+Unfortunately the edges of the test sample were falsely tested as positive and none of the voids were detected.
+The discrepancies are the edges can be due to inaccurate face segmentation or poor alignment of the \emph{aRTist} projection to the obtained projection.
 
 \section{Conclusion}
+
+To summarise the proposed method, Figure \ref{fig:inference_flowchart} shows a flowchart which summarises the process of the experiment and defect detection and how the empirical null filter fits in.
+The CAD model was used as a blueprint for the manufacture of the test sample.
+Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty.
+The uncertainty was modelled using the replicated projections.
+The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values.
+A threshold was used for the $p$-values to classify pixels as positive for defects or not.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{../figures/flowchart.eps}
+  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
+  \label{fig:inference_flowchart}
+\end{figure}
 
@@
 
+In the experiment, the larger voids of diameter \SI{2.4}{\milli\metre} were detected in the ABS test sample.
 False positives do occur but this is unavoidable because tests were done at the 5\% FDR level.
@@
 
-For good results, the faces of the 3D printed cuboid were segmented.
+For good results, the faces of the test sample were segmented.
 This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly.
 Manual segmentation was easy to do because a cuboid has 6 faces.
-However, segmentation of faces cannot be generalised well to 3D printed samples with complicated geometry and curved surfaces.
-
-The main issue was how slow the filter was.
-Figure \ref{fig:inference_timing} shows the timings of the empirical null filter and the mean variance filter.
-For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.
-
-\begin{figure}[htp]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
-        \caption{Empirical null filter}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
-        \caption{Mean variance null filter}
-      \end{subfigure}
-    }
-  \caption{Timings when filtering a $256\times 256$ image. Note the y-axis change scale.}
-  \label{fig:inference_timing}
-\end{figure}
+However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.
+
+While the empirical null filter performed well ABS test sample, it failed in the titanium test sample due to dominate effects on the edges.
+This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection.
+This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point it cannot perform and fails.
+
+The main issue with implementing this method onto the production line was how slow the filter was.
+The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
+Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
+On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.
 
 There are a few strategies to accelerate the filter.
-The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \texttt{CUDA} and \texttt{C++} is fruitless if there may exist a faster method.
+The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method.
 Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation.
@@
 However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
-
-The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
-Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
-On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.

### 2019-08-08 inference/defectdetect/DefectDetectSubRoi.m

@@ -41,7 +41,7 @@ classdef (Abstract) DefectDetectSubRoi < DefectDetect
         
         %plot the test image with the significant pixels from each segment
         fig = LatexFigure.sub();
-        sigPlot = Imagesc(this.scan.loadImageStack(this.testIndex));
+        sigPlot = Imagesc(this.testImage);
         sigPlot.addPositivePixels(sigImage);
         sigPlot.setDilateSize(2);
         sigPlot.plot();

### 2019-08-08 scan/TiFilterDeg120.m

@@ -7,6 +7,7 @@ classdef TiFilterDeg120 < TiFilter
           '120deg_');
       this.addArtistFile(fullfile('data','titaniumBlock_SnFilter_Dec16','sim','phantom', ...
           '120deg.tif'));
+      this.nSubSegmentation = 7;
     end
     
   end

### 2019-08-09 reports/thesis/chapters/5_inference.tex
Tidy up figures in inference

@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
+        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
+        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
         \caption{$-\log p$}
@@
 
-To summarise the proposed method, Figure \ref{fig:inference_flowchart} shows a flowchart which summarises the process of the experiment and defect detection and how the empirical null filter fits in.
+To summarise the proposed method, Figure \ref{fig:inference_flowchart} shows a flowchart of the process of the experiment and defect detection and how the empirical null filter fits in.
 The CAD model was used as a blueprint for the manufacture of the test sample.
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{../figures/flowchart.eps}
+  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
   \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
@@
 However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.
-
-While the empirical null filter performed well ABS test sample, it failed in the titanium test sample due to dominate effects on the edges.
+Automatic segmentation may be possible with geometrical information from the CAD model.
+
+While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges.
 This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection.
-This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point it cannot perform and fails.
+This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecification null statistics cannot be distinguished from non-null statistics.
 

### 2019-08-09 inference/defectdetect/DefectDetectSubRoiTiFilterDeg120.m

@@ -7,7 +7,7 @@ classdef DefectDetectSubRoiTiFilterDeg120 < DefectDetectSubRoi
     end
     
     function printResults(this)
-      this.printResults@DefectDetectSubRoi([-6, 8], [0,8], 15);
+      this.printResults@DefectDetectSubRoi([-10, 15], [0,15], 10);
     end
     
   end

### 2019-08-09 reports/paper1/paper.tex
Adjust paper.tex

@@
   \centering
-  \includegraphics[width=0.7\textwidth]{../figures/flowchart.eps}
+  \includegraphics[width=0.7\textwidth]{../figures/flowchart.pdf}
   \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection.}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
-  \caption{The x-ray projection was segmented further into 7 segments or ROI.}
+  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.eps}
+  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
   \label{fig:inference_segmentFurther}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
         \caption{X-ray projection with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
         \caption{$-\log p$}

### 2019-08-09 reports/paper1/paper.tex
corrected paper

@@
 A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample.
-XCT is not an instantaneous process so progress bars are usually featured XCT marketing such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}.
+XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}.
 Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.
@@
 
-In the experiment with the test sample, the angle was chosen to distinguish the designed voids.
+In the experiment, the angle was chosen to distinguish the designed voids.
 For general AM products, finding a suitable singular projection angle can be difficult.

### 2019-08-09 reports/thesis/chapters/5_inference.tex
Adjustment to thesis
inferenceSubRoi run required experiments
95 percent confidence interval used throughout

@@
   \centering
-  \includegraphics[width=0.7\textwidth]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
+  \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
   \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 95\% prediction interval.}
@@
 The empirical null distribution had a very large standard deviation and would test all pixels as negative, this is incorrect.
-
-\begin{figure}
-  \centering
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
-    \caption{Test statistics}
-  \end{subfigure}
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
-    \caption{Empirical null fitted onto histogram}
-  \end{subfigure}
-  \caption{The resulting test statistics are shown in a).
-The density estimate of the statistics is shown in b).
-The empirical null distribution multiplied by some constant is also plotted in b); this is to illustrate the curvature is the same as the density estimate at the mode.}
-  \label{fig:inference_inferenceSubsampleAll}
-\end{figure}
 
@@
  The empirical null filter aims to estimate the parameters $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ for all $x$ and $y$.
+
+ \begin{figure}[t]
+  \centering
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
+    \caption{Test statistics}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
+    \caption{Empirical null fitted onto histogram}
+  \end{subfigure}
+  \caption{The resulting test statistics are shown in a).
+The density estimate of the statistics is shown in b).
+The empirical null distribution multiplied by some constant is also plotted in b); this is to illustrate the curvature is the same as the density estimate at the mode.}
+  \label{fig:inference_inferenceSubsampleAll}
+\end{figure}
 
@@
     }
-    \caption{Various spread filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
+    \caption{Various dispersion filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
     \label{fig:inference_fijiStd}
@@
 
-In this experiment, the empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination.
+The empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination.
 A \emph{defect} is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
@@
 The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
+As a result, increasing the kernel radius slows down the filter.
 Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.

### 2019-08-09 varmean/varMeanExample.m

@@ -56,8 +56,8 @@ function plotExample(scan, termMatrixArray, linkArray)
     yPlot = model.predict(XPlot) * yStd;
     
     %get the 1 sigma error bars
-    upError = gaminv(normcdf(1), alpha, yPlot/alpha);
-    downError = gaminv(normcdf(-1), alpha, yPlot/alpha);
+    upError = gaminv(0.975, alpha, yPlot/alpha);
+    downError = gaminv(0.025, alpha, yPlot/alpha);
     
     %plot the heat map
     hist3Heatmap = Hist3Heatmap();

### 2019-08-09 reports/thesis/book.tex
inference chapter
subroi for more projections
use of dotsc
plot sub roi section
Intro and abstract

@@
 \newcommand{\T}{^\textup{T}}
-\newcommand{\dotdotdot}{\cdots}
 \newcommand{\BIC}{\mathrm{BIC}}
@@
 \chapter{Acknowledgements}
-I would like to thank my supervisors Julia Brettschneider and Tom Nichols.
-I would also like to thank my calibrators, as part of the Inside-Out group, in Warwick Statistics, Clair Barnes, Wilfred Kendall and Audrey Kueh, and the Warwick Manufacturing Group, Greg Gibbons, Jay Warnett and Mark Williams.
+I would like to thank my supervisors Julia Brettschneider and Tom Nichols for their guidance throughout my PhD.
+I would also like to thank my calibrators who are part of the Inside-Out group, in Warwick Statistics, Clair Barnes, Wilfred Kendall and Audrey Kueh, and the Warwick Manufacturing Group, Greg Gibbons, Jay Warnett and Mark Williams.
 
@@
 \chapter{Abstract}
-X-ray computed tomography (CT) can be used for defect detection in 3D printing.
-The object is scanned at multiple angles to reconstruct the object in 3D space.
-The process can be time consuming.
-The aim of this project was to investigate if it is possible to conduct defect detection in projection space from a single scan to speed up the defect detection procedure.
-To do this, a 3D printed sample was manufactured with voids to see if they can be detected.
+X-ray computed tomography can be used for defect detection in additive manufacturing.
+Typically, several x-ray projections of the product at hundreds of angles are used to reconstruct the object in 3D to look for any defects.
+The process can be time-consuming.
+This thesis aims to investigate if it is possible to conduct defect detection from a single projection to speed up the process.
+An additive manufacturing test sample was created with voids to see if they can be detected.
 
-X-ray photons behave randomly.
-Hence to do defect detection pixel by pixel, uncertainty must be taken into account.
-A compound Poisson model was used to model the grey valyes in a pixel.
-It assumed that photon arrivals are a Poisson process with Gamma distributed energy.
-This resulted in a linear relationship between the mean and variance of the grey value, which was used for variance prediction and to quantify the uncertainty.
+The uncertainty of the projection was modelled using a compound Poisson distribution.
+This arises from x-ray photon arrivals being a Poisson process and each photon has random energy.
+This resulted in a linear relationship between the mean and variance of the grey value in the projection, which was used for variance prediction and to quantify the uncertainty.
+Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model.
 
-Software, called \texttt{aRTist}, was used to simulate the scan and it was compared with the x-ray acquisition under the face of uncertainty.
-However the software, and the information provided to it, was not perfect which led to model misspecification and incorrect inference.
-The empirical null filter was proposed.
-It adjust each pixel statistic so that inference was done by comparing each pixel with the majority of its local pixels.
+Software, called \emph{aRTist}, was used to simulate the projection and compared with the obtained projection.
+The comparison was done under the face of uncertainty by treating each pixel as a hypothesis test.
+To overcome the imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
+Voids with diameters in the order of millimetres were detectable.
+
+This thesis is a contribution to real-time quality control in additive manufacturing.
 
@@
 
+Probability and statistics is used throughout in science.
+In particular, undergraduates are drilled to quote confidence intervals, use an appropriate number of significant figures and plot error bars in their studies.
+In physics, probability is used to model randomness in quantum mechanics and used to handle millions of particles in statistical mechanics.
+
+In the field of engineering, additive manufacturing is an emerging technology and has uses in producing bespoke products.
+Because it is a new form of technology, the process is not well understood and tolerances are not as precise as other forms of manufacturing.
+As a result, there exist methods for quality control of additive manufactured products.
+Typically, this is done using x-ray computed tomography and requires hundreds of x-ray projections, making this a slow process.
+
+The aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process.
+By using fewer x-ray projections, uncertainty is introduced.
+This is where statistics comes in.
+It enables the sensible handling of uncertainty from sources of errors such as the random behaviour of x-ray photons to model misspecification of the problem.
+
+The front cover shows the before and after of the statistical analysis.
+The left hand side shows an x-ray projection of an additive manufactured cuboid.
+Its edges appeared curved due to spot and panel effects and this can be fixed using shading correction.
+The right hand side shows the $p$-values of the resulting inference.
+Lighter colours shows evidence of a defect and they successfully highlighted voids put in there purposefully.
+
+In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed.
+Sources of error were looked at and it was investigated to see how they were handled.
+In Chapter \ref{chapter2}, a test sample was additive manufactured and the chapter describes how experimental x-ray projections were obtained.
+Shading correction is explained here and it was used to remove sources of systematic errors in the projections.
+In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays.
+In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and methods were used to predict it.
+In Chapter \ref{chapter5}, statistical techniques were employed to look for defects in the test sample under the face of uncertainty.
+The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made.
+The thesis ends with an evaluation in Chapter \ref{chapter6}.
+
+Undergraduate level physics and statistics is assumed.
+The physics and mathematics used can be reviewed in undergraduate textbooks such as \cite{serway2018physics} and \cite{riley2006mathematical} respectively.
+The statistics can be reviewed in \cite{rice2009mathematical}.
+Knowledge of generalised linear models \citep{nelder1972generalized,nelder1972generalized_2, mccullagh1984generalized} and analysis of variance (ANOVA) is also assumed.
+
+This thesis can be reproduced using the source code in the \emph{GitHub} repository \url{https://github.com/shermanip/oxwasp_phd}.
+
 \chapter{Literature Review}
+\label{chapter1}
 \input{chapters/1_literatureReview.tex}
@@
 \chapter{Data Collection}
+\label{chapter2}
 \input{chapters/2_dataCollection.tex}
@@
 \chapter{Compound Poisson}
+\label{chapter3}
 \input{chapters/3_compoundPoisson.tex}
@@
 \chapter{Variance Prediction}
+\label{chapter4}
 \input{chapters/4_variancePrediction.tex}
@@
 \chapter{Inference}
+\label{chapter5}
 \input{chapters/5_inference.tex}
+
+\chapter{Evaluation}
+\label{chapter6}
 

### 2019-08-14 reports/thesis/book.tex
conclusion

@@
 
-\chapter{Evaluation}
+\chapter{Conclusion}
 \label{chapter6}
+To summarise the thesis, Figure \ref{fig:evaluation_flowchart} shows a flowchart of the process of the experiment.
+A test sample was designed using a CAD model and was manufactured with purposefully designed voids.
+Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}.
+The obtained projections was used to help align the simulated projection.
+The aim of the experiment was to develop a statistical method to detect these designed voids.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
+  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
+  \label{fig:evaluation_flowchart}
+\end{figure}
+
+Shading correction was required to remove spot and panel effects from the obtained projections.
+This was done by using the greyscale projections from a number of powers of the x-ray tube.
+By assuming each pixel has a linear response to the power, a linear regression was used.
+This is discussed in Chapter \ref{chapter2}.
+
+In Chapter \ref{chapter3}, it was attempted to fit a compound Poisson distributed onto the grey values of a projection to quantify the noise.
+Unfortunately, the model suffered from identifiability issues for high photon counts.
+However, it was found that the grey value variance has a linear relationship with the grey value.
+In Chapter \ref{chapter4}, various GLM were fitted onto the variance-mean data and it was verified a linear relationship is a good model.
+The model was used as a tool to predict the variance of a grey value.
+
+In Chapter \ref{chapter5}, the replicated projections were split into two.
+19 randomly selected projections were used for the variance-mean model to fit onto.
+The remaining projection was compared with the simulated projection under the face of uncertainty.
+The uncertainty was predicted using the variance-mean model.
+Inference was done on the test statistics, one for each pixel in a projection.
+Unfortunately, the simulation was not perfect which led to model misspecification, thus false positives.
+The empirical null filter was developed and used to smooth the test statistics.
+This allows the inference to pick out areas which are unusual and unlike its neighbours.
+The filtered test statistics was converted to $p$-values so that hypothesis testing can be done to detect the voids.
+
+In the ABS test sample, voids of the order of millimetres were detectable using this method.
+However, for the titanium test sample, the voids were undetectable due to dominating edge effects.
+The reason for this is unknown.
+It was speculated that the main source of error was from the simulated projection not being quite pixel-perfect aligned causing model misspecification at the edges.
+Therefore, the method was unable to distinguish disagreement due to model misspecification or a void.
+This method could be improved if \emph{aRTist} was integrated into it.
+For example, the simulated projection could be realigned to minimise the number of positives.
+This will help eliminate sources of error due to \emph{aRTist}.
+A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.
+
+Two angular projections were looked at in this thesis.
+The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection.
+Repeating the experiment using difficult angles may indicate weaknesses from using a singular angle.
+Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden in a particular angle.
+
+The experiment could be improved if the location of the defects were known in the projection.
+This would allow identifying which positives are true positives and false positives and the analysis can be quantified using a ROC curve.
+
+This thesis is a contribution to real-time quality control for additive manufacturing.
+A powerful multi-core computer could be used to conduct the statistical analysis of x-ray projections of AM products on a conveyor belt.
+By using fewer projections, quality control can be faster which advances the development and increase the scope of applications of additive manufacturing.
 

### 2019-08-14 reports/thesis/chapters/5_inference.tex
printResults corrected in BandwidthSelection2
conclusion

@@
   \centering
-  \input{../figures/inference/BandwidthSelection2_bandwidthEstimate.txt}
+  \begin{tabular}{l|l}
+           &Estimate \\ \hline
+  Intercept&\input{../figures/inference/BandwidthSelection2_coeff1.txt}\\
+  Gradient &\input{../figures/inference/BandwidthSelection2_coeff2.txt}
+  \end{tabular}
   \caption{Estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
@@
 
-To summarise the proposed method, Figure \ref{fig:inference_flowchart} shows a flowchart of the process of the experiment and defect detection and how the empirical null filter fits in.
-The CAD model was used as a blueprint for the manufacture of the test sample.
-Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty.
-The uncertainty was modelled using the replicated projections.
-The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values.
-A threshold was used for the $p$-values to classify pixels as positive for defects or not.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
-  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
-  \label{fig:inference_flowchart}
-\end{figure}
-
 The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference.
@@
 This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection.
-This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecification null statistics cannot be distinguished from non-null statistics.
+This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecified null statistics cannot be distinguished from non-null statistics.
+Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}.
 

### 2019-08-15 reports/thesis/chapters/3_compoundPoisson.tex
Update bib

@@
 
-In an x-ray tube, photons are emitted as a Poisson process and each photon has some random energy due to bremsstrahlung and characteristic radiation.
+In an x-ray tube, photons are emitted as a Poisson process \citep{cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}.
 This shares similarities to the compound Poisson.

### 2019-08-16 reports/thesis/book.tex
Revise bib and intro
Format for Warwick thesis
Revise intro

@@
-\documentclass[12pt, a4paper]{memoir}
+\documentclass[12pt, a4paper, oneside]{memoir}
+%oneside for soft copy
+%twoside for hard final copy
+\setlrmargins{4cm}{*}{*}
+\checkandfixthelayout
 %\documentclass[12pt, a4paper, oldfontcommands]{memoir}
@@
 \DeclareSIUnit\adu{ADU}
-
+\OnehalfSpacing*
 \begin{document}\sloppy
@@
 
-\newpage
+\cleardoublepage
 \tableofcontents*
-\newpage
+\cleardoublepage
 \listoffigures
-\newpage
+\cleardoublepage
 \listoftables
@@
 
-Probability and statistics is used throughout in science.
+Probability and statistics is used throughout in science to handle data and uncertainty.
 In particular, undergraduates are drilled to quote confidence intervals, use an appropriate number of significant figures and plot error bars in their studies.
 In physics, probability is used to model randomness in quantum mechanics and used to handle millions of particles in statistical mechanics.
+Uncertainty is a daily occurrence.
 
@@
 This is where statistics comes in.
-It enables the sensible handling of uncertainty from sources of errors such as the random behaviour of x-ray photons to model misspecification of the problem.
+It enables the sensible handling of uncertainty from sources of errors such as from the random behaviour of x-ray photons or from the model misspecification of the problem.
 
@@
 The right hand side shows the $p$-values of the resulting inference.
-Lighter colours shows evidence of a defect and they successfully highlighted voids put in there purposefully.
+Lighter colours show evidence of a defect and they successfully highlighted voids put in there purposefully.
 
@@
 In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays.
-In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and methods were used to predict it.
+In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it.
 In Chapter \ref{chapter5}, statistical techniques were employed to look for defects in the test sample under the face of uncertainty.
@@
 This allows the inference to pick out areas which are unusual and unlike its neighbours.
-The filtered test statistics was converted to $p$-values so that hypothesis testing can be done to detect the voids.
+The filtered test statistics were converted to $p$-values so that hypothesis testing can be done to detect the voids.
 
@@
 Repeating the experiment using difficult angles may indicate weaknesses from using a singular angle.
-Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden in a particular angle.
+Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.
 
 The experiment could be improved if the location of the defects were known in the projection.
-This would allow identifying which positives are true positives and false positives and the analysis can be quantified using a ROC curve.
+This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.
 
 This thesis is a contribution to real-time quality control for additive manufacturing.
-A powerful multi-core computer could be used to conduct the statistical analysis of x-ray projections of AM products on a conveyor belt.
+A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt.
 By using fewer projections, quality control can be faster which advances the development and increase the scope of applications of additive manufacturing.

### 2019-08-18 reports/thesis/chapters/1_literatureReview.tex
Update bib

@@
   \caption{Examples of additive manufactured parts: a) lattice structure, b) toy, c) chain, d) model of a facial implant, e) spanner, f) ratchet mechanism, g) toy, h) series of rotatable gears, i) lattice structure.
-Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
+Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
+Clearance Center, Inc.}
   \label{fig:literature_3dprint}
@@
   }
-  \caption{Diagrams of various AM technologies. Reprinted from \cite{wang20173d} with permission from Elsevier.}
+  \caption{Diagrams of various AM technologies. Reprinted from \cite{wang20173d}\textsuperscript{\textcopyright}, with permission from Elsevier.}
   \label{fig:literature_technologies}
@@
   \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
-  \caption{An example of a CAD model (left) converted to a STL file (right). Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
+  \caption{An example of a CAD model (left) converted to a STL file (right). Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
+Clearance Center, Inc.}
   \label{fig:literature_stl}
@@
   \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_balling.png}
-  \caption{A scanning electron microscope image of balling on a selective laser melting manufactured object. Reprinted from \cite{li2012balling} with permission from Springer Nature.}
+  \caption{A scanning electron microscope image of balling on a selective laser melting manufactured object.
+Reprinted by permission from Springer Nature: \cite{li2012balling}\textsuperscript{\textcopyright}.}
   \label{fig:literature_balling}
@@
 By collecting readings at different angles, the image of the patient can be reconstructed.
-Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
+Reprinted from \cite{michael2001x}.
+\textcopyright\ IOP Publishing.
+Reproduced with permission.
+All rights reserved.}
   \label{fig:literature_medicalct}
@@
   \includegraphics[width=0.8\textwidth]{../figures/literatureReview/literature_tube.png}
-  \caption{An x-ray tube. Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
+  \caption{An x-ray tube. Reprinted from \cite{michael2001x}. \textcopyright\ IOP Publishing. Reproduced with permission. All rights reserved.}
   \label{fig:literature_tube}
@@
 Bremsstrahlung and characteristic radiation contribute to the continuous and discrete components of the distribution.
-Reprinted from \cite{michael2001x} with permission from IOP Publishing.}
+Reprinted from \cite{michael2001x}.
+\textcopyright\ IOP Publishing.
+Reproduced with permission.
+All rights reserved.}
   \label{fig:literature_spectrum}
@@
   \caption{Various reference standards: a) aluminium hollow cylinder, outer diameters \SI{30}{\milli\metre} and \SI{20}{\milli\metre}, b) aluminium step-cylinder with diameter \SI{300}{\milli\metre}, c) ceramic balls of diameter \SI{30}{\milli\metre} on a carbon fibre rod, the balls are separated by \SI{100}{\milli\metre}.
-Reprinted from \citep{bartscher2007enhancement} with permission from Elsevier.}
+Reprinted from \cite{bartscher2007enhancement}\textsuperscript{\textcopyright} with permission from Elsevier.}
   \label{fig:literature_referenceStandards}
@@
 Because of a finite x-ray spot size, blurry effects are produced using a magnification too large.
-Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
+Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
   \label{fig:literature_magnification}
@@
   \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
-  \caption{A reconstruction when scanning three aligned balls using a different number angular projections. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
+  \caption{A reconstruction when scanning three aligned balls using a different number angular projections.
+Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
   \label{fig:literature_angles}
@@
 A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}.
-Early reconstruction algorithms assumed no beam hardening but it can be corrected using modern methods \citep{sun2016applications}.
+Early reconstruction algorithms assumed no beam hardening but it can be corrected using modern methods \citep{elbakri2001statistical, sun2016applications}.
 
@@
 In b) a filter was placed in front of the x-ray tube.
-Reprinted from \citep{kruth2011computed} with permission from Elsevier}
+Reprinted from \citep{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier}
   \label{fig:literature_hardening}

### 2019-08-18 reports/thesis/chapters/4_variancePrediction.tex

@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction.
-The solid red line shows the GLM fit along with the $\Phi(+1)-\Phi(-1)$ prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
     \label{fig:meanVar_varMeanExample_AbsNoFilter}
@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction.
-The solid red line shows the GLM fit along with the $\Phi(+1)-\Phi(-1)$ prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
     \label{fig:meanVar_varMeanExample_AbsFilter}
@@
 The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
-The dashed red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the predicted residual.}
+The dashed red line shows the 95\% confidence interval of the predicted residual.}
   \label{fig:meanVar_residualGreyvalue}

### 2019-08-19 reports/thesis/chapters/5_inference.tex
Adjust figures in DefectAlt

@@
 A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated.
-Before the experiment, various baselines were obtained.
-An image with a defect was simulated and then tested to obtain the ROC area, type 1 error, type 2 error and the FDR.
-The image was than contaminated and tested to obtain the 4 measurements again.
-This was repeated 300 times to obtain the empirical distribution of the AUC, type 1 error, type 2 error and FDR when testing on a un/contaminated image with defects.
-The ROC area, type 1 error, type 2 error and FDR were measured when testing on a filtered contaminated image with defects, a kernel radius of $r=20$ was used and was repeated 100 times.
+The AUC, type 1 error, type 2 error and FDR were measured when testing on an image with a defect before and after contamination and then after filtering with the contamination.
+A kernel radius of $r=20$ was used and was repeated 100 times by simulating another image.
 
@@
   \caption{AUC and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
-a) shows the AUC when testing the image before/after contamination and after filtering.
-In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination.
+In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
+In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination.
 The filter used a kernel radius of 20.

### 2019-08-20 reports/thesis/chapters/3_compoundPoisson.tex
add graphical model figure
Use 1 sigma confidence interval

@@
     \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
-In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
+In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
     \label{fig:compoundPoisson_histogram_1_1_1}
@@
     \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
-In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
+In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
     \label{fig:compoundPoisson_histogram_1_100_1}
@@
     \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
-The dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
+The dotted red line shows the 68\% confidence interval of the expected frequency density.}
     \label{fig:compoundPoisson_histogram_approx}
@@
     \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
-On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
+On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
     \label{fig:compoundPoisson_histogram_10_1_1}
@@
     \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
-On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
+On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
     \label{fig:compoundPoisson_histogram_100_1_1}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{../figures/compoundpoisson/graphicalModel.eps}
+  \includegraphics[width=0.6\textwidth]{../figures/compoundpoisson/graphicalModel.pdf}
   \caption{Graphical model of the grey value $X_{i,j}$ for each of the $m$ pixels in the $n$ replicate projections.

### 2019-08-20 reports/thesis/chapters/4_variancePrediction.tex
Use 1 sigma confidence interval

@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction.
-The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.}
     \label{fig:meanVar_varMeanExample_AbsNoFilter}
@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction.
-The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.}
     \label{fig:meanVar_varMeanExample_AbsFilter}
@@
 The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
-The dashed red line shows the 95\% confidence interval of the predicted residual.}
+The dashed red line shows the 68\% confidence interval of the predicted residual.}
   \label{fig:meanVar_residualGreyvalue}

### 2019-08-20 reports/thesis/chapters/5_inference.tex
Use 1 sigma confidence interval

@@
   \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
-  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 95\% prediction interval.}
+  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 68\% prediction interval.}
   \label{fig:inference_BandwidthSelection2_ruleOfThumb}
@@
 Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
+The dotted lines show the 68\% confidence interval for the sample mean.}
   \label{fig:inference_NullIidMean}
@@
 Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
+The dotted lines show the 68\% confidence interval for the sample variance.}
   \label{fig:inference_NullIidStd}
@@
 Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
+The dotted lines show the 68\% confidence interval for the sample mean.}
   \label{fig:inference_NullIidMixtureMean}
@@
 Shown are the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
+The dotted lines show the 68\% confidence interval for the sample variance.}
   \label{fig:inference_NullIidMixtureStd}
@@
 The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
   \label{fig:inference_AllNullGaussian_mean}
@@
 The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
   \label{fig:inference_AllNullGaussian_var}
@@
 The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
   \label{fig:inference_AllNullGaussian_kurtosis}
@@
 The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
   \label{fig:inference_AllNullPlane_mean}
@@
 The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
   \label{fig:inference_AllNullPlane_var}
@@
 The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
   \label{fig:inference_AllNullPlane_kurtosis}
@@
 In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
-In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination.
+In b) c) d) the dashed lines shows the 68\% empirical confidence interval of the resulting error when testing the defected image before contamination.
 The filter used a kernel radius of 20.
@@
   \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
+The dashed lines show the resulting 68\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
 Defected pixels have the distribution $\normal(3,1)$.
@@
   \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
+The dashed lines show the resulting 68\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
 Defected pixels have the distribution $\normal(3,1)$.

### 2019-08-20 inference/bandwidthselection/BandwidthSelection2.m

@@ -84,8 +84,8 @@ classdef BandwidthSelection2 < Experiment
       scatter(x, this.kOptimal, 'x');
       hold on;
       plot(x, y, 'Color', colour2);
-      plot(x, gaminv(0.975, shapeParameter, gammaScale), 'Color', colour2, 'LineStyle',':');
-      plot(x, gaminv(0.025, shapeParameter, gammaScale), 'Color', colour2, 'LineStyle',':');
+      plot(x, gaminv(normcdf(1), shapeParameter, gammaScale), 'Color', colour2, 'LineStyle',':');
+      plot(x, gaminv(normcdf(-1), shapeParameter, gammaScale), 'Color', colour2, 'LineStyle',':');
       xlabel('n^{-1/5}');
       ylabel('optimal bandwidth');
       ax = gca;

### 2019-08-20 inference/defectsimulation/DefectAlt.m

@@ -72,8 +72,7 @@ classdef DefectAlt < Experiment
       
       %Plots pre/post contamination results on the same graph, so offset them
       offset = 0.06;
-      baseLineConfidence = 0.95;
-      baseLineQuantile = (1 - baseLineConfidence)/2;
+      baseLineQuantile = normcdf(-1);
       
       %plot roc area vs alt mean
       fig = LatexFigure.sub();

### 2019-08-22 reports/thesis/chapters/3_compoundPoisson.tex
Compound Poisson
Typo in CompoundPoisson.m for the objective function
Few formatting changes and typo in report
Adjust compound Poisson chapter
Revise compoundpoisson

@@
 Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log likelihood is defined to be
-\begin{align}
-  \ln L(\lambda,\alpha,\beta;X) &= \sum_{i=1}^n
+\begin{equation*}
+  \ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
   \left[
@@
   \right]
-  \nonumber \\
-  &\!\begin{multlined}[b]
-  =
+\end{equation*}
+and using the results in Appendix \ref{chapter:appendix_tweedie}
+\begin{equation}
+  \ln L(\lambda,\alpha,\beta;X) =
     \sum_{i=1}^n
@@
       +\mathbb{I}(x_i>0)\left(
-      -1-\beta x_i-\lambda-\ln x -\ln\sum_{y=1}^\infty W_y
+      -\beta x_i-\lambda-\ln x +\ln\sum_{y=1}^\infty W_y
       \right)
     \right] \ .
-  \end{multlined}
-\end{align}
-$\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
+\end{equation}
+Maximum likelihood estimators are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
 

### 2019-08-22 reports/thesis/chapters/5_inference.tex
Use 2 sigma confidence interval when comparing different things in inference
Small revisions

--- 2019-08-19 reports/thesis/chapters/5_inference.tex
@@
 The median squared error was obtained by taking the median over all squared errors from the 100 estimates.
+300 values of $n$ from 10 to $10^6$ and 30 values of $h$ from 0.09 to 1.5 were investigated.
 Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors.
@@
 The optimal bandwidth for a given $n$ was found numerically.
-Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $n$.
+Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $h$ and $n$.
 A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimised the log squared error for a given $n$.

### 2019-08-22 inference/allnull/AllNullPlane.m

@@ -2,7 +2,7 @@
 %Copyright (c) 2019 Sherman Lo
 
 %CLASS: EXPERIMENT ALL NULL PALNE
-%See superclass Experiment_AllNull
+%See superclass AllNull
 %Experiment with the empirical null filter on a gaussian image x 2 + plane
 classdef AllNullPlane < AllNull
   

### 2019-08-22 inference/bandwidthselection/BandwidthSelection.m

@@ -15,10 +15,10 @@ classdef BandwidthSelection < Experiment
     kArray = linspace(0.09, 1.5, 30)'; %array of kernel width
     nRepeat = 100;
     
-    %array to store the mode and half width estimation using the Parzen density estimation
-    %dim 1: for each repeat
-    %dim 2: for each kernel width
-    %dim 3: for each n or each sample size
+    %array to store the null parameters estimates
+      %dim 1: for each repeat
+      %dim 2: for each kernel width
+      %dim 3: for each n or each sample size
     meanArray;
     stdArray;
     
@@ -37,16 +37,16 @@ classdef BandwidthSelection < Experiment
       
       %meshgrid for n and k
       [nPlot, kPlot] = meshgrid(log10(this.nArray), this.kArray);
-      factor_array = [0.9, 1.06, 1.144]; %array of fudge factors
+      factorArray = [0.9, 1.06, 1.144]; %array of fudge factors
       
       %for the mode estimation, then half width estimation
-      for i_array = 1:3
+      for iArray = 1:3
         
         %get the corresponding array
-        if i_array == 1
+        if iArray == 1
           array = squeeze(median(this.meanArray.^2));
           zLabel = 'median squared error';
-        elseif i_array == 2
+        elseif iArray == 2
           array = squeeze(median((this.stdArray-1).^2));
           zLabel = 'median squared error';
         else
@@ -63,35 +63,38 @@ classdef BandwidthSelection < Experiment
         zlabel(zLabel);
         hold on;
         
-        %plot the path of the rule of thumb
-        %logn_path is array of logn to evaluate the rule of thumb
-        logn_path = interp1((1:numel(this.nArray))',log10(this.nArray), ...
+        %plot the path of the rule of thumb (line plot)
+        %logNPath is array of logn to evaluate the rule of thumb
+        %use interp1 to have more points provided in nArray
+        logNPath = interp1( (1:numel(this.nArray))', log10(this.nArray), ...
             linspace(1,numel(this.nArray),1000*numel(this.nArray))');
-        if i_array ~= 3
+        if iArray ~= 3
           %for each fudge factor
-          for i = 1:numel(factor_array)
-            %for each logn_path, work out the rule of thumb k
-            k_path = factor_array(i)*((10.^logn_path).^(-1/5));
-            %then for each k and logn pair, interpolate to get the value of the array
-            path = interp2(nPlot,kPlot,array,logn_path,k_path);
[…]

### 2019-08-22 inference/nulliid/NullIid.m

@@ -7,7 +7,9 @@
     %Z~N(0,1), the normalised z statistics is (z - null mean) / null std.
 %For a given n, n x N(0,1) are simulated, the null mean and null std are estimated using these
     %simulated data. The null parameters are recorded. The null parameters are then used normalise
-    %the simulated data. The mean, variance and kurtosis of the normalised statistics are recorded
+    %the simulated data. The mean, variance and kurtosis of the normalised statistics are recorded.
+    %This is repeated by simulating another data set.
+%Various n are investigated
 %METHODS TO BE IMPLEMENTED;
   %[nullMean, nullStd] = getNull(this, z)
     %given an array of data z, return the nullMean and nullStd

### 2019-08-22 inference/scripts/inferenceSubsample.m

@@ -18,8 +18,8 @@ close all;
 randStream = RandStream('mt19937ar', 'Seed', uint32(3538096789));
 zImage = getZImage(AbsFilterDeg120(), randStream);
 subsampleExample(zImage, 1:2000, 1:2000, strcat(mfilename,'All')); %whole image
-%subsampleExample(zImage, 1100:1299, 400:599, strcat(mfilename,'1')); %subimage with no defect
-%subsampleExample(zImage, 500:699, 500:699, strcat(mfilename,'2')); %subimage with defect
+subsampleExample(zImage, 1100:1299, 400:599, strcat(mfilename,'1')); %subimage with no defect
+subsampleExample(zImage, 500:699, 500:699, strcat(mfilename,'2')); %subimage with defect
 
 %PARAMETERS:
   %zImage: image of z statistics

### 2019-08-22 shadingcorrection/ShadingCorrectionAnova.m

@@ -1,7 +1,7 @@
 %MIT License
 %Copyright (c) 2019 Sherman Lo
 
-%CLASS: SHADING CORRECTION ANOVA
+%ABSTRACT CLASS: SHADING CORRECTION ANOVA
 %Does ANOVA on the shading corrected grey value in a greyscale projection
 %
 %One randomly selected replication from each power is assigned to the training set which trains the

### 2019-08-22 varmean/varmeancv/VarMeanCv.m

@@ -1,7 +1,7 @@
 %MIT License
 %Copyright (c) 2019 Sherman Lo
 
-%CLASS: VARIANCE MEAN CROSS VALIDATION
+%ABSTRACT CLASS: VARIANCE MEAN CROSS VALIDATION
 %Experiment to do cross validation to assess the different GLM
 %
 %Random images (that is selecting which replicate projections to use with replacement) were selected

### 2019-08-22 reports/thesis/chapters/5_inference.tex
Adjust DefectExample
DefectExample is now an experiment
Supress warning when saving java object
Change parameter ordering in PlaneMultLine
Added p value plot in inference
EmpiricalNullFilter saves the image correctly transposed

@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_imageClean.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilterimageFiltered.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilternullStd.eps}
         \caption{Empirical null std}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_imageClean.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_EmpiricalNullFilterimageFiltered.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_EmpiricalNullFilternullStd.eps}
         \caption{Empirical null std}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_imageClean.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_EmpiricalNullFilterimageFiltered.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_EmpiricalNullFilternullMean.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imagePreContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageClean.eps}
         \caption{Uncontaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
         \caption{Contaminated}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageFiltered.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullStd.eps}
         \caption{Filtered}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullMean.eps}
         \caption{Empirical null mean}
@@
 Defected pixels have the distribution $\normal(3,1)$.
+The speckle defect has density $\pi_1 = 0.1$.
+The line defect is 5 pixels thick.
 The square defect is $30\times 30$ pixels in size.
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-In a) and c),
-  highlighted in red are pixels tested as positive at the 5\% FDR level.}
+In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
   \label{fig:inference_defectSquare2Example}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilterpValueFiltered.eps}
+        \caption{Dust defect, $r=20$}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_EmpiricalNullFilterpValueFiltered.eps}
+        \caption{Line defect, $r=20$}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_EmpiricalNullFilterpValueFiltered}
+        \caption{Square defect, $r=20$}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilterpValueFiltered}
+        \caption{Square defect, $r=40$}
+      \end{subfigure}
+    }
+  \caption{A $256 \times 256$ contamined defected Gaussian image was filtered using the empirical null filter with kernel radius $r$.
+Shown are the values of the image converted to $p$-values.
+Defected pixels have the distribution $\normal(3,1)$.
+The square defect is $30\times 30$ pixels in size.
+The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The critical region is for testing at the 5\% FDR level.}
+  \label{fig:inference_defectExamplePValue}
 \end{figure}
@@
 In this scenario, the empirical null filter recovered the gradient in the empirical null which was then used for normalisation.
+
+Figure \ref{fig:inference_defectExamplePValue} shows the $p$-values after filtering a contaminated defected image.
+The FDR can be estimated in these figures by dividing the number of null statistics in the critical region by the number of statistics in the critical region.
+With a sensible kernel radius, some of the defects can be detected.
+False negatives do appear but this is inevitable in order to control for the FDR.
+The figure shows that using a kernel radius of $r=20$ for the square defect detected no pixels for defects.
+This, again, emphasise the importance of a good kernel radius.
 

### 2019-08-22 inference/defectsimulation/DefectRadiusLine.m

@@ -23,7 +23,7 @@ classdef DefectRadiusLine < DefectRadius
     
     function defectSimulator = getDefectSimulator(this)
       defectSimulator = PlaneMultLine(this.randStream, this.gradContamination, ...
-          this.multContamination, this.altMean, this.altStd, this.lineThickness);
+          this.multContamination, this.lineThickness, this.altMean, this.altStd);
     end
     
   end

### 2019-08-23 reports/thesis/chapters/5_inference.tex
In inference, make comment on initial value in DefectExample

@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilterimageFiltered.eps}
         \caption{Filtered}
@@
 In this scenario, the empirical null filter recovered the gradient in the empirical null which was then used for normalisation.
+
+The empirical null mean in Figure \ref{fig:inference_defectSquareExample} demonstrates the multi-thread nature of the implementation of the empirical null filter.
+It can be seen that there are horizontal streaks where the defect is.
+This is the result of each thread filtering a row each and jumping from one mode, the null, to the other, the non-null, at different times.
+The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pin point which mode is greater.
 

### 2019-08-27 reports/paper1/paper.tex
Use 1 sigma confidence interval
Comment on time change in paper

@@
 
-The running times for the empirical null filter with radius \SI{50}{\pixel} were measured to be \SI[separate-uncertainty = true]{26.72(35)}{\second}.
-This was compared to simpler filters such as the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation.
-Running times of \SI[separate-uncertainty = true]{0.0100(12)}{\second} were achieved using the mean-variance filter.
-With both of these filters, running time increased with kernel radius.
+The running times for the empirical null filter increased with kernel radius.
+Compared to typical filters, say the mean and variance filter, the empirical null filter is a number of magnitudes slower.
+The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
 
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
+  \includegraphics[width=0.49\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
   \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect.

### 2019-08-27 reports/thesis/chapters/5_inference.tex
Adjust defectdetect
ROC area use 1000 points
Made commment on ROC integration

@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_roc.eps}
         \caption{Dust defect $\pi_1=0.1$, $r=20$}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_roc.eps}
         \caption{5 pixels thick line defect, $r=20$}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_roc.eps}
         \caption{$30\times 30$ square defect, $r=20$}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_roc.eps}
         \caption{$30\times 30$ square defect, $r=40$}
@@
 The AUC, type 1 error, type 2 error and FDR were measured when testing on an image with a defect before and after contamination and then after filtering with the contamination.
+The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1000 trapeziums.
 A kernel radius of $r=20$ was used and was repeated 100 times by simulating another image.
@@
 Hypothesis testing was done on the uncontaminated and filtered contaminated image and the AUC and various errors were recorded, this was repeated 100 times.
+The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1000 trapeziums.
 The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.

### 2019-08-27 reports/paper1/paper.tex
Add BW method, one less parameter in Boxplots, paper uses linear shading correction

@@
 \author[1]{S.E.~Lo}
-\author[2]{J.W.~Warnett}
+\author[2]{J.M.~Warnett}
 \author[2]{G.J.~Gibbons}
@@
 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}.
-A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using 20 black (\SI{0}{\kilo\volt}) and 20 white images (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.
+A shading correction \citep{seibert1998flat} was applied to each projection using 20 greyscale projections, with powers \SI{0}{\kilo\volt}, \SI{5}{\kilo\volt}, \SI{10}{\kilo\volt}, \SI{15}{\kilo\volt} and \SI{20}{\kilo\volt}, to remove intensity influences and variations in pixels of the detector.
 
@@
 Numerical methods were used to align the simulated projection to the obtained projection.
-The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated white image.
+The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated greyscale projections.
 
@@
 where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.
-The variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}.
+The variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{ma2012varaince, yang2010noise}.
 A gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} was used with an identity link.
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/TestObject.png}
+  \includegraphics[width=0.49\textwidth]{../figures/inference/TestObjectBW.png}
   \caption{The CAD model of the test sample with voids.
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
+  \includegraphics[width=0.49\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminatedBW.eps}
   \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect.
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.eps}
-  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
+  \includegraphics[width=0.49\textwidth]{../figures/inference/segmentBW.eps}
+  \caption{The $z$ image was segmented further into 7 segments shown by the dashed lines.}
   \label{fig:inference_segmentFurther}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_rocBW.eps}
         \caption{AUC}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1BW.eps}
         \caption{Type 1 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2BW.eps}
         \caption{Type 2 error}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdrBW.eps}
         \caption{FDR}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
         \caption{X-ray projection with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}\vspace{-1mm}
         \caption{$-\log p$}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMeanBW.eps}
         \caption{Empirical null mean}
@@
       \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStdBW.eps}
         \caption{Empirical null std}
@@
   \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$.
-a) X-ray projection with highlighted red positive pixels at the 5\% FDR level.
+a) X-ray projection with highlighted white positive pixels at the 5\% FDR level.
 b) $p$-values on the log scale.

### 2019-08-27 reports/thesis/book.tex
Add BW method, one less parameter in Boxplots, paper uses linear shading correction

@@
 This arises from x-ray photon arrivals being a Poisson process and each photon has random energy.
-This resulted in a linear relationship between the mean and variance of the grey value in the projection, which was used for variance prediction and to quantify the uncertainty.
+This resulted in a linear relationship between the mean and variance of the grey value in the projection.
 Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model.
+Instead, a gamma distributed generalised linear model was fitted and used for variance prediction and to quantify the uncertainty.
 

### 2019-08-27 inference/defectsimulation/DefectExample.m

@@ -68,6 +68,13 @@ classdef DefectExample < Experiment
       imageContaminatedPlot.setCLim(imageCleanPlot.clim);
       imageContaminatedPlot.plot();
       saveas(fig,fullfile(directory, strcat(this.experimentName,'_imageContaminated.eps')),'epsc');
+      %bw plot
+      fig = LatexFigure.sub();
+      imageContaminatedPlot.setToBw();
+      imageContaminatedPlot.plot();
+      saveas(fig,fullfile(directory, strcat(this.experimentName,'_imageContaminatedBW.eps')),'eps');
+      saveas(fig,fullfile(directory, strcat(this.experimentName, ...
+          '_imageContaminatedBW.tiff')),'tiff');
       
       %for each filter, plot image filtered with positive pixels, p value, empirical null mean, and
           %empricial null std with positive pixels

### 2019-08-27 inference/defectsimulation/DefectRadius.m

@@ -53,7 +53,7 @@ classdef DefectRadius < Experiment
       %plot roc area vs alt mean
       fig = LatexFigure.sub();
       ax = gca;
-      boxplot = Boxplots(this.rocAreaArray(:,:,2), true);
+      boxplot = Boxplots(this.rocAreaArray(:,:,2));
       boxplot.setPosition(this.radiusArray);
       boxplot.plot();
       hold on;
@@ -65,11 +65,16 @@ classdef DefectRadius < Experiment
       xlabel('radius (px)');
       ylabel('AUC');
       saveas(fig,fullfile(directory, strcat(this.experimentName,'_roc.eps')),'epsc');
+      %plot bw
+      boxplot.setToBw();
+      boxplot.plot();
+      saveas(fig,fullfile(directory, strcat(this.experimentName,'_rocBW.eps')),'eps')
+      saveas(fig,fullfile(directory, strcat(this.experimentName,'_rocVW.tiff')),'tiff')
       
       %plot type 1 error vs alt mean
       fig = LatexFigure.sub();
       ax = gca;
-      boxplot = Boxplots(this.type1ErrorArray(:,:,2), true);
+      boxplot = Boxplots(this.type1ErrorArray(:,:,2));
       boxplot.setPosition(this.radiusArray);
       boxplot.plot();
       hold on;
@@ -81,11 +86,16 @@ classdef DefectRadius < Experiment
       xlabel('radius (px)');
       ylabel('type 1 error');
       saveas(fig,fullfile(directory, strcat(this.experimentName,'_type1.eps')),'epsc');
+      %plot bw
+      boxplot.setToBw();
+      boxplot.plot();
+      saveas(fig,fullfile(directory, strcat(this.experimentName,'_type1BW.eps')),'eps');
+      saveas(fig,fullfile(directory, strcat(this.experimentName,'_type1BW.tiff')),'tiff');
       
       %plot type 2 error vs alt mean
       fig = LatexFigure.sub();
       ax = gca;
-      boxplot = Boxplots(this.type2ErrorArray(:,:,2), true);
+      boxplot = Boxplots(this.type2ErrorArray(:,:,2));
       boxplot.setPosition(this.radiusArray);
       boxplot.plot();
       hold on;
@@ -97,11 +107,16 @@ classdef DefectRadius < Experiment
       xlabel('radius (px)');
       ylabel('type 2 error');
[…]

### 2019-08-27 reports/paper1/paper.tex
Revise paper

@@
 A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible.
-20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}.
-A shading correction \citep{seibert1998flat} was applied to each projection using 20 greyscale projections, with powers \SI{0}{\kilo\volt}, \SI{5}{\kilo\volt}, \SI{10}{\kilo\volt}, \SI{15}{\kilo\volt} and \SI{20}{\kilo\volt}, to remove intensity influences and variations in pixels of the detector.
+20 replicate greyscale projections were acquired using an exposure time of \SI{500}{\milli\second} and the following powers: \SI{0}{\kilo\volt}, \SI{5}{\kilo\volt}, \SI{10}{\kilo\volt}, \SI{15}{\kilo\volt} and \SI{20}{\kilo\volt}.
+A shading correction \citep{seibert1998flat} was applied to each projection of the test sample using the greyscale projections to remove intensity influences and variations in pixels of the detector.
 
@@
 Numerical methods were used to align the simulated projection to the obtained projection.
-The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated greyscale projections.
+The same shading correction was applied to the simulated projection, but instead using a flat black image and simulated greyscale projections.
 

### 2019-08-30 reports/thesis/chapters/2_dataCollection.tex
inference chapter
subroi for more projections
use of dotsc
plot sub roi section
Revise thesis and qq plot for compound poisson

@@
 
-Greyscale projections were taken in addition to the projection of the test object.
+Greyscale projections were taken for calibration \citep{wang2008experimental} in addition to the projection of the test object.
 These are projections with nothing between the source and the detector with the x-ray tube at different powers.
@@
 $S_{x,y}(P)$ may be averaged over replications.
-Let $x=1,2,3,\cdots, W$ and $y=1,2,3,\cdots,H$.
+Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$.
 Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$.
@@
 For each power, the within and between pixel variance was calculated.
-Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\cdots,n$ replicates.
+Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,n$ replicates.
 The within and between pixel variance are
@@
 
-Linear shading correction performed well, in terms of ANOVA, on all greyscale projections except for the black image.
+Linear shading correction outperformed BW shading correction, in terms of ANOVA, on all greyscale projections except for the black image.
 This is because linear shading correction trains on greyscale projections of various powers and generalises to these powers.

### 2019-08-30 reports/thesis/chapters/5_inference.tex
Revise thesis and qq plot for compound poisson

@@
 It can be shown that $\alpha$ controls the false positive rate.
-$\alpha=5.0\%$ is a typical choice and is used throughout this thesis.
+$\alpha=5.0\%$ is a typical choice \citep{wasserstein2019moving} and is used throughout this thesis.
 Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.
@@
 Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}.
+Lastly, because the titanium test sample was created using a power-based method, the voids may be filled with power thus appear with less contrast in the projections making it hard to detect.
 
@@
 Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
+The use of density estimation for robust estimation is also featured when using loss functions derived from the Hellinger-divergence \citep{beran1977minimum, jewson2018principles} or the beta-divergence \citep{basu1998robust, jewson2018principles} which bears similarities to the empirical null.
+However, numerical methods are still required to find the mode.
+Exact solutions for the mode using Bayesian methods is impossible \citep{heinrich2013the} which suggest avoiding the use of numerical methods can be difficult.
+
 The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.

### 2019-08-30 Imagesc.m
Add scale bar

@@ -129,6 +129,25 @@ classdef Imagesc < handle
       
     end
     
+    %METHOD: ADD SCALE
+    %Add scale bar to the imagesc
+    %Optimise to be used with LatexFigure.sub();
+    %To be called after plot();
+    %
+    %PARAMETERS:
+      %scan: scan object containing magnification and detector resolution
+      %lengthCm: the length of the scale bar in cm
+      %scaleColour: colour of the scale bar using MATLAB notation, eg 'k' or [1,0,0]
+    function addScale(this, scan, lengthCm, scaleColour)
+      xStart = 20;
+      imageHeight = numel(this.image(:,1));
+      lengthOfCm = scan.magnification * lengthCm * 1E-2 / scan.resolution;
+      line([xStart, xStart+lengthOfCm], [imageHeight, imageHeight]*0.9,...
+          'LineWidth',3,'Color',scaleColour);
+      text(xStart+lengthOfCm/2,imageHeight*0.95,strcat(num2str(lengthCm),'cm'), ...
+          'HorizontalAlignment','center','Color',scaleColour);
+    end
+    
   end
   
 end

### 2019-08-30 inference/defectdetect/DefectDetectSubRoiAbsFilterDeg120.m

@@ -10,7 +10,7 @@ classdef DefectDetectSubRoiAbsFilterDeg120 < DefectDetectSubRoi
     end
     
     function printResults(this)
-      this.printResults@DefectDetectSubRoi([-6, 8], [0,8], 15);
+      this.printResults@DefectDetectSubRoi([-6, 8], [0,8], 15, 1);
     end
     
   end

### 2019-08-30 inference/scripts/inferenceSubsample.m

@@ -16,23 +16,30 @@ clearvars;
 close all;
 
 randStream = RandStream('mt19937ar', 'Seed', uint32(3538096789));
-zImage = getZImage(AbsFilterDeg120(), randStream);
-subsampleExample(zImage, 1:2000, 1:2000, strcat(mfilename,'All')); %whole image
-subsampleExample(zImage, 1100:1299, 400:599, strcat(mfilename,'1')); %subimage with no defect
-subsampleExample(zImage, 500:699, 500:699, strcat(mfilename,'2')); %subimage with defect
+scan = AbsFilterDeg120();
+zImage = getZImage(scan, randStream);
+%whole image
+subsampleExample(scan, zImage, 1:2000, 1:2000, 1, strcat(mfilename,'All'));
+%subimage with no defect
+subsampleExample(scan, zImage, 1100:1299, 400:599, 0.1, strcat(mfilename,'1'));
+%subimage with defect
+subsampleExample(scan, zImage, 500:699, 500:699, 0.1, strcat(mfilename,'2'));
 
 %PARAMETERS:
+  %scan: scan object
   %zImage: image of z statistics
   %rowSubsample: vector of indicies of rows which indiciate the position of the subimage
   %colSubsample: vector of indicies of columns which indiciate the position of the subimage
+  %scaleLength: the length of the scale bar in cm
   %name: prefix used when saving results
-function subsampleExample(zImage, rowSubsample, colSubsample, name)
+function subsampleExample(scan, zImage, rowSubsample, colSubsample, scaleLength, name)
   
   %FIGURE
   %Plot the z image with a rectangle highlighting the subsample
   fig = LatexFigure.sub();
-  image_plot = Imagesc(zImage);
-  image_plot.plot();
+  imagePlot = Imagesc(zImage);
+  imagePlot.plot();
+  imagePlot.addScale(scan,1,'y');
   hold on;
   rectangle('Position', [colSubsample(1), rowSubsample(1), ...
       colSubsample(end)-colSubsample(1)+1, rowSubsample(end)-rowSubsample(1)+1], ...
@@ -105,9 +112,10 @@ function subsampleExample(zImage, rowSubsample, colSubsample, name)
   %FIGURE
   %Plot the subsample z statistics along with the positive pixels
   fig = LatexFigure.sub();
-  image_plot = Imagesc(zSampleImage);
-  image_plot.addPositivePixels(zTester.positiveImage);
[…]

### 2019-08-30 reports/paper1/paper.tex
Change github address
align defect detect figures

@@
 \section{Appendix}
-Code which reproduces this paper can be found on the \emph{GitHub} page \url{https://github.com/shermanip/oxwasp_insideout}.
+Code which reproduces this paper can be found on the \emph{GitHub} page \url{https://github.com/shermanlo77/oxwasp_insideout}.
 
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
+        \includegraphics[width=1.05\textwidth, height=5.0cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
         \caption{X-ray projection with positive pixels}

### 2019-08-30 reports/thesis/chapters/5_inference.tex
align defect detect figures

@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
+        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
+        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
         \caption{Image with positive pixels}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
+        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
         \caption{Image with positive pixels}

### 2019-08-30 reports/thesis/chapters/1_literatureReview.tex
Revise thesis and qq plot for compound poisson
Revise thesis

@@
 
-X-ray computed tomography (XCT) can be used as a non-destructive test for AM products, this is the main theme of this thesis.
+X-ray computed tomography (XCT) can be used as a non-destructive test for AM products.
 Various reviews on AM exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}.
@@
 Typically this is a slow and expensive method compared to destructive methods such as computer numerical control (CNC) machining for example.
-However, this is not the full picture.
-The set up cost for AM is low, in particular destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}.
-This is why AM used to be called rapid prototyping \citep{kruth1991material}, it was suitable to manufacture bespoke items.
+An advantage of AM is that the set up cost is low, in particular, destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}.
+This makes it suitable to manufacture bespoke items which achieves the goals of AM's predecessor called rapid prototyping \citep{kruth1991material}.
 
@@
 It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}.
-The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer.
-The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.
+The platform moves, and controlled by a computer, in the $xy$ plane, or left to right and front to back, to produce a layer.
+The jetting head can move in the $z$-axis, or up and down, to manufacture the next layer.
 In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).
@@
 Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}.
-Reverse engineering is possible when XCT is combined with AM, for example it was used for improving existing hollow engine valves \citep{cooper2015design}.
+XCT can be used to reverse engineer existing products and improved.
+The improved can be fabricated using AM, for example, it was used for improving existing hollow engine valves \citep{cooper2015design}.
 However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}.
-This is because there is a lot of inconsistent in the setup of XCT apparatuses and on controlling the sources of error.
+This is because there is a lot of inconsistencies in the setup of XCT apparatuses and on controlling the sources of error.
 
@@
 
-The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a bed.
+The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a flat bed.
 An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient using different paths.
@@
 
-\subsection{Acquisition Process}
+\subsection{Acquisition Process in Manufacturing}
 
-High power x-rays can be used in XCT for the purpose of manufacturing and metrology because there is no consequence of the manufactured object absorbing the radiation.
+In manufacturing and metrology, high power x-rays can be used in XCT because there is no consequence of the manufactured object absorbing the radiation.
 The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
@@
 
-The efficiency of an x-ray tube is poor, 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.
+The efficiency of an x-ray tube is poor. 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.
 
-Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process \citep{cierniak2011x}.
+Photons, making up the radiation, are emitted from the x-ray tube which can be modelled as a Poisson process \citep{whiting2006properties, cierniak2011x}.
 The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode.
-The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies \citep{sun2012overview}.
+Sources of energy of each photon come from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies \citep{sun2012overview}.
 An example is shown in Figure \ref{fig:literature_spectrum}.
@@
 
-The scanned object are exposed to x-ray photons which undergoes attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}.
+The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}.
 The object can absorb the photons via the photoelectric effect.
-In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}.
+In the photoelectric effect, the photons transfer all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}.
 Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron.
@@
 Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law.
-In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the detected photons \citep{sun2012overview}.
+In general low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}.
 This is called beam hardening.
@@
 The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}.
-The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
+This makes the detection a two stage process, converting the x-ray photons into visible light which are then detected \citep{cierniak2011x}.
+There exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct} but this is unrivalled by solid state CT systems, such as sintillator-photodiodes detectors, which have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
 
@@
 
-There exist many reconstruction algorithms in XCT \citep{smith1990cone} such as the filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
+A number of reconstruction algorithms in XCT have been developed \citep{smith1990cone} such as the filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
 Once the reconstruction has been done, the shape or surface can be extracted by use of thresholding \citep{kruth2011computed}.
-There exist many software for the reconstruction stage of XCT \citep{reinhart2008industrial, sun2012overview}.
+There are many software packages available for the reconstruction stage of XCT \citep{reinhart2008industrial, sun2012overview}.
 
@@
 
-XCT can be used to measure the length of the object, making it useful for measuring AM objects internally and externally.
+XCT can be used to measuring lengths and distances, making it useful for measuring the dimensions of AM objects internally and externally.
 \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.
@@
 These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}.
-The magnification can be adjusted by adjusting the distances between the x-ray tube, the object and the x-ray detector.
+The magnification can be modified by altering the distances between the x-ray tube, the object and the x-ray detector.
 Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}.
@@
 More angles produce a more accurate reconstruction but requires more acquisition time.
-Figure \ref{fig:literature_angles} shows an example of a reconstruction using various number of angles.
+Figure \ref{fig:literature_angles} shows an example of a reconstruction using various numbers of angles.
 
@@
 Problems can occur in the detector.
-For examples pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
-Spatially correlated noise within a projection can be observed \citep{sun2016characterisation} as well as correlation between acquisitions, this is known as image lag \citep{yang2009evaluation}.
+For example, pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
+Another problem is that there exist spatially correlated noise within a projection which can detected experimentally \citep{sun2016characterisation} as well as correlation between acquisitions, known as image lag \citep{yang2009evaluation}.
 Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.
@@
 Errors due to beam hardening can occur.
-Low energy photons are more likely to be absorbed or scattered, this causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior.
-This can cause flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed} as well as artefacts \citep{sun2016applications}.
-Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate, called a filter, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper.
+Low energy photons are more likely to be absorbed or scattered, which causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior.
+This can cause artefacts \citep{sun2016applications} such as flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed}.
+Beam hardening can be tackled by eliminating the low energy photons by placing a filter, a thin metal plate, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper.
 Figure \ref{fig:literature_hardening} shows an example of a reconstruction with and without a filter, without the filter the outer perimeter appears less dense than it should be.
 A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}.
-Early reconstruction algorithms assumed no beam hardening but it can be corrected using modern methods \citep{elbakri2001statistical, sun2016applications}.
+Early reconstruction algorithms ignored beam hardening but modern methods can take beam hardening into account \citep{elbakri2001statistical, sun2016applications}.
 
@@
 
-The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm as it caters for cone beams.
-However it assumes a circular trajectory from the source which can cause artefacts if assumptions are not met \citep{sun2016applications}.
+The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm because it caters for cone beams.
+However, it assumes a circular trajectory from the source which can cause artefacts if the trajectory is actually not circular \citep{sun2016applications}.
 
@@
 This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.
-The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}.
-Accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.
 
-An advantage of XCT is that the location of the pores can be visualised, for example in Figure \ref{fig:literature_pores3D}, and compared to the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
-Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}.
-The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}.
+The porosity is defined by dividing the volume of all of the pores by the volume of solid material \citep{taud2005porosity}.
+This can be used to quantified the material's strength and can be measured accurately using Archimedes' method \citep{spierings2011comparison}.
+Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage} and it was found the location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}.
+XCT can be used to measure porosity and has an advantage over Archimedes' method because the location of the pores can be visualised in XCT.
+An example of visualising pores is shown in Figure \ref{fig:literature_pores3D} and the pores can be compared to the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
 In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD model and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.
@@
 XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control.
-The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}.
+The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}.
+More angular projections would take more time but will improve the accuracy of the reconstruction \citep{kruth2011computed}.
 \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction.
@@
 Instead of reconstructing the object, the analysis can be done on the projections itself, or in projection space, by comparing it to a simulated projection produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-\cite{brierley2018optimized} developed an algorithm to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition.
-It is however very complicated as it is optimising over a very large dimensional space.
-\cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without.
+It can simulate projections of the object given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the CAD of the object \citep{bellon2011simulation, deresch2012simulating}.
+
+An algorithm was developed to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition \citep{brierley2018optimized}.
+However, it is very complicated as it is optimising over a very large dimensional space \citep{brierley2018optimized}.
+It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}.
 Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.
 
-It is however inevitable that accuracy is lost from the jump from reconstruction space to projection space, for example, a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.
+It is however inevitable that accuracy is lost from the transition from reconstruction space to projection space, for example, in the diagnostic of pneumonia, a CT scan has superior performance compared to a chest radiograph \citep{hayden2009chest}.

### 2019-08-31 reports/thesis/book.tex
Change github address

@@
 
-Parts of this thesis have been published by the author:
+Parts of this thesis is anticipated to be published by the author:
 \begin{itemize}
@@
 Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model.
-Instead, a gamma distributed generalised linear model was fitted and used for variance prediction and to quantify the uncertainty.
+Instead, a gamma distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.
 
-Software, called \emph{aRTist}, was used to simulate the projection and compared with the obtained projection.
-The comparison was done under the face of uncertainty by treating each pixel as a hypothesis test.
-To overcome the imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
+Software, called \emph{aRTist}, was used to simulate the projection and compared with the obtained projection in the face of uncertainty by treating each pixel as a hypothesis test.
+To overcome the imperfections of the simulation, the empirical null filter was used to cater for model misspecification so that sensible inference was achieved.
+This was done by locally normalising the test statistics using the mode.
 Voids with diameters in the order of millimetres were detectable.
@@
 
-Probability and statistics is used throughout in science to handle data and uncertainty.
-In particular, undergraduates are drilled to quote confidence intervals, use an appropriate number of significant figures and plot error bars in their studies.
-In physics, probability is used to model randomness in quantum mechanics and used to handle millions of particles in statistical mechanics.
-Uncertainty is a daily occurrence.
-
 In the field of engineering, additive manufacturing is an emerging technology and has uses in producing bespoke products.
@@
 
-The aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process.
+The main aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process.
 By using fewer x-ray projections, uncertainty is introduced.
 This is where statistics comes in.
-It enables the sensible handling of uncertainty from sources of errors such as from the random behaviour of x-ray photons or from the model misspecification of the problem.
+It enables the sensible handling of uncertainty from sources of error such as random error and systematic error.
+
+The analysis was done by comparing the experimental projection with a simulated projection to look for areas with disagreement in the face of uncertainty.
+Random error can arise from how x-ray photons are produced in an x-ray tube and how they interact with the additive manufactured product and the x-ray detector.
+This was modelled by using the compound Poisson distribution.
+Incorrect simulation of the projection can cause systematic error and this was corrected using the empirical null filter.
+These sources of error were considered in the comparison of projections with the use of hypothesis testing.
 
@@
 In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it.
-In Chapter \ref{chapter5}, statistical techniques were employed to look for defects in the test sample under the face of uncertainty.
+In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty.
+This was done by comparing the experimental projection with a simulated projection and looking for any disagreement.
 The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made.
@@
 
-Undergraduate level physics and statistics is assumed.
-The physics and mathematics used can be reviewed in undergraduate textbooks such as \cite{serway2018physics} and \cite{riley2006mathematical} respectively.
-The statistics can be reviewed in \cite{rice2009mathematical}.
-Knowledge of generalised linear models \citep{nelder1972generalized,nelder1972generalized_2, mccullagh1984generalized} and analysis of variance (ANOVA) is also assumed.
-
-This thesis can be reproduced using the source code in the \emph{GitHub} repository \url{https://github.com/shermanip/oxwasp_phd}.
+The results presented in this thesis can be reproduced using the source code in the \emph{GitHub} repository \url{https://github.com/shermanlo77/oxwasp_phd}.
 

### 2019-08-31 reports/thesis/chapters/2_dataCollection.tex
Add scale bar

@@
 The simulated projections were produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-It can simulate projections of the test sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the CAD of the test sample \citep{bellon2011simulation, deresch2012simulating}.
 
@@
 
-Greyscale projections were taken for calibration \citep{wang2008experimental} in addition to the projection of the test object.
+Greyscale projections were taken in addition to the projection of the test object.
 These are projections with nothing between the source and the detector with the x-ray tube at different powers.

### 2019-08-31 reports/thesis/chapters/3_compoundPoisson.tex

@@
 
+The compound Poisson has applications in, for example, modelling rainfall \citep{revfeim1984initial} and insurance claims \citep{jorgensen1994fitting, smyth2002fitting}.
+
 This chapter starts with a literature review on the compound Poisson distribution, how it is derived from the behaviour of photons, how its likelihood is evaluated and methods for fitting it onto data.
@@
 
-In an x-ray tube, photons are emitted as a Poisson process \citep{cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}.
+In an x-ray tube, photons are emitted as a Poisson process \citep{whiting2006properties, cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}.
 This shares similarities to the compound Poisson.
@@
 This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ and $\phi$ because the above is in the form of a distribution in the dispersive exponential family.
-This has applications in, for example, insurance claim data \citep{jorgensen1994fitting, smyth2002fitting}.
 
@@
 
-The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation of the m.g.f.~giving the p.d.f.
+The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation or the m.g.f.~giving the p.d.f.~and has been used in XCT \citep{elbakri2003statistical, elbakri2003efficient}.
 Inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}.
@@
 To correctly represent the empirical distribution of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers.
-However, the Normal approximation and the saddlepoint approximation does not have support at zero.
+However, the Normal approximation and the saddlepoint approximation does not have mass support at zero.
 Therefore, to compare these approximate densities to the empirical distribution fairly, a histogram containing both zero and positive samples was used when appropriate.
@@
 \end{equation}
-for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant which was chosen to be
+for 10\,000 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant which was chosen to be
 \begin{equation}
@@
 \end{equation}
-The density was then was normalised by numerically integrating it using the trapezium rule using the 500 evaluated points.
+The density was then was normalised by numerically integrating it using the trapezium rule using the 10\,000 evaluated points.
 
@@
 If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin.
-For the exact method and the saddlepoint approximate, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums.
+For the exact method and the saddlepoint approximation, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums.
+Because the saddlepoint approximation does not support zero, the numerical integration cannot start at zero.
 $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
-Because the Normal and saddlepoint approximation does not support zero, the Q-Q plot was omitted for small $\lambda$.
 
@@
 
-For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}, \ref{fig:compoundPoisson_histogram_1_100_1} and \ref{fig:compoundPoisson_histogram_approx}) there is a chance of simulating zeros.
+For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}to \ref{fig:compoundPoisson_histogram_approx_1_100_1}) there is a chance of simulating zeros.
 For $\lambda = 1$, the Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values.
 The saddlepoint approximation did capture the probability mass at zero as shown by an increase in probability density towards zero.
-For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough to capture them.
-In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation or inversion of the c.d.f.
+For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough to capture them.
+In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation of the numerical calculation of the c.d.f.~and its inversion.
 
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
-        \caption{$\CPoisson(1,1,1)$ Normal approx.}
-    \end{subfigure}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha1beta1.eps}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \vspace{1em}
+    \centerline{
     \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
-        \caption{$\CPoisson(1,1,1)$ saddlepoint approx.}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha1beta1.eps}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the approximate p.d.f.
+On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_approx_1_1_1}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha100beta1.eps}
+        \caption{Q-Q plot - Normal approx.}
     \end{subfigure}
@@
     \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
-        \caption{$\CPoisson(1,100,1)$ Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
-        \caption{$\CPoisson(1,100,1)$ saddlepoint approx.}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha100beta1.eps}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the approximate p.d.f.
+On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
     \label{fig:compoundPoisson_histogram_approx_1_100_1}
-    \end{subfigure}
-    }
-    \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods.
-The dotted red line shows the 68\% confidence interval of the expected frequency density.}
-    \label{fig:compoundPoisson_histogram_approx}
 \end{figure}
@@
 $a$ and $\kappa$ are unknown parameters but can be estimated beforehand from replicate black images.
+Care must be taken to use the replicate black images for either shading correction or for estimating $a$ and $\kappa$ to avoid using the data twice.
 The energy of each photon $U\sim\gammaDist(\alpha,\beta)$ was omitted in the graphical model because the conditional distribution $X|Y\sim\gammaDist(Y\alpha,\beta)$ encapsulates each detected photon energy already.
@@
 The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
-The use of the EM algorithm here for the compound Poisson is similar to \cite{elbakri2003statistical, xu2009electronic}.
+The use of the EM algorithm for the compound Poisson in XCT has been studied in \cite{elbakri2003statistical, xie2008x, xu2009electronic}.
 

### 2019-09-01 reports/thesis/chapters/5_inference.tex

@@
 The implementation uses multiple threads, each thread filters a row in parallel.
-This was done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache.
-Then for each column, the thread does calculations using the cache then replaces the pixel value of the image to be filtered with the resulting calculation.
-Once the row has been filtered, the thread then moves onto the next unfiltered row.
-Rows in the cache not needed are overwritten with more recent rows.
 

### 2019-09-01 reports/thesis/chapters/2_dataCollection.tex

@@
 The target material in the x-ray tube is tungsten.
-The detector is made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produce a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
+The detector is made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produce a 16-bit projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
 Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$.

### 2019-09-09 reports/thesis/book.tex
Revise

@@
 This arises from x-ray photon arrivals being a Poisson process and each photon has random energy.
-This resulted in a linear relationship between the mean and variance of the grey value in the projection.
+This results in a linear relationship between the mean and variance of the grey value in the projection.
 Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model.
-Instead, a gamma distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.
+Instead, a gamma-distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.
 
-Software, called \emph{aRTist}, was used to simulate the projection and compared with the obtained projection in the face of uncertainty by treating each pixel as a hypothesis test.
+Software, called \emph{aRTist}, was used to simulate the projection and compared with the experimental projection in the face of uncertainty by treating each pixel as a hypothesis test.
 To overcome the imperfections of the simulation, the empirical null filter was used to cater for model misspecification so that sensible inference was achieved.
@@
 
-The main aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process.
+The main aim of this thesis is to investigate if it is possible to speed up the quality control process of additive manufactured products by using only a few x-ray projections.
 By using fewer x-ray projections, uncertainty is introduced.
-This is where statistics comes in.
-It enables the sensible handling of uncertainty from sources of error such as random error and systematic error.
+This can be tackled by using statistics because it enables the sensible handling of uncertainty from sources of error such as random error and systematic error.
 
@@
 This was modelled by using the compound Poisson distribution.
-Incorrect simulation of the projection can cause systematic error and this was corrected using the empirical null filter.
-These sources of error were considered in the comparison of projections with the use of hypothesis testing.
+Incorrect simulation of the projection contribute to systematic error and this was corrected using the empirical null filter.
+These sources of error were considered in the comparison of the projections with the use of hypothesis testing.
 
 The front cover shows the before and after of the statistical analysis.
-The left hand side shows an x-ray projection of an additive manufactured cuboid.
+The left-hand side shows an x-ray projection of an additive manufactured cuboid.
 Its edges appeared curved due to spot and panel effects and this can be fixed using shading correction.
-The right hand side shows the $p$-values of the resulting inference.
+The right-hand side shows the $p$-values of the resulting inference.
 Lighter colours show evidence of a defect and they successfully highlighted voids put in there purposefully.
@@
 In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed.
-Sources of error were looked at and it was investigated to see how they were handled.
-In Chapter \ref{chapter2}, a test sample was additive manufactured and the chapter describes how experimental x-ray projections were obtained.
-Shading correction is explained here and it was used to remove sources of systematic errors in the projections.
+Sources of error were investigated and see how they were handled.
+In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained.
+Shading correction is explained here and it was used to remove sources of systematic error in the projections.
 In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays.

### 2019-09-09 reports/thesis/chapters/1_literatureReview.tex
Revise

@@
 
-The different AM technologies can be classified based on the apparatus, for example liquid based or power based, and/or on the method of manufacturing, for example point by point or layer by layer \citep{kruth1991material}.
+The different AM technologies can be classified based on the apparatus, for example liquid based or powder based, and/or on the method of manufacturing, for example point by point or layer by layer \citep{kruth1991material}.
 The liquid based AM technologies presented here are stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} and fused deposition modelling \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
-The following power based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}.
+The following powder based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}.
 Illustrations of these technologies are shown in Figure \ref{fig:literature_technologies}.
@@
 The binding agent is cured via evaporation or heating which glues the powder particles together.
-The jetting head can move in the $x-y$ plane and the object is manufactured layer by layer by moving the platform in the $z$ direction and renewing the powder using a roller.
-The binding agent must have low viscosity so it can be deposited, it may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}.
+The jetting head can move in the $xy$-plane and the object is manufactured layer by layer by moving the platform in the $z$-axis and renewing the powder using a roller.
+The binding agent must have low viscosity so it can be deposited and may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}.
 The thickness of each layer is determined by the size of the droplets of the binding agent, which can be as small as \SI{15}{\micro\metre} in diameter \citep{sachs1990three}.
@@
 Selective laser sintering, electron beam melting and laser engineered net shaping are powder based AM technology.
-Selective laser sintering is similar to 3D printing but instead a laser is used to sinter or fuse the powder particles together.
-This is done in a chamber heated just below the melting point of the material \citep{wong2012review}.
+Selective laser sintering is similar to 3D printing, but instead, a laser is used to sinter or fuse the powder particles together in a chamber heated just below the melting point of the material \citep{wong2012review}.
 Various materials such as metals and plastics can be used \citep{wong2012review}.
-Electron beam melting is similar but instead an electron beam is used instead of a laser and this is done in a high vacuum chamber to avoid oxidation \citep{wong2012review}.
+Electron beam melting is similar, but instead of a laser, an electron beam is used.
+This is done in a high vacuum chamber to avoid oxidation \citep{wong2012review}.
 In laser engineered net shaping, a powder bed is not used; the powder is deposited on the desired location and then melted using a laser, as shown in Figure \ref{fig:literature_lens}.
@@
 Factors such as material cost, mechanical properties and the resolution of the manufacturing were considered.
-There are also safety aspects to assess, for example powder in powder based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}.
+There are also safety aspects to assess, for example, powder in powder based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}.
 This makes fused deposition modelling a popular choice and can be used in an office environment \citep{ngo2018additive}.
@@
 The blueprint of the object to be manufactured is called a computer-aided design (CAD) model.
-For it to be processed by an AM apparatus, the CAD model is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of a series of triangles, an example is shown in Figure \ref{fig:literature_stl}.
+For it to be processed by an AM apparatus, the CAD model is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces by a series of triangles, an example is shown in Figure \ref{fig:literature_stl}.
 STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}.
@@
 When the AM object is manufactured, post processing techniques can be done at this stage.
-For example sanding may be done to smooth the surfaces \citep{gibson2010additive}.
-The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
+For example, sanding may be done to smooth the surfaces \citep{gibson2010additive}.
+The manufactured object may be inspected for pores or defects by comparing the x-ray projection of the object with the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.
 
@@
 Other factors which can cause defects include misalignment of the platform or nozzle, depletion of material and lack of adhesion due to low temperatures \citep{gunaydin2018common}.
-There are also problems in the manufacturing of metal parts \citep{everton2016review}.
-For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}, they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}.
-Layers may not fuse together and form elongated pores, this can be fixed by increasing the energy of the beam but too high will cause evaporation of the AM part \citep{mumtaz2008high}.
-They can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review}.
-They are observable using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}.
-Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}.
+
+There are also problems in the manufacturing of metal parts \citep{everton2016review}, for example, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}.
+These gas pores can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}.
+
+Layers may not fuse together and form elongated pores.
+This can be fixed by increasing the energy of the beam but too increasing it too much will cause evaporation of the AM part \citep{mumtaz2008high}.
+These pores can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review} and can be observed using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}.
+
+Low wetting ability of the melt pool can cause balling which is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}.
 The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}.
-Low oxygen content in the environment \citep{niu1999instability} and higher energy beams \citep{gu2009balling} can reduce the balling effect.
+The balling effect can be reducted by ensuring low oxygen content in the environment \citep{niu1999instability} and using higher energy beams \citep{gu2009balling}.
 Some examples are shown in Figure \ref{fig:literature_balling} using an electron scanning microscope.
+
 Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.
@@
 The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}.
-The idea is that problems in the manufacturing are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
-Various methods are used for in-situ process monitoring.
-Most commonly a high speed camera is installed capturing the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}.
+The idea is that problems during the manufacturing processare found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
+Various methods are used for in-situ process monitoring, for example, a high speed camera can be installed to capture the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}.
 Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}.
@@
 Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}.
-XCT can be used to reverse engineer existing products and improved.
-The improved can be fabricated using AM, for example, it was used for improving existing hollow engine valves \citep{cooper2015design}.
-However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}.
-This is because there is a lot of inconsistencies in the setup of XCT apparatuses and on controlling the sources of error.
+XCT can be used to reverse engineer existing products and improvements can be fabricated using AM, for example, it was used for improving existing hollow engine valves \citep{cooper2015design}.
+However, the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}.
+This is because there are a lot of inconsistencies in the setup of XCT apparatuses and on controlling the sources of error.
 
@@
 The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a flat bed.
-An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient using different paths.
+An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient via different paths.
 X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}.
@@
 
-The patient cannot be exposed to too much radiation, therefore the x-rays used are of low power.
-This can cause noisy readings from the detector.
+The patient cannot be exposed to too much radiation, therefore the x-rays used are of low power which can cause noisy readings from the detector.
 The sources of noise are from the behaviour of the x-rays and from the electronics in the detector \citep{yang2010noise}.
@@
 In manufacturing and metrology, high power x-rays can be used in XCT because there is no consequence of the manufactured object absorbing the radiation.
-The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
+As a result, the XCT setup is different.
+The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector.
 X-ray projections are taken while the object rotates.
@@
 The energy lost by the electrons is emitted as bremsstrahlung radiation.
-It depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}.
+The energy of the radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}.
 Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it.
@@
 
-The efficiency of an x-ray tube is poor. 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.
+The efficiency of an x-ray tube is poor. Over 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.
 
@@
 The object can absorb the photons via the photoelectric effect.
-In the photoelectric effect, the photons transfer all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}.
-Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron.
+In the photoelectric effect, the photons transfer all of its energy to a bounded electron and ejects it from the atom in the object \citep{millikan1916direct}.
+Photons can be scattered by the object by colliding inelastically with, and transfers its energy to, an electron.
 This process is known as Compton scattering \citep{compton1923quantum}.
-The photoelectric effect and Compton scattering make a number of photons undetectable.
-However if some of the photons avoid these processes, they are detected and their energy is left unaffected.
+The photoelectric effect and Compton scattering cause a number of photons to be undetectable.
+If some of the photons avoid these processes, they are detected and their energy is left unaffected.
 
@@
 \begin{equation}
-I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(u)\diff u\right] \ .
+I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(x)\diff x\right] \ .
 \label{eq:beerLaw}
@@
 This makes the detection a two stage process, converting the x-ray photons into visible light which are then detected \citep{cierniak2011x}.
-There exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct} but this is unrivalled by solid state CT systems, such as sintillator-photodiodes detectors, which have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
+There exist equipment which detects x-ray directly such as a xenon gas ionisation detector \citep{fuchs2000direct} but this is unrivalled by solid state CT systems, such as sintillator-photodiodes detectors, which have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
 
-Once multiple projections of the object have been acquired at multiple angles, the reconstruction process can start.
+Once projections of the object have been acquired at multiple angles, the reconstruction process can start.
 The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray projections.
@@
 
-There are many variables in XCT and a lot of them have to be controlled.
-For example XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.
+There are many variables in XCT and a lot of them have to be controlled, for example, XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.
 
-The set up of XCT has a number of variables.
 The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray projection.
@@
 These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}.
+
 The magnification can be modified by altering the distances between the x-ray tube, the object and the x-ray detector.
@@
 
-All of the parameters of XCT discussed can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however there may be inconsistencies.
-For example even though the target material of the anode and power is specified, the energy spectrum can still vary \citep{stumbo2004direct}.
+All of the parameters of XCT discussed can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however, there may be inconsistencies.
+For example, even though the target material of the anode and power is specified, the energy spectrum can still vary \citep{stumbo2004direct}.
 
-Problems can occur in the detector.
-For example, pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
-Another problem is that there exist spatially correlated noise within a projection which can detected experimentally \citep{sun2016characterisation} as well as correlation between acquisitions, known as image lag \citep{yang2009evaluation}.
+Problems can occur in the detector, for example, pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
+Another problem is that there exist spatially correlated noise within a projection which can be detected experimentally \citep{sun2016characterisation} as well as correlation between acquisitions, known as image lag \citep{yang2009evaluation}.
 Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.
@@
 \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction.
-This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}.
+This was done by placing the object on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}.
 Fewer angular projections were taken but they can be obtained in one go, speeding up the process.

### 2019-09-09 reports/thesis/chapters/1_literatureReview.tex
Use proofreader

@@
 In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patient has an x-ray image taken at multiple angles.
-These x-ray images are used to reconstruct what was taken in 3D in order to make a diagnostic.
+These x-ray images are used to reconstruct what was taken in 3D to make a diagnostic.
 
@@
 Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer.
-Typically this is a slow and expensive method compared to destructive methods such as computer numerical control (CNC) machining for example.
-An advantage of AM is that the set up cost is low, in particular, destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}.
+Typically, this is a slow and expensive method compared to destructive methods such as computer numerical control (CNC) machining for example.
+An advantage of AM is that the setup cost is low, in particular, destructive methods require planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}.
 This makes it suitable to manufacture bespoke items which achieves the goals of AM's predecessor called rapid prototyping \citep{kruth1991material}.
 
-Various different AM technologies were invented during the advancement of AM.
+Various AM technologies were invented during the advancement of AM.
 Because of this, there are various applications of AM, for example in medical and biomedical sciences \citep{kang20163d, kourra2018computed}, engineering \citep{cooper2015design}, food engineering \citep{godoi20163d} and art \citep{ornes2013mathematics, grossman2019bathsheba}.
@@
 
-The different AM technologies can be classified based on the apparatus, for example liquid based or powder based, and/or on the method of manufacturing, for example point by point or layer by layer \citep{kruth1991material}.
-The liquid based AM technologies presented here are stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} and fused deposition modelling \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
-The following powder based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}.
+The different AM technologies can be classified based on the apparatus, for example, liquid-based or powder-based, and/or on the method of manufacturing, for example, point by point or layer by layer \citep{kruth1991material}.
+The liquid-based AM technologies presented here are stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} and fused deposition modelling \citep{crump1991fused, crump1992apparatus, stratasys2019what}.
+The following powder-based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}.
 Illustrations of these technologies are shown in Figure \ref{fig:literature_technologies}.
@@
 
-Stereolithography is a liquid based AM technology.
-It consist of a container containing a liquid photo-hardening monomer or polymer as well as a piston and platform which holds and moves the manufactured product up and down.
+Stereolithography is a liquid-based AM technology.
+It consists of a container containing a liquid photo-hardening monomer or polymer as well as a piston and platform which holds and moves the manufactured product up and down.
 A laser with a specific wavelength, typically \SIrange{300}{400}{\nano\metre} \citep{kodama1981automatic}, is emitted onto a point of the surface of the liquid and solidifies.
@@
 
-Fused deposition modelling is another liquid based AM technology.
+Fused deposition modelling is another liquid-based AM technology.
 A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer.
-The material is usually plastic in a form of a thin filament.
+The material is usually plastic in the form of a thin filament.
 It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}.
@@
 
-3D printing is a powder based AM technology.
-A jetting head deposit a binding agent in droplets onto a bed of powder of ceramic, metal or polymer.
+3D printing is a powder-based AM technology.
+A jetting head deposits a binding agent in droplets onto a bed of powder of ceramic, metal or polymer.
 The binding agent is cured via evaporation or heating which glues the powder particles together.
 The jetting head can move in the $xy$-plane and the object is manufactured layer by layer by moving the platform in the $z$-axis and renewing the powder using a roller.
-The binding agent must have low viscosity so it can be deposited and may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}.
+The binding agent must have a low viscosity so it can be deposited and may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}.
 The thickness of each layer is determined by the size of the droplets of the binding agent, which can be as small as \SI{15}{\micro\metre} in diameter \citep{sachs1990three}.
@@
 
-Selective laser sintering, electron beam melting and laser engineered net shaping are powder based AM technology.
-Selective laser sintering is similar to 3D printing, but instead, a laser is used to sinter or fuse the powder particles together in a chamber heated just below the melting point of the material \citep{wong2012review}.
+Selective laser sintering, electron beam melting and laser engineered net shaping are powder-based AM technology.
+Selective laser sintering is similar to 3D printing, but instead, a laser is used to sinter or fuse the powder particles in a chamber heated just below the melting point of the material \citep{wong2012review}.
 Various materials such as metals and plastics can be used \citep{wong2012review}.
@@
 
-There are many more AM technologies but they can be found in numerous review literatures.
-A comparison of the mentioned AM technologies available at the time were done by \cite{pham1998comparison, kim2008benchmark}.
+There are many more AM technologies but they can be found in numerous review literature.
+A comparison of the mentioned AM technologies available at the time was done by \cite{pham1998comparison, kim2008benchmark}.
 Factors such as material cost, mechanical properties and the resolution of the manufacturing were considered.
-There are also safety aspects to assess, for example, powder in powder based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}.
+There are also safety aspects to assess, for example, powder in powder-based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}.
 This makes fused deposition modelling a popular choice and can be used in an office environment \citep{ngo2018additive}.
 
-The strength of the manufactured object vary from geometry to geometry but also from direction to direction.
-Because the manufactured object are made layer by layer, the strength varies if the load was applied in the building direction (vertical) or the scanning direction (horizontal) \citep{kim2008benchmark}.
-Experimental results shown that fused deposition modelling has superior strength in the scanning direction but weak in the building direction \citep{kim2008benchmark}.
+The strength of the manufactured object varies from geometry to geometry but also from direction to direction.
+Because the manufactured object is made layer by layer, the strength varies if the load was applied in the building direction (vertical) or the scanning direction (horizontal) \citep{kim2008benchmark}.
+Experimental results have shown that fused deposition modelling has superior strength in the scanning direction but weak in the building direction \citep{kim2008benchmark}.
 
-The strongest manufactured methods were found to be powder based methods and stereolithography, however they are slow and material costs are high \citep{kim2008benchmark}.
+The strongest manufacturing methods were found to be powder-based methods and stereolithography, however, they are slow and material costs are high \citep{kim2008benchmark}.
 Fused deposition modelling has low costs and high speeds but suffers from weak mechanical properties \citep{ngo2018additive}.
@@
 The blueprint of the object to be manufactured is called a computer-aided design (CAD) model.
-For it to be processed by an AM apparatus, the CAD model is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces by a series of triangles, an example is shown in Figure \ref{fig:literature_stl}.
-STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}.
+For it to be processed by an AM apparatus, the CAD model is converted to an STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces by a series of triangles, an example is shown in Figure \ref{fig:literature_stl}.
+STL stands for stereolithography but could also be called standard tessellation language \citep{wong2012review}.
 Some accuracy is lost here as the surface of the CAD model is represented approximately by triangles \citep{gibson2010additive}.
@@
 
-When the AM object is manufactured, post processing techniques can be done at this stage.
+When the AM object is manufactured, post-processing techniques can be done at this stage.
 For example, sanding may be done to smooth the surfaces \citep{gibson2010additive}.
@@
 
-Layers may not fuse together and form elongated pores.
-This can be fixed by increasing the energy of the beam but too increasing it too much will cause evaporation of the AM part \citep{mumtaz2008high}.
+Layers may not fuse and form elongated pores.
+This can be fixed by increasing the energy of the beam but increasing it too much will cause evaporation of the AM part \citep{mumtaz2008high}.
 These pores can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review} and can be observed using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}.
@@
 The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}.
-The balling effect can be reducted by ensuring low oxygen content in the environment \citep{niu1999instability} and using higher energy beams \citep{gu2009balling}.
+The balling effect can be reduced by ensuring low oxygen content in the environment \citep{niu1999instability} and using higher energy beams \citep{gu2009balling}.
 Some examples are shown in Figure \ref{fig:literature_balling} using an electron scanning microscope.
@@
 The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}.
-The idea is that problems during the manufacturing processare found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
-Various methods are used for in-situ process monitoring, for example, a high speed camera can be installed to capture the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}.
+The idea is that problems during the manufacturing process are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.
+Various methods are used for in-situ process monitoring, for example, a high-speed camera can be installed to capture the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}.
 Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}.
@@
 
-XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement.
+XCT started its use in the medical field but the advancement of the technology saw its use in manufacturing and metrology, the science of measurement.
 Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}.
@@
 
-The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a flat bed.
+The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a flatbed.
 An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient via different paths.
 X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}.
-To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}.
+To reduce scanning times, fan-shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}.
 These multiple x-ray readings can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}.
@@
   \includegraphics[width=0.99\textwidth]{../figures/literatureReview/literature_medicalct.png}
-  \caption{In medical XCT, a fan shaped x-ray beam is emitted and attenuate through the patient and detected by a detector.
+  \caption{In medical XCT, a fan-shaped x-ray beam is emitted and attenuate through the patient and detected by a detector.
 The x-ray source and detector rotate around and translate along the patient.
@@
 The patient cannot be exposed to too much radiation, therefore the x-rays used are of low power which can cause noisy readings from the detector.
-The sources of noise are from the behaviour of the x-rays and from the electronics in the detector \citep{yang2010noise}.
+The sources of noise are from the behaviour of the x-rays and the electronics in the detector \citep{yang2010noise}.
 In this realm of low signal to noise ratio, the noise has a compound Poisson element to it \citep{whiting2002signal, whiting2006properties}.
-Many reconstruction algorithms have been proposed to take the compound Poisson noise into consideration \citep{elbakri2002statistical, elbakri2003efficient, elbakri2003statistical, lasio2007statistical, xie2008x}.
+Many reconstruction algorithms have been proposed to consider the compound Poisson noise \citep{elbakri2002statistical, elbakri2003efficient, elbakri2003statistical, lasio2007statistical, xie2008x}.
 
@@
 X-ray projections are taken while the object rotates.
-Typically the x-ray is a cone beam \citep{kruth2011computed}.
+Typically the x-ray is a cone-beam \citep{kruth2011computed}.
 This is illustrated in Figure \ref{fig:literature_xct}.
@@
 
-The acquisition process consist of the production of x-rays, x-rays attenuating the object, the detection of x-rays and the reconstruction process.
+The acquisition process consists of the production of x-rays, x-rays attenuating the object, the detection of x-rays and the reconstruction process.
 
 X-rays \citep{rontgen1896on} are produced in an x-ray tube, a diagram shown in Figure \ref{fig:literature_tube}.
-It consist of a vacuum tube containing a cathode and an anode.
+It consists of a vacuum tube containing a cathode and an anode.
 Electrons are fired from the cathode to the anode due to an electric potential.
@@
 
-The electrons can interact with the anode in a number of ways.
+The electrons can interact with the anode in many ways.
 The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material.
@@
 Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it.
-This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state.
+This produces a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state.
 This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.
@@
 
-The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}.
+The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in several ways \citep{cantatore2011introduction}.
 The object can absorb the photons via the photoelectric effect.
-In the photoelectric effect, the photons transfer all of its energy to a bounded electron and ejects it from the atom in the object \citep{millikan1916direct}.
-Photons can be scattered by the object by colliding inelastically with, and transfers its energy to, an electron.
+In the photoelectric effect, a photon transfer all of its energy to a bounded electron and ejects it from the atom in the object \citep{millikan1916direct}.
+Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron.
 This process is known as Compton scattering \citep{compton1923quantum}.
-The photoelectric effect and Compton scattering cause a number of photons to be undetectable.
+The photoelectric effect and Compton scattering cause several photons to be undetectable.
 If some of the photons avoid these processes, they are detected and their energy is left unaffected.
@@
 Beer's law simplifies these quantum mechanistic process.
-Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis.
-Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation.
-A differential equation can be set up to model the decay of photons as it attenuate through the object such that
+Suppose the x-ray beam with a rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis.
+Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has a rate of emission $I$ after attenuation.
+A differential equation can be set up to model the decay of photons as it attenuates through the object such that
 \begin{equation}
@@
 After attenuation, the x-ray photons are detected by the x-ray detector.
-The detectors used in XCT are typically flat bed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes.
-The x-ray photons interact with the scintiallator material and produce visible light pluses \citep{rossner1993conversion}.
+The detectors used in XCT are typically flatbed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes.
+The x-ray photons interact with the scintillator material and produce visible light pluses \citep{rossner1993conversion}.
 These pulses are detected by photodiodes and converted into an electrical signal \citep{nikl2006scintillation, ren2018tutorial}.
@@
 The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}.
-This makes the detection a two stage process, converting the x-ray photons into visible light which are then detected \citep{cierniak2011x}.
-There exist equipment which detects x-ray directly such as a xenon gas ionisation detector \citep{fuchs2000direct} but this is unrivalled by solid state CT systems, such as sintillator-photodiodes detectors, which have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
+This makes the detection a two-stage process, converting the x-ray photons into visible light which are then detected \citep{cierniak2011x}.
+There exist equipment which detects x-ray directly such as a xenon gas ionisation detector \citep{fuchs2000direct} but this is unrivalled by solid-state CT systems, such as scintillator-photodiodes detectors, which have a high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.
 
@@
 A number of reconstruction algorithms in XCT have been developed \citep{smith1990cone} such as the filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}.
-Once the reconstruction has been done, the shape or surface can be extracted by use of thresholding \citep{kruth2011computed}.
+Once the reconstruction has been done, the shape or surface can be extracted by the use of thresholding \citep{kruth2011computed}.
 There are many software packages available for the reconstruction stage of XCT \citep{reinhart2008industrial, sun2012overview}.
@@
 In XCT, the scale of each voxel in the reconstruction can be obtained by using XCT on an object with pre-determined lengths, these are known as reference standards \citep{bartscher2007enhancement} but can have similar names.
-Reference standards can vary in geometry such as a sphere on a cylinder \citep{lifton2013application}, two spheres on a cylinder \citep{sun2016reference}, a cube with cut outs \citep{kiekens2011test}, a hollow cylinder, a step-cylinder and a ball-bar \citep{bartscher2007enhancement}; the latter three are shown in Figure \ref{fig:literature_referenceStandards}.
+Reference standards can vary in geometry such as a sphere on a cylinder \citep{lifton2013application}, two spheres on a cylinder \citep{sun2016reference}, a cube with cut-outs \citep{kiekens2011test}, a hollow cylinder, a step-cylinder and a ball-bar \citep{bartscher2007enhancement}; the latter three are shown in Figure \ref{fig:literature_referenceStandards}.
 
@@
 
-There are many variables in XCT and a lot of them have to be controlled, for example, XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.
+There are many variables in XCT and a lot of them have to be controlled, for example, XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however, this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.
 
@@
 The exposure time is also a factor.
-These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}.
+These settings should be set high enough to avoid beam extinction but low enough that there is a contrast where less material is present \citep{kruth2011computed}.
 
 The magnification can be modified by altering the distances between the x-ray tube, the object and the x-ray detector.
-Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}.
+Increasing the magnification increases the image resolution but can cause blurry images, this is the result of using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}.
 Larger spot sizes cause more blurry results, this is known as the penumbra effect \citep{kueh2016modelling}.
@@
 There is also the question on how to orient the object on the turntable \citep{corcoran2016observations} as well as how many angles to use \citep{kruth2011computed}.
-More angles produce a more accurate reconstruction but requires more acquisition time.
+More angles produce a more accurate reconstruction but require more acquisition time.
 Figure \ref{fig:literature_angles} shows an example of a reconstruction using various numbers of angles.
@@
 
-Problems can occur in the detector, for example, pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
-Another problem is that there exist spatially correlated noise within a projection which can be detected experimentally \citep{sun2016characterisation} as well as correlation between acquisitions, known as image lag \citep{yang2009evaluation}.
-Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.
+Problems can occur in the detector, for example, pixels in the acquired projection can be defective or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
+Another problem is that there exist spatially correlated noise within a projection which can be detected experimentally \citep{sun2016characterisation} as well as a correlation between acquisitions, known as image lag \citep{yang2009evaluation}.
+Precautions can be taken to reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.
 
@@
 This can cause artefacts \citep{sun2016applications} such as flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed}.
-Beam hardening can be tackled by eliminating the low energy photons by placing a filter, a thin metal plate, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper.
-Figure \ref{fig:literature_hardening} shows an example of a reconstruction with and without a filter, without the filter the outer perimeter appears less dense than it should be.
+Beam hardening can be tackled by eliminating the low energy photons by placing a filter, a thin metal plate, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example, copper.
+Figure \ref{fig:literature_hardening} shows an example of reconstruction with and without a filter.
+Without the filter, the outer perimeter appears less dense than it should be.
 A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}.
@@
 The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm because it caters for cone beams.
-However, it assumes a circular trajectory from the source which can cause artefacts if the trajectory is actually not circular \citep{sun2016applications}.
+However, it assumes a circular trajectory from the source which can cause artefacts if the trajectory is not circular \citep{sun2016applications}.
 
@@
 XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control.
-The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}.
+The reconstruction can take between 5 minutes to several hours \citep{warnett2016towards}.
 More angular projections would take more time but will improve the accuracy of the reconstruction \citep{kruth2011computed}.
-\cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction.
+\cite{warnett2016towards} improved the speed of XCT by sacrificing the accuracy of the reconstruction.
 This was done by placing the object on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}.
@@
 
-Instead of reconstructing the object, the analysis can be done on the projections itself, or in projection space, by comparing it to a simulated projection produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+Instead of reconstructing the object, the analysis can be done on the projections itself, or in projection space, by comparing it to a simulated projection produced by a software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
 It can simulate projections of the object given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the CAD of the object \citep{bellon2011simulation, deresch2012simulating}.

### 2019-09-11 reports/thesis/chapters/1_literatureReview.tex
Revise

@@
 
-Problems can occur in the detector, for example, pixels in the acquired projection can be defective or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}.
+Problems can occur in the detector, for example, pixels in the acquired projection can be defective or dead \citep{brettschneider2014spatial}, the panel structure of the detector can be observed \citep{yang2009evaluation} and the cone-beam appears as a spot.
+The x-ray spot could be fitted by using a mixture of a Gaussian spot and a uniform spot \citep{kueh2016modelling}.
 Another problem is that there exist spatially correlated noise within a projection which can be detected experimentally \citep{sun2016characterisation} as well as a correlation between acquisitions, known as image lag \citep{yang2009evaluation}.

### 2019-09-11 reports/thesis/chapters/2_dataCollection.tex
Revise

--- 2019-08-31 reports/thesis/chapters/2_dataCollection.tex
@@
-The objective of this thesis is to investigate if voids can be detected using a single projection.
+The objective is to investigate if voids can be detected using a single projection.
+The quality control procedure can be sped up if defect detection can be done in projection space rather than reconstruction space.
 An experiment was conducted where a test sample was additively manufactured with purposely designed voids.
 This was done by comparing a projection of the test sample with the simulation of that projection as if the voids were not there.
-The simulated projections were produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
-
-\cite{brierley2018optimized} did something similar by comparing a projection of the test sample, with no voids, with a simulation of that projection with voids added.
-The experiment presented here is the other side of the coin, putting voids in the physical test sample rather than in the simulated projection.
-This makes the experiment more realistic by attempting to detect real voids.
-Being able to detect voids suggest quality control can be done in projection space, rather than reconstruction space, to speed up the quality control procedure.
+The simulated projections were produced by using software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.
+Any disagreement in the comparison can suggest evidence of a defect.
 
@@
 
-The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids, the CAD shown in Figure \ref{fig:inference_testObject}.
+The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids.
 The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
 6 voids for each diameter were designed in the CAD.
-Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly.
+Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly.
+The CAD model of the test sample is shown in Figure \ref{fig:inference_testObject}.
 
@@
 X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector.
-The target material in the x-ray tube is tungsten.
-The detector is made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produce a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
-Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$.
+The target material in the x-ray tube was tungsten.
+The detector was made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produced a 16-bit projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
+Therefore, the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$.
 The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects.
-The gain and offset were adjusted by the engineers to produce a projection with good contrast and with negligible penumbra effect.
+The gain and offset were adjusted by the engineers to produce a projection with good contrast and negligible penumbra effect.
 Each pixel has a grey value in units of analogue to digital units (\SI{}{\adu}).
@@
 Greyscale projections were taken in addition to the projection of the test object.
-These are projections with nothing between the source and the detector with the x-ray tube at different powers.
+These are projections with nothing between the source and the detector, obtained with the x-ray tube at different powers.
 The power was varied by fixing the potential difference and varying the current.
@@
 
-Filters were used, such as \SI{0.350}{\milli\metre} of copper and \SI{2.000}{\milli\metre} of tin, to tackle beam hardening.
+Filters were used, such as a \SI{0.35}{\milli\metre} copper filter and a \SI{2.0}{\milli\metre} tin filter, to tackle beam hardening.
 
@@
 They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections.
-Projections of the ABS test sample were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}, the titanium test sample was used in \texttt{TiFilter}.
+Projections of the ABS test sample were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}.
+The titanium test sample was scanned in \texttt{TiFilter}.
 To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter} and \texttt{TiFilter}.
@@
 The properties of each dataset are shown in Table \ref{table:data_dataset}.
-Properties include the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections.
+These include the properties of the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections.
 A sample of the obtained, simulated and greyscale projections for the datasets \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter} are shown in Figures \ref{fig:data_AbsNoFilter}, \ref{fig:data_AbsFilter} and \ref{fig:data_TiFilter} respectively.
@@
 power (\SI{}{\watt})                                   & 36                   & 20                             & 20                       \\
-filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper & \SI{3}{\milli\metre} tin \\
+filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper & \SI{2.0}{\milli\metre} tin \\
 time exposure (\SI{}{\milli\second})                   & 708                  & 500                            & 1415                     \\
@@
 
-The projections do indeed show the test sample, however, with panel and spot effects.
+The projections show the test sample, but, with panel and spot effects.
 The structure of the 32 panels are predominate in the black image in particular, this was observed by \cite{yang2009evaluation} as well.
-This is concerning because systematic errors could be caused as a result of the panel effects in the black image when presented only with background radiation.
-The x-ray spot can be observed, in particular in the white image, and this is the result of using a cone beam.
-\cite{kueh2016modelling} studied the x-ray spot by fitting a mixture of a Gaussian spot and an uniform spot onto the x-ray spot.
+This is concerning because systematic errors could be introduced as a result of the panel effects in the black image.
+This should not happen because in a black image, the detector is exposed only to background radiation.
+The x-ray spot can be observed, in particular, in the white image, and this is the result of using a cone beam.
 
@@
 
-Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity of the projections as a result from panel and spot effects.
-Shading correction is typically done by using the greyscale projections and looking at how the grey values respond to different powers for different pixels.
-For example the black and white image can be used to correct the projections using
+Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity, observed in the projections, as a result from panel effects, spot effects and other artefacts.
+Shading correction is done by using the greyscale projections and examining how the grey values respond to different powers for different pixels.
+For example, the black and white image can be used to correct the projections using
 \begin{equation}
@@
 where $N_{x,y}$ is the obtained projection, $U_{x,y}$ is the shading corrected projection and $A$ and $B$ are some user defined constants \citep{young2000shading, munzenmayer2003enhancing}.
-This can be extended to include more greyscale projections by using the fact that the grey value respond linearly to the power of the x-ray source \citep{seibert1998flat}.
+This can be extended to include more greyscale projections by modelling the grey value to respond linearly to the power of the x-ray source \citep{seibert1998flat}.
 More generally, shading correction can be expressed as
@@
 where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}.
-There is an argument that this model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ may depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.
-Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to some parametric function \citep{likar2000retrospective} and using a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.
+This model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ may depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}.
+Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to be some parametric function \citep{likar2000retrospective} and using a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.
 
 In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user defined constants.
-The shading correction was then experimented to investigate its performance when shading correcting greyscale projections.
+The shading correction was experimented to investigate its performance when shading correcting greyscale projections.
 
@@
 The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.
+For both the greyscale projections and the projection of the test sample, the power was varied by fixing the potential difference and varying the current of the x-ray tube.
 
-The shading free image is not truly known, but it should expected that the shading corrected greyscale projection should be flat with some noise.
+The shading free image is not known, but it is expected that the shading corrected greyscale projection should be flat with some noise.
 In other words, all pixels in a shading corrected greyscale projection should have grey values with the same expectation $\mu_{S}(P)$ and same variance $\sigma_{S}^2(P)$.
@@
 for $P\in \mathbb{P}$ where $\mathbb{P} = \left\{0,P_1,P_2,\cdots, P_\text{proj}\right\}$ are the powers used for the greyscale projections.
-$\varepsilon$ is a random variable and an error term, it is included only for formality purposes.
+$\varepsilon$ is a random variable and an error term, it is included for formality purposes.
 Let $b_{x,y}$ and $a_{x,y}$ be the estimated parameters of $\beta_{x,y}$ and $\alpha_{x,y}$ from the linear regression respectively.
@@
 The resulting shading correction for the \texttt{AbsNoFilter} projection is shown in Figure \ref{fig:data_shadingCorrectionExample_image}.
-It can be observed that the shading correction removed the panel and spot effects from the background and test object.
+It can be observed that the shading correction removed the panel and spot effects from the background and test sample.
 
@@
 It was investigated if shading correction on a greyscale projection result in an image which is flat with some noise.
-To avoid overfitting, one greyscale projection from each power were held out and used to fit the parameters of the shading correction.
-Shading correction was then used on unused greyscale projections in this exploratory analysis.
+To avoid overfitting, one greyscale projection from each power was held out and used to fit the parameters of the shading correction.
+Shading correction was then used on the unused greyscale projections in this exploratory analysis.
 
 Figure \ref{fig:data_shadingCorrectionExample_greyvaluePower} shows the grey values in each greyscale projections before and after shading correction.
-The sensitivity, which corresponds to the gradient in units of \SI{}{\adu\per\watt}, became more consistent between pixels with shading correction.
-This should mean that pixels will respond similarly to each other for varying power.
+The sensitivity of the pixels, which corresponds to the gradient in units of \SI{}{\adu\per\watt}, became more consistent with shading correction.
+This should imply that pixels should respond similarly to each other for varying power with shading correction
 
@@
 The flatness of the image can be shown using a profile plot, this is a plot of the grey values along a column or row, an example shown in Figure \ref{fig:data_oddEven}.
-The figure shows that the shading uncorrected black image is not flat but a remarkable structure can be observed by plotting only the odd rows and even rows separately.
+The figure shows that the shading uncorrected black image was not flat but a remarkable structure was observed by plotting the odd rows and even rows separately.
 Such a plot shows that the grey values depend on neighbouring pixels, where the majority of pixels on even rows have grey values larger than pixels above and below it.
@@
 The BW shading corrected black and white image appeared uniform but there is some structure in the linear shading correction.
-By giving linear shading correction various greyscale projections, it tried to generalise to a range of powers, thus may struggle at shading correcting the black and white images.
+By giving linear shading correction various greyscale projections, it attempts to generalise to a range of powers, thus may struggle at shading correcting the black and white images.
 
@@
 Applying shading correction on the greyscale image should remove effects from the panels and the spot, leaving a flat noisy image with no spatial structure.
-The variance within a pixel and across replications should be similar to between pixels within a replication if the shading correction flatten the greyscale images.
+The variance within a pixel and across replications should be similar to the variance between pixels within a replication if shading correction flatten the greyscale images.
 
@@
 \end{equation}
-and should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.
+and it should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.
 
@@
 With shading correction, the within and between pixel variance became more similar.
-A difference between BW and linear shading correction is that for the black image, the $F$ statistic is better for BW compared to linear shading correction.
-For the rest of the powers, linear shading correction outperforms BW shading correction.
-This shows that linear shading correction generalise to powers between the black and white image.
+A difference between BW and linear shading correction was that for the black image, the $F$ statistic is closer to one for BW shading correction compared to linear shading correction.
+For the rest of the powers, linear shading correction outperformed BW shading correction.
+This shows that linear shading correction generalise to powers between zero and $P_\text{proj}$.
 Since beam extinction is avoided, black grey values in the obtained projection should not be possible.
@@
 The variance of the greyscale projections were studied in this chapter.
-This is fairly straightforward because the greyscale projections are flat images.
-The noise of a projection of a test sample is studied in the next chapter and this is done by modelling the grey value of each pixel as a compound Poisson random variable.
+This is straightforward because the greyscale projections are flat images.
+The noise of a projection of a test sample is studied in the next chapter and this was done by modelling the grey value of each pixel as a compound Poisson random variable.

### 2019-09-11 reports/thesis/chapters/2_dataCollection.tex
Use proofreader

@@
 
-Many figures presented here were given by engineers in relation to the experiment or by the manufacturer. Figures with no error bars were rounded to an appropriate number of significant figures.
+Many figures presented here were given by engineers concerning the experiment or by the manufacturer. Figures with no error bars were rounded to an appropriate number of significant figures.
 
@@
 \emph{aRTist} was used to simulate the test object projection and all greyscale projections except for the black image.
-The black image was simulated by producing an uniform image with grey value the mean over the obtained black image.
+The black image was simulated by producing a uniform image with a grey value the mean over the obtained black image.
 The engineers used numerical methods to align the simulated projection with the obtained projection.
@@
 The projections show the test sample, but, with panel and spot effects.
-The structure of the 32 panels are predominate in the black image in particular, this was observed by \cite{yang2009evaluation} as well.
+The structure of the 32 panels are predominate in the black image, in particular, this was observed by \cite{yang2009evaluation} as well.
 This is concerning because systematic errors could be introduced as a result of the panel effects in the black image.
-This should not happen because in a black image, the detector is exposed only to background radiation.
+This should not happen because, in a black image, the detector is exposed only to background radiation.
 The x-ray spot can be observed, in particular, in the white image, and this is the result of using a cone beam.
@@
 
-In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user defined constants.
+In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user-defined constants.
 The shading correction was experimented to investigate its performance when shading correcting greyscale projections.
@@
 
-A variation of the shading correction which uses only the black and white image such that $\mathbb{P}=\left\{0,P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.
+A variation of the shading correction which uses only the black and white image such that $\mathbb{P}=\left\{0, P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.
 
@@
 
-It was investigated if shading correction on a greyscale projection result in an image which is flat with some noise.
+It was investigated if shading correction on a greyscale projection results in an image which is flat with some noise.
 To avoid overfitting, one greyscale projection from each power was held out and used to fit the parameters of the shading correction.
@@
 Applying shading correction on the greyscale image should remove effects from the panels and the spot, leaving a flat noisy image with no spatial structure.
-The variance within a pixel and across replications should be similar to the variance between pixels within a replication if shading correction flatten the greyscale images.
+The variance within a pixel and across replications should be similar to the variance between pixels within a replication if shading correction flattens the greyscale images.
 
@@
 One randomly selected replication from each power was assigned to the training set and used to calibrate the shading correction.
-The remaining images was assigned to the test set and the shading correction was applied to each image.
+The remaining images were assigned to the test set and the shading correction was applied to each image.
 
@@
 For the rest of the powers, linear shading correction outperformed BW shading correction.
-This shows that linear shading correction generalise to powers between zero and $P_\text{proj}$.
+This shows that linear shading correction generalises to powers between zero and $P_\text{proj}$.
 Since beam extinction is avoided, black grey values in the obtained projection should not be possible.
@@
 Using the $F$ test from ANOVA was found to be too strict in this experiment.
-Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1,WH(n-1)}$.
-In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for the purpose of this analysis.
-This may be due to the grey values of the greyscale projections not satisfying the assumptions for the $F$ test, for example they may not be i.i.d.
+Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1, WH(n-1)}$.
+In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for this analysis.
+This may be due to the grey values of the greyscale projections not satisfying the assumptions for the $F$ test, for example, they may not be i.i.d.
 
@@
 Shading correction is important because it removes any panel and spot effects from projections which may cause systematic errors in any statistical analysis.
-Shading correcting the greyscale projections visually produced a flat image but there were some spatial variation which was picked up by the between pixel variances in ANOVA.
+Shading correcting the greyscale projections visually produced a flat image but there was some spatial variation which was picked up by the between pixel variances in ANOVA.
 
@@
 
-The variance of the greyscale projections were studied in this chapter.
+The variance of the greyscale projections was studied in this chapter.
 This is straightforward because the greyscale projections are flat images.

### 2019-09-11 reports/thesis/chapters/2_dataCollection.tex
Revise

@@
 The results are shown in Figures \ref{fig:data_anovaAbsNoFilter} and \ref{fig:data_anovaAbsFilter} for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively.
-With shading correction, the within and between pixel variance became more similar.
-A difference between BW and linear shading correction was that for the black image, the $F$ statistic is closer to one for BW shading correction compared to linear shading correction.
+With shading correction, the within and between pixel variance became similar.
+A difference between BW and linear shading correction was that for the black image, the $F$ statistic is closer to one for BW shading correction compared with linear shading correction.
 For the rest of the powers, linear shading correction outperformed BW shading correction.

### 2019-09-11 reports/thesis/chapters/3_compoundPoisson.tex
Revise

@@
 
-The compound Poisson has applications in, for example, modelling rainfall \citep{revfeim1984initial} and insurance claims \citep{jorgensen1994fitting, smyth2002fitting}.
+The compound Poisson distribution has applications in, for example, modelling rainfall \citep{revfeim1984initial} and insurance claims \citep{jorgensen1994fitting, smyth2002fitting}.
 
 This chapter starts with a literature review on the compound Poisson distribution, how it is derived from the behaviour of photons, how its likelihood is evaluated and methods for fitting it onto data.
-A model was proposed for the pixel's grey values and the expectation-maximization (EM) algorithm was implemented to fit the model onto data.
-It was found that for high photon rate, there were identifiability issues.
+A model was proposed for the grey values and the expectation-maximisation (EM) algorithm was implemented to fit the model onto data.
+It was found that for high photon rates, there were identifiability issues.
 The chapter is concluded on a discussion on why the EM algorithm failed.
@@
 In an x-ray tube, photons are emitted as a Poisson process \citep{whiting2006properties, cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}.
-This shares similarities to the compound Poisson.
+This shares similarities to the compound Poisson distribution.
 Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$.
-Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\dotsc$.
-$U_i$ has p.d.f.~$p_U(u)$.
-The random variables discussed here covers all the latent variables in the compound Poisson.
+Each photon is assumed to be i.i.d.~with random energy $U_i$ for $i=1,2,3,\dotsc$ with p.d.f.~$p_U(u)$.
+The random variables discussed here cover all the latent variables in the compound Poisson.
 
@@
 Scattered photons may be detected but it is very rare \citep{cantatore2011introduction}.
-Attenuated photon energy remains unaffected so attenuation decreases the parameter $\lambda$ and the amount it decreases by depends on the attenuation coefficient of the material and the amount of material the x-ray attenuates.
-The parameters of the random variable $U_i$ remains unchanged because the energy of each photon remains the same after attenuation, assuming no beam hardening.
+The energy of the attenuated photons remain unaffected so attenuation decreases the parameter $\lambda$.
+The amount it decreases by depends on the attenuation coefficient of the material and the amount of material the x-ray attenuates.
+The density of the random variable $U_i$ remains unchanged because the energy of each photon remains the same after attenuation, assuming no beam hardening.
 
 When the photons interact with the scintillator in the detector, they are converted into visible light.
-The visible light photons are then detected and converted into a digital signal.
-A quantum counter set the digital signal to be linear with to the number of photons detected \citep{whiting2006properties}.
+The visible light photons are then detected and converted into a digital signal or grey value.
+A quantum counter set the digital signal to be linear with the number of photons detected \citep{whiting2006properties}.
 Let $X$ be the grey value observed, then
@@
 
-An energy integrating detector records the grey value as linear to the energy detected \citep{whiting2006properties}. The grey value $X$ is
+In an energy integrating detector, the recorded grey value is linear to the energy detected \citep{whiting2006properties}. The grey value $X$ is
 \begin{equation}
@@
 \end{equation}
-This is the compound Poisson with Normal noise added to it.
+This is the compound Poisson distribution with Normal noise added to it.
 The scale factor $b$ is not included as this can be absorbed into $U$.
@@
 Experiments have been done to verify the compound Poisson nature of the detector.
-This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation, yang2010noise} at different voltages and powers.
-It was found there were two components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise.
+This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation, yang2010noise} using different exposures.
+It was found there were two components in the noise, one was signal dependent and comes from the compound Poisson distribution, the other was signal independent and may be electronic noise.
 The electronic noise can be modelled using a Normal distribution \citep{xu2009electronic}.
@@
 
-Returning back to the compound Poisson with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$.
-Let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
+Returning back to the compound Poisson with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
 It can be shown that the m.g.f.~is
@@
 
-\subsection{Compound Poisson-Gamma}
+\subsection{Compound Poisson-Gamma Distribution}
 \label{chapter:compoundPoisson_compoundPoissonGamma}
@@
 This was used for example in \cite{xu2009electronic}.
-This is known as the compound Poisson-gamma distribution.
-This is denoted by $X\sim\CPoisson(\lambda,\alpha,\beta)$ and has p.d.f.
+The distribution is known as the compound Poisson-gamma distribution and is denoted by $X\sim\CPoisson(\lambda,\alpha,\beta)$.
+The p.d.f.~is
 \begin{equation}
@@
 It can be shown that the compound Poisson-gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}.
-To show this, it is useful to parametrise the compound Poisson-gamma distribution using the following:
+To show this, the compound Poisson-gamma distribution was parametrised using the following:
 \begin{equation}
@@
 \end{equation}
-The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively.
-The parameters take the values of $1<p<2$, $\mu>0$ and $\phi>0$.
-After parametrising, it can be shown that the p.m.f.~at zero is
+The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively and take the values of $1<p<2$, $\mu>0$ and $\phi>0$. It can be shown that the p.m.f.~at zero is
 \begin{equation}
@@
 The derivation is shown in Appendix \ref{chapter:appendix_tweedie}.
-This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ and $\phi$ because the above is in the form of a distribution in the dispersive exponential family.
-
-Parameter estimation for fixed $p$ can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
-Estimating $p$ is difficult and various methods were discussed by \cite{zhang2013likelihood}.
+This is in the form of a distribution in the dispersive exponential family.\citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ and $\phi$.
+
+Parameter estimation for known $p$ can be done via the generalised linear model framework and can be extended to include linear mixed models \citep{zhang2013likelihood}.
+Estimating $p$ is difficult and various methods were discussed \citep{zhang2013likelihood}.
 One way is to estimate $\mu$ and $\phi$ on a grid of $p$'s and then select the $p$ which maximises the likelihood \citep{dunn2005series}.
@@
 
-The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma random variable.
-Suppose $\widehat{\mu}_1$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$.
-Then the estimators
+The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma distribution.
+Suppose $\widehat{\mu}_1$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$, then the estimators
 \begin{equation}
@@
 \end{equation}
-are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}, this is shown in Appendix \ref{chapter:appendix_methodofmoments} These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
+are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}, this is shown in Appendix \ref{chapter:appendix_methodofmoments}.
+These estimators suffer because estimation is not done through the sufficient statistics and can be negative.
+This is a problem because the parameters do not take non-positive values.
 
@@
 
-The evaluation of the density of a compound Poisson-gamma distribution is useful so that the likelihood can be obtained.
-The likelihood then can be used to find, for example, maximum likelihood estimators.
+The evaluation of the p.d.f.~of a compound Poisson-gamma distribution is useful so that the likelihood can be obtained.
+The likelihood can be used to find, for example, maximum likelihood estimators.
 A problem occurs when dealing with the infinite sum in the p.d.f.~because it cannot be simplified.
@@
 
-The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation or the m.g.f.~giving the p.d.f.~and has been used in XCT \citep{elbakri2003statistical, elbakri2003efficient}.
+The saddlepoint approximation \citep{daniels1954saddlepoint} uses the approximate solution to inverting the Laplace transformation or the m.g.f.
+This has been used in XCT \citep{elbakri2003statistical, elbakri2003efficient}.
 Inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}.
@@
 \end{equation}
-where $K_X(\theta) = \ln\left(M_X(\theta)\right)$, and $s=s(x)$ is the solution to the saddle point equation $K_X'(s)=x$.
+where $K_X(\theta) = \ln\left(M_X(\theta)\right)$ and $s=s(x)$ is the solution to the saddle point equation $K_X'(s)=x$.
 
@@
 
-The integral of the density approximation over the support may not equal to one, it can be numerically re-normalised if necessary.
-Thus it may be more sensible to write the approximation up to a constant
+The integral of the density approximation over the support may not equal to one and it can be numerically re-normalised if necessary.
+Thus, it may be more sensible to write the approximation up to a constant
 \begin{equation}
@@
 The infinite sum, $\sum_{y=1}^\infty W_y$, can be computationally summed in a clever way in order to evaluate the p.d.f.
-This was done by summing only large terms in the sum and ignore small terms \citep{dunn2005series}.
+This was done by summing only large terms in the sum and ignoring small terms \citep{dunn2005series}.
 \cite{dunn2005series} approximated the sum by truncation
@@
 The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonSeries}.
-Because values of $y$ should be a positive integer, it would be appropriate to round the solution to $y_\text{max}$ accordingly
+Because values of $y$ are positive integers, it would be appropriate to round $y_\text{max}$ accordingly
 \begin{equation}
@@
 
-$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}.
-To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} by using the following equation
+$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example, $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}.
+To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} by using the equation
 \begin{equation}
@@
 
-Simulations of a compound Poisson-gamma random variable were conducted with the aim to compare how well these density evaluations methods perform.
-This was done by comparing the evaluated densities with the histogram of simulations and a Q-Q plot.
+Simulations of a compound Poisson-gamma random variable were conducted with the aim to compare how well these density evaluation methods performed.
+This was done by comparing the evaluated densities using the histogram of simulations and a Q-Q plot.
 The following compound Poisson-gamma distributions were used in the simulations to capture the variety in the compound Poisson-gamma family: $\CPoisson(1,1,1)$, $\CPoisson(1,100,1)$, $\CPoisson(10,1,1)$, $\CPoisson(100,100,1)$.
-Varying $\beta$ is not interesting here as this only scales the random variable.
+For each of these distribution, 1\,000 random variables were simulated.
+Varying $\beta$ is not interesting as this only scales the random variable.
 
 There were a few technical problems with the histogram because the compound Poisson has probability mass at zero and probability density for positive numbers.
-To correctly represent the empirical distribution of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers.
+To correctly represent the empirical density of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers.
 However, the Normal approximation and the saddlepoint approximation does not have mass support at zero.
@@
 The evaluation of the p.d.f.~using the saddlepoint approximate required a bit of caution to avoid over/underflow problems.
-Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
+Suppose realisations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
 The saddlepoint approximation was computed up to a constant using
@@
 For the exact method and the saddlepoint approximation, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums.
-Because the saddlepoint approximation does not support zero, the numerical integration cannot start at zero.
+For the saddlepoint approximation, it does not support zero, thus the numerical integration started at a non-zero value.
 $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.
@@
 
-For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}to \ref{fig:compoundPoisson_histogram_approx_1_100_1}) there is a chance of simulating zeros.
+For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1} to \ref{fig:compoundPoisson_histogram_approx_1_100_1}) there was a chance of simulating zeros.
 For $\lambda = 1$, the Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values.
 The saddlepoint approximation did capture the probability mass at zero as shown by an increase in probability density towards zero.
-For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough to capture them.
+For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1}, the compound Poisson-gamma p.d.f.~contained multiple peaks and the saddlepoint approximation was not flexible enough to capture them.
 In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation of the numerical calculation of the c.d.f.~and its inversion.
 
-As $\lambda$ increased, in Figures \ref{fig:compoundPoisson_histogram_10_1_1} and \ref{fig:compoundPoisson_histogram_100_1_1}, all 3 density evaluation methods performed quite well.
-For $\CPoisson(10,1,1)$ in Figure \ref{fig:compoundPoisson_histogram_10_1_1}, the Normal approximation did not quite capture the skewness.
-In Figure \ref{fig:compoundPoisson_histogram_100_1_1}, $\lambda$ was high enough where the compound-Poisson distribution starts to converge to a Normal distribution.
+As $\lambda$ increased (Figures \ref{fig:compoundPoisson_histogram_10_1_1} and \ref{fig:compoundPoisson_histogram_100_1_1}), all 3 density evaluation methods performed quite well.
+For $\CPoisson(10,1,1)$ in Figure \ref{fig:compoundPoisson_histogram_10_1_1}, the Normal approximation did not capture the skewness.
+In Figure \ref{fig:compoundPoisson_histogram_100_1_1}, $\lambda$ was high enough where the compound-Poisson distribution started to converge to a Normal distribution.
 All methods performed well in this realm.
@@
     }
-    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
+    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical density is compared to the p.d.f.~evaluated using the exact method.
 In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
@@
     }
-    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method.
+    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical density is compared to the p.d.f.~evaluated using the exact method.
 In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
@@
     }
-    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the approximate p.d.f.
+    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical density is compared to the approximate p.d.f.
 On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
@@
     }
-    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the approximate p.d.f.
+    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical density is compared to the approximate p.d.f.
 On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
@@
     }
-    \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
+    \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical density is compared to the p.d.f.
 On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
@@
     }
-    \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.
+    \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical density is compared to the p.d.f.
 On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
@@
 
-The compound Poisson-gamma distribution can be used to model the grey values of each pixel in a projection.
+The compound Poisson-gamma distribution can be used to model the grey value of each pixel in a projection.
 Suppose a projection has $m$ pixels and $n$ replicate projections were obtained.
@@
 By assuming no beam hardening, the distribution of the photon energy does not change with attenuation.
-As a result all pixels will detect photons with identical energy distributions thus $\alpha$ and $\beta$ are the same for all pixels.
+As a result, all pixels will detect photons with identical energy distributions, thus, $\alpha$ and $\beta$ are the same for all pixels.
 Attenuation does affect the photon count, the more material a photon has to attenuate, the lower the number of detectable photons.
@@
 
-The graphical model in Figure \ref{fig:compoundPoisson_graphicalModel} illustrates how all of these variables link together.
+The graphical model in Figure \ref{fig:compoundPoisson_graphicalModel} illustrates how all of these variables are linked.
 $a$ and $\kappa$ are unknown parameters but can be estimated beforehand from replicate black images.
@@
 
-The model may be simplified by omitting the electronic noise, this can be done by setting $a=0$ and $\kappa=0$.
-The number of pixels can be set to $m=1$ as well.
+The model may be simplified by omitting the electronic noise and this can be done by setting $a=0$ and $\kappa=0$.
+The number of pixels can be set to $m=1$ to simplify the model further.
 Parameter estimation can be done using gradient methods because the likelihood of the compound Poisson can be evaluated \citep{dunn2005series}.
@@
 
-The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
-The use of the EM algorithm for the compound Poisson in XCT has been studied in \cite{elbakri2003statistical, xie2008x, xu2009electronic}.
+The EM algorithm \citep{dempster1977maximum} was proposed to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
+The use of the EM algorithm for the compound Poisson distribution in XCT have been studied in \cite{elbakri2003statistical, xie2008x, xu2009electronic}.
 
@@
 \end{equation}
-Maximum likelihood estimators are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
-
-The EM algorithm \citep{dempster1977maximum} instead treats $Y\sim\poisson(\lambda)$ as a latent variable.
-Let $\left\{Y_1,Y_2,Y_3,\dotsc, Y_n\right\}$ be realizations of $Y$ and $\left\{x_1,x_2,x_3,\dotsc, x_n\right\}$ be the respective measurements of $X|Y$.
+Maximum likelihood estimators are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximise the log likelihood.
+
+The EM algorithm \citep{dempster1977maximum} treats $Y\sim\poisson(\lambda)$ as a latent variable.
+Let $\left\{Y_1,Y_2,Y_3,\dotsc, Y_n\right\}$ be realisations of $Y$.
 Define the joint log likelihood to be
@@
 \end{multline}
-The estimators are found by optimising the joint log likelihood.
-This is done iteratively by estimating the $Y$s given the $X$s and parameters (E step), followed by estimating the parameters given the $Y$s and $X$s (M step) until some convergence conditions are met.
+The estimators were found by optimising the joint log likelihood.
+This was done iteratively by estimating the $Y$s given the $X$s and parameters (E step), followed by estimating the parameters given the $Y$s and $X$s (M step) until some convergence conditions were met.
 
@@
 
-In the E step, the realizations of $Y$ are estimate using
+In the E step, the realisations of $Y$ are estimated using
 \begin{equation}
@@
 \end{equation}
-for given parameters $\lambda$, $\alpha$ and $\beta$. The conditional expectation is calculated using
+given the parameters $\lambda$, $\alpha$ and $\beta$. The conditional expectation is calculated using
 \begin{equation}
@@
 \end{equation*}
-and
+which is simplified to
 \begin{equation}
@@
 \end{equation}
-Then the conditional expectation is
+Then, the conditional expectation is
 \begin{equation}
@@
 As discussed before, the sum in the denominator can be evaluated using the method by \cite{dunn2005series}.
-A similar method for evaluating the numerator can be obtained by truncating the sum and summing large terms.
+A similar method for evaluating the numerator can be obtained by truncating the sum and summing over large terms.
 
@@
 \end{equation}
-where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. By expressing $\ln(W^{(r)}_y)$ as
+where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. $\ln(W^{(r)}_y)$ can be expressed as
 \begin{equation}
@@
 \end{equation}
-and then taking the derivative with respect to $y$
+and taking the derivative with respect to $y$ obtains
 \begin{equation}
@@
 \end{equation}
-Therefore the maximum of $W_y^{(r)}$ is located at $y_\text{max}$ for all $r=0,1,2,\dotsc$.
-The same method of evaluating $W_y$ can be used to evaluate $W_y^{(r)}$.
+Therefore, the maximum of $W_y^{(r)}$ is located at $y_\text{max}$ for all $r=0,1,2,\dotsc$.
+As a results, the same method for evaluating $W_y$ can be used to evaluate $W_y^{(r)}$.
 For a given $r=0,1,2,\dotsc$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
@@
 \end{equation}
-obtains a M step estimator, and a familiar one, for $\lambda$. Taking the second derivative with respect to $\lambda$
+obtains a M step estimator for $\lambda$. Taking the second derivative with respect to $\lambda$
 \begin{equation}
@@
 \end{equation}
-verifies $\widehat{\lambda}$ maximises T. In addition
+verifies that $\widehat{\lambda}$ maximises $T$. In addition,
 \begin{equation}
@@
 
-Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second order can be obtained. For the first order these are:
+Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second order can be obtained. For the first order, these are:
 \begin{multline}
@@
 \end{equation}
-Since increasing $T$ is sufficient for the EM algorithm \citep{dempster1977maximum}, one step of the Newton-Raphson iterative update was chosen in the M step to avoid implementing a convergence condition.
+Since increasing $T$ is sufficient for the EM algorithm \citep{dempster1977maximum}, one step of the Newton-Raphson iterative update was chosen in the M step to avoid implementing a convergence condition for the Newton-Raphson method.
 
@@
 For $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log likelihood.
-It appears the EM algorithm failed for $\lambda>10$ looking at these particular examples.
+It appeared that the EM algorithm failed for $\lambda>10$ looking at these particular examples.
 
@@
 It should be convincing that the EM algorithm failed when the compound Poisson-gamma random variable starts behaving Normally.
-In particular in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ are stable while estimates of $\alpha$ and $\beta$ struggled to converge.
-This could be because as the compound Poisson-gamma distribution approach the Normal distribution, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate because there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$ using the three parameters $(\lambda,\alpha,\beta)$.
+In particular, in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ were stable while estimates of $\alpha$ and $\beta$ struggled to converge.
+This could be because as the compound Poisson-gamma distribution approaches the Normal distribution, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate because there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$ using the three parameters $(\lambda,\alpha,\beta)$.
 
@@
 \end{multline*}
-For high $\alpha$ and high $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$.
-Firstly, using Stirling's approximation $\ln\Gamma(n)\approx\ln(n!)\approx n\ln n-n$ then
+For high $\alpha$ and $\lambda$, and hence high $y_i$'s, an approximation can be used for the polygamma functions $\psi^{(k)}(n)$.
+Using Stirling's approximation $\ln\Gamma(n)\approx\ln(n!)\approx n\ln n-n$, then
 \begin{equation}
@@
 
-It was observed there is a saddle point in the log likelihood for the $\CPoisson(1,100,1)$ case.
+It was observed that there is a saddle point in the log likelihood for the $\CPoisson(1,100,1)$ case.
 This is when the log likelihood increased and decreased when varying $\alpha$ and $\beta$.
@@
 
-As a results, there is no unique maximum likelihood estimator and the EM algorithm would be very sensitive to the starting position, including for small $\lambda$.
+As a result, there is no unique maximum likelihood estimator and the EM algorithm would be very sensitive to the starting position, including for small $\lambda$.
 
@@
 XCT is in the realm of high $\lambda$ and this can be shown using back of the envelope calculations.
-Using the properties in the \texttt{AbsNoFilter} dataset, the power and potential difference of the x-ray tube are $P=\SI{36}{\watt}$ and $V=\SI{80}{\kilo\volt}$ respectively.
-The time exposure is $\tau=\SI{708}{\milli\second}$.
+Using the properties in the \texttt{AbsNoFilter} dataset, the power and potential difference of the x-ray tube were $P=\SI{36}{\watt}$ and $V=\SI{80}{\kilo\volt}$ respectively.
+The time exposure was $\tau=\SI{708}{\milli\second}$.
 Assume an efficiency of \SI{0.01}{{photon.}{electron}^{-1}} and the charge per electron is $e=\SI{1.602e-19}{\coulomb\,{electron}^{-1}}$.
-Assume the photons projected onto the array of $2\,000^2\,\si{\pixel}$.
-The number of photons detected per pixel is
+Assume that the photons were projected onto the array of $2\,000^2\,\si{\pixel}$.
+The number of photons detected per pixel is calculated to be
 \begin{align*}
@@
 
-All is not lost though, it was found there is a linear relationship between the variance and mean of the grey value in a pixel.
+All is not lost though, it was found that there is a linear relationship between the variance and mean of the grey value in a pixel.
 This suggest the uncertainty can be predicted by using such a relationship.

### 2019-09-11 reports/thesis/chapters/3_compoundPoisson.tex
Use proofreader

@@
 In an x-ray tube, photons are emitted as a Poisson process \citep{whiting2006properties, cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}.
-This shares similarities to the compound Poisson distribution.
+This is similar to the compound Poisson distribution.
 Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$.
@@
 Experiments have been done to verify the compound Poisson nature of the detector.
-This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation, yang2010noise} using different exposures.
-It was found there were two components in the noise, one was signal dependent and comes from the compound Poisson distribution, the other was signal independent and may be electronic noise.
+This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethene cylinder \citep{yang2009evaluation, yang2010noise} using different exposures.
+It was found there were two components in the noise, one was signal-dependent and comes from the compound Poisson distribution, the other was signal independent and maybe electronic noise.
 The electronic noise can be modelled using a Normal distribution \citep{xu2009electronic}.
@@
 One special property of the compound Poisson-gamma distribution is that it is in the Tweedie dispersion exponential family \citep{jorgensen1987exponential}.
-It can be shown that it has a special variance mean relationship
+It can be shown that it has a special variance-mean relationship
 \begin{equation}
@@
 It should be noted that this relationship is for fixed $p$ and $\phi$.
-This is different from the linear variance mean relationship found at the start of the chapter which was for fixed $\alpha$ and $\beta$ from assuming no beam hardening.
+This is different from the linear variance-mean relationship found at the start of the chapter which was for fixed $\alpha$ and $\beta$ from assuming no beam hardening.
 
@@
 A problem occurs when dealing with the infinite sum in the p.d.f.~because it cannot be simplified.
-There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
+There are several approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}.
 Monte Carlo methods can be used to evaluate the p.d.f.~by simulating compound Poisson-gamma random variables.
@@
 
-The infinite sum, $\sum_{y=1}^\infty W_y$, can be computationally summed in a clever way in order to evaluate the p.d.f.
+The infinite sum, $\sum_{y=1}^\infty W_y$, can be computationally summed cleverly to evaluate the p.d.f.
 This was done by summing only large terms in the sum and ignoring small terms \citep{dunn2005series}.
@@
 
-Simulations of a compound Poisson-gamma random variable were conducted with the aim to compare how well these density evaluation methods performed.
+Simulations of a compound Poisson-gamma random variable were conducted to compare how well these density evaluation methods performed.
 This was done by comparing the evaluated densities using the histogram of simulations and a Q-Q plot.
@@
 There were a few technical problems with the histogram because the compound Poisson has probability mass at zero and probability density for positive numbers.
-To correctly represent the empirical density of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers.
+To correctly represent the empirical density of a compound Poisson random variable, a bar chart was used to show the frequency of zeros and a histogram to show the frequency density of positive numbers.
 However, the Normal approximation and the saddlepoint approximation does not have mass support at zero.
@@
 
-Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log likelihood is defined to be
+Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log-likelihood is defined to be
 \begin{equation*}
@@
 \end{equation}
-Maximum likelihood estimators are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximise the log likelihood.
+Maximum likelihood estimators are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximise the log-likelihood.
 
@@
 Let $\left\{Y_1,Y_2,Y_3,\dotsc, Y_n\right\}$ be realisations of $Y$.
-Define the joint log likelihood to be
+Define the joint log-likelihood to be
 \begin{multline*}
@@
 \end{multline}
-The estimators were found by optimising the joint log likelihood.
+The estimators were found by optimising the joint log-likelihood.
 This was done iteratively by estimating the $Y$s given the $X$s and parameters (E step), followed by estimating the parameters given the $Y$s and $X$s (M step) until some convergence conditions were met.
@@
 
-In the M step, the conditional expected joint log likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is
+In the M step, the conditional expected joint log-likelihood is maximised with respect to the parameters $\lambda$, $\alpha$ and $\beta$. The objective function is
 \begin{align}
@@
 
-Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second order can be obtained. For the first order, these are:
+Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second-order can be obtained.
+For the first-order derivatives, these are:
 \begin{multline}
@@
 \end{equation}
-The second orders are:
+The second-order derivatives are:
 \begin{equation}
@@
 The EM algorithm was initialised with its parameters at the true values to investigate the convergence in that vicinity.
-The log likelihood $\ln L(\lambda,\alpha,\beta;X)$ and the parameters were recorded at every EM step.
+The log-likelihood $\ln L(\lambda,\alpha,\beta;X)$ and the parameters were recorded at every EM step.
 The experiment was repeated 10 times using different simulated samples.
@@
 
-For $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log likelihood.
+For $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log-likelihood.
 It appeared that the EM algorithm failed for $\lambda>10$ looking at these particular examples.
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha1beta1_lnL.eps}
-        \caption{Log likelihood}
+        \caption{Log-likelihood}
     \end{subfigure}
@@
     \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda1alpha100beta1_lnL.eps}
-        \caption{Log likelihood}
+        \caption{Log-likelihood}
     \end{subfigure}
@@
     \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda10alpha1beta1_lnL.eps}
-        \caption{Log likelihood}
+        \caption{Log-likelihood}
     \end{subfigure}
@@
     \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
         \includegraphics[width=\textwidth]{../figures/compoundpoisson/CpEmAlgorithm_CompoundPoissonlambda100alpha100beta1_lnL.eps}
-        \caption{Log likelihood}
+        \caption{Log-likelihood}
     \end{subfigure}
@@
     \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
 In particular, in Figure \ref{fig:compoundPoisson_convergence_4}, estimates of $\lambda$ were stable while estimates of $\alpha$ and $\beta$ struggled to converge.
-This could be because as the compound Poisson-gamma distribution approaches the Normal distribution, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate because there is more than one way to represent a two parameter random variable $\normal(\mu,\sigma^2)$ using the three parameters $(\lambda,\alpha,\beta)$.
+This could be because as the compound Poisson-gamma distribution approaches the Normal distribution, the parameters $(\lambda,\alpha,\beta)$ becomes degenerate because there is more than one way to represent a two-parameter random variable $\normal(\mu,\sigma^2)$ using three parameters $(\lambda,\alpha,\beta)$.
 
@@
 
-\subsection{Log Likelihood Plot}
+\subsection{Log-Likelihood Plot}
 
@@
     }
-    \caption{Log likelihood from a simulation of 100 compound Poisson-gamma random variables. $\lambda$ is fixed at the true value.}
+    \caption{Log-likelihood from a simulation of 100 compound Poisson-gamma random variables. $\lambda$ is fixed at the true value.}
     \label{fig:compoundPoisson_loglikelihoodplot}
@@
 
-The log likelihood, using a simulation of 100 compound Poisson-gamma random variables, are plotted for fixed $\lambda$ in Figure \ref{fig:compoundPoisson_loglikelihoodplot}.
-These plots are concerning because the likelihood appeared not to be convex and there is no unique maxima for all $\lambda$ investigated.
-
-It was observed that there is a saddle point in the log likelihood for the $\CPoisson(1,100,1)$ case.
-This is when the log likelihood increased and decreased when varying $\alpha$ and $\beta$.
-This suggest a possibility of a local maxima.
+The log-likelihood, using a simulation of 100 compound Poisson-gamma random variables, are plotted for fixed $\lambda$ in Figure \ref{fig:compoundPoisson_loglikelihoodplot}.
+These plots are concerning because the likelihood appeared not convex and there is no unique maximum for all $\lambda$ investigated.
+
+It was observed that there is a saddle point in the log-likelihood for the $\CPoisson(1,100,1)$ case.
+This is when the log-likelihood increased and decreased when varying $\alpha$ and $\beta$.
+This suggests the possibility of local maxima.
 
@@
 All is not lost though, it was found that there is a linear relationship between the variance and mean of the grey value in a pixel.
-This suggest the uncertainty can be predicted by using such a relationship.
+This suggests that uncertainty can be predicted by using such a relationship.
 The next chapter investigates this.

### 2019-09-12 reports/thesis/chapters/4_variancePrediction.tex
Revise

@@
-In the previous chapter, it was found that it was hard to fit a compound Poisson distribution onto the grey values.
+It was found that it was hard to fit a compound Poisson distribution onto the grey values.
 Results did show that the variance of the grey value has a linear relationship with the mean grey value.
@@
 
-The sample variance-mean data were obtained from the replicated projections.
+The sample variance-mean data were obtained from the replicate projections.
 Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotsc,n$.
-The pixel sample mean is
+The sample mean and sample variance grey value for the pixel at $(i,j)$ are
 \begin{equation}
@@
 \end{equation}
-and the pixel sample variance is
+and
 \begin{equation}
@@
         \right)^2
-    \ .
 \end{equation}
-Only pixels in the region of interest (ROI) were considered here, that is pixels which represent the test sample. The ROI was created by manually segmenting the test sample from the projection.
+respectively.
+Only pixels in the region of interest (ROI) were considered here, that is, pixels which represent the test sample.
+The ROI was created by manually segmenting the test sample from the projection.
 
-The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by fitting a model onto the sample variance-mean data.
-No spatial information was used, thus the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
+The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by using a model fitted onto the sample variance-mean data.
+No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
 Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$.
-It was assumed the standard error from estimating the mean was negligible so that the uncertainty is captured by the random variable $Y$.
+It was assumed that the standard error from estimating the mean was negligible so that the uncertainty is captured by the random variable $Y$.
 It was assumed that for a given pixel, the grey values are Normal and i.i.d.
@@
 This framework allows the use of generalised linear models (GLM) \citep{nelder1972generalized,nelder1972generalized_2, mccullagh1984generalized}.
-In the gamma distribution case, GLM can be used to model
+In the gamma distribution case, a GLM can be used to model
 \begin{equation}
@@
 There is also the log link $g(y)=\ln y$ but $y$ must be a unitless quantity, for example Poisson counts, for it to be comparable.
-Because $y$ is in units of $\SI{}{\adu^2}$, the log link is not used in this analysis.
+Because $y$ is in units of $\SI{}{\adu^2}$, the log link was not used in this analysis.
 
-An example of a systematic component are polynomial features $\eta(x)=\beta_0+\sum_{j=1}^{p-1}\beta_j x^j$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \beta_0+\sum_{j=1}^{p-1}\beta_j x^j$.
-Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \dotsc, \beta_{p-1}$ given data for the model to fit onto.
+An example of a systematic component are polynomial features $\eta(x)=\sum_{r=0}^{p}\beta_r x^{r}$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \sum_{r=0}^{p}\beta_r x^{r}$.
+Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_2, \dotsc, \beta_{p}$ given data for the model to fit onto.
 
@@
 \begin{equation}
-\AIC = 2p-2\ln L
+\AIC = 2k-2\ln L
 \end{equation}
@@
 \begin{equation}
-\BIC = p\ln m - 2\ln L
+\BIC = k\ln m - 2\ln L
 \end{equation}
-respectively where $p$ is the number of features in the systematic component and $\ln L$ is the log likelihood of the GLM.
+respectively where $k$ is the number of parameters in the systematic component and $\ln L$ is the log-likelihood of the GLM.
 The model with the lowest AIC or BIC is preferred.
-GLM aims to maximise the log likelihood but the additional terms in the criteria penalise models with too many terms.
-The log likelihood is given as
+GLM aims to maximise the log-likelihood but the additional terms in the criteria penalise models with too many terms.
+The log-likelihood is given as
 \begin{equation}
@@
 \end{equation}
-where $\widehat{y}_i=\widehat{y}(x_i)$. It should be reminded that $\alpha=(n-1)/2$ was assumed to be known and does not need to be estimated.
+where $\widehat{y}_i=\widehat{y}(x_i)$. $\alpha=(n-1)/2$ was assumed to be known so does not need to be estimated.
 
 The procedure is as follows.
-A criterion and a link function is chosen beforehand.
-In the initial step, a GLM with systematic component $\eta(x)=\beta_0$ is fitted and the criterion is recorded.
-In the next step, a polynomial feature with one order higher is added to the systematic component $\eta(x)=\beta_0+\beta_1 x$, fitted and the criterion recorded.
-In addition, a polynomial feature with one order lower is added $\beta(x)=\beta_{-1}x^{-1}+\beta_0$ and fitted separately with the criterion recorded.
-The model which decreases the criterion the most is accepted.
-Adding higher and lower order polynomials to the systematic component is repeated, for example after accepting $\eta(x)=\beta_0+\beta_1 x$, the following systematic components $\eta(x)=\beta_0+\beta_1 x+\beta_2x^2$ and $\eta(x)=\beta_{-1}x^{-1}+\beta_0+\beta_1 x$ are fitted and assessed.
-The fitted parameters $\beta_0$ and $\beta_1$ may change when adding more terms.
+A criterion and a link function was chosen beforehand.
+In the initial step, a GLM with systematic component $\eta(x)=\beta_0$ was fitted and the criterion was recorded.
+In the next step, a polynomial feature with one order higher was added to the systematic component $\eta(x)=\beta_0+\beta_1 x$, fitted and the criterion recorded.
+In addition, a polynomial feature with one order lower was added $\beta(x)=\beta_{-1}x^{-1}+\beta_0$ and fitted separately with the criterion recorded.
+The model which decreased the criterion the most was accepted.
+Adding higher and lower order polynomials to the systematic component was repeated, for example after accepting $\eta(x)=\beta_0+\beta_1 x$, the following systematic components $\eta(x)=\beta_0+\beta_1 x+\beta_2x^2$ and $\eta(x)=\beta_{-1}x^{-1}+\beta_0+\beta_1 x$ were fitted and assessed.
+The fitted parameters, $\beta_0$ and $\beta_1$ in this example, may change when adding more terms.
 This is repeated until the criterion cannot be decreased and the procedure is left with the final model.
@@
 Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter}.
-The procedure was repeated 10 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data.
+The procedure was repeated 10 times by using a random permutation with replacement of the replicate projections to obtain a different sample variance-mean data which introduced some variation to the data \citep{efron1979bootstrap}.
 The procedure was also repeated using various shading corrections to investigate the effects of shading correction on the variance-mean relationship.
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{30}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsNoFilter} at \ang{30}.
 The columns of the table represent different shading corrections used on the projections.
-Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
 `Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsNoFilter} at \ang{120}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsNoFilter} at \ang{120}.
 The columns of the table represent different shading corrections used on the projections.
-Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
 `Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{30}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsFilter} at \ang{30}.
 The columns of the table represent different shading corrections used on the projections.
-Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
 `Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
@@
 \end{tabular}
-\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data of the grey values from the projections in \texttt{AbsFilter} at \ang{120}.
+\caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsFilter} at \ang{120}.
 The columns of the table represent different shading corrections used on the projections.
-Forward stepwise selection was repeated 10 times by using a different random permutation with replacement to obtain a different sample variance-mean data.
+Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
 `Order' shows the most commonly selected polynomial orders and `votes' shows the number of times it was selected out of the 10 repeats.
@@
 Different shading correction or different criteria had no effect on the selected model.
-The method is quite robust to the variation introduced to the dataset when repeating the experiment because all 10 repeats consistently selected the same model.
+The method was quite robust to the variation introduced to the dataset when repeating the experiment because all 10 repeats consistently selected the same model.
 
 There was some variation to the selected models between datasets.
-For example when using the identity link, \texttt{AbsNoFilter} prefers $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilter} prefers $\eta(x)=\beta_{-1}x^{-1}+\beta_0$.
+For example, when using the identity link, \texttt{AbsNoFilter} preferred $\eta(x)=\beta_0+\beta_1 x$ whereas \texttt{AbsFilter} preferred $\eta(x)=\beta_{-1}x^{-1}+\beta_0$.
 Using the canonical link, both datasets selected $\eta(x)=\beta_{-1}x^{-1}+\beta_0$ which correspond to $\widehat{y}(x)=\left(\beta_{-1}x^{-1}+\beta_0\right)^{-1}$.
@@
 The fits all looked reasonable except for \texttt{AbsNoFilter} at \ang{120} where the fit did not capture the inflection.
-The forward stepwise selection may not pick this up because there are a lot of low grey values, causing a leverage towards these low grey values and the inflection does not stand out to the method.
+The forward stepwise selection may not picked this up because there were a lot of low grey values, causing a leverage towards these low grey values.
+As a result, the inflection did not stand out to the method.
 
@@
 
-Instead of assessing the model fit using the AIC and BIC, the performance on predicting the variance given a grey value can be assessed using cross validation \citep{friedman2001elements}.
-Cross validation assess the model to make predictions on data it has not seen before.
-This is done by randomly splitting the $m$ data points into two disjoint sets, the training set and the test set.
+Instead of assessing the model fit using the AIC and BIC, the performance on predicting the variance given a grey value was assessed using cross validation \citep{friedman2001elements}.
+Cross validation assesses the model to make predictions on data it has not seen before.
+This was done by randomly splitting the $m$ data points into two disjoint sets, the training set and the test set.
 It was chosen that the training and test set are of the same size.
-The model is fitted onto the training set.
-Afterwards, the fitted model predict the variances given the grey values in the test set which are compared to the actual variances.
+The model was fitted onto the training set.
+Afterwards, the fitted model predicts the variances given the grey values in the test set which were then compared to the actual variances.
 
@@
 
-The mean scaled deviance is a loss function which increases as $y_i/\widehat{y}_i$ deviates from one, this is shown in Figure \ref{fig:meanVar_deviance} and it should be noted the $x$-axis is in log scale.
-Another way to show this is by letting $r_i = y_i/\widehat{y}_i$ and $d_i = 2\left[r-1-\ln r\right]$ be an element from the sum in the deviance.
-For $r_i\approx 1$, $\ln(r)\approx(r-1)-(r-1)^2/2$ which implies $d_i\approx (r-1)^2$ with minimum at one.
+The mean scaled deviance is a loss function which increases as $y_i/\widehat{y}_i$ deviates from one, this is shown in Figure \ref{fig:meanVar_deviance} and it should be noted that the $x$-axis is in log scale.
+Another way to show this is by letting $r_i = y_i/\widehat{y}_i$ and $d_i = 2\left[r_i-1-\ln r_i\right]$ be an element from the sum in the deviance.
+For $r_i\approx 1$, $\ln(r_i)\approx(r_i-1)-(r_i-1)^2/2$ which implies that $d_i\approx (r_i-1)^2$ with minimum at one.
 For $r_i$ deviate greatly from one, the loss function is asymmetric.
 For example a ratio of $r_i=10^1$ has a greater penalty than $r_i=10^{-1}$.
-This means in extreme cases, overestimates are penalised less than underestimates relative to $y_i$.
+This means that in extreme cases, overestimates are penalised less than underestimates relative to $y_i$.
 
-Assuming the model is correct, it is given that $D\sim\chi_{m-p}^2$ which implies that for large $m$,
+Assuming the model is correct, it is given that $D\sim\chi_{m-k}^2$ which implies that for large $m$,
 \begin{equation}
@@
 They are ${y}(x)=\beta_0+\beta_1 x$ and ${y}(x)=\beta_{-1}x^{-1}+\beta_0$ using the identity link and ${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ using the canonical link.
-The analysis was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data.
+The analysis was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data \citep{efron1979bootstrap}.
 
@@
   \caption{Test mean scaled deviance from predicting variances in a test set using a GLM fitted onto a training set.
-The box plot represent the 100 repeats of the analysis by by using a random permutation with replacement of the replicated projections to work out a different sample variance-mean data.}
+The box plot represent the 100 repeats of the analysis by bootstrapping the replicate projections.}
   \label{fig:meanVar_varMeanCv}
@@
 
-A residual analysis was conducted to look for anything overlooked.
-The model ${y}(x)=\beta_0+\beta_1 x$ was analysed A residual plot plots $r_i=y_i-\widehat{y}(x_i)$ for all $x_i$ in the dataset.
-This was done using a 2D histogram.
-Due to the gamma GLM, higher grey values typically have bigger residuals in magnitude, a predicted residual interval is included in the histogram to aid judging the residuals.
-This interval was obtained by obtaining the prediction interval and subtracting it from the fit.
+A residual analysis was conducted to study for anything overlooked.
+The model ${y}(x)=\beta_0+\beta_1 x$ was fitted onto the entire sample variance-mean data.
+A residual plot plots $r_i=y_i-\widehat{y}(x_i)$ for all $x_i$ in the dataset which was done using a 2D histogram.
+Due to the gamma GLM, higher grey values typically have bigger residuals in magnitude.
+A predicted residual interval is included in the histogram to aid judging the residuals.
+This interval was acquired by obtaining the prediction interval and subtracting it from the fit.
 
@@
   \caption{Log frequency density histogram of the residuals given the mean grey value.
-The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
+The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicate projections.
 The dashed red line shows the 68\% confidence interval of the predicted residual.}
@@
 The residual plots are shown in Figure \ref{fig:meanVar_residualGreyvalue}.
-The residuals are all sensible and increase in size with grey value which is captured by the predicted residual interval.
+The residuals are all sensible and increased in magnitude with grey value which is captured by the predicted residual interval.
 The inflection in \texttt{AbsNoFilter} at \ang{120}, as discussed previously, can be seen more clearly here.
@@
   }
-  \caption{Absolute value residuals from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections.
+  \caption{Absolute value residuals from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicate projections.
 Highlighted in a red box is an example of an inflection.}
@@
 Because no spatial information was used in modelling the variance, the residuals were plotted on top of the projections to look for any spatial structure, this is shown in Figure \ref{fig:meanVar_spatialResidual}.
-Because of the geometry of the test sample, lower grey values, thus smaller residuals, are found in the middle of the projection.
-Similarly, higher grey values, thus bigger residuals, are found on the edges of the test sample.
+Because of the geometry of the test sample, lower grey values, thus smaller residuals, were found in the middle of the projection.
+Similarly, higher grey values, thus bigger residuals, were found on the edges of the test sample.
 Considering that, the residuals do not show any striking spatial structure.
@@
 In terms of cross-validation, most of the models looked at have similar prediction performance when predicting the variance given a grey value.
-Thus the relationship $\widehat{y}(x)=\beta_0+\beta_1 x$ using the identity link is attractive for its simplicity and links with the compound Poisson model.
+Thus, the relationship $\widehat{y}(x)=\beta_0+\beta_1 x$ using the identity link is attractive for its simplicity and links with the compound Poisson model.
 
-It was found shading correction had little effect on the variance-mean relationship.
+It was found that shading correction had little effect on the variance-mean relationship.
 
-As discussed in the compound Poisson chapter, a linear relationship can be derived by assuming no beam hardening.
-Then it should be expected that a linear relationship is observed in the dataset \texttt{AbsFilter}.
+As discussed in the compound Poisson chapter, a linear relationship can be derived by assuming no beam hardening, then it should be expected that a linear relationship is observed in the dataset \texttt{AbsFilter}.
 In the forward stepwise selection, \texttt{AbsNoFilter} consistently selected the linear model, given the identity link function.

### 2019-09-12 compoundpoisson/cpLogLikelihoodPlot.m

@@ -79,7 +79,7 @@ function cpPlotlnL(compoundPoisson, alpha, beta, n)
   surf(alphaGrid, betaGrid, lnLFullGrid);
   xlabel('\alpha');
   ylabel('\beta');
-  zlabel('log likelihood');
+  zlabel('log-likelihood');
   view(-45,35.264);
   saveas(fig, fullfile(fullfile('reports','figures','compoundpoisson'), ...
       strcat(mfilename,'_',compoundPoissonTrue.toString(),'.eps')),'epsc');

### 2019-09-12 varmean/glmselect/GlmSelect.m

@@ -99,9 +99,9 @@ classdef GlmSelect < Experiment
 
           end
 
-          %quote deviance
+          %quote criteria
           devianceQuote = siUncertainity(mean(this.criterionArray(:,iLink,iShadingCorrection)), ...
-              std(this.criterionArray(:,iLink,iShadingCorrection)), 2);
+              std(this.criterionArray(:,iLink,iShadingCorrection)), 1);
           %quote polynomial with the most votes
           [maxCount,maxKey] = max(polynomialCount);
           

### 2019-09-12 reports/thesis/chapters/4_variancePrediction.tex
Use proofreader

@@
 As a result, it would be possible to predict the variance of the grey value, given the grey value.
-This opens up new ways to predict the uncertainty of each individual pixel in an x-ray projection.
+This opens up new ways to predict the uncertainty of each pixel in an x-ray projection.
 
 In this chapter, generalised linear models \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} with different link functions and polynomial features were selected using forward step-wise selection.
-These selected models were compared using cross validation to find the best model and verified using residual analysis.
+These selected models were compared using cross-validation to find the best model and verified using residual analysis.
 
@@
 The procedure is as follows.
-A criterion and a link function was chosen beforehand.
+A criterion and a link function were chosen beforehand.
 In the initial step, a GLM with systematic component $\eta(x)=\beta_0$ was fitted and the criterion was recorded.
 In the next step, a polynomial feature with one order higher was added to the systematic component $\eta(x)=\beta_0+\beta_1 x$, fitted and the criterion recorded.
-In addition, a polynomial feature with one order lower was added $\beta(x)=\beta_{-1}x^{-1}+\beta_0$ and fitted separately with the criterion recorded.
+Also, a polynomial feature with one order lower was added $\beta(x)=\beta_{-1}x^{-1}+\beta_0$ and fitted separately with the criterion recorded.
 The model which decreased the criterion the most was accepted.
@@
 Forward stepwise selection was conducted on the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter}.
-The procedure was repeated 10 times by using a random permutation with replacement of the replicate projections to obtain a different sample variance-mean data which introduced some variation to the data \citep{efron1979bootstrap}.
+The procedure was repeated 10 times by using a random permutation, with replacement, of the replicate projections to obtain a different sample variance-mean data which introduced some variation to the data \citep{efron1979bootstrap}.
 The procedure was also repeated using various shading corrections to investigate the effects of shading correction on the variance-mean relationship.
@@
 
-\section{Cross Validation}
+\section{Cross-Validation}
 
-Instead of assessing the model fit using the AIC and BIC, the performance on predicting the variance given a grey value was assessed using cross validation \citep{friedman2001elements}.
-Cross validation assesses the model to make predictions on data it has not seen before.
+Instead of assessing the model fit using the AIC and BIC, the performance on predicting the variance given a grey value was assessed using cross-validation \citep{friedman2001elements}.
+Cross-validation assesses the model to make predictions on data it has not seen before.
 This was done by randomly splitting the $m$ data points into two disjoint sets, the training set and the test set.
@@
 
-The results from the cross validation is shown in Figure \ref{fig:meanVar_varMeanCv}.
-The performance of the three candidate models were very similar.
+The results from the cross-validation is shown in Figure \ref{fig:meanVar_varMeanCv}.
+The performances of the three candidate models were very similar.
 One exception is the model ${y}(x)=\beta_{-1}x^{-1}+\beta_0$ fitted onto the \texttt{AbsNoFilter} dataset, the mean scaled deviance was significantly larger and this is expected from a model not favoured in the forward step-wise selection in the previous section.
 
-Shading correction did not had a significant effect in the analysis.
+Shading correction did not have a significant effect on the analysis.
 
@@
 
-A residual analysis was conducted to study for anything overlooked.
+Residual analysis was conducted to study for anything overlooked.
 The model ${y}(x)=\beta_0+\beta_1 x$ was fitted onto the entire sample variance-mean data.
@@
 The residual plots are shown in Figure \ref{fig:meanVar_residualGreyvalue}.
-The residuals are all sensible and increased in magnitude with grey value which is captured by the predicted residual interval.
+The residuals are all sensible and increased in magnitude with the grey value which is captured by the predicted residual interval.
 The inflection in \texttt{AbsNoFilter} at \ang{120}, as discussed previously, can be seen more clearly here.
@@
 With the ability to predict the variance given a grey value of a pixel, the uncertainty can be quantified.
-In the next chapter, the projection is compared to a simulated projection under the face of that uncertainty.
+In the next chapter, the projection is compared to a simulated projection in the face of that uncertainty.

### 2019-09-12 reports/thesis/chapters/3_compoundPoisson.tex
Add and adjust bib

@@
 
-The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} from the Fisher's information matrix defined as
+The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} from the Fisher's information matrix \citep{fisher1922on} defined as
 \begin{equation}

### 2019-09-12 reports/thesis/chapters/4_variancePrediction.tex
Add and adjust bib

@@
 
-This section describes how forward stepwise selection \citep{friedman2001elements} was used to select which polynomial features to use in the systematic component.
+This section describes how forward stepwise selection \citep{efroymson1960multiple, friedman2001elements} was used to select which polynomial features to use in the systematic component.
 
@@
 This is continued until the model cannot be improved subject to overfitting.
-The Akaike information criterion (AIC) \citep{friedman2001elements} and the Bayesian information criterion (BIC) \citep{friedman2001elements} are criteria which can be used to assess the fit of the model at each step without overfitting to the data too much.
+The Akaike information criterion (AIC) \citep{akaike1974new, friedman2001elements} and the Bayesian information criterion (BIC) \citep{schwarz1978estimating, friedman2001elements} are criteria which can be used to assess the fit of the model at each step without overfitting to the data too much.
 

### 2019-09-15 reports/thesis/chapters/5_inference.tex
Revise

@@
-Disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other, any values too big in magnitude can be considered as a defect.
-However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance.
-Thus the comparisons should be done under the face of uncertainty.
-
-A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ was calculated for all pixels at $(x,y)$. This test statistic is
+Disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other.
+Any values too big in magnitude can be considered as a defect.
+However, in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance.
+Thus, the comparisons should be done in the face of uncertainty.
+
+A pixel by pixel hypothesis test was proposed to do defect detection. The test statistic, for the pixel located at $(x,y)$, is
 \begin{equation}
@@
 \end{equation}
-where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.
+where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance.
+The test statistic was calculated for each pixel in the projection.
 For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution.
-Thus by treating the simulated projection from \emph{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
+Thus, if there are no significant differences between the obtained and \emph{aRTist} projections, then the randomness of the test statistics can be approximately quantified as
 \begin{equation}
@@
 \end{equation}
-As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.
+As with usual statistical convention, an upper case $Z$ denotes a random variable. A lower case $z$ denotes a realisation or an observation of that random variable.
 
 To illustrate this method of inference, the projections from the dataset \texttt{AbsFilter} at \ang{120} was used.
-To recap, replicate projections of a test sample with purposefully manufactured voids were obtained.
+To recap, replicate projections of a test sample, with purposefully manufactured voids, were obtained.
 \emph{aRTist} was used to create a simulation of that projection but as if the voids were not there.
@@
 
-A projection and the \emph{aRTist} projection is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
+The obtained and \emph{aRTist} projections are shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
 The 20 replicate projections were spilt into two.
 19 randomly selected projections were used for the variance-mean model to fit onto.
-A gamma GLM with a basic linear relationship was used.
-The remaining projection was compared with the \emph{aRTist} projection, the variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.
+A gamma GLM, with a basic linear relationship, was used for the variance-mean model.
+The remaining projection was compared with the \emph{aRTist} projection.
+The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.
 
@@
   }
-  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect the purposefully manufactured voids.
-The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level.
-Pixels detected as positive are shown in red in d).}
+  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect purposefully manufactured voids.
+The $p$-values obtained were used for hypotheses testing.
+Pixels detected as positive are shown in red in d) using the \cite{benjamini1995controlling} procedure at the 5\% false discovery rate level.}
   \label{fig:inference_inferenceIntro_inference}
@@
 
-For each pixel, a test statistic was calculated.
+For each pixel, a test statistic was calculated, which forms a $z$ image.
 A test statistic too large in magnitude, relative to the anticipated variance, will classify that pixel as a positive result.
-In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
+In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, $p$-values can be used to represent the test statistics in a different way
 \begin{equation}
@@
 It should be expected that small $p$-values are in areas of the defects.
-Pixels are tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$.
+Pixels were tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$ to 2 decimal places.
 This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure.
@@
 The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}.
-It can be seen that the majority of the test statistics does come from a Normal distribution.
-Also, the majority of the $p$-values are not look uniformly distributed.
+It can be seen that the test statistics were not compatible with the standard Normal distribution.
+Also, the majority of the $p$-values did not look uniformly distributed.
 This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.
@@
 b) The $p$-values are ordered and plotted.
-The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure.
+The critical region corresponds to controlling the false discovery rate at 5\% level using the \cite{benjamini1995controlling} procedure.
 The dotted line shows the result if the $p$-values were uniformly distributed.}
@@
 
-Consider a test statistic from a pixel.
+Consider a test statistic $Z$ from a pixel.
 If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$.
-This can be described in another way by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$.
+This can be described by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$.
 A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$.
-A statistic which does not have the null distribution is known as non-null.
-
-In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example.
+A statistic which does not has the null distribution is known as non-null.
+
+In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user-defined size of the test $\alpha$, also known as the significance level in this specific example.
 A positive result is declared when $p<\alpha$, else it is a negative result.
 Correct and incorrect testing of the statistics can occur.
-For example testing a null statistic as positive is known as a false positive.
+For example, testing a null statistic as positive is known as a false positive.
 It can be shown that $\alpha$ controls the false positive rate.
 $\alpha=5.0\%$ is a typical choice \citep{wasserstein2019moving} and is used throughout this thesis.
-Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.
-
-Multiple hypothesis testing occurs when there are more than one hypotheses to test.
-For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$.
+
+Multiple hypotheses testing occurs when there are more than one hypotheses to test.
+For example, $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$.
 The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,n$.
@@
 PCER is the proportion of false positives out of all tests.
-The number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}.
-Using the notation, PCER is defined as
+The notation for the number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}.
+Using the notation, the PCER is defined as
 \begin{equation}
@@
   \end{tabular}
-  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
+  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypotheses testing}
   \label{table:inference_randomvariables}
@@
 \end{equation}
-However, in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives.
+In practice, the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives.
 This is because the correction traded too many false positives for false negatives.
@@
 
-The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test.
-It adapts to the data and choose different sizes for different data.
+The BH procedure adjusts the size of the test between the Bonferroni correction and the uncorrected test.
+It adapts to the data and chooses different sizes for different data.
 The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(n)}$.
@@
 The BH procedure comes from the fact that if all the statistics are null and independent, then the $p$-values are uniformly distributed \citep{simes1986improved}.
-However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.
+However, it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.
 It can be shown that the BH procedure controls the FDR such that
@@
     \end{tabular}
-    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
+    \caption{Different types of corrections for multiple hypotheses testing are listed here, along with what they control for.}
     \label{table:inference_corrections}
@@
 
-Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+Consider a small example where a $\SI{200}{\pixel}\times\SI{200}{\pixel}$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}.
 The distribution of the test statistics appeared Normal but not centred at zero.
-So by using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$, almost half of the pixels were tested positive.
-It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.
+By using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$ to 2 decimal places, almost half of the pixels were tested positive.
+It is questionable whether such a number of positive results is sensible, in particular, in an area where defects were not expected.
 
@@
     \caption{The resulting $z$ image is shown in a).
-A $200\times 200$ sub-image was taken shown by the dashed lines.
+A $\SI{200}{\pixel}\times\SI{200}{\pixel}$ sub-image was taken shown by the dashed lines.
 A histogram of the test statistics in the sub-image is shown in b).
-The critical region was obtained by using the BH procedure at the 5\% FDR level.}
+The critical region corresponds to the 5\% FDR level.}
     \label{fig:inference_inferenceSubsample1_histogram}
@@
 
-This problem commonly occur in large scale multiple hypothesis testing \citep{efron2004large} such as in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
-It appears that the null distribution was misspecified as $Z_i|H_{0,i}\sim\normal(0,1)$ when in reality they are distributed as $Z_i|H_{0,i}\sim\normal(\mu_0,\sigma_0^2)$, where $\mu_0$ and $\sigma_0$ are the null mean and null standard deviation respectively.
+This problem commonly occurs in large scale multiple hypotheses testing \citep{efron2004large} such as in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}.
+It appeared that the null distribution was misspecified as $Z_i|H_{0,i}\sim\normal(0,1)$ when in reality they are distributed as $Z_i|H_{0,i}\sim\normal(\mu_0,\sigma_0^2)$, where $\mu_0$ and $\sigma_0$ are the null mean and null standard deviation respectively.
 
@@
 The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified.
-Assume that the majority of the data are null and non-null test statistics are rare, say $\pi_0>0.9$ \citep{efron2004large}.
-Then around the mode, the probability density function would be dominated by the null distribution.
+Assume that the majority of the data are null and non-null test statistics are rare, say $\pi_0>0.9$ \citep{efron2004large}, then around the mode, the probability density function would be dominated by the null distribution.
 This implies that
@@
   \right)
-  \nonumber\\
-  &=
+  \\
+  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) &=
   -\dfrac{
@@
 This method does not need estimations of $\pi_0$ which makes it quite convenient.
-The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}.
-\cite{efron2004large} motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.
+Estimations of $\pi_0$ are discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}.
+\cite{efron2004large} motivated the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.
 
 The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
-There exist various methods for the empicial null.
-\cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate.
+There exist various methods for the empicial null, for example, \cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate.
 The empirical characteristic function was used in \cite{jin2007estimating}.
@@
 \end{equation}
-where $h$ is the bandwidth and $phi(x)$ is the standard Normal density. The bandwidth was chosen such that
+where $h$ is the bandwidth and $\phi(x)$ is the standard Normal density. The bandwidth was chosen such that
 \begin{equation}
@@
 The null standard deviation was estimated using Equation \eqref{eq:inference_nullStdEstimator}.
-This results in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
+This resulted in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
 In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.
@@
 \end{equation}
-and then were used in the BH procedure.
+and were used in the BH procedure.
 The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$.
@@
     }
-    \caption{Histogram of the test statistics from the sub-image in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
-Also shown are the critical regions and $p$-values which were adjusted using the empirical null.}
+    \caption{Histogram and $p$-values of the test statistics from the sub-image in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+The critical regions were adjusted using the empirical null and correspond to the 5\% FDR level.}
     \label{fig:inference_inferenceSubsample1_nullResults}
@@
 
-No positive results were found and the $p$-values were sensible as they resemble the uniformly distribution.
+No positive results were found and the $p$-values were sensible as they resemble the uniform distribution.
 This demonstrated that the empirical null adjusted the parameters of the null distribution to fit onto the majority of the data in order to make sensible inference.
@@
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_zImage.eps}
-        \caption{test statistics}
+        \caption{Test statistics}
     \end{subfigure}
@@
     }
-    \caption{A $200\times 200$ sub-image containing a defect is shown in a).
+    \caption{The resulting $z$ image is shown in a).
+A $\SI{200}{\pixel}\times\SI{200}{\pixel}$ sub-image was taken shown by the dashed lines.
 The empirical null was used to test pixels, positive pixels are shown in red in b).
@@
 The normalised $p$-values are shown in d).
-The critical regions were adjusted using the empirical null and obtained using the BH procedure at the 5\% FDR level.}
+The critical regions were adjusted using the empirical null and correspond to the 5\% FDR level.}
     \label{fig:inference_inferenceSubsample2}
@@
 
-Another example is shown in Figure \ref{fig:inference_inferenceSubsample2} where a $200\times 200$ sub-image containing a defect was used.
-It can be seen that the null distribution was not centred at zero, however the empirical null took it into account.
+Another example is shown in Figure \ref{fig:inference_inferenceSubsample2} where a $\SI{200}{\pixel}\times\SI{200}{\pixel}$ sub-image containing a defect was used.
+It can be seen that the null distribution was not centred at zero which can be taken into account by using the empirical null.
 The estimation of the empirical null parameters were robust as it depends on the density estimate at the mode only, it should not be affected by non-null test statistics.
@@
 $\inputNumber{../figures/inference/inferenceSubsample2_nPositive.txt}$ pixels were tested positive.
-The majority of the positive pixels were found to be clustered together, which highlighted the defect.
-Not all of the defects were tested positive, but a good number of them are.
+The majority of the positive pixels were found to be clustered together which highlighted the defect.
+The entire area of the defects were not tested positive but a good portion of them are.
 This should be enough to raise suspicion in that particular area.
-Only a few pixels were falsely tested as positive, however they are typically isolated single pixels.
+Only a few pixels were falsely tested as positive, however, they are typically isolated single pixels.
 Isolated positive pixels should be discarded as they are more than likely to be tested positive by random chance.
 
-This section describes the empirical null implementation in detail, in particular the numerical and computational aspects.
+This section describes the empirical null implementation in detail, in particular, the numerical and computational aspects.
 The empirical properties of the sampling distribution of the null parameter estimators were studied.
@@
 
-The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$ numerically. The Newton-Raphson method was used to solve
+The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$ numerically. This was done by using the Newton-Raphson method to solve
 \begin{equation}
@@
     \frac{z_i-z}{h}
-  \right) $
-so that the log density is
+  \right) $,
+so the log density is
 \begin{equation}
@@
 \end{equation}
-Taking the first derivative
+Taking the first-order derivative
 \begin{equation*}
@@
   \ln\widehat{p}_Z(z)
-  \right|_{z=\widehat{\mu}_0}
+  \right|_{z=z^{(r)}}
   \right|\right]
@@
     \ln\widehat{p}_Z(z)
-  \right|_{z=\widehat{\mu}_0}
+  \right|_{z=z^{(r)}}
   < 0 \ .
@@
 The best solution, the one with the largest $\ln\widehat{p}_Z\left(\widehat{\mu}_0\right)$, out of all the different initial values was used as the final answer.
-The Newton-Raphson method can fail if it converges to a stationary point other than a global maximum, for example a local maximum or a point of inflection.
+The Newton-Raphson method may converge to a local maximum.
 
@@
 
-The bandwidth $h$ controls how smooth the kernel density estimator is, higher values producing smoother curves \citep{friedman2001elements}.
+The bandwidth $h$ controls how smooth the kernel density estimator is, higher values produce smoother curves \citep{friedman2001elements}.
 Cross validation methods to select $h$ do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
@@
 The kernel density estimator was only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$.
-Thus a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate.
+Thus, a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate.
 Exact properties of these estimators based on the kernel density estimators can be rather complicated.
-For example numerous approximations were needed to show that $\widehat{\sigma}_0^2$ is an unbiased estimator of $\sigma_0^2$ to the first order, where higher order terms are functions of $(\widehat{\mu}_0 - \mu_0)^2$ and $h$.
+For example, numerous approximations were needed to show that $\widehat{\sigma}_0^2$ is an unbiased estimator of $\sigma_0^2$ to the first-order and higher-order terms are functions of $(\widehat{\mu}_0 - \mu_0)^2$ and $h$.
 This is shown in Appendix \ref{chapter:appendix_expectationNullStdEstimator}.
@@
 300 values of $n$ from 10 to $10^6$ and 30 values of $h$ from 0.09 to 1.5 were investigated.
-Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors.
+Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors with the rules of thumb.
 
@@
 A smooth valley can be seen for the median squared error for $\widehat{\sigma}_0$.
-It appeared for a given $n$, there exist a bandwidth which minimise the median squared error.
+It appeared for a given $n$, there exist a bandwidth which minimises the median squared error.
 The rules of thumb did not optimise for $\widehat{\sigma}_0$ and undershot it.
@@
   \end{subfigure}
-  \caption{Median squared error of the estimators of the empirical null parameters from 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
+  \caption{Median squared error of the estimates of the empirical null parameters from 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
   \label{fig:inference_BandwidthSelection_error}
@@
 The optimal bandwidth for a given $n$ was found numerically.
-Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $h$ and $n$.
-A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimised the log squared error for a given $n$.
+Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $h$ given $n$.
+A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimises the log squared error for a given $n$.
 \emph{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures.
@@
     }
-    \caption{A smoothing spline was fitted on the log squared error for estimating $\sigma_0$ on $n$ simulated standard Normal random variables.
-The bandwidth was varied.
+    \caption{A smoothing spline was fitted on the log squared error, for estimating $\sigma_0$ on $n$ simulated standard Normal random variables, versus bandwidth.
 The experiment was repeated by simulating the standard Normal random variables again.
-The boxplots represent the variation of the error from the 100 repeats.
+The boxplots represent the variation of the errors from the 100 repeats.
 The red dashed line shows the bandwidth which minimised the fitted spline.}
@@
   \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
-  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 68\% prediction interval.}
+  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experiment. The dotted lines shows the 68\% prediction interval.}
   \label{fig:inference_BandwidthSelection2_ruleOfThumb}
@@
 The method used in fitting the smoothing spline could contribute to the underfitting.
-For example if the smoothing spline was not smooth enough so that multiple local minimums appeared, it would add variance to the location of the optimal bandwidth if the optimisation algorithm converges to a local minimum.
-A basic linear relationship was chosen to avoid overfitting and keep the rule of thumb simple.
+For example, if the smoothing spline was not smooth enough so that multiple local minima appeared, it would add variance to the optimal bandwidth if the optimisation algorithm converges to a local minimum.
+A basic linear relationship was chosen to avoid overfitting and to keep the rule of thumb simple.
 
 In conclusion, a small bias added to the rule of thumb improved the performance of the estimator $\widehat{\sigma}_0$.
-\cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggested the use of $b=0.9$.
+\cite{silverman1986density} pointed out that a smaller bandwidth should be used when, in particular, the distribution is bimodal.
+This is why \cite{silverman1986density} suggested the use of $b=0.9$.
 Following from this, it was chosen that the intercept was added to Silverman's rule of thumb for the use in the empirical null $h = \left(0.9n^{-1/5}+ 0.16\right) \times\text{min}\left(s_z,\text{IQR}_z/1.34\right)$.
@@
 \afterpage{\clearpage}
-\subsection{Sampling Distribution Experiments}
-
-Various estimators of central tendency and dispersion were compared with the empirical null estimates of the null mean and null standard deviation.
+\subsection{Comparison with Other Robust Estimators}
+
+Various estimates of central tendency and dispersion were compared with estimates of the null mean and null standard deviation.
 The empirical sampling distribution of these estimators were observed to look for properties such as bias, variance and robustness.
-The central tendency looked at were the median and mean.
-The dispersions looked at were the median absolute deviation (MAD) around the mode $\times 1.4826$, interquartile range (IQR) $\div 1.349$ and the standard deviation.
+The central tendency estimates looked at were the median and mean.
+The dispersion estimates looked at were the median absolute deviation (MAD) around the mode $\times 1.483$, interquartile range (IQR) $\div 1.349$ and the standard deviation.
 The normalisation constants were used so that the MAD and IQR can be compared directly to the standard deviation.
@@
 Further fine tuning on the bandwidth would be required for the empirical null standard deviation to be unbiased.
-For example it appeared there was consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
-The source of bias could come from the fact that the bandwidth was tuned to minimise the mean squared error rather than the squared bias.
+For example, it appeared there was consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
+The source of bias could come from the fact that the bandwidth was tuned to minimise the log squared error rather than the squared bias.
 
@@
 The empirical null estimators are robust to the non-null component but still suffers from high variance.
-The rest of the estimators were affected by the non-null statistics, making them unsuitable to estimate parameters of the null component.
+The rest of the estimators were affected by the non-null statistics, making them unsuitable to estimate parameters of the null parameters.
 
@@
   \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables.
-Shown are the sampling distributions from 100 repeats.
+The boxplots represent the sampling distributions from 100 repeats.
 The dotted lines show the 95\% confidence interval for the sample mean.}
@@
   \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables.
-Shown are the sampling distributions from 100 repeats.
+The boxplots represent the sampling distributions from 100 repeats.
 The dotted lines show the 95\% confidence interval for the sample variance.}
@@
 The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-Shown are the sampling distributions from 100 repeats.
+The boxplots represent the sampling distributions from 100 repeats.
 The dotted lines show the 95\% confidence interval for the sample mean.}
@@
 The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-Shown are the sampling distributions from 100 repeats.
+The boxplots represent the sampling distributions from 100 repeats.
 The dotted lines show the 95\% confidence interval for the sample variance.}
@@
 The resulting empirical null distribution is shown in Figure \ref{fig:inference_inferenceSubsampleAll}.
-The empirical null distribution had a very large standard deviation and would test all pixels as negative, this is incorrect.
+The critical boundary, adjusted using the empirical null, which correspond to the 5\% FDR level was found to be $z\leqslant\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical2.txt}\geqslant z$ to 2 decimal places.
+This would test all pixels as negative which is incorrect.
 
@@
     \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
-    \caption{Empirical null fitted onto histogram}
+    \caption{Distribution of test statistics}
   \end{subfigure}
@@
 \end{equation}
-where the density estimate is
+where
 \begin{equation}
@@
     \dfrac{z_{i,j}-z}{h}
-  \right)
-\end{equation}
-and $K_{x,y} = C_r(x,y) \cap \text{ROI}$. Using these estimates, the test statistics were normalised using
+  \right) \ ,
+\end{equation}
+$K_{x,y} = C_r(x,y) \cap \text{ROI}$ and $n=\left|K_{x,y}\right|$. Using these estimates, the test statistics were normalised using
 \begin{equation}
@@
 \end{equation}
-and only the normalised test statistics were used in hypothesis testing. It should be noted that because the kernels can overlap, correlation between $T_{x,y}$ for different $(x,y)$ is introduced.
+and only the normalised test statistics were used in hypotheses testing. It should be noted that because the kernels can overlap, correlation between $T_{x,y}$ for different $(x,y)$ is introduced.
 
@@
 The empirical null filter assumes that the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal.
-If $r$ is too big, the kernel will capture far away test statistics with a very different null distribution.
+If $r$ is too big, the kernel will capture far away test statistics with a very different null distributions.
 If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution.
@@
 
-$r$ control the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$.
+$r$ controls the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$.
 $r$ should be selected so that $\pi_0$ is of a sensible value, for example $>90\%$.
 In practice, the defects are unknown so various kernel radiuses should be tried out.
-In general, the kernel radius should be much larger than the size of the defect.
-
-There exist similar filters, for example the local normalization filter \citep{sage2003teaching, sage2018local} uses a Gaussian filter to obtain $\widehat{\mu}_{0,x,y}$.
+The kernel radius should be much larger than the size of the defect.
+
+There exist similar filters, for example the local normalisation filter \citep{sage2003teaching, sage2018local} uses a Gaussian filter to obtain $\widehat{\mu}_{0,x,y}$.
 $\widehat{\sigma}_{0,x,y}^2$ was obtained by applying another Gaussian filter on the $\left(z_{x,y}-\widehat{\mu}_{0,x,y}\right)^2$ image.
 The purpose of this filter was to normalise images with uneven illumination.
-The disadvantage of using the local normalization filter for estimating the null parameters is that it uses a Gaussian filter.
-This is a type weighted mean which is not robust to non-null statistics.
+The disadvantage of using this filter, for estimating the null parameters, is that it uses a Gaussian filter.
+This is a type of weighted mean which is not robust to non-null statistics.
 In addition, the two Gaussian filters can have different radiuses, it is not clear how to set them.
@@
 
-The empirical null filter was implemented in an open source software called \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \emph{GitHub} \citep{imagej2018rank}.
+The empirical null filter was implemented using open source software called \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \emph{GitHub} \citep{imagej2018rank}.
 This class implemented filters, such as the mean filter and median filter, using a circular kernel, making this a suitable framework for the empirical null filter.
@@
 
-As a test, the empirical null filter with $r=5$ was used on a \emph{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
-It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it did verify that the filter worked on arbitrary images with some computational considerations.
-The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all ${x,y}$ could be of interest.
-In particular the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}.
+As a test, the empirical null filter with $r=\SI{5}{\pixel}$ was used on a \emph{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
+It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however, it did verify that the filter worked on arbitrary images with some computational considerations.
+The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ could be of interest, in particular, the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}.
 Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters.
-The empirical null mean created an impasto effect and preserved edges which is similar to the result in \cite{griffin2000mean}.
+The empirical null mean has an impasto effect and preserved edges which is similar to the result in \cite{griffin2000mean}.
 Dispersion filters such as the standard deviation filter can be used to detect edges.
@@
     }
-    \caption{Empirical null filter with $r=5$ on the sample image \texttt{bridge.gif}.}
+    \caption{Empirical null filter with $r=\SI{5}{\pixel}$ on the sample image \texttt{bridge.gif}.}
     \label{fig:inference_fijiBridgeFilter}
@@
     }
-    \caption{Various average filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}}
+    \caption{Various averaging filters, with kernel radius $r=\SI{5}{\pixel}$, were used on the sample image \texttt{bridge.gif}}
     \label{fig:inference_fijiMean}
@@
     }
-    \caption{Various dispersion filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
+    \caption{Various dispersion filters, with kernel radius $r=\SI{5}{\pixel}$, were on the sample image \texttt{bridge.gif}.}
     \label{fig:inference_fijiStd}
@@
 When using the the empirical null filter in \emph{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
-Here the user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
-The menu also has options for by-product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, and quartile filters.
-Advanced options are available to the user.
-The number of initial values set the number of valid solutions to be found in the Newton-Raphson method on finding the mode of the density estimate.
+The user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
+The menu also has options for by-product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, quartile filters.
+Advanced options are available to the user, for example, the number of initial values set the number of valid solutions to be found when using the Newton-Raphson method to find the mode of the density estimate.
 The user can also set the maximum number of steps and tolerance for the Newton-Raphson method.
@@
 
-Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design had already been done.
+Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design has already been done.
 \texttt{RankFilters} contain implementations of filters such as the mean filter and median filter.
@@
 This is not suitable for the empirical null filter as this will cause bias in the density estimation.
-The empirical null filter used \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}.
+The empirical null filter uses \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}.
 This indicate that these pixels are outside the ROI and are ignored.
@@
   \end{subfigure}
-  \caption{When a kernel contain pixels outside the region of interest as shown by the solid line, the missing pixels can either be extrapolated using the nearest pixel or completely ignored by filling in the missing pixels with \texttt{NaN}.}
+  \caption{When a kernel contains pixels outside the ROI, as shown by the solid line, the pixels can either be extrapolated using the nearest pixel or completely ignored by filling in the missing pixels with \texttt{NaN}.}
   \label{fig:inference_padding}
@@
 Line filtering was done from left to right.
-At the start on the far left, an initial value of the median of all the pixels in the kernel was used.
+At the start on the far left, an initial value of the median over the pixels in the kernel was used.
 In addition, various initial values were randomly tried out until a requested number of valid solutions were found.
-For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as a initial point.
+For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial value.
 This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
@@
 \texttt{bridge.gif} is an 8-bit image so values were represented as integers.
-This opened up opportunities for the inter-quartile range and the standard deviation to be zero, this caused problems as this set the bandwidth to be zero.
+This opened up opportunities for the inter-quartile range and the standard deviation to be zero.
+This caused problems as this would set the bandwidth to zero.
 When the standard deviation is zero, it was set to $0.289$ which corresponds to the standard deviation of a uniform random variable.
@@
 
-When the number of initial values is too few, poor solutions to $\widehat{\mu}_0$ are uncommon which then propagate to the pixel to the right and used as its initial value.
+When the number of initial values is too few, poor solutions to $\widehat{\mu}_0$ are possible which then can propagate to the pixel to the right and used as its initial value.
 Poor initial values could cause the Newton-Raphson method to never converge.
-If the Newton-Raphson method failed to converge too many times, the median is used as the new initial value.
+If the Newton-Raphson method failed to converge too many times, the median, over pixels in the kernel, is used as the new initial value.
 Should it fail too, the program gives up and puts a $\texttt{NaN}$ in that pixel.
@@
 
-An experiment was conducted to demonstrate the effects of the empirical null filter on a simulated $256\times 256$ Gaussian image, where all the pixels have value distributed as standard Normal.
-The purpose is to simulate test statistics which are null and ideally no positive results should be detected.
+An experiment was conducted to demonstrate the effects of the empirical null filter on a simulated $\SI{256}{\pixel}\times\SI{256}{\pixel}$ Gaussian image, where all the pixels have value distributed as standard Normal.
+The purpose is to simulate test statistics which are null and no positive results should be detected.
 The test statistics after filtering should preserve its original distribution, or at least close to it.
 The statistical moments before and after filtering should be the same and were investigated.
-Because the empirical null mean and empirical null standard deviation are random variables with some distribution, the filtered pixels will never be Normal and any normality tests would be too strict for the purpose of this experiment.
+Because the empirical null mean and empirical null standard deviation are random variables, the filtered pixels will never be Normal and any normality tests would be too strict for the purpose of this experiment.
 
 \emph{Contamination} is defined as some smooth and slowly varying function added and/or multiplied to an image.
-Contaminating a Gaussian image may cause errors in hypothesis testing if the null distribution was incorrectly specified as standard Normal.
+Conducting hypotheses testing on a contaminated Gaussian image may cause errors if the null distributions were incorrectly specified as standard Normal.
 In this experiment, the contamination was a gradient such that the pixel at position $(x,y)$ have a value distributed as $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_{0,x,y}^2)$ where
@@
 
-A caveat is that some bias to the null variance estimation would be introduced because of the contamination.
+A caveat is that some bias to the null standard deviation estimation would be introduced because of the contamination.
 This is because sources of variance captured by the kernel are from $\sigma_{0,x,y}$ and also from the variability of $\mu_{0,x,y}$.
@@
 
+\begin{figure}[p]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_beforeFilter.eps}
+    \caption{Unfiltered}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_afterFilter.eps}
+    \caption{Filtered}
+    \label{fig:inference_allNullGaussianScript_afterFilter}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullMean.eps}
+    \caption{Empirical null mean}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullStd.eps}
+    \caption{Empirical null std}
+  \end{subfigure}
+  }
+  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian image before and after filtering with kernel radius \SI{20}{\pixel}.
+Also shown are the empirical null mean and empirical null standard deviation.}
+  \label{fig:inference_allNullGaussianScript}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_beforeFilter.eps}
+    \caption{Unfiltered}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_afterFilter.eps}
+    \caption{Filtered}
+    \label{fig:inference_allNullPlaneScript_afterFilter}
+  \end{subfigure}
+  }
+  \centerline{
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullMean.eps}
+    \caption{Empirical null mean}
+  \end{subfigure}
+  \begin{subfigure}[b]{\subSize}
+    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullStd.eps}
+    \caption{Empirical null std}
+  \end{subfigure}
+  }
+  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image before and after filtering with kernel radius \SI{20}{\pixel}.
+Also shown are the empirical null mean and empirical null standard deviation.}
+  \label{fig:inference_allNullPlaneScript}
+\end{figure}
+
 \begin{figure}
@@
   \end{subfigure}
-  \caption{$p$-values from a filtered $256\times 256$ Gaussian image with kernel radius 20.
+  \caption{$p$-values from a filtered $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian image with kernel radius \SI{20}{\pixel}.
 In b), the Gaussian image was contaminated before filtering.
@@
   \label{fig:inference_allNull_pValues}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_beforeFilter.eps}
-    \caption{Unfiltered}
-  \end{subfigure}
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_afterFilter.eps}
-    \caption{Filtered}
-    \label{fig:inference_allNullGaussianScript_afterFilter}
-  \end{subfigure}
-  }
-  \centerline{
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullMean.eps}
-    \caption{Empirical null mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullGaussianScript_nullStd.eps}
-    \caption{Empirical null std}
-  \end{subfigure}
-  }
-  \caption{A $256\times 256$ Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
-  \label{fig:inference_allNullGaussianScript}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-  \centerline{
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_beforeFilter.eps}
-    \caption{Unfiltered}
-  \end{subfigure}
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_afterFilter.eps}
-    \caption{Filtered}
-    \label{fig:inference_allNullPlaneScript_afterFilter}
-  \end{subfigure}
-  }
-  \centerline{
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullMean.eps}
-    \caption{Empirical null mean}
-  \end{subfigure}
-  \begin{subfigure}[b]{\subSize}
-    \includegraphics[width=\textwidth]{../figures/inference/allNullPlaneScript_nullStd.eps}
-    \caption{Empirical null std}
-  \end{subfigure}
-  }
-  \caption{A $256\times 256$ contaminated Gaussian image before and after filtering with kernel radius 20. Also shown are the empirical null mean and empirical null standard deviation.}
-  \label{fig:inference_allNullPlaneScript}
 \end{figure}
@@
 For a given kernel radius $r$, 100 different Gaussian images were filtered to investigate the within image mean, standard deviation and kurtosis of the filtered statistics.
-Various other filters were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter.
+Various other filters for normalisation were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter.
 They use different estimators to estimate the null parameters as their name suggest, Table \ref{table:inference_nullFilters} clarifies them.
@@
     Filters&Null mean&Null Standard deviation\\\hline
-    MAD mode null&Mode&MAD around the mode $\times1.4826$\\
+    MAD mode null&Mode&MAD around the mode $\times1.483$\\
     Median IQR null&Median&IQR $\div1.349$\\
@@
 This is shown in Figure \ref{fig:inference_AllNullPlane_var}.
-As discussed before, the kernel captured the variation due to the contamination and this added intrinsic bias to the null variance.
-As a result, this added bias when estimating the null variance.
-
-The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} showed that the empirical null filter caused the filtered statistics to have heavy tails, in particular for small kernel radiuses.
-This could cause problems in hypothesis testing because heavy tails could be misinterpreted as contribution from non-null statistics.
+As discussed before, the kernel captured the variation due to the contamination and this added bias to the estimation of dispersion.
+
+The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} showed that the empirical null filter caused the filtered statistics to have heavy tails, in particular, for small kernel radiuses.
+This could cause problems in hypotheses testing because heavy tails could be misinterpreted as contribution from non-null statistics.
 The source of the kurtosis inflation is from the estimation of the null standard deviation.
@@
 
-The empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination.
-A \emph{defect} is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution.
-For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
+The empirical null filter was tested to see if it can assist in detecting simulated defects from an image with/without contamination.
+A \emph{defect} assign pixels to have a value not distributed under the null distribution, but instead, under an alternative, or non-null, distribution.
+For example, suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect assign certain pixels to have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
 
 To recap, \emph{contamination} is the result of a linear transform of the test statistics $Z_{x,y}$.
-For example in this experiment, the image was multiplied by 2 and a gradient was added to it.
-Suppose the image does contain defects, then an example of a resulting distribution is
+For example, in this experiment, the image was multiplied by 2 and a gradient was added to it.
+The resulting null and alternative distributions are
 \begin{align}
@@
 \end{align}
-where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects.
+respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects.
 
 The empirical null filter aims to estimate the null distribution parameters from $Z_{x,y}$ in order to normalise it to form $T_{x,y}$.
-By normalising it, $T_{x,y}|H_{0,x,y}$ should be approximately standard Normal and hypothesis testing can be used to detect defects.
+By normalising it, $T_{x,y}|H_{0,x,y}$ should be approximately standard Normal and hypotheses testing can be used to detect defects.
 
@@
 Speckle defect with density $\pi_1$ assign all test statistics to be non-null with probability $\pi_1$, and are null otherwise.
-This was chosen because the proportion of null statistics captured by the kernel should be the same all for all kernel radiuses.
+This was chosen because the proportion of null statistics captured by the kernel should be the same for all kernel radiuses.
 A line defect assign columns of pixels to be non-null, a kernel would only capture a section of defect.
@@
     }
-  \caption{A $256 \times 256$ Gaussian image with \emph{speckle} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius 20 in c).
-Defected pixels have the distribution $\normal(3,1)$.
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with \emph{speckle} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius \SI{20}{\pixel} in c).
+Non-null pixels have the distribution $\normal(3,1)$.
 The speckle defect has density $\pi_1 = 0.1$.
@@
     }
-  \caption{A $256 \times 256$ Gaussian image with a \emph{line} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius 20 in c).
-Defected pixels have the distribution $\normal(3,1)$.
-The line defect is 5 pixels thick.
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a \emph{line} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius \SI{20}{\pixel} in c).
+Non-null pixels have the distribution $\normal(3,1)$.
+The line defect is \SI{5}{\pixel} thick.
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
@@
     }
-  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius \emph{20} in c).
-Defected pixels have the distribution $\normal(3,1)$.
-The square defect is $30\times 30$ pixels in size.
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a \emph{square} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius \SI{20}{\pixel} in c).
+Non-null pixels have the distribution $\normal(3,1)$.
+The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size.
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
@@
     }
-  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a).
-The image was contaminated in b) and then filtered with kernel radius \emph{40} in c).
-Defected pixels have the distribution $\normal(3,1)$.
-The speckle defect has density $\pi_1 = 0.1$.
-The line defect is 5 pixels thick.
-The square defect is $30\times 30$ pixels in size.
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a \emph{square} defect is shown in a).
+The image was contaminated in b) and then filtered with kernel radius \SI{40}{\pixel} in c).
+Non-null pixels have the distribution $\normal(3,1)$.
+The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size.
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilterpValueFiltered.eps}
-        \caption{Dust defect, $r=20$}
+        \caption{Dust defect, $r=\SI{20}{\pixel}$}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_EmpiricalNullFilterpValueFiltered.eps}
-        \caption{Line defect, $r=20$}
+        \caption{Line defect, $r=\SI{20}{\pixel}$}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_EmpiricalNullFilterpValueFiltered}
-        \caption{Square defect, $r=20$}
+        \caption{Square defect, $r=\SI{20}{\pixel}$}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilterpValueFiltered}
-        \caption{Square defect, $r=40$}
-      \end{subfigure}
-    }
-  \caption{A $256 \times 256$ contamined defected Gaussian image was filtered using the empirical null filter with kernel radius $r$.
-Shown are the values of the image converted to $p$-values.
-Defected pixels have the distribution $\normal(3,1)$.
-The square defect is $30\times 30$ pixels in size.
+        \caption{Square defect, $r=\SI{40}{\pixel}$}
+      \end{subfigure}
+    }
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ contamined defected Gaussian image was filtered using the empirical null filter with kernel radius $r$.
+Shown are the $p$-values converted from the filtered image.
+Non-null pixels have the distribution $\normal(3,1)$.
+The speckle defect has density $\pi_1=0.1$.
+The line defect is \SI{5}{\pixel} thick.
+The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size.
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The critical region is for testing at the 5\% FDR level.}
+The critical region corresponds to the 5\% FDR level.}
   \label{fig:inference_defectExamplePValue}
@@
 Without filtering, the top-left and bottom-right of the contaminated image have large, in magnitude, test statistics.
-In these areas, a lot of pixels would be detected as falsely positive.
+In these areas, a lot of pixels would be tested as falsely positive.
 By using the empirical null filter, the resulting filtered image reassemble the uncontaminated image and appropriate inference can be done on the filtered image.
-However, some statistical power was lost when conducting inference on the filtered image because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
-This cannot be avoided as areas of high empirical null standard deviation was due to the sampling error.
+However, some statistical power was lost when conducting hypotheses testing on the filtered image because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
+This cannot be avoided as areas of high empirical null standard deviation was due to the randomness in sampling.
 Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_defectLineExample}.
@@
 The square defected images, including the contaminated ones, are shown in Figures \ref{fig:inference_defectSquareExample} and \ref{fig:inference_defectSquare2Example}.
-Figure \ref{fig:inference_defectSquareExample} filtered the contaminated image using a kernel radius of $r=20$, while Figure \ref{fig:inference_defectSquare2Example} used a kernel radius of $r=40$.
-With $r=20$, the kernel is smaller than the square defect, therefore the defect was treated as the null.
+Figure \ref{fig:inference_defectSquareExample} filtered the contaminated image using a kernel radius of $r=\SI{20}{\pixel}$, while Figure \ref{fig:inference_defectSquare2Example} used a kernel radius of $r=\SI{40}{\pixel}$.
+With $r=\SI{20}{\pixel}$, the kernel is smaller than the square defect, therefore, the defect was treated as the null.
 This is evident because the empirical null mean captured the defect.
 This resulted in difficulty detecting the defect.
-With $r=40$, the kernel is bigger than the defect and treated the defect as non-null.
+With $r=\SI{40}{\pixel}$, the kernel is bigger than the defect and treated the defect as non-null.
 In this scenario, the empirical null filter recovered the gradient in the empirical null which was then used for normalisation.
 
-The empirical null mean in Figure \ref{fig:inference_defectSquareExample} demonstrates the multi-thread nature of the implementation of the empirical null filter.
-It can be seen that there are horizontal streaks where the defect is.
-This is the result of each thread filtering a row each and jumping from one mode, the null, to the other, the non-null, at different times.
+The empirical null mean in Figure \ref{fig:inference_defectSquareExample} demonstrated the multi-thread nature of the implementation of the empirical null filter.
+It can be seen that there were horizontal streaks where the defect is.
+This is the result of each thread filtering a row and jumping from one mode, the null, to the other, the non-null, at different times.
 The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pin point which mode is greater.
@@
 With a sensible kernel radius, some of the defects can be detected.
-False negatives do appear but this is inevitable in order to control for the FDR.
-The figure shows that using a kernel radius of $r=20$ for the square defect detected no pixels for defects.
+False negatives are common but this is inevitable in order to control for the FDR.
+The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, tested no pixels for defects.
 This, again, emphasise the importance of a good kernel radius.
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_roc.eps}
-        \caption{Dust defect $\pi_1=0.1$, $r=20$}
+        \caption{Dust defect, $r=\SI{20}{\pixel}$}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_roc.eps}
-        \caption{5 pixels thick line defect, $r=20$}
+        \caption{Line defect, $r=\SI{20}{\pixel}$}
       \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_roc.eps}
-        \caption{$30\times 30$ square defect, $r=20$}
+        \caption{Square defect, $r=\SI{20}{\pixel}$}
         \label{fig:inference_defectSimulationRoc_square20}
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_roc.eps}
-        \caption{$30\times 30$ square defect, $r=40$}
-      \end{subfigure}
-    }
-  \caption{ROC curves for various defected $256\times 256$ Gaussian images.
+        \caption{Square defect, $r=\SI{40}{\pixel}$}
+      \end{subfigure}
+    }
+  \caption{ROC curves for various defected $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian images.
 The upper/lower dashed line show the resulting ROC curve when testing on an image without/with contamination respectively.
 The different curves are the resulting ROC curves after filtering a contaminated image.
+The speckle defect has density $\pi_1=0.1$.
+The line defect is \SI{5}{\pixel} thick.
+The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size.
 Defected pixels have the distribution $\normal(3,1)$.
@@
 
-In terms of AUC, the empirical null filter improved the performance over using the unfiltered contaminated image.
+In terms of the AUC, the empirical null filter improved the performance of hypotheses testing compared with using the unfiltered contaminated image.
 The performance before contamination cannot be recovered but it was an improvement.
@@
 
-The ROC curves considers all thresholds or specificities used in the hypothesis testing.
-In the previous experiment, it was found there was some variance mismatch before and after filtering with regards to the test statistics.
-As a result, for a given threshold such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
-
-An experiment was conducted to investigate the specificity of the test before and after filtering.
-A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated.
+The ROC curves considers all thresholds or specificities used in the hypotheses testing.
+In the previous experiment, it was found variance of the test statistics were different before and after filtering.
+As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
+
+An experiment was conducted to investigate how filtering affects hypotheses testing.
+A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian image with speckle defect, with density $\pi_1=0.1$, and various values of $\mu_1$ were investigated.
 The AUC, type 1 error, type 2 error and FDR were measured when testing on an image with a defect before and after contamination and then after filtering with the contamination.
-The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1000 trapeziums.
-A kernel radius of $r=20$ was used and was repeated 100 times by simulating another image.
+The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1\,000 trapeziums.
+A kernel radius of $r=\SI{20}{\pixel}$ was used and was repeated 100 times by simulating another image.
 
@@
     }
-  \caption{AUC and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image.
+  \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$.
 In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
 In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination.
-The filter used a kernel radius of 20.
+The filter used a kernel radius of \SI{20}{\pixel}.
 Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
@@
 The test was done at the 5\% FDR level.
-The box plot summarise the 100 repeats of the experiment.}
+The boxplot summarise the 100 repeats of the experiment.}
   \label{fig:inference_DefectSimulationDust}
@@
 The type 1 error, or specificity, did decreased after filtering.
-However the results illustrated that the FDR is controlled quite well at around 5\% after filtering.
-This meant that in this particular example, the FDR control is consistent after contamination and filtering.
+However, the results illustrated that the FDR is controlled quite well at around 5\% after filtering.
+This meant that in this particular example, the FDR control is consistent after filtering.
 At situations with low detection power, the FDR can fluctuate between 0 and 1 and can take only so many values.
@@
 
-There is the question of what kernel size to choose for a given defect.
+There is the question of what kernel radius to choose for a given defect.
 Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $\pi_1=0.1$ to satisfy some assumptions made for the empirical null.
-Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of kernel which is a defect to 10\%.
-In other words for a kernel with radius $r$
+Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of kernel which contains a defect to 10\%.
+In other words, for a kernel with radius $r$
 \begin{equation}
@@
 \end{equation}
-For a $d \times d$ square defect this is $r > d \sqrt{10/\pi}$.
-In the example of $d=30$, this is about $r>54$.
-For the line defect with thickness $5$, the radius is about $r>32$.
+For a $d \times d$ square defect, this is $r > d \sqrt{10/\pi}$.
+In the example of $d=\SI{30}{\pixel}$, this is about $r>\SI{54}{\pixel}$.
+For the line defect with thickness $\SI{5}{\pixel}$, the radius is about $r>\SI{32}{\pixel}$.
 These are rules of thumb because the kernel is not perfectly circular when used on a grid of pixels.
@@
     }
-  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
+  \caption{AUC and various errors obtained when conducting hypotheses test on the filtered contaminated line defected Gaussian image, of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$, using various kernel radiuses.
+The dashed lines show the resulting 95\% empirical confidence interval when the hypotheses test was done on the uncontaminated image.
 Defected pixels have the distribution $\normal(3,1)$.
-The line defect is 5 pixels thick.
+The line defect is \SI{5}{\pixel} thick.
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
-The box plot summarise the 100 repeats of the experiment.}
+The boxplot summarise the 100 repeats of the experiment.}
   \label{fig:inference_Experiment_DefectRadiusLine}
@@
     }
-  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image.
+  \caption{AUC and various errors obtained when conducting hypotheses test on the filtered contaminated square defected Gaussian image, of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$, using various kernel radiuses.
+The dashed lines show the resulting 95\% empirical confidence interval when the hypotheses test was done on the uncontaminated image.
 Defected pixels have the distribution $\normal(3,1)$.
-The square defect is $30\times 30$ pixels in size.
+The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ pixels in size.
 The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
-The box plot summarise the 100 repeats of the experiment.}
+The boxplot summarise the 100 repeats of the experiment.}
   \label{fig:inference_Experiment_DefectRadiusSquare}
@@
 
-An experiment was conducted where the contaminated defected image were filtered for various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
-Hypothesis testing was done on the uncontaminated and filtered contaminated image and the AUC and various errors were recorded, this was repeated 100 times.
-The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1000 trapeziums.
+An experiment was conducted where the contaminated defected image were filtered using various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
+Hypotheses testing was done on the uncontaminated and filtered contaminated image.
+The AUC and various errors were recorded, this was repeated 100 times.
+The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1\,000 trapeziums.
 The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.
@@
 The results showed that the AUC increased with kernel radius.
-This highlighted that a kernel with a good radius can performance almost as though there was no contamination.
+This highlighted that a kernel with a good radius can perform almost as though there was no contamination.
 It also appeared that the optimal AUC was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
 
-For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%.
-It appeared a large kernel radius helped preserve FDR control after filtering in these examples.
-However a large kernel radius did come at a computational cost.
-Choosing a kernel radius is a matter of trading computational cost with precise FDR control.
-
-It appeared there exist a kernel radius which minimised the type 2 error. So a large kernel radius is required for FDR control but too large can lose statistical power.
+For large enough kernel radius, the FDR was controlled at around 5\%.
+It appeared that a large kernel radius helped preserve FDR control after filtering in these examples.
+It was observed that there exist a kernel radius which minimised the type 2 error.
+So a large kernel radius is required for FDR control but too large can lose statistical power.
+It was noticed that filtering using large kernel radiuses is computationally slower.
 
@@
 \section{Results}
-The empirical null filter has been developed and tested thoroughly on simulated images.
-In this section, the filter is applied to the projections in the \texttt{AbsFilter} and \texttt{TiFilter} datasets.
+The empirical null filter was developed and tested thoroughly on simulated images. In this section, the filter was applied to the projections in the \texttt{AbsFilter} and \texttt{TiFilter} datasets.
 
@@
   \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ was used.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
   \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ was used.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 The empirical null filter was applied to the \texttt{AbsFilter} projection at \ang{120}.
-Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} and \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference when using a kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ and $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ respectively.
+Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} and \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference when using a kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ and $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ respectively.
 With a small radius, the empirical null treated the voids as the null which is shown by the empirical null mean capturing the features of the voids.
-When a large enough radius was used, the larger voids were highlighted by the hypothesis test and the empirical null mean became smoother.
-This is evident that this method ironed out the false positives observed at the start of the chapter.
+When a large enough radius was used, the larger voids were highlighted by the hypotheses test and the empirical null mean became smoother.
+This is evidence that this method ironed out  false positives observed at the start of the chapter.
 
@@
 False positives were detected on the bottom right of the test sample.
-This was the result of the null distribution being bimodal where each face had a different distribution.
+When placing the corner on the bottom right corner, the null distribution is bimodal because each face has a different distribution.
 Figure \ref{fig:inference_cornerSelect} illustrates this.
@@
   \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$ was used.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
   \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}$ was used.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
   \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}$ was used.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
   \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}$ was used.
+A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used.
 a) Highlighted in red are positive pixels at the 5\% FDR level.
@@
 Unfortunately the edges of the test sample were falsely tested as positive and none of the voids were detected.
-The discrepancies are the edges can be due to inaccurate face segmentation or poor alignment of the \emph{aRTist} projection to the obtained projection.
+The discrepancies are at the edges and can be due to inaccurate face segmentation or poor alignment of the \emph{aRTist} projection to the obtained projection.
 
@@
 In the experiments, it was found that the FDR level is preserved after filtering.
-In experiments it was found that the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}.
-
-In the experiment, the larger voids of diameter \SI{2.4}{\milli\metre} were detected in the ABS test sample.
+Also, the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}.
+
+Larger voids of diameter \SI{2.4}{\milli\metre} were detected in the ABS test sample.
 False positives do occur but this is unavoidable because tests were done at the 5\% FDR level.
@@
 Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}.
-Lastly, because the titanium test sample was created using a power-based method, the voids may be filled with power thus appear with less contrast in the projections making it hard to detect.
+Lastly, because the titanium test sample was created using a power-based method, powder may become trapped \citep{brierley2018optimized} in the void.
+This results in the voids appearing with less contrast in the projections, making it harder to detect.
 
 The main issue with implementing this method onto the production line was how slow the filter was.
-The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
+The main bottleneck is the evaluation of the density estimate.
+Each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.
 As a result, increasing the kernel radius slows down the filter.
-Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline.
-On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.
+There may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however, that would require tuning the histogram bins as well as the tuning parameters for the spline.
+On the other hand, the method in \cite{schwartzman2008empirical}, which uses the histogram count, found that the estimation of the null parameters was insensitive to the histogram binning.
 
 There are a few strategies to accelerate the filter.
-The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method.
-Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation.
-The problem is that the assumption of a slow varying null parameter is required much more because of the use of interpolation, this may cause bigger problems due to the face to face transition observed in the experiments.
-It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbour pixels due to the interpolation.
+The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however, efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method.
+Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels are interpolated.
+This requires the null parameters to be slowly varying, otherwise, the interpolation may underfit.
+This may cause problems because of the face to face transition observed in the experiments.
+It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbouring pixels due to the interpolation.
 
 Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics.
-Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
+Potential faster methods compared to the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
 The use of density estimation for robust estimation is also featured when using loss functions derived from the Hellinger-divergence \citep{beran1977minimum, jewson2018principles} or the beta-divergence \citep{basu1998robust, jewson2018principles} which bears similarities to the empirical null.
 However, numerical methods are still required to find the mode.
-Exact solutions for the mode using Bayesian methods is impossible \citep{heinrich2013the} which suggest avoiding the use of numerical methods can be difficult.
+Exact estimation of the mode using Bayesian methods is impossible \citep{heinrich2013the} which suggest avoiding the use of numerical methods can be difficult.
 

### 2019-09-15 inference/allnull/AllNull.m

@@ -69,7 +69,7 @@ classdef AllNull < Experiment
       plot([0,this.radiusArray(end)+10],[meanCritical,meanCritical], 'k--');
       plot([0,this.radiusArray(end)+10],[-meanCritical,-meanCritical], 'k--');
       xlim([0,this.radiusArray(end)+10]);
-      ylabel('post filter image greyvalue mean');
+      ylabel('image mean');
       xlabel('radius (px)');
       if (~isempty(this.getYLim(3)))
         ylim(this.getYLim(3));
@@ -87,7 +87,7 @@ classdef AllNull < Experiment
       plot([0,this.radiusArray(end)+10],[stdCritical1,stdCritical1], 'k--');
       plot([0,this.radiusArray(end)+10],[stdCritical2,stdCritical2], 'k--');
       xlim([0,this.radiusArray(end)+10]);
-      ylabel('post filter image greyvalue std');
+      ylabel('image std');
       xlabel('radius (px)');
       if (~isempty(this.getYLim(4)))
         ylim(this.getYLim(4));
@@ -104,7 +104,7 @@ classdef AllNull < Experiment
       plot([0,this.radiusArray(end)+10],3+sqrt(24)*[meanCritical,meanCritical], 'k--');
       plot([0,this.radiusArray(end)+10],3+sqrt(24)*[-meanCritical,-meanCritical], 'k--');
       xlim([0,this.radiusArray(end)+10]);
-      ylabel('post filter image greyvalue kurtosis');
+      ylabel('image kurtosis');
       xlabel('radius (px)');
       if (~isempty(this.getYLim(5)))
         ylim(this.getYLim(5));

### 2019-09-15 reports/thesis/chapters/5_inference.tex
Use proofreader

@@
-Disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other.
+A disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other.
 Any values too big in magnitude can be considered as a defect.
@@
 The obtained and \emph{aRTist} projections are shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
-The 20 replicate projections were spilt into two.
+The 20 replicate projections were split into two.
 19 randomly selected projections were used for the variance-mean model to fit onto.
@@
 It should be expected that small $p$-values are in areas of the defects.
-Pixels were tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$ to 2 decimal places.
+Pixels were tested positive or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$ to 2 decimal places.
 This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure.
@@
 This proposed method for defect detection failed because too many false positives were detected.
-These false positives appear to have some structure, for example clustering in the corners or on surfaces.
-In addition, false negatives were detected because not all of the defects were detected.
+These false positives appear to have some structure, for example, clustering in the corners or on surfaces.
+Also, false negatives were detected because not all of the defects were detected.
 
@@
 This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test.
-Assumptions used on the hypothesis testing can be relaxed by using the empirical null \citep{efron2004large}, which is reviewed here.
+Assumptions used in the hypotheses testing can be relaxed by using the empirical null \citep{efron2004large}, which is reviewed here.
 The empirical null is then extended to an image filter, called the empirical null filter.
-This filter adjust each test statistic according to its neighbours, ironing out false positive results.
+This filter adjusts each test statistic according to its neighbours, ironing out false positive results.
 Simulations and results are shown towards the end of the chapter.
@@
 By using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$ to 2 decimal places, almost half of the pixels were tested positive.
-It is questionable whether such a number of positive results is sensible, in particular, in an area where defects were not expected.
+It is questionable whether such many positive results are sensible, in particular, in an area where defects were not expected.
 
@@
 The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.
-There exist various methods for the empicial null, for example, \cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate.
+There exist various methods for the empirical null, for example, \cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate.
 The empirical characteristic function was used in \cite{jin2007estimating}.
@@
 No positive results were found and the $p$-values were sensible as they resemble the uniform distribution.
-This demonstrated that the empirical null adjusted the parameters of the null distribution to fit onto the majority of the data in order to make sensible inference.
+This demonstrated that the empirical null adjusted the parameters of the null distribution to fit onto the majority of the data to make a sensible inference.
 
@@
 It can be seen that the null distribution was not centred at zero which can be taken into account by using the empirical null.
-The estimation of the empirical null parameters were robust as it depends on the density estimate at the mode only, it should not be affected by non-null test statistics.
+The estimation of the empirical null parameters was robust as it depends on the density estimate at the mode only, it should not be affected by non-null test statistics.
 
@@
 The majority of the positive pixels were found to be clustered together which highlighted the defect.
-The entire area of the defects were not tested positive but a good portion of them are.
+The entire area of the defects was not tested positive but a good portion of them are.
 This should be enough to raise suspicion in that particular area.
@@
 
-A convergence criteria was met when either 10 update steps were taken or when
+The convergence criteria were met when either 10 update steps were taken or when
 \begin{equation}
@@
 The bandwidth $h$ controls how smooth the kernel density estimator is, higher values produce smoother curves \citep{friedman2001elements}.
-Cross validation methods to select $h$ do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
-Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are typically of the form
+Cross-validation methods to select $h$ do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive.
+Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are usually of the form
 \begin{equation}
@@
 For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation of the dataset.
-The median squared error was obtained by taking the median over all squared errors from the 100 estimates.
+The median squared error was obtained by taking the median over all the squared errors from the 100 estimates.
 300 values of $n$ from 10 to $10^6$ and 30 values of $h$ from 0.09 to 1.5 were investigated.
@@
 
-$\widehat{\mu}_0$ has low median squared error for large bandwidths.
+$\widehat{\mu}_0$ has a low median squared error for large bandwidths.
 For low $n$, large bandwidths are particularly useful because smoother curves prevent any false bimodal features appearing, making it easier to find the mode.
@@
 Recall that the normalised test statistics are $t_i = \dfrac{z_i - \widehat{\mu}_0}{\widehat{\sigma}_0}$.
-Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $t_i$, potentially testing more of these test statistics as positive.
-High values of $\widehat{\sigma}_0$ does the opposite.
-Large number of positives can led to more false positives and vice versa.
+Low values of $\widehat{\sigma}_0$ produce large values, in magnitude, of $t_i$, potentially testing more of these test statistics as positive.
+High values of $\widehat{\sigma}_0$ do the opposite.
+A large number of positives can lead to more false positives and vice versa.
 
@@
 
-A relationship between the optimal bandwidth and $n$ was attempted to be found. It was assumed such a relationship has the linear from
+A relationship between the optimal bandwidth and $n$ was attempted to be found. It was assumed such a relationship has the linear form
 \begin{equation}
@@
 Various estimates of central tendency and dispersion were compared with estimates of the null mean and null standard deviation.
-The empirical sampling distribution of these estimators were observed to look for properties such as bias, variance and robustness.
-The central tendency estimates looked at were the median and mean.
+The empirical sampling distribution of these estimators was observed to look for properties such as bias, variance and robustness.
+The central tendency estimates looked at were the median and the mean.
 The dispersion estimates looked at were the median absolute deviation (MAD) around the mode $\times 1.483$, interquartile range (IQR) $\div 1.349$ and the standard deviation.
@@
 
-A dataset of $n = \pi r^2$ standard Normal random variables were simulated to obtain estimates of central tendency and dispersion.
+A dataset of $n = \pi r^2$ standard Normal random variables was simulated to obtain estimates of central tendency and dispersion.
 This was repeated 100 times to obtain a sampling distribution.
@@
 The empirical null standard deviation had some positive bias and it was found that this bias was quite sensitive to the bandwidth.
-Further fine tuning on the bandwidth would be required for the empirical null standard deviation to be unbiased.
+Further fine-tuning on the bandwidth would be required for the empirical null standard deviation to be unbiased.
 For example, it appeared there was consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.

### 2019-09-15 reports/thesis/book.tex
Revise

@@
 Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}.
-The obtained projections was used to help align the simulated projection.
-The aim of the experiment was to develop a statistical method to detect these designed voids.
+The obtained projections were used to help align the simulated projection.
+The experiment aimed to develop a statistical method to detect the designed voids.
 
@@
 Shading correction was required to remove spot and panel effects from the obtained projections.
-This was done by using the greyscale projections from a number of powers of the x-ray tube.
-By assuming each pixel has a linear response to the power, a linear regression was used.
+This was done by using the greyscale projections at different exposures.
+By assuming each pixel has a linear response to the power of the x-ray tube, a linear regression was used.
 This is discussed in Chapter \ref{chapter2}.
 
-In Chapter \ref{chapter3}, it was attempted to fit a compound Poisson distributed onto the grey values of a projection to quantify the noise.
+In Chapter \ref{chapter3}, it was attempted to fit a compound Poisson distribution onto the grey values of a projection to quantify the noise.
 Unfortunately, the model suffered from identifiability issues for high photon counts.
@@
 19 randomly selected projections were used for the variance-mean model to fit onto.
-The remaining projection was compared with the simulated projection under the face of uncertainty.
+The remaining projection was compared with the simulated projection in the face of uncertainty.
 The uncertainty was predicted using the variance-mean model.
-Inference was done on the test statistics, one for each pixel in a projection.
-Unfortunately, the simulation was not perfect which led to model misspecification, thus false positives.
+Hypothesis testing was done on the test statistics, one for each pixel in a projection.
+Unfortunately, the simulation was not perfect which led to model misspecification, thus, false positives.
 The empirical null filter was developed and used to smooth the test statistics.
-This allows the inference to pick out areas which are unusual and unlike its neighbours.
-The filtered test statistics were converted to $p$-values so that hypothesis testing can be done to detect the voids.
+This allows the hypotheses test to pick out areas which are unusual and unlike its neighbours.
+The filtered test statistics were converted to $p$-values so that hypotheses testing can be done to detect the voids.
 
-In the ABS test sample, voids of the order of millimetres were detectable using this method.
+In the ABS test sample, voids in the order of millimetres were detectable using this method.
 However, for the titanium test sample, the voids were undetectable due to dominating edge effects.
@@
 The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection.
-Repeating the experiment using difficult angles may indicate weaknesses from using a singular angle.
+Defect detection can be tough if a difficult projection angle was used.
 Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.
 
-The experiment could be improved if the location of the defects were known in the projection.
+The inference could be improved if the location of the defects were known in the projection.
 This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.
@@
 A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt.
-By using fewer projections, quality control can be faster which advances the development and increase the scope of applications of additive manufacturing.
+By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of additive manufacturing.
 

### 2019-09-15 reports/thesis/chapters/2_dataCollection.tex
Change notation

@@
 For each power, the within and between pixel variance was calculated.
-Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,n$ replicates.
+Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,m$ replicates.
 The within and between pixel variance are
 \begin{equation}
-s_\mathrm{w}^2(P)=\dfrac{1}{WH(n-1)}
-  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{n}
+s_\mathrm{w}^2(P)=\dfrac{1}{WH(m-1)}
+  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{m}
   \left(
@@
 \begin{equation}
-s_\mathrm{b}^2(P)=\dfrac{n}{WH-1}
+s_\mathrm{b}^2(P)=\dfrac{m}{WH-1}
   \sum_{x=1}^{W}\sum_{y=1}^{H}
@@
 \begin{equation}
-  \overline{U}_{x,y}(P) = \dfrac{1}{n}\sum_{j=1}^{n}U_{x,y}^{(j)}(P)
+  \overline{U}_{x,y}(P) = \dfrac{1}{m}\sum_{j=1}^{m}U_{x,y}^{(j)}(P)
 \end{equation}
@@
 \end{equation}
-In this specific experiment, $W=2000$, $H=2000$ and $n=19$. The $F$ statistic is
+In this specific experiment, $W=2000$, $H=2000$ and $m=19$. The $F$ statistic is
 \begin{equation}
@@
 Using the $F$ test from ANOVA was found to be too strict in this experiment.
-Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1, WH(n-1)}$.
+Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1, WH(m-1)}$.
 In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for this analysis.

### 2019-09-15 reports/thesis/chapters/3_compoundPoisson.tex
Change notation

@@
 The compound Poisson-gamma distribution can be used to model the grey value of each pixel in a projection.
-Suppose a projection has $m$ pixels and $n$ replicate projections were obtained.
+Suppose a projection has $N$ pixels and $m$ replicate projections were obtained.
 Let $X_{i,j}$ and $Y_{i,j}$ be the grey value and photon count, respectively, of the $i$th pixel in the $j$th replicate projection.
@@
 The model may be simplified by omitting the electronic noise and this can be done by setting $a=0$ and $\kappa=0$.
-The number of pixels can be set to $m=1$ to simplify the model further.
+The number of pixels can be set to $N=1$ to simplify the model further.
 Parameter estimation can be done using gradient methods because the likelihood of the compound Poisson can be evaluated \citep{dunn2005series}.

### 2019-09-15 reports/thesis/chapters/4_variancePrediction.tex
Change notation

@@
 The sample variance-mean data were obtained from the replicate projections.
-Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotsc,n$.
+Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotsc,m$.
 The sample mean and sample variance grey value for the pixel at $(i,j)$ are
 \begin{equation}
-    \overline{x}_{i,j}=\frac{1}{n}\sum_{r=1}^n x_{i,j}^{(r)}
+    \overline{x}_{i,j}=\frac{1}{m}\sum_{r=1}^m x_{i,j}^{(r)}
 \end{equation}
@@
     y_{i,j} =
-    \frac{1}{n-1}
-    \sum_{r=1}^n
+    \frac{1}{m-1}
+    \sum_{r=1}^m
         \left(
@@
 The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by using a model fitted onto the sample variance-mean data.
-No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset.
+No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_N,y_N)$ from now on, where $N$ is the area of the ROI or the size of the dataset.
 Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$.
@@
 \begin{equation}
-\dfrac{(n-1)Y(x)}{\sigma^2(x)}\sim\chi^2_{n-1}
+\dfrac{(m-1)Y(x)}{\sigma^2(x)}\sim\chi^2_{m-1}
 \end{equation}
@@
 \end{equation}
-where $\alpha=(n-1)/2$ is the shape parameter. The expectation and variance are
+where $\alpha=(m-1)/2$ is the shape parameter. The expectation and variance are
 \begin{equation}
@@
 \begin{equation}
-  \ln L = \sum_{i=1}^m \left[
+  \ln L = \sum_{i=1}^N \left[
     \alpha\ln\alpha
@@
 \end{equation}
-where $\widehat{y}_i=\widehat{y}(x_i)$. $\alpha=(n-1)/2$ was assumed to be known so does not need to be estimated.
+where $\widehat{y}_i=\widehat{y}(x_i)$. $\alpha=(m-1)/2$ was assumed to be known so does not need to be estimated.
 
@@
 \begin{equation}
-  \ln L_\mathrm{s} = \sum_{i=1}^m \left[
+  \ln L_\mathrm{s} = \sum_{i=1}^N \left[
     \alpha\ln\alpha
@@
   D = 2\alpha
-  \sum_{i=1}^m\left[
+  \sum_{i=1}^N\left[
       \dfrac{
@@
 \end{equation}
-The mean scaled deviance is obtained by removing the factor of $\alpha$ and dividing by $m$ to get
+The mean scaled deviance is obtained by removing the factor of $\alpha$ and dividing by $N$ to get
 \begin{equation}
-    D_\mathrm{s} = \dfrac{2}{m}
-    \sum_{i=1}^m\left[
+    D_\mathrm{s} = \dfrac{2}{N}
+    \sum_{i=1}^N\left[
         \dfrac{
@@
 
-Assuming the model is correct, it is given that $D\sim\chi_{m-k}^2$ which implies that for large $m$,
+Assuming the model is correct, it is given that $D\sim\chi_{N-k}^2$ which implies that for large $N$,
 \begin{equation}
@@
 \begin{equation}
-\variance\left[D_\mathrm{s}\right] = \dfrac{2}{\alpha^2 m} \ .
+\variance\left[D_\mathrm{s}\right] = \dfrac{2}{\alpha^2 N} \ .
 \end{equation}
-Because $\alpha=(n-1)/2$, this shows that the number of replicated projections used to obtain the sample variance-mean data has an influence on the mean scaled deviance.
+Because $\alpha=(m-1)/2$, this shows that the number of replicated projections used to obtain the sample variance-mean data has an influence on the mean scaled deviance.
 This result can be used to estimate $\alpha$ if it is unknown.

### 2019-09-15 reports/thesis/chapters/5_inference.tex
Change notation

@@
-A disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other.
+Disagreements between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other.
 Any values too big in magnitude can be considered as a defect.
@@
 where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance.
-The test statistic was calculated for each pixel in the projection.
+The test statistic was calculated for each pixel in the ROI, that is, pixels which represent the test sample.
+The ROI was created by manually segmenting the test sample from the projection.
+
 For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution.
@@
 Multiple hypotheses testing occurs when there are more than one hypotheses to test.
-For example, $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$.
-The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,n$.
-Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_n$.
+For example, $N$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_N$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,N$.
+The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,N$.
+Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_N$.
 
@@
   \text{PCER}=
-  \dfrac{1}{n}
+  \dfrac{1}{N}
   \expectation[V]
@@
 \end{equation}
-It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
+It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/N_0 = \alpha$, then it controls the PCER such that
 \begin{equation}
@@
     &Negative&Positive&Total\\\hline
-    Null & $U$ & $V$ & $n_0$\\
-    Non-null & $T$ & $S$ & $n-n_0$\\\hline
-    &$n-R$&$R$&$n$
+    Null & $U$ & $V$ & $N_0$\\
+    Non-null & $T$ & $S$ & $N-N_0$\\\hline
+    &$N-R$&$R$&$N$
   \end{tabular}
@@
 \end{equation}
-This is done by adjusting the size of the test to be $\alpha/n$.
-By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$.
-Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$.
+This is done by adjusting the size of the test to be $\alpha/N$.
+By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/N)^N\right]$.
+Using the approximation $(1-\alpha/N)^N\approx 1-\alpha$ then $\text{FWER}\approx \alpha$.
 This shows that the Bonferroni correction controls the family-wise error rate such that
@@
 It adapts to the data and chooses different sizes for different data.
-The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(n)}$.
+The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(N)}$.
 Suppose a size $\alpha$ is provided beforehand.
@@
 \begin{equation}
-  \alpha_{\text{BH}} = \frac{\alpha k}{n}
+  \alpha_{\text{BH}} = \frac{\alpha k}{N}
 \end{equation}
@@
 \begin{equation}
-  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
+  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{N}\alpha
   \ .
@@
 This test the statistics with $p$-values $p_{(1)},p_{(2)},\dotsc,p_{(k)}$ as positive.
-For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
-For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.
+For the case where $p_{(1)}>\alpha/N$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes.
+For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/N$.
 
@@
 Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively.
-The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\dotsc,n$.
+The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\dotsc,N$.
 
@@
 \end{equation}
-where $h$ is the bandwidth and $\phi(x)$ is the standard Normal density. The bandwidth was chosen such that
+where $h$ is the bandwidth, $\phi(x)$ is the standard Normal density and $n=N$ is number of terms in the summation. The bandwidth was chosen such that
 \begin{equation}
@@
 
-The test statistics were normalised to $T_1,T_2,\dotsc,T_n$ by using
+The test statistics were normalised to $T_1,T_2,\dotsc,T_N$ by using
 \begin{equation}
@@
 \end{equation}
-for $i=1,2,\dotsc,n$. The normalised $p$-values were obtained by using
+for $i=1,2,\dotsc,N$. The normalised $p$-values were obtained by using
 \begin{equation}
@@
 \end{equation}
-$K_{x,y} = C_r(x,y) \cap \text{ROI}$ and $n=\left|K_{x,y}\right|$. Using these estimates, the test statistics were normalised using
+$K_{x,y} = C_r(x,y) \cap \text{ROI}$ and $n=\left|K_{x,y}\right|$, not to be confused with $N$.
+A bandwidth of $h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)$ was used where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$.
+
+After obtaining the estimates of the empirical null parameters, the test statistics were normalised using
 \begin{equation}

### 2019-09-17 reports/thesis/chapters/3_compoundPoisson.tex
Revise

@@
 
-Returning back to the compound Poisson with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
+Returning back to the compound Poisson distribution with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
 It can be shown that the m.g.f.~is
@@
 \label{chapter:compoundPoisson_compoundPoissonGamma}
-A special case of the compound Poisson is when $U\sim\gammaDist\left(\alpha,\beta\right)$ where $\alpha>0$ is the gamma shape parameter and $\beta>0$ is the gamma rate parameter.
+A special case of the compound Poisson distribution is when $U\sim\gammaDist\left(\alpha,\beta\right)$ where $\alpha>0$ is the gamma shape parameter and $\beta>0$ is the gamma rate parameter.
 This was used for example in \cite{xu2009electronic}.
@@
 \end{equation}
-Similarly
+Similarly,
 \begin{equation}
@@
 \end{equation}
-Therefore, the maximum of $W_y^{(r)}$ is located at $y_\text{max}$ for all $r=0,1,2,\dotsc$.
-As a results, the same method for evaluating $W_y$ can be used to evaluate $W_y^{(r)}$.
+Therefore, the maximum of $W_y^{(r)}$ is located at $y_\text{max}=\dfrac{x^{2-p}}{\phi(2-p)}$ for all $r=0,1,2,\dotsc$.
+As a result, the same method for evaluating $W_y$ can be used to evaluate $W_y^{(r)}$.
 For a given $r=0,1,2,\dotsc$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
@@
   \nonumber\\
-  &\!\begin{multlined}[b]=
+  &=\begin{multlined}[t]
     -n\lambda

### 2019-09-17 reports/thesis/chapters/3_compoundPoisson.tex
Adjust Fisher information matrix in compound Poisson

@@
   \ .
+  \label{eq:compoundPoisson_jointLogLikelihood}
 \end{multline}
@@
 \end{equation}
-The calculation is similar to the derivatives of $T$ using the same approximations.
-Using the fact that $\expectation[Y]=\lambda$ and another approximation $\expectation\left[\psi^{(r)}(\alpha Y)\right]\approx\psi^{(r)}(\alpha \lambda)$, then
-\begin{equation}
+
+Most of the calculations for the elements of the matrix are similar to the derivatives of $T$.
+For the $\alpha$ component, taking derivatives of the joint log-likelihood (Equation \eqref{eq:compoundPoisson_jointLogLikelihood}) obtains
+\begin{equation}
+\dfrac{\partial\ln L}{\partial\alpha} = \sum_{i=1}^n\mathbb{I}(x_i>0)
+\left[
+  Y_i\ln\beta - \psi(Y_i\alpha)Y_i+Y_i\ln x_i
+\right]
+\end{equation}
+\begin{equation}
+\dfrac{\partial^2\ln L}{\partial\alpha^2} = \sum_{i=1}^n\mathbb{I}(x_i>0)
+\left[
+  -\psi'(Y_i\alpha)Y_i^2
+\right] \ .
+\end{equation}
+The expectation of the second-order derivative is
+\begin{equation}
+-\expectation\left[\dfrac{\partial^2\ln L}{\partial\alpha^2}\right]
+=
+n\left(1-\euler^{-\lambda}\right)
+\expectation\left[
+  \psi'(Y\alpha)Y^2
+\right]
+\end{equation}
+where the factor $\left(1-\euler^{-\lambda}\right)$ is the proportion of data where $x_i>0$. $\expectation\left[\psi'(Y\alpha)Y^2\right]$ can be approximated. Let $g(Y)=\psi'(Y\alpha)Y^2$, then
+\begin{equation}
+\expectation\left[\psi'(Y\alpha)Y^2\right]
+\approx
+\psi'(\lambda\alpha)\lambda^2
++\dfrac{\lambda}{2}g''(\lambda) \ .
+\end{equation}
+The derivatives of $g(Y)$ are
+\begin{align}
+g'(Y)&=\psi''(Y\alpha)Y^2\alpha + 2\psi'(Y\alpha)Y
+\\
+g''(Y)&=Y^2\alpha^2\psi'''(Y\alpha)+4Y\alpha\psi''(Y\alpha)+2\psi'(Y\alpha)\ .
+\end{align}
+Therefore,
+\begin{multline}
+-\expectation\left[\dfrac{\partial^2\ln L}{\partial\alpha^2}\right]=n\left(1-\euler^{-\lambda}\right)
+\\
+\times\left[(\lambda^2+\lambda)\psi'(\lambda\alpha)+2\lambda^2\alpha\psi''(\lambda\alpha)+\dfrac{\lambda^3\alpha^2}{2}\psi'''(\lambda\alpha)\right]
+\end{multline}
+
+The Fisher's information matrix is
+\begin{multline}
   \matr{I}=
-  \begin{pmatrix}
-    \dfrac{n}{\lambda} & 0 & 0 \\
-    0 & (\lambda^2+\lambda)\psi'(\alpha\lambda)+2\alpha\lambda^2\psi''(\alpha\lambda)+\frac{1}{2}\alpha^2\lambda^3\psi'''(\alpha\lambda) & -\dfrac{n\lambda}{\beta}\\
-    0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
-  \end{pmatrix}
-  \ .
-\end{equation}
-The Cram\'er-Rao lower bound is then
+  n
+  \left(\begin{matrix}
+    \dfrac{1}{\lambda} & 0\\
+    0 & \left(1-\euler^{-\lambda}\right)\left[(\lambda^2+\lambda)\psi'(\lambda\alpha)+2\lambda^2\alpha\psi''(\lambda\alpha)+\dfrac{\lambda^3\alpha^2}{2}\psi'''(\lambda\alpha)\right]\\
+    0 & -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}
+  \end{matrix}\right.
+  \\
+  \left.\begin{matrix}
+  \vphantom{\dfrac{1}{\lambda}}0\\
+  -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}\\
+  \dfrac{\left(1-\euler^{-\lambda}\right)\alpha\lambda}{\beta^2}
+  \end{matrix}\right)
+  \ .
+\end{multline}
+The Cram\'er-Rao lower bound can be obtained using
 \begin{equation}

### 2019-09-18 reports/thesis/chapters/4_variancePrediction.tex
Check algebra

@@
 \begin{equation}
-\variance\left[Y(x)\right]=\dfrac{\sigma^2(x)}{\alpha}
+\variance\left[Y(x)\right]=\left(\dfrac{\sigma^2(x)}{\alpha}\right)^2
 \end{equation}
@@
 An example of a systematic component are polynomial features $\eta(x)=\sum_{r=0}^{p}\beta_r x^{r}$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \sum_{r=0}^{p}\beta_r x^{r}$.
-Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_2, \dotsc, \beta_{p}$ given data for the model to fit onto.
+Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \dotsc, \beta_{p}$ given data for the model to fit onto.
 
@@
 \begin{equation}
-\BIC = k\ln m - 2\ln L
+\BIC = k\ln N - 2\ln L
 \end{equation}
@@
     -\ln\Gamma(\alpha)
-    -\alpha\ln{y_i}
-    +(\alpha-1)\ln y_i
+    -\ln y_i
     -\alpha

### 2019-09-18 reports/thesis/chapters/5_inference.tex
Check algebra

@@
 \end{equation}
-for $r=0,1,2,3,\dotsc$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is $\widehat{p}_Z(z)=
-  \frac{1}{nh}
-  \sum_{i=1}^n\phi\left(
-    \frac{z_i-z}{h}
-  \right) $,
-so the log density is
+for $r=0,1,2,3,\dotsc$ until some convergence condition is met.
+The derivatives for the log density were obtained via the following.
+Recall the kernel density estimate in Equation \eqref{eq:inference_kernel_density_estimate}, the log density is
 \begin{equation}

### 2019-09-20 reports/thesis/book.tex
Revise

@@
 \vspace{1cm}
-{\Large Sherman E.~Lo\par}
+{\Large Sherman Edea Lo\par}
 {\Large Doctor of Philosophy in Statistics\par}
@@
 This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1).
-I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar M\"{a}rtens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.
+I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar M\"{a}rtens, Marcin Mider, Xenia Miscouridou, Paul Vanetti, Andi Wang.
 

### 2019-09-20 reports/thesis/chapters/1_literatureReview.tex
Typo
Revise

@@
 There are various discontinuities in AM.
-In FDM, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}.
+In fused deposition modelling, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}.
 Internal voids can be formed due to insufficient material flow \citep{weeren1995quality}.
@@
 However, it is very complicated as it is optimising over a very large dimensional space \citep{brierley2018optimized}.
-It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}.
+Studies have been conducted comparing simulated projections with each other, one with defects and the other without, by looking at the contrast to noise ratio of the defects.
+This is done at various projection angles as part of a large optimisation problem \citep{brierley2018optimized}.
 Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.

### 2019-09-20 reports/thesis/chapters/2_dataCollection.tex
Revise

@@
   }
-  \caption{\texttt{AbsNoFilter} projections at \ang{30}; note the colour scale may vary.}
+  \caption{\texttt{AbsNoFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
   \label{fig:data_AbsNoFilter}
@@
   }
-  \caption{\texttt{AbsFilter} projections at \ang{30}; note the colour scale may vary.}
+  \caption{\texttt{AbsFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
   \label{fig:data_AbsFilter}
@@
   }
-  \caption{\texttt{TiFilter} projections at \ang{30}; note the colour scale may vary.}
+  \caption{\texttt{TiFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
   \label{fig:data_TiFilter}
@@
   }
-  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction.}
+  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction. The colour scales are in units of \SI{}{\adu}.}
   \label{fig:data_shadingCorrectionExample_image}
@@
   }
-  \caption{The black and white images before and after shading correction from the \texttt{AbsNoFilter} dataset.}
+  \caption{The black and white images before and after shading correction from the \texttt{AbsNoFilter} dataset. The colour scales are in units of \SI{}{\adu}.}
   \label{fig:data_shadingCorrectionExample_greyscale}

### 2019-09-20 reports/thesis/chapters/5_inference.tex
Revise

@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
-      \caption{X-ray image}
+      \caption{Obtained projection (\SI{}{\adu})}
       \label{fig:inference_inferenceIntro_inference_scan}
@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
-      \caption{\texttt{aRTist} simulation}
+      \caption{\emph{aRTist} projection (\SI{}{\adu})}
       \label{fig:inference_inferenceIntro_inference_artist}
@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
-      \caption{Positive pixels}
+      \caption{Positive pixels overlaid on a)}
       \label{fig:inference_inferenceIntro_inference_positivePixels}
@@
   }
-  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect purposefully manufactured voids.
-The $p$-values obtained were used for hypotheses testing.
+  \caption{The obtained projection of the test sample (a), from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} projection (b) to detect purposefully manufactured voids.
+The $p$-values (c) obtained were used for hypotheses testing.
 Pixels detected as positive are shown in red in d) using the \cite{benjamini1995controlling} procedure at the 5\% false discovery rate level.}
@@
         \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
-        \caption{Image with positive pixels}
+        \caption{Obtained projection (\SI{}{\adu})}
       \end{subfigure}
@@
         \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
-        \caption{Image with positive pixels}
+        \caption{{Obtained projection (\SI{}{\adu})}}
       \end{subfigure}
@@
         \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
-        \caption{Image with positive pixels}
+        \caption{{Obtained projection (\SI{}{\adu})}}
       \end{subfigure}
@@
         \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
-        \caption{Image with positive pixels}
+        \caption{{Obtained projection (\SI{}{\adu})}}
       \end{subfigure}
@@
         \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
-        \caption{Image with positive pixels}
+        \caption{{Obtained projection (\SI{}{\adu})}}
       \end{subfigure}
@@
         \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
-        \caption{Image with positive pixels}
+        \caption{{Obtained projection (\SI{}{\adu})}}
       \end{subfigure}

### 2019-09-23 reports/paper1/paper.tex
Modify graphs to align and look better

@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=1.05\textwidth, height=5.0cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
         \caption{X-ray projection with positive pixels}
@@
       \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}
         \caption{$-\log p$}

### 2019-09-23 reports/thesis/chapters/5_inference.tex
Modify graphs to align and look better

@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
+        \caption{Type 1 error}
         \label{fig:inference_DefectSimulationDust_type1}
-        \caption{Type 1 error}
       \end{subfigure}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
         \caption{Obtained projection (\SI{}{\adu})}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
         \caption{{Obtained projection (\SI{}{\adu})}}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}
         \caption{$-\log p$}
@@
 
-\begin{figure}
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.eps}
-      \caption{$z$ image with section highlighted}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHist.eps}
-      \caption{Histogram of $z$ in the kernel}
-    \end{subfigure}
-  }
-  \caption{A section of the bottom right of a unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
-  \label{fig:inference_cornerSelect}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\subSize]{../figures/inference/segment.eps}
-  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
-  \label{fig:inference_segmentFurther}
-\end{figure}
-
 False positives were detected on the bottom right of the test sample.
@@
 
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.eps}
+      \caption{$z$ image with section highlighted}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHist.eps}
+      \caption{Histogram of $z$ in the kernel}
+    \end{subfigure}
+  }
+  \caption{A section of the bottom right of a unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
+  \label{fig:inference_cornerSelect}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\subSize]{../figures/inference/segment.eps}
+  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
+  \label{fig:inference_segmentFurther}
+\end{figure}
+
 \begin{figure}[p]
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
         \caption{{Obtained projection (\SI{}{\adu})}}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
         \caption{{Obtained projection (\SI{}{\adu})}}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
         \caption{{Obtained projection (\SI{}{\adu})}}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}
         \caption{$-\log p$}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
         \caption{{Obtained projection (\SI{}{\adu})}}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
+        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}
         \caption{$-\log p$}

### 2019-09-23 inference/scripts/inferenceSubsample.m

@@ -36,15 +36,16 @@ function subsampleExample(scan, zImage, rowSubsample, colSubsample, scaleLength,
   
   %FIGURE
   %Plot the z image with a rectangle highlighting the subsample
-  fig = LatexFigure.sub();
+  fig = LatexFigure.subLoose();
   imagePlot = Imagesc(zImage);
   imagePlot.plot();
   imagePlot.addScale(scan,1,'y');
+  imagePlot.removeLabelSpace();
   hold on;
   rectangle('Position', [colSubsample(1), rowSubsample(1), ...
       colSubsample(end)-colSubsample(1)+1, rowSubsample(end)-rowSubsample(1)+1], ...
       'EdgeColor','r','LineStyle','--');
-  saveas(fig,fullfile('reports','figures','inference',strcat(name,'_zImage.eps')),'epsc');
+  print(fig,fullfile('reports','figures','inference',strcat(name,'_zImage.eps')),'-depsc','-loose');
 
   %get the subsample of z statistics and do BH multiple hypothesis testing without any empirical
       %null correction
@@ -64,9 +65,10 @@ function subsampleExample(scan, zImage, rowSubsample, colSubsample, scaleLength,
 
   %FIGURE
   %Plot the histogram of the z statistics with the BH critical boundary
-  fig = LatexFigure.sub();
+  fig = LatexFigure.subLoose();
   zTester.plotHistogram2(false);
-  saveas(fig, fullfile('reports','figures','inference',strcat(name,'_histogram.eps')),'epsc');
+  print(fig, fullfile('reports','figures','inference',strcat(name,'_histogram.eps')),'-depsc',...
+      '-loose');
 
   %estimate the empirical null and do the test
   zTester.estimateNull(0, int32(-854868324));
@@ -84,7 +86,7 @@ function subsampleExample(scan, zImage, rowSubsample, colSubsample, scaleLength,
 
   %FIGURE
   %Plot the frequency density estimate along with the empirical null
-  fig = LatexFigure.sub(); 
+  fig = LatexFigure.subLoose(); 
   plot(xPlot, numel(zSampleVector)*fHat); %plot density estimate
   hold on;
   %draw the null std
@@ -95,7 +97,8 @@ function subsampleExample(scan, zImage, rowSubsample, colSubsample, scaleLength,
   ylabel('frequency density');
   xlabel('z statistic');
   xlim([min(zSampleVector), max(zSampleVector)]);
[…]

### 2019-09-23 shadingcorrection/ShadingCorrectionAnova.m

@@ -56,6 +56,7 @@ classdef (Abstract) ShadingCorrectionAnova < Experiment
         boxplotBetween.setPosition(powerArray);
         boxplotBetween.plot();
         ax.YScale = 'log';
+        ax.Box = 'on';
         xlabel('power (W)');
         %the use of unicode so that it renders properly in .eps output
         %see https://uk.mathworks.com/matlabcentral/answers/159732-2014b-axis-label-errors-when-printing-to-postscript
@@ -82,6 +83,7 @@ classdef (Abstract) ShadingCorrectionAnova < Experiment
         legendAxes(iShading) = boxPlotF.getLegendAx();
       end
       ax.YScale = 'log';
+      ax.Box = 'on';
       xlabel('power (W)');
       ylabel('F statistic');
       legend(legendAxes, this.shadingCorrectionNameArray, 'Location', 'best');

### 2019-09-23 shadingcorrection/shadingCorrectionExample.m

@@ -59,42 +59,45 @@ for i = 1:numel(scanArray)
   scan = scanArray(i); %get the scan, shading correction already applied
   
   %plot the scan
-  fig = LatexFigure.sub();
+  fig = LatexFigure.subLoose();
   imagesc = Imagesc(scan.loadImage(1));
   if (~isempty(climProjection))
     imagesc.setCLim(climProjection);
   end
   imagesc.plot();
   imagesc.addScale(scan,1,'k');
+  imagesc.removeLabelSpace();
   climProjection = imagesc.clim; %save the clim
-  saveas(fig,fullfile('reports','figures','data', ...
-      strcat(mfilename,'_image_',scan.getShadingCorrectionStatus(),'.eps')),'epsc');
+  print(fig,fullfile('reports','figures','data', ...
+      strcat(mfilename,'_image_',scan.getShadingCorrectionStatus(),'.eps')),'-depsc','-loose');
   
   %get the black and white image
   black = scan.calibrationScanArray(1).loadImage(calibrationIndex(2,1));
   white = scan.calibrationScanArray(scan.whiteIndex).loadImage(calibrationIndex(2,end));
   
   %plot the black image
-  fig = LatexFigure.sub();
+  fig = LatexFigure.subLoose();
   imagesc = Imagesc(black);
   if (~isempty(climBlack))
     imagesc.setCLim(climBlack);
   end
   imagesc.plot();
+  imagesc.removeLabelSpace();
   climBlack = imagesc.clim; %save the clim
-  saveas(fig,fullfile('reports','figures','data', ...
-      strcat(mfilename,'_black_',scan.getShadingCorrectionStatus(),'.eps')),'epsc');
+  print(fig,fullfile('reports','figures','data', ...
+      strcat(mfilename,'_black_',scan.getShadingCorrectionStatus(),'.eps')),'-depsc','-loose');
   
   %plot the white image
-  fig = LatexFigure.sub();
+  fig = LatexFigure.subLoose();
   imagesc = Imagesc(white);
   if (~isempty(climWhite))
     imagesc.setCLim(climWhite);
   end
   imagesc.plot();
+  imagesc.removeLabelSpace();
   climWhite = imagesc.clim; %save the clim
-  saveas(fig,fullfile('reports','figures','data', ...
-      strcat(mfilename,'_white_',scan.getShadingCorrectionStatus(),'.eps')),'epsc');
[…]

### 2019-09-23 varmean/varMeanExample.m

@@ -64,20 +64,21 @@ function plotExample(scan, termMatrixArray, linkArray)
     
     %plot the heat map
     hist3Heatmap = Hist3Heatmap();
-    fig = LatexFigure.sub();
+    fig = LatexFigure.subLoose();
     hist3Heatmap.plot(xOriginal, yOriginal);
     hold on;
     plot(xPlot, yPlot, 'r');
     plot(xPlot, upError, 'r--');
     plot(xPlot, downError, 'r--');
+    ytickformat('%.1f');
     xlabel('mean grey value (ADU)');
     ylabel('variance grey value (ADU²)');
     
     %save the figure
     terms = reshape(num2str(termMatrix'),1,[]);
     terms(terms==' ') = [];
-    saveas(fig, fullfile('reports','figures','varmean', ...
-        strcat(mfilename,'_',class(scan),'_',link,terms,'.eps')),'epsc');
+    print(fig, fullfile('reports','figures','varmean', ...
+        strcat(mfilename,'_',class(scan),'_',link,terms,'.eps')),'-depsc','-loose');
     
   end
   

### 2019-09-23 varmean/varMeanResidual.m

@@ -55,32 +55,35 @@ for iScan = 1:numel(scanArray)
 
   %plot the heat map of the residual vs grey value
   hist3Heatmap = Hist3Heatmap();
-  fig = LatexFigure.sub();
+  fig = LatexFigure.subLoose();
   hist3Heatmap.plot(xOriginal, residual);
   hold on;
   plot(xPlot, upError, 'r--');
   plot(xPlot, downError, 'r--');
   xlabel('mean grey value (ADU)');
   ylabel('residual (ADU²)');
-  saveas(fig, fullfile(directory,strcat(mfilename,class(scan),'_vsgreyvalue.eps')), 'epsc');
+  ytickformat('%.1f');
+  print(fig, fullfile(directory,strcat(mfilename,class(scan),'_vsgreyvalue.eps')), '-depsc', ...
+      '-loose');
   
   %plot the residual on the segmentation
   residualSpatial = double(scan.getSegmentation());
   residualSpatial(residualSpatial==1) = residual;
   residualSpatial(residualSpatial==0) = nan;
-  fig = LatexFigure.sub();
+  fig = LatexFigure.subLoose();
   imagesc = Imagesc(abs(residualSpatial));
   imagesc.setCLim([0,max(upError)]);
   imagesc.plot();
+  imagesc.addScale(scan, 1.0, [1,1,0]);
+  imagesc.removeLabelSpace();
   %for AbsNoFilterDeg120, highlight where the inflection is
   if (isa(scan,'AbsNoFilterDeg120'))
     hold on;
-    axis xy;
     plot([220,220],[130,1860],'r--');
     plot([620,620],[130,1860],'r--');
     plot([220,620],[130,130],'r--');
     plot([220,620],[1860,1860],'r--');
   end
-  saveas(fig, fullfile(directory,strcat(mfilename,class(scan),'_spatial.eps')), 'epsc');
+  print(fig, fullfile(directory,strcat(mfilename,class(scan),'_spatial.eps')), '-depsc', '-loose');
   
 end

### 2019-09-23 varmean/varmeancv/VarMeanCv.m

@@ -66,7 +66,7 @@ classdef VarMeanCv < Experiment
         end
 
         %plot the test deviance for each shading correction
-        fig = LatexFigure.sub();
+        fig = LatexFigure.subLoose();
         legendArray = line(0,0);
         for iShadingCorrection = 1:this.nShadingCorrection
           boxplots = this.getBoxplot(-0.1 + ((iShadingCorrection-1)*0.1), isTrainingDeviance, ...
@@ -80,6 +80,8 @@ classdef VarMeanCv < Experiment
         %label each glm with its name
         ax.XTickLabel = this.modelArray;
         ax.XLim = [0.5,numel(this.modelArray)+0.5];
+        ax.Box = 'on';
+        ax.YAxis.Exponent = floor(log10(abs(ax.YLim(2))));
         %label the axis and legend
         ylabel(statName);
         legend(legendArray,shadingCorrectionNameArray,'Location','best');
@@ -88,7 +90,7 @@ classdef VarMeanCv < Experiment
         fileName = fullfile('reports','figures','varmean', ...
             strcat(class(this),'_',statName,'.eps'));
         fileName(fileName == ' ') = [];
-        saveas(fig,fileName,'epsc');
+        print(fig,fileName,'-depsc','-loose');
       end
     end
     

### 2019-09-23 reports/thesis/chapters/2_dataCollection.tex
Remove Ti

@@
 The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.
-Another test object was manufactured made from titanium (Ti-6Al-4V)
 
@@
 
-Filters were used, such as a \SI{0.35}{\milli\metre} copper filter and a \SI{2.0}{\milli\metre} tin filter, to tackle beam hardening.
+A \SI{0.35}{\milli\metre} copper filter was used to tackle beam hardening.
 
@@
 
-Three datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}.
+Two datasets were collected and named \texttt{AbsNoFilter} and \texttt{AbsFilter}.
 They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections.
-Projections of the ABS test sample were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}.
-The titanium test sample was scanned in \texttt{TiFilter}.
-To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter} and \texttt{TiFilter}.
+To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.
 
@@
 These include the properties of the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections.
-A sample of the obtained, simulated and greyscale projections for the datasets \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter} are shown in Figures \ref{fig:data_AbsNoFilter}, \ref{fig:data_AbsFilter} and \ref{fig:data_TiFilter} respectively.
+A sample of the obtained, simulated and greyscale projections from the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} are shown in Figures \ref{fig:data_AbsNoFilter} and \ref{fig:data_AbsFilter} respectively.
 
@@
 \centering
-\begin{tabular}{l|lll}
-                                                       & \multicolumn{3}{c}{Dataset name}                                                \\
-                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             & \texttt{TiFilter}        \\ \hline
-potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             & 190                      \\
-power (\SI{}{\watt})                                   & 36                   & 20                             & 20                       \\
-filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper & \SI{2.0}{\milli\metre} tin \\
-time exposure (\SI{}{\milli\second})                   & 708                  & 500                            & 1415                     \\
-distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            & 86                       \\
-distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            & 875                      \\
-number of replications for each angle                  & 100                  & 20                             & 20                       \\ \hline
-powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            & 0.0                      \\
-\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            & 10                       \\
-\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             & 20                       \\
-\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             &                          \\
-\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             &                          \\
-number of replications for each power                  & 20                   & 20                             & 20                    
+\begin{tabular}{l|ll}
+                                                       & \multicolumn{2}{c}{Dataset name}                      \\
+                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             \\ \hline
+potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             \\
+power (\SI{}{\watt})                                   & 36                   & 20                             \\
+filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper \\
+time exposure (\SI{}{\milli\second})                   & 708                  & 500                            \\
+distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            \\
+distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            \\
+number of replications for each angle                  & 100                  & 20                             \\ \hline
+powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            \\
+\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            \\
+\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             \\
+\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             \\
+\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             \\
+number of replications for each power                  & 20                   & 20                             
 \end{tabular}
@@
   \label{fig:data_AbsFilter}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30.eps}
-      \caption{Obtained projection at \SI{20}{\watt}}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30_sim.eps}
-      \caption{Simulated projection at \SI{20}{\watt}}
-    \end{subfigure}
-  }
-  \centerline{
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration1.eps}
-      \caption{Greyscale projection at \SI{0}{\watt}}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration3.eps}
-      \caption{Greyscale projection at \SI{20}{\watt}}
-    \end{subfigure}
-  }
-  \caption{\texttt{TiFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
-  \label{fig:data_TiFilter}
 \end{figure}

### 2019-09-23 reports/thesis/chapters/5_inference.tex
Remove Ti

@@
 \section{Results}
-The empirical null filter was developed and tested thoroughly on simulated images. In this section, the filter was applied to the projections in the \texttt{AbsFilter} and \texttt{TiFilter} datasets.
-
-\subsection{ABS Test Sample}
+
+The empirical null filter was applied to the \texttt{AbsFilter} projection at \ang{120}.
+Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} and \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference when using a kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ and $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ respectively.
+With a small radius, the empirical null treated the voids as the null which is shown by the empirical null mean capturing the features of the voids.
+When a large enough radius was used, the larger voids were highlighted by the hypotheses test and the empirical null mean became smoother.
+This is evidence that this method ironed out false positives observed at the start of the chapter.
 
@@
 
-The empirical null filter was applied to the \texttt{AbsFilter} projection at \ang{120}.
-Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} and \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference when using a kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ and $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ respectively.
-With a small radius, the empirical null treated the voids as the null which is shown by the empirical null mean capturing the features of the voids.
-When a large enough radius was used, the larger voids were highlighted by the hypotheses test and the empirical null mean became smoother.
-This is evidence that this method ironed out  false positives observed at the start of the chapter.
+\begin{figure}
+  \centering
+  \centerline{
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.eps}
+      \caption{$z$ image with section highlighted}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHist.eps}
+      \caption{Histogram of $z$ in the kernel}
+    \end{subfigure}
+  }
+  \caption{A section of the bottom right of a unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
+  \label{fig:inference_cornerSelect}
+\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-  \centerline{
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.eps}
-      \caption{$z$ image with section highlighted}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHist.eps}
-      \caption{Histogram of $z$ in the kernel}
-    \end{subfigure}
-  }
-  \caption{A section of the bottom right of a unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
-  \label{fig:inference_cornerSelect}
-\end{figure}
+The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}.
+It was segmented using the edges of the $z$ image.
+The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
+The resulting filtered segments were stitched together to form the resulting filtered image.
+By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
+It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
+Most of false positives around the corners and edges have been eliminated.
+
+The same procedure was done on the projection at \ang{30}, as shown in Figure \ref{fig:inference_subroiAbsFilterDeg30_inference_radius1}, with similar results.
 
@@
 
-The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}.
-It was segmented using the edges of the $z$ image.
-The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on.
-The resulting filtered segments were stitched together to form the resulting filtered image.
-By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.
-It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
-Most of false positives around the corners and edges have been eliminated.
-
-The same procedure was done on the projection at \ang{30}, as shown in Figure \ref{fig:inference_subroiAbsFilterDeg30_inference_radius1}, with similar results.
-
-\subsection{Titanium Test Sample}
-
-The whole procedure was repeated on the titanium test sample in the dataset \texttt{TiFilter}.
-The resulting $z$ statistics are shown in Figure \ref{fig:inference_subroiTiFilter_unfiteredZ} and shows, as in the \texttt{AbsFilter} case, a boundary on the edges of the test sample.
-The faces of the test sample were manually segmented and the empirical null filter was used on each segment separately and stitched together to form the final stages of the analysis.
-
-\begin{figure}
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_unfilteredZ.eps}
-        \caption{\ang{30}}
-      \end{subfigure}
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_unfilteredZ.eps}
-        \caption{\ang{120}}
-      \end{subfigure}
-    }
-  \caption{Unfiltered $z$ images from the dataset \texttt{TiFilter}}
-  \label{fig:inference_subroiTiFilter_unfiteredZ}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
-        \caption{{Obtained projection (\SI{}{\adu})}}
-      \end{subfigure}
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-The test statistics from all segments were combined in the BH procedure.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and standard deviation.}
-  \label{fig:inference_subroiTiFilterDeg30_inference}
-\end{figure}
-
-\begin{figure}[p]
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
-        \caption{{Obtained projection (\SI{}{\adu})}}
-      \end{subfigure}
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}
-        \caption{$-\log p$}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
-        \caption{Empirical null std}
-      \end{subfigure}
-    }
-  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently.
-A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used.
-a) Highlighted in red are positive pixels at the 5\% FDR level.
-The test statistics from all segments were combined in the BH procedure.
-b) $p$-values on the log scale.
-c) and d) Empirical null mean and standard deviation.}
-  \label{fig:inference_subroiTiFilterDeg120_inference}
-\end{figure}
-
-The resulting inference are shown in Figures \ref{fig:inference_subroiTiFilterDeg30_inference} and \ref{fig:inference_subroiTiFilterDeg120_inference}.
-Unfortunately the edges of the test sample were falsely tested as positive and none of the voids were detected.
-The discrepancies are at the edges and can be due to inaccurate face segmentation or poor alignment of the \emph{aRTist} projection to the obtained projection.
-
 \section{Conclusion}
@@
 The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference.
-In the experiments, it was found that the FDR level is preserved after filtering.
+In the simulations, it was found that the FDR level is preserved after filtering.
 Also, the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}.
-
-Larger voids of diameter \SI{2.4}{\milli\metre} were detected in the ABS test sample.
+A sensible kernel radius is required to aid distinguishing misspecified null statistics from non-null statistics, for example, a kernel too small would treat defects as the null.
+
+In the experiment, the larger voids of diameter \SI{2.4}{\milli\metre} were detected in the test sample.
 False positives do occur but this is unavoidable because tests were done at the 5\% FDR level.
@@
 
+The assessment of the inference could be improved if the location of the defects were known in the projection.
+This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.
+
 For good results, the faces of the test sample were segmented.
@@
 Automatic segmentation may be possible with geometrical information from the CAD model.
-
-While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges.
-This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection.
-This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecified null statistics cannot be distinguished from non-null statistics.
-Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}.
-Lastly, because the titanium test sample was created using a power-based method, powder may become trapped \citep{brierley2018optimized} in the void.
-This results in the voids appearing with less contrast in the projections, making it harder to detect.
 

### 2019-09-23 reports/thesis/chapters/5_inference.tex
Minor revise
Use proofreader

@@
 
-Returning back to the example at the start of the chapter, the empirical null could be used on the histogram shown in Figure \ref{fig:inference_inferenceIntro_histogram}.
+Returning to the example at the start of the chapter, the empirical null could be used on the histogram shown in Figure \ref{fig:inference_inferenceIntro_histogram}.
 The resulting empirical null distribution is shown in Figure \ref{fig:inference_inferenceSubsampleAll}.
-The critical boundary, adjusted using the empirical null, which correspond to the 5\% FDR level was found to be $z\leqslant\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical2.txt}\geqslant z$ to 2 decimal places.
+The critical boundary, adjusted using the empirical null, which corresponds to the 5\% FDR level was found to be $z\leqslant\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical2.txt}\geqslant z$ to 2 decimal places.
 This would test all pixels as negative which is incorrect.
 
-The problem was that the empirical distribution of all of the test statistics looked like it did not came from a Normal distribution.
+The problem was that the empirical distribution of all of the test statistics looked like it did not come from a Normal distribution.
 It appeared that the test statistics varied spatially, suggesting the empirical null varied spatially as well.
-To account for the spatially variability of the null parameters, one possible extension is to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
+To account for the spatial variability of the null parameters, one possible extension is to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
 There are problems with this though.
-The first problem is that how the grid is overlaid can be arbitrary, for example the grid can be translated to produce different sections.
+The first problem is that how the grid is overlaid can be arbitrary, for example, the grid can be translated to produce different sections.
 Secondly, it is not clear how to combine the results from each section together \citep{efron2008simultaneous}.
@@
 The empirical null filter assumes that the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal.
-If $r$ is too big, the kernel will capture far away test statistics with a very different null distributions.
+If $r$ is too big, the kernel will capture distanced test statistics with very different null distributions.
 If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution.
@@
 $r$ controls the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$.
-$r$ should be selected so that $\pi_0$ is of a sensible value, for example $>90\%$.
+$r$ should be selected so that $\pi_0$ is of sensible value, for example, $>90\%$.
 In practice, the defects are unknown so various kernel radiuses should be tried out.
@@
 This is a type of weighted mean which is not robust to non-null statistics.
-In addition, the two Gaussian filters can have different radiuses, it is not clear how to set them.
+Also, the two Gaussian filters can have different radiuses, it is not clear how to set them.
 
@@
 
-The empirical null filter was implemented using open source software called \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \emph{GitHub} \citep{imagej2018rank}.
+The empirical null filter was implemented using open-source software called \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \emph{GitHub} \citep{imagej2018rank}.
 This class implemented filters, such as the mean filter and median filter, using a circular kernel, making this a suitable framework for the empirical null filter.
@@
 As a test, the empirical null filter with $r=\SI{5}{\pixel}$ was used on a \emph{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}.
-It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however, it did verify that the filter worked on arbitrary images with some computational considerations.
+It is meaningless to use the empirical null filter on an arbitrary image, however, it did verify that the filter coped with it with some computational considerations.
 The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ could be of interest, in particular, the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}.
 Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters.
-The empirical null mean has an impasto effect and preserved edges which is similar to the result in \cite{griffin2000mean}.
+The empirical null mean has an impasto effect and preserved edges which are similar to the result in \cite{griffin2000mean}.
 Dispersion filters such as the standard deviation filter can be used to detect edges.
@@
 
-When using the the empirical null filter in \emph{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
+When using the empirical null filter in \emph{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
 The user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
-The menu also has options for by-product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, quartile filters.
+The menu also has options for by-product images to be shown: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, quartile filters.
 Advanced options are available to the user, for example, the number of initial values set the number of valid solutions to be found when using the Newton-Raphson method to find the mode of the density estimate.
@@
 The empirical null filter uses \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}.
-This indicate that these pixels are outside the ROI and are ignored.
+This indicates that these pixels are outside the ROI and are ignored.
 The number of non-\texttt{NaN} captured by the kernel was kept track for calculations such as the bandwidth.
@@
 At the start on the far left, an initial value of the median over the pixels in the kernel was used.
-In addition, various initial values were randomly tried out until a requested number of valid solutions were found.
+Also, various initial values were randomly tried out until a requested number of valid solutions were found.
 For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial value.
@@
 \texttt{bridge.gif} is an 8-bit image so values were represented as integers.
-This opened up opportunities for the inter-quartile range and the standard deviation to be zero.
+This opened up opportunities for the interquartile range and the standard deviation to be zero.
 This caused problems as this would set the bandwidth to zero.
@@
 The statistical moments before and after filtering should be the same and were investigated.
-Because the empirical null mean and empirical null standard deviation are random variables, the filtered pixels will never be Normal and any normality tests would be too strict for the purpose of this experiment.
+Because the empirical null mean and empirical null standard deviation are random variables, the filtered pixels will never be Normal and any normality tests would be too strict for this experiment.
 
@@
 The $p$-values after filtering are shown in Figure \ref{fig:inference_allNull_pValues}.
-A quick inspection suggest that the filtered pixels appeared reasonably Normal for this particular example.
+A quick inspection suggests that the filtered pixels appeared reasonably Normal for this particular example.
 
@@
 Various other filters for normalisation were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter.
-They use different estimators to estimate the null parameters as their name suggest, Table \ref{table:inference_nullFilters} clarifies them.
+They use different estimators to estimate the null parameters as their name suggests, Table \ref{table:inference_nullFilters} clarifies them.
 
@@
 When using the empirical null filter, there was some negative bias with the standard deviation of the filtered test statistics.
-The negative bias comes from the positive bias when estimating the null standard deviation.
+The negative bias comes from a positive bias when estimating the null standard deviation.
 
@@
 The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} showed that the empirical null filter caused the filtered statistics to have heavy tails, in particular, for small kernel radiuses.
-This could cause problems in hypotheses testing because heavy tails could be misinterpreted as contribution from non-null statistics.
+This could cause problems in hypotheses testing because heavy tails could be misinterpreted as a contribution from non-null statistics.
 The source of the kurtosis inflation is from the estimation of the null standard deviation.
@@
 
-The empirical null filter aims to estimate the null distribution parameters from $Z_{x,y}$ in order to normalise it to form $T_{x,y}$.
+The empirical null filter aims to estimate the null distribution parameters from $Z_{x,y}$ to normalise it to form $T_{x,y}$.
 By normalising it, $T_{x,y}|H_{0,x,y}$ should be approximately standard Normal and hypotheses testing can be used to detect defects.
@@
 Various defects were investigated.
-Speckle defect with density $\pi_1$ assign all test statistics to be non-null with probability $\pi_1$, and are null otherwise.
+Speckle defect with density $\pi_1$ assign all test statistics to be non-null with probability $\pi_1$ and are null otherwise.
 This was chosen because the proportion of null statistics captured by the kernel should be the same for all kernel radiuses.
-A line defect assign columns of pixels to be non-null, a kernel would only capture a section of defect.
+A line defect assigns columns of pixels to be non-null, a kernel would only capture a section of the defect.
 A square defect was also investigated and a kernel can only capture the entire defect if its radius is large enough.
@@
 By using the empirical null filter, the resulting filtered image reassemble the uncontaminated image and appropriate inference can be done on the filtered image.
-However, some statistical power was lost when conducting hypotheses testing on the filtered image because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
+However, some statistical power was lost when conducting hypotheses testing on the filtered image because, in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power.
 This cannot be avoided as areas of high empirical null standard deviation was due to the randomness in sampling.
@@
 This is the result of each thread filtering a row and jumping from one mode, the null, to the other, the non-null, at different times.
-The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pin point which mode is greater.
+The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pinpoint which mode is greater.
 
@@
 With a sensible kernel radius, some of the defects can be detected.
-False negatives are common but this is inevitable in order to control for the FDR.
+False negatives are common but this is inevitable to control for the FDR.
 The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, tested no pixels for defects.
@@
 
-The ROC curves considers all thresholds or specificities used in the hypotheses testing.
-In the previous experiment, it was found variance of the test statistics were different before and after filtering.
+The ROC curves consider all thresholds or specificities used in the hypotheses testing.
+In the previous experiment, it was found the variance of the test statistics were different before and after filtering.
 As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
@@
 The AUC quantified showed that using the filter improved the performance of the test from the contamination.
-The type 1 error, or specificity, did decreased after filtering.
+The type 1 error, or specificity, did decrease after filtering.
 However, the results illustrated that the FDR is controlled quite well at around 5\% after filtering.
-This meant that in this particular example, the FDR control is consistent after filtering.
+This meant that in this particular example, FDR control is consistent after filtering.
 At situations with low detection power, the FDR can fluctuate between 0 and 1 and can take only so many values.
-For example if 3 positive pixels were detected, then the FDR can only take values of multiples of $1/3$ between and including 0 and 1.
+For example, if 3 positive pixels were detected, then the FDR can only take values of multiples of $1/3$ between and including 0 and 1.
 
@@
 Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $\pi_1=0.1$ to satisfy some assumptions made for the empirical null.
-Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of kernel which contains a defect to 10\%.
+Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of the kernel which contains a defect to 10\%.
 In other words, for a kernel with radius $r$
@@
 
-An experiment was conducted where the contaminated defected image were filtered using various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
+An experiment was conducted where the contaminated defected image was filtered using various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
 Hypotheses testing was done on the uncontaminated and filtered contaminated image.
@@
 This highlighted that a kernel with a good radius can perform almost as though there was no contamination.
-It also appeared that the optimal AUC was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.
+It also appeared that the optimal AUC was achieved when using the kernel radius from the rule of thumb, making these results consistent with the literature.
 
@@
 \afterpage{\clearpage}
-\section{Results}
+\subsection{Application to Real Projections}
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\subSize]{../figures/inference/segment.eps}
+  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
+  \label{fig:inference_segmentFurther}
+\end{figure}
+
 False positives were detected on the bottom right of the test sample.
@@
 It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges.
-Most of false positives around the corners and edges have been eliminated.
+Most of the false positives around the corners and edges have been eliminated.
 
 The same procedure was done on the projection at \ang{30}, as shown in Figure \ref{fig:inference_subroiAbsFilterDeg30_inference_radius1}, with similar results.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\subSize]{../figures/inference/segment.eps}
-  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
-  \label{fig:inference_segmentFurther}
-\end{figure}
 
@@
 
-The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference.
+The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make a sensible inference.
 In the simulations, it was found that the FDR level is preserved after filtering.
 Also, the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}.
-A sensible kernel radius is required to aid distinguishing misspecified null statistics from non-null statistics, for example, a kernel too small would treat defects as the null.
+A sensible kernel radius is required to avoid treating defects as the null.
 
@@
 The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however, efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method.
-Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels are interpolated.
+Instead, accuracy may be sacrificed for speed by only estimating the null parameters for several regularly spaced pixels, the remaining pixels are interpolated.
 This requires the null parameters to be slowly varying, otherwise, the interpolation may underfit.
@@
 Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics.
-Potential faster methods compared to the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
+Potential faster methods compared to the empirical null could exist in the literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}.
 The use of density estimation for robust estimation is also featured when using loss functions derived from the Hellinger-divergence \citep{beran1977minimum, jewson2018principles} or the beta-divergence \citep{basu1998robust, jewson2018principles} which bears similarities to the empirical null.
@@
 The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters.
-However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
+However, the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.

### 2019-09-23 reports/thesis/book.tex

@@
 
-In the ABS test sample, voids in the order of millimetres were detectable using this method.
-However, for the titanium test sample, the voids were undetectable due to dominating edge effects.
-The reason for this is unknown.
-It was speculated that the main source of error was from the simulated projection not being quite pixel-perfect aligned causing model misspecification at the edges.
-Therefore, the method was unable to distinguish disagreement due to model misspecification or a void.
-This method could be improved if \emph{aRTist} was integrated into it.
-For example, the simulated projection could be realigned to minimise the number of positives.
-This will help eliminate sources of error due to \emph{aRTist}.
-A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.
-
 Two angular projections were looked at in this thesis.
@@
 Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.
+Another possible extension is to integrate \emph{aRTist} into the inference.
+for example, the simulated projection could be realigned to minimise the number of positives.
+This will help eliminate sources of error due to \emph{aRTist}.
+A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.
 
-The inference could be improved if the location of the defects were known in the projection.
-This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.
+In the ABS test sample, voids in the order of millimetres were detectable using this method.
+Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V).
+This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}.
+Another problem is that because titanium products are created using a power-based method, powder may become trapped \citep{brierley2018optimized} in designed voids.
+This results in voids appearing with less contrast in the projections, making it harder to detect.
 

### 2019-09-25 reports/thesis/book.tex
Revise

@@
 %twoside for hard final copy
-\setlrmargins{4cm}{*}{*}
+\setlrmargins{4.3cm}{*}{*}
 \checkandfixthelayout
@@
 This arises from x-ray photon arrivals being a Poisson process and each photon has random energy.
-This results in a linear relationship between the mean and variance of the grey value in the projection.
+This results in a linear relationship between the mean and variance of the grey values in the projection.
 Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model.
-Instead, a gamma-distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.
+Instead, a gamma-distributed generalised linear model was fitted onto sample variance-mean data and used for variance prediction to quantify the uncertainty.
 
@@
 To summarise the thesis, Figure \ref{fig:evaluation_flowchart} shows a flowchart of the process of the experiment.
-A test sample was designed using a CAD model and was manufactured with purposefully designed voids.
+An ABS test sample, with purposefully designed voids, was created using a CAD model and manufactured using fused deposition modelling.
 Replicate x-ray projections were taken of the test sample with voids as well as a simulation of that projection without the voids using \emph{aRTist}.
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
+  \includegraphics[width=0.64\textwidth]{../figures/flowchart.pdf}
   \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
@@
 The uncertainty was predicted using the variance-mean model.
-Hypothesis testing was done on the test statistics, one for each pixel in a projection.
+Hypotheses testing was done on the test statistics, one for each pixel in a projection.
 Unfortunately, the simulation was not perfect which led to model misspecification, thus, false positives.
@@
 Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.
-Another possible extension is to integrate \emph{aRTist} into the inference.
-for example, the simulated projection could be realigned to minimise the number of positives.
+Another possible extension is to integrate \emph{aRTist} into the inference, for example, the simulated projection could be realigned to minimise the number of positives.
 This will help eliminate sources of error due to \emph{aRTist}.
@@
 
-In the ABS test sample, voids in the order of millimetres were detectable using this method.
+Voids in the order of millimetres were detectable using this method.
 Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V).
@@
 
-This thesis is a contribution to real-time quality control for additive manufacturing.
+This thesis is a contribution to real-time quality control for AM.
 A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt.
-By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of additive manufacturing.
+By using fewer projections, quality control can be faster which advances the development, and increases the scope of applications, of AM.
 

### 2019-09-25 reports/thesis/chapters/1_literatureReview.tex
Revise

@@
 It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}.
-The platform moves, and controlled by a computer, in the $xy$ plane, or left to right and front to back, to produce a layer.
+The platform moves, and controlled by a computer, in the $xy$-plane, or left to right and front to back, to produce a layer.
 The jetting head can move in the $z$-axis, or up and down, to manufacture the next layer.
@@
 X-ray projections are taken while the object rotates.
-Typically the x-ray is a cone-beam \citep{kruth2011computed}.
+Typically, the x-ray is a cone-beam \citep{kruth2011computed}.
 This is illustrated in Figure \ref{fig:literature_xct}.
@@
 The energy of the radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}.
-Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it.
+Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionising it.
 This produces a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state.
@@
 The photoelectric effect and Compton scattering cause several photons to be undetectable.
-If some of the photons avoid these processes, they are detected and their energy is left unaffected.
+If some of the photons avoid these processes, they are detected with their energy unaffected.
 
@@
 Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law.
-In general low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}.
+In general, low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}.
 This is called beam hardening.
@@
   \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_magnification.png}
-  \caption{The magnification can be adjusted by adjusting the distances between the x-ray source, the object and the x-ray detector.
+  \caption{The magnification can be tuned by adjusting the distances between the x-ray source, the object and the x-ray detector.
 Because of a finite x-ray spot size, blurry effects are produced using a magnification too large.

### 2019-09-25 reports/thesis/chapters/2_dataCollection.tex
Revise

@@
 The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
-6 voids for each diameter were designed in the CAD.
+6 voids for each diameter were designed in the CAD model.
 Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly.
@@
 They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections.
-To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.
+To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter} and a filter was used in \texttt{AbsFilter}.
 
@@
 \centering
-\begin{tabular}{l|ll}
+\begin{tabular}{l|cc}
                                                        & \multicolumn{2}{c}{Dataset name}                      \\
@@
 \end{tabular}
-\caption{Properties of the three datasets obtained for the experiment.}
+\caption{Properties of the two datasets obtained for the experiment.}
 \label{table:data_dataset}
@@
 This is concerning because systematic errors could be introduced as a result of the panel effects in the black image.
-This should not happen because, in a black image, the detector is exposed only to background radiation.
+A black image should be flat because the detector is exposed only to background radiation.
 The x-ray spot can be observed, in particular, in the white image, and this is the result of using a cone beam.
@@
 The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.
-For both the greyscale projections and the projection of the test sample, the power was varied by fixing the potential difference and varying the current of the x-ray tube.
+The power was varied by fixing the potential difference and varying the current of the x-ray tube.
 
@@
   }
-  \caption{For each pixel, a linear regression was fitted on the within projection mean versus the grey value for each greyscale projection.
+  \caption{For each pixel, a linear regression was fitted on the within projection mean versus the pixel's grey value.
 The \texttt{AbsNoFilter} dataset was used.
@@
   }
-  \caption{Left shows the profile plot of a \texttt{AbsNoFilter} black image at $(879,y)$ using various shading corrections. Right shows two curves for odd and even $y$.}
+  \caption{Left shows the profile plot of an \texttt{AbsNoFilter} black image at $(879,y)$ using various shading corrections. Right shows two curves for odd and even $y$.}
   \label{fig:data_oddEven}

### 2019-09-25 reports/thesis/chapters/3_compoundPoisson.tex
Check algebra
Revise

@@
 
-Returning back to the compound Poisson distribution with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
+Returning to the compound Poisson distribution with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
 It can be shown that the m.g.f.~is
@@
 \end{equation}
-The density was then was normalised by numerically integrating it using the trapezium rule using the 10\,000 evaluated points.
+The density was then normalised by numerically integrating it using the trapezium rule using the 10\,000 evaluated points.
 
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   \includegraphics[width=0.6\textwidth]{../figures/compoundpoisson/graphicalModel.pdf}
-  \caption{Graphical model of the grey value $X_{i,j}$ for each of the $m$ pixels in the $n$ replicate projections.
+  \caption{Graphical model of the grey value $X_{i,j}$ for each of the $N$ pixels in the $m$ replicate projections.
 $Y_{i,j}\sim\poisson(\lambda_i)$ is the photon count.
@@
 The estimators were found by optimising the joint log-likelihood.
-This was done iteratively by estimating the $Y$s given the $X$s and parameters (E step), followed by estimating the parameters given the $Y$s and $X$s (M step) until some convergence conditions were met.
+This was done iteratively by estimating the $Y$'s given the $X$'s and parameters (E step), followed by estimating the parameters given the $Y$'s and $X$'s (M step) until some convergence conditions were met.
 
@@
 \end{equation}
-Then, the conditional expectation is
+As a result, the conditional expectation is
 \begin{equation}
@@
 \end{equation}
-The expectation terms, $y_i$ and $\zeta_i$, are evaluated in the M step so that they can be used in the E step. The evaluation can be done by truncating the sum
+The expectation terms, $y_i$ and $\zeta_i$, are evaluated here so that they can be used in the M step. The evaluation can be done by truncating the sum
 \begin{equation}
@@
 \end{equation}
-where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. $\ln(W^{(r)}_y)$ can be expressed as
+where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. $\ln\left(W^{(r)}_y\right)$ can be expressed as
 \begin{equation}
@@
 \begin{equation}
-  \frac{\partial \ln(W_y^{(r)})}{\partial y} = \frac{r}{y } + \frac{\partial \ln(W_y)}{\partial y}
+  \frac{\partial }{\partial y} \ln\left(W_y^{(r)}\right) = \frac{r}{y } + \frac{\partial }{\partial y}\ln\left(W_y\right)
   \ .
@@
 \begin{equation}
-  \frac{\partial \ln(W_y^{(r)})}{\partial y} \approx \frac{\partial \ln(W_y)}{\partial y}
+  \frac{\partial }{\partial y} \ln\left(W_y^{(r)}\right)\approx \frac{\partial }{\partial y} \ln\left(W_y\right)
   \ .
@@
 \begin{multline}
-  T(\lambda,\alpha,\beta)=
+  T(\lambda,\alpha,\beta)\approx
   -n\lambda
@@
 \end{equation}
-The second-order derivatives are:
+The second-order derivatives are
 \begin{equation}
@@
   \right]
+  \ ,
   \label{eq:compoundPoisson:d2td2b}
@@
 For the $\alpha$ component, taking derivatives of the joint log-likelihood (Equation \eqref{eq:compoundPoisson_jointLogLikelihood}) obtains
-\begin{equation}
-\dfrac{\partial\ln L}{\partial\alpha} = \sum_{i=1}^n\mathbb{I}(x_i>0)
+\begin{align}
+\dfrac{\partial\ln L}{\partial\alpha} &= \sum_{i=1}^n\mathbb{I}(x_i>0)
 \left[
@@
 \right]
-\end{equation}
-\begin{equation}
-\dfrac{\partial^2\ln L}{\partial\alpha^2} = \sum_{i=1}^n\mathbb{I}(x_i>0)
+\\
+\dfrac{\partial^2\ln L}{\partial\alpha^2} &= \sum_{i=1}^n\mathbb{I}(x_i>0)
 \left[
@@
 \right] \ .
-\end{equation}
+\end{align}
 The expectation of the second-order derivative is
@@
 \begin{multline}
--\expectation\left[\dfrac{\partial^2\ln L}{\partial\alpha^2}\right]=n\left(1-\euler^{-\lambda}\right)
+-\expectation\left[\dfrac{\partial^2\ln L}{\partial\alpha^2}\right]\approx n\left(1-\euler^{-\lambda}\right)
 \\
@@
 
-For $\lambda=10$ and $\lambda=100$ case, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log-likelihood.
+For $\lambda=10$ and $\lambda=100$, the estimates of $\alpha$ and $\beta$ struggled to converge and increased/decreased without bounds without affecting the log-likelihood.
 It appeared that the EM algorithm failed for $\lambda>10$ looking at these particular examples.
@@
     }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+    \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples.
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
     }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+    \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples.
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
     }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+    \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples.
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
     }
-    \caption{EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples, repeated 10 times.
-The graphs show the log-likelihood and the estimated parameters at each EM step for each repeat of the experiment.
+    \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples.
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
 The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
@@
 
-One investigation is to look at the Newton-Raphson step in the M step, in particular the Hessian matrix $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ for high $\lambda$.
+One investigation is to look at the Newton-Raphson step in the M step, in particular, the Hessian matrix $\nabla_{\alpha,\beta}\nabla_{\alpha,\beta}\T T$ for high $\lambda$.
 The elements of the Hessian matrix can be found in Equations \eqref{eq:compoundPoisson:d2tdadb}, \eqref{eq:compoundPoisson:d2td2b} and \eqref{eq:compoundPoisson:d2td2a}.
@@
 \begin{align}
-  T(\lambda,\alpha)&=
+  T(\lambda,\alpha)&\approx
   \begin{multlined}[t]
@@
   \nonumber\\
-  &\!\begin{multlined}[b]=
+  &\!\begin{multlined}[b]\approx
     -n\lambda+
@@
 \begin{equation}
-  \frac{\partial T}{\partial \alpha} =
+  \frac{\partial T}{\partial \alpha} \approx
   \sum_{i=1}^n
@@
 \end{equation}
-and this is not $\alpha$ dependent, thus there is no solution to $\alpha$.
+and this is not $\alpha$ dependent, thus there is no solution for $\alpha$.
 

### 2019-09-25 reports/thesis/chapters/4_variancePrediction.tex
Revise

@@
 
-In this chapter, generalised linear models \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} with different link functions and polynomial features were selected using forward step-wise selection.
+In this chapter, generalised linear models \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} with different link functions and polynomial features were selected using forward stepwise selection.
 These selected models were compared using cross-validation to find the best model and verified using residual analysis.
@@
 
-The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by using a model fitted onto the sample variance-mean data.
+The aim is to model and predict the grey value variance of a pixel given the its grey value by using a model fitted onto the sample variance-mean data.
 No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_N,y_N)$ from now on, where $N$ is the area of the ROI or the size of the dataset.
@@
 The model which decreased the criterion the most was accepted.
-Adding higher and lower order polynomials to the systematic component was repeated, for example after accepting $\eta(x)=\beta_0+\beta_1 x$, the following systematic components $\eta(x)=\beta_0+\beta_1 x+\beta_2x^2$ and $\eta(x)=\beta_{-1}x^{-1}+\beta_0+\beta_1 x$ were fitted and assessed.
-The fitted parameters, $\beta_0$ and $\beta_1$ in this example, may change when adding more terms.
+Adding higher and lower order polynomials to the systematic component was repeated, for example, after accepting $\eta(x)=\beta_0+\beta_1 x$, the following systematic components $\eta(x)=\beta_0+\beta_1 x+\beta_2x^2$ and $\eta(x)=\beta_{-1}x^{-1}+\beta_0+\beta_1 x$ were fitted and assessed.
+The fitted parameters may change when adding more terms.
 This is repeated until the criterion cannot be decreased and the procedure is left with the final model.
@@
 \centering
-\begin{tabular}{cc|ccc}
+\begin{tabular}{ll|ccc}
 \multicolumn{2}{c|}{Identity Link}& null & bw & linear \\ \hline
@@
 \caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsNoFilter} at \ang{30}.
-The columns of the table represent different shading corrections used on the projections.
+The columns of the table represent different shading corrections.
 Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
@@
 \caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsNoFilter} at \ang{120}.
-The columns of the table represent different shading corrections used on the projections.
+The columns of the table represent different shading corrections.
 Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
@@
 \caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsFilter} at \ang{30}.
-The columns of the table represent different shading corrections used on the projections.
+The columns of the table represent different shading corrections.
 Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
@@
 \caption{Forward stepwise selection was used to find suitable polynomial features when fitting a gamma GLM onto the sample variance-mean data from the projections in \texttt{AbsFilter} at \ang{120}.
-The columns of the table represent different shading corrections used on the projections.
+The columns of the table represent different shading corrections.
 Forward stepwise selection was repeated 10 times by bootstrapping the replicate projections.
@@
 The models selected are quite simple and all have two features.
-Different shading correction or different criteria had no effect on the selected model.
+Different shading corrections or different criteria had no effect on the selected model.
 The method was quite robust to the variation introduced to the dataset when repeating the experiment because all 10 repeats consistently selected the same model.
@@
 The forward stepwise selection may not picked this up because there were a lot of low grey values, causing a leverage towards these low grey values.
-As a result, the inflection did not stand out to the method.
+As a result, the inflection did not stood out to the method.
 
@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction.
-The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.
+The colour scales are in units of $\log\SI{}{\adu^{-3}}$.}
     \label{fig:meanVar_varMeanExample_AbsNoFilter}
@@
     \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction.
-The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.}
+The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.
+The colour scales are in units of $\log\SI{}{\adu^{-3}}$.}
     \label{fig:meanVar_varMeanExample_AbsFilter}
@@
 Cross-validation assesses the model to make predictions on data it has not seen before.
-This was done by randomly splitting the $m$ data points into two disjoint sets, the training set and the test set.
-It was chosen that the training and test set are of the same size.
+This was done by randomly splitting the $N$ data points into two disjoint sets, the training set and the test set $\tau$.
+It was chosen that the training and test set are of the same size $N_\tau$.
 The model was fitted onto the training set.
@@
 
-The mean scaled deviance was used to assess the performance of variance prediction. The deviance is defined to be
+The mean scaled deviance was used to assess the performance of variance prediction of the test set. The deviance is defined to be
 \begin{equation}
   D = 2\left(
-    \ln L_\mathrm{s} - \ln L
+    \ln L_\mathrm{s} - \ln L_\tau
   \right)
 \end{equation}
-where $L$ and $L_\mathrm{s}$ are the likelihood and saturated likelihood respectively.  The saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ in the likelihood so that
+where
 \begin{equation}
-  \ln L_\mathrm{s} = \sum_{i=1}^N \left[
+\ln L_\tau = \sum_{i\in\tau} \left[
+    \alpha\ln\alpha
+    -\ln\Gamma(\alpha)
+    -\alpha\ln \widehat{y}_i
+    +(\alpha-1)\ln y_i
+    -\frac{\alpha y_i}{\widehat{y}_i}
+  \right]
+\end{equation}
+is the log-likelihood of the test set given the fitted model and $\ln L_\mathrm{s}$ is the saturated likelihood. This is obtained by replacing all $\widehat{y}_i$ with $y_i$ in $\ln L_\tau$ so that
+\begin{equation}
+  \ln L_\mathrm{s} = \sum_{i\in\tau}\left[
     \alpha\ln\alpha
@@
   D = 2\alpha
-  \sum_{i=1}^N\left[
+  \sum_{i\in\tau}\left[
       \dfrac{
@@
 \end{equation}
-The mean scaled deviance is obtained by removing the factor of $\alpha$ and dividing by $N$ to get
+The mean scaled deviance is obtained by removing the factor of $\alpha$ and dividing by $N_\tau$ to get
 \begin{equation}
-    D_\mathrm{s} = \dfrac{2}{N}
-    \sum_{i=1}^N\left[
+    D_\mathrm{s} = \dfrac{2}{N_\tau}
+    \sum_{i\in\tau}\left[
         \dfrac{
@@
 
-Assuming the model is correct, it is given that $D\sim\chi_{N-k}^2$ which implies that for large $N$,
+Assuming the model is correct, it is given that $D\sim\chi_{N_\tau-k}^2$ which implies that for large $N_\tau$,
 \begin{equation}
@@
 \begin{equation}
-\variance\left[D_\mathrm{s}\right] = \dfrac{2}{\alpha^2 N} \ .
+\variance\left[D_\mathrm{s}\right] = \dfrac{2}{\alpha^2 N_\tau} \ .
 \end{equation}
@@
 Cross validation was performed on the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} with various shading corrections.
-The models selected from forward step-wise selection in the previous section were assessed.
+The models selected from forward stepwise selection in the previous section were assessed.
 They are ${y}(x)=\beta_0+\beta_1 x$ and ${y}(x)=\beta_{-1}x^{-1}+\beta_0$ using the identity link and ${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ using the canonical link.
-The analysis was repeated 100 times by using a random permutation with replacement of the replicated projections to obtain a different sample variance-mean data which introduces some variation to the data \citep{efron1979bootstrap}.
+The analysis was repeated 100 times by using a random permutation with replacement of the replicate projections to obtain a different sample variance-mean data which introduced some variation to the data \citep{efron1979bootstrap}.
 
@@
   \caption{Test mean scaled deviance from predicting variances in a test set using a GLM fitted onto a training set.
-The box plot represent the 100 repeats of the analysis by bootstrapping the replicate projections.}
+The different colours represent different shading corrections.
+The boxplot represent the 100 repeats of the analysis by bootstrapping the replicate projections.}
   \label{fig:meanVar_varMeanCv}
@@
 The performances of the three candidate models were very similar.
-One exception is the model ${y}(x)=\beta_{-1}x^{-1}+\beta_0$ fitted onto the \texttt{AbsNoFilter} dataset, the mean scaled deviance was significantly larger and this is expected from a model not favoured in the forward step-wise selection in the previous section.
+One exception is the model ${y}(x)=\beta_{-1}x^{-1}+\beta_0$ fitted onto the \texttt{AbsNoFilter} dataset because the mean scaled deviance was significantly larger.
+This is expected from a model not favoured in the forward stepwise selection in the previous section.
 
@@
 Due to the gamma GLM, higher grey values typically have bigger residuals in magnitude.
-A predicted residual interval is included in the histogram to aid judging the residuals.
+A prediction residual interval is included in the histogram to aid judging the residuals.
 This interval was acquired by obtaining the prediction interval and subtracting it from the fit.
@@
 The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicate projections.
-The dashed red line shows the 68\% confidence interval of the predicted residual.}
+The dashed red line shows the 68\% prediction residual interval.
+The colour scales are in units of $\log\SI{}{\adu^{-3}}$.}
   \label{fig:meanVar_residualGreyvalue}
@@
 The residual plots are shown in Figure \ref{fig:meanVar_residualGreyvalue}.
-The residuals are all sensible and increased in magnitude with the grey value which is captured by the predicted residual interval.
+The residuals are all sensible and increased in magnitude with the grey value which is captured by the prediction residual interval.
 The inflection in \texttt{AbsNoFilter} at \ang{120}, as discussed previously, can be seen more clearly here.
@@
   \caption{Absolute value residuals from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicate projections.
-Highlighted in a red box is an example of an inflection.}
+Highlighted in a dashed red box is an example of an inflection.
+The colour scales are in units of \SI{}{\adu^2}.}
   \label{fig:meanVar_spatialResidual}
@@
 In the forward stepwise selection, \texttt{AbsNoFilter} consistently selected the linear model, given the identity link function.
-\texttt{AbsFilter} did not select the linear model but in terms of cross-validation prediction performance, the linear model was just as good as the other models.
+\texttt{AbsFilter} did not select the linear model but in terms of cross-validation, the linear model was just as good as the other models.
 

### 2019-09-25 reports/thesis/chapters/5_inference.tex
Revise

@@
 
-A pixel by pixel hypothesis test was proposed to do defect detection. The test statistic, for the pixel located at $(x,y)$, is
+A pixel by pixel hypothesis test was proposed to do defect detection.
+Beforehand, linear shading correction was applied to the projections.
+The \emph{aRTist} projections were shading corrected using the simulated greyscale projections.
+The test statistic, for the pixel located at $(x,y)$, is
 \begin{equation}
@@
 \emph{aRTist} was used to create a simulation of that projection but as if the voids were not there.
-Thus the method should pick these voids up.
+Thus, the method should pick these voids up.
 
@@
 This proposed method for defect detection failed because too many false positives were detected.
-These false positives appear to have some structure, for example, clustering in the corners or on surfaces.
+These false positives appeared to have some structure, for example, clustering in the corners or on surfaces.
 Also, false negatives were detected because not all of the defects were detected.
@@
 }
-  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution.
+  \caption{a) The histogram of the test statistics, from the \texttt{AbsFilter} projection at \ang{120}, is compared with the standard Normal distribution.
 The standard Normal distribution is known as the null distribution in this scenario.
 b) The $p$-values are ordered and plotted.
-The critical region corresponds to controlling the false discovery rate at 5\% level using the \cite{benjamini1995controlling} procedure.
+The critical region corresponds to controlling the false discovery rate at the 5\% level using the \cite{benjamini1995controlling} procedure.
 The dotted line shows the result if the $p$-values were uniformly distributed.}
@@
 This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}.
-This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}.
+This method does control the per-comparison error rate (PCER) \citep{benjamini1995controlling}.
 PCER is the proportion of false positives out of all tests.
@@
   \centering
-  \begin{tabular}{c|c|c|c}
+  \begin{tabular}{l|cc|c}
     &Negative&Positive&Total\\\hline
@@
     \centering
-    \begin{tabular}{c|c}
+    \begin{tabular}{l|l}
         Correction&Controls for\\\hline
@@
 The distribution of the test statistics appeared Normal but not centred at zero.
-By using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$ to 2 decimal places, almost half of the pixels were tested positive.
+By using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$ to 2 decimal places, almost half of the pixels were tested positive at the 5\% FDR level.
 It is questionable whether such many positive results are sensible, in particular, in an area where defects were not expected.
@@
       \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
-      \caption{Histogram of test in sub-image}
-    \end{subfigure}
-    }
-    \caption{The resulting $z$ image is shown in a).
+      \caption{Histogram}
+    \end{subfigure}
+    }
+    \caption{The resulting test statistics for the \texttt{AbsFilter} projection at \ang{120} are shown in a).
 A $\SI{200}{\pixel}\times\SI{200}{\pixel}$ sub-image was taken shown by the dashed lines.
@@
 
-In practice $\mu_0$ and $\sigma_0$ are unknown.
+In practice, $\mu_0$ and $\sigma_0$ are unknown.
 The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate.
@@
 
-Returning back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
+Returning to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}.
 The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}.
@@
   \includegraphics[width=\subSize]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
-  \caption{The density of the test statistics was estimated using a kernel density estimate.
-The dot dash lines show the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
+  \caption{The density of the test statistics, from Figure \ref{fig:inference_inferenceSubsample1_histogram}, was estimated using a kernel density estimate.
+The dot dashed line shows the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
   \label{fig:inference_inferenceSubsample1_densityEstimate}
@@
 and were used in the BH procedure.
-The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$.
+The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$ at the 5\% FDR level.
 In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places.
@@
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullHistogram.eps}
-        \caption{Histogram of $z$}
+        \caption{Histogram}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_subimagePositive.eps}
-        \caption{$z$ from the sub-image}
+        \caption{Sub-image}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullHistogram.eps}
-        \caption{Histogram of $z$}
+        \caption{Histogram}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullPValues.eps}
-        \caption{$p$ values}
-    \end{subfigure}
-    }
-    \caption{The resulting $z$ image is shown in a).
+        \caption{$p$-values}
+    \end{subfigure}
+    }
+    \caption{The resulting test statistics for the \texttt{AbsFilter} projection at \ang{120} are shown in a).
 A $\SI{200}{\pixel}\times\SI{200}{\pixel}$ sub-image was taken shown by the dashed lines.
-The empirical null was used to test pixels, positive pixels are shown in red in b).
-The histogram of the test statistics are shown in c) along with the critical region.
-The normalised $p$-values are shown in d).
+Positive pixels are shown in red in b).
+The histogram of the test statistics in the sub-image are shown in c) along with the critical region.
+The $p$-values are shown in d).
 The critical regions were adjusted using the empirical null and correspond to the 5\% FDR level.}
@@
 The BH procedure was conducted using the normalised $p$-values.
-$\inputNumber{../figures/inference/inferenceSubsample2_nPositive.txt}$ pixels were tested positive.
+$\inputNumber{../figures/inference/inferenceSubsample2_nPositive.txt}$ pixels were tested positive at the 5\% FDR level.
 The majority of the positive pixels were found to be clustered together which highlighted the defect.
@@
   \end{subfigure}
-  \caption{Median squared error of the estimates of the empirical null parameters from 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
+  \caption{Median squared error of the estimates of the empirical null parameters over 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
   \label{fig:inference_BandwidthSelection_error}
@@
     \end{subfigure}
-    \caption{Median value of $\widehat{\sigma}_0$ from 100 repeats of $n$ simulated standard Normal data. The true value is $\sigma_0=1$ which is represented by a horizontal plane.}
+    \caption{Median value of $\widehat{\sigma}_0$ over 100 repeats of $n$ simulated standard Normal data. The true value is $\sigma_0=1$ which is represented by a horizontal plane.}
     \label{fig:inference_BandwidthSelection_error3}
@@
 The experiment was repeated by simulating the standard Normal random variables again.
-The boxplots represent the variation of the errors from the 100 repeats.
+The boxplots represent the 100 repeats.
 The red dashed line shows the bandwidth which minimised the fitted spline.}
@@
   \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
-  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experiment. The dotted lines shows the 68\% prediction interval.}
+  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experiment. The dashed lines shows the 68\% prediction interval.}
   \label{fig:inference_BandwidthSelection2_ruleOfThumb}
@@
   \centering
-  \begin{tabular}{l|l}
+  \begin{tabular}{l|c}
            &Estimate \\ \hline
@@
 
-Various estimates of central tendency and dispersion were compared with estimates of the null mean and null standard deviation.
+Various estimates of central tendency and dispersion were compared with the empirical null mean and empirical null standard deviation.
 The empirical sampling distribution of these estimators was observed to look for properties such as bias, variance and robustness.
@@
 The results are shown in Figures \ref{fig:inference_NullIidMean} and \ref{fig:inference_NullIidStd}.
-The empirical null mean and empirical null standard deviation estimations both suffered from high variance, much higher than typical robust estimators such as the median and IQR.
+The empirical null mean and empirical null standard deviation both suffered from high variance, much higher than typical robust estimators such as the median and IQR.
 
@@
   \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables.
-The boxplots represent the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
+The boxplots represent the sampling distributions over 100 estimates.
+The dashed lines show the 95\% confidence interval for the sample mean.}
   \label{fig:inference_NullIidMean}
@@
         \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
-        \caption{Empirical null std.}
+        \caption{Empirical null std}
       \end{subfigure}
@@
   \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables.
-The boxplots represent the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
+The boxplots represent the sampling distributions over 100 estimates.
+The dashed lines show the 95\% confidence interval for the sample variance.}
   \label{fig:inference_NullIidStd}
@@
 The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-The boxplots represent the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample mean.}
+The boxplots represent the sampling distributions over 100 estimates.
+The dashed lines show the 95\% confidence interval for the sample mean.}
   \label{fig:inference_NullIidMixtureMean}
@@
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
-        \caption{Empirical null std.}
+        \caption{Empirical null std}
       \end{subfigure}
@@
 The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$.
-The boxplots represent the sampling distributions from 100 repeats.
-The dotted lines show the 95\% confidence interval for the sample variance.}
+The boxplots represent the sampling distributions over 100 estimates.
+The dashed lines show the 95\% confidence interval for the sample variance.}
   \label{fig:inference_NullIidMixtureStd}
@@
 The problem was that the empirical distribution of all of the test statistics looked like it did not come from a Normal distribution.
-It appeared that the test statistics varied spatially, suggesting the empirical null varied spatially as well.
-To account for the spatial variability of the null parameters, one possible extension is to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
+It appeared that the test statistics varied spatially, suggesting that the empirical null varied spatially as well.
+To account for the spatial variability of the null parameters, one possible extension to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately.
 There are problems with this though.
@@
 The empirical null filter extends the empirical null to images.
-The parameters of the null distribution varies spatially, slowly and smoothly in 2D space.
+The parameters of the null distribution varies spatially, slowly and smoothly.
 Let the test statistic of the pixel at position $(x,y)$ be
@@
   \end{subfigure}
-  \caption{The resulting test statistics are shown in a).
+  \caption{The resulting test statistics for the \texttt{AbsFilter} projection at \ang{120} are shown in a).
 The density estimate of the statistics is shown in b).
@@
     }
-    \caption{Empirical null filter with $r=\SI{5}{\pixel}$ on the sample image \texttt{bridge.gif}.}
+    \caption{The empirical null filter, with kernel radius $r=\SI{5}{\pixel}$, was used on the sample image \texttt{bridge.gif}.}
     \label{fig:inference_fijiBridgeFilter}
@@
     }
-    \caption{Various averaging filters, with kernel radius $r=\SI{5}{\pixel}$, were used on the sample image \texttt{bridge.gif}}
+    \caption{Various averaging filters, with kernel radius $r=\SI{5}{\pixel}$, were used on the sample image \texttt{bridge.gif}.}
     \label{fig:inference_fijiMean}
@@
     }
-    \caption{Various dispersion filters, with kernel radius $r=\SI{5}{\pixel}$, were on the sample image \texttt{bridge.gif}.}
+    \caption{Various dispersion filters, with kernel radius $r=\SI{5}{\pixel}$, were used on the sample image \texttt{bridge.gif}.}
     \label{fig:inference_fijiStd}
@@
 
-When using the empirical null filter in \emph{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
+When using the empirical null filter in \emph{ImageJ} or \emph{Fiji}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}.
 The user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius.
@@
 
-Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design has already been done.
-\texttt{RankFilters} contain implementations of filters such as the mean filter and median filter.
+Line filtering was done from left to right.
+At the start on the far left, an initial value of the median over the pixels in the kernel was used.
+Also, various initial values were randomly tried out until a requested number of valid solutions were found.
+For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial value.
+This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
 The implementation uses multiple threads, each thread filters a row in parallel.
@@
 
-Line filtering was done from left to right.
-At the start on the far left, an initial value of the median over the pixels in the kernel was used.
-Also, various initial values were randomly tried out until a requested number of valid solutions were found.
-For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial value.
-This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.
-
 When filtering arbitrary images such as \texttt{bridge.gif}, a few computational considerations were needed.
@@
 
-\subsection{All-null Experiment}
+\subsection{Filtering an Image with No Defects}
 
@@
 
-\emph{Contamination} is defined as some smooth and slowly varying function added and/or multiplied to an image.
+Contamination is defined as some smooth and slowly varying function added and/or multiplied to an image.
 Conducting hypotheses testing on a contaminated Gaussian image may cause errors if the null distributions were incorrectly specified as standard Normal.
@@
   \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image before and after filtering with kernel radius \SI{20}{\pixel}.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 Also shown are the empirical null mean and empirical null standard deviation.}
@@
 In b), the Gaussian image was contaminated before filtering.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The $p$-values were obtained from the images in Figures \ref{fig:inference_allNullGaussianScript_afterFilter} and \ref{fig:inference_allNullPlaneScript_afterFilter}.
+The critical region corresponds to the 5\% FDR level.
 The dotted lines shows the $p$-values if they were uniformly distributed.}
@@
   \centering
-  \begin{tabular}{c|c|c}
-    Filters&Null mean&Null Standard deviation\\\hline
+  \begin{tabular}{l|l|l}
+    Filters&Null mean&Null standard deviation\\\hline
     MAD mode null&Mode&MAD around the mode $\times1.483$\\
@@
   }
-  \caption{The within image sample \emph{mean} of the test statistics in a filtered Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \caption{The within image sample mean of a filtered Gaussian image of size $\SI{256}{\pixel}\times\SI{256}{\pixel}$.
+The boxplots summarise the 100 repeated simulations of the image.
+The dashed lines show the 95\% confidence interval using standard tests and assuming independence.}
   \label{fig:inference_AllNullGaussian_mean}
@@
   }
-  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \caption{The within image sample standard deviation of a filtered Gaussian image of size $\SI{256}{\pixel}\times\SI{256}{\pixel}$.
+The boxplots summarise the 100 repeated simulations of the image.
+The dashed lines show the 95\% confidence interval using standard tests and assuming independence.}
   \label{fig:inference_AllNullGaussian_var}
@@
   }
-  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \caption{The within image sample kurtosis of a filtered Gaussian image of size $\SI{256}{\pixel}\times\SI{256}{\pixel}$.
+The boxplots summarise the 100 repeated simulations of the image.
+The dashed lines show the 95\% confidence interval using standard tests and assuming independence.}
   \label{fig:inference_AllNullGaussian_kurtosis}
@@
   }
-  \caption{The within image sample \emph{mean} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \caption{The within image sample mean of a filtered contaminated Gaussian image of size $\SI{256}{\pixel}\times\SI{256}{\pixel}$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The boxplots summarise the 100 repeated simulations of the image.
+The dashed lines show the 95\% confidence interval using standard tests and assuming independence.}
   \label{fig:inference_AllNullPlane_mean}
@@
   }
-  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \caption{The within image sample standard deviation of a filtered contaminated Gaussian image of size $\SI{256}{\pixel}\times\SI{256}{\pixel}$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The boxplots summarise the 100 repeated simulations of the image.
+The dashed lines show the 95\% confidence interval using standard tests and assuming independence.}
   \label{fig:inference_AllNullPlane_var}
@@
   }
-  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$.
-The box plots summarise the 100 repeats of the experiment.
-The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
+  \caption{The within image sample kurtosis of a filtered contaminated Gaussian image of size $\SI{256}{\pixel}\times\SI{256}{\pixel}$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The boxplots summarise the 100 repeated simulations of the image.
+The dashed lines show the 95\% confidence interval using standard tests and assuming independence.}
   \label{fig:inference_AllNullPlane_kurtosis}
@@
 The results for the filtered images are shown in Figures \ref{fig:inference_AllNullGaussian_mean}, \ref{fig:inference_AllNullGaussian_var} and \ref{fig:inference_AllNullGaussian_kurtosis}.
-For the filtered \emph{contaminated} images, they are in Figures \ref{fig:inference_AllNullPlane_mean}, \ref{fig:inference_AllNullPlane_var} and \ref{fig:inference_AllNullPlane_kurtosis}.
+For the filtered contaminated images, they are in Figures \ref{fig:inference_AllNullPlane_mean}, \ref{fig:inference_AllNullPlane_var} and \ref{fig:inference_AllNullPlane_kurtosis}.
 The filtered test statistic means did agree with zero as expected, showing that the filters centred the statistics when normalising.
@@
 This is shown in Figure \ref{fig:inference_AllNullPlane_var}.
-As discussed before, the kernel captured the variation due to the contamination and this added bias to the estimation of dispersion.
+As discussed before, the kernel captured the variation due to the contamination and this added bias to the estimation of the null standard deviation.
 
@@
 The empirical null filter was tested to see if it can assist in detecting simulated defects from an image with/without contamination.
-A \emph{defect} assign pixels to have a value not distributed under the null distribution, but instead, under an alternative, or non-null, distribution.
+A defect assign pixels to have a value not distributed under the null distribution, but instead, under an alternative, or non-null, distribution.
 For example, suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect assign certain pixels to have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
 
-To recap, \emph{contamination} is the result of a linear transform of the test statistics $Z_{x,y}$.
+To recap, contamination is the result of a linear transform of the test statistics $Z_{x,y}$.
 For example, in this experiment, the image was multiplied by 2 and a gradient was added to it.
@@
     }
-  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with \emph{speckle} defect is shown in a).
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with speckle defect is shown in a).
 The image was contaminated in b) and then filtered with kernel radius \SI{20}{\pixel} in c).
@@
 The speckle defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
@@
     }
-  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a \emph{line} defect is shown in a).
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a line defect is shown in a).
 The image was contaminated in b) and then filtered with kernel radius \SI{20}{\pixel} in c).
@@
 The line defect is \SI{5}{\pixel} thick.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
@@
     }
-  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a \emph{square} defect is shown in a).
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a square defect is shown in a).
 The image was contaminated in b) and then filtered with kernel radius \SI{20}{\pixel} in c).
@@
 The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
@@
     }
-  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a \emph{square} defect is shown in a).
+  \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ Gaussian image with a square defect is shown in a).
 The image was contaminated in b) and then filtered with kernel radius \SI{40}{\pixel} in c).
@@
   \caption{A $\SI{256}{\pixel} \times \SI{256}{\pixel}$ contamined defected Gaussian image was filtered using the empirical null filter with kernel radius $r$.
-Shown are the $p$-values converted from the filtered image.
+Shown are the $p$-values converted from the filtered images.
 Non-null pixels have the distribution $\normal(3,1)$.
@@
 The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
-The critical region corresponds to the 5\% FDR level.}
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The critical region corresponds to the 5\% FDR level.
+The dotted lines shows the $p$-values if they were uniformly distributed.}
   \label{fig:inference_defectExamplePValue}
@@
 False negatives are common but this is inevitable to control for the FDR.
-The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, tested no pixels for defects.
+The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, tested few pixels for defects.
 This, again, emphasise the importance of a good kernel radius.
@@
   \caption{ROC curves for various defected $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian images.
-The upper/lower dashed line show the resulting ROC curve when testing on an image without/with contamination respectively.
+The upper/lower dot dashed lines show the resulting ROC curve when testing on an image without/with contamination respectively.
 The different curves are the resulting ROC curves after filtering a contaminated image.
@@
 Defected pixels have the distribution $\normal(3,1)$.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
   \label{fig:inference_defectSimulationRoc}
@@
 The ROC curves consider all thresholds or specificities used in the hypotheses testing.
-In the previous experiment, it was found the variance of the test statistics were different before and after filtering.
+In the previous experiment, it was found that the variance of the test statistics were different before and after filtering.
 As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
@@
   \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$.
-In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
-In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination.
+In a), the upper/lower dot dashed lines shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
+In b), c) and d), the dashed lines show the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination.
 The filter used a kernel radius of \SI{20}{\pixel}.
@@
 The salt defect has density $\pi_1 = 0.1$.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
-The boxplot summarise the 100 repeats of the experiment.}
+The boxplots summarise the 100 repeated simulations of the image.}
   \label{fig:inference_DefectSimulationDust}
@@
     }
-  \caption{AUC and various errors obtained when conducting hypotheses test on the filtered contaminated line defected Gaussian image, of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$, using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypotheses test was done on the uncontaminated image.
+  \caption{AUC and various errors obtained when conducting hypotheses testing on a filtered contaminated line defected Gaussian image, of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$, using various kernel radiuses.
+The dashed lines show the resulting 95\% empirical confidence interval when the hypotheses testing was done on the uncontaminated defected image.
 Defected pixels have the distribution $\normal(3,1)$.
 The line defect is \SI{5}{\pixel} thick.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
-The boxplot summarise the 100 repeats of the experiment.}
+The boxplots summarise the 100 repeated simulations of the image.}
   \label{fig:inference_Experiment_DefectRadiusLine}
@@
     }
-  \caption{AUC and various errors obtained when conducting hypotheses test on the filtered contaminated square defected Gaussian image, of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$, using various kernel radiuses.
-The dashed lines show the resulting 95\% empirical confidence interval when the hypotheses test was done on the uncontaminated image.
+  \caption{AUC and various errors obtained when conducting hypotheses testing on a filtered contaminated square defected Gaussian image, of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$, using various kernel radiuses.
+The dashed lines show the resulting 95\% empirical confidence interval when the hypotheses testing was done on the uncontaminated defected image.
 Defected pixels have the distribution $\normal(3,1)$.
 The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ pixels in size.
-The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
+The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
 The test was done at the 5\% FDR level.
-The boxplot summarise the 100 repeats of the experiment.}
+The boxplots summarise the 100 repeated simulations of the image.}
   \label{fig:inference_Experiment_DefectRadiusSquare}
@@
 
-An experiment was conducted where the contaminated defected image was filtered using various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
-Hypotheses testing was done on the uncontaminated and filtered contaminated image.
-The AUC and various errors were recorded, this was repeated 100 times.
+An experiment was conducted where a contaminated defected Gaussian image, of size $\SI{256}{\pixel}\times\SI{256}{\pixel}$, was filtered using various kernel radiuses for a fixed alternative distribution $\normal(3,1)$.
+Hypotheses testing was done on the uncontaminated defected and filtered contaminated defected images.
+The AUC and various errors were recorded.
+This was repeated 100 times by simulating the image again.
 The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1\,000 trapeziums.
-The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.
+The results of the uncontaminated defected image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.
 Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.
@@
     }
-  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection.
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} projection at \ang{120}.
 A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used.
@@
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
+c) and d) Empirical null mean and empirical null standard deviation.}
   \label{fig:inference_AbsFilterDeg120_inference_radius1}
@@
     }
-  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection.
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} projection at \ang{120}.
 A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used.
@@
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and deviation.}
+c) and d) Empirical null mean and empirical null standard deviation.}
   \label{fig:inference_AbsFilterDeg120_inference_radius4}
@@
 False positives were detected on the bottom right of the test sample.
-When placing the corner on the bottom right corner, the null distribution is bimodal because each face has a different distribution.
+When placing the kernel on the bottom right corner, the null distribution is bimodal because each face has a different distribution.
 Figure \ref{fig:inference_cornerSelect} illustrates this.
@@
     }
-  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently.
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} projection at \ang{120} and on each segment independently.
 A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used.
@@
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and standard deviation.}
+c) and d) Empirical null mean and empirical null standard deviation.}
   \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
@@
     }
-  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently.
+  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} projection at \ang{30} and on each segment independently.
 A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used.
@@
 b) $p$-values on the log scale.
-c) and d) Empirical null mean and standard deviation.}
+c) and d) Empirical null mean and empirical null standard deviation.}
   \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
@@
 
-The assessment of the inference could be improved if the location of the defects were known in the projection.
+The assessment of the inference could be improved if the location of the defects were known in the projections.
 This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.

### 2019-09-25 reports/thesis/chapters/5_inference.tex
Revise and used proofreader

@@
   \caption{The density of the test statistics, from Figure \ref{fig:inference_inferenceSubsample1_histogram}, was estimated using a kernel density estimate.
-The dot dashed line shows the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
+The dot-dashed line shows the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
   \label{fig:inference_inferenceSubsample1_densityEstimate}
@@
   \end{subfigure}
-  \caption{Median squared error of the estimates of the empirical null parameters over 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
+  \caption{The median squared error of the estimates of the empirical null parameters over 100 repeats of $n$ simulated standard Normal data.
+Lines represent the rule of thumb for various values of $b$.}
   \label{fig:inference_BandwidthSelection_error}
@@
   \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
-  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experiment. The dashed lines shows the 68\% prediction interval.}
+  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experiment. The dashed lines show the 68\% prediction interval.}
   \label{fig:inference_BandwidthSelection2_ruleOfThumb}
@@
   \end{tabular}
-  \caption{Estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
+  \caption{The estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
   \label{table:inference_BandwidthSelection2_ruleOfThumb}
@@
     \includegraphics[width=\textwidth]{../figures/inference/fiji/gui.png}
-    \caption{Graphical user interface of the empirical null filter in \emph{Fiji}.
+    \caption{The graphical user interface of the empirical null filter in \emph{Fiji}.
 The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate.
@@
 The empirical null filter was tested to see if it can assist in detecting simulated defects from an image with/without contamination.
-A defect assign pixels to have a value not distributed under the null distribution, but instead, under an alternative, or non-null, distribution.
+A defect assigns pixels to have a value not distributed under the null distribution, but instead, under an alternative, or non-null, distribution.
 For example, suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect assign certain pixels to have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.
@@
   \caption{ROC curves for various defected $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian images.
-The upper/lower dot dashed lines show the resulting ROC curve when testing on an image without/with contamination respectively.
+The upper/lower dot-dashed lines show the resulting ROC curve when testing on an image without/with contamination respectively.
 The different curves are the resulting ROC curves after filtering a contaminated image.
@@
 The ROC curves consider all thresholds or specificities used in the hypotheses testing.
-In the previous experiment, it was found that the variance of the test statistics were different before and after filtering.
+In the previous experiment, it was found that the variance of the test statistics was different before and after filtering.
 As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.
@@
   \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$.
-In a), the upper/lower dot dashed lines shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
+In a), the upper/lower dot-dashed lines shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
 In b), c) and d), the dashed lines show the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination.
@@
   }
-  \caption{A section of the bottom right of a unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
+  \caption{A section of the bottom right of an unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
   \label{fig:inference_cornerSelect}

### 2019-09-25 reports/thesis/book.tex

@@
 This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}.
-Another problem is that because titanium products are created using a power-based method, powder may become trapped \citep{brierley2018optimized} in designed voids.
+Another problem is that because titanium products are created using a power-based method, the powder may become trapped \citep{brierley2018optimized} in designed voids.
 This results in voids appearing with less contrast in the projections, making it harder to detect.
@@
 A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt.
-By using fewer projections, quality control can be faster which advances the development, and increases the scope of applications, of AM.
+By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.
 

### 2019-09-25 reports/thesis/chapters/1_literatureReview.tex

@@
   \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
-  \caption{An example of a CAD model (left) converted to a STL file (right). Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
+  \caption{An example of a CAD model (left) converted to an STL file (right). Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
 Clearance Center, Inc.}
@@
   \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
-  \caption{A reconstruction when scanning three aligned balls using a different number angular projections.
+  \caption{A reconstruction when scanning three aligned balls using a different number of angular projections.
 Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}

### 2019-09-25 reports/thesis/chapters/2_dataCollection.tex
Final revise

@@
 
-The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids.
+The test sample is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids.
 The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}.
@@
   \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
-  \caption{CAD model of the test sample; the scale shown is approximate.}
+  \caption{The CAD model of the test sample. The scale is approximate.}
   \label{fig:inference_testObject}
@@
 
-The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test object made of plastic (acrylonitrile butadiene styrene or ABS).
+The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test sample made of plastic (acrylonitrile butadiene styrene or ABS).
 The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.
@@
 The target material in the x-ray tube was tungsten.
+A \SI{0.35}{\milli\metre} copper filter was used to tackle beam hardening.
 The detector was made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produced a 16-bit projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}.
@@
 
-Greyscale projections were taken in addition to the projection of the test object.
+Greyscale projections were taken in addition to the projection of the test sample.
 These are projections with nothing between the source and the detector, obtained with the x-ray tube at different powers.
@@
 
-A \SI{0.35}{\milli\metre} copper filter was used to tackle beam hardening.
-
-\emph{aRTist} was used to simulate the test object projection and all greyscale projections except for the black image.
+\emph{aRTist} was used to simulate the test sample projection and all greyscale projections except for the black image.
 The black image was simulated by producing a uniform image with a grey value the mean over the obtained black image.
@@
                                                        & \texttt{AbsNoFilter} & \texttt{AbsFilter}             \\ \hline
-potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             \\
-power (\SI{}{\watt})                                   & 36                   & 20                             \\
+potential difference (\SI{}{\kilo\volt}) of x-ray tube & 80                   & 80                             \\
+power (\SI{}{\watt}) of x-ray tube                     & 36                   & 20                             \\
 filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper \\
@@
 Shading correction is done by using the greyscale projections and examining how the grey values respond to different powers for different pixels.
-For example, the black and white image can be used to correct the projections using
+For example, the black and white images can be used to correct the projections using
 \begin{equation}
@@
 Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$.
-The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.
+The black and white images can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.
 The power was varied by fixing the potential difference and varying the current of the x-ray tube.
@@
 
-A variation of the shading correction which uses only the black and white image such that $\mathbb{P}=\left\{0, P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.
+A variation of the shading correction which uses only the black and white images such that $\mathbb{P}=\left\{0, P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.
 
@@
   }
-  \caption{Grey values in the greyscale projections before and after shading correction using the \texttt{AbsNoFilter} dataset. The box plot summarise all $2\,000\times2\,000$ pixels in a projection.}
+  \caption{Grey values in the greyscale projections before and after shading correction using the \texttt{AbsNoFilter} dataset. The boxplots summarise all $2\,000\times2\,000$ pixels in a projection.}
   \label{fig:data_shadingCorrectionExample_greyvaluePower}
@@
 
-The BW shading corrected black and white image appeared uniform but there is some structure in the linear shading correction.
+The BW shading corrected black and white images appeared uniform but there is some structure in the linear shading correction.
 By giving linear shading correction various greyscale projections, it attempts to generalise to a range of powers, thus may struggle at shading correcting the black and white images.
@@
 The experiment was repeated by reselecting the greyscale projections used for training the shading correction.
-The box plots represent the 100 repeats.
+The boxplots represent the 100 repeats.
 The \texttt{AbsNoFilter} dataset was used here.}
@@
 The experiment was repeated by reselecting the greyscale projections used for training the shading correction.
-The box plots represent the 100 repeats.
+The boxplots represent the 100 repeats.
 The \texttt{AbsFilter} dataset was used here.}

### 2019-09-25 reports/thesis/chapters/3_compoundPoisson.tex
Revise and used proofreader
Final revise

@@
 
-Returning to the compound Poisson distribution with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
+Returning to the compound Poisson distribution with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.)~of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$.
 It can be shown that the m.g.f.~is
@@
 \end{equation}
-obtains a M step estimator for $\lambda$. Taking the second derivative with respect to $\lambda$
+obtains a M step estimator for $\lambda$. Taking the second-order derivative with respect to $\lambda$
 \begin{equation}
@@
 Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second-order can be obtained.
-For the first-order derivatives, these are:
+For the first-order derivatives, these are
 \begin{multline}
@@
 
-The Fisher's information matrix is
+Fisher's information matrix is
 \begin{multline}

### 2019-09-25 reports/thesis/chapters/4_variancePrediction.tex
Revise and used proofreader
Final revise

@@
 
-The aim is to model and predict the grey value variance of a pixel given the its grey value by using a model fitted onto the sample variance-mean data.
+The aim is to model and predict the grey value variance of a pixel given its grey value by using a model fitted onto the sample variance-mean data.
 No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_N,y_N)$ from now on, where $N$ is the area of the ROI or the size of the dataset.
@@
 \end{equation}
-is the log-likelihood of the test set given the fitted model and $\ln L_\mathrm{s}$ is the saturated likelihood. This is obtained by replacing all $\widehat{y}_i$ with $y_i$ in $\ln L_\tau$ so that
+is the log-likelihood of the test set given the fitted model and $\ln L_\mathrm{s}$ is the saturated log-likelihood.
+This is obtained by replacing all $\widehat{y}_i$ with $y_i$ in $\ln L_\tau$ so that
 \begin{equation}
@@
   \includegraphics[width=\subSize]{../figures/varmean/devianceGraph.eps}
-  \caption{Scaled deviance loss function}
+  \caption{The scaled deviance loss function}
   \label{fig:meanVar_deviance}
@@
 The different colours represent different shading corrections.
-The boxplot represent the 100 repeats of the analysis by bootstrapping the replicate projections.}
+The boxplots represent the 100 repeats of the analysis by bootstrapping the replicate projections.}
   \label{fig:meanVar_varMeanCv}

### 2020-04-04 reports/thesis/chapters/1_literatureReview.tex
Final revise
Corrections

@@
 
-Imaging using x-rays \citep{rontgen1896on} have been used in the medical field.
+Imaging using x-rays \citep{rontgen1896on} has been used in the medical field.
 In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patient has an x-ray image taken at multiple angles.
@@
 Fused deposition modelling is another liquid-based AM technology.
-A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer.
+A jetting head, or nozzle, deposits the molten material onto a platform or on top of the previous layer.
 The material is usually plastic in the form of a thin filament.
@@
 The detectors used in XCT are typically flatbed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes.
-The x-ray photons interact with the scintillator material and produce visible light pluses \citep{rossner1993conversion}.
+The x-ray photons interact with the scintillator material and produce visible light pulses \citep{rossner1993conversion}.
 These pulses are detected by photodiodes and converted into an electrical signal \citep{nikl2006scintillation, ren2018tutorial}.
@@
 
-XCT can be used to measuring lengths and distances, making it useful for measuring the dimensions of AM objects internally and externally.
+XCT can be used to measure lengths and distances, making it useful for measuring the dimensions of AM objects internally and externally.
 \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.
@@
 Figure \ref{fig:literature_hardening} shows an example of reconstruction with and without a filter.
-Without the filter, the outer perimeter appears less dense than it should be.
+Without the filter, the interior of the object appears less dense than it should be.
 A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}.

### 2020-04-04 reports/thesis/chapters/2_dataCollection.tex
Corrections

@@
 Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$.
-$S_{x,y}(P)$ may be averaged over replications.
-Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$.
+The projection, $S_{x,y}(P)$, may be averaged over replications.
+Let $x=1,2,3,\ldots, W$ and $y=1,2,3,\ldots,H$.
 Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$.
@@
       \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_linear.eps}
-      \caption{linear shading correction}
+      \caption{Linear shading correction}
     \end{subfigure}
@@
 For each power, the within and between pixel variance was calculated.
-Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,m$ replicates.
+Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\ldots,m$ replicates.
 The within and between pixel variance are
@@
       \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
-      \caption{Linear shading Correction}
+      \caption{Linear shading correction}
     \end{subfigure}
@@
       \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
-      \caption{Linear shading Correction}
+      \caption{Linear shading correction}
     \end{subfigure}

### 2020-04-04 reports/thesis/chapters/3_compoundPoisson.tex
Corrections

@@
 The compound Poisson distribution is studied here because of the compound Poission-like behaviour from the detection of photons \citep{whiting2002signal, elbakri2003efficient, whiting2006properties}.
-It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.) $\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!}$ for $y=0,1,2,\dotsc$, where $\lambda>0$ is the Poisson rate parameter.
-Let $U_i$ be some independent and identically distributed (i.i.d.) latent random variables with probability density function (p.d.f.) $p_U(u)$ for $i=1,2,3,\dotsc$.
+It is defined by defining a latent variable $Y\sim\poisson(\lambda)$ with probability mass function (p.m.f.) $\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!}$ for $y=0,1,2,\ldots$, where $\lambda>0$ is the Poisson rate parameter.
+Let $U_i$ be some independent and identically distributed (i.i.d.) latent random variables with probability density function (p.d.f.) $p_U(u)$ for $i=1,2,3,\ldots$.
 Let $X$ be a compound Poisson random variable where
@@
 Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$.
-Each photon is assumed to be i.i.d.~with random energy $U_i$ for $i=1,2,3,\dotsc$ with p.d.f.~$p_U(u)$.
+Each photon is assumed to be i.i.d.~with random energy $U_i$ for $i=1,2,3,\ldots$ with p.d.f.~$p_U(u)$.
 The random variables discussed here cover all the latent variables in the compound Poisson.
@@
 By assuming no beam hardening, $\expectation\left[U\right]$ and $\expectation\left[U^2\right]$ remains constant, thus there is a linear relationship between the variance and expectation of the grey value \citep{yang2009evaluation}.
-There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
+There are other types of detection schemes \citep{whiting2006properties} but it shall not be considered here.
 
@@
 The derivation is shown in Appendix \ref{chapter:appendix_tweedie}.
-This is in the form of a distribution in the dispersive exponential family.\citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ and $\phi$.
+This is in the form of a distribution in the dispersive exponential family \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$.
 
@@
 
-$y_\text{l}$ and $y_\text{u}$ can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example, $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}.
+The limits, $y_\text{l}$ and $y_\text{u}$, can be chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}$ where $\epsilon$ is some small constant, for example, $\epsilon=\euler^{-37}$ will be better than machine precision in 64 bits \citep{dunn2005series}.
 To prevent overflow problems, it is advised to calculate each term in the summation in log scale \citep{dunn2005series} by using the equation
@@
 The evaluation of the p.d.f.~using the saddlepoint approximate required a bit of caution to avoid over/underflow problems.
-Suppose realisations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
+Suppose realisations of $X$ were simulated $\left\{x_1,x_2,x_3,\ldots,x_n\right\}$.
 The saddlepoint approximation was computed up to a constant using
@@
   k =
-  \max_{i\in\left\{1,2,3,\dotsc,n\right\}}
+  \max_{i\in\left\{1,2,3,\ldots,n\right\}}
   \left[
@@
 \end{equation}
-then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotsc,\frac{n-0.5}{n}$.
+then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\ldots,\frac{n-0.5}{n}$.
 If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin.
@@
 Consider a bin in a histogram, the confidence intervals were obtained by assuming that the frequency in a bin $\sim\poisson(\text{p.d.f.~evaluated at the bin}\times 1\,000 \times \text{bin width})$.
+The 68\% confidence interval was chosen because this is a typical choice in physics \citep{cowan1998statistical}.
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\mainSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
+        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
+    \end{subfigure}
+    }
+    \vspace{2em}
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha1beta1.eps}
+        \caption{Q-Q plot}
+    \end{subfigure}
+    }
+    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical density is compared to the p.d.f.~evaluated using the exact method.
+In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
+    \label{fig:compoundPoisson_histogram_1_1_1}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\mainSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
+        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
+    \end{subfigure}
+    }
+    \vspace{2em}
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha100beta1.eps}
+        \caption{Q-Q plot}
+    \end{subfigure}
+    }
+    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical density is compared to the p.d.f.~evaluated using the exact method.
+In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
+    \label{fig:compoundPoisson_histogram_1_100_1}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha1beta1.eps}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \vspace{1em}
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha1beta1.eps}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical density is compared to the approximate p.d.f.
+On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_approx_1_1_1}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
+        \caption{Histogram - Normal approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha100beta1.eps}
+        \caption{Q-Q plot - Normal approx.}
+    \end{subfigure}
+    }
+    \vspace{1em}
+    \centerline{
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
+        \caption{Histogram - Saddlepoint approx.}
+    \end{subfigure}
+    \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha100beta1.eps}
+        \caption{Q-Q plot - Saddlepoint approx.}
+    \end{subfigure}
+    }
+    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical density is compared to the approximate p.d.f.
+On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
+    \label{fig:compoundPoisson_histogram_approx_1_100_1}
+\end{figure}
 
 For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1} to \ref{fig:compoundPoisson_histogram_approx_1_100_1}) there was a chance of simulating zeros.
-For $\lambda = 1$, the Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values.
-The saddlepoint approximation did capture the probability mass at zero as shown by an increase in probability density towards zero.
-For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1}, the compound Poisson-gamma p.d.f.~contained multiple peaks and the saddlepoint approximation was not flexible enough to capture them.
+The exact method has an advantage here because it can evaluate probability mass at zero.
+The Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values.
+The saddlepoint approximation improves on the Normal approximation by capturing the skewness and kurtosis of the distribution \citep{bedrick1992empirical, butler2007saddlepoint}.
+As a result, it captured the probability mass at zero as shown by an increase in probability density towards zero.
+
+For $\CPoisson(1,100,1)$, the compound Poisson-gamma p.d.f.~contained multiple peaks.
+Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1} shows that the saddlepoint approximation was not flexible enough to capture them.
 In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation of the numerical calculation of the c.d.f.~and its inversion.
@@
     \centerline{
-    \begin{subfigure}[b]{\mainSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
-        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
-    \end{subfigure}
-    }
-    \vspace{2em}
-    \centerline{
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha1beta1.eps}
-        \caption{Q-Q plot}
-    \end{subfigure}
-    }
-    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical density is compared to the p.d.f.~evaluated using the exact method.
-In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
-    \label{fig:compoundPoisson_histogram_1_1_1}
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{\mainSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
-        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
-    \end{subfigure}
-    }
-    \vspace{2em}
-    \centerline{
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha100beta1.eps}
-        \caption{Q-Q plot}
-    \end{subfigure}
-    }
-    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical density is compared to the p.d.f.~evaluated using the exact method.
-In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
-    \label{fig:compoundPoisson_histogram_1_100_1}
-\end{figure}
-
-\begin{figure}[t]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha1beta1.eps}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \vspace{1em}
-    \centerline{
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha1beta1.eps}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical density is compared to the approximate p.d.f.
-On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
-    \label{fig:compoundPoisson_histogram_approx_1_1_1}
-\end{figure}
-
-\begin{figure}[t]
-  \centering
-    \centerline{
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
-        \caption{Histogram - Normal approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha100beta1.eps}
-        \caption{Q-Q plot - Normal approx.}
-    \end{subfigure}
-    }
-    \vspace{1em}
-    \centerline{
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
-        \caption{Histogram - Saddlepoint approx.}
-    \end{subfigure}
-    \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha100beta1.eps}
-        \caption{Q-Q plot - Saddlepoint approx.}
-    \end{subfigure}
-    }
-    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical density is compared to the approximate p.d.f.
-On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
-    \label{fig:compoundPoisson_histogram_approx_1_100_1}
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centerline{
     \begin{subfigure}[b]{\subSize}
@@
 \section{Proposed Model}
+\label{chapter2:proposed_model}
 
@@
 The amount of attenuation depends on the specific path from the source to a pixel in a detector, so $\lambda_i$ varies from pixel to pixel.
-Electronic Normal noise $\epsilon_{i,j}\sim\normal(a,\kappa)$ may be added as well.
+Electronic Normal noise $\epsilon_{i,j}\sim\normal(a,\kappa)$ is added to model noise recorded by the x-ray detector when no x-rays are exposed.
+This was observed in the black images in Chapter \ref{chapter2}.
 
@@
 
+The assumption of a gamma-distributed x-ray photon energy and Normal electronic noise was applied to XCT by \cite{xu2009electronic}.
+The assumptions were verified by investigating the variance of radiographs for different x-ray exposures.
+More statistically sound methods could use goodness of fit tests or Q-Q plots.
+The use of the gamma distribution will not be exactly correct because the sources of x-ray photon energy are characteristic and bremsstrahlung radiation which does not behave like a gamma random variable.
+However, characterisation of the density of the x-ray photon energy is difficult and usually involve more apparatuses and numerical methods \citep{fewell1977photon, stumbo2004direct}.
+
 The model may be simplified by omitting the electronic noise and this can be done by setting $a=0$ and $\kappa=0$.
-The number of pixels can be set to $N=1$ to simplify the model further.
+Further simplification can be done by removing spatial variation by setting $\lambda=\lambda_1=\lambda_2=\ldots=\lambda_N$.
 Parameter estimation can be done using gradient methods because the likelihood of the compound Poisson can be evaluated \citep{dunn2005series}.
@@
 
-The EM algorithm \citep{dempster1977maximum} was proposed to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$.
+The EM algorithm \citep{dempster1977maximum} was proposed to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\ldots,x_n\right\}$.
 The use of the EM algorithm for the compound Poisson distribution in XCT have been studied in \cite{elbakri2003statistical, xie2008x, xu2009electronic}.
@@
 The EM algorithm \citep{dempster1977maximum} treats $Y\sim\poisson(\lambda)$ as a latent variable.
-Let $\left\{Y_1,Y_2,Y_3,\dotsc, Y_n\right\}$ be realisations of $Y$.
+Let $\left\{Y_1,Y_2,Y_3,\ldots, Y_n\right\}$ be realisations of $Y$.
 Define the joint log-likelihood to be
@@
 
-It will be shown that using some approximations, the E step and M step can be implemented.
-The Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} can also be found by using a few approximations.
-However, simulations showed that these estimators struggle for high $\lambda$.
+It will be shown that using some approximations, the E step and M step can be implemented. However, simulations showed that these estimators struggle for high $\lambda$.
 
@@
 \begin{equation}
-  W_y^{(r)} = y^r W_y \quad \text{for }r=1,2,3,\dotsc
+  W_y^{(r)} = y^r W_y \quad \text{for }r=1,2,3,\ldots
 \end{equation}
@@
 \end{equation}
-where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. $\ln\left(W^{(r)}_y\right)$ can be expressed as
-\begin{equation}
-  \ln\left(W_y^{(r)}\right)=r\ln(y)+\ln(W_y)
+where $y_\text{l}<y_\text{max}<y_\text{u}$ and $y_\text{max}$ is the value of $y$ which maximises $W_y^{(r)}$. This term can be expressed as
+\begin{equation}
+  \ln W_y^{(r)} =r\ln y+\ln W_y
 \end{equation}
@@
 \begin{equation}
-  \frac{\partial }{\partial y} \ln\left(W_y^{(r)}\right) = \frac{r}{y } + \frac{\partial }{\partial y}\ln\left(W_y\right)
-  \ .
-\end{equation}
-Keep in mind that $y=1,2,3,\dotsc$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
-\begin{equation}
-  \frac{\partial }{\partial y} \ln\left(W_y^{(r)}\right)\approx \frac{\partial }{\partial y} \ln\left(W_y\right)
-  \ .
-\end{equation}
-Therefore, the maximum of $W_y^{(r)}$ is located at $y_\text{max}=\dfrac{x^{2-p}}{\phi(2-p)}$ for all $r=0,1,2,\dotsc$.
+  \frac{\partial }{\partial y} \ln W_y^{(r)} = \frac{r}{y } + \frac{\partial }{\partial y}\ln W_y
+  \ .
+\end{equation}
+Keep in mind that $y=1,2,3,\ldots$ so for large $y$, an approximation can be made $r/y\approx 0$ so that
+\begin{equation}
+  \frac{\partial }{\partial y} \ln W_y^{(r)}\approx \frac{\partial }{\partial y} \ln W_y
+  \ .
+\end{equation}
+Therefore, the maximum of $W_y^{(r)}$ is located at $y_\text{max}=\dfrac{x^{2-p}}{\phi(2-p)}$ for all $r=0,1,2,\ldots$.
 As a result, the same method for evaluating $W_y$ can be used to evaluate $W_y^{(r)}$.
-For a given $r=0,1,2,\dotsc$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ are chosen such that $W_{y_\text{l}}$ and $W_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
+For a given $r=0,1,2,\ldots$, the limit of the sum $\sum_{y=y_\text{l}}^{y_\text{u}} W^{(r)}_y$ were chosen such that $W^{(r)}_{y_\text{l}}$ and $W^{(r)}_{y_\text{u}}$ are less than $\epsilon W_{y_\text{max}}^{(r)}$ where $\epsilon$ is some small constant.
 The limits will be different for different values of $r$.
@@
 
-\subsection{Estimation Error}
-
-The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} from the Fisher's information matrix \citep{fisher1922on} defined as
-\begin{equation}
-  \matr{I} = -\expectation\left[
-    \nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
-  \right]
-\end{equation}
-where
-\begin{equation}
-  \nabla_{\lambda, \alpha,\beta}=
-  \begin{pmatrix}
-    {\partial}/{\partial \lambda}
-    \\
-    {\partial}/{\partial \alpha}
-    \\
-    {\partial}/{\partial \beta}
-  \end{pmatrix}
-  \ .
-\end{equation}
-
-Most of the calculations for the elements of the matrix are similar to the derivatives of $T$.
-For the $\alpha$ component, taking derivatives of the joint log-likelihood (Equation \eqref{eq:compoundPoisson_jointLogLikelihood}) obtains
-\begin{align}
-\dfrac{\partial\ln L}{\partial\alpha} &= \sum_{i=1}^n\mathbb{I}(x_i>0)
-\left[
-  Y_i\ln\beta - \psi(Y_i\alpha)Y_i+Y_i\ln x_i
-\right]
-\\
-\dfrac{\partial^2\ln L}{\partial\alpha^2} &= \sum_{i=1}^n\mathbb{I}(x_i>0)
-\left[
-  -\psi'(Y_i\alpha)Y_i^2
-\right] \ .
-\end{align}
-The expectation of the second-order derivative is
-\begin{equation}
--\expectation\left[\dfrac{\partial^2\ln L}{\partial\alpha^2}\right]
-=
-n\left(1-\euler^{-\lambda}\right)
-\expectation\left[
-  \psi'(Y\alpha)Y^2
-\right]
-\end{equation}
-where the factor $\left(1-\euler^{-\lambda}\right)$ is the proportion of data where $x_i>0$. $\expectation\left[\psi'(Y\alpha)Y^2\right]$ can be approximated. Let $g(Y)=\psi'(Y\alpha)Y^2$, then
-\begin{equation}
-\expectation\left[\psi'(Y\alpha)Y^2\right]
-\approx
-\psi'(\lambda\alpha)\lambda^2
-+\dfrac{\lambda}{2}g''(\lambda) \ .
-\end{equation}
-The derivatives of $g(Y)$ are
-\begin{align}
-g'(Y)&=\psi''(Y\alpha)Y^2\alpha + 2\psi'(Y\alpha)Y
-\\
-g''(Y)&=Y^2\alpha^2\psi'''(Y\alpha)+4Y\alpha\psi''(Y\alpha)+2\psi'(Y\alpha)\ .
-\end{align}
-Therefore,
-\begin{multline}
--\expectation\left[\dfrac{\partial^2\ln L}{\partial\alpha^2}\right]\approx n\left(1-\euler^{-\lambda}\right)
-\\
-\times\left[(\lambda^2+\lambda)\psi'(\lambda\alpha)+2\lambda^2\alpha\psi''(\lambda\alpha)+\dfrac{\lambda^3\alpha^2}{2}\psi'''(\lambda\alpha)\right]
-\end{multline}
-
-Fisher's information matrix is
-\begin{multline}
-  \matr{I}=
-  n
-  \left(\begin{matrix}
-    \dfrac{1}{\lambda} & 0\\
-    0 & \left(1-\euler^{-\lambda}\right)\left[(\lambda^2+\lambda)\psi'(\lambda\alpha)+2\lambda^2\alpha\psi''(\lambda\alpha)+\dfrac{\lambda^3\alpha^2}{2}\psi'''(\lambda\alpha)\right]\\
-    0 & -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}
-  \end{matrix}\right.
-  \\
-  \left.\begin{matrix}
-  \vphantom{\dfrac{1}{\lambda}}0\\
-  -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}\\
-  \dfrac{\left(1-\euler^{-\lambda}\right)\alpha\lambda}{\beta^2}
-  \end{matrix}\right)
-  \ .
-\end{multline}
-The Cram\'er-Rao lower bound can be obtained using
-\begin{equation}
-  \cov\left[
-    \begin{pmatrix}
-      \widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
-    \end{pmatrix}
-  \right]
-  =
-  \matr{I}^{-1}
-  \ .
-\end{equation}
-
 \subsection{Simulations}
@@
     \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(1,1,1)$ random variable using 1\,000 simulated samples.
-The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.}
     \label{fig:compoundPoisson_convergence_1}
@@
     \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(1,100,1)$ random variable using 1\,000 simulated samples.
-The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.}
     \label{fig:compoundPoisson_convergence_2}
@@
     \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(10,1,1)$ random variable using 1\,000 simulated samples.
-The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.}
     \label{fig:compoundPoisson_convergence_3}
@@
     \caption{The EM algorithm was used to estimate the parameters of a $\CPoisson(100,100,1)$ random variable using 1\,000 simulated samples.
-The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.
-The dashed lines show the standard deviation using the Cram\'er-Rao lower bound.}
+The graphs show the log-likelihood and the estimated parameters at each EM step for 10 different simulations.}
     \label{fig:compoundPoisson_convergence_4}
@@
 The compound Poisson-gamma distribution was studied but it was found there were identifiability issues when fitting the model onto simulated data, in particular for high $\lambda$.
-
-XCT is in the realm of high $\lambda$ and this can be shown using back of the envelope calculations.
-Using the properties in the \texttt{AbsNoFilter} dataset, the power and potential difference of the x-ray tube were $P=\SI{36}{\watt}$ and $V=\SI{80}{\kilo\volt}$ respectively.
-The time exposure was $\tau=\SI{708}{\milli\second}$.
-Assume an efficiency of \SI{0.01}{{photon.}{electron}^{-1}} and the charge per electron is $e=\SI{1.602e-19}{\coulomb\,{electron}^{-1}}$.
-Assume that the photons were projected onto the array of $2\,000^2\,\si{\pixel}$.
-The number of photons detected per pixel is calculated to be
-\begin{align*}
-\lambda &\approx \dfrac{\text{efficiency} \times P \tau}{\text{number of pixels} \times V e}
-\\
-&\sim 10^7\,\si{{photon}\,\pixel^{-1}}
-\ .
-\end{align*}
-Fitting the compound Poisson model onto XCT data would not be possible with such a high value of $\lambda$.
-
-All is not lost though, it was found that there is a linear relationship between the variance and mean of the grey value in a pixel.
-This suggests that uncertainty can be predicted by using such a relationship.
-The next chapter investigates this.
+It was found that the log-likelihood was quite flat because, by using numerous approximations, it was found that the determinant of the Hessian is zero.
+This cast doubts if a unique maximum likelihood estimator exists.
+Tighter bounds for the Hessian is beyond the scope of this thesis.
+
+The problem with the EM algorithm is that it is sensitive to the initial value and does not guarantee convergence to a global maximum \citep{moon1996expectation}.
+Another disadvantage is that the EM algorithm does not produce uncertainty quantification for the estimators.
+Methods such as bootstrapping \citep{efron1979bootstrap} and Louis' missing information principle \citep{louis1982finding} can be used to obtain such uncertainty quantification.
+
+There are methods to deal with flat likelihoods by extending the likelihood to include penalising terms \citep{cole2014maximum}.
+Another approach is to use Bayesian methods \citep{bishop2006pattern} where a prior distribution is defined for the parameters $\alpha$, $\beta$, $\lambda_1,\lambda_2,\ldots,\lambda_N$, $a$ and $\kappa$ where $N$ is the number of pixels and $a$ and $\kappa$ are the mean and variance terms for the Normal noise, defined in Section \ref{chapter2:proposed_model}.
+The prior distribution can reflect prior knowledge of the model, for example, the statistical properties of the sample of black images can be embedded into the priors of $a$ and $\kappa$.
+Back of the envelope calculations can be used to show that $\lambda_i \sim 10^7\,\si{{photon}\,\pixel^{-1}}$ which can be used to aid in the creation of a prior distribution for $\lambda_i$.
+Poisson graphical models \citep{yang2013poisson} and Gaussian processes \citep{williams1996gaussian} can impose a spatial dependency on $Y_{i,j}$ and $\lambda_i$ respectively as well.
+
+Bayesian inference is done by studying the posterior distribution where
+\begin{equation*}
+\mathrm{posterior} \propto \mathrm{likelhood} \times \mathrm{prior} \ .
+\end{equation*}
+By multiplying the likelihood with the prior, the posterior should hopefully be convex and enable better convergence.
+Studying the posterior distribution typically requires Markov chains using Monte Carlo methods \citep{brooks2011handbook} such as Metropolis-Hastings \citep{metropolis1953equation, hastings1970monte}, Gibbs sampling \citep{geman1984stochastic}, Hamiltonian Monte Carlo \citep{neal2011mcmc, hoffman2014no} and slice sampling \citep{neal2003slice, murray2010elliptical}.
+
+To keep the frequentist theme throughout this thesis, the next chapter studies the linear relationship between the variance and mean of the grey value in a pixel.
+The uncertainty can be predicted by using such a relationship.

### 2020-04-04 reports/thesis/chapters/4_variancePrediction.tex
Flowchart is png
Corrections

@@
-It was found that it was hard to fit a compound Poisson distribution onto the grey values.
-Results did show that the variance of the grey value has a linear relationship with the mean grey value.
+In the previous chapter, the grey values were modelled using a compound Poisson distribution to reflect the science of x-rays.
+This model has a linear relationship between the variance and the expectation.
 As a result, it would be possible to predict the variance of the grey value, given the grey value.
@@
 The sample variance-mean data were obtained from the replicate projections.
-Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotsc,m$.
-The sample mean and sample variance grey value for the pixel at $(i,j)$ are
+Let $x_{i,j}$ be the grey value of the $i$th pixel, ignoring any spatial information, from the $j$th replicate projection for $i=1,2,3,\ldots,N$ and $j=1,2,3,\ldots,m$.
+The sample mean and sample variance grey value for the $i$th pixel are
 \begin{equation}
-    \overline{x}_{i,j}=\frac{1}{m}\sum_{r=1}^m x_{i,j}^{(r)}
+    \overline{x}_{i}=\frac{1}{m}\sum_{j=1}^m x_{i,j}
 \end{equation}
@@
 \begin{equation}
-    y_{i,j} =
+    y_{i} =
     \frac{1}{m-1}
-    \sum_{r=1}^m
+    \sum_{j=1}^m
         \left(
-            x_{i,j}^{(r)} - \overline{x}_{i,j}
+            x_{i,j} - \overline{x}_{i}
         \right)^2
@@
 respectively.
+The symbol $y$ should not be confused with the latent varible in the previous chapter.
 Only pixels in the region of interest (ROI) were considered here, that is, pixels which represent the test sample.
@@
 The aim is to model and predict the grey value variance of a pixel given its grey value by using a model fitted onto the sample variance-mean data.
-No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_N,y_N)$ from now on, where $N$ is the area of the ROI or the size of the dataset.
+The variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\ldots,(x_N,y_N)$ where $N$ is the area of the ROI or the size of the dataset.
 Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$.
@@
 \end{equation}
-There is also the log link $g(y)=\ln y$ but $y$ must be a unitless quantity, for example Poisson counts, for it to be comparable.
-Because $y$ is in units of $\SI{}{\adu^2}$, the log link was not used in this analysis.
 
 An example of a systematic component are polynomial features $\eta(x)=\sum_{r=0}^{p}\beta_r x^{r}$ so that when used with the identity link, for example, $\expectation\left[Y(x)\right] = \sum_{r=0}^{p}\beta_r x^{r}$.
-Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \dotsc, \beta_{p}$ given data for the model to fit onto.
+Iterative reweighted least squares \citep{friedman2001elements} can be used to estimate the parameters $\beta_0, \beta_1, \ldots, \beta_{p}$ given data for the model to fit onto.
 
@@
 The forward stepwise selection may not picked this up because there were a lot of low grey values, causing a leverage towards these low grey values.
-As a result, the inflection did not stood out to the method.
+As a result, the inflection did not stand out to the method.
 
@@
 
-Instead of assessing the model fit using the AIC and BIC, the performance on predicting the variance given a grey value was assessed using cross-validation \citep{friedman2001elements}.
+Instead of assessing the model fit using the AIC and BIC, the performance on predicting the variance given a grey value was assessed using cross-validation \citep{allen1974relationship, stone1974cross, stone1977asymptotic, friedman2001elements}.
 Cross-validation assesses the model to make predictions on data it has not seen before.
 This was done by randomly splitting the $N$ data points into two disjoint sets, the training set and the test set $\tau$.
-It was chosen that the training and test set are of the same size $N_\tau$.
 The model was fitted onto the training set.
 Afterwards, the fitted model predicts the variances given the grey values in the test set which were then compared to the actual variances.
+
+It was chosen that the training and test set are of the same size, a 50:50 spilt.
+The sizes of the sets can be different, for example, a 75:25 spilt.
+A 50:50 spilt was chosen because a large training set is an overkill for a high data and low dimensional problem.
+Here, a model with a few parameters is fitted onto millions of pixels.
 
@@
       \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg120_vsgreyvalue.eps}
-      \caption{\texttt{AbsFilter} at \ang{120}}
+      \caption{\texttt{AbsNoFilter} at \ang{120}}
   \end{subfigure}
@@
 A good explanation was not found but perhaps the absence of an x-ray filter may have contributed to this.
+As a result, the \texttt{AbsNoFilter} dataset was discarded in favour of the \texttt{AbsFilter} dataset from the next chapter.
 
+There exist model selection methods such as lasso and elastic net \citep{tibshirani1996regression, zou2005regularization, friedman2010regularization} but they are catered for high dimensional problems involving hundreds of parameters.
+In this problem, only a few parameters were needed to find a good model.
 More flexible models such as non-parametric and machine learning methods may be used, however, they are slow and are unnecessary in a low dimensional problem with a large number of data points.

### 2020-04-13 reports/thesis/book.tex
Flowchart is png
Corrections
Corrections
CpEmAlgorithm does not plot estimated std
roc calculates area exactly
Recoded NullIid and included biweighted mean

@@
-\documentclass[12pt, a4paper, oneside]{memoir}
+\documentclass[12pt, a4paper, twoside]{memoir}
 %oneside for soft copy
@@
 
+%page number of odd page on new chapter
 \let\footruleskip\undefined
@@
 \renewcommand{\footrulewidth}{0pt}}
+\aliaspagestyle{cleared}{plain} %page number of blank even
 
@@
 
+%\includepdf[page={1,2,3,4}]{licence.pdf}
+
 \begin{titlingpage}
@@
 
-Parts of this thesis is anticipated to be published by the author:
-\begin{itemize}
-  \item\nobibliography*\bibentry{lo2019detection}
-\end{itemize}
-
 \chapter{Abstract}
@@
 Voids with diameters in the order of millimetres were detectable.
-
-This thesis is a contribution to real-time quality control in additive manufacturing.
 
@@
 In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed.
-Sources of error were investigated and see how they were handled.
+Sources of error were investigated and it was discuused how they were handled.
 In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained.
@@
   \centering
-  \includegraphics[width=0.64\textwidth]{../figures/flowchart.pdf}
+  \includegraphics[width=0.64\textwidth]{../figures/flowchart.png}
   \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
@@
 
+The main statistical novelty was extending the empirical null \citep{efron2004large} to a filter where it can be applied to images.
+This has been implemented in \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image}.
+A by-product is the empirical null mean, which is effectively the mode filter, which can be used to smooth images.
+
 Two angular projections were looked at in this thesis.
@@
 Defect detection can be tough if a difficult projection angle was used.
-Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.
+This experiment could be improved by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.
 Another possible extension is to integrate \emph{aRTist} into the inference, for example, the simulated projection could be realigned to minimise the number of positives.
@@
 This results in voids appearing with less contrast in the projections, making it harder to detect.
+Different types of challenging defects could be investigated.
+For example, the orientation of cracks can affect the detectability of it \citep{wooldridge1997demonstrating}.
 
-This thesis is a contribution to real-time quality control for AM.
+This thesis is a contribution to real-time quality control for AM and perhaps inverse problems in imaging \citep{bertero1998introduction} and robust statistics.
 A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt.
+This could be competitive with other converyor belt inspection methods, for example \cite{warnett2016towards}, by using less projections and hopefully less computational time.
 By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.

### 2020-04-13 reports/thesis/chapters/5_inference.tex
Final revise
Corrections
CpEmAlgorithm does not plot estimated std
roc calculates area exactly
Recoded NullIid and included biweighted mean

@@
 A pixel by pixel hypothesis test was proposed to do defect detection.
+To illustrate this method of inference, the projections from the dataset \texttt{AbsFilter} at \ang{120} was used.
+To recap, 20 replicate projections of a test sample, with purposefully manufactured voids, were obtained.
+\emph{aRTist} was used to create a simulation of that projection but as if the voids were not there.
+Thus, the method should pick these voids up.
+
 Beforehand, linear shading correction was applied to the projections.
 The \emph{aRTist} projections were shading corrected using the simulated greyscale projections.
+The 20 replicate projections were split into two.
+19 randomly selected projections were used for the variance-mean model to fit onto.
+The remaining projection was compared with the \emph{aRTist} projection.
+This remaining projection and the \emph{aRTist} projections are shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
+
+A gamma GLM, with a basic linear relationship, was used for the variance-mean model, as described in Chapter \ref{chapter4}.
+The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.
+
 The test statistic, for the pixel located at $(x,y)$, is
@@
   {
-    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
-  }
-\end{equation}
-where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance.
+    \sqrt{s^2\left[\emph{aRTist}_{x,y}\right]}
+  }
+\end{equation}
+where $s^2\left[\emph{aRTist}_{x,y}\right]$ is the predicted grey value variance.
 The test statistic was calculated for each pixel in the ROI, that is, pixels which represent the test sample.
@@
 
-For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution.
-Thus, if there are no significant differences between the obtained and \emph{aRTist} projections, then the randomness of the test statistics can be approximately quantified as
+It is important to identity which quantites are random and which are not.
+For high photon rates, it was shown in the previous chapters that the grey values in the projection can be modelled using a Normal distribution.
+Thus, $\text{projection}_{x,y}$ is a random quantity.
+The simulation $\emph{aRTist}_{x,y}$ is not random because this was obtained through a computer software.
+Given the 19 selected projections used for training the variance-mean model, the variance prediction $s^2\left[\emph{aRTist}_{x,y}\right]$ is not random because the variance-mean model was fitted before encountering the remaining projection to be compared with \emph{aRTist}.
+The variance-mean model can be made random if a different set of 19 projections was used to train the model each time this inference was conducted, but this shall not be considered here.
+
+If there are no significant differences between the obtained and \emph{aRTist} projections, then the randomness of the test statistics can be approximately quantified as
 \begin{equation}
@@
 
-To illustrate this method of inference, the projections from the dataset \texttt{AbsFilter} at \ang{120} was used.
-To recap, replicate projections of a test sample, with purposefully manufactured voids, were obtained.
-\emph{aRTist} was used to create a simulation of that projection but as if the voids were not there.
-Thus, the method should pick these voids up.
-
-The obtained and \emph{aRTist} projections are shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.
-The 20 replicate projections were split into two.
-19 randomly selected projections were used for the variance-mean model to fit onto.
-A gamma GLM, with a basic linear relationship, was used for the variance-mean model.
-The remaining projection was compared with the \emph{aRTist} projection.
-The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.
+For each pixel, a test statistic was calculated, which forms a $z$ image.
+A test statistic too large in magnitude, relative to the anticipated variance, will classify that pixel as a positive result.
+In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, $p$-values can be used to represent the test statistics in a different way
+\begin{equation}
+  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
+\end{equation}
+which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.
 
@@
 \end{figure}
-
-For each pixel, a test statistic was calculated, which forms a $z$ image.
-A test statistic too large in magnitude, relative to the anticipated variance, will classify that pixel as a positive result.
-In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, $p$-values can be used to represent the test statistics in a different way
-\begin{equation}
-  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
-\end{equation}
-which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.
 
@@
 
+It can be noted that this mode finding method can be aplied to other distributions in general.
+
 \subsection{Bandwidth Tuning}
@@
 
-The GLM fit in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} appeared to underfit, which suggest there may be a more complicated relationship between the optimal bandwidth and $n$.
+The GLM fit in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} appeared to underfit, which suggest there may be a more complicated relationship between the optimal bandwidth and $n$, for example, a quadratic term can be added to the GLM fit.
 The method used in fitting the smoothing spline could contribute to the underfitting.
@@
 A basic linear relationship was chosen to avoid overfitting and to keep the rule of thumb simple.
+It would also choose a large bandwidth for small $n$ which would improve the performance $\widehat{\mu}_0$ by working on a smoother density estimate for the price of a less optimal $s^2\left[\emph{aRTist}_{x,y}\right]$.
 
@@
 
-Various estimates of central tendency and dispersion were compared with the empirical null mean and empirical null standard deviation.
+The empirical null mean is effectively the mode and the empirical null standard deivation is a measure of dispersion.
+It was investigated how they compare with various estimates of central tendency and dispersion for varying sample sizes $n$.
 The empirical sampling distribution of these estimators was observed to look for properties such as bias, variance and robustness.
-The central tendency estimates looked at were the median and the mean.
-The dispersion estimates looked at were the median absolute deviation (MAD) around the mode $\times 1.483$, interquartile range (IQR) $\div 1.349$ and the standard deviation.
-The normalisation constants were used so that the MAD and IQR can be compared directly to the standard deviation.
-
-A dataset of $n = \pi r^2$ standard Normal random variables was simulated to obtain estimates of central tendency and dispersion.
+
+The central tendency estimates looked at were the median, the mean and Tukey's biweighted mean \citep{beaton1974fitting}.
+In summary, the biweighted mean weigh each data point using a smooth function of its residual and ignores any data points with residuals greater than a certain value.
+\emph{MATLAB}'s \texttt{robustfit} function was used for the biweighted mean and selects any tuning parmaeters.
+
+The dispersion estimates looked at were the interquartile range (IQR) $\div 1.349$, the standard deviation and the median absolute deviation around the mode (MADA-mode) $\times 1.483$, .
+The normalisation constants were used so that MADA-mode and IQR can be compared directly to the standard deviation.
+MADA-mode was considered to investigate how estimators, which depends on the mode, perform.
+
+In the next section, these estimators are used on a circular kernel with radius $r$ containing $\pi r^2$ pixels.
+To make results comparable, the sample size $n$ may be represented using $r=\sqrt{n/\pi}$.
+
+A sample of standard Normal random variables was simulated to obtain estimates of central tendency and dispersion.
 This was repeated 100 times to obtain a sampling distribution.
 The results are shown in Figures \ref{fig:inference_NullIidMean} and \ref{fig:inference_NullIidStd}.
-The empirical null mean and empirical null standard deviation both suffered from high variance, much higher than typical robust estimators such as the median and IQR.
+The mode and empirical null standard deviation both suffered from high variance, much higher than typical robust estimators.
 
@@
 
-To test for robustness, a dataset of $n = \pi r^2$ mixture of Gaussian random variables were simulated with the following distribution: $\normal(0,1)$ with probability $90\%$, $\normal(3,1)$ with probability $10\%$.
+It is interesting to compare the empirical null standard devaition with MADA-mode, in Figure \ref{fig:inference_NullIidStd}, because they both depend on the mode.
+The mode suffered from high variance with may affect dispersion estimators using the mode.
+The figure shows that MADA-mode has less variance than the empirical null standard deviation.
+This suggests that using the curvature of the density estimate at the mode is a main source of variance for the empirical null standard devation.
+
+To test for robustness, a sample of mixture of Gaussian random variables were simulated with the following distribution: $\normal(0,1)$ with probability $90\%$, $\normal(3,1)$ with probability $10\%$.
 The $\normal(3,1)$ component acts as non-null statistics and robust estimators should be unaffected by it.
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullMean1.eps}
+        \caption{Mode}
+      \end{subfigure}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullMean2.eps}
+        \caption{Bisquare weighted mean}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullMean3.eps}
         \caption{Median}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullMean4.eps}
         \caption{Mean}
@@
 
-\begin{figure}
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullStd1.eps}
         \caption{Empirical null std}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMadMode_nullStd.eps}
-        \caption{MAD mode}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullStd2.eps}
+        \caption{MADA-mode}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullStd3.eps}
         \caption{IQR}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullStd4.eps}
         \caption{Standard deviation}
@@
 
-\begin{figure}
-  \centering
-    \centerline{
-      \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullMean.eps}
-        \caption{Empirical null mean}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullMean.eps}
+\begin{figure}[p]
+  \centering
+    \centerline{
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullMean1.eps}
+        \caption{Mode}
+      \end{subfigure}
+      \begin{subfigure}[b]{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullMean2.eps}
+        \caption{Bisquared weighted mean}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullMean3.eps}
         \caption{Median}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullMean.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullMean4.eps}
         \caption{Mean}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullStd1.eps}
         \caption{Empirical null std}
@@
       \begin{subfigure}[b]{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMadMode_nullStd.eps}
-        \caption{MAD mode}
-      \end{subfigure}
-    }
-    \centerline{
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullStd2.eps}
+        \caption{MADA-mode}
+      \end{subfigure}
+    }
+    \centerline{
+      \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullStd3.eps}
         \caption{IQR}
@@
       \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullStd.eps}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullStd4.eps}
         \caption{Standard deviation}
@@
 \begin{equation}
-Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{x,y}^2)
+Z_{x,y}\sim\normal(\mu_{0,x,y},\widehat{\sigma}_{0,x,y}^2)
 \end{equation}
@@
 \begin{equation}
-  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
+  H_{0,x,y}:\mu_{0,x,y}=\widehat{\mu}_{0,x,y}
 \end{equation}
@@
 \begin{equation}
-  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
+  H_{1,x,y}:\mu_{0,x,y}\neq\widehat{\mu}_{0,x,y} \ .
 \end{equation}
@@
 The parameter of choice is the kernel radius $r$.
-A $r$ too small will treat defects as the null and will not detect them.
-A $r$ too big can also cause problems as well.
+A radius too small will treat defects as the null and will not detect them, too big can also cause problems as well.
 The empirical null filter assumes that the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal.
-If $r$ is too big, the kernel will capture distanced test statistics with very different null distributions.
+If the radius is too big, the kernel will capture distanced test statistics with very different null distributions.
 If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution.
@@
 
-$r$ controls the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$.
-$r$ should be selected so that $\pi_0$ is of sensible value, for example, $>90\%$.
+The radius controls the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$.
+It should be selected so that $\pi_0$ is of sensible value, for example, $>90\%$.
 In practice, the defects are unknown so various kernel radiuses should be tried out.
@@
 An experiment was conducted to demonstrate the effects of the empirical null filter on a simulated $\SI{256}{\pixel}\times\SI{256}{\pixel}$ Gaussian image, where all the pixels have value distributed as standard Normal.
-The purpose is to simulate test statistics which are null and no positive results should be detected.
+The purpose is to simulate test statistics which are null and few positive results, subject to the FDR, should be detected.
 The test statistics after filtering should preserve its original distribution, or at least close to it.
@@
 Conducting hypotheses testing on a contaminated Gaussian image may cause errors if the null distributions were incorrectly specified as standard Normal.
-In this experiment, the contamination was a gradient such that the pixel at position $(x,y)$ have a value distributed as $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_{0,x,y}^2)$ where
+In this experiment, the contamination was a gradient such that the pixel at position $(x,y)$ has a value distributed as $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_{0,x,y}^2)$ where
 \begin{equation}
@@
 This is because sources of variance captured by the kernel are from $\sigma_{0,x,y}$ and also from the variability of $\mu_{0,x,y}$.
-This can be shown.
-Let $Z_{x,y}$ be the value of the pixels captured by the circular kernel for integer values of $(x,y)$ such that $x^2+y^2\leqslant r^2$.
-Suppose that $Z_{x,y}\sim\normal(ax+by,c^2\sigma^2)$.
+This can be shown with an example.
+Let $Z_{x,y}$ be the value of the pixels captured by the circular kernel, centred at the origin, for integer values of $(x,y)$ such that $x^2+y^2\leqslant r^2$.
+Suppose that $Z_{x,y}\sim\normal(ax+by,\sigma^2)$.
+The quantities of interest are the expectation and variance of all the values contained in the kernel because this is the quantity the estimators are estimating.
+
 The calculations of the expectation and variance of $Z_{x,y}$ can be approximated by treating $x$ and $y$ as uniformly distributed within a circle centred at the origin with radius $r$.
-The expectation is $\expectation[Z_{X,Y}] = \expectation\expectation[Z_{X,Y}|X,Y]=0$.
+The expectation is
+\begin{equation}
+\expectation[Z_{X,Y}] = \expectation\expectation[Z_{X,Y}|X,Y]=0 \ .
+\end{equation}
+
 The variance is given as $\variance[Z_{X,Y}] = \expectation\variance[Z_{X,Y}|X,Y] + \variance\expectation[Z_{X,Y}|X,Y]$.
-From the distribution of $Z_{X,Y}$, $\expectation\variance[Z_{X,Y}|X,Y] = c^2\sigma^2$ and $\variance\expectation[Z_{X,Y}|X,Y]=\variance[aX+bY]$.
+From the distribution of $Z_{X,Y}$, $\expectation\variance[Z_{X,Y}|X,Y] = \sigma^2$ and $\variance\expectation[Z_{X,Y}|X,Y]=\variance[aX+bY]$.
 This is worked out to be
@@
 \begin{equation}
-\variance[Z_{X,Y}] = \dfrac{1}{4}(a^2+b^2)r^2 + c^2\sigma^2 \ .
+\variance[Z_{X,Y}] = \dfrac{1}{4}(a^2+b^2)r^2 + \sigma^2 \ .
 \end{equation}
@@
 For a given kernel radius $r$, 100 different Gaussian images were filtered to investigate the within image mean, standard deviation and kurtosis of the filtered statistics.
-Various other filters for normalisation were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter.
+Various other filters for normalisation were used as well such as the MADA-mode null filter, median IQR null filter and the mean variance null filter.
 They use different estimators to estimate the null parameters as their name suggests, Table \ref{table:inference_nullFilters} clarifies them.
@@
     Filters&Null mean&Null standard deviation\\\hline
-    MAD mode null&Mode&MAD around the mode $\times1.483$\\
+    MADA-mode null&Mode&MADA-mode $\times1.483$\\
     Median IQR null&Median&IQR $\div1.349$\\
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_mean.eps}
-    \caption{Empirical Null}
+    \caption{Empirical null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_mean.eps}
-    \caption{MAD Mode Null}
+    \caption{MADA-mode null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_mean.eps}
-    \caption{Median IQR Null}
+    \caption{Median IQR null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_mean.eps}
-    \caption{Mean Var Null}
+    \caption{Mean var null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_variance.eps}
-    \caption{Empirical Null}
+    \caption{Empirical null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_variance.eps}
-    \caption{MAD Mode Null}
+    \caption{MADA-mode null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_variance.eps}
-    \caption{Median IQR Null}
+    \caption{Median IQR null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_variance.eps}
-    \caption{Mean Var Null}
+    \caption{Mean var null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_kurtosis.eps}
-    \caption{Empirical Null}
+    \caption{Empirical null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_kurtosis.eps}
-    \caption{MAD Mode Null}
+    \caption{MADA-mode null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_kurtosis.eps}
-    \caption{Median IQR Null}
+    \caption{Median IQR null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_kurtosis.eps}
-    \caption{Mean Var Null}
+    \caption{Mean var null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_mean.eps}
-    \caption{Empirical Null}
+    \caption{Empirical null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_mean.eps}
-    \caption{MAD Mode Null}
+    \caption{MADA-mode null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_mean.eps}
-    \caption{Median IQR Null}
+    \caption{Median IQR null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_mean.eps}
-    \caption{Mean Var Null}
+    \caption{Mean var null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_variance.eps}
-    \caption{Empirical Null}
+    \caption{Empirical null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_variance.eps}
-    \caption{MAD Mode Null}
+    \caption{MADA-mode null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_variance.eps}
-    \caption{Median IQR Null}
+    \caption{Median IQR null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_variance.eps}
-    \caption{Mean Var Null}
+    \caption{Mean var null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_kurtosis.eps}
-    \caption{Empirical Null}
+    \caption{Empirical null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_kurtosis.eps}
-    \caption{MAD Mode Null}
+    \caption{MADA-mode null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_kurtosis.eps}
-    \caption{Median IQR Null}
+    \caption{Median IQR null filter}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_kurtosis.eps}
-    \caption{Mean Var Null}
+    \caption{Mean var null filter}
   \end{subfigure}
@@
 The source of the kurtosis inflation is from the estimation of the null standard deviation.
-This can be seen by comparing the empirical null filter with the MAD mode null filter because the only difference between the two filters is in the estimation of the null standard deviation.
+This can be seen by comparing the empirical null filter with the MADA-mode null filter because the only difference between the two filters is in the estimation of the null standard deviation.
 
@@
 A line defect assigns columns of pixels to be non-null, a kernel would only capture a section of the defect.
-A square defect was also investigated and a kernel can only capture the entire defect if its radius is large enough.
+A square defect was also investigated and a kernel can capture the entire defect only if its radius is large enough.
 
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilterpValueFiltered.eps}
-        \caption{Dust defect, $r=\SI{20}{\pixel}$}
+        \caption{Speckle defect, $r=\SI{20}{\pixel}$}
       \end{subfigure}
@@
 The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pinpoint which mode is greater.
+However, this would be at a computational cost.
 
@@
 False negatives are common but this is inevitable to control for the FDR.
-The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, tested few pixels for defects.
+The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, failed to capture the defect.
 This, again, emphasise the importance of a good kernel radius.
@@
         \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_roc.eps}
-        \caption{Dust defect, $r=\SI{20}{\pixel}$}
+        \caption{Speckle defect, $r=\SI{20}{\pixel}$}
       \end{subfigure}
@@
 The AUC, type 1 error, type 2 error and FDR were measured when testing on an image with a defect before and after contamination and then after filtering with the contamination.
-The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1\,000 trapeziums.
+The AUC was obtained by integrating the ROC curve.
 A kernel radius of $r=\SI{20}{\pixel}$ was used and was repeated 100 times by simulating another image.
@@
     }
-  \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$.
+  \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated speckle defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$.
 In a), the upper/lower dot-dashed lines shows the resulting mean AUC when testing on a defected image before/after contamination respectively.
@@
 Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment.
-The salt defect has density $\pi_1 = 0.1$.
+The speckle defect has density $\pi_1 = 0.1$.
 The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.
@@
 Typically in the experiments, false positives were isolated single pixels and probably occurred due to random chance.
-Clusters of positive pixels should raise suspicion.
-One could create a binary image, assigning a Boolean value whether that pixel was tested positive or not.
+Clusters of positive pixels should raise suspicion so it would be a good idea to borrow strength from neighbouring pixels.
+For example, one could create a binary image, assigning a Boolean value whether that pixel was tested positive or not.
 A binary image filter, such as erode followed by a dilate, can be used to remove isolated positive pixels to emphasise the cluster of positive pixels.

### 2020-04-13 inference/defectsimulation/DefectExample.m

@@ -18,7 +18,6 @@ classdef DefectExample < Experiment
     
     nFilter = 4; %number of filters to be investigated
     filterArray; %cell array of filters
-    nRoc = 1000; %for roc function
     
     %z statistics (images)
     imageClean; %before contamination
@@ -128,19 +127,25 @@ classdef DefectExample < Experiment
       
       
       %plot ROC
+      %thin the rates to make vector figure
+      %it should be stairs rather than plot but accurracy is traded for quality of the figures 
+      thinningIndex = round(linspace(1, this.imageSize(1)*this.imageSize(2) + 2, 1000));
+      
       fig = LatexFigure.sub();
       for iFilter = 1:this.nFilter
-        plot(this.falsePositiveFilter(:,iFilter), this.truePositiveFilter(:,iFilter));
+        plot(this.falsePositiveFilter(thinningIndex,iFilter), ...
+            this.truePositiveFilter(thinningIndex,iFilter));
         hold on;
       end
-      plot(this.falsePositiveClean, this.truePositiveClean, 'k-.');
+      plot(this.falsePositiveClean(thinningIndex), this.truePositiveClean(thinningIndex), 'k-.');
       hold on;
-      plot(this.falsePositiveContaminated, this.truePositiveContaminated, 'k-.');
+      plot(this.falsePositiveContaminated(thinningIndex), ...
+          this.truePositiveContaminated(thinningIndex), 'k-.');
       plot([0,1],[0,1],'k:');
       xlabel('false positive rate');
       ylabel('true positive rate');
-      legend('empirical','mad mode','meadian iqr','mean var','Location','southeast');
-      saveas(fig,fullfile(directory, strcat(this.experimentName,'_roc.eps')),'epsc');
+      legend('empirical null','MADA-mode','meadian IQR','mean var','Location','southeast');
+      print(fig,fullfile(directory, strcat(this.experimentName,'_roc.eps')),'-depsc');
 
     end
     
@@ -155,8 +160,9 @@ classdef DefectExample < Experiment
       this.imageSize = imageSize;
       this.radius = radius;
       this.randStream = this.defectSimulator.randStream;
-      this.falsePositiveFilter = zeros(this.nRoc, this.nFilter);
-      this.truePositiveFilter = zeros(this.nRoc, this.nFilter);
+      nPoints = imageSize(1) * imageSize(2) + 1;
+      this.falsePositiveFilter = zeros(nPoints, this.nFilter);
[…]

### 2020-04-13 inference/nulliid/NullIidMixtureMadMode.m

@@ -1,23 +1,0 @@
-%MIT License
-%Copyright (c) 2019 Sherman Lo
-
-classdef NullIidMixtureMadMode < NullIidMixture
-
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@NullIidMixture(uint32(4284207830));
-    end
-    
-    function [nullMean, nullStd] = getNull(this, z)
-      empiricalNull = MadModeNull(z, 0, ...
-          this.randStream.randi([intmin('int32'),intmax('int32')],'int32'));
-      empiricalNull.estimateNull();
-      nullMean = empiricalNull.getNullMean();
-      nullStd = empiricalNull.getNullStd();
-    end
-    
-  end
-  
-end
-

### 2020-04-13 inference/nulliid/NullIidMixtureMedianIqr.m

@@ -1,21 +1,0 @@
-%MIT License
-%Copyright (c) 2019 Sherman Lo
-
-classdef NullIidMixtureMedianIqr < NullIidMixture
-
-  methods (Access = protected)
-    
-    function setup(this)
-      this.setup@NullIidMixture(uint32(1384381930));
-    end
-    
-    function [nullMean, nullStd] = getNull(this, z)
-      q = quantile(z, [0.25, 0.5, 0.75]);
-      nullMean = q(2);
-      nullStd = (q(3)-q(1))/1.349;
-    end
-    
-  end
-  
-end
-

### 2020-04-18 reports/thesis/chapters/5_inference.tex
Correction
Variance prediciton symbol y

@@
   {
-    \sqrt{s^2\left[\emph{aRTist}_{x,y}\right]}
-  }
-\end{equation}
-where $s^2\left[\emph{aRTist}_{x,y}\right]$ is the predicted grey value variance.
+    \sqrt{\widehat{y}\left[\emph{aRTist}_{x,y}\right]}
+  }
+\end{equation}
+where $\widehat{y}\left[\emph{aRTist}_{x,y}\right]$ is the predicted grey value variance.
 The test statistic was calculated for each pixel in the ROI, that is, pixels which represent the test sample.
@@
 The simulation $\emph{aRTist}_{x,y}$ is not random because this was obtained through a computer software.
-Given the 19 selected projections used for training the variance-mean model, the variance prediction $s^2\left[\emph{aRTist}_{x,y}\right]$ is not random because the variance-mean model was fitted before encountering the remaining projection to be compared with \emph{aRTist}.
+Given the 19 selected projections used for training the variance-mean model, the variance prediction $\widehat{y}\left[\emph{aRTist}_{x,y}\right]$ is not random because the variance-mean model was fitted before encountering the remaining projection to be compared with \emph{aRTist}.
 The variance-mean model can be made random if a different set of 19 projections was used to train the model each time this inference was conducted, but this shall not be considered here.
@@
 This was repeated 100 times by simulating the image again.
-The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1\,000 trapeziums.
+The AUC was obtained by integrating the ROC curve.
 The results of the uncontaminated defected image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.

### 2020-04-18 reports/thesis/book.tex
Corrections

@@
 {\Large Department of Statistics\par}
-{\Large September 2019\par}
+{\Large May 2020\par}
 \end{titlingpage}
@@
 Voids with diameters in the order of millimetres were detectable.
+
+This thesis is a contribution to real-time quality control in additive manufacturing.
 
@@
 This has been implemented in \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image}.
-A by-product is the empirical null mean, which is effectively the mode filter, which can be used to smooth images.
+A by-product is the empirical null mean, effectively the mode filter, which can be used to smooth images.
 
@@
 This results in voids appearing with less contrast in the projections, making it harder to detect.
-Different types of challenging defects could be investigated.
-For example, the orientation of cracks can affect the detectability of it \citep{wooldridge1997demonstrating}.
+Different types of challenging defects could be investigated, for example, the orientation of cracks can affect the detectability of it \citep{wooldridge1997demonstrating}.
 

### 2020-04-18 reports/thesis/chapters/3_compoundPoisson.tex
Corrections

@@
 The compound Poisson-gamma distribution was studied but it was found there were identifiability issues when fitting the model onto simulated data, in particular for high $\lambda$.
-It was found that the log-likelihood was quite flat because, by using numerous approximations, it was found that the determinant of the Hessian is zero.
+It was found that the log-likelihood was quite flat because, by using numerous approximations, it was found that the determinant of the Hessian is about zero.
 This cast doubts if a unique maximum likelihood estimator exists.

### 2020-04-18 reports/thesis/chapters/4_variancePrediction.tex
Corrections
CpEmAlgorithm does not plot estimated std
roc calculates area exactly
Recoded NullIid and included biweighted mean
Corrections

@@
 \begin{equation}
-    \overline{x}_{i}=\frac{1}{m}\sum_{j=1}^m x_{i,j}
+    x_{i}=\frac{1}{m}\sum_{j=1}^m x_{i,j}
 \end{equation}
@@
 
-It was unusual to see an infection in the sample variance-mean data in \texttt{AbsNoFilter} at \ang{120} which was not captured by the GLM.
+It was unusual to see an inflection in the sample variance-mean data in \texttt{AbsNoFilter} at \ang{120} which was not captured by the GLM.
 A good explanation was not found but perhaps the absence of an x-ray filter may have contributed to this.
@@
 There exist model selection methods such as lasso and elastic net \citep{tibshirani1996regression, zou2005regularization, friedman2010regularization} but they are catered for high dimensional problems involving hundreds of parameters.
-In this problem, only a few parameters were needed to find a good model.
+In this problem, only a few parameters were needed to find a good model thus forward stepwise selection was sufficient.
 More flexible models such as non-parametric and machine learning methods may be used, however, they are slow and are unnecessary in a low dimensional problem with a large number of data points.

### 2020-04-18 reports/thesis/chapters/5_inference.tex
Corrections

@@
 
-It is important to identity which quantites are random and which are not.
+It is important to identify which quantities are random and which are not.
 For high photon rates, it was shown in the previous chapters that the grey values in the projection can be modelled using a Normal distribution.
 Thus, $\text{projection}_{x,y}$ is a random quantity.
-The simulation $\emph{aRTist}_{x,y}$ is not random because this was obtained through a computer software.
+The simulation $\emph{aRTist}_{x,y}$ is not random because this was obtained through computer software.
 Given the 19 selected projections used for training the variance-mean model, the variance prediction $\widehat{y}\left[\emph{aRTist}_{x,y}\right]$ is not random because the variance-mean model was fitted before encountering the remaining projection to be compared with \emph{aRTist}.
@@
 
-It can be noted that this mode finding method can be aplied to other distributions in general.
+It can be noted that this mode finding method can be applied to other distributions in general.
 
@@
 A basic linear relationship was chosen to avoid overfitting and to keep the rule of thumb simple.
-It would also choose a large bandwidth for small $n$ which would improve the performance $\widehat{\mu}_0$ by working on a smoother density estimate for the price of a less optimal $s^2\left[\emph{aRTist}_{x,y}\right]$.
+It would also choose a large bandwidth for small $n$ which would improve the performance $\widehat{\mu}_0$ by working on a smoother density estimate for the price of a less optimal $\widehat{\sigma}_0$.
 
@@
 
-The empirical null mean is effectively the mode and the empirical null standard deivation is a measure of dispersion.
+The empirical null mean is effectively the mode and the empirical null standard deviation is a measure of dispersion.
 It was investigated how they compare with various estimates of central tendency and dispersion for varying sample sizes $n$.
@@
 The central tendency estimates looked at were the median, the mean and Tukey's biweighted mean \citep{beaton1974fitting}.
-In summary, the biweighted mean weigh each data point using a smooth function of its residual and ignores any data points with residuals greater than a certain value.
-\emph{MATLAB}'s \texttt{robustfit} function was used for the biweighted mean and selects any tuning parmaeters.
-
-The dispersion estimates looked at were the interquartile range (IQR) $\div 1.349$, the standard deviation and the median absolute deviation around the mode (MADA-mode) $\times 1.483$, .
+In summary, the biweighted mean weighs each data point using a smooth function of its residual and ignores any data points with residuals greater than a certain value.
+\emph{MATLAB}'s \texttt{robustfit} function was used for the biweighted mean and selects any tuning parameters.
+
+The dispersion estimates looked at were the interquartile range (IQR) $\div 1.349$, the standard deviation and the median absolute deviation around the mode (MADA-mode) $\times 1.483$.
 The normalisation constants were used so that MADA-mode and IQR can be compared directly to the standard deviation.
@@
 Further fine-tuning on the bandwidth would be required for the empirical null standard deviation to be unbiased.
-For example, it appeared there was consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
+For example, it appeared there was a consistent positive bias for all $r$ investigated, perhaps suggesting the bandwidth parameter $a$ should be decreased ever so slightly.
 The source of bias could come from the fact that the bandwidth was tuned to minimise the log squared error rather than the squared bias.
 
-It is interesting to compare the empirical null standard devaition with MADA-mode, in Figure \ref{fig:inference_NullIidStd}, because they both depend on the mode.
-The mode suffered from high variance with may affect dispersion estimators using the mode.
+It is interesting to compare the empirical null standard deviation with MADA-mode, in Figure \ref{fig:inference_NullIidStd}, because they both depend on the mode.
+The mode suffered from high variance which may affect dispersion estimators using the mode.
 The figure shows that MADA-mode has less variance than the empirical null standard deviation.
-This suggests that using the curvature of the density estimate at the mode is a main source of variance for the empirical null standard devation.
+This suggests that using the curvature of the density estimate at the mode is the main source of variance for the empirical null standard deviation.
 
@@
       \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullMean4.eps}
+        \caption{Median}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullMean3.eps}
-        \caption{Median}
-      \end{subfigure}
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullMean4.eps}
         \caption{Mean}
@@
       \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullStd4.eps}
+        \caption{IQR}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullStd3.eps}
-        \caption{IQR}
-      \end{subfigure}
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIid_nullStd4.eps}
         \caption{Standard deviation}
@@
       \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullMean4.eps}
+        \caption{Median}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullMean3.eps}
-        \caption{Median}
-      \end{subfigure}
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullMean4.eps}
         \caption{Mean}
@@
       \begin{subfigure}{\subSize}
+        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullStd4.eps}
+        \caption{IQR}
+      \end{subfigure}
+      \begin{subfigure}{\subSize}
         \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullStd3.eps}
-        \caption{IQR}
-      \end{subfigure}
-      \begin{subfigure}{\subSize}
-        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixture_nullStd4.eps}
         \caption{Standard deviation}

### 2020-04-23 reports/thesis/book.tex
typo

@@
 {\Large Department of Statistics\par}
-{\Large May 2020\par}
+{\Large April 2020\par}
 \end{titlingpage}
@@
 In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed.
-Sources of error were investigated and it was discuused how they were handled.
+Sources of error were investigated and it was discussed how they were handled.
 In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained.
@@
 A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt.
-This could be competitive with other converyor belt inspection methods, for example \cite{warnett2016towards}, by using less projections and hopefully less computational time.
+This could be competitive with other conveyor belt inspection methods, for example \cite{warnett2016towards}, by using fewer projections and hopefully less computational time.
 By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.

### 2020-04-23 reports/thesis/chapters/5_inference.tex
Final corrections

@@
 The mode suffered from high variance which may affect dispersion estimators using the mode.
-The figure shows that MADA-mode has less variance than the empirical null standard deviation.
-This suggests that using the curvature of the density estimate at the mode is the main source of variance for the empirical null standard deviation.
+The figure shows that MADA-mode had less variance than the empirical null standard deviation.
+This suggests that using the curvature of the density estimate at the mode was the main source of variance for the empirical null standard deviation.
 

### 2020-05-12 reports/paper1/paper.tex
Paper

@@
   {
-    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
+    \sqrt{{s}^2\left[\emph{aRTist}_{x,y}\right]}
   }
 \end{equation}
-where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.
-The variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{ma2012varaince, yang2010noise}.
+where ${s}^2\left[\emph{aRTist}_{x,y}\right]$ is the predicted grey value variance of pixel $(x,y)$ in the projection using \emph{aRTist} as a predictor.
+The variance model ${s}^2\left[\emph{aRTist}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{ma2012varaince, yang2010noise}.
 A gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} was used with an identity link.
